### 2017-03-31 paper/sexSelectionSpacing-ver1.tex
Version rejected by Demography and explanation in paper/ReadMe.md

% Revamped version for Demography focusing on method

% sex-selective Abortion
% Begun originally: 01/11/02
% Begun.: 2016-05-12
% Edited: 2016-11-07

\documentclass[12pt,letterpaper]{article}

\usepackage{mathpazo}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
\usepackage{xyling}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[pdftex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
\usepackage{xfrac}

% \bibpunct{(}{)}{;}{a}{}{,}
\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
\newcommand{\X}{$\times$ }
\newcommand{\hs}{\hspace{15pt}}

% Attempt to squeeze more floats in
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

%------------------------------------------------------------------------

% Fertility, Birth Spacing and the Determinants of sex-selective Abortions
% Understanding Sex Selection: Fertility, Abortions and Birth Spacing
% The Determinants of sex-selective Abortions: A New Method/Approach
% Sex Selection: A New Method for Estimating Determinants
% Fertility, Birth Spacing and Abortions in India
% Fertility, Birth Spacing and Sex Selection
% Fertility, Birth Spacing and sex-selective Abortions
% Fertility, Spacing and Sex Selection
% Fertility, Sex Selection, and Spacing
% Fertility, Sex Selection, and Birth Spacing
% Fertility, Birth Spacing and Missing Girls
% Where have all the girls gone: An analysis of sex-selective abortions

\title{Sex-Selective Abortions, Fertility, and Birth Spacing
% \protect\thanks{%
% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
% I owe thanks to three anonymous referees, Shelly Lundberg, Daniel Rees, David Ribar, 
% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
% University of Washington, University of \AA{}rhus, the Fourth 
% Annual Conference on Population, Reproductive Health, 
% and Economic Development, and the Economic Demography Workshop for helpful suggestions and comments.
% I would also like to thank Nalina Varanasi for research assistance.
% Support from the University of Washington Royalty Research Fund and the 
% Development Research Group of the World Bank is gratefully acknowledged.
% The views and findings expressed here are those of the author and
% should not be attributed to the World Bank or any of its member countries.
% Partial support for this research came from a Eunice Kennedy Shriver National
% Institute of Child Health and Human Development research infrastructure grant,
% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
% University of Washington.
% Prior versions of this paper were presented under the title ``The 
% Determinants of sex-selective Abortions.''
% }
}

\author{}

\author{Claus C P\"ortner\\
    Department of Economics\\
    Albers School of Business and Economics\\
    Seattle University, P.O. Box 222000\\
    Seattle, WA 98122\\
    \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
    \& \\
    Center for Studies in Demography and Ecology \\
    University of Washington\\ \vspace{2cm}
    }

\date{April 2017}

%------------------------------------------------------------------------

\begin{document}
\graphicspath{{graphs/},{figures/}}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}

% \setcounter{page}{-1}
% \maketitle
% \thispagestyle{empty}
% 
% % \setcounter{page}{0}
% \newpage
% 
% \doublespacing
% % \onehalfspacing
% 
% 
% % \thispagestyle{empty}

\maketitle
\thispagestyle{empty}

% \newpage
\doublespacing

\begin{abstract}

% Demography abstract
\noindent This paper addresses two main questions:
what is the relationship between fertility and sex selection 
and
how does birth spacing interact with the use of sex-selective abortions? 
I introduce a statistical method that incorporates how sex-selective abortions 
affect both the likelihood of a son and spacing between births.
Using India's National Family and Health Surveys,
I show that falling fertility intensifies use of sex selection, leading to use at 
lower parities, and longer spacing after a daughter is born.
Women with 8 or more years of education, both in urban and rural areas, are the main users 
of sex-selective abortions and have the lowest fertility.
Women with less education have substantially higher fertility and do not appear to use 
sex selection.
Predicted lifetime fertility for high-education women declined more than 10\% 
between 1985--1994, when sex selection was legal, and 1995--2006, when sex selection was illegal.
Fertility is now around replacement level.
Abortions per woman increased almost 20\% for urban women and 50\%
for rural women between the two periods, suggesting that making sex selection illegal has 
not reversed its use.
Finally, sex selection appears to be used to ensure one son rather than multiple sons.

\noindent JEL: J1, O12, I1
\noindent Keywords: India, prenatal sex determination, censoring, competing risk
\end{abstract}

\newpage

%------------------------------------------------------------------------

\section{Introduction\label{sec:intro}}

% India's male to female ratio increased almost continuously during the last century, 
% mainly because of excess mortality of girls \citep{murthi95,dyson01}.

The males-to-females ratio at birth increased dramatically over the last three 
decades in India as access to prenatal sex determination expanded.%
\footnote{
See \citet{das_gupta97}, \citet{Sudha1999},
\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
India is not alone; both China and South Korea saw
significant changes in the sex ratio at birth \citep{Yi1993,park95}.
}
Our understanding of the use of sex selection is, however, constrained by 
lack of information;
there are no official data on sex selection, and the few surveys that ask about use of 
sex selection show signs of serious under-reporting \citep{goodkind96}.
With no direct information, researchers have relied on a simple method for establishing 
factors that affect sex selection: use the sex of children born as the 
dependent variable, and estimate the effects of variables on the probability of having a son.%
\footnote{
In the absence of any interventions, the probability of having a son
is approximately 0.512, which is independent of genetic factors \citep{ben-porath76b,jacobsen99}.
With fetus sex random, a statistically significant variable indicates an association with 
use of sex-selective abortions.
Examples of studies that have used this approach are \cite{retherford03b},
\cite{jha06}, and \cite{abrevaya09}. 
% Poor nutritional and health status of women may lead to 
% relatively more girls being born, probably as an evolutionary
% response to maximise reproductive success \citep{trivers73,wells00}.
% Empirical evidence from Ethiopia and from cross-country data supports
% this hypothesis \citep{klasen02,gibson03}.
% % , although acute under-nutrition may not have this effect \citep{stein04}.
% See also the discussion for India in \citet{bhaskar07}.
}
Based on this simple method, we know that families with no sons are more likely to
use sex selection the higher the parity;
that use of sex selection increases with socioeconomic status, especially education;
and that sex selection is more widespread in cities than in rural areas 
\citep{retherford03b,jha06,abrevaya09}.%
\footnote{
There is substantial disagreement on whether sex-selective abortion is used for the 
first birth \citep{retherford03b,jha06}.
}

I address two important questions that the prior literature has been unable
to examine because of the simple method's limitations.
First, what is the relationship between fertility decisions and use of sex selection?
Second, how does birth spacing interact with use of sex-selective abortions?
I introduce a novel method that directly incorporates that sex-selective 
abortions affect both the likelihood of a son being born \emph{and} the duration between 
births.
I use the method to argue that differences in fertility over time and between groups
explain a substantial portion of the changes in the use of sex selection in 
India, and to show how spacing between births play an important role in our understanding 
of fertility and sex selection decisions.

We already know that fertility and son preference are related from the substantial literature
on fertility stopping behavior before sex selection was available.
This literature shows that families are more likely to stop childbearing after the 
birth of a son than after the birth of a daughter
\cite[see, for example,][]{Das1987,Arnold1997,clark00}.%
\footnote{
\citet{filmer09} analyse the relationship between the sex composition of previous
children and subsequent fertility behavior using data from 64 countries.
}
It is also easy to see how declining fertility may increase use of sex selection.
Take a family that wants one son.
If the family is willing to have up to 4 children, the probability of having a son
is more than 94 percent, even without sex selection, and that increases to almost 99 
percent if the family is willing to have up to 6 children.%
\footnote{
The probability of not having a son are 48.8 percent for one child, 23.8 percent for
two children, 11.6 percent for 3 children, 5.7 percent for 4 children, 2.8 percent
for 5 children, and 1.4 percent for 6 children.
}
% If the family is willing to have up to six children, the probability of having a son
% is more than 99 percent, even without sex selection.
If the desire is instead for one son \emph{and} a maximum of two children, there 
is a 24 percent chance that the family will have to resort to sex selection to achieve 
both targets.
% Working in the opposite direction, the stated preference for sons appears to decline with 
% lower fertility \citep{das_gupta97,bhat03}.
Despite these opposite targets, there is little empirical analysis of 
the effects of fertility on sex selection using individual level data 
\citep{park95,Ebenstein2011}.%
\footnote{
\citet{Dharmalingam2014} examine how state level fertility in India
relates to desired family size and son preference over time, but does 
not look at how fertility preferences shape the decision on sex-selective 
abortions.
At country level \citet{Bongaarts2013} shows how sex ratios at births are 
only elevated for countries with lower fertility and
\citet{Bongaarts2015} use national level estimates of the relationship
between sex ratio at birth and fertility as part of their
prediction of the number of missing women past and present.
Simulations suggest that in Korea introduction of sex selection
changed family size little, but did result in abortions
of female fetuses equal to about 5 percent of actual female
births \citep{park95}.
For China allowing a three-child policy has been predicted to 
increase the fertility rate by 35 percent, but also reduce the
number of girls aborted by 56 percent \citep{Ebenstein2011}.
}

% Not only can a decline in desired fertility increase the use of sex selection, 
% increasing the availability of prenatal sex determination also allows a 
% woman to reach a desired number of sons with fewer births.
% To fully understand the use of sex selection we therefore need
% to understand both its use by parity \emph{and} by the fertility decision.
% This is especially important if lower fertility is the driver of the
% increased use of sex selection.

% The use of sex-selective abortions may increase over time for a number of different reasons.
% 1. preferences can change to make people desire boys more than before
% 2. the return to girls can fall further 
% 3. desired fertility can fall (even if nothing else changes)
% 3. the cost of sex-selective abortions can fall, which increases its use even though
% there are no other changes.

% [literature on birth spacing - why spacing is important]

Closely related to the overall fertility decisions are decisions on  spacing between births.
In the absence of sex-selective abortions, son preference often leads to a shorter duration 
until the next birth if the previous birth was a daughter  
\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
The resulting shorter spacing is thought to be associated with worse health outcomes for
the girls \citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.

What has not previously been appreciated is that the introduction of sex-selective 
abortions substantially changed the relationship between son preference and birth spacing.
The change happens because each abortion significantly increases the duration until the
next birth.
The increase in duration can be divided into three parts starting from the time of
the abortion.
First, the uterus needs at least two menstrual cycles to recover 
before conception, because a less than three months space 
between abortion and conception substantially increases the likelihood 
of a spontaneous abortion \citep{zhou00b}.
Secondly, the average expected time to conception is about 6 months.
Finally, sex determination tests are generally reliable only from 3 months of gestation onwards.
The result is that each abortion delays the next birth by approximately a year.%
\footnote{
There are three well-developed technologies for determining a fetus' sex: 
Chorionic villus sampling (CVS), amniocentesis, and ultrasound.
CVS can be applied after the shortest period
of gestation (8 to 12 weeks).
It is the most complicated, but also the most reliable, and an abortion can be done in 
the first trimester.
Amniocentesis can be performed after fourteen weeks, but requires three to four weeks
before the result is available, so an abortion cannot be performed until more than 
halfway through the second trimester.
Ultrasound has the advantages of being non-invasive and relatively cheap but 
is associated with higher risk of faulty sex determination if done early.
Generally, a fetus' sex can be determined in the third month of gestation if it is a
boy and the fourth month if it a girl.

The waiting time to conception does vary by woman, but
even if it is very short, say one  month, the minimum additional space between
births would be 6 months per abortion.
For a discussion of time to conception see \citep{Wang2003}
}

% [why this matters]
How spacing interacts with sex selection is important for two reasons.
First, 
spacing, by itself, can no longer be used to predict son preference. 
Because each abortions extends spacing by about a year, we now have a situation 
where the \emph{longest} spacing is likely observed for families with the 
strongest son preference.
To further complicate matters, 
we may still observe short spacing after the birth of daughter as a representation 
of son preference for families who either have less access to sex-selective 
abortions or are willing to have more children.
Spacing is still important and useful in understanding sex selection and son
preference, but only if combined with the outcome of that spacing---in other words 
the likelihood of observing a boy or a girl.

% using spacing itself to predict son preference becomes useless if
% families have low desired fertility and access to sex-selective abortions!!!!
Second,
families may reverse their decision to use sex selection in-between births.
A reversal could happen if they do not want the space between children to be 
``too long'', or if there are concerns about possible infertility as a result of 
too many abortions in a row without a birth.
Hence, for a given parity, the sample of women for whom we do observe a birth 
may behave differently from the sample of women who have not yet had a birth.
This is a problem because births to women with shorter spacing are more likely 
to be in the survey for a given parity.
Hence, if decisions on sex selection change with duration since last birth,
the predicted sex ratio for a parity using the simple method will be a 
biased estimate of the final observed sex ratio for the parity when 
childbearing is complete.

% [contribution of paper]
The main contribution of this paper is the introduction and application of a method that 
incorporates the decisions about fertility, birth spacing, and sex-selective abortions.
The method allows us to better understand the relationship between these three decisions.
% The method allows us to better understand the relationship between sex-selective abortions, 
% fertility, and birth spacing.
The empirical model is a competing risk, non-proportional hazard model with two exit 
states: either a boy or a girl is born.
This approach has three major advantages over the simple method.
First and foremost, it models fertility and spacing decisions jointly with the birth 
outcome, which makes it possible to better understand how changing fertility decisions
affects the use of sex selection.
Secondly, by explicitly incorporating censoring of birth spacing, it addresses any 
potential bias from ignoring how sex selection decisions may change with duration from 
the previous birth.
Finally, the method allows us to predict completed fertility, total number of abortions, 
and final sex ratio over a woman's reproductive life cycle.
These provide a better way of measuring changes in the use of sex selection 
than what we can get from individual parities---especially because individual 
parities may show a decline in sex selection at the same time as overall
use is increasing.
None of these is possible using the simple method.

% [EXPLAIN RESULTS HERE]
% Main findings!
I apply the method to birth histories from India's National Family and Health Surveys 
for Hindu women covering the period 1972 to 2006. 
There are three main findings.
First, fertility is an important factor in the decision to use sex-selective 
abortions.
On the one hand, women with fewer than 8 years of education have relatively high fertility 
and do not appear to use sex selection.
On the other hand, better-educated women in both urban and rural areas have much lower
fertility and are the main users of sex-selective abortions.
For women with 8 or more years of education and only daughters the 
use is substantial: around 60 percent of the children born are boys.
Furthermore, as better-educated women's fertility has declined over time, sex selection 
occurs for earlier and earlier parities and has correspondingly increased in intensity.
There is, however, still no evidence of sex selection being used on the first birth.

Secondly, sex selection appears to be used for securing one son, rather than a large 
number of sons.
There is only limited use of sex-selective abortions for better-educated
women with one or more sons.
The exception is rural women with one son and one daughter, presumably to compensate for 
the higher child mortality in rural areas.
These results are in line with the differential stopping behavior observed in many studies
before sex selection became available \citep{repetto72,arnold98,dreze01}.

Finally, 
the legal steps taken to combat sex-selective abortions have not been able 
to reverse its use.
In 1994, the Central Government passed the Prenatal Diagnostic Techniques (PNDT) Act 
making determining and communicating the sex of a fetus illegal.%
\footnote{
Abortion has been legal in India since 1971 and still is.
The Act is described in detail at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
The number of convictions has been low.
It took until January 2008 for the first state, Haryana, to reach 5 convictions.
Hence, private clinics operate with little risk of legal action \citep{Sudha1999}.
Maharashtra was the first state to pass a similar law in 1988.
}
In the period 1985-1994 the predicted total number of abortions per 100 women by the 
end of childbearing was 8 for urban women and 6.8 for rural women.
As completed fertility for high-education women fell to now 
around 2 in urban areas and 2.6 in rural areas, 
the number of sex-selective abortions 100 women are predicted to have 
during their childbearing years has increased to 9.4 for urban women and 
10.5 for rural women.
In other words, close to one in ten well-educated women will now have at least 
one abortion motivated by sex selection during their childbearing.
Hence, although it is possible that the PDNT Act slowed the increase in use 
of sex selection, the total predicted number of abortions per woman continued 
to increase after the law was enacted.
The end result is a sex ratio across all children of 53.7\% boys for well-educated 
urban women and 53.4\% for well-educated rural women.

% This is a substantial increase in sex-selective abortions compared to
% the period before the practice was made illegal nationwide in India in 1994.

\section{Theory\label{sec:model}}

The model I present here serves three purposes.
First, it allows me to illustrate how fertility, sex selection, and birth 
spacing interact when changing the cost of children and access to sex selection.
Second, I show that there are cases where parents reconsider their decision to 
use sex selection between births, which underscores why 
using only observed births may provide a biased view of how much
sex selection takes place and what the final sex ratio will be.
Finally, the model informs the empirical strategy presented below.

In the model, parents decide on fertility sequentially,
given the number of boys and girls they already have.
Parents fully control fertility in each period and the only
source of uncertainty is whether they conceive a boy or a girl.
This means that spacing between births arise only from 
the use of sex selection.%
\footnote{
A more realistic approach would have parents choose how 
``intensive'' they want to use contraceptives, where the
intensiveness translates into a stochastic conception process,
so that parents do not directly control the timing of births 
but rather the probability of having a birth in a given period.
The added complexity would, however, not add anything substantial 
to help answer the main question of what the relationship between fertility 
and sex selection is, and would detract from the main source of uncertainty,
which is whether the couple will conceive a male or female fetus.
Assuming that parents fully control fertility is relatively common 
in the economics literature on dynamic models of fertility, such as
\citet{Happel1984}, \citet{wolpin84}, \citet{rosenzweig85}.
The empirical approach does allow for stochastic occurrence of births
through the use of a hazard model.

See \citet{Leung1991} for a model that incorporates both stochastic 
births based on a chosen level of contraception and differential 
preferences for boys and girls.
The model does not, however, allow for abortions and it does
not appear possible to extend the model to incorporate abortions
and still solve it an similar manner.
}
This is obviously a simplification and since the interaction
between son preference and spacing is at the core of this paper,
I first discuss factors that may affect spacing between birth.%
\footnote{
It is possible that parents care directly about the
length of spacing between births, but 
spacing outcomes are more likely the results of parents weighing many
factors against each other.
}

One factor that might impact desired spacing is health.
As discussed above, shorter spacing after the birth of a girl is 
associated with worse health outcomes for both mother and children.%
\footnote{
\citet{wolpin84} and \citet{Newman1988} present dynamic models 
where both births and deaths are stochastic, but the likelihood of
a child dying is independent of the length of spacing to
the prior birth.
}
Because of the potential health effects, most of the literature on spacing 
for countries like India naturally focus on whether spacing is too short.

With the introduction of sex-selective abortions, ``too long'' spacing 
may, however, become a greater concern for parents, as 
repeated abortions can result in very long durations between births.%
\footnote{
Shorter spacing was probably less of a concern to begin with for
better educated mothers---who are also the most likely to use 
sex selection---since their children are substantially less likely 
to be negatively affected by short spacing than children of less 
educated mothers \citep{Whitworth2002}.
In general, mortality risk is negatively related to maternal
education \citep[for India, see, for example,][]{Tulasidhar1993},
although the underlying mechanism is subject
to debate \citep{Kovsted2002}.
}
If ``too long'' spacing leads parents to reverse their decision to use
prenatal sex determination within a spell this has important implications 
for the empirical method.
A reversal may happen, for example, if parents have concerns about possible 
infertility from repeated abortions.
Furthermore, with the increasing education and wealth in India, a growing 
portion of the population is likely to behave in a manner that makes the 
literature on shorter spacing in middle- and high-income countries more relevant.%
\footnote{
For the first birth, a potentially important factor in India is 
the pressure to show fecundity, which would tend to shorten
the duration to the first birth \citep{dyson83,Sethuraman2007,Dommaraju2009}.
}
There may, for example, be economies of scale in childrearing---both
in terms of time cost and direct cost---that are easier to
take advantage of if births are closer \citep[p 947]{Newman1984}.
Similarly, if women's wages increase with age parents prefer
to have their children early and close together while 
the opportunity cost of children is lower \citep{Heckman1976}.%
\footnote{
The time needed to care for young children can also impact 
timing if skills depreciate when out of the labor market \citep{Happel1984}.
Whether depreciation leads to longer or shorter spacing depends
on the specification of the depreciation function.
See also the discussion in \citet[p 315]{Hotz1997}
and references therein.
}
% %
% \footnote{
% As \citet{Heckman1976} show an increasing
% income stream can also lead to longer spacing.
% If children are costly in each period, as in the
% model presented here, parent may use contraception to wait for
% sufficiently higher income before having the next child.
% Notice, that we would expect both the income and the
% cost of children to increase as women's education goes up and
% it is likely that the cost of children increases faster
% than income.
% }

Finally, increased reliability of access and effectiveness of
contraceptive can lead to shorter spacing between births 
\citep{Keyfitz1971,Heckman1976}.
With less reliable contraception parents choose a higher level of 
contraception---resulting in longer spacing---to avoid having 
too many children by accident.
But, as contraception becomes more effective parents can more
easily avoid future births, allowing them to reduce the spacing 
between births without having to worry about overshooting their 
preferred number of children.
This idea may also help explain shorter spacing for better 
educated women than for less educated women, provided that   
knowledge and ability to use contraception differ
across education groups \citep{Tulasidhar1993,Whitworth2002}.

% "Solving" the model

Instead of trying to model each of the factors that may affect
spacing I instead set up a dynamic model with a discount rate.
Parents maximize utility over a finite time horizon $T$
\begin{equation}
\max E \sum_{t=0}^T d^t [ 
u(c_t) + \alpha u^b(b_t) + (1-\alpha) u^g(g_t) 
],
\label{eq:utility_1}
\end{equation}
where $E$ is the expectation operator,
$c_t$ consumption in period $t$, 
$b_t$ the stock of boys in period $t$,
$g_t$ the stock of girls in period $t$, and
$d$ the discount rate.
For ease of analysis I assume that utility in each period is separable in 
parental consumption, boys, and girls.
I define son preference, $\alpha$, as higher marginal utility of next child 
being a boy if parents have an equal number, possibly zero, of boys and girls.
The utility function covers a variety of different preferences 
from equal utility of boys and girls ($\alpha = 0.5$ provided
$u^b(\cdot) = u^g(\cdot)$) to an extreme 
son preference where there is no utility of having a daughter 
($\alpha = 1$).%
\footnote{
Other ways of defining son preference, such as wanting at least one son 
and not caring about sex composition after that, are possible but 
will be explored here.
The basic results remain as long as there is different
utility of sons and daughters for at least some sex compositions.
}
The lower $d$ is the more parents prefer immediate utility relative
to future utility.
Hence, the discount factor is a convenient way to capture how patient parents 
are and therefore how willing parents are to wait through multiple abortions 
to ensure a son.

At the beginning of each period parents have 3 possible choices:
no pregnancy, a pregnancy without a prenatal sex determination scan,
or a pregnancy with a prenantal sex determination scan followed by an
abortion if the fetus is female.
The probability of conceiving a boy is $\pi$, which is
the same for all parents and in all periods.
There is no child mortality, so both
$b$ and $g$ are non-decreasing over time.

If a child is born parents incur a cost $p_k$ for
that child in the period of birth and all subsequent periods
until the end of the time horizon.%
\footnote{
Clearly boys and girls may carry different costs, but since 
the model already assumes that
parents have different preferences over boys and
girls there is no reason to further complicate the model.
Similarly, the cost of maintaining a child likely depend on 
its age, but incorporating that would add little to 
the conclusions.
}
If parents select a pregnancy with prenatal sex determination
they pay $p_s$ and also $p_k$ if the fetus is a son
and therefore carried to term.
For two reasons the prenatal sex determination scan is best thought of as
a bundled service that includes both the prenatal sex determination scan 
\emph{and} the abortion if the fetus is female.
First, it is more tractable than including additional steps in
the decision process, especially since the only motivation for
a prenatal scan in the model is sex selection, and a scan would
therefore be ``wasted'' unless a female fetus was aborted.
Second, I argue in the online Appendix that both parents and providers 
may prefer a bundled service, where there is an upfront cost and the service 
includes both the prenatal screening and the abortion---if needed---from the 
same provider.
The budget constraint for each period is then
\begin{equation}
I_t = c_t + p_k(b_t + g_t) + p_s s,
\end{equation}
where $I_t$ is income in period $t$
and
$s$ is an indicator variable for whether the 
parents purchased prenatal sex determination.%
\footnote{
This assumes that there is no saving or borrowing
across periods.
This is a common assumption in this type of model.
See, for example, 
\citet{Heckman1976},
\citet{wolpin84},
\citet{rosenzweig85},
\citet{Newman1988},
and
\citet{Leung1991}.
That there are only two stock variables, the number
of boys and the number of girls, greatly simplifies the analysis.
}

This maximization problem can be solved using dynamic programming, 
but because the choice variable and the state variables (number of
boys and girls) are discrete a closed-form solution
is generally not available.
% There are two discrete state variables (boys and girls) and one
% choice variable with three potential choices (no pregnancy, pregnancy without prenatal sex 
% determination, and pregnancy with prenatal sex determination).
% Combined with the finite time horizon a problem of this type is especially suited for
% simulation and the model is simulated using backward induction.
This means that simulation is the best way to analyze the model,
but before turning to simulations it is worthwhile illustrating
how the model works.
I begin with the possible utility outcomes in period $T$, the last period 
in which parents make decisions on fertility.
If parents decide on ``no pregnancy'' their utility in the final period will be
\begin{equation}
U_T^N =
u(I - p_k(b_{T-1} + g_{T-1})) + \alpha u^b(b_{T-1}) + (1 - \alpha) u^g(g_{T-1}).
\end{equation}
If they instead decide to have a pregnancy without a prenatal scan 
their expected utility will be 
\begin{multline}
U_T^B = 
\pi [ 
u(I - p_k(b_{T-1} + g_{T-1} + 1)) + \alpha u^b(b_{T-1}+1) + (1-\alpha) u^g(g_{T-1}) 
]
+\\
(1-\pi) [ 
u(I - p_k(b_{T-1} + g_{T-1} + 1)) + \alpha u^b(b_{T-1}) + (1-\alpha) u^g(g_{T-1}+1) 
].
\end{multline}
Finally, if they decide to use prenatal sex determination their
expected utility will be
\begin{multline}
U_T^S = 
\pi [ 
u(I - p_k(b_{T-1} + g_{T-1} + 1) - p_s) + \alpha u^b(b_{T-1}+1) + (1-\alpha) u^g(g_{T-1}) 
]
+ \\
(1-\pi) [ 
u(I - p_k(b_{T-1} + g_{T-1}) - p_s) + \alpha u^b(b_{T-1}) + (1-\alpha) u^g(g_{T-1}) 
],
\end{multline}
since parents incur the cost of the scan, $p_s$, whether they conceive
a male or a female fetus, but will not incur any additional childrearing costs
if a girl is conceived.

To illustrate how the decision process works, consider
the decision in the final period on whether to use sex selection or not
(assuming that both are superior to no birth).
Parents choose a pregnancy without prenatal sex determination
if $U_T^B > U_T^S$, which leads to
\begin{multline} \label{eq:last_simple}
(1-\pi)(1-\alpha) [ u^g(g_{T-1}+1) - u^g(g_{T-1}) ]
> \\
\pi u(I - p_k(b_{T-1} + g_{T-1} + 1) - p_s) 
+ (1-\pi) u(I - p_k(b_{T-1} + g_{T-1}) - p_s) \\
- u(I - p_k(b_{T-1} + g_{T-1}+1)).
\end{multline}
% This can also be written as
% \begin{multline} \label{eq:last_full}
% (1-\pi)(1-\alpha) [ u^g(g_{T-1}+1) - u^g(g_{T-1}) ]
% > \\
% \pi [u(I - p_k(b_{T-1} + g_{T-1} + 1) - p_s) - u(I - p_k(b_{T-1} + g_{T-1}+1))] \\
% + (1-\pi) [ u(I - p_k(b_{T-1} + g_{T-1}) - p_s) - u(I - p_k(b_{T-1} + g_{T-1}+1))].
% \end{multline}
Hence, parents choose a pregnancy without prenatal scan over
a pregnancy with a prenatal scan in the final period if
the additional utility of having an extra girl (the left-hand-side),
weighted by the probability of having a girl and the weight parents
assign to utility from having girls, is larger than the expected impact on
utility from consumption (the right-hand side), where
the first two terms are the expected utility from consumption if 
using prenatal sex determination and the last term is utility from
consumption if parents simply have a birth.%
\footnote{
Notice that the marginal utility of having a boy does not enter
into the decision on whether to use prenatal sex determination or not
(except through the value of $\alpha$).
Only the marginal utility of having another girl
and the total number of children, which affects the trade-off between
consumption and use of sex selection, matters.
This is an artifact of the separability between consumption, number of
boys, and number of girls in the utility function.
}
% With some abuse of language I will call this difference the 
% marginal utility of a child, in this case a girl.

If a son is conceived the money for a prenatal scan are ``wasted,''
which means that the utility from consumption if they use prenatal scan
and conceive a boy is alway going to be lower than utility from consumption 
if the parents had a birth without a prenatal scan.
Hence, assuming that the marginal utility of girls is always positive,
but declining in the number of girls they have, parents will pick
a birth with scan over a birth without scan only if the difference between
utility from consumption when using prenatal scan and conceiving a girl
is sufficiently higher than the utility of consumption if the parents
simply had a child without a scan.
It follows that the higher the cost of the prenatal scan is relatively
to the cost of maintaining a child the less likely it is that parents will 
use sex selection.
Furthermore, if the cost of a prenatal scan, 
$p_s$, is larger than the cost of maintaining a child in one period, $p_k$, 
parents will never select a prenantal scan in the final period.
This result holds, however, only because this is the last period. 
The earlier the decision on sex selection is made in the time horizon
the lower the cost of prenatal sex determination is going to be 
relative to the cost of maintaining the child until the end of the time
horizon.

Finally, increasing the cost of children, $p_k$---as would happen 
with higher education of mothers---increases the likelihood that sex 
selection will be used at a given number of children.%
\footnote{
Higher education likely also increases household income, which
makes it \emph{less} likely parents will choose a birth with prenantal 
scan over a birth without a prenatal scan.
Higher income means lower marginal utility from consumption, which makes the 
whole right-hand side move toward zero.
For a given number of girls, this makes it more likely 
that the utility from an additional girl is sufficiently high that parents 
will simply have a birth.
Empirically, increasing education of mothers is, however, strongly associated 
with lower fertility, which indicates that 
the negative effect of higher opportunity cost more than outweighing 
the positive effect of higher income \citep{schultz97}.
}
There are two reasons for this.
First,  when the cost per child goes up the given number of children 
translates into less income per period available for consumption.
Second, the decline in consumption from having an additional
child becomes larger.
These combine to increase the marginal utility of consumption and thereby 
make it more attractive to have a prenatal scan.

% % Theory on whether reversal of use
% A question of interest is when parents would pick
% a scan in one period and no scan in the following period.
% For this to happen parents must choose scan, conceive a girl, and then
% have a birth without a scan.
% The available choices in the second to last period are the same as in the last
% period: no birth, pregnancy without a scan, and a pregnancy with a scan.
% Let $V_T(B)$ be the expected utility of the optimal choice in the last
% period if the outcome of the choice in period $T-1$ is a boy.
% Similarly, $V_T(G)$ and $V_T(N)$ are the expected utilities from
% having a girl and no birth in period $T-1$.
% In period $T-1$ parents will choose to have a pregnancy without a scan
% over a pregnancy with a scan if
% \begin{multline}
% (1-\pi)(1-\alpha) [ u^g(g_{T-2}+1) - u^g(g_{T-2}) ] 
% > \\
% \pi u(I - p_k(b_{T-2} + g_{T-2} + 1) - p_s) \\
% + (1-\pi) [ u(I - p_k(b_{T-2} + g_{T-2}) - p_s) + d( V_T(N)- V_T(G))] \\
% - u(I - p_k(b_{T-2} + g_{T-2} + 1)).
% \end{multline}
% As before the left-hand side is the marginal utility of
% an additional daughter, but the right-hand side now also 
% incorporates the discounted value of the difference between expected utility 
% in the last period if no children are born in $T-1$ and expected utility in 
% the last period if a girl is born in $T-1$.
% 
% For parents to change their decision on abortion it must be
% the case that the right-hand side for $T-1$ is larger than 
% the left-hand side \emph{and} the left-hand side need to 
% be larger than the right-hand side without the discounted value
% of the difference in expected utility.
% Note that the left-hand side remains the same because with
% a scan no girls are born and the parents therefore enter the
% last period with the same number of girls as they exited
% period $T-2$.%
% \footnote{
% This would not be the case if utility was not separable between
% boys and girls.
% }
% This, in turn, requires that $V_T(N) - V_T(G)$ is positive.
% Identifying when this holds becomes complicated and the
% level of complication increases as we move towards to the
% beginning of the time horizon.

% [Simulation of model]
Although it is possible to examine how decisions are made in the last period,
the absence of closed-form solutions means that I cannot directly 
examine important questions such as whether parents will reverse their
use of sex selection between births.
I therefore now turn to simulation of the model for different parameters.
Appendix Tables \ref{tab:simul_fertility_100}-\ref{tab:simul_fertility_85} 
show the simulation results for average  fertility and the ratio of boys to births for 
selected values of son preference ($\alpha$), cost of prenatal sex determination ($p_s$) 
and cost of children ($k$).
Appendix Tables \ref{tab:simul_abortion_100}-\ref{tab:simul_abortion_85}
show the corresponding simulation results for number of abortions per 100 women, 
average number of spells where prenatal scan has been used, 
and the percent of spells where the choice is initially
pregnancy \emph{with} a prenatal scan but the birth is from a pregnancy \emph{without}
a prenatal scan.
The latter captures the likelihood of changing the decision to use sex selection
between births and I cover that separately below.
Appendix Tables \ref{tab:simul_spacing_r100_a05}-\ref{tab:simul_spacing_r100_a065}
show the average and maximum spacing between births by parity.

The specification and parameter values are chosen to illustrate
the effects of changing parameters, rather than to provide
a realistic set of outcomes.
The utility function used for the simulations is%
\footnote{
See \citet{leung94} for a discussion of potential utility
functions with different preferences for sons and daughters.
}
\[
U = 0.27\frac{(c-30)^{0.5}}{0.5} + \alpha \frac{b^{0.75}}{0.75} + (1-\alpha) \frac{g^{0.75}}{0.75}.
\]
The simulations presented in the tables assume 15 periods, a period income of 
$I = 200$, and that the probability of a son is 0.5.
The four parameters and their examined values are the cost of 
children ($k \in 12, 14, 16, 18, 20, 22$), 
cost of prenatal sex determination ($p \in 12, 16, 20, 24,  200$)---where 
the last value is equivalent to no prenatal sex determination available,
the degree of son preference ($\alpha \in 0.5, 0.55, 0.6, 0.65$),
and the discount rate ($d \in 0.85, 0,9, 0.95, 1.0$).
The optimal choice sets are applied to a sample of 50,000 ``individuals'', each 
with 15 ``potential'' children, whose sex comes from a binomial distribution 
with the probability above.%
\footnote{
I also ran simulations on an expanded set of parameter values.
I use these results for regression analysis of the effect of parameters.
These are available upon request.
}

In the absence of prenatal sex determination, stronger son preference is often thought 
to increase overall fertility.
That is not the case here.
In fact, there is little correlation between the weight placed on utility from boys and 
fertility.%
\footnote{
This is confirmed by regressing the weight places on sons, cost of children,
and discount factor against fertility for the expanded set of values.
}
Similarly, parents' discount factor has no impact on fertility in the absence of
prenatal sex determination.
The one factor that does affect fertility is the cost of children;
increasing the cost of children substantially reduces fertility.

% Access / cost of prenatal sex determination

Introducing prenatal sex determination has two opposing effects on fertility 
in the model.
On one hand, it takes fewer births to reach a desired number of sons and this 
reduces fertility.
On the other hand, parents no longer have to pay for unwanted children and 
this ``wealth effect'' increases fertility.
% The simulations show a small negative effect of lowering the cost of
% sex selection holding the other parameters constant.
The simulations show that for most combinations of son preference and 
cost of children cutting the cost of abortion has little effect 
on fertility---even if the cut is substantial---indicating that for this 
set-up and the chosen parameter values the two effects 
cancel each other out.%
\footnote{
Running regressions on the expanded simulation results show a negative, but
statistically insignificant relationship between cost of abortion
and fertility.
For high son preference and cost of children the effect of 
decreasing cost of prenatal scan is either nill or slightly
positive.
See also the discussions in \cite{leung94} and \cite{davies97}.
}

Lowering the cost of prenatal sex determination does, however, bias the overall sex 
ratio further towards boys, and the stronger the son preference and the 
more patient the parents, the larger the change in sex ratio.
Correspondingly, both the number of abortions per woman and the
average number of spells per woman where a prenatal scan is used also increases.
Since fertility changes little, the increased use of abortion
is associated with longer spacing between births.
This increase in spacing is, however, not uniform across parities.
In addition to increasing the overall sex ratio, lower cost of prenatal 
scan leads to use of sex selection at earlier parities.
The result is that in some cases there is either no change or a \emph{decrease} 
in average spacing for a given parity---although with a more than compensating 
increase in an earlier parity.%
\footnote{
One example is the second parity for $k= 22$ and $\alpha = 0.65$
when cost of prenatal scan decreases from 24 to 20.
The average spacing for the second parity falls from 1.5 to 1.25,
but the average spacing for the first parity goes from 1 (no
use of sex selection) to 1.5.
Another example is for $\alpha = 0.5$ when cost of prenatal scan falls 
from 20 to 16 when cost of children is 16. 
The average spacing for parity 5 births falls from 1.44 to 1.18, but
the spacing for parity 4 births increases only from 1 to 1.09. 
What this hides is, of course, that there are substantially more 
parity 4 births than there are parity 5 births--and only a slight 
decline in fertility from 4.16 to 4.11---and that the number of
abortions per 100 woman doubles. 
}
Hence, it is possible for individual parities to show a \emph{decline}
in sex selection at the same time as the overall use goes up.
This is an important caution against over-interpreting
individual parity results.
It also highlights the need to incorporate fertility progression into
estimates, something the simple model is incapable of.

% Cost of children

The strongest driver of fertility in the model is the cost of
child maintenance per period.
% For a period maintenance cost of 12 fertility is between 7 and 7.5,
% while for a cost of 22 fertility it is only 2.
As fertility decreases with higher cost of children, sex ratios 
become more male biased---although it is possible that there is 
non-linearity in the effect of child cost on sex ratios.%
\footnote{
The changes in sex ratio are not uniformly positive, possibly because 
the discrete nature of fertility decisions combined with the uncertainty 
of the sex of the next conception produce knife-edge cases that can
dramatically swing the outcomes.
}
This non-linearity also shows up in the number of abortions 
and spells where a prenatal scan has been used, 
but the overall trend is towards more abortions and more spells with
prenatal scan per birth as the cost of children increase.

% Son preference

Increasing the value of having sons, $\alpha$, when there is access to 
sex selection results in slightly lower fertility in most cases,
but the effect is neither strong nor uniform.
What is clear is that the sex ratio becomes more male biased 
the stronger the son preference.
Correspondingly, there is an increased number of abortions,
more spells where a prenatal scan is used,
and the spacing between births is longer.

Son preference, however, manifests in two ways in this model.
First, if $\alpha$ is larger than 0.5 parents gain more utility
from having an additional son than from an additional daughter---provided
the had the same number of sons and daughters before.
Second, parents will never abort a male fetus, only a female one.
This explains why even when parents have equal utility from an additional
son or daughter sex ratios still increases as cost of children 
increases and cost of prenatal scans decline.

At $\alpha = 0.5$ parents prefer an equal number of boys and girls.
The more children you have the less likely it is that you will
resort to sex selection to ensure a balance between sons and daughters.
First, the chances of having, for example, only boys or only
girls, decreases with each additional child.%
\footnote{
For 2 children the likelihood of only boys or only girls
is 50\%, but for 4 children it is 12.5\% (assuming equal probability
of a boy or a girl).
}
Second, the more children you have the lower the marginal
utility of having another, which means that, for a given price
of prenatal scan, the less attractive it is to bear the cost of using
prenatal scans to ensure a specific sex.
As fertility fall to, say, two, however, those parents who had a girl as their 
first child will now want to use prenatal sex determination to 
ensure a balanced number of sons and daughters and this is why
the sex ratio is so unbalanced as the cost of children increases.
Parents who had a son as their first child would also want to
use sex selection to ensure both a son \emph{and} a daughter, but since
that option is not available here they have their
second birth without scan.

Stretching the interpretation of the model, think of $\alpha=0.5$ 
as capturing parents treating sons and daughters equally once born.
The use of sex selection to achieve balance---but only when the
fetus is female---could be a potential explanation for the
suggestion that sons and daughters are treated relatively equally and 
we are still seeing an unequal sex ratio.
What is relevant here it that there is no way to identify which 
of these two different types of son preference affect sex ratios 
from fertility data.
This is a concern because the way we currently measure son preference
allows us to capture only the distribution preference, and 
the different types of son preference likely have different policy 
implications.

% The non-uniform effect in spacing by parity when changing
% the cost of prenatal scan show up here as well.
% Consider, for example, the case when cost of prenatal scan falls from 20
% to 16 when cost of children is 16. 
% The average spacing for parity 5 births falls from 1.44 to 1.18, but
% the spacing for parity 4 births increases only from 1 to 1.09. 
% What this hides is, of course, that there are substantially more 
% parity 4 births than there are parity 5 births--and only a slight 
% decline in fertility from 4.16 to 4.11---and that the number of
% abortions per 100 woman doubles.

% non-uniform effect in spacing by parity
% Interestingly, something similar happens when there is no son preference
% See a=0.5, k = 18 all p. Fourth parity reduces throughout, but third parity
% increases throughout.

% from p= 20 to p=16 it looks like sex selection is falling overall
% because the average spacing goes down substantially for parity 5 (1.44 to 1.18)
% and spacing for parity 4 only increases from 1 to 1.09

% Less clear but generally similar is k = 14]

% The problem with testing this idea is that balance would, for example,
% show up as people using sex selection on having 2 girls and 1 boy and
% the desired fertility is 4. 
% But, if people have high alpha then we would get the same outcome.

% [something on the importance of this and the idea that are 
% multiple forms of son preference.
% people may treat their children equally, but would not abort
% a male to ensure equal number of sons and daughters]

% Discount rate

The discount rate affects fertility little, but sex ratios 
become more biased the more patient people are (higher $d$).%
\footnote{
If son preference is very strong the effect appear to 
depend on the cost of children. 
For low cost of children higher impatience leads to higher
fertility, but for higher cost of children it is sometimes reversed.
Furthermore, these effects are not very strong or clear and
potentially non-linear.
}
% The motivation for this is that less weight you place on the future
% the more appealing it is to simply have another child instead of
% paying for prenatal sex determination, which is ``wasted'' if
% you have a boy.
Similarly, the number of abortions and the number of spells where
prenatal scans are used are higher the more 
weight is place on future utility over current utility.
Just like the discount rate, increasing parents'  
horizon (larger $T$) changes fertility little, but does tend to 
increase the sex ratio in favor of boys when there is access 
to sex selection.%
\footnote{
These simulation results are presented in the online Appendix.
}
Correspondingly, the number of abortions are higher the 
longer the time horizon.

% Highlights and tie into empirical model:

An important question here is whether parents ever
change their use of prenatal sex determination between
two consecutive births.
I capture this by the percent of spells where prenatal
scans were initially used for one or more period, but the birth
is the result of a pregnancy without a prenatal scan.
Whether parents will consider the duration from last birth too long 
depends mainly on the discount rate.
On average, the more impatient parents are---the less they
like long spells between births---the more likely they are to
change their decision to use sex selection.%
\footnote{
Using only those situations where there are any abortions,
regressing the discount rate against the percent spells where
prenatal scan is initially used but not for the birth show
a strong positive effect---higher number, more patient---holding
all the other parameters constant.
}
Lowering the cost of prenatal sex determination generally leads to 
a smaller percentage of parents who change their use of sex selection.
But, the total number of spells with a change may still
go up because lower cost of prenatal sex determination also
increases the use of sex selection.%
\footnote{
An example of this is when the discount rate is 0.95, cost of
children 14, cost preference of 0.6, and the cost of a prenatal scan falls 
from 16 to 12, resulting in a decline in the probability of changing 
from 38.1\% to 30.9\%.
In this case the average number of spells with a change increases
from 0.19 spells at the higher cost of prenatal scan 
to 0.37 for the lower cost.
}

Another reason for parents to change their decision to use sex
selection is that they get ``too close'' to the end of the time
horizon after extensive use of abortions and prefer any child to 
the potential of having no child at all.
This type of reversal explains why the effects of changing the discount 
rate and cost of prenatal sex determination are not uniform.
Related, extending the time horizon leads to a smaller likelihood of parents 
reversing their use of sex selection between births when
there is strong incentive to use sex selection.%
\footnote{
These results are available in the online Appendix.
}

Increasing the cost of children and the degree of son preference
both tend to lower the likelihood that parents will change their
decision to use sex selection.
Working in the opposite direction is that some women with higher cost
of children, for example because of higher education, are also likely 
to marry later.
The later marriage effectively shortens their reproductive time horizon
and thereby makes it more likely that they will reverse their use of 
sex selection between births.
% Again, the caveat is that extensive use of sex selection
% can lead parents close to the end of the time horizon, at which
% point they may change their decision.

% Hence, this shows that parents may reverse the use of sex selection, 
% both when they use sex selection relatively infrequently and when they 
% use it heavily.

% Furthermore, the reversal of use of sex selection is 
% often followed by a spell where sex selection is used again,
% especially in the case when a girl is born.

% What are the model highlights 
There are three main conclusions from the model.%
\footnote{
A caveat is that these results reflect the particular utility 
function chosen.
If parents have a different utility function, like a preference
for one son but otherwise no preference across boys and girls
the results may look different.
% As shown it still is possible, however, to get sex selection
% for balance and for parents to change their decision on use
% of sex selection between births.
}
First, the strongest driver of increased use of sex selection is 
the fertility decline that arise from an higher cost of 
children---for example because of more education for women or 
migration to urban areas.
% As discussed, an important predictor of cost of children is the
% mother's education---more educated women have higher opportunity 
% cost of time.
The increased use of sex selection shows up both in the 
proportion of boys among births and longer spacing between 
births---and the higher the parity the longer the duration between 
births.
The other factors, such as the price of sex selection, 
discount factor, and son preference also affect the use
of sex selection, but to a much smaller degree.
Second, parents do reverse the use of sex selection, 
both when they use sex selection relatively infrequently and when 
they use it heavily.
Reversal are more likely the more impatient parents are or the
shorter time they have left in their reproductive horizon, which
means that the longer the duration has been since the last birth
the more likely they are to reverse their decision to use sex selection.
% Furthermore, as the simulations show it is possible for son 
% preference to decline while the sex ratios becoming more unequal 
% provided the cost of prenatal scan decreases and/or cost of children 
% increases sufficiently (or people become more patient).
Finally, the model shows that son preference in the number of
children is not required for an unequal sex ratio.
As long as parents are only willing to abort female fetuses, declining
fertility will lead to increased use of sex selection to ensure 
a balanced number of sons and daughters.

% Wonder if it would be possible to that some of the
% couples with a son already that look like they are
% using sex selection were not planning on having the
% last child, but with prenatal testing and access to
% abortion they would abort a female fetus but not
% a male one, even if the pregnancy was ``unintended''
% (as in having selected a high $e$, but random 
% chance lead to a pregnancy anyway.

% Empirical method
The model highlights three major limitations of the simple 
empirical method, which a better empirical approach needs to 
allow for.
% First, as fertility declines the proportion of boys among births 
% increases and the spells between births become longer.
% Second, the higher the parity the longer the duration between births because of
% the more intensive use of sex selection.
% Finally, households may reverse its decision to use sex selection within a spell.
First, the simple model cannot capture changes in fertility and the extent 
to which these fertility changes drive the use of sex selection.
Second, increased use of sex selection leads to longer spacing which,
everything else equal, reduces the number of births available for 
estimation in the simple model and thereby lowers its precision
because fewer parents will make it to a given parity by the time of the survey.
Furthermore, the more intensively sex selection is used the larger 
the decline in sample size.
Finally, by using only observed births the simple method cannot capture
when parents change their decision on the use of sex selection;
with a reversal the spell can still result in the birth of a girl.
This last point is especially important when trying to establish whether 
son preference has changed over time in a situation where the cost of prenatal 
sex determination has likely \emph{increased} over time because of the PNDT act.
As I show an increase the cost of prenatal sex determination does 
decrease the sex ratio and lower the number of abortions, but 
it also \emph{increases} the likelihood that parents change their initial
decision to use sex selection within a spell.

%------------------------------------------------------------------------------------

\section{Estimation Strategy\label{sec:strategy}}

The theoretical model has three implications for fertility decisions with access to 
sex-selective abortions: 
a higher probability that next child is a son, 
longer average time to next birth, 
and that the use of prenatal sex determination may change between one observed birth and 
the next.
All three must be incorporated into the estimation strategy
to provide unbiased and precise estimates of the use of sex-selective abortions.%
\footnote{
For comparison the online Appendix presents the estimation strategy 
for the simple model.
The online Appendix also shows how individual parity results compare 
between the simple model and the model suggested here.
As mentioned, the simple model cannot provide complete fertility 
and total number of abortions predictions.
}

The empirical model is a discrete time non-proportional competing risk hazard model with 
two exit states: either a boy or a girl is born.%
\footnote{
\cite{merli00} used a discrete hazard model to examine whether 
there were under-reporting of births in rural China, although they 
estimated separate waiting time regressions for boys and girls.
}
A woman's reproductive life is divided into spells which each covers the period between
births (from marriage to first birth for the first spell).
For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
the spell continues until time $t_i$ when either a birth occurs or the spell is censored.
The time of censoring is assumed independent of the hazard rate,
as is standard in the literature.

There are two exit states: birth of a boy, $j=1$, or birth of a girl, $j=2$, and 
$J_i$ is a random variable indicating which event took place.
The discrete time hazard rate $h_{ijt}$ is
\begin{equation}
 h_{ijt} = \Pr (T_i=t, J_i=j \mid T_i \geq t; \mathbf{Z}_{it},\mathbf{X}_{i} ),
\end{equation}
where $T_i$ is a discrete random variable that captures when woman $i$'s birth occurs.
To ease presentation the indicator for spell number is suppressed.
The vectors of explanatory variable $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$ include 
information about various individual, household, and community characteristics 
discussed below.

The hazard rate is specified as
\begin{equation}
 h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
 {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
 \label{eq:hazard}
\end{equation}
where $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
by dummies and the associated coefficients,
\begin{equation}
D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
\end{equation}
where $D_m = 1$ if $t=m$ and zero otherwise.
This approach to modeling the baseline hazard is flexible and does not place overly strong 
restrictions on the baseline hazard.

Specifying the model as a proportional hazard model, i.e.\ one where explanatory variables 
simply shift the hazard rates up or down independent of spell length, results in 
greater efficiency provided the proportionality assumption holds.
The problem is that the proportional hazard model does not allow covariates
to have different effects over time within a spell and ignoring differences in the shape 
of the hazard functions between different types of individuals can lead to substantial bias.
It is highly unlikely, even in the absence of prenatal sex determination, that the 
baseline hazards are the same across education levels, areas of residence, or sex 
composition of previous births.
The bias from the proportionality assumption is likely exacerbated by the 
introduction of prenatal sex determination for two reasons.
First, one of the main points of this paper is that use of sex-selective abortions 
affects birth spacing, and use of sex selection differs across groups.
Second, as discussed above, the use of sex selection may vary within a spell depending
on the length of the spell.

I therefore use a non-proportional model where the main 
explanatory variables and the interactions between them are interacted with the baseline hazards.
This is captured by the $Z$ set of explanatory variables
\begin{equation}
 \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
\end{equation}
where $D_j(t)$ is the piece-wise linear baseline hazard and $\mathbf{Z}_1$ captures sex 
composition of previous children, if any, and $Z_2$ captures area of residence.
This allows the effects of the main explanatory variables 
on the probabilities of having a boy, a girl, or no birth to vary over time within a spell.
The use of a non-proportional specification, together with a flexible baseline hazard, 
also mitigates any potential effects of unobserved heterogeneity \citep{Dolton1995}.

The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
% %
% \footnote{
% It is possible to incorporate time-variant characteristics of the explanatory
% variables in this set-up, but none of the explanatory variable change within a spell here.
% }
To further minimize any potential bias from assuming proportionality, estimations are 
done separately for different levels of mothers' education and for different time periods.
The exact specifications and the individual variables are described below.

Equation (\ref{eq:hazard}) is equivalent to the logistic hazard model and has the same 
likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
Hence, if the data are transformed so the unit of analysis is spell unit rather 
than the individual woman, the model can be estimated using a standard multinomial logit model.%
\footnote{
% [problem with IIA assumption (independence of irrelevant alternatives]
A potentially issue is that the multinomial model assumes that alternative 
exit states are stochastically independent,
also known as the Independence of Irrelevant Alternatives (IIA) assumption.
% Even though boys and girls are not perfect substitutes they are 
% very similar and this may present a problem for the IIA assumption.
This assumption rules out any individual-specific unmeasured or 
unobservable factors that affect both the hazard of having a girl and the 
hazard of having a boy.
% In other words, the assumption requires that the hazard of having a boy 
% relative to not having a child is uncorrelated with the corresponding
% hazard of having a girl relative to not having a child.
% An important unobservable factor is fecundity.
% Assume that a couple has low fecundity.
% Even with a strong son preference, low fecundity  makes the couple less 
% likely to engage in sex-selective abortions because they will have
% difficulty conceiving again and having a girl might be preferable to having
% no children.
% This is exacerbated by the potential for a further lowering of fecundity
% as a direct result of using abortions.
% Fecundity therefore affect both the hazards of having children and the
% relative likelihood of having a boy versus a girl.
To address this issue the estimations include a proxy for fecundity
discussed in Section \ref{sec:data}.
In addition, the multivariate probit model can be used as an alternative
to the multinomial logit because the IIA is not imposed \citep{han90}.
The results are essentially identical between these two models and
available upon request.
% Finally, what is of interest here is the relationship between the covariates 
% and the rate of occurrence of the different exit types rather than the interrelation between the failure
% types or what would happen if one of the exit types were removed
% making the independence assumption less problematic.%
% \footnote{
% As shown by \citet{kalbfleisch02} data with spell length, exit states and
% fixed covariates does not allow one to distinguish between an independent 
% competing risk model and an infinitude of dependent models that lead to the
% same type-specific hazards.
% }
}
In the reorganized data the outcome variable is zero if the
woman does not have a child in a given period, one if she gives birth to a son in that period,
and two if she gives birth to a daughter in that period.

Direct interpretation of the estimated coefficients for this model is challenging because 
of the competing risk setup.
First, coefficients show the change in hazards relative to the base outcome, no birth, 
rather than simply the hazard of an event.
Second, a positive coefficient does not necessarily imply that an increase in a
variable's value increases the probability of the associated event because the 
probability of another event may increase even more \citep{thomas96}.

The model does, however, make it straightforward to calculate the 
predicted probabilities of having a boy and of having a girl for each $t$, conditional
on a set of explanatory variables and not having had a child before that period.
The predicted probability of having a boy in period $t$ for a given set of explanatory
variable values, $\mathbf{Z}_k$ and $\mathbf{X}_k$, is
\begin{equation}
P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
=  
\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})},
\label{eq:probability_boy}
\end{equation}
and the predicted probability of having a girl is
\begin{equation}
P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
=  
\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}.
\label{eq:probability_girl}
\end{equation}
With these two probabilities is it easy to calculate, for each $t$, the estimated
percentage of children born that are boys, $\hat{Y}$, 
\begin{equation}
\hat{Y}_t 
= 
\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
\times 100,
\label{eq:probability_son}
\end{equation}
and the associated confidence interval for given values of explanatory variables.%
\footnote{
Within each period $1-P(b_{t})-P(g_{t})$ is the probability of not having a birth in 
period $t$.
}

For ease of exposition the procedure is presented here in two steps, but the actual
calculation of the percent boys is done in one step with the 95 percent confidence interval 
calculated using the Delta method.
Results are presented as the estimated percent boys born by length of birth spacing
using graphs.%
\footnote{
The parameter estimates are available on request.
}
For each graph, the extent to which the percent boys is statistically 
significantly above the natural sex ratio indicates the use of sex selection.

Another important aspect of the hazard model is the survival curve, which shows the 
probability of not having had a birth yet by spell duration.
The survival curve for $t$ is 
\begin{equation}
S_{t} 
= 
\prod_{d=1}^t 
\left( 
	1- \left(P(b_{d} | \mathbf{X}_{k}, \mathbf{Z}_{kd}, d) 
	+ P(g_{d} | \mathbf{X}_{k}, \mathbf{Z}_{kd}, d) \right) 
\right),
 \label{eq:survival}
\end{equation}
or equivalently
\begin{equation}
S_{t} 
= 
\prod_{d=1}^t
\left(
\frac{ 1 }
{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
\right).
\end{equation}

The survival curves are presented for two reasons.
First, they show progression to the next birth and how quickly 
it occurs, if at all.
In the absence of sex selection, I expect most parities to show an 
``inverted s'' pattern, where there initially are relatively few births, 
followed by a substantial number of births over a 1 to 2 year period, and then
relatively few births thereafter.
As sex selection becomes more widely used the associated
longer spacing shows up by making the survival curve straighter,
indicating that some of the births that would originally have taken place
now take place later because of abortions.
The use of sex selection is clearly not the only factor that can change the shape of
the survival curves; factors such as the desired number of children and
use of contraceptives may also shape the shape.
To account for this it is best to compare survival curves for an individual
parity between women who are likely to use sex selection and women who are
not, for example because they already have one or more sons.

Secondly, the survival curves provide ``weighting'' for the associated percentage 
boys born.
The steeper the survival curve, the more weight should be assigned to a given
spell period because it is based on more births, 
whereas a period with a flat survival curve should be given little weight because the 
percentage boys is based on few births.
Hence, although they cannot by themselves show sex selection, the survival
curves are a crucial complement to the estimated sex ratios by duration.

\section{Data\label{sec:data}}

The data come from the three rounds of the National Family Health Survey 
(NFHS-1, NFHS-2 and NFHS-3),
collected in 1992--93, 1998--99, and 2005--2006.%
\footnote{
A delay in the survey for Tripura means that NFHS-2 has a small number of observation 
collected in 2000.
}
The International Institute for Population Sciences in Mumbai collected the data,
which have nationwide coverage.
% All are based on the Demographic and Health Survey Model B, with
% NFHS-1 using the DHS II questionnaire while NFHS-2 and NFHS-3 using, 
% respectively, the DHS III questionnaire and the Measure DHS questionnaire.
The surveys are large: NFHS-1 covered 89,777 ever-married women 
aged 13--49 from 88,562 households,
NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households
and NFHS-3 covered 124,385 never-married and ever-married women aged 
15--49 from 109,041 households.

I exclude visitors to the household, as well as
women married more than once, divorced, or not living with their husband,
women with inconsistent information on age of marriage,
and those with missing information on education.
Women interviewed in NFHS-3 who were never married or where gauna had not
been performed were also dropped.
The same goes for women who had at least one multiple birth,
reported having a birth before age 12, had a birth before marriage, or
a duration between births less than 9 months.
Women who reported less than 9 months between marriage and first birth
remain in the sample unless they are dropped for another reason.%
\footnote{
Women who report less than 9 months between marriage and first birth are retained 
because between 10 and 20 percent fall into this category.
Although it is possible that some of these births are premature the high number of
women who report a birth less than 6 months after marriage indicates that conception
likely occurred before marriage in most cases.
}

Finally, I restrict the sample to Hindus,
who constitute about 80 percent of India's population.
If use of sex selection differ between Hindu and other religions, such 
as Sikhs, assuming that the baseline hazard is the same would lead to bias.
The other groups are, however, each so small relative to Hindus that it is not
possible to estimate different baseline hazards for each group.
Furthermore, the groups are so different in terms of background and son preference
that combining them into one group would not make sense.

There are four advantages to using the NFHS.
First, surveys enumerators pay careful attention to spacing between births and
probe for ``missed'' births.
Second, no other surveys cover as long a period in the same amount of detail.
The three NFHS rounds allow me to show the development from before sex-selective 
abortions were available until 2006.
Third, NFHS has birth histories for a large number of women.%
\footnote{
The Special Fertility and Mortality Survey appears to cover a much large number of households
than the three rounds of the NFHS combined, but \citet{jha06} only use the births that 
took place in 1997 making their sample sizes by parity smaller than here.
Their sample consists of 133,738 births of which 38,177 were first
born, 36,241 second born, and 23,756 were third born.
The differences in results for first born children are discussed in the online 
Appendix.
% This is based on Table 1, p 212, and is only for births that took place in 1997.
% Part of problem is the sex ratio on first birth
}
Finally, even if probing for missing births may not completely eliminate recall error,   
the overlap in cohorts covered and the large sample size make it possible to establish 
where recall error remains a problem.

Recall error arise mainly from child mortality, when respondents are reluctant to
discuss deceased children.%
\footnote{
The online Appendix contains a more thorough discussion of recall error and how I address it.
} 
Systematic recall error, where the likelihood of reporting a deceased child depends on
the sex of the child, is especially problematic because it biases the sex ratios.
Probing catches many missed births, but systematic recall error is still a potentially 
substantial problem.
Three factors contribute to the problem here.
First, girls have significantly higher mortality risk than boys.
Second, son preference may increase the probability that boys are remembered relative to girls.
Finally, in NFHS-1 and NFHS-2 enumerators probed only for a missed birth if the
initial reported birth interval was four calendar years or more.
But, given short durations between births, especially after the birth of a girl,
that procedure is unlikely to pick up all missed children.

Observed sex ratios by cohort provide a straightforward way to determine 
whether recall error is a problem.
Because prenatal sex determination techniques did not become widely available until the 
mid-1980s, a higher than natural sex ratio for cohorts born before that time must be 
the result of systematic recall error.
As shown in the online Appendix, the observed sex ratio by parity becomes more male dominated the 
further back births took place.
In addition, births in the same cohort tend to be more male dominated the more recent the 
survey (births in the cohort took place longer ago relative to the survey).
Hence, there is evidence of recall error and the degree of recall error increases
with length of time between survey and cohort.

Using cohort year of birth to analyze recall error and decide which observations
to keep is, however, problematic because the year of birth for a given parity is affected 
by recall error; for example, a second born child listed as first born will be 
born later than the real first born child.
Year of marriage should, however, be unaffected by recall error.
Using year of marriage the basic recall error pattern remains with women married longer 
ago more likely to report that their child was a boy for a given parity.
Similarly, comparing women married in the same period across surveys shows
that women married longer ago are more likely to report having sons.

That recall error increases the longer ago somebody was married means
that duration of marriage is a better predictor of recall error than calendar year of 
marriage.
Figure \ref{fig:sexRatioMarriage} shows the observed sex ratio for children 
reported as first born as a function of duration of marriage combining all three surveys.%
\footnote{
The graph for second births shows a similar pattern.
The graphs for the second births and the individual survey rounds are available upon request.
}
The solid line is the sex ratio of children reported 
as first born by the number of years between the survey and marriage, 
the dashed lines indicate the 95 percent confidence interval 
and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes the years are grouped in twos.

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
\caption{Ratio of boys in ``first'' births}
\label{fig:sexRatioMarriage}
\end{figure}

% \begin{figure}[htp]%
% \centering
% \includegraphics[width=0.4\textwidth]{sex_ratio_marriage}
% \caption{Ratio of boys in ``first'' births
% \label{fig:sex_ratio_recall}}
% \end{figure}

Figure \ref{fig:sexRatioMarriage} clearly illustrates the systematic recall error
problem.
The observed sex ratio is increasingly above the expected value the
longer ago the parents were married.
The increasingly unequal sex ratio with increasing marriage duration suggests that
a solution to the recall error problem is to drop women who were married ``too far'' from 
the survey year.
The main problem is establishing what the best cut-off point should be.
The observed sex ratio is consistently significantly higher than the natural sex ratio 
from around 24 years of marriage, so one possibility is simply to drop all women married 
more than 24 years at the time of the survey.
But, as the Appendix shows, there are differences across the three surveys and between 
parities.
Based on the differences between surveys the cut-off points I use vary by survey round.
For NFHS-1 women married 22 years or more were dropped, with the corresponding cut-off 
points 23 years for NFHS-2  and 26 years for NFHS-3.
The final sample consists of 146,096 women, with 332,951 parity one through four births.%
\footnote{
The online Appendix presents the results for a more restrictive definition and for the
women dropped because of recall error concerns.
}

\subsection{Spell Definition\label{sec:spell_def}}

Spell duration is measured in quarters of a year, that is 3 month periods, hereafter
referred to as quarters.
The first spell begins at the month of marriage rather than 9 months after because many 
women report giving birth less than 9 months after they were married.
For women who began living with their husbands at too young an age to conceive the 
starting point should ideally be first ovulation, when she becomes ``at risk'' for a 
pregnancy, rather than month of marriage.
Unfortunately, information on age of menarche is only available in NFHS-1.
Instead, for women who began living with their husband before age 12, I set the 
the month they turned 12 years of age as staring point for the first spell.

The second and subsequent spells begin 9 months after the previous birth 
because that is the earliest we should expect to observe a new birth.
A few women report births that occurred less than 9 months 
after the previous birth; those women are dropped.

All spells continue until either a child is born or the spell is censored.
Censoring can happen for three reasons:
the survey takes place;
the woman is sterilized;
or the number of births observed becomes too sparse for the method to work.
The timing of censoring because of too few births vary slightly by spell but is generally 
21 quarters after the beginning of the spell.

I group spells into three time periods based on spell start date:
1972--1984, 1985--1994, and 1995--2006.
The first period covers the time before sex-selective abortions became widely available.
Abortion was legalized in 1971 and amniocentesis was introduced
in India in 1975, but the first newspaper reports on the availability of prenatal sex 
determination were not until 1982--83 \citep{Sudha1999,bhat06,Grover2006}.
The number of clinics quickly increased, and knowledge about sex selection became widespread
after a senior government official's wife aborted a fetus that turned out to be male \citep[p.\ 598]{Sudha1999}.
The second period covers the time from the widespread emergence of sex-selective abortions
until the prenatal Diagnostic Techniques (PNDT) act was passed in 1994.
The final period is from the PNDT act until the last available survey.
The PNDT act made it a criminal offence to reveal the sex of the fetus and was
followed by a campaign against the use of sex selection, although
enforcement appears to be relatively lax.

By dividing spells into these periods I can examine how fertility
decisions and the use of sex selection have changed across the three different regimes.
Note that the periods are based on the spells' beginning year, and some spells 
will therefore cover two periods.
A couple may, for example, be married in 1984, but not have their first child until 1986.
That couple's first spell will be in the 1972--1984 period, even though most of the 
spell actually falls in the 1985--1994 period.
Some children born from spells that began in the 1972--1984 period may therefore have been
conceive when prenatal sex determination techniques were available, which could result
in evidence of sex-selective abortions even for this period.
Similarly, a spell that began in the 1985--1994 period may have been partly or mostly
under the PDNT act.
The overall effect is to bias downwards any differences between the periods.

\subsection{Explanatory Variables}

The explanatory variables are divided into two groups.
The first group consists of variables expected to affect the shape of the hazard function: 
mother's education, sex composition of previous children, and area of residence.
Increasing the number of variables interacted with the baseline hazard lowers the risk 
of bias but requires more data to precisely estimate.
I chose these variables because the prior literature shows that they affect 
fertility and spacing choices and because the prior literature on sex selection indicates 
that these are correlated with sex selection.
The second group of variables are those expected to have a proportional effect on the 
hazard: age of the mother at the beginning of the spell, length of her first spell 
(for second spell and above), whether the household owns land, and whether the household 
belongs to a scheduled tribe or caste.

Increasing education of mothers is strongly associated with lower fertility, with
the negative effect of higher opportunity cost on fertility more than outweighing the 
positive effect of higher income \citep{schultz97}.%
\footnote{
Fathers' education has two opposite predicted effects: the associated higher income
should increase fertility and therefore lower the pressure to use sex selection, but
the higher income also makes the use of sex selection cheaper.
In practice, fathers' education had little effect on the hazards and the use of 
sex-selective abortions and is not included.
}
Higher education should therefore be associated with higher use of sex selection.
I divide women into three education groups:
no education, 1 to 7 years of education, and 8 and more years of education.
The models are estimated separately for each education level.
A potential concern here is reverse causation, where the sex of children
affect women's education.
Although no direct information is available on when women left school it is
possible to estimate school leaving age from the highest completed grade
and the usual starting age.
As described in the online Appendix, relatively few women could potentially 
have returned to school after the birth of their first child,
and only 56 could possibly have ended up in the wrong education group. 
Hence, there is little likelihood that reverse causation is a substantial
concern here.

As discussed, the sex composition of previous children affects both the timing
of fertility and the use of sex-selective abortions.
Here I capture sex composition of previous children by dummy variables for the
possible combinations for the specific spell, ignoring the ordering of births.
As an example, for the third spell three groups are used: Two boys,
one girl and one boy, and two girls.

The area of residence is a dummy variable for the household living in
an urban area.%
\footnote{
NFHS uses four categories for area of residence: Large city, small city, town
and countryside.
To reach a sufficient sample size urban areas are merged into one group.
}
Area of residence captures both access to prenatal sex determination techniques 
and the cost of children.
The cost of children is higher in urban areas than in rural and access to prenatal
sex determination is easier;
both are expected to lead to greater use of sex-selective abortions in urban than 
in rural areas.
Because of concerns about selective migration I use where the household was living
at the end of each spell.%
\footnote{
As online Appendix Table D.1 shows there is little difference across
education levels in migration patterns within each period and patterns across periods
are also relatively stable.
}

The sex composition of children, area of residence, and their interactions
are interacted with the piece-wise linear baseline hazard dummies.
In other words, the baseline hazards are assumed to be different depending on
where a woman lives and the sex composition of her previous children.
As an example, for the second spell a separate regression is
run for each education level and in each regression four different baseline hazards 
are included (first child a boy in rural area, first child a boy in urban area,
first child a girl in rural area, first child a girl in urban area).
Although this approach substantially increases the number of regressions and estimated parameters it
reduces the potential problem of including other variables as proportional effects.
In addition, it forces attention to how much data are really available to estimate
the determinants of sex-selective abortions.

The remaining variables are expected to affect hazards proportionally.
% Age of the mother is captured by her age in years at the beginning of
% a the spell.
% On one hand, an older woman might be less able to conceive and therefore less
% likely to use sex-selective abortions.
% On the other hand, for a given spell, a higher age might also be associated 
% with more education or previous longer spells because of the use of sex selection.
% The correlation between age and education is a potential downside to using
% the three categories of education, but this is outweighed by the fact
% that fewer assumptions are imposed on the baseline hazards.
Although fecundity cannot be observed directly a suitable
proxy is the duration from marriage until first birth.
Most Indian women do not use contraception before the first birth
and there is pressure to show that a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
This is confirmed by the very short spells between marriage and first birth,
even among the most educated.
Hence, a long spell between marriage and first birth is likely due to low fecundity.
The expected effect of a longer first spell is to reduce sex-selective abortions in subsequent spells.
For both this variable and the age of the mother at the beginning of the spell the squares are also included.
The remaining variables are dummies for household ownership of land and membership
of a scheduled caste or tribe.
% All are assumed to affect the hazards proportionally.
% The first round of the NFHS asked only about membership of either 
% a scheduled caste or tribe but the later rounds also asked
% about membership of other backward castes.
% To ensure consistency the only two variables used are dummies for whether
% a woman belongs to a scheduled caste or a scheduled tribe, respectively.
% Unfortunately, there is no information on belonging to a higher caste, although
% higher education is often related to higher status.

\subsection{Descriptive Statistics}

Appendix Table \ref{tab:des_stat1} presents descriptive statistics for
the spells by education level and when the spell began.
There is a substantial number of censored observations.
As an example, for highly educated women who had their first child in the 1995--2006
period, almost half did not have their second child by the time of the survey.
Hence, although about 13,000 women began the second spell 
there are only about 7,000 births to these women.
Censoring becomes even more important for the third and fourth
spells, where around 70 percent of the observations are censored.
Generally, censoring increases with parity and time period.
% %
% \footnote{
% The exception is for women without education where twelve percent of
% the women who married in the 1972 to 1984 period did not have a first
% birth at the time of the survey.
% }
This reflects a combination of factors: timing of the surveys
relative to the periods of interest, later beginning of childbearing, 
falling fertility, and the longer spells from sex-selective abortions.
The high number of censored observations underscore the importance of controlling for
censoring when examining the relationship between fertility and sex selection.

The descriptive statistics also provide a first indication of how the
sex ratio at birth changes over time and by spell.
For the first spell the sex ratio is very close to the natural
for all education groups and all three time periods.
As an example, among the highly educated group for the 1995--2006 period,
51.3 percent of the children born were boys.%
\footnote{
There still appears to be some recall error for the group of women without
education for the 1972--1984 period, where 52.3 percent of the children born were boys.
}
For the second spell, all but the highly educated group in the last two
periods have sex ratios in line with the natural sex ratio.
Women with 8 or more years of education have 53.1 and 54.3 percent
boys in the 1985--1994 and 1995--2006 periods, respectively.
This pattern repeats itself for the third spell, except the percentage
boys is higher for the high education group (55.3 and 55.9 for the last
two time periods).
Finally, for the fourth spell the high education group 
had 60 percent boys in the last period, i.e. after the PNDT act was introduced.
Note, however, that for the fourth spell the number of births is substantially
smaller and censoring even more important than for the other spells.

India's population has become progressively more urban.
For the first period, 32 percent of the women entering the first spell lived in urban areas.
This increases to 35 percent for the second period and to 42 percent for the final period.
The population is also substantially better educated.
Women with no education constituted almost 60 percent 
in the first period, but less than thirty percent in the last period.
Correspondingly, in the first period just over twenty percent had 8 or more 
years of education, but in the last period it was almost half.
Part of the increase in education is correlated with the increase in urbanization,
but the proportion of better-educated women has increased substantially
in the rural areas as well.
Among the high education group almost 70 percent lived in urban areas
during the first period but this had fallen to less than 60 percent
in the last period.

The increase in urbanization and education is likely to exert downward pressure
on fertility and the high censoring rates for the later periods are evidence of this.
The average number of children born to women by the time they turn 35 illustrate how
strong the decline in fertility has been.%
\footnote{
Figure \ref{fig:fertility} shows the full results.
}
Women born in the early 1940s had on average close to 5 children when 
they reached 35, but women born in the early 1970s had only just over three children.
The low number of children is especially remarkable because it combines
all education levels and all areas of residence.
% Hence, fertility in cities is likely substantially lower.

\section{Results\label{sec:results}}

% [NEW OUTLINE]
% - Desired fertility analysis
% - changes over time for well-educated women (spell 2 and 3)
% - comparison across groups (no, some, high education, for spells 1, 2, and 3)

% - 1st spell for all individuals (compare with other research)
% - High education group for spell 2 and above
% - Medium education group for spell 2 and above
% - Low education group for spell 2 and above
% - Predicted changes in fertility and number of abortion and comparison with standard model

One of the main questions here is how fertility affects sex selection use.
I start by showing the relationship between self-reported desired fertility and sex 
selection, which also illustrates how to interpret the results.
Although self-reported desired fertility is an imperfect proxy for actual
fertility behavior, the analysis of desired fertility indicates that there is 
a relationship between fertility decisions and the use of sex selection and motivates 
examining the relationship more closely.

Because of the desired fertility measure's potential shortcomings, I next examine the 
relationship between actual fertility and use of sex selection for better-educated women.
There are two steps in this process.
First, I show how fertility has declined for better-educated women with one son---a group 
unlikely to use sex selection, which means that sex selection will not affect the 
progression rates to next birth for these women.
Second, I show how, corresponding to the fertility decline, there is an increase in
sex-selective abortions for better-educated women without a son.
I next show how women with lower cost of children appear to follow a high fertility, low
use of sex selection strategy compared to the low fertility, high use of sex selection of
the better-educated women.
The results all show clear evidence of son preference in fertility and sex selection use, 
but exactly what form son preference takes is important, so I next discuss what we can
learn about son preference from the sex selection behavior.
% [Then I compare my suggested model with the simple model previously used.]
Finally, I predict lifetime fertility, number of abortions, and final sex ratios for
the better-educated women.

Except for the predictions, results are presented using graphs of estimated percentage boys 
born by quarter, the associated 95 percent confidence interval, and the survival curve for 
a ``representative woman'' using the method detailed in Section \ref{sec:strategy}.
The ``representative woman'' characteristics are based on means of continuous 
explanatory variables and the majority category for categorical explanatory variables.
Common to all ``representative women'' is that they do not own land and belong to neither 
a scheduled caste nor a scheduled tribe.
The graphs also show the expected natural rate of boys, approximately 51.2 percent, for
comparison.
Graphs for all groups and spells, even if not discussed here, are available in 
the online Appendix.

% % [Seems to be a repeat of what is in estimation strategy]
% The survival curves show the estimated probability of not having had a birth
% yet by length of the spell.
% The survival curves are included for two reasons.
% First, they show the progression to the next birth by quarter and how quickly it occurs,
% if at all.
% Second, they provide ``weighting'' for the associated percentage boys born.
% The steeper the survival curve, the more weight a given spell period has because it is 
% based on more births, whereas a flat survival curve means little weight because the 
% percentage boys is based on few births.

\subsection{Desired Fertility and Sex Selection}

A first step to understand the relationship between fertility and sex selection
is to examine how use of sex-selective abortions vary with self-reported desired 
fertility.
If lower fertility drives sex selection and desired and actual fertility are
at least partly correlated, women with lower desired fertility should be more 
likely to use sex selection than women with higher desired fertility, 
holding other characteristics constant.
Figure \ref{fig:results_spell2_high_want} presents results by desired fertility 
for the second spell of women with 8 or more years of education whose first child was a 
girl.%
\footnote{
For women with living children the question asked was
``If you could go back to the time you did not have any children and could choose exactly 
the number of children to have in your whole life, how many would that be?'', while
for women with no living children the question was
``If you could choose exactly the number of children to have in your whole life, how many 
would that be?''
% P 116 Appendix F in NFHS book
}

A majority of better-educated women report that they want two or fewer 
children, and the proportion who wants two or fewer is increasing over time.%
\footnote{
In the first period 2,055 out of 8,202 (25\%) women wanted 3 or more 
children, including giving a non-numeric response.
In the second period this number was 2,583 out of 16,600 (16\%) 
and in the third period it was 1,264 out of 13,610 (9\%).
} 
To achieve a large enough sample of women who want three or more children, I use all 
second spells that began in the period 1985 to 2006.
This allows me to estimate non-proportional hazards by area of residence, sex of 
previous child, and desired fertility.
For both rural and urban women, the left panel shows the results for women who want two 
or fewer children and the right panel shows the results for women who 
want three or more children.%
\footnote{
Restricting to wanting exactly 3 children has little to no impact on the spacing
pattern, suggesting that higher desired number of children does not lead to
substantially shorter spacing.
}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[Wants 2 or fewer children (N=7,779)]{
    \begin{minipage}{0.31\textwidth}
    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r8_pc}}\\
    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r8_s}}
    \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[Wants 3 or more children (N=864)]{
    \begin{minipage}{0.31\textwidth}
    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r4_pc}}\\
    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r4_s}}
    \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{0}
\subfloat[Wants 2 or fewer children (N=4,851)]{
    \begin{minipage}{0.31\textwidth}
    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r7_pc}}\\
    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r7_s}} 
    \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{1}
\subfloat[Wants 3 or more children (N=1,077)]{
    \begin{minipage}{0.31\textwidth}
    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r3_pc}}\\
    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r3_s}}
    \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Desired fertility and predicted probabilities of having a boy and 
no birth yet from 9 months after first birth for
women with 8 or more years of education by quarter (3 month period). 
Predictions based on first child a girl and woman age 22 at first birth.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_high_want}
\end{figure}

Three main results stand out.
First, the sex ratios by quarter for women who want 2 or fewer children show 
substantial evidence of sex selection, while there is little evidence among those who want 
3 or more.
This supports that fertility is an important factor in the use of sex selection.
Second, for women who want 2 or fewer children, use of sex selection is higher among urban 
than rural women, but not significantly so.
The proportion of boys born is between 55 and 60 percent and statistically 
significant higher than the natural sex ratio for all quarters for urban women, whereas
for rural women the proportion is generally 2 to 3 percentage points below the urban 
level.%
\footnote{
For comparison, if 55 percent of children born in a given quarter were boys,
approximately 14 percent of the female fetuses were aborted.
Assume 105 boys per 100 girls born, the expected natural sex ratio.
With $b$ boys, we should expect $b\frac{100}{105}$ girls born.
If we observe $g$ girls the number of abortions is therefore $b\frac{100}{105}-g$
and the percent aborted female fetuses is 
$\frac{b\frac{100}{105}-g}{b\frac{100}{105}}\times 100$.
With 55 percent boys we get $\frac{55\frac{100}{105}-45}{55\frac{100}{105}}\times 100 = 14.09$.
The corresponding numbers for 60 percent and 65 percent boys are approximately 30 percent and
43 percent of the female fetuses aborted.
}

Third, the effects of sex-selective abortions on spacing show clearly in the differences 
across the survival curves for the different groups.
A normal spacing pattern without sex-selective abortions---where most women have the second 
child relatively early---leads to a survival curve with a steep slope first, followed 
by a leveling off.
This pattern is followed by rural women who want 3 or more children.
As discussed above, use of sex-selective abortions should results in substantially
longer spacing between births, which makes the survival curves appear more as 
straight lines.
Urban women who want 2 or fewer children show this pattern.

Another way to see the effects of sex-selective abortions on spacing is to compare the 
proportion of women who have not had a second birth yet at a specific time.
Ten quarters into the spell---equivalent to 13 quarters (3\sfrac{1}{4} years) after the 
first birth---just below 35\% of rural women who want 3 or more children have not had their 
second birth yet, compared with more than 45\% among rural women who want 2 or fewer children.
Similarly, among urban women about 35\% of those who want 3 or more children have not had 
a second birth yet at 10 quarters after their first birth, compared with almost 55\% of 
those  who want 2 or fewer.
% These numbers reinforce that there is little sex selection among women who want 3 or
% more children, regardless of whether they live in rural or urban areas, and that for
% women who want 2 or fewer children more sex selection takes place among urban than
% rural women.%
% % \footnote{
% % % proportions who end up with a second birth!
% % The proportion of women who have not yet had a second birth at the end of the estimated
% % spell period is higher for 
% % }

There are, however, three major methodological concerns with using self-reported 
desired fertility.
First, although the correlation between desired and actual fertility is positive,
it is far from one.
Second, it is potentially endogenous to the number of children a woman already has 
and may be measured with error \citep{Jensen1985,Rasul2008,Ashraf2009}.
Finally, there is much less variation in desired fertility than in actual fertility,
making it difficult to precisely estimate changes in sex selection over time.
I therefore next examine whether decreases in observed fertility over time are
associated with increased use of sex-selective abortions.

% The predicted percentage boys for the second, third and fourth spells for 
% women with 8 or more years of education show that this is, indeed, the case.
% As for the first spell, the results are presented using a representative woman
% with the same characteristics as above, except that the ages at the beginning of
% the spell are 22, 24 and 25 years for the second, third and fourth
% spell and that the first spell length is set equal to 16 months.

\subsection{Changes in Fertility over Time\label{sec:changes}}

The first step when examining how declining fertility affects the use of sex selection is 
to show how fertility has decreased over time.
The challenge is that women who use sex selection have longer birth spacing, which 
makes it look like they have lower fertility than they really do, and consequently would
make the relationship between fertility and sex selection appear stronger than it really is.
As I show below, and as suggested by the previous literature, women with one or more sons 
do not appear to use sex selection.
Hence, these women's fertility decisions will not be affected by the availability
of prenatal sex determination techniques.
I therefore show fertility progression only for women who have already had at least one 
son, continuing to focus on the better-educated women.

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-3}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[2nd spell---has 1 boy (N=2,806)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}}\\
        \subfloat[3rd spell---has 1 boy (N=1,409)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}}\\
        \subfloat[3rd spell---has 2 boys  (N=780)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}}   
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-2}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[2nd spell---has 1 boy  (N=5,246)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}\\
        \subfloat[3rd spell---has 1 boy (N=3,460)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}\\
        \subfloat[3rd spell---has 2 boys (N=1,660)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[2nd spell---has 1 boy  (N=3,969)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}\\
        \subfloat[3rd spell---has 1 boy (N=2,357)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}\\
        \subfloat[3rd spell---has 2 boys (N=1,098)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted progression to birth for women with 8 or more years of education by 
quarter (3 month period) conditional on having at least one boy. 
Left column shows results prior to sex selection available, middle column before
sex selection illegal, and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:fertility_progression_boys}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{Rural}
\setcounter{subfigure}{0}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[2nd spell---has 1 boy (N=1,404)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} \\
        \subfloat[3rd spell---has 1 boy (N=700)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} \\
        \subfloat[3rd spell---has 2 boys (N=370)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}}  
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{1}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[2nd spell---has 1 boy (N=3,381)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}\\
        \subfloat[3rd spell---has 1 boy (N=1,987)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}\\
        \subfloat[3rd spell---has 2 boys (N=945)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[2nd spell---has 1 boy (N=3,044)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}\\
        \subfloat[3rd spell---has 1 boy (N=1,819)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}\\
        \subfloat[3rd spell---has 2 boys (N=790)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted progression to birth for women with 8 or more years of education by 
quarter (3 month period) conditional on having at least one boy. 
Left column shows results prior to sex selection available, middle column before
sex selection illegal, and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:fertility_progression_boys}
\end{figure}

Figure \ref{fig:fertility_progression_boys} shows the predicted progression to
next birth for urban and rural women with 8 or more years of education, conditional on 
having at least one boy, by the starting period of the spell, and within each period by 
spell.%
\footnote{
Could the prior births for each of these groups have been the result of sex selection?
As I show in the online Appendix there is little evidence of sex selection on first births,
so it is unlikely that women with a son as their first child ended up with a 
boy through anything other than random chance.
Similarly, for the third spell group, women with two boys are unlikely to have used sex 
selection since there is no evidence on sex selection on first birth and no evidence of 
sex selection if a son is already present.
It is possible that third spell women with one son and one daughter could 
have used sex selection in a prior spell, if they had the girl as the first child, as
described below.
There is, however, little difference in fertility progression for the third spell between 
women with two sons and women with one son and one daughter as their first children.
}
In all cases the proportion of women without a birth by the end of the spell period has 
increased substantial.
In other words, fertility has declined over time for both urban and rural women.
Although it is possible that some women will have a child after the end
of each estimated spell, it is unlikely to be a substantial number given the shape
of the survival curves.

For urban women with a son as the first child, the proportion who did not have a second 
child 6 years after the birth of their first child increased from around 15\% in 
1972--1984 period to more than 30\% in the 1995--2006 period.%
\footnote{
Recall that for the second and higher spell, the spells are estimated starting from the 
fourth quarter after the birth of their previous child.
Hence, 3 quarters has to be added to the spell lengths in the figure to get the actual
spacing.
}
Similarly, the proportion who did not have a third child by 6\sfrac{3}{4} years after their second
birth went from 40\% in the 1972--1984 period to almost 70\% in the 1995--2006 period
if the woman already had one son, and from 45\% to more than 70\% if she had two sons.
Rural fertility is higher, but the underlying pattern is the same.
In all cases, more women finish the spell without another birth in the last period than 
in the first.%
\footnote{
The results for the fourth spell---available in the on-line Appendix---show similar 
results with women with at least one son experiencing large reductions in progression
rates over time.
}

Changes over time for this group of women provides an indication of whether increased 
availability of contraceptives affects the spacing between births over time.
Increased use of modern, reversible contraceptives allows greater control over spacing, 
potentially making the survival curves straighter if there are \emph{uniformly} distributed
``preferences'' for how long spacing between births should ideally be.
There are two reasons why this is not a substantial concern here.
First, use rates of modern, reversible contraceptive have not changed much.
For India as a whole current use of any modern method has gone from 36.5\% in NFHS-1 to 
48.5\% in NFHS-3, but most of this increase has come from female sterilization, which has 
increased from 27.4\% to 37.3\% over the same period 
\citep[p.\ 127]{International-Institute-for-Population-Sciences-IIPS2007}.
Second, survival curves in Figure \ref{fig:fertility_progression_boys} appear to have 
retained their shapes across periods to the extent possible given fertility declines, 
suggesting that the availability of contraceptives has not had a strong effect on the 
spacing between births.
Because the estimations are done separately by periods the similarity of shapes come from 
the data, not from assumptions about functional form.

% [refer to discussion in model section on opposite effect on fertility of access
% to sex selection.
% Also use R3's point on differences in costs between boys and girls and the
% effect of access to sex selection on fertility.
% Given that abortion is relatively cheap the decline in fertility would 
% suggest that girls are not substantially more costly than boys.
% Thank anonymous referee for this point.
% Include Jat village paper reference on cost of sex selection.]

The decline in fertility over time implicitly provide information on the relative
cost of having a boy versus a girl.%
\footnote{
I am grateful to an anonymous reviewer for suggesting this point.
}
As discussed in Section \ref{sec:model}, there are two opposite effects of introducing
sex selection on fertility: parents can reach their desired number of sons with fewer 
births, which reduces fertility, but also do not have to pay for unwanted children,
and this wealth effect will tend to increase fertility.
The size of the wealth effect depends on the relative cost of boys and girls and the cost 
of sex selection; if girls are very costly and abortion cheap the wealth effect will be
larger, making it more likely that fertility increases with introduction of 
sex selection.
The cost of sex selection does, indeed, appear to be relatively low 
\citep[see, for example][]{Khanna1997}.
Hence, the decline in fertility after the introduction of sex determination is an 
indicator that girls are not substantially more expensive than boys.

\subsection{Effect of Declining Fertility on Sex-selective Abortions}

\begin{figure}[htpb]
\centering
\caption*{Second spell for urban women---first child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,689)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,869)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=3,774)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Third spell---first two children girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=709)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,654)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=1,000)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from 9 months after first birth for urban
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth for second spell and on age 24 at second
birth for third spell.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:over_time_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Second spell for rural women---first child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=1,305)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=3,105)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,823)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Third spell---first two children girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=348)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=982)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=863)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from 9 months after first birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth for second spell and on age 24 at second
birth for third spell.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:over_time_rural}
\end{figure}

The second step is to show that with the fertility decline there is a corresponding 
increase in sex-selective abortions.
If the decline in fertility drives the increase in use of sex-selective abortions, we 
should see an increase in sex ratios for a given spell number \emph{and} use of sex 
selection for earlier spells over time.
As discussed, the group most likely to use sex selection is women without sons.
Figures \ref{fig:over_time_urban} and \ref{fig:over_time_rural} therefore show the 
development in sex ratios by quarter for second and third spells for women without sons in 
urban and rural areas.
Both urban and rural women follow the expected pattern, consistent with declining 
fertility driving the use of sex selection.

For urban women's third spell in the first period, the predicted sex ratios  
show no evidence of sex-selective abortions.
After the introduction of prenatal sex determination techniques there is substantial
evidence of sex selection both before and after sex selection was made illegal.
The increased sex ratio within the spell for the 1985--1994 period is likely the
result of those women who---for one reason or another---waited longer to try for 
a third child having easier access to sex selection.
Compared to the 1985--1994 period, there appears to be a leveling off of the sex ratio 
for the 1995--2006 period and the overall sex ratio may even be a little lower.
Consistent with this there is little difference in the survival curves between
the two periods.

Does the small difference between the two last periods for the third spell then show that 
banning sex selection at least stalled the increase in the use of sex selection?
The results for the second spell show that this is not the case.
With the falling fertility there is increased use of sex selection for the 
second spell.
There is limited evidence of sex selection for the second spell in the 1985--1994 
period, which is expected given that many women were still having 
three children.
For the 1995--2006 period, however, there is is a consistently high and 
statistically significant sex ratio.
Hence, with declining fertility the use of sex selection has simply moved to an
earlier parity.
Consistent with the theoretical model predictions the result is a decline in 
sex ratio for an \emph{individual} parity at the same time as the overall
use of sex selection increases.
The most likely explanation for the relative small difference between periods for 
the third spell is that a smaller proportion of women make it to a situation
where they have two girls as their first two children in the latest period;
those with the strongest preference for having a boy and for lower fertility have 
already used sex selection during the second spell.

Rural women follow the same general pattern as urban women, but the samples are smaller
making for noisier estimates.
The changes between the 1985--1994 and 1995--2006 periods for the third spell is again
of special interest because it appears that the use of sex selection falls over time.
But, the change for the second spell over time is even more pronounces for rural women
than for urban women with very substantial increase in the use of sex selection for
the second spell.

Another way to see the interaction between fertility and sex selection is to compare
the survival curves across sex composition and spells.
As fertility has fallen the survival curves have become straighter for
women without sons relative to for women with sons;
the result of longer spacing arising from the use of sex selection.
Among women with no sons the proportion of women without a birth by the end of 
the spells has increased, but to a much smaller extent than for women with 
at least one son.
% Furthermore, the close to straight survival curves even at the end of the spells is an 
% indication that at least some women who have not had a birth yet by the end of the spell 
% may still have a child.

\subsection{Fertility and Sex Selection Across Groups}

As shown the decline in fertility over time is associated with both an increased use 
of sex-selective abortions for a given spell \emph{and} use of sex selection for 
earlier spells for the women most likely to have low and falling fertility, women
with 8 or more years of education.
What remains is to show that women who have lower costs of children have higher
fertility and consequently show less or no use of sex-selective abortions. 
Assuming that preferences for having one son is similar across education groups
the lower cost of children makes it more attractive for less-educated women to continue
having children with the aim of having at least one son instead of resorting to
sex selection.

\begin{figure}[htpb]
\centering
\caption*{No Education}
\setcounter{subfigure}{-2}
\subfloat[Spell 1 (N=1,762)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[Spell 2 - 1 girl (N=952)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Spell 3 - 2 girls (N=475)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{1 to 7 Years of Education}
\setcounter{subfigure}{1}
\subfloat[Spell 1 (N=2,302)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[Spell 2 - 1 girl (N=1,082)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[Spell 3 - 2 girls (N=425)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{8 or More Years of Education}
\setcounter{subfigure}{4}
\subfloat[Spell 1 (N=9,116)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{5}
\subfloat[Spell 2 - 1 girl (N=3,774)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[Spell 3 - 2 girls (N=1,000)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth by quarter (3 month period) for urban women for 1995--2006. 
N is number of women in the relevant group in the underlying samples.
}
\label{fig:groups_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{No Education}
\setcounter{subfigure}{-2}
\subfloat[Spell 1 (N=7,922)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[Spell 2 - 1 girl (N=3,686)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Spell 3 - 2 girls (N=1,879)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{1 to 7 Years of Education}
\setcounter{subfigure}{1}
\subfloat[Spell 1 (N=5,208)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[Spell 2 - 1 girl (N=2,159)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[Spell 3 - 2 girls (N=848)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{8 or More Years of Education}
\setcounter{subfigure}{4}
\subfloat[Spell 1 (N=7,504)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{5}
\subfloat[Spell 2 - 1 girl (N=2,823)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[Spell 3 - 2 girls (N=863)]{
    \begin{minipage}{0.21\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth by quarter (3 month period) for rural women for 1995--2006. 
N is number of women in the relevant group in the underlying samples.
}
\label{fig:groups_rural}
\end{figure}

Figures \ref{fig:groups_urban} and \ref{fig:groups_rural} show sex ratios and
survival curves for the three education groups for the latest period, 1995--2006,
for urban and rural women.
For each education group the figure shows the first spell, from marriage to first
birth, the second spell for women with a girl as the first child, and, finally,
the third spell for women with two girls as their first children.
The second and third spells for the better-educated women are the same as in
Figure \ref{fig:over_time_urban} and \ref{fig:over_time_rural}, panels (c) and (f),
and are reproduced to ease comparison.

As expected, progression rates are higher the lower the education level and higher in
rural areas than in urban areas.
The proportion of women with no education who end up with no birth at the end of the 
third spell is less than 10 \% for urban women and less than 5\% for rural women.
For those with 1 to 7 years of education less than 20\% of urban women do not go on to 
having a third child, while for rural women it is less than 10\%.
What is more, the progression rates for women with either two boys or a boy and a girl
as their first children are only marginally higher than for women with two girls.%
\footnote{
In the interest of space these are shown in the online Appendix. 
The Appendix also shows progression rates for the fourth spell.
Although samples become very small, the results correspond well.
Progression rates are higher the lower the education and higher for rural women than
for urban women.
The samples become so small exactly for the reason discussed above:
there is a less than 12\% chance of not having a son by the third child.
}
Hence, women with less than 8 years of education still have high fertility in both
urban and rural areas.

Corresponding to the higher fertility among women with less education there is little
evidence of sex selection among women with less than 8 years of education.
Generally the predicted sex ratios are not statistically significantly
higher than the natural rate and the survival curves all show a similar pattern where
most of the births occur early in the spell and there is no evidence of the changing
survival curves associated with longer spells that would indicate use of sex-selective 
abortions.%
\footnote{
The exceptions are small parts of the second spell for no education women and 
third spell for women with 1 to 7 years of education. 
As the survival curves show both are based on very few births.
Fourth spell results generally confirm the absence of sex selection among women with 
less education.
}
Hence, there is evidence of two different paths to having a son:
high education women have few children and substantial use of sex selection, while
low education women have many children and little to no use of sex selection.

Two other important results stand out.
First, there is no evidence of sex selection on first birth, no matter the education
level.
The sex ratios are never statistically significant different from the expected and 
timing of births is close to identical for all groups, with most women having their 
first child soon after marrying.%
\footnote{
This cast serious doubts on the data used by \citet{jha06} and their result that 
there is substantial use of sex selection on first births.
As discussed above and in the online Appendix their results are likely the result of
substantial recall bias.
}
Second, the natural sex ratio for India appear to be in line with what is found for 
other countries at around 105 boys per 100 girls.
For all groups for whom we would expect little to no use of sex selection and have
many births to base the estimate on, such as rural women with no education and urban
women with 8 or more years of education, the sex ratios almost completely coincide 
with the 105/100 line.

% points to cover:
% - fertility is higher, the lower the education level, as shown by the lower proportion
% who end up with no birth (also refer to appendix figures)
% - no evidence of sex selection for lower educated women (both sex ratios and survival
% curves show this)
% - no sex selection on first birth, no matter the education level
% - sex ratio at birth is 105/100, showing no differences between India and other places

\subsection{One Son or Many Sons?}

In the discussion of declining fertility I rely on sex selection not being used by 
families that already has one son.
The extent to which this holds is of interest for two reasons.
First and foremost, it can help us understand what form son preference takes in India.
This is important in itself, but especially as we try to predict what will happen to 
fertility and sex selection use in the future.
Second,
if families use sex selection to reach two or more sons, progression rates for families 
with one son may overestimate the decline in fertility.

Women with 8 or more years of education is the group the most likely to use sex 
selection if they have no son as shown above.
Hence, if sex selection is also used to achieve more than one son, we should be
most likely to find evidence for this group of women as well.
Figure \ref{fig:boys_latest} therefore shows sex ratios and survival curves for 
the 1995--2006 period for urban and rural women with 8 or more years of education, 
conditional on having at least one son.
The first column shows outcomes for the second spell if the first born is a son,
the second column shows third spell when the first two children were a son and 
a daughter, and the third column shows third spell when the first two children were sons.

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[Spell 2 - 1 boy (N=3,969)]{
    \begin{minipage}{0.30\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[Spell 3 - 1 boy/1 girl (N=2,357)]{
    \begin{minipage}{0.30\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[Spell 3 - 2 boys (N=1,098)]{
    \begin{minipage}{0.30\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[Spell 2 - 1 boy (N=3,044)]{
    \begin{minipage}{0.30\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[Spell 3 - 1 boy/1 girl (N=1,819)]{
    \begin{minipage}{0.30\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[Spell 3 - 2 boys (N=790)]{
    \begin{minipage}{0.30\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth by quarter (3 month period) for women with 8 or more years
of education for 1995--2006. 
N is number of women in the relevant group in the underlying samples.
}
\label{fig:boys_latest}
\end{figure}

For the second spell the predicted sex ratios closely follow the natural sex 
ratio for both urban and rural women.
Furthermore, the survival curves follow the expected pattern if no sex selection 
is taking place.
% As discussed above the likelihood of having a second birth if your first child is a son
% is higher in rural than in urban areas, but even for urban women 65\% do have a second
% child by the end of the second spell period.
There is also no evidence of sex selection for the third spell for women with two sons;
the sex ratios follow the natural sex ratio for both urban and rural women.
Sample sizes are, however, less than \sfrac{1}{3} of the sample sizes for the second 
spell and the progression rate to a third birth is low at only 30\% for urban women and 
55\% for rural women, resulting in wide confidence intervals.
The survival curves are particularly flat for the first year, meaning that the apparent 
deviations from the natural sex ratio in the beginning of the spell are based on very few births.

% [Spell 3 - 1b/1g most interesting]

Even though there is no evidence of using sex selection to have an additional son when the 
previous children are all sons, it is possible that families want more sons than daughters 
and therefore use sex selection for the third spell when they already have one of each.
Urban women show little evidence of this being the case.
Although the sex ratio is above the natural from quarter 11 until the end of the spell,
only about \sfrac{1}{3} of the births occur in this interval.
Furthermore, the dip below the natural sex ratio prior to this point also accounts for
approximately \sfrac{1}{3} of the births.
Hence, these two parts cancel each other out.
With the first part being to the natural sex ratio the end result is that there
is little evidence for urban women using sex selection if they already have a son and
a daughter.

% Despite the larger sample size than for two sons, the results are based on only 
% approximately 700 births.
% urban: Based on about 700 births
% The first flat part is about 10\% of women 
% The dip below natural sex ratio accounts for close to 10\% of women
% The high part from 11 quarter onward account for the last 10\% of women
% That means that the dip and the high part approximately cancel each other out.

For rural women, however, the dip and the associated number of births is not
large enough to bring the overall sex ratio for the spell back to natural sex ratio.
The sex ratio for the entire spell is therefore likely more male dominated
than the natural rate, although it is only statistically significantly higher for two 
individual quarters of the spell.
There are two possible explanations for rural women appearing more likely than urban
women to use sex selection on the third spell if they already have a son and a daughter.
First, rural women could have a stronger son preference than urban women and want two sons 
rather than only one.
Second, mortality is higher in rural than urban areas and this higher mortality, either 
experienced or anticipated, make rural women use sex selection to secure a second son, 
essentially as an insurance.
%  much as royal British families have been know to aim 
% for an heir and a spare.
Separating these two possible explanations is difficult, but the ``heir and a spare''
explanation appears  more likely than difference in preferences given that urban women use 
sex selection more than rural women for the second birth in the absence of a son.
An alternative explanation is that what we are observing is simply random variation.
This would explain why we get see differences in sex ratios between urban and rural
women with one son across the third and fourth spells as shown in the online Appendix.%
\footnote{
Urban women with a son and two daughters as their first 3 births show a sex ratio
that is significantly higher than the natural, but no evidence of sex
selection if they have two sons and a daughter as their first children.
Rural women show only a marginally higher sex ratio with a son and two daughters and no 
effect at all with two sons and a daughter.
These results are, however, based on very small samples.
There are 590 urban women with a son and two daughters, of which less than 40\% have a
fourth child, 344 urban women with two sons and one daughter, and only 20\% of those
have a fourth child.
For rural women the numbers are 564, with 40\% having a fourth child, and 367 with
approximately 30\% having a fourth birth.
This comes to approximately 300 urban births and only slightly more for rural across
the two sex compositions.
}

Son preference can manifest itself through other channels than sex selection.
Differential investments in education and health across boys and girls, resulting in
lower education and higher mortality of girls relatively to boys, could be thought 
of as evidence of son preference, although \cite{rosenzweig82} argue that both may 
represent parents' rational response to market opportunities rather than inherent 
preferences of parents.
Whatever way son preference presents itself, it appears that the dominant  
preference---as expressed through use of sex selection---is for one son, rather 
than multiple sons.

\subsection{Predicted Lifetime Number of Children and Abortions}

One of the main advantages of the method proposed is that we can predict what 
completed fertility, total number of abortions, and the sex ratios will be for 
women in the samples at the end of childbearing. 
This cannot be done with the simple model because it does not predict fertility
progression, does not take into account censoring, and cannot capture if parents
change their use of sex selection within a spell.

The predictions are important for three reasons.
First, they allows us to quantify whether overall use of sex selection is 
intensifying or easing over time by examining how the total number of abortions 
women will have over their childbearing, and the resulting final sex ratios, change.
This is a more accurate representation than what we get from sex ratios 
for individual parities.
As the theory section shows, it is possible to get no change---or even a 
decline---in use of sex selection for an individual parity, at the same time 
as the overall use of sex selection is increasing.
Second, completed fertility and sex ratios are what matters when examining the future 
impacts of sex selection in areas such as the chance of finding a spouse, savings 
behavior, and the potential problems associated with a surplus of bachelors 
\citep{lancaster02,Ding2009,Wei2009,Edlund2013}.
% In other words, this tells us both how much sex selection is used and what the final 
% outcome will be.
% [Final outcome is what matter for things like access to a spouse and associated 
% problems - crime, etc]
Finally, as I show in the online Appendix and discuss above, relying only on observed 
sex ratios of recorded births is problematic because these are based on selection and 
the observed sex ratio may be biased predictors of final sex ratio when people change 
their use of sex selection during a spell.

% 1. it tells us what fertility and the final sex ratio will be, which helps put the individual
% spells and sex compositions in perspective.
% 
% 2. presumably what we care about is what the end result will be.
% 
% 3. Makes it easier to see whether use of sex selection is intensifying or easing over
% time.
% 
% 4. "What actually happens" is based on a select sample. Maybe refer to the appendix
% on comparing the simple and the hazard models here.

Table \ref{tab:predicted} shows predicted birth progression rates, number of abortions, 
sex ratios, and completed fertility for the three samples of women with 8 or more years 
of education:  
the 11,271 women who were married in the the 1972-1984 period,
the 19,072 women who were married in the 1985--1994 period,
and the 16,620 women who were married in the 1995--2006 period.%
\footnote{
These are the women used to estimate the results for the spell from marriage to first 
birth above.
For more information see Table \ref{tab:des_stat1}.
}
Predictions for each period assumes that behavior remains constant and that all spells 
a woman goes through are within the same period. 
Each woman is assumed to follow the fertility and sex selection behavior for 
each spell up to and including the fourth spell using the period's estimates and her 
characteristics. 
All results are for women predicted to have one or more births.%
\footnote{
This means that fertility predictions are larger than standard estimates, which include
women with no children.
Working in the opposite direction is that number of children is restricted to be at most 
four.
}

The predictions are done as follows.
Starting with the first spell I calculate each woman's probabilities of having a boy,
$P(b_t)$, a girl, $P(g_t)$, or no birth, $1-P(b_t)-P(g_t)$, in each quarter after marriage
based on the period results for 
equations (\ref{eq:probability_boy}) and (\ref{eq:probability_girl}) using her individual 
values for $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$.
She then is assigned one of these outcomes---boy, girl, or no birth---based on random 
draws from a uniform distribution.
The first quarter she has a draw that results in a birth she leaves the spell
and the quarter reached is used to calculate her starting age for the second spell.
If she has no draw that result in a birth by the end of the spell her childbearing 
stops and she does not enter the next spell.
If she does have birth, the process is repeated for the second through fourth spells.
Randomization is necessary because each spell's results, except for the first, depends on
the sex composition of previous children and the duration of the first spell. 
The results presented are averaged outcomes over all urban women and all rural women 
using 1,000 repetitions.

Birth progression rates are the percentage of women predicted to have a birth 
by the end of each spell.
Fertility is the average number of children born according to the randomization.
With the large number of replications this number is the same as using progression
rates at the end of the spell to calculate the average number of children.%
\footnote{
Given that all numbers are conditional on having at least one child, using progression
rates for, say, urban women from the 1985-1994 period leads to 
$1+1\times0.782+1\times0.782\times0.499+1\times0.782\times0.499\times0.448=2.3 $  
children.
}

For abortions I first calculate each quarter's probability of abortions using
$\frac{100}{105}P(b_t)-P(g_t)$,
where $\frac{100}{105}P(b_t)$ is the probability of having a girl that should have 
prevailed in the absence of sex selection (0.952 girls born per boy).
This probability is multiplied with the probability of not having had a birth yet at 
the beginning of the quarter.
Abortions for each spell are then found by summing over the entire spell.%
\footnote{
One way to see how this works is to imagine that we start the spell with 100 women.
After the first quarter we are left with $N_2 = (1-P(b_1)-P(g_1)) \times 100$, where
$N_2$ is the number of women who start the second quarter. 
After the second quarter we then have $N_3 = (1-P(b_2)-P(g_2)) \times N_2$, etc.

Say that 65.88 women of the original 100 still have not had a birth yet by the start
of quarter 6 and that the predicted probability of having a son in quarter 6 is 0.0931 and 
the probability of having a girl is 0.0566 (the probability of not having a birth in 
quarter 6 is 0.8503).
For this quarter the abortion probability is then 
$\frac{100}{105}\times 0.0931 - 0.0566 = 0.0321$.
In other words, the probability of having a girl should have been 
$\frac{100}{105}\times 0.0931 = 0.0887$, but only a probability of $0.0566$ was 
predicted.
Hence, in quarter 6 the predicted number of sons born is $ 0.0931 \times 65.88 = 6.13$, 
the predicted number of daughters born is $ 0.0566 \times 65.88 = 3.73$, and 
$0.0321 \times 65.88 = 2.11$ abortions must have taken place to reach these births.
% From anSimulate_test for spell 4, line 44
% If only given a percent and to find the number of abortions the formula is
% abortions = (10,000-205*percent girls)/105.
% This is because one less abortion would add an additional birth so that
% (number of girls + abortions)/(100 + abortions) = 100 / 205
}
To account for random variation, the abortion rate is the sum over both positive 
(more boys than the natural rate) and negative (more girls than the natural
rate) values of the abortion calculation within the spell.
% This sum is the predicted probability of having an abortion for a woman with the given
% set of characteristics.
Finally, the percentage of children born that are boys is based on the randomization of
births described above.%
\footnote{
This number is the predicted sex ratio at birth and differ from actual observed sex 
ratios when the children are older because of mortality.
On one hand, the anticipated or experienced death of a son increases the likelihood
of sex selection even if parents already had a son, which would make the later observed 
sex ratio lower than what is predicted here. 
On the other hand, mortality risk is higher for girls than for boy, which would make
the sex ratio more male dominated.
}

\begin{table}[htbp]
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
Abortions for Women with 8 or More Years of Education}
\label{tab:predicted}
\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
\midrule
\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
Spell 2          &       85.9   &  2.0    &  1.8    &  52.3   &       78.2   &  4.7    &  3.7  &  53.7   &       68.0   &  8.0    &  5.4   &  55.3      \\
Spell 3          &       64.4   &  5.1    &  3.3    &  53.9   &       49.9   &  9.8    &  4.9  &  56.2   &       38.6   &  7.8    &  3.0   &  55.3      \\
Spell 4          &       57.0   &  2.8    &  1.6    &  52.6   &       44.8   &  2.6    &  1.1  &  52.6   &       33.7   &  21.8   &  7.3   &  62.3      \\
Overall\tnote{d} &       2.7    &  2.0    &  5.5    &  52.3   &       2.3    &  3.4    &  8.0  &  53.1   &       2.0    &  4.6    &  9.4   &  53.7      \\
\addlinespace 
\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
Spell 2          &       92.5   &  -1.4   &  -1.3   &  50.5   &       87.6   &  3.1    &  2.7  &  52.8   &       83.1   &  4.4    &  3.6   &  53.5      \\
Spell 3          &       80.9   &  2.6    &  2.1    &  52.5   &       70.6   &  6.5    &  4.6  &  54.5   &       59.6   &  10.6   &  6.3   &  56.7      \\
Spell 4          &       75.7   &  -3.1   &  -2.4   &  49.6   &       62.0   &  0.2    &  0.1  &  51.3   &       51.9   &  6.1    &  3.2   &  54.4      \\
Overall\tnote{d} &       3.2    &  -0.3   &  -1.1   &  51.2   &       2.9    &  2.4    &  6.8  &  52.8   &       2.6    &  4.1    &  10.5  &  53.4      \\
\bottomrule
\end{tabular}                        
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
The samples consist of all women from the data with 8 or more years of education who
married during the indicated period using the estimation results for that periods 
and the women's characteristics at the start of their marriage. 
All numbers presented are for women predicted to have one or more births.
Birth/progression rates are based on the ratio of women predicted to have a birth 
by the end of each spell.
Abortion rates within each spell are based on the predicted number of abortions each
woman would have if she went through the entire spell.
To generate conditions such as sex composition and fecundity for second and higher spells 
each woman is randomly assigned outcomes based on the estimation results and
her characteristics as follows.
For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
She is assigned one of these outcomes based on a random draw from a uniform distribution.
The first quarter where she has a draw that results in a birth she leaves the spell
and the quarter reached is used to calculate her starting age for the subsequent spell.
If she has no draw that result in a birth within a spell her childbearing stops and
she does not enter the next spell.
Results are averaged over 1,000 repetitions.
\item[a] For individual spells the column shows the percent of women who started the
spell and ended up with a birth by the end of the spell period covered.
For the ``Overall'' row, the number is the expected number of children born per woman over 
the first four spells, conditional on having at least one birth.
\item[b] For individual spells the column shows the number of abortions per 100
births predicted to take place by the end of the spell.
For the ``Overall'' row, the number is the total number of abortion per 100 births 
predicted to take place over all four spells.
\item[c]  For individual spells the column shows the number of abortions 
predicted to take place by the end of the spell per 100 women who started the spell .
For the ``Overall'' row, the number is the total number of abortion 
predicted to take place over all four spells per 100 women who had at least one child.
\item[d] Covers first through fourth spells. 
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}

The results show a substantial reduction in fertility over time.
% The percentage women with a birth by the end of each spell, conditional to making
% it to the beginning of the spell, has decreased more than
% 10 percentage points between the two periods.%
% \footnote{
% The exception is rural women's second spell, where the reductions between periods
% were 4.9 and 4.5 percentage points.
% }
Predicted completed fertility went from 2.7 for urban women married in  
the 1972--1984 period to just 2 for urban women married in the 1995--2006 period.
Hence, urban fertility is now below replacement, especially considering that
these predictions are conditional on having at least one child.
Rural women showed a similar decline in completed fertility, going from 3.2 to 2.6.
Corresponding to the decline in overall fertility, there were also substantial
reductions in the individual parity progression rates.
For example, urban women with 3 children went from having a 57\% chance of having a 
4th child for the 1972--1984 cohort to a 33\% chance for the 1995--2006 cohort---and 
they had a substantially lower probability of even making it to 3 children
in the first place.

Associated with the decline in completed fertility is an increase in sex selection.
For urban women the predicted number of abortions per 100 women by the end of
childbearing have gone up by over 17 percent between the last two cohorts (8.0 to 9.4) 
and the number of abortions per 100 births have gone up by over 35 percent (3.4 to 4.6).
% The reason the percentage change per birth is higher than per women is the
% combination of falling fertility and more intense use of sex selection.
For rural women, abortions per 100 women increased almost 55 percent (6.8 to 10.5), 
while abortions per 100 births increased over 70 percent (2.4 to 4.1).%
\footnote{
Unfortunately there are no solid official estimates to compare these numbers to.
The total number of abortions per year, not just those based on son preference, vary 
between the official count of 600,000--700,000 
and an estimate of 6.4 million from the 2002 Abortion Assessment Project-India.
The 6.4 million abortions per year may even be an underestimate \citep{Stillman2014}.
NFHS does ask about abortions in all three surveys, although the questions change 
substantially between surveys.
However, the PNDT act prohibits using prenatal diagnostic tests to determine a fetus' sex
and revealing a fetus' sex to parents.
Hence, respondents have a strong incentive not to disclose abortions motivated by son 
preference. 
In addition, abortion are considered a taboo subject and many women are unwilling or 
uncomfortable reporting their abortions to government sponsored enumerators 
\citep{Rossier2003,Stillman2014}.
}
The combined effects of the declines in fertility and increased use of sex selection
are that the percentage boys increases from 53.1 to 53.7 percent for urban
women, and from 52.8 to 53.4 percent for rural women.

Of particular note is the high number of abortions among rural women for the 
1985--1994 period.
Educated rural women obviously had few constraints on access to 
prenatal sex determination even when the techniques were relatively new.
The higher abortion rate per woman for rural women than urban women likely comes from
a combination of higher likelihood of having an additional child and changes in use of 
sex selection within spell as shown in the graphs above.

The results from theoretical model showed that it is possible for the use of sex 
selection to fall for an individual parity, even as overall use of sex selection 
increases. 
This is the case here, where the use of sex selection fell for the third spell 
from 9.8 per 100 births to 7.8 for urban women between the last two periods.
As already discussed, total use of sex selection went up between the last two
periods, so the reduction for the third spell is not an indication of reduced 
use of sex selection overall, but simply the result of fewer women making it to a 
third birth and those who did were more likely to already have a son---for 
the second spell the number of abortions per 100 births for urban women 
went from 4.7 to 8.0, a 70 percent increase.%
\footnote{
The amount of sex selection in the fourth spell reinforces this point:
abortions per 100 births went up almost tenfold.
Only 26 percent of urban women with at least one child make it to the beginning 
of the fourth spell in the last period, and less than 10 of all women have a fourth birth, 
but for those who do make it to the fourth spell the pressure to ensure a son is large.
}
This underscores why focusing exclusively on individual parities can be misleading.

The results for rural women illustrate the two different strategies for achieving one
son: either have many children or have few children and use sex selection.
For the 1986--1994 period there is no use of sex selection on fourth birth, which fits
with 62 percent of women end up with three or more children and a full 62 percent of women with 
three children have a fourth birth (recall that there is a 94 percent chance of having at 
least one son if you have four children).
The use of sex selection on second and third spells indicates that one group of rural
women follows the high fertility route, whereas the other group follows the pattern of
urban women and combine restricting fertility with use of sex selection.

% how many even make it to spell 4? 39 percent for 1st period for urban. only 26 percent 
% for second period (and more likely to have a boy by then).
% compare to rural: 62 percent first period, 50 percent second period.

Another way to see the spread of access to sex selection over time is to compare
urban women in the first period with rural women in the last period.
At 2.7 fertility is already relatively low for urban women in the 1972--1984 period and 
there is some evidence of sex selection for these women.
As discussed in Section \ref{sec:spell_def}, the higher than natural sex ratio for
urban well-educated women this early is likely a combination of early access to prenatal
sex determination and that some of the spells end in the 1985--1994 period when there 
was more widespread access.
Rural women in the 1995--2006 period had a fertility only slightly lower than that
of urban women in the 1972--1984 periode, but the number of abortions both per birth and 
per woman were twice as high.
% For rural women, however, the overall sex ratio is the same as the natural for the
% first period and predicted completed fertility is 3.2, which is likely a lower-bound
% estimate since the estimates did not incorporate parities higher than 4.
% In the last period, rural women have higher fertility than urban women and therefore need 
% fewer sex-selective abortions to ensure a son, but given differences in fertility
% the numbers of abortions for rural women are not far behind those of urban women.

For comparison Appendix Tables \ref{tab:predicted_low} and \ref{tab:predicted_med}
show predicted fertility, number of abortions, and sex ratio for the two other
education groups.
As expected, fertility for women with no education is substantially higher
and the decline over time much smaller than for the high education group.
Predicted fertility fell from 3.6 to 3.3 for urban women and from 3.7 to 3.5 for rural 
women between the 1972--1984 and the 1995--2006 periods.%
\footnote{
A caveat is that my estimates did not cover parities higher than 4, which could
bias downward the change in predicted fertility.
}
Consistent with the discussion above, there is evidence of sex selection for neither
urban nor rural women, with the sex ratio for all predicted births in the last two periods 
close to normal.%
\footnote{
The higher than normal sex ratios for the 1972--1984 period are most likely
remnants of recall error not removed by the sample restriction. 
}
Random variation makes it appears that some individual parities had a higher
than normal sex ratio, which, if studied in isolation, could be taken as evidence
of use of sex selection, and reinforces why supplementing analysis of individual 
parities with this analysis of the overall pattern is important.

Fertility for women with between 1 and 7 years of education was slightly lower than the 
no education group in the 1972--1984 period, but the decline over time was larger.
For the 1995--2006 period predicted completed fertility was 2.8 for urban women and
3.2 for rural women.
There is only limited evidence of sex selection for urban women in this education group.
The exception is for rural women in the last period where the overall sex ratio is
52.1\% boys, although given the high fertility for this group and the small sample
size for this education group it is unclear whether this simply reflects random variation.

% [women in no education group:
% I: 30,004 (25,486 rural)
% II: 27,669 (23,360 rural)
% III: 9,684 (7,922 rural)
% 
% check how many women in urban vs rural sample for 1-7 years of education group: 
% I: 11,162 (7,496 rural)
% II: 13,104 (9,000 rural)
% III: 7,510 (5,208 rural)
% ]

The predictions discussed here provide further support for the idea that there are 
two alternative strategies to ensure the birth of a son, either have many children 
or use sex-selective abortions.
The best educated group mostly follow the low fertility, high use of sex selection
strategy, whereas the two lower education groups still have relatively high fertility
and little to no use of sex selection.
It is, however, clear that fertility is declining over time for all groups.
With lower fertility in both urban and rural areas, we are likely to see 
further increases in the use of sex-selective abortions among those who already
use sex selection, and among the groups who have not previously use sex selection
we will see beginning use of sex-selective abortions.

% \subsection{Regional Results}
% 
%      2 "Andhra Pradesh"
%      3 "Assam"  
%      4 "Bihar"
%      5 "Goa"
%      6 "Gujarat"
%      7 "Haryana"
%      8 "Himachal Pradesh"
%      9 "Jammu"
%     10 "Karnataka"
%     11 "Kerala"
%     12 "Madhya Pradesh"
%     13 "Maharashtra"
%     14 "Manipur"
%     15 "Meghalaya"
%     16 "Mizoram"
%     17 "Nagaland"
%     18 "Orissa"
%     19 "Punjab"
%     20 "Rajasthan"
%     21 "Sikkim"
%     22 "Tamil Nadu"
%     23 "West Bengal"
%     24 "Uttar Pradesh"
%     30 "New Delhi"
%     34 "ArunachalPradesh"
%     35 "Tripura"
% 
% egen north = eqany(state), v(7 8 9 19 20 30)
% egen central = eqany(state), v(12 24 4)
% egen west = eqany(state), v(5 6 13)
% egen east = eqany(state), v(18 23 3 14 15 16 17 21 34 35)
% egen south = eqany(state), v(2 10 11 22)
%

\section{Conclusion\label{sec:conclusion}}

% 1. how to interpret stated son preference from survey data and especially whether son
% preference is declining over time.
% 
% In NFHS, and DHSs in general, son preference is measured as part of the general fertility
% questions, where the first question is how many children a woman would have if she
% could choose exactly how many to have.
% This if followed by the sex preference question:
% ``How many of these children would you like to be boys, how many would you like to be girls 
% and for how many would the sex not matter?''
% The problem here is that if parents want one son, but will do pretty much anything to get
% that son, this will not be captured by this question.
% In that case, any changes over time in the answers to this question will only reflect 
% a true change in son preference if the respondents answer something less than 1 for boys
% and allocate all to ``either''.

% 2. it affects how we think about future developments in sex ratios and use of 
% sex selection as fertility falls further.
% 
% This is of more than theoretical interest.
% If son preference is expressed as a very strong preference for having at least one
% son then any further reductions in fertility will lead to a further increase in the use 
% of sex selection.
% This matter not only for well-educated rural women, who have higher fertility than 
% urban women, but are catching up quickly.
% The main concern is what happens when fertility fall below 4 for women with little or
% no education. 
% So far, there is little evidence for sex selection for these groups, but if they hold
% similar preferences to the better-educated women and experience a reduction in 
% desired fertility it is more than likely that they will begin using sex selection on 
% a large scale.

% 3. it is important when trying to understand what is behind son preference.
% If it is only one boy the argument on dowry does not seem to make much sense.
% Especially since sex-selective abortions are concentrated among the wealthy households.
% 
% An oft-repeated, but poorly substantiated, argument for why there is son preference and 
% especially sex selection in India is the presence of dowry practices, where the bride's 
% family pays the groom and/or the groom's family for taking their daughter in marriage.
% This explanation, however, fits poorly with the observed behavior.
% Sex selection is predominantly used by wealthier households and if only used to secure
% one son there is little support for the dowry explanation.
% If dowries were the main driver behind sex selection we would rather expect poorer
% households to use sex selection and use it to achieve a higher number of sons than
% daughters.
% For example, a family with 1 son and 2 daughters should use sex selection on the next
% birth to at least ensure a break-even in terms of dowry payments and receipts.
% Similarly, we would expect at least some families to use sex selection to ensure that
% they come out ahead as a family in terms of how much dowry they receive compared to
% how much is being paid out.
% 
% This is important because banning dowries should have little influence on the use of
% sex selection if sex selection is only used to ensure one son.

% \citet{clark00} p. 100 uses the number of sons, daughters, either question in her paper
% as a dependent variable.
% 
% \citet{Jensen2009} QJE paper uses a question about the sex of the next child (if want
% more children)
% 
% \citet{Hu2015} uses ratio of ideal number of son to ideal number of daughters

% May make sense to change son preference question to be minimum number instead of ideal 
% number: What is the minimum number of sons you would like? What is the minimum number of 
% daughters you would like?
% 
% Might be a paper in this somewhere about changes in fertility and what exactly we can
% learn from these son preference question.
% Clark does argue that her calculated measure is a minimum proportion of sons 
% desired, but, of course, this is neither here nor there if there is an absolute
% minimum number of sons desired.
%

% [future research - importance]
% girls may now have a much longer space before their next sibling
% 
% fertility will look lower because of increased spacing
% 
% potentially better health for those girls that are followed by sex-selective abortions
% because of the longer space (although these are also generally born into the 
% wealthier families)
% 
% who the agents are
% 
% \cite{das_gupta09a}
% 
% \cite{Klasen02}

% [Hence, the decline in fertility is an indicator that girls are not relatively more
% expensive than boys.
% 
% only one boys also suggests that use of sex selection is not roted in the cost
% of girls (dowries).]
% 
% 
% [original from here]
% [EXPAND ON MODEL AND ITS IMPORTANCE - MORE ON PROBLEMS WITH LOGIT AND NOT USING ALL INFORMATION 
% SEE RETHERFORD AND ROY PAPER]

If women have preferences over both the number of children they have \emph{and} the sex 
composition of these children, they face a trade-off between the cost---both monetary 
and psychological---of sex selection and the cost of children.
This paper introduces a novel approach to understanding the relationship between
fertility and use of sex selection, and how sex selection interact with birth spacing.
The proposed method allows for joint estimation of fertility and sex-selective abortions 
using a non-proportional, competing risk hazard model.

Three results stand out.
First, lower fertility is an important factor in the decision to use sex-selective abortions.
% Women wanting more than two births did not use sex selection on the second birth, while
% those who want two or fewer use sex selection intensively.
In both urban and rural areas, only women with the lowest predicted fertility---those
with 8 or more years of education---use sex selection, and as fertility falls they use it 
for earlier parities.
Women with less education instead follow a high fertility strategy to ensure they have
a son and do not appear to use sex selection.
Previous research was unable to explain why sex selection in India only occurred 
among higher education women because it failed to tie the use of sex selection and the 
fertility decision together.

Second, the legal steps taken to combat sex-selective abortion have not been able
to reverse the practice.
The use of sex selection has been increasing over time and is higher now than before the
PNDT Act was passed.
The predicted number of sex-selective abortions per 100 women during their childbearing 
years is now around 10 for women with 8 or more years of education in both urban and
rural areas.
This is especially interesting given that the cost of prenatal sex determination 
has likely increased in response to the PNDT Act.
This also emphasizes why accounting for the possibility that parents may change
their decision to use sex selection within a spell is important. 
As the theory shows an increase in the cost of prenatal sex determination 
increases the likelihood of parents changing their decision to use sex selection.%
\footnote{
% This trade-off is also evident within spells.
A feature of the new approach is that it allows for changes in the decision 
to use sex selection within a spell.
This is most clearly seen for better-educated urban women whose only child is a girl, 
for whom the use of sex selection declines as the second spell becomes longer.
% The result is that the simple model predicts a substantially higher percentage of boys
% born than the hazard model, because the standard model cannot take into account
% censoring and changes within spells.
% The simple model also failed to fully captured the increased access to prenatal 
% sex determination for urban women and therefore underestimated the final sex ratio for
% third children in the period before the PNDT Act was passed.
}

Third,  there is little evidence that women with one or more sons use sex selection,
and their probability of another birth declines substantially once they have a son.
The main exception is for rural women with one son and one daughter, presumably as an 
insurance against mortality.
Hence, parents appear to have a preference for one son rather than multiple sons.

These results imply that the way we have been measuring son preference may not be useful
for understanding how people make decisions on use of sex selection.
Recent research suggests that son preference in India, when measured as ideally having 
more boys than girls, is decreasing over time and with higher education \citep{bhat03,pande07}.%
\footnote{
This measure of son preference is commonly used in the literature. 
See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
In NFHS, and Demographic and Health Surveys in general, son preference is measured as part 
of the general fertility questions.
The first question is how many children a woman would have if she could choose exactly how 
many.
This if followed by the sex preference question:
``How many of these children would you like to be boys, how many would you like to be girls 
and for how many would the sex not matter?''
}
Despite this, use of sex selection has increased and for exactly the group 
argued to show declining preference for sons.
The culprit may be that parents want \emph{one} son and will use sex selection 
intensively to get that son, but refrain from using sex selection to have more sons, 
and our standard measure of son preference cannot captured that.
% In fact, any changes over time in the answers to this question may only reflect 
% a true change in son preference as it relates to sex selection if the respondents answer 
% something less than 1 for boys and allocate all to ``either''.
A better approach may be to directly ask if there is a minimum number of each sex that 
respondents want, possibly in combination with ideal number questions.

This is of more than theoretical interest.
If son preference is expressed as a very strong desire for having at least one
son then reductions in fertility will lead to a further increase in the use of sex 
selection across all groups that hold that preference.
What is more, as shown in the theory section, it is possible to get increasingly
unequal sex ratio when fertility falls even if parents do not want more sons
than daughters as long as they only use abortion on female fetuses.
A deeper understanding of exactly what type of son preference is responsible 
for the increase use of sex selection is clearly an important question for
future data collection and research.

% The findings also have implications for our understanding of the relation between
% the marriage market and sex selection.

An often-repeated, but poorly substantiated, argument for why there is sex selection 
in India is the dowry system.
This explanation fits poorly with observed behavior.
If true, dowries increase the cost of having girls relative to boys because you have to 
pay to ensure your girls are married.
This implies that poorer households should be the most likely to use sex selection, and 
that the use of sex selection should increase the more girls they have.%
\footnote{
The exception would be if dowries increase more than proportionally with education level 
and income, but there does not appear to be evidence of this.
} 
Similarly, for all households there would be a financial incentive to achieve a higher 
number of sons than daughters.
As shown here, however, sex selection is predominantly used by better educated and 
therefore, on average, wealthier households and only to secure one son rather than multiple 
sons.
Finally, fertility's rapid decline after the introduction of prenatal sex 
determination, combined with low cost of sex selection, suggests that parents'
perceived costs of boys and girls are similar.%
\footnote{
See the discussion in Section \ref{sec:changes} for more detail.
}
Hence, banning dowries, as India has done, is unlikely to affect the use of sex 
selection. 
% Recent data with information on both birth histories and average dowries within 
% areas allow for a direct test of this relationship, making this a worthwhile area for 
% future research.

The results presented here lead to a number of important questions for future research.
One is whether marriage market sex ratios affect the use of sex selection.
Parents may care not only about the number and type of children they have but 
also whether they will have grandchildren.
If they care about grandchildren, then a boy could still be preferred over a girl, but a 
married girl would be preferred over an unmarried boy \citep{Bhaskar2011}.
The implication is that parents respond to changes in the expected sex ratio of their
children's marriage market, even given their preference for a son.
This hypothesis can be tested using measures of the observed distributions of
boys and girls and the method proposed here.

A second question for future research, which is especially important when designing 
policies aimed at reducing the use of sex selection, is who the agents are in the decisions 
to use sex selection.
Here, I have treated the household as a single unit, but it is possible, and indeed likely, 
that husband and wife have different preferences over both the factors that determine  
use of sex selection and sex selection itself.
Some of the popular press have assumed that the decision to use sex selection rests 
with the husband.
This, however, does not fit well with the general pattern that women, on average, prefer to 
have fewer children than men do and that declining fertility appear to be the main
driver of sex selection.
A better understanding of who holds what preferences in the family would be a good 
first step to disentangling who makes decisions about sex selection.

% The implication is that the decision to use sex selection rest with the woman given the 
% other constraints she faces, such as potentially a strong preference for a son in 
% the rest of the family.

% [METHOD CAN BE USED TO ESTIMATE EFFECT OF SSA ON CHILD OUTCOMES: 
% PREDICT PROBABILITY THAT SSA HAS BEEN USED AND USE THIS PROBABILITY AS
% AN EXPLANATORY VARIABLE IN CHILD OUTCOMES.
% SINCE SSA MAINLY USED BY HIGHLY EDUCATED WOMEN WHO ARE ALSO LESS LIKELY
% TO SUFFER CHILD MORTALITY THIS EFFECT IS LIKELY TO BE SMALL BUT WOULD BE
% INTERESTING TO SHOW.
% CAN ALSO BE EXTENDED SO THAT THE PREDICTED USED OF SSA IN AN AREA AMONG
% THE well-educated CAN BE USED TO EXPLAIN CHILD OUTCOMES FOR OTHER GROUPS.]

A third question is whether there are interactions between sex selection and child outcomes,
such a survival and education.
It has been argued that access to sex selection may benefit girls because those girls
who are born are more likely to be wanted by their parents.
For mortality it is, however, possible that improvements are the result of a purely 
mechanical effect.
As I have shown, increased use of sex selection lengthens the birth spacing after a girl 
and that by itself can improve her survival chances, even if she is no more wanted than before.
The method suggested here can predict the likelihood of a woman using prenatal sex 
determination for a given birth based on her characteristics.
This predicted probability can then be used in estimations of the determinants
of child health to directly test whether increasing use of sex selection is 
beneficial for the girls who are born.
It is unlikely, however, that a substantial mortality effect exists since sex 
selection is mainly used by well-educated women, who tend to have lower mortality, 
but there might be effects on education investments.
% The method can, however, also be extended to other outcomes, such as education,
% or the use of sex selection can be predicted for a geographical area and the 
% predicted use for the area can then be used as an explanatory variable.

% [developments in the future]
In conclusion, the results provide strong clues to how sex selection use will change in the future.
Because lower fertility is responsible for the increase in sex-selective abortions, 
it is likely that we will see further increases in the practice as more families 
want fewer children, either because of urbanization or because of increases in female 
education.
With already low fertility for better-educated urban women, a substantial future increase 
in sex-selective abortions per woman is unlikely, 
but a higher proportion of women will belong to this group in the future.
For rural, better-educated women fertility is still falling.
To the extent that it falls to the same level as for urban
women, I expect a corresponding increase in sex selection.
Finally, and most importantly, we are beginning to see evidence of lower fertility 
for women with lower levels of education.
If women with less education hold the same preference for one son as the better-educated,
once the less-educated women's fertility begins to drop to three---and even two---we are 
likely to see a substantially increased use of sex selection in India.

% why interesting/important:
% - prediction about future development
% - effect of unequal sex ratio on individual child (survival, education, marriage)
% - effect of unequal sex ratio on society
% - morbidity/mortality from abortions
% - secondary sterility, abandonment, remarriage

% [to be added]
% In summary, the purpose of this project is to develop an empirical 
% method that can contribute to an understanding of the changing sex ratio at birth in India.
% Beside being of intrinsic interest, this first step is likely to have a 
% significant impact on future analyses in areas such as child health and
% mortality, maternal mortality, female abandonment and changes in the marriage markets.
% These are important areas for future research.

% [MOVE TO CONCLUSION?]
% A second issue is that the model estimates the progression from one birth to
% the next and not the complete fertility path.
% This ignores any potential sample selection problems that might
% arise from not all women making it to a given parity.
% With the exception of the first spell, a woman must have had enough children 
% to be observed in a particular spell.
% Women with long previous spells, possibly because of sex selection,
% are therefore less likely to be observed.
% One possible solution is to model the selection problem directly,
% for example, by ``weighting'' observations by the inverse of the 
% probability that the observation is observed.
% This is an important area for future research.

% Although solid data are generally not available the effects of abortions are 
% likely to be worse in developing countries than developed countries, especially if 
% the abortions are preformed outside the regular health care system or in the second trimester.
% Both are a significant concern in this case.
% Since sex-selective abortions are illegal it is entirely possible 
% that many of the abortions take place illegally.
% Furthermore, the use of ultrasound and amniocentesis means that the abortion
% will not take place until the second trimester.
% Understanding the impact of sex-selective abortions on the mother's health, subsequent
% fecundity and pregnancy outcomes are important areas for future research both in
% their own right and because of their impact on economic development.
% All of these will have adverse effects on children, their health and their human
% capital accumulation.
% This may, for example, happen when women die or are abandoned as a result of
% infertility.

% Problem  for understanding mortality as well.
% Selection problem will also affect analysis of mortality.
% For those with stronger son preference we are less likely to observe their
% children and those children born will be younger
% and hence it is less likely that those children will die.
% Same ideas as Pitt's articles on fertility selection for understanding mortality \citep{pitt97}.
% This problem becomes more important the closer to the survey date one gets.
% Hence, if ones want to examine a relatively recent change in policy this
% is especially important.
% This is even more so if the policy is prompted by increased use of sex-selective
% abortions as is likely in India.
% In other words, if the policy is implemented because sex-selective abortion is
% a problem (or an increasing problem) the policy can appear effective even though
% what is really happening is that we are not controlling for the fertility selection /
% sample selection that comes from use of SSA.
% Those with stronger son preference probably also have higher mortality of girls
% relative to those with lower son preference.
% reference to \citet{rosenblum09} paper on mortality that do not take account of
% this problem and \citet{das_gupta09a}.
% Also look for \citet{klasen02} to see what they do.
% Also, a problem for looking at macro level sex ratios (same Das Gupta et al. paper)

\newpage
\onehalfspacing
% \bibliographystyle{aea}
\bibliographystyle{aer}
% \bibliography{econ}
% \bibliography{library}
\bibliography{collection}

\addcontentsline{toc}{section}{References}

\clearpage
\newpage

\appendix
\section{Appendix}

% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}
\renewcommand\thetable{\thesection.\arabic{table}}    
\setcounter{table}{0}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_100}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.41 &  50.3 &  5.41 &  50.2 &  5.42 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.10 &  51.4 &  4.11 &  51.3 &  4.16 &  50.6 &  4.17 &  50.5 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.19 &  52.9 &  3.25 &  51.7 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  54.7 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  61.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.29 &  50.6 &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.26 &  53.3 &  5.37 &  51.5 &  5.40 &  50.4 &  5.41 &  50.1 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  57.8 &  4.10 &  52.6 &  4.10 &  51.4 &  4.11 &  51.2 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  57.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.8 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.27 &  60.7 &  2.31 &  59.5 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.14 &  54.2 &  7.26 &  51.4 &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  61.7 &  5.07 &  56.1 &  5.11 &  53.6 &  5.22 &  50.9 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  66.3 &  4.06 &  60.1 &  4.07 &  58.6 &  4.07 &  55.2 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  69.7 &  3.13 &  68.3 &  3.13 &  64.9 &  3.13 &  57.5 &  3.32 &  50.0 \\
 k = 20        &  2.68 &  67.5 &  2.25 &  61.2 &  2.25 &  61.1 &  2.25 &  61.1 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.09 &  62.8 &  7.13 &  57.5 &  7.19 &  53.9 &  7.26 &  51.7 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  73.9 &  5.05 &  66.6 &  5.07 &  61.9 &  5.08 &  58.5 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  74.9 &  4.06 &  73.0 &  4.06 &  68.8 &  4.07 &  63.3 &  4.17 &  49.9 \\
 k = 18        &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.5 &  3.13 &  68.3 &  3.32 &  50.0 \\
 k = 20        &  2.73 &  72.5 &  2.69 &  72.1 &  2.56 &  70.7 &  2.25 &  66.6 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  97.2 &  2.00 &  86.6 &  2.00 &  68.7 &  2.00 &  62.5 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_95}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.41 &  50.2 &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.11 &  51.3 &  4.16 &  50.7 &  4.17 &  50.3 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  53.9 &  3.25 &  51.9 &  3.25 &  51.7 &  3.25 &  50.0 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.0 &  2.50 &  55.0 &  2.50 &  54.7 &  2.50 &  52.6 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.1 &  2.00 &  59.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.30 &  50.1 &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.38 &  51.4 &  5.40 &  50.2 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  54.9 &  4.10 &  51.4 &  4.13 &  51.0 &  4.17 &  50.5 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.26 &  51.8 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.1 &  2.27 &  60.7 &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.27 &  51.2 &  7.33 &  50.1 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.06 &  58.0 &  5.14 &  52.7 &  5.22 &  50.8 &  5.25 &  50.1 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  59.0 &  4.06 &  57.8 &  4.07 &  52.6 &  4.08 &  51.2 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  69.0 &  3.13 &  64.8 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.27 &  60.7 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.11 &  58.4 &  7.23 &  52.2 &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  68.2 &  5.06 &  60.3 &  5.10 &  54.7 &  5.20 &  51.5 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  74.1 &  4.06 &  69.0 &  4.06 &  61.3 &  4.07 &  57.5 &  4.17 &  49.9 \\
 k = 18        &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  68.3 &  3.13 &  64.9 &  3.32 &  50.0 \\
 k = 20        &  2.71 &  72.4 &  2.56 &  70.7 &  2.00 &  62.5 &  2.00 &  62.4 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  85.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_90}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.16 &  50.7 &  4.17 &  50.5 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.25 &  51.9 &  3.25 &  51.8 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.0 &  2.50 &  54.7 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.3 &  2.00 &  56.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.17 &  50.5 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.16 &  53.5 &  3.26 &  51.8 &  3.28 &  50.9 &  3.32 &  50.0 \\
 k = 20        &  2.27 &  60.8 &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  53.8 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.1 &  2.00 &  56.2 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.10 &  53.4 &  5.24 &  50.5 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  58.4 &  4.07 &  52.2 &  4.10 &  51.0 &  4.13 &  50.5 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  66.8 &  3.13 &  54.0 &  3.14 &  53.8 &  3.26 &  51.8 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.28 &  60.3 &  2.50 &  55.0 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.3 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.16 &  53.9 &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  62.5 &  5.08 &  54.1 &  5.22 &  50.8 &  5.26 &  50.0 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  71.3 &  4.06 &  58.8 &  4.07 &  55.2 &  4.08 &  51.2 &  4.17 &  49.9 \\
 k = 18        &  3.13 &  69.9 &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  53.9 &  3.32 &  50.0 \\
 k = 20        &  2.64 &  71.6 &  2.00 &  62.5 &  2.00 &  62.5 &  2.01 &  62.3 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_85}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.42 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.16 &  50.6 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.25 &  51.9 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.40 &  50.2 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
 k = 16        &  4.16 &  50.7 &  4.17 &  50.6 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.14 &  53.7 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 &  3.32 &  50.0 \\
 k = 20        &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  52.6 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.24 &  51.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  52.2 &  4.13 &  50.7 &  4.14 &  50.4 &  4.16 &  49.9 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.14 &  53.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.31 &  59.5 &  2.50 &  55.0 &  2.52 &  54.4 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.13 &  58.1 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.31 &  50.7 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.07 &  54.9 &  5.24 &  50.5 &  5.26 &  50.0 &  5.27 &  50.0 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  59.0 &  4.07 &  55.2 &  4.10 &  51.0 &  4.17 &  50.1 &  4.17 &  49.9 \\
 k = 18        &  3.13 &  69.7 &  3.13 &  57.0 &  3.13 &  53.9 &  3.26 &  51.8 &  3.32 &  50.0 \\
 k = 20        &  2.00 &  62.5 &  2.00 &  62.5 &  2.01 &  62.2 &  2.25 &  55.5 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_100}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}  
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.6 &    0.0 &   54.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    3.1 &    0.0 &    8.4 &    2.6 &    0.0 &   28.5 &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . \\
 k = 16        &   12.4 &    0.1 &    3.9 &   10.9 &    0.1 &   23.5 &    5.5 &    0.1 &   12.9 &    4.7 &    0.1 &   25.6 \\
 k = 18        &   25.1 &    0.3 &    2.0 &   23.5 &    0.3 &   12.5 &   18.6 &    0.3 &   41.8 &   11.0 &    0.1 &   12.7 \\
 k = 20        &   25.3 &    0.3 &    0.2 &   25.1 &    0.3 &    0.8 &   24.4 &    0.3 &    3.2 &   23.6 &    0.3 &    6.4 \\
 k = 22        &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 &   48.7 &    0.5 &    3.2 &   44.0 &    0.5 &   12.6 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &    8.3 &    0.2 &   47.8 &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   35.0 &    0.5 &   24.5 &   16.7 &    0.3 &   38.3 &    4.4 &    0.1 &   45.4 &    1.6 &    0.0 &   51.2 \\
 k = 16        &   64.2 &    0.7 &   12.0 &   22.0 &    0.3 &   23.0 &   12.0 &    0.1 &    7.8 &   10.6 &    0.1 &   25.1 \\
 k = 18        &   44.1 &    0.6 &   22.6 &   25.2 &    0.3 &    1.1 &   25.0 &    0.3 &    2.2 &   24.1 &    0.3 &    7.9 \\
 k = 20        &   50.3 &    0.5 &    0.3 &   49.9 &    0.5 &    1.7 &   48.7 &    0.5 &    6.3 &   43.9 &    0.6 &   22.9 \\
 k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.1 &    0.5 &    0.4 &   49.9 &    0.5 &    0.9 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &   60.4 &    0.9 &   32.5 &   20.5 &    0.3 &   27.7 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
 k = 14        &  119.3 &    1.3 &   12.1 &   62.1 &    0.8 &   21.9 &   37.0 &    0.5 &   26.6 &   10.2 &    0.1 &   27.6 \\
 k = 16        &  133.6 &    1.7 &   20.4 &   82.8 &    0.9 &   10.1 &   70.2 &    1.0 &   32.7 &   43.0 &    0.6 &   33.1 \\
 k = 18        &  123.8 &    1.2 &    1.4 &  114.6 &    1.2 &    6.9 &   93.4 &    1.1 &   18.3 &   47.0 &    0.5 &   12.2 \\
 k = 20        &   94.3 &    0.9 &    0.0 &   50.3 &    0.5 &    0.1 &   50.2 &    0.5 &    0.5 &   50.0 &    0.5 &    1.1 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  182.2 &    2.2 &   16.8 &  108.0 &    1.4 &   25.0 &   56.7 &    0.9 &   40.2 &   25.2 &    0.5 &   50.1 \\
 k = 14        &  241.8 &    2.7 &   11.2 &  169.4 &    2.0 &   17.3 &  121.4 &    1.6 &   23.0 &   86.8 &    1.3 &   31.6 \\
 k = 16        &  203.9 &    2.1 &    3.2 &  188.2 &    2.0 &    7.9 &  154.2 &    1.8 &   16.2 &  109.7 &    1.3 &   14.6 \\
 k = 18        &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 &  122.2 &    1.2 &    2.5 &  114.5 &    1.2 &    6.9 \\
 k = 20        &  123.9 &    1.2 &    0.0 &  119.5 &    1.2 &    0.0 &  106.9 &    1.1 &    0.1 &   75.3 &    0.7 &    0.2 \\
 k = 22        &  189.4 &    2.0 &    4.4 &  147.3 &    1.8 &   17.6 &   75.1 &    1.3 &   39.9 &   50.3 &    0.5 &    0.1 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_95}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}  
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    3.0 &    0.0 &   16.7 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &   11.0 &    0.1 &   22.8 &    6.0 &    0.1 &    7.0 &    3.1 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
 k = 18        &   24.4 &    0.3 &    6.7 &   12.2 &    0.1 &    3.5 &   11.0 &    0.1 &   12.7 &    0.0 &    0.0 &      . \\
 k = 20        &   25.2 &    0.3 &    0.5 &   24.9 &    0.3 &    1.8 &   23.6 &    0.3 &    6.4 &   12.6 &    0.3 &   50.4 \\
 k = 22        &   50.1 &    0.5 &    0.4 &   48.7 &    0.5 &    3.2 &   37.7 &    0.5 &   25.4 &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &    1.2 &    0.0 &   27.5 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   15.6 &    0.3 &   46.0 &    2.8 &    0.0 &   14.1 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . \\
 k = 16        &   41.0 &    0.7 &   38.5 &   12.1 &    0.1 &    7.1 &    9.1 &    0.2 &   42.5 &    4.7 &    0.1 &   25.6 \\
 k = 18        &   25.2 &    0.3 &    0.6 &   25.0 &    0.3 &    2.2 &   23.5 &    0.3 &   12.5 &   11.8 &    0.1 &    6.4 \\
 k = 20        &   50.1 &    0.5 &    0.9 &   48.7 &    0.5 &    6.3 &   25.1 &    0.3 &    0.8 &   24.4 &    0.3 &    3.2 \\
 k = 22        &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 &   48.7 &    0.5 &    3.2 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &   18.3 &    0.2 &   23.7 &    2.0 &    0.0 &   51.9 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   82.1 &    1.2 &   30.9 &   28.5 &    0.5 &   38.1 &    8.3 &    0.2 &   50.1 &    1.6 &    0.0 &   51.2 \\
 k = 16        &   73.7 &    0.7 &    2.3 &   64.2 &    0.7 &   12.1 &   21.8 &    0.3 &   23.8 &   10.6 &    0.1 &   25.1 \\
 k = 18        &  119.3 &    1.2 &    4.2 &   92.6 &    1.1 &   19.5 &   25.1 &    0.3 &    0.8 &   24.7 &    0.3 &    4.0 \\
 k = 20        &   50.3 &    0.5 &    0.2 &   50.3 &    0.5 &    0.2 &   50.0 &    0.5 &    1.1 &   48.5 &    0.5 &    6.5 \\
 k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.1 &    0.5 &    0.4 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  120.8 &    1.7 &   30.9 &   31.9 &    0.4 &   23.7 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
 k = 14        &  184.4 &    2.5 &   25.6 &  105.0 &    1.3 &   17.7 &   48.5 &    0.8 &   37.5 &   16.6 &    0.3 &   50.3 \\
 k = 16        &  197.8 &    2.1 &    5.1 &  155.7 &    1.8 &   15.7 &   93.2 &    1.3 &   26.1 &   61.8 &    1.0 &   39.3 \\
 k = 18        &  125.3 &    1.2 &    0.5 &  123.8 &    1.2 &    1.4 &  114.5 &    1.2 &    6.9 &   93.3 &    1.1 &   18.3 \\
 k = 20        &  122.3 &    1.2 &    0.0 &  106.9 &    1.1 &    0.1 &   50.3 &    0.5 &    0.2 &   50.1 &    0.5 &    0.4 \\
 k = 22        &  144.2 &    1.8 &   20.8 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_90}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}  
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &    6.2 &    0.1 &    3.4 &    4.7 &    0.1 &   25.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 18        &   12.6 &    0.1 &    0.9 &   11.8 &    0.1 &    6.4 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 20        &   25.1 &    0.3 &    0.8 &   23.6 &    0.3 &    6.4 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 22        &   49.5 &    0.5 &    1.6 &   25.0 &    0.5 &   50.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &    0.3 &    0.0 &   26.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    3.1 &    0.0 &    8.4 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &   12.4 &    0.1 &    3.9 &    6.2 &    0.1 &    3.4 &    4.7 &    0.1 &   25.6 &    0.0 &    0.0 &      . \\
 k = 18        &   25.2 &    0.3 &    1.1 &   22.1 &    0.3 &   22.7 &   11.8 &    0.1 &    6.4 &    6.3 &    0.1 &   49.6 \\
 k = 20        &   48.7 &    0.5 &    6.2 &   25.2 &    0.3 &    0.5 &   24.4 &    0.3 &    3.2 &   18.9 &    0.3 &   25.0 \\
 k = 22        &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 &   48.7 &    0.5 &    3.2 &   25.0 &    0.5 &   50.3 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &    5.0 &    0.1 &   41.4 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   35.0 &    0.5 &   24.5 &    5.4 &    0.1 &   25.7 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . \\
 k = 16        &   69.1 &    0.7 &    7.0 &   18.7 &    0.3 &   41.8 &    9.1 &    0.2 &   42.5 &    4.7 &    0.1 &   25.6 \\
 k = 18        &  105.3 &    1.2 &   13.2 &   25.2 &    0.3 &    1.1 &   24.3 &    0.3 &    7.0 &   11.8 &    0.1 &    6.4 \\
 k = 20        &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    1.0 &   47.1 &    0.5 &   12.1 &   24.9 &    0.3 &    1.8 \\
 k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 &   49.5 &    0.5 &    1.6 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &   55.9 &    0.9 &   39.5 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &  127.6 &    1.4 &    9.0 &   42.1 &    0.5 &   21.3 &    8.3 &    0.2 &   50.1 &    0.8 &    0.0 &   50.3 \\
 k = 16        &  174.7 &    2.0 &   11.4 &   72.0 &    0.7 &    4.0 &   43.1 &    0.6 &   33.1 &   10.6 &    0.1 &   25.1 \\
 k = 18        &  124.8 &    1.2 &    0.8 &  119.3 &    1.2 &    4.2 &   47.0 &    0.5 &   12.2 &   24.7 &    0.3 &    4.0 \\
 k = 20        &  114.8 &    1.1 &    0.0 &   50.3 &    0.5 &    0.1 &   50.2 &    0.5 &    0.5 &   49.7 &    0.5 &    2.0 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_85}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}  
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &    5.8 &    0.1 &   15.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 18        &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 20        &   24.9 &    0.3 &    1.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 22        &   18.9 &    0.2 &    0.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    2.4 &    0.0 &   43.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &    6.3 &    0.1 &    1.9 &    5.2 &    0.1 &   28.9 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 18        &   23.7 &    0.3 &   12.0 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 20        &   25.3 &    0.3 &    0.2 &   24.9 &    0.3 &    1.8 &   12.6 &    0.3 &   50.4 &    0.0 &    0.0 &      . \\
 k = 22        &   50.3 &    0.5 &    0.2 &   49.1 &    0.5 &    3.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &    0.6 &    0.0 &   54.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   13.7 &    0.2 &   39.1 &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &   18.9 &    0.3 &   40.7 &    6.2 &    0.1 &    3.4 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
 k = 18        &   25.3 &    0.3 &    0.2 &   24.4 &    0.3 &    6.7 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . \\
 k = 20        &   50.2 &    0.5 &    0.5 &   44.0 &    0.6 &   22.7 &   24.9 &    0.3 &    1.8 &   22.0 &    0.3 &   12.5 \\
 k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 &   34.4 &    0.6 &   45.1 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &   10.3 &    0.1 &   24.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   50.8 &    0.7 &   31.2 &    5.8 &    0.1 &   15.2 &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . \\
 k = 16        &   73.7 &    0.7 &    2.3 &   43.2 &    0.6 &   32.7 &    9.1 &    0.2 &   42.5 &    1.6 &    0.0 &   51.2 \\
 k = 18        &  123.8 &    1.2 &    1.5 &   44.0 &    0.6 &   22.7 &   24.7 &    0.3 &    4.0 &   11.8 &    0.1 &    6.4 \\
 k = 20        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.3 &   49.5 &    0.5 &    3.4 &   24.9 &    0.3 &    1.8 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_spacing_r100_a05}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13} 
Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.50 &    10 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.25 &     7 &  1.50 &    10 &     . &     . \\
 4             &  1.00 &     1 &  1.00 &     1 &  1.12 &     6 &  1.01 &     3 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.00 &     1 &  1.03 &     3 &     . &     . &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.08 &     5 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.03 &     2 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.01 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.20 &     2 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.50 &     8 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.22 &     4 &  1.50 &     8 &     . &     . \\
 4             &  1.00 &     1 &  1.00 &     1 &  1.09 &     3 &  1.10 &     4 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.00 &     1 &  1.18 &     4 &     . &     . &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.06 &     3 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.10 &     2 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.49 &     6 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.13 &     2 &  1.49 &     6 &     . &     . \\
 4             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.32 &     5 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 &     . &     . &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.25 &     2 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.47 &     5 &     . &     . \\
 4             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.43 &     4 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.00 &     1 &  1.37 &     3 &     . &     . &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_spacing_r100_a055}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13} 
Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.38 &     3 &  1.50 &    10 &  1.50 &    12 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.24 &     6 &  1.06 &     8 &  1.00 &     2 &     . &     . \\
 4             &  1.00 &     1 &  1.12 &     5 &  1.40 &     4 &  1.00 &     1 &     . &     . &     . &     . \\
 5             &  1.03 &     2 &  1.21 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.01 &     3 &  1.10 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.04 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.49 &     7 &  1.50 &    10 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.19 &     3 &  1.25 &     8 &  1.02 &     4 &     . &     . \\
 4             &  1.00 &     1 &  1.09 &     3 &  1.03 &     5 &  1.00 &     2 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.01 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.18 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.01 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.47 &     5 &  1.50 &     9 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.25 &     7 &  1.06 &     5 &     . &     . \\
 4             &  1.00 &     1 &  1.00 &     1 &  1.12 &     5 &  1.01 &     2 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.03 &     2 &  1.03 &     2 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.03 &     3 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.38 &     3 &  1.50 &     8 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.24 &     5 &  1.20 &     6 &     . &     . \\
 4             &  1.00 &     1 &  1.00 &     1 &  1.09 &     3 &  1.03 &     2 &     . &     . &     . &     . \\
 5             &  1.00 &     1 &  1.00 &     1 &  1.16 &     3 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.04 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_spacing_r100_a06}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13} 
Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.49 &     6 &  1.50 &    10 &  1.50 &    12 &  1.50 &    13 \\
 3             &  1.00 &     1 &  1.25 &     7 &  1.57 &     5 &  1.74 &     8 &  1.18 &     2 &  1.00 &     1 \\
 4             &  1.12 &     5 &  1.47 &     6 &  1.27 &     5 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.25 &     4 &  1.47 &     4 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.17 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.06 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 &  1.50 &     8 &  1.50 &    11 &  1.50 &    12 \\
 3             &  1.00 &     1 &  1.24 &     5 &  1.03 &     5 &  1.65 &     5 &  1.00 &     1 &  1.00 &     1 \\
 4             &  1.09 &     3 &  1.32 &     3 &  1.36 &     6 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.01 &     2 &  1.06 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.10 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.25 &     2 &  1.49 &     6 &  1.50 &     9 &  1.50 &    11 \\
 3             &  1.00 &     1 &  1.19 &     3 &  1.12 &     5 &  1.45 &     4 &  1.00 &     2 &  1.00 &     1 \\
 4             &  1.00 &     1 &  1.02 &     3 &  1.33 &     4 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.03 &     2 &  1.16 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.01 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 &  1.50 &     8 &  1.50 &    10 \\
 3             &  1.00 &     1 &  1.00 &     1 &  1.24 &     5 &  1.03 &     5 &  1.00 &     2 &  1.00 &     1 \\
 4             &  1.00 &     1 &  1.09 &     3 &  1.19 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.00 &     1 &  1.01 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_spacing_r100_a065}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13} 
Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.99 &     8 \\
 2             &  1.00 &     1 &  1.50 &     8 &  1.50 &    10 &  1.50 &    12 &  1.50 &    12 &  1.90 &     6 \\
 3             &  1.25 &     7 &  1.72 &     7 &  1.75 &     9 &  1.75 &    10 &  1.91 &     7 &  1.00 &     1 \\
 4             &  1.47 &     6 &  1.74 &     6 &  1.79 &     7 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.55 &     5 &  1.45 &     4 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 6             &  1.44 &     4 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 7             &  1.12 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.94 &     5 \\
 2             &  1.00 &     1 &  1.49 &     7 &  1.50 &     9 &  1.50 &    11 &  1.50 &    12 &  1.53 &     8 \\
 3             &  1.24 &     5 &  1.65 &     5 &  1.72 &     7 &  1.74 &     8 &  1.78 &     5 &  1.00 &     1 \\
 4             &  1.40 &     4 &  1.41 &     3 &  1.66 &     5 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.37 &     3 &  1.14 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.07 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.50 &     2 \\
 2             &  1.00 &     1 &  1.47 &     5 &  1.50 &     8 &  1.50 &     9 &  1.50 &    11 &  1.25 &    11 \\
 3             &  1.22 &     4 &  1.45 &     3 &  1.64 &     5 &  1.72 &     7 &  1.50 &     3 &  1.00 &     1 \\
 4             &  1.19 &     2 &  1.10 &     3 &  1.40 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.06 &     2 &  1.19 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.09 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
 2             &  1.00 &     1 &  1.44 &     4 &  1.49 &     6 &  1.50 &     8 &  1.50 &    10 &  1.50 &    11 \\
 3             &  1.13 &     2 &  1.27 &     2 &  1.57 &     4 &  1.65 &     5 &  1.00 &     1 &  1.00 &     1 \\
 4             &  1.03 &     2 &  1.16 &     3 &  1.04 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
 5             &  1.09 &     2 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 7             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 9             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
 and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

% \begin{sidewaystable}
\begin{table}[htp]
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
% \caption{Descriptive Statistics by Education Level and Beginning of Spell for First and Second Spell}
\caption{Descriptive Statistics by Education Level and Beginning of Spell}
\label{tab:des_stat1}
\begin{tabular} {@{} c l D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} @{}} \toprule
                    &                     & \multicolumn{3}{c}{No Education}                                & \multicolumn{3}{c}{1--7 Years of Education}                      & \multicolumn{3}{c}{8+ Years of Education} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
                    &                     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     \\ % \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
\midrule
\multirow{16}{*}{\rotatebox{90}{First Spell}}                   
                    &Boy born            &       0.467         &       0.438         &       0.363         &       0.476         &       0.447         &       0.368         &       0.483         &       0.453         &       0.377         \\
                    &                    &     (0.499)         &     (0.496)         &     (0.481)         &     (0.499)         &     (0.497)         &     (0.482)         &     (0.500)         &     (0.498)         &     (0.485)         \\
                    &Girl born           &       0.427         &       0.410         &       0.352         &       0.439         &       0.429         &       0.356         &       0.454         &       0.420         &       0.353         \\
                    &                    &     (0.495)         &     (0.492)         &     (0.478)         &     (0.496)         &     (0.495)         &     (0.479)         &     (0.498)         &     (0.494)         &     (0.478)         \\
                    &Censored            &       0.106         &       0.152         &       0.284         &       0.085         &       0.124         &       0.276         &       0.063         &       0.127         &       0.270         \\
                    &                    &     (0.308)         &     (0.359)         &     (0.451)         &     (0.279)         &     (0.330)         &     (0.447)         &     (0.243)         &     (0.333)         &     (0.444)         \\
                    &Urban               &       0.181         &       0.176         &       0.200         &       0.366         &       0.334         &       0.322         &       0.690         &       0.604         &       0.561         \\
                    &                    &     (0.385)         &     (0.381)         &     (0.400)         &     (0.482)         &     (0.472)         &     (0.467)         &     (0.463)         &     (0.489)         &     (0.496)         \\
                    &Age                 &      15.854         &      16.301         &      16.871         &      16.983         &      17.470         &      17.844         &      19.516         &      20.036         &      20.766         \\
                    &                    &     (2.482)         &     (2.643)         &     (2.858)         &     (2.733)         &     (3.041)         &     (3.221)         &     (3.331)         &     (3.614)         &     (3.916)         \\
                    &Owns land           &       0.589         &       0.578         &       0.540         &       0.500         &       0.497         &       0.482         &       0.321         &       0.387         &       0.414         \\
                    &                    &     (0.492)         &     (0.494)         &     (0.498)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.467)         &     (0.487)         &     (0.493)         \\
                    &Sched.\ caste/tribe &       0.357         &       0.395         &       0.441         &       0.170         &       0.227         &       0.318         &       0.071         &       0.119         &       0.175         \\
                    &                    &     (0.479)         &     (0.489)         &     (0.497)         &     (0.376)         &     (0.419)         &     (0.466)         &     (0.257)         &     (0.324)         &     (0.380)         \\
                    &Number of quarters  & \mco{  330,315         } & \mco{  257,757         } & \mco{   75,841         } & \mco{  108,463         } & \mco{  108,863         } & \mco{   54,704         } & \mco{  102,238         } & \mco{  154,582         } & \mco{  116,272         } \\
                    &Number of women     & \mco{   30,004         } & \mco{   27,669         } & \mco{    9,684         } & \mco{   11,162         } & \mco{   13,104         } & \mco{    7,510         } & \mco{   11,271         } & \mco{   19,072         } & \mco{   16,620         } \\
                    \addlinespace
% \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
\midrule
\multirow{22}{*}{\rotatebox{90}{Second Spell}}
                    & Boy born            &       0.490         &       0.444         &       0.359         &       0.477         &       0.437         &       0.338         &       0.457         &       0.399         &       0.285         \\
                    &                     &     (0.500)         &     (0.497)         &     (0.480)         &     (0.500)         &     (0.496)         &     (0.473)         &     (0.498)         &     (0.490)         &     (0.451)         \\
                    & Girl born           &       0.451         &       0.413         &       0.327         &       0.462         &       0.413         &       0.319         &       0.426         &       0.351         &       0.239         \\
                    &                     &     (0.498)         &     (0.492)         &     (0.469)         &     (0.499)         &     (0.492)         &     (0.466)         &     (0.495)         &     (0.477)         &     (0.427)         \\
                    & Censored            &       0.059         &       0.143         &       0.314         &       0.061         &       0.150         &       0.344         &       0.117         &       0.251         &       0.476         \\
                    &                     &     (0.236)         &     (0.350)         &     (0.464)         &     (0.239)         &     (0.357)         &     (0.475)         &     (0.321)         &     (0.433)         &     (0.499)         \\
                    & One boy             &       0.527         &       0.515         &       0.508         &       0.519         &       0.513         &       0.505         &       0.513         &       0.520         &       0.515         \\
                    &                     &     (0.499)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         \\
                    & One girl            &       0.473         &       0.485         &       0.492         &       0.481         &       0.487         &       0.495         &       0.487         &       0.480         &       0.485         \\
                    &                     &     (0.499)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         \\
                    & Urban               &       0.181         &       0.180         &       0.212         &       0.370         &       0.348         &       0.345         &       0.697         &       0.628         &       0.578         \\
                    &                     &     (0.385)         &     (0.384)         &     (0.409)         &     (0.483)         &     (0.476)         &     (0.475)         &     (0.459)         &     (0.483)         &     (0.494)         \\
                    & Age                 &      17.774         &      18.357         &      18.870         &      18.620         &      19.200         &      19.581         &      20.988         &      21.589         &      22.252         \\
                    &                     &     (2.743)         &     (3.054)         &     (3.284)         &     (2.864)         &     (3.206)         &     (3.373)         &     (3.371)         &     (3.621)         &     (3.901)         \\
                    & First spell length  &      25.630         &      29.145         &      29.133         &      21.924         &      24.513         &      24.787         &      20.608         &      22.154         &      22.217         \\
                    &                     &    (20.345)         &    (25.044)         &    (27.216)         &    (18.142)         &    (22.027)         &    (23.204)         &    (15.371)         &    (18.651)         &    (19.176)         \\
                    & Owns land           &       0.590         &       0.572         &       0.528         &       0.497         &       0.492         &       0.468         &       0.313         &       0.369         &       0.402         \\
                    &                     &     (0.492)         &     (0.495)         &     (0.499)         &     (0.500)         &     (0.500)         &     (0.499)         &     (0.464)         &     (0.483)         &     (0.490)         \\
                    & Sched.\ caste/tribe &       0.353         &       0.390         &       0.430         &       0.164         &       0.218         &       0.304         &       0.068         &       0.110         &       0.169         \\
                    &                     &     (0.478)         &     (0.488)         &     (0.495)         &     (0.371)         &     (0.413)         &     (0.460)         &     (0.251)         &     (0.313)         &     (0.374)         \\
                    & Number of quarters  & \mco{  176,227         } & \mco{  231,546         } & \mco{   68,455         } & \mco{   67,432         } & \mco{  103,656         } & \mco{   49,236         } & \mco{   77,416         } & \mco{  164,752         } & \mco{  119,864         } \\
                    & Number of women     & \mco{   21,171         } & \mco{   28,251         } & \mco{    9,428         } & \mco{    8,209         } & \mco{   12,449         } & \mco{    6,542         } & \mco{    8,204         } & \mco{   16,601         } & \mco{   13,610         } \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
% \item \hspace*{-7pt} \textbf{Note.}
\item \hspace*{-0.7em} \textbf{Note.}
Means without parentheses and standard deviation in parentheses.
Interactions between variables, baseline hazard dummies and squares not shown.
Quarters refer to number of 3 month periods observed.
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}
% \end{sidewaystable}

\addtocounter{table}{-1}

% \begin{sidewaystable}
\begin{table}
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
% \caption{Descriptive Statistics by Education Level and Beginning of Spell for Third and Fourth Spell}
\caption{(Continued) Descriptive Statistics by Education Level and Beginning of Spell}
% \label{tab:des_stat2}
\begin{tabular} {@{} c l D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} @{}} \toprule
                    &                     & \multicolumn{3}{c}{No Education}                                & \multicolumn{3}{c}{1-7 Years of Education}                      & \multicolumn{3}{c}{8+ Years of Education} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
                    &                     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     \\ % \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
\midrule                    
\multirow{24}{*}{\rotatebox{90}{Third Spell}}
                    & Boy born            &       0.478         &       0.425         &       0.319         &       0.455         &       0.388         &       0.261         &       0.353         &       0.264         &       0.163         \\
                    &                     &     (0.500)         &     (0.494)         &     (0.466)         &     (0.498)         &     (0.487)         &     (0.439)         &     (0.478)         &     (0.441)         &     (0.369)         \\
                    & Girl born           &       0.442         &       0.393         &       0.306         &       0.423         &       0.357         &       0.239         &       0.313         &       0.214         &       0.128         \\
                    &                     &     (0.497)         &     (0.488)         &     (0.461)         &     (0.494)         &     (0.479)         &     (0.426)         &     (0.464)         &     (0.410)         &     (0.334)         \\
                    & Censored            &       0.080         &       0.182         &       0.376         &       0.121         &       0.255         &       0.500         &       0.334         &       0.521         &       0.709         \\
                    &                     &     (0.271)         &     (0.386)         &     (0.484)         &     (0.326)         &     (0.436)         &     (0.500)         &     (0.472)         &     (0.500)         &     (0.454)         \\
                    & Two boys            &       0.276         &       0.257         &       0.243         &       0.248         &       0.245         &       0.232         &       0.266         &       0.244         &       0.238         \\
                    &                     &     (0.447)         &     (0.437)         &     (0.429)         &     (0.432)         &     (0.430)         &     (0.422)         &     (0.442)         &     (0.429)         &     (0.426)         \\
                    & One boy, one girl   &       0.490         &       0.502         &       0.506         &       0.508         &       0.501         &       0.515         &       0.489         &       0.510         &       0.527         \\
                    &                     &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.499)         \\
                    & Two girls           &       0.234         &       0.241         &       0.252         &       0.243         &       0.254         &       0.253         &       0.245         &       0.247         &       0.235         \\
                    &                     &     (0.424)         &     (0.428)         &     (0.434)         &     (0.429)         &     (0.435)         &     (0.435)         &     (0.430)         &     (0.431)         &     (0.424)         \\
                    & Urban               &       0.179         &       0.182         &       0.208         &       0.378         &       0.354         &       0.343         &       0.693         &       0.646         &       0.568         \\
                    &                     &     (0.383)         &     (0.386)         &     (0.406)         &     (0.485)         &     (0.478)         &     (0.475)         &     (0.461)         &     (0.478)         &     (0.495)         \\
                    & Age                 &      19.978         &      20.693         &      21.278         &      20.794         &      21.453         &      21.998         &      22.963         &      23.825         &      24.548         \\
                    &                     &     (2.895)         &     (3.196)         &     (3.551)         &     (2.937)         &     (3.239)         &     (3.618)         &     (3.405)         &     (3.748)         &     (4.067)         \\
                    & First spell length  &      24.547         &      27.575         &      27.099         &      20.971         &      23.901         &      23.532         &      19.991         &      21.246         &      21.236         \\
                    &                     &    (18.832)         &    (22.779)         &    (24.364)         &    (16.875)         &    (20.378)         &    (21.155)         &    (14.646)         &    (16.835)         &    (17.363)         \\
                    & Owns land           &       0.602         &       0.575         &       0.538         &       0.503         &       0.503         &       0.490         &       0.320         &       0.369         &       0.421         \\
                    &                     &     (0.490)         &     (0.494)         &     (0.499)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.467)         &     (0.483)         &     (0.494)         \\
                    & Sched.\ caste/tribe &       0.344         &       0.392         &       0.432         &       0.159         &       0.218         &       0.298         &       0.067         &       0.107         &       0.169         \\
                    &                     &     (0.475)         &     (0.488)         &     (0.495)         &     (0.366)         &     (0.413)         &     (0.457)         &     (0.251)         &     (0.310)         &     (0.375)         \\
                    & Number of quarters  & \mco{  109,026         } & \mco{  206,988         } & \mco{   70,391         } & \mco{   43,434         } & \mco{   87,537         } & \mco{   41,400         } & \mco{   49,799         } & \mco{  126,733         } & \mco{   79,068         } \\
                    & Number of women     & \mco{   13,196         } & \mco{   25,135         } & \mco{    9,355         } & \mco{    4,960         } & \mco{    9,775         } & \mco{    5,034         } & \mco{    4,316         } & \mco{   10,688         } & \mco{    7,927         } \\
\addlinespace
% \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
\midrule
\multirow{26}{*}{\rotatebox{90}{Fourth Spell}}
                    & Boy born            &       0.463         &       0.384         &       0.291         &       0.403         &       0.347         &       0.233         &       0.310         &       0.227         &       0.170         \\
                    &                     &     (0.499)         &     (0.486)         &     (0.454)         &     (0.491)         &     (0.476)         &     (0.423)         &     (0.462)         &     (0.419)         &     (0.376)         \\
                    & Girl born           &       0.408         &       0.363         &       0.268         &       0.391         &       0.303         &       0.198         &       0.298         &       0.197         &       0.113         \\
                    &                     &     (0.491)         &     (0.481)         &     (0.443)         &     (0.488)         &     (0.460)         &     (0.399)         &     (0.458)         &     (0.397)         &     (0.316)         \\
                    & Censored            &       0.130         &       0.254         &       0.441         &       0.206         &       0.350         &       0.569         &       0.392         &       0.576         &       0.717         \\
                    &                     &     (0.336)         &     (0.435)         &     (0.497)         &     (0.405)         &     (0.477)         &     (0.495)         &     (0.488)         &     (0.494)         &     (0.450)         \\
                    & Three boys          &       0.134         &       0.124         &       0.111         &       0.107         &       0.105         &       0.102         &       0.106         &       0.101         &       0.082         \\
                    &                     &     (0.341)         &     (0.329)         &     (0.315)         &     (0.309)         &     (0.307)         &     (0.303)         &     (0.308)         &     (0.302)         &     (0.275)         \\
                    & Two boys, one girl  &       0.374         &       0.357         &       0.346         &       0.348         &       0.323         &       0.308         &       0.358         &       0.304         &       0.289         \\
                    &                     &     (0.484)         &     (0.479)         &     (0.476)         &     (0.476)         &     (0.468)         &     (0.462)         &     (0.480)         &     (0.460)         &     (0.453)         \\
                    & One boys, two girls &       0.362         &       0.389         &       0.400         &       0.400         &       0.413         &       0.423         &       0.393         &       0.439         &       0.469         \\
                    &                     &     (0.481)         &     (0.488)         &     (0.490)         &     (0.490)         &     (0.492)         &     (0.494)         &     (0.489)         &     (0.496)         &     (0.499)         \\
                    & Three girls         &       0.129         &       0.130         &       0.142         &       0.145         &       0.159         &       0.167         &       0.143         &       0.156         &       0.159         \\
                    &                     &     (0.335)         &     (0.337)         &     (0.350)         &     (0.353)         &     (0.365)         &     (0.373)         &     (0.350)         &     (0.363)         &     (0.366)         \\
                    & Urban               &       0.171         &       0.181         &       0.197         &       0.363         &       0.346         &       0.325         &       0.670         &       0.601         &       0.511         \\
                    &                     &     (0.377)         &     (0.385)         &     (0.398)         &     (0.481)         &     (0.476)         &     (0.469)         &     (0.470)         &     (0.490)         &     (0.500)         \\
                    & Age                 &      21.926         &      22.885         &      23.608         &      22.611         &      23.519         &      24.317         &      24.257         &      25.472         &      26.061         \\
                    &                     &     (3.019)         &     (3.332)         &     (3.711)         &     (2.894)         &     (3.364)         &     (3.759)         &     (3.171)         &     (3.702)         &     (4.143)         \\
                    & First spell length  &      23.281         &      26.609         &      26.460         &      20.495         &      23.069         &      24.215         &      19.106         &      20.826         &      21.423         \\
                    &                     &    (17.481)         &    (21.556)         &    (23.272)         &    (15.546)         &    (19.078)         &    (21.244)         &    (13.991)         &    (16.277)         &    (16.585)         \\
                    & Owns land           &       0.610         &       0.587         &       0.557         &       0.523         &       0.530         &       0.509         &       0.339         &       0.414         &       0.466         \\
                    &                     &     (0.488)         &     (0.492)         &     (0.497)         &     (0.500)         &     (0.499)         &     (0.500)         &     (0.474)         &     (0.493)         &     (0.499)         \\
                    & Sched.\ caste/tribe &       0.338         &       0.403         &       0.442         &       0.154         &       0.224         &       0.297         &       0.085         &       0.113         &       0.193         \\
                    &                     &     (0.473)         &     (0.491)         &     (0.497)         &     (0.361)         &     (0.417)         &     (0.457)         &     (0.280)         &     (0.316)         &     (0.395)         \\
                    & Number of quarters  & \mco{   54,446         } & \mco{  151,285         } & \mco{   56,756         } & \mco{   18,852         } & \mco{   49,108         } & \mco{   23,209         } & \mco{   14,287         } & \mco{   43,339         } & \mco{   23,586         } \\
                    & Number of women     & \mco{    6,832         } & \mco{   18,436         } & \mco{    7,637         } & \mco{    2,201         } & \mco{    5,564         } & \mco{    2,768         } & \mco{    1,347         } & \mco{    3,933         } & \mco{    2,459         } \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
% \item \hspace*{-7pt} \textbf{Note.}
\item \hspace*{-0.7em} \textbf{Note.}
Means without parentheses and standard deviation in parentheses.
Interactions between variables, baseline hazard dummies and squares not shown.
Quarters refer to number of 3 month periods observed.
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}
% \end{sidewaystable}

\clearpage
\newpage

% \begin{figure}[h]
% \begin{center}
% \Treek{1.5}{  &&   &        &           &                       &       & \K[5.2]{n=0}\Bkk{5.2,0}{-5.2,0}{dlll}\Bkk{5.2,0}{5.2,0}{dd}\Bkk{5.2,0}{5.2,0}{drrrr} \\
% \K[-6]{\emph{t=1}}              &&              & \K[5.2]{-S}\Bkk{5.2,0}{5.2,0}{dll}\Bkk{5.2,0}{5.2,0}{drr}  & &      & & & &      & & \K[5.2]{S}\Bkk{5.2,0}{5.2,0}{dll}\Bkk{5.2,0}{5.2,0}{drr}              \\
%              & \K[5.2]{b (boy)}\bkl\bkd\bkr &   &  &                    &   \K[5.2]{g (girl)}\bkl\bkd\bkr & & \K[5.2]{0} &      & \K[5.2]{0 (no child)}\bkl\bkd\bkr & &&                   &  \K[5.2]{b (boy)}\bkl\bkd\bkr     \\
% \K[-6]{\emph{t=2}}\K[5.2]{-S}\bkv\bkh&       & \K[5.2]{S}\bkv\bkh    & & \K[5.2]{-S}\bkv\bkh &    & \K[5.2]{S}\bkv\bkh &              &\K[5.2]{-S}\bkv\bkh&       & \K[5.2]{S}\bkv\bkh &  &\K[5.2]{-S}\bkv\bkh&   & \K[5.2]{S}\bkv\bkh  \\
% \K{bb}             & \K{bg}  \K[5.2]{b}  & \K{b} & \K{bb}        & \K{gb}  &\K{gg} \K[5.2]{g}   & \K{g} & \K{gb}    & \K{g}  &\K{b} \K[5.2]{0}  & \K{0} & \K{b}    & \K{bb}  &\K{bg} \K[5.2]{b}  & \K{b} & \K{bb}     \\
% }
% \end{center}
% \caption{Decision tree for a two period model with prenatal sex screening, where -S is no prenatal sex determination and S is sex determination}
% \label{fig:tree}
% \end{figure}

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{des_fertility_35}
% this graph is sex_ratio_marriage_2yrs_p1.pdf from andescribe.do
\caption{Children ever born at age 35}
\label{fig:fertility}
\end{figure}

\clearpage
\newpage

\begin{table}[htbp]
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
Abortions for Women with No Education}
\label{tab:predicted_low}
\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
\midrule
\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
Spell 2          &       93.2   &  1.8    &  1.6    &  52.2   &       92.4   &  1.5    &  1.3    &  52.0   &       90.0   &  1.4    &  1.2    &  52.0   \\
Spell 3          &       93.8   &  4.6    &  4.3    &  53.6   &       91.1   &  -1.2   &  -1.1   &  50.7   &       85.6   &  -4.7   &  -4.0   &  48.8   \\
Spell 4          &       87.1   &  5.5    &  4.8    &  54.1   &       84.4   &  2.3    &  2.0    &  52.5   &       75.3   &  5.6    &  4.2    &  54.1   \\
Overall\tnote{d} &       3.6    &  2.8    &  9.8    &  52.9   &       3.5    &  0.6    &  2.0    &  51.7   &       3.3    &  0.3    &  0.9    &  51.2   \\
\addlinespace 
\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
Spell 2          &       94.5   &  1.7    &  1.6    &  52.1   &       93.7   &  1.0    &  1.0    &  51.7   &       92.9   &  3.4    &  3.2    &  53.0   \\
Spell 3          &       95.1   &  1.5    &  1.4    &  52.0   &       93.4   &  1.9    &  1.7    &  52.2   &       91.3   &  -0.5   &  -0.5   &  51.0   \\
Spell 4          &       91.1   &  3.4    &  3.1    &  52.9   &       87.3   &  0.1    &  0.1    &  51.3   &       83.3   &  0.1    &  0.1    &  51.3   \\
Overall\tnote{d} &       3.7    &  1.6    &  5.7    &  52.3   &       3.6    &  0.7    &  2.7    &  51.7   &       3.5    &  0.8    &  2.8    &  51.5   \\
\bottomrule
\end{tabular}                        
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
The samples consist of all women from the data no education who
married during the indicated period using the estimation results for that periods 
and the women's characteristics at the start of their marriage. 
All numbers presented are for women predicted to have one or more births.
Birth/progression rates are based on the ratio of women predicted to have a birth 
by the end of each spell.
Abortion rates within each spell are based on the predicted number of abortions each
woman would have if she went through the entire spell.
To generate conditions such as sex composition and fecundity for second and higher spells 
each woman is randomly assigned outcomes based on the estimation results and
her characteristics as follows.
For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
She is assigned one of these outcomes based on a random draw from a uniform distribution.
The first quarter where she has a draw that results in a birth she leaves the spell
and the quarter reached is used to calculate her starting age for the subsequent spell.
If she has no draw that result in a birth within a spell her childbearing stops and
she does not enter the next spell.
Results are averaged over 1,000 repetitions.
\item[a] For individual spells the column shows the percent of women who started the
spell and ended up with a birth by the end of the spell period covered.
For the ``Overall'' row, the number is the expected number of children born per woman over 
the first four spells, conditional on having at least one birth.
\item[b] For individual spells the column shows the number of abortions per 100
births predicted to take place by the end of the spell.
For the ``Overall'' row, the number is the total number of abortion per 100 births 
predicted to take place over all four spells.
\item[c]  For individual spells the column shows the number of abortions 
predicted to take place by the end of the spell per 100 women who started the spell .
For the ``Overall'' row, the number is the total number of abortion 
predicted to take place over all four spells per 100 women who had at least one child.
\item[d] Covers first through fourth spells. 
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}

\begin{table}[htbp]
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
Abortions for Women with 1 to 7 Years of Education}
\label{tab:predicted_med}
\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
\midrule
\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
Spell 2          &       93.4   &  -2.1   &  -2.0   &  50.1   &       89.7   &  -0.1   &  -0.1   &  51.2   &       84.5   &  -0.9   &  -0.7   &  50.7   \\
Spell 3          &       89.2   &  1.4    &  1.3    &  52.0   &       82.5   &  1.4    &  1.2    &  51.9   &       71.1   &  2.4    &  1.7    &  52.4   \\
Spell 4          &       79.0   &  3.4    &  2.7    &  52.9   &       70.9   &  1.0    &  0.7    &  51.7   &       61.9   &  6.8    &  4.2    &  54.7   \\
Overall\tnote{d} &       3.4    &  0.4    &  1.4    &  51.7   &       3.2    &  0.5    &  1.5    &  51.7   &       2.8    &  1.1    &  3.2    &  51.9   \\
\addlinespace 
\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
Spell 2          &       94.6   &  -1.3   &  -1.2   &  50.5   &       93.0   &  0.4    &  0.4    &  51.4   &       91.6   &  2.2    &  2.0    &  52.3   \\
Spell 3          &       92.8   &  0.6    &  0.6    &  51.5   &       88.0   &  1.0    &  0.8    &  51.7   &       80.7   &  3.5    &  2.8    &  53.0   \\
Spell 4          &       86.2   &  -2.2   &  -1.9   &  50.1   &       80.3   &  4.5    &  3.6    &  53.5   &       68.0   &  3.6    &  2.5    &  53.1   \\
Overall\tnote{d} &       3.6    &  -0.7   &  -2.4   &  51.0   &       3.4    &  1.2    &  4.1    &  51.6   &       3.2    &  2.0    &  6.4    &  52.1   \\
\bottomrule
\end{tabular}                        
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
The samples consist of all women from the data with 1 to 7 years of education who
married during the indicated period using the estimation results for that periods 
and the women's characteristics at the start of their marriage. 
All numbers presented are for women predicted to have one or more births.
Birth/progression rates are based on the ratio of women predicted to have a birth 
by the end of each spell.
Abortion rates within each spell are based on the predicted number of abortions each
woman would have if she went through the entire spell.
To generate conditions such as sex composition and fecundity for second and higher spells 
each woman is randomly assigned outcomes based on the estimation results and
her characteristics as follows.
For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
She is assigned one of these outcomes based on a random draw from a uniform distribution.
The first quarter where she has a draw that results in a birth she leaves the spell
and the quarter reached is used to calculate her starting age for the subsequent spell.
If she has no draw that result in a birth within a spell her childbearing stops and
she does not enter the next spell.
Results are averaged over 1,000 repetitions.
\item[a] For individual spells the column shows the percent of women who started the
spell and ended up with a birth by the end of the spell period covered.
For the ``Overall'' row, the number is the expected number of children born per woman over 
the first four spells, conditional on having at least one birth.
\item[b] For individual spells the column shows the number of abortions per 100
births predicted to take place by the end of the spell.
For the ``Overall'' row, the number is the total number of abortion per 100 births 
predicted to take place over all four spells.
\item[c]  For individual spells the column shows the number of abortions 
predicted to take place by the end of the spell per 100 women who started the spell .
For the ``Overall'' row, the number is the total number of abortion 
predicted to take place over all four spells per 100 women who had at least one child.
\item[d] Covers first through fourth spells. 
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}

\end{document}

### 2017-04-03 paper/sexSelectionSpacing-ver1.tex
Begun removing discussion of fertility from intro and theory

@@
 
-\title{Sex-Selective Abortions, Fertility, and Birth Spacing
-% \protect\thanks{%
-% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-% I owe thanks to three anonymous referees, Shelly Lundberg, Daniel Rees, David Ribar, 
-% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-% University of Washington, University of \AA{}rhus, the Fourth 
-% Annual Conference on Population, Reproductive Health, 
-% and Economic Development, and the Economic Demography Workshop for helpful suggestions and comments.
-% I would also like to thank Nalina Varanasi for research assistance.
-% Support from the University of Washington Royalty Research Fund and the 
-% Development Research Group of the World Bank is gratefully acknowledged.
-% The views and findings expressed here are those of the author and
-% should not be attributed to the World Bank or any of its member countries.
-% Partial support for this research came from a Eunice Kennedy Shriver National
-% Institute of Child Health and Human Development research infrastructure grant,
-% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
-% University of Washington.
+\title{Sex-Selective Abortions and Birth Spacing
+\protect\thanks{%
+I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+I owe thanks to three anonymous referees, Shelly Lundberg, Daniel Rees, David Ribar, 
+Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
+University of Washington, University of \AA{}rhus, the Fourth 
+Annual Conference on Population, Reproductive Health, 
+and Economic Development, and the Economic Demography Workshop for helpful suggestions and comments.
+I would also like to thank Nalina Varanasi for research assistance.
+Support from the University of Washington Royalty Research Fund and the 
+Development Research Group of the World Bank is gratefully acknowledged.
+The views and findings expressed here are those of the author and
+should not be attributed to the World Bank or any of its member countries.
+Partial support for this research came from a Eunice Kennedy Shriver National
+Institute of Child Health and Human Development research infrastructure grant,
+5R24HD042828, to the Center for Studies in Demography and Ecology at the
+University of Washington.
 % Prior versions of this paper were presented under the title ``The 
 % Determinants of sex-selective Abortions.''
-% }
+}
 }
@@
 \begin{document}
-\graphicspath{{graphs/},{figures/}}
+\graphicspath{{figures/}}
 \DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
@@
 
-% \newpage
+\newpage
 \doublespacing
@@
 % Demography abstract
-\noindent This paper addresses two main questions:
-what is the relationship between fertility and sex selection 
-and
+\noindent This paper addresses the question:
 how does birth spacing interact with the use of sex-selective abortions? 
@@
 Using India's National Family and Health Surveys,
-I show that falling fertility intensifies use of sex selection, leading to use at 
-lower parities, and longer spacing after a daughter is born.
+I show that use of sex selection leads to longer spacing after a daughter is born.
 Women with 8 or more years of education, both in urban and rural areas, are the main users 
-of sex-selective abortions and have the lowest fertility.
-Women with less education have substantially higher fertility and do not appear to use 
-sex selection.
+of sex-selective abortions.
+Women with less education do not appear to use sex selection.
 Predicted lifetime fertility for high-education women declined more than 10\% 
 between 1985--1994, when sex selection was legal, and 1995--2006, when sex selection was illegal.
-Fertility is now around replacement level.
 Abortions per woman increased almost 20\% for urban women and 50\%
@@
 \section{Introduction\label{sec:intro}}
-
-% India's male to female ratio increased almost continuously during the last century, 
-% mainly because of excess mortality of girls \citep{murthi95,dyson01}.
 
@@
 
-I address two important questions that the prior literature has been unable
-to examine because of the simple method's limitations.
-First, what is the relationship between fertility decisions and use of sex selection?
-Second, how does birth spacing interact with use of sex-selective abortions?
+I address an important questions that the prior literature has been unable
+to examine because of the simple method's limitations:
+how does birth spacing interact with use of sex-selective abortions?
 I introduce a novel method that directly incorporates that sex-selective 
@@
 births.
-I use the method to argue that differences in fertility over time and between groups
-explain a substantial portion of the changes in the use of sex selection in 
-India, and to show how spacing between births play an important role in our understanding 
-of fertility and sex selection decisions.
-
-We already know that fertility and son preference are related from the substantial literature
-on fertility stopping behavior before sex selection was available.
-This literature shows that families are more likely to stop childbearing after the 
-birth of a son than after the birth of a daughter
-\cite[see, for example,][]{Das1987,Arnold1997,clark00}.%
-\footnote{
-\citet{filmer09} analyse the relationship between the sex composition of previous
-children and subsequent fertility behavior using data from 64 countries.
-}
-It is also easy to see how declining fertility may increase use of sex selection.
-Take a family that wants one son.
-If the family is willing to have up to 4 children, the probability of having a son
-is more than 94 percent, even without sex selection, and that increases to almost 99 
-percent if the family is willing to have up to 6 children.%
-\footnote{
-The probability of not having a son are 48.8 percent for one child, 23.8 percent for
-two children, 11.6 percent for 3 children, 5.7 percent for 4 children, 2.8 percent
-for 5 children, and 1.4 percent for 6 children.
-}
-% If the family is willing to have up to six children, the probability of having a son
-% is more than 99 percent, even without sex selection.
-If the desire is instead for one son \emph{and} a maximum of two children, there 
-is a 24 percent chance that the family will have to resort to sex selection to achieve 
-both targets.
-% Working in the opposite direction, the stated preference for sons appears to decline with 
-% lower fertility \citep{das_gupta97,bhat03}.
-Despite these opposite targets, there is little empirical analysis of 
-the effects of fertility on sex selection using individual level data 
-\citep{park95,Ebenstein2011}.%
-\footnote{
-\citet{Dharmalingam2014} examine how state level fertility in India
-relates to desired family size and son preference over time, but does 
-not look at how fertility preferences shape the decision on sex-selective 
-abortions.
-At country level \citet{Bongaarts2013} shows how sex ratios at births are 
-only elevated for countries with lower fertility and
-\citet{Bongaarts2015} use national level estimates of the relationship
-between sex ratio at birth and fertility as part of their
-prediction of the number of missing women past and present.
-Simulations suggest that in Korea introduction of sex selection
-changed family size little, but did result in abortions
-of female fetuses equal to about 5 percent of actual female
-births \citep{park95}.
-For China allowing a three-child policy has been predicted to 
-increase the fertility rate by 35 percent, but also reduce the
-number of girls aborted by 56 percent \citep{Ebenstein2011}.
-}
-
-% Not only can a decline in desired fertility increase the use of sex selection, 
-% increasing the availability of prenatal sex determination also allows a 
-% woman to reach a desired number of sons with fewer births.
-% To fully understand the use of sex selection we therefore need
-% to understand both its use by parity \emph{and} by the fertility decision.
-% This is especially important if lower fertility is the driver of the
-% increased use of sex selection.
-
-% The use of sex-selective abortions may increase over time for a number of different reasons.
-% 1. preferences can change to make people desire boys more than before
-% 2. the return to girls can fall further 
-% 3. desired fertility can fall (even if nothing else changes)
-% 3. the cost of sex-selective abortions can fall, which increases its use even though
-% there are no other changes.
+I use the method to show how spacing between births play an important role in our 
+understanding of sex selection decisions.
 
@@
 
-Closely related to the overall fertility decisions are decisions on  spacing between births.
 In the absence of sex-selective abortions, son preference often leads to a shorter duration 
@@
 % [contribution of paper]
+[TK maybe not focus so much on the simple method but rather understanding son preference].
 The main contribution of this paper is the introduction and application of a method that 
-incorporates the decisions about fertility, birth spacing, and sex-selective abortions.
-The method allows us to better understand the relationship between these three decisions.
-% The method allows us to better understand the relationship between sex-selective abortions, 
-% fertility, and birth spacing.
+incorporates the decisions about birth spacing, and sex-selective abortions.
 The empirical model is a competing risk, non-proportional hazard model with two exit 
 states: either a boy or a girl is born.
-This approach has three major advantages over the simple method.
-First and foremost, it models fertility and spacing decisions jointly with the birth 
-outcome, which makes it possible to better understand how changing fertility decisions
-affects the use of sex selection.
+This approach has TK major advantages over the simple method
+
 Secondly, by explicitly incorporating censoring of birth spacing, it addresses any 
@@
 the previous birth.
-Finally, the method allows us to predict completed fertility, total number of abortions, 
-and final sex ratio over a woman's reproductive life cycle.
-These provide a better way of measuring changes in the use of sex selection 
-than what we can get from individual parities---especially because individual 
-parities may show a decline in sex selection at the same time as overall
-use is increasing.
+
 None of these is possible using the simple method.
@@
 There are three main findings.
-First, fertility is an important factor in the decision to use sex-selective 
-abortions.
-On the one hand, women with fewer than 8 years of education have relatively high fertility 
-and do not appear to use sex selection.
-On the other hand, better-educated women in both urban and rural areas have much lower
-fertility and are the main users of sex-selective abortions.
-For women with 8 or more years of education and only daughters the 
-use is substantial: around 60 percent of the children born are boys.
-Furthermore, as better-educated women's fertility has declined over time, sex selection 
-occurs for earlier and earlier parities and has correspondingly increased in intensity.
+
 There is, however, still no evidence of sex selection being used on the first birth.
@@
 
-Finally, 
-the legal steps taken to combat sex-selective abortions have not been able 
-to reverse its use.
-In 1994, the Central Government passed the Prenatal Diagnostic Techniques (PNDT) Act 
-making determining and communicating the sex of a fetus illegal.%
-\footnote{
-Abortion has been legal in India since 1971 and still is.
-The Act is described in detail at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
-The number of convictions has been low.
-It took until January 2008 for the first state, Haryana, to reach 5 convictions.
-Hence, private clinics operate with little risk of legal action \citep{Sudha1999}.
-Maharashtra was the first state to pass a similar law in 1988.
-}
-In the period 1985-1994 the predicted total number of abortions per 100 women by the 
-end of childbearing was 8 for urban women and 6.8 for rural women.
-As completed fertility for high-education women fell to now 
-around 2 in urban areas and 2.6 in rural areas, 
-the number of sex-selective abortions 100 women are predicted to have 
-during their childbearing years has increased to 9.4 for urban women and 
-10.5 for rural women.
-In other words, close to one in ten well-educated women will now have at least 
-one abortion motivated by sex selection during their childbearing.
-Hence, although it is possible that the PDNT Act slowed the increase in use 
-of sex selection, the total predicted number of abortions per woman continued 
-to increase after the law was enacted.
-The end result is a sex ratio across all children of 53.7\% boys for well-educated 
-urban women and 53.4\% for well-educated rural women.
-
-% This is a substantial increase in sex-selective abortions compared to
-% the period before the practice was made illegal nationwide in India in 1994.
-
-\section{Theory\label{sec:model}}
-
-The model I present here serves three purposes.
-First, it allows me to illustrate how fertility, sex selection, and birth 
-spacing interact when changing the cost of children and access to sex selection.
+\section{Theoretical Framework\label{sec:model}}
+
+[TK Calling this a model will be overkill - save the model for the fertility paper]
+
+[TK find examples of the son preference spacing papers and look at what they did
+for "theory"]
+
+The model I present here serves two purposes.
+First, the model informs the empirical strategy presented below.
 Second, I show that there are cases where parents reconsider their decision to 
@@
 sex selection takes place and what the final sex ratio will be.
-Finally, the model informs the empirical strategy presented below.
-
-In the model, parents decide on fertility sequentially,
-given the number of boys and girls they already have.
-Parents fully control fertility in each period and the only
-source of uncertainty is whether they conceive a boy or a girl.
-This means that spacing between births arise only from 
-the use of sex selection.%
-\footnote{
-A more realistic approach would have parents choose how 
-``intensive'' they want to use contraceptives, where the
-intensiveness translates into a stochastic conception process,
-so that parents do not directly control the timing of births 
-but rather the probability of having a birth in a given period.
-The added complexity would, however, not add anything substantial 
-to help answer the main question of what the relationship between fertility 
-and sex selection is, and would detract from the main source of uncertainty,
-which is whether the couple will conceive a male or female fetus.
-Assuming that parents fully control fertility is relatively common 
-in the economics literature on dynamic models of fertility, such as
-\citet{Happel1984}, \citet{wolpin84}, \citet{rosenzweig85}.
-The empirical approach does allow for stochastic occurrence of births
-through the use of a hazard model.
-
-See \citet{Leung1991} for a model that incorporates both stochastic 
-births based on a chosen level of contraception and differential 
-preferences for boys and girls.
-The model does not, however, allow for abortions and it does
-not appear possible to extend the model to incorporate abortions
-and still solve it an similar manner.
-}
+
+[move discussion of spacing from footnote above to here?]
+
 This is obviously a simplification and since the interaction
@@
 }
-% %
-% \footnote{
-% As \citet{Heckman1976} show an increasing
-% income stream can also lead to longer spacing.
-% If children are costly in each period, as in the
-% model presented here, parent may use contraception to wait for
-% sufficiently higher income before having the next child.
-% Notice, that we would expect both the income and the
-% cost of children to increase as women's education goes up and
-% it is likely that the cost of children increases faster
-% than income.
-% }
 
@@
 
-In the absence of prenatal sex determination, stronger son preference is often thought 
-to increase overall fertility.
-That is not the case here.
-In fact, there is little correlation between the weight placed on utility from boys and 
-fertility.%
-\footnote{
-This is confirmed by regressing the weight places on sons, cost of children,
-and discount factor against fertility for the expanded set of values.
-}
-Similarly, parents' discount factor has no impact on fertility in the absence of
-prenatal sex determination.
-The one factor that does affect fertility is the cost of children;
-increasing the cost of children substantially reduces fertility.
-
 % Access / cost of prenatal sex determination
-
-Introducing prenatal sex determination has two opposing effects on fertility 
-in the model.
-On one hand, it takes fewer births to reach a desired number of sons and this 
-reduces fertility.
-On the other hand, parents no longer have to pay for unwanted children and 
-this ``wealth effect'' increases fertility.
-% The simulations show a small negative effect of lowering the cost of
-% sex selection holding the other parameters constant.
-The simulations show that for most combinations of son preference and 
-cost of children cutting the cost of abortion has little effect 
-on fertility---even if the cut is substantial---indicating that for this 
-set-up and the chosen parameter values the two effects 
-cancel each other out.%
-\footnote{
-Running regressions on the expanded simulation results show a negative, but
-statistically insignificant relationship between cost of abortion
-and fertility.
-For high son preference and cost of children the effect of 
-decreasing cost of prenatal scan is either nill or slightly
-positive.
-See also the discussions in \cite{leung94} and \cite{davies97}.
-}
 
@@
 
-% Cost of children
-
-The strongest driver of fertility in the model is the cost of
-child maintenance per period.
-% For a period maintenance cost of 12 fertility is between 7 and 7.5,
-% while for a cost of 22 fertility it is only 2.
-As fertility decreases with higher cost of children, sex ratios 
-become more male biased---although it is possible that there is 
-non-linearity in the effect of child cost on sex ratios.%
-\footnote{
-The changes in sex ratio are not uniformly positive, possibly because 
-the discrete nature of fertility decisions combined with the uncertainty 
-of the sex of the next conception produce knife-edge cases that can
-dramatically swing the outcomes.
-}
-This non-linearity also shows up in the number of abortions 
-and spells where a prenatal scan has been used, 
-but the overall trend is towards more abortions and more spells with
-prenatal scan per birth as the cost of children increase.
-
 % Son preference
@@
 
-% The non-uniform effect in spacing by parity when changing
-% the cost of prenatal scan show up here as well.
-% Consider, for example, the case when cost of prenatal scan falls from 20
-% to 16 when cost of children is 16. 
-% The average spacing for parity 5 births falls from 1.44 to 1.18, but
-% the spacing for parity 4 births increases only from 1 to 1.09. 
-% What this hides is, of course, that there are substantially more 
-% parity 4 births than there are parity 5 births--and only a slight 
-% decline in fertility from 4.16 to 4.11---and that the number of
-% abortions per 100 woman doubles.
-
-% non-uniform effect in spacing by parity
-% Interestingly, something similar happens when there is no son preference
-% See a=0.5, k = 18 all p. Fourth parity reduces throughout, but third parity
-% increases throughout.
-
-% from p= 20 to p=16 it looks like sex selection is falling overall
-% because the average spacing goes down substantially for parity 5 (1.44 to 1.18)
-% and spacing for parity 4 only increases from 1 to 1.09
-
-% Less clear but generally similar is k = 14]
-
-% The problem with testing this idea is that balance would, for example,
-% show up as people using sex selection on having 2 girls and 1 boy and
-% the desired fertility is 4. 
-% But, if people have high alpha then we would get the same outcome.
-
-% [something on the importance of this and the idea that are 
-% multiple forms of son preference.
-% people may treat their children equally, but would not abort
-% a male to ensure equal number of sons and daughters]
-
-% Discount rate
-
-The discount rate affects fertility little, but sex ratios 
-become more biased the more patient people are (higher $d$).%
-\footnote{
-If son preference is very strong the effect appear to 
-depend on the cost of children. 
-For low cost of children higher impatience leads to higher
-fertility, but for higher cost of children it is sometimes reversed.
-Furthermore, these effects are not very strong or clear and
-potentially non-linear.
-}
-% The motivation for this is that less weight you place on the future
-% the more appealing it is to simply have another child instead of
-% paying for prenatal sex determination, which is ``wasted'' if
-% you have a boy.
-Similarly, the number of abortions and the number of spells where
-prenatal scans are used are higher the more 
-weight is place on future utility over current utility.
-Just like the discount rate, increasing parents'  
-horizon (larger $T$) changes fertility little, but does tend to 
-increase the sex ratio in favor of boys when there is access 
-to sex selection.%
-\footnote{
-These simulation results are presented in the online Appendix.
-}
-Correspondingly, the number of abortions are higher the 
-longer the time horizon.
-
 % Highlights and tie into empirical model:
@@
 }
-First, the strongest driver of increased use of sex selection is 
-the fertility decline that arise from an higher cost of 
-children---for example because of more education for women or 
-migration to urban areas.
-% As discussed, an important predictor of cost of children is the
-% mother's education---more educated women have higher opportunity 
-% cost of time.
 The increased use of sex selection shows up both in the 
@@
 
-% Wonder if it would be possible to that some of the
-% couples with a son already that look like they are
-% using sex selection were not planning on having the
-% last child, but with prenatal testing and access to
-% abortion they would abort a female fetus but not
-% a male one, even if the pregnancy was ``unintended''
-% (as in having selected a high $e$, but random 
-% chance lead to a pregnancy anyway.
-
 % Empirical method
-The model highlights three major limitations of the simple 
+The model highlights two major limitations of the simple 
 empirical method, which a better empirical approach needs to 
 allow for.
-% First, as fertility declines the proportion of boys among births 
-% increases and the spells between births become longer.
-% Second, the higher the parity the longer the duration between births because of
-% the more intensive use of sex selection.
-% Finally, households may reverse its decision to use sex selection within a spell.
-First, the simple model cannot capture changes in fertility and the extent 
-to which these fertility changes drive the use of sex selection.
-Second, increased use of sex selection leads to longer spacing which,
+First, increased use of sex selection leads to longer spacing which,
 everything else equal, reduces the number of births available for 
@@
 the decline in sample size.
-Finally, by using only observed births the simple method cannot capture
+Second, by using only observed births the simple method cannot capture
 when parents change their decision on the use of sex selection;
@@
 
-\subsection{Desired Fertility and Sex Selection}
-
-A first step to understand the relationship between fertility and sex selection
-is to examine how use of sex-selective abortions vary with self-reported desired 
-fertility.
-If lower fertility drives sex selection and desired and actual fertility are
-at least partly correlated, women with lower desired fertility should be more 
-likely to use sex selection than women with higher desired fertility, 
-holding other characteristics constant.
-Figure \ref{fig:results_spell2_high_want} presents results by desired fertility 
-for the second spell of women with 8 or more years of education whose first child was a 
-girl.%
-\footnote{
-For women with living children the question asked was
-``If you could go back to the time you did not have any children and could choose exactly 
-the number of children to have in your whole life, how many would that be?'', while
-for women with no living children the question was
-``If you could choose exactly the number of children to have in your whole life, how many 
-would that be?''
-% P 116 Appendix F in NFHS book
-}
-
-A majority of better-educated women report that they want two or fewer 
-children, and the proportion who wants two or fewer is increasing over time.%
-\footnote{
-In the first period 2,055 out of 8,202 (25\%) women wanted 3 or more 
-children, including giving a non-numeric response.
-In the second period this number was 2,583 out of 16,600 (16\%) 
-and in the third period it was 1,264 out of 13,610 (9\%).
-} 
-To achieve a large enough sample of women who want three or more children, I use all 
-second spells that began in the period 1985 to 2006.
-This allows me to estimate non-proportional hazards by area of residence, sex of 
-previous child, and desired fertility.
-For both rural and urban women, the left panel shows the results for women who want two 
-or fewer children and the right panel shows the results for women who 
-want three or more children.%
-\footnote{
-Restricting to wanting exactly 3 children has little to no impact on the spacing
-pattern, suggesting that higher desired number of children does not lead to
-substantially shorter spacing.
-}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[Wants 2 or fewer children (N=7,779)]{
-    \begin{minipage}{0.31\textwidth}
-    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r8_pc}}\\
-    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r8_s}}
-    \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[Wants 3 or more children (N=864)]{
-    \begin{minipage}{0.31\textwidth}
-    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r4_pc}}\\
-    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r4_s}}
-    \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{0}
-\subfloat[Wants 2 or fewer children (N=4,851)]{
-    \begin{minipage}{0.31\textwidth}
-    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r7_pc}}\\
-    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r7_s}} 
-    \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{1}
-\subfloat[Wants 3 or more children (N=1,077)]{
-    \begin{minipage}{0.31\textwidth}
-    \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-    \subfloat[Probability of a boy (\%)]{\includegraphics[width=\textwidth]{want_spell2_high_r3_pc}}\\
-    \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{want_spell2_high_r3_s}}
-    \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Desired fertility and predicted probabilities of having a boy and 
-no birth yet from 9 months after first birth for
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on first child a girl and woman age 22 at first birth.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_want}
-\end{figure}
-
-Three main results stand out.
-First, the sex ratios by quarter for women who want 2 or fewer children show 
-substantial evidence of sex selection, while there is little evidence among those who want 
-3 or more.
-This supports that fertility is an important factor in the use of sex selection.
-Second, for women who want 2 or fewer children, use of sex selection is higher among urban 
-than rural women, but not significantly so.
-The proportion of boys born is between 55 and 60 percent and statistically 
-significant higher than the natural sex ratio for all quarters for urban women, whereas
-for rural women the proportion is generally 2 to 3 percentage points below the urban 
-level.%
-\footnote{
-For comparison, if 55 percent of children born in a given quarter were boys,
-approximately 14 percent of the female fetuses were aborted.
-Assume 105 boys per 100 girls born, the expected natural sex ratio.
-With $b$ boys, we should expect $b\frac{100}{105}$ girls born.
-If we observe $g$ girls the number of abortions is therefore $b\frac{100}{105}-g$
-and the percent aborted female fetuses is 
-$\frac{b\frac{100}{105}-g}{b\frac{100}{105}}\times 100$.
-With 55 percent boys we get $\frac{55\frac{100}{105}-45}{55\frac{100}{105}}\times 100 = 14.09$.
-The corresponding numbers for 60 percent and 65 percent boys are approximately 30 percent and
-43 percent of the female fetuses aborted.
-}
-
-Third, the effects of sex-selective abortions on spacing show clearly in the differences 
-across the survival curves for the different groups.
-A normal spacing pattern without sex-selective abortions---where most women have the second 
-child relatively early---leads to a survival curve with a steep slope first, followed 
-by a leveling off.
-This pattern is followed by rural women who want 3 or more children.
-As discussed above, use of sex-selective abortions should results in substantially
-longer spacing between births, which makes the survival curves appear more as 
-straight lines.
-Urban women who want 2 or fewer children show this pattern.
-
-Another way to see the effects of sex-selective abortions on spacing is to compare the 
-proportion of women who have not had a second birth yet at a specific time.
-Ten quarters into the spell---equivalent to 13 quarters (3\sfrac{1}{4} years) after the 
-first birth---just below 35\% of rural women who want 3 or more children have not had their 
-second birth yet, compared with more than 45\% among rural women who want 2 or fewer children.
-Similarly, among urban women about 35\% of those who want 3 or more children have not had 
-a second birth yet at 10 quarters after their first birth, compared with almost 55\% of 
-those  who want 2 or fewer.
-% These numbers reinforce that there is little sex selection among women who want 3 or
-% more children, regardless of whether they live in rural or urban areas, and that for
-% women who want 2 or fewer children more sex selection takes place among urban than
-% rural women.%
-% % \footnote{
-% % % proportions who end up with a second birth!
-% % The proportion of women who have not yet had a second birth at the end of the estimated
-% % spell period is higher for 
-% % }
-
-There are, however, three major methodological concerns with using self-reported 
-desired fertility.
-First, although the correlation between desired and actual fertility is positive,
-it is far from one.
-Second, it is potentially endogenous to the number of children a woman already has 
-and may be measured with error \citep{Jensen1985,Rasul2008,Ashraf2009}.
-Finally, there is much less variation in desired fertility than in actual fertility,
-making it difficult to precisely estimate changes in sex selection over time.
-I therefore next examine whether decreases in observed fertility over time are
-associated with increased use of sex-selective abortions.
-
-% The predicted percentage boys for the second, third and fourth spells for 
-% women with 8 or more years of education show that this is, indeed, the case.
-% As for the first spell, the results are presented using a representative woman
-% with the same characteristics as above, except that the ages at the beginning of
-% the spell are 22, 24 and 25 years for the second, third and fourth
-% spell and that the first spell length is set equal to 16 months.
-
-\subsection{Changes in Fertility over Time\label{sec:changes}}
-
-The first step when examining how declining fertility affects the use of sex selection is 
-to show how fertility has decreased over time.
-The challenge is that women who use sex selection have longer birth spacing, which 
-makes it look like they have lower fertility than they really do, and consequently would
-make the relationship between fertility and sex selection appear stronger than it really is.
-As I show below, and as suggested by the previous literature, women with one or more sons 
-do not appear to use sex selection.
-Hence, these women's fertility decisions will not be affected by the availability
-of prenatal sex determination techniques.
-I therefore show fertility progression only for women who have already had at least one 
-son, continuing to focus on the better-educated women.
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[2nd spell---has 1 boy (N=2,806)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}}\\
-        \subfloat[3rd spell---has 1 boy (N=1,409)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}}\\
-        \subfloat[3rd spell---has 2 boys  (N=780)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}}   
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-2}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[2nd spell---has 1 boy  (N=5,246)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}\\
-        \subfloat[3rd spell---has 1 boy (N=3,460)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}\\
-        \subfloat[3rd spell---has 2 boys (N=1,660)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[2nd spell---has 1 boy  (N=3,969)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}\\
-        \subfloat[3rd spell---has 1 boy (N=2,357)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}\\
-        \subfloat[3rd spell---has 2 boys (N=1,098)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted progression to birth for women with 8 or more years of education by 
-quarter (3 month period) conditional on having at least one boy. 
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal, and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:fertility_progression_boys}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{Rural}
-\setcounter{subfigure}{0}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[2nd spell---has 1 boy (N=1,404)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} \\
-        \subfloat[3rd spell---has 1 boy (N=700)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} \\
-        \subfloat[3rd spell---has 2 boys (N=370)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}}  
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{1}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[2nd spell---has 1 boy (N=3,381)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}\\
-        \subfloat[3rd spell---has 1 boy (N=1,987)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}\\
-        \subfloat[3rd spell---has 2 boys (N=945)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[2nd spell---has 1 boy (N=3,044)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}\\
-        \subfloat[3rd spell---has 1 boy (N=1,819)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}\\
-        \subfloat[3rd spell---has 2 boys (N=790)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted progression to birth for women with 8 or more years of education by 
-quarter (3 month period) conditional on having at least one boy. 
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal, and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:fertility_progression_boys}
-\end{figure}
-
-Figure \ref{fig:fertility_progression_boys} shows the predicted progression to
-next birth for urban and rural women with 8 or more years of education, conditional on 
-having at least one boy, by the starting period of the spell, and within each period by 
-spell.%
-\footnote{
-Could the prior births for each of these groups have been the result of sex selection?
-As I show in the online Appendix there is little evidence of sex selection on first births,
-so it is unlikely that women with a son as their first child ended up with a 
-boy through anything other than random chance.
-Similarly, for the third spell group, women with two boys are unlikely to have used sex 
-selection since there is no evidence on sex selection on first birth and no evidence of 
-sex selection if a son is already present.
-It is possible that third spell women with one son and one daughter could 
-have used sex selection in a prior spell, if they had the girl as the first child, as
-described below.
-There is, however, little difference in fertility progression for the third spell between 
-women with two sons and women with one son and one daughter as their first children.
-}
-In all cases the proportion of women without a birth by the end of the spell period has 
-increased substantial.
-In other words, fertility has declined over time for both urban and rural women.
-Although it is possible that some women will have a child after the end
-of each estimated spell, it is unlikely to be a substantial number given the shape
-of the survival curves.
-
-For urban women with a son as the first child, the proportion who did not have a second 
-child 6 years after the birth of their first child increased from around 15\% in 
-1972--1984 period to more than 30\% in the 1995--2006 period.%
-\footnote{
-Recall that for the second and higher spell, the spells are estimated starting from the 
-fourth quarter after the birth of their previous child.
-Hence, 3 quarters has to be added to the spell lengths in the figure to get the actual
-spacing.
-}
-Similarly, the proportion who did not have a third child by 6\sfrac{3}{4} years after their second
-birth went from 40\% in the 1972--1984 period to almost 70\% in the 1995--2006 period
-if the woman already had one son, and from 45\% to more than 70\% if she had two sons.
-Rural fertility is higher, but the underlying pattern is the same.
-In all cases, more women finish the spell without another birth in the last period than 
-in the first.%
-\footnote{
-The results for the fourth spell---available in the on-line Appendix---show similar 
-results with women with at least one son experiencing large reductions in progression
-rates over time.
-}
-
-Changes over time for this group of women provides an indication of whether increased 
-availability of contraceptives affects the spacing between births over time.
-Increased use of modern, reversible contraceptives allows greater control over spacing, 
-potentially making the survival curves straighter if there are \emph{uniformly} distributed
-``preferences'' for how long spacing between births should ideally be.
-There are two reasons why this is not a substantial concern here.
-First, use rates of modern, reversible contraceptive have not changed much.
-For India as a whole current use of any modern method has gone from 36.5\% in NFHS-1 to 
-48.5\% in NFHS-3, but most of this increase has come from female sterilization, which has 
-increased from 27.4\% to 37.3\% over the same period 
-\citep[p.\ 127]{International-Institute-for-Population-Sciences-IIPS2007}.
-Second, survival curves in Figure \ref{fig:fertility_progression_boys} appear to have 
-retained their shapes across periods to the extent possible given fertility declines, 
-suggesting that the availability of contraceptives has not had a strong effect on the 
-spacing between births.
-Because the estimations are done separately by periods the similarity of shapes come from 
-the data, not from assumptions about functional form.
-
-% [refer to discussion in model section on opposite effect on fertility of access
-% to sex selection.
-% Also use R3's point on differences in costs between boys and girls and the
-% effect of access to sex selection on fertility.
-% Given that abortion is relatively cheap the decline in fertility would 
-% suggest that girls are not substantially more costly than boys.
-% Thank anonymous referee for this point.
-% Include Jat village paper reference on cost of sex selection.]
-
-The decline in fertility over time implicitly provide information on the relative
-cost of having a boy versus a girl.%
-\footnote{
-I am grateful to an anonymous reviewer for suggesting this point.
-}
-As discussed in Section \ref{sec:model}, there are two opposite effects of introducing
-sex selection on fertility: parents can reach their desired number of sons with fewer 
-births, which reduces fertility, but also do not have to pay for unwanted children,
-and this wealth effect will tend to increase fertility.
-The size of the wealth effect depends on the relative cost of boys and girls and the cost 
-of sex selection; if girls are very costly and abortion cheap the wealth effect will be
-larger, making it more likely that fertility increases with introduction of 
-sex selection.
-The cost of sex selection does, indeed, appear to be relatively low 
-\citep[see, for example][]{Khanna1997}.
-Hence, the decline in fertility after the introduction of sex determination is an 
-indicator that girls are not substantially more expensive than boys.
-
-\subsection{Effect of Declining Fertility on Sex-selective Abortions}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Second spell for urban women---first child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,689)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,869)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=3,774)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Third spell---first two children girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=709)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,654)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=1,000)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from 9 months after first birth for urban
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 22 at first birth for second spell and on age 24 at second
-birth for third spell.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:over_time_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Second spell for rural women---first child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=1,305)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=3,105)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,823)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Third spell---first two children girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=348)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=982)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=863)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from 9 months after first birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 22 at first birth for second spell and on age 24 at second
-birth for third spell.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:over_time_rural}
-\end{figure}
-
-The second step is to show that with the fertility decline there is a corresponding 
-increase in sex-selective abortions.
-If the decline in fertility drives the increase in use of sex-selective abortions, we 
-should see an increase in sex ratios for a given spell number \emph{and} use of sex 
-selection for earlier spells over time.
-As discussed, the group most likely to use sex selection is women without sons.
-Figures \ref{fig:over_time_urban} and \ref{fig:over_time_rural} therefore show the 
-development in sex ratios by quarter for second and third spells for women without sons in 
-urban and rural areas.
-Both urban and rural women follow the expected pattern, consistent with declining 
-fertility driving the use of sex selection.
-
-For urban women's third spell in the first period, the predicted sex ratios  
-show no evidence of sex-selective abortions.
-After the introduction of prenatal sex determination techniques there is substantial
-evidence of sex selection both before and after sex selection was made illegal.
-The increased sex ratio within the spell for the 1985--1994 period is likely the
-result of those women who---for one reason or another---waited longer to try for 
-a third child having easier access to sex selection.
-Compared to the 1985--1994 period, there appears to be a leveling off of the sex ratio 
-for the 1995--2006 period and the overall sex ratio may even be a little lower.
-Consistent with this there is little difference in the survival curves between
-the two periods.
-
-Does the small difference between the two last periods for the third spell then show that 
-banning sex selection at least stalled the increase in the use of sex selection?
-The results for the second spell show that this is not the case.
-With the falling fertility there is increased use of sex selection for the 
-second spell.
-There is limited evidence of sex selection for the second spell in the 1985--1994 
-period, which is expected given that many women were still having 
-three children.
-For the 1995--2006 period, however, there is is a consistently high and 
-statistically significant sex ratio.
-Hence, with declining fertility the use of sex selection has simply moved to an
-earlier parity.
-Consistent with the theoretical model predictions the result is a decline in 
-sex ratio for an \emph{individual} parity at the same time as the overall
-use of sex selection increases.
-The most likely explanation for the relative small difference between periods for 
-the third spell is that a smaller proportion of women make it to a situation
-where they have two girls as their first two children in the latest period;
-those with the strongest preference for having a boy and for lower fertility have 
-already used sex selection during the second spell.
-
-Rural women follow the same general pattern as urban women, but the samples are smaller
-making for noisier estimates.
-The changes between the 1985--1994 and 1995--2006 periods for the third spell is again
-of special interest because it appears that the use of sex selection falls over time.
-But, the change for the second spell over time is even more pronounces for rural women
-than for urban women with very substantial increase in the use of sex selection for
-the second spell.
-
-Another way to see the interaction between fertility and sex selection is to compare
-the survival curves across sex composition and spells.
-As fertility has fallen the survival curves have become straighter for
-women without sons relative to for women with sons;
-the result of longer spacing arising from the use of sex selection.
-Among women with no sons the proportion of women without a birth by the end of 
-the spells has increased, but to a much smaller extent than for women with 
-at least one son.
-% Furthermore, the close to straight survival curves even at the end of the spells is an 
-% indication that at least some women who have not had a birth yet by the end of the spell 
-% may still have a child.
-
-\subsection{Fertility and Sex Selection Across Groups}
-
-As shown the decline in fertility over time is associated with both an increased use 
-of sex-selective abortions for a given spell \emph{and} use of sex selection for 
-earlier spells for the women most likely to have low and falling fertility, women
-with 8 or more years of education.
-What remains is to show that women who have lower costs of children have higher
-fertility and consequently show less or no use of sex-selective abortions. 
-Assuming that preferences for having one son is similar across education groups
-the lower cost of children makes it more attractive for less-educated women to continue
-having children with the aim of having at least one son instead of resorting to
-sex selection.
-
-\begin{figure}[htpb]
-\centering
-\caption*{No Education}
-\setcounter{subfigure}{-2}
-\subfloat[Spell 1 (N=1,762)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[Spell 2 - 1 girl (N=952)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Spell 3 - 2 girls (N=475)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{1 to 7 Years of Education}
-\setcounter{subfigure}{1}
-\subfloat[Spell 1 (N=2,302)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[Spell 2 - 1 girl (N=1,082)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[Spell 3 - 2 girls (N=425)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{8 or More Years of Education}
-\setcounter{subfigure}{4}
-\subfloat[Spell 1 (N=9,116)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{5}
-\subfloat[Spell 2 - 1 girl (N=3,774)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[Spell 3 - 2 girls (N=1,000)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth by quarter (3 month period) for urban women for 1995--2006. 
-N is number of women in the relevant group in the underlying samples.
-}
-\label{fig:groups_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{No Education}
-\setcounter{subfigure}{-2}
-\subfloat[Spell 1 (N=7,922)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[Spell 2 - 1 girl (N=3,686)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Spell 3 - 2 girls (N=1,879)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{1 to 7 Years of Education}
-\setcounter{subfigure}{1}
-\subfloat[Spell 1 (N=5,208)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[Spell 2 - 1 girl (N=2,159)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[Spell 3 - 2 girls (N=848)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{8 or More Years of Education}
-\setcounter{subfigure}{4}
-\subfloat[Spell 1 (N=7,504)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{5}
-\subfloat[Spell 2 - 1 girl (N=2,823)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[Spell 3 - 2 girls (N=863)]{
-    \begin{minipage}{0.21\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth by quarter (3 month period) for rural women for 1995--2006. 
-N is number of women in the relevant group in the underlying samples.
-}
-\label{fig:groups_rural}
-\end{figure}
-
-Figures \ref{fig:groups_urban} and \ref{fig:groups_rural} show sex ratios and
-survival curves for the three education groups for the latest period, 1995--2006,
-for urban and rural women.
-For each education group the figure shows the first spell, from marriage to first
-birth, the second spell for women with a girl as the first child, and, finally,
-the third spell for women with two girls as their first children.
-The second and third spells for the better-educated women are the same as in
-Figure \ref{fig:over_time_urban} and \ref{fig:over_time_rural}, panels (c) and (f),
-and are reproduced to ease comparison.
-
-As expected, progression rates are higher the lower the education level and higher in
-rural areas than in urban areas.
-The proportion of women with no education who end up with no birth at the end of the 
-third spell is less than 10 \% for urban women and less than 5\% for rural women.
-For those with 1 to 7 years of education less than 20\% of urban women do not go on to 
-having a third child, while for rural women it is less than 10\%.
-What is more, the progression rates for women with either two boys or a boy and a girl
-as their first children are only marginally higher than for women with two girls.%
-\footnote{
-In the interest of space these are shown in the online Appendix. 
-The Appendix also shows progression rates for the fourth spell.
-Although samples become very small, the results correspond well.
-Progression rates are higher the lower the education and higher for rural women than
-for urban women.
-The samples become so small exactly for the reason discussed above:
-there is a less than 12\% chance of not having a son by the third child.
-}
-Hence, women with less than 8 years of education still have high fertility in both
-urban and rural areas.
-
-Corresponding to the higher fertility among women with less education there is little
-evidence of sex selection among women with less than 8 years of education.
-Generally the predicted sex ratios are not statistically significantly
-higher than the natural rate and the survival curves all show a similar pattern where
-most of the births occur early in the spell and there is no evidence of the changing
-survival curves associated with longer spells that would indicate use of sex-selective 
-abortions.%
-\footnote{
-The exceptions are small parts of the second spell for no education women and 
-third spell for women with 1 to 7 years of education. 
-As the survival curves show both are based on very few births.
-Fourth spell results generally confirm the absence of sex selection among women with 
-less education.
-}
-Hence, there is evidence of two different paths to having a son:
-high education women have few children and substantial use of sex selection, while
-low education women have many children and little to no use of sex selection.
-
-Two other important results stand out.
-First, there is no evidence of sex selection on first birth, no matter the education
-level.
-The sex ratios are never statistically significant different from the expected and 
-timing of births is close to identical for all groups, with most women having their 
-first child soon after marrying.%
-\footnote{
-This cast serious doubts on the data used by \citet{jha06} and their result that 
-there is substantial use of sex selection on first births.
-As discussed above and in the online Appendix their results are likely the result of
-substantial recall bias.
-}
-Second, the natural sex ratio for India appear to be in line with what is found for 
-other countries at around 105 boys per 100 girls.
-For all groups for whom we would expect little to no use of sex selection and have
-many births to base the estimate on, such as rural women with no education and urban
-women with 8 or more years of education, the sex ratios almost completely coincide 
-with the 105/100 line.
-
-% points to cover:
-% - fertility is higher, the lower the education level, as shown by the lower proportion
-% who end up with no birth (also refer to appendix figures)
-% - no evidence of sex selection for lower educated women (both sex ratios and survival
-% curves show this)
-% - no sex selection on first birth, no matter the education level
-% - sex ratio at birth is 105/100, showing no differences between India and other places
+\subsection{Comparing the Hazard and Simple Models}
+
+As detailed in the main paper, one of the main advantages of the hazard model 
+approach is that it can be used to predict what completed fertility, number of abortions, 
+and sex ratios will be once women are done with childbearing.
+This cannot be done with the simple model because it does not predict fertility
+progression, does not take into account censoring, and cannot capture if parents
+change their use of sex selection within a spell.
+% This is possible because the hazard model approach uses both censored and 
+% uncensored observations, which, in turn, allows me to predict both how many 
+% women will have a next birth and the final sex ratio for that parity, under the 
+% assumption that the patterns of spacing and use of sex selection remain 
+% the same within a spell.
+We can, however, still compare differences in predicted sex ratios for 
+\emph{individual} parities.%
+\footnote{
+The simple model uses only observed births and the predicted sex ratio is 
+therefore simply what we observe for the relevant uncensored sample.
+}
+
+For each parity, the simple model is
+\begin{equation}
+Y_i = \gamma + \alpha' \mathbf{Z_i} + \beta' \mathbf{X}_{i} + \epsilon_i,
+\end{equation}
+where $Y$ is a dummy variable that takes the value 1 if the child born is a boy and zero 
+if it is a girl, and the vectors of explanatory variables, $\mathbf{Z}_{i}$ and 
+$\mathbf{X}_{i}$, are the same as for the proposed method, except that 
+$\mathbf{Z}_{i}$ obviously does not include the baseline hazard and that there are 
+no time dependence.%
+\footnote{
+To ease presentation, the indicator for parity number is not shown.
+}
+I estimate this using a logit model, although a linear probability model leads to
+similar results.
+This model is estimated on all observed births for a given parity in the relevant 
+period to ensure that the results are as close to the standard method of 
+examining sex selection \citep[see, for example, ][]{retherford03b,jha06,abrevaya09}.
+
+% Two factors determine the differences in the predicted sex ratio and number 
+% of abortions between the two models.
+% First, how many women have censored spells but will have a birth after the survey.
+% Second, how much use of sex selection changes within a spell.
+% % If there are few censored spells or the women with the censored spells have low likelihoods
+% % of having a next birth the two models produce similar predicted sex ratios and 
+% % number of abortions.
+% % If there is little change in the use of sex-selective abortions over a spell then the
+% % predicted sex ratio is going to be similar for the two models, although the predicted
+% % number of abortions will differ depending on how many censored observations there are
+% % and how likely they are to exit with a birth.
+% Consider four possible combinations of the two factors.
+% First, there are few censored birth spells and use of sex selection is constant over
+% the spell.
+% In that case, the predictions will be similar across the two models.
+% Second, there are many censored birth spells and use of sex selection is constant over
+% the spell.
+% The predicted sex ratios will be similar, but the simple model will predict a too low
+% number of abortions per woman and fertility will appear to be falling faster than it is.
+% Third, there are few censored birth spells and use of sex selection changes substantially
+% with spell length.
+% The sex ratios again are close to each other in the two models, but the estimated use of
+% abortions will be biased in the simple model because it cannot account for the changes
+% in use of sex selection over the spell.
+% Finally, there are many censored birth spells and use of sex selection changes substantially
+% with spell length.
+% In this case the predicted sex ratio based on the simple model will be biased.
+% Specifically, if use of sex selection declines over the spell, the simple model 
+% will predict a higher final sex ratio than the hazard model.
+% Similarly, the predicted number of abortions will also be biased. 
+% With sex selection and falling fertility censored spells become more and more likely,
+% but how much this matter is an empirical question.
+
+% To determine the predicted number of abortions I use the natural sex ratio.
+% On average, 105 boys should be born per 100 girls born, which corresponds exactly
+% with what we observe for first births in India as seen above.
+% Hence, if we observe $b$ boys, then we should expect to see $b\frac{100}{105}$ girls.
+% If we observe $g$ girls the number of abortions is therefore $b\frac{100}{105}-g$.
+% The standard approach is to use the observed sex ratio for a given parity and 
+% calculate the number of abortions using this formula.
+% For the hazard model it is, however, possible to calculate the number of predicted
+% abortions for each time period based on the predicted sex ratio and the 
+% number of women predicted to exit with a birth in that period using the same formula.
+% Summing across the entire period covered by the hazard model provides a predicted total 
+% number of abortions.%
+% \footnote{
+% There is no difference between the two method in the predicted number of abortions for 
+% those women for whom we observe the subsequent birth.
+% }
+
+% [NEED TO WORK THROUGH A MATH EXAMPLE OF THE FIRST FACTOR: IS THAT REALLY CORRECT?]
+% period 0: 100 births 65 boys 35 girls 26.90476191
+% period 1: 100 births 60 boys 40 girls 17.14285714
+% period 2: 100 births 55 boys 45 girls 7.380952381
+%                     180 boys 120 girls abortions: 51.42857143
+% 
+% period 0: 1000 women: 512 boys 400 girls , 88 abortions  87.61904762
+% period 1:   98 women: 50 boys 42 girls, 6 Abortions  5.619047619
+% period 1:    6 women: 3.073 boys 2.927 girls 0 abortions -0.000333333
+%                     562 boys 442 girls    93.23809524 93.2377619 93.23776191
+% 
+% [HOW TO CALCULATE NUMBER OF ABORTIONS HERE]
+%
+% In addition, the standard model does not provide any information about abortions
+% for those women for whom we do not observe a birth.
+% In contrast, the hazard model can be used to predict the number of abortions even for 
+% those women who have not yet had a birth at the parity of interest.
+% This number is the sum of two set of predictions.
+% First, the number of abortions that are predicted have occurred up to the time of the 
+% survey for women without a given parity birth.
+% Second, we can predict how many additional abortions will take in the future for these
+% women from the time of censoring until the end of the spell period used for the hazard
+% model.
+% This follows directly from the standard feature of hazard models where one can predict
+% the likelihood of future exits for those censored.
+% To the extent that people change their use of sex-selective abortions within a spell
+% the two numbers will be different.
+%
+% [TRYING TO WORK THROUGH THE SET-UP HERE]
+% 
+% For each women who had one birth we follow her until 24 quarters (6 years) after the 
+% birth of her first child. 
+% Contrary to the standard logit model we can predict two things: How likely it is that she
+% will have her second child during a particular quarter and what the sex ratio will be in 
+% that quarter.
+% In other words, by the end of the 24 quarter period we will know the probability of her
+% having had a child, which is what is shown by the survival curves in the graphs above,
+% and expected sex ratio for all women like her.
+% So, one women might have 73 percent probability of giving birth to a second child within
+% the 24 quarters with 58.3 percent probability of a boy and a 41.7 percent probability
+% of a girl, whereas another might only have a 29 percent probability of giving birth to a 
+% second child with a 55.4 percent probability of a son and a 44.6 percent probability of a
+% girl.
+% 
+% Summing across all women with specific characteristics, like being an urban woman with
+% a girl as her first child, we can then predict how many children will be born to these
+% women in the 6 years after the birth of their first child, together with information on
+% how many abortions will have taken place and the final sex ratio for those second-born
+% children.
+% 
+% The advantage of this is that it is not reliant just on observed births.
+% To the extent that the probability of using sex-selective abortions changes with time since
+% the last birth the results from the hazard model prediction will be different from the
+% Logit model prediction (which is just the sex ratio for birth observed in the 6 year 
+% period).
+% Furthermore, even if the probability of sex-selective abortions does not change substantially 
+% with duration since last birth, the hazard model provides an estimate of how many births
+% there will be and what the final sex ratio for a given parity birth will be.
+% The more censored observations there are the bigger the difference between the logit and
+% the hazard models are going to be.
+% This is important because that those numbers are an input into determining what the
+% population sex ratio will be.
+
+% [is there a way of understanding the difference between censored and uncensored women
+% using the hazard model?
+% One option would be to run everybody until they are censored and see if that fits with
+% the logit numbers.
+% that should presumably match the logit results except for picking up differences in use
+% of sex-selective abortions. 
+% This means that the births should be the same for the two methods.
+% 
+% For those censored we could then run the rest of the time. 
+% This would require that we started from one woman again, instead of continuing from the
+% censoring left off.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{footnotesize}
+\begin{threeparttable}
+\caption{Comparison of Hazard and Simple Models for  \protect\linebreak
+Women with 8 or More Years of Education}
+\label{tab:compare2}
+\begin{tabular} {@{} l D{.}{.}{5.2} D{.}{.}{5.2} D{.}{.}{5.2} D{.}{.}{5.2}   @{}} \toprule
+                                  &  \multicolumn{2}{c}{Urban}        & \multicolumn{2}{c}{Rural}         \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+                                  & \mco{Simple}     &  \mco{Hazard}   &  \mco{Simple}    & \mco{Hazard}      \\   \midrule
+                                  & \multicolumn{4}{c}{1985--1994 - Second Birth} \\ \cmidrule(l){2-5}
+                                  & \multicolumn{4}{c}{1 girl} \\
+Number of women\tnote{a}          &             & 4,869   &         & 3,105   \\
+Births\tnote{b}                   &     3,848   & 3,926   & 2,417   & 2,795   \\
+Percentage boys                   &      54.0   &  54.7   &  52.6   &  53.5   \\
+Sex ratio (boys per 100 girls)    &     117.4   & 120.7   & 110.9   & 115.1   \\
+\addlinespace 
+                                  & \multicolumn{4}{c}{1985--1994 - Third Birth}  \\ \cmidrule(l){2-5}
+%                                   & \multicolumn{4}{c}{1 boy and 1 girl}        \\
+% Number of women\tnote{a}          &             & 3,460   &         & 1,987   \\
+% Births\tnote{c}                   &     1,431   & 1,558   & 1,107   & 1,336   \\
+% Percentage boys                   &      53.0   &  52.5   &  53.5   &  54.6   \\
+% Sex ratio (boys per 100 girls)    &     112.9   & 110.4   & 115.0   & 120.2   \\
+% \addlinespace
+                                  & \multicolumn{4}{c}{2 girls}        \\
+Number of women\tnote{a}          &             & 1,654   &         &   982   \\
+Births\tnote{c}                   &     1,034   & 1,092   &   682   &   853   \\
+Percentage boys                   &      60.8   &  63.7   &  54.7   &  57.4   \\
+Sex ratio (boys per 100 girls)    &     155.3   & 175.3   & 120.7   & 134.6   \\
+\addlinespace 
+                                  & \multicolumn{4}{c}{1995--2006 - Second Birth} \\ \cmidrule(l){2-5}
+                                  & \multicolumn{4}{c}{1 girl} \\                                                  
+Number of women\tnote{a}          &             & 3,774   &         & 2,823   \\
+Births\tnote{b}                   &     3,031   & 2,704   & 2,489   & 2,407   \\
+Percentage boys                   &      58.0   &  58.6   &  56.0   &  56.9   \\
+Sex ratio (boys per 100 girls)    &     138.1   & 141.3   & 127.1   & 132.2   \\
+\addlinespace 
+                                  & \multicolumn{4}{c}{1995--2006 - Third Birth}  \\ \cmidrule(l){2-5}
+%                                   & \multicolumn{4}{c}{1 boy and 1 girl}        \\
+% Number of women\tnote{a}          &             & 2,357   &         & 1,819   \\
+% Births\tnote{c}                   &       830   &   775   &   853   &   998   \\
+% Percentage boys                   &      53.9   &  52.9   &  55.5   &  56.5   \\
+% Sex ratio (boys per 100 girls)    &     116.7   & 112.1   & 124.5   & 129.8   \\
+% \addlinespace
+                                  & \multicolumn{4}{c}{2 girls}        \\
+Number of women\tnote{a}          &             & 1,000   &         &   863   \\
+Births\tnote{c}                   &       695   &   600   &   690   &   661   \\
+Percentage boys                   &      65.5   &  62.4   &  62.0   &  61.7   \\
+Sex ratio (boys per 100 girls)    &     189.6   & 166.0   & 163.4   & 161.0   \\
+\bottomrule
+\end{tabular}                        
+\begin{tablenotes} \tiny
+\item \hspace*{-0.5em} \textbf{Note.} 
+The simple models are estimated using logit on all births for a given parity that
+occurred during the relevant time period.
+The hazard models are estimated using all spells that began in the relevant time period.
+For the second birth the hazard model covers the period from beginning of spell to 6 
+years (24 quarters) after the birth of the first child.
+For the third birth it covers the period from beginning of spell to 7.25 years 
+(29 quarters) after the birth of the second child for the period 1985--1994 and from 
+beginning of spell to 5.75 years (23 quarters) after the birth of the second child for 
+the period 1995--2006.
+\item[a] Number of women in period who began the spell with given sex composition of prior 
+child/children in the relevant period.
+\item[b] For Logit model the number of women who are observed to have a second birth
+in the period. 
+For hazard model the predicted number of second births that will occur between beginning 
+of the spell and 6 years (24 quarters) after the birth of the first child.
+% \item[c] Number of women in period who had one boy and one girl as their first two children.
+\item[c] For Logit model the number of women who are observed to have a third birth
+in the period. 
+For hazard model the predicted number of third births that will occur between beginning of 
+the spell and 7.25 years (29 quarters) after the birth of the second child for the
+1985--1994 period and between beginning of the spell and 5.75 years (23 quarters) after 
+the birth of the second child for the 1995--2006 period.
+\end{tablenotes}
+\end{threeparttable}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+I focus on those cases where there is evidence of sex-selective abortions: the spells
+from parity one to two and two to three for women with eight or more years of education.%
+\footnote{
+The results for the spell from parity three to four are available on request.
+They are not presented because the number of educated women who end up with three births 
+and the probability of having a fourth birth are small, which makes
+comparing the simple and hazard models with any precision difficult.
+}
+Table \ref{tab:compare2} shows the number of women who enter the second and third spells
+for the hazard model,
+the number of births, observed in the case of the simple model and predicted in the case 
+of the hazard model, predicted percent boys, and the associated predicted sex ratio.
+It is possible for the number of births used for the simple model to be larger than the
+hazard models' predicted number of births because the simple model is based
+on all births that occurred in the period---independently of when the prior birth
+occurred---whereas the hazard model uses only spells that began in the period.
+
+%
+% We begin with women who had a girl as their first child.
+% Table \ref{tab:compare2} shows the number of women who enter the second spell,
+% the number of births by the end of the six year period following the first birth,  
+% observed in the case of the logit model and predicted in the case of the hazard model, 
+% predicted number of abortions, and the sex ratio.%
+% \footnote{
+% The two latter obviously captures the same information and is both presented for
+% the reader's convenience.
+% }
+
+For the 1985--1994 period---which is when sex selection become available---the 
+hazard model consistently predicts a higher sex ratio than the logit model.
+Furthermore, some of these differences are substantial.
+For urban women with 2 girls as their first two children, the hazard model
+predicts a sex ratio of 175 boys per 100 girls, whereas the simple method
+``only'' predicts 155 boys per 100 girls.
+The difference is smaller in rural areas but still 14 boys per 100 girls
+higher for the hazard model than for the simple model.
+A similar, if less pronounced pattern, show up for the second birth,
+where the hazard model predict 3 and 5 boys more per 100 girls for
+urban and rural women.
+
+For the latest period, 1995--2006, the hazard model still produces higher 
+predicted sex ratios for second birth and the differences are of a 
+similar magnitude to the 1985--1994 period.
+The predicted sex ratios for the third birth are, however, 
+higher for the simple model than for the hazard model.
+This difference is substantially for urban women where the difference 
+is 23 boys extra per 100 girls.
+
+A possible explanation for these differences is that the simple model 
+fails to capture the move towards lower fertility and the subsequent 
+increase in the use of sex-selective abortions at earlier parities that 
+occurred over the periods.
+The results also suggest that the take-up of sex selection occurred 
+rapidly as the new methods became available and that this take-up
+is not fully captured by the simple model.
+More broadly, a possible interpretation of the differences is that
+the simple model will tend to underestimate when sex-selective abortions
+are initially spreading in use and overestimate when the spread of sex 
+selection is slowing.
+This is most clearly seen for the third births for urban women where
+the hazard model show a \emph{decline} is use of sex-selective abortions,
+consistent with the lower fertility as discussed in the main paper,
+while the simple model show a substantial increase.
+
+% [CLOSING ARGUMENTS ON COMPARISON?]
+% [logit will tend to underestimate when sex-selective abortions is spreading/increasing
+% and overestimate when sex-selective abortions is declining.]
+
+% Urban
+% 0.566585492 hazard sex ratio for 1985
+% 0.592900726 hazard sex ratio for 1995
+% 
+% 0.554402294 logit sex ratio for 1985
+% 0.593989533 logit sex ratio for 1995
+% 
+% Rural
+% 0.544119243 hazard sex ratio for 1985
+% 0.579341591 hazard sex ratio for 1995
+% 
+% 0.530621491 logit sex ratio for 1985
+% 0.573022963 logit sex ratio for 1995
+
+% I begin with women who had a girl as their first child.
+% For rural women in the 1985--1994 period relatively few censored women are
+% predicted to go on to have a second birth (only 5 percent of the starting population
+% is predicted to have a second birth and have not yet had one).
+% In addition, there is only some evidence of sex-selective abortions.
+% Hence, the predicted sex ratios for the simple and hazard models are close. 
+% There are slightly more abortions for the hazard model, but the abortion rates (number
+% of abortions per birth) are fairly similar between the observed births and those predicted
+% to have a birth later.
+% 
+% Urban women in the same time period follow a similar pattern with relatively few 
+% censored women predicted to move on to a second birth (around 2 percent of starting 
+% population), but the abortion rate for those additional births is 8.1 abortions per 100 
+% births, whereas it is only 6.7 for the observed births, as we would expect from the 
+% increasing probability of having a son with increasing spell length seen in panel (b) in 
+% Figure \ref{fig:results_spell2_high_urban}.
+% Despite this the resulting difference in sex ratios is
+% relatively small because of the small number of censored women predicted to exit with a
+% birth.
+% 
+% 
+% Not surprisingly there are substantially more censored observations for the 1995--2006
+% period.
+% For urban women about 19 percent of the starting population are predicted to have a
+% second birth but have not yet had one and for rural women it is 23 percent.
+% This allows for potentially larger differences in predicted sex ratios and number of
+% abortions.
+% Despite the large number of censored observations for rural women there is relatively
+% little difference in the predicted sex ratio.
+% The more interesting difference is for urban women in the 1995--2006 period.
+% The hazard model predicts 100 more abortions by the end of the spell, but the simple 
+% model \emph{overestimates} the final sex ratio.
+% The simple model predicts 143.5 boys and the hazard model 141.3 boys per 100 girls.
+% This is consistent with the very high probability of having a son early on in the spell
+% followed by a somewhat lower probability for later births seen in panel (c) in 
+% Figure \ref{fig:results_spell2_high_urban}.
+% 
+% 
+% 
+% The lower two panels of Table \ref{tab:compare2} presents the predicted outcomes for urban
+% and rural women for the third spell, split by the sex composition of their first two 
+% children and when the spell began.%
+% \footnote{
+% There is no evidence of sex-selective abortions and very few births for women with two boys 
+% and those predictions are therefore not presented.
+% }
+% For urban women with two girls in the 1985--1994 period there are only 77 more births for 
+% the hazard model, but the difference in number of abortions is 15 with the hazard model 
+% predicting 266 abortions and the simple model 251.
+% The resulting sex ratio is 175.3 for the hazard model versus ``only'' 170.0 for
+% the simple model.
+% In other words, it appears that the simple model underestimates the spread of the use of
+% sex-selective abortions during the expansion of access to prenatal sex determination 
+% for this group of urban women.
+% As discussed in the paper, use of sex selection for urban women with two girls appears to  
+% have fallen from the 1985--1994 period to the 1995--2006 period, but this is mainly an 
+% indication that sex-selective abortions are being used more during the spell to second 
+% birth for this group of women for the 1995--2006 period.
+% The result is fewer women with two girls for their first two births and those who do are 
+% substantially less likely to have a third birth than they were before.
+% 
+% For rural women the main difference between the two models is for those with one boy
+% and one girl in the 1995--2006 period.
+% Only about 60\% of the birth predicted by the hazard model are observed in the simple
+% model, leading to substantial censoring.
+% Furthermore, use of sex-selective abortions is predicted to be substantial for those
+% remaining births resulting in a sex ratio of 129.8 for the hazard model and 124.6 for
+% the simple model. 
+% As discussed in the paper, this case is the exception to the rule that sex selection
+% does not appear to be used by families that already have one son.
+% Presumably the use by rural women in this case is an insurance against mortality.
 
@@
 \setcounter{table}{0}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_100}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.41 &  50.3 &  5.41 &  50.2 &  5.42 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
- k = 16        &  4.10 &  51.4 &  4.11 &  51.3 &  4.16 &  50.6 &  4.17 &  50.5 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.19 &  52.9 &  3.25 &  51.7 &  3.25 &  50.0 \\
- k = 20        &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  54.7 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  61.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.29 &  50.6 &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
- k = 14        &  5.26 &  53.3 &  5.37 &  51.5 &  5.40 &  50.4 &  5.41 &  50.1 &  5.42 &  50.0 \\
- k = 16        &  4.10 &  57.8 &  4.10 &  52.6 &  4.10 &  51.4 &  4.11 &  51.2 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  57.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.8 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.27 &  60.7 &  2.31 &  59.5 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.14 &  54.2 &  7.26 &  51.4 &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  61.7 &  5.07 &  56.1 &  5.11 &  53.6 &  5.22 &  50.9 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  66.3 &  4.06 &  60.1 &  4.07 &  58.6 &  4.07 &  55.2 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  69.7 &  3.13 &  68.3 &  3.13 &  64.9 &  3.13 &  57.5 &  3.32 &  50.0 \\
- k = 20        &  2.68 &  67.5 &  2.25 &  61.2 &  2.25 &  61.1 &  2.25 &  61.1 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.09 &  62.8 &  7.13 &  57.5 &  7.19 &  53.9 &  7.26 &  51.7 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  73.9 &  5.05 &  66.6 &  5.07 &  61.9 &  5.08 &  58.5 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  74.9 &  4.06 &  73.0 &  4.06 &  68.8 &  4.07 &  63.3 &  4.17 &  49.9 \\
- k = 18        &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.5 &  3.13 &  68.3 &  3.32 &  50.0 \\
- k = 20        &  2.73 &  72.5 &  2.69 &  72.1 &  2.56 &  70.7 &  2.25 &  66.6 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  97.2 &  2.00 &  86.6 &  2.00 &  68.7 &  2.00 &  62.5 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_95}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.41 &  50.2 &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
- k = 16        &  4.11 &  51.3 &  4.16 &  50.7 &  4.17 &  50.3 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  53.9 &  3.25 &  51.9 &  3.25 &  51.7 &  3.25 &  50.0 &  3.25 &  50.0 \\
- k = 20        &  2.50 &  55.0 &  2.50 &  55.0 &  2.50 &  54.7 &  2.50 &  52.6 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.1 &  2.00 &  59.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.30 &  50.1 &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
- k = 14        &  5.38 &  51.4 &  5.40 &  50.2 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 \\
- k = 16        &  4.10 &  54.9 &  4.10 &  51.4 &  4.13 &  51.0 &  4.17 &  50.5 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.26 &  51.8 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.1 &  2.27 &  60.7 &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.27 &  51.2 &  7.33 &  50.1 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.06 &  58.0 &  5.14 &  52.7 &  5.22 &  50.8 &  5.25 &  50.1 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  59.0 &  4.06 &  57.8 &  4.07 &  52.6 &  4.08 &  51.2 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  69.0 &  3.13 &  64.8 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.27 &  60.7 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.11 &  58.4 &  7.23 &  52.2 &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  68.2 &  5.06 &  60.3 &  5.10 &  54.7 &  5.20 &  51.5 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  74.1 &  4.06 &  69.0 &  4.06 &  61.3 &  4.07 &  57.5 &  4.17 &  49.9 \\
- k = 18        &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  68.3 &  3.13 &  64.9 &  3.32 &  50.0 \\
- k = 20        &  2.71 &  72.4 &  2.56 &  70.7 &  2.00 &  62.5 &  2.00 &  62.4 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  85.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_90}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
- k = 16        &  4.16 &  50.7 &  4.17 &  50.5 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.25 &  51.9 &  3.25 &  51.8 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
- k = 20        &  2.50 &  55.0 &  2.50 &  54.7 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.3 &  2.00 &  56.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
- k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
- k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.17 &  50.5 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.16 &  53.5 &  3.26 &  51.8 &  3.28 &  50.9 &  3.32 &  50.0 \\
- k = 20        &  2.27 &  60.8 &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  53.8 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.1 &  2.00 &  56.2 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.10 &  53.4 &  5.24 &  50.5 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  58.4 &  4.07 &  52.2 &  4.10 &  51.0 &  4.13 &  50.5 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  66.8 &  3.13 &  54.0 &  3.14 &  53.8 &  3.26 &  51.8 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.28 &  60.3 &  2.50 &  55.0 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.3 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.16 &  53.9 &  7.32 &  50.3 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  62.5 &  5.08 &  54.1 &  5.22 &  50.8 &  5.26 &  50.0 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  71.3 &  4.06 &  58.8 &  4.07 &  55.2 &  4.08 &  51.2 &  4.17 &  49.9 \\
- k = 18        &  3.13 &  69.9 &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  53.9 &  3.32 &  50.0 \\
- k = 20        &  2.64 &  71.6 &  2.00 &  62.5 &  2.00 &  62.5 &  2.01 &  62.3 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_85}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.42 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
- k = 16        &  4.16 &  50.6 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.25 &  51.9 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
- k = 20        &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
- k = 14        &  5.40 &  50.2 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
- k = 16        &  4.16 &  50.7 &  4.17 &  50.6 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.14 &  53.7 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 &  3.32 &  50.0 \\
- k = 20        &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  52.6 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.24 &  51.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  52.2 &  4.13 &  50.7 &  4.14 &  50.4 &  4.16 &  49.9 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.14 &  53.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.31 &  59.5 &  2.50 &  55.0 &  2.52 &  54.4 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.13 &  58.1 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.31 &  50.7 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.07 &  54.9 &  5.24 &  50.5 &  5.26 &  50.0 &  5.27 &  50.0 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  59.0 &  4.07 &  55.2 &  4.10 &  51.0 &  4.17 &  50.1 &  4.17 &  49.9 \\
- k = 18        &  3.13 &  69.7 &  3.13 &  57.0 &  3.13 &  53.9 &  3.26 &  51.8 &  3.32 &  50.0 \\
- k = 20        &  2.00 &  62.5 &  2.00 &  62.5 &  2.01 &  62.2 &  2.25 &  55.5 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_100}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.6 &    0.0 &   54.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    3.1 &    0.0 &    8.4 &    2.6 &    0.0 &   28.5 &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . \\
- k = 16        &   12.4 &    0.1 &    3.9 &   10.9 &    0.1 &   23.5 &    5.5 &    0.1 &   12.9 &    4.7 &    0.1 &   25.6 \\
- k = 18        &   25.1 &    0.3 &    2.0 &   23.5 &    0.3 &   12.5 &   18.6 &    0.3 &   41.8 &   11.0 &    0.1 &   12.7 \\
- k = 20        &   25.3 &    0.3 &    0.2 &   25.1 &    0.3 &    0.8 &   24.4 &    0.3 &    3.2 &   23.6 &    0.3 &    6.4 \\
- k = 22        &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 &   48.7 &    0.5 &    3.2 &   44.0 &    0.5 &   12.6 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &    8.3 &    0.2 &   47.8 &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   35.0 &    0.5 &   24.5 &   16.7 &    0.3 &   38.3 &    4.4 &    0.1 &   45.4 &    1.6 &    0.0 &   51.2 \\
- k = 16        &   64.2 &    0.7 &   12.0 &   22.0 &    0.3 &   23.0 &   12.0 &    0.1 &    7.8 &   10.6 &    0.1 &   25.1 \\
- k = 18        &   44.1 &    0.6 &   22.6 &   25.2 &    0.3 &    1.1 &   25.0 &    0.3 &    2.2 &   24.1 &    0.3 &    7.9 \\
- k = 20        &   50.3 &    0.5 &    0.3 &   49.9 &    0.5 &    1.7 &   48.7 &    0.5 &    6.3 &   43.9 &    0.6 &   22.9 \\
- k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.1 &    0.5 &    0.4 &   49.9 &    0.5 &    0.9 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &   60.4 &    0.9 &   32.5 &   20.5 &    0.3 &   27.7 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
- k = 14        &  119.3 &    1.3 &   12.1 &   62.1 &    0.8 &   21.9 &   37.0 &    0.5 &   26.6 &   10.2 &    0.1 &   27.6 \\
- k = 16        &  133.6 &    1.7 &   20.4 &   82.8 &    0.9 &   10.1 &   70.2 &    1.0 &   32.7 &   43.0 &    0.6 &   33.1 \\
- k = 18        &  123.8 &    1.2 &    1.4 &  114.6 &    1.2 &    6.9 &   93.4 &    1.1 &   18.3 &   47.0 &    0.5 &   12.2 \\
- k = 20        &   94.3 &    0.9 &    0.0 &   50.3 &    0.5 &    0.1 &   50.2 &    0.5 &    0.5 &   50.0 &    0.5 &    1.1 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  182.2 &    2.2 &   16.8 &  108.0 &    1.4 &   25.0 &   56.7 &    0.9 &   40.2 &   25.2 &    0.5 &   50.1 \\
- k = 14        &  241.8 &    2.7 &   11.2 &  169.4 &    2.0 &   17.3 &  121.4 &    1.6 &   23.0 &   86.8 &    1.3 &   31.6 \\
- k = 16        &  203.9 &    2.1 &    3.2 &  188.2 &    2.0 &    7.9 &  154.2 &    1.8 &   16.2 &  109.7 &    1.3 &   14.6 \\
- k = 18        &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 &  122.2 &    1.2 &    2.5 &  114.5 &    1.2 &    6.9 \\
- k = 20        &  123.9 &    1.2 &    0.0 &  119.5 &    1.2 &    0.0 &  106.9 &    1.1 &    0.1 &   75.3 &    0.7 &    0.2 \\
- k = 22        &  189.4 &    2.0 &    4.4 &  147.3 &    1.8 &   17.6 &   75.1 &    1.3 &   39.9 &   50.3 &    0.5 &    0.1 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_95}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    3.0 &    0.0 &   16.7 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &   11.0 &    0.1 &   22.8 &    6.0 &    0.1 &    7.0 &    3.1 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
- k = 18        &   24.4 &    0.3 &    6.7 &   12.2 &    0.1 &    3.5 &   11.0 &    0.1 &   12.7 &    0.0 &    0.0 &      . \\
- k = 20        &   25.2 &    0.3 &    0.5 &   24.9 &    0.3 &    1.8 &   23.6 &    0.3 &    6.4 &   12.6 &    0.3 &   50.4 \\
- k = 22        &   50.1 &    0.5 &    0.4 &   48.7 &    0.5 &    3.2 &   37.7 &    0.5 &   25.4 &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &    1.2 &    0.0 &   27.5 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   15.6 &    0.3 &   46.0 &    2.8 &    0.0 &   14.1 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . \\
- k = 16        &   41.0 &    0.7 &   38.5 &   12.1 &    0.1 &    7.1 &    9.1 &    0.2 &   42.5 &    4.7 &    0.1 &   25.6 \\
- k = 18        &   25.2 &    0.3 &    0.6 &   25.0 &    0.3 &    2.2 &   23.5 &    0.3 &   12.5 &   11.8 &    0.1 &    6.4 \\
- k = 20        &   50.1 &    0.5 &    0.9 &   48.7 &    0.5 &    6.3 &   25.1 &    0.3 &    0.8 &   24.4 &    0.3 &    3.2 \\
- k = 22        &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 &   48.7 &    0.5 &    3.2 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &   18.3 &    0.2 &   23.7 &    2.0 &    0.0 &   51.9 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   82.1 &    1.2 &   30.9 &   28.5 &    0.5 &   38.1 &    8.3 &    0.2 &   50.1 &    1.6 &    0.0 &   51.2 \\
- k = 16        &   73.7 &    0.7 &    2.3 &   64.2 &    0.7 &   12.1 &   21.8 &    0.3 &   23.8 &   10.6 &    0.1 &   25.1 \\
- k = 18        &  119.3 &    1.2 &    4.2 &   92.6 &    1.1 &   19.5 &   25.1 &    0.3 &    0.8 &   24.7 &    0.3 &    4.0 \\
- k = 20        &   50.3 &    0.5 &    0.2 &   50.3 &    0.5 &    0.2 &   50.0 &    0.5 &    1.1 &   48.5 &    0.5 &    6.5 \\
- k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.1 &    0.5 &    0.4 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  120.8 &    1.7 &   30.9 &   31.9 &    0.4 &   23.7 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
- k = 14        &  184.4 &    2.5 &   25.6 &  105.0 &    1.3 &   17.7 &   48.5 &    0.8 &   37.5 &   16.6 &    0.3 &   50.3 \\
- k = 16        &  197.8 &    2.1 &    5.1 &  155.7 &    1.8 &   15.7 &   93.2 &    1.3 &   26.1 &   61.8 &    1.0 &   39.3 \\
- k = 18        &  125.3 &    1.2 &    0.5 &  123.8 &    1.2 &    1.4 &  114.5 &    1.2 &    6.9 &   93.3 &    1.1 &   18.3 \\
- k = 20        &  122.3 &    1.2 &    0.0 &  106.9 &    1.1 &    0.1 &   50.3 &    0.5 &    0.2 &   50.1 &    0.5 &    0.4 \\
- k = 22        &  144.2 &    1.8 &   20.8 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_90}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &    6.2 &    0.1 &    3.4 &    4.7 &    0.1 &   25.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 18        &   12.6 &    0.1 &    0.9 &   11.8 &    0.1 &    6.4 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 20        &   25.1 &    0.3 &    0.8 &   23.6 &    0.3 &    6.4 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 22        &   49.5 &    0.5 &    1.6 &   25.0 &    0.5 &   50.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &    0.3 &    0.0 &   26.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    3.1 &    0.0 &    8.4 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &   12.4 &    0.1 &    3.9 &    6.2 &    0.1 &    3.4 &    4.7 &    0.1 &   25.6 &    0.0 &    0.0 &      . \\
- k = 18        &   25.2 &    0.3 &    1.1 &   22.1 &    0.3 &   22.7 &   11.8 &    0.1 &    6.4 &    6.3 &    0.1 &   49.6 \\
- k = 20        &   48.7 &    0.5 &    6.2 &   25.2 &    0.3 &    0.5 &   24.4 &    0.3 &    3.2 &   18.9 &    0.3 &   25.0 \\
- k = 22        &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 &   48.7 &    0.5 &    3.2 &   25.0 &    0.5 &   50.3 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &    5.0 &    0.1 &   41.4 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   35.0 &    0.5 &   24.5 &    5.4 &    0.1 &   25.7 &    1.2 &    0.0 &   27.5 &    0.0 &    0.0 &      . \\
- k = 16        &   69.1 &    0.7 &    7.0 &   18.7 &    0.3 &   41.8 &    9.1 &    0.2 &   42.5 &    4.7 &    0.1 &   25.6 \\
- k = 18        &  105.3 &    1.2 &   13.2 &   25.2 &    0.3 &    1.1 &   24.3 &    0.3 &    7.0 &   11.8 &    0.1 &    6.4 \\
- k = 20        &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    1.0 &   47.1 &    0.5 &   12.1 &   24.9 &    0.3 &    1.8 \\
- k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 &   49.5 &    0.5 &    1.6 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &   55.9 &    0.9 &   39.5 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &  127.6 &    1.4 &    9.0 &   42.1 &    0.5 &   21.3 &    8.3 &    0.2 &   50.1 &    0.8 &    0.0 &   50.3 \\
- k = 16        &  174.7 &    2.0 &   11.4 &   72.0 &    0.7 &    4.0 &   43.1 &    0.6 &   33.1 &   10.6 &    0.1 &   25.1 \\
- k = 18        &  124.8 &    1.2 &    0.8 &  119.3 &    1.2 &    4.2 &   47.0 &    0.5 &   12.2 &   24.7 &    0.3 &    4.0 \\
- k = 20        &  114.8 &    1.1 &    0.0 &   50.3 &    0.5 &    0.1 &   50.2 &    0.5 &    0.5 &   49.7 &    0.5 &    2.0 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_85}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4}  \cmidrule(lr){5-7}  \cmidrule(lr){8-10}  \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &    5.8 &    0.1 &   15.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 18        &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 20        &   24.9 &    0.3 &    1.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 22        &   18.9 &    0.2 &    0.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    2.4 &    0.0 &   43.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &    6.3 &    0.1 &    1.9 &    5.2 &    0.1 &   28.9 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 18        &   23.7 &    0.3 &   12.0 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 20        &   25.3 &    0.3 &    0.2 &   24.9 &    0.3 &    1.8 &   12.6 &    0.3 &   50.4 &    0.0 &    0.0 &      . \\
- k = 22        &   50.3 &    0.5 &    0.2 &   49.1 &    0.5 &    3.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &    0.6 &    0.0 &   54.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   13.7 &    0.2 &   39.1 &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &   18.9 &    0.3 &   40.7 &    6.2 &    0.1 &    3.4 &    3.9 &    0.1 &   50.0 &    0.0 &    0.0 &      . \\
- k = 18        &   25.3 &    0.3 &    0.2 &   24.4 &    0.3 &    6.7 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . \\
- k = 20        &   50.2 &    0.5 &    0.5 &   44.0 &    0.6 &   22.7 &   24.9 &    0.3 &    1.8 &   22.0 &    0.3 &   12.5 \\
- k = 22        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 &   34.4 &    0.6 &   45.1 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &   10.3 &    0.1 &   24.3 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   50.8 &    0.7 &   31.2 &    5.8 &    0.1 &   15.2 &    0.8 &    0.0 &   50.3 &    0.0 &    0.0 &      . \\
- k = 16        &   73.7 &    0.7 &    2.3 &   43.2 &    0.6 &   32.7 &    9.1 &    0.2 &   42.5 &    1.6 &    0.0 &   51.2 \\
- k = 18        &  123.8 &    1.2 &    1.5 &   44.0 &    0.6 &   22.7 &   24.7 &    0.3 &    4.0 &   11.8 &    0.1 &    6.4 \\
- k = 20        &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.3 &   49.5 &    0.5 &    3.4 &   24.9 &    0.3 &    1.8 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   49.9 &    0.5 &    0.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_spacing_r100_a05}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
-Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.50 &    10 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.25 &     7 &  1.50 &    10 &     . &     . \\
- 4             &  1.00 &     1 &  1.00 &     1 &  1.12 &     6 &  1.01 &     3 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.00 &     1 &  1.03 &     3 &     . &     . &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.08 &     5 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.03 &     2 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.01 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.20 &     2 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.50 &     8 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.22 &     4 &  1.50 &     8 &     . &     . \\
- 4             &  1.00 &     1 &  1.00 &     1 &  1.09 &     3 &  1.10 &     4 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.00 &     1 &  1.18 &     4 &     . &     . &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.06 &     3 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.10 &     2 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.49 &     6 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.13 &     2 &  1.49 &     6 &     . &     . \\
- 4             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.32 &     5 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 &     . &     . &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.25 &     2 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.47 &     5 &     . &     . \\
- 4             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.43 &     4 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.00 &     1 &  1.37 &     3 &     . &     . &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_spacing_r100_a055}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
-Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.38 &     3 &  1.50 &    10 &  1.50 &    12 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.24 &     6 &  1.06 &     8 &  1.00 &     2 &     . &     . \\
- 4             &  1.00 &     1 &  1.12 &     5 &  1.40 &     4 &  1.00 &     1 &     . &     . &     . &     . \\
- 5             &  1.03 &     2 &  1.21 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.01 &     3 &  1.10 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.04 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.49 &     7 &  1.50 &    10 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.19 &     3 &  1.25 &     8 &  1.02 &     4 &     . &     . \\
- 4             &  1.00 &     1 &  1.09 &     3 &  1.03 &     5 &  1.00 &     2 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.01 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.18 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.01 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.47 &     5 &  1.50 &     9 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.25 &     7 &  1.06 &     5 &     . &     . \\
- 4             &  1.00 &     1 &  1.00 &     1 &  1.12 &     5 &  1.01 &     2 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.03 &     2 &  1.03 &     2 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.03 &     3 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.38 &     3 &  1.50 &     8 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.24 &     5 &  1.20 &     6 &     . &     . \\
- 4             &  1.00 &     1 &  1.00 &     1 &  1.09 &     3 &  1.03 &     2 &     . &     . &     . &     . \\
- 5             &  1.00 &     1 &  1.00 &     1 &  1.16 &     3 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.04 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_spacing_r100_a06}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
-Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.49 &     6 &  1.50 &    10 &  1.50 &    12 &  1.50 &    13 \\
- 3             &  1.00 &     1 &  1.25 &     7 &  1.57 &     5 &  1.74 &     8 &  1.18 &     2 &  1.00 &     1 \\
- 4             &  1.12 &     5 &  1.47 &     6 &  1.27 &     5 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.25 &     4 &  1.47 &     4 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.17 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.06 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 &  1.50 &     8 &  1.50 &    11 &  1.50 &    12 \\
- 3             &  1.00 &     1 &  1.24 &     5 &  1.03 &     5 &  1.65 &     5 &  1.00 &     1 &  1.00 &     1 \\
- 4             &  1.09 &     3 &  1.32 &     3 &  1.36 &     6 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.01 &     2 &  1.06 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.10 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.25 &     2 &  1.49 &     6 &  1.50 &     9 &  1.50 &    11 \\
- 3             &  1.00 &     1 &  1.19 &     3 &  1.12 &     5 &  1.45 &     4 &  1.00 &     2 &  1.00 &     1 \\
- 4             &  1.00 &     1 &  1.02 &     3 &  1.33 &     4 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.03 &     2 &  1.16 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.01 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.44 &     4 &  1.50 &     8 &  1.50 &    10 \\
- 3             &  1.00 &     1 &  1.00 &     1 &  1.24 &     5 &  1.03 &     5 &  1.00 &     2 &  1.00 &     1 \\
- 4             &  1.00 &     1 &  1.09 &     3 &  1.19 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.00 &     1 &  1.01 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Average and Maximum Spacing by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_spacing_r100_a065}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} D{.}{.}{1.2} D{.}{.}{2.0} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-               & \mct{k = 12}              & \mct{k = 14}              & \mct{k = 16}              & \mct{k = 18}              & \mct{k = 20}              & \mct{k = 22}              \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
-Parity         & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} & \mco{Average} & \mco{Max} \\ \midrule
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 12 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.99 &     8 \\
- 2             &  1.00 &     1 &  1.50 &     8 &  1.50 &    10 &  1.50 &    12 &  1.50 &    12 &  1.90 &     6 \\
- 3             &  1.25 &     7 &  1.72 &     7 &  1.75 &     9 &  1.75 &    10 &  1.91 &     7 &  1.00 &     1 \\
- 4             &  1.47 &     6 &  1.74 &     6 &  1.79 &     7 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.55 &     5 &  1.45 &     4 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 6             &  1.44 &     4 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 7             &  1.12 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 16 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.94 &     5 \\
- 2             &  1.00 &     1 &  1.49 &     7 &  1.50 &     9 &  1.50 &    11 &  1.50 &    12 &  1.53 &     8 \\
- 3             &  1.24 &     5 &  1.65 &     5 &  1.72 &     7 &  1.74 &     8 &  1.78 &     5 &  1.00 &     1 \\
- 4             &  1.40 &     4 &  1.41 &     3 &  1.66 &     5 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.37 &     3 &  1.14 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.07 &     2 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 20 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.50 &     2 \\
- 2             &  1.00 &     1 &  1.47 &     5 &  1.50 &     8 &  1.50 &     9 &  1.50 &    11 &  1.25 &    11 \\
- 3             &  1.22 &     4 &  1.45 &     3 &  1.64 &     5 &  1.72 &     7 &  1.50 &     3 &  1.00 &     1 \\
- 4             &  1.19 &     2 &  1.10 &     3 &  1.40 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.06 &     2 &  1.19 &     3 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.09 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-               &  \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p = 24 $)}                         \\ 
- 1             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 \\
- 2             &  1.00 &     1 &  1.44 &     4 &  1.49 &     6 &  1.50 &     8 &  1.50 &    10 &  1.50 &    11 \\
- 3             &  1.13 &     2 &  1.27 &     2 &  1.57 &     4 &  1.65 &     5 &  1.00 &     1 &  1.00 &     1 \\
- 4             &  1.03 &     2 &  1.16 &     3 &  1.04 &     2 &  1.00 &     1 &  1.00 &     1 &     . &     . \\
- 5             &  1.09 &     2 &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . \\
- 6             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 7             &  1.00 &     1 &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . \\
- 8             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 9             &  1.00 &     1 &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . \\
- 10            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
- 11            &  1.00 &     1 &     . &     . &     . &     . &     . &     . &     . &     . &     . &     . \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 15 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
 
@@
 
-\clearpage
-\newpage
-
-% \begin{figure}[h]
-% \begin{center}
-% \Treek{1.5}{  &&   &        &           &                       &       & \K[5.2]{n=0}\Bkk{5.2,0}{-5.2,0}{dlll}\Bkk{5.2,0}{5.2,0}{dd}\Bkk{5.2,0}{5.2,0}{drrrr} \\
-% \K[-6]{\emph{t=1}}              &&              & \K[5.2]{-S}\Bkk{5.2,0}{5.2,0}{dll}\Bkk{5.2,0}{5.2,0}{drr}  & &      & & & &      & & \K[5.2]{S}\Bkk{5.2,0}{5.2,0}{dll}\Bkk{5.2,0}{5.2,0}{drr}              \\
-%              & \K[5.2]{b (boy)}\bkl\bkd\bkr &   &  &                    &   \K[5.2]{g (girl)}\bkl\bkd\bkr & & \K[5.2]{0} &      & \K[5.2]{0 (no child)}\bkl\bkd\bkr & &&                   &  \K[5.2]{b (boy)}\bkl\bkd\bkr     \\
-% \K[-6]{\emph{t=2}}\K[5.2]{-S}\bkv\bkh&       & \K[5.2]{S}\bkv\bkh    & & \K[5.2]{-S}\bkv\bkh &    & \K[5.2]{S}\bkv\bkh &              &\K[5.2]{-S}\bkv\bkh&       & \K[5.2]{S}\bkv\bkh &  &\K[5.2]{-S}\bkv\bkh&   & \K[5.2]{S}\bkv\bkh  \\
-% \K{bb}             & \K{bg}  \K[5.2]{b}  & \K{b} & \K{bb}        & \K{gb}  &\K{gg} \K[5.2]{g}   & \K{g} & \K{gb}    & \K{g}  &\K{b} \K[5.2]{0}  & \K{0} & \K{b}    & \K{bb}  &\K{bg} \K[5.2]{b}  & \K{b} & \K{bb}     \\
-% }
-% \end{center}
-% \caption{Decision tree for a two period model with prenatal sex screening, where -S is no prenatal sex determination and S is sex determination}
-% \label{fig:tree}
-% \end{figure}
-
-\begin{figure}[htp]%
-\centering
-\includegraphics[width=0.9\textwidth]{des_fertility_35}
-% this graph is sex_ratio_marriage_2yrs_p1.pdf from andescribe.do
-\caption{Children ever born at age 35}
-\label{fig:fertility}
-\end{figure}
-
-\clearpage
-\newpage
-
-\begin{table}[htbp]
-\begin{center}
-\begin{scriptsize}
-\begin{threeparttable}
-\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
-Abortions for Women with No Education}
-\label{tab:predicted_low}
-\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
-                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
-                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
-                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
-\midrule
-\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
-Spell 2          &       93.2   &  1.8    &  1.6    &  52.2   &       92.4   &  1.5    &  1.3    &  52.0   &       90.0   &  1.4    &  1.2    &  52.0   \\
-Spell 3          &       93.8   &  4.6    &  4.3    &  53.6   &       91.1   &  -1.2   &  -1.1   &  50.7   &       85.6   &  -4.7   &  -4.0   &  48.8   \\
-Spell 4          &       87.1   &  5.5    &  4.8    &  54.1   &       84.4   &  2.3    &  2.0    &  52.5   &       75.3   &  5.6    &  4.2    &  54.1   \\
-Overall\tnote{d} &       3.6    &  2.8    &  9.8    &  52.9   &       3.5    &  0.6    &  2.0    &  51.7   &       3.3    &  0.3    &  0.9    &  51.2   \\
-\addlinespace 
-\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
-Spell 2          &       94.5   &  1.7    &  1.6    &  52.1   &       93.7   &  1.0    &  1.0    &  51.7   &       92.9   &  3.4    &  3.2    &  53.0   \\
-Spell 3          &       95.1   &  1.5    &  1.4    &  52.0   &       93.4   &  1.9    &  1.7    &  52.2   &       91.3   &  -0.5   &  -0.5   &  51.0   \\
-Spell 4          &       91.1   &  3.4    &  3.1    &  52.9   &       87.3   &  0.1    &  0.1    &  51.3   &       83.3   &  0.1    &  0.1    &  51.3   \\
-Overall\tnote{d} &       3.7    &  1.6    &  5.7    &  52.3   &       3.6    &  0.7    &  2.7    &  51.7   &       3.5    &  0.8    &  2.8    &  51.5   \\
-\bottomrule
-\end{tabular}                        
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
-(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
-The samples consist of all women from the data no education who
-married during the indicated period using the estimation results for that periods 
-and the women's characteristics at the start of their marriage. 
-All numbers presented are for women predicted to have one or more births.
-Birth/progression rates are based on the ratio of women predicted to have a birth 
-by the end of each spell.
-Abortion rates within each spell are based on the predicted number of abortions each
-woman would have if she went through the entire spell.
-To generate conditions such as sex composition and fecundity for second and higher spells 
-each woman is randomly assigned outcomes based on the estimation results and
-her characteristics as follows.
-For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
-She is assigned one of these outcomes based on a random draw from a uniform distribution.
-The first quarter where she has a draw that results in a birth she leaves the spell
-and the quarter reached is used to calculate her starting age for the subsequent spell.
-If she has no draw that result in a birth within a spell her childbearing stops and
-she does not enter the next spell.
-Results are averaged over 1,000 repetitions.
-\item[a] For individual spells the column shows the percent of women who started the
-spell and ended up with a birth by the end of the spell period covered.
-For the ``Overall'' row, the number is the expected number of children born per woman over 
-the first four spells, conditional on having at least one birth.
-\item[b] For individual spells the column shows the number of abortions per 100
-births predicted to take place by the end of the spell.
-For the ``Overall'' row, the number is the total number of abortion per 100 births 
-predicted to take place over all four spells.
-\item[c]  For individual spells the column shows the number of abortions 
-predicted to take place by the end of the spell per 100 women who started the spell .
-For the ``Overall'' row, the number is the total number of abortion 
-predicted to take place over all four spells per 100 women who had at least one child.
-\item[d] Covers first through fourth spells. 
-\end{tablenotes}
-\end{threeparttable}
-\end{scriptsize}
-\end{center}
-\end{table}
-
-\begin{table}[htbp]
-\begin{center}
-\begin{scriptsize}
-\begin{threeparttable}
-\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
-Abortions for Women with 1 to 7 Years of Education}
-\label{tab:predicted_med}
-\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
-                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
-                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
-                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
-\midrule
-\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
-Spell 2          &       93.4   &  -2.1   &  -2.0   &  50.1   &       89.7   &  -0.1   &  -0.1   &  51.2   &       84.5   &  -0.9   &  -0.7   &  50.7   \\
-Spell 3          &       89.2   &  1.4    &  1.3    &  52.0   &       82.5   &  1.4    &  1.2    &  51.9   &       71.1   &  2.4    &  1.7    &  52.4   \\
-Spell 4          &       79.0   &  3.4    &  2.7    &  52.9   &       70.9   &  1.0    &  0.7    &  51.7   &       61.9   &  6.8    &  4.2    &  54.7   \\
-Overall\tnote{d} &       3.4    &  0.4    &  1.4    &  51.7   &       3.2    &  0.5    &  1.5    &  51.7   &       2.8    &  1.1    &  3.2    &  51.9   \\
-\addlinespace 
-\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
-Spell 2          &       94.6   &  -1.3   &  -1.2   &  50.5   &       93.0   &  0.4    &  0.4    &  51.4   &       91.6   &  2.2    &  2.0    &  52.3   \\
-Spell 3          &       92.8   &  0.6    &  0.6    &  51.5   &       88.0   &  1.0    &  0.8    &  51.7   &       80.7   &  3.5    &  2.8    &  53.0   \\
-Spell 4          &       86.2   &  -2.2   &  -1.9   &  50.1   &       80.3   &  4.5    &  3.6    &  53.5   &       68.0   &  3.6    &  2.5    &  53.1   \\
-Overall\tnote{d} &       3.6    &  -0.7   &  -2.4   &  51.0   &       3.4    &  1.2    &  4.1    &  51.6   &       3.2    &  2.0    &  6.4    &  52.1   \\
-\bottomrule
-\end{tabular}                        
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
-(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
-The samples consist of all women from the data with 1 to 7 years of education who
-married during the indicated period using the estimation results for that periods 
-and the women's characteristics at the start of their marriage. 
-All numbers presented are for women predicted to have one or more births.
-Birth/progression rates are based on the ratio of women predicted to have a birth 
-by the end of each spell.
-Abortion rates within each spell are based on the predicted number of abortions each
-woman would have if she went through the entire spell.
-To generate conditions such as sex composition and fecundity for second and higher spells 
-each woman is randomly assigned outcomes based on the estimation results and
-her characteristics as follows.
-For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
-She is assigned one of these outcomes based on a random draw from a uniform distribution.
-The first quarter where she has a draw that results in a birth she leaves the spell
-and the quarter reached is used to calculate her starting age for the subsequent spell.
-If she has no draw that result in a birth within a spell her childbearing stops and
-she does not enter the next spell.
-Results are averaged over 1,000 repetitions.
-\item[a] For individual spells the column shows the percent of women who started the
-spell and ended up with a birth by the end of the spell period covered.
-For the ``Overall'' row, the number is the expected number of children born per woman over 
-the first four spells, conditional on having at least one birth.
-\item[b] For individual spells the column shows the number of abortions per 100
-births predicted to take place by the end of the spell.
-For the ``Overall'' row, the number is the total number of abortion per 100 births 
-predicted to take place over all four spells.
-\item[c]  For individual spells the column shows the number of abortions 
-predicted to take place by the end of the spell per 100 women who started the spell .
-For the ``Overall'' row, the number is the total number of abortion 
-predicted to take place over all four spells per 100 women who had at least one child.
-\item[d] Covers first through fourth spells. 
-\end{tablenotes}
-\end{threeparttable}
-\end{scriptsize}
-\end{center}
-\end{table}
-
 \end{document}

### 2017-04-03 paper/sexSelectionSpacingAppendix-ver1.tex
Begun removing discussion of fertility from intro and theory

% Begun.: 2017-04-02
% Edited: 2017-04-02

\documentclass[12pt,letterpaper]{article}
% \documentclass[AER,draftmode]{AEA}

\usepackage{mathpazo}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
% \usepackage[pdftex]{graphicx}
% \usepackage[all]{xypic}
\usepackage{xyling}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[pdftex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
% \usepackage[nolists,tablesfirst]{endfloat}

% \bibpunct{(}{)}{;}{a}{}{,}
\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
\newcommand{\X}{$\times$ }
\newcommand{\hs}{\hspace{15pt}}

% Attempt to squeeze more floats in
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

% \renewcommand\subfigtopskip{0pt}
% \renewcommand\subfigcapskip{0pt}
%\renewcommand\subfigbottomskip{2pt}

\newcommand{\bkv}{\Bkk{5.2,0}{0,0}{d}}
\newcommand{\bkh}{\Bkk{5.2,0}{0,0}{dr}}
\newcommand{\bkl}{\Bkk{5.2,0}{5.2,0}{dl}}
\newcommand{\bkd}{\Bkk{5.2,0}{5.2,0}{dd}}
\newcommand{\bkr}{\Bkk{5.2,0}{5.2,0}{dr}}

%
% If tree is not showing remove divps in line 60 in the following file
% /Library/TeX/Root/texmf-dist/tex/latex/xyling/xyling.sty
%

% For estout tables
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}

%------------------------------------------------------------------------

\title{Sex Selective Abortions, Fertility, and Birth Spacing
% \protect\thanks{%
% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, Hendrik Wolff, 
% seminar participants at University of Copenhagen, University of Michigan, 
% University of Washington, University of \AA{}rhus, the Fourth 
% Annual Conference on Population, Reproductive Health, 
% and Economic Development, and the Economic Demography Workshop for helpful suggestions and comments.
% I would also like to thank Nalina Varanasi for research assistance.
% Support from the University of Washington Royalty Research Fund and the 
% Development Research Group of the World Bank is gratefully acknowledged.
% The views and findings expressed here are those of the author and
% should not be attributed to the World Bank or any of its member countries.
% Partial support for this research came from a Eunice Kennedy Shriver National
% Institute of Child Health and Human Development research infrastructure grant,
% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
% University of Washington.
% Prior versions of this paper were presented under the title ``The 
% Determinants of Sex Selective Abortions.''
% }
}

\author{}

% \author{Claus C P\"ortner\\
%     Department of Economics\\
%     Albers School of Business and Economics\\
%     Seattle University, P.O. Box 222000\\
%     Seattle, WA 98122\\
%     \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
%     \href{http://www.portner.dk}{\texttt{www.portner.dk}}\\
%     \& \\
%     Center for Studies in Demography and Ecology \\
%     University of Washington\\ \vspace{2cm}
%     }

% \date{May 2010\\ \bigskip PRELIMINARY}
\date{March 2015}

%------------------------------------------------------------------------

\begin{document}

\graphicspath{{graphs/},{figures/}}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
\doublespacing

\appendix

% \section{Recall Error}

% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
\renewcommand\thefigure{\thesection.\arabic{figure}}    
% \setcounter{figure}{0}    
% \setcounter{postfig}{0}

\renewcommand\thetable{\thesection.\arabic{table}}    
\setcounter{table}{0}
% \setcounter{posttbl}{0}

\section{Why Bundle Scan and Abortion?}

The easiest way to show why a bundled service makes sense is to model 
the provider's problem first and then show that both provider and
buyer will be better off if a bundled service is offered.
Take a provider with with cost, $c_a$, of providing an abortion,
and cost, $c_s$, of providing a scan.
These costs include expenses for equipment, labor,
and possibly a premium for getting caught and prosecuted. 
The provider can either charge separately for the two services,
in which case he will charge $p_s$ for the scan and $p_a$ for
the abortion, or he can charge $p_b$ for the bundle.

The provider's profit if he offers the two services separately, $\pi_{sep}$,
to $n$ buyers, who conceive girls with the probability $p(g)$, will be
\begin{equation}
\pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
\end{equation}
The first part is profit from the customers who want a scan
and the second part is the profit from the fraction of the
original customers who conceived a girl.
If the provider instead offered the same $n$ buyers a bundle service
the profit, $\pi_{bun}$, would be
\begin{equation}
\pi_{bun} = n p_b - n c_s - p(g) n c_a,
\end{equation}
since all customers pays $p_b$, all customers get a scan 
at cost $c_s$, and the fraction $p(g)$ who conceived a girl
would receive an abortion at cost $c_a$.
A profit maximizing provider then picks bundled pricing if 
$\pi_{bun} > \pi_{sep}$, or
\begin{equation}
 p_b > p_s + p(g) p_a.
\end{equation}

Assume that buyers are risk averse and that the only motivation
for getting a prenatal sex determination test is to abort 
female fetuses and that parents will abort the fetus if the test 
show a female fetus (I will relax the last assumptions below).
Furthermore, to ease exposition assume that buyers can only
spend money on two things: consumption $c$ and prenatal sex
determinations/abortions.
For a buyer facing separate services the expected utility
is then
\begin{equation}
U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
\end{equation}
where the first part is the utility if the fetus is a boy
and the buyers therefore only spend on the scan, which
happens with probability $1-p(g)$, and the
second part is the utility if the fetus is a female
and they therefore also has to pay for the abortion,
which happens with probability $p(g)$.
For a buyer facing a bundled service the utility is simply
\begin{equation}
U = U(c-p_b).
\end{equation}

If follows from the standard assumptions about utility functions
and the risk aversion assumption that
\begin{equation}
U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
\end{equation}
In other words risk averse buyers prefer a sure thing---where they pay 
upfront---over the gamble that they either have a boy and pay only for the
scanning or have a girl and pay for both the scan and the abortion.
In fact, risk aversion implies that they are willing to pay 
\emph{more} than the expected cost.
In other words,
\begin{equation}
U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
\end{equation}
where $\delta$ is a positive number that depends on the
degree of risk aversion (the more risk averse the larger
$\delta$ is).

The provider realizes that buyers are risk averse
and therefore offer a bundle where the price is in 
the range
\begin{equation}
p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
\end{equation}
Hence, the optimal pricing scheme for both provider
and buyer is bundled pricing, where you pay a flat fee
and get the pre-natal sex determination and an abortion
if needed.
% Where the provider ends up in the possible range of
% prices depends on the nature of the provider market.

I implicitly assumed that the provider is risk-neutral.
The same result hold, however, if the provider
is risk-averse as long as there are enough potential clients.
In that case, the law of large numbers will ensure that 
the risk-neutral and risk-averse choices are the same
for the provider---essentially there is no gamble if you see 
enough clients, $p(g)$ of them will present with a female fetus 
and $1-p(g)$ with a male fetus.
In fact, it is possible for the provider to be \emph{more}
risk averse than the buyers and still prefer the bundled 
pricing scheme.

Now imagine a situation where there there is some 
uncertainty about whether a buyer will go through with
the abortion after the prenatal sex determination.
This can be represented by the probability $\rho$ that
a buyer who had a prenatal sex determination test that
showed a female fetus will go through with the abortion.
If parents know that there is probability $1-\rho$ that they
will not go through with the abortion their utility is
\begin{equation}
U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
\end{equation}
where I have made the assumption that they
are equally happy with a boy or a girl if they
are in the $1-\rho$ portion of the population that
have a prenatal sex determination which show a female
fetus but do not go through with the abortion (obviously
this cannot be the case because if they were there
would be no point in having the prenatal sex determination,
but if I can show that the bundle price arise here it
would trivially hold if there were some lower utility
associated with having a girl than a boy).

Because the buyers are still risk averse they would continue
to prefer the ``sure'' thing over the gamble
\begin{equation}
U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
\end{equation}
The provider still offers a bundle, but the price is now 
in  the range
\begin{equation}
p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
\end{equation}
where $\delta$ still depends on the degree of risk aversion.

If parents on the other hand initially believe that they will always
go through with the abortion if the fetus is female but
still have probability $1-\rho$ that they will not, they would
be back to the original comparison of the utility.
\begin{equation}
U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
\end{equation}
All that would do is \emph{increase} the profit for the
provider because the law of large numbers would tell them
exactly how many would not go through with the abortion.
In other words, they would offer the original
bundled price because the buyers did not know that they
will change their mind
\begin{equation}
p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
\end{equation}
but the provider will have profit of
\begin{equation}
p_b - c_s - \rho c_a,
\end{equation}
which is strictly larger than the profit in either of
the other cases.
Also, they do not need to know which buyers are more
or less likely to use abortion, just that some
fraction will not use their purchased abortion.

\clearpage
\newpage

\section{Simulation Results for 20 Periods}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_100}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
 k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
 k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
 k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
 k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
 k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
 k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
 k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
 k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_95}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.09 &  56.9 &  7.19 &  52.4 &  7.30 &  50.5 &  7.33 &  50.1 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  63.7 &  5.05 &  56.4 &  5.10 &  53.6 &  5.21 &  51.0 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  69.1 &  4.06 &  59.2 &  4.06 &  58.8 &  4.06 &  55.3 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  70.0 &  3.13 &  69.7 &  3.13 &  64.9 &  3.13 &  56.0 &  3.32 &  50.0 \\
 k = 20        &  2.50 &  65.1 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.07 &  67.6 &  7.08 &  60.9 &  7.13 &  54.8 &  7.26 &  51.4 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  78.3 &  5.05 &  67.8 &  5.05 &  62.7 &  5.06 &  56.7 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  76.0 &  4.06 &  75.4 &  4.06 &  69.7 &  4.06 &  63.3 &  4.17 &  49.9 \\
 k = 18        &  3.13 &  70.1 &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.32 &  50.0 \\
 k = 20        &  2.75 &  72.7 &  2.74 &  72.6 &  2.64 &  71.6 &  2.00 &  62.5 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  99.1 &  2.00 &  71.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_90}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
 k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
 k = 16        &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.25 &  51.9 &  3.25 &  51.4 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
 k = 20        &  2.50 &  55.1 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.01 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
 k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
 k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
 k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.24 &  55.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.30 &  50.5 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.24 &  52.3 &  5.24 &  50.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  58.8 &  4.07 &  51.5 &  4.13 &  50.7 &  4.16 &  50.1 &  4.16 &  49.9 \\
 k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 \\
 k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.63 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.12 &  53.6 &  7.31 &  50.3 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
 k = 14        &  5.05 &  63.2 &  5.21 &  52.6 &  5.24 &  50.3 &  5.26 &  50.0 &  5.27 &  50.0 \\
 k = 16        &  4.06 &  61.5 &  4.06 &  59.0 &  4.07 &  51.5 &  4.13 &  50.7 &  4.17 &  49.9 \\
 k = 18        &  3.13 &  70.0 &  3.13 &  68.3 &  3.13 &  54.0 &  3.16 &  53.5 &  3.32 &  50.0 \\
 k = 20        &  2.43 &  69.2 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  55.6 &  2.38 &  50.0 \\
 k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_fertility_85}
\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
\toprule
               & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
\midrule
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 \\
 k = 14        &  5.42 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
 k = 16        &  4.16 &  50.7 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
 k = 18        &  3.25 &  51.9 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 \\
 k = 20        &  2.50 &  54.9 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 \\
 k = 14        &  5.40 &  50.2 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 \\
 k = 16        &  4.15 &  50.7 &  4.16 &  50.6 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
 k = 18        &  3.14 &  53.8 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 &  3.31 &  50.1 \\
 k = 20        &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  52.5 &  2.50 &  50.0 &  2.50 &  50.0 \\
 k = 22        &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  7.33 &  50.1 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
 k = 14        &  5.23 &  51.3 &  5.25 &  50.2 &  5.25 &  50.0 &  5.25 &  50.0 &  5.25 &  50.0 \\
 k = 16        &  4.06 &  52.3 &  4.12 &  50.7 &  4.14 &  50.5 &  4.15 &  50.0 &  4.15 &  50.0 \\
 k = 18        &  3.12 &  54.0 &  3.13 &  53.9 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 \\
 k = 20        &  2.25 &  61.0 &  2.31 &  59.4 &  2.50 &  54.9 &  2.51 &  54.3 &  2.62 &  50.0 \\
 k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.12 &  58.0 &  2.25 &  50.0 \\
               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  7.30 &  50.7 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
 k = 14        &  5.06 &  55.0 &  5.23 &  50.6 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
 k = 16        &  4.06 &  58.9 &  4.06 &  55.2 &  4.10 &  51.1 &  4.16 &  50.2 &  4.17 &  50.0 \\
 k = 18        &  3.12 &  69.7 &  3.13 &  57.1 &  3.13 &  53.9 &  3.25 &  51.8 &  3.31 &  50.1 \\
 k = 20        &  2.00 &  62.4 &  2.00 &  62.4 &  2.01 &  62.1 &  2.25 &  55.4 &  2.37 &  50.0 \\
 k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.25 &  50.0 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a]Percent boys is the percent boys of all births.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_100}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13} 
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    6.0 &    0.1 &   22.3 &    1.4 &    0.0 &   28.2 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
 k = 14        &   21.6 &    0.2 &   12.3 &    5.6 &    0.1 &   23.2 &    3.2 &    0.0 &    4.8 &    3.0 &    0.0 &   15.0 \\
 k = 16        &   12.7 &    0.1 &    0.2 &   12.6 &    0.1 &    1.0 &   12.2 &    0.1 &    6.4 &    9.5 &    0.2 &   40.1 \\
 k = 18        &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   25.1 &    0.3 &    1.8 &   23.7 &    0.3 &   12.0 \\
 k = 20        &   49.6 &    0.5 &    3.2 &   37.8 &    0.6 &   40.1 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &   47.0 &    0.6 &   21.7 &   18.1 &    0.3 &   37.6 &    6.5 &    0.1 &   47.3 &    1.3 &    0.0 &   29.1 \\
 k = 14        &   56.5 &    0.9 &   36.7 &   41.9 &    0.5 &    7.6 &   31.2 &    0.5 &   34.0 &   10.8 &    0.1 &   25.1 \\
 k = 16        &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.0 &   56.4 &    0.7 &   19.4 &   22.1 &    0.3 &   22.7 \\
 k = 18        &  119.3 &    1.2 &    4.1 &   47.3 &    0.5 &   11.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 \\
 k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.2 &    0.5 &    0.9 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &  165.3 &    2.1 &   22.6 &  102.2 &    1.4 &   27.9 &   61.3 &    0.9 &   32.2 &   29.3 &    0.5 &   40.6 \\
 k = 14        &  158.7 &    1.6 &    1.0 &  135.6 &    1.4 &    4.8 &  108.0 &    1.3 &   15.4 &   64.1 &    0.8 &   19.1 \\
 k = 16        &  204.5 &    2.1 &    3.2 &  175.9 &    1.9 &   10.7 &  109.5 &    1.3 &   15.8 &   84.6 &    0.9 &    8.6 \\
 k = 18        &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 &  119.4 &    1.2 &    4.0 \\
 k = 20        &  123.9 &    1.2 &    0.0 &  107.0 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  319.6 &    3.8 &   15.6 &  256.2 &    3.3 &   21.9 &  188.1 &    2.5 &   26.3 &  131.1 &    1.6 &   17.7 \\
 k = 14        &  331.2 &    3.4 &    1.5 &  277.3 &    2.9 &    5.4 &  230.2 &    2.6 &   10.7 &  179.1 &    2.0 &   13.1 \\
 k = 16        &  213.6 &    2.1 &    0.2 &  212.2 &    2.1 &    0.7 &  208.2 &    2.1 &    2.0 &  190.3 &    2.0 &    6.6 \\
 k = 18        &  191.3 &    1.9 &    0.0 &  126.0 &    1.2 &    0.1 &  125.9 &    1.2 &    0.2 &  125.4 &    1.2 &    0.5 \\
 k = 20        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  122.3 &    1.2 &    0.0 \\
 k = 22        &  200.3 &    2.0 &    0.3 &  197.2 &    2.0 &    1.5 &  181.2 &    1.9 &    7.3 &   97.1 &    1.0 &    6.1 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a] Average number of spells per woman where scan has been used at least once.
\item[b] Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_95}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13} 
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.9 &    0.0 &    8.3 &    0.4 &    0.0 &    7.7 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . \\
 k = 14        &    3.3 &    0.0 &    0.8 &    3.2 &    0.0 &    7.2 &    1.6 &    0.0 &    7.4 &    0.8 &    0.0 &   50.3 \\
 k = 16        &   12.6 &    0.1 &    1.0 &    9.6 &    0.2 &   39.9 &    6.3 &    0.1 &    1.9 &    6.0 &    0.1 &    7.0 \\
 k = 18        &   25.3 &    0.3 &    0.3 &   23.7 &    0.3 &   11.8 &   12.6 &    0.1 &    0.5 &   12.2 &    0.1 &    3.5 \\
 k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 &   24.9 &    0.3 &    1.8 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.9 &    0.5 &    0.9 &   44.0 &    0.5 &   12.6 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &   12.3 &    0.2 &   21.2 &    4.3 &    0.1 &   42.6 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
 k = 14        &   40.5 &    0.5 &   11.8 &   18.8 &    0.2 &   20.7 &    4.8 &    0.1 &   41.2 &    2.8 &    0.0 &   24.3 \\
 k = 16        &   73.7 &    0.7 &    2.4 &   22.2 &    0.3 &   22.4 &   12.6 &    0.1 &    1.8 &   11.0 &    0.1 &   22.4 \\
 k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   24.9 &    0.3 &    3.3 \\
 k = 20        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.2 &   48.8 &    0.5 &    6.1 &   25.3 &    0.3 &    0.1 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &   98.2 &    1.3 &   23.7 &   34.6 &    0.5 &   32.0 &    8.0 &    0.1 &   39.3 &    1.3 &    0.0 &   29.1 \\
 k = 14        &  139.2 &    1.4 &    3.3 &   65.2 &    0.8 &   19.4 &   36.8 &    0.5 &   20.7 &   10.8 &    0.1 &   25.1 \\
 k = 16        &  156.3 &    1.9 &   17.6 &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.1 &   43.4 &    0.6 &   32.5 \\
 k = 18        &  125.7 &    1.2 &    0.3 &  123.9 &    1.2 &    1.4 &   93.6 &    1.1 &   18.2 &   37.7 &    0.6 &   40.2 \\
 k = 20        &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.3 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  248.9 &    2.8 &   10.0 &  155.2 &    2.0 &   24.1 &   69.0 &    0.8 &   19.1 &   21.0 &    0.3 &   26.7 \\
 k = 14        &  285.7 &    3.0 &    4.5 &  180.6 &    2.2 &   18.4 &  129.1 &    1.4 &    7.6 &   68.2 &    0.8 &   12.8 \\
 k = 16        &  213.0 &    2.1 &    0.4 &  208.3 &    2.1 &    2.0 &  161.3 &    1.8 &   12.1 &  108.9 &    1.3 &   16.2 \\
 k = 18        &  126.0 &    1.2 &    0.0 &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 \\
 k = 20        &  125.9 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  114.9 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 \\
 k = 22        &  197.1 &    2.0 &    1.6 &   87.6 &    1.1 &   22.2 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a] Average number of spells per woman where scan has been used at least once.
\item[b] Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_90}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13} 
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.4 &    0.0 &    5.0 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    3.2 &    0.0 &    4.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &    6.4 &    0.1 &    0.2 &    6.4 &    0.1 &    1.0 &    2.4 &    0.0 &   25.8 &    0.0 &    0.0 &      . \\
 k = 18        &   19.1 &    0.3 &   40.4 &   12.7 &    0.1 &    0.3 &   11.8 &    0.1 &    6.4 &    0.0 &    0.0 &      . \\
 k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.2 &   22.0 &    0.3 &   12.5 &    0.0 &    0.0 &      . \\
 k = 22        &   50.4 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &    4.4 &    0.1 &   41.3 &    0.4 &    0.0 &    7.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   21.6 &    0.2 &   12.3 &    3.2 &    0.0 &    4.4 &    1.6 &    0.0 &    7.4 &    0.0 &    0.0 &      . \\
 k = 16        &   12.7 &    0.1 &    0.2 &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.0 &    5.2 &    0.1 &   28.9 \\
 k = 18        &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.9 &   12.7 &    0.1 &    0.3 &   12.5 &    0.1 &    1.7 \\
 k = 20        &   50.3 &    0.5 &    0.2 &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.1 &    0.3 &    0.8 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &   33.0 &    0.4 &   22.5 &    4.8 &    0.1 &   47.7 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . \\
 k = 14        &   43.9 &    0.4 &    1.7 &   26.1 &    0.3 &   11.2 &    4.8 &    0.1 &   41.2 &    1.6 &    0.0 &    7.4 \\
 k = 16        &   75.6 &    0.8 &    0.4 &   69.2 &    0.7 &    7.0 &   12.6 &    0.1 &    1.8 &    6.4 &    0.1 &    1.0 \\
 k = 18        &  124.8 &    1.2 &    0.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 &   24.9 &    0.3 &    3.3 \\
 k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.4 &   37.7 &    0.6 &   40.1 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &  139.8 &    1.5 &    7.8 &   44.0 &    0.5 &   19.3 &    5.4 &    0.1 &   36.8 &    0.2 &    0.0 &   48.2 \\
 k = 14        &  144.2 &    1.4 &    0.7 &  120.3 &    1.3 &   11.4 &   39.1 &    0.5 &   14.0 &    5.9 &    0.1 &   14.2 \\
 k = 16        &  210.7 &    2.1 &    1.2 &  116.1 &    1.3 &   11.2 &   73.7 &    0.7 &    2.2 &   24.5 &    0.3 &    6.7 \\
 k = 18        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.3 &  119.4 &    1.2 &    4.0 &   44.1 &    0.6 &   22.6 \\
 k = 20        &  125.4 &    1.2 &    0.0 &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a] Average number of spells per woman where scan has been used at least once.
\item[b] Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\begin{table}[!htp]
\centering
\scriptsize
\begin{threeparttable}
\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
\label{tab:simul_abortion_85}
\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
\toprule
               & \multicolumn{12}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13} 
                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
\midrule
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
 k = 12        &    0.2 &    0.0 &   16.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    1.7 &    0.0 &    2.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &    6.4 &    0.1 &    0.7 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 18        &   12.7 &    0.1 &    0.2 &    9.4 &    0.1 &   24.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 20        &   25.3 &    0.3 &    0.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 22        &   49.3 &    0.5 &    3.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
 k = 12        &    0.4 &    0.0 &    5.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &    3.3 &    0.0 &    2.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 16        &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.3 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . \\
 k = 18        &   25.3 &    0.3 &    0.5 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . \\
 k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   24.9 &    0.3 &    1.8 &    0.0 &    0.0 &      . \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   24.4 &    0.2 &    0.0 &    0.0 &    0.0 &      . \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
 k = 12        &    7.0 &    0.1 &   13.3 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
 k = 14        &   24.8 &    0.3 &    2.3 &    3.2 &    0.0 &    4.0 &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . \\
 k = 16        &   72.0 &    0.7 &    4.3 &   12.5 &    0.1 &    3.5 &    6.3 &    0.1 &    2.4 &    1.6 &    0.0 &   51.2 \\
 k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.3 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 \\
 k = 20        &   50.4 &    0.5 &    0.0 &   50.2 &    0.5 &    0.9 &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.5 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   49.8 &    0.5 &    1.8 \\
               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
 k = 12        &   52.3 &    0.6 &   14.5 &    4.4 &    0.1 &   41.3 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . \\
 k = 14        &  134.3 &    1.4 &    7.0 &   27.3 &    0.3 &    6.2 &    3.1 &    0.0 &   14.2 &    0.8 &    0.0 &   50.3 \\
 k = 16        &   94.6 &    1.1 &   12.0 &   73.8 &    0.7 &    2.2 &   12.6 &    0.1 &    1.8 &    6.2 &    0.1 &    4.3 \\
 k = 18        &  126.0 &    1.2 &    0.1 &  114.7 &    1.2 &    6.8 &   25.3 &    0.3 &    0.2 &   22.2 &    0.3 &   22.4 \\
 k = 20        &   94.4 &    0.9 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   25.3 &    0.3 &    0.1 \\
 k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
\bottomrule
\end{tabular}
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
 and a probability of a son of 0.5.
\item[a] Average number of spells per woman where scan has been used at least once.
\item[b] Percent of spells where prenatal scan was initially used but birth is the result
of pregnancy without prenatal scan.
\end{tablenotes}
\end{threeparttable}
\normalsize
\end{table}

\clearpage
\newpage

\section{Recall Error and the Sex Ratio}

\setcounter{figure}{0}
\setcounter{table}{0}

% \footnote{%
% This also has implications for analyses of child mortality and fertility.
% % Relatively little attention has been paid to this problem despite the
% % potential for substantially underestimating mortality, especially for girls.
% A companion paper examines fertility and mortality trends in India when
% account is taken of recall error.
% % The method suggested here can also be used to establish the extent of
% % recall error and what factors are associated with recall error.
% }
% This is important because the estimation method proposed
% rely on good quality data on both the sex of children born and the spacing between these 
% children.
% Recall error makes an analysis of the spread of sex determinations techniques
% less precise, because there may appear to be little change in the sex
% ratio over time even though the actual sex ratio at birth has increased.
% It also makes it more difficult to identify which families are using sex selective abortions.
%

Since the proposed method relies both on spacing between births and  birth outcomes, the 
quality of the results depends on the reliability of the birth 
histories provided by the respondents.
An important concern here is child mortality.
A respondent may not provide information about deceased children because of
the painful nature of the topic.
% First, deceased children may not be listed in a respondent's birth history because
% the sensitivity of the topic.
Furthermore, the likelihood of reporting a deceased child may depend on sex of the child. 
Systematic recall error, where children of a specific sex are missed non-randomly, 
is especially problematic because it directly biases the sex ratios results.

NFHS enumerators probe for any missed births, although the method depends on the survey.%
\footnote{%
NFHS-1 probe for each calendar birth interval that is 4 or more years.
NFHS-2 asked for stillbirths, spontaneous and induced abortions and also probed 
for each calendar birth interval 4 or more years.
NFHS-3 did not directly use birth intervals, but asked whether were there any other live births 
between (name of previous birth) and (name), including any children who died after birth. 
It did ask for births before the birth listed as first birth.
}
Probing catches many originally missed births but systematic recall error based on son
preference may still be a problem.
First, strong son preference lead to significantly higher mortality for girls than boys.
Secondly, for children who died son preference makes it more likely that parents will
remember boys than girls.
Finally, in the absence of sex selective abortions, son preference lead parents to have 
the next birth sooner if the last child was a girl than if it was a boy.
If this girl subsequently dies she is more likely to be missed because probing for missed 
births is only done for long intervals.%
\footnote{
As an example, imagine a family whose first child is a girl.
Because of son preference this girl is followed quickly by another child.
If this child is also a girl the parents will quickly try for a third child.
This can lead to three children in three years and
if the middle child dies and is not listed the enumerators will not probe for
missing births because the interval between the first and last child is only two years.
}

To assess the extent of systematic recall error Table \ref{tab:recallBirth} 
shows sex ratios of children recorded as first-born and second-born
by year of birth together with tests for whether the observed sex ratio is
significantly higher than the natural sex ratio.
Births are combined into five-year cohorts to achieve sufficient power for a test of 
differences in sex ratios.
Prenatal sex determination techniques did not become widely available until the 
mid-1980s and any significant deviation from the natural sex ratio before that time
is therefore likely the result of recall error.
Furthermore, births and deaths that took place longer ago may be more 
likely to be subject to recall error than more recent events.
The three NFHS surveys make it possible to examine whether recall error increases with 
time by comparing sex ratios for births that took place during the same years but were 
surveyed at different times.
Table \ref{tab:recallBirth} therefore also shows tests for whether more recent surveys 
have a higher sex ratio for the cohort than older surveys.

% Main points:
% - births that took place further away from the survey show a higher sex ratio
% - there is evidence of a U-shaped relationship in sex ratio over time for second
% and especially the three parities combined with cohorts furthest away from the
% survey showing the highest sex ratios. The sex ratio then declines and only begins
% claiming again when sex selective abortions became available in the mid-1980s.
% The exception to this pattern is children listed as first-born for whom the
% sex ratios declines steadily over time leveling off at the natural sex ratio.
% - lack of power for individual parities means that relatively few cohorts show
% significantly different sex ratios across surveys; there is more power for
% the three first parities combined

% [Is this worth including?]
% the reason that sex ratio for second born can be higher in more recent surveys
% (NFHS-3 compared to NFHS-1) is that a higher proportion of women in the
% recent survey have lower desired fertility and are better educated.
% They should also be younger, as in born more recently.

% The decline in sex ratio over time followed by the increase after sex selection
% became available may be best argument against referee 1's concern about whether 
% this is simply infanticide.

\begin{table}[!htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{Observed sex ratios by year of birth in five-year cohorts }
\label{tab:recallBirth}
\begin{tabular} {@{} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l  @{}} \toprule
                   & \multicolumn{4}{c}{Listed as first-born}                          & \multicolumn{4}{c}{Listed as second-born} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9}
                   & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.         & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.              \\
                   & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} \\ \midrule
1960--1964         & 0.5473\sym{***}   &      .\sym{}      &      .\sym{}      &       & 0.5172\sym{}      &      .\sym{}      &      .\sym{}      &           \\
                   & (0.0004)          & (     .)          & (     .)          &       & (0.4382)          & (     .)          & (     .)          &           \\
                   & \mco{[2,673]}     & \mco{[.]}         & \mco{[.]}         &       & \mco{[1,189]}     & \mco{[.]}         & \mco{[.]}         &           \\
1965--1969         & 0.5274\sym{**}    & 0.5538\sym{***}   &      .\sym{}      & A     & 0.5327\sym{**}    & 0.5244\sym{}      &      .\sym{}      &           \\
                   & (0.0306)          & (0.0002)          & (     .)          &       & (0.0124)          & (0.3310)          & (     .)          &           \\
                   & \mco{[5,429]}     & \mco{[1,997]}     & \mco{[.]}         &       & \mco{[3,888]}     & \mco{[595]}       & \mco{[.]}         &           \\
1970--1974         & 0.5354\sym{***}   & 0.5341\sym{***}   & 0.5411\sym{}      &       & 0.5212\sym{}      & 0.5313\sym{**}    & 0.6160\sym{**}    & BC        \\
                   & (0.0001)          & (0.0019)          & (0.1208)          &       & (0.1497)          & (0.0248)          & (0.0143)          &           \\
                   & \mco{[7,763]}     & \mco{[5,546]}     & \mco{[523]}       &       & \mco{[6,249]}     & \mco{[3,499]}     & \mco{[125]}       &           \\
1975--1979         & 0.5207\sym{}      & 0.5151\sym{}      & 0.5255\sym{*}     &       & 0.5185\sym{}      & 0.5262\sym{**}    & 0.5384\sym{**}    & B         \\
                   & (0.1258)          & (0.4669)          & (0.0920)          &       & (0.2477)          & (0.0340)          & (0.0225)          &           \\
                   & \mco{[8,749]}     & \mco{[7,478]}     & \mco{[3,762]}     &       & \mco{[7,819]}     & \mco{[6,220]}     & \mco{[1,811]}     &           \\
1980--1984         & 0.5210\sym{*}     & 0.5244\sym{**}    & 0.5280\sym{***}   &       & 0.5236\sym{**}    & 0.5236\sym{**}    & 0.5249\sym{*}     &           \\
                   & (0.0872)          & (0.0273)          & (0.0094)          &       & (0.0361)          & (0.0492)          & (0.0628)          &           \\
                   & \mco{[11,147]}    & \mco{[9,709]}     & \mco{[7,718]}     &       & \mco{[9,950]}     & \mco{[8,478]}     & \mco{[5,532]}     &           \\
1985--1989         & 0.5187\sym{}      & 0.5132\sym{}      & 0.5118\sym{}      &       & 0.5157\sym{}      & 0.5194\sym{}      & 0.5165\sym{}      &           \\
                   & (0.1916)          & (0.6153)          & (0.7091)          &       & (0.4099)          & (0.1695)          & (0.3716)          &           \\
                   & \mco{[11,276]}    & \mco{[11,048]}    & \mco{[9,422]}     &       & \mco{[10,296]}    & \mco{[9,857]}     & \mco{[8,022]}     &           \\
1990--1994         & 0.5174\sym{}      & 0.5185\sym{}      & 0.5183\sym{}      &       & 0.5120\sym{}      & 0.5166\sym{}      & 0.5289\sym{***}   & BC        \\
                   & (0.3263)          & (0.2006)          & (0.2207)          &       & (0.6570)          & (0.3430)          & (0.0030)          &           \\
                   & \mco{[6,544]}     & \mco{[11,653]}    & \mco{[10,601]}    &       & \mco{[5,869]}     & \mco{[10,653]}    & \mco{[9,299]}     &           \\
1995--1999         &      .\sym{}      & 0.5222\sym{*}     & 0.4980\sym{}      &       &      .\sym{}      & 0.5230\sym{*}     & 0.5262\sym{**}    &           \\
                   & (     .)          & (0.0788)          & (0.9998)          &       & (     .)          & (0.0664)          & (0.0103)          &           \\
                   & \mco{[.]}         & \mco{[8,642]}     & \mco{[11,111]}    &       & \mco{[.]}         & \mco{[7,990]}     & \mco{[9,956]}     &           \\
2000--2006         &      .\sym{}      &      .\sym{}      & 0.5135\sym{}      &       &      .\sym{}      &      .\sym{}      & 0.5292\sym{***}   &           \\
                   & (     .)          & (     .)          & (0.5978)          &       & (     .)          & (     .)          & (0.0008)          &           \\
                   & \mco{[.]}         & \mco{[.]}         & \mco{[13,413]}    &       & \mco{[.]}         & \mco{[.]}         & \mco{[11,645]}    &           \\
\bottomrule
\end{tabular}                        
\begin{tablenotes} \scriptsize
\item \hspace*{-0.6em} \textbf{Note.} 
Sample consists of Hindu women only.
First number in cell is ratio of boys to girls. 
Second number in parentheses is p-value for the hypothesis that observed sex ratio is 
greater than 105/205 using a binomial probability test (bitest in Stata 13)
with asterisks indicating significance as follows: 
* sign.\ at 10\%; ** sign.\ at 5\%; *** sign.\ at 1\%.
Third number in square brackets is number of observations.
\item[a] 
Test (prtest in Stata 13) whether recall error increases 
with time passed, which would manifest itself in a higher sex ratio for a more recent
survey than an earlier for the same cohort.
A: Cohort sex ratio significantly larger in NFHS-2 than NFHS-1 at the 10 percent level. 
B: Cohort sex ratio significantly larger in NFHS-3 than NFHS-1 at the 10 percent level. 
C: Cohort sex ratio significantly larger in NFHS-3 than NFHS-2 at the 10 percent level. 
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

The ``first-born'' sex ratios illustrate the systematic recall error problem well. 
According to the birth histories in NFHS-1 almost 55 percent of children born between 1960 
and 1964 were boys.
Given that this is more than two decades before sex selection techniques became available
in India the most likely explanation for the skewed sex ratio is that some children
listed as first-borns were not, in fact, the first children born in their families.
Instead, for a substantial proportion of families the first-born was a girl who died and was 
skipped when enumerators asked about birth history.

% Recall error is less of an issue for more recent births than for births that took place 
% longer ago.
As expected, the difference between the observed sex ratio and the natural sex ratio is 
less pronounced the closer to the survey date the cohort is.
The observed sex ratio for children born just prior to the NFHS-1 survey and listed as 
first-born is 0.517, which is not statistically significant different from the
natural sex ratio.
The same general pattern holds for NFHS-2 and NFHS-3, with cohorts further away
from the survey date more likely to have a sex ratio skewed male.

Second births show a pattern very similar to that for first births.
An interesting difference is that there is evidence of a U-shaped relationship between
time and sex ratio for second births.
Cohorts furthest away from the survey year show the highest sex ratios, but declines to the
natural sex ratio in the mid-1980s, and the sex ratio is then significantly higher again 
for more recent births.
This is in line with the results in the paper that show that sex selective abortions take 
place on lower parity births as desired fertility declined.

Finally, across surveys the same cohort tends to show a higher sex ratio the more recent 
the survey (births in the cohort took place longer ago), especially for second-borns.%
\footnote{
Births in the 1970-1974 cohort, for example, took place
between 18 and 23 years ago for NFHS-1, 
between 24 and 29 years ago for NFHS-2,
and  between 31 and 36 years ago for NFHS-3.
}
Despite this, few cohorts show significantly different sex ratios across surveys, most 
likely because of a lack of power.

Using year of birth to analyze recall error is problematic because year of birth for a 
given parity is affected by recall error; for example, a second born child listed as first 
born will naturally be born later than the real first born child.
Recorded year of marriage should, however, be affected neither by parental recall error 
nor use of sex selective abortions.
Table \ref{tab:recallMarriage} therefore shows sex ratios of children recorded as 
first-born and second-born by year of parents'
marriage, together with tests for whether the observed sex ratio is
significantly higher than the natural sex ratio and whether more recent surveys show
a higher sex ratio for the cohort than older surveys.

The basic recall error pattern remains with women married longer ago more
likely to report that their first-born is a boy.
If anything the pattern is more consistent when using year of marriage than 
year of birth. 
Before the introduction of sex selection there are only two instances  across the two 
parities where the observed sex ratio is lower for women married longer ago than for women 
married closer to the survey date.%
\footnote{
For first-borns it is between 1970--1974 and 1975-1979 for NFHS-3 and for second-borns
it is between 1975--1979 and 1980--1984 for NFHS-1.
}
Similarly, comparing women married in the same five-year period across surveys shows
that women married longer ago are more likely to report having a son.

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{Observed sex ratios by year of parents' marriage in five-year cohorts }
\label{tab:recallMarriage}
\begin{tabular} {@{} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l  @{}} \toprule
                   & \multicolumn{4}{c}{Listed as first-born}                          & \multicolumn{4}{c}{Listed as second-born} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9}
                   & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.         & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.              \\
                   & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} \\ \midrule
1960--1964         & 0.5368\sym{***}   &      .\sym{}      &      .\sym{}      &        & 0.5274\sym{**}    &      .\sym{}      &      .\sym{}      &          \\
                   & (0.0002)          & (     .)          & (     .)          &        & (0.0239)          & (     .)          & (     .)          &          \\
                   & \mco{[6,200]}     & \mco{[.]}         & \mco{[.]}         &        & \mco{[6,001]}     & \mco{[.]}         & \mco{[.]}         &          \\
1965--1969         & 0.5333\sym{***}   & 0.5450\sym{***}   &      .\sym{}      &        & 0.5277\sym{**}    & 0.5401\sym{***}   &      .\sym{}      &          \\
                   & (0.0011)          & (0.0000)          & (     .)          &        & (0.0181)          & (0.0005)          & (     .)          &          \\
                   & \mco{[6,707]}     & \mco{[4,268]}     & \mco{[.]}         &        & \mco{[6,449]}     & \mco{[4,142]}     & \mco{[.]}         &          \\
1970--1974         & 0.5244\sym{**}    & 0.5222\sym{}      & 0.5271\sym{}      &        & 0.5182\sym{}      & 0.5235\sym{*}     & 0.5384\sym{**}    & B        \\
                   & (0.0386)          & (0.1120)          & (0.1372)          &        & (0.2651)          & (0.0805)          & (0.0194)          &          \\
                   & \mco{[8,154]}     & \mco{[6,546]}     & \mco{[1,973]}     &        & \mco{[7,843]}     & \mco{[6,308]}     & \mco{[1,913]}     &          \\
1975--1979         & 0.5272\sym{***}   & 0.5202\sym{}      & 0.5316\sym{***}   & C      & 0.5157\sym{}      & 0.5183\sym{}      & 0.5278\sym{**}    & B        \\
                   & (0.0062)          & (0.1477)          & (0.0050)          &        & (0.4208)          & (0.2499)          & (0.0242)          &          \\
                   & \mco{[9,829]}     & \mco{[8,644]}     & \mco{[5,798]}     &        & \mco{[9,295]}     & \mco{[8,294]}     & \mco{[5,608]}     &          \\
1980--1984         & 0.5151\sym{}      & 0.5142\sym{}      & 0.5195\sym{}      &        & 0.5198\sym{}      & 0.5171\sym{}      & 0.5187\sym{}      &          \\
                   & (0.4616)          & (0.5322)          & (0.1877)          &        & (0.1514)          & (0.3178)          & (0.2332)          &          \\
                   & \mco{[10,814]}    & \mco{[9,924]}     & \mco{[8,316]}     &        & \mco{[9,788]}     & \mco{[9,409]}     & \mco{[7,906]}     &          \\
1985--1989         & 0.5176\sym{}      & 0.5209\sym{*}     & 0.5095\sym{}      &        & 0.5131\sym{}      & 0.5194\sym{}      & 0.5267\sym{**}    & B        \\
                   & (0.2753)          & (0.0925)          & (0.8425)          &        & (0.5918)          & (0.1651)          & (0.0105)          &          \\
                   & \mco{[9,971]}     & \mco{[10,990]}    & \mco{[9,717]}     &        & \mco{[5,790]}     & \mco{[10,130]}    & \mco{[9,077]}     &          \\
1990--1994         & 0.5180\sym{}      & 0.5182\sym{}      & 0.5125\sym{}      &        & 0.4366\sym{}      & 0.5191\sym{}      & 0.5251\sym{**}    & AB       \\
                   & (0.3836)          & (0.2282)          & (0.6692)          &        & (0.9740)          & (0.2097)          & (0.0199)          &          \\
                   & \mco{[2,170]}     & \mco{[10,619]}    & \mco{[10,574]}    &        & \mco{[142]}       & \mco{[7,994]}     & \mco{[9,600]}     &          \\
1995--1999         &      .\sym{}      & 0.5243\sym{*}     & 0.5017\sym{}      &        &      .\sym{}      & 0.5613\sym{***}   & 0.5312\sym{***}   &          \\
                   & (     .)          & (0.0845)          & (0.9965)          &        & (     .)          & (0.0015)          & (0.0009)          &          \\
                   & \mco{[.]}         & \mco{[5,081]}     & \mco{[10,960]}    &        & \mco{[.]}         & \mco{[1,019]}     & \mco{[8,969]}     &          \\
2000--2006         &      .\sym{}      &      .\sym{}      & 0.5169\sym{}      &        &      .\sym{}      &      .\sym{}      & 0.5247\sym{}      &          \\
                   & (     .)          & (     .)          & (0.3280)          &        & (     .)          & (     .)          & (0.1243)          &          \\
                   & \mco{[.]}         & \mco{[.]}         & \mco{[9,210]}     &        & \mco{[.]}         & \mco{[.]}         & \mco{[3,316]}     &          \\
\bottomrule
\end{tabular}                        
\begin{tablenotes} \scriptsize
\item \hspace*{-0.6em} \textbf{Note.} 
Sample consists of Hindu women only.
First number in cell is ratio of boys to girls. 
Second number in parentheses is p-value for the hypothesis that observed sex ratio is 
greater than 105/205 using a binomial probability test (bitest in Stata 13)
with asterisks indicating significance as follows: 
* sign.\ at 10\%; ** sign.\ at 5\%; *** sign.\ at 1\%.
Third number in square brackets is number of observations.
\item[a] 
Test (prtest in Stata 13) whether recall error increases 
with time passed, which would manifest itself in a higher sex ratio for a more recent
survey than an earlier for the same cohort.
A: Cohort sex ratio significantly larger in NFHS-2 than NFHS-1 at the 10 percent level. 
B: Cohort sex ratio significantly larger in NFHS-3 than NFHS-1 at the 10 percent level. 
C: Cohort sex ratio significantly larger in NFHS-3 than NFHS-2 at the 10 percent level. 
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

The relationship between length of marriage and recall error can also seen in 
Figure \ref{fig:sexRatioMarriage}, which shows the observed sex ratio for children reported
as first born as a function of duration of marriage at the time of the survey combining 
all three surveys.
The solid line is the sex ratio of children reported 
as first born by the number of years between the survey and marriage, 
the dashed lines indicate the 95 percent confidence interval 
and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes the years are grouped in twos.
In line with the results from Table \ref{tab:recallMarriage}, the observed ratio of boys 
is increasingly above the expected value the longer ago the parents were married.%
\footnote{
The graph for second births shows a similar pattern with the
likelihood of the second child being a boy going up with increasing marriage duration.
The graphs for the second births and the individual survey rounds are available upon request.
% It is interesting to note that the graphs of ``first'' births for NFHS-1 and 2 
% very clearly show the effect of the 1965-1967 drought in India.
% There is a sharp drop in the percentage boys corresponding to the drought.
% For the surrounding years the percentage of boys among ``first-born'' is around
% 54 percent and increasing, but for the drought years the percentage is slightly
% \emph{below} the natural.
% See also the discussion in Section \ref{sec:review} on nutrition and sex ratios.
}

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
\caption{Sex ratio of ``first'' births by duration of marriage}
\label{fig:sexRatioMarriage}}
\end{figure}

The increasingly unequal sex ratio with increasing marriage duration suggests that
a solution to the recall error problem is to drop observations for 
women who were married ``too far'' from the survey year.
The main problem is establishing what the best cut-off point should be.
As Table \ref{tab:recallMarriage} shows there are differences in recall error across the
three surveys and between parities.
One possibility is simply to drop all women married in cohorts where the observed
sex ratio is substantially higher than the natural sex ratio, but even this is not
straightforward.
For ``first'' born this would imply dropping all women married before 1980, but
for ``second'' born it would be imply dropping all married before 1970 for NFHS-1, before 1975 
for NFHS-2, and before 1980 NFHS-3.
Because of the differences between ``first'' and ``second'' born in the different surveys
I vary the cut-off point by survey round.

NFHS-3 is the most straightforward in that the implied cut-off point is the same for
both first and second born.
Based on Table \ref{tab:recallMarriage}, women in NFHS-3 who were married 26 years or
more before the survey date are dropped.
For NFHS-1 and NFHS-2 the trade-off is between ensuring enough information and not bias 
the results unduly.
Given that sex selective abortions are more likely in higher parity birth I base the
cut-off point on the second births instead of the first births.
Hence, for NFHS-1 women who were married 22 years or more before the survey date 
were dropped and for NFHS-2 women who were married 23 year or more before the survey date 
were dropped.
The final sample consists of 146,096 women, with 332,951 
parity one through four births.

% \begin{figure}
% \centering
% \subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r1}}
% \subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r2}} \\
% \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r3}} 
% \caption{Ratio of Boys for ``First'' Births by Survey Round}
% \label{fig:sex_ratio_recall_rounds}
% \end{figure}

% This indicates the problem with using older data for analyzing sex selective abortions.
% Even more important it shows why using year of birth as a cut-off point
% for addressing recall error is problematic.

\subsection{Sensitivity of Results to Recall Error}

% [referee 2 wants a discussion of how results are impacted by changes in number of
% women dropped because of recall error]

The last three sections in this Appendix show results for the three education groups for 
three samples: the preferred sample used in the paper (Figures \ref{fig:results_spell1_low}
through \ref{fig:results_spell4_high_rural}), 
a more restricted sample where only women married less than 19 years are 
included (Figures \ref{fig:results_limit_spell1_low} through \ref{fig:results_limit_spell3_high_rural}),
and the sample of women dropped because of potential recall error bias, i.e.\ all women 
dropped from the data to reach the preferred sample (Figures \ref{fig:results_dropped_spell1_low}
through \ref{fig:results_dropped_spell3_high_rural}).
For the ``dropped'' sample it is only possible to estimate sex ratios for the period
before sex-selective abortions became available.
The period covered is different from the other two samples because the births for 
the sample takes place over a much longer period; the sample covers spells that begin
between 1950 and 1984.

The different results for women with no education illustrates the potential problems 
with recall error.
Figures \ref{fig:results_spell1_low}, \ref{fig:results_limit_spell1_low}, and 
\ref{fig:results_dropped_spell1_low} show the different results for women with no
education across the three samples.
The preferred and the restricted samples show almost identical results with the main
difference that the restricted sample has wider confidence intervals because of the
smaller sample size.
The results from the dropped sample, on the other hand, show sex ratios that are 
statistically significantly above the natural sex ratio in many periods, which is
consistent with recall error.
Furthermore, the survival curves are substantially closer to being linear indicating
that observed births took place further away from the time of marriage as expected if 
the couple had a girl first but counted a subsequent son as their first-born.

The second spell results demonstrate the trade-off inherent in dealing with recall error.
While the results for women with no education are similar across the preferred and the
restricted samples in rural areas (Figures \ref{fig:results_spell2_low_rural} and
\ref{fig:results_limit_spell2_low_rural}), the results for urban women with no 
education in the restricted sample are much less stable and have substantially wider
confidence intervals than the preferred sample (Figures \ref{fig:results_spell2_low_urban}
and \ref{fig:results_limit_spell2_low_urban}).
This happens because the restricted sample is down to less than 900 urban women, compared
to close to 1,600 urban women in the preferred sample.

An interesting difference to this pattern is for the third spell for women with 8 or more
years of education.
This group shows no evidence on an unequal sex ratio for the ``dropped'' sample in 
either urban or rural areas (Figures \ref{fig:results_dropped_spell3_high_urban} and
\ref{fig:results_dropped_spell3_high_rural}).
However, for the preferred sample there are consistently more boys than girls for urban
women when the first two children are either two girls or one girl and one boy (Figure 
\ref{fig:results_spell3_high_urban}).
Furthermore, the sex ratios become even more unequal when restricting the sample to
women married less than 19 years (Figure \ref{fig:results_limit_spell3_high_urban}), 
although the sample sizes also become substantially smaller.
This is because spell periods are based on the starting year of the spell.
Hence, some of the pregnancies in the 1972--1984 period will have been exposed to the  
availability of prenatal sex determination.
For Figure \ref{fig:results_spell3_high_urban}(a) 25 percent of observed births 
occur in  1986 or after, meaning that conception took place in the 1985--1994 period, 
while for Figure \ref{fig:results_spell3_high_urban}(d) the number is 29 percent.
Hence, it is possible that the unequal sex ratios observed are, indeed, evidence of 
sex-selective abortions.

\clearpage
\newpage

\section{Potential for Reverse Causation in Education?}

The data provides no direct way to tell whether a mother is currently in
school or have returned to school.
The questions in the survey simply ask whether the respondent has ever
attended school, and if yes, what the highest level (standard) completed is.
My best estimate of the age somebody left school is therefore their years of
schooling completed plus 6 years for school starting age.
Based on this, more than 75 percent exit school at age 16 or before,
while 96 percent have stopped school by age 21.

It is possible to get a sense of whether women might return to school after 
giving birth using this information.
To find the year when a woman would have completed school I take her birth
year and add the estimated age at school completion.
If the year the woman is estimated to have completed school is equal to or greater than 
the year of the first birth it is conceivable that the woman may have returned to 
school after giving birth.
This ignores the possibility of grade repetitions, but if somebody needs to
repeat grades it is unlikely that they will go on to secondary or higher education.
Out of 146,096 women in the main sample only 2,615, or less than 2 percent, fall 
into this category.
Furthermore, only 322 are possibly in school at the time of the second school.
Among women who appear to return to school after their first child the sex ratio of their
first birth is skewed somewhat more male than normal (54 percent boys), so their 
return may, indeed, be tied to the sex of their first child.

The estimates are conservative in the sense that it is possible to finish school 
first and then have the child later in the year.
Using if the estimated end of schooling comes \emph{after} the year the child 
is born the numbers fall to 1,234, or less than 1 percent, for
the first birth and 162 for the second birth.

How much of a problem is this then?
It is, indeed, possible that some women return to school after their first child,
but it appears to be relatively  uncommon.
Furthermore, almost nobody are in school after their second child.
Since there is little evidence of sex-selective abortions among first-born children
the possibility of return to school should not affect the estimates.

Furthermore, I use 8 years of education as the cut-off point and hence only women who
had their first child before age 14 would potentially be misclassified in terms of
education group for their first birth. 
There are only 56 women who end up with 8 or more years of education but had their
first birth at age 12 or 13.
None are possibly misclassified for second birth or above, which is where sex-selective 
abortions become important.
The upshot is that while it is possible that there might be some reverse causation of
education and sex of children this should not affect the estimates.

\clearpage
\newpage

\section{Sex Ratios at First Birth}

\setcounter{figure}{0}
\setcounter{table}{0}

% [WHY DO EVERYBODY - COMPARISON WITH JHA ET AL. - ESTABLISH THE ACTUAL SEX RATIO - 
% SHOW THAT LENGTH OF 1ST SPELL GENERALLY SHORT AND RELATION TO FECUNDITY]
% [what do the graphs show - representative woman - later use sample -
% regression results ]

I present a separate analysis of first spell births for three reasons.
First, previous research claims that the largest number of missing girls
is for first order births \citep{jha06}.
Secondly, there are substantially more first births than subsequent births, allowing
for a precise estimation of the ``natural'' percentage boys born in India if there
are no sex selection.
Finally, the results provide an indication of whether first spell length is
a good indicator for fecundity.

Figures \ref{fig:results_spell1_low}, \ref{fig:results_spell1_med}, and 
\ref{fig:results_spell1_high} show the predicted
percentage boys born by quarter from marriage to first birth and the associated
survival functions for the lowest, middle, and highest education groups for representative 
women.
For the first spell the representative woman is 16 years old at the beginning of the 
spell for the no education group, 17 years old for the middle education group, and 
20 years old for the high education group.
Each column represents a time period with the top panel showing urban results and 
the bottom panel rural results.
The graphs also show the expected natural rate of boys, approximately 51.2 percent.%
\footnote{
For comparison, if 55 percent of children born in a given quarter were boys,
approximately 14 percent of the female fetuses were aborted.
Assume 105 boys per 100 girls born, the expected natural sex ratio.
With $b$ boys,  $b\frac{100}{105}$ girls should be born.
If $g$ girls are observed the number of abortions is therefore $b\frac{100}{105}-g$
and the percent aborted female fetuses is 
$\frac{b\frac{100}{105}-g}{b\frac{100}{105}}\times 100$.
With 55 percent boys we get $\frac{55\frac{100}{105}-45}{55\frac{100}{105}}\times 100 = 14.09$.
The corresponding numbers for 60 percent and 65 percent boys are approximately 30 percent and
43 percent of the female fetuses aborted.
}

The most interesting result is how close to the natural sex ratio the predicted percentage
boys is for each group and for each period.
As Figure \ref{fig:results_spell1_low}(d) shows, for rural women without education before 1985, 
who also represent the biggest group, the predicted sex ratios align almost perfectly with 
the expected sex ratio.
For the other groups there is more volatility in the predicted percentage boys, but
nowhere is it statistically significantly larger than 51.2 percent.%
\footnote{
The urban no education group for the 1972--1984 period show two quarters where the predicted
percentage boys is just statistically significantly higher than 51.2 percent, but this
is likely due to recall error not perfectly caught by the method above
and the periods around those two quarters are below the natural percentage boys.
}
Furthermore, for quarters with more substantial deviations from the natural
sex ratio, the predictions are generally based on few births.
In other words, it appears that the probability of having a boy is exactly the same in 
India as it is in other places.

For the group most likely to use sex selection, highly
educated, urban women in the 1995--2006 period, the predicted percentage
boys is also almost perfectly aligned with the expected percentage boys, as shown
in Figure \ref{fig:results_spell1_high}(c).
Hence, there is no evidence that Hindus in India use sex selection on first births.
This cast serious doubts on the data used by \cite{jha06} and their results, as
also discussed by \cite{george06} and \cite{bhat06}.
% \footnote{%
% \cite{jha06} found that in both urban and rural areas there were 54.4 percent boys born 
% among first-borns.
% This translate into 0.17 to 0.23 million females missing among first-borns per year.
% The recall error problem is also noted by \cite{george06} and \cite{bhat06}.
% }

For all education groups and for all periods more than ninety percent of women had their 
first child within 21 quarters of being married and the proportion is increasing in education.
Furthermore, 70 to 85 percent of women will had their first child within ten quarters 
(2.5 years ) of their marriage and the average time between marriage and first birth has 
become shorter over time.
The most likely explanation for the reductions in duration and the increase 
in the number of women who have their first child before 21 quarters is improvements
in health status.
This is also consistent with the differences between education groups where more
educated women are healthier and therefore more likely to conceive.
There are two implications of this.
First, it reinforces the need for estimating the models separately for different
education levels.
Secondly, it confirms that the first spell length can serve as a suitable
proxy for fecundity and that Hindu women in India have their first birth very soon
after marriage, even among highly educated, urban women.

% \subsection{High Education Group}
% 
% If lower fertility is the driving force behind sex selection,
% women with the most education should be the earliest adopters and use it
% for lower parity children than those with less education.
% The predicted percentage boys for the second, third and fourth spells for 
% women with eight or more years of education show that this is, indeed, the case.
% As for the first spell, the results are presented using a representative woman
% with the same characteristics as above, except that the ages at the beginning of
% the spell are 22, 24 and 25 years for the second, third and fourth
% spell and that the first spell length is set equal to 16 months.
% 
% Figures \ref{fig:results_spell2_high_urban} and \ref{fig:results_spell2_high_rural}
% show the second spell predicted percentage boys and the survival curves by spell length 
% for urban and rural women.%
% \footnote{
% Recall, zero quarters is equivalent to nine months after the first birth.
% }
% For both figures, the top panel shows the results if the first child was a girl and the
% bottom panel the results if the first child was a boy.
% Not surprisingly, there is no evidence of sex selection for the 1972--1984 period;
% the predicted percentage boys match up closely with the natural.
% There is some evidence that spacing is shorter after the birth of a girl than
% after a boy, but the differences between the survival curves in the beginning of
% the spells are not large.
% The largest difference at five quarters is for urban women and that 
% is only around five percentage points.
% This is consistent with more educated women being more aware of the
% potential negative effects of close spacing.
% 
% 
% % SPELL 2 - URBAN
% 
% \begin{center}
% [Figure 4 about here.]
% \end{center}
% 
% % \begin{figure}[htpb]
% % \centering
% % \caption*{First child a girl}
% % \setcounter{subfigure}{-2}
% % \subfloat[1972-1984 (N=2,791)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}} 
% % \setcounter{subfigure}{-1}
% % \subfloat[1985--1994 (N=5,011)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{0}
% % \subfloat[1995--2006 (N=3,827)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption*{First child a boy}
% % \setcounter{subfigure}{1}
% % \subfloat[1972-1984 (N=2,877)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % } 
% % \setcounter{subfigure}{2}
% % \subfloat[1985--1994 (N=5,421)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{3}
% % \subfloat[1995--2006 (N=4,015)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption{Predicted probability of having a boy and probability of
% % no birth yet from nine months after first birth for urban 
% % women with 8 or more years of education by quarter. 
% % Predictions based on age 22 at first birth.
% % Left column shows results prior to sex selection available, middle column before
% % sex selection illegal and right column after sex selection illegal.
% % N indicates the number of women in the relevant group in the underlying samples.
% % }
% % \label{fig:results_spell2_high_urban}
% % \end{figure}
% 
% 
% 
% % SPELL 2 - RURAL
% 
% \begin{center}
% [Figure 5 about here.]
% \end{center}
% 
% 
% % \begin{figure}[htpb]
% % \centering
% % \caption*{First child a girl}
% % \setcounter{subfigure}{-2}
% % \subfloat[1972-1984 (N=1,183)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}} 
% % \setcounter{subfigure}{-1}
% % \subfloat[1985--1994 (N=2,967)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{0}
% % \subfloat[1995--2006 (N=2,740)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption*{First child a boy}
% % \setcounter{subfigure}{1}
% % \subfloat[1972-1984 (N=1,305)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % } 
% % \setcounter{subfigure}{2}
% % \subfloat[1985--1994 (N=3,213)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{3}
% % \subfloat[1995--2006 (N=2,945)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption{Predicted probability of having a boy and probability of
% % no birth yet from nine months after first birth for rural
% % women with 8 or more years of education by quarter. 
% % Predictions based on age 22 at first birth.
% % Left column shows results prior to sex selection available, middle column before
% % sex selection illegal and right column after sex selection illegal.
% % N indicates the number of women in the relevant group in the underlying samples.
% % }
% % \label{fig:results_spell2_high_rural}
% % \end{figure}
% 
% The first substantive evidence of sex selection is for urban women with one girl
% in the 1985--1994 period (Figure \ref{fig:results_spell2_high_urban}b).
% The percentage boys begins at the natural level but then increases to almost 60 
% percent after which it drops slightly.
% The use of sex-selective abortions becomes even more apparent for the 1995--2006
% period, where the percentage boys born to highly educated women with one girl 
% begins at just below 60 percent, increases to above 65 percent, followed by a decline to
% just over 55 percent.
% These results are especially remarkable given that the numbers are for all of India, not
% just the states with traditionally strong son preferences.
% 
% % [explain shape of curves]
% Of particularly interest is how the predicted percentage boys changes with spell length.
% The development in the percentage boys by quarter for the 1995--2006 period
% (Figure \ref{fig:results_spell2_high_urban}c), 
% is consistent with some women changing their 
% decision to use sex selection after going through one or more abortions.
% The results are for the median level of fecundity, and it is therefore unlikely 
% that the decline is due to lower fecundity for women who give birth later in the spell.%
% \footnote{
% It is, of course, possible that women find it harder to conceive during the
% second spell, but the survival curve would be very close to the survival 
% curve for the first period if the female fetuses were carried to term.
% }
% The 1985--1994 period (Figure \ref{fig:results_spell2_high_urban}b)
% shows the same fall at the end of the observed spell, but it also
% begins at the natural level, consistent with increasing access and 
% acceptance of sex selection over the early period.
% Women who began their second spell early in the 1985--1994 period were less likely
% to have access than women who began their second spell later in the period.
% % Furthermore, women who did not conceive early after a girl but
% % either decided to wait or had trouble getting pregnant were also more likely
% % to have sex selection techniques available to them.
% The 1985--1994 results can be thought of as the pattern that will
% prevail as sex selection is introduced, and the 1995--2006 results show
% the pattern with a mature and readily available technology.
% That sex selection for the 1995--2006 period is used earlier in the 
% spell compared to later also shows that not taking account of timing of births
% and the potential censoring of birth spell can lead to an upward bias in the
% final sex ratio of second born children.
% 
% % [compare to changes in rural areas for shape]
% For rural areas there is no sign of sex-selective abortion during the 1985--1994 period,
% but for the 1995--2006 period the percentage boys born to highly educated women who have
% a girl as their first child increases gradually from 55 percent to over 60 percent until
% dropping off to the normal percentage boys (Figure \ref{fig:results_spell2_high_rural}c).
% Hence, there appears to be easy access to prenatal sex determination even
% in rural areas.
% The difference between urban and rural women for the 1985--1994
% period is more likely to be the result of differences in fertility than in access
% to prenatal sex determinantion as shown below.
% As more and more rural women have only two children the use of sex selection
% goes up.
% The implication is that rural areas lag behind urban areas but not by 
% much and that the expected pattern for the next round of 
% the NFHS for rural educated women should closely mirror what is found 
% for the 1995--2006 period for urban women.
% 
% Women who had a boy as their first child do not appear to be using sex-selective abortions.
% This holds for urban and rural areas and for all time periods.
% In addition, women with a boy are less likely to have a second birth within the
% 21 quarters.
% This is especially prevalent for urban women, although rural women show the same pattern.
% For urban women with one boy, more than thirty percent are not predicted to have
% their second child within the 21 quarters covered here.
% This means that six years have passed since the birth of their first child and given
% the flatness of the survival function it it unlikely that many of these women will
% ever have a second child.
% Even for rural women around twenty percent of women will likely not have a second child.
% 
% 
% [THIS NEEDS TO BE REWRITTEN TO INCORPORATE R3'S QUESTION ABOUT PANELS (A) AND (D) AND
% THE HIGH SEX RATIO FOR THE 1972-1984 PERIOD]
% 
% The results for the third spell are shown in Figures \ref{fig:results_spell3_high_urban} 
% and \ref{fig:results_spell3_high_rural} for the representative 
% urban and rural women.
% The top panel shows the result if the first two children were girls, the middle
% panel if the couple had one boy and one girl, and the bottom panel if the
% first two children were boys.
% Again there is no evidence of sex-selective abortions before 1985, but
% clearly there is more volatility in the predicted percentage boys due
% to the lower sample sizes.
% 
% 
% % SPELL 3 - URBAN
% 
% \begin{center}
% [Figure 6 about here.]
% \end{center}
% 
% % \begin{figure}[htpb]
% % \centering
% % \caption*{First two children girls}
% % \setcounter{subfigure}{-2}
% % \subfloat[1972-1984 (N=735)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}} 
% % \setcounter{subfigure}{-1}
% % \subfloat[1985--1994 (N=1,681)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{0}
% % \subfloat[1995--2006 (N=1,015)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption*{First two children one boy and one girl}
% % \setcounter{subfigure}{1}
% % \subfloat[1972-1984 (N=1,416)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % } 
% % \setcounter{subfigure}{2}
% % \subfloat[1985--1994 (N=3,506)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{3}
% % \subfloat[1995--2006 (N=2,367)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption{Predicted probability of having a boy and probability of
% % no birth yet from nine months after second birth for urban 
% % women with 8 or more years of education by quarter. 
% % Predictions based on age 24 at second birth.
% % Left column shows results prior to sex selection available, middle column before
% % sex selection illegal and right column after sex selection illegal.
% % N indicates the number of women in the relevant group in the underlying samples.
% % }
% % \label{fig:results_spell3_high_urban}
% % \end{figure}
% % 
% % 
% % \begin{figure}[htpb]
% % \centering
% % \caption*{First two children boys}
% % \setcounter{subfigure}{4}
% % \subfloat[1972-1984 (N=789)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % } 
% % \setcounter{subfigure}{5}
% % \subfloat[1985--1994 (N=1,665)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{6}
% % \subfloat[1995--2006 (N=1,086)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % % \label{fig:results_spell3_high_urban}
% % \caption{(Continued) Predicted probability of having a boy and probability of
% % no birth yet from nine months after second birth for urban 
% % women with 8 or more years of education by quarter. 
% % Predictions based on age 24 at second birth.
% % Left column shows results prior to sex selection available, middle column before
% % sex selection illegal and right column after sex selection illegal.
% % N indicates the number of women in the relevant group in the underlying samples.
% % \ContinuedFloat
% % }
% % \addtocounter{figure}{1}
% % \end{figure}
% 
% % HAVE NO IDEA WHY THIS IS NEEDED BUT SOMETHING SEESM TO GO WRONG WITH THE COMBINATION
% % OF SUBFIGURE AND CONTINUEDFLOAT
% % 
% 
% % SPELL 3 - RURAL
% 
% \begin{center}
% [Figure 7 about here.]
% \end{center}
% 
% % \begin{figure}[htpb]
% % \centering
% % \caption*{First two children girls}
% % \setcounter{subfigure}{-2}
% % \subfloat[1972-1984 (N=312)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}} 
% % \setcounter{subfigure}{-1}
% % \subfloat[1985--1994 (N=942)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{0}
% % \subfloat[1995--2006 (N=842)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption*{First two children one boy and one girl}
% % \setcounter{subfigure}{1}
% % \subfloat[1972-1984 (N=666)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % } 
% % \setcounter{subfigure}{2}
% % \subfloat[1985--1994 (N=1,909)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{3}
% % \subfloat[1995--2006 (N=1,763)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption{Predicted probability of having a boy and probability of
% % no birth yet from nine months after second birth for rural
% % women with 8 or more years of education by quarter. 
% % Predictions based on age 24 at second birth.
% % Left column shows results prior to sex selection available, middle column before
% % sex selection illegal and right column after sex selection illegal.
% % N indicates the number of women in the relevant group in the underlying samples.
% % }
% % \label{fig:results_spell3_high_rural}
% % \end{figure}
% % 
% % 
% % \begin{figure}[htpb]
% % % \TheContinuedFloat
% % \centering
% % \caption*{First two children boys}
% % \setcounter{subfigure}{4}
% % \subfloat[1972-1984 (N=339)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}} 
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % } 
% % \setcounter{subfigure}{5}
% % \subfloat[1985--1994 (N=899)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \setcounter{subfigure}{6}
% % \subfloat[1995--2006 (N=763)]{
% % \begin{minipage}{0.25\textwidth}
% % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
% % \captionsetup[subfigure]{labelformat=parens}
% % \end{minipage}
% % }
% % \caption{(Continued) Predicted probability of having a boy and probability of
% % no birth yet from nine months after second birth for rural
% % women with 8 or more years of education by quarter. 
% % Predictions based on age 24 at second birth.
% % Left column shows results prior to sex selection available, middle column before
% % sex selection illegal and right column after sex selection illegal.
% % N indicates the number of women in the relevant group in the underlying samples.
% % \ContinuedFloat
% % }
% % % \label{fig:results_spell3_high_rural}
% % \addtocounter{figure}{1}
% % \end{figure}
% 
% % HAVE NO IDEA WHY THIS IS NEEDED BUT SOMETHING SEESM TO GO WRONG WITH THE COMBINATION
% % OF SUBFIGURE AND CONTINUEDFLOAT
% % \addtocounter{figure}{1}
% 
% 
% 
% In urban areas there is clear evidence of sex-selective abortions among women
% with two girls for both 1985--1994 and 1995--2006.
% For the first of these periods, births early in the spell are close to the natural sex ratio,
% but births after the fifth quarter are significantly above the natural level
% at around 65 percent boys.%
% \footnote{
% The sex ratio increases substantially for births after the 15th quarter, but 
% given the low number of births it is not clear how much one can learn from this increase.
% }
% Interestingly, there does not appear to be an increase in the use of sex-selective
% abortions in the 1995--2006 period compared to the 1985--1994 period.
% This can be explained by the increase in the use of sex-selective
% abortions for second births combined with lower desired fertility.
% Fewer women have two girls and given the apparent ready access to prenatal
% sex determination those who do are more likely to do so by choice.%
% \footnote{
% For urban women, 25 percent of the sample in the first period had two girls, 
% while only 22.7 percent of the third period sample had two girls.
% }
% Even then, the percentage boys born is between 60 and 65 percent.
% This pattern of sex selection for women with two girls is mirrored by rural women.
% As expected, given that most educated women do not want more than two children,
% there is no evidence for declining use of sex selection toward the end of the spell.
% 
% Women with either two boys or one boy and one girl as 
% their first two children do not appear to use sex selection.
% Relatively few of these women go on to have a third child
% and the proportion that does declines substantially over time.
% This is best illustrated by the urban women in the 1995--2006 period (Figures 
% \ref{fig:results_spell3_high_urban}c, f, i).
% Close to sixty percent of the women with two girls will have a third child,
% while only around thirty percent of those with at least one boy will
% have a third child.
% For comparison, during the 1972--1984 period eighty percent of the urban women 
% with two girls had a third child and almost sixty percent of those
% with at least one boy had a third child.
% The numbers are higher for rural women, but the pattern is the same.
% 
% 
% Relatively few women with eight or more years of education have three children and 
% even fewer have four.
% This means that caution should be used in interpreting the results and in the interest
% of space the graphs are not presented here.%
% \footnote{
% Graphs and underlying estimation results are available on request.
% }
% As for the other spells there is no evidence of sex selection for the first period.
% Again, families without boys are the main users of sex-selective abortions.
% For urban women with three girls the predicted percentage boys is between 60 and 75 for both
% the 1985--1994 and 1995--2006 time periods.
% The numbers for rural women with three girls are in line with those for urban women.
% It is worth noting that there are only 211 and 155 observed births for
% urban women for the two time periods, and only 167 and 178 births for the rural women.
% % What appear to be the only evidence against the ``funeral pyre'' hypothesis
% % comes from urban women with two girls and one boy for whom the predicted percentage
% % boys is above 65 percent for all quarters, but this result is based on only 292 births
% % and does not show up for other urban women or for rural women.
% Urban women with with two girls and one boy show a predicted percentage boys above 65 
% percent for all quarters, but this result is based on only 292 births.
% Finally, it is interesting that the probability of having a fourth child is
% higher for women with three boys than it is for women with two boys and one girl.
% This might be evidence of a slight gender balance preference, although 
% there is absolutely no evidence that women are aborting boys and the number
% of observed births to both groups is very small.
% 
% 
% 
% % SPELL 2 - URBAN
% % \begin{figure}
% % \centering
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r7_pc}}
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r8_pc}} \\ \setcounter{subfigure}{0}
% % \subfloat[Rural (N=4,663)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r7_s}}
% % \subfloat[Urban (N=7,940)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r8_s}} \\
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r3_pc}}
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r4_pc}} \\ \setcounter{subfigure}{2}
% % \subfloat[Rural (N=1,044)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r3_s}}
% % \subfloat[Urban (N=898)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r4_s}}
% % \caption{Predicted percent boys born and ``survival'' functions by spacing after first birth
% % and by areas of residence for women with 8 or more years of education with the first child a girl.
% % Top Panel shows Wants 2 or Fewer Children and Bottom Panel 3 or More. \protect\linebreak
% % N indicates Number of Women who Began a Spell.}
% % \label{fig:results_spell2_high_want}
% % \end{figure}
% 
% 
% % \begin{figure}[htpb]
% % \centering
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r7_pc}}
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r3_pc}}
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r8_pc}} 
% % \subfloat{\includegraphics[width=.25\textwidth]{want_spell2_high_r4_pc}} \\ \setcounter{subfigure}{0}
% % \subfloat[Rural (N=4,663)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r7_s}}
% % \subfloat[Rural (N=1,044)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r3_s}}
% % \subfloat[Urban (N=7,940)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r8_s}} 
% % \subfloat[Urban (N=898)]{\includegraphics[width=.25\textwidth]{want_spell2_high_r4_s}}
% % \caption{Predicted percent boys born and survival functions by spacing after first birth
% % and by areas of residence for women with 8 or more years of education with first child a girl.
% % Left shows wants 2 or fewer children and right 3 or more. 
% % N indicates number of women who began a spell.}
% % \label{fig:results_spell2_high_want}
% % \end{figure}
% 
% \subsection{Middle and Low Education Groups}
% 
% For women with one to seven years of education, a representative woman is 
% used with the first spell length set to 16 months and the ages at the 
% beginning of the spell 19, 21 and 24 for the second, third and fourth spells, respectively.
% There are two factors that make it difficult to establish whether sex selection
% is used among the middle education group.
% First, there are fewer observations for this group compared with the high
% education group.
% That problem becomes especially acute when looking at the higher spells
% divided by sex composition of previous children.
% Secondly, even for those spells with more information there is substantially
% more noise in the 1972--1984 results than for the high education group.%
% \footnote{
% The results are available on request.
% }
% % The results are presented in Appendix A.
% 
% For the second spell there is no evidence of sex-selective abortions for
% either urban or rural women and the proportion of women who have a second
% birth remains high across all three time periods.
% The same is the case for the third spell, although there are signs of falling
% fertility in that the proportion of women who have a third child is decreasing,
% especially among those with one or two boys.%
% \footnote{
% There are relatively few urban women with two girls in this education group 
% and although there might be some evidence of sex-selective abortions the
% results are too noisy to conclude anything with any degree of confidence.
% }
% Even for the fourth spell, women with three girls do not show statistically
% significant use of sex-selective abortions and this holds for both urban 
% and rural women.
% For both urban and rural women there has been a substantial decline in the
% number of women who have a fourth child and again this decline is concentrated
% among women with one or more boys.
% 
% 
% For women with no education, the starting ages are 18, 21 and 23 for 
% the second, third and fourth spells, respectively.
% Although there are not a large number of women in urban areas without education
% there are substantial numbers in the rural areas.%
% \footnote{
% The results are available on request.
% }
% % The results are presented in Appendix A.
% For urban women without education there is little evidence of sex selection
% for any of the spells.%
% \footnote{
% Urban women with three girls do have a higher percentage boys, but only 208 are in this group.
% }
% Although the percentage boys for rural women with one girl for the second
% spell is a very precisely estimated flat line for the 1985--1994 period,
% the percentage boys for the third period is between 55 and 60 from the
% seventh to the thirteenth quarter and this percentage is statistically 
% significant.\footnote{
% These quarters account for more than twenty percent of the births or
% slightly more than 700 births.
% }
% Two things makes this result puzzling.
% First, there is little evidence of women stopping
% childbearing once they have a son.
% Even among rural women with two sons almost ninety percent go on to
% have a third child and eighty percent of women with three boys
% have a fourth child.
% Hence, fertility remains very high for this group and therefore also
% the probability of having at least one son without the use of sex-selective 
% abortions.
% Secondly, one would expect more use of sex selection for women with
% two girls in the third spell or three girls in the fourth spell, but
% for both the predicted percentage boys is close to the natural rate.
%

\clearpage
\newpage

\section{Migration}

\setcounter{figure}{0}
\setcounter{table}{0}

\begin{table}[hp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Migration by Beginning of Spell}
\label{tab:migrate}
\begin{tabular}{l  D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} } \toprule
                & \multicolumn{9}{c}{Years of Education} \\ \cmidrule(lr){2-10}
                & \multicolumn{3}{c}{None}                   & \multicolumn{3}{c}{1--7 Years}              & \multicolumn{3}{c}{8 or More Years} \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10}
                & \mco{1972--} & \mco{1985--} & \mco{1995--} & \mco{1972--} & \mco{1985--} & \mco{1995--}  & \mco{1972--} & \mco{1985--} & \mco{1995--} \\
                & \mco{1984}   & \mco{1994}   & \mco{2006}   & \mco{1984}   & \mco{1994}   & \mco{2006}    & \mco{1984}   & \mco{1994}   & \mco{2006} \\
\midrule                
\multicolumn{10}{l}{\textbf{After marriage (\%)}} \\
Did not move    &       51.20&       59.60&       64.04&       50.24&       58.38&       63.68&       42.16&       51.07&       61.07\\
Within same type&       39.76&       32.69&       27.99&       34.85&       29.94&       25.95&       41.38&       34.69&       27.35\\
Rural to urban  &        7.20&        5.91&        5.87&       10.91&        8.18&        7.33&       11.91&        9.93&        7.75\\
Urban to rural  &        1.85&        1.80&        2.10&        4.00&        3.49&        3.04&        4.55&        4.30&        3.83\\
\addlinespace 
\multicolumn{10}{l}{\textbf{After first birth (\%)}} \\
Did not move    &       80.66&       86.63&       88.78&       75.16&       82.93&       88.32&       66.60&       76.85&       86.33\\
Within same type&       14.06&        9.23&        7.02&       16.11&       10.95&        7.12&       24.16&       16.21&        9.44\\
Rural to urban  &        4.25&        3.28&        3.23&        6.39&        4.33&        3.36&        6.63&        4.97&        3.04\\
Urban to rural  &        1.03&        0.85&        0.97&        2.34&        1.78&        1.21&        2.61&        1.96&        1.18\\
\addlinespace 
\multicolumn{10}{l}{\textbf{After second birth (\%)}} \\
Did not move    &       80.66&       85.40&       85.77&       75.17&       81.42&       85.08&       66.64&       74.58&       82.48\\
Within same type&       14.08&       10.12&        8.91&       16.15&       11.93&        9.33&       24.08&       17.59&       11.84\\
Rural to urban  &        4.22&        3.56&        4.02&        6.37&        4.72&        4.07&        6.72&        5.62&        4.09\\
Urban to rural  &        1.04&        0.93&        1.30&        2.32&        1.94&        1.51&        2.56&        2.20&        1.58\\
\addlinespace 
\multicolumn{10}{l}{\textbf{After third birth (\%)}} \\
Did not move    &       80.76&       84.22&       84.47&       75.19&       81.01&       82.24&       68.55&       75.25&       82.54\\
Within same type&       13.98&       10.89&        9.98&       15.88&       12.13&       11.51&       21.98&       16.62&       10.82\\
Rural to urban  &        4.25&        3.91&        4.28&        6.57&        4.93&        4.74&        7.02&        5.89&        4.98\\
Urban to rural  &        1.01&        0.98&        1.26&        2.35&        1.93&        1.51&        2.46&        2.24&        1.66\\
\bottomrule
\end{tabular}
\begin{tablenotes} 
\scriptsize
\item \hspace*{-0.5em} \textbf{Note.}
``Within same type'' indicates either a move from a rural area to another rural area,
or a move from an urban area to another urban area.
\end{tablenotes}
\end{threeparttable}
\end{table}

% \begin{table}[hp]
% \centering
% \footnotesize
% \begin{threeparttable}
% \caption{Migration by beginning of spell for women with no education}
% \label{tab:migrate_low}
% \begin{tabular}{l  D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} } \toprule
%                 & \mco{1972--1984} & \mco{1985--1994} & \mco{1995--2006} \\
%                 & \multicolumn{3}{c}{After marriage (\%)} \\
% Did not move    &       51.20&       59.60&       64.04\\
% Within same type&       39.76&       32.69&       27.99\\
% Rural to urban  &        7.20&        5.91&        5.87\\
% Urban to rural  &        1.85&        1.80&        2.10\\
%                 & \multicolumn{3}{c}{After first birth (\%)} \\
% Did not move&       80.66&       86.63&       88.78\\
% Within same type&       14.06&        9.23&        7.02\\
% Rural to urban&        4.25&        3.28&        3.23\\
% Urban to rural&        1.03&        0.85&        0.97\\
%                 & \multicolumn{3}{c}{After second birth (\%)} \\
% Did not move&       80.66&       85.40&       85.77\\
% Within same type&       14.08&       10.12&        8.91\\
% Rural to urban&        4.22&        3.56&        4.02\\
% Urban to rural&        1.04&        0.93&        1.30\\
%                 & \multicolumn{3}{c}{After third birth (\%)} \\
% Did not move&       80.76&       84.22&       84.47\\
% Within same type&       13.98&       10.89&        9.98\\
% Rural to urban&        4.25&        3.91&        4.28\\
% Urban to rural&        1.01&        0.98&        1.26\\
% \bottomrule
% \end{tabular}
% \begin{tablenotes} 
% \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.}
% ``Within same type'' indicates either a move from a rural area to another rural area,
% or a move from an urban area to another urban area.
% \end{tablenotes}
% \end{threeparttable}
% \end{table}
% 
% 
% \begin{table}
% \centering
% \footnotesize
% \begin{threeparttable}
% \caption{Migration by beginning of spell for women with 1 through 7 years of education}
% \label{tab:migrate_med}
% \begin{tabular}{l  D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} } \toprule
%                 & \mco{1972--1984} & \mco{1985--1994} & \mco{1995--2006} \\
%                 & \multicolumn{3}{c}{After marriage (\%)} \\
% Did not move    &       50.24&       58.38&       63.68\\
% Within same type&       34.85&       29.94&       25.95\\
% Rural to urban  &       10.91&        8.18&        7.33\\
% Urban to rural  &        4.00&        3.49&        3.04\\
%                 & \multicolumn{3}{c}{After first birth (\%)} \\
% Did not move    &       75.16&       82.93&       88.32\\
% Within same type&       16.11&       10.95&        7.12\\
% Rural to urban  &        6.39&        4.33&        3.36\\
% Urban to rural  &        2.34&        1.78&        1.21\\
%                 & \multicolumn{3}{c}{After second birth (\%)} \\
% Did not move    &       75.17&       81.42&       85.08\\
% Within same type&       16.15&       11.93&        9.33\\
% Rural to urban  &        6.37&        4.72&        4.07\\
% Urban to rural  &        2.32&        1.94&        1.51\\
%                 & \multicolumn{3}{c}{After third birth (\%)} \\
% Did not move    &       75.19&       81.01&       82.24\\
% Within same type&       15.88&       12.13&       11.51\\
% Rural to urban  &        6.57&        4.93&        4.74\\
% Urban to rural  &        2.35&        1.93&        1.51\\
% \bottomrule
% \end{tabular}
% \begin{tablenotes} 
% \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.}
% ``Within same type'' indicates either a move from a rural area to another rural area,
% or a move from an urban area to another urban area.
% \end{tablenotes}
% \end{threeparttable}
% \end{table}
% 
% 
% \begin{table}
% \centering
% \footnotesize
% \begin{threeparttable}
% \caption{Migration by beginning of spell for women with 8 or more years of education}
% \label{tab:migrate_high}
% \begin{tabular}{l  D{.}{.}{2,2} D{.}{.}{2,2} D{.}{.}{2,2} } \toprule
%                 & \mco{1972--1984} & \mco{1985--1994} & \mco{1995--2006} \\
%                 & \multicolumn{3}{c}{After marriage (\%)} \\
% Did not move    &       42.16&       51.07&       61.07\\
% Within same type&       41.38&       34.69&       27.35\\
% Rural to urban  &       11.91&        9.93&        7.75\\
% Urban to rural  &        4.55&        4.30&        3.83\\
%                 & \multicolumn{3}{c}{After first birth (\%)} \\
% Did not move    &       66.60&       76.85&       86.33\\
% Within same type&       24.16&       16.21&        9.44\\
% Rural to urban  &        6.63&        4.97&        3.04\\
% Urban to rural  &        2.61&        1.96&        1.18\\
%                 & \multicolumn{3}{c}{After second birth (\%)} \\
% Did not move    &       66.64&       74.58&       82.48\\
% Within same type&       24.08&       17.59&       11.84\\
% Rural to urban  &        6.72&        5.62&        4.09\\
% Urban to rural  &        2.56&        2.20&        1.58\\
%                 & \multicolumn{3}{c}{After third birth (\%)} \\
% Did not move    &       68.55&       75.25&       82.54\\
% Within same type&       21.98&       16.62&       10.82\\
% Rural to urban  &        7.02&        5.89&        4.98\\
% Urban to rural  &        2.46&        2.24&        1.66\\
% \bottomrule
% \end{tabular}
% \begin{tablenotes} 
% \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.}
% ``Within same type'' indicates either a move from a rural area to another rural area,
% or a move from an urban area to another urban area.
% \end{tablenotes}
% \end{threeparttable}
% \end{table}

\clearpage
\newpage

\section{All Graphs using Main Sample}

\setcounter{figure}{0}
\setcounter{table}{0}

% Figures \ref{fig:results_spell2_low_urban} to \ref{fig:results_spell4_low_rural_cont}
% show the results for the group of women with no education.
% The starting ages are 18, 21 and 23 for the second, third and fourth spells,
% respectively.

% The results for women with one to seven years of education are presented
% in Figures \ref{fig:results_spell2_med_urban} to \ref{fig:results_spell4_med_rural_cont}.
% Again a representative woman is used with the first spell length set to
% 16 months and the ages at the beginning of the spell 19, 21 and 24
% for the second, third and fourth spells, respectively.

% [FIRST SPELL]

\begin{figure}[htpb!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=4,518)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,309)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,762)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=25,486)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=23,360)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,922)]{
\begin{minipage}{0.28\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with no education by quarter (3 month
period). 
Predictions based on age 16 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_low}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=3,666)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,104)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,302)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=7,496)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=9,000)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=5,208)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
period). 
Predictions based on age 17 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_med}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=7,338)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=11,045)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=9,116)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=3,933)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=8,027)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,504)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 8 or more years of education by quarter
(3 month period). 
Predictions based on age 20 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell1_high}
\end{figure}

\clearpage
\newpage

\subsection{Second Spell}

% SPELL 2 - URBAN - LOW
\begin{figure}[h]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=1,596)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=2,232)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=952)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=1,754)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=2,411)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=930)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_urban}
\end{figure}

% SPELL 2 - rural - LOW
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=8,426)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=11,481)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=3,686)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=9,395)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=12,127)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=3,860)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_rural}
\end{figure}

% SPELL 2 - URBAN - MEDIUM
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=1,342)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=1,969)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=1,082)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=1,461)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=2,182)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=1,104)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 19 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_med_urban}
\end{figure}

% SPELL 2 - rural - MEDIUM
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=2,603)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=4,095)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=2,159)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=2,803)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=4,203)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=2,197)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 19 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_med_rural}
\end{figure}

% High education

\begin{figure}[htpb]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,689)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,869)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=3,774)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=2,806)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=5,246)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,969)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=1,305)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=3,105)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,823)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,404)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=3,381)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,044)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_high_rural}
\end{figure}

\clearpage
\newpage

\subsection{Third Spell}

% low education

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=493)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=996)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=475)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,083)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=2,141)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=950)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_low_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=569)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,124)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=426)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell3_low_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,599)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=5,062)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,879)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=5,382)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=10,473)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,779)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_low_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=3,070)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=5,339)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=1,846)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell3_low_rural}
\end{figure}

% Medium education

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=432)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=825)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=425)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=883)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,673)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=848)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_med_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=446)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=848)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=438)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell3_med_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=775)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=1,659)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=848)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,639)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=3,222)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=1,773)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_med_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=785)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,548)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=730)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell3_med_rural}
\end{figure}

% High education

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=709)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=1,654)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,000)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,409)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=3,460)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=2,357)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=780)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,660)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=1,098)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell3_high_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=348)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=982)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=863)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=700)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,987)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=1,819)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_high_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=370)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=945)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=790)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell3_high_rural}
\end{figure}

\clearpage
\newpage

\subsection{Fourth Spell}

% low education

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=130)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=446)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=200)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=410)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,185)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=601)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_low_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=389)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,145)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=486)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children three boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=141)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=382)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=155)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell4_low_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=752)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=1,954)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=888)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=2,065)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=5,990)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=2,456)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_low_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=2,168)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=5,439)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=2,155)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=777)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,895)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=696)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell4_low_rural}
\end{figure}

% Medium education

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=110)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=282)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=144)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=299)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=765)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=372)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_med_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=274)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=600)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=275)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children three boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=77)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=230)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=90)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell4_med_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=210)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=601)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=317)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=581)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,532)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=800)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_med_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=492)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,197)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=578)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children three boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=158)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=357)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=192)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell4_med_rural}
\end{figure}

% High education

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=131)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=355)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=191)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=353)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,062)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=590)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=309)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=681)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=344)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children three boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=87)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=233)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=110)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell4_high_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=62)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=257)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=201)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=176)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=664)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=564)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_high_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=173)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=515)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=367)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=56)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=166)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=92)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell4_high_rural}
\end{figure}

\clearpage

\section{Graphs using Women Married less than 19 Years}

\setcounter{figure}{0}
\setcounter{table}{0}

% Figures \ref{fig:results_spell2_low_urban} to \ref{fig:results_spell4_low_rural_cont}
% show the results for the group of women with no education.
% The starting ages are 18, 21 and 23 for the second, third and fourth spells,
% respectively.

% The results for women with one to seven years of education are presented
% in Figures \ref{fig:results_spell2_med_urban} to \ref{fig:results_spell4_med_rural_cont}.
% Again a representative woman is used with the first spell length set to
% 16 months and the ages at the beginning of the spell 19, 21 and 24
% for the second, third and fourth spells, respectively.

% [FIRST SPELL]

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,529)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=3,831)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,762)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=16,293)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=21,631)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,922)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with no education by quarter (3 month
period). 
Predictions based on age 16 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell1_low}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,022)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=3,653)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,302)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=4,575)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=8,356)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=5,208)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
period). 
Predictions based on age 17 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell1_med}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=4,408)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_pc}}\\
\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=10,118)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=9,116)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=2,668)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_s}} 
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=7,585)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=7,504)]{
\begin{minipage}{0.31\textwidth}
\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_pc}}\\
\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_s}}
\captionsetup[subfigure]{labelformat=parens}
\end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 8 or more years of education by quarter
(3 month period). 
Predictions based on age 20 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell1_high}
\end{figure}

\clearpage

\subsection{Second Spell}

% SPELL 2 - URBAN - LOW
\begin{figure}[hp]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=861)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=1,763)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=946)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=951)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=1,929)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=921)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell2_low_urban}
\end{figure}

% SPELL 2 - rural - LOW
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=5,103)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=9,913)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=3,653)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=5,500)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=10,437)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=3,834)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell2_low_rural}
\end{figure}

% SPELL 2 - URBAN - MEDIUM
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=714)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=1,578)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=1,074)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=791)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=1,766)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=1,096)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 19 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell2_med_urban}
\end{figure}

% SPELL 2 - rural - MEDIUM
\begin{figure}
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972-1984 (N=1,464)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985-1994 (N=3,510)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1995-2006 (N=2,151)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972-1984 (N=1,645)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985-1994 (N=3,671)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995-2006 (N=2,182)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 19 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell2_med_rural}
\end{figure}

% High education

\begin{figure}[htpb]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=1,576)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,105)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=3,762)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=1,667)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=4,431)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,953)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell2_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=847)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=2,788)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=2,816)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=925)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=3,033)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,039)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell2_high_rural}
\end{figure}

\clearpage
\subsection{Third Spell}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=252)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=690)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=458)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=564)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,497)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=915)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell3_low_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=293)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=783)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=410)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_limit_spell3_low_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=1,417)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,060)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=1,827)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=2,803)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=8,265)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,661)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell3_low_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=1,613)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=4,200)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=1,786)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_limit_spell3_low_rural}
\end{figure}

% Medium education

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=223)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=577)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=409)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=433)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,188)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=804)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell3_med_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=229)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=594)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=423)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_limit_spell3_med_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=395)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=1,264)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=840)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=829)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=2,549)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=1,737)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell3_med_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=419)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,216)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=716)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_limit_spell3_med_rural}
\end{figure}

% High education

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=390)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=1,196)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=981)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=778)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=2,543)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=2,309)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell3_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=442)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,230)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=1,068)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_limit_spell3_high_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First two children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=200)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=798)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=857)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First two children one boy and one girl}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=412)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,646)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=1,805)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_limit_spell3_high_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First two children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=209)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=767)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=782)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_limit_spell3_high_rural}
\end{figure}

\clearpage

\section{Graphs using Women Dropped Because of Recall Error}

\setcounter{figure}{0}
\setcounter{table}{0}

% [FIRST SPELL]

\begin{figure}[htpb]
\centering
\caption*{1950--1980}
\setcounter{subfigure}{-2}
\subfloat[Urban (N=3,775)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[Rural (N=19,635)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with no education by quarter (3 month
period). 
Predictions based on age 16 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell1_low}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1954--1980 }
\setcounter{subfigure}{-2}
\subfloat[Urban (N=2,864)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[Rural (N=4,885)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
period). 
Predictions based on age 17 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell1_med}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1955--1980}
\setcounter{subfigure}{-2}
\subfloat[Urban (N=3,157)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[Rural (N=1,491)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from time of marriage for women with 8 or more years of education by quarter
(3 month period). 
Predictions based on age 20 at marriage.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell1_high}
\end{figure}

\clearpage

\subsection{Second Spell}

% SPELL 2 - URBAN - LOW
\begin{figure}[hb]
\centering
\caption*{1954--1984 }
\setcounter{subfigure}{-2}
\subfloat[First child a girl (N=1,760)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[First child a boy (N=2,050)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell2_low_urban}
\end{figure}

% SPELL 2 - rural - LOW
\begin{figure}
\centering
\caption*{1954--1984 }
\setcounter{subfigure}{-2}
\subfloat[First child a girl (N=8,594)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[First child a boy (N=10,123)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with no education by quarter (3 month period). 
Predictions based on age 18 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell2_low_rural}
\end{figure}

% SPELL 2 - URBAN - MEDIUM
\begin{figure}
\centering
\caption*{1955--1984 }
\setcounter{subfigure}{-2}
\subfloat[First child a girl (N=1,362)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[First child a boy (N=1,472)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 19 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell2_med_urban}
\end{figure}

% SPELL 2 - rural - MEDIUM
\begin{figure}
\centering
\caption*{1955--1984 }
\setcounter{subfigure}{-2}
\subfloat[First child a girl (N=2,254)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[First child a boy (N=2,368)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 19 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell2_med_rural}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1957--1984 }
\setcounter{subfigure}{-2}
\subfloat[First child a girl (N=1,498)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[First child a boy (N=1,607)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell2_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1957--1984 }
\setcounter{subfigure}{-2}
\subfloat[First child a girl (N=655)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[First child a boy (N=743)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell2_high_rural}
\end{figure}

\clearpage

\subsection{Third Spell}

\begin{figure}[htpb]
\centering
\caption*{1957--1984}
\setcounter{subfigure}{-2}
\subfloat[Two girls (N=763)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[One boy and one girl (N=1,743)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Two boys (N=982)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell3_low_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1957--1984 }
\setcounter{subfigure}{-2}
\subfloat[Two girls (N=3,796)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[One boy and one girl (N=8,390)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[1972--1984 (N=4,903)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell3_low_rural}
\end{figure}

% Medium education

\begin{figure}[htpb]
\centering
\caption*{1958--1984 }
\setcounter{subfigure}{-2}
\subfloat[Two girls (N=633)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[One boy and one girl (N=1,236)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Two boys (N=716)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell3_med_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1958--1984 }
\setcounter{subfigure}{-2}
\subfloat[Two girls (N=995)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[One boy and one girl (N=2,037)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Two boys (N=1,093)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 1 to 7 years of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell3_med_rural}
\end{figure}

% High education

\begin{figure}[htpb]
\centering
\caption*{1960--1984 }
\setcounter{subfigure}{-2}
\subfloat[Two girls (N=660)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[One boy and one girl (N=1,375)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Two boys (N=673)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell3_high_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{1960--1984 }
\setcounter{subfigure}{-2}
\subfloat[Two girls (N=267)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[One boy and one girl (N=573)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{0}
\subfloat[Two boys (N=341)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with 8 or more years of education by quarter (3 month period). 
Predictions based on age 24 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_dropped_spell3_high_rural}
\end{figure}

\clearpage

\bibliographystyle{aer}
% \bibliography{econ}
% \bibliography{library}
\bibliography{collection}

\addcontentsline{toc}{section}{References}

\end{document}

### 2017-04-04 paper/sexSelectionSpacing-ver1.tex
Shorten the theory section to focus on spacing only

@@
 % Begun originally: 01/11/02
-% Begun.: 2016-05-12
-% Edited: 2016-11-07
+% Begun.: 2017-04-03
+% Edited: 2017-04-03
 
@@
 
-% \setcounter{page}{-1}
-% \maketitle
+\setcounter{page}{-1}
+\maketitle
+\thispagestyle{empty}
+
+% \setcounter{page}{0}
+\newpage
+
+\doublespacing
+% \onehalfspacing
+
 % \thispagestyle{empty}
-% 
-% % \setcounter{page}{0}
-% \newpage
-% 
-% \doublespacing
-% % \onehalfspacing
-% 
-% 
-% % \thispagestyle{empty}
 
@@
 \cite{jha06}, and \cite{abrevaya09}. 
-% Poor nutritional and health status of women may lead to 
-% relatively more girls being born, probably as an evolutionary
-% response to maximise reproductive success \citep{trivers73,wells00}.
-% Empirical evidence from Ethiopia and from cross-country data supports
-% this hypothesis \citep{klasen02,gibson03}.
-% % , although acute under-nutrition may not have this effect \citep{stein04}.
-% See also the discussion for India in \citet{bhaskar07}.
 }
@@
 
-\section{Theoretical Framework\label{sec:model}}
-
-[TK Calling this a model will be overkill - save the model for the fertility paper]
+The method can better predict ``final'' sex ratios than the simple model
+
+\section{The Interaction between Son Preference and Birth Spacing\label{sec:model}}
+
+The extension of birth spacing that result from abortions as described above is 
+only one part of the interaction between son preference and birth spacing.
+
+- the decision on sex selection and spacing
+    - the mechanical extension
+    - the possibility of changing use of sex selection
+
+- what other factors might change birth spacing?
+    - increased use of contraceptives
+    - changes in labor force participation
+
+\citep{Soest2012} for a recent example of spacing and son preference
 
@@
 
-The model I present here serves two purposes.
-First, the model informs the empirical strategy presented below.
-Second, I show that there are cases where parents reconsider their decision to 
+I show that there are cases where parents reconsider their decision to 
 use sex selection between births, which underscores why 
@@
 
-[move discussion of spacing from footnote above to here?]
-
-This is obviously a simplification and since the interaction
-between son preference and spacing is at the core of this paper,
-I first discuss factors that may affect spacing between birth.%
-\footnote{
-It is possible that parents care directly about the
-length of spacing between births, but 
-spacing outcomes are more likely the results of parents weighing many
-factors against each other.
-}
-
-One factor that might impact desired spacing is health.
 As discussed above, shorter spacing after the birth of a girl is 
@@
 
+[TK this needs to move to later]
 Finally, increased reliability of access and effectiveness of
@@
 
-% "Solving" the model
-
-Instead of trying to model each of the factors that may affect
-spacing I instead set up a dynamic model with a discount rate.
-Parents maximize utility over a finite time horizon $T$
-\begin{equation}
-\max E \sum_{t=0}^T d^t [ 
-u(c_t) + \alpha u^b(b_t) + (1-\alpha) u^g(g_t) 
-],
-\label{eq:utility_1}
-\end{equation}
-where $E$ is the expectation operator,
-$c_t$ consumption in period $t$, 
-$b_t$ the stock of boys in period $t$,
-$g_t$ the stock of girls in period $t$, and
-$d$ the discount rate.
-For ease of analysis I assume that utility in each period is separable in 
-parental consumption, boys, and girls.
-I define son preference, $\alpha$, as higher marginal utility of next child 
-being a boy if parents have an equal number, possibly zero, of boys and girls.
-The utility function covers a variety of different preferences 
-from equal utility of boys and girls ($\alpha = 0.5$ provided
-$u^b(\cdot) = u^g(\cdot)$) to an extreme 
-son preference where there is no utility of having a daughter 
-($\alpha = 1$).%
-\footnote{
-Other ways of defining son preference, such as wanting at least one son 
-and not caring about sex composition after that, are possible but 
-will be explored here.
-The basic results remain as long as there is different
-utility of sons and daughters for at least some sex compositions.
-}
-The lower $d$ is the more parents prefer immediate utility relative
-to future utility.
-Hence, the discount factor is a convenient way to capture how patient parents 
-are and therefore how willing parents are to wait through multiple abortions 
-to ensure a son.
-
-At the beginning of each period parents have 3 possible choices:
-no pregnancy, a pregnancy without a prenatal sex determination scan,
-or a pregnancy with a prenantal sex determination scan followed by an
-abortion if the fetus is female.
-The probability of conceiving a boy is $\pi$, which is
-the same for all parents and in all periods.
-There is no child mortality, so both
-$b$ and $g$ are non-decreasing over time.
-
-If a child is born parents incur a cost $p_k$ for
-that child in the period of birth and all subsequent periods
-until the end of the time horizon.%
-\footnote{
-Clearly boys and girls may carry different costs, but since 
-the model already assumes that
-parents have different preferences over boys and
-girls there is no reason to further complicate the model.
-Similarly, the cost of maintaining a child likely depend on 
-its age, but incorporating that would add little to 
-the conclusions.
-}
-If parents select a pregnancy with prenatal sex determination
-they pay $p_s$ and also $p_k$ if the fetus is a son
-and therefore carried to term.
-For two reasons the prenatal sex determination scan is best thought of as
-a bundled service that includes both the prenatal sex determination scan 
-\emph{and} the abortion if the fetus is female.
-First, it is more tractable than including additional steps in
-the decision process, especially since the only motivation for
-a prenatal scan in the model is sex selection, and a scan would
-therefore be ``wasted'' unless a female fetus was aborted.
-Second, I argue in the online Appendix that both parents and providers 
-may prefer a bundled service, where there is an upfront cost and the service 
-includes both the prenatal screening and the abortion---if needed---from the 
-same provider.
-The budget constraint for each period is then
-\begin{equation}
-I_t = c_t + p_k(b_t + g_t) + p_s s,
-\end{equation}
-where $I_t$ is income in period $t$
-and
-$s$ is an indicator variable for whether the 
-parents purchased prenatal sex determination.%
-\footnote{
-This assumes that there is no saving or borrowing
-across periods.
-This is a common assumption in this type of model.
-See, for example, 
-\citet{Heckman1976},
-\citet{wolpin84},
-\citet{rosenzweig85},
-\citet{Newman1988},
-and
-\citet{Leung1991}.
-That there are only two stock variables, the number
-of boys and the number of girls, greatly simplifies the analysis.
-}
-
-This maximization problem can be solved using dynamic programming, 
-but because the choice variable and the state variables (number of
-boys and girls) are discrete a closed-form solution
-is generally not available.
-% There are two discrete state variables (boys and girls) and one
-% choice variable with three potential choices (no pregnancy, pregnancy without prenatal sex 
-% determination, and pregnancy with prenatal sex determination).
-% Combined with the finite time horizon a problem of this type is especially suited for
-% simulation and the model is simulated using backward induction.
-This means that simulation is the best way to analyze the model,
-but before turning to simulations it is worthwhile illustrating
-how the model works.
-I begin with the possible utility outcomes in period $T$, the last period 
-in which parents make decisions on fertility.
-If parents decide on ``no pregnancy'' their utility in the final period will be
-\begin{equation}
-U_T^N =
-u(I - p_k(b_{T-1} + g_{T-1})) + \alpha u^b(b_{T-1}) + (1 - \alpha) u^g(g_{T-1}).
-\end{equation}
-If they instead decide to have a pregnancy without a prenatal scan 
-their expected utility will be 
-\begin{multline}
-U_T^B = 
-\pi [ 
-u(I - p_k(b_{T-1} + g_{T-1} + 1)) + \alpha u^b(b_{T-1}+1) + (1-\alpha) u^g(g_{T-1}) 
-]
-+\\
-(1-\pi) [ 
-u(I - p_k(b_{T-1} + g_{T-1} + 1)) + \alpha u^b(b_{T-1}) + (1-\alpha) u^g(g_{T-1}+1) 
-].
-\end{multline}
-Finally, if they decide to use prenatal sex determination their
-expected utility will be
-\begin{multline}
-U_T^S = 
-\pi [ 
-u(I - p_k(b_{T-1} + g_{T-1} + 1) - p_s) + \alpha u^b(b_{T-1}+1) + (1-\alpha) u^g(g_{T-1}) 
-]
-+ \\
-(1-\pi) [ 
-u(I - p_k(b_{T-1} + g_{T-1}) - p_s) + \alpha u^b(b_{T-1}) + (1-\alpha) u^g(g_{T-1}) 
-],
-\end{multline}
-since parents incur the cost of the scan, $p_s$, whether they conceive
-a male or a female fetus, but will not incur any additional childrearing costs
-if a girl is conceived.
-
 To illustrate how the decision process works, consider
@@
 \end{multline}
-% This can also be written as
-% \begin{multline} \label{eq:last_full}
-% (1-\pi)(1-\alpha) [ u^g(g_{T-1}+1) - u^g(g_{T-1}) ]
-% > \\
-% \pi [u(I - p_k(b_{T-1} + g_{T-1} + 1) - p_s) - u(I - p_k(b_{T-1} + g_{T-1}+1))] \\
-% + (1-\pi) [ u(I - p_k(b_{T-1} + g_{T-1}) - p_s) - u(I - p_k(b_{T-1} + g_{T-1}+1))].
-% \end{multline}
 Hence, parents choose a pregnancy without prenatal scan over
@@
 }
-% With some abuse of language I will call this difference the 
-% marginal utility of a child, in this case a girl.
 
@@
 
-Finally, increasing the cost of children, $p_k$---as would happen 
-with higher education of mothers---increases the likelihood that sex 
-selection will be used at a given number of children.%
-\footnote{
-Higher education likely also increases household income, which
-makes it \emph{less} likely parents will choose a birth with prenantal 
-scan over a birth without a prenatal scan.
-Higher income means lower marginal utility from consumption, which makes the 
-whole right-hand side move toward zero.
-For a given number of girls, this makes it more likely 
-that the utility from an additional girl is sufficiently high that parents 
-will simply have a birth.
-Empirically, increasing education of mothers is, however, strongly associated 
-with lower fertility, which indicates that 
-the negative effect of higher opportunity cost more than outweighing 
-the positive effect of higher income \citep{schultz97}.
-}
-There are two reasons for this.
-First,  when the cost per child goes up the given number of children 
-translates into less income per period available for consumption.
-Second, the decline in consumption from having an additional
-child becomes larger.
-These combine to increase the marginal utility of consumption and thereby 
-make it more attractive to have a prenatal scan.
-
-% % Theory on whether reversal of use
-% A question of interest is when parents would pick
-% a scan in one period and no scan in the following period.
-% For this to happen parents must choose scan, conceive a girl, and then
-% have a birth without a scan.
-% The available choices in the second to last period are the same as in the last
-% period: no birth, pregnancy without a scan, and a pregnancy with a scan.
-% Let $V_T(B)$ be the expected utility of the optimal choice in the last
-% period if the outcome of the choice in period $T-1$ is a boy.
-% Similarly, $V_T(G)$ and $V_T(N)$ are the expected utilities from
-% having a girl and no birth in period $T-1$.
-% In period $T-1$ parents will choose to have a pregnancy without a scan
-% over a pregnancy with a scan if
-% \begin{multline}
-% (1-\pi)(1-\alpha) [ u^g(g_{T-2}+1) - u^g(g_{T-2}) ] 
-% > \\
-% \pi u(I - p_k(b_{T-2} + g_{T-2} + 1) - p_s) \\
-% + (1-\pi) [ u(I - p_k(b_{T-2} + g_{T-2}) - p_s) + d( V_T(N)- V_T(G))] \\
-% - u(I - p_k(b_{T-2} + g_{T-2} + 1)).
-% \end{multline}
-% As before the left-hand side is the marginal utility of
-% an additional daughter, but the right-hand side now also 
-% incorporates the discounted value of the difference between expected utility 
-% in the last period if no children are born in $T-1$ and expected utility in 
-% the last period if a girl is born in $T-1$.
-% 
-% For parents to change their decision on abortion it must be
-% the case that the right-hand side for $T-1$ is larger than 
-% the left-hand side \emph{and} the left-hand side need to 
-% be larger than the right-hand side without the discounted value
-% of the difference in expected utility.
-% Note that the left-hand side remains the same because with
-% a scan no girls are born and the parents therefore enter the
-% last period with the same number of girls as they exited
-% period $T-2$.%
-% \footnote{
-% This would not be the case if utility was not separable between
-% boys and girls.
-% }
-% This, in turn, requires that $V_T(N) - V_T(G)$ is positive.
-% Identifying when this holds becomes complicated and the
-% level of complication increases as we move towards to the
-% beginning of the time horizon.
-
-% [Simulation of model]
-Although it is possible to examine how decisions are made in the last period,
-the absence of closed-form solutions means that I cannot directly 
-examine important questions such as whether parents will reverse their
-use of sex selection between births.
-I therefore now turn to simulation of the model for different parameters.
-Appendix Tables \ref{tab:simul_fertility_100}-\ref{tab:simul_fertility_85} 
-show the simulation results for average  fertility and the ratio of boys to births for 
-selected values of son preference ($\alpha$), cost of prenatal sex determination ($p_s$) 
-and cost of children ($k$).
-Appendix Tables \ref{tab:simul_abortion_100}-\ref{tab:simul_abortion_85}
-show the corresponding simulation results for number of abortions per 100 women, 
-average number of spells where prenatal scan has been used, 
-and the percent of spells where the choice is initially
-pregnancy \emph{with} a prenatal scan but the birth is from a pregnancy \emph{without}
-a prenatal scan.
-The latter captures the likelihood of changing the decision to use sex selection
-between births and I cover that separately below.
-Appendix Tables \ref{tab:simul_spacing_r100_a05}-\ref{tab:simul_spacing_r100_a065}
-show the average and maximum spacing between births by parity.
-
-The specification and parameter values are chosen to illustrate
-the effects of changing parameters, rather than to provide
-a realistic set of outcomes.
-The utility function used for the simulations is%
-\footnote{
-See \citet{leung94} for a discussion of potential utility
-functions with different preferences for sons and daughters.
-}
-\[
-U = 0.27\frac{(c-30)^{0.5}}{0.5} + \alpha \frac{b^{0.75}}{0.75} + (1-\alpha) \frac{g^{0.75}}{0.75}.
-\]
-The simulations presented in the tables assume 15 periods, a period income of 
-$I = 200$, and that the probability of a son is 0.5.
-The four parameters and their examined values are the cost of 
-children ($k \in 12, 14, 16, 18, 20, 22$), 
-cost of prenatal sex determination ($p \in 12, 16, 20, 24,  200$)---where 
-the last value is equivalent to no prenatal sex determination available,
-the degree of son preference ($\alpha \in 0.5, 0.55, 0.6, 0.65$),
-and the discount rate ($d \in 0.85, 0,9, 0.95, 1.0$).
-The optimal choice sets are applied to a sample of 50,000 ``individuals'', each 
-with 15 ``potential'' children, whose sex comes from a binomial distribution 
-with the probability above.%
-\footnote{
-I also ran simulations on an expanded set of parameter values.
-I use these results for regression analysis of the effect of parameters.
-These are available upon request.
-}
-
-% Access / cost of prenatal sex determination
-
 Lowering the cost of prenatal sex determination does, however, bias the overall sex 
@@
 in average spacing for a given parity---although with a more than compensating 
-increase in an earlier parity.%
-\footnote{
-One example is the second parity for $k= 22$ and $\alpha = 0.65$
-when cost of prenatal scan decreases from 24 to 20.
-The average spacing for the second parity falls from 1.5 to 1.25,
-but the average spacing for the first parity goes from 1 (no
-use of sex selection) to 1.5.
-Another example is for $\alpha = 0.5$ when cost of prenatal scan falls 
-from 20 to 16 when cost of children is 16. 
-The average spacing for parity 5 births falls from 1.44 to 1.18, but
-the spacing for parity 4 births increases only from 1 to 1.09. 
-What this hides is, of course, that there are substantially more 
-parity 4 births than there are parity 5 births--and only a slight 
-decline in fertility from 4.16 to 4.11---and that the number of
-abortions per 100 woman doubles. 
-}
+increase in an earlier parity.
 Hence, it is possible for individual parities to show a \emph{decline}
@@
 go up because lower cost of prenatal sex determination also
-increases the use of sex selection.%
-\footnote{
-An example of this is when the discount rate is 0.95, cost of
-children 14, cost preference of 0.6, and the cost of a prenatal scan falls 
-from 16 to 12, resulting in a decline in the probability of changing 
-from 38.1\% to 30.9\%.
-In this case the average number of spells with a change increases
-from 0.19 spells at the higher cost of prenatal scan 
-to 0.37 for the lower cost.
-}
+increases the use of sex selection.
 
@@
 
-Increasing the cost of children and the degree of son preference
-both tend to lower the likelihood that parents will change their
-decision to use sex selection.
-Working in the opposite direction is that some women with higher cost
-of children, for example because of higher education, are also likely 
-to marry later.
-The later marriage effectively shortens their reproductive time horizon
-and thereby makes it more likely that they will reverse their use of 
-sex selection between births.
-% Again, the caveat is that extensive use of sex selection
-% can lead parents close to the end of the time horizon, at which
-% point they may change their decision.
-
-% Hence, this shows that parents may reverse the use of sex selection, 
-% both when they use sex selection relatively infrequently and when they 
-% use it heavily.
-
-% Furthermore, the reversal of use of sex selection is 
-% often followed by a spell where sex selection is used again,
-% especially in the case when a girl is born.
-
 % What are the model highlights 
@@
 the results may look different.
-% As shown it still is possible, however, to get sex selection
-% for balance and for parents to change their decision on use
-% of sex selection between births.
 }
@@
 the more likely they are to reverse their decision to use sex selection.
-% Furthermore, as the simulations show it is possible for son 
-% preference to decline while the sex ratios becoming more unequal 
-% provided the cost of prenatal scan decreases and/or cost of children 
-% increases sufficiently (or people become more patient).
 Finally, the model shows that son preference in the number of
@@
 longer average time to next birth, 
-and that the use of prenatal sex determination may change between one observed birth and 
-the next.
+and that the use of prenatal sex determination may change between one observed 
+birth and the next.
 All three must be incorporated into the estimation strategy
 to provide unbiased and precise estimates of the use of sex-selective abortions.%
-\footnote{
-For comparison the online Appendix presents the estimation strategy 
-for the simple model.
-The online Appendix also shows how individual parity results compare 
-between the simple model and the model suggested here.
-As mentioned, the simple model cannot provide complete fertility 
-and total number of abortions predictions.
-}
 
@@
 \footnote{
-\cite{merli00} used a discrete hazard model to examine whether 
+\cite{Merli2000} used a discrete hazard model to examine whether 
 there were under-reporting of births in rural China, although they 
@@
 \footnote{
-% [problem with IIA assumption (independence of irrelevant alternatives]
 A potentially issue is that the multinomial model assumes that alternative 
@@
 also known as the Independence of Irrelevant Alternatives (IIA) assumption.
-% Even though boys and girls are not perfect substitutes they are 
-% very similar and this may present a problem for the IIA assumption.
 This assumption rules out any individual-specific unmeasured or 
@@
 hazard of having a boy.
-% In other words, the assumption requires that the hazard of having a boy 
-% relative to not having a child is uncorrelated with the corresponding
-% hazard of having a girl relative to not having a child.
-% An important unobservable factor is fecundity.
-% Assume that a couple has low fecundity.
-% Even with a strong son preference, low fecundity  makes the couple less 
-% likely to engage in sex-selective abortions because they will have
-% difficulty conceiving again and having a girl might be preferable to having
-% no children.
-% This is exacerbated by the potential for a further lowering of fecundity
-% as a direct result of using abortions.
-% Fecundity therefore affect both the hazards of having children and the
-% relative likelihood of having a boy versus a girl.
 To address this issue the estimations include a proxy for fecundity
@@
 available upon request.
-% Finally, what is of interest here is the relationship between the covariates 
-% and the rate of occurrence of the different exit types rather than the interrelation between the failure
-% types or what would happen if one of the exit types were removed
-% making the independence assumption less problematic.%
-% \footnote{
-% As shown by \citet{kalbfleisch02} data with spell length, exit states and
-% fixed covariates does not allow one to distinguish between an independent 
-% competing risk model and an infinitude of dependent models that lead to the
-% same type-specific hazards.
-% }
 }
@@
 Appendix.
-% This is based on Table 1, p 212, and is only for births that took place in 1997.
-% Part of problem is the sex ratio on first birth
 }
@@
 \end{figure}
-
-% \begin{figure}[htp]%
-% \centering
-% \includegraphics[width=0.4\textwidth]{sex_ratio_marriage}
-% \caption{Ratio of boys in ``first'' births
-% \label{fig:sex_ratio_recall}}
-% \end{figure}
 
@@
 The remaining variables are expected to affect hazards proportionally.
-% Age of the mother is captured by her age in years at the beginning of
-% a the spell.
-% On one hand, an older woman might be less able to conceive and therefore less
-% likely to use sex-selective abortions.
-% On the other hand, for a given spell, a higher age might also be associated 
-% with more education or previous longer spells because of the use of sex selection.
-% The correlation between age and education is a potential downside to using
-% the three categories of education, but this is outweighed by the fact
-% that fewer assumptions are imposed on the baseline hazards.
 Although fecundity cannot be observed directly a suitable
@@
 of a scheduled caste or tribe.
-% All are assumed to affect the hazards proportionally.
-% The first round of the NFHS asked only about membership of either 
-% a scheduled caste or tribe but the later rounds also asked
-% about membership of other backward castes.
-% To ensure consistency the only two variables used are dummies for whether
-% a woman belongs to a scheduled caste or a scheduled tribe, respectively.
-% Unfortunately, there is no information on belonging to a higher caste, although
-% higher education is often related to higher status.
 
@@
 Generally, censoring increases with parity and time period.
-% %
-% \footnote{
-% The exception is for women without education where twelve percent of
-% the women who married in the 1972 to 1984 period did not have a first
-% birth at the time of the survey.
-% }
 This reflects a combination of factors: timing of the surveys
@@
 
-% [NEW OUTLINE]
-% - Desired fertility analysis
-% - changes over time for well-educated women (spell 2 and 3)
-% - comparison across groups (no, some, high education, for spells 1, 2, and 3)
-
-% - 1st spell for all individuals (compare with other research)
-% - High education group for spell 2 and above
-% - Medium education group for spell 2 and above
-% - Low education group for spell 2 and above
-% - Predicted changes in fertility and number of abortion and comparison with standard model
-
 One of the main questions here is how fertility affects sex selection use.
@@
 learn about son preference from the sex selection behavior.
-% [Then I compare my suggested model with the simple model previously used.]
 Finally, I predict lifetime fertility, number of abortions, and final sex ratios for
@@
 
-% % [Seems to be a repeat of what is in estimation strategy]
-% The survival curves show the estimated probability of not having had a birth
-% yet by length of the spell.
-% The survival curves are included for two reasons.
-% First, they show the progression to the next birth by quarter and how quickly it occurs,
-% if at all.
-% Second, they provide ``weighting'' for the associated percentage boys born.
-% The steeper the survival curve, the more weight a given spell period has because it is 
-% based on more births, whereas a flat survival curve means little weight because the 
-% percentage boys is based on few births.
-
 \subsection{Comparing the Hazard and Simple Models}
@@
 change their use of sex selection within a spell.
-% This is possible because the hazard model approach uses both censored and 
-% uncensored observations, which, in turn, allows me to predict both how many 
-% women will have a next birth and the final sex ratio for that parity, under the 
-% assumption that the patterns of spacing and use of sex selection remain 
-% the same within a spell.
 We can, however, still compare differences in predicted sex ratios for 
@@
 examining sex selection \citep[see, for example, ][]{retherford03b,jha06,abrevaya09}.
-
-% Two factors determine the differences in the predicted sex ratio and number 
-% of abortions between the two models.
-% First, how many women have censored spells but will have a birth after the survey.
-% Second, how much use of sex selection changes within a spell.
-% % If there are few censored spells or the women with the censored spells have low likelihoods
-% % of having a next birth the two models produce similar predicted sex ratios and 
-% % number of abortions.
-% % If there is little change in the use of sex-selective abortions over a spell then the
-% % predicted sex ratio is going to be similar for the two models, although the predicted
-% % number of abortions will differ depending on how many censored observations there are
-% % and how likely they are to exit with a birth.
-% Consider four possible combinations of the two factors.
-% First, there are few censored birth spells and use of sex selection is constant over
-% the spell.
-% In that case, the predictions will be similar across the two models.
-% Second, there are many censored birth spells and use of sex selection is constant over
-% the spell.
-% The predicted sex ratios will be similar, but the simple model will predict a too low
-% number of abortions per woman and fertility will appear to be falling faster than it is.
-% Third, there are few censored birth spells and use of sex selection changes substantially
-% with spell length.
-% The sex ratios again are close to each other in the two models, but the estimated use of
-% abortions will be biased in the simple model because it cannot account for the changes
-% in use of sex selection over the spell.
-% Finally, there are many censored birth spells and use of sex selection changes substantially
-% with spell length.
-% In this case the predicted sex ratio based on the simple model will be biased.
-% Specifically, if use of sex selection declines over the spell, the simple model 
-% will predict a higher final sex ratio than the hazard model.
-% Similarly, the predicted number of abortions will also be biased. 
-% With sex selection and falling fertility censored spells become more and more likely,
-% but how much this matter is an empirical question.
-
-% To determine the predicted number of abortions I use the natural sex ratio.
-% On average, 105 boys should be born per 100 girls born, which corresponds exactly
-% with what we observe for first births in India as seen above.
-% Hence, if we observe $b$ boys, then we should expect to see $b\frac{100}{105}$ girls.
-% If we observe $g$ girls the number of abortions is therefore $b\frac{100}{105}-g$.
-% The standard approach is to use the observed sex ratio for a given parity and 
-% calculate the number of abortions using this formula.
-% For the hazard model it is, however, possible to calculate the number of predicted
-% abortions for each time period based on the predicted sex ratio and the 
-% number of women predicted to exit with a birth in that period using the same formula.
-% Summing across the entire period covered by the hazard model provides a predicted total 
-% number of abortions.%
-% \footnote{
-% There is no difference between the two method in the predicted number of abortions for 
-% those women for whom we observe the subsequent birth.
-% }
-
-% [NEED TO WORK THROUGH A MATH EXAMPLE OF THE FIRST FACTOR: IS THAT REALLY CORRECT?]
-% period 0: 100 births 65 boys 35 girls 26.90476191
-% period 1: 100 births 60 boys 40 girls 17.14285714
-% period 2: 100 births 55 boys 45 girls 7.380952381
-%                     180 boys 120 girls abortions: 51.42857143
-% 
-% period 0: 1000 women: 512 boys 400 girls , 88 abortions  87.61904762
-% period 1:   98 women: 50 boys 42 girls, 6 Abortions  5.619047619
-% period 1:    6 women: 3.073 boys 2.927 girls 0 abortions -0.000333333
-%                     562 boys 442 girls    93.23809524 93.2377619 93.23776191
-% 
-% [HOW TO CALCULATE NUMBER OF ABORTIONS HERE]
-%
-% In addition, the standard model does not provide any information about abortions
-% for those women for whom we do not observe a birth.
-% In contrast, the hazard model can be used to predict the number of abortions even for 
-% those women who have not yet had a birth at the parity of interest.
-% This number is the sum of two set of predictions.
-% First, the number of abortions that are predicted have occurred up to the time of the 
-% survey for women without a given parity birth.
-% Second, we can predict how many additional abortions will take in the future for these
-% women from the time of censoring until the end of the spell period used for the hazard
-% model.
-% This follows directly from the standard feature of hazard models where one can predict
-% the likelihood of future exits for those censored.
-% To the extent that people change their use of sex-selective abortions within a spell
-% the two numbers will be different.
-%
-% [TRYING TO WORK THROUGH THE SET-UP HERE]
-% 
-% For each women who had one birth we follow her until 24 quarters (6 years) after the 
-% birth of her first child. 
-% Contrary to the standard logit model we can predict two things: How likely it is that she
-% will have her second child during a particular quarter and what the sex ratio will be in 
-% that quarter.
-% In other words, by the end of the 24 quarter period we will know the probability of her
-% having had a child, which is what is shown by the survival curves in the graphs above,
-% and expected sex ratio for all women like her.
-% So, one women might have 73 percent probability of giving birth to a second child within
-% the 24 quarters with 58.3 percent probability of a boy and a 41.7 percent probability
-% of a girl, whereas another might only have a 29 percent probability of giving birth to a 
-% second child with a 55.4 percent probability of a son and a 44.6 percent probability of a
-% girl.
-% 
-% Summing across all women with specific characteristics, like being an urban woman with
-% a girl as her first child, we can then predict how many children will be born to these
-% women in the 6 years after the birth of their first child, together with information on
-% how many abortions will have taken place and the final sex ratio for those second-born
-% children.
-% 
-% The advantage of this is that it is not reliant just on observed births.
-% To the extent that the probability of using sex-selective abortions changes with time since
-% the last birth the results from the hazard model prediction will be different from the
-% Logit model prediction (which is just the sex ratio for birth observed in the 6 year 
-% period).
-% Furthermore, even if the probability of sex-selective abortions does not change substantially 
-% with duration since last birth, the hazard model provides an estimate of how many births
-% there will be and what the final sex ratio for a given parity birth will be.
-% The more censored observations there are the bigger the difference between the logit and
-% the hazard models are going to be.
-% This is important because that those numbers are an input into determining what the
-% population sex ratio will be.
-
-% [is there a way of understanding the difference between censored and uncensored women
-% using the hazard model?
-% One option would be to run everybody until they are censored and see if that fits with
-% the logit numbers.
-% that should presumably match the logit results except for picking up differences in use
-% of sex-selective abortions. 
-% This means that the births should be the same for the two methods.
-% 
-% For those censored we could then run the rest of the time. 
-% This would require that we started from one woman again, instead of continuing from the
-% censoring left off.
 
@@
 
-%
-% We begin with women who had a girl as their first child.
-% Table \ref{tab:compare2} shows the number of women who enter the second spell,
-% the number of births by the end of the six year period following the first birth,  
-% observed in the case of the logit model and predicted in the case of the hazard model, 
-% predicted number of abortions, and the sex ratio.%
-% \footnote{
-% The two latter obviously captures the same information and is both presented for
-% the reader's convenience.
-% }
-
 For the 1985--1994 period---which is when sex selection become available---the 
@@
 
-% [CLOSING ARGUMENTS ON COMPARISON?]
-% [logit will tend to underestimate when sex-selective abortions is spreading/increasing
-% and overestimate when sex-selective abortions is declining.]
-
-% Urban
-% 0.566585492 hazard sex ratio for 1985
-% 0.592900726 hazard sex ratio for 1995
-% 
-% 0.554402294 logit sex ratio for 1985
-% 0.593989533 logit sex ratio for 1995
-% 
-% Rural
-% 0.544119243 hazard sex ratio for 1985
-% 0.579341591 hazard sex ratio for 1995
-% 
-% 0.530621491 logit sex ratio for 1985
-% 0.573022963 logit sex ratio for 1995
-
-% I begin with women who had a girl as their first child.
-% For rural women in the 1985--1994 period relatively few censored women are
-% predicted to go on to have a second birth (only 5 percent of the starting population
-% is predicted to have a second birth and have not yet had one).
-% In addition, there is only some evidence of sex-selective abortions.
-% Hence, the predicted sex ratios for the simple and hazard models are close. 
-% There are slightly more abortions for the hazard model, but the abortion rates (number
-% of abortions per birth) are fairly similar between the observed births and those predicted
-% to have a birth later.
-% 
-% Urban women in the same time period follow a similar pattern with relatively few 
-% censored women predicted to move on to a second birth (around 2 percent of starting 
-% population), but the abortion rate for those additional births is 8.1 abortions per 100 
-% births, whereas it is only 6.7 for the observed births, as we would expect from the 
-% increasing probability of having a son with increasing spell length seen in panel (b) in 
-% Figure \ref{fig:results_spell2_high_urban}.
-% Despite this the resulting difference in sex ratios is
-% relatively small because of the small number of censored women predicted to exit with a
-% birth.
-% 
-% 
-% Not surprisingly there are substantially more censored observations for the 1995--2006
-% period.
-% For urban women about 19 percent of the starting population are predicted to have a
-% second birth but have not yet had one and for rural women it is 23 percent.
-% This allows for potentially larger differences in predicted sex ratios and number of
-% abortions.
-% Despite the large number of censored observations for rural women there is relatively
-% little difference in the predicted sex ratio.
-% The more interesting difference is for urban women in the 1995--2006 period.
-% The hazard model predicts 100 more abortions by the end of the spell, but the simple 
-% model \emph{overestimates} the final sex ratio.
-% The simple model predicts 143.5 boys and the hazard model 141.3 boys per 100 girls.
-% This is consistent with the very high probability of having a son early on in the spell
-% followed by a somewhat lower probability for later births seen in panel (c) in 
-% Figure \ref{fig:results_spell2_high_urban}.
-% 
-% 
-% 
-% The lower two panels of Table \ref{tab:compare2} presents the predicted outcomes for urban
-% and rural women for the third spell, split by the sex composition of their first two 
-% children and when the spell began.%
-% \footnote{
-% There is no evidence of sex-selective abortions and very few births for women with two boys 
-% and those predictions are therefore not presented.
-% }
-% For urban women with two girls in the 1985--1994 period there are only 77 more births for 
-% the hazard model, but the difference in number of abortions is 15 with the hazard model 
-% predicting 266 abortions and the simple model 251.
-% The resulting sex ratio is 175.3 for the hazard model versus ``only'' 170.0 for
-% the simple model.
-% In other words, it appears that the simple model underestimates the spread of the use of
-% sex-selective abortions during the expansion of access to prenatal sex determination 
-% for this group of urban women.
-% As discussed in the paper, use of sex selection for urban women with two girls appears to  
-% have fallen from the 1985--1994 period to the 1995--2006 period, but this is mainly an 
-% indication that sex-selective abortions are being used more during the spell to second 
-% birth for this group of women for the 1995--2006 period.
-% The result is fewer women with two girls for their first two births and those who do are 
-% substantially less likely to have a third birth than they were before.
-% 
-% For rural women the main difference between the two models is for those with one boy
-% and one girl in the 1995--2006 period.
-% Only about 60\% of the birth predicted by the hazard model are observed in the simple
-% model, leading to substantial censoring.
-% Furthermore, use of sex-selective abortions is predicted to be substantial for those
-% remaining births resulting in a sex ratio of 129.8 for the hazard model and 124.6 for
-% the simple model. 
-% As discussed in the paper, this case is the exception to the rule that sex selection
-% does not appear to be used by families that already have one son.
-% Presumably the use by rural women in this case is an insurance against mortality.
-
 \subsection{One Son or Many Sons?}
@@
 is taking place.
-% As discussed above the likelihood of having a second birth if your first child is a son
-% is higher in rural than in urban areas, but even for urban women 65\% do have a second
-% child by the end of the second spell period.
 There is also no evidence of sex selection for the third spell for women with two sons;
@@
 
-% Despite the larger sample size than for two sons, the results are based on only 
-% approximately 700 births.
-% urban: Based on about 700 births
-% The first flat part is about 10\% of women 
-% The dip below natural sex ratio accounts for close to 10\% of women
-% The high part from 11 quarter onward account for the last 10\% of women
-% That means that the dip and the high part approximately cancel each other out.
-
 For rural women, however, the dip and the associated number of births is not
@@
 essentially as an insurance.
-%  much as royal British families have been know to aim 
-% for an heir and a spare.
 Separating these two possible explanations is difficult, but the ``heir and a spare''
@@
 \citep{lancaster02,Ding2009,Wei2009,Edlund2013}.
-% In other words, this tells us both how much sex selection is used and what the final 
-% outcome will be.
-% [Final outcome is what matter for things like access to a spouse and associated 
-% problems - crime, etc]
 Finally, as I show in the online Appendix and discuss above, relying only on observed 
@@
 their use of sex selection during a spell.
-
-% 1. it tells us what fertility and the final sex ratio will be, which helps put the individual
-% spells and sex compositions in perspective.
-% 
-% 2. presumably what we care about is what the end result will be.
-% 
-% 3. Makes it easier to see whether use of sex selection is intensifying or easing over
-% time.
-% 
-% 4. "What actually happens" is based on a select sample. Maybe refer to the appendix
-% on comparing the simple and the hazard models here.
 
@@
 $0.0321 \times 65.88 = 2.11$ abortions must have taken place to reach these births.
-% From anSimulate_test for spell 4, line 44
-% If only given a percent and to find the number of abortions the formula is
-% abortions = (10,000-205*percent girls)/105.
-% This is because one less abortion would add an additional birth so that
-% (number of girls + abortions)/(100 + abortions) = 100 / 205
 }
@@
 rate) values of the abortion calculation within the spell.
-% This sum is the predicted probability of having an abortion for a woman with the given
-% set of characteristics.
 Finally, the percentage of children born that are boys is based on the randomization of
@@
 and the number of abortions per 100 births have gone up by over 35 percent (3.4 to 4.6).
-% The reason the percentage change per birth is higher than per women is the
-% combination of falling fertility and more intense use of sex selection.
 For rural women, abortions per 100 women increased almost 55 percent (6.8 to 10.5), 
@@
 
-% how many even make it to spell 4? 39 percent for 1st period for urban. only 26 percent 
-% for second period (and more likely to have a boy by then).
-% compare to rural: 62 percent first period, 50 percent second period.
-
 Another way to see the spread of access to sex selection over time is to compare
@@
 per woman were twice as high.
-% For rural women, however, the overall sex ratio is the same as the natural for the
-% first period and predicted completed fertility is 3.2, which is likely a lower-bound
-% estimate since the estimates did not incorporate parities higher than 4.
-% In the last period, rural women have higher fertility than urban women and therefore need 
-% fewer sex-selective abortions to ensure a son, but given differences in fertility
-% the numbers of abortions for rural women are not far behind those of urban women.
 
@@
 size for this education group it is unclear whether this simply reflects random variation.
-
-% [women in no education group:
-% I: 30,004 (25,486 rural)
-% II: 27,669 (23,360 rural)
-% III: 9,684 (7,922 rural)
-% 
-% check how many women in urban vs rural sample for 1-7 years of education group: 
-% I: 11,162 (7,496 rural)
-% II: 13,104 (9,000 rural)
-% III: 7,510 (5,208 rural)
-% ]
 
@@
 
-% \subsection{Regional Results}
-% 
-%      2 "Andhra Pradesh"
-%      3 "Assam"  
-%      4 "Bihar"
-%      5 "Goa"
-%      6 "Gujarat"
-%      7 "Haryana"
-%      8 "Himachal Pradesh"
-%      9 "Jammu"
-%     10 "Karnataka"
-%     11 "Kerala"
-%     12 "Madhya Pradesh"
-%     13 "Maharashtra"
-%     14 "Manipur"
-%     15 "Meghalaya"
-%     16 "Mizoram"
-%     17 "Nagaland"
-%     18 "Orissa"
-%     19 "Punjab"
-%     20 "Rajasthan"
-%     21 "Sikkim"
-%     22 "Tamil Nadu"
-%     23 "West Bengal"
-%     24 "Uttar Pradesh"
-%     30 "New Delhi"
-%     34 "ArunachalPradesh"
-%     35 "Tripura"
-% 
-% egen north = eqany(state), v(7 8 9 19 20 30)
-% egen central = eqany(state), v(12 24 4)
-% egen west = eqany(state), v(5 6 13)
-% egen east = eqany(state), v(18 23 3 14 15 16 17 21 34 35)
-% egen south = eqany(state), v(2 10 11 22)
-%
-
 \section{Conclusion\label{sec:conclusion}}
-
-% 1. how to interpret stated son preference from survey data and especially whether son
-% preference is declining over time.
-% 
-% In NFHS, and DHSs in general, son preference is measured as part of the general fertility
-% questions, where the first question is how many children a woman would have if she
-% could choose exactly how many to have.
-% This if followed by the sex preference question:
-% ``How many of these children would you like to be boys, how many would you like to be girls 
-% and for how many would the sex not matter?''
-% The problem here is that if parents want one son, but will do pretty much anything to get
-% that son, this will not be captured by this question.
-% In that case, any changes over time in the answers to this question will only reflect 
-% a true change in son preference if the respondents answer something less than 1 for boys
-% and allocate all to ``either''.
-
-% 2. it affects how we think about future developments in sex ratios and use of 
-% sex selection as fertility falls further.
-% 
-% This is of more than theoretical interest.
-% If son preference is expressed as a very strong preference for having at least one
-% son then any further reductions in fertility will lead to a further increase in the use 
-% of sex selection.
-% This matter not only for well-educated rural women, who have higher fertility than 
-% urban women, but are catching up quickly.
-% The main concern is what happens when fertility fall below 4 for women with little or
-% no education. 
-% So far, there is little evidence for sex selection for these groups, but if they hold
-% similar preferences to the better-educated women and experience a reduction in 
-% desired fertility it is more than likely that they will begin using sex selection on 
-% a large scale.
-
-% 3. it is important when trying to understand what is behind son preference.
-% If it is only one boy the argument on dowry does not seem to make much sense.
-% Especially since sex-selective abortions are concentrated among the wealthy households.
-% 
-% An oft-repeated, but poorly substantiated, argument for why there is son preference and 
-% especially sex selection in India is the presence of dowry practices, where the bride's 
-% family pays the groom and/or the groom's family for taking their daughter in marriage.
-% This explanation, however, fits poorly with the observed behavior.
-% Sex selection is predominantly used by wealthier households and if only used to secure
-% one son there is little support for the dowry explanation.
-% If dowries were the main driver behind sex selection we would rather expect poorer
-% households to use sex selection and use it to achieve a higher number of sons than
-% daughters.
-% For example, a family with 1 son and 2 daughters should use sex selection on the next
-% birth to at least ensure a break-even in terms of dowry payments and receipts.
-% Similarly, we would expect at least some families to use sex selection to ensure that
-% they come out ahead as a family in terms of how much dowry they receive compared to
-% how much is being paid out.
-% 
-% This is important because banning dowries should have little influence on the use of
-% sex selection if sex selection is only used to ensure one son.
-
-% \citet{clark00} p. 100 uses the number of sons, daughters, either question in her paper
-% as a dependent variable.
-% 
-% \citet{Jensen2009} QJE paper uses a question about the sex of the next child (if want
-% more children)
-% 
-% \citet{Hu2015} uses ratio of ideal number of son to ideal number of daughters
-
-% May make sense to change son preference question to be minimum number instead of ideal 
-% number: What is the minimum number of sons you would like? What is the minimum number of 
-% daughters you would like?
-% 
-% Might be a paper in this somewhere about changes in fertility and what exactly we can
-% learn from these son preference question.
-% Clark does argue that her calculated measure is a minimum proportion of sons 
-% desired, but, of course, this is neither here nor there if there is an absolute
-% minimum number of sons desired.
-%
-
-% [future research - importance]
-% girls may now have a much longer space before their next sibling
-% 
-% fertility will look lower because of increased spacing
-% 
-% potentially better health for those girls that are followed by sex-selective abortions
-% because of the longer space (although these are also generally born into the 
-% wealthier families)
-% 
-% who the agents are
-% 
-% \cite{das_gupta09a}
-% 
-% \cite{Klasen02}
-
-% [Hence, the decline in fertility is an indicator that girls are not relatively more
-% expensive than boys.
-% 
-% only one boys also suggests that use of sex selection is not roted in the cost
-% of girls (dowries).]
-% 
-% 
-% [original from here]
-% [EXPAND ON MODEL AND ITS IMPORTANCE - MORE ON PROBLEMS WITH LOGIT AND NOT USING ALL INFORMATION 
-% SEE RETHERFORD AND ROY PAPER]
 
@@
 \footnote{
-% This trade-off is also evident within spells.
 A feature of the new approach is that it allows for changes in the decision 
@@
 for whom the use of sex selection declines as the second spell becomes longer.
-% The result is that the simple model predicts a substantially higher percentage of boys
-% born than the hazard model, because the standard model cannot take into account
-% censoring and changes within spells.
-% The simple model also failed to fully captured the increased access to prenatal 
-% sex determination for urban women and therefore underestimated the final sex ratio for
-% third children in the period before the PNDT Act was passed.
 }
@@
 and our standard measure of son preference cannot captured that.
-% In fact, any changes over time in the answers to this question may only reflect 
-% a true change in son preference as it relates to sex selection if the respondents answer 
-% something less than 1 for boys and allocate all to ``either''.
 A better approach may be to directly ask if there is a minimum number of each sex that 
@@
 
-% The findings also have implications for our understanding of the relation between
-% the marriage market and sex selection.
-
 An often-repeated, but poorly substantiated, argument for why there is sex selection 
@@
 selection.
-% Recent data with information on both birth histories and average dowries within 
-% areas allow for a direct test of this relationship, making this a worthwhile area for 
-% future research.
 
@@
 first step to disentangling who makes decisions about sex selection.
-
-% The implication is that the decision to use sex selection rest with the woman given the 
-% other constraints she faces, such as potentially a strong preference for a son in 
-% the rest of the family.
-
-% [METHOD CAN BE USED TO ESTIMATE EFFECT OF SSA ON CHILD OUTCOMES: 
-% PREDICT PROBABILITY THAT SSA HAS BEEN USED AND USE THIS PROBABILITY AS
-% AN EXPLANATORY VARIABLE IN CHILD OUTCOMES.
-% SINCE SSA MAINLY USED BY HIGHLY EDUCATED WOMEN WHO ARE ALSO LESS LIKELY
-% TO SUFFER CHILD MORTALITY THIS EFFECT IS LIKELY TO BE SMALL BUT WOULD BE
-% INTERESTING TO SHOW.
-% CAN ALSO BE EXTENDED SO THAT THE PREDICTED USED OF SSA IN AN AREA AMONG
-% THE well-educated CAN BE USED TO EXPLAIN CHILD OUTCOMES FOR OTHER GROUPS.]
 
@@
 but there might be effects on education investments.
-% The method can, however, also be extended to other outcomes, such as education,
-% or the use of sex selection can be predicted for a geographical area and the 
-% predicted use for the area can then be used as an explanatory variable.
 
@@
 
-% why interesting/important:
-% - prediction about future development
-% - effect of unequal sex ratio on individual child (survival, education, marriage)
-% - effect of unequal sex ratio on society
-% - morbidity/mortality from abortions
-% - secondary sterility, abandonment, remarriage
-
-% [to be added]
-% In summary, the purpose of this project is to develop an empirical 
-% method that can contribute to an understanding of the changing sex ratio at birth in India.
-% Beside being of intrinsic interest, this first step is likely to have a 
-% significant impact on future analyses in areas such as child health and
-% mortality, maternal mortality, female abandonment and changes in the marriage markets.
-% These are important areas for future research.
-
-% [MOVE TO CONCLUSION?]
-% A second issue is that the model estimates the progression from one birth to
-% the next and not the complete fertility path.
-% This ignores any potential sample selection problems that might
-% arise from not all women making it to a given parity.
-% With the exception of the first spell, a woman must have had enough children 
-% to be observed in a particular spell.
-% Women with long previous spells, possibly because of sex selection,
-% are therefore less likely to be observed.
-% One possible solution is to model the selection problem directly,
-% for example, by ``weighting'' observations by the inverse of the 
-% probability that the observation is observed.
-% This is an important area for future research.
-
-% Although solid data are generally not available the effects of abortions are 
-% likely to be worse in developing countries than developed countries, especially if 
-% the abortions are preformed outside the regular health care system or in the second trimester.
-% Both are a significant concern in this case.
-% Since sex-selective abortions are illegal it is entirely possible 
-% that many of the abortions take place illegally.
-% Furthermore, the use of ultrasound and amniocentesis means that the abortion
-% will not take place until the second trimester.
-% Understanding the impact of sex-selective abortions on the mother's health, subsequent
-% fecundity and pregnancy outcomes are important areas for future research both in
-% their own right and because of their impact on economic development.
-% All of these will have adverse effects on children, their health and their human
-% capital accumulation.
-% This may, for example, happen when women die or are abandoned as a result of
-% infertility.
-
-% Problem  for understanding mortality as well.
-% Selection problem will also affect analysis of mortality.
-% For those with stronger son preference we are less likely to observe their
-% children and those children born will be younger
-% and hence it is less likely that those children will die.
-% Same ideas as Pitt's articles on fertility selection for understanding mortality \citep{pitt97}.
-% This problem becomes more important the closer to the survey date one gets.
-% Hence, if ones want to examine a relatively recent change in policy this
-% is especially important.
-% This is even more so if the policy is prompted by increased use of sex-selective
-% abortions as is likely in India.
-% In other words, if the policy is implemented because sex-selective abortion is
-% a problem (or an increasing problem) the policy can appear effective even though
-% what is really happening is that we are not controlling for the fertility selection /
-% sample selection that comes from use of SSA.
-% Those with stronger son preference probably also have higher mortality of girls
-% relative to those with lower son preference.
-% reference to \citet{rosenblum09} paper on mortality that do not take account of
-% this problem and \citet{das_gupta09a}.
-% Also look for \citet{klasen02} to see what they do.
-% Also, a problem for looking at macro level sex ratios (same Das Gupta et al. paper)
-
 \newpage
 \onehalfspacing
-% \bibliographystyle{aea}
 \bibliographystyle{aer}
-% \bibliography{econ}
-% \bibliography{library}
 \bibliography{collection}

### 2017-04-05 paper/sexSelectionSpacing-ver1.tex
Added condensed discussion of why reversal of sex selection

@@
 
+\citep{Soest2012} for a recent example of spacing and son preference
+
 \section{The Interaction between Son Preference and Birth Spacing\label{sec:model}}
 
-The extension of birth spacing that result from abortions as described above is 
-only one part of the interaction between son preference and birth spacing.
-
-- the decision on sex selection and spacing
-    - the mechanical extension
-    - the possibility of changing use of sex selection
-
-- what other factors might change birth spacing?
-    - increased use of contraceptives
-    - changes in labor force participation
-
-\citep{Soest2012} for a recent example of spacing and son preference
-
-[TK find examples of the son preference spacing papers and look at what they did
-for "theory"]
-
-I show that there are cases where parents reconsider their decision to 
-use sex selection between births, which underscores why 
-using only observed births may provide a biased view of how much
-sex selection takes place and what the final sex ratio will be.
-
-As discussed above, shorter spacing after the birth of a girl is 
-associated with worse health outcomes for both mother and children.%
-\footnote{
-\citet{wolpin84} and \citet{Newman1988} present dynamic models 
-where both births and deaths are stochastic, but the likelihood of
-a child dying is independent of the length of spacing to
-the prior birth.
-}
+In the absence of prenatal sex determination, parents' only choice if they 
+wanted a son was to try for another pregnancy as soon as possible after
+the birth of a girl. 
+This led to shorter spacing after the birth of a girl and what
+is known as differential stopping behavior, where parents were 
+more likely to cease child bearing after the birth of a son than
+after a daughter [TK add references here]. 
+As discussed above, the shorter spacing after the birth of a girl is 
+associated with worse health outcomes for both mother and children.
 Because of the potential health effects, most of the literature on spacing 
-for countries like India naturally focus on whether spacing is too short.
-
-With the introduction of sex-selective abortions, ``too long'' spacing 
-may, however, become a greater concern for parents, as 
-repeated abortions can result in very long durations between births.%
-\footnote{
-Shorter spacing was probably less of a concern to begin with for
+for countries like India naturally focus on whether spacing was too short.
+
+With the introduction of sex-selective abortions, parents can abort
+fetuses of unwanted sex.
+With an approximately 12 months additional duration per abortion,
+this strategy can result in very long durations between births, and
+``too long'' spacing may become a greater concern for parents than 
+``too short'' spacing.%
+\footnote{
+Shorter spacing was likely less of a concern to begin with for
 better educated mothers---who are also the most likely to use 
@@
 educated mothers \citep{Whitworth2002}.
-In general, mortality risk is negatively related to maternal
-education \citep[for India, see, for example,][]{Tulasidhar1993},
-although the underlying mechanism is subject
-to debate \citep{Kovsted2002}.
-}
-If ``too long'' spacing leads parents to reverse their decision to use
-prenatal sex determination within a spell this has important implications 
-for the empirical method.
-A reversal may happen, for example, if parents have concerns about possible 
-infertility from repeated abortions.
-Furthermore, with the increasing education and wealth in India, a growing 
-portion of the population is likely to behave in a manner that makes the 
-literature on shorter spacing in middle- and high-income countries more relevant.%
-\footnote{
-For the first birth, a potentially important factor in India is 
-the pressure to show fecundity, which would tend to shorten
-the duration to the first birth \citep{dyson83,Sethuraman2007,Dommaraju2009}.
-}
-There may, for example, be economies of scale in childrearing---both
-in terms of time cost and direct cost---that are easier to
-take advantage of if births are closer \citep[p 947]{Newman1984}.
-Similarly, if women's wages increase with age parents prefer
-to have their children early and close together while 
+}
+If the duration from last birth becomes long enough parents may 
+reverse their decision to use prenatal sex determination
+and carry the next pregnancy to term whether it is a male or female fetus.
+
+At least four different factors may make a reversal of the decision 
+to use sex selection between one birth and the next more likely, 
+everything else equal.
+First, the more concerned parents are about possible infertility 
+from repeated abortions or the closer they are to the end of their 
+reproductive period, they more likely they are to decide that any 
+child is better than not having an additional child at all.
+Second, the higher the parents' discount factor is---that is, the
+more the value present outcomes relative to future outcomes---the
+more likely they are to reverse their decision to sex selection.
+Third, economies of scale in childrearing---both in terms of time cost 
+and direct cost---are easier to take advantage of if births 
+are closer \citep[p 947]{Newman1984}.
+Hence, the stronger these economies of scale are, the more likely
+parents are to reverse their decision to use sex selection.
+Finally, if women's wages increase with age, parents prefer
+to have their children early and close together, while 
 the opportunity cost of children is lower \citep{Heckman1976}.%
@@
 }
+The more pronounced the increase in wage is with age, the more 
+attractive it will be to reverse the decision to use sex selection.
+Although, the latter two are most associated with the literature
+on shorter spacing in middle- and  high-income countries, 
+the increasing education and wealth in India means that a growing 
+portion of the population is likely to behave in a similar manner.%
+\footnote{
+The possible exception is for the first birth, where the pressure to show 
+fecundity---which shortens the duration to the first birth---is potentially 
+an important factor in India \citep{dyson83,Sethuraman2007,Dommaraju2009}.
+}
+
+If ``too long'' spacing leads parents to reverse their decision to use
+prenatal sex determination within a spell this has important implications 
+for the empirical method.
+
+[TK find examples of the son preference spacing papers and look at what they did
+for "theory"]
 
@@
 across education groups \citep{Tulasidhar1993,Whitworth2002}.
-
-To illustrate how the decision process works, consider
-the decision in the final period on whether to use sex selection or not
-(assuming that both are superior to no birth).
-Parents choose a pregnancy without prenatal sex determination
-if $U_T^B > U_T^S$, which leads to
-\begin{multline} \label{eq:last_simple}
-(1-\pi)(1-\alpha) [ u^g(g_{T-1}+1) - u^g(g_{T-1}) ]
-> \\
-\pi u(I - p_k(b_{T-1} + g_{T-1} + 1) - p_s) 
-+ (1-\pi) u(I - p_k(b_{T-1} + g_{T-1}) - p_s) \\
-- u(I - p_k(b_{T-1} + g_{T-1}+1)).
-\end{multline}
-Hence, parents choose a pregnancy without prenatal scan over
-a pregnancy with a prenatal scan in the final period if
-the additional utility of having an extra girl (the left-hand-side),
-weighted by the probability of having a girl and the weight parents
-assign to utility from having girls, is larger than the expected impact on
-utility from consumption (the right-hand side), where
-the first two terms are the expected utility from consumption if 
-using prenatal sex determination and the last term is utility from
-consumption if parents simply have a birth.%
-\footnote{
-Notice that the marginal utility of having a boy does not enter
-into the decision on whether to use prenatal sex determination or not
-(except through the value of $\alpha$).
-Only the marginal utility of having another girl
-and the total number of children, which affects the trade-off between
-consumption and use of sex selection, matters.
-This is an artifact of the separability between consumption, number of
-boys, and number of girls in the utility function.
-}
-
-If a son is conceived the money for a prenatal scan are ``wasted,''
-which means that the utility from consumption if they use prenatal scan
-and conceive a boy is alway going to be lower than utility from consumption 
-if the parents had a birth without a prenatal scan.
-Hence, assuming that the marginal utility of girls is always positive,
-but declining in the number of girls they have, parents will pick
-a birth with scan over a birth without scan only if the difference between
-utility from consumption when using prenatal scan and conceiving a girl
-is sufficiently higher than the utility of consumption if the parents
-simply had a child without a scan.
-It follows that the higher the cost of the prenatal scan is relatively
-to the cost of maintaining a child the less likely it is that parents will 
-use sex selection.
-Furthermore, if the cost of a prenatal scan, 
-$p_s$, is larger than the cost of maintaining a child in one period, $p_k$, 
-parents will never select a prenantal scan in the final period.
-This result holds, however, only because this is the last period. 
-The earlier the decision on sex selection is made in the time horizon
-the lower the cost of prenatal sex determination is going to be 
-relative to the cost of maintaining the child until the end of the time
-horizon.
 

### 2017-04-05 paper/sexSelectionSpacing-ver1.tex
Further edits to theory section

@@
 
+[ways to get at son preference:
+- stated fertility preferences
+- longer spacing after son
+- differential stopping behavior
+- biased sex ratio (overall before sex selection, and specifically at birth later)]
+
+[why do these work less well after introduction of sex selection?]
+
+[how can my method remedy those problems?]
+
+[main results]
+
 The males-to-females ratio at birth increased dramatically over the last three 
@@
 is known as differential stopping behavior, where parents were 
-more likely to cease child bearing after the birth of a son than
+more likely to cease childbearing after the birth of a son than
 after a daughter [TK add references here]. 
@@
 Because of the potential health effects, most of the literature on spacing 
-for countries like India naturally focus on whether spacing was too short.
-
-With the introduction of sex-selective abortions, parents can abort
-fetuses of unwanted sex.
+for countries like India naturally focus on whether spacing was too short
+and used the shorter birth spacing after the birth of a girl than after the
+birth of a boy as a measure of the degree of son preference.
+
+With the introduction of sex-selective abortions, parents can now abort
+a fetus of unwanted sex.
 With an approximately 12 months additional duration per abortion,
-this strategy can result in very long durations between births, and
+this can result in substantially longer durations between births, and
 ``too long'' spacing may become a greater concern for parents than 
@@
 }
-If the duration from last birth becomes long enough parents may 
+If the duration from last birth becomes long enough, parents may 
 reverse their decision to use prenatal sex determination
-and carry the next pregnancy to term whether it is a male or female fetus.
-
-At least four different factors may make a reversal of the decision 
-to use sex selection between one birth and the next more likely, 
+and carry the next pregnancy to term whether male or female.
+
+A number of factors make a reversal of the decision to use sex 
+selection between one birth and the next more likely, 
 everything else equal.
@@
 Finally, if women's wages increase with age, parents prefer
-to have their children early and close together, while 
+to have their children early and close together while 
 the opportunity cost of children is lower \citep{Heckman1976}.%
@@
 attractive it will be to reverse the decision to use sex selection.
-Although, the latter two are most associated with the literature
+Although the latter two factor are most often associated with the literature
 on shorter spacing in middle- and  high-income countries, 
@@
 
+For a given sex composition of prior children, there are two main drivers 
+of sex selection: the degree of son preference and the cost of sex selection.
+The more parents care about having a son as their next child, the more
+likely they are to use sex selection and the less likely they are to
+reverse the decision once started.
+The result is an increased number of abortions, more spells where a
+prenatal scan is used, and the spacing between births is longer.
+
+Lowering the cost of sex selection bias the overall sex ratio further 
+towards boys.
+Correspondingly, both the number of abortions per woman and the
+number of spells where a prenatal scan is used should also increase,
+resulting in longer average spacing between births.
+This increase in spacing is, however, not likely to be uniform across parities.
+In addition to increasing the overall sex ratio, lower cost of prenatal 
+scan should also lead to use of sex selection at earlier parities.
+It is therefore possible to see either no change or a \emph{decrease} 
+in average spacing for a later parity---although with a more than compensating 
+increase in an earlier parity.
+In other words, it is possible for individual parities to show a \emph{decline}
+in sex selection at the same time as the overall use goes up.
+This is an important caution against over-interpreting individual 
+parity results.
+
+It also highlights the need to incorporate fertility progression into
+estimates, something the simple model is incapable of.
+
 If ``too long'' spacing leads parents to reverse their decision to use
 prenatal sex determination within a spell this has important implications 
-for the empirical method.
+for the empirical method [TK explain what they are instead!].
 
@@
 
-Lowering the cost of prenatal sex determination does, however, bias the overall sex 
-ratio further towards boys, and the stronger the son preference and the 
-more patient the parents, the larger the change in sex ratio.
-Correspondingly, both the number of abortions per woman and the
-average number of spells per woman where a prenatal scan is used also increases.
-Since fertility changes little, the increased use of abortion
-is associated with longer spacing between births.
-This increase in spacing is, however, not uniform across parities.
-In addition to increasing the overall sex ratio, lower cost of prenatal 
-scan leads to use of sex selection at earlier parities.
-The result is that in some cases there is either no change or a \emph{decrease} 
-in average spacing for a given parity---although with a more than compensating 
-increase in an earlier parity.
-Hence, it is possible for individual parities to show a \emph{decline}
-in sex selection at the same time as the overall use goes up.
-This is an important caution against over-interpreting
-individual parity results.
-It also highlights the need to incorporate fertility progression into
-estimates, something the simple model is incapable of.
-
-% Son preference
-
-Increasing the value of having sons, $\alpha$, when there is access to 
-sex selection results in slightly lower fertility in most cases,
-but the effect is neither strong nor uniform.
-What is clear is that the sex ratio becomes more male biased 
-the stronger the son preference.
-Correspondingly, there is an increased number of abortions,
-more spells where a prenatal scan is used,
-and the spacing between births is longer.
-
-Son preference, however, manifests in two ways in this model.
-First, if $\alpha$ is larger than 0.5 parents gain more utility
-from having an additional son than from an additional daughter---provided
-the had the same number of sons and daughters before.
-Second, parents will never abort a male fetus, only a female one.
-This explains why even when parents have equal utility from an additional
-son or daughter sex ratios still increases as cost of children 
-increases and cost of prenatal scans decline.
-
-At $\alpha = 0.5$ parents prefer an equal number of boys and girls.
-The more children you have the less likely it is that you will
-resort to sex selection to ensure a balance between sons and daughters.
-First, the chances of having, for example, only boys or only
-girls, decreases with each additional child.%
-\footnote{
-For 2 children the likelihood of only boys or only girls
-is 50\%, but for 4 children it is 12.5\% (assuming equal probability
-of a boy or a girl).
-}
-Second, the more children you have the lower the marginal
-utility of having another, which means that, for a given price
-of prenatal scan, the less attractive it is to bear the cost of using
-prenatal scans to ensure a specific sex.
-As fertility fall to, say, two, however, those parents who had a girl as their 
-first child will now want to use prenatal sex determination to 
-ensure a balanced number of sons and daughters and this is why
-the sex ratio is so unbalanced as the cost of children increases.
-Parents who had a son as their first child would also want to
-use sex selection to ensure both a son \emph{and} a daughter, but since
-that option is not available here they have their
-second birth without scan.
-
-Stretching the interpretation of the model, think of $\alpha=0.5$ 
-as capturing parents treating sons and daughters equally once born.
-The use of sex selection to achieve balance---but only when the
-fetus is female---could be a potential explanation for the
-suggestion that sons and daughters are treated relatively equally and 
-we are still seeing an unequal sex ratio.
-What is relevant here it that there is no way to identify which 
-of these two different types of son preference affect sex ratios 
-from fertility data.
-This is a concern because the way we currently measure son preference
-allows us to capture only the distribution preference, and 
-the different types of son preference likely have different policy 
-implications.
-
 % Highlights and tie into empirical model:
@@
 increases the use of sex selection.
-
-Another reason for parents to change their decision to use sex
-selection is that they get ``too close'' to the end of the time
-horizon after extensive use of abortions and prefer any child to 
-the potential of having no child at all.
-This type of reversal explains why the effects of changing the discount 
-rate and cost of prenatal sex determination are not uniform.
-Related, extending the time horizon leads to a smaller likelihood of parents 
-reversing their use of sex selection between births when
-there is strong incentive to use sex selection.%
-\footnote{
-These results are available in the online Appendix.
-}
 

### 2017-04-06 paper/sexSelectionSpacing-ver1.tex
Further edits of theory part; moved tables out of doc; moved comparison back to appendix

@@
 sex selection show signs of serious under-reporting \citep{goodkind96}.
+
 With no direct information, researchers have relied on a simple method for establishing 
@@
 % families have low desired fertility and access to sex-selective abortions!!!!
-Second,
-families may reverse their decision to use sex selection in-between births.
+Second, families may reverse their decision to use sex selection in-between births.
 A reversal could happen if they do not want the space between children to be 
@@
 \citep{Soest2012} for a recent example of spacing and son preference
+
+Recent research suggests that son preference in India, when measured as ideally having 
+more boys than girls, is decreasing over time and with higher education \citep{bhat03,pande07}.%
+\footnote{
+This measure of son preference is commonly used in the literature. 
+See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
+In NFHS, and Demographic and Health Surveys in general, son preference is measured as part 
+of the general fertility questions.
+The first question is how many children a woman would have if she could choose exactly how 
+many.
+This if followed by the sex preference question:
+``How many of these children would you like to be boys, how many would you like to be girls 
+and for how many would the sex not matter?''
+}
 
@@
 
-It also highlights the need to incorporate fertility progression into
-estimates, something the simple model is incapable of.
+Lowering the cost of prenatal sex determination generally leads to 
+a smaller percentage of parents who change their use of sex selection.
+But, the total number of spells with a change may still
+go up because lower cost of prenatal sex determination also
+increases the use of sex selection.
 
@@
 
-% Highlights and tie into empirical model:
-
-An important question here is whether parents ever
-change their use of prenatal sex determination between
-two consecutive births.
-I capture this by the percent of spells where prenatal
-scans were initially used for one or more period, but the birth
-is the result of a pregnancy without a prenatal scan.
-Whether parents will consider the duration from last birth too long 
-depends mainly on the discount rate.
-On average, the more impatient parents are---the less they
-like long spells between births---the more likely they are to
-change their decision to use sex selection.%
-\footnote{
-Using only those situations where there are any abortions,
-regressing the discount rate against the percent spells where
-prenatal scan is initially used but not for the birth show
-a strong positive effect---higher number, more patient---holding
-all the other parameters constant.
-}
-Lowering the cost of prenatal sex determination generally leads to 
-a smaller percentage of parents who change their use of sex selection.
-But, the total number of spells with a change may still
-go up because lower cost of prenatal sex determination also
-increases the use of sex selection.
-
 % What are the model highlights 
-There are three main conclusions from the model.%
-\footnote{
-A caveat is that these results reflect the particular utility 
-function chosen.
-If parents have a different utility function, like a preference
-for one son but otherwise no preference across boys and girls
-the results may look different.
-}
+There are three main conclusions from the model.
 The increased use of sex selection shows up both in the 
@@
 
-The theoretical model has three implications for fertility decisions with access to 
-sex-selective abortions: 
+As the discussion above shows there are three main
+implications of the availability of sex-selective abortions
+combined with son preference:
 a higher probability that next child is a son, 
-longer average time to next birth, 
-and that the use of prenatal sex determination may change between one observed 
-birth and the next.
+longer spacing to next birth with use of sex selection, 
+and that the use of prenatal sex determination may change between 
+one observed birth and the next.
 All three must be incorporated into the estimation strategy
 to provide unbiased and precise estimates of the use of sex-selective abortions.%
+
+To understand son preference when sex selection is available,
+we need an empirical model that can jointly estimate the sex of
+children born and the spacing between birth.
 
@@
 }
-A woman's reproductive life is divided into spells which each covers the period between
-births (from marriage to first birth for the first spell).
+A woman's reproductive life is divided into spells which each covers 
+the period between births (from marriage to first birth for the first spell).
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
@@
 
+[This need a much better explanation; the survival curve captures the spacing
+between births and how long it takes; may need to combine with and without
+sons to show differences in spacing over time; maybe it should also have
+predicted average/median spacing with some confidence intervals to test]
+
 The survival curves are presented for two reasons.
@@
 which have nationwide coverage.
-% All are based on the Demographic and Health Survey Model B, with
-% NFHS-1 using the DHS II questionnaire while NFHS-2 and NFHS-3 using, 
-% respectively, the DHS III questionnaire and the Measure DHS questionnaire.
 The surveys are large: NFHS-1 covered 89,777 ever-married women 
@@
 
-By dividing spells into these periods I can examine how fertility
-decisions and the use of sex selection have changed across the three different regimes.
+By dividing spells into these periods I can examine how the use of sex selection 
+has changed across the three different regimes.
 Note that the periods are based on the spells' beginning year, and some spells 
@@
 
-\subsection{Comparing the Hazard and Simple Models}
-
-As detailed in the main paper, one of the main advantages of the hazard model 
-approach is that it can be used to predict what completed fertility, number of abortions, 
-and sex ratios will be once women are done with childbearing.
-This cannot be done with the simple model because it does not predict fertility
-progression, does not take into account censoring, and cannot capture if parents
-change their use of sex selection within a spell.
-We can, however, still compare differences in predicted sex ratios for 
-\emph{individual} parities.%
-\footnote{
-The simple model uses only observed births and the predicted sex ratio is 
-therefore simply what we observe for the relevant uncensored sample.
-}
-
-For each parity, the simple model is
-\begin{equation}
-Y_i = \gamma + \alpha' \mathbf{Z_i} + \beta' \mathbf{X}_{i} + \epsilon_i,
-\end{equation}
-where $Y$ is a dummy variable that takes the value 1 if the child born is a boy and zero 
-if it is a girl, and the vectors of explanatory variables, $\mathbf{Z}_{i}$ and 
-$\mathbf{X}_{i}$, are the same as for the proposed method, except that 
-$\mathbf{Z}_{i}$ obviously does not include the baseline hazard and that there are 
-no time dependence.%
-\footnote{
-To ease presentation, the indicator for parity number is not shown.
-}
-I estimate this using a logit model, although a linear probability model leads to
-similar results.
-This model is estimated on all observed births for a given parity in the relevant 
-period to ensure that the results are as close to the standard method of 
-examining sex selection \citep[see, for example, ][]{retherford03b,jha06,abrevaya09}.
-
-\begin{table}[htbp]
-\begin{center}
-\begin{footnotesize}
-\begin{threeparttable}
-\caption{Comparison of Hazard and Simple Models for  \protect\linebreak
-Women with 8 or More Years of Education}
-\label{tab:compare2}
-\begin{tabular} {@{} l D{.}{.}{5.2} D{.}{.}{5.2} D{.}{.}{5.2} D{.}{.}{5.2}   @{}} \toprule
-                                  &  \multicolumn{2}{c}{Urban}        & \multicolumn{2}{c}{Rural}         \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5}
-                                  & \mco{Simple}     &  \mco{Hazard}   &  \mco{Simple}    & \mco{Hazard}      \\   \midrule
-                                  & \multicolumn{4}{c}{1985--1994 - Second Birth} \\ \cmidrule(l){2-5}
-                                  & \multicolumn{4}{c}{1 girl} \\
-Number of women\tnote{a}          &             & 4,869   &         & 3,105   \\
-Births\tnote{b}                   &     3,848   & 3,926   & 2,417   & 2,795   \\
-Percentage boys                   &      54.0   &  54.7   &  52.6   &  53.5   \\
-Sex ratio (boys per 100 girls)    &     117.4   & 120.7   & 110.9   & 115.1   \\
-\addlinespace 
-                                  & \multicolumn{4}{c}{1985--1994 - Third Birth}  \\ \cmidrule(l){2-5}
-%                                   & \multicolumn{4}{c}{1 boy and 1 girl}        \\
-% Number of women\tnote{a}          &             & 3,460   &         & 1,987   \\
-% Births\tnote{c}                   &     1,431   & 1,558   & 1,107   & 1,336   \\
-% Percentage boys                   &      53.0   &  52.5   &  53.5   &  54.6   \\
-% Sex ratio (boys per 100 girls)    &     112.9   & 110.4   & 115.0   & 120.2   \\
-% \addlinespace
-                                  & \multicolumn{4}{c}{2 girls}        \\
-Number of women\tnote{a}          &             & 1,654   &         &   982   \\
-Births\tnote{c}                   &     1,034   & 1,092   &   682   &   853   \\
-Percentage boys                   &      60.8   &  63.7   &  54.7   &  57.4   \\
-Sex ratio (boys per 100 girls)    &     155.3   & 175.3   & 120.7   & 134.6   \\
-\addlinespace 
-                                  & \multicolumn{4}{c}{1995--2006 - Second Birth} \\ \cmidrule(l){2-5}
-                                  & \multicolumn{4}{c}{1 girl} \\                                                  
-Number of women\tnote{a}          &             & 3,774   &         & 2,823   \\
-Births\tnote{b}                   &     3,031   & 2,704   & 2,489   & 2,407   \\
-Percentage boys                   &      58.0   &  58.6   &  56.0   &  56.9   \\
-Sex ratio (boys per 100 girls)    &     138.1   & 141.3   & 127.1   & 132.2   \\
-\addlinespace 
-                                  & \multicolumn{4}{c}{1995--2006 - Third Birth}  \\ \cmidrule(l){2-5}
-%                                   & \multicolumn{4}{c}{1 boy and 1 girl}        \\
-% Number of women\tnote{a}          &             & 2,357   &         & 1,819   \\
-% Births\tnote{c}                   &       830   &   775   &   853   &   998   \\
-% Percentage boys                   &      53.9   &  52.9   &  55.5   &  56.5   \\
-% Sex ratio (boys per 100 girls)    &     116.7   & 112.1   & 124.5   & 129.8   \\
-% \addlinespace
-                                  & \multicolumn{4}{c}{2 girls}        \\
-Number of women\tnote{a}          &             & 1,000   &         &   863   \\
-Births\tnote{c}                   &       695   &   600   &   690   &   661   \\
-Percentage boys                   &      65.5   &  62.4   &  62.0   &  61.7   \\
-Sex ratio (boys per 100 girls)    &     189.6   & 166.0   & 163.4   & 161.0   \\
-\bottomrule
-\end{tabular}                        
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} 
-The simple models are estimated using logit on all births for a given parity that
-occurred during the relevant time period.
-The hazard models are estimated using all spells that began in the relevant time period.
-For the second birth the hazard model covers the period from beginning of spell to 6 
-years (24 quarters) after the birth of the first child.
-For the third birth it covers the period from beginning of spell to 7.25 years 
-(29 quarters) after the birth of the second child for the period 1985--1994 and from 
-beginning of spell to 5.75 years (23 quarters) after the birth of the second child for 
-the period 1995--2006.
-\item[a] Number of women in period who began the spell with given sex composition of prior 
-child/children in the relevant period.
-\item[b] For Logit model the number of women who are observed to have a second birth
-in the period. 
-For hazard model the predicted number of second births that will occur between beginning 
-of the spell and 6 years (24 quarters) after the birth of the first child.
-% \item[c] Number of women in period who had one boy and one girl as their first two children.
-\item[c] For Logit model the number of women who are observed to have a third birth
-in the period. 
-For hazard model the predicted number of third births that will occur between beginning of 
-the spell and 7.25 years (29 quarters) after the birth of the second child for the
-1985--1994 period and between beginning of the spell and 5.75 years (23 quarters) after 
-the birth of the second child for the 1995--2006 period.
-\end{tablenotes}
-\end{threeparttable}
-\end{footnotesize}
-\end{center}
-\end{table}
-
-I focus on those cases where there is evidence of sex-selective abortions: the spells
-from parity one to two and two to three for women with eight or more years of education.%
-\footnote{
-The results for the spell from parity three to four are available on request.
-They are not presented because the number of educated women who end up with three births 
-and the probability of having a fourth birth are small, which makes
-comparing the simple and hazard models with any precision difficult.
-}
-Table \ref{tab:compare2} shows the number of women who enter the second and third spells
-for the hazard model,
-the number of births, observed in the case of the simple model and predicted in the case 
-of the hazard model, predicted percent boys, and the associated predicted sex ratio.
-It is possible for the number of births used for the simple model to be larger than the
-hazard models' predicted number of births because the simple model is based
-on all births that occurred in the period---independently of when the prior birth
-occurred---whereas the hazard model uses only spells that began in the period.
-
-For the 1985--1994 period---which is when sex selection become available---the 
-hazard model consistently predicts a higher sex ratio than the logit model.
-Furthermore, some of these differences are substantial.
-For urban women with 2 girls as their first two children, the hazard model
-predicts a sex ratio of 175 boys per 100 girls, whereas the simple method
-``only'' predicts 155 boys per 100 girls.
-The difference is smaller in rural areas but still 14 boys per 100 girls
-higher for the hazard model than for the simple model.
-A similar, if less pronounced pattern, show up for the second birth,
-where the hazard model predict 3 and 5 boys more per 100 girls for
-urban and rural women.
-
-For the latest period, 1995--2006, the hazard model still produces higher 
-predicted sex ratios for second birth and the differences are of a 
-similar magnitude to the 1985--1994 period.
-The predicted sex ratios for the third birth are, however, 
-higher for the simple model than for the hazard model.
-This difference is substantially for urban women where the difference 
-is 23 boys extra per 100 girls.
-
-A possible explanation for these differences is that the simple model 
-fails to capture the move towards lower fertility and the subsequent 
-increase in the use of sex-selective abortions at earlier parities that 
-occurred over the periods.
-The results also suggest that the take-up of sex selection occurred 
-rapidly as the new methods became available and that this take-up
-is not fully captured by the simple model.
-More broadly, a possible interpretation of the differences is that
-the simple model will tend to underestimate when sex-selective abortions
-are initially spreading in use and overestimate when the spread of sex 
-selection is slowing.
-This is most clearly seen for the third births for urban women where
-the hazard model show a \emph{decline} is use of sex-selective abortions,
-consistent with the lower fertility as discussed in the main paper,
-while the simple model show a substantial increase.
-
 \subsection{One Son or Many Sons?}
 
-In the discussion of declining fertility I rely on sex selection not being used by 
-families that already has one son.
-The extent to which this holds is of interest for two reasons.
+The extent to which people use sex selection for different sex compositions
+of previous children is of interest for two reasons.
 First and foremost, it can help us understand what form son preference takes in India.
-This is important in itself, but especially as we try to predict what will happen to 
-fertility and sex selection use in the future.
+This is important in itself, but is especially important as we try to predict 
+what will happen to sex selection use in the future.
+[need an explanation of this based on what I have in the introduction]
 Second,
@@
 
-\begin{table}[htbp]
-\begin{center}
-\begin{scriptsize}
-\begin{threeparttable}
-\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
-Abortions for Women with 8 or More Years of Education}
-\label{tab:predicted}
-\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
-                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
-                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
-                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
-\midrule
-\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
-Spell 2          &       85.9   &  2.0    &  1.8    &  52.3   &       78.2   &  4.7    &  3.7  &  53.7   &       68.0   &  8.0    &  5.4   &  55.3      \\
-Spell 3          &       64.4   &  5.1    &  3.3    &  53.9   &       49.9   &  9.8    &  4.9  &  56.2   &       38.6   &  7.8    &  3.0   &  55.3      \\
-Spell 4          &       57.0   &  2.8    &  1.6    &  52.6   &       44.8   &  2.6    &  1.1  &  52.6   &       33.7   &  21.8   &  7.3   &  62.3      \\
-Overall\tnote{d} &       2.7    &  2.0    &  5.5    &  52.3   &       2.3    &  3.4    &  8.0  &  53.1   &       2.0    &  4.6    &  9.4   &  53.7      \\
-\addlinespace 
-\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
-Spell 2          &       92.5   &  -1.4   &  -1.3   &  50.5   &       87.6   &  3.1    &  2.7  &  52.8   &       83.1   &  4.4    &  3.6   &  53.5      \\
-Spell 3          &       80.9   &  2.6    &  2.1    &  52.5   &       70.6   &  6.5    &  4.6  &  54.5   &       59.6   &  10.6   &  6.3   &  56.7      \\
-Spell 4          &       75.7   &  -3.1   &  -2.4   &  49.6   &       62.0   &  0.2    &  0.1  &  51.3   &       51.9   &  6.1    &  3.2   &  54.4      \\
-Overall\tnote{d} &       3.2    &  -0.3   &  -1.1   &  51.2   &       2.9    &  2.4    &  6.8  &  52.8   &       2.6    &  4.1    &  10.5  &  53.4      \\
-\bottomrule
-\end{tabular}                        
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
-(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
-The samples consist of all women from the data with 8 or more years of education who
-married during the indicated period using the estimation results for that periods 
-and the women's characteristics at the start of their marriage. 
-All numbers presented are for women predicted to have one or more births.
-Birth/progression rates are based on the ratio of women predicted to have a birth 
-by the end of each spell.
-Abortion rates within each spell are based on the predicted number of abortions each
-woman would have if she went through the entire spell.
-To generate conditions such as sex composition and fecundity for second and higher spells 
-each woman is randomly assigned outcomes based on the estimation results and
-her characteristics as follows.
-For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
-She is assigned one of these outcomes based on a random draw from a uniform distribution.
-The first quarter where she has a draw that results in a birth she leaves the spell
-and the quarter reached is used to calculate her starting age for the subsequent spell.
-If she has no draw that result in a birth within a spell her childbearing stops and
-she does not enter the next spell.
-Results are averaged over 1,000 repetitions.
-\item[a] For individual spells the column shows the percent of women who started the
-spell and ended up with a birth by the end of the spell period covered.
-For the ``Overall'' row, the number is the expected number of children born per woman over 
-the first four spells, conditional on having at least one birth.
-\item[b] For individual spells the column shows the number of abortions per 100
-births predicted to take place by the end of the spell.
-For the ``Overall'' row, the number is the total number of abortion per 100 births 
-predicted to take place over all four spells.
-\item[c]  For individual spells the column shows the number of abortions 
-predicted to take place by the end of the spell per 100 women who started the spell .
-For the ``Overall'' row, the number is the total number of abortion 
-predicted to take place over all four spells per 100 women who had at least one child.
-\item[d] Covers first through fourth spells. 
-\end{tablenotes}
-\end{threeparttable}
-\end{scriptsize}
-\end{center}
-\end{table}
+% Tables of predictions 
+\input{../tables/predictedFertility.tex}
 
 The results show a substantial reduction in fertility over time.
-% The percentage women with a birth by the end of each spell, conditional to making
-% it to the beginning of the spell, has decreased more than
-% 10 percentage points between the two periods.%
-% \footnote{
-% The exception is rural women's second spell, where the reductions between periods
-% were 4.9 and 4.5 percentage points.
-% }
 Predicted completed fertility went from 2.7 for urban women married in  
@@
 
-% \begin{sidewaystable}
-\begin{table}[htp]
-\begin{center}
-\begin{scriptsize}
-\begin{threeparttable}
-% \caption{Descriptive Statistics by Education Level and Beginning of Spell for First and Second Spell}
-\caption{Descriptive Statistics by Education Level and Beginning of Spell}
-\label{tab:des_stat1}
-\begin{tabular} {@{} c l D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} @{}} \toprule
-                    &                     & \multicolumn{3}{c}{No Education}                                & \multicolumn{3}{c}{1--7 Years of Education}                      & \multicolumn{3}{c}{8+ Years of Education} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-                    &                     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     \\ % \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-\midrule
-\multirow{16}{*}{\rotatebox{90}{First Spell}}                   
-                    &Boy born            &       0.467         &       0.438         &       0.363         &       0.476         &       0.447         &       0.368         &       0.483         &       0.453         &       0.377         \\
-                    &                    &     (0.499)         &     (0.496)         &     (0.481)         &     (0.499)         &     (0.497)         &     (0.482)         &     (0.500)         &     (0.498)         &     (0.485)         \\
-                    &Girl born           &       0.427         &       0.410         &       0.352         &       0.439         &       0.429         &       0.356         &       0.454         &       0.420         &       0.353         \\
-                    &                    &     (0.495)         &     (0.492)         &     (0.478)         &     (0.496)         &     (0.495)         &     (0.479)         &     (0.498)         &     (0.494)         &     (0.478)         \\
-                    &Censored            &       0.106         &       0.152         &       0.284         &       0.085         &       0.124         &       0.276         &       0.063         &       0.127         &       0.270         \\
-                    &                    &     (0.308)         &     (0.359)         &     (0.451)         &     (0.279)         &     (0.330)         &     (0.447)         &     (0.243)         &     (0.333)         &     (0.444)         \\
-                    &Urban               &       0.181         &       0.176         &       0.200         &       0.366         &       0.334         &       0.322         &       0.690         &       0.604         &       0.561         \\
-                    &                    &     (0.385)         &     (0.381)         &     (0.400)         &     (0.482)         &     (0.472)         &     (0.467)         &     (0.463)         &     (0.489)         &     (0.496)         \\
-                    &Age                 &      15.854         &      16.301         &      16.871         &      16.983         &      17.470         &      17.844         &      19.516         &      20.036         &      20.766         \\
-                    &                    &     (2.482)         &     (2.643)         &     (2.858)         &     (2.733)         &     (3.041)         &     (3.221)         &     (3.331)         &     (3.614)         &     (3.916)         \\
-                    &Owns land           &       0.589         &       0.578         &       0.540         &       0.500         &       0.497         &       0.482         &       0.321         &       0.387         &       0.414         \\
-                    &                    &     (0.492)         &     (0.494)         &     (0.498)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.467)         &     (0.487)         &     (0.493)         \\
-                    &Sched.\ caste/tribe &       0.357         &       0.395         &       0.441         &       0.170         &       0.227         &       0.318         &       0.071         &       0.119         &       0.175         \\
-                    &                    &     (0.479)         &     (0.489)         &     (0.497)         &     (0.376)         &     (0.419)         &     (0.466)         &     (0.257)         &     (0.324)         &     (0.380)         \\
-                    &Number of quarters  & \mco{  330,315         } & \mco{  257,757         } & \mco{   75,841         } & \mco{  108,463         } & \mco{  108,863         } & \mco{   54,704         } & \mco{  102,238         } & \mco{  154,582         } & \mco{  116,272         } \\
-                    &Number of women     & \mco{   30,004         } & \mco{   27,669         } & \mco{    9,684         } & \mco{   11,162         } & \mco{   13,104         } & \mco{    7,510         } & \mco{   11,271         } & \mco{   19,072         } & \mco{   16,620         } \\
-                    \addlinespace
-% \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-\midrule
-\multirow{22}{*}{\rotatebox{90}{Second Spell}}
-                    & Boy born            &       0.490         &       0.444         &       0.359         &       0.477         &       0.437         &       0.338         &       0.457         &       0.399         &       0.285         \\
-                    &                     &     (0.500)         &     (0.497)         &     (0.480)         &     (0.500)         &     (0.496)         &     (0.473)         &     (0.498)         &     (0.490)         &     (0.451)         \\
-                    & Girl born           &       0.451         &       0.413         &       0.327         &       0.462         &       0.413         &       0.319         &       0.426         &       0.351         &       0.239         \\
-                    &                     &     (0.498)         &     (0.492)         &     (0.469)         &     (0.499)         &     (0.492)         &     (0.466)         &     (0.495)         &     (0.477)         &     (0.427)         \\
-                    & Censored            &       0.059         &       0.143         &       0.314         &       0.061         &       0.150         &       0.344         &       0.117         &       0.251         &       0.476         \\
-                    &                     &     (0.236)         &     (0.350)         &     (0.464)         &     (0.239)         &     (0.357)         &     (0.475)         &     (0.321)         &     (0.433)         &     (0.499)         \\
-                    & One boy             &       0.527         &       0.515         &       0.508         &       0.519         &       0.513         &       0.505         &       0.513         &       0.520         &       0.515         \\
-                    &                     &     (0.499)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         \\
-                    & One girl            &       0.473         &       0.485         &       0.492         &       0.481         &       0.487         &       0.495         &       0.487         &       0.480         &       0.485         \\
-                    &                     &     (0.499)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         \\
-                    & Urban               &       0.181         &       0.180         &       0.212         &       0.370         &       0.348         &       0.345         &       0.697         &       0.628         &       0.578         \\
-                    &                     &     (0.385)         &     (0.384)         &     (0.409)         &     (0.483)         &     (0.476)         &     (0.475)         &     (0.459)         &     (0.483)         &     (0.494)         \\
-                    & Age                 &      17.774         &      18.357         &      18.870         &      18.620         &      19.200         &      19.581         &      20.988         &      21.589         &      22.252         \\
-                    &                     &     (2.743)         &     (3.054)         &     (3.284)         &     (2.864)         &     (3.206)         &     (3.373)         &     (3.371)         &     (3.621)         &     (3.901)         \\
-                    & First spell length  &      25.630         &      29.145         &      29.133         &      21.924         &      24.513         &      24.787         &      20.608         &      22.154         &      22.217         \\
-                    &                     &    (20.345)         &    (25.044)         &    (27.216)         &    (18.142)         &    (22.027)         &    (23.204)         &    (15.371)         &    (18.651)         &    (19.176)         \\
-                    & Owns land           &       0.590         &       0.572         &       0.528         &       0.497         &       0.492         &       0.468         &       0.313         &       0.369         &       0.402         \\
-                    &                     &     (0.492)         &     (0.495)         &     (0.499)         &     (0.500)         &     (0.500)         &     (0.499)         &     (0.464)         &     (0.483)         &     (0.490)         \\
-                    & Sched.\ caste/tribe &       0.353         &       0.390         &       0.430         &       0.164         &       0.218         &       0.304         &       0.068         &       0.110         &       0.169         \\
-                    &                     &     (0.478)         &     (0.488)         &     (0.495)         &     (0.371)         &     (0.413)         &     (0.460)         &     (0.251)         &     (0.313)         &     (0.374)         \\
-                    & Number of quarters  & \mco{  176,227         } & \mco{  231,546         } & \mco{   68,455         } & \mco{   67,432         } & \mco{  103,656         } & \mco{   49,236         } & \mco{   77,416         } & \mco{  164,752         } & \mco{  119,864         } \\
-                    & Number of women     & \mco{   21,171         } & \mco{   28,251         } & \mco{    9,428         } & \mco{    8,209         } & \mco{   12,449         } & \mco{    6,542         } & \mco{    8,204         } & \mco{   16,601         } & \mco{   13,610         } \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-% \item \hspace*{-7pt} \textbf{Note.}
-\item \hspace*{-0.7em} \textbf{Note.}
-Means without parentheses and standard deviation in parentheses.
-Interactions between variables, baseline hazard dummies and squares not shown.
-Quarters refer to number of 3 month periods observed.
-\end{tablenotes}
-\end{threeparttable}
-\end{scriptsize}
-\end{center}
-\end{table}
-% \end{sidewaystable}
-
-\addtocounter{table}{-1}
-
-% \begin{sidewaystable}
-\begin{table}
-\begin{center}
-\begin{scriptsize}
-\begin{threeparttable}
-% \caption{Descriptive Statistics by Education Level and Beginning of Spell for Third and Fourth Spell}
-\caption{(Continued) Descriptive Statistics by Education Level and Beginning of Spell}
-% \label{tab:des_stat2}
-\begin{tabular} {@{} c l D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} D{.}{.}{1.3} @{}} \toprule
-                    &                     & \multicolumn{3}{c}{No Education}                                & \multicolumn{3}{c}{1-7 Years of Education}                      & \multicolumn{3}{c}{8+ Years of Education} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-                    &                     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     & \mco{1972--1984}     & \mco{1985--1994}     & \mco{1995--2006}     \\ % \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-\midrule                    
-\multirow{24}{*}{\rotatebox{90}{Third Spell}}
-                    & Boy born            &       0.478         &       0.425         &       0.319         &       0.455         &       0.388         &       0.261         &       0.353         &       0.264         &       0.163         \\
-                    &                     &     (0.500)         &     (0.494)         &     (0.466)         &     (0.498)         &     (0.487)         &     (0.439)         &     (0.478)         &     (0.441)         &     (0.369)         \\
-                    & Girl born           &       0.442         &       0.393         &       0.306         &       0.423         &       0.357         &       0.239         &       0.313         &       0.214         &       0.128         \\
-                    &                     &     (0.497)         &     (0.488)         &     (0.461)         &     (0.494)         &     (0.479)         &     (0.426)         &     (0.464)         &     (0.410)         &     (0.334)         \\
-                    & Censored            &       0.080         &       0.182         &       0.376         &       0.121         &       0.255         &       0.500         &       0.334         &       0.521         &       0.709         \\
-                    &                     &     (0.271)         &     (0.386)         &     (0.484)         &     (0.326)         &     (0.436)         &     (0.500)         &     (0.472)         &     (0.500)         &     (0.454)         \\
-                    & Two boys            &       0.276         &       0.257         &       0.243         &       0.248         &       0.245         &       0.232         &       0.266         &       0.244         &       0.238         \\
-                    &                     &     (0.447)         &     (0.437)         &     (0.429)         &     (0.432)         &     (0.430)         &     (0.422)         &     (0.442)         &     (0.429)         &     (0.426)         \\
-                    & One boy, one girl   &       0.490         &       0.502         &       0.506         &       0.508         &       0.501         &       0.515         &       0.489         &       0.510         &       0.527         \\
-                    &                     &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.499)         \\
-                    & Two girls           &       0.234         &       0.241         &       0.252         &       0.243         &       0.254         &       0.253         &       0.245         &       0.247         &       0.235         \\
-                    &                     &     (0.424)         &     (0.428)         &     (0.434)         &     (0.429)         &     (0.435)         &     (0.435)         &     (0.430)         &     (0.431)         &     (0.424)         \\
-                    & Urban               &       0.179         &       0.182         &       0.208         &       0.378         &       0.354         &       0.343         &       0.693         &       0.646         &       0.568         \\
-                    &                     &     (0.383)         &     (0.386)         &     (0.406)         &     (0.485)         &     (0.478)         &     (0.475)         &     (0.461)         &     (0.478)         &     (0.495)         \\
-                    & Age                 &      19.978         &      20.693         &      21.278         &      20.794         &      21.453         &      21.998         &      22.963         &      23.825         &      24.548         \\
-                    &                     &     (2.895)         &     (3.196)         &     (3.551)         &     (2.937)         &     (3.239)         &     (3.618)         &     (3.405)         &     (3.748)         &     (4.067)         \\
-                    & First spell length  &      24.547         &      27.575         &      27.099         &      20.971         &      23.901         &      23.532         &      19.991         &      21.246         &      21.236         \\
-                    &                     &    (18.832)         &    (22.779)         &    (24.364)         &    (16.875)         &    (20.378)         &    (21.155)         &    (14.646)         &    (16.835)         &    (17.363)         \\
-                    & Owns land           &       0.602         &       0.575         &       0.538         &       0.503         &       0.503         &       0.490         &       0.320         &       0.369         &       0.421         \\
-                    &                     &     (0.490)         &     (0.494)         &     (0.499)         &     (0.500)         &     (0.500)         &     (0.500)         &     (0.467)         &     (0.483)         &     (0.494)         \\
-                    & Sched.\ caste/tribe &       0.344         &       0.392         &       0.432         &       0.159         &       0.218         &       0.298         &       0.067         &       0.107         &       0.169         \\
-                    &                     &     (0.475)         &     (0.488)         &     (0.495)         &     (0.366)         &     (0.413)         &     (0.457)         &     (0.251)         &     (0.310)         &     (0.375)         \\
-                    & Number of quarters  & \mco{  109,026         } & \mco{  206,988         } & \mco{   70,391         } & \mco{   43,434         } & \mco{   87,537         } & \mco{   41,400         } & \mco{   49,799         } & \mco{  126,733         } & \mco{   79,068         } \\
-                    & Number of women     & \mco{   13,196         } & \mco{   25,135         } & \mco{    9,355         } & \mco{    4,960         } & \mco{    9,775         } & \mco{    5,034         } & \mco{    4,316         } & \mco{   10,688         } & \mco{    7,927         } \\
-\addlinespace
-% \cmidrule(lr){1-2} \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-\midrule
-\multirow{26}{*}{\rotatebox{90}{Fourth Spell}}
-                    & Boy born            &       0.463         &       0.384         &       0.291         &       0.403         &       0.347         &       0.233         &       0.310         &       0.227         &       0.170         \\
-                    &                     &     (0.499)         &     (0.486)         &     (0.454)         &     (0.491)         &     (0.476)         &     (0.423)         &     (0.462)         &     (0.419)         &     (0.376)         \\
-                    & Girl born           &       0.408         &       0.363         &       0.268         &       0.391         &       0.303         &       0.198         &       0.298         &       0.197         &       0.113         \\
-                    &                     &     (0.491)         &     (0.481)         &     (0.443)         &     (0.488)         &     (0.460)         &     (0.399)         &     (0.458)         &     (0.397)         &     (0.316)         \\
-                    & Censored            &       0.130         &       0.254         &       0.441         &       0.206         &       0.350         &       0.569         &       0.392         &       0.576         &       0.717         \\
-                    &                     &     (0.336)         &     (0.435)         &     (0.497)         &     (0.405)         &     (0.477)         &     (0.495)         &     (0.488)         &     (0.494)         &     (0.450)         \\
-                    & Three boys          &       0.134         &       0.124         &       0.111         &       0.107         &       0.105         &       0.102         &       0.106         &       0.101         &       0.082         \\
-                    &                     &     (0.341)         &     (0.329)         &     (0.315)         &     (0.309)         &     (0.307)         &     (0.303)         &     (0.308)         &     (0.302)         &     (0.275)         \\
-                    & Two boys, one girl  &       0.374         &       0.357         &       0.346         &       0.348         &       0.323         &       0.308         &       0.358         &       0.304         &       0.289         \\
-                    &                     &     (0.484)         &     (0.479)         &     (0.476)         &     (0.476)         &     (0.468)         &     (0.462)         &     (0.480)         &     (0.460)         &     (0.453)         \\
-                    & One boys, two girls &       0.362         &       0.389         &       0.400         &       0.400         &       0.413         &       0.423         &       0.393         &       0.439         &       0.469         \\
-                    &                     &     (0.481)         &     (0.488)         &     (0.490)         &     (0.490)         &     (0.492)         &     (0.494)         &     (0.489)         &     (0.496)         &     (0.499)         \\
-                    & Three girls         &       0.129         &       0.130         &       0.142         &       0.145         &       0.159         &       0.167         &       0.143         &       0.156         &       0.159         \\
-                    &                     &     (0.335)         &     (0.337)         &     (0.350)         &     (0.353)         &     (0.365)         &     (0.373)         &     (0.350)         &     (0.363)         &     (0.366)         \\
-                    & Urban               &       0.171         &       0.181         &       0.197         &       0.363         &       0.346         &       0.325         &       0.670         &       0.601         &       0.511         \\
-                    &                     &     (0.377)         &     (0.385)         &     (0.398)         &     (0.481)         &     (0.476)         &     (0.469)         &     (0.470)         &     (0.490)         &     (0.500)         \\
-                    & Age                 &      21.926         &      22.885         &      23.608         &      22.611         &      23.519         &      24.317         &      24.257         &      25.472         &      26.061         \\
-                    &                     &     (3.019)         &     (3.332)         &     (3.711)         &     (2.894)         &     (3.364)         &     (3.759)         &     (3.171)         &     (3.702)         &     (4.143)         \\
-                    & First spell length  &      23.281         &      26.609         &      26.460         &      20.495         &      23.069         &      24.215         &      19.106         &      20.826         &      21.423         \\
-                    &                     &    (17.481)         &    (21.556)         &    (23.272)         &    (15.546)         &    (19.078)         &    (21.244)         &    (13.991)         &    (16.277)         &    (16.585)         \\
-                    & Owns land           &       0.610         &       0.587         &       0.557         &       0.523         &       0.530         &       0.509         &       0.339         &       0.414         &       0.466         \\
-                    &                     &     (0.488)         &     (0.492)         &     (0.497)         &     (0.500)         &     (0.499)         &     (0.500)         &     (0.474)         &     (0.493)         &     (0.499)         \\
-                    & Sched.\ caste/tribe &       0.338         &       0.403         &       0.442         &       0.154         &       0.224         &       0.297         &       0.085         &       0.113         &       0.193         \\
-                    &                     &     (0.473)         &     (0.491)         &     (0.497)         &     (0.361)         &     (0.417)         &     (0.457)         &     (0.280)         &     (0.316)         &     (0.395)         \\
-                    & Number of quarters  & \mco{   54,446         } & \mco{  151,285         } & \mco{   56,756         } & \mco{   18,852         } & \mco{   49,108         } & \mco{   23,209         } & \mco{   14,287         } & \mco{   43,339         } & \mco{   23,586         } \\
-                    & Number of women     & \mco{    6,832         } & \mco{   18,436         } & \mco{    7,637         } & \mco{    2,201         } & \mco{    5,564         } & \mco{    2,768         } & \mco{    1,347         } & \mco{    3,933         } & \mco{    2,459         } \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-% \item \hspace*{-7pt} \textbf{Note.}
-\item \hspace*{-0.7em} \textbf{Note.}
-Means without parentheses and standard deviation in parentheses.
-Interactions between variables, baseline hazard dummies and squares not shown.
-Quarters refer to number of 3 month periods observed.
-\end{tablenotes}
-\end{threeparttable}
-\end{scriptsize}
-\end{center}
-\end{table}
-% \end{sidewaystable}
+% Descriptive statistics tables
+\input{../tables/desStat.tex}
 

### 2017-04-06 paper/sexSelectionSpacingAppendix-ver1.tex
Further edits of theory part; moved tables out of doc; moved comparison back to appendix

@@
 sex-selective abortions.
+
+\clearpage
+\newpage
+
+\subsection{Comparing the Hazard and Simple Models}
+
+As detailed in the main paper, one of the main advantages of the hazard model 
+approach is that it can be used to predict what completed fertility, number of abortions, 
+and sex ratios will be once women are done with childbearing.
+This cannot be done with the simple model because it does not predict fertility
+progression, does not take into account censoring, and cannot capture if parents
+change their use of sex selection within a spell.
+We can, however, still compare differences in predicted sex ratios for 
+\emph{individual} parities.%
+\footnote{
+The simple model uses only observed births and the predicted sex ratio is 
+therefore simply what we observe for the relevant uncensored sample.
+}
+
+For each parity, the simple model is
+\begin{equation}
+Y_i = \gamma + \alpha' \mathbf{Z_i} + \beta' \mathbf{X}_{i} + \epsilon_i,
+\end{equation}
+where $Y$ is a dummy variable that takes the value 1 if the child born is a boy and zero 
+if it is a girl, and the vectors of explanatory variables, $\mathbf{Z}_{i}$ and 
+$\mathbf{X}_{i}$, are the same as for the proposed method, except that 
+$\mathbf{Z}_{i}$ obviously does not include the baseline hazard and that there are 
+no time dependence.%
+\footnote{
+To ease presentation, the indicator for parity number is not shown.
+}
+I estimate this using a logit model, although a linear probability model leads to
+similar results.
+This model is estimated on all observed births for a given parity in the relevant 
+period to ensure that the results are as close to the standard method of 
+examining sex selection \citep[see, for example, ][]{retherford03b,jha06,abrevaya09}.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{footnotesize}
+\begin{threeparttable}
+\caption{Comparison of Hazard and Simple Models for  \protect\linebreak
+Women with 8 or More Years of Education}
+\label{tab:compare2}
+\begin{tabular} {@{} l D{.}{.}{5.2} D{.}{.}{5.2} D{.}{.}{5.2} D{.}{.}{5.2}   @{}} \toprule
+                                  &  \multicolumn{2}{c}{Urban}        & \multicolumn{2}{c}{Rural}         \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5}
+                                  & \mco{Simple}     &  \mco{Hazard}   &  \mco{Simple}    & \mco{Hazard}      \\   \midrule
+                                  & \multicolumn{4}{c}{1985--1994 - Second Birth} \\ \cmidrule(l){2-5}
+                                  & \multicolumn{4}{c}{1 girl} \\
+Number of women\tnote{a}          &             & 4,869   &         & 3,105   \\
+Births\tnote{b}                   &     3,848   & 3,926   & 2,417   & 2,795   \\
+Percentage boys                   &      54.0   &  54.7   &  52.6   &  53.5   \\
+Sex ratio (boys per 100 girls)    &     117.4   & 120.7   & 110.9   & 115.1   \\
+\addlinespace 
+                                  & \multicolumn{4}{c}{1985--1994 - Third Birth}  \\ \cmidrule(l){2-5}
+%                                   & \multicolumn{4}{c}{1 boy and 1 girl}        \\
+% Number of women\tnote{a}          &             & 3,460   &         & 1,987   \\
+% Births\tnote{c}                   &     1,431   & 1,558   & 1,107   & 1,336   \\
+% Percentage boys                   &      53.0   &  52.5   &  53.5   &  54.6   \\
+% Sex ratio (boys per 100 girls)    &     112.9   & 110.4   & 115.0   & 120.2   \\
+% \addlinespace
+                                  & \multicolumn{4}{c}{2 girls}        \\
+Number of women\tnote{a}          &             & 1,654   &         &   982   \\
+Births\tnote{c}                   &     1,034   & 1,092   &   682   &   853   \\
+Percentage boys                   &      60.8   &  63.7   &  54.7   &  57.4   \\
+Sex ratio (boys per 100 girls)    &     155.3   & 175.3   & 120.7   & 134.6   \\
+\addlinespace 
+                                  & \multicolumn{4}{c}{1995--2006 - Second Birth} \\ \cmidrule(l){2-5}
+                                  & \multicolumn{4}{c}{1 girl} \\                                                  
+Number of women\tnote{a}          &             & 3,774   &         & 2,823   \\
+Births\tnote{b}                   &     3,031   & 2,704   & 2,489   & 2,407   \\
+Percentage boys                   &      58.0   &  58.6   &  56.0   &  56.9   \\
+Sex ratio (boys per 100 girls)    &     138.1   & 141.3   & 127.1   & 132.2   \\
+\addlinespace 
+                                  & \multicolumn{4}{c}{1995--2006 - Third Birth}  \\ \cmidrule(l){2-5}
+%                                   & \multicolumn{4}{c}{1 boy and 1 girl}        \\
+% Number of women\tnote{a}          &             & 2,357   &         & 1,819   \\
+% Births\tnote{c}                   &       830   &   775   &   853   &   998   \\
+% Percentage boys                   &      53.9   &  52.9   &  55.5   &  56.5   \\
+% Sex ratio (boys per 100 girls)    &     116.7   & 112.1   & 124.5   & 129.8   \\
+% \addlinespace
+                                  & \multicolumn{4}{c}{2 girls}        \\
+Number of women\tnote{a}          &             & 1,000   &         &   863   \\
+Births\tnote{c}                   &       695   &   600   &   690   &   661   \\
+Percentage boys                   &      65.5   &  62.4   &  62.0   &  61.7   \\
+Sex ratio (boys per 100 girls)    &     189.6   & 166.0   & 163.4   & 161.0   \\
+\bottomrule
+\end{tabular}                        
+\begin{tablenotes} \tiny
+\item \hspace*{-0.5em} \textbf{Note.} 
+The simple models are estimated using logit on all births for a given parity that
+occurred during the relevant time period.
+The hazard models are estimated using all spells that began in the relevant time period.
+For the second birth the hazard model covers the period from beginning of spell to 6 
+years (24 quarters) after the birth of the first child.
+For the third birth it covers the period from beginning of spell to 7.25 years 
+(29 quarters) after the birth of the second child for the period 1985--1994 and from 
+beginning of spell to 5.75 years (23 quarters) after the birth of the second child for 
+the period 1995--2006.
+\item[a] Number of women in period who began the spell with given sex composition of prior 
+child/children in the relevant period.
+\item[b] For Logit model the number of women who are observed to have a second birth
+in the period. 
+For hazard model the predicted number of second births that will occur between beginning 
+of the spell and 6 years (24 quarters) after the birth of the first child.
+% \item[c] Number of women in period who had one boy and one girl as their first two children.
+\item[c] For Logit model the number of women who are observed to have a third birth
+in the period. 
+For hazard model the predicted number of third births that will occur between beginning of 
+the spell and 7.25 years (29 quarters) after the birth of the second child for the
+1985--1994 period and between beginning of the spell and 5.75 years (23 quarters) after 
+the birth of the second child for the 1995--2006 period.
+\end{tablenotes}
+\end{threeparttable}
+\end{footnotesize}
+\end{center}
+\end{table}
+
+I focus on those cases where there is evidence of sex-selective abortions: the spells
+from parity one to two and two to three for women with eight or more years of education.%
+\footnote{
+The results for the spell from parity three to four are available on request.
+They are not presented because the number of educated women who end up with three births 
+and the probability of having a fourth birth are small, which makes
+comparing the simple and hazard models with any precision difficult.
+}
+Table \ref{tab:compare2} shows the number of women who enter the second and third spells
+for the hazard model,
+the number of births, observed in the case of the simple model and predicted in the case 
+of the hazard model, predicted percent boys, and the associated predicted sex ratio.
+It is possible for the number of births used for the simple model to be larger than the
+hazard models' predicted number of births because the simple model is based
+on all births that occurred in the period---independently of when the prior birth
+occurred---whereas the hazard model uses only spells that began in the period.
+
+For the 1985--1994 period---which is when sex selection become available---the 
+hazard model consistently predicts a higher sex ratio than the logit model.
+Furthermore, some of these differences are substantial.
+For urban women with 2 girls as their first two children, the hazard model
+predicts a sex ratio of 175 boys per 100 girls, whereas the simple method
+``only'' predicts 155 boys per 100 girls.
+The difference is smaller in rural areas but still 14 boys per 100 girls
+higher for the hazard model than for the simple model.
+A similar, if less pronounced pattern, show up for the second birth,
+where the hazard model predict 3 and 5 boys more per 100 girls for
+urban and rural women.
+
+For the latest period, 1995--2006, the hazard model still produces higher 
+predicted sex ratios for second birth and the differences are of a 
+similar magnitude to the 1985--1994 period.
+The predicted sex ratios for the third birth are, however, 
+higher for the simple model than for the hazard model.
+This difference is substantially for urban women where the difference 
+is 23 boys extra per 100 girls.
+
+A possible explanation for these differences is that the simple model 
+fails to capture the move towards lower fertility and the subsequent 
+increase in the use of sex-selective abortions at earlier parities that 
+occurred over the periods.
+The results also suggest that the take-up of sex selection occurred 
+rapidly as the new methods became available and that this take-up
+is not fully captured by the simple model.
+More broadly, a possible interpretation of the differences is that
+the simple model will tend to underestimate when sex-selective abortions
+are initially spreading in use and overestimate when the spread of sex 
+selection is slowing.
+This is most clearly seen for the third births for urban women where
+the hazard model show a \emph{decline} is use of sex-selective abortions,
+consistent with the lower fertility as discussed in the main paper,
+while the simple model show a substantial increase.
 

### 2017-04-06 tables/predictedFertility.tex
Further edits of theory part; moved tables out of doc; moved comparison back to appendix

\begin{table}[htbp]
\begin{center}
\begin{scriptsize}
\begin{threeparttable}
\caption{Predicted Fertility Behavior, Sex Ratio, and \protect\linebreak
Abortions for Women with 8 or More Years of Education}
\label{tab:predicted}
\begin{tabular} {@{} l D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1} D{.}{.}{2.1}  @{}} \toprule
                 & \multicolumn{4}{c}{1972-1984}                                                               & \multicolumn{4}{c}{1985-1994}                                                               & \multicolumn{4}{c}{1995-2006} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9} \cmidrule(lr){10-13}
                 & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      & \mco{Births (\%)}          & \mct{Abortions per 100}                      & \mco{Boys}      \\
                 & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      & \mco{/ fertility\tnote{a}} & \mco{births\tnote{b}} & \mco{women\tnote{c}} & \mco{(\%)}      \\
\midrule
\bf Urban        & \multicolumn{12}{c}{} \\                                                                    
Spell 2          &       85.9   &  2.0    &  1.8    &  52.3   &       78.2   &  4.7    &  3.7  &  53.7   &       68.0   &  8.0    &  5.4   &  55.3      \\
Spell 3          &       64.4   &  5.1    &  3.3    &  53.9   &       49.9   &  9.8    &  4.9  &  56.2   &       38.6   &  7.8    &  3.0   &  55.3      \\
Spell 4          &       57.0   &  2.8    &  1.6    &  52.6   &       44.8   &  2.6    &  1.1  &  52.6   &       33.7   &  21.8   &  7.3   &  62.3      \\
Overall\tnote{d} &       2.7    &  2.0    &  5.5    &  52.3   &       2.3    &  3.4    &  8.0  &  53.1   &       2.0    &  4.6    &  9.4   &  53.7      \\
\addlinespace 
\bf Rural        & \multicolumn{12}{c}{} \\                                                                                  
Spell 2          &       92.5   &  -1.4   &  -1.3   &  50.5   &       87.6   &  3.1    &  2.7  &  52.8   &       83.1   &  4.4    &  3.6   &  53.5      \\
Spell 3          &       80.9   &  2.6    &  2.1    &  52.5   &       70.6   &  6.5    &  4.6  &  54.5   &       59.6   &  10.6   &  6.3   &  56.7      \\
Spell 4          &       75.7   &  -3.1   &  -2.4   &  49.6   &       62.0   &  0.2    &  0.1  &  51.3   &       51.9   &  6.1    &  3.2   &  54.4      \\
Overall\tnote{d} &       3.2    &  -0.3   &  -1.1   &  51.2   &       2.9    &  2.4    &  6.8  &  52.8   &       2.6    &  4.1    &  10.5  &  53.4      \\
\bottomrule
\end{tabular}                        
\begin{tablenotes} \tiny
\item \hspace*{-0.5em} \textbf{Note.} Predictions are based on estimates of equations 
(\ref{eq:probability_boy}) and (\ref{eq:probability_girl}).
The samples consist of all women from the data with 8 or more years of education who
married during the indicated period using the estimation results for that periods 
and the women's characteristics at the start of their marriage. 
All numbers presented are for women predicted to have one or more births.
Birth/progression rates are based on the ratio of women predicted to have a birth 
by the end of each spell.
Abortion rates within each spell are based on the predicted number of abortions each
woman would have if she went through the entire spell.
To generate conditions such as sex composition and fecundity for second and higher spells 
each woman is randomly assigned outcomes based on the estimation results and
her characteristics as follows.
For each quarter, her probabilities of having a boy, a girl, or no birth is calculated.
She is assigned one of these outcomes based on a random draw from a uniform distribution.
The first quarter where she has a draw that results in a birth she leaves the spell
and the quarter reached is used to calculate her starting age for the subsequent spell.
If she has no draw that result in a birth within a spell her childbearing stops and
she does not enter the next spell.
Results are averaged over 1,000 repetitions.
\item[a] For individual spells the column shows the percent of women who started the
spell and ended up with a birth by the end of the spell period covered.
For the ``Overall'' row, the number is the expected number of children born per woman over 
the first four spells, conditional on having at least one birth.
\item[b] For individual spells the column shows the number of abortions per 100
births predicted to take place by the end of the spell.
For the ``Overall'' row, the number is the total number of abortion per 100 births 
predicted to take place over all four spells.
\item[c]  For individual spells the column shows the number of abortions 
predicted to take place by the end of the spell per 100 women who started the spell .
For the ``Overall'' row, the number is the total number of abortion 
predicted to take place over all four spells per 100 women who had at least one child.
\item[d] Covers first through fourth spells. 
\end{tablenotes}
\end{threeparttable}
\end{scriptsize}
\end{center}
\end{table}

### 2017-04-06 paper/sexSelectionSpacing-ver1.tex
Editing estimation strategy section

@@
 
-As the discussion above shows there are three main
-implications of the availability of sex-selective abortions
+To improve on the literature's current approaches to understanding 
+son preference, a new empirical method must be able to capture the 
+three main implications of the availability of sex-selective abortions
 combined with son preference:
-a higher probability that next child is a son, 
+a higher probability that the next child is a son, 
 longer spacing to next birth with use of sex selection, 
 and that the use of prenatal sex determination may change between 
-one observed birth and the next.
-All three must be incorporated into the estimation strategy
-to provide unbiased and precise estimates of the use of sex-selective abortions.%
-
-To understand son preference when sex selection is available,
-we need an empirical model that can jointly estimate the sex of
-children born and the spacing between birth.
-
-The empirical model is a discrete time non-proportional competing risk hazard model with 
-two exit states: either a boy or a girl is born.%
+one observed birth and the next.%
+\footnote{
+In addition, it should be able to capture the shorter spacing between
+births observed in the absence of use or availability of prenatal 
+sex determination.
+}
+This means that we need an empirical model that can jointly estimate 
+the association between covariates and both the sex of children born 
+and the spacing from last birth. 
+My proposed model is a discrete time, non-proportional competing risk 
+hazard model with two exit states: either a boy or a girl is born.%
 \footnote{
@@
 }
-A woman's reproductive life is divided into spells which each covers 
+
+I divide a woman's reproductive life into spells that each covers 
 the period between births (from marriage to first birth for the first spell).
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
-the spell continues until time $t_i$ when either a birth occurs or the spell is censored.
+the spell continues until time $t_i$ when either a birth occurs or the spell 
+is censored.%
+\footnote{
 The time of censoring is assumed independent of the hazard rate,
 as is standard in the literature.
-
+}
 There are two exit states: birth of a boy, $j=1$, or birth of a girl, $j=2$, and 
@@
 where $D_m = 1$ if $t=m$ and zero otherwise.
-This approach to modeling the baseline hazard is flexible and does not place overly strong 
-restrictions on the baseline hazard.
-
-Specifying the model as a proportional hazard model, i.e.\ one where explanatory variables 
-simply shift the hazard rates up or down independent of spell length, results in 
-greater efficiency provided the proportionality assumption holds.
-The problem is that the proportional hazard model does not allow covariates
-to have different effects over time within a spell and ignoring differences in the shape 
-of the hazard functions between different types of individuals can lead to substantial bias.
-It is highly unlikely, even in the absence of prenatal sex determination, that the 
-baseline hazards are the same across education levels, areas of residence, or sex 
-composition of previous births.
-The bias from the proportionality assumption is likely exacerbated by the 
+This approach to modeling the baseline hazard is flexible and does not place 
+overly strong restrictions on the baseline hazard.
+
+[TK I am not very satisfied with this explanation of the problems with
+proportionality and the associated bias; non-proportionality is required
+to capture changes in use of sex selection]
+
+In principle, specifying the model as a proportional hazard model, i.e.\ one 
+where covariates simply shift the hazard rates up or down independent of 
+spell length, is more efficient, but only provided that the proportionality 
+assumption holds.
+If the proportionality assumption does not hold, however, the result is
+a potentially substantial bias in estimates.
+The problem is that a proportional hazard model does not allow covariates
+to have different effects at different times within a spell and therefore
+cannot capture differences in the shape of the hazard functions between 
+different groups. 
+It is highly unlikely---even in the absence of prenatal sex determination---that 
+the baseline hazards are the same across education levels, areas of residence, 
+or sex composition of previous births.
+Any bias from the proportionality assumption is likely exacerbated by the 
 introduction of prenatal sex determination for two reasons.
-First, one of the main points of this paper is that use of sex-selective abortions 
-affects birth spacing, and use of sex selection differs across groups.
-Second, as discussed above, the use of sex selection may vary within a spell depending
-on the length of the spell.
-
-I therefore use a non-proportional model where the main 
-explanatory variables and the interactions between them are interacted with the baseline hazards.
+First, one of the main points of this paper is that use of sex-selective 
+abortions affects birth spacing, and use of sex selection differs across groups.
+Second, as discussed above, the use of sex selection may vary within a spell,
+depending on the length of the spell.
+
+I therefore use a non-proportional model where the main explanatory variables 
+and the interactions between them are interacted with the baseline hazards.
 This is captured by the $Z$ set of explanatory variables
@@
 composition of previous children, if any, and $Z_2$ captures area of residence.
-This allows the effects of the main explanatory variables 
-on the probabilities of having a boy, a girl, or no birth to vary over time within a spell.
+This allows the effects of the main explanatory variables on the probabilities 
+of having a boy, a girl, or no birth to vary over time within a spell.
 The use of a non-proportional specification, together with a flexible baseline hazard, 
@@
 The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
-% %
-% \footnote{
-% It is possible to incorporate time-variant characteristics of the explanatory
-% variables in this set-up, but none of the explanatory variable change within a spell here.
-% }
-To further minimize any potential bias from assuming proportionality, estimations are 
-done separately for different levels of mothers' education and for different time periods.
+To further minimize any potential bias from assuming proportionality, estimations 
+are done separately for different levels of mothers' education and for different 
+time periods.
 The exact specifications and the individual variables are described below.
@@
 Hence, if the data are transformed so the unit of analysis is spell unit rather 
-than the individual woman, the model can be estimated using a standard multinomial logit model.%
+than the individual woman, the model can be estimated using a standard multinomial 
+logit model.%
 \footnote{
@@
 In the reorganized data the outcome variable is zero if the
-woman does not have a child in a given period, one if she gives birth to a son in that period,
-and two if she gives birth to a daughter in that period.
-
-Direct interpretation of the estimated coefficients for this model is challenging because 
-of the competing risk setup.
-First, coefficients show the change in hazards relative to the base outcome, no birth, 
-rather than simply the hazard of an event.
+woman does not have a child in a given period, one if she gives birth to a son 
+in that period, and two if she gives birth to a daughter in that period.
+
+The main downside of my approach is that direct interpretation of the estimated 
+coefficients for this model is challenging because of the competing risk setup.
+First, coefficients show the change in hazards relative to the base outcome, 
+no birth, rather than simply the hazard of an event.
 Second, a positive coefficient does not necessarily imply that an increase in a
@@
 
-The model does, however, make it straightforward to calculate the 
-predicted probabilities of having a boy and of having a girl for each $t$, conditional
-on a set of explanatory variables and not having had a child before that period.
-The predicted probability of having a boy in period $t$ for a given set of explanatory
-variable values, $\mathbf{Z}_k$ and $\mathbf{X}_k$, is
+It is, however, straightforward to calculate the predicted probabilities of 
+having a boy and of having a girl for each $t$ within a spell, conditional on 
+a set of explanatory variables and not having had a child before that period.
+The predicted probability of having a boy in period $t$ for a given set of 
+explanatory variable values, $\mathbf{Z}_k$ and $\mathbf{X}_k$, is
 \begin{equation}
@@
 \end{equation}
-and the associated confidence interval for given values of explanatory variables.%
+together with the associated confidence interval for given values of explanatory 
+variables.%
 \footnote{
@@
 For ease of exposition the procedure is presented here in two steps, but the actual
-calculation of the percent boys is done in one step with the 95 percent confidence interval 
-calculated using the Delta method.
+calculation of the percent boys is done in one step with the 95 percent confidence 
+interval calculated using the Delta method.
 Results are presented as the estimated percent boys born by length of birth spacing
@@
 
-Another important aspect of the hazard model is the survival curve, which shows the 
-probability of not having had a birth yet by spell duration.
-The survival curve for $t$ is 
+[TK  may need to combine with and without sons to show differences in spacing 
+over time; maybe it should also have predicted average/median spacing with some 
+confidence intervals to test]
+
+The other important part of the model is the spacing between births.
+Spacing is captured by the survival curve, which shows the probability of not 
+having had a birth yet by spell duration.
+The survival curve at time $t$ is 
 \begin{equation}
@@
 
-[This need a much better explanation; the survival curve captures the spacing
-between births and how long it takes; may need to combine with and without
-sons to show differences in spacing over time; maybe it should also have
-predicted average/median spacing with some confidence intervals to test]
-
-The survival curves are presented for two reasons.
-First, they show progression to the next birth and how quickly 
-it occurs, if at all.
 In the absence of sex selection, I expect most parities to show an 
@@
 
-Secondly, the survival curves provide ``weighting'' for the associated percentage 
-boys born.
+Furthermore, the survival curves also provide ``weighting'' for the 
+associated percentage boys born.
 The steeper the survival curve, the more weight should be assigned to a given

### 2017-04-10 paper/sexSelectionSpacing-ver1.tex
Edits of Data section and try new intro

@@
 
-\title{Sex-Selective Abortions and Birth Spacing
+\title{Son Preference, Sex-Selective Abortions, and Birth Spacing
 \protect\thanks{%
@@
 
-The males-to-females ratio at birth increased dramatically over the last three 
-decades in India as access to prenatal sex determination expanded.%
+Understanding and measuring son preference has been an important research 
+area for decades and---with increases in many countries' male-to-female ratios 
+at birth---is as salient as ever.
+India, for example, has seen
+
+Initial research relied on how birth spacing and the likelihood of stopping 
+childbearing differed across births of sons versus daughters to establish 
+son preference.
+With the introduction of prenatal sex determination the sex of children
+born was
+
+%
 \footnote{
@@
 }
+
 Our understanding of the use of sex selection is, however, constrained by 
@@
 
-Furthermore, the survival curves also provide ``weighting'' for the 
-associated percentage boys born.
+In addition to information about spacing, the survival curves also provide 
+``weighting'' for the associated percentage boys born.
 The steeper the survival curve, the more weight should be assigned to a given
@@
 }
-The International Institute for Population Sciences in Mumbai collected the data,
-which have nationwide coverage.
 The surveys are large: NFHS-1 covered 89,777 ever-married women 
@@
 as Sikhs, assuming that the baseline hazard is the same would lead to bias.
-The other groups are, however, each so small relative to Hindus that it is not
+The other groups are each so small relative to Hindus that it is not
 possible to estimate different baseline hazards for each group.
@@
 Second, no other surveys cover as long a period in the same amount of detail.
-The three NFHS rounds allow me to show the development from before sex-selective 
-abortions were available until 2006.
+The three NFHS rounds allow me to show the development in spacing and 
+sex ratio from before sex-selective abortions were available until 2006.
 Third, NFHS has birth histories for a large number of women.%
@@
 the result of systematic recall error.
-As shown in the online Appendix, the observed sex ratio by parity becomes more male dominated the 
-further back births took place.
+As shown in the online Appendix, the observed sex ratio by parity becomes more male 
+dominated the further back births took place.
 In addition, births in the same cohort tend to be more male dominated the more recent the 
@@
 parities.
-Based on the differences between surveys the cut-off points I use vary by survey round.
+I therefore use different cut-off points by survey round.
 For NFHS-1 women married 22 years or more were dropped, with the corresponding cut-off 
@@
 I chose these variables because the prior literature shows that they affect 
-fertility and spacing choices and because the prior literature on sex selection indicates 
+spacing choices and because the prior literature on sex selection indicates 
 that these are correlated with sex selection.
-The second group of variables are those expected to have a proportional effect on the 
-hazard: age of the mother at the beginning of the spell, length of her first spell 
-(for second spell and above), whether the household owns land, and whether the household 
-belongs to a scheduled tribe or caste.
+The second group of variables are those expected to have an approximately 
+proportional effect on the hazard: age of the mother at the beginning of the spell, 
+length of her first spell (for second spell and above), whether the household owns 
+land, and whether the household belongs to a scheduled tribe or caste.
 
@@
 the negative effect of higher opportunity cost on fertility more than outweighing the 
-positive effect of higher income \citep{schultz97}.%
+positive effect of higher income \citep{schultz97}.
+Higher education should therefore be associated with higher use of sex selection.%
 \footnote{
@@
 }
-Higher education should therefore be associated with higher use of sex selection.
 I divide women into three education groups:
 no education, 1 to 7 years of education, and 8 and more years of education.
-The models are estimated separately for each education level.
+The models are estimated separately for each education level.%
+\footnote{
 A potential concern here is reverse causation, where the sex of children
@@
 concern here.
+}
 
 As discussed, the sex composition of previous children affects both the timing
-of fertility and the use of sex-selective abortions.
-Here I capture sex composition of previous children by dummy variables for the
+of births and the use of sex-selective abortions.
+I capture sex composition of previous children with dummy variables for the
 possible combinations for the specific spell, ignoring the ordering of births.
@@
 }
-Area of residence captures both access to prenatal sex determination techniques 
-and the cost of children.
 The cost of children is higher in urban areas than in rural and access to prenatal
-sex determination is easier;
-both are expected to lead to greater use of sex-selective abortions in urban than 
-in rural areas.
+sex determination is easier, and both are expected to be associated with
+greater use of sex-selective abortions in urban than in rural areas.
 Because of concerns about selective migration I use where the household was living
@@
 
-The sex composition of children, area of residence, and their interactions
-are interacted with the piece-wise linear baseline hazard dummies.
+The sex composition of children, area of residence, and the interactions between
+these are all interacted with the piece-wise linear baseline hazard dummies.
 In other words, the baseline hazards are assumed to be different depending on
@@
 first child a girl in rural area, first child a girl in urban area).
-Although this approach substantially increases the number of regressions and estimated parameters it
-reduces the potential problem of including other variables as proportional effects.
-In addition, it forces attention to how much data are really available to estimate
-the determinants of sex-selective abortions.
+Although this approach substantially increases the number of regressions and 
+estimated parameters it reduces the potential problem of including other variables 
+as proportional effects.
 
@@
 Most Indian women do not use contraception before the first birth
-and there is pressure to show that a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
+and there is pressure to show that a newly married woman can conceive 
+\citep{dyson83,Sethuraman2007,Dommaraju2009}.
 This is confirmed by the very short spells between marriage and first birth,
@@
 Hence, a long spell between marriage and first birth is likely due to low fecundity.
-The expected effect of a longer first spell is to reduce sex-selective abortions in subsequent spells.
-For both this variable and the age of the mother at the beginning of the spell the squares are also included.
+For both this variable and the age of the mother at the beginning of the spell 
+the squares are also included.
 The remaining variables are dummies for household ownership of land and membership

### 2017-04-10 paper/sexSelectionSpacing-ver1.tex
Editing hook in introduction

@@
 Understanding and measuring son preference has been an important research 
-area for decades and---with increases in many countries' male-to-female ratios 
-at birth---is as salient as ever.
-India, for example, has seen
-
-Initial research relied on how birth spacing and the likelihood of stopping 
-childbearing differed across births of sons versus daughters to establish 
-son preference.
-With the introduction of prenatal sex determination the sex of children
-born was
-
-%
+area for decades and is as salient as ever.
+India, for example, has seen dramatic increases in the males-to-females ratio 
+at birth over the last three decades as access to prenatal sex determination 
+expanded.%
 \footnote{
@@
 }
-
+Recent research suggests, however, that son preference in India, when measured 
+as ideally having more boys than girls, is decreasing over time and with 
+higher education \citep{bhat03,pande07}.%
+\footnote{
+This measure of son preference is commonly used in the literature. 
+See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
+}
+
+In the absence of prenatal sex determination, parents' only choice if they 
+want a son is to try for another pregnancy as soon as possible after
+the birth of a girl. 
+Hence, in the absence of sex-selective abortions, son preference  
+leads to a shorter duration until the next birth if the previous 
+birth was a daughter  
+\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
+The resulting shorter spacing is thought to be associated with worse 
+health outcomes for the girls 
+\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
+Parents are also more likely to cease childbearing after the birth of 
+a son than after a daughter \citep{ben-porath76b,Das1987,Arnold1997,clark00}.
+
+With the introduction of sex-selective abortions, parents can now abort
+a fetus of unwanted sex and the use of sex selection can therefore 
+directly provide us a picture of the degree of son preference.
 Our understanding of the use of sex selection is, however, constrained by 
 lack of information;
-there are no official data on sex selection, and the few surveys that ask about use of 
-sex selection show signs of serious under-reporting \citep{goodkind96}.
-
-With no direct information, researchers have relied on a simple method for establishing 
-factors that affect sex selection: use the sex of children born as the 
-dependent variable, and estimate the effects of variables on the probability of having a son.%
+there are no official data on sex selection, and the few surveys that ask 
+about use of sex selection show signs of serious under-reporting \citep{goodkind96}.
+With no direct information, researchers have relied on a simple method for 
+establishing factors that affect sex selection: use the sex of children born as 
+the dependent variable, and estimate the effects of variables on the probability 
+of having a son.%
 \footnote{
@@
 }
+
+Because of the potential health effects, most of the literature on spacing 
+for countries like India naturally focus on whether spacing was too short
+and used the shorter birth spacing after the birth of a girl than after the
+birth of a boy as a measure of the degree of son preference.
 
@@
 % [literature on birth spacing - why spacing is important]
-
-In the absence of sex-selective abortions, son preference often leads to a shorter duration 
-until the next birth if the previous birth was a daughter  
-\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
-The resulting shorter spacing is thought to be associated with worse health outcomes for
-the girls \citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
 
@@
 
-Recent research suggests that son preference in India, when measured as ideally having 
-more boys than girls, is decreasing over time and with higher education \citep{bhat03,pande07}.%
-\footnote{
-This measure of son preference is commonly used in the literature. 
-See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-In NFHS, and Demographic and Health Surveys in general, son preference is measured as part 
-of the general fertility questions.
-The first question is how many children a woman would have if she could choose exactly how 
-many.
-This if followed by the sex preference question:
-``How many of these children would you like to be boys, how many would you like to be girls 
-and for how many would the sex not matter?''
-}
-
 \section{The Interaction between Son Preference and Birth Spacing\label{sec:model}}
-
-In the absence of prenatal sex determination, parents' only choice if they 
-wanted a son was to try for another pregnancy as soon as possible after
-the birth of a girl. 
-This led to shorter spacing after the birth of a girl and what
-is known as differential stopping behavior, where parents were 
-more likely to cease childbearing after the birth of a son than
-after a daughter [TK add references here]. 
-As discussed above, the shorter spacing after the birth of a girl is 
-associated with worse health outcomes for both mother and children.
-Because of the potential health effects, most of the literature on spacing 
-for countries like India naturally focus on whether spacing was too short
-and used the shorter birth spacing after the birth of a girl than after the
-birth of a boy as a measure of the degree of son preference.
 

### 2017-04-12 paper/sexSelectionSpacing-ver1.tex
Edit first part of introduction

@@
 
-Understanding and measuring son preference has been an important research 
-area for decades and is as salient as ever.
-India, for example, has seen dramatic increases in the males-to-females ratio 
-at birth over the last three decades as access to prenatal sex determination 
-expanded.%
-\footnote{
-See \citet{das_gupta97}, \citet{Sudha1999},
-\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
-India is not alone; both China and South Korea saw
-significant changes in the sex ratio at birth \citep{Yi1993,park95}.
-}
-Recent research suggests, however, that son preference in India, when measured 
-as ideally having more boys than girls, is decreasing over time and with 
-higher education \citep{bhat03,pande07}.%
-\footnote{
-This measure of son preference is commonly used in the literature. 
-See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-}
-
-In the absence of prenatal sex determination, parents' only choice if they 
-want a son is to try for another pregnancy as soon as possible after
-the birth of a girl. 
-Hence, in the absence of sex-selective abortions, son preference  
-leads to a shorter duration until the next birth if the previous 
-birth was a daughter  
+The extent of son preference has been an important research area for 
+decades and is as salient as ever.
+Three approaches have been in widespread use in the literature:
+birth spacing, parity progression, and sex ratio \citep{Leung1988}.
+Before the availability of prenatal sex determination, parents' only choice 
+if they wanted a son was to try for another pregnancy as soon as possible 
+after the birth of a girl. 
+In that case, son preference leads to a shorter spacing from the birth
+of a daughter until the next birth   
 \citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
@@
 Parents are also more likely to cease childbearing after the birth of 
-a son than after a daughter \citep{ben-porath76b,Das1987,Arnold1997,clark00}.
+a son than after a daughter, resulting in a lower parity progression
+with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}.
+
+Sex ratio is the ratio of boys to girls measured for given ages, 
+or, after the introduction of prenatal sex determination, at birth.
+Deviation from the natural sex ratio is taken as an indication of sex preference
+leading to differential mortality and/or use of prenatal sex selection.
+
+India, for example, has seen dramatic increases in the males-to-females ratio 
+at birth over the last three decades as access to prenatal sex determination 
+expanded.%
+\footnote{
+See \citet{das_gupta97}, \citet{Sudha1999},
+\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
+India is not alone; both China and South Korea saw
+significant changes in the sex ratio at birth over the same period \citep{Yi1993,park95}.
+}
+
+Recent research suggests, however, that son preference in India, when measured 
+as ideally having more boys than girls, is decreasing over time and with 
+higher education \citep{bhat03,pande07}.%
+\footnote{
+This measure of son preference is commonly used in the literature. 
+See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
+}
 

### 2017-04-13 paper/sexSelectionSpacing-ver1.tex
Edit intro part

@@
 decades and is as salient as ever.
-Three approaches have been in widespread use in the literature:
+Three approaches have been in widespread use in this literature:
 birth spacing, parity progression, and sex ratio \citep{Leung1988}.
-Before the availability of prenatal sex determination, parents' only choice 
-if they wanted a son was to try for another pregnancy as soon as possible 
-after the birth of a girl. 
-In that case, son preference leads to a shorter spacing from the birth
-of a daughter until the next birth   
-\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
+Before prenatal sex determination became widely available, parents' only 
+option if they wanted a son was to try for another pregnancy as soon as 
+possible after the birth of a girl.
+A preference for sons can therefore lead to shorter spacing until next 
+birth after the birth of a daughter than after the birth of a son 
+\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
 The resulting shorter spacing is thought to be associated with worse 
@@
 with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}. 
-
-Sex ratio is the ratio of boys to girls measured for given ages, 
+Finally, increase in the sex ratio---the ration of boys to
+girls---can serve as an indication of son preference because 
+of differential mortality or underreporting \citep{sen90,sen92,Merli2000,anderson08}.
+
+ and/or use of prenatal sex selection
+
 or, after the introduction of prenatal sex determination, at birth.
-Deviation from the natural sex ratio is taken as an indication of sex preference
-leading to differential mortality and/or use of prenatal sex selection.
+In the absence of any interventions, the probability of having a son
+is approximately 0.512, which is independent of genetic factors 
+\citep{ben-porath76b,jacobsen99}.
+With fetus sex random, a statistically significant variable indicates an 
+association with use of sex-selective abortions \citep{retherford03b,jha06,abrevaya09}.
 
@@
 
-With the introduction of sex-selective abortions, parents can now abort
-a fetus of unwanted sex and the use of sex selection can therefore 
-directly provide us a picture of the degree of son preference.
 Our understanding of the use of sex selection is, however, constrained by 

### 2017-04-19 paper/sexSelectionSpacing-ver1.tex
Minor edits

@@
 
-\title{Son Preference, Sex-Selective Abortions, and Birth Spacing
+\title{Son Preference, Sex-Selective Abortions,\\ and Birth Spacing
 \protect\thanks{%
@@
 
-[ways to get at son preference:
-- stated fertility preferences
-- longer spacing after son
-- differential stopping behavior
-- biased sex ratio (overall before sex selection, and specifically at birth later)]
-
-[why do these work less well after introduction of sex selection?]
-
-[how can my method remedy those problems?]
-
-[main results]
-
-The extent of son preference has been an important research area for 
-decades and is as salient as ever.
-Three approaches have been in widespread use in this literature:
+% [ways to get at son preference:
+% - stated fertility preferences
+% - longer spacing after son
+% - differential stopping behavior
+% - biased sex ratio (overall before sex selection, and specifically at birth later)]
+% 
+% [why do these work less well after introduction of sex selection?]
+% 
+% [how can my method remedy those problems?]
+% 
+% [main results]
+
+Understanding and measuring son preference has been an important research 
+area for decades and is as salient as ever.
+[brief description of where identified]
+Three approaches to measuring son preference have been in widespread use:
 birth spacing, parity progression, and sex ratio \citep{Leung1988}.
+
 Before prenatal sex determination became widely available, parents' only 
@@
 possible after the birth of a girl.
-A preference for sons can therefore lead to shorter spacing until next 
-birth after the birth of a daughter than after the birth of a son 
-\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
+A preference for sons is therefore often associated with shorter birth spacing 
+after the birth of a daughter than after the birth of a son 
+\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012}.
 The resulting shorter spacing is thought to be associated with worse 
@@
 with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}. 
-Finally, increase in the sex ratio---the ration of boys to
-girls---can serve as an indication of son preference because 
-of differential mortality or underreporting \citep{sen90,sen92,Merli2000,anderson08}.
-
- and/or use of prenatal sex selection
-
-or, after the introduction of prenatal sex determination, at birth.
-In the absence of any interventions, the probability of having a son
-is approximately 0.512, which is independent of genetic factors 
-\citep{ben-porath76b,jacobsen99}.
-With fetus sex random, a statistically significant variable indicates an 
-association with use of sex-selective abortions \citep{retherford03b,jha06,abrevaya09}.
-
-India, for example, has seen dramatic increases in the males-to-females ratio 
-at birth over the last three decades as access to prenatal sex determination 
-expanded.%
-\footnote{
-See \citet{das_gupta97}, \citet{Sudha1999},
-\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
-India is not alone; both China and South Korea saw
-significant changes in the sex ratio at birth over the same period \citep{Yi1993,park95}.
-}
-
-Recent research suggests, however, that son preference in India, when measured 
-as ideally having more boys than girls, is decreasing over time and with 
-higher education \citep{bhat03,pande07}.%
-\footnote{
-This measure of son preference is commonly used in the literature. 
-See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-}
-
-Our understanding of the use of sex selection is, however, constrained by 
+Finally, increase in the ratio of males to females 
+can serve as an indication of son preference because 
+of differential mortality, for example because of the shorter
+birth spacing, or underreporting \citep{sen90,sen92,Merli2000,anderson08}.
+
+After the introduction of prenatal sex determination, a substantial
+literature has focused on the use of prenatal sex selection as a direct 
+measure of son preference.
+Our understanding of sex selection usage is, however, constrained by a
 lack of information;
@@
 about use of sex selection show signs of serious under-reporting \citep{goodkind96}.
-With no direct information, researchers have relied on a simple method for 
-establishing factors that affect sex selection: use the sex of children born as 
-the dependent variable, and estimate the effects of variables on the probability 
-of having a son.%
-\footnote{
-In the absence of any interventions, the probability of having a son
-is approximately 0.512, which is independent of genetic factors \citep{ben-porath76b,jacobsen99}.
-With fetus sex random, a statistically significant variable indicates an association with 
-use of sex-selective abortions.
-Examples of studies that have used this approach are \cite{retherford03b},
-\cite{jha06}, and \cite{abrevaya09}. 
-}
+With no direct information, researchers have instead used the sex of children 
+born as the dependent variable, and estimate the effects of variables on the 
+probability of having a son.
+The idea is that in the absence of any interventions, the probability of having 
+a son is approximately 0.512, and this is independent of genetic 
+factors \citep{ben-porath76b,jacobsen99}.
+With fetus sex random, a statistically significant coefficient therefore 
+indicates an association between the variable and use of sex-selective 
+abortions.
 Based on this simple method, we know that families with no sons are more likely to
@@
 
-Because of the potential health effects, most of the literature on spacing 
-for countries like India naturally focus on whether spacing was too short
-and used the shorter birth spacing after the birth of a girl than after the
-birth of a boy as a measure of the degree of son preference.
-
-I address an important questions that the prior literature has been unable
-to examine because of the simple method's limitations:
-how does birth spacing interact with use of sex-selective abortions?
-I introduce a novel method that directly incorporates that sex-selective 
-abortions affect both the likelihood of a son being born \emph{and} the duration between 
-births.
-I use the method to show how spacing between births play an important role in our 
-understanding of sex selection decisions.
-
-% [literature on birth spacing - why spacing is important]
-
-What has not previously been appreciated is that the introduction of sex-selective 
-abortions substantially changed the relationship between son preference and birth spacing.
-The change happens because each abortion significantly increases the duration until the
-next birth.
-The increase in duration can be divided into three parts starting from the time of
+What has not previously been appreciated, however, is that the introduction 
+of sex-selective abortions substantially changed the relationship between 
+son preference and birth spacing.
+The change happened because each abortion significantly increases the duration 
+until the next birth.
+This increase in duration can be divided into three parts starting from the time of
 the abortion.
@@
 Secondly, the average expected time to conception is about 6 months.
-Finally, sex determination tests are generally reliable only from 3 months of gestation onwards.
-The result is that each abortion delays the next birth by approximately a year.%
+Finally, sex determination tests are generally reliable only from 3 months 
+of gestation onwards.%
 \footnote{
@@
 boy and the fourth month if it a girl.
-
+}
+The result is that each abortion delays the next birth by approximately 
+a year.%
+\footnote{
 The waiting time to conception does vary by woman, but
@@
 How spacing interacts with sex selection is important for two reasons.
-First, 
-spacing, by itself, can no longer be used to predict son preference. 
-Because each abortions extends spacing by about a year, we now have a situation 
+First, spacing, by itself, can no longer be used to predict son preference. 
+Because each abortion extends spacing by about a year, we now have a situation 
 where the \emph{longest} spacing is likely observed for families with the 
@@
 % families have low desired fertility and access to sex-selective abortions!!!!
-Second, families may reverse their decision to use sex selection in-between births.
-A reversal could happen if they do not want the space between children to be 
-``too long'', or if there are concerns about possible infertility as a result of 
-too many abortions in a row without a birth.
+Second, if the duration from last birth becomes long enough, parents may 
+reverse their decision to use prenatal sex determination,
+and carry the next pregnancy to term whether male or female.
 Hence, for a given parity, the sample of women for whom we do observe a birth 
@@
 Hence, if decisions on sex selection change with duration since last birth,
-the predicted sex ratio for a parity using the simple method will be a 
+the predicted sex ratio for a parity using the current method will be a 
 biased estimate of the final observed sex ratio for the parity when 
 childbearing is complete.
-
-% [contribution of paper]
-[TK maybe not focus so much on the simple method but rather understanding son preference].
-The main contribution of this paper is the introduction and application of a method that 
-incorporates the decisions about birth spacing, and sex-selective abortions.
-The empirical model is a competing risk, non-proportional hazard model with two exit 
-states: either a boy or a girl is born.
-This approach has TK major advantages over the simple method
-
-Secondly, by explicitly incorporating censoring of birth spacing, it addresses any 
-potential bias from ignoring how sex selection decisions may change with duration from 
-the previous birth.
-
-None of these is possible using the simple method.
-
-% [EXPLAIN RESULTS HERE]
-% Main findings!
-I apply the method to birth histories from India's National Family and Health Surveys 
-for Hindu women covering the period 1972 to 2006. 
-There are three main findings.
-
-There is, however, still no evidence of sex selection being used on the first birth.
-
-Secondly, sex selection appears to be used for securing one son, rather than a large 
-number of sons.
-There is only limited use of sex-selective abortions for better-educated
-women with one or more sons.
-The exception is rural women with one son and one daughter, presumably to compensate for 
-the higher child mortality in rural areas.
-These results are in line with the differential stopping behavior observed in many studies
-before sex selection became available \citep{repetto72,arnold98,dreze01}.
-
-The method can better predict ``final'' sex ratios than the simple model
-
-\citep{Soest2012} for a recent example of spacing and son preference
-
-\section{The Interaction between Son Preference and Birth Spacing\label{sec:model}}
-
-With the introduction of sex-selective abortions, parents can now abort
-a fetus of unwanted sex.
-With an approximately 12 months additional duration per abortion,
-this can result in substantially longer durations between births, and
-``too long'' spacing may become a greater concern for parents than 
-``too short'' spacing.%
-\footnote{
-Shorter spacing was likely less of a concern to begin with for
-better educated mothers---who are also the most likely to use 
-sex selection---since their children are substantially less likely 
-to be negatively affected by short spacing than children of less 
-educated mothers \citep{Whitworth2002}.
-}
-If the duration from last birth becomes long enough, parents may 
-reverse their decision to use prenatal sex determination
-and carry the next pregnancy to term whether male or female.
 
@@
 from repeated abortions or the closer they are to the end of their 
-reproductive period, they more likely they are to decide that any 
-child is better than not having an additional child at all.
+reproductive period, they more likely they are to decide that a 
+child of any sex is better than not having a child at all.
 Second, the higher the parents' discount factor is---that is, the
@@
 
-For a given sex composition of prior children, there are two main drivers 
-of sex selection: the degree of son preference and the cost of sex selection.
-The more parents care about having a son as their next child, the more
-likely they are to use sex selection and the less likely they are to
-reverse the decision once started.
-The result is an increased number of abortions, more spells where a
-prenatal scan is used, and the spacing between births is longer.
-
-Lowering the cost of sex selection bias the overall sex ratio further 
-towards boys.
-Correspondingly, both the number of abortions per woman and the
-number of spells where a prenatal scan is used should also increase,
-resulting in longer average spacing between births.
-This increase in spacing is, however, not likely to be uniform across parities.
-In addition to increasing the overall sex ratio, lower cost of prenatal 
-scan should also lead to use of sex selection at earlier parities.
-It is therefore possible to see either no change or a \emph{decrease} 
-in average spacing for a later parity---although with a more than compensating 
-increase in an earlier parity.
-In other words, it is possible for individual parities to show a \emph{decline}
-in sex selection at the same time as the overall use goes up.
-This is an important caution against over-interpreting individual 
-parity results.
-
-Lowering the cost of prenatal sex determination generally leads to 
-a smaller percentage of parents who change their use of sex selection.
-But, the total number of spells with a change may still
-go up because lower cost of prenatal sex determination also
-increases the use of sex selection.
-
-If ``too long'' spacing leads parents to reverse their decision to use
-prenatal sex determination within a spell this has important implications 
-for the empirical method [TK explain what they are instead!].
-
-[TK find examples of the son preference spacing papers and look at what they did
-for "theory"]
+% [contribution of paper]
+% [TK maybe not focus so much on the simple method but rather understanding son preference].
+My main contribution here is the introduction and application
+of a novel method that directly incorporates that sex-selective 
+abortions affect both the likelihood of a son being born \emph{and} the 
+duration between births.
+[TK move to estimation strategy?]
+The empirical model is a competing risk, non-proportional hazard model with 
+two exit states: either a boy or a girl is born.
+This approach has TK major advantages over the simple method
+
+Secondly, by explicitly incorporating censoring of birth spacing, it addresses any 
+potential bias from ignoring how sex selection decisions may change with duration from 
+the previous birth.
+
+The method can better predict ``final'' sex ratios than the simple model
+
+None of these is possible using the simple method.
+
+I use the method to show how spacing between births has changed with
+the introduction prenatal sex determination and how birth spacing plays 
+an important role in our understanding of sex selection decisions and 
+son preferences.
+
+% [Why India?]
+I apply the method to birth histories from India's National Family and Health 
+Surveys for Hindu women covering the period 1972 to 2006. 
+India is a particularly interesting case.
+On one hand, India has seen dramatic increases in the males-to-females ratio 
+at birth over the last three decades as access to prenatal sex determination 
+expanded.%
+\footnote{
+See \citet{das_gupta97}, \citet{Sudha1999},
+\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
+India is not alone; both China and South Korea saw
+significant changes in the sex ratio at birth over the same period \citep{Yi1993,park95}.
+}
+On the other hand, recent research suggests, however, that son preference in 
+India, when measured as ideally having more boys than girls, is decreasing 
+over time and with higher education \citep{bhat03,pande07}.%
+\footnote{
+This measure of son preference is commonly used in the literature. 
+See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
+}
+
+% [EXPLAIN RESULTS HERE]
+% Main findings!
+There are three main findings.
+
+There is, however, still no evidence of sex selection being used on the first birth.
+
+Secondly, sex selection appears to be used for securing one son, rather than a large 
+number of sons.
+There is only limited use of sex-selective abortions for better-educated
+women with one or more sons.
+The exception is rural women with one son and one daughter, presumably to compensate for 
+the higher child mortality in rural areas.
+These results are in line with the differential stopping behavior observed in many studies
+before sex selection became available \citep{repetto72,arnold98,dreze01}.
+
+%------------------------------------------------------------------------------------
+
+\section{Estimation Strategy\label{sec:strategy}}
 
@@
 \citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level of 
-contraception---resulting in longer spacing---to avoid having 
+With less reliable contraception parents choose a higher level 
+of contraception---resulting in longer spacing---to avoid having 
 too many children by accident.
@@
 across education groups \citep{Tulasidhar1993,Whitworth2002}.
-
-% What are the model highlights 
-There are three main conclusions from the model.
-The increased use of sex selection shows up both in the 
-proportion of boys among births and longer spacing between 
-births---and the higher the parity the longer the duration between 
-births.
-The other factors, such as the price of sex selection, 
-discount factor, and son preference also affect the use
-of sex selection, but to a much smaller degree.
-Second, parents do reverse the use of sex selection, 
-both when they use sex selection relatively infrequently and when 
-they use it heavily.
-Reversal are more likely the more impatient parents are or the
-shorter time they have left in their reproductive horizon, which
-means that the longer the duration has been since the last birth
-the more likely they are to reverse their decision to use sex selection.
-Finally, the model shows that son preference in the number of
-children is not required for an unequal sex ratio.
-As long as parents are only willing to abort female fetuses, declining
-fertility will lead to increased use of sex selection to ensure 
-a balanced number of sons and daughters.
-
-% Empirical method
-The model highlights two major limitations of the simple 
-empirical method, which a better empirical approach needs to 
-allow for.
-First, increased use of sex selection leads to longer spacing which,
-everything else equal, reduces the number of births available for 
-estimation in the simple model and thereby lowers its precision
-because fewer parents will make it to a given parity by the time of the survey.
-Furthermore, the more intensively sex selection is used the larger 
-the decline in sample size.
-Second, by using only observed births the simple method cannot capture
-when parents change their decision on the use of sex selection;
-with a reversal the spell can still result in the birth of a girl.
-This last point is especially important when trying to establish whether 
-son preference has changed over time in a situation where the cost of prenatal 
-sex determination has likely \emph{increased} over time because of the PNDT act.
-As I show an increase the cost of prenatal sex determination does 
-decrease the sex ratio and lower the number of abortions, but 
-it also \emph{increases} the likelihood that parents change their initial
-decision to use sex selection within a spell.
-
-%------------------------------------------------------------------------------------
-
-\section{Estimation Strategy\label{sec:strategy}}
 

### 2017-05-24 paper/sexSelectionSpacing-ver1.tex
Work on new introduction
- Simple edits of main paper
- New intro in notes.txt

@@
 
-\title{Son Preference, Sex-Selective Abortions,\\ and Birth Spacing
+\title{Son Preference, Birth Spacing, and Sex-Selective Abortions%
 \protect\thanks{%
@@
 Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-University of Washington, University of \AA{}rhus, the Fourth 
+University of Washington, University of Aarhus, the Fourth 
 Annual Conference on Population, Reproductive Health, 
@@
 % Demography abstract
-\noindent This paper addresses the question:
-how does birth spacing interact with the use of sex-selective abortions? 
-I introduce a statistical method that incorporates how sex-selective abortions 
+\noindent This paper examines how birth spacing interact with the use of 
+sex-selective abortions. 
+I introduce a statistical method that incorporates that sex-selective abortions 
 affect both the likelihood of a son and spacing between births.
 Using India's National Family and Health Surveys,
-I show that use of sex selection leads to longer spacing after a daughter is born.
-Women with 8 or more years of education, both in urban and rural areas, are the main users 
-of sex-selective abortions.
-Women with less education do not appear to use sex selection.
+I show that use of sex selection leads to \emph{longer} spacing after a daughter 
+is born.
+Women with 8 or more years of education, both in urban and rural areas, are 
+the main users of sex-selective abortions, whereas women with less education 
+do not appear to use sex selection.
 Predicted lifetime fertility for high-education women declined more than 10\% 
-between 1985--1994, when sex selection was legal, and 1995--2006, when sex selection was illegal.
+between 1985--1994, when sex selection was legal, and 1995--2006, when sex selection 
+was illegal.
 Abortions per woman increased almost 20\% for urban women and 50\%
-for rural women between the two periods, suggesting that making sex selection illegal has 
-not reversed its use.
-Finally, sex selection appears to be used to ensure one son rather than multiple sons.
+for rural women between the two periods, suggesting that making sex 
+selection illegal has not reversed its use.
+Finally, sex selection appears to be used to ensure one son rather 
+than multiple sons.
 
@@
 
-Understanding and measuring son preference has been an important research 
-area for decades and is as salient as ever.
-[brief description of where identified]
-Three approaches to measuring son preference have been in widespread use:
-birth spacing, parity progression, and sex ratio \citep{Leung1988}.
-
-Before prenatal sex determination became widely available, parents' only 
-option if they wanted a son was to try for another pregnancy as soon as 
-possible after the birth of a girl.
-A preference for sons is therefore often associated with shorter birth spacing 
-after the birth of a daughter than after the birth of a son 
+The effects of son preference has been an active research area for decades.
+Before prenatal sex determination, a preference for sons was often associated 
+with shorter birth spacing after the birth of a daughter than after the 
+birth of a son, because that was the only way to achieve a son 
 \citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012}.
-The resulting shorter spacing is thought to be associated with worse 
-health outcomes for the girls 
+The resulting shorter spacing is associated with worse health outcomes 
+for the girls 
 \citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.

### 2017-05-28 paper/sexSelectionSpacing-ver1.tex
Move new Introduction into paper

@@
 
-% [ways to get at son preference:
-% - stated fertility preferences
-% - longer spacing after son
-% - differential stopping behavior
-% - biased sex ratio (overall before sex selection, and specifically at birth later)]
-% 
-% [why do these work less well after introduction of sex selection?]
-% 
-% [how can my method remedy those problems?]
-% 
-% [main results]
-
-The effects of son preference has been an active research area for decades.
-Before prenatal sex determination, a preference for sons was often associated 
-with shorter birth spacing after the birth of a daughter than after the 
-birth of a son, because that was the only way to achieve a son 
-\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012}.
-The resulting shorter spacing is associated with worse health outcomes 
-for the girls 
-\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
-Parents are also more likely to cease childbearing after the birth of 
-a son than after a daughter, resulting in a lower parity progression
-with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}. 
-Finally, increase in the ratio of males to females 
-can serve as an indication of son preference because 
-of differential mortality, for example because of the shorter
-birth spacing, or underreporting \citep{sen90,sen92,Merli2000,anderson08}.
-
-After the introduction of prenatal sex determination, a substantial
-literature has focused on the use of prenatal sex selection as a direct 
-measure of son preference.
-Our understanding of sex selection usage is, however, constrained by a
-lack of information;
-there are no official data on sex selection, and the few surveys that ask 
-about use of sex selection show signs of serious under-reporting \citep{goodkind96}.
-With no direct information, researchers have instead used the sex of children 
-born as the dependent variable, and estimate the effects of variables on the 
-probability of having a son.
-The idea is that in the absence of any interventions, the probability of having 
-a son is approximately 0.512, and this is independent of genetic 
-factors \citep{ben-porath76b,jacobsen99}.
-With fetus sex random, a statistically significant coefficient therefore 
-indicates an association between the variable and use of sex-selective 
-abortions.
-Based on this simple method, we know that families with no sons are more likely to
-use sex selection the higher the parity;
-that use of sex selection increases with socioeconomic status, especially education;
-and that sex selection is more widespread in cities than in rural areas 
-\citep{retherford03b,jha06,abrevaya09}.%
-\footnote{
-There is substantial disagreement on whether sex-selective abortion is used for the 
-first birth \citep{retherford03b,jha06}.
-}
-
-What has not previously been appreciated, however, is that the introduction 
-of sex-selective abortions substantially changed the relationship between 
+Spacing between births has long been used as a measure of son preference 
+\citep{Leung1988}.
+Before prenatal sex determination became available, the only recourse for
+parents who wanted a son, but did not yet have one, was to have the 
+next birth sooner.
+The result was shorter average spacing after the births of girls than boys,
+and worse health outcomes for girls.%
+\footnote{
+See, for example, 
+\citet{Das1987}, \citet{Rahman1993}, \citet{Pong1994}, \citet{Haughton1996},
+\citet{Arnold1997}, and \citet{Soest2012} on shorter birth spacing after
+girls
+and 
+\citet{arnold98}, \citet{Whitworth2002}, \citet{Rutstein2005},
+and \citet{Conde-Agudelo2006} on the association between shorter birth
+spacing and worse health outcomes for girls.
+Parents were also more likely to cease childbearing after the birth of 
+a son than after a daughter 
+\citep{ben-porath76b,Das1987,Arnold1997,clark00,filmer09,Altindag2016}
+}
+
+What has not previously been appreciated is that the introduction 
+of prenatal sex determination substantially changed the relationship between 
 son preference and birth spacing.
-The change happened because each abortion significantly increases the duration 
-until the next birth.
-This increase in duration can be divided into three parts starting from the time of
-the abortion.
+The issue is that each sex-selective abortion increases the duration between 
+observed births by approximately a year.%
+\footnote{
+This increase consists of three parts starting from the time of the 
+abortion.
 First, the uterus needs at least two menstrual cycles to recover 
@@
 of a spontaneous abortion \citep{zhou00b}.
-Secondly, the average expected time to conception is about 6 months.
+Second, an average of 6 months to next conception \citep{Wang2003}.
 Finally, sex determination tests are generally reliable only from 3 months 
-of gestation onwards.%
-\footnote{
-There are three well-developed technologies for determining a fetus' sex: 
-Chorionic villus sampling (CVS), amniocentesis, and ultrasound.
-CVS can be applied after the shortest period
-of gestation (8 to 12 weeks).
-It is the most complicated, but also the most reliable, and an abortion can be done in 
-the first trimester.
-Amniocentesis can be performed after fourteen weeks, but requires three to four weeks
-before the result is available, so an abortion cannot be performed until more than 
-halfway through the second trimester.
-Ultrasound has the advantages of being non-invasive and relatively cheap but 
-is associated with higher risk of faulty sex determination if done early.
-Generally, a fetus' sex can be determined in the third month of gestation if it is a
-boy and the fourth month if it a girl.
-}
-The result is that each abortion delays the next birth by approximately 
-a year.%
-\footnote{
-The waiting time to conception does vary by woman, but
-even if it is very short, say one  month, the minimum additional space between
-births would be 6 months per abortion.
-For a discussion of time to conception see \citep{Wang2003}
-}
-
-% [why this matters]
+of gestation onwards.
+These three parts add up to 12 months.
+The waiting time to conception does vary by woman, but even if it is very 
+short, say one  month, the additional space between births would still
+be 6 months per abortion.
+}
+We therefore now have a situation where families with the \emph{strongest} son 
+preference likely show the \emph{longest} spacing after the birth of a daughter.
+But, to further complicate matters, we may still observe short spacing 
+after the birth of daughter as a representation of son preference for 
+families who---for one reason or another---do not use prenatal sex selection.
+In this paper, I introduce and apply a novel method that
+directly incorporates the effects of sex-selective abortions on
+the likelihood of a son being born \emph{and} the duration between births.
+The method can be used to analyse both situations with and without prenatal
+sex selection.
+
 How spacing interacts with sex selection is important for two reasons.
-First, spacing, by itself, can no longer be used to predict son preference. 
-Because each abortion extends spacing by about a year, we now have a situation 
-where the \emph{longest} spacing is likely observed for families with the 
-strongest son preference.
-To further complicate matters, 
-we may still observe short spacing after the birth of daughter as a representation 
-of son preference for families who either have less access to sex-selective 
-abortions or are willing to have more children.
-Spacing is still important and useful in understanding sex selection and son
-preference, but only if combined with the outcome of that spacing---in other words 
-the likelihood of observing a boy or a girl.
-
-% using spacing itself to predict son preference becomes useless if
-% families have low desired fertility and access to sex-selective abortions!!!!
-Second, if the duration from last birth becomes long enough, parents may 
-reverse their decision to use prenatal sex determination,
+First, spacing, by itself, can no longer be used to measure son preference. 
+Spacing is still important and useful in understanding son preference, but 
+only if combined with the likelihood of observing a boy or a girl.
+Short spacing after a girl is indicative of son preference if observed
+births are close to the natural sex ratio, whereas long spacing is indicative
+of son preference if observed births are male biased.
+
+Second, the duration since last birth may affect the decision on sex selection.
+For example, as the duration from last birth becomes long enough, parents 
+may reverse their decision to use prenatal sex determination,
 and carry the next pregnancy to term whether male or female.
-Hence, for a given parity, the sample of women for whom we do observe a birth 
-may behave differently from the sample of women who have not yet had a birth.
-This is a problem because births to women with shorter spacing are more likely 
-to be in the survey for a given parity.
-Hence, if decisions on sex selection change with duration since last birth,
-the predicted sex ratio for a parity using the current method will be a 
-biased estimate of the final observed sex ratio for the parity when 
-childbearing is complete.
-
-A number of factors make a reversal of the decision to use sex 
-selection between one birth and the next more likely, 
-everything else equal.
-First, the more concerned parents are about possible infertility 
-from repeated abortions or the closer they are to the end of their 
-reproductive period, they more likely they are to decide that a 
-child of any sex is better than not having a child at all.
-Second, the higher the parents' discount factor is---that is, the
-more the value present outcomes relative to future outcomes---the
-more likely they are to reverse their decision to sex selection.
-Third, economies of scale in childrearing---both in terms of time cost 
-and direct cost---are easier to take advantage of if births 
-are closer \citep[p 947]{Newman1984}.
-Hence, the stronger these economies of scale are, the more likely
-parents are to reverse their decision to use sex selection.
-Finally, if women's wages increase with age, parents prefer
-to have their children early and close together while 
-the opportunity cost of children is lower \citep{Heckman1976}.%
-\footnote{
-The time needed to care for young children can also impact 
-timing if skills depreciate when out of the labor market \citep{Happel1984}.
-Whether depreciation leads to longer or shorter spacing depends
-on the specification of the depreciation function.
-See also the discussion in \citet[p 315]{Hotz1997}
-and references therein.
-}
-The more pronounced the increase in wage is with age, the more 
-attractive it will be to reverse the decision to use sex selection.
-Although the latter two factor are most often associated with the literature
-on shorter spacing in middle- and  high-income countries, 
-the increasing education and wealth in India means that a growing 
-portion of the population is likely to behave in a similar manner.%
-\footnote{
-The possible exception is for the first birth, where the pressure to show 
-fecundity---which shortens the duration to the first birth---is potentially 
-an important factor in India \citep{dyson83,Sethuraman2007,Dommaraju2009}.
-}
+Hence, by examining whether sex selection decisions change with
+spacing, we can draw a more nuanced picture of the degree of son preference.
 
@@
 two exit states: either a boy or a girl is born.
-This approach has TK major advantages over the simple method
-
-Secondly, by explicitly incorporating censoring of birth spacing, it addresses any 
-potential bias from ignoring how sex selection decisions may change with duration from 
-the previous birth.
-
-The method can better predict ``final'' sex ratios than the simple model
-
-None of these is possible using the simple method.
 

### 2017-05-30 paper/sexSelectionSpacing-ver1.tex
Restructure and edit Introduction
- move paper purpose to later
- move paper purpose to separate paragraph
- add application to India with brief outline of 3 periods
- minor edits for first two paragraphs

@@
 Before prenatal sex determination became available, the only recourse for 
-parents who wanted a son, but did not yet have one, was to have the 
-next birth sooner.
-The result was shorter average spacing after the births of girls than boys,
-and worse health outcomes for girls.%
+parents who wanted a son---but did not yet have one---was to have the next 
+birth sooner.
+Son preference was therefore often associated with shorter average spacing 
+after the births of girls than boys, which, in turn, was associated with worse 
+health outcomes for girls.%
 \footnote{
@@
 What has not previously been appreciated is that the introduction 
-of prenatal sex determination substantially changed the relationship between 
+of prenatal sex determination fundamentally changed the relationship between 
 son preference and birth spacing.
-The issue is that each sex-selective abortion increases the duration between 
+This is because each sex-selective abortion increases the duration between 
 observed births by approximately a year.%
@@
 }
-We therefore now have a situation where families with the \emph{strongest} son 
+As a result, we now have a situation where families with the \emph{strongest} son 
 preference likely show the \emph{longest} spacing after the birth of a daughter.
@@
 families who---for one reason or another---do not use prenatal sex selection.
-In this paper, I introduce and apply a novel method that
-directly incorporates the effects of sex-selective abortions on
-the likelihood of a son being born \emph{and} the duration between births.
-The method can be used to analyse both situations with and without prenatal
-sex selection.
-
-How spacing interacts with sex selection is important for two reasons.
-First, spacing, by itself, can no longer be used to measure son preference. 
-Spacing is still important and useful in understanding son preference, but 
-only if combined with the likelihood of observing a boy or a girl.
+
+Spacing, by itself, can therefore no longer be used to measure son preference. 
+Spacing is, however, still important and useful in understanding son preference, 
+but only if combined with the likelihood of observing a boy or a girl.
 Short spacing after a girl is indicative of son preference if observed
@@
 
-Second, the duration since last birth may affect the decision on sex selection.
+In this paper, I introduce and apply a novel method that directly incorporates 
+the effects of sex-selective abortions on the likelihood of a son being born 
+\emph{and} the duration between births.
+The method can be used to analyse both situations with and without prenatal
+sex selection.
+Furthermore, my proposed method allow for the duration since the last 
+birth to affect the decision on sex selection.
 For example, as the duration from last birth becomes long enough, parents 
@@
 and carry the next pregnancy to term whether male or female.
-Hence, by examining whether sex selection decisions change with
-spacing, we can draw a more nuanced picture of the degree of son preference.
-
-% [contribution of paper]
-% [TK maybe not focus so much on the simple method but rather understanding son preference].
-My main contribution here is the introduction and application
-of a novel method that directly incorporates that sex-selective 
-abortions affect both the likelihood of a son being born \emph{and} the 
-duration between births.
-[TK move to estimation strategy?]
-The empirical model is a competing risk, non-proportional hazard model with 
-two exit states: either a boy or a girl is born.
-
-I use the method to show how spacing between births has changed with
-the introduction prenatal sex determination and how birth spacing plays 
-an important role in our understanding of sex selection decisions and 
-son preferences.
+By examining whether sex selection decisions change with spacing, we can 
+draw a more nuanced picture of the degree of son preference.
 
 % [Why India?]
-I apply the method to birth histories from India's National Family and Health 
-Surveys for Hindu women covering the period 1972 to 2006. 
+I apply the method to birth histories for Hindu women, using data from 
+India's National Family and Health Surveys (NFHS), covering the period 
+1972 to 2006. 
 India is a particularly interesting case.
@@
 \citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
-India is not alone; both China and South Korea saw
-significant changes in the sex ratio at birth over the same period \citep{Yi1993,park95}.
-}
-On the other hand, recent research suggests, however, that son preference in 
+India is clearly not alone; both China and South Korea saw
+significant changes in the sex ratio at birth over the same period 
+\citep{Yi1993,park95}.
+}
+On the other hand, recent research suggests that son preference in 
 India, when measured as ideally having more boys than girls, is decreasing 
@@
 }
+In addition, there has been substantial changes in access and legality of
+prenatal sex determination in India over the period covered.
+Abortion has been legal in India since 1971 and still is, but the 
+first reports of on the availability of prenatal sex determination did
+not appear until 1982--83 \citep{Sudha1999,bhat06,Grover2006}.
+In 1994, the Central Government passed the Prenatal Diagnostic Techniques 
+(PNDT) Act, making determining and communicating the sex of a fetus illegal.%
+\footnote{
+The Act is described in detail at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
+The number of convictions has been low.
+It took until January 2008 for the first state, Haryana, to reach 5 convictions.
+Hence, private clinics apparently operate with little risk of legal action 
+\citep{Sudha1999}.
+Maharashtra was the first state to pass a similar law in 1988.
+}
+Hence, the data make it possible to show how spacing between births and
+sex ratios have changed with the introduction of prenatal sex determination,
+and whether the ban affected the relationship between birth spacing and sex 
+ratios.
 

### 2017-06-03 paper/sexSelectionSpacing-ver1.tex
Change reference/name for descriptive stat file

@@
 
-\begin{figure}[htp]%
-\centering
-\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
-\caption{Ratio of boys in ``first'' births}
-\label{fig:sexRatioMarriage}
-\end{figure}
+% \begin{figure}[htp]%
+% \centering
+% \includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
+% \caption{Ratio of boys in ``first'' births}
+% \label{fig:sexRatioMarriage}
+% \end{figure}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[Spell 2 - 1 boy (N=3,969)]{
-    \begin{minipage}{0.30\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[Spell 3 - 1 boy/1 girl (N=2,357)]{
-    \begin{minipage}{0.30\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[Spell 3 - 2 boys (N=1,098)]{
-    \begin{minipage}{0.30\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[Spell 2 - 1 boy (N=3,044)]{
-    \begin{minipage}{0.30\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[Spell 3 - 1 boy/1 girl (N=1,819)]{
-    \begin{minipage}{0.30\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[Spell 3 - 2 boys (N=790)]{
-    \begin{minipage}{0.30\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth by quarter (3 month period) for women with 8 or more years
-of education for 1995--2006. 
-N is number of women in the relevant group in the underlying samples.
-}
-\label{fig:boys_latest}
-\end{figure}
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[Spell 2 - 1 boy (N=3,969)]{
+%     \begin{minipage}{0.30\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{-1}
+% \subfloat[Spell 3 - 1 boy/1 girl (N=2,357)]{
+%     \begin{minipage}{0.30\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[Spell 3 - 2 boys (N=1,098)]{
+%     \begin{minipage}{0.30\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[Spell 2 - 1 boy (N=3,044)]{
+%     \begin{minipage}{0.30\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[Spell 3 - 1 boy/1 girl (N=1,819)]{
+%     \begin{minipage}{0.30\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[Spell 3 - 2 boys (N=790)]{
+%     \begin{minipage}{0.30\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth by quarter (3 month period) for women with 8 or more years
+% of education for 1995--2006. 
+% N is number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:boys_latest}
+% \end{figure}
 
@@
 
-\subsection{Predicted Lifetime Number of Children and Abortions}
-
-One of the main advantages of the method proposed is that we can predict what 
-completed fertility, total number of abortions, and the sex ratios will be for 
-women in the samples at the end of childbearing. 
-This cannot be done with the simple model because it does not predict fertility
-progression, does not take into account censoring, and cannot capture if parents
-change their use of sex selection within a spell.
-
-The predictions are important for three reasons.
-First, they allows us to quantify whether overall use of sex selection is 
-intensifying or easing over time by examining how the total number of abortions 
-women will have over their childbearing, and the resulting final sex ratios, change.
-This is a more accurate representation than what we get from sex ratios 
-for individual parities.
-As the theory section shows, it is possible to get no change---or even a 
-decline---in use of sex selection for an individual parity, at the same time 
-as the overall use of sex selection is increasing.
-Second, completed fertility and sex ratios are what matters when examining the future 
-impacts of sex selection in areas such as the chance of finding a spouse, savings 
-behavior, and the potential problems associated with a surplus of bachelors 
-\citep{lancaster02,Ding2009,Wei2009,Edlund2013}.
-Finally, as I show in the online Appendix and discuss above, relying only on observed 
-sex ratios of recorded births is problematic because these are based on selection and 
-the observed sex ratio may be biased predictors of final sex ratio when people change 
-their use of sex selection during a spell.
-
-Table \ref{tab:predicted} shows predicted birth progression rates, number of abortions, 
-sex ratios, and completed fertility for the three samples of women with 8 or more years 
-of education:  
-the 11,271 women who were married in the the 1972-1984 period,
-the 19,072 women who were married in the 1985--1994 period,
-and the 16,620 women who were married in the 1995--2006 period.%
-\footnote{
-These are the women used to estimate the results for the spell from marriage to first 
-birth above.
-For more information see Table \ref{tab:des_stat1}.
-}
-Predictions for each period assumes that behavior remains constant and that all spells 
-a woman goes through are within the same period. 
-Each woman is assumed to follow the fertility and sex selection behavior for 
-each spell up to and including the fourth spell using the period's estimates and her 
-characteristics. 
-All results are for women predicted to have one or more births.%
-\footnote{
-This means that fertility predictions are larger than standard estimates, which include
-women with no children.
-Working in the opposite direction is that number of children is restricted to be at most 
-four.
-}
-
-The predictions are done as follows.
-Starting with the first spell I calculate each woman's probabilities of having a boy,
-$P(b_t)$, a girl, $P(g_t)$, or no birth, $1-P(b_t)-P(g_t)$, in each quarter after marriage
-based on the period results for 
-equations (\ref{eq:probability_boy}) and (\ref{eq:probability_girl}) using her individual 
-values for $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$.
-She then is assigned one of these outcomes---boy, girl, or no birth---based on random 
-draws from a uniform distribution.
-The first quarter she has a draw that results in a birth she leaves the spell
-and the quarter reached is used to calculate her starting age for the second spell.
-If she has no draw that result in a birth by the end of the spell her childbearing 
-stops and she does not enter the next spell.
-If she does have birth, the process is repeated for the second through fourth spells.
-Randomization is necessary because each spell's results, except for the first, depends on
-the sex composition of previous children and the duration of the first spell. 
-The results presented are averaged outcomes over all urban women and all rural women 
-using 1,000 repetitions.
-
-Birth progression rates are the percentage of women predicted to have a birth 
-by the end of each spell.
-Fertility is the average number of children born according to the randomization.
-With the large number of replications this number is the same as using progression
-rates at the end of the spell to calculate the average number of children.%
-\footnote{
-Given that all numbers are conditional on having at least one child, using progression
-rates for, say, urban women from the 1985-1994 period leads to 
-$1+1\times0.782+1\times0.782\times0.499+1\times0.782\times0.499\times0.448=2.3 $  
-children.
-}
-
-For abortions I first calculate each quarter's probability of abortions using
-$\frac{100}{105}P(b_t)-P(g_t)$,
-where $\frac{100}{105}P(b_t)$ is the probability of having a girl that should have 
-prevailed in the absence of sex selection (0.952 girls born per boy).
-This probability is multiplied with the probability of not having had a birth yet at 
-the beginning of the quarter.
-Abortions for each spell are then found by summing over the entire spell.%
-\footnote{
-One way to see how this works is to imagine that we start the spell with 100 women.
-After the first quarter we are left with $N_2 = (1-P(b_1)-P(g_1)) \times 100$, where
-$N_2$ is the number of women who start the second quarter. 
-After the second quarter we then have $N_3 = (1-P(b_2)-P(g_2)) \times N_2$, etc.
-
-Say that 65.88 women of the original 100 still have not had a birth yet by the start
-of quarter 6 and that the predicted probability of having a son in quarter 6 is 0.0931 and 
-the probability of having a girl is 0.0566 (the probability of not having a birth in 
-quarter 6 is 0.8503).
-For this quarter the abortion probability is then 
-$\frac{100}{105}\times 0.0931 - 0.0566 = 0.0321$.
-In other words, the probability of having a girl should have been 
-$\frac{100}{105}\times 0.0931 = 0.0887$, but only a probability of $0.0566$ was 
-predicted.
-Hence, in quarter 6 the predicted number of sons born is $ 0.0931 \times 65.88 = 6.13$, 
-the predicted number of daughters born is $ 0.0566 \times 65.88 = 3.73$, and 
-$0.0321 \times 65.88 = 2.11$ abortions must have taken place to reach these births.
-}
-To account for random variation, the abortion rate is the sum over both positive 
-(more boys than the natural rate) and negative (more girls than the natural
-rate) values of the abortion calculation within the spell.
-Finally, the percentage of children born that are boys is based on the randomization of
-births described above.%
-\footnote{
-This number is the predicted sex ratio at birth and differ from actual observed sex 
-ratios when the children are older because of mortality.
-On one hand, the anticipated or experienced death of a son increases the likelihood
-of sex selection even if parents already had a son, which would make the later observed 
-sex ratio lower than what is predicted here. 
-On the other hand, mortality risk is higher for girls than for boy, which would make
-the sex ratio more male dominated.
-}
-
-% Tables of predictions 
-\input{../tables/predictedFertility.tex}
-
-The results show a substantial reduction in fertility over time.
-Predicted completed fertility went from 2.7 for urban women married in  
-the 1972--1984 period to just 2 for urban women married in the 1995--2006 period.
-Hence, urban fertility is now below replacement, especially considering that
-these predictions are conditional on having at least one child.
-Rural women showed a similar decline in completed fertility, going from 3.2 to 2.6.
-Corresponding to the decline in overall fertility, there were also substantial
-reductions in the individual parity progression rates.
-For example, urban women with 3 children went from having a 57\% chance of having a 
-4th child for the 1972--1984 cohort to a 33\% chance for the 1995--2006 cohort---and 
-they had a substantially lower probability of even making it to 3 children
-in the first place.
-
-Associated with the decline in completed fertility is an increase in sex selection.
-For urban women the predicted number of abortions per 100 women by the end of
-childbearing have gone up by over 17 percent between the last two cohorts (8.0 to 9.4) 
-and the number of abortions per 100 births have gone up by over 35 percent (3.4 to 4.6).
-For rural women, abortions per 100 women increased almost 55 percent (6.8 to 10.5), 
-while abortions per 100 births increased over 70 percent (2.4 to 4.1).%
-\footnote{
-Unfortunately there are no solid official estimates to compare these numbers to.
-The total number of abortions per year, not just those based on son preference, vary 
-between the official count of 600,000--700,000 
-and an estimate of 6.4 million from the 2002 Abortion Assessment Project-India.
-The 6.4 million abortions per year may even be an underestimate \citep{Stillman2014}.
-NFHS does ask about abortions in all three surveys, although the questions change 
-substantially between surveys.
-However, the PNDT act prohibits using prenatal diagnostic tests to determine a fetus' sex
-and revealing a fetus' sex to parents.
-Hence, respondents have a strong incentive not to disclose abortions motivated by son 
-preference. 
-In addition, abortion are considered a taboo subject and many women are unwilling or 
-uncomfortable reporting their abortions to government sponsored enumerators 
-\citep{Rossier2003,Stillman2014}.
-}
-The combined effects of the declines in fertility and increased use of sex selection
-are that the percentage boys increases from 53.1 to 53.7 percent for urban
-women, and from 52.8 to 53.4 percent for rural women.
-
-Of particular note is the high number of abortions among rural women for the 
-1985--1994 period.
-Educated rural women obviously had few constraints on access to 
-prenatal sex determination even when the techniques were relatively new.
-The higher abortion rate per woman for rural women than urban women likely comes from
-a combination of higher likelihood of having an additional child and changes in use of 
-sex selection within spell as shown in the graphs above.
-
-The results from theoretical model showed that it is possible for the use of sex 
-selection to fall for an individual parity, even as overall use of sex selection 
-increases. 
-This is the case here, where the use of sex selection fell for the third spell 
-from 9.8 per 100 births to 7.8 for urban women between the last two periods.
-As already discussed, total use of sex selection went up between the last two
-periods, so the reduction for the third spell is not an indication of reduced 
-use of sex selection overall, but simply the result of fewer women making it to a 
-third birth and those who did were more likely to already have a son---for 
-the second spell the number of abortions per 100 births for urban women 
-went from 4.7 to 8.0, a 70 percent increase.%
-\footnote{
-The amount of sex selection in the fourth spell reinforces this point:
-abortions per 100 births went up almost tenfold.
-Only 26 percent of urban women with at least one child make it to the beginning 
-of the fourth spell in the last period, and less than 10 of all women have a fourth birth, 
-but for those who do make it to the fourth spell the pressure to ensure a son is large.
-}
-This underscores why focusing exclusively on individual parities can be misleading.
-
-The results for rural women illustrate the two different strategies for achieving one
-son: either have many children or have few children and use sex selection.
-For the 1986--1994 period there is no use of sex selection on fourth birth, which fits
-with 62 percent of women end up with three or more children and a full 62 percent of women with 
-three children have a fourth birth (recall that there is a 94 percent chance of having at 
-least one son if you have four children).
-The use of sex selection on second and third spells indicates that one group of rural
-women follows the high fertility route, whereas the other group follows the pattern of
-urban women and combine restricting fertility with use of sex selection.
-
-Another way to see the spread of access to sex selection over time is to compare
-urban women in the first period with rural women in the last period.
-At 2.7 fertility is already relatively low for urban women in the 1972--1984 period and 
-there is some evidence of sex selection for these women.
-As discussed in Section \ref{sec:spell_def}, the higher than natural sex ratio for
-urban well-educated women this early is likely a combination of early access to prenatal
-sex determination and that some of the spells end in the 1985--1994 period when there 
-was more widespread access.
-Rural women in the 1995--2006 period had a fertility only slightly lower than that
-of urban women in the 1972--1984 periode, but the number of abortions both per birth and 
-per woman were twice as high.
-
-For comparison Appendix Tables \ref{tab:predicted_low} and \ref{tab:predicted_med}
-show predicted fertility, number of abortions, and sex ratio for the two other
-education groups.
-As expected, fertility for women with no education is substantially higher
-and the decline over time much smaller than for the high education group.
-Predicted fertility fell from 3.6 to 3.3 for urban women and from 3.7 to 3.5 for rural 
-women between the 1972--1984 and the 1995--2006 periods.%
-\footnote{
-A caveat is that my estimates did not cover parities higher than 4, which could
-bias downward the change in predicted fertility.
-}
-Consistent with the discussion above, there is evidence of sex selection for neither
-urban nor rural women, with the sex ratio for all predicted births in the last two periods 
-close to normal.%
-\footnote{
-The higher than normal sex ratios for the 1972--1984 period are most likely
-remnants of recall error not removed by the sample restriction. 
-}
-Random variation makes it appears that some individual parities had a higher
-than normal sex ratio, which, if studied in isolation, could be taken as evidence
-of use of sex selection, and reinforces why supplementing analysis of individual 
-parities with this analysis of the overall pattern is important.
-
-Fertility for women with between 1 and 7 years of education was slightly lower than the 
-no education group in the 1972--1984 period, but the decline over time was larger.
-For the 1995--2006 period predicted completed fertility was 2.8 for urban women and
-3.2 for rural women.
-There is only limited evidence of sex selection for urban women in this education group.
-The exception is for rural women in the last period where the overall sex ratio is
-52.1\% boys, although given the high fertility for this group and the small sample
-size for this education group it is unclear whether this simply reflects random variation.
-
-The predictions discussed here provide further support for the idea that there are 
-two alternative strategies to ensure the birth of a son, either have many children 
-or use sex-selective abortions.
-The best educated group mostly follow the low fertility, high use of sex selection
-strategy, whereas the two lower education groups still have relatively high fertility
-and little to no use of sex selection.
-It is, however, clear that fertility is declining over time for all groups.
-With lower fertility in both urban and rural areas, we are likely to see 
-further increases in the use of sex-selective abortions among those who already
-use sex selection, and among the groups who have not previously use sex selection
-we will see beginning use of sex-selective abortions.
-
 \section{Conclusion\label{sec:conclusion}}
@@
 % Descriptive statistics tables
-\input{../tables/desStat.tex}
+\input{../tables/des_stat.tex}
 

### 2017-06-06 paper/sexSelectionSpacing-ver1.tex
Try to fix Makefile
- dependencies do not appear to work
- .eps does not work with pdflatex :-(
Move to XeLaTeX for paper
- download TeX Gyre Pagella
- change preamle to tex document to allow for both text and math
- update ReadMe with download location for fonts
- update ReadMe with instructions to use XeLaTeX

@@
 
-\usepackage{mathpazo}
+\usepackage{fontspec}
+\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
+\usepackage{unicode-math}
+\setmathfont{TeX Gyre Pagella Math}
+% \usepackage{mathpazo}
 \usepackage[title]{appendix}
@@
 \usepackage[longnamesfirst]{natbib}
-\usepackage{amssymb}
-\usepackage{amsmath}
 \usepackage{dcolumn}
@@
 \usepackage[font=scriptsize]{subfig}
-\usepackage[pdftex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
+\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
 \usepackage{adjustbox}
@@
 \begin{document}
-\graphicspath{{figures/}}
-\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
+\graphicspath{{../figures/}}
+\DeclareGraphicsExtensions{.eps,.jpg,.pdf,.mps,.png}
 
@@
 % \setcounter{page}{0}
+
 \newpage
-
-\doublespacing
-% \onehalfspacing
-
-% \thispagestyle{empty}
-
-\maketitle
 \thispagestyle{empty}
-
-\newpage
 \doublespacing
@@
 lower education and higher mortality of girls relatively to boys, could be thought 
-of as evidence of son preference, although \cite{rosenzweig82} argue that both may 
+of as evidence of son preference, although \cite{rosenzweig1982a} argue that both may 
 represent parents' rational response to market opportunities rather than inherent 
@@
 than multiple sons.
+
+\begin{figure}[htp]%
+\centering
+\includegraphics[width=0.9\textwidth]{spell2_g3_high_r4_s.eps}
+\caption{Survival curve example}
+\label{fig:survival}
+\end{figure}
 

### 2017-09-28 paper/sexSelectionSpacing-ver1.tex
Add draft of discussion of how to compare survival curves

@@
 birth sooner.
-Son preference was therefore often associated with shorter average spacing 
-after the births of girls than boys, which, in turn, was associated with worse 
+Son preference was therefore often associated with shorter spacing after the 
+births of girls than boys, which, in turn, was associated with worse 
 health outcomes for girls.%
@@
 son preference and birth spacing.
-This is because each sex-selective abortion increases the duration between 
-observed births by approximately a year.%
+This is because each sex-selective abortion substantially increases the 
+spacing from last birth. 
+For every abortion a woman has we should expect the duration from last
+birth to increase by approximately a year.%
 \footnote{
@@
 }
+
 As a result, we now have a situation where families with the \emph{strongest} son 
-preference likely show the \emph{longest} spacing after the birth of a daughter.
+preference may show the \emph{longest} spacing after the birth of a daughter
+because of the use of sex-selective abortions.
 But, to further complicate matters, we may still observe short spacing 
@@
 birth to affect the decision on sex selection.
-For example, as the duration from last birth becomes long enough, parents 
-may reverse their decision to use prenatal sex determination,
-and carry the next pregnancy to term whether male or female.
+For example, as the duration from last birth becomes long enough, even 
+parents with strong son preference may reverse their decision to use 
+prenatal sex determination, and carry the next pregnancy to term whether 
+male or female.
 By examining whether sex selection decisions change with spacing, we can 
@@
 curves are a crucial complement to the estimated sex ratios by duration.
+
+[How to compare survival curves?]
+
+In principle, in order to understand how birth spacing changes in response
+to the introduction of prenatal sex determination one could simply compare survival 
+curves between different sex compositions of prior births over time.
+If the idea that the availability of sex-selective abortion increases the
+spacing more after the birth of girls than after the birth of boys is 
+correct, we should see the two survival curves become closer to each other
+and we might even be able to directly observe that the survival curve for prior
+child being a girl is above the survival curve for prior child being a boy,
+instead of substantially below as was generally the case before prenatal
+sex determination become widely available.
+
+There are, however, two (interrelated) problems.
+First, the probability that a woman will progress to a next birth  
+is not the same across different sex compositions of prior children.
+Specifically, one of the ways that past research has tried to establish
+son preference in fertility behavior is to compare parity progression
+rates for different sex compositions [TK references - see footnote 1].
+The idea was that if there is son preference a couple would be less likely
+to progress to a next birth if they have one or more son already for a
+given number of prior births.
+
+The fact that the probability of having a next birth also depends on the
+sex composition complicates the comparison of survival curves. 
+A lower parity progression probability will naturally make the survival
+curve flatter.
+This means that the survival curve for a girl composition will be more
+likely to be below the boy composition.
+Even if the use of sex selection is substantial enough to move the
+survival curve for girl composition to the right of the boy
+composition the lower parity progression probability for boy 
+composition means that the survival curves would eventually have to
+cross.
+This makes it difficult---if not impossible---to design a direct test
+of how the survival curves compare.
+
+The problem of different parity progression rates across different
+sex composition is exacerbated by falling fertility over time.
+This is because there are now more parities where they may be a 
+substantial differences in parity progression rates and because
+the difference in parity progression for a given parity will 
+become larger if there is son preference.
+As the parity progression probability decreases it becomes impossible
+to capture the time until a certain survival point (like 0.5 of women
+having had a child; the survival curve may never actually reach this
+point).
+
+In addition, it is possible that falling fertility also generically 
+leads to longer spacing between births.
+This means that we have to separate out which part of the longer
+spacing comes from falling fertility (and therefore should also
+affect boy composition) and which parts comes from increased use
+of sex selection.
+
+[We should expect sex selection to be mainly used for the last---or close to
+last---birth that a couple expect to have because of the cost and risk
+of the procedures.]
+
+One solution to this problem is to condition on the parity progression
+rates.
+That is, instead of comparing say how long it takes for 50\% of women
+who began the spell to have the next birth across boy and girl composition, 
+which would work well if the next birth was nearly universal, we 
+could calculate how long it takes for 50\% of those women who will 
+eventually have a next child to have that child based on the estimated
+survival curves.
+This number can then be compared across sex compositions to 
+understand if the spell length for girl composition increases
+more than for boy composition with the introduction of sex selection.
+
+Obviously, this should be calculated for different percentages.
+Actually, it probably makes more sense to show this graphically
+instead. 
+All compositions would begin at 100\% and end at 0\% because
+we condition on having the next child.
+
+Note, this is not the same as simply calculating the average 
+\emph{observed} spell lengths among women who have a given parity
+child in the survey because that number does not take into account
+the censoring of some spells that will eventually lead to a birth.
 

### 2017-09-30 paper/sexSelectionSpacing-ver1.tex
Rename files for ease of reading
Introduce conditional survival curves for 2nd
Modified versions of original files to generate results and
produce graphs of percentages, standard survival curves, and
survival curves conditional on parity progression.

@@
 I show that use of sex selection leads to \emph{longer} spacing after a daughter 
-is born.
+is born than after a son.
 Women with 8 or more years of education, both in urban and rural areas, are 
@@
 
-\begin{figure}[htp]%
+% High education
+
+\begin{figure}[htpb]
 \centering
-\includegraphics[width=0.9\textwidth]{spell2_g3_high_r4_s.eps}
-\caption{Survival curve example}
-\label{fig:survival}
+\caption*{First child a girl}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=2,689)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=4,869)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=3,774)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First child a boy}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=2,806)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=5,246)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=3,969)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after first birth for urban 
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 22 at first birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{First child a girl}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=1,305)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=3,105)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=2,823)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First child a boy}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=1,404)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=3,381)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=3,044)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after first birth for rural
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 22 at first birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_rural}
+\end{figure}
+
+% Survival curves conditional on progression
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_urban}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_rural}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_urban}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_rural}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_pps}
 \end{figure}

### 2017-10-01 paper/sexSelectionSpacing-ver1.tex
Add spell 3 files and update paper

@@
 I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to three anonymous referees, Shelly Lundberg, Daniel Rees, David Ribar, 
+I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
 Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
@@
     Seattle, WA 98122\\
-    \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
+    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
@@
 
-\date{April 2017}
+\date{September 2017\\
+\bigskip
+Preliminary}
 
@@
 I show that use of sex selection leads to \emph{longer} spacing after a daughter 
-is born than after a son.
+is born than after a son, but for families that do not use sex selection
+duration to next birth is still shorter when no boys are present.
 Women with 8 or more years of education, both in urban and rural areas, are 
@@
 do not appear to use sex selection.
-Predicted lifetime fertility for high-education women declined more than 10\% 
-between 1985--1994, when sex selection was legal, and 1995--2006, when sex selection 
-was illegal.
-Abortions per woman increased almost 20\% for urban women and 50\%
-for rural women between the two periods, suggesting that making sex 
-selection illegal has not reversed its use.
-Finally, sex selection appears to be used to ensure one son rather 
-than multiple sons.
 
@@
 
+[Outline of findings here]
+
 % [EXPLAIN RESULTS HERE]
 % Main findings!
-There are three main findings.
-
-There is, however, still no evidence of sex selection being used on the first birth.
-
-Secondly, sex selection appears to be used for securing one son, rather than a large 
-number of sons.
-There is only limited use of sex-selective abortions for better-educated
-women with one or more sons.
-The exception is rural women with one son and one daughter, presumably to compensate for 
-the higher child mortality in rural areas.
-These results are in line with the differential stopping behavior observed in many studies
-before sex selection became available \citep{repetto72,arnold98,dreze01}.
+% There are three main findings.
+% 
+% There is, however, still no evidence of sex selection being used on the first birth.
+% 
+% Secondly, sex selection appears to be used for securing one son, rather than a large 
+% number of sons.
+% There is only limited use of sex-selective abortions for better-educated
+% women with one or more sons.
+% The exception is rural women with one son and one daughter, presumably to compensate for 
+% the higher child mortality in rural areas.
+% These results are in line with the differential stopping behavior observed in many studies
+% before sex selection became available \citep{repetto72,arnold98,dreze01}.
+%
 
@@
 
-[How to compare survival curves?]
+[The problem with comparing survival curves]
 
@@
 more than for boy composition with the introduction of sex selection.
-
-Obviously, this should be calculated for different percentages.
-Actually, it probably makes more sense to show this graphically
-instead. 
-All compositions would begin at 100\% and end at 0\% because
+Obviously, this should be calculated for different percentages
+and the easiest way to interpret the result is to graph survival
+conditional on parity progression occurring.
+All compositions therefore begin at 100\% and end at 0\% because
 we condition on having the next child.
@@
 
-% \begin{figure}[htp]%
-% \centering
-% \includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
-% \caption{Ratio of boys in ``first'' births}
-% \label{fig:sexRatioMarriage}
-% \end{figure}
+\begin{figure}[htp]%
+\centering
+\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
+\caption{Ratio of boys in ``first'' births}
+\label{fig:sexRatioMarriage}
+\end{figure}
 
@@
 
-One of the main questions here is how fertility affects sex selection use.
-I start by showing the relationship between self-reported desired fertility and sex 
-selection, which also illustrates how to interpret the results.
-Although self-reported desired fertility is an imperfect proxy for actual
-fertility behavior, the analysis of desired fertility indicates that there is 
-a relationship between fertility decisions and the use of sex selection and motivates 
-examining the relationship more closely.
-
-Because of the desired fertility measure's potential shortcomings, I next examine the 
-relationship between actual fertility and use of sex selection for better-educated women.
-There are two steps in this process.
-First, I show how fertility has declined for better-educated women with one son---a group 
-unlikely to use sex selection, which means that sex selection will not affect the 
-progression rates to next birth for these women.
-Second, I show how, corresponding to the fertility decline, there is an increase in
-sex-selective abortions for better-educated women without a son.
-I next show how women with lower cost of children appear to follow a high fertility, low
-use of sex selection strategy compared to the low fertility, high use of sex selection of
-the better-educated women.
-The results all show clear evidence of son preference in fertility and sex selection use, 
-but exactly what form son preference takes is important, so I next discuss what we can
-learn about son preference from the sex selection behavior.
-Finally, I predict lifetime fertility, number of abortions, and final sex ratios for
-the better-educated women.
-
-Except for the predictions, results are presented using graphs of estimated percentage boys 
-born by quarter, the associated 95 percent confidence interval, and the survival curve for 
-a ``representative woman'' using the method detailed in Section \ref{sec:strategy}.
-The ``representative woman'' characteristics are based on means of continuous 
-explanatory variables and the majority category for categorical explanatory variables.
-Common to all ``representative women'' is that they do not own land and belong to neither 
-a scheduled caste nor a scheduled tribe.
-The graphs also show the expected natural rate of boys, approximately 51.2 percent, for
-comparison.
-Graphs for all groups and spells, even if not discussed here, are available in 
-the online Appendix.
-
-\subsection{One Son or Many Sons?}
-
-The extent to which people use sex selection for different sex compositions
-of previous children is of interest for two reasons.
-First and foremost, it can help us understand what form son preference takes in India.
-This is important in itself, but is especially important as we try to predict 
-what will happen to sex selection use in the future.
-[need an explanation of this based on what I have in the introduction]
-Second,
-if families use sex selection to reach two or more sons, progression rates for families 
-with one son may overestimate the decline in fertility.
-
-Women with 8 or more years of education is the group the most likely to use sex 
-selection if they have no son as shown above.
-Hence, if sex selection is also used to achieve more than one son, we should be
-most likely to find evidence for this group of women as well.
-Figure \ref{fig:boys_latest} therefore shows sex ratios and survival curves for 
-the 1995--2006 period for urban and rural women with 8 or more years of education, 
-conditional on having at least one son.
-The first column shows outcomes for the second spell if the first born is a son,
-the second column shows third spell when the first two children were a son and 
-a daughter, and the third column shows third spell when the first two children were sons.
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[Spell 2 - 1 boy (N=3,969)]{
-%     \begin{minipage}{0.30\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{-1}
-% \subfloat[Spell 3 - 1 boy/1 girl (N=2,357)]{
-%     \begin{minipage}{0.30\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[Spell 3 - 2 boys (N=1,098)]{
-%     \begin{minipage}{0.30\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[Spell 2 - 1 boy (N=3,044)]{
-%     \begin{minipage}{0.30\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[Spell 3 - 1 boy/1 girl (N=1,819)]{
-%     \begin{minipage}{0.30\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[Spell 3 - 2 boys (N=790)]{
-%     \begin{minipage}{0.30\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth by quarter (3 month period) for women with 8 or more years
-% of education for 1995--2006. 
-% N is number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:boys_latest}
-% \end{figure}
-
-For the second spell the predicted sex ratios closely follow the natural sex 
-ratio for both urban and rural women.
-Furthermore, the survival curves follow the expected pattern if no sex selection 
-is taking place.
-There is also no evidence of sex selection for the third spell for women with two sons;
-the sex ratios follow the natural sex ratio for both urban and rural women.
-Sample sizes are, however, less than \sfrac{1}{3} of the sample sizes for the second 
-spell and the progression rate to a third birth is low at only 30\% for urban women and 
-55\% for rural women, resulting in wide confidence intervals.
-The survival curves are particularly flat for the first year, meaning that the apparent 
-deviations from the natural sex ratio in the beginning of the spell are based on very few births.
-
-% [Spell 3 - 1b/1g most interesting]
-
-Even though there is no evidence of using sex selection to have an additional son when the 
-previous children are all sons, it is possible that families want more sons than daughters 
-and therefore use sex selection for the third spell when they already have one of each.
-Urban women show little evidence of this being the case.
-Although the sex ratio is above the natural from quarter 11 until the end of the spell,
-only about \sfrac{1}{3} of the births occur in this interval.
-Furthermore, the dip below the natural sex ratio prior to this point also accounts for
-approximately \sfrac{1}{3} of the births.
-Hence, these two parts cancel each other out.
-With the first part being to the natural sex ratio the end result is that there
-is little evidence for urban women using sex selection if they already have a son and
-a daughter.
-
-For rural women, however, the dip and the associated number of births is not
-large enough to bring the overall sex ratio for the spell back to natural sex ratio.
-The sex ratio for the entire spell is therefore likely more male dominated
-than the natural rate, although it is only statistically significantly higher for two 
-individual quarters of the spell.
-There are two possible explanations for rural women appearing more likely than urban
-women to use sex selection on the third spell if they already have a son and a daughter.
-First, rural women could have a stronger son preference than urban women and want two sons 
-rather than only one.
-Second, mortality is higher in rural than urban areas and this higher mortality, either 
-experienced or anticipated, make rural women use sex selection to secure a second son, 
-essentially as an insurance.
-Separating these two possible explanations is difficult, but the ``heir and a spare''
-explanation appears  more likely than difference in preferences given that urban women use 
-sex selection more than rural women for the second birth in the absence of a son.
-An alternative explanation is that what we are observing is simply random variation.
-This would explain why we get see differences in sex ratios between urban and rural
-women with one son across the third and fourth spells as shown in the online Appendix.%
-\footnote{
-Urban women with a son and two daughters as their first 3 births show a sex ratio
-that is significantly higher than the natural, but no evidence of sex
-selection if they have two sons and a daughter as their first children.
-Rural women show only a marginally higher sex ratio with a son and two daughters and no 
-effect at all with two sons and a daughter.
-These results are, however, based on very small samples.
-There are 590 urban women with a son and two daughters, of which less than 40\% have a
-fourth child, 344 urban women with two sons and one daughter, and only 20\% of those
-have a fourth child.
-For rural women the numbers are 564, with 40\% having a fourth child, and 367 with
-approximately 30\% having a fourth birth.
-This comes to approximately 300 urban births and only slightly more for rural across
-the two sex compositions.
-}
-
-Son preference can manifest itself through other channels than sex selection.
-Differential investments in education and health across boys and girls, resulting in
-lower education and higher mortality of girls relatively to boys, could be thought 
-of as evidence of son preference, although \cite{rosenzweig1982a} argue that both may 
-represent parents' rational response to market opportunities rather than inherent 
-preferences of parents.
-Whatever way son preference presents itself, it appears that the dominant  
-preference---as expressed through use of sex selection---is for one son, rather 
-than multiple sons.
+[Only a subset of the planned analyses to demonstrate the method and interpretation]
 
@@
 
+Figure \ref{fig:results_spell2_high_urban} 
+shows the predicted probabilities of having a boy and standard survival curves
+for the three periods for urban women with 8 or more years of education.%
+\footnote{
+The corresponding graphs for rural women and for women with no education are
+shown in Figures \ref{fig:results_spell2_high_rural}, \ref{fig:results_spell2_low_urban},
+and \ref{fig:results_spell2_low_rural}
+}
+Two main results stand out.
+First, women whose first child was a boy do not appear to use sex selection during
+the second spell.
+The predicted percent boys is consistently close to the natural level in all three
+panels (\ref{fig:results_spell2_high_urban}(d)-(f)).
+Second, as prenatal sex determination became available there is more and more
+evidence of sex selection affecting the sex ratio for women with a girl as their
+first child.
+In panel (a), which covers the period before sex selection became generally
+available, there is no significant evidence of a sex ratio biased towards males.
+Panel (b) shows a more male biased sex ratio but only a few of quarters show
+a statistically significant difference from the natural rate and the shallow 
+slope of the survival curve indicates that relatively few births took place
+during these quarters.
+Panel (c), however, shows clear evidence of the effect of access to prenatal
+sex determination with a male biased sex ratio for more of the two first years.%
+\footnote{
+Recall that quarter 0 is equivalent to 9 months (3 quarters) after the birth
+of the first child.
+}
+
+% Survival curves conditional on progression
+
+Figures \ref{fig:results_spell2_low_pps} and \ref{fig:results_spell2_high_pps}
+show survival curves for the second spell (from first birth) for women with
+no education and women with 8 or more years of education.
+To allow for comparison these survival curves show the ratio of women who
+have not had a birth yet, given that they will eventually are predicted to
+have a birth.
+Women with no education show relatively similar survival curves whether their
+first child was a girl or a boy, but to the extent that a pattern is present
+it shows, as expected, shorter spacing a girl than a boy.
+Rural women with 8 or more years of education show essentially the same 
+pattern.
+The lack of clear results is not surprising given that all three groups of
+women are likely to have more than two children.
+
+The effect of sex selection on spacing first show up for urban women with
+8 or more years of education.
+Panel (a) in Figure \ref{fig:results_spell2_high_pps} show shorter spacing
+for the second spell when the first child is a girl than a boy, and this
+pattern is also present in Panel (b).
+Panel (c) on the other hand show first evidence of \emph{longer} spacing 
+after the birth of a girl than after a boy, consistent with the male-biased
+sex ratio in Panel (c) in Figure \ref{fig:fig:results_spell2_high_urban}.
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_urban}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_rural}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_urban}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_rural}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_pps}
+\end{figure}
+
+% 3rd spell
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_pps_urban}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_pps_rural}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_low_pps}
+\end{figure}
+
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_pps_urban}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_pps_urban}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_pps_rural}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_pps_rural}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_high_pps}
+\end{figure}
+
+The effect of sex selection on spacing is even more pronounced in
+Figure \ref{fig:results_spell3_high_pps}, which shows the conditional
+survival curves for the third spell (from second birth) for women with
+8 or more years of education.
+Before prenatal sex determination became available there is little difference
+in spacing pattern no matter the sex composition of the first two children.
+This changes after the introduction as shown in Panel (b), where the spacing
+is longer when the first two children are girls than either one boy/one girl
+or two boys.
+Even more substantial are the results from Panel (c), which shows much 
+longer spacing when the first two children are girls.
+These results are consistent with the biased sex ratios shown in 
+Figure \ref{fig:results_spell3_high_urban}.
+
+\clearpage
+
+\section{Conclusion\label{sec:conclusion}}
+
+[To be added]
+
+\clearpage
+
+\onehalfspacing
+\bibliographystyle{aer}
+\bibliography{collection}
+
+\addcontentsline{toc}{section}{References}
+
+\clearpage
+\newpage
+
+\appendix
+\section{Appendix}
+
+% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
+\renewcommand\thefigure{\thesection.\arabic{figure}}    
+\setcounter{figure}{0}
+\renewcommand\thetable{\thesection.\arabic{table}}    
+\setcounter{table}{0}
+
+% Descriptive statistics tables
+\input{../tables/des_stat.tex}
+
+\clearpage
+
+\subsection{Second Spell}
+
+% SPELL 2 - URBAN - LOW
+\begin{figure}[h]
+\centering
+\caption*{First child a girl}
+\setcounter{subfigure}{-2}
+\subfloat[1972-1984 (N=1,596)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r4_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r4_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985-1994 (N=2,232)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r4_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r4_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[1995-2006 (N=952)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption*{First child a boy}
+\setcounter{subfigure}{1}
+\subfloat[1972-1984 (N=1,754)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r2_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985-1994 (N=2,411)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995-2006 (N=930)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after first birth for urban 
+women with no education by quarter (3 month period). 
+Predictions based on age 18 at first birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_low_urban}
+\end{figure}
+
+% SPELL 2 - rural - LOW
+\begin{figure}
+\centering
+\caption*{First child a girl}
+\setcounter{subfigure}{-2}
+\subfloat[1972-1984 (N=8,426)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r3_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r3_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985-1994 (N=11,481)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r3_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r3_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[1995-2006 (N=3,686)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption*{First child a boy}
+\setcounter{subfigure}{1}
+\subfloat[1972-1984 (N=9,395)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r1_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985-1994 (N=12,127)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995-2006 (N=3,860)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after first birth for rural 
+women with no education by quarter (3 month period). 
+Predictions based on age 18 at first birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_low_rural}
+\end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=2,689)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=4,869)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=3,774)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=2,806)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=5,246)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=3,969)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 22 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_spell2_high_urban}
+% \end{figure}
+
 \begin{figure}[htpb]
@@
 
-% Survival curves conditional on progression
-
-% Low education
+\clearpage
+
+\subsection{Third Spell}
+
+% low education
 
@@
 \centering
-\caption*{Urban}
+\caption*{First two children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=493)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r6_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r6_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
 \setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_urban}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_urban}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+\subfloat[1985--1994 (N=996)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r6_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r6_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=475)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First two children one boy and one girl}
 \setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_urban}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
+\subfloat[1972--1984 (N=1,083)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r4_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
 \setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_rural}} 
+\subfloat[1985--1994 (N=2,141)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r4_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_rural}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_rural}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by quarter (3 month period).
+\subfloat[1995--2006 (N=950)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r4_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
 Left column shows results prior to sex selection available, middle column before
@@
 }
-\label{fig:results_spell2_low_pps}
+\label{fig:results_spell3_low_urban}
 \end{figure}
-
-% High education
 
@@
 \centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_urban}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_urban}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_urban}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_rural}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_rural}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+\ContinuedFloat
+\caption*{First two children boys}
 \setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_rural}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by quarter (3 month period).
+\subfloat[1972--1984 (N=569)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r2_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=1,124)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=426)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+% \label{fig:results_spell3_low_urban}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
 Left column shows results prior to sex selection available, middle column before
@@
 }
-\label{fig:results_spell2_high_pps}
 \end{figure}
 
-\section{Conclusion\label{sec:conclusion}}
-
-If women have preferences over both the number of children they have \emph{and} the sex 
-composition of these children, they face a trade-off between the cost---both monetary 
-and psychological---of sex selection and the cost of children.
-This paper introduces a novel approach to understanding the relationship between
-fertility and use of sex selection, and how sex selection interact with birth spacing.
-The proposed method allows for joint estimation of fertility and sex-selective abortions 
-using a non-proportional, competing risk hazard model.
-
-Three results stand out.
-First, lower fertility is an important factor in the decision to use sex-selective abortions.
-% Women wanting more than two births did not use sex selection on the second birth, while
-% those who want two or fewer use sex selection intensively.
-In both urban and rural areas, only women with the lowest predicted fertility---those
-with 8 or more years of education---use sex selection, and as fertility falls they use it 
-for earlier parities.
-Women with less education instead follow a high fertility strategy to ensure they have
-a son and do not appear to use sex selection.
-Previous research was unable to explain why sex selection in India only occurred 
-among higher education women because it failed to tie the use of sex selection and the 
-fertility decision together.
-
-Second, the legal steps taken to combat sex-selective abortion have not been able
-to reverse the practice.
-The use of sex selection has been increasing over time and is higher now than before the
-PNDT Act was passed.
-The predicted number of sex-selective abortions per 100 women during their childbearing 
-years is now around 10 for women with 8 or more years of education in both urban and
-rural areas.
-This is especially interesting given that the cost of prenatal sex determination 
-has likely increased in response to the PNDT Act.
-This also emphasizes why accounting for the possibility that parents may change
-their decision to use sex selection within a spell is important. 
-As the theory shows an increase in the cost of prenatal sex determination 
-increases the likelihood of parents changing their decision to use sex selection.%
-\footnote{
-A feature of the new approach is that it allows for changes in the decision 
-to use sex selection within a spell.
-This is most clearly seen for better-educated urban women whose only child is a girl, 
-for whom the use of sex selection declines as the second spell becomes longer.
-}
-
-Third,  there is little evidence that women with one or more sons use sex selection,
-and their probability of another birth declines substantially once they have a son.
-The main exception is for rural women with one son and one daughter, presumably as an 
-insurance against mortality.
-Hence, parents appear to have a preference for one son rather than multiple sons.
-
-These results imply that the way we have been measuring son preference may not be useful
-for understanding how people make decisions on use of sex selection.
-Recent research suggests that son preference in India, when measured as ideally having 
-more boys than girls, is decreasing over time and with higher education \citep{bhat03,pande07}.%
-\footnote{
-This measure of son preference is commonly used in the literature. 
-See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-In NFHS, and Demographic and Health Surveys in general, son preference is measured as part 
-of the general fertility questions.
-The first question is how many children a woman would have if she could choose exactly how 
-many.
-This if followed by the sex preference question:
-``How many of these children would you like to be boys, how many would you like to be girls 
-and for how many would the sex not matter?''
-}
-Despite this, use of sex selection has increased and for exactly the group 
-argued to show declining preference for sons.
-The culprit may be that parents want \emph{one} son and will use sex selection 
-intensively to get that son, but refrain from using sex selection to have more sons, 
-and our standard measure of son preference cannot captured that.
-A better approach may be to directly ask if there is a minimum number of each sex that 
-respondents want, possibly in combination with ideal number questions.
-
-This is of more than theoretical interest.
-If son preference is expressed as a very strong desire for having at least one
-son then reductions in fertility will lead to a further increase in the use of sex 
-selection across all groups that hold that preference.
-What is more, as shown in the theory section, it is possible to get increasingly
-unequal sex ratio when fertility falls even if parents do not want more sons
-than daughters as long as they only use abortion on female fetuses.
-A deeper understanding of exactly what type of son preference is responsible 
-for the increase use of sex selection is clearly an important question for
-future data collection and research.
-
-An often-repeated, but poorly substantiated, argument for why there is sex selection 
-in India is the dowry system.
-This explanation fits poorly with observed behavior.
-If true, dowries increase the cost of having girls relative to boys because you have to 
-pay to ensure your girls are married.
-This implies that poorer households should be the most likely to use sex selection, and 
-that the use of sex selection should increase the more girls they have.%
-\footnote{
-The exception would be if dowries increase more than proportionally with education level 
-and income, but there does not appear to be evidence of this.
-} 
-Similarly, for all households there would be a financial incentive to achieve a higher 
-number of sons than daughters.
-As shown here, however, sex selection is predominantly used by better educated and 
-therefore, on average, wealthier households and only to secure one son rather than multiple 
-sons.
-Finally, fertility's rapid decline after the introduction of prenatal sex 
-determination, combined with low cost of sex selection, suggests that parents'
-perceived costs of boys and girls are similar.%
-\footnote{
-See the discussion in Section \ref{sec:changes} for more detail.
-}
-Hence, banning dowries, as India has done, is unlikely to affect the use of sex 
-selection.
-
-The results presented here lead to a number of important questions for future research.
-One is whether marriage market sex ratios affect the use of sex selection.
-Parents may care not only about the number and type of children they have but 
-also whether they will have grandchildren.
-If they care about grandchildren, then a boy could still be preferred over a girl, but a 
-married girl would be preferred over an unmarried boy \citep{Bhaskar2011}.
-The implication is that parents respond to changes in the expected sex ratio of their
-children's marriage market, even given their preference for a son.
-This hypothesis can be tested using measures of the observed distributions of
-boys and girls and the method proposed here.
-
-A second question for future research, which is especially important when designing 
-policies aimed at reducing the use of sex selection, is who the agents are in the decisions 
-to use sex selection.
-Here, I have treated the household as a single unit, but it is possible, and indeed likely, 
-that husband and wife have different preferences over both the factors that determine  
-use of sex selection and sex selection itself.
-Some of the popular press have assumed that the decision to use sex selection rests 
-with the husband.
-This, however, does not fit well with the general pattern that women, on average, prefer to 
-have fewer children than men do and that declining fertility appear to be the main
-driver of sex selection.
-A better understanding of who holds what preferences in the family would be a good 
-first step to disentangling who makes decisions about sex selection.
-
-A third question is whether there are interactions between sex selection and child outcomes,
-such a survival and education.
-It has been argued that access to sex selection may benefit girls because those girls
-who are born are more likely to be wanted by their parents.
-For mortality it is, however, possible that improvements are the result of a purely 
-mechanical effect.
-As I have shown, increased use of sex selection lengthens the birth spacing after a girl 
-and that by itself can improve her survival chances, even if she is no more wanted than before.
-The method suggested here can predict the likelihood of a woman using prenatal sex 
-determination for a given birth based on her characteristics.
-This predicted probability can then be used in estimations of the determinants
-of child health to directly test whether increasing use of sex selection is 
-beneficial for the girls who are born.
-It is unlikely, however, that a substantial mortality effect exists since sex 
-selection is mainly used by well-educated women, who tend to have lower mortality, 
-but there might be effects on education investments.
-
-% [developments in the future]
-In conclusion, the results provide strong clues to how sex selection use will change in the future.
-Because lower fertility is responsible for the increase in sex-selective abortions, 
-it is likely that we will see further increases in the practice as more families 
-want fewer children, either because of urbanization or because of increases in female 
-education.
-With already low fertility for better-educated urban women, a substantial future increase 
-in sex-selective abortions per woman is unlikely, 
-but a higher proportion of women will belong to this group in the future.
-For rural, better-educated women fertility is still falling.
-To the extent that it falls to the same level as for urban
-women, I expect a corresponding increase in sex selection.
-Finally, and most importantly, we are beginning to see evidence of lower fertility 
-for women with lower levels of education.
-If women with less education hold the same preference for one son as the better-educated,
-once the less-educated women's fertility begins to drop to three---and even two---we are 
-likely to see a substantially increased use of sex selection in India.
-
-\newpage
-\onehalfspacing
-\bibliographystyle{aer}
-\bibliography{collection}
-
-\addcontentsline{toc}{section}{References}
+\begin{figure}[htpb]
+\centering
+\caption*{First two children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=2,599)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r5_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r5_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=5,062)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r5_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r5_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=1,879)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First two children one boy and one girl}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=5,382)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r3_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=10,473)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r3_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=3,779)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r3_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_low_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\ContinuedFloat
+\centering
+\caption*{First two children boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=3,070)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r1_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=5,339)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=1,846)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+% \label{fig:results_spell3_low_rural}
+\end{figure}
+
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{First two children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=709)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=1,654)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=1,000)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First two children one boy and one girl}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=1,409)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=3,460)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=2,357)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_high_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\ContinuedFloat
+\caption*{First two children boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=780)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=1,660)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=1,098)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+% \label{fig:results_spell3_high_urban}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{First two children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=348)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=982)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=863)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First two children one boy and one girl}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=700)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=1,987)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=1,819)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_high_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\ContinuedFloat
+\centering
+\caption*{First two children boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=370)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=945)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=790)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+% \label{fig:results_spell3_high_rural}
+\end{figure}
 
@@
 
-\appendix
-\section{Appendix}
-
-% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
-\renewcommand\thefigure{\thesection.\arabic{figure}}    
-\setcounter{figure}{0}
-\renewcommand\thetable{\thesection.\arabic{table}}    
-\setcounter{table}{0}
-
-% Descriptive statistics tables
-\input{../tables/des_stat.tex}
-
 \end{document}

### 2017-10-10 paper/sexSelectionSpacing-ver1.tex
Minor edits

@@
 
-\date{September 2017\\
+\date{October 2017\\
 \bigskip
@@
 I show that use of sex selection leads to \emph{longer} spacing after a daughter 
-is born than after a son, but for families that do not use sex selection
+than after a son, but for families that do not use sex selection
 duration to next birth is still shorter when no boys are present.
@@
 What has not previously been appreciated is that the introduction 
-of prenatal sex determination fundamentally changed the relationship between 
-son preference and birth spacing.
+of prenatal sex determination fundamentally changed the relationship 
+between son preference and birth spacing.
 This is because each sex-selective abortion substantially increases the 

### 2017-10-13 paper/sexSelectionSpacingAppendix-ver1.tex
Initial edits of Appendix for this version

@@
 
-\usepackage{mathpazo}
+\usepackage{fontspec}
+\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
+\usepackage{unicode-math}
+\setmathfont{TeX Gyre Pagella Math}
 \usepackage[title]{appendix}
@@
 \usepackage{setspace}
-% \usepackage[pdftex]{graphicx}
-% \usepackage[all]{xypic}
-\usepackage{xyling}
 \usepackage[justification=centering]{caption}
 \usepackage[font=scriptsize]{subfig}
-\usepackage[pdftex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
+\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
 \usepackage{adjustbox}
@@
 % \date{May 2010\\ \bigskip PRELIMINARY}
-\date{March 2015}
+\date{October 2017}
 
@@
 
-\graphicspath{{graphs/},{figures/}}
-\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
+\graphicspath{{../figures/}}
+\DeclareGraphicsExtensions{.eps,.jpg,.pdf,.mps,.png}
 \doublespacing
@@
 
-\section{Why Bundle Scan and Abortion?}
-
-The easiest way to show why a bundled service makes sense is to model 
-the provider's problem first and then show that both provider and
-buyer will be better off if a bundled service is offered.
-Take a provider with with cost, $c_a$, of providing an abortion,
-and cost, $c_s$, of providing a scan.
-These costs include expenses for equipment, labor,
-and possibly a premium for getting caught and prosecuted. 
-The provider can either charge separately for the two services,
-in which case he will charge $p_s$ for the scan and $p_a$ for
-the abortion, or he can charge $p_b$ for the bundle.
-
-The provider's profit if he offers the two services separately, $\pi_{sep}$,
-to $n$ buyers, who conceive girls with the probability $p(g)$, will be
-\begin{equation}
-\pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
-\end{equation}
-The first part is profit from the customers who want a scan
-and the second part is the profit from the fraction of the
-original customers who conceived a girl.
-If the provider instead offered the same $n$ buyers a bundle service
-the profit, $\pi_{bun}$, would be
-\begin{equation}
-\pi_{bun} = n p_b - n c_s - p(g) n c_a,
-\end{equation}
-since all customers pays $p_b$, all customers get a scan 
-at cost $c_s$, and the fraction $p(g)$ who conceived a girl
-would receive an abortion at cost $c_a$.
-A profit maximizing provider then picks bundled pricing if 
-$\pi_{bun} > \pi_{sep}$, or
-\begin{equation}
- p_b > p_s + p(g) p_a.
-\end{equation}
-
-Assume that buyers are risk averse and that the only motivation
-for getting a prenatal sex determination test is to abort 
-female fetuses and that parents will abort the fetus if the test 
-show a female fetus (I will relax the last assumptions below).
-Furthermore, to ease exposition assume that buyers can only
-spend money on two things: consumption $c$ and prenatal sex
-determinations/abortions.
-For a buyer facing separate services the expected utility
-is then
-\begin{equation}
-U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
-\end{equation}
-where the first part is the utility if the fetus is a boy
-and the buyers therefore only spend on the scan, which
-happens with probability $1-p(g)$, and the
-second part is the utility if the fetus is a female
-and they therefore also has to pay for the abortion,
-which happens with probability $p(g)$.
-For a buyer facing a bundled service the utility is simply
-\begin{equation}
-U = U(c-p_b).
-\end{equation}
-
-If follows from the standard assumptions about utility functions
-and the risk aversion assumption that
-\begin{equation}
-U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
-\end{equation}
-In other words risk averse buyers prefer a sure thing---where they pay 
-upfront---over the gamble that they either have a boy and pay only for the
-scanning or have a girl and pay for both the scan and the abortion.
-In fact, risk aversion implies that they are willing to pay 
-\emph{more} than the expected cost.
-In other words,
-\begin{equation}
-U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
-\end{equation}
-where $\delta$ is a positive number that depends on the
-degree of risk aversion (the more risk averse the larger
-$\delta$ is).
-
-The provider realizes that buyers are risk averse
-and therefore offer a bundle where the price is in 
-the range
-\begin{equation}
-p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
-\end{equation}
-Hence, the optimal pricing scheme for both provider
-and buyer is bundled pricing, where you pay a flat fee
-and get the pre-natal sex determination and an abortion
-if needed.
-% Where the provider ends up in the possible range of
-% prices depends on the nature of the provider market.
-
-I implicitly assumed that the provider is risk-neutral.
-The same result hold, however, if the provider
-is risk-averse as long as there are enough potential clients.
-In that case, the law of large numbers will ensure that 
-the risk-neutral and risk-averse choices are the same
-for the provider---essentially there is no gamble if you see 
-enough clients, $p(g)$ of them will present with a female fetus 
-and $1-p(g)$ with a male fetus.
-In fact, it is possible for the provider to be \emph{more}
-risk averse than the buyers and still prefer the bundled 
-pricing scheme.
-
-Now imagine a situation where there there is some 
-uncertainty about whether a buyer will go through with
-the abortion after the prenatal sex determination.
-This can be represented by the probability $\rho$ that
-a buyer who had a prenatal sex determination test that
-showed a female fetus will go through with the abortion.
-If parents know that there is probability $1-\rho$ that they
-will not go through with the abortion their utility is
-\begin{equation}
-U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
-\end{equation}
-where I have made the assumption that they
-are equally happy with a boy or a girl if they
-are in the $1-\rho$ portion of the population that
-have a prenatal sex determination which show a female
-fetus but do not go through with the abortion (obviously
-this cannot be the case because if they were there
-would be no point in having the prenatal sex determination,
-but if I can show that the bundle price arise here it
-would trivially hold if there were some lower utility
-associated with having a girl than a boy).
-
-Because the buyers are still risk averse they would continue
-to prefer the ``sure'' thing over the gamble
-\begin{equation}
-U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
-\end{equation}
-The provider still offers a bundle, but the price is now 
-in  the range
-\begin{equation}
-p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
-\end{equation}
-where $\delta$ still depends on the degree of risk aversion.
-
-If parents on the other hand initially believe that they will always
-go through with the abortion if the fetus is female but
-still have probability $1-\rho$ that they will not, they would
-be back to the original comparison of the utility.
-\begin{equation}
-U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
-\end{equation}
-All that would do is \emph{increase} the profit for the
-provider because the law of large numbers would tell them
-exactly how many would not go through with the abortion.
-In other words, they would offer the original
-bundled price because the buyers did not know that they
-will change their mind
-\begin{equation}
-p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
-\end{equation}
-but the provider will have profit of
-\begin{equation}
-p_b - c_s - \rho c_a,
-\end{equation}
-which is strictly larger than the profit in either of
-the other cases.
-Also, they do not need to know which buyers are more
-or less likely to use abortion, just that some
-fraction will not use their purchased abortion.
-
-\clearpage
-\newpage
-
-\section{Simulation Results for 20 Periods}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_100}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
- k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
- k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
- k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
- k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
- k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
- k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
- k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
- k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
- k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_95}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
- k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
- k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
- k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
- k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.09 &  56.9 &  7.19 &  52.4 &  7.30 &  50.5 &  7.33 &  50.1 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  63.7 &  5.05 &  56.4 &  5.10 &  53.6 &  5.21 &  51.0 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  69.1 &  4.06 &  59.2 &  4.06 &  58.8 &  4.06 &  55.3 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  70.0 &  3.13 &  69.7 &  3.13 &  64.9 &  3.13 &  56.0 &  3.32 &  50.0 \\
- k = 20        &  2.50 &  65.1 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.07 &  67.6 &  7.08 &  60.9 &  7.13 &  54.8 &  7.26 &  51.4 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  78.3 &  5.05 &  67.8 &  5.05 &  62.7 &  5.06 &  56.7 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  76.0 &  4.06 &  75.4 &  4.06 &  69.7 &  4.06 &  63.3 &  4.17 &  49.9 \\
- k = 18        &  3.13 &  70.1 &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.32 &  50.0 \\
- k = 20        &  2.75 &  72.7 &  2.74 &  72.6 &  2.64 &  71.6 &  2.00 &  62.5 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  99.1 &  2.00 &  71.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_90}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
- k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
- k = 16        &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.25 &  51.9 &  3.25 &  51.4 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
- k = 20        &  2.50 &  55.1 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.01 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
- k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
- k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
- k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.24 &  55.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.30 &  50.5 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.24 &  52.3 &  5.24 &  50.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  58.8 &  4.07 &  51.5 &  4.13 &  50.7 &  4.16 &  50.1 &  4.16 &  49.9 \\
- k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 \\
- k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.63 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.12 &  53.6 &  7.31 &  50.3 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
- k = 14        &  5.05 &  63.2 &  5.21 &  52.6 &  5.24 &  50.3 &  5.26 &  50.0 &  5.27 &  50.0 \\
- k = 16        &  4.06 &  61.5 &  4.06 &  59.0 &  4.07 &  51.5 &  4.13 &  50.7 &  4.17 &  49.9 \\
- k = 18        &  3.13 &  70.0 &  3.13 &  68.3 &  3.13 &  54.0 &  3.16 &  53.5 &  3.32 &  50.0 \\
- k = 20        &  2.43 &  69.2 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  55.6 &  2.38 &  50.0 \\
- k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\footnotesize
-\begin{threeparttable}
-\caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_fertility_85}
-\begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-\toprule
-               & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
-               & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-\multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-                                       & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-\midrule
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 \\
- k = 14        &  5.42 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
- k = 16        &  4.16 &  50.7 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
- k = 18        &  3.25 &  51.9 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 \\
- k = 20        &  2.50 &  54.9 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 \\
- k = 14        &  5.40 &  50.2 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 \\
- k = 16        &  4.15 &  50.7 &  4.16 &  50.6 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
- k = 18        &  3.14 &  53.8 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 &  3.31 &  50.1 \\
- k = 20        &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  52.5 &  2.50 &  50.0 &  2.50 &  50.0 \\
- k = 22        &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  7.33 &  50.1 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
- k = 14        &  5.23 &  51.3 &  5.25 &  50.2 &  5.25 &  50.0 &  5.25 &  50.0 &  5.25 &  50.0 \\
- k = 16        &  4.06 &  52.3 &  4.12 &  50.7 &  4.14 &  50.5 &  4.15 &  50.0 &  4.15 &  50.0 \\
- k = 18        &  3.12 &  54.0 &  3.13 &  53.9 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 \\
- k = 20        &  2.25 &  61.0 &  2.31 &  59.4 &  2.50 &  54.9 &  2.51 &  54.3 &  2.62 &  50.0 \\
- k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.12 &  58.0 &  2.25 &  50.0 \\
-               &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  7.30 &  50.7 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
- k = 14        &  5.06 &  55.0 &  5.23 &  50.6 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
- k = 16        &  4.06 &  58.9 &  4.06 &  55.2 &  4.10 &  51.1 &  4.16 &  50.2 &  4.17 &  50.0 \\
- k = 18        &  3.12 &  69.7 &  3.13 &  57.1 &  3.13 &  53.9 &  3.25 &  51.8 &  3.31 &  50.1 \\
- k = 20        &  2.00 &  62.4 &  2.00 &  62.4 &  2.01 &  62.1 &  2.25 &  55.4 &  2.37 &  50.0 \\
- k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.25 &  50.0 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a]Percent boys is the percent boys of all births.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_100}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    6.0 &    0.1 &   22.3 &    1.4 &    0.0 &   28.2 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
- k = 14        &   21.6 &    0.2 &   12.3 &    5.6 &    0.1 &   23.2 &    3.2 &    0.0 &    4.8 &    3.0 &    0.0 &   15.0 \\
- k = 16        &   12.7 &    0.1 &    0.2 &   12.6 &    0.1 &    1.0 &   12.2 &    0.1 &    6.4 &    9.5 &    0.2 &   40.1 \\
- k = 18        &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   25.1 &    0.3 &    1.8 &   23.7 &    0.3 &   12.0 \\
- k = 20        &   49.6 &    0.5 &    3.2 &   37.8 &    0.6 &   40.1 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &   47.0 &    0.6 &   21.7 &   18.1 &    0.3 &   37.6 &    6.5 &    0.1 &   47.3 &    1.3 &    0.0 &   29.1 \\
- k = 14        &   56.5 &    0.9 &   36.7 &   41.9 &    0.5 &    7.6 &   31.2 &    0.5 &   34.0 &   10.8 &    0.1 &   25.1 \\
- k = 16        &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.0 &   56.4 &    0.7 &   19.4 &   22.1 &    0.3 &   22.7 \\
- k = 18        &  119.3 &    1.2 &    4.1 &   47.3 &    0.5 &   11.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 \\
- k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.2 &    0.5 &    0.9 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &  165.3 &    2.1 &   22.6 &  102.2 &    1.4 &   27.9 &   61.3 &    0.9 &   32.2 &   29.3 &    0.5 &   40.6 \\
- k = 14        &  158.7 &    1.6 &    1.0 &  135.6 &    1.4 &    4.8 &  108.0 &    1.3 &   15.4 &   64.1 &    0.8 &   19.1 \\
- k = 16        &  204.5 &    2.1 &    3.2 &  175.9 &    1.9 &   10.7 &  109.5 &    1.3 &   15.8 &   84.6 &    0.9 &    8.6 \\
- k = 18        &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 &  119.4 &    1.2 &    4.0 \\
- k = 20        &  123.9 &    1.2 &    0.0 &  107.0 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  319.6 &    3.8 &   15.6 &  256.2 &    3.3 &   21.9 &  188.1 &    2.5 &   26.3 &  131.1 &    1.6 &   17.7 \\
- k = 14        &  331.2 &    3.4 &    1.5 &  277.3 &    2.9 &    5.4 &  230.2 &    2.6 &   10.7 &  179.1 &    2.0 &   13.1 \\
- k = 16        &  213.6 &    2.1 &    0.2 &  212.2 &    2.1 &    0.7 &  208.2 &    2.1 &    2.0 &  190.3 &    2.0 &    6.6 \\
- k = 18        &  191.3 &    1.9 &    0.0 &  126.0 &    1.2 &    0.1 &  125.9 &    1.2 &    0.2 &  125.4 &    1.2 &    0.5 \\
- k = 20        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  122.3 &    1.2 &    0.0 \\
- k = 22        &  200.3 &    2.0 &    0.3 &  197.2 &    2.0 &    1.5 &  181.2 &    1.9 &    7.3 &   97.1 &    1.0 &    6.1 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a] Average number of spells per woman where scan has been used at least once.
-\item[b] Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_95}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.9 &    0.0 &    8.3 &    0.4 &    0.0 &    7.7 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . \\
- k = 14        &    3.3 &    0.0 &    0.8 &    3.2 &    0.0 &    7.2 &    1.6 &    0.0 &    7.4 &    0.8 &    0.0 &   50.3 \\
- k = 16        &   12.6 &    0.1 &    1.0 &    9.6 &    0.2 &   39.9 &    6.3 &    0.1 &    1.9 &    6.0 &    0.1 &    7.0 \\
- k = 18        &   25.3 &    0.3 &    0.3 &   23.7 &    0.3 &   11.8 &   12.6 &    0.1 &    0.5 &   12.2 &    0.1 &    3.5 \\
- k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 &   24.9 &    0.3 &    1.8 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.9 &    0.5 &    0.9 &   44.0 &    0.5 &   12.6 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &   12.3 &    0.2 &   21.2 &    4.3 &    0.1 &   42.6 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
- k = 14        &   40.5 &    0.5 &   11.8 &   18.8 &    0.2 &   20.7 &    4.8 &    0.1 &   41.2 &    2.8 &    0.0 &   24.3 \\
- k = 16        &   73.7 &    0.7 &    2.4 &   22.2 &    0.3 &   22.4 &   12.6 &    0.1 &    1.8 &   11.0 &    0.1 &   22.4 \\
- k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   24.9 &    0.3 &    3.3 \\
- k = 20        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.2 &   48.8 &    0.5 &    6.1 &   25.3 &    0.3 &    0.1 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &   98.2 &    1.3 &   23.7 &   34.6 &    0.5 &   32.0 &    8.0 &    0.1 &   39.3 &    1.3 &    0.0 &   29.1 \\
- k = 14        &  139.2 &    1.4 &    3.3 &   65.2 &    0.8 &   19.4 &   36.8 &    0.5 &   20.7 &   10.8 &    0.1 &   25.1 \\
- k = 16        &  156.3 &    1.9 &   17.6 &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.1 &   43.4 &    0.6 &   32.5 \\
- k = 18        &  125.7 &    1.2 &    0.3 &  123.9 &    1.2 &    1.4 &   93.6 &    1.1 &   18.2 &   37.7 &    0.6 &   40.2 \\
- k = 20        &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.3 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  248.9 &    2.8 &   10.0 &  155.2 &    2.0 &   24.1 &   69.0 &    0.8 &   19.1 &   21.0 &    0.3 &   26.7 \\
- k = 14        &  285.7 &    3.0 &    4.5 &  180.6 &    2.2 &   18.4 &  129.1 &    1.4 &    7.6 &   68.2 &    0.8 &   12.8 \\
- k = 16        &  213.0 &    2.1 &    0.4 &  208.3 &    2.1 &    2.0 &  161.3 &    1.8 &   12.1 &  108.9 &    1.3 &   16.2 \\
- k = 18        &  126.0 &    1.2 &    0.0 &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 \\
- k = 20        &  125.9 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  114.9 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 \\
- k = 22        &  197.1 &    2.0 &    1.6 &   87.6 &    1.1 &   22.2 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a] Average number of spells per woman where scan has been used at least once.
-\item[b] Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_90}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.4 &    0.0 &    5.0 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    3.2 &    0.0 &    4.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &    6.4 &    0.1 &    0.2 &    6.4 &    0.1 &    1.0 &    2.4 &    0.0 &   25.8 &    0.0 &    0.0 &      . \\
- k = 18        &   19.1 &    0.3 &   40.4 &   12.7 &    0.1 &    0.3 &   11.8 &    0.1 &    6.4 &    0.0 &    0.0 &      . \\
- k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.2 &   22.0 &    0.3 &   12.5 &    0.0 &    0.0 &      . \\
- k = 22        &   50.4 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &    4.4 &    0.1 &   41.3 &    0.4 &    0.0 &    7.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   21.6 &    0.2 &   12.3 &    3.2 &    0.0 &    4.4 &    1.6 &    0.0 &    7.4 &    0.0 &    0.0 &      . \\
- k = 16        &   12.7 &    0.1 &    0.2 &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.0 &    5.2 &    0.1 &   28.9 \\
- k = 18        &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.9 &   12.7 &    0.1 &    0.3 &   12.5 &    0.1 &    1.7 \\
- k = 20        &   50.3 &    0.5 &    0.2 &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.1 &    0.3 &    0.8 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &   33.0 &    0.4 &   22.5 &    4.8 &    0.1 &   47.7 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . \\
- k = 14        &   43.9 &    0.4 &    1.7 &   26.1 &    0.3 &   11.2 &    4.8 &    0.1 &   41.2 &    1.6 &    0.0 &    7.4 \\
- k = 16        &   75.6 &    0.8 &    0.4 &   69.2 &    0.7 &    7.0 &   12.6 &    0.1 &    1.8 &    6.4 &    0.1 &    1.0 \\
- k = 18        &  124.8 &    1.2 &    0.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 &   24.9 &    0.3 &    3.3 \\
- k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.4 &   37.7 &    0.6 &   40.1 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &  139.8 &    1.5 &    7.8 &   44.0 &    0.5 &   19.3 &    5.4 &    0.1 &   36.8 &    0.2 &    0.0 &   48.2 \\
- k = 14        &  144.2 &    1.4 &    0.7 &  120.3 &    1.3 &   11.4 &   39.1 &    0.5 &   14.0 &    5.9 &    0.1 &   14.2 \\
- k = 16        &  210.7 &    2.1 &    1.2 &  116.1 &    1.3 &   11.2 &   73.7 &    0.7 &    2.2 &   24.5 &    0.3 &    6.7 \\
- k = 18        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.3 &  119.4 &    1.2 &    4.0 &   44.1 &    0.6 &   22.6 \\
- k = 20        &  125.4 &    1.2 &    0.0 &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a] Average number of spells per woman where scan has been used at least once.
-\item[b] Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\begin{table}[!htp]
-\centering
-\scriptsize
-\begin{threeparttable}
-\caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-\label{tab:simul_abortion_85}
-\begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-\toprule
-               & \multicolumn{12}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
-               & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-               & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-                                      & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-\multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-                                      & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-\midrule
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
- k = 12        &    0.2 &    0.0 &   16.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    1.7 &    0.0 &    2.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &    6.4 &    0.1 &    0.7 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 18        &   12.7 &    0.1 &    0.2 &    9.4 &    0.1 &   24.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 20        &   25.3 &    0.3 &    0.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 22        &   49.3 &    0.5 &    3.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
- k = 12        &    0.4 &    0.0 &    5.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &    3.3 &    0.0 &    2.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 16        &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.3 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . \\
- k = 18        &   25.3 &    0.3 &    0.5 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . \\
- k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   24.9 &    0.3 &    1.8 &    0.0 &    0.0 &      . \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   24.4 &    0.2 &    0.0 &    0.0 &    0.0 &      . \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
- k = 12        &    7.0 &    0.1 &   13.3 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
- k = 14        &   24.8 &    0.3 &    2.3 &    3.2 &    0.0 &    4.0 &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . \\
- k = 16        &   72.0 &    0.7 &    4.3 &   12.5 &    0.1 &    3.5 &    6.3 &    0.1 &    2.4 &    1.6 &    0.0 &   51.2 \\
- k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.3 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 \\
- k = 20        &   50.4 &    0.5 &    0.0 &   50.2 &    0.5 &    0.9 &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.5 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   49.8 &    0.5 &    1.8 \\
-               &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
- k = 12        &   52.3 &    0.6 &   14.5 &    4.4 &    0.1 &   41.3 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . \\
- k = 14        &  134.3 &    1.4 &    7.0 &   27.3 &    0.3 &    6.2 &    3.1 &    0.0 &   14.2 &    0.8 &    0.0 &   50.3 \\
- k = 16        &   94.6 &    1.1 &   12.0 &   73.8 &    0.7 &    2.2 &   12.6 &    0.1 &    1.8 &    6.2 &    0.1 &    4.3 \\
- k = 18        &  126.0 &    1.2 &    0.1 &  114.7 &    1.2 &    6.8 &   25.3 &    0.3 &    0.2 &   22.2 &    0.3 &   22.4 \\
- k = 20        &   94.4 &    0.9 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   25.3 &    0.3 &    0.1 \\
- k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-\bottomrule
-\end{tabular}
-\begin{tablenotes} \tiny
-\item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
- and a probability of a son of 0.5.
-\item[a] Average number of spells per woman where scan has been used at least once.
-\item[b] Percent of spells where prenatal scan was initially used but birth is the result
-of pregnancy without prenatal scan.
-\end{tablenotes}
-\end{threeparttable}
-\normalsize
-\end{table}
-
-\clearpage
-\newpage
+% \section{Why Bundle Scan and Abortion?}
+% 
+% The easiest way to show why a bundled service makes sense is to model 
+% the provider's problem first and then show that both provider and
+% buyer will be better off if a bundled service is offered.
+% Take a provider with with cost, $c_a$, of providing an abortion,
+% and cost, $c_s$, of providing a scan.
+% These costs include expenses for equipment, labor,
+% and possibly a premium for getting caught and prosecuted. 
+% The provider can either charge separately for the two services,
+% in which case he will charge $p_s$ for the scan and $p_a$ for
+% the abortion, or he can charge $p_b$ for the bundle.
+% 
+% The provider's profit if he offers the two services separately, $\pi_{sep}$,
+% to $n$ buyers, who conceive girls with the probability $p(g)$, will be
+% \begin{equation}
+% \pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
+% \end{equation}
+% The first part is profit from the customers who want a scan
+% and the second part is the profit from the fraction of the
+% original customers who conceived a girl.
+% If the provider instead offered the same $n$ buyers a bundle service
+% the profit, $\pi_{bun}$, would be
+% \begin{equation}
+% \pi_{bun} = n p_b - n c_s - p(g) n c_a,
+% \end{equation}
+% since all customers pays $p_b$, all customers get a scan 
+% at cost $c_s$, and the fraction $p(g)$ who conceived a girl
+% would receive an abortion at cost $c_a$.
+% A profit maximizing provider then picks bundled pricing if 
+% $\pi_{bun} > \pi_{sep}$, or
+% \begin{equation}
+%  p_b > p_s + p(g) p_a.
+% \end{equation}
+% 
+% Assume that buyers are risk averse and that the only motivation
+% for getting a prenatal sex determination test is to abort 
+% female fetuses and that parents will abort the fetus if the test 
+% show a female fetus (I will relax the last assumptions below).
+% Furthermore, to ease exposition assume that buyers can only
+% spend money on two things: consumption $c$ and prenatal sex
+% determinations/abortions.
+% For a buyer facing separate services the expected utility
+% is then
+% \begin{equation}
+% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
+% \end{equation}
+% where the first part is the utility if the fetus is a boy
+% and the buyers therefore only spend on the scan, which
+% happens with probability $1-p(g)$, and the
+% second part is the utility if the fetus is a female
+% and they therefore also has to pay for the abortion,
+% which happens with probability $p(g)$.
+% For a buyer facing a bundled service the utility is simply
+% \begin{equation}
+% U = U(c-p_b).
+% \end{equation}
+% 
+% If follows from the standard assumptions about utility functions
+% and the risk aversion assumption that
+% \begin{equation}
+% U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
+% \end{equation}
+% In other words risk averse buyers prefer a sure thing---where they pay 
+% upfront---over the gamble that they either have a boy and pay only for the
+% scanning or have a girl and pay for both the scan and the abortion.
+% In fact, risk aversion implies that they are willing to pay 
+% \emph{more} than the expected cost.
+% In other words,
+% \begin{equation}
+% U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
+% \end{equation}
+% where $\delta$ is a positive number that depends on the
+% degree of risk aversion (the more risk averse the larger
+% $\delta$ is).
+% 
+% The provider realizes that buyers are risk averse
+% and therefore offer a bundle where the price is in 
+% the range
+% \begin{equation}
+% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
+% \end{equation}
+% Hence, the optimal pricing scheme for both provider
+% and buyer is bundled pricing, where you pay a flat fee
+% and get the pre-natal sex determination and an abortion
+% if needed.
+% % Where the provider ends up in the possible range of
+% % prices depends on the nature of the provider market.
+% 
+% I implicitly assumed that the provider is risk-neutral.
+% The same result hold, however, if the provider
+% is risk-averse as long as there are enough potential clients.
+% In that case, the law of large numbers will ensure that 
+% the risk-neutral and risk-averse choices are the same
+% for the provider---essentially there is no gamble if you see 
+% enough clients, $p(g)$ of them will present with a female fetus 
+% and $1-p(g)$ with a male fetus.
+% In fact, it is possible for the provider to be \emph{more}
+% risk averse than the buyers and still prefer the bundled 
+% pricing scheme.
+% 
+% Now imagine a situation where there there is some 
+% uncertainty about whether a buyer will go through with
+% the abortion after the prenatal sex determination.
+% This can be represented by the probability $\rho$ that
+% a buyer who had a prenatal sex determination test that
+% showed a female fetus will go through with the abortion.
+% If parents know that there is probability $1-\rho$ that they
+% will not go through with the abortion their utility is
+% \begin{equation}
+% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
+% \end{equation}
+% where I have made the assumption that they
+% are equally happy with a boy or a girl if they
+% are in the $1-\rho$ portion of the population that
+% have a prenatal sex determination which show a female
+% fetus but do not go through with the abortion (obviously
+% this cannot be the case because if they were there
+% would be no point in having the prenatal sex determination,
+% but if I can show that the bundle price arise here it
+% would trivially hold if there were some lower utility
+% associated with having a girl than a boy).
+% 
+% Because the buyers are still risk averse they would continue
+% to prefer the ``sure'' thing over the gamble
+% \begin{equation}
+% U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
+% \end{equation}
+% The provider still offers a bundle, but the price is now 
+% in  the range
+% \begin{equation}
+% p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
+% \end{equation}
+% where $\delta$ still depends on the degree of risk aversion.
+% 
+% If parents on the other hand initially believe that they will always
+% go through with the abortion if the fetus is female but
+% still have probability $1-\rho$ that they will not, they would
+% be back to the original comparison of the utility.
+% \begin{equation}
+% U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
+% \end{equation}
+% All that would do is \emph{increase} the profit for the
+% provider because the law of large numbers would tell them
+% exactly how many would not go through with the abortion.
+% In other words, they would offer the original
+% bundled price because the buyers did not know that they
+% will change their mind
+% \begin{equation}
+% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
+% \end{equation}
+% but the provider will have profit of
+% \begin{equation}
+% p_b - c_s - \rho c_a,
+% \end{equation}
+% which is strictly larger than the profit in either of
+% the other cases.
+% Also, they do not need to know which buyers are more
+% or less likely to use abortion, just that some
+% fraction will not use their purchased abortion.
+% 
+% \clearpage
+% \newpage
+%
+
+% \section{Simulation Results for 20 Periods}
+% 
+% \begin{table}[!htp]
+% \centering
+% \footnotesize
+% \begin{threeparttable}
+% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_fertility_100}
+% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
+% \toprule
+%                & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
+%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
+% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
+%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
+% \midrule
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
+%  k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
+%  k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
+%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
+%  k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
+%  k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
+%  k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
+%  k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
+%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
+%  k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
+%  k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
+%  k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
+%  k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
+%  k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
+%  k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
+%  k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
+%  k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
+%  k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \scriptsize
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a]Percent boys is the percent boys of all births.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% 
+% \begin{table}[!htp]
+% \centering
+% \footnotesize
+% \begin{threeparttable}
+% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_fertility_95}
+% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
+% \toprule
+%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
+%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
+% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
+%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
+% \midrule
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
+%  k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
+%  k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
+%  k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
+%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
+%  k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
+%  k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
+%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
+%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &  7.09 &  56.9 &  7.19 &  52.4 &  7.30 &  50.5 &  7.33 &  50.1 &  7.34 &  50.0 \\
+%  k = 14        &  5.05 &  63.7 &  5.05 &  56.4 &  5.10 &  53.6 &  5.21 &  51.0 &  5.26 &  50.0 \\
+%  k = 16        &  4.06 &  69.1 &  4.06 &  59.2 &  4.06 &  58.8 &  4.06 &  55.3 &  4.16 &  49.9 \\
+%  k = 18        &  3.13 &  70.0 &  3.13 &  69.7 &  3.13 &  64.9 &  3.13 &  56.0 &  3.32 &  50.0 \\
+%  k = 20        &  2.50 &  65.1 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  7.07 &  67.6 &  7.08 &  60.9 &  7.13 &  54.8 &  7.26 &  51.4 &  7.34 &  50.0 \\
+%  k = 14        &  5.05 &  78.3 &  5.05 &  67.8 &  5.05 &  62.7 &  5.06 &  56.7 &  5.27 &  50.0 \\
+%  k = 16        &  4.06 &  76.0 &  4.06 &  75.4 &  4.06 &  69.7 &  4.06 &  63.3 &  4.17 &  49.9 \\
+%  k = 18        &  3.13 &  70.1 &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.32 &  50.0 \\
+%  k = 20        &  2.75 &  72.7 &  2.74 &  72.6 &  2.64 &  71.6 &  2.00 &  62.5 &  2.38 &  50.0 \\
+%  k = 22        &  2.00 &  99.1 &  2.00 &  71.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \scriptsize
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a]Percent boys is the percent boys of all births.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% \begin{table}[!htp]
+% \centering
+% \footnotesize
+% \begin{threeparttable}
+% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_fertility_90}
+% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
+% \toprule
+%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
+%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
+% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
+%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
+% \midrule
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
+%  k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
+%  k = 16        &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
+%  k = 18        &  3.25 &  51.9 &  3.25 &  51.4 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
+%  k = 20        &  2.50 &  55.1 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
+%  k = 22        &  2.01 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
+%  k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
+%  k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 \\
+%  k = 18        &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
+%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.24 &  55.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &  7.30 &  50.5 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
+%  k = 14        &  5.24 &  52.3 &  5.24 &  50.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
+%  k = 16        &  4.06 &  58.8 &  4.07 &  51.5 &  4.13 &  50.7 &  4.16 &  50.1 &  4.16 &  49.9 \\
+%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 \\
+%  k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.63 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  7.12 &  53.6 &  7.31 &  50.3 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
+%  k = 14        &  5.05 &  63.2 &  5.21 &  52.6 &  5.24 &  50.3 &  5.26 &  50.0 &  5.27 &  50.0 \\
+%  k = 16        &  4.06 &  61.5 &  4.06 &  59.0 &  4.07 &  51.5 &  4.13 &  50.7 &  4.17 &  49.9 \\
+%  k = 18        &  3.13 &  70.0 &  3.13 &  68.3 &  3.13 &  54.0 &  3.16 &  53.5 &  3.32 &  50.0 \\
+%  k = 20        &  2.43 &  69.2 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  55.6 &  2.38 &  50.0 \\
+%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \scriptsize
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a]Percent boys is the percent boys of all births.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% \begin{table}[!htp]
+% \centering
+% \footnotesize
+% \begin{threeparttable}
+% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_fertility_85}
+% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
+% \toprule
+%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
+%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
+% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
+%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
+% \midrule
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 \\
+%  k = 14        &  5.42 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
+%  k = 16        &  4.16 &  50.7 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
+%  k = 18        &  3.25 &  51.9 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 \\
+%  k = 20        &  2.50 &  54.9 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
+%  k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 \\
+%  k = 14        &  5.40 &  50.2 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 \\
+%  k = 16        &  4.15 &  50.7 &  4.16 &  50.6 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
+%  k = 18        &  3.14 &  53.8 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 &  3.31 &  50.1 \\
+%  k = 20        &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  52.5 &  2.50 &  50.0 &  2.50 &  50.0 \\
+%  k = 22        &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &  7.33 &  50.1 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
+%  k = 14        &  5.23 &  51.3 &  5.25 &  50.2 &  5.25 &  50.0 &  5.25 &  50.0 &  5.25 &  50.0 \\
+%  k = 16        &  4.06 &  52.3 &  4.12 &  50.7 &  4.14 &  50.5 &  4.15 &  50.0 &  4.15 &  50.0 \\
+%  k = 18        &  3.12 &  54.0 &  3.13 &  53.9 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 \\
+%  k = 20        &  2.25 &  61.0 &  2.31 &  59.4 &  2.50 &  54.9 &  2.51 &  54.3 &  2.62 &  50.0 \\
+%  k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.12 &  58.0 &  2.25 &  50.0 \\
+%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  7.30 &  50.7 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
+%  k = 14        &  5.06 &  55.0 &  5.23 &  50.6 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
+%  k = 16        &  4.06 &  58.9 &  4.06 &  55.2 &  4.10 &  51.1 &  4.16 &  50.2 &  4.17 &  50.0 \\
+%  k = 18        &  3.12 &  69.7 &  3.13 &  57.1 &  3.13 &  53.9 &  3.25 &  51.8 &  3.31 &  50.1 \\
+%  k = 20        &  2.00 &  62.4 &  2.00 &  62.4 &  2.01 &  62.1 &  2.25 &  55.4 &  2.37 &  50.0 \\
+%  k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.25 &  50.0 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \scriptsize
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a]Percent boys is the percent boys of all births.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% 
+% \begin{table}[!htp]
+% \centering
+% \scriptsize
+% \begin{threeparttable}
+% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_abortion_100}
+% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
+% \toprule
+%                & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
+%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
+%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
+% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
+%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
+% \midrule
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &    6.0 &    0.1 &   22.3 &    1.4 &    0.0 &   28.2 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
+%  k = 14        &   21.6 &    0.2 &   12.3 &    5.6 &    0.1 &   23.2 &    3.2 &    0.0 &    4.8 &    3.0 &    0.0 &   15.0 \\
+%  k = 16        &   12.7 &    0.1 &    0.2 &   12.6 &    0.1 &    1.0 &   12.2 &    0.1 &    6.4 &    9.5 &    0.2 &   40.1 \\
+%  k = 18        &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   25.1 &    0.3 &    1.8 &   23.7 &    0.3 &   12.0 \\
+%  k = 20        &   49.6 &    0.5 &    3.2 &   37.8 &    0.6 &   40.1 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &   47.0 &    0.6 &   21.7 &   18.1 &    0.3 &   37.6 &    6.5 &    0.1 &   47.3 &    1.3 &    0.0 &   29.1 \\
+%  k = 14        &   56.5 &    0.9 &   36.7 &   41.9 &    0.5 &    7.6 &   31.2 &    0.5 &   34.0 &   10.8 &    0.1 &   25.1 \\
+%  k = 16        &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.0 &   56.4 &    0.7 &   19.4 &   22.1 &    0.3 &   22.7 \\
+%  k = 18        &  119.3 &    1.2 &    4.1 &   47.3 &    0.5 &   11.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 \\
+%  k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.2 &    0.5 &    0.9 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &  165.3 &    2.1 &   22.6 &  102.2 &    1.4 &   27.9 &   61.3 &    0.9 &   32.2 &   29.3 &    0.5 &   40.6 \\
+%  k = 14        &  158.7 &    1.6 &    1.0 &  135.6 &    1.4 &    4.8 &  108.0 &    1.3 &   15.4 &   64.1 &    0.8 &   19.1 \\
+%  k = 16        &  204.5 &    2.1 &    3.2 &  175.9 &    1.9 &   10.7 &  109.5 &    1.3 &   15.8 &   84.6 &    0.9 &    8.6 \\
+%  k = 18        &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 &  119.4 &    1.2 &    4.0 \\
+%  k = 20        &  123.9 &    1.2 &    0.0 &  107.0 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  319.6 &    3.8 &   15.6 &  256.2 &    3.3 &   21.9 &  188.1 &    2.5 &   26.3 &  131.1 &    1.6 &   17.7 \\
+%  k = 14        &  331.2 &    3.4 &    1.5 &  277.3 &    2.9 &    5.4 &  230.2 &    2.6 &   10.7 &  179.1 &    2.0 &   13.1 \\
+%  k = 16        &  213.6 &    2.1 &    0.2 &  212.2 &    2.1 &    0.7 &  208.2 &    2.1 &    2.0 &  190.3 &    2.0 &    6.6 \\
+%  k = 18        &  191.3 &    1.9 &    0.0 &  126.0 &    1.2 &    0.1 &  125.9 &    1.2 &    0.2 &  125.4 &    1.2 &    0.5 \\
+%  k = 20        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  122.3 &    1.2 &    0.0 \\
+%  k = 22        &  200.3 &    2.0 &    0.3 &  197.2 &    2.0 &    1.5 &  181.2 &    1.9 &    7.3 &   97.1 &    1.0 &    6.1 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \tiny
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a] Average number of spells per woman where scan has been used at least once.
+% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
+% of pregnancy without prenatal scan.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% 
+% \begin{table}[!htp]
+% \centering
+% \scriptsize
+% \begin{threeparttable}
+% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_abortion_95}
+% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
+% \toprule
+%                & \multicolumn{12}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
+%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
+%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
+% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
+%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
+% \midrule
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &    0.9 &    0.0 &    8.3 &    0.4 &    0.0 &    7.7 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . \\
+%  k = 14        &    3.3 &    0.0 &    0.8 &    3.2 &    0.0 &    7.2 &    1.6 &    0.0 &    7.4 &    0.8 &    0.0 &   50.3 \\
+%  k = 16        &   12.6 &    0.1 &    1.0 &    9.6 &    0.2 &   39.9 &    6.3 &    0.1 &    1.9 &    6.0 &    0.1 &    7.0 \\
+%  k = 18        &   25.3 &    0.3 &    0.3 &   23.7 &    0.3 &   11.8 &   12.6 &    0.1 &    0.5 &   12.2 &    0.1 &    3.5 \\
+%  k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 &   24.9 &    0.3 &    1.8 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.9 &    0.5 &    0.9 &   44.0 &    0.5 &   12.6 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &   12.3 &    0.2 &   21.2 &    4.3 &    0.1 &   42.6 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
+%  k = 14        &   40.5 &    0.5 &   11.8 &   18.8 &    0.2 &   20.7 &    4.8 &    0.1 &   41.2 &    2.8 &    0.0 &   24.3 \\
+%  k = 16        &   73.7 &    0.7 &    2.4 &   22.2 &    0.3 &   22.4 &   12.6 &    0.1 &    1.8 &   11.0 &    0.1 &   22.4 \\
+%  k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   24.9 &    0.3 &    3.3 \\
+%  k = 20        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.2 &   48.8 &    0.5 &    6.1 &   25.3 &    0.3 &    0.1 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &   98.2 &    1.3 &   23.7 &   34.6 &    0.5 &   32.0 &    8.0 &    0.1 &   39.3 &    1.3 &    0.0 &   29.1 \\
+%  k = 14        &  139.2 &    1.4 &    3.3 &   65.2 &    0.8 &   19.4 &   36.8 &    0.5 &   20.7 &   10.8 &    0.1 &   25.1 \\
+%  k = 16        &  156.3 &    1.9 &   17.6 &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.1 &   43.4 &    0.6 &   32.5 \\
+%  k = 18        &  125.7 &    1.2 &    0.3 &  123.9 &    1.2 &    1.4 &   93.6 &    1.1 &   18.2 &   37.7 &    0.6 &   40.2 \\
+%  k = 20        &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.3 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  248.9 &    2.8 &   10.0 &  155.2 &    2.0 &   24.1 &   69.0 &    0.8 &   19.1 &   21.0 &    0.3 &   26.7 \\
+%  k = 14        &  285.7 &    3.0 &    4.5 &  180.6 &    2.2 &   18.4 &  129.1 &    1.4 &    7.6 &   68.2 &    0.8 &   12.8 \\
+%  k = 16        &  213.0 &    2.1 &    0.4 &  208.3 &    2.1 &    2.0 &  161.3 &    1.8 &   12.1 &  108.9 &    1.3 &   16.2 \\
+%  k = 18        &  126.0 &    1.2 &    0.0 &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 \\
+%  k = 20        &  125.9 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  114.9 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 \\
+%  k = 22        &  197.1 &    2.0 &    1.6 &   87.6 &    1.1 &   22.2 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \tiny
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a] Average number of spells per woman where scan has been used at least once.
+% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
+% of pregnancy without prenatal scan.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% \begin{table}[!htp]
+% \centering
+% \scriptsize
+% \begin{threeparttable}
+% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_abortion_90}
+% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
+% \toprule
+%                & \multicolumn{12}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
+%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
+%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
+% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
+%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
+% \midrule
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &    0.4 &    0.0 &    5.0 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 14        &    3.2 &    0.0 &    4.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 16        &    6.4 &    0.1 &    0.2 &    6.4 &    0.1 &    1.0 &    2.4 &    0.0 &   25.8 &    0.0 &    0.0 &      . \\
+%  k = 18        &   19.1 &    0.3 &   40.4 &   12.7 &    0.1 &    0.3 &   11.8 &    0.1 &    6.4 &    0.0 &    0.0 &      . \\
+%  k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.2 &   22.0 &    0.3 &   12.5 &    0.0 &    0.0 &      . \\
+%  k = 22        &   50.4 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &    4.4 &    0.1 &   41.3 &    0.4 &    0.0 &    7.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 14        &   21.6 &    0.2 &   12.3 &    3.2 &    0.0 &    4.4 &    1.6 &    0.0 &    7.4 &    0.0 &    0.0 &      . \\
+%  k = 16        &   12.7 &    0.1 &    0.2 &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.0 &    5.2 &    0.1 &   28.9 \\
+%  k = 18        &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.9 &   12.7 &    0.1 &    0.3 &   12.5 &    0.1 &    1.7 \\
+%  k = 20        &   50.3 &    0.5 &    0.2 &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.1 &    0.3 &    0.8 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &   33.0 &    0.4 &   22.5 &    4.8 &    0.1 &   47.7 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . \\
+%  k = 14        &   43.9 &    0.4 &    1.7 &   26.1 &    0.3 &   11.2 &    4.8 &    0.1 &   41.2 &    1.6 &    0.0 &    7.4 \\
+%  k = 16        &   75.6 &    0.8 &    0.4 &   69.2 &    0.7 &    7.0 &   12.6 &    0.1 &    1.8 &    6.4 &    0.1 &    1.0 \\
+%  k = 18        &  124.8 &    1.2 &    0.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 &   24.9 &    0.3 &    3.3 \\
+%  k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.4 &   37.7 &    0.6 &   40.1 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &  139.8 &    1.5 &    7.8 &   44.0 &    0.5 &   19.3 &    5.4 &    0.1 &   36.8 &    0.2 &    0.0 &   48.2 \\
+%  k = 14        &  144.2 &    1.4 &    0.7 &  120.3 &    1.3 &   11.4 &   39.1 &    0.5 &   14.0 &    5.9 &    0.1 &   14.2 \\
+%  k = 16        &  210.7 &    2.1 &    1.2 &  116.1 &    1.3 &   11.2 &   73.7 &    0.7 &    2.2 &   24.5 &    0.3 &    6.7 \\
+%  k = 18        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.3 &  119.4 &    1.2 &    4.0 &   44.1 &    0.6 &   22.6 \\
+%  k = 20        &  125.4 &    1.2 &    0.0 &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \tiny
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a] Average number of spells per woman where scan has been used at least once.
+% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
+% of pregnancy without prenatal scan.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% \begin{table}[!htp]
+% \centering
+% \scriptsize
+% \begin{threeparttable}
+% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
+% \label{tab:simul_abortion_85}
+% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
+% \toprule
+%                & \multicolumn{12}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
+%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
+%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
+%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
+% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
+%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
+% \midrule
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
+%  k = 12        &    0.2 &    0.0 &   16.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 14        &    1.7 &    0.0 &    2.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 16        &    6.4 &    0.1 &    0.7 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 18        &   12.7 &    0.1 &    0.2 &    9.4 &    0.1 &   24.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 20        &   25.3 &    0.3 &    0.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 22        &   49.3 &    0.5 &    3.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
+%  k = 12        &    0.4 &    0.0 &    5.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 14        &    3.3 &    0.0 &    2.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 16        &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.3 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . \\
+%  k = 18        &   25.3 &    0.3 &    0.5 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . \\
+%  k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   24.9 &    0.3 &    1.8 &    0.0 &    0.0 &      . \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   24.4 &    0.2 &    0.0 &    0.0 &    0.0 &      . \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
+%  k = 12        &    7.0 &    0.1 &   13.3 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
+%  k = 14        &   24.8 &    0.3 &    2.3 &    3.2 &    0.0 &    4.0 &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . \\
+%  k = 16        &   72.0 &    0.7 &    4.3 &   12.5 &    0.1 &    3.5 &    6.3 &    0.1 &    2.4 &    1.6 &    0.0 &   51.2 \\
+%  k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.3 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 \\
+%  k = 20        &   50.4 &    0.5 &    0.0 &   50.2 &    0.5 &    0.9 &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.5 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   49.8 &    0.5 &    1.8 \\
+%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
+%  k = 12        &   52.3 &    0.6 &   14.5 &    4.4 &    0.1 &   41.3 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . \\
+%  k = 14        &  134.3 &    1.4 &    7.0 &   27.3 &    0.3 &    6.2 &    3.1 &    0.0 &   14.2 &    0.8 &    0.0 &   50.3 \\
+%  k = 16        &   94.6 &    1.1 &   12.0 &   73.8 &    0.7 &    2.2 &   12.6 &    0.1 &    1.8 &    6.2 &    0.1 &    4.3 \\
+%  k = 18        &  126.0 &    1.2 &    0.1 &  114.7 &    1.2 &    6.8 &   25.3 &    0.3 &    0.2 &   22.2 &    0.3 &   22.4 \\
+%  k = 20        &   94.4 &    0.9 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   25.3 &    0.3 &    0.1 \\
+%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes} \tiny
+% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
+%  and a probability of a son of 0.5.
+% \item[a] Average number of spells per woman where scan has been used at least once.
+% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
+% of pregnancy without prenatal scan.
+% \end{tablenotes}
+% \end{threeparttable}
+% \normalsize
+% \end{table}
+% 
+% 
+% \clearpage
+% \newpage
+%
 
@@
 
-\begin{figure}[htp]%
-\centering
-\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
-\caption{Sex ratio of ``first'' births by duration of marriage}
-\label{fig:sexRatioMarriage}}
-\end{figure}
+[Figure sex ratio marriage here!]
+
+% \begin{figure}[htp]%
+% \centering
+% \includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
+% \caption{Sex ratio of ``first'' births by duration of marriage}
+% \label{fig:sexRatioMarriage}}
+% \end{figure}
 
@@
 
-\begin{figure}[htpb!]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=4,518)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,309)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,762)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=25,486)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=23,360)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=7,922)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with no education by quarter (3 month
-period). 
-Predictions based on age 16 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell1_low}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=3,666)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,104)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,302)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=7,496)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=9,000)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=5,208)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-period). 
-Predictions based on age 17 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell1_med}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=7,338)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=11,045)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=9,116)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=3,933)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=8,027)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=7,504)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 8 or more years of education by quarter
-(3 month period). 
-Predictions based on age 20 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell1_high}
-\end{figure}
-
-\clearpage
-\newpage
+% \begin{figure}[htpb!]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=4,518)]{
+% \begin{minipage}{0.28\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}} 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=4,309)]{
+% \begin{minipage}{0.28\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=1,762)]{
+% \begin{minipage}{0.28\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=25,486)]{
+% \begin{minipage}{0.28\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=23,360)]{
+% \begin{minipage}{0.28\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=7,922)]{
+% \begin{minipage}{0.28\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with no education by quarter (3 month
+% period). 
+% Predictions based on age 16 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_spell1_low}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=3,666)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}} 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=4,104)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=2,302)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=7,496)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=9,000)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=5,208)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
+% period). 
+% Predictions based on age 17 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_spell1_med}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=7,338)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}} 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=11,045)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=9,116)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=3,933)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=8,027)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=7,504)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with 8 or more years of education by quarter
+% (3 month period). 
+% Predictions based on age 20 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_spell1_high}
+% \end{figure}
+% 
+% \clearpage
+% \newpage
 
@@
 
-\subsection{Fourth Spell}
-
-% low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=130)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=446)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=200)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=410)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,185)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=601)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_low_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=389)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,145)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=486)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=141)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=382)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=155)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+% \subsection{Fourth Spell}
+% 
+% % low education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First three children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=130)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=446)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=200)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children one boy and two girls}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=410)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=1,185)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=601)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_spell4_low_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=752)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,954)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=888)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,065)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=5,990)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=2,456)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_low_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=2,168)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=5,439)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=2,155)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=777)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,895)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=696)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \ContinuedFloat
+% \caption*{First three children two boys and one girl}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=389)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=1,145)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=486)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children three boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=141)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=382)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=155)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% % \label{fig:results_spell4_low_urban}
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First three children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=752)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=1,954)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=888)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children one boy and two girls}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=2,065)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=5,990)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=2,456)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_spell4_low_rural}
-\end{figure}
-
-% Medium education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=110)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=282)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=144)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=299)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=765)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=372)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_med_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=274)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=600)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=275)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=77)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=230)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=90)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \ContinuedFloat
+% \centering
+% \caption*{First three children two boys and one girl}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=2,168)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=5,439)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=2,155)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=777)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=1,895)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=696)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% % \label{fig:results_spell4_low_rural}
+% \end{figure}
+% 
+% 
+% 
+% % Medium education
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First three children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=110)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=282)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=144)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children one boy and two girls}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=299)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=765)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=372)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_spell4_med_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=210)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=601)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=317)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=581)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,532)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=800)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_med_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=492)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,197)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=578)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=158)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=357)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=192)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \ContinuedFloat
+% \caption*{First three children two boys and one girl}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=274)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=600)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=275)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children three boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=77)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=230)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=90)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% % \label{fig:results_spell4_med_urban}
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First three children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=210)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=601)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=317)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children one boy and two girls}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=581)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=1,532)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=800)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_spell4_med_rural}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=131)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=355)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=191)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=353)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,062)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=590)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=309)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=681)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=344)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=87)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=233)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=110)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \ContinuedFloat
+% \centering
+% \caption*{First three children two boys and one girl}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=492)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=1,197)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=578)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children three boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=158)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=357)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=192)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% % \label{fig:results_spell4_med_rural}
+% \end{figure}
+% 
+% 
+% 
+% 
+% 
+% % High education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First three children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=131)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=355)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=191)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children one boy and two girls}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=353)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=1,062)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=590)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_spell4_high_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=62)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=257)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=201)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=176)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=664)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=564)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_high_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=173)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=515)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=367)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=56)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=166)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=92)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \ContinuedFloat
+% \caption*{First three children two boys and one girl}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=309)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=681)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=344)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children three boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=87)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=233)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=110)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% % \label{fig:results_spell4_high_urban}
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First three children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=62)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=257)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=201)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children one boy and two girls}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=176)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=664)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=564)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_spell4_high_rural}
-\end{figure}
-
-\clearpage
-
-\section{Graphs using Women Married less than 19 Years}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% Figures \ref{fig:results_spell2_low_urban} to \ref{fig:results_spell4_low_rural_cont}
-% show the results for the group of women with no education.
-% The starting ages are 18, 21 and 23 for the second, third and fourth spells,
-% respectively.
-
-% The results for women with one to seven years of education are presented
-% in Figures \ref{fig:results_spell2_med_urban} to \ref{fig:results_spell4_med_rural_cont}.
-% Again a representative woman is used with the first spell length set to
-% 16 months and the ages at the beginning of the spell 19, 21 and 24
-% for the second, third and fourth spells, respectively.
-
-% [FIRST SPELL]
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,529)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=3,831)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,762)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=16,293)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=21,631)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=7,922)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with no education by quarter (3 month
-period). 
-Predictions based on age 16 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell1_low}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,022)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=3,653)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,302)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=4,575)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=8,356)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=5,208)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-period). 
-Predictions based on age 17 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell1_med}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=4,408)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=10,118)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=9,116)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,668)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=7,585)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=7,504)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 8 or more years of education by quarter
-(3 month period). 
-Predictions based on age 20 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell1_high}
-\end{figure}
-
-\clearpage
-
-\subsection{Second Spell}
-
-% SPELL 2 - URBAN - LOW
-\begin{figure}[hp]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=861)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=1,763)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=946)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=951)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=1,929)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=921)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with no education by quarter (3 month period). 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell2_low_urban}
-\end{figure}
-
-% SPELL 2 - rural - LOW
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=5,103)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=9,913)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=3,653)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=5,500)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=10,437)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=3,834)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with no education by quarter (3 month period). 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell2_low_rural}
-\end{figure}
-
-% SPELL 2 - URBAN - MEDIUM
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=714)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=1,578)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=1,074)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=791)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=1,766)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=1,096)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 19 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell2_med_urban}
-\end{figure}
-
-% SPELL 2 - rural - MEDIUM
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=1,464)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=3,510)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=2,151)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=1,645)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=3,671)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=2,182)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 19 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell2_med_rural}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=1,576)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,105)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=3,762)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,667)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=4,431)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,953)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell2_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=847)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=2,788)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,816)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=925)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=3,033)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,039)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell2_high_rural}
-\end{figure}
-
-\clearpage
-\subsection{Third Spell}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=252)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=690)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=458)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=564)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,497)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=915)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell3_low_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=293)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=783)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=410)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \ContinuedFloat
+% \centering
+% \caption*{First three children two boys and one girl}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=173)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=515)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=367)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First three children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=56)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=166)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=92)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% % \label{fig:results_spell4_high_rural}
+% \end{figure}
+% 
+% 
+% \clearpage
+
+% 
+% \section{Graphs using Women Married less than 19 Years}
+% 
+% \setcounter{figure}{0}
+% \setcounter{table}{0}
+% 
+% 
+% % Figures \ref{fig:results_spell2_low_urban} to \ref{fig:results_spell4_low_rural_cont}
+% % show the results for the group of women with no education.
+% % The starting ages are 18, 21 and 23 for the second, third and fourth spells,
+% % respectively.
+% 
+% % The results for women with one to seven years of education are presented
+% % in Figures \ref{fig:results_spell2_med_urban} to \ref{fig:results_spell4_med_rural_cont}.
+% % Again a representative woman is used with the first spell length set to
+% % 16 months and the ages at the beginning of the spell 19, 21 and 24
+% % for the second, third and fourth spells, respectively.
+% 
+% 
+% % [FIRST SPELL]
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=2,529)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}} 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=3,831)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=1,762)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=16,293)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=21,631)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=7,922)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with no education by quarter (3 month
+% period). 
+% Predictions based on age 16 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell1_low}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=2,022)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}} 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=3,653)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=2,302)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=4,575)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=8,356)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=5,208)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
+% period). 
+% Predictions based on age 17 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell1_med}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=4,408)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}} 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=10,118)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=9,116)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=2,668)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_s}} 
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=7,585)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=7,504)]{
+% \begin{minipage}{0.31\textwidth}
+% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_s}}
+% \captionsetup[subfigure]{labelformat=parens}
+% \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with 8 or more years of education by quarter
+% (3 month period). 
+% Predictions based on age 20 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell1_high}
+% \end{figure}
+% 
+% \clearpage
+% 
+% \subsection{Second Spell}
+% 
+% 
+% % SPELL 2 - URBAN - LOW
+% \begin{figure}[hp]
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972-1984 (N=861)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985-1994 (N=1,763)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[1995-2006 (N=946)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972-1984 (N=951)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985-1994 (N=1,929)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995-2006 (N=921)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with no education by quarter (3 month period). 
+% Predictions based on age 18 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell2_low_urban}
+% \end{figure}
+% 
+% 
+% % SPELL 2 - rural - LOW
+% \begin{figure}
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972-1984 (N=5,103)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985-1994 (N=9,913)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[1995-2006 (N=3,653)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972-1984 (N=5,500)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985-1994 (N=10,437)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995-2006 (N=3,834)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for rural 
+% women with no education by quarter (3 month period). 
+% Predictions based on age 18 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell2_low_rural}
+% \end{figure}
+% 
+% 
+% % SPELL 2 - URBAN - MEDIUM
+% \begin{figure}
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972-1984 (N=714)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985-1994 (N=1,578)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[1995-2006 (N=1,074)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972-1984 (N=791)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985-1994 (N=1,766)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995-2006 (N=1,096)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 19 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell2_med_urban}
+% \end{figure}
+% 
+% 
+% % SPELL 2 - rural - MEDIUM
+% \begin{figure}
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972-1984 (N=1,464)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985-1994 (N=3,510)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[1995-2006 (N=2,151)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972-1984 (N=1,645)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985-1994 (N=3,671)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995-2006 (N=2,182)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for rural 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 19 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell2_med_rural}
+% \end{figure}
+% 
+% % High education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=1,576)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=4,105)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=3,762)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=1,667)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=4,431)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=3,953)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 22 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell2_high_urban}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First child a girl}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=847)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=2,788)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=2,816)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First child a boy}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=925)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=3,033)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=3,039)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 22 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_limit_spell2_high_rural}
+% \end{figure}
+% 
+% \clearpage
+% \subsection{Third Spell}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First two children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=252)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=690)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=458)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First two children one boy and one girl}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=564)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=1,497)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=915)]{
+%     \begin{minipage}{0.26\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_limit_spell3_low_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=1,417)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,060)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,827)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,803)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=8,265)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,661)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell3_low_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=1,613)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=4,200)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=1,786)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \ContinuedFloat
+% \caption*{First two children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=293)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=783)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=410)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% % \label{fig:results_limit_spell3_low_urban}
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First two children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=1,417)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=4,060)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=1,827)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First two children one boy and one girl}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=2,803)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=8,265)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=3,661)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_limit_spell3_low_rural}
-\end{figure}
-
-% Medium education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=223)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=577)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=409)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=433)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,188)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=804)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell3_med_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=229)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=594)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=423)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \ContinuedFloat
+% \centering
+% \caption*{First two children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=1,613)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=4,200)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=1,786)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% % \label{fig:results_limit_spell3_low_rural}
+% \end{figure}
+% 
+% 
+% 
+% % Medium education
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First two children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=223)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=577)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=409)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First two children one boy and one girl}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=433)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=1,188)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=804)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_limit_spell3_med_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=395)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,264)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=840)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=829)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=2,549)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=1,737)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell3_med_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=419)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,216)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=716)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \ContinuedFloat
+% \caption*{First two children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=229)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=594)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=423)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% % \label{fig:results_limit_spell3_med_urban}
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First two children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=395)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=1,264)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=840)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First two children one boy and one girl}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=829)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=2,549)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=1,737)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_limit_spell3_med_rural}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=390)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,196)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=981)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=778)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=2,543)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=2,309)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell3_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=442)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,230)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=1,068)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \ContinuedFloat
+% \centering
+% \caption*{First two children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=419)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=1,216)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=716)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% % \label{fig:results_limit_spell3_med_rural}
+% \end{figure}
+% 
+% 
+% % High education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First two children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=390)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=1,196)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=981)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First two children one boy and one girl}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=778)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=2,543)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=2,309)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_limit_spell3_high_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=200)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=798)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=857)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=412)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,646)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=1,805)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_limit_spell3_high_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=209)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=767)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=782)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \ContinuedFloat
+% \caption*{First two children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=442)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=1,230)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=1,068)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% % \label{fig:results_limit_spell3_high_urban}
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{First two children girls}
+% \setcounter{subfigure}{-2}
+% \subfloat[1972--1984 (N=200)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[1985--1994 (N=798)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{0}
+% \subfloat[1995--2006 (N=857)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{First two children one boy and one girl}
+% \setcounter{subfigure}{1}
+% \subfloat[1972--1984 (N=412)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{2}
+% \subfloat[1985--1994 (N=1,646)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{3}
+% \subfloat[1995--2006 (N=1,805)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
 % \label{fig:results_limit_spell3_high_rural}
-\end{figure}
-
-\clearpage
-
-\section{Graphs using Women Dropped Because of Recall Error}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% [FIRST SPELL]
-
-\begin{figure}[htpb]
-\centering
-\caption*{1950--1980}
-\setcounter{subfigure}{-2}
-\subfloat[Urban (N=3,775)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[Rural (N=19,635)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with no education by quarter (3 month
-period). 
-Predictions based on age 16 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell1_low}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1954--1980 }
-\setcounter{subfigure}{-2}
-\subfloat[Urban (N=2,864)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[Rural (N=4,885)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-period). 
-Predictions based on age 17 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell1_med}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1955--1980}
-\setcounter{subfigure}{-2}
-\subfloat[Urban (N=3,157)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[Rural (N=1,491)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 8 or more years of education by quarter
-(3 month period). 
-Predictions based on age 20 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell1_high}
-\end{figure}
-
-\clearpage
-
-\subsection{Second Spell}
-
-% SPELL 2 - URBAN - LOW
-\begin{figure}[hb]
-\centering
-\caption*{1954--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[First child a girl (N=1,760)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[First child a boy (N=2,050)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with no education by quarter (3 month period). 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell2_low_urban}
-\end{figure}
-
-% SPELL 2 - rural - LOW
-\begin{figure}
-\centering
-\caption*{1954--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[First child a girl (N=8,594)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[First child a boy (N=10,123)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with no education by quarter (3 month period). 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell2_low_rural}
-\end{figure}
-
-% SPELL 2 - URBAN - MEDIUM
-\begin{figure}
-\centering
-\caption*{1955--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[First child a girl (N=1,362)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[First child a boy (N=1,472)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 19 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell2_med_urban}
-\end{figure}
-
-% SPELL 2 - rural - MEDIUM
-\begin{figure}
-\centering
-\caption*{1955--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[First child a girl (N=2,254)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[First child a boy (N=2,368)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 19 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell2_med_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1957--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[First child a girl (N=1,498)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[First child a boy (N=1,607)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell2_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1957--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[First child a girl (N=655)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[First child a boy (N=743)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell2_high_rural}
-\end{figure}
-
-\clearpage
-
-\subsection{Third Spell}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1957--1984}
-\setcounter{subfigure}{-2}
-\subfloat[Two girls (N=763)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[One boy and one girl (N=1,743)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Two boys (N=982)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell3_low_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1957--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[Two girls (N=3,796)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[One boy and one girl (N=8,390)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1972--1984 (N=4,903)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell3_low_rural}
-\end{figure}
-
-% Medium education
-
-\begin{figure}[htpb]
-\centering
-\caption*{1958--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[Two girls (N=633)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[One boy and one girl (N=1,236)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Two boys (N=716)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell3_med_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1958--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[Two girls (N=995)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[One boy and one girl (N=2,037)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Two boys (N=1,093)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by quarter (3 month period). 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell3_med_rural}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{1960--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[Two girls (N=660)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[One boy and one girl (N=1,375)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Two boys (N=673)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell3_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{1960--1984 }
-\setcounter{subfigure}{-2}
-\subfloat[Two girls (N=267)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[One boy and one girl (N=573)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Two boys (N=341)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by quarter (3 month period). 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_dropped_spell3_high_rural}
-\end{figure}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \ContinuedFloat
+% \centering
+% \caption*{First two children boys}
+% \setcounter{subfigure}{4}
+% \subfloat[1972--1984 (N=209)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{5}
+% \subfloat[1985--1994 (N=767)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[1995--2006 (N=782)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_s}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{(Continued) Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% % \label{fig:results_limit_spell3_high_rural}
+% \end{figure}
+% 
+% 
+% 
+% \clearpage
+% 
+% 
+% \section{Graphs using Women Dropped Because of Recall Error}
+% 
+% \setcounter{figure}{0}
+% \setcounter{table}{0}
+% 
+% 
+% % [FIRST SPELL]
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1950--1980}
+% \setcounter{subfigure}{-2}
+% \subfloat[Urban (N=3,775)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[Rural (N=19,635)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with no education by quarter (3 month
+% period). 
+% Predictions based on age 16 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell1_low}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1954--1980 }
+% \setcounter{subfigure}{-2}
+% \subfloat[Urban (N=2,864)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[Rural (N=4,885)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
+% period). 
+% Predictions based on age 17 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell1_med}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1955--1980}
+% \setcounter{subfigure}{-2}
+% \subfloat[Urban (N=3,157)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[Rural (N=1,491)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from time of marriage for women with 8 or more years of education by quarter
+% (3 month period). 
+% Predictions based on age 20 at marriage.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell1_high}
+% \end{figure}
+% 
+% \clearpage
+% 
+% \subsection{Second Spell}
+% 
+% 
+% % SPELL 2 - URBAN - LOW
+% \begin{figure}[hb]
+% \centering
+% \caption*{1954--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[First child a girl (N=1,760)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[First child a boy (N=2,050)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with no education by quarter (3 month period). 
+% Predictions based on age 18 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell2_low_urban}
+% \end{figure}
+% 
+% 
+% % SPELL 2 - rural - LOW
+% \begin{figure}
+% \centering
+% \caption*{1954--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[First child a girl (N=8,594)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[First child a boy (N=10,123)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for rural 
+% women with no education by quarter (3 month period). 
+% Predictions based on age 18 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell2_low_rural}
+% \end{figure}
+% 
+% 
+% % SPELL 2 - URBAN - MEDIUM
+% \begin{figure}
+% \centering
+% \caption*{1955--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[First child a girl (N=1,362)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[First child a boy (N=1,472)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 19 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell2_med_urban}
+% \end{figure}
+% 
+% 
+% % SPELL 2 - rural - MEDIUM
+% \begin{figure}
+% \centering
+% \caption*{1955--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[First child a girl (N=2,254)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[First child a boy (N=2,368)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for rural 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 19 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell2_med_rural}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1957--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[First child a girl (N=1,498)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[First child a boy (N=1,607)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 22 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell2_high_urban}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1957--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[First child a girl (N=655)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[First child a boy (N=743)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after first birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 22 at first birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell2_high_rural}
+% \end{figure}
+% 
+% \clearpage
+% 
+% 
+% \subsection{Third Spell}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1957--1984}
+% \setcounter{subfigure}{-2}
+% \subfloat[Two girls (N=763)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[One boy and one girl (N=1,743)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[Two boys (N=982)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell3_low_urban}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1957--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[Two girls (N=3,796)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[One boy and one girl (N=8,390)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[1972--1984 (N=4,903)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with no of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell3_low_rural}
+% \end{figure}
+% 
+% 
+% % Medium education
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1958--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[Two girls (N=633)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[One boy and one girl (N=1,236)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[Two boys (N=716)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell3_med_urban}
+% \end{figure}
+% 
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1958--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[Two girls (N=995)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[One boy and one girl (N=2,037)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[Two boys (N=1,093)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 1 to 7 years of education by quarter (3 month period). 
+% Predictions based on age 21 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell3_med_rural}
+% \end{figure}
+% 
+% 
+% % High education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1960--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[Two girls (N=660)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[One boy and one girl (N=1,375)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[Two boys (N=673)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for urban 
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell3_high_urban}
+% \end{figure}
+% 
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{1960--1984 }
+% \setcounter{subfigure}{-2}
+% \subfloat[Two girls (N=267)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-1}
+% \subfloat[One boy and one girl (N=573)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[Two boys (N=341)]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_s}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{Predicted probability of having a boy and probability of
+% no birth yet from nine months after second birth for rural
+% women with 8 or more years of education by quarter (3 month period). 
+% Predictions based on age 24 at second birth.
+% Left column shows results prior to sex selection available, middle column before
+% sex selection illegal and right column after sex selection illegal.
+% N indicates the number of women in the relevant group in the underlying samples.
+% }
+% \label{fig:results_dropped_spell3_high_rural}
+% \end{figure}
 

### 2017-10-14 paper/sexSelectionSpacing-ver1.tex
Minor edits
Reverse pps and area in graph names and move graph generation to separate file

@@
 \usepackage{setspace}
-\usepackage{xyling}
+% \usepackage{xyling}
 \usepackage[justification=centering]{caption}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_urban}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_pps_rural}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_urban}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_pps_rural}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_pps_urban}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_pps_rural}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_pps_urban}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_pps_urban}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_pps_rural}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_pps_rural}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}

### 2017-10-14 paper/sexSelectionSpacing-ver1.tex
Rename all graphs and update Makefile with dependencies/targets
Instead of a numbering system, which was hard to read, all graphs
are now named with urban/rural and the sex composition of prior
children, if any.

All references in paper and appendix changed to fit the new
naming system.

The Makefile was update as well and now include the relevant
targets and dependencies with the new naming system. In principle,
it should be possible to shorten the generation of the dependencies
and targets, but that would require an if statement and the if
function in Make runs of whether a given piece of te

@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r2_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_r1_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r6_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r6_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r6_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r4_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r2_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r5_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r5_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r5_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r3_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_r1_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}

### 2017-10-14 paper/sexSelectionSpacingAppendix-ver1.tex
Rename all graphs and update Makefile with dependencies/targets
Instead of a numbering system, which was hard to read, all graphs
are now named with urban/rural and the sex composition of prior
children, if any.

All references in paper and appendix changed to fit the new
naming system.

The Makefile was update as well and now include the relevant
targets and dependencies with the new naming system. In principle,
it should be possible to shorten the generation of the dependencies
and targets, but that would require an if statement and the if
function in Make runs of whether a given piece of te

@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_pc}}\\
-% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r4_s}} 
+% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
+% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r4_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r4_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r2_s}} 
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r2_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r2_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_pc}}\\
-% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r3_s}} 
+% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_pc}}\\
+% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r3_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r3_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_r1_s}} 
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_r1_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_r1_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_pc}}\\
-% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r6_s}} 
+% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_pc}}\\
+% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r6_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r6_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r4_s}} 
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r4_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r4_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r2_s}} 
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r2_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r2_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_pc}}\\
-% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r5_s}} 
+% % \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_pc}}\\
+% % \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r5_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r5_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r3_s}} 
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r3_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r3_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_r1_s}} 
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_s}} 
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_r1_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 % % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_pc}}\\
-% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_r1_s}}
+% % \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_pc}}\\
+% % \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_s}}
 % % \captionsetup[subfigure]{labelformat=parens}
@@
 
-% \begin{figure}[htpb!]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=4,518)]{
-% \begin{minipage}{0.28\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r2_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}} 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=4,309)]{
-% \begin{minipage}{0.28\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r2_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=1,762)]{
-% \begin{minipage}{0.28\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r2_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=25,486)]{
-% \begin{minipage}{0.28\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_r1_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=23,360)]{
-% \begin{minipage}{0.28\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_r1_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=7,922)]{
-% \begin{minipage}{0.28\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_r1_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with no education by quarter (3 month
-% period). 
-% Predictions based on age 16 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_spell1_low}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=3,666)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r2_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}} 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=4,104)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r2_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=2,302)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r2_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=7,496)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_r1_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=9,000)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_r1_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=5,208)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_r1_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-% period). 
-% Predictions based on age 17 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_spell1_med}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=7,338)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r2_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}} 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=11,045)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r2_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=9,116)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r2_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=3,933)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_r1_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=8,027)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_r1_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=7,504)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_r1_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with 8 or more years of education by quarter
-% (3 month period). 
-% Predictions based on age 20 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_spell1_high}
-% \end{figure}
-% 
-% \clearpage
-% \newpage
+\begin{figure}[htpb!]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=4,518)]{
+\begin{minipage}{0.28\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_pc}}\\
+\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_s}} 
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=4,309)]{
+\begin{minipage}{0.28\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=1,762)]{
+\begin{minipage}{0.28\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=25,486)]{
+\begin{minipage}{0.28\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_s}} 
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=23,360)]{
+\begin{minipage}{0.28\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=7,922)]{
+\begin{minipage}{0.28\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from time of marriage for women with no education by quarter (3 month
+period). 
+Predictions based on age 16 at marriage.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell1_low}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=3,666)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_pc}}\\
+\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_s}} 
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=4,104)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=2,302)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=7,496)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_s}} 
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=9,000)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=5,208)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
+period). 
+Predictions based on age 17 at marriage.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell1_med}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=7,338)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_pc}}\\
+\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_s}} 
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=11,045)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=9,116)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=3,933)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_s}} 
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=8,027)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=7,504)]{
+\begin{minipage}{0.31\textwidth}
+\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_pc}}\\
+\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_s}}
+\captionsetup[subfigure]{labelformat=parens}
+\end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from time of marriage for women with 8 or more years of education by quarter
+(3 month period). 
+Predictions based on age 20 at marriage.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell1_high}
+\end{figure}
+
+\clearpage
+\newpage
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r4_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r2_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_b_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r3_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_g_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_r1_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_b_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_b_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r6_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r6_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_gg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_gg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r6_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r6_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r4_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r4_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r4_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r2_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r2_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r2_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r5_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r5_s}} 
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_gg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_gg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r5_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r5_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_gg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_gg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r3_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bg_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r3_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r3_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bg_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_r1_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_r1_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_r1_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r2_s}} 
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_urban_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_urban_s}} 
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r2_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_urban_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_urban_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r2_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_urban_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_urban_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_r1_s}} 
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_rural_s}} 
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_r1_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_rural_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_r1_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_rural_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r2_s}} 
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_urban_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_urban_s}} 
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r2_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_urban_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_urban_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r2_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_urban_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_urban_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_r1_s}} 
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_rural_s}} 
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_r1_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_rural_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_r1_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_rural_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r2_s}} 
+% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_urban_pc}}\\
+% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_urban_s}} 
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r2_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_urban_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_urban_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r2_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_urban_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_urban_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_r1_s}} 
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_rural_s}} 
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_r1_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_rural_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 % \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_r1_s}}
+% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_rural_pc}}\\
+% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_rural_s}}
 % \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_g_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_g_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_g_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_g_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_g_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_g_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_g_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_g_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_b_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r6_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r6_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r6_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r4_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r5_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r5_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r5_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r3_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r6_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r6_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r6_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r4_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r5_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r5_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r5_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r3_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r6_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r6_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r6_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r4_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r4_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r2_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r5_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r5_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r5_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_gg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_gg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r3_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r3_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bg_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_r1_s}}
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bb_s}}
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r2_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_urban_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_urban_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_rural_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_rural_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r2_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_urban_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_urban_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_rural_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_rural_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r2_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_urban_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_urban_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_rural_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_rural_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r4_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r3_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_g_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_g_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_b_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_b_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r6_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r4_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r5_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r3_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r6_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r4_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r5_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r3_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r6_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r4_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r2_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r5_s}} 
+%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_gg_pc}}\\
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_gg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r3_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bg_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bg_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_r1_s}} 
+%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bb_pc}}\\
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bb_s}} 
 %         \captionsetup[subfigure]{labelformat=parens}

### 2017-10-14 paper/sexSelectionSpacingAppendix-ver1.tex
Create parity progression graphs for spell 1 for Appendix

@@
 
+\begin{figure}[htpb]
+\centering
+\caption*{No Education}
+\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
+\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
+\caption*{1-7 Years of Education}
+\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
+\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
+\caption*{8 or more Years of Education}
+\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
+\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
+\caption{[Parity progression conditional survival]}
+\label{fig:results_spell1_pps}
+\end{figure}
+
 \clearpage

### 2017-10-15 paper/sexSelectionSpacingAppendix-ver1.tex
Minor edits
Add spell 2 & 3 parity progression graphs and fix Makefile

@@
 
+\subsection{First Spell}
+
 \begin{figure}[htpb!]
@@
 
+% PARITY PROGRESSION SURVIVAL CURVES - Low
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
 % SPELL 2 - URBAN - MEDIUM
@@
 
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1-7 years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_med_pps}
+\end{figure}
+
 % High education
@@
 \label{fig:results_spell2_high_rural}
+\end{figure}
+
+% PARITY PROGRESSION SURVIVAL - High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_pps}
 \end{figure}
@@
 
+% PARITY PROGRESSION SURVIVAL - LOW
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_low_pps}
+\end{figure}
+
 % Medium education
@@
 
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1 to 7 years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_med_pps}
+\end{figure}
+
 % High education
@@
 
+% PARITY PROGRESSION SURVIVAL - high
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell3_high_pps}
+\end{figure}
+
 \clearpage

### 2017-10-17 paper/sexSelectionSpacing-ver1.tex
Fix figure reference

@@
 after the birth of a girl than after a boy, consistent with the male-biased
-sex ratio in Panel (c) in Figure \ref{fig:fig:results_spell2_high_urban}.
+sex ratio in Panel (c) in Figure \ref{fig:results_spell2_high_urban}.
 

### 2017-10-17 paper/sexSelectionSpacingAppendix-ver1.tex
Include spell 4 sex ration and survival graphs in Appendix

@@
 
-% \subsection{Fourth Spell}
-% 
-% % low education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First three children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=130)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=446)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=200)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children one boy and two girls}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=410)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=1,185)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=601)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with no of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
+\subsection{Fourth Spell}
+
+% low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{First three children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=130)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_ggg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_ggg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=446)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=200)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children one boy and two girls}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=410)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bgg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=1,185)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=601)]{
+    \begin{minipage}{0.26\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_low_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\ContinuedFloat
+\caption*{First three children two boys and one girl}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=389)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=1,145)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=486)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children three boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=141)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=382)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=155)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 % \label{fig:results_spell4_low_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \ContinuedFloat
-% \caption*{First three children two boys and one girl}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=389)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=1,145)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=486)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children three boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=141)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=382)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=155)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% % \label{fig:results_spell4_low_urban}
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with no of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First three children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=752)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=1,954)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=888)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children one boy and two girls}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=2,065)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=5,990)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=2,456)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with no of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{First three children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=752)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_ggg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_ggg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=1,954)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=888)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children one boy and two girls}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=2,065)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bgg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=5,990)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=2,456)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_low_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\ContinuedFloat
+\centering
+\caption*{First three children two boys and one girl}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=2,168)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=5,439)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=2,155)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=777)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbb_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=1,895)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbb_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=696)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbb_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with no of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
 % \label{fig:results_spell4_low_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \ContinuedFloat
-% \centering
-% \caption*{First three children two boys and one girl}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=2,168)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=5,439)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=2,155)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=777)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=1,895)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=696)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with no of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% % \label{fig:results_spell4_low_rural}
-% \end{figure}
-% 
-% 
-% 
-% % Medium education
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First three children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=110)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=282)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=144)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children one boy and two girls}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=299)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=765)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=372)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 1 to 7 years of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
+\end{figure}
+
+% Medium education
+
+\begin{figure}[htpb]
+\centering
+\caption*{First three children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=110)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_ggg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_ggg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=282)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=144)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children one boy and two girls}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=299)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bgg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=765)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=372)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with 1 to 7 years of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_med_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\ContinuedFloat
+\caption*{First three children two boys and one girl}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=274)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=600)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=275)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children three boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=77)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=230)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=90)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 % \label{fig:results_spell4_med_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \ContinuedFloat
-% \caption*{First three children two boys and one girl}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=274)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=600)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=275)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children three boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=77)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=230)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=90)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% % \label{fig:results_spell4_med_urban}
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 1 to 7 years of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First three children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=210)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=601)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=317)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children one boy and two girls}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=581)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=1,532)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=800)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 1 to 7 years of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with 1 to 7 years of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{First three children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=210)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_ggg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_ggg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=601)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=317)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children one boy and two girls}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=581)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bgg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=1,532)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=800)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with 1 to 7 years of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_med_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\ContinuedFloat
+\centering
+\caption*{First three children two boys and one girl}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=492)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=1,197)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=578)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children three boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=158)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbb_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=357)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbb_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=192)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbb_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with 1 to 7 years of education by quarter (3 month period). 
+Predictions based on age 21 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
 % \label{fig:results_spell4_med_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \ContinuedFloat
-% \centering
-% \caption*{First three children two boys and one girl}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=492)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=1,197)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=578)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children three boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=158)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=357)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=192)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 1 to 7 years of education by quarter (3 month period). 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% % \label{fig:results_spell4_med_rural}
-% \end{figure}
-% 
-% 
-% 
-% 
-% 
-% % High education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First three children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=131)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=355)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=191)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children one boy and two girls}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=353)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=1,062)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=590)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 8 or more years of education by quarter (3 month period). 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
+\end{figure}
+
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{First three children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=131)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_ggg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_ggg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=355)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=191)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children one boy and two girls}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=353)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bgg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=1,062)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=590)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_high_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\ContinuedFloat
+\caption*{First three children two boys and one girl}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=309)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=681)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=344)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children three boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=87)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=233)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=110)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 % \label{fig:results_spell4_high_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \ContinuedFloat
-% \caption*{First three children two boys and one girl}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=309)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=681)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=344)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r4_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children three boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=87)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r2_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=233)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=110)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r2_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% % \label{fig:results_spell4_high_urban}
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 8 or more years of education by quarter (3 month period). 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First three children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=62)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r7_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=257)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r7_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=201)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r7_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children one boy and two girls}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=176)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r5_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=664)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r5_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=564)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r5_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 8 or more years of education by quarter (3 month period). 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for urban 
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{First three children girls}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=62)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_ggg_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_ggg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=257)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=201)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_ggg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_ggg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children one boy and two girls}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=176)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bgg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=664)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=564)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bgg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bgg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_high_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\ContinuedFloat
+\centering
+\caption*{First three children two boys and one girl}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=173)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbg_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=515)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=367)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbg_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbg_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First three children boys}
+\setcounter{subfigure}{4}
+\subfloat[1972--1984 (N=56)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbb_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{5}
+\subfloat[1985--1994 (N=166)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbb_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006 (N=92)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbb_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{(Continued) Predicted probability of having a boy and probability of
+no birth yet from nine months after second birth for rural
+women with 8 or more years of education by quarter (3 month period). 
+Predictions based on age 24 at second birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
 % \label{fig:results_spell4_high_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \ContinuedFloat
-% \centering
-% \caption*{First three children two boys and one girl}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=173)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r3_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=515)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=367)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r3_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First three children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=56)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r1_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=166)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=92)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r1_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 8 or more years of education by quarter (3 month period). 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% % \label{fig:results_spell4_high_rural}
-% \end{figure}
-% 
-% 
-% \clearpage
+\end{figure}
+
+\clearpage
 

### 2017-10-17 paper/sexSelectionSpacingAppendix-ver1.tex
Fix spell 4 parity progression survival graph generation and include in Appendix

@@
 
+% PARITY PROGRESSION SURVIVAL - LOW
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_low_pps}
+\end{figure}
+
 % Medium education
@@
 
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1 to 7 years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_med_pps}
+\end{figure}
+
 % High education
@@
 
+% PARITY PROGRESSION SURVIVAL - high
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{2}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{3}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{4}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by quarter (3 month period).
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell4_high_pps}
+\end{figure}
+
 \clearpage

### 2017-10-19 paper/sexSelectionSpacingAppendix-ver1.tex
Add stand-alone bib file
Fix spell 4 file names for all boys

@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_s}} 
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbb_s}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_s}}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbb_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbb_s}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \bibliographystyle{aer}
-% \bibliography{econ}
-% \bibliography{library}
-\bibliography{collection}
+\bibliography{sex_selection_spacing}
 

### 2017-10-20 paper/sexSelectionSpacing-ver1.tex
Add stand-alone bib file
Update median duration tables with loop over education

@@
 
+% Median duration and sex ratio tables
+\input{../tables/median_sex_ratio_low.tex}
+
+\input{../tables/median_sex_ratio_med.tex}
+
+\input{../tables/median_sex_ratio_high.tex}
+
+\subsection{[Specific spell/education/area combinations of special interest]}
 [Only a subset of the planned analyses to demonstrate the method and interpretation]
@@
 \bibliographystyle{aer}
-\bibliography{collection}
+\bibliography{sex_selection_spacing}
 

### 2017-10-22 paper/sexSelectionSpacing-ver1.tex
Change from quarters to months

@@
 no birth yet from nine months after first birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
+women with 8 or more years of education by month beginning 9 months after prior birth. 
 Predictions based on age 22 at first birth.
@@
 \caption{Survival curves conditional on parity progression
-for women with no education by quarter (3 month period).
+for women with no education by month beginning 9 months after prior birth.
 Left column shows results prior to sex selection available, middle column before
@@
 \caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by quarter (3 month period).
+for women with 8 or more years of education by month beginning 9 months after prior birth.
 Left column shows results prior to sex selection available, middle column before
@@
 no birth yet from nine months after first birth for urban 
-women with no education by quarter (3 month period). 
+women with no education by month beginning 9 months after prior birth. 
 Predictions based on age 18 at first birth.
@@
 no birth yet from nine months after first birth for rural 
-women with no education by quarter (3 month period). 
+women with no education by month beginning 9 months after prior birth. 
 Predictions based on age 18 at first birth.
@@
 % no birth yet from nine months after first birth for urban 
-% women with 8 or more years of education by quarter (3 month period). 
+% women with 8 or more years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 22 at first birth.
@@
 no birth yet from nine months after first birth for rural
-women with 8 or more years of education by quarter (3 month period). 
+women with 8 or more years of education by month beginning 9 months after prior birth. 
 Predictions based on age 22 at first birth.
@@
 no birth yet from nine months after second birth for urban 
-women with no of education by quarter (3 month period). 
+women with no of education by month beginning 9 months after prior birth. 
 Predictions based on age 21 at second birth.
@@
 no birth yet from nine months after second birth for rural
-women with no of education by quarter (3 month period). 
+women with no of education by month beginning 9 months after prior birth. 
 Predictions based on age 21 at second birth.
@@
 no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by quarter (3 month period). 
+women with 8 or more years of education by month beginning 9 months after prior birth. 
 Predictions based on age 24 at second birth.
@@
 no birth yet from nine months after second birth for rural
-women with 8 or more years of education by quarter (3 month period). 
+women with 8 or more years of education by month beginning 9 months after prior birth. 
 Predictions based on age 24 at second birth.

### 2017-10-22 paper/sexSelectionSpacingAppendix-ver1.tex
Change from quarters to months

@@
 \caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with no education by quarter (3 month
-period). 
+no birth yet from time of marriage for women with no education by month beginning at marriage. 
 Predictions based on age 16 at marriage.
@@
 \caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-period). 
+no birth yet from time of marriage for women with 1 to 7 years of education by month beginning at marriage. 
 Predictions based on age 17 at marriage.
@@
 \caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 8 or more years of education by quarter
-(3 month period). 
+no birth yet from time of marriage for women with 8 or more years of education by month beginning at marriage. 
 Predictions based on age 20 at marriage.
@@
 no birth yet from nine months after first birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
+women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 Predictions based on age 19 at first birth.
@@
 no birth yet from nine months after first birth for rural 
-women with 1 to 7 years of education by quarter (3 month period). 
+women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 Predictions based on age 19 at first birth.
@@
 \caption{Survival curves conditional on parity progression
-for women with 1-7 years of education by quarter (3 month period).
+for women with 1-7 years of education by month beginning 9 months after prior birth.
 Left column shows results prior to sex selection available, middle column before
@@
 no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by quarter (3 month period). 
+women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 Predictions based on age 21 at second birth.
@@
 no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by quarter (3 month period). 
+women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 Predictions based on age 21 at second birth.
@@
 \caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by quarter (3 month period).
+for women with 1 to 7 years of education by month beginning 9 months after prior birth.
 Left column shows results prior to sex selection available, middle column before
@@
 % no birth yet from nine months after first birth for urban 
-% women with no education by quarter (3 month period). 
+% women with no education by month beginning 9 months after prior birth. 
 % Predictions based on age 18 at first birth.
@@
 % no birth yet from nine months after first birth for rural 
-% women with no education by quarter (3 month period). 
+% women with no education by month beginning 9 months after prior birth. 
 % Predictions based on age 18 at first birth.
@@
 % no birth yet from nine months after first birth for urban 
-% women with 1 to 7 years of education by quarter (3 month period). 
+% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 19 at first birth.
@@
 % no birth yet from nine months after first birth for rural 
-% women with 1 to 7 years of education by quarter (3 month period). 
+% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 19 at first birth.
@@
 % no birth yet from nine months after first birth for rural
-% women with 8 or more years of education by quarter (3 month period). 
+% women with 8 or more years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 22 at first birth.
@@
 % no birth yet from nine months after second birth for urban 
-% women with no of education by quarter (3 month period). 
+% women with no of education by month beginning 9 months after prior birth. 
 % Predictions based on age 21 at second birth.
@@
 % no birth yet from nine months after second birth for rural
-% women with no of education by quarter (3 month period). 
+% women with no of education by month beginning 9 months after prior birth. 
 % Predictions based on age 21 at second birth.
@@
 % no birth yet from nine months after second birth for urban 
-% women with 1 to 7 years of education by quarter (3 month period). 
+% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 21 at second birth.
@@
 % no birth yet from nine months after second birth for rural
-% women with 1 to 7 years of education by quarter (3 month period). 
+% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 21 at second birth.
@@
 % no birth yet from nine months after second birth for urban 
-% women with 8 or more years of education by quarter (3 month period). 
+% women with 8 or more years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 24 at second birth.
@@
 % no birth yet from nine months after second birth for rural
-% women with 8 or more years of education by quarter (3 month period). 
+% women with 8 or more years of education by month beginning 9 months after prior birth. 
 % Predictions based on age 24 at second birth.

### 2017-10-24 paper/sexSelectionSpacing-ver1.tex
Introduce median duration and sex ration tables in text

@@
 For every abortion a woman has we should expect the duration from last
-birth to increase by approximately a year.%
-\footnote{
+birth to increase by approximately a year.
 This increase consists of three parts starting from the time of the 
@@
 of gestation onwards.
-These three parts add up to 12 months.
+These three parts add up to 12 months.%
+\footnote{
 The waiting time to conception does vary by woman, but even if it is very 
@@
 
-The main downside of my approach is that direct interpretation of the estimated 
+The main downside of this approach is that direct interpretation of the estimated 
 coefficients for this model is challenging because of the competing risk setup.
@@
 
-Spell duration is measured in quarters of a year, that is 3 month periods, hereafter
-referred to as quarters.
-The first spell begins at the month of marriage rather than 9 months after because many 
+Spell duration is measured in months.
+The first spell begins at the month of marriage because many 
 women report giving birth less than 9 months after they were married.
-For women who began living with their husbands at too young an age to conceive the 
+For women who began living with their husbands at too young an age to conceive, the 
 starting point should ideally be first ovulation, when she becomes ``at risk'' for a 
@@
 or the number of births observed becomes too sparse for the method to work.
-The timing of censoring because of too few births vary slightly by spell but is generally 
-21 quarters after the beginning of the spell.
+The timing of censoring because of too few births vary slightly by spell but 
+is generally 5 years or longer after the beginning of the spell.
 
@@
 Because of concerns about selective migration I use where the household was living
-at the end of each spell.%
-\footnote{
-As online Appendix Table D.1 shows there is little difference across
-education levels in migration patterns within each period and patterns across periods
-are also relatively stable.
-}
+at the end of each spell.
+% %
+% \footnote{
+% As online Appendix Table D.1 shows there is little difference across
+% education levels in migration patterns within each period and patterns across periods
+% are also relatively stable.
+% }
 
@@
 
-The increase in urbanization and education is likely to exert downward pressure
-on fertility and the high censoring rates for the later periods are evidence of this.
-The average number of children born to women by the time they turn 35 illustrate how
-strong the decline in fertility has been.%
-\footnote{
-Figure \ref{fig:fertility} shows the full results.
-}
-Women born in the early 1940s had on average close to 5 children when 
-they reached 35, but women born in the early 1970s had only just over three children.
-The low number of children is especially remarkable because it combines
-all education levels and all areas of residence.
-% Hence, fertility in cities is likely substantially lower.
+% The increase in urbanization and education is likely to exert downward pressure
+% on fertility and the high censoring rates for the later periods are evidence of this.
+% The average number of children born to women by the time they turn 35 illustrate how
+% strong the decline in fertility has been.%
+% \footnote{
+% Figure \ref{fig:fertility} shows the full results.
+% }
+% Women born in the early 1940s had on average close to 5 children when 
+% they reached 35, but women born in the early 1970s had only just over three children.
+% The low number of children is especially remarkable because it combines
+% all education levels and all areas of residence.
+% % Hence, fertility in cities is likely substantially lower.
 
 \section{Results\label{sec:results}}
+
+The main question of interest here is how the duration between one
+birth and the next is related to son preference.
+The hypothese examined here is that in the absence of sex selection son 
+preference leads to shorter spacing after the birth of a girl than after the 
+birth of a boy, whereas son preference increases the spacing after the birth 
+of a girl relative to after the birth of a boy when prenatal sex selection is 
+used.
+We would still expect parents to \emph{begin} trying to conceive earlier
+after the birth of a girl than after a boy, but the abortions will automatically
+increase the length of the space, and may even lead to longer spacing after the
+birth of girls than after boys.
+
+To provide a first look at how the hypothese holds up, Tables 
+\ref{tab:median_sex_ratio_low},
+\ref{tab:median_sex_ratio_med}, and
+\ref{tab:median_sex_ratio_high}
+show predicted median duration and sex ratios for the three different
+education levels by spell, sex composition, and periods.
+These predictions are based on the estimation results employing the method 
+detailed in Section \ref{sec:strategy} and are calculated using the means of 
+the continuous explanatory variables and the majority category for categorical 
+explanatory variables.
+The median duration is the number of months it is predicted to take for
+half of the women who are predicted to have a birth by the end of spell length
+covered.
+For example, if 80\% of women with a given set of characteristics are predicted to
+have a birth by the end of the end of spell, the median duration is the number of
+months it would take for 40\% of women to have a birth.
+The sex ratio is the percent of births that result in a son, based on all the 
+births predicted to happen over the spell.
 
@@
 available, there is no significant evidence of a sex ratio biased towards males.
-Panel (b) shows a more male biased sex ratio but only a few of quarters show
+Panel (b) shows a more male biased sex ratio but only a few months show
 a statistically significant difference from the natural rate and the shallow 
 slope of the survival curve indicates that relatively few births took place
-during these quarters.
+during these months.
 Panel (c), however, shows clear evidence of the effect of access to prenatal
@@
 \footnote{
-Recall that quarter 0 is equivalent to 9 months (3 quarters) after the birth
+Recall that month 0 is equivalent to 9 months after the birth
 of the first child.

### 2017-10-24 paper/sexSelectionSpacing-ver1.tex
Minor edits

@@
 births predicted to happen over the spell.
+If the estimations are based on 100 or fewer births in a cell the predictions
+for that cell are not presented.
+Furthermore, those cells with 500 or fewer births are marked.
 
@@
 \input{../tables/median_sex_ratio_low.tex}
+
+Table \ref{tab:median_sex_ratio_low} show the predictions for women with 
+no education.
+Overall, spacing is shorter the fewer boys a couple has, although the
+differences in median duration are never more than 3 months and most
+are only one or two months.%
+\footnote{
+This is ignoring those cells with few births.
+}
+Furthermore, there is little change across the 3 periods.
+This is consistent with an absence of sex-selective abortions for
+this group of women.
 

### 2017-10-26 paper/sexSelectionSpacing-ver1.tex
Edit no education duration discussion

--- 2017-10-24 paper/sexSelectionSpacing-ver1.tex
@@
 \input{../tables/median_sex_ratio_low.tex}
+
+Table \ref{tab:median_sex_ratio_low} shows the predictions for women 
+with no education.
+Overall, spacing is shorter the fewer boys a couple has, but the
+differences in median duration are never more than 3 months and most
+are only one or two months
+(the exceptions to this pattern are mostly for small cells).
+Furthermore, although the median duration generally increases over 
+time---with the exception of the first spell---there is little 
+change in the relative pattern of durations across sex compositions
+over time.
+These results point to an absence of sex-selective abortions for 
+this group of women, which is also supported by the fact that
+most of the predicted sex ratios are close to the natural sex ratio.%
+\footnote{
+I return to whether there are statistically significant 
+differences below when examining sex ratios within spells.
+}
 

### 2017-12-04 paper/sexSelectionSpacing-ver1.tex

@@
 
+[Difference in approach: use the sex composition of prior
+children, rather the sex of the last child.
+Problem is that the cell sizes become too small if we further split up
+the higher spell cells.
+
+Define cell]
+
 The main question of interest here is how the duration between one
@@
 These results point to an absence of sex-selective abortions for 
-this group of women, which is also supported by the fact that
-most of the predicted sex ratios are close to the natural sex ratio.%
+this group of women, which is supported by predicted sex ratios
+that mostly close to the natural sex ratio.%
 \footnote{
@@
 
+For women with between 1 and 7 years of education it is harder
+to discern a pattern, partly because a larger number of area,
+sex composition, and periods combinations have relatively few 
+births in them.
+That said, the predicted median durations show less evidence 
+of son preference than for women without education.
+The exception to this are for the third spell for rural women
+for the 1972-1984 and 1985-1994 periods where the median
+durations are two and three months shorted with only girls
+compared to only boys, although the duration is longer for
+only girls in the 1995-2006 period.
+As for women with no education, there is little evidence of
+sex selection for women with 1 to 7 years of education,
+consistent with the absence of changes in relative durations
+across periods.
+
 \input{../tables/median_sex_ratio_high.tex}
+
+\clearpage
 
@@
 [Only a subset of the planned analyses to demonstrate the method and interpretation]
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,689)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,869)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=3,774)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,806)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=5,246)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,969)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_urban}
-\end{figure}
 
@@
 
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{First child a girl}
+\setcounter{subfigure}{-2}
+\subfloat[1972--1984 (N=2,689)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-1}
+\subfloat[1985--1994 (N=4,869)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{0}
+\subfloat[1995--2006 (N=3,774)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{First child a boy}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984 (N=2,806)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[1985--1994 (N=5,246)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{3}
+\subfloat[1995--2006 (N=3,969)]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of
+no birth yet from nine months after first birth for urban 
+women with 8 or more years of education by month beginning 9 months after prior birth. 
+Predictions based on age 22 at first birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_urban}
+\end{figure}
+
 % Survival curves conditional on progression
@@
 Figure \ref{fig:results_spell3_high_urban}.
-
-\clearpage
 

### 2017-12-04 paper/sexSelectionSpacing-ver1.tex
Edit abstract and introduction
Abstract:
- Emphasize changes in spacing over time

Introduction:
- General edits
- Highlight why spacing is still important to understand

@@
 
-\date{October 2017\\
+\date{December 2017\\
 \bigskip
@@
 % Demography abstract
-\noindent This paper examines how birth spacing interact with the use of 
-sex-selective abortions. 
-I introduce a statistical method that incorporates that sex-selective abortions 
-affect both the likelihood of a son and spacing between births.
+\noindent
+
+Strong son preference has frequently been associated with shorter 
+spacing between births after the birth of a girl.
+The spread of access to prenatal sex determination and 
+sex-selective abortions has the potential to reverse this pattern
+because each abortion adds substantially to the duration between births.
+I introduce a statistical method that simultaneously account for how sex 
+selection increases the likelihood of a son \emph{and} the spacing between births.
 Using India's National Family and Health Surveys,
 I show that use of sex selection leads to \emph{longer} spacing after a daughter 
-than after a son, but for families that do not use sex selection
-duration to next birth is still shorter when no boys are present.
+than after a son; a reversal of the pattern before the availability of sex selection.
+For families that do not use sex selection, the duration to next birth is still 
+shorter when no boys are present.
+
 Women with 8 or more years of education, both in urban and rural areas, are 
@@
 between son preference and birth spacing.
-This is because each sex-selective abortion substantially increases the 
-spacing from last birth. 
-For every abortion a woman has we should expect the duration from last
-birth to increase by approximately a year.
-This increase consists of three parts starting from the time of the 
-abortion.
-First, the uterus needs at least two menstrual cycles to recover 
-before conception, because a less than three months space 
-between abortion and conception substantially increases the likelihood 
-of a spontaneous abortion \citep{zhou00b}.
-Second, an average of 6 months to next conception \citep{Wang2003}.
+Couples with stronger son preferences are more likely to use prenatal
+sex determination and sex-selective abortions, but each sex-selective 
+abortion substantially increases the duration from last birth. 
+Each abortion increases spacing between births by approximately a year.
+The increase consists of three parts.
+First, starting from the time of the abortion, the uterus needs at 
+least two menstrual cycles to recover;  otherwise, the likelihood 
+of a spontaneous abortion increases substantially \citep{zhou00b}.
+The second part is the waiting time to conception, which I set to 6 
+months \citep{Wang2003}.
 Finally, sex determination tests are generally reliable only from 3 months 
@@
 \footnote{
-The waiting time to conception does vary by woman, but even if it is very 
+The waiting time to conception varies by woman, but even if it is very 
 short, say one  month, the additional space between births would still
@@
 As a result, we now have a situation where families with the \emph{strongest} son 
-preference may show the \emph{longest} spacing after the birth of a daughter
-because of the use of sex-selective abortions.
+preference may show the \emph{longest} spacing after the birth of a daughter,
+because of their use of sex-selective abortions.
 But, to further complicate matters, we may still observe short spacing 
-after the birth of daughter as a representation of son preference for 
+after the births of daughters as a representation of son preference for 
 families who---for one reason or another---do not use prenatal sex selection.
@@
 Spacing, by itself, can therefore no longer be used to measure son preference.
-Spacing is, however, still important and useful in understanding son preference, 
-but only if combined with the likelihood of observing a boy or a girl.
-Short spacing after a girl is indicative of son preference if observed
-births are close to the natural sex ratio, whereas long spacing is indicative
-of son preference if observed births are male biased.
+Understanding birth spacing remains, however, an important undertaking.
+First, spacing is still important and useful in understanding son preference, 
+if combined with the likelihood of observing a boy or a girl.
+% Short spacing after a girl is indicative of son preference if observed
+% births are close to the natural sex ratio, whereas long spacing is indicative
+% of son preference if observed births are male biased.
+Second, if spacing affect health outcomes for mother and/or children, it is 
+important to understand what drives changes in spacing.
+The better health outcomes for girls in the presence of sex selection may,
+for example, be an unintended side-effect of the longer spacing that arise
+from sex-selective abortions rather than be driven by a higher value of
+girls resulting from lower supply \citep{Lin2014,Hu2015}.
+Third, spacing may be an important factor in parents' decisions, either
+for preference or economic reasons, such as labor force participation.
+This is especially important here because even parents with strong
+son preference may reverse their decision to use prenatal sex determination, 
+and carry the next pregnancy to term whether male or female, as the duration 
+from last birth becomes sufficiently sufficiently long.%
+\footnote{
+More generally, we know less about what determines spacing behavior in 
+developing countries than in developed countries.
+With increasing numbers of women entering the labor force in developing
+countries, understanding how timing decisions are made will be important
+for the design of suitable policies \citep{Portner2018}.
+}
 
@@
 birth to affect the decision on sex selection.
-For example, as the duration from last birth becomes long enough, even 
-parents with strong son preference may reverse their decision to use 
-prenatal sex determination, and carry the next pregnancy to term whether 
-male or female.
 By examining whether sex selection decisions change with spacing, we can 
@@
 prenatal sex determination in India over the period covered.
-Abortion has been legal in India since 1971 and still is, but the 
-first reports of on the availability of prenatal sex determination did
+Abortion has been legal in India since 1971, and still is, but the 
+first reports of prenatal sex determination did
 not appear until 1982--83 \citep{Sudha1999,bhat06,Grover2006}.

### 2017-12-05 paper/sexSelectionSpacing-ver1.tex
Edit Estimation Strategy section
- Add notes on why not use observed spacing (needs writing)
- Begin rewrite of why not proportionality in hazards
- General edits

@@
 % Revamped version for Demography focusing on method
-
-% sex-selective Abortion
-% Begun originally: 01/11/02
-% Begun.: 2017-04-03
-% Edited: 2017-04-03
 
@@
 
-[TK this needs to move to later]
-Finally, increased reliability of access and effectiveness of
-contraceptive can lead to shorter spacing between births 
-\citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level 
-of contraception---resulting in longer spacing---to avoid having 
-too many children by accident.
-But, as contraception becomes more effective parents can more
-easily avoid future births, allowing them to reduce the spacing 
-between births without having to worry about overshooting their 
-preferred number of children.
-This idea may also help explain shorter spacing for better 
-educated women than for less educated women, provided that   
-knowledge and ability to use contraception differ
-across education groups \citep{Tulasidhar1993,Whitworth2002}.
-
-To improve on the literature's current approaches to understanding 
-son preference, a new empirical method must be able to capture the 
-three main implications of the availability of sex-selective abortions
-combined with son preference:
+Although it might be tempting to simply examine how observed
+spacing has changed over time this is problematic.
+
+Possible ways of doing this:
+- Only closed spells (where a birth is observed)
+    - can be split by the outcome (ending birth is either male or female)
+    - can be split by the sex composition of prior children
+- All spells (whether closed or not)
+    - can only be split by the sex composition of prior children
+
+Problems:
+- Using closed spells only ignore that those families with the strongest
+  son preference are also likely to have the longest spacing and therefore be 
+  less likely to show up as a complete spell.
+- Because of the potential for changes in the use of sex selection within a spell
+  it is possible that parents go through multiple sex-selective abortions and still
+  end up with a girl
+- Some open spells may not result in a birth (childbearing finished with prior birth),
+  which is especially a problem for higher parities where sex composition of
+  prior children has a large effect on the probability of parity progression.
+
+Need a method that accounts for censoring.
+
+In addition to accounting for censoring, the empirical method must be able 
+to capture the three main implications of the availability of sex-selective 
+abortions combined with son preference:
 a higher probability that the next child is a son, 
@@
 and that the use of prenatal sex determination may change between 
-one observed birth and the next.%
-\footnote{
+one observed birth and the next.
 In addition, it should be able to capture the shorter spacing between
@@
 sex determination.
-}
-This means that we need an empirical model that can jointly estimate 
+This means an empirical model that can jointly estimate 
 the association between covariates and both the sex of children born 
@@
 I divide a woman's reproductive life into spells that each covers 
-the period between births (from marriage to first birth for the first spell).
+the period between births (or from marriage to first birth for the first spell).
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
-the spell continues until time $t_i$ when either a birth occurs or the spell 
+the spell continues until time $t_i$, when either a birth occurs or the spell 
 is censored.%
@@
 To ease presentation the indicator for spell number is suppressed.
-The vectors of explanatory variable $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$ include 
-information about various individual, household, and community characteristics 
-discussed below.
+The explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, include 
+individual, household, and community characteristics discussed below.
 
@@
 overly strong restrictions on the baseline hazard.
+
+The standard proportionality of hazards assumption does not work here.
+First, even in the absense of sex selection, it is unlikely that the shape of
+hazard functions are identical across groups.
+[sex composition]
 
@@
 the censoring of some spells that will eventually lead to a birth.
+
+[TK not sure where to fit this into]
+Finally, increased reliability of access and effectiveness of
+contraceptive can lead to shorter spacing between births 
+\citep{Keyfitz1971,Heckman1976}.
+With less reliable contraception parents choose a higher level 
+of contraception---resulting in longer spacing---to avoid having 
+too many children by accident.
+But, as contraception becomes more effective parents can more
+easily avoid future births, allowing them to reduce the spacing 
+between births without having to worry about overshooting their 
+preferred number of children.
+This idea may also help explain shorter spacing for better 
+educated women than for less educated women, provided that   
+knowledge and ability to use contraception differ
+across education groups \citep{Tulasidhar1993,Whitworth2002}.
 

### 2017-12-05 paper/sexSelectionSpacing-ver1.tex
Edits of intro and empirical strategy

@@
 between son preference and birth spacing.
-Couples with stronger son preferences are more likely to use prenatal
-sex determination and sex-selective abortions, but each sex-selective 
-abortion substantially increases the duration from last birth. 
-Each abortion increases spacing between births by approximately a year.
+Couples, who used to have short birth spacing because of son preference,
+now have access to prenatal sex determination and sex-selective abortions,
+but each sex-selective abortion they have substantially increases the space
+between births. 
+Birth spacing increases by approximately a year per abortion.
 The increase consists of three parts.
@@
 preference may show the \emph{longest} spacing after the birth of a daughter,
-because of their use of sex-selective abortions.
+because they use sex-selective abortions.
 But, to further complicate matters, we may still observe short spacing 
@@
 Spacing, by itself, can therefore no longer be used to measure son preference.
-Understanding birth spacing remains, however, an important undertaking.
-First, spacing is still important and useful in understanding son preference, 
+However, understanding birth spacing remains an important undertaking.
+First, spacing is still useful in understanding son preference, 
 if combined with the likelihood of observing a boy or a girl.
@@
 % of son preference if observed births are male biased.
-Second, if spacing affect health outcomes for mother and/or children, it is 
+Second, if spacing affects health outcomes for mother and/or children, it is 
 important to understand what drives changes in spacing.
@@
 for example, be an unintended side-effect of the longer spacing that arise
-from sex-selective abortions rather than be driven by a higher value of
-girls resulting from lower supply \citep{Lin2014,Hu2015}.
+from sex-selective abortions, rather than, as often assumed, be driven by a 
+higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
 Third, spacing may be an important factor in parents' decisions, either
-for preference or economic reasons, such as labor force participation.
-This is especially important here because even parents with strong
+for preference or economic reasons.
+This is especially important here, because even parents with strong
 son preference may reverse their decision to use prenatal sex determination, 
 and carry the next pregnancy to term whether male or female, as the duration 
-from last birth becomes sufficiently sufficiently long.%
-\footnote{
-More generally, we know less about what determines spacing behavior in 
+from the prior birth becomes sufficiently sufficiently long.
+Finally, we know less about what determines spacing behavior in 
 developing countries than in developed countries.
@@
 for the design of suitable policies \citep{Portner2018}.
-}
-
-In this paper, I introduce and apply a novel method that directly incorporates 
+
+In this paper, I introduce and apply a novel empirical method that directly incorporates 
 the effects of sex-selective abortions on the likelihood of a son being born 
@@
 sex selection.
-Furthermore, my proposed method allow for the duration since the last 
+Furthermore, my proposed method allow for the duration since the prior 
 birth to affect the decision on sex selection.

### 2017-12-07 paper/sexSelectionSpacing-ver1.tex
Add method requirements to beginning of Estimation Strategy

@@
 
-Although it might be tempting to simply examine how observed
-spacing has changed over time this is problematic.
-
-Possible ways of doing this:
-- Only closed spells (where a birth is observed)
-    - can be split by the outcome (ending birth is either male or female)
-    - can be split by the sex composition of prior children
-- All spells (whether closed or not)
-    - can only be split by the sex composition of prior children
-
-Problems:
-- Using closed spells only ignore that those families with the strongest
-  son preference are also likely to have the longest spacing and therefore be 
-  less likely to show up as a complete spell.
-- Because of the potential for changes in the use of sex selection within a spell
-  it is possible that parents go through multiple sex-selective abortions and still
-  end up with a girl
-- Some open spells may not result in a birth (childbearing finished with prior birth),
-  which is especially a problem for higher parities where sex composition of
-  prior children has a large effect on the probability of parity progression.
-
-Need a method that accounts for censoring.
-
-In addition to accounting for censoring, the empirical method must be able 
-to capture the three main implications of the availability of sex-selective 
-abortions combined with son preference:
-a higher probability that the next child is a son, 
-longer spacing to next birth with use of sex selection, 
-and that the use of prenatal sex determination may change between 
-one observed birth and the next.
-In addition, it should be able to capture the shorter spacing between
-births observed in the absence of use or availability of prenatal 
-sex determination.
-This means an empirical model that can jointly estimate 
-the association between covariates and both the sex of children born 
-and the spacing from last birth. 
-My proposed model is a discrete time, non-proportional competing risk 
-hazard model with two exit states: either a boy or a girl is born.%
+Requirements for method and the intuition behind each:  
+ - Account for censoring (hazard model)
+ - Work both with and without sex selection (competing risk part)
+ - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
+ - Capture that the shape of the hazard function differ across groups
+   (non-proportionality); needs a better description, maybe using example
+   of shorter spacing and/or use of sex selection. Differences in parity
+   progression likelihood.
+
+I divide a woman's reproductive life into one or more spells.
+Each spell covers the period from one birth, or marriage for the first spell,
+to the following birth; I define how the duration is measured in more 
+detail in Section \ref{sec:data}.
+A basic problem is that some spells' durations are censored, either
+because the survey took place before the end birth for the spell or because
+the couple has finished childbearing.
+The standard approach, which I follow here, is to use a hazard models to 
+address the censoring of spells.
+
+Prior research on birth spacing have used hazard models where the exit 
+state was the birth of a child. 
+This works when there is no sex selection---making the sex of the child 
+a random event---but not here because at least some couples use 
+sex selection. 
+To capture that the sex of children are no longer a random event, I instead
+use a competing risk framework with two possible exit states: either a boy 
+or a girl is born.%
 \footnote{
@@
 
-I divide a woman's reproductive life into spells that each covers 
-the period between births (or from marriage to first birth for the first spell).
+Proportional hazard models, where covariate have an multiplicative 
+effect on the hazard rate, are more efficient than non-proportional 
+models, but only provided that the proportionality assumption holds.
+The problem here is that a proportional hazard model does not allow covariates
+to have different sized effects at different times within a spell and therefore
+cannot capture differences in the shape of the hazard functions between 
+different groups, and if the proportionality assumption does not hold 
+the result is a potentially substantial bias in estimates.
+It is unlikely---even in the absence of prenatal sex 
+determination---that the effect of, for example, the sex composition
+of prior births have the same effect throughout the entire spell.
+[son preference and parity progression also leads to differences!]
+Furthermore, any bias from the proportionality assumption is likely 
+exacerbated by the introduction of prenatal sex determination.
+First, sex-selective abortions affects birth spacing and its use
+vary across groups.
+Second, the use of sex selection may vary within a spell, which means 
+that the effect of covariate may vary within the spell as well.
+Finally, the use of a non-proportional specification, together with a 
+flexible baseline hazard, also mitigates any potential effects of 
+unobserved heterogeneity \citep{Dolton1995}.
+My proposed model is a discrete time, non-proportional competing risk 
+hazard model with two exit states: either a boy or a girl is born.
+
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
@@
 
-The standard proportionality of hazards assumption does not work here.
-First, even in the absense of sex selection, it is unlikely that the shape of
-hazard functions are identical across groups.
-[sex composition]
-
-[TK I am not very satisfied with this explanation of the problems with
-proportionality and the associated bias; non-proportionality is required
-to capture changes in use of sex selection]
-
-In principle, specifying the model as a proportional hazard model, i.e.\ one 
-where covariates simply shift the hazard rates up or down independent of 
-spell length, is more efficient, but only provided that the proportionality 
-assumption holds.
-If the proportionality assumption does not hold, however, the result is
-a potentially substantial bias in estimates.
-The problem is that a proportional hazard model does not allow covariates
-to have different effects at different times within a spell and therefore
-cannot capture differences in the shape of the hazard functions between 
-different groups. 
-It is highly unlikely---even in the absence of prenatal sex determination---that 
-the baseline hazards are the same across education levels, areas of residence, 
-or sex composition of previous births.
-Any bias from the proportionality assumption is likely exacerbated by the 
-introduction of prenatal sex determination for two reasons.
-First, one of the main points of this paper is that use of sex-selective 
-abortions affects birth spacing, and use of sex selection differs across groups.
-Second, as discussed above, the use of sex selection may vary within a spell,
-depending on the length of the spell.
-
-I therefore use a non-proportional model where the main explanatory variables 
-and the interactions between them are interacted with the baseline hazards.
-This is captured by the $Z$ set of explanatory variables
+The $Z$ set of explanatory variable and the interactions between them 
+are the non-proportional part of the model, which means that they are
+interacted with the baseline hazard:
 \begin{equation}
@@
 of having a boy, a girl, or no birth to vary over time within a spell.
-The use of a non-proportional specification, together with a flexible baseline hazard, 
-also mitigates any potential effects of unobserved heterogeneity \citep{Dolton1995}.
-
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
 To further minimize any potential bias from assuming proportionality, estimations 
@@
 time periods.
-The exact specifications and the individual variables are described below.
+The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
+% The exact specifications and the individual variables are described below.
 
@@
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, if the data are transformed so the unit of analysis is spell unit rather 
-than the individual woman, the model can be estimated using a standard multinomial 
-logit model.%
+Hence, if the data are transformed so the unit of analysis is spell unit, in 
+this case 3 months periods, rather than the individual woman, the model can be 
+estimated using a standard multinomial logit model.%
 \footnote{
@@
 
-The main downside of this approach is that direct interpretation of the estimated 
-coefficients for this model is challenging because of the competing risk setup.
+The main downside is that direct interpretation of the estimated 
+coefficients is challenging because of the competing risk setup.
 First, coefficients show the change in hazards relative to the base outcome, 
 no birth, rather than simply the hazard of an event.
-Second, a positive coefficient does not necessarily imply that an increase in a
-variable's value increases the probability of the associated event because the 
+Second, a, for example, positive coefficient does not necessarily imply that
+a higher variable value is associated with a higher event probability because the 
 probability of another event may increase even more \citep{thomas96}.
@@
 
-The other important part of the model is the spacing between births.
-Spacing is captured by the survival curve, which shows the probability of not 
-having had a birth yet by spell duration.
+The distribution of spacing is captured by the survival curve, which shows 
+the probability of not having had a birth yet by spell duration.
 The survival curve at time $t$ is 
@@
 
-In the absence of sex selection, I expect most parities to show an 
-``inverted s'' pattern, where there initially are relatively few births, 
-followed by a substantial number of births over a 1 to 2 year period, and then
-relatively few births thereafter.
-As sex selection becomes more widely used the associated
-longer spacing shows up by making the survival curve straighter,
-indicating that some of the births that would originally have taken place
-now take place later because of abortions.
-The use of sex selection is clearly not the only factor that can change the shape of
-the survival curves; factors such as the desired number of children and
-use of contraceptives may also shape the shape.
-To account for this it is best to compare survival curves for an individual
-parity between women who are likely to use sex selection and women who are
-not, for example because they already have one or more sons.
-
-In addition to information about spacing, the survival curves also provide 
-``weighting'' for the associated percentage boys born.
-The steeper the survival curve, the more weight should be assigned to a given
-spell period because it is based on more births, 
-whereas a period with a flat survival curve should be given little weight because the 
-percentage boys is based on few births.
-Hence, although they cannot by themselves show sex selection, the survival
-curves are a crucial complement to the estimated sex ratios by duration.
-
 [The problem with comparing survival curves]
@@
 the censoring of some spells that will eventually lead to a birth.
-
-[TK not sure where to fit this into]
-Finally, increased reliability of access and effectiveness of
-contraceptive can lead to shorter spacing between births 
-\citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level 
-of contraception---resulting in longer spacing---to avoid having 
-too many children by accident.
-But, as contraception becomes more effective parents can more
-easily avoid future births, allowing them to reduce the spacing 
-between births without having to worry about overshooting their 
-preferred number of children.
-This idea may also help explain shorter spacing for better 
-educated women than for less educated women, provided that   
-knowledge and ability to use contraception differ
-across education groups \citep{Tulasidhar1993,Whitworth2002}.
 
@@
 \section{Results\label{sec:results}}
+
+[TK not sure where to fit this into]
+Finally, increased reliability of access and effectiveness of
+contraceptive can lead to shorter spacing between births 
+\citep{Keyfitz1971,Heckman1976}.
+With less reliable contraception parents choose a higher level 
+of contraception---resulting in longer spacing---to avoid having 
+too many children by accident.
+But, as contraception becomes more effective parents can more
+easily avoid future births, allowing them to reduce the spacing 
+between births without having to worry about overshooting their 
+preferred number of children.
+This idea may also help explain shorter spacing for better 
+educated women than for less educated women, provided that   
+knowledge and ability to use contraception differ
+across education groups \citep{Tulasidhar1993,Whitworth2002}.
+
+[Moved from estimation strategy]
+In the absence of sex selection, I expect most parities to follow
+a pattern, where there initially are relatively few births, 
+followed by a substantial number of births over a 1 to 2 year period, and then
+relatively few births thereafter.
+As sex selection becomes more widely used the associated
+longer spacing shows up by making the survival curve straighter,
+indicating that some of the births that would originally have taken place
+now take place later because of abortions.
+The use of sex selection is clearly not the only factor that can change the shape of
+the survival curves; factors such as the desired number of children and
+use of contraceptives may also shape the shape.
+To account for this it is best to compare survival curves for an individual
+parity between women who are likely to use sex selection and women who are
+not, for example because they already have one or more sons.
+
+[Moved from estimation strategy]
+In addition to information about spacing, the survival curves also provide 
+``weighting'' for the associated percentage boys born.
+The steeper the survival curve, the more weight should be assigned to a given
+spell period because it is based on more births, 
+whereas a period with a flat survival curve should be given little weight because the 
+percentage boys is based on few births.
 

### 2017-12-07 paper/sexSelectionSpacing-ver1.tex
Edit of model requirements/set-up

@@
 
-Requirements for method and the intuition behind each:  
- - Account for censoring (hazard model)
- - Work both with and without sex selection (competing risk part)
- - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
- - Capture that the shape of the hazard function differ across groups
-   (non-proportionality); needs a better description, maybe using example
-   of shorter spacing and/or use of sex selection. Differences in parity
-   progression likelihood.
-
-I divide a woman's reproductive life into one or more spells.
-Each spell covers the period from one birth, or marriage for the first spell,
-to the following birth; I define how the duration is measured in more 
-detail in Section \ref{sec:data}.
-A basic problem is that some spells' durations are censored, either
-because the survey took place before the end birth for the spell or because
-the couple has finished childbearing.
+% Requirements for method and the intuition behind each:  
+%  - Account for censoring (hazard model)
+%  - Work both with and without sex selection (competing risk part)
+%  - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
+%  - Capture that the shape of the hazard function differ across groups
+%    (non-proportionality); needs a better description, maybe using example
+%    of shorter spacing and/or use of sex selection. Differences in parity
+%    progression likelihood.
+
+I divide women's reproductive lives into spells, which are the periods from 
+one birth, or marriage for the first spell, to the following birth
+(I define how spell duration is measured in Section \ref{sec:data}).
+A basic problem is that some spells' duration are censored, either
+because the survey took place before the birth that would end the spell 
+or because the couple has finished childbearing.
 The standard approach, which I follow here, is to use a hazard models to 
@@
 
-Prior research on birth spacing have used hazard models where the exit 
-state was the birth of a child. 
+Prior research on birth spacing have used hazard models where the only 
+exit state was the birth of a child. 
 This works when there is no sex selection---making the sex of the child 
@@
 sex selection. 
-To capture that the sex of children are no longer a random event, I instead
-use a competing risk framework with two possible exit states: either a boy 
-or a girl is born.%
+To capture that the sex of children are no longer necessarily a random event, 
+I instead use a competing risk framework with two possible exit states: 
+either a boy or a girl is born.%
 \footnote{
@@
 
-Proportional hazard models, where covariate have an multiplicative 
+Proportional hazard models, where covariates have an multiplicative 
 effect on the hazard rate, are more efficient than non-proportional 
 models, but only provided that the proportionality assumption holds.
-The problem here is that a proportional hazard model does not allow covariates
-to have different sized effects at different times within a spell and therefore
-cannot capture differences in the shape of the hazard functions between 
-different groups, and if the proportionality assumption does not hold 
-the result is a potentially substantial bias in estimates.
-It is unlikely---even in the absence of prenatal sex 
-determination---that the effect of, for example, the sex composition
-of prior births have the same effect throughout the entire spell.
-[son preference and parity progression also leads to differences!]
-Furthermore, any bias from the proportionality assumption is likely 
+Because proportional hazard models do not allow covariates to have 
+different sized effects at different times within a spell,
+they cannot capture differences in the shape of the hazard functions 
+between different groups, and if the proportionality assumption does 
+not hold the estimates may be biased.
+It is unlikely---even in the absence of prenatal sex determination---that 
+the effect of, for example, the sex composition of prior births have 
+the same effect throughout the entire spell.
+This is especially the case for later spells where different
+sex composition of prior births can lead to substantial difference 
+both in the likelihood of progressing to the next birth and
+how soon couples want their next child if they are going to have one.
+Any bias from the proportionality assumption is likely 
 exacerbated by the introduction of prenatal sex determination.
-First, sex-selective abortions affects birth spacing and its use
+First, sex-selective abortions affect birth spacing and use
 vary across groups.
 Second, the use of sex selection may vary within a spell, which means 
-that the effect of covariate may vary within the spell as well.
-Finally, the use of a non-proportional specification, together with a 
-flexible baseline hazard, also mitigates any potential effects of 
-unobserved heterogeneity \citep{Dolton1995}.
-My proposed model is a discrete time, non-proportional competing risk 
+that the effects of covariates vary within the spell as well.
+Because of these concerns I use a non-proportional specification.
+The use of a non-proportional specification also has the benefit 
+that it mitigates any potential effects of unobserved heterogeneity 
+when used in conjunction with a flexible baseline hazard \citep{Dolton1995}.
+My proposed model is a discrete time, non-proportional, competing risk 
 hazard model with two exit states: either a boy or a girl is born.

### 2017-12-07 paper/sexSelectionSpacing-ver1.tex
Edit of model set-up

@@
 when used in conjunction with a flexible baseline hazard \citep{Dolton1995}.
-My proposed model is a discrete time, non-proportional, competing risk 
+In summary, my proposed model is a discrete time, non-proportional, competing risk 
 hazard model with two exit states: either a boy or a girl is born.
@@
 overly strong restrictions on the baseline hazard.
-
-The $Z$ set of explanatory variable and the interactions between them 
+The explanatory variables in $\mathbf{Z}$ and the interactions between them 
 are the non-proportional part of the model, which means that they are
@@
 of having a boy, a girl, or no birth to vary over time within a spell.
-To further minimize any potential bias from assuming proportionality, estimations 
+The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
+but to further minimize any potential bias from assuming proportionality, estimations 
 are done separately for different levels of mothers' education and for different 
 time periods.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
 % The exact specifications and the individual variables are described below.
@@
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, if the data are transformed so the unit of analysis is spell unit, in 
+Hence, if the data are transformed so the unit of analysis is a time period, in 
 this case 3 months periods, rather than the individual woman, the model can be 
@@
 }
-In the reorganized data the outcome variable is zero if the
-woman does not have a child in a given period, one if she gives birth to a son 
-in that period, and two if she gives birth to a daughter in that period.
-
-The main downside is that direct interpretation of the estimated 
-coefficients is challenging because of the competing risk setup.
-First, coefficients show the change in hazards relative to the base outcome, 
-no birth, rather than simply the hazard of an event.
-Second, a, for example, positive coefficient does not necessarily imply that
-a higher variable value is associated with a higher event probability because the 
-probability of another event may increase even more \citep{thomas96}.
-
+In the reorganized data the outcome variable is 0 if the
+woman does not have a child in a given period (the base outcome), 1 if 
+she gives birth to a son in that period, and 2 if she gives birth to 
+a daughter in that period.
+
+The main downside of this set-up is that direct interpretation of the estimated 
+coefficients is challenging;
+the coefficients show the change in hazards relative to the base outcome, 
+here no birth, rather than simply the hazard of an event.
+Hence, a positive coefficient does not necessarily imply that the associated 
+exit state becomes likely as the explanatory variable increases because the 
+probability of the other exit state may increase even more \citep{thomas96}.
 It is, however, straightforward to calculate the predicted probabilities of 
@@
 \end{equation}
+
+[survival curve here]
+
 With these two probabilities is it easy to calculate, for each $t$, the estimated

### 2017-12-08 paper/sexSelectionSpacing-ver1.tex
Reorganization and shortening of Estimation Strategy
First present probabilities of boy and girl at each time period.
Then discuss the problem of interpretation of variables, followed
by survival curve and how to address differences in parity
progression likelihood.
Finally, show how to calculate percentage boys and discuss the
graphs associated with those.

@@
 \end{equation}
-
-[survival curve here]
-
-With these two probabilities is it easy to calculate, for each $t$, the estimated
-percentage of children born that are boys, $\hat{Y}$, 
-\begin{equation}
-\hat{Y}_t 
-= 
-\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-\times 100,
-\label{eq:probability_son}
-\end{equation}
-together with the associated confidence interval for given values of explanatory 
-variables.%
-\footnote{
-Within each period $1-P(b_{t})-P(g_{t})$ is the probability of not having a birth in 
-period $t$.
-}
-
-For ease of exposition the procedure is presented here in two steps, but the actual
-calculation of the percent boys is done in one step with the 95 percent confidence 
-interval calculated using the Delta method.
-Results are presented as the estimated percent boys born by length of birth spacing
-using graphs.%
-\footnote{
-The parameter estimates are available on request.
-}
-For each graph, the extent to which the percent boys is statistically 
-significantly above the natural sex ratio indicates the use of sex selection.
-
-[TK  may need to combine with and without sons to show differences in spacing 
-over time; maybe it should also have predicted average/median spacing with some 
-confidence intervals to test]
+Within each period the probability of not having a birth in period $t$
+is $1-P(b_{t})-P(g_{t})$.
 
 The distribution of spacing is captured by the survival curve, which shows 
-the probability of not having had a birth yet by spell duration.
+the probability of not having had a birth yet by spell duration, for
+a given set of explanatory variables.
 The survival curve at time $t$ is 
@@
 
-[The problem with comparing survival curves]
-
-In principle, in order to understand how birth spacing changes in response
-to the introduction of prenatal sex determination one could simply compare survival 
-curves between different sex compositions of prior births over time.
-If the idea that the availability of sex-selective abortion increases the
-spacing more after the birth of girls than after the birth of boys is 
-correct, we should see the two survival curves become closer to each other
-and we might even be able to directly observe that the survival curve for prior
-child being a girl is above the survival curve for prior child being a boy,
-instead of substantially below as was generally the case before prenatal
-sex determination become widely available.
-
-There are, however, two (interrelated) problems.
-First, the probability that a woman will progress to a next birth  
-is not the same across different sex compositions of prior children.
-Specifically, one of the ways that past research has tried to establish
-son preference in fertility behavior is to compare parity progression
-rates for different sex compositions [TK references - see footnote 1].
-The idea was that if there is son preference a couple would be less likely
-to progress to a next birth if they have one or more son already for a
-given number of prior births.
-
-The fact that the probability of having a next birth also depends on the
-sex composition complicates the comparison of survival curves. 
-A lower parity progression probability will naturally make the survival
-curve flatter.
-This means that the survival curve for a girl composition will be more
-likely to be below the boy composition.
-Even if the use of sex selection is substantial enough to move the
-survival curve for girl composition to the right of the boy
-composition the lower parity progression probability for boy 
-composition means that the survival curves would eventually have to
-cross.
-This makes it difficult---if not impossible---to design a direct test
-of how the survival curves compare.
-
-The problem of different parity progression rates across different
-sex composition is exacerbated by falling fertility over time.
-This is because there are now more parities where they may be a 
-substantial differences in parity progression rates and because
-the difference in parity progression for a given parity will 
-become larger if there is son preference.
-As the parity progression probability decreases it becomes impossible
-to capture the time until a certain survival point (like 0.5 of women
-having had a child; the survival curve may never actually reach this
-point).
-
-In addition, it is possible that falling fertility also generically 
-leads to longer spacing between births.
-This means that we have to separate out which part of the longer
-spacing comes from falling fertility (and therefore should also
-affect boy composition) and which parts comes from increased use
-of sex selection.
-
-[We should expect sex selection to be mainly used for the last---or close to
-last---birth that a couple expect to have because of the cost and risk
-of the procedures.]
-
-One solution to this problem is to condition on the parity progression
-rates.
-That is, instead of comparing say how long it takes for 50\% of women
-who began the spell to have the next birth across boy and girl composition, 
-which would work well if the next birth was nearly universal, we 
-could calculate how long it takes for 50\% of those women who will 
-eventually have a next child to have that child based on the estimated
-survival curves.
-This number can then be compared across sex compositions to 
-understand if the spell length for girl composition increases
-more than for boy composition with the introduction of sex selection.
-Obviously, this should be calculated for different percentages
-and the easiest way to interpret the result is to graph survival
-conditional on parity progression occurring.
-All compositions therefore begin at 100\% and end at 0\% because
-we condition on having the next child.
-
-Note, this is not the same as simply calculating the average 
-\emph{observed} spell lengths among women who have a given parity
-child in the survey because that number does not take into account
-the censoring of some spells that will eventually lead to a birth.
+An important issue is that the probability of ever having a next birth varies 
+across groups.
+For example, as the parity progression literature shows, couples with stronger 
+son preference are less likely, for a given number of prior births, to ever have 
+a next birth if they already have one or more sons.
+Direct comparison of standard survival curves therefore tells us little 
+about how the spread of sex selection affect birth spacing across, for
+example, different sex compositions of prior children.
+To overcome this problem I condition on parity progression when examining
+birth spacing using the survival curves.
+This allows me to calculate measures, such as median spell duration, for
+the women with a given set of characteristics who will eventually give
+birth in a spell.%
+\footnote{
+It is important to note that this is not the same as simply calculating 
+the median \emph{observed} spell lengths among women who have a given 
+parity child in the survey because that number does not take into account
+the censoring of spells that will eventually lead to a birth.
+}
+This number can then be compared across groups to understand how birth
+spacing changes with the introduction of sex selection.
+Obviously, this approach only works if the spell length covered is 
+sufficiently long that only very few women would be likely to give
+birth later.
+In addition to calculating conditional spell length for different 
+percentages, I also present graphs of both standard survival curves and
+survival curves conditional on parity progression (which therefore
+begin at 100\% and end at 0\%).
+
+Finally, with the predicted probabilities of having a boy and of having 
+a girl for each $t$ within a spell, is it easy to calculate the estimated 
+percentage of children born that are boys, $\hat{Y}$, at each $t$  
+\begin{equation}
+\hat{Y}_t 
+= 
+\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
+{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
+\times 100.
+\label{eq:probability_son}
+\end{equation}
+Combining the percentage boys and the likelihood of exiting across all $t$ 
+gives the predicted percent boys born over the entire spell.
+In addition to the predicted percent boys over the entire spell, 
+I also present graphs of how the percentage boys born vary across time
+within a spell, together with the associated confidence interval for given 
+values of explanatory variables calculated using the Delta method.
+These are combined with standard survival curves which shows the ``weight''
+that each period should be given, or, in other words, how many births take
+place in each period.
 
@@
 \section{Results\label{sec:results}}
+
+Results are presented as the estimated percent boys born by length of birth spacing
+using graphs.
+For each graph, the extent to which the percent boys is statistically 
+significantly above the natural sex ratio indicates the use of sex selection.
+
+[TK not sure where this fits in]
+In addition, it is possible that falling fertility also generically 
+leads to longer spacing between births.
+This means that we have to separate out which part of the longer
+spacing comes from falling fertility (and therefore should also
+affect boy composition) and which parts comes from increased use
+of sex selection.
+
+[We should expect sex selection to be mainly used for the last---or close to
+last---birth that a couple expect to have because of the cost and risk
+of the procedures.]
 

### 2017-12-08 paper/sexSelectionSpacing-ver1.tex
Revise Data section
- Move substantial parts of recall discussion to online Appendix.
- Shorten spell definition part
- Reorder explanatory variables subsection
- General edits

@@
 not appear until 1982--83 \citep{Sudha1999,bhat06,Grover2006}.
+The number of clinics quickly increased, and knowledge about sex selection 
+became widespread after a senior government official's wife aborted a 
+fetus that turned out to be male \citep[p.\ 598]{Sudha1999}.
 In 1994, the Central Government passed the Prenatal Diagnostic Techniques 
@@
 Women who reported less than 9 months between marriage and first birth
-remain in the sample unless they are dropped for another reason.%
-\footnote{
-Women who report less than 9 months between marriage and first birth are retained 
-because between 10 and 20 percent fall into this category.
-Although it is possible that some of these births are premature the high number of
+remain in the sample---unless they are dropped for another reason---because 
+10 to 20 percent fall into this category across the 3 surveys.
+Although it is possible that some of these births are premature, the high number of
 women who report a birth less than 6 months after marriage indicates that conception
 likely occurred before marriage in most cases.
-}
 
@@
 Recall error arise mainly from child mortality, when respondents are reluctant to
-discuss deceased children.%
-\footnote{
-The online Appendix contains a more thorough discussion of recall error and how I address it.
-} 
+discuss deceased children.
 Systematic recall error, where the likelihood of reporting a deceased child depends on
-the sex of the child, is especially problematic because it biases the sex ratios.
+the sex of the child, is especially problematic because it biases both spacing
+and sex ratios.
 Probing catches many missed births, but systematic recall error is still a potentially 
@@
 that procedure is unlikely to pick up all missed children.
-
-Observed sex ratios by cohort provide a straightforward way to determine 
-whether recall error is a problem.
-Because prenatal sex determination techniques did not become widely available until the 
-mid-1980s, a higher than natural sex ratio for cohorts born before that time must be 
-the result of systematic recall error.
-As shown in the online Appendix, the observed sex ratio by parity becomes more male 
-dominated the further back births took place.
-In addition, births in the same cohort tend to be more male dominated the more recent the 
-survey (births in the cohort took place longer ago relative to the survey).
-Hence, there is evidence of recall error and the degree of recall error increases
-with length of time between survey and cohort.
-
-Using cohort year of birth to analyze recall error and decide which observations
-to keep is, however, problematic because the year of birth for a given parity is affected 
-by recall error; for example, a second born child listed as first born will be 
-born later than the real first born child.
-Year of marriage should, however, be unaffected by recall error.
-Using year of marriage the basic recall error pattern remains with women married longer 
-ago more likely to report that their child was a boy for a given parity.
-Similarly, comparing women married in the same period across surveys shows
-that women married longer ago are more likely to report having sons.
-
-That recall error increases the longer ago somebody was married means
-that duration of marriage is a better predictor of recall error than calendar year of 
-marriage.
-Figure \ref{fig:sexRatioMarriage} shows the observed sex ratio for children 
-reported as first born as a function of duration of marriage combining all three surveys.%
-\footnote{
-The graph for second births shows a similar pattern.
-The graphs for the second births and the individual survey rounds are available upon request.
-}
-The solid line is the sex ratio of children reported 
-as first born by the number of years between the survey and marriage, 
-the dashed lines indicate the 95 percent confidence interval 
-and the horizontal line the natural sex ratio (approximately 0.512).
-To ensure sufficient cell sizes the years are grouped in twos.
-
-% \begin{figure}[htp]%
-% \centering
-% \includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
-% \caption{Ratio of boys in ``first'' births}
-% \label{fig:sexRatioMarriage}
-% \end{figure}
-
-Figure \ref{fig:sexRatioMarriage} clearly illustrates the systematic recall error
-problem.
-The observed sex ratio is increasingly above the expected value the
-longer ago the parents were married.
-The increasingly unequal sex ratio with increasing marriage duration suggests that
-a solution to the recall error problem is to drop women who were married ``too far'' from 
-the survey year.
-The main problem is establishing what the best cut-off point should be.
-The observed sex ratio is consistently significantly higher than the natural sex ratio 
-from around 24 years of marriage, so one possibility is simply to drop all women married 
-more than 24 years at the time of the survey.
-But, as the Appendix shows, there are differences across the three surveys and between 
-parities.
-I therefore use different cut-off points by survey round.
-For NFHS-1 women married 22 years or more were dropped, with the corresponding cut-off 
-points 23 years for NFHS-2  and 26 years for NFHS-3.
-The final sample consists of 146,096 women, with 332,951 parity one through four births.%
-\footnote{
-The online Appendix presents the results for a more restrictive definition and for the
-women dropped because of recall error concerns.
-}
+As I argue in the online Appendix, recall error is heavily dependent on the duration
+between marriage and survey, and I therefore drop women married 22 years or more 
+for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
+and 26 years for NFHS-3.
+The final sample consists of 146,096 women, with 332,951 parity one through four births.
+
+% %
+% \footnote{
+% The online Appendix presents the results for a more restrictive definition and for the
+% women dropped because of recall error concerns.
+% }
 
@@
 
-Spell duration is measured in months.
-The first spell begins at the month of marriage because many 
-women report giving birth less than 9 months after they were married.
-For women who began living with their husbands at too young an age to conceive, the 
-starting point should ideally be first ovulation, when she becomes ``at risk'' for a 
-pregnancy, rather than month of marriage.
-Unfortunately, information on age of menarche is only available in NFHS-1.
-Instead, for women who began living with their husband before age 12, I set the 
-the month they turned 12 years of age as staring point for the first spell.
-
+Spell duration is measured in 
+As mentioned above, 10 to 20 percent of women gave birth less than 9 months
+after they were married.
+The first spell therefore begins at the month of marriage.
+The exception is for women married very young, where I use the month they 
+turned 12 rather than age of menarche, which is only available in NFHS-1.
 The second and subsequent spells begin 9 months after the previous birth 
@@
 the woman is sterilized;
-or the number of births observed becomes too sparse for the method to work.
+or too few births are observed for the method to work.
 The timing of censoring because of too few births vary slightly by spell but 
@@
 
+To examine how the use of sex selection has changed over time,
 I group spells into three time periods based on spell start date:
 1972--1984, 1985--1994, and 1995--2006.
-The first period covers the time before sex-selective abortions became widely available.
-Abortion was legalized in 1971 and amniocentesis was introduced
-in India in 1975, but the first newspaper reports on the availability of prenatal sex 
-determination were not until 1982--83 \citep{Sudha1999,bhat06,Grover2006}.
-The number of clinics quickly increased, and knowledge about sex selection became widespread
-after a senior government official's wife aborted a fetus that turned out to be male \citep[p.\ 598]{Sudha1999}.
-The second period covers the time from the widespread emergence of sex-selective abortions
-until the prenatal Diagnostic Techniques (PNDT) act was passed in 1994.
-The final period is from the PNDT act until the last available survey.
-The PNDT act made it a criminal offence to reveal the sex of the fetus and was
-followed by a campaign against the use of sex selection, although
-enforcement appears to be relatively lax.
-
-By dividing spells into these periods I can examine how the use of sex selection 
-has changed across the three different regimes.
+These years follow the important changes in availability and legality of 
+prenatal sex determination discussed in the Introduction.
 Note that the periods are based on the spells' beginning year, and some spells 
@@
 under the PDNT act.
-The overall effect is to bias downwards any differences between the periods.
+The effect is to bias downwards any differences between the periods.
 
@@
 The explanatory variables are divided into two groups.
-The first group consists of variables expected to affect the shape of the hazard function: 
+The first group consists of variables expected to affect the shape of the hazard function
+(the $\mathbf{Z}$ variables): 
 mother's education, sex composition of previous children, and area of residence.
-Increasing the number of variables interacted with the baseline hazard lowers the risk 
-of bias but requires more data to precisely estimate.
 I chose these variables because the prior literature shows that they affect 
-spacing choices and because the prior literature on sex selection indicates 
-that these are correlated with sex selection.
-The second group of variables are those expected to have an approximately 
-proportional effect on the hazard: age of the mother at the beginning of the spell, 
-length of her first spell (for second spell and above), whether the household owns 
-land, and whether the household belongs to a scheduled tribe or caste.
+spacing choices and are correlated with sex selection.
+Increasing the number of variables interacted with the baseline hazard would
+further lower the risk of bias but at the cost of requiring more data to 
+precisely estimate.
 
@@
 no education, 1 to 7 years of education, and 8 and more years of education.
-The models are estimated separately for each education level.%
+The models are estimated separately for each education level to reduce
+the potential problem of including other variables as proportional.%
 \footnote{
@@
 
-The sex composition of children, area of residence, and the interactions between
-these are all interacted with the piece-wise linear baseline hazard dummies.
-In other words, the baseline hazards are assumed to be different depending on
-where a woman lives and the sex composition of her previous children.
-As an example, for the second spell a separate regression is
-run for each education level and in each regression four different baseline hazards 
-are included (first child a boy in rural area, first child a boy in urban area,
-first child a girl in rural area, first child a girl in urban area).
-Although this approach substantially increases the number of regressions and 
-estimated parameters it reduces the potential problem of including other variables 
-as proportional effects.
-
-The remaining variables are expected to affect hazards proportionally.
-Although fecundity cannot be observed directly a suitable
-proxy is the duration from marriage until first birth.
+The second group of variables are those expected to have an approximately 
+proportional effect on the hazard: 
+length of her first spell (for second spell and above to capture fecundity), 
+age of the mother at the beginning of the spell, 
+whether the household owns land, 
+and whether the household belongs to a scheduled tribe or caste.
+Fecundity cannot be observed directly, but a suitable proxy is the 
+duration from marriage until first birth.
 Most Indian women do not use contraception before the first birth
-and there is pressure to show that a newly married woman can conceive 
-\citep{dyson83,Sethuraman2007,Dommaraju2009}.
-This is confirmed by the very short spells between marriage and first birth,
-even among the most educated.
+and there is pressure to show that a newly married woman can conceive,
+as confirmed below by the very short spells between marriage and first birth,
+even among the most educated \citep{dyson83,Sethuraman2007,Dommaraju2009}.
 Hence, a long spell between marriage and first birth is likely due to low fecundity.
-For both this variable and the age of the mother at the beginning of the spell 
+For this variable and the age of the mother at the beginning of the spell 
 the squares are also included.
@@
 falling fertility, and the longer spells from sex-selective abortions.
-The high number of censored observations underscore the importance of controlling for
-censoring when examining the relationship between fertility and sex selection.
-
-The descriptive statistics also provide a first indication of how the
+
+The descriptive statistics provide a first indication of how the
 sex ratio at birth changes over time and by spell.
 For the first spell the sex ratio is very close to the natural
-for all education groups and all three time periods.
-As an example, among the highly educated group for the 1995--2006 period,
-51.3 percent of the children born were boys.%
+for all education groups and all three time periods.%
 \footnote{
@@
 Correspondingly, in the first period just over twenty percent had 8 or more 
-years of education, but in the last period it was almost half.
+years of education, whereas in the last period it was almost half.
 Part of the increase in education is correlated with the increase in urbanization,

### 2017-12-10 paper/sexSelectionSpacingAppendix-ver1.tex
Removed commented out sections in Appendix
Add recall error section from paper to appendix

@@
 % \date{May 2010\\ \bigskip PRELIMINARY}
-\date{October 2017}
+\date{December 2017}
 
@@
 \appendix
-
-% \section{Recall Error}
 
@@
 
-% \section{Why Bundle Scan and Abortion?}
-% 
-% The easiest way to show why a bundled service makes sense is to model 
-% the provider's problem first and then show that both provider and
-% buyer will be better off if a bundled service is offered.
-% Take a provider with with cost, $c_a$, of providing an abortion,
-% and cost, $c_s$, of providing a scan.
-% These costs include expenses for equipment, labor,
-% and possibly a premium for getting caught and prosecuted. 
-% The provider can either charge separately for the two services,
-% in which case he will charge $p_s$ for the scan and $p_a$ for
-% the abortion, or he can charge $p_b$ for the bundle.
-% 
-% The provider's profit if he offers the two services separately, $\pi_{sep}$,
-% to $n$ buyers, who conceive girls with the probability $p(g)$, will be
-% \begin{equation}
-% \pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
-% \end{equation}
-% The first part is profit from the customers who want a scan
-% and the second part is the profit from the fraction of the
-% original customers who conceived a girl.
-% If the provider instead offered the same $n$ buyers a bundle service
-% the profit, $\pi_{bun}$, would be
-% \begin{equation}
-% \pi_{bun} = n p_b - n c_s - p(g) n c_a,
-% \end{equation}
-% since all customers pays $p_b$, all customers get a scan 
-% at cost $c_s$, and the fraction $p(g)$ who conceived a girl
-% would receive an abortion at cost $c_a$.
-% A profit maximizing provider then picks bundled pricing if 
-% $\pi_{bun} > \pi_{sep}$, or
-% \begin{equation}
-%  p_b > p_s + p(g) p_a.
-% \end{equation}
-% 
-% Assume that buyers are risk averse and that the only motivation
-% for getting a prenatal sex determination test is to abort 
-% female fetuses and that parents will abort the fetus if the test 
-% show a female fetus (I will relax the last assumptions below).
-% Furthermore, to ease exposition assume that buyers can only
-% spend money on two things: consumption $c$ and prenatal sex
-% determinations/abortions.
-% For a buyer facing separate services the expected utility
-% is then
-% \begin{equation}
-% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
-% \end{equation}
-% where the first part is the utility if the fetus is a boy
-% and the buyers therefore only spend on the scan, which
-% happens with probability $1-p(g)$, and the
-% second part is the utility if the fetus is a female
-% and they therefore also has to pay for the abortion,
-% which happens with probability $p(g)$.
-% For a buyer facing a bundled service the utility is simply
-% \begin{equation}
-% U = U(c-p_b).
-% \end{equation}
-% 
-% If follows from the standard assumptions about utility functions
-% and the risk aversion assumption that
-% \begin{equation}
-% U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
-% \end{equation}
-% In other words risk averse buyers prefer a sure thing---where they pay 
-% upfront---over the gamble that they either have a boy and pay only for the
-% scanning or have a girl and pay for both the scan and the abortion.
-% In fact, risk aversion implies that they are willing to pay 
-% \emph{more} than the expected cost.
-% In other words,
-% \begin{equation}
-% U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
-% \end{equation}
-% where $\delta$ is a positive number that depends on the
-% degree of risk aversion (the more risk averse the larger
-% $\delta$ is).
-% 
-% The provider realizes that buyers are risk averse
-% and therefore offer a bundle where the price is in 
-% the range
-% \begin{equation}
-% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
-% \end{equation}
-% Hence, the optimal pricing scheme for both provider
-% and buyer is bundled pricing, where you pay a flat fee
-% and get the pre-natal sex determination and an abortion
-% if needed.
-% % Where the provider ends up in the possible range of
-% % prices depends on the nature of the provider market.
-% 
-% I implicitly assumed that the provider is risk-neutral.
-% The same result hold, however, if the provider
-% is risk-averse as long as there are enough potential clients.
-% In that case, the law of large numbers will ensure that 
-% the risk-neutral and risk-averse choices are the same
-% for the provider---essentially there is no gamble if you see 
-% enough clients, $p(g)$ of them will present with a female fetus 
-% and $1-p(g)$ with a male fetus.
-% In fact, it is possible for the provider to be \emph{more}
-% risk averse than the buyers and still prefer the bundled 
-% pricing scheme.
-% 
-% Now imagine a situation where there there is some 
-% uncertainty about whether a buyer will go through with
-% the abortion after the prenatal sex determination.
-% This can be represented by the probability $\rho$ that
-% a buyer who had a prenatal sex determination test that
-% showed a female fetus will go through with the abortion.
-% If parents know that there is probability $1-\rho$ that they
-% will not go through with the abortion their utility is
-% \begin{equation}
-% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
-% \end{equation}
-% where I have made the assumption that they
-% are equally happy with a boy or a girl if they
-% are in the $1-\rho$ portion of the population that
-% have a prenatal sex determination which show a female
-% fetus but do not go through with the abortion (obviously
-% this cannot be the case because if they were there
-% would be no point in having the prenatal sex determination,
-% but if I can show that the bundle price arise here it
-% would trivially hold if there were some lower utility
-% associated with having a girl than a boy).
-% 
-% Because the buyers are still risk averse they would continue
-% to prefer the ``sure'' thing over the gamble
-% \begin{equation}
-% U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
-% \end{equation}
-% The provider still offers a bundle, but the price is now 
-% in  the range
-% \begin{equation}
-% p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
-% \end{equation}
-% where $\delta$ still depends on the degree of risk aversion.
-% 
-% If parents on the other hand initially believe that they will always
-% go through with the abortion if the fetus is female but
-% still have probability $1-\rho$ that they will not, they would
-% be back to the original comparison of the utility.
-% \begin{equation}
-% U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
-% \end{equation}
-% All that would do is \emph{increase} the profit for the
-% provider because the law of large numbers would tell them
-% exactly how many would not go through with the abortion.
-% In other words, they would offer the original
-% bundled price because the buyers did not know that they
-% will change their mind
-% \begin{equation}
-% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
-% \end{equation}
-% but the provider will have profit of
-% \begin{equation}
-% p_b - c_s - \rho c_a,
-% \end{equation}
-% which is strictly larger than the profit in either of
-% the other cases.
-% Also, they do not need to know which buyers are more
-% or less likely to use abortion, just that some
-% fraction will not use their purchased abortion.
-% 
-% \clearpage
-% \newpage
-%
-
-% \section{Simulation Results for 20 Periods}
-% 
-% \begin{table}[!htp]
-% \centering
-% \footnotesize
-% \begin{threeparttable}
-% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_fertility_100}
-% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-% \toprule
-%                & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-% \midrule
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
-%  k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
-%  k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
-%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
-%  k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
-%  k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
-%  k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
-%  k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
-%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
-%  k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
-%  k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
-%  k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
-%  k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
-%  k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
-%  k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
-%  k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
-%  k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
-%  k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \scriptsize
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% 
-% \begin{table}[!htp]
-% \centering
-% \footnotesize
-% \begin{threeparttable}
-% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_fertility_95}
-% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-% \toprule
-%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
-%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-% \midrule
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
-%  k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
-%  k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
-%  k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
-%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
-%  k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
-%  k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
-%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
-%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &  7.09 &  56.9 &  7.19 &  52.4 &  7.30 &  50.5 &  7.33 &  50.1 &  7.34 &  50.0 \\
-%  k = 14        &  5.05 &  63.7 &  5.05 &  56.4 &  5.10 &  53.6 &  5.21 &  51.0 &  5.26 &  50.0 \\
-%  k = 16        &  4.06 &  69.1 &  4.06 &  59.2 &  4.06 &  58.8 &  4.06 &  55.3 &  4.16 &  49.9 \\
-%  k = 18        &  3.13 &  70.0 &  3.13 &  69.7 &  3.13 &  64.9 &  3.13 &  56.0 &  3.32 &  50.0 \\
-%  k = 20        &  2.50 &  65.1 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  7.07 &  67.6 &  7.08 &  60.9 &  7.13 &  54.8 &  7.26 &  51.4 &  7.34 &  50.0 \\
-%  k = 14        &  5.05 &  78.3 &  5.05 &  67.8 &  5.05 &  62.7 &  5.06 &  56.7 &  5.27 &  50.0 \\
-%  k = 16        &  4.06 &  76.0 &  4.06 &  75.4 &  4.06 &  69.7 &  4.06 &  63.3 &  4.17 &  49.9 \\
-%  k = 18        &  3.13 &  70.1 &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.32 &  50.0 \\
-%  k = 20        &  2.75 &  72.7 &  2.74 &  72.6 &  2.64 &  71.6 &  2.00 &  62.5 &  2.38 &  50.0 \\
-%  k = 22        &  2.00 &  99.1 &  2.00 &  71.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \scriptsize
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% \begin{table}[!htp]
-% \centering
-% \footnotesize
-% \begin{threeparttable}
-% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_fertility_90}
-% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-% \toprule
-%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
-%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-% \midrule
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
-%  k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
-%  k = 16        &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
-%  k = 18        &  3.25 &  51.9 &  3.25 &  51.4 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
-%  k = 20        &  2.50 &  55.1 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
-%  k = 22        &  2.01 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
-%  k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
-%  k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 \\
-%  k = 18        &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
-%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.24 &  55.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &  7.30 &  50.5 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
-%  k = 14        &  5.24 &  52.3 &  5.24 &  50.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
-%  k = 16        &  4.06 &  58.8 &  4.07 &  51.5 &  4.13 &  50.7 &  4.16 &  50.1 &  4.16 &  49.9 \\
-%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 \\
-%  k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.63 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  7.12 &  53.6 &  7.31 &  50.3 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
-%  k = 14        &  5.05 &  63.2 &  5.21 &  52.6 &  5.24 &  50.3 &  5.26 &  50.0 &  5.27 &  50.0 \\
-%  k = 16        &  4.06 &  61.5 &  4.06 &  59.0 &  4.07 &  51.5 &  4.13 &  50.7 &  4.17 &  49.9 \\
-%  k = 18        &  3.13 &  70.0 &  3.13 &  68.3 &  3.13 &  54.0 &  3.16 &  53.5 &  3.32 &  50.0 \\
-%  k = 20        &  2.43 &  69.2 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  55.6 &  2.38 &  50.0 \\
-%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \scriptsize
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% \begin{table}[!htp]
-% \centering
-% \footnotesize
-% \begin{threeparttable}
-% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_fertility_85}
-% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
-% \toprule
-%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
-%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
-% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
-%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
-% \midrule
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 \\
-%  k = 14        &  5.42 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
-%  k = 16        &  4.16 &  50.7 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
-%  k = 18        &  3.25 &  51.9 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 \\
-%  k = 20        &  2.50 &  54.9 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
-%  k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 \\
-%  k = 14        &  5.40 &  50.2 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 \\
-%  k = 16        &  4.15 &  50.7 &  4.16 &  50.6 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
-%  k = 18        &  3.14 &  53.8 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 &  3.31 &  50.1 \\
-%  k = 20        &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  52.5 &  2.50 &  50.0 &  2.50 &  50.0 \\
-%  k = 22        &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &  7.33 &  50.1 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
-%  k = 14        &  5.23 &  51.3 &  5.25 &  50.2 &  5.25 &  50.0 &  5.25 &  50.0 &  5.25 &  50.0 \\
-%  k = 16        &  4.06 &  52.3 &  4.12 &  50.7 &  4.14 &  50.5 &  4.15 &  50.0 &  4.15 &  50.0 \\
-%  k = 18        &  3.12 &  54.0 &  3.13 &  53.9 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 \\
-%  k = 20        &  2.25 &  61.0 &  2.31 &  59.4 &  2.50 &  54.9 &  2.51 &  54.3 &  2.62 &  50.0 \\
-%  k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.12 &  58.0 &  2.25 &  50.0 \\
-%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  7.30 &  50.7 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
-%  k = 14        &  5.06 &  55.0 &  5.23 &  50.6 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
-%  k = 16        &  4.06 &  58.9 &  4.06 &  55.2 &  4.10 &  51.1 &  4.16 &  50.2 &  4.17 &  50.0 \\
-%  k = 18        &  3.12 &  69.7 &  3.13 &  57.1 &  3.13 &  53.9 &  3.25 &  51.8 &  3.31 &  50.1 \\
-%  k = 20        &  2.00 &  62.4 &  2.00 &  62.4 &  2.01 &  62.1 &  2.25 &  55.4 &  2.37 &  50.0 \\
-%  k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.25 &  50.0 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \scriptsize
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a]Percent boys is the percent boys of all births.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% 
-% \begin{table}[!htp]
-% \centering
-% \scriptsize
-% \begin{threeparttable}
-% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_abortion_100}
-% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-% \toprule
-%                & \multicolumn{12}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
-%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-% \midrule
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &    6.0 &    0.1 &   22.3 &    1.4 &    0.0 &   28.2 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
-%  k = 14        &   21.6 &    0.2 &   12.3 &    5.6 &    0.1 &   23.2 &    3.2 &    0.0 &    4.8 &    3.0 &    0.0 &   15.0 \\
-%  k = 16        &   12.7 &    0.1 &    0.2 &   12.6 &    0.1 &    1.0 &   12.2 &    0.1 &    6.4 &    9.5 &    0.2 &   40.1 \\
-%  k = 18        &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   25.1 &    0.3 &    1.8 &   23.7 &    0.3 &   12.0 \\
-%  k = 20        &   49.6 &    0.5 &    3.2 &   37.8 &    0.6 &   40.1 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   50.1 &    0.5 &    0.4 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &   47.0 &    0.6 &   21.7 &   18.1 &    0.3 &   37.6 &    6.5 &    0.1 &   47.3 &    1.3 &    0.0 &   29.1 \\
-%  k = 14        &   56.5 &    0.9 &   36.7 &   41.9 &    0.5 &    7.6 &   31.2 &    0.5 &   34.0 &   10.8 &    0.1 &   25.1 \\
-%  k = 16        &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.0 &   56.4 &    0.7 &   19.4 &   22.1 &    0.3 &   22.7 \\
-%  k = 18        &  119.3 &    1.2 &    4.1 &   47.3 &    0.5 &   11.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 \\
-%  k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.2 &   50.2 &    0.5 &    0.9 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &  165.3 &    2.1 &   22.6 &  102.2 &    1.4 &   27.9 &   61.3 &    0.9 &   32.2 &   29.3 &    0.5 &   40.6 \\
-%  k = 14        &  158.7 &    1.6 &    1.0 &  135.6 &    1.4 &    4.8 &  108.0 &    1.3 &   15.4 &   64.1 &    0.8 &   19.1 \\
-%  k = 16        &  204.5 &    2.1 &    3.2 &  175.9 &    1.9 &   10.7 &  109.5 &    1.3 &   15.8 &   84.6 &    0.9 &    8.6 \\
-%  k = 18        &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 &  119.4 &    1.2 &    4.0 \\
-%  k = 20        &  123.9 &    1.2 &    0.0 &  107.0 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  319.6 &    3.8 &   15.6 &  256.2 &    3.3 &   21.9 &  188.1 &    2.5 &   26.3 &  131.1 &    1.6 &   17.7 \\
-%  k = 14        &  331.2 &    3.4 &    1.5 &  277.3 &    2.9 &    5.4 &  230.2 &    2.6 &   10.7 &  179.1 &    2.0 &   13.1 \\
-%  k = 16        &  213.6 &    2.1 &    0.2 &  212.2 &    2.1 &    0.7 &  208.2 &    2.1 &    2.0 &  190.3 &    2.0 &    6.6 \\
-%  k = 18        &  191.3 &    1.9 &    0.0 &  126.0 &    1.2 &    0.1 &  125.9 &    1.2 &    0.2 &  125.4 &    1.2 &    0.5 \\
-%  k = 20        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  122.3 &    1.2 &    0.0 \\
-%  k = 22        &  200.3 &    2.0 &    0.3 &  197.2 &    2.0 &    1.5 &  181.2 &    1.9 &    7.3 &   97.1 &    1.0 &    6.1 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \tiny
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a] Average number of spells per woman where scan has been used at least once.
-% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
-% of pregnancy without prenatal scan.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% 
-% \begin{table}[!htp]
-% \centering
-% \scriptsize
-% \begin{threeparttable}
-% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_abortion_95}
-% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-% \toprule
-%                & \multicolumn{12}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
-%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-% \midrule
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &    0.9 &    0.0 &    8.3 &    0.4 &    0.0 &    7.7 &    0.2 &    0.0 &   48.2 &    0.0 &    0.0 &      . \\
-%  k = 14        &    3.3 &    0.0 &    0.8 &    3.2 &    0.0 &    7.2 &    1.6 &    0.0 &    7.4 &    0.8 &    0.0 &   50.3 \\
-%  k = 16        &   12.6 &    0.1 &    1.0 &    9.6 &    0.2 &   39.9 &    6.3 &    0.1 &    1.9 &    6.0 &    0.1 &    7.0 \\
-%  k = 18        &   25.3 &    0.3 &    0.3 &   23.7 &    0.3 &   11.8 &   12.6 &    0.1 &    0.5 &   12.2 &    0.1 &    3.5 \\
-%  k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.2 &   24.9 &    0.3 &    1.8 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.9 &    0.5 &    0.9 &   44.0 &    0.5 &   12.6 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &   12.3 &    0.2 &   21.2 &    4.3 &    0.1 &   42.6 &    0.6 &    0.0 &   49.1 &    0.2 &    0.0 &   48.2 \\
-%  k = 14        &   40.5 &    0.5 &   11.8 &   18.8 &    0.2 &   20.7 &    4.8 &    0.1 &   41.2 &    2.8 &    0.0 &   24.3 \\
-%  k = 16        &   73.7 &    0.7 &    2.4 &   22.2 &    0.3 &   22.4 &   12.6 &    0.1 &    1.8 &   11.0 &    0.1 &   22.4 \\
-%  k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.5 &   24.9 &    0.3 &    3.3 \\
-%  k = 20        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.2 &   48.8 &    0.5 &    6.1 &   25.3 &    0.3 &    0.1 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &   98.2 &    1.3 &   23.7 &   34.6 &    0.5 &   32.0 &    8.0 &    0.1 &   39.3 &    1.3 &    0.0 &   29.1 \\
-%  k = 14        &  139.2 &    1.4 &    3.3 &   65.2 &    0.8 &   19.4 &   36.8 &    0.5 &   20.7 &   10.8 &    0.1 &   25.1 \\
-%  k = 16        &  156.3 &    1.9 &   17.6 &   75.2 &    0.8 &    0.8 &   72.1 &    0.7 &    4.1 &   43.4 &    0.6 &   32.5 \\
-%  k = 18        &  125.7 &    1.2 &    0.3 &  123.9 &    1.2 &    1.4 &   93.6 &    1.1 &   18.2 &   37.7 &    0.6 &   40.2 \\
-%  k = 20        &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.3 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  248.9 &    2.8 &   10.0 &  155.2 &    2.0 &   24.1 &   69.0 &    0.8 &   19.1 &   21.0 &    0.3 &   26.7 \\
-%  k = 14        &  285.7 &    3.0 &    4.5 &  180.6 &    2.2 &   18.4 &  129.1 &    1.4 &    7.6 &   68.2 &    0.8 &   12.8 \\
-%  k = 16        &  213.0 &    2.1 &    0.4 &  208.3 &    2.1 &    2.0 &  161.3 &    1.8 &   12.1 &  108.9 &    1.3 &   16.2 \\
-%  k = 18        &  126.0 &    1.2 &    0.0 &  126.0 &    1.2 &    0.1 &  125.4 &    1.2 &    0.5 &  123.9 &    1.2 &    1.3 \\
-%  k = 20        &  125.9 &    1.2 &    0.0 &  124.9 &    1.2 &    0.0 &  114.9 &    1.1 &    0.0 &   50.4 &    0.5 &    0.0 \\
-%  k = 22        &  197.1 &    2.0 &    1.6 &   87.6 &    1.1 &   22.2 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \tiny
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a] Average number of spells per woman where scan has been used at least once.
-% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
-% of pregnancy without prenatal scan.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% \begin{table}[!htp]
-% \centering
-% \scriptsize
-% \begin{threeparttable}
-% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_abortion_90}
-% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-% \toprule
-%                & \multicolumn{12}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
-%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-% \midrule
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &    0.4 &    0.0 &    5.0 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 14        &    3.2 &    0.0 &    4.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 16        &    6.4 &    0.1 &    0.2 &    6.4 &    0.1 &    1.0 &    2.4 &    0.0 &   25.8 &    0.0 &    0.0 &      . \\
-%  k = 18        &   19.1 &    0.3 &   40.4 &   12.7 &    0.1 &    0.3 &   11.8 &    0.1 &    6.4 &    0.0 &    0.0 &      . \\
-%  k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.2 &   22.0 &    0.3 &   12.5 &    0.0 &    0.0 &      . \\
-%  k = 22        &   50.4 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &    4.4 &    0.1 &   41.3 &    0.4 &    0.0 &    7.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 14        &   21.6 &    0.2 &   12.3 &    3.2 &    0.0 &    4.4 &    1.6 &    0.0 &    7.4 &    0.0 &    0.0 &      . \\
-%  k = 16        &   12.7 &    0.1 &    0.2 &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.0 &    5.2 &    0.1 &   28.9 \\
-%  k = 18        &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.9 &   12.7 &    0.1 &    0.3 &   12.5 &    0.1 &    1.7 \\
-%  k = 20        &   50.3 &    0.5 &    0.2 &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   25.1 &    0.3 &    0.8 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   49.5 &    0.5 &    1.6 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &   33.0 &    0.4 &   22.5 &    4.8 &    0.1 &   47.7 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . \\
-%  k = 14        &   43.9 &    0.4 &    1.7 &   26.1 &    0.3 &   11.2 &    4.8 &    0.1 &   41.2 &    1.6 &    0.0 &    7.4 \\
-%  k = 16        &   75.6 &    0.8 &    0.4 &   69.2 &    0.7 &    7.0 &   12.6 &    0.1 &    1.8 &    6.4 &    0.1 &    1.0 \\
-%  k = 18        &  124.8 &    1.2 &    0.9 &   25.3 &    0.3 &    0.1 &   25.3 &    0.3 &    0.3 &   24.9 &    0.3 &    3.3 \\
-%  k = 20        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   50.3 &    0.5 &    0.4 &   37.7 &    0.6 &   40.1 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &  139.8 &    1.5 &    7.8 &   44.0 &    0.5 &   19.3 &    5.4 &    0.1 &   36.8 &    0.2 &    0.0 &   48.2 \\
-%  k = 14        &  144.2 &    1.4 &    0.7 &  120.3 &    1.3 &   11.4 &   39.1 &    0.5 &   14.0 &    5.9 &    0.1 &   14.2 \\
-%  k = 16        &  210.7 &    2.1 &    1.2 &  116.1 &    1.3 &   11.2 &   73.7 &    0.7 &    2.2 &   24.5 &    0.3 &    6.7 \\
-%  k = 18        &  126.0 &    1.2 &    0.0 &  125.7 &    1.2 &    0.3 &  119.4 &    1.2 &    4.0 &   44.1 &    0.6 &   22.6 \\
-%  k = 20        &  125.4 &    1.2 &    0.0 &   75.5 &    0.7 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \tiny
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a] Average number of spells per woman where scan has been used at least once.
-% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
-% of pregnancy without prenatal scan.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% \begin{table}[!htp]
-% \centering
-% \scriptsize
-% \begin{threeparttable}
-% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
-% \label{tab:simul_abortion_85}
-% \begin{tabular}{@{} c D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} D{.}{.}{3.1} D{.}{.}{1.1} D{.}{.}{1.1} @{}}
-% \toprule
-%                & \multicolumn{12}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
-%                & \multicolumn{12}{c}{Cost of Prenatal Sex Determination ($ p_s $)}                         \\ 
-%                & \multicolumn{3}{c}{12}    & \multicolumn{3}{c}{16}    & \multicolumn{3}{c}{20}    & \multicolumn{3}{c}{24}    \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10} \cmidrule(lr){11-13}
-%                                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       & \mco{Abortions}  & \mco{Average}           &                       \\
-% \multirow{2}{9mm}{Cost of\\children}  & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         & \mco{per 100}    & \mco{Spells}            & \mco{Percent}         \\
-%                                       & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} & \mco{Women}      & \mco{w.\ Scan\tnote{a}} & \mco{Change\tnote{b}} \\
-% \midrule
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
-%  k = 12        &    0.2 &    0.0 &   16.0 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 14        &    1.7 &    0.0 &    2.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 16        &    6.4 &    0.1 &    0.7 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 18        &   12.7 &    0.1 &    0.2 &    9.4 &    0.1 &   24.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 20        &   25.3 &    0.3 &    0.1 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 22        &   49.3 &    0.5 &    3.2 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
-%  k = 12        &    0.4 &    0.0 &    5.8 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 14        &    3.3 &    0.0 &    2.0 &    1.6 &    0.0 &    3.7 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 16        &   12.3 &    0.1 &    6.2 &    6.4 &    0.1 &    1.3 &    1.6 &    0.0 &   51.2 &    0.0 &    0.0 &      . \\
-%  k = 18        &   25.3 &    0.3 &    0.5 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 &    0.0 &    0.0 &      . \\
-%  k = 20        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.1 &   24.9 &    0.3 &    1.8 &    0.0 &    0.0 &      . \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.3 &    0.5 &    0.1 &   24.4 &    0.2 &    0.0 &    0.0 &    0.0 &      . \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
-%  k = 12        &    7.0 &    0.1 &   13.3 &    0.4 &    0.0 &   13.6 &    0.0 &    0.0 &      . &    0.0 &    0.0 &      . \\
-%  k = 14        &   24.8 &    0.3 &    2.3 &    3.2 &    0.0 &    4.0 &    1.5 &    0.0 &   13.2 &    0.0 &    0.0 &      . \\
-%  k = 16        &   72.0 &    0.7 &    4.3 &   12.5 &    0.1 &    3.5 &    6.3 &    0.1 &    2.4 &    1.6 &    0.0 &   51.2 \\
-%  k = 18        &   25.3 &    0.3 &    0.0 &   25.3 &    0.3 &    0.3 &   12.7 &    0.1 &    0.2 &   12.2 &    0.1 &    3.5 \\
-%  k = 20        &   50.4 &    0.5 &    0.0 &   50.2 &    0.5 &    0.9 &   25.3 &    0.3 &    0.1 &   25.2 &    0.3 &    0.5 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   49.8 &    0.5 &    1.8 \\
-%                &  \multicolumn{12}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
-%  k = 12        &   52.3 &    0.6 &   14.5 &    4.4 &    0.1 &   41.3 &    0.1 &    0.0 &   55.7 &    0.0 &    0.0 &      . \\
-%  k = 14        &  134.3 &    1.4 &    7.0 &   27.3 &    0.3 &    6.2 &    3.1 &    0.0 &   14.2 &    0.8 &    0.0 &   50.3 \\
-%  k = 16        &   94.6 &    1.1 &   12.0 &   73.8 &    0.7 &    2.2 &   12.6 &    0.1 &    1.8 &    6.2 &    0.1 &    4.3 \\
-%  k = 18        &  126.0 &    1.2 &    0.1 &  114.7 &    1.2 &    6.8 &   25.3 &    0.3 &    0.2 &   22.2 &    0.3 &   22.4 \\
-%  k = 20        &   94.4 &    0.9 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.1 &   25.3 &    0.3 &    0.1 \\
-%  k = 22        &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 &   50.4 &    0.5 &    0.0 \\
-% \bottomrule
-% \end{tabular}
-% \begin{tablenotes} \tiny
-% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
-%  and a probability of a son of 0.5.
-% \item[a] Average number of spells per woman where scan has been used at least once.
-% \item[b] Percent of spells where prenatal scan was initially used but birth is the result
-% of pregnancy without prenatal scan.
-% \end{tablenotes}
-% \end{threeparttable}
-% \normalsize
-% \end{table}
-% 
-% 
-% \clearpage
-% \newpage
-%
+\section{[Recall error paragraphs from paper]}
+
+Observed sex ratios by cohort provide a straightforward way to determine 
+whether recall error is a problem.
+Because prenatal sex determination techniques did not become widely available until the 
+mid-1980s, a higher than natural sex ratio for cohorts born before that time must be 
+the result of systematic recall error.
+As shown in the online Appendix, the observed sex ratio by parity becomes more male 
+dominated the further back births took place.
+In addition, births in the same cohort tend to be more male dominated the more recent the 
+survey (births in the cohort took place longer ago relative to the survey).
+Hence, there is evidence of recall error and the degree of recall error increases
+with length of time between survey and cohort.
+
+Using cohort year of birth to analyze recall error and decide which observations
+to keep is, however, problematic because the year of birth for a given parity is affected 
+by recall error; for example, a second born child listed as first born will be 
+born later than the real first born child.
+Year of marriage should, however, be unaffected by recall error.
+Using year of marriage the basic recall error pattern remains with women married longer 
+ago more likely to report that their child was a boy for a given parity.
+Similarly, comparing women married in the same period across surveys shows
+that women married longer ago are more likely to report having sons.
+
+That recall error increases the longer ago somebody was married means
+that duration of marriage is a better predictor of recall error than calendar year of 
+marriage.
+Figure \ref{fig:sexRatioMarriage} shows the observed sex ratio for children 
+reported as first born as a function of duration of marriage combining all three surveys.%
+\footnote{
+The graph for second births shows a similar pattern.
+The graphs for the second births and the individual survey rounds are available upon request.
+}
+The solid line is the sex ratio of children reported 
+as first born by the number of years between the survey and marriage, 
+the dashed lines indicate the 95 percent confidence interval 
+and the horizontal line the natural sex ratio (approximately 0.512).
+To ensure sufficient cell sizes the years are grouped in twos.
+
+\begin{figure}[htp]%
+\centering
+\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
+\caption{Ratio of boys in ``first'' births}
+\label{fig:sexRatioMarriage}
+\end{figure}
+
+Figure \ref{fig:sexRatioMarriage} clearly illustrates the systematic recall error
+problem.
+The observed sex ratio is increasingly above the expected value the
+longer ago the parents were married.
+The increasingly unequal sex ratio with increasing marriage duration suggests that
+a solution to the recall error problem is to drop women who were married ``too far'' from 
+the survey year.
+The main problem is establishing what the best cut-off point should be.
+The observed sex ratio is consistently significantly higher than the natural sex ratio 
+from around 24 years of marriage, so one possibility is simply to drop all women married 
+more than 24 years at the time of the survey.
+But, as the Appendix shows, there are differences across the three surveys and between 
+parities.
+I therefore use different cut-off points by survey round.
+For NFHS-1 women married 22 years or more were dropped, with the corresponding cut-off 
+points 23 years for NFHS-2  and 26 years for NFHS-3.
+The final sample consists of 146,096 women, with 332,951 parity one through four births.
 
@@
 
-% 
-% \section{Graphs using Women Married less than 19 Years}
-% 
-% \setcounter{figure}{0}
-% \setcounter{table}{0}
-% 
-% 
-% % Figures \ref{fig:results_spell2_low_urban} to \ref{fig:results_spell4_low_rural_cont}
-% % show the results for the group of women with no education.
-% % The starting ages are 18, 21 and 23 for the second, third and fourth spells,
-% % respectively.
-% 
-% % The results for women with one to seven years of education are presented
-% % in Figures \ref{fig:results_spell2_med_urban} to \ref{fig:results_spell4_med_rural_cont}.
-% % Again a representative woman is used with the first spell length set to
-% % 16 months and the ages at the beginning of the spell 19, 21 and 24
-% % for the second, third and fourth spells, respectively.
-% 
-% 
-% % [FIRST SPELL]
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=2,529)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_urban_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_urban_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}} 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=3,831)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_urban_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_urban_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=1,762)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_urban_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_urban_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=16,293)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_low_rural_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=21,631)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_low_rural_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=7,922)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_low_rural_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with no education by quarter (3 month
-% period). 
-% Predictions based on age 16 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell1_low}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=2,022)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_urban_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_urban_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}} 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=3,653)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_urban_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_urban_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=2,302)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_urban_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_urban_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=4,575)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_med_rural_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=8,356)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_med_rural_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=5,208)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_med_rural_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-% period). 
-% Predictions based on age 17 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell1_med}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=4,408)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_urban_pc}}\\
-% \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_urban_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}} 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=10,118)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_urban_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_urban_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=9,116)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_urban_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_urban_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=2,668)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g1_high_rural_s}} 
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=7,585)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g2_high_rural_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=7,504)]{
-% \begin{minipage}{0.31\textwidth}
-% \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-% \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_rural_pc}}\\
-% \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell1_g3_high_rural_s}}
-% \captionsetup[subfigure]{labelformat=parens}
-% \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with 8 or more years of education by quarter
-% (3 month period). 
-% Predictions based on age 20 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell1_high}
-% \end{figure}
-% 
-% \clearpage
-% 
-% \subsection{Second Spell}
-% 
-% 
-% % SPELL 2 - URBAN - LOW
-% \begin{figure}[hp]
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972-1984 (N=861)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985-1994 (N=1,763)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[1995-2006 (N=946)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972-1984 (N=951)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985-1994 (N=1,929)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995-2006 (N=921)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with no education by month beginning 9 months after prior birth. 
-% Predictions based on age 18 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell2_low_urban}
-% \end{figure}
-% 
-% 
-% % SPELL 2 - rural - LOW
-% \begin{figure}
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972-1984 (N=5,103)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985-1994 (N=9,913)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[1995-2006 (N=3,653)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972-1984 (N=5,500)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_low_rural_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985-1994 (N=10,437)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_low_rural_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995-2006 (N=3,834)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_low_rural_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for rural 
-% women with no education by month beginning 9 months after prior birth. 
-% Predictions based on age 18 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell2_low_rural}
-% \end{figure}
-% 
-% 
-% % SPELL 2 - URBAN - MEDIUM
-% \begin{figure}
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972-1984 (N=714)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985-1994 (N=1,578)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[1995-2006 (N=1,074)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972-1984 (N=791)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985-1994 (N=1,766)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995-2006 (N=1,096)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 19 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell2_med_urban}
-% \end{figure}
-% 
-% 
-% % SPELL 2 - rural - MEDIUM
-% \begin{figure}
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972-1984 (N=1,464)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985-1994 (N=3,510)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[1995-2006 (N=2,151)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972-1984 (N=1,645)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_med_rural_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985-1994 (N=3,671)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_med_rural_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995-2006 (N=2,182)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_med_rural_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for rural 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 19 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell2_med_rural}
-% \end{figure}
-% 
-% % High education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=1,576)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=4,105)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_g_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_g_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=3,762)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_g_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_g_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=1,667)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=4,431)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=3,953)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 22 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell2_high_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=847)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=2,788)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_g_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_g_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=2,816)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_g_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_g_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=925)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g1_high_rural_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=3,033)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g2_high_rural_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=3,039)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell2_g3_high_rural_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for rural
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 22 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell2_high_rural}
-% \end{figure}
-% 
-% \clearpage
-% \subsection{Third Spell}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First two children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=252)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=690)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=458)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First two children one boy and one girl}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=564)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=1,497)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=915)]{
-%     \begin{minipage}{0.26\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with no of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell3_low_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \ContinuedFloat
-% \caption*{First two children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=293)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_urban_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=783)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_urban_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=410)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_urban_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% % \label{fig:results_limit_spell3_low_urban}
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with no of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First two children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=1,417)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=4,060)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=1,827)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First two children one boy and one girl}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=2,803)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=8,265)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=3,661)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with no of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell3_low_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \ContinuedFloat
-% \centering
-% \caption*{First two children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=1,613)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_low_rural_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=4,200)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_low_rural_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=1,786)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_low_rural_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with no of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% % \label{fig:results_limit_spell3_low_rural}
-% \end{figure}
-% 
-% 
-% 
-% % Medium education
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First two children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=223)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=577)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=409)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First two children one boy and one girl}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=433)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=1,188)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=804)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell3_med_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \ContinuedFloat
-% \caption*{First two children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=229)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_urban_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=594)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_urban_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=423)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_urban_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% % \label{fig:results_limit_spell3_med_urban}
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First two children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=395)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=1,264)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=840)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First two children one boy and one girl}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=829)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=2,549)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=1,737)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell3_med_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \ContinuedFloat
-% \centering
-% \caption*{First two children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=419)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_med_rural_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=1,216)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_med_rural_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=716)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_med_rural_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% % \label{fig:results_limit_spell3_med_rural}
-% \end{figure}
-% 
-% 
-% % High education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First two children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=390)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=1,196)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=981)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First two children one boy and one girl}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=778)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=2,543)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=2,309)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell3_high_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \ContinuedFloat
-% \caption*{First two children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=442)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_urban_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=1,230)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_urban_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=1,068)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_urban_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% % \label{fig:results_limit_spell3_high_urban}
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First two children girls}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=200)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=798)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=857)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_gg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_gg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First two children one boy and one girl}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=412)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=1,646)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=1,805)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bg_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_limit_spell3_high_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \ContinuedFloat
-% \centering
-% \caption*{First two children boys}
-% \setcounter{subfigure}{4}
-% \subfloat[1972--1984 (N=209)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g1_high_rural_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{5}
-% \subfloat[1985--1994 (N=767)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g2_high_rural_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[1995--2006 (N=782)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{limit_spell3_g3_high_rural_bb_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{(Continued) Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% % \label{fig:results_limit_spell3_high_rural}
-% \end{figure}
-% 
-% 
-% 
-% \clearpage
-% 
-% 
-% \section{Graphs using Women Dropped Because of Recall Error}
-% 
-% \setcounter{figure}{0}
-% \setcounter{table}{0}
-% 
-% 
-% % [FIRST SPELL]
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1950--1980}
-% \setcounter{subfigure}{-2}
-% \subfloat[Urban (N=3,775)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_urban_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_urban_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[Rural (N=19,635)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_rural_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_low_rural_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with no education by quarter (3 month
-% period). 
-% Predictions based on age 16 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell1_low}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1954--1980 }
-% \setcounter{subfigure}{-2}
-% \subfloat[Urban (N=2,864)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_urban_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_urban_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[Rural (N=4,885)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_rural_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_med_rural_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with 1 to 7 years of education by quarter (3 month
-% period). 
-% Predictions based on age 17 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell1_med}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1955--1980}
-% \setcounter{subfigure}{-2}
-% \subfloat[Urban (N=3,157)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_urban_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_urban_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[Rural (N=1,491)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_rural_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell1_g1_high_rural_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from time of marriage for women with 8 or more years of education by quarter
-% (3 month period). 
-% Predictions based on age 20 at marriage.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell1_high}
-% \end{figure}
-% 
-% \clearpage
-% 
-% \subsection{Second Spell}
-% 
-% 
-% % SPELL 2 - URBAN - LOW
-% \begin{figure}[hb]
-% \centering
-% \caption*{1954--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[First child a girl (N=1,760)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[First child a boy (N=2,050)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with no education by month beginning 9 months after prior birth. 
-% Predictions based on age 18 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell2_low_urban}
-% \end{figure}
-% 
-% 
-% % SPELL 2 - rural - LOW
-% \begin{figure}
-% \centering
-% \caption*{1954--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[First child a girl (N=8,594)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[First child a boy (N=10,123)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_low_rural_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for rural 
-% women with no education by month beginning 9 months after prior birth. 
-% Predictions based on age 18 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell2_low_rural}
-% \end{figure}
-% 
-% 
-% % SPELL 2 - URBAN - MEDIUM
-% \begin{figure}
-% \centering
-% \caption*{1955--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[First child a girl (N=1,362)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[First child a boy (N=1,472)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 19 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell2_med_urban}
-% \end{figure}
-% 
-% 
-% % SPELL 2 - rural - MEDIUM
-% \begin{figure}
-% \centering
-% \caption*{1955--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[First child a girl (N=2,254)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[First child a boy (N=2,368)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_med_rural_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for rural 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 19 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell2_med_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1957--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[First child a girl (N=1,498)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[First child a boy (N=1,607)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 22 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell2_high_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1957--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[First child a girl (N=655)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[First child a boy (N=743)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell2_g1_high_rural_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for rural
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 22 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell2_high_rural}
-% \end{figure}
-% 
-% \clearpage
-% 
-% 
-% \subsection{Third Spell}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1957--1984}
-% \setcounter{subfigure}{-2}
-% \subfloat[Two girls (N=763)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[One boy and one girl (N=1,743)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[Two boys (N=982)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_urban_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with no of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell3_low_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1957--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[Two girls (N=3,796)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[One boy and one girl (N=8,390)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[1972--1984 (N=4,903)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_low_rural_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with no of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell3_low_rural}
-% \end{figure}
-% 
-% 
-% % Medium education
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1958--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[Two girls (N=633)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[One boy and one girl (N=1,236)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[Two boys (N=716)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_urban_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell3_med_urban}
-% \end{figure}
-% 
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1958--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[Two girls (N=995)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[One boy and one girl (N=2,037)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[Two boys (N=1,093)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_med_rural_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 21 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell3_med_rural}
-% \end{figure}
-% 
-% 
-% % High education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1960--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[Two girls (N=660)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[One boy and one girl (N=1,375)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[Two boys (N=673)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_urban_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for urban 
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell3_high_urban}
-% \end{figure}
-% 
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{1960--1984 }
-% \setcounter{subfigure}{-2}
-% \subfloat[Two girls (N=267)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_gg_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_gg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[One boy and one girl (N=573)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bg_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bg_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[Two boys (N=341)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bb_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{dropped_spell3_g1_high_rural_bb_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after second birth for rural
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 24 at second birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_dropped_spell3_high_rural}
-% \end{figure}
-
-\clearpage
-
 \bibliographystyle{aer}

### 2018-02-01 paper/sexSelectionSpacingAppendix-ver1.tex
LaTeX code for graphs now generated by Stata together with number of observations

@@
 
-\begin{figure}[htpb!]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=4,518)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_urban_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,309)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_urban_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,762)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_urban_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=25,486)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_low_rural_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=23,360)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_low_rural_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=7,922)]{
-\begin{minipage}{0.28\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_low_rural_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with no education by month beginning at marriage. 
-Predictions based on age 16 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell1_low}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=3,666)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_urban_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,104)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_urban_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,302)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_urban_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=7,496)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_med_rural_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=9,000)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_med_rural_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=5,208)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_med_rural_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 1 to 7 years of education by month beginning at marriage. 
-Predictions based on age 17 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell1_med}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=7,338)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_pc}}\\
-\subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_urban_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=11,045)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_urban_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=9,116)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_urban_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=3,933)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g1_high_rural_s}} 
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=8,027)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g2_high_rural_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=7,504)]{
-\begin{minipage}{0.31\textwidth}
-\captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-\subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_pc}}\\
-\subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell1_g3_high_rural_s}}
-\captionsetup[subfigure]{labelformat=parens}
-\end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from time of marriage for women with 8 or more years of education by month beginning at marriage. 
-Predictions based on age 20 at marriage.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell1_high}
-\end{figure}
+\input{../figures/appendix_spell1_low.tex}
+
+\input{../figures/appendix_spell1_med.tex}
+
+\input{../figures/appendix_spell1_high.tex}
 
@@
 
-% SPELL 2 - URBAN - LOW
-\begin{figure}[h]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=1,596)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=2,232)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=952)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=1,754)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=2,411)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=930)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with no education by month beginning 9 months after prior birth. 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_low_urban}
-\end{figure}
-
-% SPELL 2 - rural - LOW
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=8,426)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=11,481)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=3,686)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=9,395)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=12,127)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=3,860)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with no education by month beginning 9 months after prior birth. 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_low_rural}
-\end{figure}
+\input{../figures/appendix_spell2_low.tex}
 
@@
 % SPELL 2 - URBAN - MEDIUM
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=1,342)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=1,969)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=1,082)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=1,461)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=2,182)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=1,104)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 19 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_med_urban}
-\end{figure}
-
-% SPELL 2 - rural - MEDIUM
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=2,603)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=4,095)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=2,159)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=2,803)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=4,203)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=2,197)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 19 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_med_rural}
-\end{figure}
+
+\input{../figures/appendix_spell2_med.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,689)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,869)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=3,774)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,806)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=5,246)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,969)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=1,305)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=3,105)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,823)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,404)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=3,381)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,044)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_rural}
-\end{figure}
+\input{../figures/appendix_spell2_high.tex}
 
@@
 % low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=493)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=996)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=475)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,083)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=2,141)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=950)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_low_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=569)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,124)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=426)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell3_low_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,599)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=5,062)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,879)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=5,382)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=10,473)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,779)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_low_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=3,070)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=5,339)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=1,846)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell3_low_rural}
-\end{figure}
+\input{../figures/appendix_spell3_low.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=432)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=825)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=425)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=883)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,673)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=848)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_med_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=446)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=848)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=438)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell3_med_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=775)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,659)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=848)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,639)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=3,222)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=1,773)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_med_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=785)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,548)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=730)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell3_med_rural}
-\end{figure}
+\input{../figures/appendix_spell3_med.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=709)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,654)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,000)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,409)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=3,460)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=2,357)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=780)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,660)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=1,098)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell3_high_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=348)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=982)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=863)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=700)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,987)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=1,819)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_high_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=370)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=945)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=790)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell3_high_rural}
-\end{figure}
+\input{../figures/appendix_spell3_high.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=130)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_ggg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_ggg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=446)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=200)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=410)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bgg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,185)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=601)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_low_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=389)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,145)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=486)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=141)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=382)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=155)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell4_low_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=752)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_ggg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_ggg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,954)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=888)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,065)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bgg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=5,990)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=2,456)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_low_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=2,168)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=5,439)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=2,155)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=777)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,895)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=696)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell4_low_rural}
-\end{figure}
+\input{../figures/appendix_spell4_low.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=110)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_ggg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_ggg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=282)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=144)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=299)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bgg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=765)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=372)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_med_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=274)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=600)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=275)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=77)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_bbb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=230)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=90)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell4_med_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=210)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_ggg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_ggg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=601)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=317)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=581)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bgg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,532)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=800)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_med_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=492)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,197)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=578)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=158)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_bbb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=357)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=192)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 1 to 7 years of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell4_med_rural}
-\end{figure}
+\input{../figures/appendix_spell4_med.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=131)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_ggg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_ggg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=355)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=191)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=353)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bgg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,062)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=590)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=309)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=681)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=344)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children three boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=87)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_bbb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=233)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=110)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell4_high_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First three children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=62)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_ggg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_ggg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=257)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=201)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_ggg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_ggg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children one boy and two girls}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=176)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bgg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=664)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=564)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bgg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bgg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_high_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First three children two boys and one girl}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=173)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=515)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=367)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First three children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=56)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_bbb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=166)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=92)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_bbb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell4_high_rural}
-\end{figure}
+\input{../figures/appendix_spell4_high.tex}
 

### 2018-02-02 paper/sexSelectionSpacingAppendix-ver1.tex
Update conditional survival curves graphs to include NFHS-4
Also changed the font size for the captions.

@@
 \usepackage[justification=centering]{caption}
+\captionsetup[figure]{font=small}
 \usepackage[font=scriptsize]{subfig}
@@
 \subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
+    \begin{minipage}{0.32\textwidth}
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
@@
 \subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
+    \begin{minipage}{0.32\textwidth}
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
@@
     \end{minipage}
-}
+} \\
 \setcounter{subfigure}{1}
 \subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
+    \begin{minipage}{0.32\textwidth}
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
@@
 }
+\setcounter{subfigure}{2}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 \caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
+% SPELL 2 - URBAN - MEDIUM
+
+\input{../figures/appendix_spell2_med.tex}
+
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 \setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
 \subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1-7 years of education by month beginning 9 months after prior birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_med_pps}
+\end{figure}
+
+% High education
+
+\input{../figures/appendix_spell2_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
 \setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_pps}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Third Spell}
+
+% low education
+\input{../figures/appendix_spell3_low.tex}
+
+% PARITY PROGRESSION SURVIVAL - LOW
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
 \setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell2_low_pps}
+\label{fig:results_spell3_low_pps}
 \end{figure}
 
-% SPELL 2 - URBAN - MEDIUM
-
-\input{../figures/appendix_spell2_med.tex}
+% Medium education
+
+\input{../figures/appendix_spell3_med.tex}
 
 % PARITY PROGRESSION SURVIVAL - MEDIUM
-
-% Low education
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
 \setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \caption*{Rural}
-\setcounter{subfigure}{2}
+\setcounter{subfigure}{3}
 \subfloat[1972--1984]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \caption{Survival curves conditional on parity progression
-for women with 1-7 years of education by month beginning 9 months after prior birth.
+for women with 1 to 7 years of education by month beginning 9 months after prior birth.
 Left column shows results prior to sex selection available, middle column before
@@
 }
-\label{fig:results_spell2_med_pps}
+\label{fig:results_spell3_med_pps}
 \end{figure}
@@
 
-\input{../figures/appendix_spell2_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - High education
+\input{../figures/appendix_spell3_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - high
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
 \setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell2_high_pps}
+\label{fig:results_spell3_high_pps}
 \end{figure}
@@
 
-\subsection{Third Spell}
+\subsection{Fourth Spell}
 
 % low education
-\input{../figures/appendix_spell3_low.tex}
+
+\input{../figures/appendix_spell4_low.tex}
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
 \setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell3_low_pps}
+\label{fig:results_spell4_low_pps}
 \end{figure}
@@
 
-\input{../figures/appendix_spell3_med.tex}
+\input{../figures/appendix_spell4_med.tex}
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
 \setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell3_med_pps}
+\label{fig:results_spell4_med_pps}
 \end{figure}
@@
 
-\input{../figures/appendix_spell3_high.tex}
+\input{../figures/appendix_spell4_high.tex}
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
 \setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell3_high_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Fourth Spell}
-
-% low education
-
-\input{../figures/appendix_spell4_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_low_pps}
-\end{figure}
-
-% Medium education
-
-\input{../figures/appendix_spell4_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell4_med_pps}
-\end{figure}
-
-% High education
-
-\input{../figures/appendix_spell4_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - high
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
 \label{fig:results_spell4_high_pps}

### 2018-02-06 paper/sexSelectionSpacing-ver1.tex
Update ref to bootstrap tables
Adjust presentation of pps curves to allow for NFHS-4

@@
 % Median duration and sex ratio tables
-\input{../tables/median_sex_ratio_low.tex}
+\input{../tables/bootstrap_duration_sex_ratio_low.tex}
 
@@
 
-\input{../tables/median_sex_ratio_med.tex}
+\input{../tables/bootstrap_duration_sex_ratio_med.tex}
 
@@
 
-\input{../tables/median_sex_ratio_high.tex}
+\input{../tables/bootstrap_duration_sex_ratio_high.tex}
 
@@
 }
+\setcounter{subfigure}{2}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 \caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[1995--2006]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
+% High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
 \setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
 \subfloat[1972--1984]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+Left column shows results prior to sex selection available, middle column before
+sex selection illegal and right column after sex selection illegal.
+N indicates the number of women in the relevant group in the underlying samples.
+}
+\label{fig:results_spell2_high_pps}
+\end{figure}
+
+% 3rd spell
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
 \setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
 \subfloat[1985--1994]{
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell2_low_pps}
+\label{fig:results_spell3_low_pps}
 \end{figure}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_pps}
-\end{figure}
-
-% 3rd spell
-
-% Low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_low_pps}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{2}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{3}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
@@
     \end{minipage}
-}
-\setcounter{subfigure}{4}
-\subfloat[1995--2006]{
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
     \begin{minipage}{0.31\textwidth}
@@
         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}

### 2018-02-16 paper/sexSelectionSpacing-ver1.tex
Begin incorporating NFHS-4

@@
 
-The data come from the three rounds of the National Family Health Survey 
-(NFHS-1, NFHS-2 and NFHS-3),
-collected in 1992--93, 1998--99, and 2005--2006.%
+The data come from the four rounds of the National Family Health Survey 
+(NFHS-1, NFHS-2, NFHS-3, and NFHS-4),
+collected in 1992--93, 1998--99, 2005--2006, and 2015--2016.%
 \footnote{
@@
 aged 13--49 from 88,562 households,
-NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households
-and NFHS-3 covered 124,385 never-married and ever-married women aged 
-15--49 from 109,041 households.
+NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households,
+NFHS-3 covered 124,385 never-married and ever-married women aged 
+15--49 from 109,041 households,
+and 
+NFHS-4 covered 699,686 never-married and ever-married women aged
+15--49 from 601,509 households surveyed.
 
@@
 and those with missing information on education.
-Women interviewed in NFHS-3 who were never married or where gauna had not
-been performed were also dropped.
+Women interviewed in NFHS-3 or NFHS-4 who were never married or where gauna 
+had not been performed were also dropped.
 The same goes for women who had at least one multiple birth,
@@
 remain in the sample---unless they are dropped for another reason---because 
-10 to 20 percent fall into this category across the 3 surveys.
+10 to 20 percent fall into this category across the 4 surveys.
 Although it is possible that some of these births are premature, the high number of
-women who report a birth less than 6 months after marriage indicates that conception
-likely occurred before marriage in most cases.
+women who report a birth less than 6 months after marriage indicates that for
+a majority conception likely occurred before marriage.
 
@@
 possible to estimate different baseline hazards for each group.
-Furthermore, the groups are so different in terms of background and son preference
-that combining them into one group would not make sense.
+Furthermore, the other groups are so different in terms of background and son 
+preference that combining them into one group would not make sense.
 
@@
 Second, no other surveys cover as long a period in the same amount of detail.
-The three NFHS rounds allow me to show the development in spacing and 
-sex ratio from before sex-selective abortions were available until 2006.
+The four NFHS rounds allow me to show the development in spacing and 
+sex ratio from before sex-selective abortions were available until 2016.
 Third, NFHS has birth histories for a large number of women.%
@@
 for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
-and 26 years for NFHS-3.
-The final sample consists of 146,096 women, with 332,951 parity one through four births.
+and 25 years for NFHS-3 and NFHS-4.
+The final sample consists of TK women, with TK parity one through four births.
 
@@
 
-Spell duration is measured in 
 As mentioned above, 10 to 20 percent of women gave birth less than 9 months
@@
 or too few births are observed for the method to work.
-The timing of censoring because of too few births vary slightly by spell but 
-is generally 5 years or longer after the beginning of the spell.
+For spell 1 I set censoring at 72 months after marriage,
+while for spells 2 and 3 censoring is at 72 months and for spell 4
+57 months after a birth can occur.
 
@@
 I group spells into three time periods based on spell start date:
-1972--1984, 1985--1994, and 1995--2006.
+1972--1984, 1985--1994, 1995--2004, and 2005--2016.
 These years follow the important changes in availability and legality of 

### 2018-03-02 paper/sexSelectionSpacing-ver1.tex
Sample sizes were hardcoded into paper
Editing

@@
 
-% Fertility, Birth Spacing and the Determinants of sex-selective Abortions
-% Understanding Sex Selection: Fertility, Abortions and Birth Spacing
-% The Determinants of sex-selective Abortions: A New Method/Approach
-% Sex Selection: A New Method for Estimating Determinants
-% Fertility, Birth Spacing and Abortions in India
-% Fertility, Birth Spacing and Sex Selection
-% Fertility, Birth Spacing and sex-selective Abortions
-% Fertility, Spacing and Sex Selection
-% Fertility, Sex Selection, and Spacing
-% Fertility, Sex Selection, and Birth Spacing
-% Fertility, Birth Spacing and Missing Girls
-% Where have all the girls gone: An analysis of sex-selective abortions
-
 \title{Son Preference, Birth Spacing, and Sex-Selective Abortions%
@@
 University of Washington.
-% Prior versions of this paper were presented under the title ``The 
-% Determinants of sex-selective Abortions.''
-}
-}
-
-\author{}
+}
+}
 
@@
 
-\date{December 2017\\
+\date{March 2018\\
 \bigskip
@@
 
-Spacing between births has long been used as a measure of son preference 
+Parents' spacing between births has long served as a measure of son preference 
 \citep{Leung1988}.
@@
 birth sooner.
-Son preference was therefore often associated with shorter spacing after the 
-births of girls than boys, which, in turn, was associated with worse 
-health outcomes for girls.%
+Son preference is therefore often associated with shorter spacing after the 
+births of girls than boys 
+\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012}.
+Shorter spacing is, in turn, associated with worse health outcomes for girls 
+\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
 \footnote{
-See, for example, 
-\citet{Das1987}, \citet{Rahman1993}, \citet{Pong1994}, \citet{Haughton1996},
-\citet{Arnold1997}, and \citet{Soest2012} on shorter birth spacing after
-girls
-and 
-\citet{arnold98}, \citet{Whitworth2002}, \citet{Rutstein2005},
-and \citet{Conde-Agudelo2006} on the association between shorter birth
-spacing and worse health outcomes for girls.
-Parents were also more likely to cease childbearing after the birth of 
+Parents are also more likely to cease childbearing after the birth of 
 a son than after a daughter 
-\citep{ben-porath76b,Das1987,Arnold1997,clark00,filmer09,Altindag2016}
-}
-
-What has not previously been appreciated is that the introduction 
-of prenatal sex determination fundamentally changed the relationship 
-between son preference and birth spacing.
-Couples, who used to have short birth spacing because of son preference,
+\citep{ben-porath76b,Das1987,Arnold1997,clark00,filmer09,Altindag2016}.
+}
+
+The introduction of prenatal sex determination fundamentally changed the 
+relationship between son preference and birth spacing.
+Couples, who before had shorter birth spacing because of son preference,
 now have access to prenatal sex determination and sex-selective abortions,
-but each sex-selective abortion they have substantially increases the space
-between births. 
-Birth spacing increases by approximately a year per abortion.
+and each abortion increases birth spacing by approximately a year.
 The increase consists of three parts.
@@
 least two menstrual cycles to recover;  otherwise, the likelihood 
-of a spontaneous abortion increases substantially \citep{zhou00b}.
-The second part is the waiting time to conception, which I set to 6 
-months \citep{Wang2003}.
-Finally, sex determination tests are generally reliable only from 3 months 
+of spontaneous abortion increases substantially \citep{zhou00b}.
+The second part is the waiting time to conception, which I set to six 
+months \citep{Wang2003}.%
+\footnote{
+The waiting time to conception varies by woman, but even if it is, say, one 
+month, the additional space between births would still be six months per abortion.
+}
+Finally, sex determination tests are reliable only from 3 months 
 of gestation onwards.
-These three parts add up to 12 months.%
-\footnote{
-The waiting time to conception varies by woman, but even if it is very 
-short, say one  month, the additional space between births would still
-be 6 months per abortion.
-}
-
-As a result, we now have a situation where families with the \emph{strongest} son 
-preference may show the \emph{longest} spacing after the birth of a daughter,
-because they use sex-selective abortions.
-But, to further complicate matters, we may still observe short spacing 
+
+As a result, we now have a situation where families with the 
+\emph{strongest} son preference may have \emph{longer} spacing after 
+the birth of a daughter,
+because of their use of sex-selective abortions.
+To further complicate matters, we may still observe short spacing 
 after the births of daughters as a representation of son preference for 
 families who---for one reason or another---do not use prenatal sex selection.
-
-Spacing, by itself, can therefore no longer be used to measure son preference.
-However, understanding birth spacing remains an important undertaking.
-First, spacing is still useful in understanding son preference, 
+Also, even if they have access to prenatal sex determination, couples 
+with stronger son preference may still try to conceive faster after daughters, 
+and may even shorten the time until they try to conceive, knowing that 
+they may have to go through multiple pregnancies and sex-selective
+abortions before they conceive a son.
+
+Spacing, by itself, can therefore no longer be used as a direct measure of 
+son preference.
+However, understanding birth spacing remains a critical undertaking.
+First, birth spacing is still useful in understanding son preference, 
 if combined with the likelihood of observing a boy or a girl.
-% Short spacing after a girl is indicative of son preference if observed
-% births are close to the natural sex ratio, whereas long spacing is indicative
-% of son preference if observed births are male biased.
-Second, if spacing affects health outcomes for mother and/or children, it is 
-important to understand what drives changes in spacing.
+Second, if spacing affects health outcomes for mother and children, it is 
+essential to understand what drives changes in spacing.
 The better health outcomes for girls in the presence of sex selection may,
-for example, be an unintended side-effect of the longer spacing that arise
+for example, be an unintended side-effect of the longer spacing that arises
 from sex-selective abortions, rather than, as often assumed, be driven by a 
 higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
-Third, spacing may be an important factor in parents' decisions, either
-for preference or economic reasons.
-This is especially important here, because even parents with strong
-son preference may reverse their decision to use prenatal sex determination, 
-and carry the next pregnancy to term whether male or female, as the duration 
-from the prior birth becomes sufficiently sufficiently long.
+Third, the duration between births may be an important factor in parents' 
+decisions, either for preference or economic reasons.
+Whether duration plays a role in parents' decisions is especially important 
+here, because even parents with strong son preference may reverse their 
+decision to use prenatal sex determination, and carry the next pregnancy 
+to term whether male or female, as the duration from the prior birth 
+becomes sufficiently long.
 Finally, we know less about what determines spacing behavior in 
@@
 With increasing numbers of women entering the labor force in developing
-countries, understanding how timing decisions are made will be important
+countries, understanding how timing decisions are made will be necessary
 for the design of suitable policies \citep{Portner2018}.
@@
 \emph{and} the duration between births.
-The method can be used to analyse both situations with and without prenatal
+The method can be used to analyze both situations with and without prenatal
 sex selection.
-Furthermore, my proposed method allow for the duration since the prior 
+Furthermore, my proposed method allows for the time since the previous 
 birth to affect the decision on sex selection.
@@
 India's National Family and Health Surveys (NFHS), covering the period 
-1972 to 2006. 
-India is a particularly interesting case.
-On one hand, India has seen dramatic increases in the males-to-females ratio 
+1972 to 2016. 
+India is a particularly compelling case.
+On the one hand, India has seen dramatic increases in the males-to-females ratio 
 at birth over the last three decades as access to prenatal sex determination 
-expanded.%
+expanded 
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06}.%
 \footnote{
-See \citet{das_gupta97}, \citet{Sudha1999},
-\citet{Arnold2002}, \cite{retherford03b} and \citet{jha06}.
-India is clearly not alone; both China and South Korea saw
+India is not alone; both China and South Korea saw
 significant changes in the sex ratio at birth over the same period 
@@
 }
-On the other hand, recent research suggests that son preference in 
+On the other hand, research suggests that son preference in 
 India, when measured as ideally having more boys than girls, is decreasing 
-over time and with higher education \citep{bhat03,pande07}.%
-\footnote{
-This measure of son preference is commonly used in the literature. 
-See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-}
-In addition, there has been substantial changes in access and legality of
+over time and with higher education \citep{bhat03,pande07}.
+% %
+% \footnote{
+% This measure of son preference is commonly used in the literature. 
+% See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
+% }
+There have also been substantial changes in access and legality of
 prenatal sex determination in India over the period covered.
-Abortion has been legal in India since 1971, and still is, but the 
+Abortion has been legal in India since 1971 and still is, but the 
 first reports of prenatal sex determination did
@@
 \footnote{
-The Act is described in detail at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
+Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
 The number of convictions has been low.
-It took until January 2008 for the first state, Haryana, to reach 5 convictions.
+It took until January 2008 for the first state, Haryana, to reach five convictions.
 Hence, private clinics apparently operate with little risk of legal action 
@@
 }
-Hence, the data make it possible to show how spacing between births and
+Hence, the data make it possible to show how the spacing between births and
 sex ratios have changed with the introduction of prenatal sex determination,
@@
 
-I divide women's reproductive lives into spells, which are the periods from 
-one birth, or marriage for the first spell, to the following birth
-(I define how spell duration is measured in Section \ref{sec:data}).
-A basic problem is that some spells' duration are censored, either
-because the survey took place before the birth that would end the spell 
-or because the couple has finished childbearing.
-The standard approach, which I follow here, is to use a hazard models to 
-address the censoring of spells.
-
-Prior research on birth spacing have used hazard models where the only 
-exit state was the birth of a child. 
-This works when there is no sex selection---making the sex of the child 
-a random event---but not here because at least some couples use 
-sex selection. 
-To capture that the sex of children are no longer necessarily a random event, 
-I instead use a competing risk framework with two possible exit states: 
-either a boy or a girl is born.%
+The unit of analysis is individual spells, the period from one birth, or marriage for
+the first spell, to the next.
+For some spells, the duration is censored, either because the survey
+took place before the birth that would end the spell or because the couple
+has finished childbearing.
+The standard approach to address the censoring of spells, which I follow here, is 
+to use a hazard model.
+To capture the effects of sex selection, I extend the standard hazard model 
+to allow for multiple exit states and a non-proportional hazard specification.
+
+First, I use a competing risk framework with two possible exit states, either a boy
+or a girl is born, because access to prenatal sex determination means that
+the sex of children born is no longer necessarily a random event.
+Prior research on birth spacing has used hazard models where the only 
+possible exit state was the birth of a child. 
+Having only one exit state works when there is no sex selection---making the 
+sex of the child a random event---but not here because at least some couples use 
+sex selection.%
 \footnote{
@@
 
-Proportional hazard models, where covariates have an multiplicative 
+Second, I use a non-proportional hazard specification because
+sex composition and the use of sex selection are likely to affect 
+the shape of the hazard functions across groups.
+Proportional hazard models, where covariates have a multiplicative 
 effect on the hazard rate, are more efficient than non-proportional 
-models, but only provided that the proportionality assumption holds.
-Because proportional hazard models do not allow covariates to have 
-different sized effects at different times within a spell,
-they cannot capture differences in the shape of the hazard functions 
-between different groups, and if the proportionality assumption does 
-not hold the estimates may be biased.
+models, but only provided that the proportionality assumption hold.
+If the proportionality assumption does not hold, the estimates
+are biased.
 It is unlikely---even in the absence of prenatal sex determination---that 
-the effect of, for example, the sex composition of prior births have 
+the effect of, for example, the sex composition of previous births have 
 the same effect throughout the entire spell.
-This is especially the case for later spells where different
-sex composition of prior births can lead to substantial difference 
+Assuming that the effect of sex composition is the same throughout a spell
+is especially problematic for higher-order spells where different
+sex composition of previous births can lead to substantial difference 
 both in the likelihood of progressing to the next birth and
 how soon couples want their next child if they are going to have one.
-Any bias from the proportionality assumption is likely 
-exacerbated by the introduction of prenatal sex determination.
-First, sex-selective abortions affect birth spacing and use
-vary across groups.
+The introduction of prenatal sex determination is likely to exacerbate 
+any bias from the proportionality assumption.
+First, sex-selective abortions affect birth spacing, and use
+varies across groups.
 Second, the use of sex selection may vary within a spell, which means 
 that the effects of covariates vary within the spell as well.
-Because of these concerns I use a non-proportional specification.
-The use of a non-proportional specification also has the benefit 
-that it mitigates any potential effects of unobserved heterogeneity 
-when used in conjunction with a flexible baseline hazard \citep{Dolton1995}.
+The use of a non-proportional specification also mitigates any potential 
+effects of unobserved heterogeneity when used in conjunction with a 
+flexible baseline hazard \citep{Dolton1995}.
+
 In summary, my proposed model is a discrete time, non-proportional, competing risk 
 hazard model with two exit states: either a boy or a girl is born.
-
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
@@
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, if the data are transformed so the unit of analysis is a time period, in 
+Hence, transforming the data, so each observation is a period---here equal
+to three months---the model can be estimated using a standard multinomial logit model.
+if the data are transformed so the unit of analysis is a time period, in 
 this case 3 months periods, rather than the individual woman, the model can be 
@@
 
-The main downside of this set-up is that direct interpretation of the estimated 
+The main downside of this set-up is that interpretation of the estimated 
 coefficients is challenging;
 the coefficients show the change in hazards relative to the base outcome, 
-here no birth, rather than simply the hazard of an event.
+here no birth, rather than the hazard of an event.
 Hence, a positive coefficient does not necessarily imply that the associated 
-exit state becomes likely as the explanatory variable increases because the 
+exit state becomes more likely as the explanatory variable increases because the 
 probability of the other exit state may increase even more \citep{thomas96}.
@@
 a next birth if they already have one or more sons.
-Direct comparison of standard survival curves therefore tells us little 
-about how the spread of sex selection affect birth spacing across, for
+Direct comparison of standard survival curves, therefore, tells us little 
+about how the spread of sex selection affects birth spacing across, for
 example, different sex compositions of prior children.
-To overcome this problem I condition on parity progression when examining
-birth spacing using the survival curves.
-This allows me to calculate measures, such as median spell duration, for
-the women with a given set of characteristics who will eventually give
-birth in a spell.%
+
+To overcome this problem, I condition on the likelihood of parity progression 
+when examining birth spacing.
+If, for example, women with a given set of characteristics have an 80\%
+chance of ending a spell with a birth their median spell duration is when
+their survival curve shows that 40\% are predicted to have exited the spell.%
 \footnote{
@@
 }
-This number can then be compared across groups to understand how birth
-spacing changes with the introduction of sex selection.
-Obviously, this approach only works if the spell length covered is 
+Median durations can then be averaged across women with different 
+characteristics using the probabilities of ending a spell with a child
+as weights.
+How well this approach works depends on whether the spell length covered is 
 sufficiently long that only very few women would be likely to give
 birth later.
+I discuss the choice of spell length below.
 In addition to calculating conditional spell length for different 
@@
 values of explanatory variables calculated using the Delta method.
-These are combined with standard survival curves which shows the ``weight''
-that each period should be given, or, in other words, how many births take
-place in each period.
+Finally, I include standard survival curves, which shows the ``weight''
+that each period has, or, in other words, how many births take place in
+each period.
 
@@
 \footnote{
-A delay in the survey for Tripura means that NFHS-2 has a small number of observation 
+A delay in the survey for Tripura means that NFHS-2 has some observation 
 collected in 2000.
@@
 The surveys are large: NFHS-1 covered 89,777 ever-married women 
-aged 13--49 from 88,562 households,
-NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households,
+aged 13--49 from 88,562 households;
+NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households;
 NFHS-3 covered 124,385 never-married and ever-married women aged 
-15--49 from 109,041 households,
+15--49 from 109,041 households;
 and 
@@
 I exclude visitors to the household, as well as
-women married more than once, divorced, or not living with their husband,
-women with inconsistent information on age of marriage,
+women who have been married more than once, divorced, or who are 
+not living with their husband,
+women with inconsistent age at marriage,
 and those with missing information on education.
@@
 had not been performed were also dropped.
-The same goes for women who had at least one multiple birth,
+The same goes for women who had at least one multiple births,
 reported having a birth before age 12, had a birth before marriage, or
-a duration between births less than 9 months.
-Women who reported less than 9 months between marriage and first birth
+duration between births of less than nine months.
+Women who reported less than nine months between marriage and first birth
 remain in the sample---unless they are dropped for another reason---because 
-10 to 20 percent fall into this category across the 4 surveys.
+10 to 20 percent fall into this category across the four surveys.
 Although it is possible that some of these births are premature, the high number of
-women who report a birth less than 6 months after marriage indicates that for
+women who report a birth less than six months after their marriage indicates that for
 a majority conception likely occurred before marriage.
@@
 who constitute about 80 percent of India's population.
-If use of sex selection differ between Hindu and other religions, such 
+If the use of sex selection differ between Hindu and other religions, such 
 as Sikhs, assuming that the baseline hazard is the same would lead to bias.
@@
 possible to estimate different baseline hazards for each group.
-Furthermore, the other groups are so different in terms of background and son 
+Furthermore, the other groups are so different in background and son 
 preference that combining them into one group would not make sense.
@@
 probe for ``missed'' births.
-Second, no other surveys cover as long a period in the same amount of detail.
-The four NFHS rounds allow me to show the development in spacing and 
-sex ratio from before sex-selective abortions were available until 2016.
-Third, NFHS has birth histories for a large number of women.%
-\footnote{
-The Special Fertility and Mortality Survey appears to cover a much large number of households
-than the three rounds of the NFHS combined, but \citet{jha06} only use the births that 
-took place in 1997 making their sample sizes by parity smaller than here.
-Their sample consists of 133,738 births of which 38,177 were first
-born, 36,241 second born, and 23,756 were third born.
-The differences in results for first born children are discussed in the online 
-Appendix.
-}
-Finally, even if probing for missing births may not completely eliminate recall error,   
-the overlap in cohorts covered and the large sample size make it possible to establish 
-where recall error remains a problem.
-
-Recall error arise mainly from child mortality, when respondents are reluctant to
-discuss deceased children.
-Systematic recall error, where the likelihood of reporting a deceased child depends on
-the sex of the child, is especially problematic because it biases both spacing
-and sex ratios.
-Probing catches many missed births, but systematic recall error is still a potentially 
-substantial problem.
+Second, no other surveys cover as extended a period in the same amount of detail.
+The four NFHS rounds allow me to show how spacing and 
+sex ratio changed from before sex-selective abortions were available until 2016.
+Third, NFHS has birth histories for a large number of women.
+% %
+% \footnote{
+% The Special Fertility and Mortality Survey appears to cover a much large number of households
+% than the three rounds of the NFHS combined, but \citet{jha06} only use the births that 
+% took place in 1997 making their sample sizes by parity smaller than here.
+% Their sample consists of 133,738 births of which 38,177 were first-born, 
+% 36,241 second-born, and 23,756 were third-born.
+% }
+Finally, even if probing for missing births does not eliminate recall error,   
+the overlap in cohorts covered and the large sample size makes it possible 
+to establish where recall error remains a problem.
+
+Recall error arises mainly from child mortality when respondents are 
+reluctant to discuss deceased children.
+Systematic recall error, where the likelihood of reporting a deceased 
+child depends on the sex of the child, is especially problematic because 
+it biases both spacing and sex ratios.
+Probing catches many missed births, but systematic recall error is 
+still a potentially substantial problem.
+
 Three factors contribute to the problem here.
 First, girls have significantly higher mortality risk than boys.
-Second, son preference may increase the probability that boys are remembered relative to girls.
+Second, son preference may increase the probability that parents recall boys 
+more readily than girls.
 Finally, in NFHS-1 and NFHS-2 enumerators probed only for a missed birth if the
-initial reported birth interval was four calendar years or more.
+initially reported birth interval was four calendar years or more.
 But, given short durations between births, especially after the birth of a girl,
 that procedure is unlikely to pick up all missed children.
-As I argue in the online Appendix, recall error is heavily dependent on the duration
-between marriage and survey, and I therefore drop women married 22 years or more 
+
+Recall error is heavily dependent on the length of marriage (TK).
+I, therefore, drop women married 22 years or more 
 for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
 and 25 years for NFHS-3 and NFHS-4.
-The final sample consists of TK women, with TK parity one through four births.
-
-% %
-% \footnote{
-% The online Appendix presents the results for a more restrictive definition and for the
-% women dropped because of recall error concerns.
-% }
+The final sample consists of 
+\input{../tables/num_women.tex}
+% [number] women, with [number] parity one through four births.
 
@@
 
-As mentioned above, 10 to 20 percent of women gave birth less than 9 months
-after they were married.
-The first spell therefore begins at the month of marriage.
+As mentioned above, 10 to 20 percent of women gave birth less than nine months
+after they were married, and the first spell, therefore, begins at the 
+month of marriage.
 The exception is for women married very young, where I use the month they 
-turned 12 rather than age of menarche, which is only available in NFHS-1.
-The second and subsequent spells begin 9 months after the previous birth 
+turned 12.
+The second and subsequent spells begin nine months after the previous birth 
 because that is the earliest we should expect to observe a new birth.
-A few women report births that occurred less than 9 months 
-after the previous birth; those women are dropped.
-
-All spells continue until either a child is born or the spell is censored.
+A few women report births that occurred less than nine months 
+after the previous birth; I drop those women from the sample.
+
+All spells continue until either a child is born or censoring occurs.
 Censoring can happen for three reasons:
 the survey takes place;
-the woman is sterilized;
+sterilization of the woman or her husband;
 or too few births are observed for the method to work.
@@
 
-To examine how the use of sex selection has changed over time,
-I group spells into three time periods based on spell start date:
+I group spells into four time periods based on spell start date:
 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-These years follow the important changes in availability and legality of 
+These years follow the main changes in availability and legality of 
 prenatal sex determination discussed in the Introduction.
-Note that the periods are based on the spells' beginning year, and some spells 
-will therefore cover two periods.
-A couple may, for example, be married in 1984, but not have their first child until 1986.
-That couple's first spell will be in the 1972--1984 period, even though most of the 
-spell actually falls in the 1985--1994 period.
-Some children born from spells that began in the 1972--1984 period may therefore have been
-conceive when prenatal sex determination techniques were available, which could result
-in evidence of sex-selective abortions even for this period.
-Similarly, a spell that began in the 1985--1994 period may have been partly or mostly
-under the PDNT act.
-The effect is to bias downwards any differences between the periods.
+Some spells cover two periods because I classify periods based on the 
+spell's beginning year.
+A couple may, for example, be married in 1984, but not have their first 
+child until 1986.
+That couple's first spell will be in the 1972--1984 period, even though 
+most of the interval falls in the 1985--1994 period.
+Hence, prenatal sex determination was likely available when some
+children from spells that began in the 1972--1984 period were conceived,
+which could result in evidence of sex-selective abortions even for this
+period.
+Similarly, a spell that started in the 1985--1994 period may have been partly 
+or mostly under the PDNT act.
+The effect is a downward bias in the differences between the periods.
 
@@
 
-The explanatory variables are divided into two groups.
+I divide the explanatory variables into two groups.
 The first group consists of variables expected to affect the shape of the hazard function
@@
 I chose these variables because the prior literature shows that they affect 
-spacing choices and are correlated with sex selection.
+spacing choices and correlate with sex selection.
 Increasing the number of variables interacted with the baseline hazard would
@@
 
-Increasing education of mothers is strongly associated with lower fertility, with
-the negative effect of higher opportunity cost on fertility more than outweighing the 
-positive effect of higher income \citep{schultz97}.
-Higher education should therefore be associated with higher use of sex selection.%
+I divide women into three groups based on education attainment: no
+education, 1 to 7 years of education, and 8 and more years of education.
+The models are estimated separately for each education level to reduce
+the potential problem of including other variables as proportional.
+Increasing education of mothers correlates closely with lower fertility 
+\citep{schultz97}, and 
+we should expect lower fertility to lead to more use of sex selection.%
 \footnote{
@@
 In practice, fathers' education had little effect on the hazards and the use of 
-sex-selective abortions and is not included.
-}
-I divide women into three education groups:
-no education, 1 to 7 years of education, and 8 and more years of education.
-The models are estimated separately for each education level to reduce
-the potential problem of including other variables as proportional.%
-\footnote{
-A potential concern here is reverse causation, where the sex of children
-affect women's education.
-Although no direct information is available on when women left school it is
-possible to estimate school leaving age from the highest completed grade
-and the usual starting age.
-As described in the online Appendix, relatively few women could potentially 
-have returned to school after the birth of their first child,
-and only 56 could possibly have ended up in the wrong education group. 
-Hence, there is little likelihood that reverse causation is a substantial
-concern here.
-}
-
+sex-selective abortions, and I, therefore, do not include it.
+}
+
+I capture sex composition with dummy variables for the
+possible combinations for the specific spell, ignoring the ordering of births.
+As an example, for the third spell, three groups are used: Two boys,
+one girl and one boy, and two girls.
+[TK this should be more specific - more boys less sex selection - maybe even use ordering]
 As discussed, the sex composition of previous children affects both the timing
 of births and the use of sex-selective abortions.
-I capture sex composition of previous children with dummy variables for the
-possible combinations for the specific spell, ignoring the ordering of births.
-As an example, for the third spell three groups are used: Two boys,
-one girl and one boy, and two girls.
 
 The area of residence is a dummy variable for the household living in
-an urban area.%
+an urban area [TK check on this for NFHS-4].%
 \footnote{
-NFHS uses four categories for area of residence: Large city, small city, town
+NFHS uses four categories for the area of residence: Large city, small city, town,
 and countryside.
@@
 }
-The cost of children is higher in urban areas than in rural and access to prenatal
-sex determination is easier, and both are expected to be associated with
-greater use of sex-selective abortions in urban than in rural areas.
-Because of concerns about selective migration I use where the household was living
-at the end of each spell.
-% %
-% \footnote{
-% As online Appendix Table D.1 shows there is little difference across
-% education levels in migration patterns within each period and patterns across periods
-% are also relatively stable.
-% }
-
-The second group of variables are those expected to have an approximately 
-proportional effect on the hazard: 
-length of her first spell (for second spell and above to capture fecundity), 
-age of the mother at the beginning of the spell, 
-whether the household owns land, 
+The cost of children is higher in urban areas than in rural areas, and 
+there is easier access to prenatal sex determination in urban areas.
+Both factors are likely to lead to higher use of sex-selective abortions
+in urban than in rural areas.
+
+The second group of variables consists of those expected to have an 
+approximately proportional effect on the hazard.
+These include the length of the first spell 
+(for the second and higher-order spells to capture fecundity), 
+the age of the mother at the beginning of the spell, 
+whether the household owns any land, 
 and whether the household belongs to a scheduled tribe or caste.
-Fecundity cannot be observed directly, but a suitable proxy is the 
-duration from marriage until first birth.
-Most Indian women do not use contraception before the first birth
-and there is pressure to show that a newly married woman can conceive,
-as confirmed below by the very short spells between marriage and first birth,
-even among the most educated \citep{dyson83,Sethuraman2007,Dommaraju2009}.
+We cannot observe fecundity directly, but the time from marriage until 
+first birth is a suitable proxy because most Indian women do not use 
+contraception before the first birth and there is pressure to show that 
+a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
+This is confirmed below by the very short spells between marriage and first birth,
+even among the most educated.
 Hence, a long spell between marriage and first birth is likely due to low fecundity.
-For this variable and the age of the mother at the beginning of the spell 
-the squares are also included.
+For both duration from marriage to first birth and the age of the mother at the 
+beginning of the spell, I also include their squares.
 The remaining variables are dummies for household ownership of land and membership

### 2018-03-02 paper/sexSelectionSpacingAppendix-ver1.tex
Wrong PPS graphs were listed
Editing

@@
 % \setcounter{posttbl}{0}
-
-\section{[Recall error paragraphs from paper]}
-
-Observed sex ratios by cohort provide a straightforward way to determine 
-whether recall error is a problem.
-Because prenatal sex determination techniques did not become widely available until the 
-mid-1980s, a higher than natural sex ratio for cohorts born before that time must be 
-the result of systematic recall error.
-As shown in the online Appendix, the observed sex ratio by parity becomes more male 
-dominated the further back births took place.
-In addition, births in the same cohort tend to be more male dominated the more recent the 
-survey (births in the cohort took place longer ago relative to the survey).
-Hence, there is evidence of recall error and the degree of recall error increases
-with length of time between survey and cohort.
-
-Using cohort year of birth to analyze recall error and decide which observations
-to keep is, however, problematic because the year of birth for a given parity is affected 
-by recall error; for example, a second born child listed as first born will be 
-born later than the real first born child.
-Year of marriage should, however, be unaffected by recall error.
-Using year of marriage the basic recall error pattern remains with women married longer 
-ago more likely to report that their child was a boy for a given parity.
-Similarly, comparing women married in the same period across surveys shows
-that women married longer ago are more likely to report having sons.
-
-That recall error increases the longer ago somebody was married means
-that duration of marriage is a better predictor of recall error than calendar year of 
-marriage.
-Figure \ref{fig:sexRatioMarriage} shows the observed sex ratio for children 
-reported as first born as a function of duration of marriage combining all three surveys.%
-\footnote{
-The graph for second births shows a similar pattern.
-The graphs for the second births and the individual survey rounds are available upon request.
-}
-The solid line is the sex ratio of children reported 
-as first born by the number of years between the survey and marriage, 
-the dashed lines indicate the 95 percent confidence interval 
-and the horizontal line the natural sex ratio (approximately 0.512).
-To ensure sufficient cell sizes the years are grouped in twos.
-
-\begin{figure}[htp]%
-\centering
-\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
-\caption{Ratio of boys in ``first'' births}
-\label{fig:sexRatioMarriage}
-\end{figure}
-
-Figure \ref{fig:sexRatioMarriage} clearly illustrates the systematic recall error
-problem.
-The observed sex ratio is increasingly above the expected value the
-longer ago the parents were married.
-The increasingly unequal sex ratio with increasing marriage duration suggests that
-a solution to the recall error problem is to drop women who were married ``too far'' from 
-the survey year.
-The main problem is establishing what the best cut-off point should be.
-The observed sex ratio is consistently significantly higher than the natural sex ratio 
-from around 24 years of marriage, so one possibility is simply to drop all women married 
-more than 24 years at the time of the survey.
-But, as the Appendix shows, there are differences across the three surveys and between 
-parities.
-I therefore use different cut-off points by survey round.
-For NFHS-1 women married 22 years or more were dropped, with the corresponding cut-off 
-points 23 years for NFHS-2  and 26 years for NFHS-3.
-The final sample consists of 146,096 women, with 332,951 parity one through four births.
-
-\section{Recall Error and the Sex Ratio}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% \footnote{%
-% This also has implications for analyses of child mortality and fertility.
-% % Relatively little attention has been paid to this problem despite the
-% % potential for substantially underestimating mortality, especially for girls.
-% A companion paper examines fertility and mortality trends in India when
-% account is taken of recall error.
-% % The method suggested here can also be used to establish the extent of
-% % recall error and what factors are associated with recall error.
-% }
-% This is important because the estimation method proposed
-% rely on good quality data on both the sex of children born and the spacing between these 
-% children.
-% Recall error makes an analysis of the spread of sex determinations techniques
-% less precise, because there may appear to be little change in the sex
-% ratio over time even though the actual sex ratio at birth has increased.
-% It also makes it more difficult to identify which families are using sex selective abortions.
-%
-
-Since the proposed method relies both on spacing between births and  birth outcomes, the 
-quality of the results depends on the reliability of the birth 
-histories provided by the respondents.
-An important concern here is child mortality.
-A respondent may not provide information about deceased children because of
-the painful nature of the topic.
-% First, deceased children may not be listed in a respondent's birth history because
-% the sensitivity of the topic.
-Furthermore, the likelihood of reporting a deceased child may depend on sex of the child. 
-Systematic recall error, where children of a specific sex are missed non-randomly, 
-is especially problematic because it directly biases the sex ratios results.
-
-NFHS enumerators probe for any missed births, although the method depends on the survey.%
-\footnote{%
-NFHS-1 probe for each calendar birth interval that is 4 or more years.
-NFHS-2 asked for stillbirths, spontaneous and induced abortions and also probed 
-for each calendar birth interval 4 or more years.
-NFHS-3 did not directly use birth intervals, but asked whether were there any other live births 
-between (name of previous birth) and (name), including any children who died after birth. 
-It did ask for births before the birth listed as first birth.
-}
-Probing catches many originally missed births but systematic recall error based on son
-preference may still be a problem.
-First, strong son preference lead to significantly higher mortality for girls than boys.
-Secondly, for children who died son preference makes it more likely that parents will
-remember boys than girls.
-Finally, in the absence of sex selective abortions, son preference lead parents to have 
-the next birth sooner if the last child was a girl than if it was a boy.
-If this girl subsequently dies she is more likely to be missed because probing for missed 
-births is only done for long intervals.%
-\footnote{
-As an example, imagine a family whose first child is a girl.
-Because of son preference this girl is followed quickly by another child.
-If this child is also a girl the parents will quickly try for a third child.
-This can lead to three children in three years and
-if the middle child dies and is not listed the enumerators will not probe for
-missing births because the interval between the first and last child is only two years.
-}
-
-To assess the extent of systematic recall error Table \ref{tab:recallBirth} 
-shows sex ratios of children recorded as first-born and second-born
-by year of birth together with tests for whether the observed sex ratio is
-significantly higher than the natural sex ratio.
-Births are combined into five-year cohorts to achieve sufficient power for a test of 
-differences in sex ratios.
-Prenatal sex determination techniques did not become widely available until the 
-mid-1980s and any significant deviation from the natural sex ratio before that time
-is therefore likely the result of recall error.
-Furthermore, births and deaths that took place longer ago may be more 
-likely to be subject to recall error than more recent events.
-The three NFHS surveys make it possible to examine whether recall error increases with 
-time by comparing sex ratios for births that took place during the same years but were 
-surveyed at different times.
-Table \ref{tab:recallBirth} therefore also shows tests for whether more recent surveys 
-have a higher sex ratio for the cohort than older surveys.
-
-% Main points:
-% - births that took place further away from the survey show a higher sex ratio
-% - there is evidence of a U-shaped relationship in sex ratio over time for second
-% and especially the three parities combined with cohorts furthest away from the
-% survey showing the highest sex ratios. The sex ratio then declines and only begins
-% claiming again when sex selective abortions became available in the mid-1980s.
-% The exception to this pattern is children listed as first-born for whom the
-% sex ratios declines steadily over time leveling off at the natural sex ratio.
-% - lack of power for individual parities means that relatively few cohorts show
-% significantly different sex ratios across surveys; there is more power for
-% the three first parities combined
-
-% [Is this worth including?]
-% the reason that sex ratio for second born can be higher in more recent surveys
-% (NFHS-3 compared to NFHS-1) is that a higher proportion of women in the
-% recent survey have lower desired fertility and are better educated.
-% They should also be younger, as in born more recently.
-
-% The decline in sex ratio over time followed by the increase after sex selection
-% became available may be best argument against referee 1's concern about whether 
-% this is simply infanticide.
-
-\begin{table}[!htbp]
-\begin{center}
-\begin{small}
-\begin{threeparttable}
-\caption{Observed sex ratios by year of birth in five-year cohorts }
-\label{tab:recallBirth}
-\begin{tabular} {@{} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l  @{}} \toprule
-                   & \multicolumn{4}{c}{Listed as first-born}                          & \multicolumn{4}{c}{Listed as second-born} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9}
-                   & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.         & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.              \\
-                   & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} \\ \midrule
-1960--1964         & 0.5473\sym{***}   &      .\sym{}      &      .\sym{}      &       & 0.5172\sym{}      &      .\sym{}      &      .\sym{}      &           \\
-                   & (0.0004)          & (     .)          & (     .)          &       & (0.4382)          & (     .)          & (     .)          &           \\
-                   & \mco{[2,673]}     & \mco{[.]}         & \mco{[.]}         &       & \mco{[1,189]}     & \mco{[.]}         & \mco{[.]}         &           \\
-1965--1969         & 0.5274\sym{**}    & 0.5538\sym{***}   &      .\sym{}      & A     & 0.5327\sym{**}    & 0.5244\sym{}      &      .\sym{}      &           \\
-                   & (0.0306)          & (0.0002)          & (     .)          &       & (0.0124)          & (0.3310)          & (     .)          &           \\
-                   & \mco{[5,429]}     & \mco{[1,997]}     & \mco{[.]}         &       & \mco{[3,888]}     & \mco{[595]}       & \mco{[.]}         &           \\
-1970--1974         & 0.5354\sym{***}   & 0.5341\sym{***}   & 0.5411\sym{}      &       & 0.5212\sym{}      & 0.5313\sym{**}    & 0.6160\sym{**}    & BC        \\
-                   & (0.0001)          & (0.0019)          & (0.1208)          &       & (0.1497)          & (0.0248)          & (0.0143)          &           \\
-                   & \mco{[7,763]}     & \mco{[5,546]}     & \mco{[523]}       &       & \mco{[6,249]}     & \mco{[3,499]}     & \mco{[125]}       &           \\
-1975--1979         & 0.5207\sym{}      & 0.5151\sym{}      & 0.5255\sym{*}     &       & 0.5185\sym{}      & 0.5262\sym{**}    & 0.5384\sym{**}    & B         \\
-                   & (0.1258)          & (0.4669)          & (0.0920)          &       & (0.2477)          & (0.0340)          & (0.0225)          &           \\
-                   & \mco{[8,749]}     & \mco{[7,478]}     & \mco{[3,762]}     &       & \mco{[7,819]}     & \mco{[6,220]}     & \mco{[1,811]}     &           \\
-1980--1984         & 0.5210\sym{*}     & 0.5244\sym{**}    & 0.5280\sym{***}   &       & 0.5236\sym{**}    & 0.5236\sym{**}    & 0.5249\sym{*}     &           \\
-                   & (0.0872)          & (0.0273)          & (0.0094)          &       & (0.0361)          & (0.0492)          & (0.0628)          &           \\
-                   & \mco{[11,147]}    & \mco{[9,709]}     & \mco{[7,718]}     &       & \mco{[9,950]}     & \mco{[8,478]}     & \mco{[5,532]}     &           \\
-1985--1989         & 0.5187\sym{}      & 0.5132\sym{}      & 0.5118\sym{}      &       & 0.5157\sym{}      & 0.5194\sym{}      & 0.5165\sym{}      &           \\
-                   & (0.1916)          & (0.6153)          & (0.7091)          &       & (0.4099)          & (0.1695)          & (0.3716)          &           \\
-                   & \mco{[11,276]}    & \mco{[11,048]}    & \mco{[9,422]}     &       & \mco{[10,296]}    & \mco{[9,857]}     & \mco{[8,022]}     &           \\
-1990--1994         & 0.5174\sym{}      & 0.5185\sym{}      & 0.5183\sym{}      &       & 0.5120\sym{}      & 0.5166\sym{}      & 0.5289\sym{***}   & BC        \\
-                   & (0.3263)          & (0.2006)          & (0.2207)          &       & (0.6570)          & (0.3430)          & (0.0030)          &           \\
-                   & \mco{[6,544]}     & \mco{[11,653]}    & \mco{[10,601]}    &       & \mco{[5,869]}     & \mco{[10,653]}    & \mco{[9,299]}     &           \\
-1995--1999         &      .\sym{}      & 0.5222\sym{*}     & 0.4980\sym{}      &       &      .\sym{}      & 0.5230\sym{*}     & 0.5262\sym{**}    &           \\
-                   & (     .)          & (0.0788)          & (0.9998)          &       & (     .)          & (0.0664)          & (0.0103)          &           \\
-                   & \mco{[.]}         & \mco{[8,642]}     & \mco{[11,111]}    &       & \mco{[.]}         & \mco{[7,990]}     & \mco{[9,956]}     &           \\
-2000--2006         &      .\sym{}      &      .\sym{}      & 0.5135\sym{}      &       &      .\sym{}      &      .\sym{}      & 0.5292\sym{***}   &           \\
-                   & (     .)          & (     .)          & (0.5978)          &       & (     .)          & (     .)          & (0.0008)          &           \\
-                   & \mco{[.]}         & \mco{[.]}         & \mco{[13,413]}    &       & \mco{[.]}         & \mco{[.]}         & \mco{[11,645]}    &           \\
-\bottomrule
-\end{tabular}                        
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.6em} \textbf{Note.} 
-Sample consists of Hindu women only.
-First number in cell is ratio of boys to girls. 
-Second number in parentheses is p-value for the hypothesis that observed sex ratio is 
-greater than 105/205 using a binomial probability test (bitest in Stata 13)
-with asterisks indicating significance as follows: 
-* sign.\ at 10\%; ** sign.\ at 5\%; *** sign.\ at 1\%.
-Third number in square brackets is number of observations.
-\item[a] 
-Test (prtest in Stata 13) whether recall error increases 
-with time passed, which would manifest itself in a higher sex ratio for a more recent
-survey than an earlier for the same cohort.
-A: Cohort sex ratio significantly larger in NFHS-2 than NFHS-1 at the 10 percent level. 
-B: Cohort sex ratio significantly larger in NFHS-3 than NFHS-1 at the 10 percent level. 
-C: Cohort sex ratio significantly larger in NFHS-3 than NFHS-2 at the 10 percent level. 
-\end{tablenotes}
-\end{threeparttable}
-\end{small}
-\end{center}
-\end{table}
-
-The ``first-born'' sex ratios illustrate the systematic recall error problem well. 
-According to the birth histories in NFHS-1 almost 55 percent of children born between 1960 
-and 1964 were boys.
-Given that this is more than two decades before sex selection techniques became available
-in India the most likely explanation for the skewed sex ratio is that some children
-listed as first-borns were not, in fact, the first children born in their families.
-Instead, for a substantial proportion of families the first-born was a girl who died and was 
-skipped when enumerators asked about birth history.
-
-% Recall error is less of an issue for more recent births than for births that took place 
-% longer ago.
-As expected, the difference between the observed sex ratio and the natural sex ratio is 
-less pronounced the closer to the survey date the cohort is.
-The observed sex ratio for children born just prior to the NFHS-1 survey and listed as 
-first-born is 0.517, which is not statistically significant different from the
-natural sex ratio.
-The same general pattern holds for NFHS-2 and NFHS-3, with cohorts further away
-from the survey date more likely to have a sex ratio skewed male.
-
-Second births show a pattern very similar to that for first births.
-An interesting difference is that there is evidence of a U-shaped relationship between
-time and sex ratio for second births.
-Cohorts furthest away from the survey year show the highest sex ratios, but declines to the
-natural sex ratio in the mid-1980s, and the sex ratio is then significantly higher again 
-for more recent births.
-This is in line with the results in the paper that show that sex selective abortions take 
-place on lower parity births as desired fertility declined.
-
-Finally, across surveys the same cohort tends to show a higher sex ratio the more recent 
-the survey (births in the cohort took place longer ago), especially for second-borns.%
-\footnote{
-Births in the 1970-1974 cohort, for example, took place
-between 18 and 23 years ago for NFHS-1, 
-between 24 and 29 years ago for NFHS-2,
-and  between 31 and 36 years ago for NFHS-3.
-}
-Despite this, few cohorts show significantly different sex ratios across surveys, most 
-likely because of a lack of power.
-
-Using year of birth to analyze recall error is problematic because year of birth for a 
-given parity is affected by recall error; for example, a second born child listed as first 
-born will naturally be born later than the real first born child.
-Recorded year of marriage should, however, be affected neither by parental recall error 
-nor use of sex selective abortions.
-Table \ref{tab:recallMarriage} therefore shows sex ratios of children recorded as 
-first-born and second-born by year of parents'
-marriage, together with tests for whether the observed sex ratio is
-significantly higher than the natural sex ratio and whether more recent surveys show
-a higher sex ratio for the cohort than older surveys.
-
-The basic recall error pattern remains with women married longer ago more
-likely to report that their first-born is a boy.
-If anything the pattern is more consistent when using year of marriage than 
-year of birth. 
-Before the introduction of sex selection there are only two instances  across the two 
-parities where the observed sex ratio is lower for women married longer ago than for women 
-married closer to the survey date.%
-\footnote{
-For first-borns it is between 1970--1974 and 1975-1979 for NFHS-3 and for second-borns
-it is between 1975--1979 and 1980--1984 for NFHS-1.
-}
-Similarly, comparing women married in the same five-year period across surveys shows
-that women married longer ago are more likely to report having a son.
-
-\begin{table}[htbp]
-\begin{center}
-\begin{small}
-\begin{threeparttable}
-\caption{Observed sex ratios by year of parents' marriage in five-year cohorts }
-\label{tab:recallMarriage}
-\begin{tabular} {@{} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l D{.}{.}{1.6} D{.}{.}{1.6} D{.}{.}{1.6} l  @{}} \toprule
-                   & \multicolumn{4}{c}{Listed as first-born}                          & \multicolumn{4}{c}{Listed as second-born} \\ \cmidrule(lr){2-5} \cmidrule(lr){6-9}
-                   & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.         & \mco{NFHS-1}      & \mco{NFHS-2}      & \mco{NFHS-3}      & Diff.              \\
-                   & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} & \mco{1992–-1993}  & \mco{1998–-1999}  & \mco{2005–-2006}  & test\tnote{a} \\ \midrule
-1960--1964         & 0.5368\sym{***}   &      .\sym{}      &      .\sym{}      &        & 0.5274\sym{**}    &      .\sym{}      &      .\sym{}      &          \\
-                   & (0.0002)          & (     .)          & (     .)          &        & (0.0239)          & (     .)          & (     .)          &          \\
-                   & \mco{[6,200]}     & \mco{[.]}         & \mco{[.]}         &        & \mco{[6,001]}     & \mco{[.]}         & \mco{[.]}         &          \\
-1965--1969         & 0.5333\sym{***}   & 0.5450\sym{***}   &      .\sym{}      &        & 0.5277\sym{**}    & 0.5401\sym{***}   &      .\sym{}      &          \\
-                   & (0.0011)          & (0.0000)          & (     .)          &        & (0.0181)          & (0.0005)          & (     .)          &          \\
-                   & \mco{[6,707]}     & \mco{[4,268]}     & \mco{[.]}         &        & \mco{[6,449]}     & \mco{[4,142]}     & \mco{[.]}         &          \\
-1970--1974         & 0.5244\sym{**}    & 0.5222\sym{}      & 0.5271\sym{}      &        & 0.5182\sym{}      & 0.5235\sym{*}     & 0.5384\sym{**}    & B        \\
-                   & (0.0386)          & (0.1120)          & (0.1372)          &        & (0.2651)          & (0.0805)          & (0.0194)          &          \\
-                   & \mco{[8,154]}     & \mco{[6,546]}     & \mco{[1,973]}     &        & \mco{[7,843]}     & \mco{[6,308]}     & \mco{[1,913]}     &          \\
-1975--1979         & 0.5272\sym{***}   & 0.5202\sym{}      & 0.5316\sym{***}   & C      & 0.5157\sym{}      & 0.5183\sym{}      & 0.5278\sym{**}    & B        \\
-                   & (0.0062)          & (0.1477)          & (0.0050)          &        & (0.4208)          & (0.2499)          & (0.0242)          &          \\
-                   & \mco{[9,829]}     & \mco{[8,644]}     & \mco{[5,798]}     &        & \mco{[9,295]}     & \mco{[8,294]}     & \mco{[5,608]}     &          \\
-1980--1984         & 0.5151\sym{}      & 0.5142\sym{}      & 0.5195\sym{}      &        & 0.5198\sym{}      & 0.5171\sym{}      & 0.5187\sym{}      &          \\
-                   & (0.4616)          & (0.5322)          & (0.1877)          &        & (0.1514)          & (0.3178)          & (0.2332)          &          \\
-                   & \mco{[10,814]}    & \mco{[9,924]}     & \mco{[8,316]}     &        & \mco{[9,788]}     & \mco{[9,409]}     & \mco{[7,906]}     &          \\
-1985--1989         & 0.5176\sym{}      & 0.5209\sym{*}     & 0.5095\sym{}      &        & 0.5131\sym{}      & 0.5194\sym{}      & 0.5267\sym{**}    & B        \\
-                   & (0.2753)          & (0.0925)          & (0.8425)          &        & (0.5918)          & (0.1651)          & (0.0105)          &          \\
-                   & \mco{[9,971]}     & \mco{[10,990]}    & \mco{[9,717]}     &        & \mco{[5,790]}     & \mco{[10,130]}    & \mco{[9,077]}     &          \\
-1990--1994         & 0.5180\sym{}      & 0.5182\sym{}      & 0.5125\sym{}      &        & 0.4366\sym{}      & 0.5191\sym{}      & 0.5251\sym{**}    & AB       \\
-                   & (0.3836)          & (0.2282)          & (0.6692)          &        & (0.9740)          & (0.2097)          & (0.0199)          &          \\
-                   & \mco{[2,170]}     & \mco{[10,619]}    & \mco{[10,574]}    &        & \mco{[142]}       & \mco{[7,994]}     & \mco{[9,600]}     &          \\
-1995--1999         &      .\sym{}      & 0.5243\sym{*}     & 0.5017\sym{}      &        &      .\sym{}      & 0.5613\sym{***}   & 0.5312\sym{***}   &          \\
-                   & (     .)          & (0.0845)          & (0.9965)          &        & (     .)          & (0.0015)          & (0.0009)          &          \\
-                   & \mco{[.]}         & \mco{[5,081]}     & \mco{[10,960]}    &        & \mco{[.]}         & \mco{[1,019]}     & \mco{[8,969]}     &          \\
-2000--2006         &      .\sym{}      &      .\sym{}      & 0.5169\sym{}      &        &      .\sym{}      &      .\sym{}      & 0.5247\sym{}      &          \\
-                   & (     .)          & (     .)          & (0.3280)          &        & (     .)          & (     .)          & (0.1243)          &          \\
-                   & \mco{[.]}         & \mco{[.]}         & \mco{[9,210]}     &        & \mco{[.]}         & \mco{[.]}         & \mco{[3,316]}     &          \\
-\bottomrule
-\end{tabular}                        
-\begin{tablenotes} \scriptsize
-\item \hspace*{-0.6em} \textbf{Note.} 
-Sample consists of Hindu women only.
-First number in cell is ratio of boys to girls. 
-Second number in parentheses is p-value for the hypothesis that observed sex ratio is 
-greater than 105/205 using a binomial probability test (bitest in Stata 13)
-with asterisks indicating significance as follows: 
-* sign.\ at 10\%; ** sign.\ at 5\%; *** sign.\ at 1\%.
-Third number in square brackets is number of observations.
-\item[a] 
-Test (prtest in Stata 13) whether recall error increases 
-with time passed, which would manifest itself in a higher sex ratio for a more recent
-survey than an earlier for the same cohort.
-A: Cohort sex ratio significantly larger in NFHS-2 than NFHS-1 at the 10 percent level. 
-B: Cohort sex ratio significantly larger in NFHS-3 than NFHS-1 at the 10 percent level. 
-C: Cohort sex ratio significantly larger in NFHS-3 than NFHS-2 at the 10 percent level. 
-\end{tablenotes}
-\end{threeparttable}
-\end{small}
-\end{center}
-\end{table}
-
-The relationship between length of marriage and recall error can also seen in 
-Figure \ref{fig:sexRatioMarriage}, which shows the observed sex ratio for children reported
-as first born as a function of duration of marriage at the time of the survey combining 
-all three surveys.
-The solid line is the sex ratio of children reported 
-as first born by the number of years between the survey and marriage, 
-the dashed lines indicate the 95 percent confidence interval 
-and the horizontal line the natural sex ratio (approximately 0.512).
-To ensure sufficient cell sizes the years are grouped in twos.
-In line with the results from Table \ref{tab:recallMarriage}, the observed ratio of boys 
-is increasingly above the expected value the longer ago the parents were married.%
-\footnote{
-The graph for second births shows a similar pattern with the
-likelihood of the second child being a boy going up with increasing marriage duration.
-The graphs for the second births and the individual survey rounds are available upon request.
-% It is interesting to note that the graphs of ``first'' births for NFHS-1 and 2 
-% very clearly show the effect of the 1965-1967 drought in India.
-% There is a sharp drop in the percentage boys corresponding to the drought.
-% For the surrounding years the percentage of boys among ``first-born'' is around
-% 54 percent and increasing, but for the drought years the percentage is slightly
-% \emph{below} the natural.
-% See also the discussion in Section \ref{sec:review} on nutrition and sex ratios.
-}
-
-[Figure sex ratio marriage here!]
-
-% \begin{figure}[htp]%
-% \centering
-% \includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
-% \caption{Sex ratio of ``first'' births by duration of marriage}
-% \label{fig:sexRatioMarriage}}
-% \end{figure}
-
-The increasingly unequal sex ratio with increasing marriage duration suggests that
-a solution to the recall error problem is to drop observations for 
-women who were married ``too far'' from the survey year.
-The main problem is establishing what the best cut-off point should be.
-As Table \ref{tab:recallMarriage} shows there are differences in recall error across the
-three surveys and between parities.
-One possibility is simply to drop all women married in cohorts where the observed
-sex ratio is substantially higher than the natural sex ratio, but even this is not
-straightforward.
-For ``first'' born this would imply dropping all women married before 1980, but
-for ``second'' born it would be imply dropping all married before 1970 for NFHS-1, before 1975 
-for NFHS-2, and before 1980 NFHS-3.
-Because of the differences between ``first'' and ``second'' born in the different surveys
-I vary the cut-off point by survey round.
-
-NFHS-3 is the most straightforward in that the implied cut-off point is the same for
-both first and second born.
-Based on Table \ref{tab:recallMarriage}, women in NFHS-3 who were married 26 years or
-more before the survey date are dropped.
-For NFHS-1 and NFHS-2 the trade-off is between ensuring enough information and not bias 
-the results unduly.
-Given that sex selective abortions are more likely in higher parity birth I base the
-cut-off point on the second births instead of the first births.
-Hence, for NFHS-1 women who were married 22 years or more before the survey date 
-were dropped and for NFHS-2 women who were married 23 year or more before the survey date 
-were dropped.
-The final sample consists of 146,096 women, with 332,951 
-parity one through four births.
-
-% \begin{figure}
-% \centering
-% \subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r1}}
-% \subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r2}} \\
-% \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r3}} 
-% \caption{Ratio of Boys for ``First'' Births by Survey Round}
-% \label{fig:sex_ratio_recall_rounds}
-% \end{figure}
-
-% This indicates the problem with using older data for analyzing sex selective abortions.
-% Even more important it shows why using year of birth as a cut-off point
-% for addressing recall error is problematic.
 
@@
 
-\section{Potential for Reverse Causation in Education?}
-
-The data provides no direct way to tell whether a mother is currently in
-school or have returned to school.
-The questions in the survey simply ask whether the respondent has ever
-attended school, and if yes, what the highest level (standard) completed is.
-My best estimate of the age somebody left school is therefore their years of
-schooling completed plus 6 years for school starting age.
-Based on this, more than 75 percent exit school at age 16 or before,
-while 96 percent have stopped school by age 21.
-
-It is possible to get a sense of whether women might return to school after 
-giving birth using this information.
-To find the year when a woman would have completed school I take her birth
-year and add the estimated age at school completion.
-If the year the woman is estimated to have completed school is equal to or greater than 
-the year of the first birth it is conceivable that the woman may have returned to 
-school after giving birth.
-This ignores the possibility of grade repetitions, but if somebody needs to
-repeat grades it is unlikely that they will go on to secondary or higher education.
-Out of 146,096 women in the main sample only 2,615, or less than 2 percent, fall 
-into this category.
-Furthermore, only 322 are possibly in school at the time of the second school.
-Among women who appear to return to school after their first child the sex ratio of their
-first birth is skewed somewhat more male than normal (54 percent boys), so their 
-return may, indeed, be tied to the sex of their first child.
-
-The estimates are conservative in the sense that it is possible to finish school 
-first and then have the child later in the year.
-Using if the estimated end of schooling comes \emph{after} the year the child 
-is born the numbers fall to 1,234, or less than 1 percent, for
-the first birth and 162 for the second birth.
-
-How much of a problem is this then?
-It is, indeed, possible that some women return to school after their first child,
-but it appears to be relatively  uncommon.
-Furthermore, almost nobody are in school after their second child.
-Since there is little evidence of sex-selective abortions among first-born children
-the possibility of return to school should not affect the estimates.
-
-Furthermore, I use 8 years of education as the cut-off point and hence only women who
-had their first child before age 14 would potentially be misclassified in terms of
-education group for their first birth. 
-There are only 56 women who end up with 8 or more years of education but had their
-first birth at age 12 or 13.
-None are possibly misclassified for second birth or above, which is where sex-selective 
-abortions become important.
-The upshot is that while it is possible that there might be some reverse causation of
-education and sex of children this should not affect the estimates.
-
-\clearpage
-\newpage
-
 \section{Sex Ratios at First Birth}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}

### 2018-03-05 paper/sexSelectionSpacing-ver1.tex
Edit of Descriptive Statistics section

@@
 Appendix Table \ref{tab:des_stat1} presents descriptive statistics for
-the spells by education level and when the spell began.
+the spells by education level and period they began.
 There is a substantial number of censored observations.
-As an example, for highly educated women who had their first child in the 1995--2006
-period, almost half did not have their second child by the time of the survey.
-Hence, although about 13,000 women began the second spell 
-there are only about 7,000 births to these women.
+As an example, for highly educated women who had their first child in the 2005--2016
+period, more than 40\% did not have their second child by the time of the survey.
 Censoring becomes even more important for the third and fourth
-spells, where around 70 percent of the observations are censored.
-Generally, censoring increases with parity and time period.
-This reflects a combination of factors: timing of the surveys
+spells, with more than 70 percent of the observations censored.
+The level of censoring also increases with parity and time period,
+which reflects a combination of factors: timing of the surveys
 relative to the periods of interest, later beginning of childbearing, 
-falling fertility, and the longer spells from sex-selective abortions.
-
-The descriptive statistics provide a first indication of how the
-sex ratio at birth changes over time and by spell.
-For the first spell the sex ratio is very close to the natural
-for all education groups and all three time periods.%
+falling fertility, and the increase in spell lengths from 
+sex-selective abortions.
+
+The share of urban women in the sample has fallen slightly over the
+periods, even though India's population has become progressively more urbanized.
+For the first and second periods, over 32\% of the women 
+entering the first spell lived in urban areas, falling to 
+30\% for the third period and 26\% in the last period.
+The most likely explanation is that the age of marriage has increased
+faster in urban areas than in rural areas.
+Hence, there are relatively more urban women, but fewer show up in the
+sample because they are not yet married.
+
+The population has become substantially better educated over time.
+Women with no education constituted almost 60 percent 
+in the first period, but less than twenty percent in the last period.
+Correspondingly, in the first period just over twenty percent had eight or more 
+years of education, whereas in the last period more than 60\% did.
+These changes are an underestimate of the increase in female
+education overall because many of the younger women with more education
+have not yet married than therefore are not in the sample.%
 \footnote{
-There still appears to be some recall error for the group of women without
-education for the 1972--1984 period, where 52.3 percent of the children born were boys.
-}
-For the second spell, all but the highly educated group in the last two
-periods have sex ratios in line with the natural sex ratio.
-Women with 8 or more years of education have 53.1 and 54.3 percent
-boys in the 1985--1994 and 1995--2006 periods, respectively.
-This pattern repeats itself for the third spell, except the percentage
-boys is higher for the high education group (55.3 and 55.9 for the last
-two time periods).
-Finally, for the fourth spell the high education group 
-had 60 percent boys in the last period, i.e. after the PNDT act was introduced.
-Note, however, that for the fourth spell the number of births is substantially
-smaller and censoring even more important than for the other spells.
-
-India's population has become progressively more urban.
-For the first period, 32 percent of the women entering the first spell lived in urban areas.
-This increases to 35 percent for the second period and to 42 percent for the final period.
-The population is also substantially better educated.
-Women with no education constituted almost 60 percent 
-in the first period, but less than thirty percent in the last period.
-Correspondingly, in the first period just over twenty percent had 8 or more 
-years of education, whereas in the last period it was almost half.
-Part of the increase in education is correlated with the increase in urbanization,
-but the proportion of better-educated women has increased substantially
-in the rural areas as well.
-Among the high education group almost 70 percent lived in urban areas
-during the first period but this had fallen to less than 60 percent
-in the last period.
-
-% The increase in urbanization and education is likely to exert downward pressure
-% on fertility and the high censoring rates for the later periods are evidence of this.
-% The average number of children born to women by the time they turn 35 illustrate how
-% strong the decline in fertility has been.%
-% \footnote{
-% Figure \ref{fig:fertility} shows the full results.
-% }
-% Women born in the early 1940s had on average close to 5 children when 
-% they reached 35, but women born in the early 1970s had only just over three children.
-% The low number of children is especially remarkable because it combines
-% all education levels and all areas of residence.
-% % Hence, fertility in cities is likely substantially lower.
+Women with eight or more years of education accounted for 65.9\% of
+unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4.
+See \citet[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
+and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
+for more information.
+ }
+
+Age at marriage increased over time across all three education groups.
+The most substantial increase was for women without any education, where
+the average went from below 16 years of age to 18.5.
+The smallest change is for the most educated women where the average age
+at marriage went up by less than a year---from 19.6 to 20.4---across the 
+four periods.
 

### 2018-03-08 paper/sexSelectionSpacing-ver1.tex
Explain result table structure and measures

@@
 probability of the other exit state may increase even more \citep{thomas96}.
+
 It is, however, straightforward to calculate the predicted probabilities of 
@@
 values of explanatory variables calculated using the Delta method.
-Finally, I include standard survival curves, which shows the ``weight''
-that each period has, or, in other words, how many births take place in
-each period.
 
@@
 
-Results are presented as the estimated percent boys born by length of birth spacing
-using graphs.
-For each graph, the extent to which the percent boys is statistically 
-significantly above the natural sex ratio indicates the use of sex selection.
-
-[TK not sure where this fits in]
-In addition, it is possible that falling fertility also generically 
-leads to longer spacing between births.
-This means that we have to separate out which part of the longer
-spacing comes from falling fertility (and therefore should also
-affect boy composition) and which parts comes from increased use
-of sex selection.
-
-[We should expect sex selection to be mainly used for the last---or close to
-last---birth that a couple expect to have because of the cost and risk
-of the procedures.]
-
-[TK not sure where to fit this into]
-Finally, increased reliability of access and effectiveness of
-contraceptive can lead to shorter spacing between births 
-\citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level 
-of contraception---resulting in longer spacing---to avoid having 
-too many children by accident.
-But, as contraception becomes more effective parents can more
-easily avoid future births, allowing them to reduce the spacing 
-between births without having to worry about overshooting their 
-preferred number of children.
-This idea may also help explain shorter spacing for better 
-educated women than for less educated women, provided that   
-knowledge and ability to use contraception differ
-across education groups \citep{Tulasidhar1993,Whitworth2002}.
-
-[Moved from estimation strategy]
-In the absence of sex selection, I expect most parities to follow
-a pattern, where there initially are relatively few births, 
-followed by a substantial number of births over a 1 to 2 year period, and then
-relatively few births thereafter.
-As sex selection becomes more widely used the associated
-longer spacing shows up by making the survival curve straighter,
-indicating that some of the births that would originally have taken place
-now take place later because of abortions.
-The use of sex selection is clearly not the only factor that can change the shape of
-the survival curves; factors such as the desired number of children and
-use of contraceptives may also shape the shape.
-To account for this it is best to compare survival curves for an individual
-parity between women who are likely to use sex selection and women who are
-not, for example because they already have one or more sons.
-
-[Moved from estimation strategy]
-In addition to information about spacing, the survival curves also provide 
-``weighting'' for the associated percentage boys born.
-The steeper the survival curve, the more weight should be assigned to a given
-spell period because it is based on more births, 
-whereas a period with a flat survival curve should be given little weight because the 
-percentage boys is based on few births.
-
-[Difference in approach: use the sex composition of prior
-children, rather the sex of the last child.
-Problem is that the cell sizes become too small if we further split up
-the higher spell cells.
-
-Define cell]
-
-The main question of interest here is how the duration between one
-birth and the next is related to son preference.
-The hypothese examined here is that in the absence of sex selection son 
+% [Hypotheses / questions]
+
+The overall hypothesis is that spacing patterns significantly changed 
+as prenatal sex determination became available.
+To address this, I examine three questions in order of importance.
+
+First, did the spacing after girls increase relative to the spacing
+after boys?
+The underlying hypothese is that in the absence of sex selection son 
 preference leads to shorter spacing after the birth of a girl than after the 
@@
 used.
-We would still expect parents to \emph{begin} trying to conceive earlier
-after the birth of a girl than after a boy, but the abortions will automatically
-increase the length of the space, and may even lead to longer spacing after the
+We would still expect parents to \emph{try} to conceive earlier after the birth 
+of a girl than after a boy, but the abortions will increase the 
+length of the space, and may even lead to longer spacing after the
 birth of girls than after boys.
-
-To provide a first look at how the hypothese holds up, Tables 
-\ref{tab:median_sex_ratio_low},
-\ref{tab:median_sex_ratio_med}, and
+[TK something on general changes in spacing? Or hold off until discussing the
+results]
+
+Second, do the shapes of survival curves differ across sex compositions 
+within a spell?
+The shapes of the survival curves provides clues to whether parents are
+still trying to conceive earlier after girls than boys.
+I expect this to be the case if there is still a strong preference for
+boys, and, as discussed above, this behavior may even become more pronounced
+with access to sex selection.
+At a more technical level, the shapes of the survival curve serve as an
+indicator for the presence of non-proportionality.
+
+Finally, do parents change their decision on sex selection within a spell?
+There are two reasons why this is interesting.
+If parents change their mind the standard method of observing sex ratios 
+will not capture the full extent of the use of sex selection.
+Furthermore, it tells us something about parents' preferences for ideal
+spacing between births and how strong their son preference is.
+
+% [How to read tables]
+Tables \ref{tab:median_sex_ratio_low}, \ref{tab:median_sex_ratio_med}, and
 \ref{tab:median_sex_ratio_high}
-show predicted median duration and sex ratios for the three different
-education levels by spell, sex composition, and periods.
-These predictions are based on the estimation results employing the method 
-detailed in Section \ref{sec:strategy} and are calculated using the means of 
-the continuous explanatory variables and the majority category for categorical 
-explanatory variables.
-The median duration is the number of months it is predicted to take for
-half of the women who are predicted to have a birth by the end of spell length
-covered.
-For example, if 80\% of women with a given set of characteristics are predicted to
-have a birth by the end of the end of spell, the median duration is the number of
-months it would take for 40\% of women to have a birth.
-The sex ratio is the percent of births that result in a son, based on all the 
-births predicted to happen over the spell.
-If the estimations are based on 100 or fewer births in a cell the predictions
-for that cell are not presented.
-Furthermore, those cells with 500 or fewer births are marked.
+show predicted median duration and sex ratios by period, spell, and sex 
+composition for the three different education levels separated by area of residence. 
+The predictions are based on the estimation method described in 
+Section \ref{sec:strategy}.
+The standard errors for both measures are based on bootstrapping, where the 
+original sample is resampled with replacement and the method is applied to 
+the new sample.
+
+The predicted median duration shown is the weighted average over the women in the 
+sample's predicted median durations, using the individual probabilities of a birth 
+as weights.
+For each woman in a sample, I calculate her probability of ending the spell 
+with a birth, and her contribution to median spacing is how long it will take
+from the beginning of the spell to where she is predicted to reach half of that probability.
+For example, if a woman has a 80\% probability of having a birth by the end of 
+the spell, her median duration is the number of months it takes to reach
+40\% probability of having exited with a birth (equivalent to the 60\% point
+in a standard survival curve because that captures how many have not yet
+exited).
+
+For second through fourth spell I show whether durations for sex composition
+other than only girls are statistically significantly different from the
+duration with only girls.
+The statistical significance is based on the bootstrapped differences in
+durations across sex compositions.
+For each new sample the difference in duration is calculated and these
+differences are used to calculate the standard error and the level of
+significance for the difference in the original sample.
+
+The cleanest test is comparing durations after only boys with durations after
+only girls.
+However, because of falling fertility the number of births to women with 
+only sons becomes small in the later periods, especially for the third and 
+fourth spell.
+Hence, it is possible to have substantial differences in spacing that are
+not statistically significant because of low power.
+Furthermore, it is, in principle, possible to estimate the model taking 
+into account the ordering of children.
+This would, however, further lower the power of the test, by leading to 
+one extra group for the third spell and four extra groups for the fourth spell.
+
+The predicted sex ratio is the weighted average over the women in the sample's 
+individual predicted sex ratios, using the individual probabilities of a birth by 
+the end of the spell as weights.
+Each woman's predicted sex ratio is the weighted average of the predicted
+percentage boys over the months in the spell calculated using equation 
+(\ref{eq:probability_son}) and the probability of giving birth in each month 
+as weights.%
+\footnote{
+Imagine a spell has two periods and that the estimated percentage boys for a
+woman are 54\% and 66\% and that the likelihood of exiting the spell is 20\% and 40\%
+(in other words, there is 40\% chance that she does not have a birth by the end of 
+the spell).
+This woman' percentage boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
+}
+The predicted sex ratio captures the percent boys that will be born to women 
+in the sample once child bearing for that spell is over.
+
+Each cell's predicted precent boys is tested against the natural percentage 
+boys using the bootstrapped standard errors.
+The natural sex ratio is approximately 105 boys to 100 girls or
+51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
+It is possible for the predicted percentage boys to be different from 
+the natural rate either because of natural variation, any remaining
+recall error, or sex selection.
 
@@
 
-\clearpage
-
-\subsection{[Specific spell/education/area combinations of special interest]}
-[Only a subset of the planned analyses to demonstrate the method and interpretation]
+\subsection{Differences in Survival Curves Across Sex Compositions}
+
+[Moved from estimation strategy]
+In the absence of sex selection, I expect most parities to follow
+a pattern, where there initially are relatively few births, 
+followed by a substantial number of births over a 1 to 2 year period, and then
+relatively few births thereafter.
+As sex selection becomes more widely used the associated
+longer spacing shows up by making the survival curve straighter,
+indicating that some of the births that would originally have taken place
+now take place later because of abortions.
+The use of sex selection is clearly not the only factor that can change the shape of
+the survival curves; factors such as the desired number of children and
+use of contraceptives may also shape the shape.
+To account for this it is best to compare survival curves for an individual
+parity between women who are likely to use sex selection and women who are
+not, for example because they already have one or more sons.
+
+\subsection{Does Sex Selection Change within Spells?}
+
+\section{Discussion}
+
+[TK not sure where this fits in]
+In addition, it is possible that falling fertility also generically 
+leads to longer spacing between births.
+This means that we have to separate out which part of the longer
+spacing comes from falling fertility (and therefore should also
+affect boy composition) and which parts comes from increased use
+of sex selection.
+
+[We should expect sex selection to be mainly used for the last---or close to
+last---birth that a couple expect to have because of the cost and risk
+of the procedures.]
+
+[TK not sure where to fit this into]
+Finally, increased reliability of access and effectiveness of
+contraceptive can lead to shorter spacing between births 
+\citep{Keyfitz1971,Heckman1976}.
+With less reliable contraception parents choose a higher level 
+of contraception---resulting in longer spacing---to avoid having 
+too many children by accident.
+But, as contraception becomes more effective parents can more
+easily avoid future births, allowing them to reduce the spacing 
+between births without having to worry about overshooting their 
+preferred number of children.
+This idea may also help explain shorter spacing for better 
+educated women than for less educated women, provided that   
+knowledge and ability to use contraception differ
+across education groups \citep{Tulasidhar1993,Whitworth2002}.
 

### 2018-03-08 paper/sexSelectionSpacing-ver1.tex
Discuss no education duration and sex ratio results

@@
 show predicted median duration and sex ratios by period, spell, and sex 
-composition for the three different education levels separated by area of residence. 
+composition for the three different education levels separated by area of residence.%
+\footnote{
+Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
+\ref{tab:p25_p75_low} show 25th and 75th percentiles durations.
+} 
 The predictions are based on the estimation method described in 
@@
 The cleanest test is comparing durations after only boys with durations after
-only girls.
-However, because of falling fertility the number of births to women with 
-only sons becomes small in the later periods, especially for the third and 
-fourth spell.
+only girls, but the number of births to women with only sons becomes small 
+in the later periods because of falling fertility.
 Hence, it is possible to have substantial differences in spacing that are
-not statistically significant because of low power.
-Furthermore, it is, in principle, possible to estimate the model taking 
-into account the ordering of children.
-This would, however, further lower the power of the test, by leading to 
-one extra group for the third spell and four extra groups for the fourth spell.
+not statistically significant because of low power, especially for the third 
+and fourth spell.
+It is, in principle, possible to estimate the model taking into account the 
+ordering of children, but this would further lower the power of the test, by 
+adding one extra group for the third spell and four extra groups for the fourth spell.
 
@@
 
-Each cell's predicted precent boys is tested against the natural percentage 
+Each predicted precent boys is tested against the natural percentage 
 boys using the bootstrapped standard errors.
@@
 51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
-It is possible for the predicted percentage boys to be different from 
-the natural rate either because of natural variation, any remaining
-recall error, or sex selection.
-
-% Median duration and sex ratio tables
+The predicted percentage boys may differ from the natural rate because of 
+natural variation, any remaining recall error not corrected for, or 
+sex selection.
+
 \input{../tables/bootstrap_duration_sex_ratio_low.tex}
 
-Table \ref{tab:median_sex_ratio_low} shows the predictions for women 
-with no education.
-Overall, spacing is shorter the fewer boys a couple has, but the
-differences in median duration are never more than 3 months and most
-are only one or two months
-(the exceptions to this pattern are mostly for small cells).
-Furthermore, although the median duration generally increases over 
-time---with the exception of the first spell---there is little 
-change in the relative pattern of durations across sex compositions
-over time.
-These results point to an absence of sex-selective abortions for 
-this group of women, which is supported by predicted sex ratios
-that mostly close to the natural sex ratio.%
-\footnote{
-I return to whether there are statistically significant 
-differences below when examining sex ratios within spells.
-}
+Women with no education follow a pattern consistent with son
+preference with shorter spacing when they have only girls compared 
+to when they have one or more sons, and the differences are often statistically 
+significant as shown in Table \ref{tab:median_sex_ratio_low}.
+Most of the women without education live in rural areas,
+while there are relatively few urban women with no education.
+There are especially very few urban women to based the third
+and fourth spell results on, and I therefore focus on rural women.
+
+Predicted median duration has generally increased over time within
+each sex composition.
+The exception is for the first spell, where there is little
+change, and possibly even a small decline.
+This decline may be the result of a combination of lower recall
+error, increasing age at marriage, and better health.
+
+The differences in duration across sex compositions are more 
+pronounced with higher-order spells.
+For the second spell, the difference in median duration between
+having a girl or a boy as the first-born are mostly between 0.5 and 1 
+month, although it varies from a low of 0.2 months for rural women 
+in 1995--2004 period to a high of 1.5 months
+for urban women in the 1985--1994 period.
+Focusing on rural women for the third spell, the difference is,
+on average, slightly over 1 months between only girls and only boys 
+and the differences are statistically significant in all periods.
+For rural women the differences for the fourth spell are just below
+2 months, with the exception of the 1972--1984 period, which is
+also the only period where the difference is not statistically significant.
+
+It is possible that remaining recall error is behind some of the
+smaller differences in duration.
+One example is the second spell in the 1995--2004 period, where there 
+are only 0.2 months difference between duration after one girl and 
+duration after one boy.
+Similarly, the small difference for the fourth spell in the 1972--1984
+period may be the result of recall error with a very high 
+percentage boys for women with three girls, despite no availability
+of sex selection.
+
+There are no clear time trends in the differences in median duration
+across sex compositions or the predicted sex ratios across the four periods.
+Despite some sex ratios that are statistically significantly higher 
+than the natural sex ratio there is therefore little consistent evidence 
+for the use of sex selection for women without education.
+There has, for example, been relatively little change in the length
+of spacing for rural women with two girls in the third spell and 
+the predicted sex ratio was higher in the 1985--1994 period
+than in the 2005--2016 period.
+The possible exception is the fourth spell, where both duration 
+and sex ratio has increased for women with three girls, although
+the \emph{difference} across sex compositions has remained almost
+the same.
 
@@
 \input{../tables/des_stat.tex}
+
+\clearpage
+
+\subsection{Additional Duration Results}
+
+\input{../tables/bootstrap_duration_p25_p75_low.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_med.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high.tex}
 

### 2018-03-10 paper/sexSelectionSpacing-ver1.tex
Discuss middle education duration and sex ratio results

@@
 Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
-\ref{tab:p25_p75_low} show 25th and 75th percentiles durations.
+\ref{tab:p25_p75_high} show 25th and 75th percentiles durations.
 } 
@@
 preference with shorter spacing when they have only girls compared 
-to when they have one or more sons, and the differences are often statistically 
-significant as shown in Table \ref{tab:median_sex_ratio_low}.
+to when they have one or more sons, and the differences are often 
+statistically significant as shown in Table \ref{tab:median_sex_ratio_low}.
 Most of the women without education live in rural areas,
@@
 Focusing on rural women for the third spell, the difference is,
-on average, slightly over 1 months between only girls and only boys 
+on average, slightly over one months between only girls and only boys 
 and the differences are statistically significant in all periods.
@@
 across sex compositions or the predicted sex ratios across the four periods.
-Despite some sex ratios that are statistically significantly higher 
+Despite that some sex ratios are statistically significantly higher 
 than the natural sex ratio there is therefore little consistent evidence 
@@
 
-For women with between 1 and 7 years of education it is harder
-to discern a pattern, partly because a larger number of area,
-sex composition, and periods combinations have relatively few 
-births in them.
-That said, the predicted median durations show less evidence 
-of son preference than for women without education.
-The exception to this are for the third spell for rural women
-for the 1972-1984 and 1985-1994 periods where the median
-durations are two and three months shorted with only girls
-compared to only boys, although the duration is longer for
-only girls in the 1995-2006 period.
-As for women with no education, there is little evidence of
-sex selection for women with 1 to 7 years of education,
-consistent with the absence of changes in relative durations
-across periods.
+Women with one to seven years of education follow a pattern
+broadly similar to those with no education as 
+Table \ref{tab:median_sex_ratio_med} shows.
+There is a more equal distribution in the number of women
+across urban and rural for this education group than for the
+no education women.
+As a result, the only spell where there are few women to base 
+results on are for the fourth spell for urban women and the first 
+period of the fourth spell for rural women.
+
+Spacing between births increased over the four decades.
+On average, the increase is approximately two months.
+The exception is again the first spell, where the time from
+marriage to first birth remained the same or fell slightly.
+
+In the period before sex selection became available, 1972--1985,
+the differences in spacing between only girls and only boys
+increase with spell number.
+For both urban and rural women the difference in duration
+is just over a month for the second spell, but for the
+third spell it is 1.4 and 2.3 months for urban and rural
+women, respectively.
+In the three later periods there is no clear pattern
+in the differences across sex compositions.
+
+The differences in duration between only girls and only boys 
+appear to decrease over time.
+The exception is for the two later periods where the
+differences are slightly larger in the last period compared
+with the second-to-last period.
+
+The decreases in differences are accompanied by increases
+in predicted sex ratios, some of which are statistically 
+significantly different from the natural sex ratio.
+Hence, even though the evidence is not strong, it does
+appear that women with one to seven years of education 
+have begun to use sex selection at higher-order spells.
+This is also consistent with the falling fertility for both
+urban and rural women shown below.
 
 \input{../tables/bootstrap_duration_sex_ratio_high.tex}
+
+Women with eight or more years of education appear the least likely
+to follow the pattern of shorter spacing when they have only girls
+compared to only boys before sex selection became available as 
+Table \ref{tab:median_sex_ratio_high} shows.
+Part of the problem may be that there are few women with that level
+of education for the 1972--1984 period.
+This means that only the results for the first and second spells in 
+both urban and rural areas are likely to be reliable.
+Furthermore, there are relatively few women with three boys who
+go on to having a fourth birth, both in urban and rural areas.
+
+The spacing between births increases substantially over time, especially
+for urban women. 
+Urban women show an increase in median duration of between a quarter
+and three-quarters of a year, whereas the increase for rural women is 
+mostly around a quarter of a year.
+The spacing between marriage and the first birth is still the
+exception, and for this group of women there is a decline of
+about a month for both urban and rural areas.
 

### 2018-03-11 paper/sexSelectionSpacing-ver1.tex
Discuss high education duration and sex ratio results

@@
 
-\title{Son Preference, Birth Spacing, and Sex-Selective Abortions%
+\title{Birth Spacing in the Presence of Son Preference and Sex-Selective Abortions:
+India's Experience over Four Decades%
 \protect\thanks{%
@@
 I would also like to thank Nalina Varanasi for research assistance.
-Support from the University of Washington Royalty Research Fund and the 
-Development Research Group of the World Bank is gratefully acknowledged.
+Support for development of the method from the University of Washington Royalty 
+Research Fund and the Development Research Group of the World Bank is gratefully 
+acknowledged.
 The views and findings expressed here are those of the author and
@@
 
-Spacing, by itself, can therefore no longer be used as a direct measure of 
-son preference.
-However, understanding birth spacing remains a critical undertaking.
+Spacing, by itself, is therefore no longer a valid direct measure of 
+son preference, but understanding birth spacing remains a critical undertaking.
 First, birth spacing is still useful in understanding son preference, 
@@
 and three-quarters of a year, whereas the increase for rural women is 
-mostly around a quarter of a year.
+around a quarter of a year.
 The spacing between marriage and the first birth is still the
@@
 about a month for both urban and rural areas.
+
+In urban areas, the increase in spacing with only girls is so 
+substantial that women with only girls have longer spacing to the 
+next birth than any of the other sex compositions from 1985 onward.%
+\footnote{
+The exception is the second spell for the 1985--1994 period, where women
+with one girl has 0.4 months longer spacing the women with one boy.
+}
+This reversal in the standard spacing pattern when there is strong
+son preference is substantial, especially for the third and fourth 
+spells.
+For the latest period the difference between only girls than the
+other sex compositions are between 3.4 and 5.4 months for the third
+and fourth spell.
+Furthermore, the differences are statistically significant, except
+for only boys for the fourth spell because few women have a fourth
+birth if they have three boys already.
+
+Rural women also show a reversal of the normal spacing pattern,
+although the changes are less pronounced than for urban women.
+The third spell show increasingly longer spacing with only
+girls compare to the other two sex compositions over time with
+most differences statistically significant, but the differences
+are smaller than for urban women.
+For the second spell there is little difference in spacing with
+one girl and with one boy and there are few rural women to 
+based the fourth spell results on.
+
+The predicted sex ratios at the end of the spells show that
+the reversal in spacing patterns is not the result of a declining son
+preference but rather corresponds to a substantially more male-biased 
+sex ratio.
+For urban women the predicted sex ratio with only girls 
+is consistently above 60\% boys for the third and fourth spells.
+For rural women the predicted sex ratios are lower than for urban
+women, but stil substantial and statistically significant at close 
+to 60\%.
+The high predicted sex ratios are presumably the result of increased 
+use of sex selection.
+
+When trying to understand the strength of son preference it is interesting
+that the sex ratio is also statistically significantly different
+from the natural rate in the case where women already have one
+son for the third and fourth spells.
+Again, the sex ratio in the presence of one son for the third and
+fourth spells are higher in urban areas than rural areas, although
+the difference is less than for women with only girls.
+Hence, it is possible that women are still willing to use sex selection
+even after giving birth to one. 
+Alternatively, this behavior may be in response to either experienced
+or expected mortality of the first son born.
+
+It also appears that there is a slightly elevated sex ratio among 
+first-born for urban women. 
+There is, however, no corresponding increase in spacing; rather
+the median duration has fallen over time and is the lowest among
+the three education groups.
+Hence, unless duration between marriage and first birth has decreased 
+substantially by itself, for example, because of improved health, it
+is not clear how much stock to place on the increased sex ratio
+among first-borns as evidence for sex selection among first-borns.
+
+Both of the last two results are different from prior studies using NFHS data.
+There are two potential explanations.
+First, NFHS-4 is substantially larger than the three prior surveys.
+Hence, it is possible that the effects have been there all along, but 
+we simply did not have the power to detect them.
+Second, it is possible that, at least, the first-born results are an
+artifact of any remaining recall error not captured by the data restrictions.
+Certain types of recall error would also explain why the sex ratio for
+the second spell is statistically significantly \emph{below} the
+natural sex ratio [TK cite my recall paper].
 

### 2018-03-12 paper/sexSelectionSpacing-ver1.tex
Parity progression survival curves and minor edits

@@
 \setmathfont{TeX Gyre Pagella Math}
-% \usepackage{mathpazo}
 \usepackage[title]{appendix}
@@
 \usepackage{setspace}
-% \usepackage{xyling}
 \usepackage[justification=centering]{caption}
@@
 
+\subsection{No Education Women}
+
 \input{../tables/bootstrap_duration_sex_ratio_low.tex}
@@
 
+\subsection{Middle Education Women}
+
 \input{../tables/bootstrap_duration_sex_ratio_med.tex}
@@
 urban and rural women shown below.
+
+\subsection{High Education Women}
 
@@
 Second, it is possible that, at least, the first-born results are an
-artifact of any remaining recall error not captured by the data restrictions.
+artifact of any recall error not captured by the data restrictions.
 Certain types of recall error would also explain why the sex ratio for
-the second spell is statistically significantly \emph{below} the
-natural sex ratio [TK cite my recall paper].
+the second spell and one boy is statistically significantly \emph{below} 
+the natural sex ratio [TK cite my recall paper].
 
 \subsection{Differences in Survival Curves Across Sex Compositions}
+
+% First spell for low and high education women
+% Might not fit very well here - maybe main point to discussion above and refer to Appendix
+
+\begin{figure}[htpb]
+\centering
+\setcounter{subfigure}{-1}
+\subfloat[Rural Women with No Education]{
+    \begin{minipage}{0.48\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[Urban Women with 8 or More Years of Education]{
+    \begin{minipage}{0.48\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption{
+Survival curves conditional on progression to first birth; start point is time of marriage.
+}
+\label{fig:pps_spell1}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption{
+Survival curves conditional on progression to TK
+}
+\label{fig:pps_low}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.46\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption{
+Survival curves conditional on progression to TK
+}
+\label{fig:pps_high}
+\end{figure}
+
+\subsection{Does Sex Selection Change within Spells?}
 
@@
 not, for example because they already have one or more sons.
-
-\subsection{Does Sex Selection Change within Spells?}
 
@@
 % Low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-}
-\label{fig:results_spell2_low_pps}
-\end{figure}
 

### 2018-03-14 paper/sexSelectionSpacing-ver1.tex
Add to conditional spacing results

@@
 
-\subsection{Differences in Survival Curves Across Sex Compositions}
+\subsection{Distribution of Spacing Across Sex Compositions and Time}
+
+Median spacing is a convenient way to understand the major developments,
+but may hide important changes in the distribution of spacing.
+This section therefore provides more detail on how spacing is distributed
+over time and over sex compositions using a graphical approach.
+
+I show survival curves conditional on parity progression rather than
+standard survival curves. 
+The advantage of this approach is that it is possible to directly compare 
+the distribution of spacing to next birth, independently of differences in
+how likely the next birth is across groups.
+In other words, these results reflect the spacing we should observe once
+all childbearing is over for the women in the sample.
+Because the conditional survival curves are independent of the likelihood
+of parity they all begin at 100\% and end at 0\%.
+
+Instead of averaging across the entire sample, I calculate the conditional
+survival curves for a representative woman using the method detailed in 
+Section \ref{sec:strategy}.
+The representative woman characteristics are the means of continuous explanatory 
+variables and the majority category for categorical explanatory variables.
+Common to all representative women is that they do not own land and belong to neither 
+a scheduled caste nor a scheduled tribe.
+
+In the interest of space, I discuss only a representative subset.
+Figure \ref{fig:pps_spell1} shows spacing within the first spell across the
+four periods for rural women with no education and for urban women with 
+eight or more years of education.
+Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex
+compositions for the second, third, and fourth spells for the first period, 
+1972--1984, and the last period, 2005--2016, for rural women with no 
+education and urban women with eight or more years of education.
+Standard and conditional survival curves for all groups and time periods 
+are shown in the Appendix, and I discuss some examples of standard survival
+curves in the following section.
 
 % First spell for low and high education women
-% Might not fit very well here - maybe main point to discussion above and refer to Appendix
 
@@
 \caption{
-Survival curves conditional on progression to first birth; start point is time of marriage.
+Survival curves conditional on progression to first birth; start point is month of marriage
 }
@@
 \end{figure}
+
+The duration from marriage to first birth is only affected by son preferences if
+people use sex selection to achieve a son as their first-born.
+As I discuss above, the biased sex ratio for the first spell for the most educated 
+women does suggest that there might be sex selection on the first birth.
+I therefore begin by comparing in Figure \ref{fig:pss_spell1} how the distribution 
+of spacing has changed over time for rural women with no education and urban women 
+with eight or more years of education.
+What is most striking is how similar the distribution of spacing is across the
+two groups.
+
+Both groups show little change in median spacing, but that masks a substantial
+compression of when most of the births occur.
+In the 1972--1984 period the middle 80\% of births for women with no education 
+are predicted to occur between approximately 6 and 52 months, whereas in the 
+2005--2016 period it is between 12 and 46 months.
+This is equivalent to a compression of a full year.
+Women with eight or more years of education show a slightly smaller compression:
+in the 1972--1984 period the middle 80\% of births are predicted to occur between
+approximately 6 and 44 months, whereas in the 2005--2016 period it is between
+9 and 40 months, or a compression of seven months.
+
+The pattern for both groups shows us that women are less likely to conceive 
+before marriage in the later time periods than earlier.
+In the first two periods there was a relatively smooth decline in number of
+women without a birth starting at the time of marriage, but in the last two
+periods there is now few women exiting early after marriage and instead a 
+substantial dip between 9 and 12 months after marriage.
+
+It is likely that the compressed spacing, beginning at nine months
+after marriage in the later periods, is associated with better health
+and higher age at marriage.
+The descriptive statistics above show, for example, that women without 
+education has seen an increase in the average age at marriage from below 
+16 to 18.5 from the first period to the last while women with the most 
+education increased from 19.5 to 20.4.
 
@@
 \caption{
-Survival curves conditional on progression to TK
+Survival curves conditional on progression to next birth for rural women without
+education; start point for each spell is nine months after prior birth
 }
@@
 \end{figure}
+
+For women with no education Figure \ref{fig:pps_low} shows that the median results
+above are consistent with the distribution of spacing within a spell with spacing 
+after only girls consistently shorter than after only boys.
+There are slight variations in how strong this effect is across the three spells.
+On the one had, for the second spell the difference in spacing between first child a girl 
+versus first child a boy as first-born remains almost the same across the four
+decades.
+On the other hand, for the third spell the differences between two girls and 
+the other sex compositions become more pronounced over time, and especially
+the difference between two girls and two boys have become substantially larger.
+The fourth spell results are based on relatively few observations, but do indicate
+that only girls and two girls and one boy is associated with shorter spacing than
+only boys or one girl and two boys.
+Although the evidence is not overly strong, it does appear that there is a slight
+preference for two boys in the sense that spacing becomes longer once the couple
+has at least two boys than for the other sex compositions.
 
@@
 \caption{
-Survival curves conditional on progression to TK
+Survival curves conditional on progression to next birth for urban women with eight or
+more years of education; start point is nine months after prior birth
 }
@@
 \end{figure}
+
+What is most remarkable about the second spell conditional survival curve for 
+urban women with eight or more years of education, shown in Figure \ref{fig:pps_high}, 
+is that the distribution of spacing is almost indistinguishable from that of rural 
+women with no education for the 1972--1984 period.
+This points to these two very different groups of women behaving in a similar fashion
+in response to son preference in a situation where there was little access to
+prenatal sex determination or little incentive to use it early even for those 
+who might have had access.
+Whereas the no education group show almost no change across the four decades,
+the high education women show a rightward shift if the spacing pattern when
+the first child is a girl.
+The result is that the spacing patterns are close to identical for the first-born 
+a girl and the first-born a boy.
 
@@
 \end{figure}
-
-% Survival curves conditional on progression
-
-Figures \ref{fig:results_spell2_low_pps} and \ref{fig:results_spell2_high_pps}
-show survival curves for the second spell (from first birth) for women with
-no education and women with 8 or more years of education.
-To allow for comparison these survival curves show the ratio of women who
-have not had a birth yet, given that they will eventually are predicted to
-have a birth.
-Women with no education show relatively similar survival curves whether their
-first child was a girl or a boy, but to the extent that a pattern is present
-it shows, as expected, shorter spacing a girl than a boy.
-Rural women with 8 or more years of education show essentially the same 
-pattern.
-The lack of clear results is not surprising given that all three groups of
-women are likely to have more than two children.
-
-The effect of sex selection on spacing first show up for urban women with
-8 or more years of education.
-Panel (a) in Figure \ref{fig:results_spell2_high_pps} show shorter spacing
-for the second spell when the first child is a girl than a boy, and this
-pattern is also present in Panel (b).
-Panel (c) on the other hand show first evidence of \emph{longer} spacing 
-after the birth of a girl than after a boy, consistent with the male-biased
-sex ratio in Panel (c) in Figure \ref{fig:results_spell2_high_urban}.
-
-% Low education
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_pps}
-\end{figure}
-
-% 3rd spell
-
-% Low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_low_pps}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_high_pps}
-\end{figure}
-
-The effect of sex selection on spacing is even more pronounced in
-Figure \ref{fig:results_spell3_high_pps}, which shows the conditional
-survival curves for the third spell (from second birth) for women with
-8 or more years of education.
-Before prenatal sex determination became available there is little difference
-in spacing pattern no matter the sex composition of the first two children.
-This changes after the introduction as shown in Panel (b), where the spacing
-is longer when the first two children are girls than either one boy/one girl
-or two boys.
-Even more substantial are the results from Panel (c), which shows much 
-longer spacing when the first two children are girls.
-These results are consistent with the biased sex ratios shown in 
-Figure \ref{fig:results_spell3_high_urban}.
 

### 2018-03-14 paper/sexSelectionSpacing-ver1.tex
Add high education conditional survival curve results

@@
 
-What is most remarkable about the second spell conditional survival curve for 
-urban women with eight or more years of education, shown in Figure \ref{fig:pps_high}, 
-is that the distribution of spacing is almost indistinguishable from that of rural 
-women with no education for the 1972--1984 period.
+The distribution of spacing, shown in Figure \ref{fig:pps_high}, for the second spell 
+conditional survival curve for urban women with eight or more years of education 
+is almost indistinguishable from that of rural women with no education 
+for the 1972--1984 period.
 This points to these two very different groups of women behaving in a similar fashion
@@
 who might have had access.
+
 Whereas the no education group show almost no change across the four decades,
@@
 the first child is a girl.
-The result is that the spacing patterns are close to identical for the first-born 
-a girl and the first-born a boy.
+The result is that the spacing patterns are close to identical after first-born 
+girls and after first-born boys.
+Given the elevated predicted percentage boys show in Table 
+\ref{tab:median_sex_ratio_high} this change is consistent with use of 
+sex selection for women with a girl as their first child.
+
+The hypothesized correlation between use of sex selection and reversal of 
+the standard spacing pattern show up clearly in the 2005--2016 period for the 
+third spell with spacing to the third child consistently longer with two girls 
+than with either two girls or one boy and one girl.
+The rightward movement for only girls from the, mostly, standard pattern in 
+the 1972--1984 period to the new pattern in the 2005--2016 period is substantial.
+There is also indications that the spacing distribution has moved rightward
+for women with one boy and one girl relatively to women with two boys, which
+provides some evidence for use of sex selection for this group.
+The caveat is that the 1972--1985 period also had an biased sex ratio, which
+points to uncorrected recall error for this group.
+
+There is a even more pronounced rightward shift for spacing after only girls
+in the fourth spell, although these results are based on fewer births, especially
+for women with two or more sons.%
+\footnote{
+As mentioned, it is possible that some women had access to sex selection even
+in the first period.
+I would expect well educated urban women with more children to be the
+most likely to know about and use this early access to prenatal sex determination.
+}
+Furthermore, the differences are large across most of the distribution.
+Twelve months after the beginning of the spell there is an approximately ten 
+percentage points difference in the conditional survival curves for only girls
+and only boys.
+That is, of the women who are predicted to have a fourth child just over 30\%
+of women with three boys have had their fourth child, while less than 20\% of
+those with three girls have had theirs.
+Even at three years after the spell there is a more than five percentage
+points difference.
+
+As discussed above there is some evidence of a two-son preference with
+the spacing pattern almost the same for women with three boys and with
+two boys and one girl.
+The conditional survival curve for women with one boy and two girls is
+consistently above those with two or more son, but below those with
+three girls.
+This fit the predicted sex ratios shown above where the highest
+predicted sex ratio is for women with only girls, followed by those
+with one son and two girls, and those with two or more boys having
+almost the same sex ratio.
 
 \subsection{Does Sex Selection Change within Spells?}
+
+[
+
+using conditional survival curves forces everybody to finish at the 
+same month.
+How many births are there?
+We can show that using standard survival curves.
+The flatter the curve the fewer births.
+
+72 months = 6 years, plus the 9 months from the previous birth.
+]
 

### 2018-03-15 paper/sexSelectionSpacing-ver1.tex
Intro on changing sex ratios within spell and delete unneeded graphs

@@
 
-[
-
-using conditional survival curves forces everybody to finish at the 
-same month.
-How many births are there?
-We can show that using standard survival curves.
-The flatter the curve the fewer births.
-
-72 months = 6 years, plus the 9 months from the previous birth.
-]
-
-[Moved from estimation strategy]
+The results so far show that as sex ratios have become more
+male-biased the spacing when a woman has only girls have become 
+longer relative to other sex compositions, presumably because
+of increased use of sex selection rather than because of a
+change in the degree of son preference.
+Neither the median spacing or the conditional survival curves
+can, however, provide us with information on how the use of
+sex selection vary \emph{within} a spell.
+Furthermore, using conditional survival curves forces everybody 
+to finish the spell in the same month and does not provide
+any information about how many births there are.
+We can, however, learn something about both changes in 
+sex selection within a spell and the likelihood of exiting
+with a birth using standard  survival curves.
+
 In the absence of sex selection, I expect most parities to follow
@@
 parity between women who are likely to use sex selection and women who are
-not, for example because they already have one or more sons.
+not, for example because they already have achieved their desired 
+number of sons.
+
+The flatter the curve the fewer births.
 
 \section{Discussion}
+
+[conditional survival curves]
+72 months = 6 years, plus the 9 months from the previous birth.
 
@@
 
-Figure \ref{fig:results_spell2_high_urban} 
-shows the predicted probabilities of having a boy and standard survival curves
-for the three periods for urban women with 8 or more years of education.%
-\footnote{
-The corresponding graphs for rural women and for women with no education are
-shown in Figures \ref{fig:results_spell2_high_rural}, \ref{fig:results_spell2_low_urban},
-and \ref{fig:results_spell2_low_rural}
-}
-Two main results stand out.
-First, women whose first child was a boy do not appear to use sex selection during
-the second spell.
-The predicted percent boys is consistently close to the natural level in all three
-panels (\ref{fig:results_spell2_high_urban}(d)-(f)).
-Second, as prenatal sex determination became available there is more and more
-evidence of sex selection affecting the sex ratio for women with a girl as their
-first child.
-In panel (a), which covers the period before sex selection became generally
-available, there is no significant evidence of a sex ratio biased towards males.
-Panel (b) shows a more male biased sex ratio but only a few months show
-a statistically significant difference from the natural rate and the shallow 
-slope of the survival curve indicates that relatively few births took place
-during these months.
-Panel (c), however, shows clear evidence of the effect of access to prenatal
-sex determination with a male biased sex ratio for more of the two first years.%
-\footnote{
-Recall that month 0 is equivalent to 9 months after the birth
-of the first child.
-}
-
 % High education
@@
 \appendix
-\section{Appendix}
+\section{Online Appendix}
 
@@
 \renewcommand\thefigure{\thesection.\arabic{figure}}    
+\renewcommand\thetable{\thesection.\arabic{table}}
+
 \setcounter{figure}{0}
-\renewcommand\thetable{\thesection.\arabic{table}}    
 \setcounter{table}{0}
@@
 
-\subsection{Additional Duration Results}
+\section{Additional Duration Results}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
 
@@
 
-\subsection{Second Spell}
-
-% SPELL 2 - URBAN - LOW
-\begin{figure}[h]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=1,596)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=2,232)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=952)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=1,754)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=2,411)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=930)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with no education by month beginning 9 months after prior birth. 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_low_urban}
-\end{figure}
-
-% SPELL 2 - rural - LOW
-\begin{figure}
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972-1984 (N=8,426)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985-1994 (N=11,481)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[1995-2006 (N=3,686)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972-1984 (N=9,395)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985-1994 (N=12,127)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995-2006 (N=3,860)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural 
-women with no education by month beginning 9 months after prior birth. 
-Predictions based on age 18 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_low_rural}
-\end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{First child a girl}
-% \setcounter{subfigure}{-2}
-% \subfloat[1972--1984 (N=2,689)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-1}
-% \subfloat[1985--1994 (N=4,869)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{0}
-% \subfloat[1995--2006 (N=3,774)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{First child a boy}
-% \setcounter{subfigure}{1}
-% \subfloat[1972--1984 (N=2,806)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{2}
-% \subfloat[1985--1994 (N=5,246)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{3}
-% \subfloat[1995--2006 (N=3,969)]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Predicted probability of having a boy and probability of
-% no birth yet from nine months after first birth for urban 
-% women with 8 or more years of education by month beginning 9 months after prior birth. 
-% Predictions based on age 22 at first birth.
-% Left column shows results prior to sex selection available, middle column before
-% sex selection illegal and right column after sex selection illegal.
-% N indicates the number of women in the relevant group in the underlying samples.
-% }
-% \label{fig:results_spell2_high_urban}
-% \end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=1,305)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=3,105)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=2,823)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,404)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=3,381)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,044)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_rural}
-\end{figure}
-
-\clearpage
-
-\subsection{Third Spell}
-
-% low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=493)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=996)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=475)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,083)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=2,141)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=950)]{
-    \begin{minipage}{0.26\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_low_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=569)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,124)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=426)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell3_low_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,599)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=5,062)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,879)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=5,382)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=10,473)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,779)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_low_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=3,070)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=5,339)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=1,846)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with no of education by month beginning 9 months after prior birth. 
-Predictions based on age 21 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell3_low_rural}
-\end{figure}
-
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=709)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=1,654)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=1,000)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=1,409)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=3,460)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=2,357)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_high_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\ContinuedFloat
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=780)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=1,660)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=1,098)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-% \label{fig:results_spell3_high_urban}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\caption*{First two children girls}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=348)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_gg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=982)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=863)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_gg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First two children one boy and one girl}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=700)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bg_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=1,987)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=1,819)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell3_high_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\ContinuedFloat
-\centering
-\caption*{First two children boys}
-\setcounter{subfigure}{4}
-\subfloat[1972--1984 (N=370)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_bb_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{5}
-\subfloat[1985--1994 (N=945)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[1995--2006 (N=790)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bb_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{(Continued) Predicted probability of having a boy and probability of
-no birth yet from nine months after second birth for rural
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 24 at second birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-% \label{fig:results_spell3_high_rural}
-\end{figure}
-
-\clearpage
-\newpage
-
 \end{document}

### 2018-03-19 paper/sexSelectionSpacing-ver1.tex
Add example graphs for how sex ratio change within spell

@@
 
-The results so far show that as sex ratios have become more
-male-biased the spacing when a woman has only girls have become 
+The results so far show that as sex ratios became more
+male-biased the spacing when a woman has only girls became 
 longer relative to other sex compositions, presumably because
-of increased use of sex selection rather than because of a
-change in the degree of son preference.
+of increased use of sex selection rather than a reduction in son preference.
 Neither the median spacing or the conditional survival curves
@@
 with a birth using standard  survival curves.
+
+The predicted sex ratio may change within a spell for, at
+least, two reasons.
+First, parents may stop using prenatal sex determination 
+once the duration from the previous birth becomes long enough
+because they prefer not to have their children too far apart.
+In this case we should observe the predicted sex ratio decline
+with spell length.
+Second, if the degree of son preference vary within the sample
+but behavior is not affected by duration from the previous birth,
+we should observe an increasing share of births come from 
+parents with stronger son preference as duration from the
+previous birth increases.
+Whereas the early births are a combination of births to
+people with lower son preference and those with stronger son
+preference who conceived a son in the first or second pregnancy,
+later births are then predominately from those with stronger
+son preference who have not yet conceived a son.
+Hence, in this case we should see an increase in the sex ratio 
+as duration increases.
+
+% Examples of declining sex ratios
+
+\begin{figure}[htpb!]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{Urban}}
+\setcounter{subfigure}{-2}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{-1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Rural}}
+\setcounter{subfigure}{0}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of 
+no birth yet from nine months after first birth for women with a girl
+as their first child and eight or more years of education 
+for the 1995--2004 and 2005--2016 periods
+} 
+\label{fig:decreasing_sex_ratio} 
+\end{figure}
+
+% Examples of increasing sex ratios
+
+\begin{figure}[htpb!]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
+\setcounter{subfigure}{-2}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{-1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
+\setcounter{subfigure}{0}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of 
+no birth yet from nine months after second birth for urban women with
+eight or more years of education 
+for the 1995--2004 and 2005--2016 periods
+} 
+\label{fig:decreasing_sex_ratio} 
+\end{figure}
+
+\section{Discussion}
 
@@
 
-The flatter the curve the fewer births.
-
-\section{Discussion}
-
 [conditional survival curves]
@@
 
-% High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{First child a girl}
-\setcounter{subfigure}{-2}
-\subfloat[1972--1984 (N=2,689)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-1}
-\subfloat[1985--1994 (N=4,869)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{0}
-\subfloat[1995--2006 (N=3,774)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{First child a boy}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984 (N=2,806)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[1985--1994 (N=5,246)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{3}
-\subfloat[1995--2006 (N=3,969)]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of
-no birth yet from nine months after first birth for urban 
-women with 8 or more years of education by month beginning 9 months after prior birth. 
-Predictions based on age 22 at first birth.
-Left column shows results prior to sex selection available, middle column before
-sex selection illegal and right column after sex selection illegal.
-N indicates the number of women in the relevant group in the underlying samples.
-}
-\label{fig:results_spell2_high_urban}
-\end{figure}
-
 \section{Conclusion\label{sec:conclusion}}

### 2018-03-20 paper/sexSelectionSpacing-ver1.tex
Fix figure reference
Discuss changes in sex ratios results

@@
 with a birth using standard  survival curves.
-
 The predicted sex ratio may change within a spell for, at
 least, two reasons.
+
+\begin{figure}[htpb!]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{Urban}}
+\setcounter{subfigure}{-2}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{-1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Rural}}
+\setcounter{subfigure}{0}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of 
+no birth yet from nine months after first birth for women with a girl
+as their first child and eight or more years of education 
+for the 1995--2004 and 2005--2016 periods
+} 
+\label{fig:decreasing_sex_ratio} 
+\end{figure}
+
+\begin{figure}[htpb!]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
+\setcounter{subfigure}{-2}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{-1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
+\setcounter{subfigure}{0}
+\subfloat[1995--2004]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\setcounter{subfigure}{1}
+\subfloat[2005--2016]{
+   \begin{minipage}{0.39\textwidth}
+       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_pc}}\\
+       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_s}}
+       \captionsetup[subfigure]{labelformat=parens}
+   \end{minipage}
+}
+\caption{Predicted probability of having a boy and probability of 
+no birth yet from nine months after second birth for urban women with
+eight or more years of education 
+for the 1995--2004 and 2005--2016 periods
+} 
+\label{fig:increasing_sex_ratio} 
+\end{figure}
+
 First, parents may stop using prenatal sex determination 
@@
 with spell length.
-Second, if the degree of son preference vary within the sample
+
+Second, if the degree of son preference across women within the sample
 but behavior is not affected by duration from the previous birth,
@@
 
-% Examples of declining sex ratios
-
-\begin{figure}[htpb!]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Urban}}
-\setcounter{subfigure}{-2}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Rural}}
-\setcounter{subfigure}{0}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of 
-no birth yet from nine months after first birth for women with a girl
-as their first child and eight or more years of education 
-for the 1995--2004 and 2005--2016 periods
-} 
-\label{fig:decreasing_sex_ratio} 
-\end{figure}
-
-% Examples of increasing sex ratios
-
-\begin{figure}[htpb!]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
-\setcounter{subfigure}{-2}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
-\setcounter{subfigure}{0}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of 
-no birth yet from nine months after second birth for urban women with
-eight or more years of education 
-for the 1995--2004 and 2005--2016 periods
-} 
-\label{fig:decreasing_sex_ratio} 
-\end{figure}
-
-\section{Discussion}
+Figures \ref{fig:decreasing_sex_ratio} and \ref{fig:increasing_sex_ratio} show
+examples of how sex ratio behave within spells.
+Both are for women with eight or more education since the results above indicate
+that they are the most likely to use sex selection or other means of achieving 
+an unequal sex ratio.
+Figure \ref{fig:decreasing_sex_ratio} shows results for the second spell for
+the 1995--2004 and 2005--2016 periods for women with a girl as their first
+child by area of residence.
+Figure \ref{fig:increasing_sex_ratio} shows results for the third spell for
+the same two periods for urban women with either two girls or one boy and one
+girl as their first two children.%
+\footnote{
+There is no evidence of unequal sex ratios in either period for similar women 
+with two boys as their first two children as shown in Figure TK.
+}
+
+Within the second spell, both urban and rural women show a declining
+sex ratio as duration increases for the 1995--2004 period, whereas there
+is little change, or possibly a small increase, with duration for the 
+2005-2016 period.
+These results are consistent with a situation where fertility is declining
+over time leaving less room for a change in the decision to use sex selection.
+Fertility decline is not immediately obvious from the second spell 
+results, but the third spell show that the likelihood of progressing from
+two to third children declines by approximately 15 percentage points if
+the woman has given birth to a boy, and, as the Appendix shows, only about 
+25\% of urban women with two boys have a third child in the 2005--2016 period, 
+down from close to 40\% in the 1995--2004 period. 
+Furthermore, it is unlikely that a substantial number of births will take
+place after the end of the spell period, which is equal to six year in
+addition to the nine months from the previous birth to the start of the spell.
+
+The third spell figures show a very different situation with almost no 
+change in sex ratios with duration for women with two girls, but substantial 
+increases in sex ratios with duration for women with one boy and one girl.
+The high, but stable, sex ratio for women with two girls is likely 
+motivated by the combined desire to limit fertility and ensure a son;
+similarly to the situation for the second spell as shown in 
+Figure \ref{fig:decreasing_sex_ratio} (b) and (d).
+
+The increase in sex ratio with duration for women who already have
+given birth to a boy likely illustrates the case where there are a
+combination of degrees of son preference.
+Say that one group wants one son and after that will not use sex
+selection, whereas another group has a strong preference for two
+sons (or either have or expect to lose the boy they already have)
+and that the two groups conceive at the same rate.
+In that case, we should expect exactly the increasing sex ratios
+we observe, especially given the declining fertility over time.
+
+\section{Conclusion\label{sec:conclusion}}
+
+[To be added]
 
@@
 
-[conditional survival curves]
-72 months = 6 years, plus the 9 months from the previous birth.
-
-[TK not sure where this fits in]
-In addition, it is possible that falling fertility also generically 
-leads to longer spacing between births.
-This means that we have to separate out which part of the longer
-spacing comes from falling fertility (and therefore should also
-affect boy composition) and which parts comes from increased use
-of sex selection.
-
-[We should expect sex selection to be mainly used for the last---or close to
-last---birth that a couple expect to have because of the cost and risk
-of the procedures.]
-
 [TK not sure where to fit this into]
@@
 
-\section{Conclusion\label{sec:conclusion}}
-
-[To be added]
-
 \clearpage
@@
 \appendix
-\section{Online Appendix}
+\section{Descriptive Statistics}
 

### 2018-03-21 paper/sexSelectionSpacing-ver1.tex
Better explanation of why changes within spell interesting

@@
 \citep{Sudha1999}.
-Maharashtra was the first state to pass a similar law in 1988.
+Furthermore, there is little evidence that bans like this significantly
+affect sex ratios \citep{Das-Gupta2016}.
 }
@@
 
-Finally, do parents change their decision on sex selection within a spell?
+Finally, does the sex ratio change within a spell?
 There are two reasons why this is interesting.
-If parents change their mind the standard method of observing sex ratios 
-will not capture the full extent of the use of sex selection.
-Furthermore, it tells us something about parents' preferences for ideal
-spacing between births and how strong their son preference is.
+First, if the sex ratio changes within a spell simply using the observed sex
+ratio at birth---as is standard practice in the literature---will not provide
+correct estimates of the use of sex selection or the sex ratio when child
+bearing is completed.
+Second, the development in the sex ratio within a spell provides clues
+to parents' preferences over the ideal spacing between births and the
+distribution of son preference in the sample.
 
@@
 Second, if the degree of son preference across women within the sample
-but behavior is not affected by duration from the previous birth,
+but behavior is not affex2cted by duration from the previous birth,
 we should observe an increasing share of births come from 

### 2018-03-21 paper/sexSelectionSpacing-ver1.tex
Future research for conclusion

@@
 Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful suggestions and comments.
+and Economic Development, and the Economic Demography Workshop for helpful 
+suggestions and comments.
 I would also like to thank Nalina Varanasi for research assistance.
@@
 after boys?
-The underlying hypothese is that in the absence of sex selection son 
+The underlying hypothesis is that in the absence of sex selection son 
 preference leads to shorter spacing after the birth of a girl than after the 
@@
 of a girl relative to after the birth of a boy when prenatal sex selection is 
-used.
-We would still expect parents to \emph{try} to conceive earlier after the birth 
+available.
+I still expect parents to \emph{try} to conceive earlier after the birth 
 of a girl than after a boy, but the abortions will increase the 
@@
 with access to sex selection.
-At a more technical level, the shapes of the survival curve serve as an
+At a technical level, the shapes of the survival curve serve as an
 indicator for the presence of non-proportionality.
@@
 
-\subsection{Distribution of Spacing Across Sex Compositions and Time}
+\subsection{Distribution of Birth Spacing Across Sex Compositions and Time}
 
@@
 
-In the interest of space, I discuss only a representative subset.
+In the interest of brevity, I discuss only a representative subset.
 Figure \ref{fig:pps_spell1} shows spacing within the first spell across the
@@
 
+The reversal have some weird side effects.
+Because there is now longer spacing after girls and this is when
+we should observe sex selection we can get an less unequal 
+sex ratio in the survey data than what we will eventually observe.
+
+This points to two important questions for future research:
+What is the role of falling fertility in the use of sex selection
+and is the use of sex selection increasing or decreasing over time?
+[more on how to analyze those]
+
+The results here lead to a host of larger important questions that
+needs to be addressed.
+
+First, to what extent are the improvements in health for girls
+relative to boys the result of selection, longer spacing between
+births, or changing son preference?
+
+Second,
+
+This suggestion that an overlooked approach to addressing a biased
+sex ratio may be to encourage higher female labor force participation.
+In addition to the obvious benefit to the women in terms of 
+bargaining power, it also increases the cost of repeated 
+sex-selective abortions.
+[Caveat, it also lowers fertility, and everything else equal that
+would may lead to higher use of sex selection]
+
+[Stuff to add somewhere in the paper]
+
 In the absence of sex selection, I expect most parities to follow
@@
 \appendix
-\section{Descriptive Statistics}
 
@@
 
+\section{Descriptive Statistics}
 \setcounter{figure}{0}

### 2018-03-21 paper/sexSelectionSpacing-ver1.tex
Add additional references

@@
 births of girls than boys 
-\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012}.
+\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012,Rossi2015}.
 Shorter spacing is, in turn, associated with worse health outcomes for girls 
-\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
+\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.%
 \footnote{
@@
 a son than after a daughter 
-\citep{ben-porath76b,Das1987,Arnold1997,clark00,filmer09,Altindag2016}.
+\citep{ben-porath76b,Das1987,Arnold1997,clark00,filmer09,Basu2010,Altindag2016}.
 }
@@
 
-Spacing, by itself, is therefore no longer a valid direct measure of 
+Spacing, by itself, can therefore no longer be used as a direct measure of 
 son preference, but understanding birth spacing remains a critical undertaking.
@@
 across education groups \citep{Tulasidhar1993,Whitworth2002}.
+It may also explain why finding statistically significant
+effects of contraception use on birth spacing is difficult \citep{Yeakey2009}.
 

### 2018-03-23 paper/sexSelectionSpacing-ver1.tex
References on spacing and maternal health

@@
 Shorter spacing is, in turn, associated with worse health outcomes for girls 
-\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.%
+and mothers 
+\citep{arnold98,Conde-Agudelo2000,Whitworth2002,Razzaque2005,Rutstein2005,Conde-Agudelo2006}.%
 \footnote{
@@
 
-The introduction of prenatal sex determination fundamentally changed the 
+But, the introduction of prenatal sex determination fundamentally changed the 
 relationship between son preference and birth spacing.
@@
 
-[To be added]
-
-The reversal have some weird side effects.
-Because there is now longer spacing after girls and this is when
-we should observe sex selection we can get an less unequal 
-sex ratio in the survey data than what we will eventually observe.
+The main question addressed here is the extent to which spacing patterns 
+significantly changed as prenatal sex determination became available,
+specifically, did the spacing after girls increase relative to the spacing
+after boys?
+The underlying idea is that in the absence of sex selection son 
+preference leads to shorter spacing after the birth of a girl than after the 
+birth of a boy, whereas son preference increases the spacing after the birth 
+of a girl relative to after the birth of a boy when prenatal sex selection is 
+available.
+The four rounds of India's NFHS provide strong support for the hypothesis.
+
+Censoring is an important issue when trying to understand the development
+in sex ratio, especially when it comes to establishing whether the
+use of sex selection is increasing or decreasing.
 

### 2018-03-23 paper/sexSelectionSpacing-ver1.tex
Full draft of conclusion

@@
 The main question addressed here is the extent to which spacing patterns 
-significantly changed as prenatal sex determination became available,
-specifically, did the spacing after girls increase relative to the spacing
+significantly changed as prenatal sex determination became available.
+Specifically, did the spacing after girls increase relative to the spacing
 after boys?
@@
 available.
-The four rounds of India's NFHS provide strong support for the hypothesis.
-
-Censoring is an important issue when trying to understand the development
-in sex ratio, especially when it comes to establishing whether the
-use of sex selection is increasing or decreasing.
-
-This points to two important questions for future research:
-What is the role of falling fertility in the use of sex selection
-and is the use of sex selection increasing or decreasing over time?
-[more on how to analyze those]
-
-The results here lead to a host of larger important questions that
-needs to be addressed.
-
+I introduce a new method that simultaneously account for spacing between
+births and the potential use of sex selection and apply the method
+to over four decades of data from India's NFHS.
+The results show two very different approaches to son preference.
+
+At one extreme, women without education mostly follow the standard 
+pattern of shorter spacing when a woman does not have the desired number of 
+son and with limited evidence of biased sex ratios and the increases in
+spacing that should follow from the use of sex selection.
+The situations where there are elevated sex ratios for women without
+education---which, by itself, should indicate use of sex selection---the
+spacing patterns are too close to the ones without sex selection that 
+it is difficult to conclude that the changes in sex ratios indicate
+sex selection rather than normal variation or problems with recall errors.
+
+At the other extreme, women with eight or more years of education have
+experienced an almost complete reversal of their spacing patterns.
+Rather than having the next birth sooner as they mostly did before 
+sex selection became available, women with either no or one son now 
+have substantially longer spacing than if they have two or more sons.
+That these changes are likely due to increased use of sex selection 
+rather than changes in son preference as shown by the increasingly
+significant deviations in the sex ratio from the natural sex ratio.
+
+Over the last 40 years there has been a general increase in median
+spacing for all education groups, but especially for the most 
+educated women.
+The exception is for the spacing between marriage and first birth
+where there are two counteracting forces: women have become more likely 
+to conceive after marriage and there has been a substantial compression 
+in the variation.
+The end result is that median spacing from marriage to first birth
+that has changed little or even declined for the best educated women.
+
+The empirical model is designed to allow for the effects of covariates
+to change within the spell.
+This is important because the use of sex selection is likely to vary
+within a spell, either because preferences for spacing between births
+that is not too long override the preference for sons or because
+of selection where the women who remain in a spell are those with
+the strongest son preference who have been through multiple 
+pregnancies that were aborted because the fetus was female.
+Because these move in opposite directions it is difficult to 
+establish the extent to which they affect the results.
+Both are, however, clearly present as can be seen from the
+cases where there is either a decline in sex ratio with spell
+duration or a substantial increase with spell duration.
+The first case is more likely at lower parities where there
+is still less pressure to ensure a son, which allows any
+preference for shorter spacing to play more of a role.
+The second is on the other hand more likely to have an effect
+for higher parities where the desire to limit further
+childbearing and ensure a son dominates any preferences for
+shorter spacing.
+
+The potential for changes in sex ratio within a spell means
+that censoring is an important issue when trying to understand the development
+in sex ratio.
+This is especially the case when it comes to establishing whether 
+the use of sex selection is increasing or decreasing.
+Take, for example, the case of women with eight or more years of
+education in the last period. 
+If we look at women who started their third spell in either the
+2005--2009 or the 2010--2014 periods and we treat end of 2015
+as the cut-off time, then the observed sex ratio for the 2005--2009
+women is 55.99\% boys while it is 55.38\% for women who started 
+in the 2010--2014 period.%
+\footnote{
+This combines urban and rural women; the basis result 
+changes little if I split by area of residence.
+I chose the 2014 cut-off to ensure that both groups cover 
+five years, even though NFHS-4 took place in 2015 and 2016.
+}
+It would therefore appear that the use of sex selection for
+this spell is slightly decreasing over time.
+This interpretation, however, ignores the role of censoring.
+If we use the estimation results to predict final sex ratio
+once childbearing for the third spell is over, the predicted
+sex ratios are 56.10\% boys and 56.08\% boys for the 
+2005--2009 and the 2010--2015 starts.
+The reason for the difference is that while for the 
+2005--2009 start we would have observed 7,134 birth out
+of a predicted 7,451 total number of births, we would
+only have observed 3,348 births out of a predicted 8,842
+for the 2010--2014 group.
+
+Although it is not possible to directly observe whether the
+unequal sex ratio and the longer spacing patterns are caused
+by sex selection the results are consistent with a general
+increase in sex selection over time.
+The increase in apparent use of sex selection is mainly found
+among women with more education and more so in urban than in
+rural areas, although the differences between urban and rural
+areas are relatively minor.
+Compared to previous research one result stands out.
+It appears that the use of sex selection is spreading to 
+women with lower levels of education, so that even women
+with one to seven years of education show unequal sex ratios
+and longer spacing for their higher-order spells.
+
+This points to two important, interconnected, questions for 
+future research:
+What is the connection between falling fertility and the 
+use of sex selection and is the use of sex selection increasing 
+or decreasing over time?
+It is clear that fertility has been declining over time in India,
+although it is important to note that the decline might be
+overstated exactly because of an increased use of sex selection and
+the resulting longer spacing between births makes it less likely 
+that we will observe births to women, even though they eventually
+will happen.
+The facts that biased sex ratio occur at earlier spells over
+time and starting to show up for women with less education 
+all indicate that lower fertility and use of sex selection are
+related, but a more detailed analysis is needed.
+Furthermore, although examining spells separately, as done here, is a useful
+first step in understanding how sex selection changes over time,
+it does not lend itself easily to examine the degree to which
+sex selection changes over time.
+For that a combined model that incorporates the full fertility
+history of women would be more appropriate.
+A model of this type would allow us to jointly model fertility
+and sex selection and help address both questions.
+
+The results here also lead to a set of broader important questions that
+need to be addressed in future research.
 First, to what extent are the improvements in health for girls
@@
 births, or changing son preference?
-
-Second,
+There is some early evidence that selection make it appear that
+girls are healthier, even though the real cause is a combination
+of sex selection and higher mortality together with recall error \citep{Portner2018a}. 
+Understanding what role these factors play in better health for
+girls is especially important when evaluating policies that 
+aim to directly limit the use of sex selection rather than 
+changing preferences or incentives.
+
+Second, we need to understand how female labor force participation
+interact with the use of sex selection.
+Increased autonomy for women, through, for example, better opportunities
+for working outside the home, has been suggested as a way to increase
+women's status and thereby lowering the use of sex selection \citep{Das-Gupta2016}.
+This may, however, be a double-edged sword.
+On the one hand, it is an obvious benefit to the women in terms of 
+bargaining power and it also increases the cost of repeated 
+sex-selective abortions.
+On the other hand, it may also further lower fertility, and everything 
+else equal, that may lead to higher use of sex selection.
+
+[Nothing is ever simple!]
 
@@
 sex ratio may be to encourage higher female labor force participation.
-In addition to the obvious benefit to the women in terms of 
-bargaining power, it also increases the cost of repeated 
-sex-selective abortions.
-[Caveat, it also lowers fertility, and everything else equal that
-would may lead to higher use of sex selection]
 

### 2018-03-24 paper/sexSelectionSpacing-ver1.tex
Reorder motivation in introduction and add recall error reference

@@
 if combined with the likelihood of observing a boy or a girl.
-Second, if spacing affects health outcomes for mother and children, it is 
-essential to understand what drives changes in spacing.
-The better health outcomes for girls in the presence of sex selection may,
-for example, be an unintended side-effect of the longer spacing that arises
-from sex-selective abortions, rather than, as often assumed, be driven by a 
-higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
-Third, the duration between births may be an important factor in parents' 
+Second, 
+the duration between births may be an important factor in parents' 
 decisions, either for preference or economic reasons.
@@
 becomes sufficiently long.
-Finally, we know less about what determines spacing behavior in 
+
+At a broader level, we know less about what determines spacing behavior in 
 developing countries than in developed countries.
 With increasing numbers of women entering the labor force in developing
-countries, understanding how timing decisions are made will be necessary
+countries, understanding how couples make timing decisions will be necessary
 for the design of suitable policies \citep{Portner2018}.
+Furthermore, if spacing does affect health outcomes for mother and children, it is 
+essential to understand what drives changes in spacing.
+The better health outcomes for girls in the presence of sex selection may,
+for example, be an unintended side-effect of the longer spacing that arises
+from sex-selective abortions, rather than, as often assumed, be driven by a 
+higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
 
@@
 
-Recall error is heavily dependent on the length of marriage (TK).
+Recall error is heavily dependent on the length of marriage \citep{Portner2018b}.
 I, therefore, drop women married 22 years or more 
@@
 the second spell and one boy is statistically significantly \emph{below} 
-the natural sex ratio [TK cite my recall paper].
+the natural sex ratio \citep{Portner2018b}.
 
@@
 because they prefer not to have their children too far apart.
+The desire for short spacing could, for example, arise from 
+economies of scale in childbearing and rearing that would be lost 
+if children were born too far apart \citep[p 374]{schultz97}. 
 In this case we should observe the predicted sex ratio decline
@@
 
+[from introduction]
+Furthermore, if spacing does affect health outcomes for mother and children, it is 
+essential to understand what drives changes in spacing.
+The better health outcomes for girls in the presence of sex selection may,
+for example, be an unintended side-effect of the longer spacing that arises
+from sex-selective abortions, rather than, as often assumed, be driven by a 
+higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
+
 This suggestion that an overlooked approach to addressing a biased

### 2018-03-25 paper/sexSelectionSpacing-ver1.tex
Minor edits

@@
 a son than after a daughter 
-\citep{ben-porath76b,Das1987,Arnold1997,clark00,filmer09,Basu2010,Altindag2016}.
+\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
 }
@@
 % }
+
 There have also been substantial changes in access and legality of
@@
 }
-Hence, the data make it possible to show how the spacing between births and
-sex ratios have changed with the introduction of prenatal sex determination,
-and whether the ban affected the relationship between birth spacing and sex 
-ratios.
-
-[Outline of findings here]
-
-% [EXPLAIN RESULTS HERE]
-% Main findings!
-% There are three main findings.
-% 
-% There is, however, still no evidence of sex selection being used on the first birth.
-% 
-% Secondly, sex selection appears to be used for securing one son, rather than a large 
-% number of sons.
-% There is only limited use of sex-selective abortions for better-educated
-% women with one or more sons.
-% The exception is rural women with one son and one daughter, presumably to compensate for 
-% the higher child mortality in rural areas.
-% These results are in line with the differential stopping behavior observed in many studies
-% before sex selection became available \citep{repetto72,arnold98,dreze01}.
-%
+% Hence, the data make it possible to show how the spacing between births and
+% sex ratios have changed with the introduction of prenatal sex determination,
+% and whether the ban affected the relationship between birth spacing and sex 
+% ratios.
+
+% [Results]
+There are four main results.
+First, there has been a general increase in the length of spacing between births
+over the four decades covered by the data.
+The exception is for first births, where the median duration has either remained
+the same or slightly declined, although this hides a substantial compression of
+the variation in spell length.
+Second, consistent with the use of sex selection, the increase in duration is 
+substantially longer for women who are most likely to use sex selection than
+for those less likely to use sex selection.
+Specifically, for the best educated women, those with no boys now has 
+significantly longer spacing and a more male-biased sex ratio than those 
+with boys.
+Third, women with no education still follow the standard pattern of short 
+spacing when they have girls and little evidence of the use of sex selection.
+In other word, these women follow a strategy where they achieve a son through
+higher fertility rather than use of sex selection.
+Finally, sex ratios are more likely to decline within spells at lower parities, 
+where the pressure to ensure a son is lower, and more likely to increase or 
+remain consistently high for higher-order spells, where the pressure to ensure 
+a son is high.
 
@@
 A few women report births that occurred less than nine months 
-after the previous birth; I drop those women from the sample.
+after the previous birth; I drop those women from the sample as mentioned above.
 
@@
 or too few births are observed for the method to work.
-For spell 1 I set censoring at 72 months after marriage,
-while for spells 2 and 3 censoring is at 72 months and for spell 4
-57 months after a birth can occur.
-
-I group spells into four time periods based on spell start date:
+For the first spell I set censoring at 72 months (six years) after marriage,
+while for the second and third spells censoring is at 72 months and 
+for the fourth spell 57 months after a birth can occur.
+With nine month between the previous birth and the beginning of
+the next spell, the maximum durations between births I consider are
+6.75 years for the second and third spells and 5.5 years for the 
+fourth spell.
+
+I group spells into four periods based on the year of marriage
+or year of the previous birth:
 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-These years follow the main changes in availability and legality of 
+The periods follow the main changes in availability and legality of 
 prenatal sex determination discussed in the Introduction.
-Some spells cover two periods because I classify periods based on the 
-spell's beginning year.
+The allocation into periods is determined by when conception and therefore 
+decisions on sex selection begin, even if no births are observed until 
+nine months later.
+
+The allocation into periods means that some spells cover two periods.
 A couple may, for example, be married in 1984, but not have their first 
@@
 The area of residence is a dummy variable for the household living in
-an urban area [TK check on this for NFHS-4].%
-\footnote{
-NFHS uses four categories for the area of residence: Large city, small city, town,
-and countryside.
-To reach a sufficient sample size urban areas are merged into one group.
-}
+an urban area.
 The cost of children is higher in urban areas than in rural areas, and 
@@
 Imagine a spell has two periods and that the estimated percentage boys for a
-woman are 54\% and 66\% and that the likelihood of exiting the spell is 20\% and 40\%
-(in other words, there is 40\% chance that she does not have a birth by the end of 
-the spell).
-This woman' percentage boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
+woman are 54\% and 66\% and that the likelihood of having a birth is 20\% and 40\%
+(measured as the change in the survival curve; in other words, there is 
+40\% chance that she does not have a birth by the end of this spell).
+This woman's percentage boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
 }
@@
 
-The results so far show that as sex ratios became more
-male-biased the spacing when a woman has only girls became 
-longer relative to other sex compositions, presumably because
-of increased use of sex selection rather than a reduction in son preference.
-Neither the median spacing or the conditional survival curves
-can, however, provide us with information on how the use of
-sex selection vary \emph{within} a spell.
-Furthermore, using conditional survival curves forces everybody 
-to finish the spell in the same month and does not provide
-any information about how many births there are.
-We can, however, learn something about both changes in 
-sex selection within a spell and the likelihood of exiting
-with a birth using standard  survival curves.
-The predicted sex ratio may change within a spell for, at
-least, two reasons.
+The above results show that length of birth spacing increased 
+more for women with only girls than for other sex compositions
+as sex ratios became more male-biased, presumably because
+of increased use of sex selection.
+Neither the median spacing or the conditional survival curves,
+however, can tell us whether sex selection vary \emph{within}
+a spell or provide any information about the likelihood of
+exiting a spell with a birth.
+To understand both, I now turn to the standard survival curves
+and predicted sex ratios by spell duration.
 
@@
 
-First, parents may stop using prenatal sex determination 
-once the duration from the previous birth becomes long enough
-because they prefer not to have their children too far apart.
+The predicted sex ratio may change within a spell for, at
+least, two reasons.
+First, parents may stop using prenatal sex determination within
+a spell once the duration from the previous birth becomes long enough.
 The desire for short spacing could, for example, arise from 
@@
 
-Second, if the degree of son preference across women within the sample
-but behavior is not affex2cted by duration from the previous birth,
-we should observe an increasing share of births come from 
+Second, if the degree of son preference vary across women within 
+the sample but behavior is not affected by duration from the 
+previous birth, we should observe an increasing share of births come from 
 parents with stronger son preference as duration from the
@@
 son preference who have not yet conceived a son.
-Hence, in this case we should see an increase in the sex ratio 
+In this case we should see an increase in the sex ratio 
 as duration increases.
@@
 have substantially longer spacing than if they have two or more sons.
-That these changes are likely due to increased use of sex selection 
+These changes are likely due to increased use of sex selection 
 rather than changes in son preference as shown by the increasingly
 significant deviations in the sex ratio from the natural sex ratio.
+This also suggests that banning prenatal sex determination has 
+not been able to reverse the use, although it is possible that it
+has slowed the rate of increase.
 
@@
 
-This points to two important, interconnected, questions for 
-future research:
+The results here point to two important, interconnected, questions 
+for future research:
 What is the connection between falling fertility and the 
@@
 
-The results here also lead to a set of broader important questions that
+The results here also lead to a set of broader questions that
 need to be addressed in future research.
@@
 This may, however, be a double-edged sword.
-On the one hand, it is an obvious benefit to the women in terms of 
+On the one hand, it is an obvious benefit to women who gain  
 bargaining power and it also increases the cost of repeated 
 sex-selective abortions.
-On the other hand, it may also further lower fertility, and everything 
-else equal, that may lead to higher use of sex selection.
+On the other hand, it may further lower desired fertility, and 
+everything else equal, that may lead to higher use of sex selection.
+Understanding the trade-off between long-term benefits from improvements in
+women's labor force participation and short-term costs from potential 
+increases in sex selection is of paramount importance.
 
@@
 higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
-
-This suggestion that an overlooked approach to addressing a biased
-sex ratio may be to encourage higher female labor force participation.
 

### 2018-03-27 paper/sexSelectionSpacing-ver1.tex
New abstract and minor edits

@@
 
-Strong son preference has frequently been associated with shorter 
-spacing between births after the birth of a girl.
-The spread of access to prenatal sex determination and 
-sex-selective abortions has the potential to reverse this pattern
-because each abortion adds substantially to the duration between births.
-I introduce a statistical method that simultaneously account for how sex 
-selection increases the likelihood of a son \emph{and} the spacing between births.
-Using India's National Family and Health Surveys,
-I show that use of sex selection leads to \emph{longer} spacing after a daughter 
-than after a son; a reversal of the pattern before the availability of sex selection.
-For families that do not use sex selection, the duration to next birth is still 
-shorter when no boys are present.
-
-Women with 8 or more years of education, both in urban and rural areas, are 
-the main users of sex-selective abortions, whereas women with less education 
-do not appear to use sex selection.
+Strong son preference is typically associated with shorter birth spacing
+in the absence of sons, but access to sex selection has the potential to
+reverse this pattern because each abortion extends spacing by six to
+twelve months. 
+I introduce a statistical method that simultaneously
+accounts for how sex selection increases both the likelihood of a son
+and the spacing between births. 
+Using four rounds of India's National
+Family and Health Surveys, I first show that, except for first births,
+the spacing between births increased substantially over the last four
+decades. 
+Birth spacing increased the most for women most likely to use
+sex selection; specifically, well-educated women with no boys now
+exhibit significantly longer spacing and more male-biased sex ratios
+than those with boys. 
+Women with no education still follow the standard
+pattern of short spacing when they have girls and little evidence of sex
+selection, with medium-educated women showing mixed results. 
+Finally,
+sex ratios are more likely to decline within spells at lower parities,
+where there is less pressure to ensure a son, and more likely to
+increase or remain consistently high for higher-order spells, where the
+pressure to provide a son is high.
 
@@
 the variation in spell length.
-Second, consistent with the use of sex selection, the increase in duration is 
-substantially longer for women who are most likely to use sex selection than
-for those less likely to use sex selection.
-Specifically, for the best educated women, those with no boys now has 
+Second, the increase in duration is substantially larger for the groups of women 
+who are most likely to use sex selection.
+Specifically, among the best educated women, those with no boys now has 
 significantly longer spacing and a more male-biased sex ratio than those 

### 2018-03-28 paper/sexSelectionSpacing-ver1.tex
Edits of results and conclusion sections

--- 2018-03-25 paper/sexSelectionSpacing-ver1.tex
@@
 How well this approach works depends on whether the spell length covered is 
-sufficiently long that only very few women would be likely to give
-birth later.
+sufficiently long that few women would be likely to give birth later.
 I discuss the choice of spell length below.
@@
 remain in the sample---unless they are dropped for another reason---because 
-10 to 20 percent fall into this category across the four surveys.
+8.5\% fall into this category across the four surveys.
 Although it is possible that some of these births are premature, the high number of
@@
 Finally, I restrict the sample to Hindus,
-who constitute about 80 percent of India's population.
+who constitute about 80\% of India's population.
 If the use of sex selection differ between Hindu and other religions, such 
@@
 
-As mentioned above, 10 to 20 percent of women gave birth less than nine months
+As mentioned above, 8.5\% of women gave birth less than nine months
 after they were married, and the first spell, therefore, begins at the 
@@
 or too few births are observed for the method to work.
-For the first spell I set censoring at 72 months (six years) after marriage,
-while for the second and third spells censoring is at 72 months and 
-for the fourth spell 57 months after a birth can occur.
-With nine month between the previous birth and the beginning of
-the next spell, the maximum durations between births I consider are
-6.75 years for the second and third spells and 5.5 years for the 
-fourth spell.
+For the first spell I set censoring at 108 months (nine years) after marriage,
+while for the second, third, and fourth spells censoring is at 96 months 
+(eight years) after a birth can occur.
+TK number of births observed after these periods.
+With these cut-offs, less than one percent of observed occur after
+the spell cut-off.
 
@@
 Censoring becomes even more important for the third and fourth
-spells, with more than 70 percent of the observations censored.
+spells, with more than 70\% of the observations censored.
 The level of censoring also increases with parity and time period,
@@
 The population has become substantially better educated over time.
-Women with no education constituted almost 60 percent 
+Women with no education constituted almost 60\% 
 in the first period, but less than twenty percent in the last period.
@@
 within a spell?
-The shapes of the survival curves provides clues to whether parents are
+The shapes of the survival curves provide clues to whether parents are
 still trying to conceive earlier after girls than boys.
@@
 There are two reasons why this is interesting.
-First, if the sex ratio changes within a spell simply using the observed sex
+First, if the sex ratio changes within a spell, relying on the observed sex
 ratio at birth---as is standard practice in the literature---will not provide
-correct estimates of the use of sex selection or the sex ratio when child
-bearing is completed.
-Second, the development in the sex ratio within a spell provides clues
+correct estimates of the use of sex selection or the sex ratio when 
+childbearing is completed.
+Second, any changes in the sex ratio within a spell provides clues
 to parents' preferences over the ideal spacing between births and the
@@
 The predicted median duration shown is the weighted average over the women in the 
-sample's predicted median durations, using the individual probabilities of a birth 
-as weights.
+sample's predicted median durations, using the individual probabilities of 
+giving birth as weights.
 For each woman in a sample, I calculate her probability of ending the spell 
@@
 from the beginning of the spell to where she is predicted to reach half of that probability.
-For example, if a woman has a 80\% probability of having a birth by the end of 
+For example, if a woman has an 80\% probability of having a birth by the end of 
 the spell, her median duration is the number of months it takes to reach
-40\% probability of having exited with a birth (equivalent to the 60\% point
-in a standard survival curve because that captures how many have not yet
-exited).
+40\% probability of having exited with a birth.
+The 40\% is equivalent to the 60\% point in a standard survival curve because that 
+captures how many have not yet exited.
 
@@
 duration with only girls.
-The statistical significance is based on the bootstrapped differences in
-durations across sex compositions.
-For each new sample the difference in duration is calculated and these
+I use bootstrapping to calculate the level of statistical significance.
+For each new sample, I calculate the difference in duration and these
 differences are used to calculate the standard error and the level of
@@
 ordering of children, but this would further lower the power of the test, by 
-adding one extra group for the third spell and four extra groups for the fourth spell.
+adding one additional group for the third spell and four additional groups for the fourth spell.
 
 The predicted sex ratio is the weighted average over the women in the sample's 
-individual predicted sex ratios, using the individual probabilities of a birth by 
-the end of the spell as weights.
+individual predicted sex ratios, using the individual probabilities of having
+given birth by the end of the spell as weights.
 Each woman's predicted sex ratio is the weighted average of the predicted
@@
 Imagine a spell has two periods and that the estimated percentage boys for a
-woman are 54\% and 66\% and that the likelihood of having a birth is 20\% and 40\%
-(measured as the change in the survival curve; in other words, there is 
-40\% chance that she does not have a birth by the end of this spell).
+woman are 54\% and 66\% and that the likelihood of having a birth is 20\% and 40\%.
+The likelihood of having a birth is the change in the survival curve; 
+in other words, there is 40\% chance that she will not have given birth by the end of 
+this spell.
 This woman's percentage boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
@@
 The predicted sex ratio captures the percent boys that will be born to women 
-in the sample once child bearing for that spell is over.
-
-Each predicted precent boys is tested against the natural percentage 
+in the sample once childbearing for that spell is over.
+
+Each predicted percent boys is tested against the natural percentage 
 boys using the bootstrapped standard errors.
@@
 
-Predicted median duration has generally increased over time within
+Predicted median duration has increased over time within
 each sex composition.
@@
 
-The differences in duration across sex compositions are more 
-pronounced with higher-order spells.
+The differences in duration across sex compositions increase with 
+spell number.
 For the second spell, the difference in median duration between
@@
 for urban women in the 1985--1994 period.
-Focusing on rural women for the third spell, the difference is,
-on average, slightly over one months between only girls and only boys 
+Focusing on rural women for the third spell, the difference is in
+duration, on average, slightly over one month between only girls and only boys 
 and the differences are statistically significant in all periods.
-For rural women the differences for the fourth spell are just below
-2 months, with the exception of the 1972--1984 period, which is
+For rural women, the differences for the fourth spell are just below
+two months, except for the 1972--1984 period, which is
 also the only period where the difference is not statistically significant.
@@
 One example is the second spell in the 1995--2004 period, where there 
-are only 0.2 months difference between duration after one girl and 
+is only 0.2 months difference between duration after one girl and 
 duration after one boy.
@@
 period may be the result of recall error with a very high 
-percentage boys for women with three girls, despite no availability
+percentage of boys for women with three girls, despite no availability
 of sex selection.
@@
 Table \ref{tab:median_sex_ratio_med} shows.
-There is a more equal distribution in the number of women
-across urban and rural for this education group than for the
-no education women.
-As a result, the only spell where there are few women to base 
+The distribution across urban and rural is more even for this education
+group than for the no education women.
+As a result, the only spells where there are few women to base 
 results on are for the fourth spell for urban women and the first 
@@
 
-Spacing between births increased over the four decades.
+The spacing between births increased over the four decades.
 On average, the increase is approximately two months.
@@
 increase with spell number.
-For both urban and rural women the difference in duration
-is just over a month for the second spell, but for the
-third spell it is 1.4 and 2.3 months for urban and rural
-women, respectively.
-In the three later periods there is no clear pattern
+For both urban and rural women, the difference in duration is just over
+a month for the second spell, but it is 1.4 and 2.3 months for urban and
+rural women, respectively, for the third spell.
+In the three later periods, there is no clear pattern
 in the differences across sex compositions.
@@
 significantly different from the natural sex ratio.
-Hence, even though the evidence is not strong, it does
+Hence, even though the evidence is not substantial, it does
 appear that women with one to seven years of education 
 have begun to use sex selection at higher-order spells.
-This is also consistent with the falling fertility for both
-urban and rural women shown below.
+An emerging use of sex selection is also consistent with the falling
+fertility for both urban and rural women shown below.
 
@@
 of education for the 1972--1984 period.
-This means that only the results for the first and second spells in 
+Hence, only the results for the first and second spells in 
 both urban and rural areas are likely to be reliable.
@@
 The spacing between marriage and the first birth is still the
-exception, and for this group of women there is a decline of
+exception, and for this group of women, there is a decline of
 about a month for both urban and rural areas.
@@
 The exception is the second spell for the 1985--1994 period, where women
-with one girl has 0.4 months longer spacing the women with one boy.
-}
-This reversal in the standard spacing pattern when there is strong
-son preference is substantial, especially for the third and fourth 
-spells.
-For the latest period the difference between only girls than the
-other sex compositions are between 3.4 and 5.4 months for the third
+with one girl have 0.4 months longer spacing the women with one boy.
+}
+This reversal in the standard spacing pattern is substantial, 
+especially for the third and fourth spells.
+For the latest period, the difference between only girls than the
+other sex compositions is between 3.4 and 5.4 months for the third
 and fourth spell.
@@
 
-Rural women also show a reversal of the normal spacing pattern,
+Rural women also show a reversal of the typical spacing pattern,
 although the changes are less pronounced than for urban women.
-The third spell show increasingly longer spacing with only
-girls compare to the other two sex compositions over time with
-most differences statistically significant, but the differences
-are smaller than for urban women.
-For the second spell there is little difference in spacing with
-one girl and with one boy and there are few rural women to 
-based the fourth spell results on.
+The third spell shows that spacing for women with only girls become
+increasing longer compared to the other two sex compositions.
+Most of the differences are statistically significant, although they are 
+smaller than for urban women.
+For the second spell, there is little difference in spacing for
+women with one girl and women with one boy.
 
@@
 the reversal in spacing patterns is not the result of a declining son
-preference but rather corresponds to a substantially more male-biased 
+preference but instead corresponds to a substantially more male-biased 
 sex ratio.
-For urban women the predicted sex ratio with only girls 
+For urban women, the predicted sex ratio with only girls 
 is consistently above 60\% boys for the third and fourth spells.
-For rural women the predicted sex ratios are lower than for urban
-women, but stil substantial and statistically significant at close 
+For rural women, the predicted sex ratios are lower than for urban
+women but still substantial and statistically significant at close 
 to 60\%.
@@
 
-When trying to understand the strength of son preference it is interesting
+When trying to understand the strength of son preference, it is interesting
 that the sex ratio is also statistically significantly different
@@
 first-born for urban women. 
-There is, however, no corresponding increase in spacing; rather
+There is, however, no corresponding increase in spacing; instead,
 the median duration has fallen over time and is the lowest among
@@
 There are two potential explanations.
-First, NFHS-4 is substantially larger than the three prior surveys.
+First, the NFHS-4 is substantially larger than the three prior surveys.
 Hence, it is possible that the effects have been there all along, but 
-we simply did not have the power to detect them.
+we did not have the power to detect them.
 Second, it is possible that, at least, the first-born results are an
@@
 
-Median spacing is a convenient way to understand the major developments,
-but may hide important changes in the distribution of spacing.
-This section therefore provides more detail on how spacing is distributed
-over time and over sex compositions using a graphical approach.
+Median spacing is a convenient way to understand the overall changes but
+may hide important differences in the distribution of spacing.
+This section, therefore, provides more detail on how spacing is distributed
+over time and sex compositions using a graphical approach.
 
@@
 The advantage of this approach is that it is possible to directly compare 
-the distribution of spacing to next birth, independently of differences in
-how likely the next birth is across groups.
-In other words, these results reflect the spacing we should observe once
-all childbearing is over for the women in the sample.
+the distribution of spacing to next birth across groups, independently of 
+differences in how likely the next birth is.
+It does, however, depend on covering a long enough spell period
+to ensure that only relatively few births are likely to take place after the
+censoring date as discussed above.
 Because the conditional survival curves are independent of the likelihood
-of parity they all begin at 100\% and end at 0\%.
+of final parity progression, they all begin at 100\% and end at 0\%.
 
 Instead of averaging across the entire sample, I calculate the conditional
-survival curves for a representative woman using the method detailed in 
+survival curves for an average woman using the method detailed in 
 Section \ref{sec:strategy}.
-The representative woman characteristics are the means of continuous explanatory 
+The average woman characteristics are the means of continuous explanatory 
 variables and the majority category for categorical explanatory variables.
-Common to all representative women is that they do not own land and belong to neither 
+Common to all is that they do not own land and belong to neither 
 a scheduled caste nor a scheduled tribe.
@@
 In the interest of brevity, I discuss only a representative subset.
-Figure \ref{fig:pps_spell1} shows spacing within the first spell across the
-four periods for rural women with no education and for urban women with 
+Figure \ref{fig:pps_spell1} shows spacing for the first spell across the
+four periods for rural women with no education and urban women with 
 eight or more years of education.
@@
 education and urban women with eight or more years of education.
-Standard and conditional survival curves for all groups and time periods 
-are shown in the Appendix, and I discuss some examples of standard survival
+The Appendix shows standard and conditional survival curves for all groups and 
+time periods, and I discuss some examples of standard survival
 curves in the following section.
@@
 women does suggest that there might be sex selection on the first birth.
-I therefore begin by comparing in Figure \ref{fig:pss_spell1} how the distribution 
+I, therefore, begin by comparing in Figure \ref{fig:pss_spell1} how the distribution 
 of spacing has changed over time for rural women with no education and urban women 
@@
 compression of when most of the births occur.
-In the 1972--1984 period the middle 80\% of births for women with no education 
+In the 1972--1984 period, the middle 80\% of births for women with no education 
 are predicted to occur between approximately 6 and 52 months, whereas in the 
 2005--2016 period it is between 12 and 46 months.
-This is equivalent to a compression of a full year.
+Hence, the compression is equivalent to a full year.
 Women with eight or more years of education show a slightly smaller compression:
-in the 1972--1984 period the middle 80\% of births are predicted to occur between
+in the 1972--1984 period, the middle 80\% of births are predicted to occur between
 approximately 6 and 44 months, whereas in the 2005--2016 period it is between
@@
 before marriage in the later time periods than earlier.
-In the first two periods there was a relatively smooth decline in number of
+In the first two periods there was a relatively smooth decline in the number of
 women without a birth starting at the time of marriage, but in the last two
-periods there is now few women exiting early after marriage and instead a 
-substantial dip between 9 and 12 months after marriage.
+periods, there are now few women who exit early after marriage and
+instead there is a substantial dip between 9 and 12 months after
+marriage.
 
@@
 The descriptive statistics above show, for example, that women without 
-education has seen an increase in the average age at marriage from below 
+education have seen an increase in the average age at marriage from below 
 16 to 18.5 from the first period to the last while women with the most 
@@
 
-For women with no education Figure \ref{fig:pps_low} shows that the median results
+For women with no education, Figure \ref{fig:pps_low} shows that the median results
 above are consistent with the distribution of spacing within a spell with spacing 
@@
 There are slight variations in how strong this effect is across the three spells.
-On the one had, for the second spell the difference in spacing between first child a girl 
-versus first child a boy as first-born remains almost the same across the four
-decades.
+On the one hand, for the second spell the difference in spacing between
+when the first child is a girl versus when the first child is a boy as
+first-born remains almost the same across the four decades.
 On the other hand, for the third spell the differences between two girls and 
@@
 the difference between two girls and two boys have become substantially larger.
-The fourth spell results are based on relatively few observations, but do indicate
-that only girls and two girls and one boy is associated with shorter spacing than
-only boys or one girl and two boys.
-Although the evidence is not overly strong, it does appear that there is a slight
+The fourth spell results are based on relatively few observations but do
+indicate that women with either only girls or two girls and one boy have
+shorter spacing than women with only boys or one girl and two boys.
+Although the evidence is not substantial, it does appear that there is a slight
 preference for two boys in the sense that spacing becomes longer once the couple
@@
 for the 1972--1984 period.
-This points to these two very different groups of women behaving in a similar fashion
+The small difference points to these two very different groups of women behaving similarly
 in response to son preference in a situation where there was little access to
@@
 girls and after first-born boys.
-Given the elevated predicted percentage boys show in Table 
-\ref{tab:median_sex_ratio_high} this change is consistent with use of 
-sex selection for women with a girl as their first child.
+Given the elevated predicted percentage boys in Table \ref{tab:median_sex_ratio_high},
+this change is consistent with the use of sex selection for women with a girl 
+as their first child.
 
@@
 the 1972--1984 period to the new pattern in the 2005--2016 period is substantial.
-There is also indications that the spacing distribution has moved rightward
+There are also indications that the spacing distribution has moved rightward
 for women with one boy and one girl relatively to women with two boys, which
-provides some evidence for use of sex selection for this group.
-The caveat is that the 1972--1985 period also had an biased sex ratio, which
+provides some evidence for the use of sex selection for this group.
+The caveat is that the 1972--1985 period also had a biased sex ratio, which
 points to uncorrected recall error for this group.
 
-There is a even more pronounced rightward shift for spacing after only girls
-in the fourth spell, although these results are based on fewer births, especially
-for women with two or more sons.%
+There is an even more pronounced rightward shift for spacing after only
+girls in the fourth spell for the first years of the spell. 
+The caveat is that there are few births to base the results on,
+especially for women with two or more sons.%
 \footnote{
@@
 }
-Furthermore, the differences are large across most of the distribution.
+Furthermore, the differences are substantial across most of the distribution.
 Twelve months after the beginning of the spell there is an approximately ten 
@@
 those with three girls have had theirs.
-Even at three years after the spell there is a more than five percentage
+Even at three years after the spell, there is a more than five percentage
 points difference.
@@
 three girls.
-This fit the predicted sex ratios shown above where the highest
+The pattern fit the predicted sex ratios shown above where the highest
 predicted sex ratio is for women with only girls, followed by those
@@
 Neither the median spacing or the conditional survival curves,
-however, can tell us whether sex selection vary \emph{within}
+however, can tell us whether sex selection varies \emph{within}
 a spell or provide any information about the likelihood of
@@
 The desire for short spacing could, for example, arise from 
-economies of scale in childbearing and rearing that would be lost 
+economies of scale in childbearing and rearing that parents lose 
 if children were born too far apart \citep[p 374]{schultz97}. 
@@
 
-Second, if the degree of son preference vary across women within 
-the sample but behavior is not affected by duration from the 
+Second, if the degree of son preference varies across women within 
+the sample, but their behavior is not affected by duration from the 
 previous birth, we should observe an increasing share of births come from 
-parents with stronger son preference as duration from the
+parents with stronger son preference as the duration from the
 previous birth increases.
@@
 preference who conceived a son in the first or second pregnancy,
-later births are then predominately from those with stronger
+births later in the spell are then predominately from those with stronger
 son preference who have not yet conceived a son.
-In this case we should see an increase in the sex ratio 
+In this case, we should see an increase in the sex ratio 
 as duration increases.
@@
 is little change, or possibly a small increase, with duration for the 
-2005-2016 period.
+2005--2016 period.
 These results are consistent with a situation where fertility is declining
 over time leaving less room for a change in the decision to use sex selection.
-Fertility decline is not immediately obvious from the second spell 
-results, but the third spell show that the likelihood of progressing from
+Fertility decline is not immediately apparent from the second spell 
+results, but the third spell shows that the likelihood of progressing from
 two to third children declines by approximately 15 percentage points if
-the woman has given birth to a boy, and, as the Appendix shows, only about 
-25\% of urban women with two boys have a third child in the 2005--2016 period, 
+the woman has given birth to a boy.
+Furthermore, as the Appendix shows, only about 25\% of urban women with 
+two boys have a third child in the 2005--2016 period, 
 down from close to 40\% in the 1995--2004 period. 
 Furthermore, it is unlikely that a substantial number of births will take
-place after the end of the spell period, which is equal to six year in
+place after the end of the spell period, which is equal to eight year, in
 addition to the nine months from the previous birth to the start of the spell.
+TK check these numbers with new spell lengths.
 
@@
 The increase in sex ratio with duration for women who already have
-given birth to a boy likely illustrates the case where there are a
+given birth to a boy likely illustrates the case where there is a
 combination of degrees of son preference.
@@
 
-The main question addressed here is the extent to which spacing patterns 
+The central question addressed here is the extent to which spacing patterns 
 significantly changed as prenatal sex determination became available.
@@
 available.
-I introduce a new method that simultaneously account for spacing between
-births and the potential use of sex selection and apply the method
-to over four decades of data from India's NFHS.
+I introduce a new method that simultaneously accounts for spacing
+between births and the potential use of sex selection. 
+I apply the method to over four decades of data from India's NFHS.
 The results show two very different approaches to son preference.
@@
 spacing that should follow from the use of sex selection.
-The situations where there are elevated sex ratios for women without
-education---which, by itself, should indicate use of sex selection---the
-spacing patterns are too close to the ones without sex selection that 
-it is difficult to conclude that the changes in sex ratios indicate
-sex selection rather than normal variation or problems with recall errors.
+ In the situations where there are elevated sex ratios for women without
+education, the spacing patterns are close to those with more regular sex
+ratios. 
+Hence, it is difficult to conclude that the changes in sex
+ratios indicate sex selection rather than normal variation or problems
+with recall errors.
 
@@
 have substantially longer spacing than if they have two or more sons.
-These changes are likely due to increased use of sex selection 
-rather than changes in son preference as shown by the increasingly
-significant deviations in the sex ratio from the natural sex ratio.
-This also suggests that banning prenatal sex determination has 
-not been able to reverse the use, although it is possible that it
-has slowed the rate of increase.
-
-Over the last 40 years there has been a general increase in median
+As shown by the increasingly significant deviations in the sex ratio
+from the natural sex ratio, these changes are likely due to increased
+use of sex selection rather than changes in son preference. 
+Banning prenatal sex determination has therefore not been able to
+reverse the use, although it is possible that it has slowed the rate 
+of increase.
+
+Over the last 40 years, there has been a general increase in median
 spacing for all education groups, but especially for the most 
@@
 where there are two counteracting forces: women have become more likely 
-to conceive after marriage and there has been a substantial compression 
+to conceive after marriage, and there has been a substantial compression 
 in the variation.
-The end result is that median spacing from marriage to first birth
-that has changed little or even declined for the best educated women.
+The result is that median spacing from marriage to first birth
+that has changed little or even declined for the best-educated women.
 
 The empirical model is designed to allow for the effects of covariates
-to change within the spell.
-This is important because the use of sex selection is likely to vary
-within a spell, either because preferences for spacing between births
-that is not too long override the preference for sons or because
-of selection where the women who remain in a spell are those with
-the strongest son preference who have been through multiple 
-pregnancies that were aborted because the fetus was female.
-Because these move in opposite directions it is difficult to 
-establish the extent to which they affect the results.
-Both are, however, clearly present as can be seen from the
-cases where there is either a decline in sex ratio with spell
-duration or a substantial increase with spell duration.
-The first case is more likely at lower parities where there
-is still less pressure to ensure a son, which allows any
-preference for shorter spacing to play more of a role.
-The second is on the other hand more likely to have an effect
-for higher parities where the desire to limit further
-childbearing and ensure a son dominates any preferences for
-shorter spacing.
-
+to change within the spell. Non-proportionality is essential because the
+use of sex selection may vary within a spell. The use of sex selection
+may change either because preferences for not too long spacing between
+births override the preference for sons or because of selection, where
+the women who remain in a spell are those with the strongest son
+preference who have been through multiple pregnancies because the
+fetuses were female. Because these move in opposite directions, I cannot
+directly establish the extent to which they affect the results. Both
+are, however, present, as can be seen from the cases where there is
+either a decline in sex ratio with spell duration or a substantial
+increase with spell duration. The first case is more likely at lower
+parities where there is still less pressure to ensure a son, which
+allows any preference for shorter spacing to play more of a role. The
+second is on the other hand more likely to have an effect for higher
+parities where the desire to limit further childbearing and ensure a son
+dominates any preferences for shorter spacing.
+
+TK check these numbers
 The potential for changes in sex ratio within a spell means
@@
 }
-It would therefore appear that the use of sex selection for
+It would, therefore, appear that the use of sex selection for
 this spell is slightly decreasing over time.
@@
 
-Although it is not possible to directly observe whether the
-unequal sex ratio and the longer spacing patterns are caused
-by sex selection the results are consistent with a general
-increase in sex selection over time.
-The increase in apparent use of sex selection is mainly found
-among women with more education and more so in urban than in
-rural areas, although the differences between urban and rural
-areas are relatively minor.
+Although it is not possible to directly observe whether sex selection
+causes the unequal sex ratio and longer spacing the results are
+consistent with a general increase in sex selection over time. 
+The apparent increase in the use of sex selection is mainly found among
+women with more education and more so in urban than in rural areas,
+although the differences between urban and rural areas are relatively
+minor. 
 Compared to previous research one result stands out. 
-It appears that the use of sex selection is spreading to 
-women with lower levels of education, so that even women
-with one to seven years of education show unequal sex ratios
-and longer spacing for their higher-order spells.
+It appears that the use of sex selection is spreading to women with lower 
+levels of education so that even women with one to seven years of 
+education show unequal sex ratios and longer spacing for their higher-order spells.
 
@@
 although it is important to note that the decline might be
-overstated exactly because of an increased use of sex selection and
+overstated precisely because of increased use of sex selection and
 the resulting longer spacing between births makes it less likely 
@@
 will happen.
-The facts that biased sex ratio occur at earlier spells over
-time and starting to show up for women with less education 
+The fact that biased sex ratio occurs at lower-order spells over
+time and is starting to show up for women with less education 
 all indicate that lower fertility and use of sex selection are
@@
 sex selection changes over time.
-For that a combined model that incorporates the full fertility
+For that, a combined model that incorporates the full fertility
 history of women would be more appropriate.
@@
 The results here also lead to a set of broader questions that
-need to be addressed in future research.
+future research should address.
 First, to what extent are the improvements in health for girls

### 2018-03-29 paper/sexSelectionSpacing-ver1.tex
Minor edits

@@
 \\
-\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
+\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
 \setcounter{subfigure}{3}
@@
 First, to what extent are the improvements in health for girls
-relative to boys the result of selection, longer spacing between
+relative to boys the result of selection, the longer spacing between
 births, or changing son preference?
-There is some early evidence that selection make it appear that
+There is some early evidence that selection makes it appear that
 girls are healthier, even though the real cause is a combination
@@
 Second, we need to understand how female labor force participation
-interact with the use of sex selection.
-Increased autonomy for women, through, for example, better opportunities
+interacts with the use of sex selection.
+Increased autonomy for women, arising from, for example, better opportunities
 for working outside the home, has been suggested as a way to increase
-women's status and thereby lowering the use of sex selection \citep{Das-Gupta2016}.
+women's status and thereby lower the use of sex selection \citep{Das-Gupta2016}.
 This may, however, be a double-edged sword.
-On the one hand, it is an obvious benefit to women who gain  
-bargaining power and it also increases the cost of repeated 
+On the one hand, it is an clear benefit to women who gain  
+bargaining power, and it also increases the cost of repeated 
 sex-selective abortions.

### 2018-03-30 paper/sexSelectionSpacing-ver1.tex
Incorporate discussion of contraceptives and spacing; also minor edits

@@
 At a broader level, we know less about what determines spacing behavior in 
-developing countries than in developed countries.
+developing countries than in developed countries.%
+\footnote{
+Even the effects of access to contraceptive on spacing are uncertain,
+On one hand, access to contraceptive allow women to avoid too 
+short spacing between birth, which would increase birth spacing.
+On the other hand, increased reliability of access and effectiveness of
+contraceptive can lead to shorter spacing between births 
+\citep{Keyfitz1971,Heckman1976}.
+With less reliable contraception parents choose a higher level 
+of contraception---resulting in longer spacing---to avoid having 
+too many children by accident.
+But, as contraception becomes more effective parents can more
+easily avoid future births, allowing them to reduce the spacing 
+between births without having to worry about overshooting their 
+preferred number of children.
+This idea may explain why better educated women tha
+shorter spacing than less educated women in certain 
+cases \citep{Tulasidhar1993,Whitworth2002}.
+These two counteracting effects may explain why finding statistically 
+significant effects of contraception use on birth spacing is 
+difficult \citep{Yeakey2009}.
+}
 With increasing numbers of women entering the labor force in developing
@@
 chance of ending a spell with a birth their median spell duration is when
-their survival curve shows that 40\% are predicted to have exited the spell.%
-\footnote{
+their survival curve shows that 40\% are predicted to have exited the spell.
 It is important to note that this is not the same as simply calculating 
@@
 the censoring of spells that will eventually lead to a birth.
-}
-Median durations can then be averaged across women with different 
-characteristics using the probabilities of ending a spell with a child
-as weights.
+
+Median durations can then be averaged across women using the probabilities 
+of ending a spell with a child as weights.
 How well this approach works depends on whether the spell length covered is 
-sufficiently long that few women would be likely to give birth later.
+sufficiently long that few women are be likely to give birth after
+the spell cut-off.
 I discuss the choice of spell length below.
@@
 one girl and one boy, and two girls.
-[TK this should be more specific - more boys less sex selection - maybe even use ordering]
 As discussed, the sex composition of previous children affects both the timing
@@
 birth of girls than after boys.
-[TK something on general changes in spacing? Or hold off until discussing the
-results]
-
-Second, do the shapes of survival curves differ across sex compositions 
-within a spell?
-The shapes of the survival curves provide clues to whether parents are
+
+Second, have the shapes of the survival curves changed?
+The shapes of the survival curves provide clues both to general
+changes in birth spacing and to whether parents are
 still trying to conceive earlier after girls than boys.
@@
 
-The spacing between births increases substantially over time, especially
-for urban women. 
-Urban women show an increase in median duration of between a quarter
-and three-quarters of a year, whereas the increase for rural women is 
-around a quarter of a year.
+Birth spacing increases substantially over time, 
+especially for urban women. 
+The median duration for urban women increase between a quarter
+and three-quarters of a year, whereas the increase for rural women 
+is around a quarter of a year.
 The spacing between marriage and the first birth is still the
@@
 women does suggest that there might be sex selection on the first birth.
-I, therefore, begin by comparing in Figure \ref{fig:pss_spell1} how the distribution 
+I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
 of spacing has changed over time for rural women with no education and urban women 
@@
 The exception is for the spacing between marriage and first birth
-where there are two counteracting forces: women have become more likely 
-to conceive after marriage, and there has been a substantial compression 
-in the variation.
+where there are two counteracting forces: women have become less likely 
+to conceive before marriage, and there has been a substantial compression 
+in the variation of spacing.
 The result is that median spacing from marriage to first birth
 that has changed little or even declined for the best-educated women.
+Both the decrease for the first spell and the increase for higher-order
+spells are consistent with an increased access to contraceptives over
+time \citep{Yeakey2009}.
 
@@
 births, or changing son preference?
-There is some early evidence that selection makes it appear that
-girls are healthier, even though the real cause is a combination
-of sex selection and higher mortality together with recall error \citep{Portner2018a}. 
+There is some early evidence that sample selection can make it appear that
+girls are healthier, even though the underlying cause is a combination
+of sex selection and higher mortality together with recall 
+error \citep{Portner2018a}. 
 Understanding what role these factors play in better health for
@@
 changing preferences or incentives.
+If the better health outcomes for girls are, for example, an unintended 
+side-effect of the longer spacing that arises from sex-selective 
+abortions then an effective ban on sex selection may, at least
+temporarily, worsen health outcomes for girls.
 
@@
 interacts with the use of sex selection.
-Increased autonomy for women, arising from, for example, better opportunities
+Increased autonomy for women, for example from better opportunities
 for working outside the home, has been suggested as a way to increase
@@
 This may, however, be a double-edged sword.
-On the one hand, it is an clear benefit to women who gain  
+On the one hand, it is an clear benefit to the women who gain  
 bargaining power, and it also increases the cost of repeated 
@@
 
-[Nothing is ever simple!]
-
-[from introduction]
-Furthermore, if spacing does affect health outcomes for mother and children, it is 
-essential to understand what drives changes in spacing.
-The better health outcomes for girls in the presence of sex selection may,
-for example, be an unintended side-effect of the longer spacing that arises
-from sex-selective abortions, rather than, as often assumed, be driven by a 
-higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
-
-[Stuff to add somewhere in the paper]
-
-In the absence of sex selection, I expect most parities to follow
-a pattern, where there initially are relatively few births, 
-followed by a substantial number of births over a 1 to 2 year period, and then
-relatively few births thereafter.
-As sex selection becomes more widely used the associated
-longer spacing shows up by making the survival curve straighter,
-indicating that some of the births that would originally have taken place
-now take place later because of abortions.
-The use of sex selection is clearly not the only factor that can change the shape of
-the survival curves; factors such as the desired number of children and
-use of contraceptives may also shape the shape.
-To account for this it is best to compare survival curves for an individual
-parity between women who are likely to use sex selection and women who are
-not, for example because they already have achieved their desired 
-number of sons.
-
-[TK not sure where to fit this into]
-Finally, increased reliability of access and effectiveness of
-contraceptive can lead to shorter spacing between births 
-\citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level 
-of contraception---resulting in longer spacing---to avoid having 
-too many children by accident.
-But, as contraception becomes more effective parents can more
-easily avoid future births, allowing them to reduce the spacing 
-between births without having to worry about overshooting their 
-preferred number of children.
-This idea may also help explain shorter spacing for better 
-educated women than for less educated women, provided that   
-knowledge and ability to use contraception differ
-across education groups \citep{Tulasidhar1993,Whitworth2002}.
-It may also explain why finding statistically significant
-effects of contraception use on birth spacing is difficult \citep{Yeakey2009}.
-
 \clearpage

### 2018-03-30 paper/sexSelectionSpacing-ver1.tex
Number of censored births by spell generated instead of hard-coded
For each spell a footnote now indicates how many births are observed
but not included in estimations because they occur after the chosen
cut-off point.

@@
 or too few births are observed for the method to work.
-For the first spell I set censoring at 108 months (nine years) after marriage,
+For the first spell I set censoring because of too few births to 108 months 
+(nine years) after marriage,
 while for the second, third, and fourth spells censoring is at 96 months 
 (eight years) after a birth can occur.
-TK number of births observed after these periods.
-With these cut-offs, less than one percent of observed occur after
-the spell cut-off.
+With these cut-offs, less than one percent of observed births occur after
+the spell cut-off.%
+\footnote{
+\input{../tables/num_missed.tex}
+Recall also that these numbers are totals across all 36 separate regressions.
+}
 
@@
 two boys have a third child in the 2005--2016 period, 
-down from close to 40\% in the 1995--2004 period. 
-Furthermore, it is unlikely that a substantial number of births will take
-place after the end of the spell period, which is equal to eight year, in
-addition to the nine months from the previous birth to the start of the spell.
-TK check these numbers with new spell lengths.
+down from close to 60\% in the 1995--2004 period.
 
@@
 
-TK check these numbers
 The potential for changes in sex ratio within a spell means
-that censoring is an important issue when trying to understand the development
-in sex ratio.
+that censoring is an important issue when trying to understand the 
+development in sex ratio.
 This is especially the case when it comes to establishing whether 
@@
 On the one hand, it is an clear benefit to the women who gain  
-bargaining power, and it also increases the cost of repeated 
-sex-selective abortions.
+bargaining power, and it increases the cost of repeated 
+sex-selective abortions because the increased duration between births
+would cause a stronger disruption in labor market participation.
 On the other hand, it may further lower desired fertility, and 
@@
 
+\section*{Appendices for Online Publication}
+
+These appendices are intended for online publication.
+They provide the descriptive statistics, additional
+estimated duration tables, and graphs for all 
+groups and periods.
+
+\clearpage
+\newpage
+
 \section{Descriptive Statistics}
@@
 \clearpage
+\newpage
 
@@
 
+\vspace*{-0.51cm}
+
 \input{../tables/bootstrap_duration_p25_p75_low.tex}

### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit abstract

@@
 I introduce a statistical method that simultaneously
-accounts for how sex selection increases both the likelihood of a son
-and the spacing between births. 
+accounts for how sex selection increases the spacing between 
+births and the likelihood of a son. 
 Using four rounds of India's National
-Family and Health Surveys, I first show that, except for first births,
+Family and Health Surveys, I show that, except for first births,
 the spacing between births increased substantially over the last four
-decades. 
-Birth spacing increased the most for women most likely to use
-sex selection; specifically, well-educated women with no boys now
+decades, with the most substantial increases among women most 
+likely to use sex selection.
+Specifically, well-educated women with no boys now
 exhibit significantly longer spacing and more male-biased sex ratios
-than those with boys. 
+than similar women with boys. 
 Women with no education still follow the standard

### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Introduction

@@
 
-Parents' spacing between births has long served as a measure of son preference 
+Parents' spacing of births has long served as a measure of son preference 
 \citep{Leung1988}.
@@
 
-But, the introduction of prenatal sex determination fundamentally changed the 
+However, the introduction of prenatal sex determination fundamentally changed the 
 relationship between son preference and birth spacing.
-Couples, who before had shorter birth spacing because of son preference,
+Couples, who had shorter birth spacing before because of son preference,
 now have access to prenatal sex determination and sex-selective abortions,
-and each abortion increases birth spacing by approximately a year.
+and each abortion increases birth spacing by six months to a year.
 The increase consists of three parts.
@@
 of spontaneous abortion increases substantially \citep{zhou00b}.
-The second part is the waiting time to conception, which I set to six 
-months \citep{Wang2003}.%
-\footnote{
-The waiting time to conception varies by woman, but even if it is, say, one 
-month, the additional space between births would still be six months per abortion.
-}
-Finally, sex determination tests are reliable only from 3 months 
+The second part is the waiting time to conception, which is between 
+one and six months \citep{Wang2003}.
+Finally, sex determination tests are reliable only from three months 
 of gestation onwards.
 
-As a result, we now have a situation where families with the 
-\emph{strongest} son preference may have \emph{longer} spacing after 
-the birth of a daughter,
-because of their use of sex-selective abortions.
-To further complicate matters, we may still observe short spacing 
+As a result, we now have a situation where we may observer \emph{longer} spacing
+for families with daughters than for families with sons, precisely because
+strong son preference leads them to use sex selection.
+Working in the opposite direction, couples with strong son preference
+will likely still try to conceive earlier in the absence of sons. 
+They may even shorten the time until conception, knowing that they might
+have to go through multiple pregnancies and abortions before they
+conceive a son.
+To further complicate matters, we can still observe shorter birth spacing 
 after the births of daughters as a representation of son preference for 
 families who---for one reason or another---do not use prenatal sex selection.
-Also, even if they have access to prenatal sex determination, couples 
-with stronger son preference may still try to conceive faster after daughters, 
-and may even shorten the time until they try to conceive, knowing that 
-they may have to go through multiple pregnancies and sex-selective
-abortions before they conceive a son.
 
@@
 son preference, but understanding birth spacing remains a critical undertaking.
-First, birth spacing is still useful in understanding son preference, 
+First, 
+birth spacing is still useful in understanding son preference, 
 if combined with the likelihood of observing a boy or a girl.
@@
 decisions, either for preference or economic reasons.
-Whether duration plays a role in parents' decisions is especially important 
-here, because even parents with strong son preference may reverse their 
-decision to use prenatal sex determination, and carry the next pregnancy 
-to term whether male or female, as the duration from the prior birth 
-becomes sufficiently long.
+It is, for example, possible that even parents with strong son preference 
+may reverse their decision to use prenatal sex determination---and carry 
+the next pregnancy to term whether male or female---as the duration from 
+the previous birth becomes sufficiently long.
 
@@
 \footnote{
-Even the effects of access to contraceptive on spacing are uncertain,
-On one hand, access to contraceptive allow women to avoid too 
+Even the effects of access to contraceptive on spacing are uncertain.
+On the one hand, access to contraceptives allows women to avoid too 
 short spacing between birth, which would increase birth spacing.
 On the other hand, increased reliability of access and effectiveness of
-contraceptive can lead to shorter spacing between births 
+contraceptives can lead to shorter spacing between births 
 \citep{Keyfitz1971,Heckman1976}.
 With less reliable contraception parents choose a higher level 
-of contraception---resulting in longer spacing---to avoid having 
+of contraception, which results in longer spacing, to avoid having 
 too many children by accident.
@@
 preferred number of children.
-This idea may explain why better educated women tha
-shorter spacing than less educated women in certain 
-cases \citep{Tulasidhar1993,Whitworth2002}.
+This idea may explain why better-educated women have
+shorter spacing than less educated women in some instances
+ \citep{Tulasidhar1993,Whitworth2002}.
 These two counteracting effects may explain why finding statistically 
@@
 essential to understand what drives changes in spacing.
-The better health outcomes for girls in the presence of sex selection may,
-for example, be an unintended side-effect of the longer spacing that arises
-from sex-selective abortions, rather than, as often assumed, be driven by a 
-higher value placed on girls because of their lower number \citep{Lin2014,Hu2015}.
+We know, for example, that health outcomes for girls appear to improve
+in the presence of sex selection \citep{Lin2014,Hu2015}.
+It is possible that these improvements are an unintended side-effect of
+the longer spacing that arises from sex-selective abortions, rather than
+because the smaller number of girls makes them more valued as is often
+assumed.
 
 In this paper, I introduce and apply a novel empirical method that directly incorporates 
-the effects of sex-selective abortions on the likelihood of a son being born 
-\emph{and} the duration between births.
+the effects of sex-selective abortions on 
+the duration between births
+\emph{and} 
+the likelihood of a son. 
 The method can be used to analyze both situations with and without prenatal
 sex selection.
-Furthermore, my proposed method allows for the time since the previous 
+My proposed method allows for the time since the previous 
 birth to affect the decision on sex selection.
-By examining whether sex selection decisions change with spacing, we can 
-draw a more nuanced picture of the degree of son preference.
+By examining under what circumstances sex selection decisions change with 
+spacing, we can draw a more nuanced picture of the degree of son preference.
 
 % [Why India?]
-I apply the method to birth histories for Hindu women, using data from 
+I apply the method to birth histories of Hindu women, using data from 
 India's National Family and Health Surveys (NFHS), covering the period 
@@
 prenatal sex determination in India over the period covered.
-Abortion has been legal in India since 1971 and still is, but the 
-first reports of prenatal sex determination did
-not appear until 1982--83 \citep{Sudha1999,bhat06,Grover2006}.
+Abortion has been legal in India since 1971 and still is.
+The first reports of sex determination appeared around 
+1982--83 \citep{Sudha1999,bhat06,Grover2006}.
 The number of clinics quickly increased, and knowledge about sex selection 
@@
 over the four decades covered by the data.
-The exception is for first births, where the median duration has either remained
-the same or slightly declined, although this hides a substantial compression of
-the variation in spell length.
-Second, the increase in duration is substantially larger for the groups of women 
-who are most likely to use sex selection.
-Specifically, among the best educated women, those with no boys now has 
-significantly longer spacing and a more male-biased sex ratio than those 
-with boys.
-Third, women with no education still follow the standard pattern of short 
-spacing when they have girls and little evidence of the use of sex selection.
-In other word, these women follow a strategy where they achieve a son through
-higher fertility rather than use of sex selection.
-Finally, sex ratios are more likely to decline within spells at lower parities, 
-where the pressure to ensure a son is lower, and more likely to increase or 
-remain consistently high for higher-order spells, where the pressure to ensure 
-a son is high.
+The exception is for first births, where the median duration has either
+remained the same or slightly declined, although this hides a
+significant compression of the variation in spell length.
+Second, the most substantial increase in spacing is for the women who
+are most likely to use sex selection.
+Specifically, among the best-educated women, those with no boys now has 
+significantly longer spacing---and a more male-biased sex ratio---than 
+similar women with boys.
+Third, women with no education still follow the standard pattern of
+short spacing when they have girls and little evidence of the use of sex
+selection.
+In other words, these women adhere to a strategy where they achieve a
+son through higher fertility rather than the use of sex selection.
+Finally, sex ratios are the most likely to decline within spells at
+lower-order spells, where the pressure to provide a son is smaller, and
+are more likely to increase or remain consistently high for higher-order
+spells, where the pressure to ensure a son is high.
 

### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Estimation Strategy

@@
 
-The unit of analysis is individual spells, the period from one birth, or marriage for
+The unit of analysis is a spell, the period from one birth, or marriage for
 the first spell, to the next.
-For some spells, the duration is censored, either because the survey
+For some spells, the duration is censored, for example, because the survey
 took place before the birth that would end the spell or because the couple
@@
 or a girl is born, because access to prenatal sex determination means that
-the sex of children born is no longer necessarily a random event.
-Prior research on birth spacing has used hazard models where the only 
-possible exit state was the birth of a child. 
-Having only one exit state works when there is no sex selection---making the 
-sex of the child a random event---but not here because at least some couples use 
-sex selection.%
+parents can choose the sex of children born.
+Prior research on birth spacing, in contrast, relied on single
+exit state hazard models.%
 \footnote{
@@
 }
+Having only one exit state works when there is no sex selection---making the 
+sex of the child a random event---but not here since at least some couples use 
+sex selection.
 
@@
 the shape of the hazard functions across groups.
+The use of a non-proportional specification also mitigates any potential 
+effects of unobserved heterogeneity when used in conjunction with a 
+flexible baseline hazard \citep{Dolton1995}.
 Proportional hazard models, where covariates have a multiplicative 
@@
 are biased.
+
 It is unlikely---even in the absence of prenatal sex determination---that 
@@
 is especially problematic for higher-order spells where different
-sex composition of previous births can lead to substantial difference 
+sex composition of previous births can lead to substantial differences 
 both in the likelihood of progressing to the next birth and
 how soon couples want their next child if they are going to have one.
+
 The introduction of prenatal sex determination is likely to exacerbate 
@@
 that the effects of covariates vary within the spell as well.
-The use of a non-proportional specification also mitigates any potential 
-effects of unobserved heterogeneity when used in conjunction with a 
-flexible baseline hazard \citep{Dolton1995}.
 
@@
 hazard model with two exit states: either a boy or a girl is born.
-For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$ and 
+For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
 the spell continues until time $t_i$, when either a birth occurs or the spell 
@@
 }
-There are two exit states: birth of a boy, $j=1$, or birth of a girl, $j=2$, and 
+There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
 $J_i$ is a random variable indicating which event took place.
@@
 overly strong restrictions on the baseline hazard.
+
 The explanatory variables in $\mathbf{Z}$ and the interactions between them 
@@
 composition of previous children, if any, and $Z_2$ captures area of residence.
-This allows the effects of the main explanatory variables on the probabilities 
+The non-proportionality allows the effects of the main explanatory variables on the probabilities 
 of having a boy, a girl, or no birth to vary over time within a spell.
@@
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, transforming the data, so each observation is a period---here equal
-to three months---the model can be estimated using a standard multinomial logit model.
-if the data are transformed so the unit of analysis is a time period, in 
-this case 3 months periods, rather than the individual woman, the model can be 
-estimated using a standard multinomial logit model.%
+Hence, transforming the data, so each observation is an interval---here equal
+to three months---the model can be estimated using a standard multinomial logit model.%
 \footnote{
-A potentially issue is that the multinomial model assumes that alternative 
+A potential issue is that the multinomial model assumes that alternative 
 exit states are stochastically independent,
@@
 hazard of having a boy.
-To address this issue the estimations include a proxy for fecundity
-discussed in Section \ref{sec:data}.
-In addition, the multivariate probit model can be used as an alternative
+I, therefore, include a proxy for fecundity discussed in Section \ref{sec:data}.
+Also, the multivariate probit model can be used as an alternative
 to the multinomial logit because the IIA is not imposed \citep{han90}.
-The results are essentially identical between these two models and
+The results are substantially identical between these two models and
 available upon request.
@@
 In the reorganized data the outcome variable is 0 if the
-woman does not have a child in a given period (the base outcome), 1 if 
-she gives birth to a son in that period, and 2 if she gives birth to 
-a daughter in that period.
+woman does not have a child in a given interval (the base outcome), 1 if 
+she gives birth to a son in that interval, and 2 if she gives birth to 
+a daughter in that interval.
 
@@
 Direct comparison of standard survival curves, therefore, tells us little 
-about how the spread of sex selection affects birth spacing across, for
-example, different sex compositions of prior children.
-
-To overcome this problem, I condition on the likelihood of parity progression 
-when examining birth spacing.
-If, for example, women with a given set of characteristics have an 80\%
-chance of ending a spell with a birth their median spell duration is when
-their survival curve shows that 40\% are predicted to have exited the spell.
-It is important to note that this is not the same as simply calculating 
-the median \emph{observed} spell lengths among women who have a given 
+about how the spread of sex selection affects birth spacing across groups.
+
+To overcome this problem, I condition on the predicted likelihood of parity 
+progression when examining birth spacing measures, such as the median duration 
+to a birth.
+How well this approach works depends on whether the spell length covered is 
+sufficiently long that few women are likely to give birth after the spell cut-off.
+I discuss the choice of spell length below.
+It is important to note that the approach is not the same as merely calculating 
+the birth spacing measures for women who already have a given 
 parity child in the survey because that number does not take into account
 the censoring of spells that will eventually lead to a birth.
-
-Median durations can then be averaged across women using the probabilities 
-of ending a spell with a child as weights.
-How well this approach works depends on whether the spell length covered is 
-sufficiently long that few women are be likely to give birth after
-the spell cut-off.
-I discuss the choice of spell length below.
-In addition to calculating conditional spell length for different 
+In addition to calculating conditional birth spacing measures for different 
 percentages, I also present graphs of both standard survival curves and
@@
 
-Finally, with the predicted probabilities of having a boy and of having 
+Finally, given the predicted probabilities of having a boy and of having 
 a girl for each $t$ within a spell, is it easy to calculate the estimated 
@@
 \end{equation}
-Combining the percentage boys and the likelihood of exiting across all $t$ 
-gives the predicted percent boys born over the entire spell.
+Combining the percentage boys and the likelihood of exiting the spell 
+across all $t$ gives the predicted percent boys born over the entire spell.
 In addition to the predicted percent boys over the entire spell, 

### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Data

@@
 (NFHS-1, NFHS-2, NFHS-3, and NFHS-4),
-collected in 1992--93, 1998--99, 2005--2006, and 2015--2016.%
+collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.%
 \footnote{
@@
 and those with missing information on education.
-Women interviewed in NFHS-3 or NFHS-4 who were never married or where gauna 
-had not been performed were also dropped.
+Women interviewed in NFHS-3 or NFHS-4 who were never married or where Gauna 
+had not yet been performed were also dropped.
 The same goes for women who had at least one multiple births,
@@
 Finally, in NFHS-1 and NFHS-2 enumerators probed only for a missed birth if the
-initially reported birth interval was four calendar years or more.
-But, given short durations between births, especially after the birth of a girl,
+initially reported birth interval was four calendar years or more,
+but, given short durations between births, especially after the birth of a girl,
 that procedure is unlikely to pick up all missed children.
 
-Recall error is heavily dependent on the length of marriage \citep{Portner2018b}.
+Recall error is heavily dependent on how long ago a woman was married 
+\citep{Portner2018b}.
 I, therefore, drop women married 22 years or more 

### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Spell Definition

@@
 The allocation into periods is determined by when conception and therefore 
-decisions on sex selection begin, even if no births are observed until 
-nine months later.
+decisions on sex selection can begin, even if we do not observe
+any births until nine months later.
 

### 2018-03-31 paper/sexSelectionSpacing-ver1.tex
Edit Explanatory Variables

@@
 I divide women into three groups based on education attainment: no
-education, 1 to 7 years of education, and 8 and more years of education.
+education, one to seven years of education, and eight and more years of education.
 The models are estimated separately for each education level to reduce
@@
 
-The area of residence is a dummy variable for the household living in
+Area of residence is a dummy variable for the household living in
 an urban area.
@@
 a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
-This is confirmed below by the very short spells between marriage and first birth,
-even among the most educated.
+The absence of contraception before the first birth is confirmed below by the 
+very short spells between marriage and first birth, even among the most educated.
 Hence, a long spell between marriage and first birth is likely due to low fecundity.

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Descriptive Statistics

@@
 Censoring becomes even more important for the third and fourth
-spells, with more than 70\% of the observations censored.
-The level of censoring also increases with parity and time period,
+spells, with around 70\% of the observations censored.
+The level of censoring also increases with parity and time,
 which reflects a combination of factors: timing of the surveys

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Results

@@
 one girl and one boy, and two girls.
+It is, in principle, possible to estimate the model taking into account
+the ordering of children, but this would further lower the power of the
+test, by adding one additional group for the third spell and four
+additional groups for the fourth spell. 
 As discussed, the sex composition of previous children affects both the timing
@@
 of a girl than after a boy, but the abortions will increase the 
-length of the space, and may even lead to longer spacing after the
+duration between births, and may even lead to longer spacing after the
 birth of girls than after boys.
@@
 Second, have the shapes of the survival curves changed?
-The shapes of the survival curves provide clues both to general
-changes in birth spacing and to whether parents are
+The shapes of the survival curves provide information both on general
+changes in birth spacing and whether parents are
 still trying to conceive earlier after girls than boys.
@@
 with access to sex selection.
-At a technical level, the shapes of the survival curve serve as an
-indicator for the presence of non-proportionality.
 
@@
 ratio at birth---as is standard practice in the literature---will not provide
-correct estimates of the use of sex selection or the sex ratio when 
-childbearing is completed.
+correct estimates of the use of sex selection or the sex ratio at
+the conclusion of childbearing.
 Second, any changes in the sex ratio within a spell provides clues
@@
 \ref{tab:median_sex_ratio_high}
-show predicted median duration and sex ratios by period, spell, and sex 
-composition for the three different education levels separated by area of residence.%
+show the predicted median duration and sex ratios by period, spell, and sex 
+composition for the three education levels separated by area of residence.%
 \footnote{
@@
 } 
-The predictions are based on the estimation method described in 
-Section \ref{sec:strategy}.
-The standard errors for both measures are based on bootstrapping, where the 
-original sample is resampled with replacement and the method is applied to 
-the new sample.
-
-The predicted median duration shown is the weighted average over the women in the 
-sample's predicted median durations, using the individual probabilities of 
-giving birth as weights.
+For each subsample, I first estimate the model described in Section 
+\ref{sec:strategy} and then use the estimated coefficients to predict 
+median duration and sex ratio.
+For the standard errors, I use bootstrapping for both measures,
+where the model is repeatedly estimated using resampling with replacement.
+
+The predicted median duration is the weighted average over the women in the 
+subsample, using the individual probabilities of giving birth as weights.
 For each woman in a sample, I calculate her probability of ending the spell 
@@
 40\% probability of having exited with a birth.
-The 40\% is equivalent to the 60\% point in a standard survival curve because that 
+The 40\% is equivalent to the 60\% point on a standard survival curve because that 
 captures how many have not yet exited.
 
-For second through fourth spell I show whether durations for sex composition
-other than only girls are statistically significantly different from the
-duration with only girls.
-I use bootstrapping to calculate the level of statistical significance.
-For each new sample, I calculate the difference in duration and these
-differences are used to calculate the standard error and the level of
-significance for the difference in the original sample.
+For the second through the fourth spell, I show whether durations for sex 
+composition other than only girls are statistically significantly different 
+from the duration with only girls.
+To calculate the level of statistical significance, I bootstrap the
+difference in spacing.
 
@@
 only girls, but the number of births to women with only sons becomes small 
-in the later periods because of falling fertility.
+in the later periods.
 Hence, it is possible to have substantial differences in spacing that are
@@
 and fourth spell.
-It is, in principle, possible to estimate the model taking into account the 
-ordering of children, but this would further lower the power of the test, by 
-adding one additional group for the third spell and four additional groups for the fourth spell.
 
@@
 }
-The predicted sex ratio captures the percent boys that will be born to women 
-in the sample once childbearing for that spell is over.
+The predicted sex ratio captures the percent boys that will have been born to women 
+in the sample when childbearing for that spell is over.
 

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit No Education Women

@@
 Most of the women without education live in rural areas,
-while there are relatively few urban women with no education.
+whereas there are relatively few urban women with no education.
 There are especially very few urban women to based the third
@@
 change, and possibly even a small decline.
-This decline may be the result of a combination of lower recall
-error, increasing age at marriage, and better health.
 
@@
 For the second spell, the difference in median duration between
-having a girl or a boy as the first-born are mostly between 0.5 and 1 
-month, although it varies from a low of 0.2 months for rural women 
-in 1995--2004 period to a high of 1.5 months
-for urban women in the 1985--1994 period.
-Focusing on rural women for the third spell, the difference is in
-duration, on average, slightly over one month between only girls and only boys 
-and the differences are statistically significant in all periods.
-For rural women, the differences for the fourth spell are just below
-two months, except for the 1972--1984 period, which is
-also the only period where the difference is not statistically significant.
-
-It is possible that remaining recall error is behind some of the
-smaller differences in duration.
-One example is the second spell in the 1995--2004 period, where there 
-is only 0.2 months difference between duration after one girl and 
-duration after one boy.
-Similarly, the small difference for the fourth spell in the 1972--1984
-period may be the result of recall error with a very high 
-percentage of boys for women with three girls, despite no availability
-of sex selection.
+having a girl or a boy as the first-born are mostly between a half
+and one month.
+For the third spell, the difference in duration between only girls 
+and only boys is, on average, slightly over one month and statistically 
+significant in all periods.
+The differences for the fourth spell are between two and three months, 
+except for the 1972--1984 period, which is also the only period where 
+the difference is not statistically significant.
 

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Middle Education Women

@@
 Table \ref{tab:median_sex_ratio_med} shows.
-The distribution across urban and rural is more even for this education
-group than for the no education women.
+The sample size is more evenly distributed across urban and rural 
+for this education group than for the no education women.
 As a result, the only spells where there are few women to base 
@@
 The spacing between births increased over the four decades.
-On average, the increase is approximately two months.
+On average, the increase is approximately three to four months.
 The exception is again the first spell, where the time from
@@
 the differences in spacing between only girls and only boys
-increase with spell number.
+increase with between the second and third spell.
 For both urban and rural women, the difference in duration is just over
-a month for the second spell, but it is 1.4 and 2.3 months for urban and
+a month for the second spell, but it is 1.4 and 2.8 months for urban and
 rural women, respectively, for the third spell.
@@
 have begun to use sex selection at higher-order spells.
-An emerging use of sex selection is also consistent with the falling
-fertility for both urban and rural women shown below.
 

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit High Education Women

@@
 
-Women with eight or more years of education appear the least likely
-to follow the pattern of shorter spacing when they have only girls
-compared to only boys before sex selection became available as 
-Table \ref{tab:median_sex_ratio_high} shows.
-Part of the problem may be that there are few women with that level
-of education for the 1972--1984 period.
-Hence, only the results for the first and second spells in 
-both urban and rural areas are likely to be reliable.
-Furthermore, there are relatively few women with three boys who
-go on to having a fourth birth, both in urban and rural areas.
+Women with eight or more year of education mostly followed 
+the traditional spacing pattern before sex selection became 
+available as shown in Table \ref{tab:median_sex_ratio_high}.
+Compared to the two other education groups there are,
+however, more situations where the pattern is less clear.
+Part of the problem may be that there are few women in
+this group for the 1972--1984 period, and, hence, only 
+the results for the first and second spells in both urban 
+and rural areas are likely reliable.
 
@@
 especially for urban women. 
-The median duration for urban women increase between a quarter
-and three-quarters of a year, whereas the increase for rural women 
-is around a quarter of a year.
+The median duration for urban women increases between a half
+and a full year, whereas the increase for rural women 
+is between a quarter and half a year.
 The spacing between marriage and the first birth is still the
@@
 The exception is the second spell for the 1985--1994 period, where women
-with one girl have 0.4 months longer spacing the women with one boy.
+with one girl have 0.1 months shorter spacing the women with one boy.
 }
@@
 For the latest period, the difference between only girls than the
-other sex compositions is between 3.4 and 5.4 months for the third
+other sex compositions is between 4.8 and 9.1 months for the third
 and fourth spell.
@@
 Hence, it is possible that women are still willing to use sex selection
-even after giving birth to one. 
-Alternatively, this behavior may be in response to either experienced
+even after giving birth to one, although this behavior may also 
+be in response to either experienced
 or expected mortality of the first son born.
@@
 we did not have the power to detect them.
-Second, it is possible that, at least, the first-born results are an
+Second, it is possible that at least the first-born results are an
 artifact of any recall error not captured by the data restrictions.

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Distribution of Birth Spacing Across Sex Compositions and Time

@@
 
-I show survival curves conditional on parity progression rather than
+I show survival curves conditional on predicted parity progression rather than
 standard survival curves. 
@@
 differences in how likely the next birth is.
-It does, however, depend on covering a long enough spell period
-to ensure that only relatively few births are likely to take place after the
-censoring date as discussed above.
 Because the conditional survival curves are independent of the likelihood
@@
 Section \ref{sec:strategy}.
-The average woman characteristics are the means of continuous explanatory 
-variables and the majority category for categorical explanatory variables.
-Common to all is that they do not own land and belong to neither 
-a scheduled caste nor a scheduled tribe.
-
-In the interest of brevity, I discuss only a representative subset.
+For each combination of education and spell, I use values based on the
+average age at the start of the spell and, for the second and higher
+spells, the average duration of the first spell.
+Furthermore, I use the majority categories for the categorical explanatory 
+variables, which means no ownership of land and not in a scheduled caste or 
+tribe.
+The characteristics used do not change across period to ensure that 
+composition effects do not drive the changes.
+
+In the interest of brevity, I discuss only a select set of subsamples.
 Figure \ref{fig:pps_spell1} shows spacing for the first spell across the
@@
 1972--1984, and the last period, 2005--2016, for rural women with no 
-education and urban women with eight or more years of education.
+education and for urban women with eight or more years of education.
 The Appendix shows standard and conditional survival curves for all groups and 
 time periods, and I discuss some examples of standard survival
-curves in the following section.
+curves in the following section.%
+\footnote{
+To ease legibility of the graphs some three months intervals are combined
+into longer ones when there are few births available in the sample.
+}
 
@@
 
-The duration from marriage to first birth is only affected by son preferences if
-people use sex selection to achieve a son as their first-born.
-As I discuss above, the biased sex ratio for the first spell for the most educated 
-women does suggest that there might be sex selection on the first birth.
+The biased sex ratio for the first spell for the most educated 
+women suggests that there might be sex selection on the first birth.
 I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
@@
 In the 1972--1984 period, the middle 80\% of births for women with no education 
-are predicted to occur between approximately 6 and 52 months, whereas in the 
-2005--2016 period it is between 12 and 46 months.
-Hence, the compression is equivalent to a full year.
+are predicted to occur between approximately 6 and 64 months, whereas in the 
+2005--2016 period it is between 12 and 54 months.
+Hence, the compression is equivalent to more than a full year.
 Women with eight or more years of education show a slightly smaller compression:
 in the 1972--1984 period, the middle 80\% of births are predicted to occur between
-approximately 6 and 44 months, whereas in the 2005--2016 period it is between
-9 and 40 months, or a compression of seven months.
-
-The pattern for both groups shows us that women are less likely to conceive 
-before marriage in the later time periods than earlier.
+approximately 6 and 48 months, whereas in the 2005--2016 period it is between
+12 and 46 months.
+Hence, the compression is eight months.
+
+Women became less likely to conceive before marriage over time.
 In the first two periods there was a relatively smooth decline in the number of
 women without a birth starting at the time of marriage, but in the last two
-periods, there are now few women who exit early after marriage and
+periods, there are few women who exit early after marriage and
 instead there is a substantial dip between 9 and 12 months after
@@
 and higher age at marriage.
-The descriptive statistics above show, for example, that women without 
-education have seen an increase in the average age at marriage from below 
-16 to 18.5 from the first period to the last while women with the most 
-education increased from 19.5 to 20.4.
+For example, women without education have seen an increase in the average 
+age at marriage from below 16 to 18.5 from the first period to the last 
+while women with the most education increased from 19.5 to 20.4.
 
@@
 
-The distribution of spacing, shown in Figure \ref{fig:pps_high}, for the second spell 
-conditional survival curve for urban women with eight or more years of education 
-is almost indistinguishable from that of rural women with no education 
-for the 1972--1984 period.
+The distribution of spacing for the second spell is almost indistinguishable 
+between urban women with eight or more years of education and rural women 
+with no education for the 1972--1984 period, as shown in Figure \ref{fig:pps_high}.
 The small difference points to these two very different groups of women behaving similarly
@@
 Furthermore, the differences are substantial across most of the distribution.
-Twelve months after the beginning of the spell there is an approximately ten 
+Twelve months after the beginning of the spell there is a more than ten 
 percentage points difference in the conditional survival curves for only girls
@@
 those with three girls have had theirs.
-Even at three years after the spell, there is a more than five percentage
-points difference.
+Even at three years after the beginning of the spell, there is a more than 
+five percentage points difference.
 
@@
 The conditional survival curve for women with one boy and two girls is
-consistently above those with two or more son, but below those with
-three girls.
+consistently above those for women with two or more son, but below those 
+with three girls.
 The pattern fit the predicted sex ratios shown above where the highest

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Does Sex Selection Change within Spells

@@
 economies of scale in childbearing and rearing that parents lose 
-if children were born too far apart \citep[p 374]{schultz97}. 
-In this case we should observe the predicted sex ratio decline
+if children are born too far apart \citep[p 374]{schultz97}. 
+In this case, we should observe the predicted sex ratio decline
 with spell length.
@@
 the same two periods for urban women with either two girls or one boy and one
-girl as their first two children.%
-\footnote{
-There is no evidence of unequal sex ratios in either period for similar women 
-with two boys as their first two children as shown in Figure TK.
-}
+girl as their first two children.
 
@@
 the woman has given birth to a boy.
-Furthermore, as the Appendix shows, only about 25\% of urban women with 
-two boys have a third child in the 2005--2016 period, 
-down from close to 60\% in the 1995--2004 period.
-
-The third spell figures show a very different situation with almost no 
-change in sex ratios with duration for women with two girls, but substantial 
-increases in sex ratios with duration for women with one boy and one girl.
-The high, but stable, sex ratio for women with two girls is likely 
+
+The third spell figures show a very different situation with substantial 
+increases in sex ratios.
+The high sex ratio for women with two girls is likely 
 motivated by the combined desire to limit fertility and ensure a son;
@@
 and that the two groups conceive at the same rate.
-In that case, we should expect exactly the increasing sex ratios
+In that case, we should expect precisely the increasing sex ratios
 we observe, especially given the declining fertility over time.

### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Conclusion

@@
 pattern of shorter spacing when a woman does not have the desired number of 
-son and with limited evidence of biased sex ratios and the increases in
+sons.
+There is also limited evidence of biased sex ratios and the increases in
 spacing that should follow from the use of sex selection.
@@
 At the other extreme, women with eight or more years of education have
-experienced an almost complete reversal of their spacing patterns.
+experienced an almost complete reversal of the traditional spacing patterns.
 Rather than having the next birth sooner as they mostly did before 
@@
 use of sex selection rather than changes in son preference. 
-Banning prenatal sex determination has therefore not been able to
+Banning prenatal sex determination has not been able to
 reverse the use, although it is possible that it has slowed the rate 
@@
 The result is that median spacing from marriage to first birth
-that has changed little or even declined for the best-educated women.
+has changed little or even declined for the best-educated women.
 Both the decrease for the first spell and the increase for higher-order
-spells are consistent with an increased access to contraceptives over
+spells are consistent with increased access to contraceptives over
 time \citep{Yeakey2009}.
 
-The empirical model is designed to allow for the effects of covariates
-to change within the spell. Non-proportionality is essential because the
-use of sex selection may vary within a spell. The use of sex selection
-may change either because preferences for not too long spacing between
-births override the preference for sons or because of selection, where
+The empirical model allows for the effects of covariates
+to vary within the spell. 
+Non-proportionality is essential because the use of sex selection may 
+vary within a spell. 
+The use of sex selection may change either because preferences for not 
+too long spacing between births override the preference for sons or 
+because of selection, where
 the women who remain in a spell are those with the strongest son
 preference who have been through multiple pregnancies because the
-fetuses were female. Because these move in opposite directions, I cannot
-directly establish the extent to which they affect the results. Both
-are, however, present, as can be seen from the cases where there is
+fetuses were female. 
+Because these move in opposite directions, I cannot
+directly establish the extent to which they affect the results. 
+Both are, however, present, as can be seen from the cases where there is
 either a decline in sex ratio with spell duration or a substantial
-increase with spell duration. The first case is more likely at lower
+increase with spell duration. 
+The first case is most likely at lower
 parities where there is still less pressure to ensure a son, which
-allows any preference for shorter spacing to play more of a role. The
-second is on the other hand more likely to have an effect for higher
+allows any preference for shorter spacing to play more of a role. 
+The second is most likely for higher
 parities where the desire to limit further childbearing and ensure a son
@@
 
-The potential for changes in sex ratio within a spell means
-that censoring is an important issue when trying to understand the 
-development in sex ratio.
-This is especially the case when it comes to establishing whether 
-the use of sex selection is increasing or decreasing.
+The potential for changes in sex ratio within a spell means that
+censoring is an important issue when trying to understand how the sex
+ratio changes over time, and especially when it comes to establishing
+whether the use of sex selection is increasing or decreasing.
 Take, for example, the case of women with eight or more years of
@@
 2005--2009 or the 2010--2014 periods and we treat end of 2015
-as the cut-off time, then the observed sex ratio for the 2005--2009
+as the cut-off point, then the observed sex ratio for the 2005--2009
 women is 55.99\% boys while it is 55.38\% for women who started 
@@
 \footnote{
-This combines urban and rural women; the basis result 
+The calculations combines urban and rural women; the basis result 
 changes little if I split by area of residence.
@@
 sex ratios are 56.10\% boys and 56.08\% boys for the 
-2005--2009 and the 2010--2015 starts.
-The reason for the difference is that while for the 
-2005--2009 start we would have observed 7,134 birth out
-of a predicted 7,451 total number of births, we would
-only have observed 3,348 births out of a predicted 8,842
-for the 2010--2014 group.
+2005--2009 and the 2010--2015 starts, which indicates
+virtually no change over time.
+The reason for the difference is that while we would have 
+observed 7,134 birth out of a predicted 7,451 total number 
+of births for the 2005--2009 start, we would only have observed 
+3,348 births out of a predicted 8,842 for the 2010--2014 group.
 
@@
 It appears that the use of sex selection is spreading to women with lower 
-levels of education so that even women with one to seven years of 
-education show unequal sex ratios and longer spacing for their higher-order spells.
+levels of education.
+Even women with one to seven years of education show unequal sex ratios 
+and longer spacing for their higher-order spells.
 
@@
 sex selection changes over time.
-For that, a combined model that incorporates the full fertility
+For both, a combined model that incorporates the full fertility
 history of women would be more appropriate.
-A model of this type would allow us to jointly model fertility
-and sex selection and help address both questions.
 
@@
 side-effect of the longer spacing that arises from sex-selective 
-abortions then an effective ban on sex selection may, at least
+abortions, then an effective ban on sex selection may, at least
 temporarily, worsen health outcomes for girls.
@@
 interacts with the use of sex selection.
-Increased autonomy for women, for example from better opportunities
+Increased autonomy for women, arising, for example, from better opportunities
 for working outside the home, has been suggested as a way to increase
@@
 This may, however, be a double-edged sword.
-On the one hand, it is an clear benefit to the women who gain  
+On the one hand, it is a clear benefit to the women who gain  
 bargaining power, and it increases the cost of repeated 
@@
 On the other hand, it may further lower desired fertility, and 
-everything else equal, that may lead to higher use of sex selection.
+that may, everything else equal, lead to higher use of sex selection.
 Understanding the trade-off between long-term benefits from improvements in

### 2018-04-02 paper/sexSelectionSpacing-ver1.tex
Appendix section with all graphs

@@
 estimated duration tables, and graphs for all 
-groups and periods.
+education groups and spells.
 
@@
 
+\section{Graphs for All Education and Spell Groups}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+% [FIRST SPELL]
+
+\subsection{First Spell}
+
+\input{../figures/appendix_spell1_low.tex}
+
+\input{../figures/appendix_spell1_med.tex}
+
+\input{../figures/appendix_spell1_high.tex}
+
+\begin{figure}[htpb]
+\centering
+\caption*{No Education}
+\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
+\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
+\caption*{1-7 Years of Education}
+\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
+\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
+\caption*{8 or more Years of Education}
+\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
+\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
+\caption{Survival curves conditional on progression to first birth; start point is month of marriage}
+\label{fig:results_spell1_pps}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Second Spell}
+
+\input{../figures/appendix_spell2_low.tex}
+
+% PARITY PROGRESSION SURVIVAL CURVES - Low
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2005]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
+% SPELL 2 - URBAN - MEDIUM
+
+\input{../figures/appendix_spell2_med.tex}
+
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+% Low education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1-7 years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_med_pps}
+\end{figure}
+
+% High education
+
+\input{../figures/appendix_spell2_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - High education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_high_pps}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Third Spell}
+
+% low education
+\input{../figures/appendix_spell3_low.tex}
+
+% PARITY PROGRESSION SURVIVAL - LOW
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_low_pps}
+\end{figure}
+
+% Medium education
+
+\input{../figures/appendix_spell3_med.tex}
+
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1 to 7 years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_med_pps}
+\end{figure}
+
+% High education
+
+\input{../figures/appendix_spell3_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - high
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_high_pps}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Fourth Spell}
+
+% low education
+
+\input{../figures/appendix_spell4_low.tex}
+
+% PARITY PROGRESSION SURVIVAL - LOW
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell4_low_pps}
+\end{figure}
+
+% Medium education
+
+\input{../figures/appendix_spell4_med.tex}
+
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 1 to 7 years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell4_med_pps}
+\end{figure}
+
+% High education
+
+\input{../figures/appendix_spell4_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - high
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell4_high_pps}
+\end{figure}
+
 \end{document}

### 2018-04-10 paper/sexSelectionSpacing-ver1-demography.tex
Version for Demography without front

--- 2018-04-02 paper/sexSelectionSpacing-ver1.tex
@@
 India's Experience over Four Decades%
-\protect\thanks{%
-I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-University of Washington, University of Aarhus, the Fourth 
-Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful 
-suggestions and comments.
-I would also like to thank Nalina Varanasi for research assistance.
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
-The views and findings expressed here are those of the author and
-should not be attributed to the World Bank or any of its member countries.
-Partial support for this research came from a Eunice Kennedy Shriver National
-Institute of Child Health and Human Development research infrastructure grant,
-5R24HD042828, to the Center for Studies in Demography and Ecology at the
-University of Washington.
-}
-}
-
-\author{Claus C P\"ortner\\
-    Department of Economics\\
-    Albers School of Business and Economics\\
-    Seattle University, P.O. Box 222000\\
-    Seattle, WA 98122\\
-    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
-    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
-    \& \\
-    Center for Studies in Demography and Ecology \\
-    University of Washington\\ \vspace{2cm}
-    }
-
-\date{March 2018\\
-\bigskip
-Preliminary}
+% \protect\thanks{%
+% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
+% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
+% University of Washington, University of Aarhus, the Fourth 
+% Annual Conference on Population, Reproductive Health, 
+% and Economic Development, and the Economic Demography Workshop for helpful 
+% suggestions and comments.
+% I would also like to thank Nalina Varanasi for research assistance.
+% Support for development of the method from the University of Washington Royalty 
+% Research Fund and the Development Research Group of the World Bank is gratefully 
+% acknowledged.
+% The views and findings expressed here are those of the author and
+% should not be attributed to the World Bank or any of its member countries.
+% Partial support for this research came from a Eunice Kennedy Shriver National
+% Institute of Child Health and Human Development research infrastructure grant,
+% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
+% University of Washington.
+% }
+}
+
+\author{}
+% \author{Claus C P\"ortner\\
+%     Department of Economics\\
+%     Albers School of Business and Economics\\
+%     Seattle University, P.O. Box 222000\\
+%     Seattle, WA 98122\\
+%     \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
+%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
+%     \& \\
+%     Center for Studies in Demography and Ecology \\
+%     University of Washington\\ \vspace{2cm}
+%     }
+
+\date{April 2018}
 
@@
 
-\newpage
+% \newpage
 \thispagestyle{empty}

### 2018-04-18 presentations/2018-paa-poster.tex
Initial commit of poster for PAA 2018

% Poster presentation for PAA 2018

\documentclass[final]{beamer}
  \mode<presentation>
  {
  \usetheme{CCP}
  }
  \usepackage[orientation=landscape,scale=1.4]{beamerposter}

\setlength{\paperwidth}{48in} 
\setlength{\paperheight}{36in}

\usepackage{fontspec}
\setsansfont[Ligatures=TeX]{Gandhi Sans}
% \usepackage{unicode-math}
% \setmathfont{TeX Gyre Pagella Math}

\title{Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades}
\author{Claus P\"ortner}
\institute{Albers School of Business and Economics, Seattle University, \& Center for Studies in Demography and Ecology, University of Washington}
\footer{\texttt{cportner@seattleu.edu}}
\begin{document}

\begin{frame}{}
\begin{columns}[t]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{column}{.3\linewidth}

\begin{block}{\LARGE Introduction}

Some text that goes in a block.

\end{block}

\end{column}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{column}{.3\linewidth}

more text

\end{column}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{column}{.3\linewidth}

even more text

\end{column}

\end{columns}

\end{frame}

\end{document}

### 2018-04-18 presentations/2018-paa-poster.tex
Add Data and Methods sections

@@
 
-\begin{block}{\LARGE Introduction}
+\begin{block}{\LARGE Background}
 
-Some text that goes in a block.
+The central question addressed here is the extent to which spacing patterns 
+significantly changed as prenatal sex determination became available.
+Specifically, did the spacing after girls increase relative to the spacing
+after boys?
+The underlying idea is that in the absence of sex selection son 
+preference leads to shorter spacing after the birth of a girl than after the 
+birth of a boy, whereas son preference increases the spacing after the birth 
+of a girl relative to after the birth of a boy when prenatal sex selection is 
+available.
+I introduce a new method that simultaneously accounts for spacing
+between births and the potential use of sex selection. 
+I apply the method to over four decades of data from India's NFHS.
+
+\end{block}
+
+\begin{block}{Objectives}
+
+\end{block}
+
+\begin{block}{Methods}
+
+The model is a discrete time, non-proportional, competing risk 
+hazard model with two exit states: either a boy or a girl is born.
+\begin{itemize}
+\item the competing risk framework captures that access to prenatal 
+sex determination means that parents can choose the sex of children born.
+\item the non-proportional hazard specification captures that  
+sex composition and the use of sex selection are likely to affect 
+the shape of the hazard functions across groups.
+\end{itemize}
+
+The probability of ever having a next birth varies across groups.
+Direct comparison of standard survival curves, therefore, tells us little 
+about how the spread of sex selection affects birth spacing across groups.
+I therefore condition on the predicted likelihood of parity 
+progression when examining birth spacing measures.
+
+In addition to calculating conditional birth spacing measures for different 
+percentages, I also present graphs of both standard survival curves and
+survival curves conditional on parity progression (which therefore
+begin at 100\% and end at 0\%).
+
+Finally, I calculate the predicted percent boys born over the entire spell.
 
@@
 
-more text
+\begin{block}{Data}
+
+The data come from the four rounds of the National Family Health Survey.
+
+I exclude visitors to the household, as well as
+women who have never been married or married more than once, divorced, or who are 
+not living with their husband,
+women with inconsistent age at marriage,
+and those with missing information on education.
+The same goes for women who had at least one multiple births,
+reported having a birth before age 12, had a birth before marriage, or
+duration between births of less than nine months.
+Finally, I restrict the sample to Hindus,
+who constitute about 80\% of India's population.
+
+Recall error is heavily dependent on how long ago a woman was married.
+I, therefore, drop women married 22 years or more 
+for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
+and 25 years for NFHS-3 and NFHS-4.
+The final sample consists of 
+\input{../tables/num_women.tex}
+% [number] women, with [number] parity one through four births.
+
+\end{block}
+
+\begin{block}{Spell Definition}
+
+The first spell begins at the month of marriage.
+
+The second and subsequent spells begin nine months after the previous birth 
+because that is the earliest we should expect to observe a new birth.
+
+All spells continue until either a child is born or censoring occurs.
+Censoring can happen for three reasons:
+the survey takes place;
+sterilization of the woman or her husband;
+or too few births are observed for the method to work.
+
+I group spells into four periods based on the year of marriage
+or year of the previous birth:
+1972--1984, 1985--1994, 1995--2004, and 2005--2016.
+
+\end{block}
+
+\begin{block}{Results}
+
+\end{block}
 
@@
 
-even more text
+\begin{block}{Conclusion}
+
+The results show two very different approaches to son preference.
+
+\bigskip
+
+At one extreme, women without education mostly follow the standard 
+pattern of shorter spacing when a woman does not have the desired number of 
+sons.
+
+\bigskip
+
+At the other extreme, women with eight or more years of education have
+experienced a reversal of the traditional spacing patterns.
+Women with either no or one son now have substantially longer spacing 
+than if they have two or more sons.
+
+\bigskip
+
+Although it is not possible to directly observe whether sex selection
+causes the unequal sex ratio and longer spacing the results are
+consistent with a general increase in sex selection over time.
+
+\bigskip
+
+Compared to previous research one result stands out: 
+the use of sex selection is spreading to women with lower levels of education.
+
+\end{block}
+
+\begin{block}{Future Research}
+
+Two important, interconnected, questions:
+What is the connection between falling fertility and the 
+use of sex selection and is the use of sex selection increasing 
+or decreasing over time?
+
+\bigskip
+
+Broader questions:
+\begin{itemize}
+\item To what extent are improvements in health for girls
+relative to boys the result of selection, the longer spacing between
+births, or changing son preference?
+\item What is the interaction between female labor force participation
+and the use of sex selection?
+\end{itemize}
+
+\end{block}
 

### 2018-04-19 presentations/2018-paa-poster.tex
Add text

@@
   }
-  \usepackage[orientation=landscape,scale=1.4]{beamerposter}
+  \usepackage[orientation=landscape,scale=1.2]{beamerposter}
 
@@
 
+\newlength{\sepwid}
+\newlength{\onecolwid}
+\newlength{\twocolwid}
+\newlength{\threecolwid}
+\setlength{\sepwid}{0.024\paperwidth}
+\setlength{\onecolwid}{0.24\paperwidth}
+\setlength{\twocolwid}{0.4\paperwidth}
+\setlength{\threecolwid}{0.19\paperwidth}
+
 \title{Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades}
@@
 \institute{Albers School of Business and Economics, Seattle University, \& Center for Studies in Demography and Ecology, University of Washington}
-\footer{\texttt{cportner@seattleu.edu}}
+
+%%% Put the name of conference here.
+	\def\conference{2018 Annual Meeting of the Population Association of America} 
+ %%% Put your e-mail address here.
+ 	\def\yourEmail{cportner@seattleu.edu}
+
 \begin{document}
@@
 
-\begin{column}{.3\linewidth}
+\begin{column}{\onecolwid}
 
-\begin{block}{\LARGE Background}
+\begin{block}{Background}
 
-The central question addressed here is the extent to which spacing patterns 
-significantly changed as prenatal sex determination became available.
-Specifically, did the spacing after girls increase relative to the spacing
-after boys?
-The underlying idea is that in the absence of sex selection son 
-preference leads to shorter spacing after the birth of a girl than after the 
-birth of a boy, whereas son preference increases the spacing after the birth 
-of a girl relative to after the birth of a boy when prenatal sex selection is 
-available.
-I introduce a new method that simultaneously accounts for spacing
-between births and the potential use of sex selection. 
-I apply the method to over four decades of data from India's NFHS.
+Son preference is often associated with shorter spacing after the 
+births of girls than boys, shorter spacing is, in turn, associated 
+with worse health outcomes for girls and mothers.
+
+However, the introduction of prenatal sex determination fundamentally changed the 
+relationship between son preference and birth spacing.
+Couples, who had shorter birth spacing before because of son preference,
+now have access to prenatal sex determination and sex-selective abortions,
+and each abortion increases birth spacing by six months to a year.
+
+As a result, we now have a situation where we may observer \emph{longer} spacing
+for families with daughters than for families with sons, precisely because
+strong son preference leads them to use sex selection.
+
+To further complicate matters, we can still observe shorter birth spacing 
+after the births of daughters as a representation of son preference for 
+families who---for one reason or another---do not use prenatal sex selection.
 
@@
 
-\begin{block}{Objectives}
+\begin{alertblock}{Contributions}
 
-\end{block}
+\begin{description}
+
+\item[Main idea:]  in the absence of sex selection son preference leads to shorter 
+spacing after the birth of a girl than after the birth of a boy, whereas 
+son preference increases the spacing after the birth of a girl relative 
+to after the birth of a boy when prenatal sex selection is available.
+
+\item[Method:] I introduce an empirical method that directly incorporates 
+the effects of sex-selective abortions on 
+the duration between births
+\emph{and} 
+the likelihood of a son.
+
+\item[Central question:] how spacing patterns changed with access
+to prenatal sex determination became available.
+Specifically, did the spacing after girls increase relative to the spacing
+after boys?
+\end{description}
+
+\end{alertblock}
 
@@
 
-\begin{column}{.3\linewidth}
+\begin{column}{\twocolwid}
 
@@
 
-\begin{column}{.3\linewidth}
+\begin{column}{\onecolwid}
 
@@
 
-The results show two very different approaches to son preference.
+\begin{enumerate}
+\item there has been a general increase in the length of spacing between births
+over the four decades covered by the data.
+The exception is for first births, where the median duration has either
+remained the same or slightly declined, although this hides a
+significant compression of the variation in spell length.
 
-\bigskip
+\item the most substantial increase in spacing is for the women who
+are most likely to use sex selection.
+Among the best-educated women, those with no boys now has 
+significantly longer spacing---and a more male-biased sex ratio---than 
+similar women with boys.
 
-At one extreme, women without education mostly follow the standard 
-pattern of shorter spacing when a woman does not have the desired number of 
-sons.
+\item women with no education still follow the standard pattern of
+short spacing when they have girls and little evidence of the use of sex
+selection.
+In other words, these women adhere to a strategy where they achieve a
+son through higher fertility rather than the use of sex selection.
 
-\bigskip
+\item sex ratios are the most likely to decline within spells at
+lower-order spells, where the pressure to provide a son is smaller, and
+are more likely to increase or remain consistently high for higher-order
+spells, where the pressure to ensure a son is high.
 
-At the other extreme, women with eight or more years of education have
-experienced a reversal of the traditional spacing patterns.
-Women with either no or one son now have substantially longer spacing 
-than if they have two or more sons.
-
-\bigskip
-
-Although it is not possible to directly observe whether sex selection
-causes the unequal sex ratio and longer spacing the results are
-consistent with a general increase in sex selection over time.
-
-\bigskip
-
-Compared to previous research one result stands out: 
-the use of sex selection is spreading to women with lower levels of education.
+\end{enumerate}
 
@@
 
+\begin{block}{Acknowledgements}
+
+Support for development of the method from the University of Washington Royalty 
+Research Fund and the Development Research Group of the World Bank is gratefully 
+acknowledged.
+The views and findings expressed here are those of the author and
+should not be attributed to the World Bank or any of its member countries.
+Partial support for this research came from a Eunice Kennedy Shriver National
+Institute of Child Health and Human Development research infrastructure grant,
+5R24HD042828, to the Center for Studies in Demography and Ecology at the
+University of Washington.
+
+\end{block}
+
 \end{column}

### 2018-04-19 presentations/2018-paa-poster.tex
Shorten background block

@@
 
-Son preference is often associated with shorter spacing after the 
-births of girls than boys, shorter spacing is, in turn, associated 
-with worse health outcomes for girls and mothers.
+Son preference has been associated with shorter spacing after the 
+births of girls than boys.
 
-However, the introduction of prenatal sex determination fundamentally changed the 
-relationship between son preference and birth spacing.
-Couples, who had shorter birth spacing before because of son preference,
-now have access to prenatal sex determination and sex-selective abortions,
-and each abortion increases birth spacing by six months to a year.
+\vskip3ex
 
-As a result, we now have a situation where we may observer \emph{longer} spacing
-for families with daughters than for families with sons, precisely because
-strong son preference leads them to use sex selection.
+Access to prenatal sex determination fundamentally changed the 
+relationship between son preference and birth spacing because each abortion 
+increases birth spacing by six months to a year.
 
-To further complicate matters, we can still observe shorter birth spacing 
-after the births of daughters as a representation of son preference for 
-families who---for one reason or another---do not use prenatal sex selection.
+\vskip3ex
+
+We may therefore now observe \alert{longer} spacing after daughters than sons, 
+precisely because strong son preference leads to the use of sex selection.
+
+\vskip3ex
+
+To complicate matters, shorter birth spacing after daughters may still 
+be a representation of son preference for 
+families who do not use prenatal sex selection.
 
@@
 son preference increases the spacing after the birth of a girl relative 
-to after the birth of a boy when prenatal sex selection is available.
+to after a boy when prenatal sex selection is available.
 
@@
 
-\item[Central question:] how spacing patterns changed with access
-to prenatal sex determination became available.
+\item[Central question:] how did spacing patterns changed with access
+to prenatal sex determination became available?
 Specifically, did the spacing after girls increase relative to the spacing

### 2018-04-19 presentations/2018-paa-poster.tex
Shorten method and data blocks

@@
 hazard model with two exit states: either a boy or a girl is born.
-\begin{itemize}
-\item the competing risk framework captures that access to prenatal 
-sex determination means that parents can choose the sex of children born.
-\item the non-proportional hazard specification captures that  
-sex composition and the use of sex selection are likely to affect 
-the shape of the hazard functions across groups.
-\end{itemize}
+\begin{description}
+\item[Competing risk] captures that
+parents can choose the sex of children born with access to prenatal 
+sex determination.
+\item[Non-proportional hazard] captures that sex composition and 
+the use of sex selection likely affect the shape of the hazard 
+functions across groups.
+\end{description}
+
+\end{block}
+
+\begin{block}{Data}
+
+The data come from the four rounds of the National Family Health Survey.
+Sample is restricted to Hindu women who are married and regular residents of
+the household and where all needed information are available.
+Because of recall error, I drop women married 22 years or more 
+for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
+and 25 years for NFHS-3 and NFHS-4.
+The final sample consists of 
+\input{../tables/num_women.tex}
+% [number] women, with [number] parity one through four births.
+
+\end{block}
+
+\end{column}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{column}{\twocolwid}
+
+\begin{block}{Spell Definition}
+
+The first spell begins at the month of marriage, whereas the second and 
+subsequent spells begin nine months after the previous birth.
+All spells continue until either a child is born or censoring occurs.
+
+\vskip3ex
+
+I group spells into four periods based on the year of marriage
+or year of the previous birth:
+1972--1984, 1985--1994, 1995--2004, and 2005--2016.
+
+\end{block}
+
+\begin{block}{Results}
 
@@
 
-\begin{column}{\twocolwid}
-
-\begin{block}{Data}
-
-The data come from the four rounds of the National Family Health Survey.
-
-I exclude visitors to the household, as well as
-women who have never been married or married more than once, divorced, or who are 
-not living with their husband,
-women with inconsistent age at marriage,
-and those with missing information on education.
-The same goes for women who had at least one multiple births,
-reported having a birth before age 12, had a birth before marriage, or
-duration between births of less than nine months.
-Finally, I restrict the sample to Hindus,
-who constitute about 80\% of India's population.
-
-Recall error is heavily dependent on how long ago a woman was married.
-I, therefore, drop women married 22 years or more 
-for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
-and 25 years for NFHS-3 and NFHS-4.
-The final sample consists of 
-\input{../tables/num_women.tex}
-% [number] women, with [number] parity one through four births.
-
-\end{block}
-
-\begin{block}{Spell Definition}
-
-The first spell begins at the month of marriage.
-
-The second and subsequent spells begin nine months after the previous birth 
-because that is the earliest we should expect to observe a new birth.
-
-All spells continue until either a child is born or censoring occurs.
-Censoring can happen for three reasons:
-the survey takes place;
-sterilization of the woman or her husband;
-or too few births are observed for the method to work.
-
-I group spells into four periods based on the year of marriage
-or year of the previous birth:
-1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-
-\end{block}
-
-\begin{block}{Results}
-
-\end{block}
-
-\end{column}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{column}{\onecolwid}
 
-\begin{block}{Conclusion}
+\begin{alertblock}{Conclusion}
 
@@
 
-\end{block}
+\end{alertblock}
 

### 2018-04-19 presentations/2018-paa-poster.tex
Minor edits

@@
 the use of sex selection likely affect the shape of the hazard 
-functions across groups.
+functions across groups and that use of sex selection may vary
+within a spell.
 \end{description}
@@
 
-Two important, interconnected, questions:
+The results lead to two important, interconnected, questions:
 What is the connection between falling fertility and the 
-use of sex selection and is the use of sex selection increasing 
+use of sex selection, and is the use of sex selection increasing 
 or decreasing over time?
@@
 
-Broader questions:
+There are also two broader questions:
 \begin{itemize}
@@
 relative to boys the result of selection, the longer spacing between
-births, or changing son preference?
+births, or changing son preference or higher value placed on girls
+with fewer of them around?
 \item What is the interaction between female labor force participation

### 2018-04-19 presentations/2018-paa-poster.tex
Begin adding tables of results

@@
 % \setmathfont{TeX Gyre Pagella Math}
+\usepackage{dcolumn}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage[flushleft]{threeparttable}
+
+\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
+\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
+\newcommand{\X}{$\times$ }
+\newcommand{\hs}{\hspace{15pt}}
 
@@
 
+\begin{table}[hp!]
+\begin{center}
+\begin{scriptsize}
+\begin{threeparttable}
+\caption{Estimated Median Duration and Sex Ratio for Rural Women with No Education}
+\label{tab:median_sex_ratio_low}
+\begin{tabular}{@{} c l D{.}{.}{2.3} D{.}{.}{2.3}  D{.}{.}{2.3} D{.}{.}{2.3} @{}}
+\toprule
+                   &                            & \mct{1972--1984}                                    & \mct{2005--2016}                                      \\ \cmidrule(lr){3-4} \cmidrule(lr){5-6} 
+                   & \mco{Composition of}       & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}   & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}     \\ 
+ \mco{Spell}       & \mco{Prior Children}       & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                          \\ \midrule
+\multirow[c]{2}{*}{1} &                            &    26.2       &    52.1^{**}  &    24.4       &    51.5        \\
+                      &                            &    (0.2)      &    (0.3)      &    (0.1)      &    (0.4)       \\
+\addlinespace 
+\multirow[c]{3}{*}{2} & \mco{One girl}             &    18.5       &    51.1       &    19.7       &    51.8        \\
+                      &                            &    (0.2)      &    (0.6)      &    (0.2)      &    (0.6)       \\
+                      & \mco{One boy}              &    19.6^{***} &    52.7^{**}  &    20.1^{*}   &    52.2^{*}    \\
+                      &                            &    (0.1)      &    (0.7)      &    (0.2)      &    (0.5)       \\
+\addlinespace 
+\multirow[c]{5}{*}{3} & \mco{Two girls}            &    17.9       &    49.4^{*}   &    20.3       &    52.9^{**}   \\
+                      &                            &    (0.3)      &    (1.0)      &    (0.2)      &    (0.7)       \\
+                      & \mco{One boy / one girl}   &    19.1^{***} &    53.0^{**}  &    21.1^{***} &    51.8        \\
+                      &                            &    (0.2)      &    (0.7)      &    (0.2)      &    (0.6)       \\
+                      & \mco{Two boys}             &    19.1^{***} &    51.4       &    22.0^{***} &    50.9        \\
+                      &                            &    (0.2)      &    (0.9)      &    (0.3)      &    (0.8)       \\
+\addlinespace 
+\bottomrule
+\end{tabular}
+\begin{tablenotes} 
+\tiny
+\item \hspace*{-0.5em} \textbf{Note.}
+Bootstrapped standard errors shown in parentheses.
+\item[a] For spells two and higher duration sex compositions other than all girls are 
+tested against the duration for all girls, with *** indicating significantly different 
+at the 1\% level, ** at the 5\% level, and * at the 10\% level, based on bootstrapped
+differences.
+\item[b] The predicted percent boys is tested against the natural percentage boys, 105 boys per 100 girls,
+with *** indicating significantly different at the 1\% level, ** at the 5\% level, 
+and * at 10\% level.
+\end{tablenotes}
+\end{threeparttable}
+\end{scriptsize}
+\end{center}
+\end{table}
+
     \end{block}
@@
 \begin{enumerate}
-\item there has been a general increase in the length of spacing between births
+\item There has been a general increase in the length of spacing between births
 over the four decades covered by the data.
@@
 
-\item the most substantial increase in spacing is for the women who
+\item The most substantial increase in spacing is for the women who
 are most likely to use sex selection.
@@
 
-\item women with no education still follow the standard pattern of
+\item Women with no education still follow the standard pattern of
 short spacing when they have girls and little evidence of the use of sex
@@
 
-\item sex ratios are the most likely to decline within spells at
+\item Sex ratios are the most likely to decline within spells at
 lower-order spells, where the pressure to provide a son is smaller, and

### 2018-04-20 presentations/2018-paa-poster.tex
Combine results into one table

--- 2018-04-19 presentations/2018-paa-poster.tex
@@
 % \setmathfont{TeX Gyre Pagella Math}
+\usepackage{dcolumn}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage[flushleft]{threeparttable}
+\usepackage{caption}
+
+\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
+\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
+\newcommand{\X}{$\times$ }
+\newcommand{\hs}{\hspace{15pt}}
+
+% Beamer thinks no table numbers and small text
+\setbeamertemplate{caption}[numbered]
+\captionsetup{font=large,labelfont=large}
 
@@
 
-\vskip3ex
-
-To complicate matters, shorter birth spacing after daughters may still 
-be a representation of son preference for 
-families who do not use prenatal sex selection.
+\vskip2ex
+% 
+% To complicate matters, shorter birth spacing after daughters may still 
+% be a representation of son preference for 
+% families who do not use prenatal sex selection.
 
@@
 
+% \end{block}
+% 
+% \begin{block}{Spell Definition}
+
+\vskip3ex
+
+The first spell begins at the month of marriage, whereas the second and 
+subsequent spells begin nine months after the previous birth.
+All spells continue until either a child is born or censoring occurs.
+I group spells into four periods based on the year of marriage
+or year of the previous birth:
+1972--1984, 1985--1994, 1995--2004, and 2005--2016.
+
 \end{block}
@@
 \begin{column}{\twocolwid}
-
-\begin{block}{Spell Definition}
-
-The first spell begins at the month of marriage, whereas the second and 
-subsequent spells begin nine months after the previous birth.
-All spells continue until either a child is born or censoring occurs.
-
-\vskip3ex
-
-I group spells into four periods based on the year of marriage
-or year of the previous birth:
-1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-
-\end{block}
 
@@
 
+\begin{table}[hp!]
+\centering
+\begin{threeparttable}
+\caption{Estimated Median Duration and Sex Ratio}
+\label{tab:median_sex_ratio_low}
+\begin{tabular}{@{} c l D{.}{.}{2.3} D{.}{.}{2.3}  D{.}{.}{2.3} D{.}{.}{2.3} p{2ex} D{.}{.}{2.3} D{.}{.}{2.3}  D{.}{.}{2.3} D{.}{.}{2.3} @{}}
+\toprule
+                   &                            & \multicolumn{4}{c}{Rural Women -- No Education}                                                            & & \multicolumn{4}{c}{Urban Women -- 8+ Years of Education} \\  \cmidrule(lr){3-6} \cmidrule(lr){8-11}
+                   &                            & \mct{1972--1984}                                    & \mct{2005--2016}                                     & & \mct{1972--1984}                                    & \mct{2005--2016}                                      \\ \cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
+                   & \mco{Composition of}       & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}   & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}    & & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}   & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}     \\
+ \mco{Spell}       & \mco{Prior Children}       & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                         & & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                          \\ \midrule
+\multirow[c]{2}{*}{1} &                            &    26.2       &    52.1^{**}  &    24.4       &    51.5        &&    19.4       &    51.2       &    18.3       &    52.6^{***}  \\
+                      &                            &    (0.2)      &    (0.3)      &    (0.1)      &    (0.4)       &&    (0.2)      &    (0.7)      &    (0.1)      &    (0.2)       \\
+\addlinespace 
+\multirow[c]{3}{*}{2} & \mco{One girl}             &    18.5       &    51.1       &    19.7       &    51.8        &&    19.2       &    52.1       &    27.1       &    56.1^{***}  \\
+                      &                            &    (0.2)      &    (0.6)      &    (0.2)      &    (0.6)       &&    (0.2)      &    (1.4)      &    (0.3)      &    (0.9)       \\
+                      & \mco{One boy}              &    19.6^{***} &    52.7^{**}  &    20.1^{*}   &    52.2^{*}    &&    20.1^{**}  &    52.0       &    26.6^{*}   &    49.9^{**}   \\
+                      &                            &    (0.1)      &    (0.7)      &    (0.2)      &    (0.5)       &&    (0.5)      &    (1.0)      &    (0.3)      &    (0.6)       \\
+\addlinespace 
+\multirow[c]{5}{*}{3} & \mco{Two girls}            &    17.9       &    49.4^{*}   &    20.3       &    52.9^{**}   &&    20.7       &    54.5       &    29.1       &    65.6^{***}  \\
+                      &                            &    (0.3)      &    (1.0)      &    (0.2)      &    (0.7)       &&    (0.7)      &    (4.2)      &    (0.7)      &    (1.3)       \\
+                      & \mco{One boy / one girl}   &    19.1^{***} &    53.0^{**}  &    21.1^{***} &    51.8        &&    19.7       &    55.5^{**}  &    24.6^{***} &    55.8^{***}  \\
+                      &                            &    (0.2)      &    (0.7)      &    (0.2)      &    (0.6)       &&    (0.4)      &    (1.7)      &    (0.9)      &    (0.6)       \\
+                      & \mco{Two boys}             &    19.1^{***} &    51.4       &    22.0^{***} &    50.9        &&    20.3       &    49.3^{**}  &    25.5^{***} &    48.5        \\
+                      &                            &    (0.2)      &    (0.9)      &    (0.3)      &    (0.8)       &&    (1.2)      &    (0.8)      &    (1.0)      &    (2.7)       \\
+\addlinespace 
+\bottomrule
+\end{tabular}
+\begin{tablenotes} 
+\tiny
+\item \hspace*{-0.5em} \textbf{Note.}
+Bootstrapped standard errors shown in parentheses.
+\item[a] For spells two and higher duration sex compositions other than all girls are 
+tested against the duration for all girls, with *** indicating significantly different 
+at the 1\% level, ** at the 5\% level, and * at the 10\% level, based on bootstrapped
+differences.
+\item[b] The predicted percent boys is tested against the natural percentage boys, 105 boys per 100 girls,
+with *** indicating significantly different at the 1\% level, ** at the 5\% level, 
+and * at 10\% level.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
     \end{block}

### 2018-04-20 presentations/2018-paa-poster.tex
Minor edits for final run

@@
 \usepackage{caption}
+\usepackage[font=scriptsize,labelfont=scriptsize]{subfig}
 
@@
 
-\title{Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades}
+\title{Birth Spacing in the Presence of Son Preference and Sex-Selective Abortions:\\ India's Experience over Four Decades}
 \author{Claus P\"ortner}
@@
 
+\graphicspath{{../figures/}}
+\DeclareGraphicsExtensions{.eps,.jpg,.pdf,.mps,.png}
+
 \begin{frame}{}
@@
 
+\hspace{1cm}%
 \begin{column}{\onecolwid}
@@
 
-\vskip3ex
+\vskip1ex
 
@@
 
-\vskip2ex
+\vskip1ex
 % 
@@
 \begin{alertblock}{Contributions}
-
+\vskip1ex
 \begin{description}
-
+\setlength{\itemsep}{2ex}
 \item[Main idea:]  in the absence of sex selection son preference leads to shorter 
@@
 
-\item[Central question:] how did spacing patterns changed with access
-to prenatal sex determination became available?
+\item[Central questions:] how did spacing patterns change with access
+to prenatal sex determination?
 Specifically, did the spacing after girls increase relative to the spacing
@@
 \end{description}
-
+\vskip1ex
 \end{alertblock}
 
+\vskip1ex
 \begin{block}{Methods}
@@
 hazard model with two  exit states: either a boy or a girl is born.
+\vskip1ex
 \begin{description}
@@
 \end{block}
-
+\vskip1ex
 \begin{block}{Data}
 
-The data come from the four rounds of the National Family Health Survey.
+The data come from the four rounds of the National Family Health Survey (NFHS).
 Sample is restricted to Hindu women who are married and regular residents of
@@
 
-\vskip3ex
+\vskip2ex
 
@@
 All spells continue until either a child is born or censoring occurs.
-I group spells into four periods based on the year of marriage
-or year of the previous birth:
+Spells are grouped into four periods based on start of spell:
 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
@@
 
-The probability of ever having a next birth varies across groups.
-Direct comparison of standard survival curves, therefore, tells us little 
-about how the spread of sex selection affects birth spacing across groups.
-I therefore condition on the predicted likelihood of parity 
-progression when examining birth spacing measures.
-
-In addition to calculating conditional birth spacing measures for different 
-percentages, I also present graphs of both standard survival curves and
-survival curves conditional on parity progression (which therefore
-begin at 100\% and end at 0\%).
-
-Finally, I calculate the predicted percent boys born over the entire spell.
-
 \begin{table}[hp!]
@@
  \mco{Spell}       & \mco{Prior Children}       & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                         & & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                          \\ \midrule
-\multirow[c]{2}{*}{1} &                            &    26.2       &    52.1^{**}  &    24.4       &    51.5        &&    19.4       &    51.2       &    18.3       &    52.6^{***}  \\
-                      &                            &    (0.2)      &    (0.3)      &    (0.1)      &    (0.4)       &&    (0.2)      &    (0.7)      &    (0.1)      &    (0.2)       \\
+\multirow[c]{2}{*}{1} &                            &    26.2       &    52.1^{**}  &    24.4       &    51.5        &&    19.1       &    52.8^{***} &    18.8       &    52.7^{***}  \\
+                      &                            &    (0.2)      &    (0.3)      &    (0.1)      &    (0.4)       &&    (0.1)      &    (0.3)      &    (0.1)      &    (0.3)       \\
 \addlinespace 
-\multirow[c]{3}{*}{2} & \mco{One girl}             &    18.5       &    51.1       &    19.7       &    51.8        &&    19.2       &    52.1       &    27.1       &    56.1^{***}  \\
-                      &                            &    (0.2)      &    (0.6)      &    (0.2)      &    (0.6)       &&    (0.2)      &    (1.4)      &    (0.3)      &    (0.9)       \\
-                      & \mco{One boy}              &    19.6^{***} &    52.7^{**}  &    20.1^{*}   &    52.2^{*}    &&    20.1^{**}  &    52.0       &    26.6^{*}   &    49.9^{**}   \\
-                      &                            &    (0.1)      &    (0.7)      &    (0.2)      &    (0.5)       &&    (0.5)      &    (1.0)      &    (0.3)      &    (0.6)       \\
+\multirow[c]{3}{*}{2} & \mco{One girl}             &    18.5       &    51.1       &    19.7       &    51.8        &&    25.9       &    58.1^{***} &    29.0       &    56.1^{***}  \\
+                      &                            &    (0.2)      &    (0.6)      &    (0.2)      &    (0.6)       &&    (0.2)      &    (0.5)      &    (0.4)      &    (0.7)       \\
+                      & \mco{One boy}              &    19.6^{***} &    52.7^{**}  &    20.1^{*}   &    52.2^{*}    &&    25.6       &    50.1^{**}  &    29.0       &    49.6^{***}  \\
+                      &                            &    (0.1)      &    (0.7)      &    (0.2)      &    (0.5)       &&    (0.2)      &    (0.6)      &    (0.4)      &    (0.6)       \\
 \addlinespace 
-\multirow[c]{5}{*}{3} & \mco{Two girls}            &    17.9       &    49.4^{*}   &    20.3       &    52.9^{**}   &&    20.7       &    54.5       &    29.1       &    65.6^{***}  \\
-                      &                            &    (0.3)      &    (1.0)      &    (0.2)      &    (0.7)       &&    (0.7)      &    (4.2)      &    (0.7)      &    (1.3)       \\
-                      & \mco{One boy / one girl}   &    19.1^{***} &    53.0^{**}  &    21.1^{***} &    51.8        &&    19.7       &    55.5^{**}  &    24.6^{***} &    55.8^{***}  \\
-                      &                            &    (0.2)      &    (0.7)      &    (0.2)      &    (0.6)       &&    (0.4)      &    (1.7)      &    (0.9)      &    (0.6)       \\
-                      & \mco{Two boys}             &    19.1^{***} &    51.4       &    22.0^{***} &    50.9        &&    20.3       &    49.3^{**}  &    25.5^{***} &    48.5        \\
-                      &                            &    (0.2)      &    (0.9)      &    (0.3)      &    (0.8)       &&    (1.2)      &    (0.8)      &    (1.0)      &    (2.7)       \\
+\multirow[c]{5}{*}{3} & \mco{Two girls}            &    17.9       &    49.4^{*}   &    20.3       &    52.9^{**}   &&    28.6       &    65.8^{***} &    33.2       &    66.3^{***}  \\
+                      &                            &    (0.3)      &    (1.0)      &    (0.2)      &    (0.7)       &&    (0.7)      &    (1.1)      &    (0.9)      &    (1.5)       \\
+                      & \mco{One boy / one girl}   &    19.1^{***} &    53.0^{**}  &    21.1^{***} &    51.8        &&    24.0^{***} &    53.5^{**}  &    26.7^{***} &    55.6^{***}  \\
+                      &                            &    (0.2)      &    (0.7)      &    (0.2)      &    (0.6)       &&    (0.5)      &    (1.0)      &    (0.9)      &    (1.4)       \\
+                      & \mco{Two boys}             &    19.1^{***} &    51.4       &    22.0^{***} &    50.9        &&    24.2^{***} &    46.6^{***} &    28.2^{***} &    48.8        \\
+                      &                            &    (0.2)      &    (0.9)      &    (0.3)      &    (0.8)       &&    (0.8)      &    (1.4)      &    (1.3)      &    (2.3)       \\
 \addlinespace 
@@
 \begin{tablenotes} 
-\tiny
+\footnotesize
 \item \hspace*{-0.5em} \textbf{Note.}
 Bootstrapped standard errors shown in parentheses.
-\item[a] For spells two and higher duration sex compositions other than all girls are 
+\item[a] For spells two and higher duration for sex compositions other than all girls are 
 tested against the duration for all girls, with *** indicating significantly different 
@@
 
+\begin{columns}[t,totalwidth=\twocolwid]
+
+\begin{column}{\threecolwid}
+
+\begin{block}{Rural -- No Education}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption{
+Survival curves conditional on predicted progression to next birth
+}
+\label{fig:pps_low}
+\end{figure}
+
+\end{block}
+
+\end{column}
+
+\begin{column}{\threecolwid}
+
+\begin{block}{Urban -- 8+ Years of Education}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{0}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
+\setcounter{subfigure}{1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.45\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\caption{
+Survival curves conditional on predicted progression to next birth
+}
+\label{fig:pps_high}
+\end{figure}
+
+\end{block}
+
+\end{column}
+
+\end{columns}
+
 \end{column}
@@
 
-\begin{alertblock}{Conclusion}
-
+\begin{alertblock}{Conclusions}
+\vskip1ex
 \begin{enumerate}
+\setlength{\itemsep}{2ex}
 \item There has been a general increase in the length of spacing between births
-over the four decades covered by the data.
+over the four decades.
 The exception is for first births, where the median duration has either
-remained the same or slightly declined, although this hides a
+remained the same or declined slightly, although this hides a
 significant compression of the variation in spell length.
@@
 selection.
-In other words, these women adhere to a strategy where they achieve a
+In other words, they adhere to a strategy where they achieve a
 son through higher fertility rather than the use of sex selection.
@@
 \end{enumerate}
+\vskip1ex
+\end{alertblock}
 
-\end{alertblock}
+\vskip1ex
 
@@
 \end{itemize}
-
+\vskip1ex
 \end{block}
@@
 
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
+Support from the University of Washington Royalty Research Fund and the 
+Development Research Group of the World Bank
+for development of the method is gratefully acknowledged.
 The views and findings expressed here are those of the author and
 should not be attributed to the World Bank or any of its member countries.
+
+\vskip1ex
+
 Partial support for this research came from a Eunice Kennedy Shriver National

### 2018-11-21 response/response-demography-1.tex
Initial commit of directory with referee reports, editor comments, and response

\documentclass[letterpaper,12pt]{article}

% Xetex preamble
\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}

\usepackage[longnamesfirst]{natbib}
%\usepackage[tabhead,nolists,tablesfirst]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{rotating}  
\usepackage{dcolumn} 
\usepackage{setspace}
%\usepackage{flafter} 
%\usepackage{longtable}
%\usepackage[pdftex]{graphicx}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black]{
hyperref} 
\usepackage[margin=1.0in]{geometry} 
\usepackage{multirow}

%opening
\title{} \author{}

\doublespacing

\begin{document}

\begin{center} \textbf{\large Birth Spacing in the Presence of Son
Preference and 
Sex-Selective Abortions: India's Experience over Four Decades}
\end{center}

\begin{center} Response to Editor and Referee Comments \end{center}

\noindent Please find attached the revised version of my paper,
``Birth Spacing in the Presence of Son Preference and Sex-Selective
Abortions:
India's Experience over Four Decades.''
I would like to thank the two referees and the editor for the very
useful comments and
suggestions, which I believe have substantially improved the paper.

[Comments from editor]

First, the description of the problem and literature review are sparse.
The front end of the paper should be revised to situate the study in the
wider literature on son preference and sex selection in the region. The
contributions of the current study should be highlighted. R1 offered
particularly useful ideas in this regard. These changes would make the
paper appeal to the broad readership of Demography.

Second, a conceptual framework or theoretical argument is needed to
motivate the decision to examine birth intervals and sex composition by
maternal education. Does maternal education proxy for access to sex
selective technology, preferences for sons, etc.? In addition, how does
selection into the highest/lowest educated categories change over the 45
years of the study? How could this impact the interpretation of results?

Third, the paper is heavy on the description of methods and results.
These sections could be shortened and reorganized to focus on the most
important issues. R1 also offered suggestions regarding the presentation
of findings.

Fourth, discussion of the fertility transition is neglected and only
discussed in the conclusion. At a minimum, you should consider providing
details on fertility levels and distributions across parities over time.
Is there an easy way to show the sample sizes/proportion of births in
each category of sex composition across years in tables 1-3? More could
be said about the potential impact of the ongoing fertility decline.

\newpage

\section*{Reviewer 1}

1. The key contribution of the paper is the use of birth spacing and sex
ratios to examine changes and differentials in possible sex-selective
abortions. While there is large literature using differential stopping
behaviours (DSB) and sex ratios to examine sex selection, the use of
birth spacing is new and could potentially provide new insights. The
methodology used is rigorous and suited for the purposes of the paper.

2. The paper would need to articulate its contribution clearly. The
paper seems to be focussed too much on methodology and less on
contextual, theoretical and substantive matters. As there is already
well established literature on sex-selection and son preference, the
paper must articulate what is substantially different in the paper. As
one of the key features is the focus on spacing, expanded review of the
literature on spacing is required.

3. The literature review must be systematic. The paper seems to move too
quickly to estimation strategy. Before presenting this, the literature
on spacing, sex ratios, sexselection should be presented. This would
help the paper to make a stronger case of its place and contribution to
the demographic literature.

4. The demographic literature, for example, by works from Christophe Z
Guilmoto, doesn’t seem to be consulted. Guilmoto and colleagues many
papers including recent work in Population Studies and Lancet are
important to consult as they cover the same substantial issues of sex
ratios, sex selection and abortions as addressed in this paper. Though
these demographic papers do not necessarily use spacing, a similar
understanding of sex-selection could be obtained using examining parity
progression. Therefore, the added insights from using spacing need to
articulated much more forcefully.

5. The use of competing hazard models is not new in demographic research
and doesn’t require long exposition. This section can be cut
sustainably. I don’t think the methodological innovation is a key
contribution of the paper as the methods are established even if they
have not been used to examine spacing.

6. The use of NFHS data including the most recent data are welcome. An
additional limitation to those addressed in the paper is the issue of
date imputation in DHS/NFHS. NFHS as with other DHS data routinely use
imputations for year and month of birth. I don’t have the reference for
India (please check data quality reports on DHS website), but the
imputation of month of birth was done for large number of cases in
earlier rounds of DHS. This could be a possible reason for seeming large
number of pre-marital conceptions which do not make sense in the context
of India.

7. It is not clear why exactly 22, 23, 25 years are used a cut-off
points.

8. I understand the empirical reason for not increasing the number of
variables. However, a key variable that is essential to consider is
region. This is important because regional influences on birth spacing
and sex selection are very strong as established in the literature. Sex
selection and abortion is especially strong in certain regions but not
in others. The regional differentials in fertility transition,
contraceptive use, spacing, sex ratios, abortions are clearly documented
in the literature. So it is vital to include this.

9. The three tables are logically organized and contain a wealth of
information. But there are too many comparisons to make in each of the
tables and I wonder if it would make sense to split the tables or
present some of the information in a much more reader friendly way (for
instance by using charts for some of the information).

10. As sex composition and sex ratios has been examined in the literature, I think
it would make sense to not present findings on that in great detail. As
the paper states, the central question addressed is spacing, and so all
other questions should not be dealt in detail

11. The results talk about compression of spacing. This is important and
literature on it should be presented in the intro or lit review section.
There is evidence of compression of the reproductive span at least in
some regions (see Padmadas, et. Al 2004). It would be important to
consider how this fits in with the results presented.

12. As there are many results presented, it would make sense to have a
paragraph at the beginning of the conclusion highlighting the key
findings.

13. Overall, the paper is empirically strong but needs to build on the
contextual, theoretical, and prior demographic literature. As the
readers of Demography are diverse, it would be good to have a balanced
presentation of all the sections. Currently it seems the paper is too
concerned with the methodology and empirical work at the expense of
other areas.

\newpage

\section*{Reviewer 7}

The article was a careful, innovative, and thorough piece of research
picking up on a conundrum concerning how son preference and sex
selection affect birth intervals. I very much enjoyed reading this piece
and think it has useful applications outside of India.  My review is
short as I do not see much to be improved upon.  My only (minor)
suggestion concerns the use of the word "spell".  It is very clear what
you mean by a spell when the paper explains this, but I think that it is
somewhat confusing to put this in the abstract without an explanation. 
It was not until I got to the explanation in the methods that I
understood the abstract fully.  I suggest rewording this section of the
abstract so it is clear what is meant by spell.

\newpage
\bibliographystyle{econometrica}
\bibliography{../paper/sex_selection_spacing.bib}
\addcontentsline{toc}{section}{References}

\end{document}

### 2018-11-23 response/response-demography-1.tex
Notes for responding to editor/referee comments
- Add "[Response:]" to all questions
- Write first impression notes for questions

@@
 India's Experience over Four Decades.''
-I would like to thank the two referees and the editor for the very
-useful comments and
-suggestions, which I believe have substantially improved the paper.
+I would like to thank the two referees and the editor for the very useful comments and 
+suggestions, which I believe substantially improved the paper.
 
-[Comments from editor]
+\section*{Editor}
 
@@
 
+[Response:]
+
+- Spacing as an indicator for son preference
+- The relationship between spacing and child health
+- The relationship between spacing and women's health
+- Important for understanding how spacing in general behaves. See last point from
+editor: if lower fertility, better health, and increased female labor market participation 
+are all is associated with a compression of spacing, the use of sex selection would
+work against this trend and make it look like India is not behaving like other countries.
+- Women's role in general
+
 Second, a conceptual framework or theoretical argument is needed to
@@
 
+[Response:]
+
 Third, the paper is heavy on the description of methods and results.
@@
 of findings.
+
+[Response:]
 
@@
 be said about the potential impact of the ongoing fertility decline.
+
+[Response:]
+
+[Generically, spacing tend to decline with lower fertility (check this). 
+Presumably the decline in spacing is because part of the cause is higher female labor 
+market participation, which makes it more attractive to space children closer together.
+Not clear whether this is the case for India - The R1 suggested paper might be a good
+starting point with a tie-in to compression.
+Compression can also come from improved health and/or less migration.
+
+On the flip side, lower fertility place additional pressure on women to use
+sex selection, which lead to *less* compression.
+]
 
@@
 
+[Response:]
+
 3. The literature review must be systematic. The paper seems to move too
@@
 the demographic literature.
+
+[Response:]
+
+[See response to Editor]
 
@@
 
+[Response:]
+
+[I should have those somewhere already. I think they were in the original version.]
+
 5. The use of competing hazard models is not new in demographic research
@@
 have not been used to examine spacing.
+
+[Response:]
+
+[Still need to include the sex ratio calculations it would seem.
+Prior readers have asked for those.]
 
@@
 
+[Response:]
+
+[Maybe run regression only on those birth intervals that does not
+involve imputations on either end of the spacing.
+This could be presented in the Appendix, unless very different from
+results.]
+
 7. It is not clear why exactly 22, 23, 25 years are used a cut-off
 points.
+
+[Response:]
+
+[Add this discussion back into Appendix]
 
@@
 
+[Response:]
+
+[Check for broad regions to incorporate. Check how to do this for the non-proportional
+hazard specification.]
+
 9. The three tables are logically organized and contain a wealth of
@@
 
+[Response:]
+
 10. As sex composition and sex ratios has been examined in the literature, I think
@@
 other questions should not be dealt in detail
+
+[Response:]
 
@@
 
+[Response:]
+
+[Compression is only for first birth as far as I remember. Need to check that.
+Check on paper for their analysis.]
+
 12. As there are many results presented, it would make sense to have a
@@
 findings.
+
+[Response:]
+
+[Add discussion when other parts are done]
 
@@
 
+[Response:]
+
 \newpage

### 2018-11-28 paper/sex_selection_spacing-ver2.tex
Copy of original submission for editing
Update month
First go at reducing length of Estimation Strategy section
Based on Editor's and R1's comments, trying to make the discussion
of the estimation strategy shorter. Still need to highlight how
the approach is different.

--- 2018-04-02 paper/sexSelectionSpacing-ver1.tex
@@
 
-\date{March 2018\\
-\bigskip
-Preliminary}
+\date{November 2018}
 
@@
 
-The unit of analysis is a spell, the period from one birth, or marriage for
-the first spell, to the next.
-For some spells, the duration is censored, for example, because the survey
-took place before the birth that would end the spell or because the couple
-has finished childbearing.
-The standard approach to address the censoring of spells, which I follow here, is 
-to use a hazard model.
-To capture the effects of sex selection, I extend the standard hazard model 
-to allow for multiple exit states and a non-proportional hazard specification.
-
-First, I use a competing risk framework with two possible exit states, either a boy
-or a girl is born, because access to prenatal sex determination means that
-parents can choose the sex of children born.
-Prior research on birth spacing, in contrast, relied on single
-exit state hazard models.%
+The unit of analysis is a spell, the period from one birth---or for the first spell from 
+marriage---to the next birth.
+The model is a discrete time, non-proportional, competing risk hazard model with two exit 
+states: either a boy or a girl is born.
+The standard approach in the spacing literature is to use a single-exit model, but
+access to sex selection means that the sex of the next child born is not random 
+and that the spacing to girls and boys depends on parents' choices.
+Both the non-randomness and differential spacing can be captured with a competing risk set 
+up.%
 \footnote{
@@
 }
-Having only one exit state works when there is no sex selection---making the 
-sex of the child a random event---but not here since at least some couples use 
-sex selection.
-
-Second, I use a non-proportional hazard specification because
-sex composition and the use of sex selection are likely to affect 
-the shape of the hazard functions across groups.
-The use of a non-proportional specification also mitigates any potential 
-effects of unobserved heterogeneity when used in conjunction with a 
-flexible baseline hazard \citep{Dolton1995}.
-Proportional hazard models, where covariates have a multiplicative 
-effect on the hazard rate, are more efficient than non-proportional 
-models, but only provided that the proportionality assumption hold.
-If the proportionality assumption does not hold, the estimates
-are biased.
-
-It is unlikely---even in the absence of prenatal sex determination---that 
-the effect of, for example, the sex composition of previous births have 
-the same effect throughout the entire spell.
-Assuming that the effect of sex composition is the same throughout a spell
-is especially problematic for higher-order spells where different
-sex composition of previous births can lead to substantial differences 
-both in the likelihood of progressing to the next birth and
+
+I use a non-proportional hazard specification, which allows the shape of the hazard 
+functions to vary across groups, rather than the standard proportional hazard function 
+for three reasons.
+First, it is unlikely---even in the absence of prenatal sex determination---that the 
+effect of household characteristics such as the sex composition of previous births have 
+the same effect throughout the entire spell.%
+\footnote{
+Assuming that the effect of sex composition is the same throughout a spell is especially 
+problematic for higher-order spells where different sex composition of previous births can 
+lead to substantial differences both in the likelihood of progressing to the next birth and
 how soon couples want their next child if they are going to have one.
-
-The introduction of prenatal sex determination is likely to exacerbate 
-any bias from the proportionality assumption.
-First, sex-selective abortions affect birth spacing, and use
-varies across groups.
-Second, the use of sex selection may vary within a spell, which means 
-that the effects of covariates vary within the spell as well.
-
-In summary, my proposed model is a discrete time, non-proportional, competing risk 
-hazard model with two exit states: either a boy or a girl is born.
+}
+Second, the introduction of prenatal sex determination likely exacerbates any bias 
+from the proportionality assumption since sex-selective abortion use varies across groups
+and affects birth spacing, and because a household's use of sex selection may vary 
+within a spell, which means that the effects of covariates vary within the spell as well.
+Finally, the use of a non-proportional specification also mitigates any potential effects 
+of unobserved heterogeneity when used in conjunction with a flexible baseline hazard 
+\citep{Dolton1995}.
+
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
@@
 $J_i$ is a random variable indicating which event took place.
-The discrete time hazard rate $h_{ijt}$ is
-\begin{equation}
- h_{ijt} = \Pr (T_i=t, J_i=j \mid T_i \geq t; \mathbf{Z}_{it},\mathbf{X}_{i} ),
-\end{equation}
-where $T_i$ is a discrete random variable that captures when woman $i$'s birth occurs.
-To ease presentation the indicator for spell number is suppressed.
-The explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, include 
-individual, household, and community characteristics discussed below.
-
-The hazard rate is specified as
+The discrete time hazard rate $h_{ijt}$ is specified as
 \begin{equation}
@@
 \end{equation}
-where $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
+where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, include 
+individual, household, and community characteristics discussed below,
+and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
 by dummies and the associated coefficients,
@@
 \end{equation}
-where $D_m = 1$ if $t=m$ and zero otherwise.
+with $D_m = 1$ if $t=m$ and zero otherwise.
 This approach to modeling the baseline hazard is flexible and does not place 
@@
 composition of previous children, if any, and $Z_2$ captures area of residence.
-The non-proportionality allows the effects of the main explanatory variables on the probabilities 
-of having a boy, a girl, or no birth to vary over time within a spell.
 The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
@@
 time periods.
-% The exact specifications and the individual variables are described below.
 
@@
 \footnote{
-A potential issue is that the multinomial model assumes that alternative 
-exit states are stochastically independent,
-also known as the Independence of Irrelevant Alternatives (IIA) assumption.
-This assumption rules out any individual-specific unmeasured or 
-unobservable factors that affect both the hazard of having a girl and the 
+The multinomial model assumes that alternative exit states are stochastically independent
+(Independence of Irrelevant Alternatives or IIA), which rules out any individual-specific 
+unmeasured or unobservable factors that affect both the hazard of having a girl and the 
 hazard of having a boy.
 I, therefore, include a proxy for fecundity discussed in Section \ref{sec:data}.
-Also, the multivariate probit model can be used as an alternative
-to the multinomial logit because the IIA is not imposed \citep{han90}.
+Also, the multivariate probit model can be used as an alternative because the IIA is not 
+imposed \citep{han90}.
 The results are substantially identical between these two models and
@@
 }
-In the reorganized data the outcome variable is 0 if the
-woman does not have a child in a given interval (the base outcome), 1 if 
-she gives birth to a son in that interval, and 2 if she gives birth to 
-a daughter in that interval.
-
-The main downside of this set-up is that interpretation of the estimated 
-coefficients is challenging;
-the coefficients show the change in hazards relative to the base outcome, 
-here no birth, rather than the hazard of an event.
-Hence, a positive coefficient does not necessarily imply that the associated 
-exit state becomes more likely as the explanatory variable increases because the 
-probability of the other exit state may increase even more \citep{thomas96}.
-
-It is, however, straightforward to calculate the predicted probabilities of 
+In the reorganized data the outcome variable is 0 if the woman does not have a child in a 
+given interval (the base outcome), 1 if she gives birth to a son in that interval, and 2 
+if she gives birth to a daughter in that interval.
+
+The distribution of spacing is captured by the survival curve, which shows the probability 
+of not having had a birth yet by spell duration, for a given set of explanatory variables.
+The survival curve at time $t$ is 
+\begin{equation}
+\label{eq:survival}
+S_{t} 
+= 
+\prod_{d=1}^t
+\left(
+\frac{ 1 }
+{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
+\right).
+\end{equation}
+
+Because the probability of ever having a next birth likely varies across groups, a direct 
+comparison of standard survival curves tells us little about how the spread of sex selection 
+affects birth spacing across groups.
+I, therefore, condition on the predicted likelihood of parity progression when examining 
+birth spacing measures, such as the median duration to a birth.
+The reliability of this approach depends on whether the spell length covered is 
+sufficiently long that few women are likely to give birth after the spell cut-off.
+I discuss the choice of spell length below.%
+\footnote{
+It is important to note that the approach is not the same as merely calculating 
+the birth spacing measures for women who already have a given 
+parity child in the survey because that number does not take into account
+the censoring of spells that will eventually lead to a birth.
+}
+In addition to calculating conditional birth spacing measures for different 
+percentages, I also present graphs of both standard survival curves and
+survival curves conditional on parity progression (which therefore
+begin at 100\% and end at 0\%).
+
+Interpretation of the model coefficients is challenging \citep{thomas96}.
+It is, however, possible to calculate the predicted probabilities of 
 having a boy and of having a girl for each $t$ within a spell, conditional on 
@@
 
-The distribution of spacing is captured by the survival curve, which shows 
-the probability of not having had a birth yet by spell duration, for
-a given set of explanatory variables.
-The survival curve at time $t$ is 
-\begin{equation}
-S_{t} 
-= 
-\prod_{d=1}^t 
-\left( 
-	1- \left(P(b_{d} | \mathbf{X}_{k}, \mathbf{Z}_{kd}, d) 
-	+ P(g_{d} | \mathbf{X}_{k}, \mathbf{Z}_{kd}, d) \right) 
-\right),
- \label{eq:survival}
-\end{equation}
-or equivalently
-\begin{equation}
-S_{t} 
-= 
-\prod_{d=1}^t
-\left(
-\frac{ 1 }
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
-\right).
-\end{equation}
-
-An important issue is that the probability of ever having a next birth varies 
-across groups.
-For example, as the parity progression literature shows, couples with stronger 
-son preference are less likely, for a given number of prior births, to ever have 
-a next birth if they already have one or more sons.
-Direct comparison of standard survival curves, therefore, tells us little 
-about how the spread of sex selection affects birth spacing across groups.
-
-To overcome this problem, I condition on the predicted likelihood of parity 
-progression when examining birth spacing measures, such as the median duration 
-to a birth.
-How well this approach works depends on whether the spell length covered is 
-sufficiently long that few women are likely to give birth after the spell cut-off.
-I discuss the choice of spell length below.
-It is important to note that the approach is not the same as merely calculating 
-the birth spacing measures for women who already have a given 
-parity child in the survey because that number does not take into account
-the censoring of spells that will eventually lead to a birth.
-In addition to calculating conditional birth spacing measures for different 
-percentages, I also present graphs of both standard survival curves and
-survival curves conditional on parity progression (which therefore
-begin at 100\% and end at 0\%).
-
-Finally, given the predicted probabilities of having a boy and of having 
-a girl for each $t$ within a spell, is it easy to calculate the estimated 
-percentage of children born that are boys, $\hat{Y}$, at each $t$  
+Given the predicted probabilities of having a boy and of having a girl for each 
+$t$ within a spell, is it easy to calculate the estimated percentage of children born that 
+are boys, $\hat{Y}$, at each $t$  
 \begin{equation}

### 2018-11-30 response/response-demography-1.tex
Minor edits
Explain changes in Estimation Strategy

@@
 
-[Still need to include the sex ratio calculations it would seem.
-Prior readers have asked for those.]
+I have reduced the length of the section by more than 1/4 (the original section was 5
+pages long, while the revised section is less than 3.5).
+There are three important differences between my approach and what is standard
+in the literature, and I believe further shortening would negatively impact readers'
+ability to understand the results.
+First, most research that use survival models employ proportional hazard models, so 
+motivating and providing more information on the non-proportional set-up is important.
+Second, the use of conditional survival curves is, to my knowledge, new, and, therefore,
+requires a detailed discussion.
+Third, the sex ratio calculations is a new way to use competing risk estimates and is 
+required to understand whether the use of sex selection vary within spells.
 

### 2018-11-30 paper/sex_selection_spacing-ver2.tex
Shorten Estimation Strategy section

@@
 \setmathfont{TeX Gyre Pagella Math}
+\usepackage{amsmath}
 \usepackage[title]{appendix}
@@
 states: either a boy or a girl is born.
-The standard approach in the spacing literature is to use a single-exit model, but
-access to sex selection means that the sex of the next child born is not random 
-and that the spacing to girls and boys depends on parents' choices.
-Both the non-randomness and differential spacing can be captured with a competing risk set 
-up.%
+The standard approach in the spacing literature is to use a single-exit model, but with
+access to sex selection the sex of the next child is not random and parents' choices 
+will impact the spacing to a girl or a boy differentially.%
 \footnote{
@@
 }
+Both the non-randomness and differential spacing can be captured with a competing risk set 
+up.
 
@@
 Second, the introduction of prenatal sex determination likely exacerbates any bias 
-from the proportionality assumption since sex-selective abortion use varies across groups
-and affects birth spacing, and because a household's use of sex selection may vary 
+from the proportionality assumption since sex-selective abortion use varies across groups,
+which affects birth spacing, and because a household's use of sex selection may vary 
 within a spell, which means that the effects of covariates vary within the spell as well.
-Finally, the use of a non-proportional specification also mitigates any potential effects 
+Finally, the use of a non-proportional specification mitigates any potential effects 
 of unobserved heterogeneity when used in conjunction with a flexible baseline hazard 
@@
 \end{equation}
-where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, include 
+where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
 individual, household, and community characteristics discussed below,
@@
 }
-In addition to calculating conditional birth spacing measures for different 
-percentages, I also present graphs of both standard survival curves and
+In addition, I also present graphs of both standard survival curves and
 survival curves conditional on parity progression (which therefore
@@
 It is, however, possible to calculate the predicted probabilities of 
-having a boy and of having a girl for each $t$ within a spell, conditional on 
-a set of explanatory variables and not having had a child before that period.
-The predicted probability of having a boy in period $t$ for a given set of 
-explanatory variable values, $\mathbf{Z}_k$ and $\mathbf{X}_k$, is
-\begin{equation}
+having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
+a set of explanatory variables and not having had a child before that period, as
+\begin{align}
 P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
-=  
+& =  
 \frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
-{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})},
-\label{eq:probability_boy}
-\end{equation}
-and the predicted probability of having a girl is
-\begin{equation}
+{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
+\label{eq:probability_boy} \\
 P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
-=  
+& =  
 \frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}.
+{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
 \label{eq:probability_girl}
-\end{equation}
-Within each period the probability of not having a birth in period $t$
-is $1-P(b_{t})-P(g_{t})$.
-
-Given the predicted probabilities of having a boy and of having a girl for each 
-$t$ within a spell, is it easy to calculate the estimated percentage of children born that 
-are boys, $\hat{Y}$, at each $t$  
+\end{align}
+It is then straightforward to calculate the estimated percentage of children born that 
+are boys, $\hat{Y}$, at each $t$:  
 \begin{equation}

### 2018-12-07 paper/sex_selection_spacing-ver2.tex
Add Appendix discussion of recall error

@@
 
+\section{Recall Error and the Sex Ratio}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+The reliability of the results depends on the correctness of the birth histories
+provided by the respondents.
+A significant concern here is underreporting of child mortality, especially a systematic
+recall error where respondents' likelihood of reporting a deceased child depends on the 
+sex of that child. 
+This section assesses the degree of recall error across the surveys and discusses methods
+to address it.
+
+NFHS enumerators probe for any missed births, although the method depends on the survey.
+NFHS-1 probe for each calendar birth interval that is 4 or more years.
+NFHS-2 asked for stillbirths, spontaneous and induced abortions and also probed 
+for each calendar birth interval 4 or more years.
+NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether were there any 
+other live births between (name of previous birth) and (name), including any children who 
+died after birth, and asked for births before the birth listed as first birth and
+after the last birth listed as the last birth.
+
+Probing catches many initially missed births, but systematic recall error based on son
+preference may still be a problem.
+First, son preference leads to significantly higher mortality for girls than boys.
+Secondly, son preference makes it more likely that parents will remember deceased boys 
+than deceased girls.
+Finally, in the absence of sex-selective abortions, parents with a preference for sons may
+have the next birth sooner if the last child was a girl than if it was a boy.
+If this girl subsequently dies, she is more likely to be missed if probing for missed 
+births is only done for long intervals as in NFHS-1 and NFHS-2.
+
+I use two approaches to examine the degree of recall error.
+The first approach is to test whether the observed sex ratio is significantly different
+from the natural sex ratio.
+Prenatal sex determination techniques did not become widely available until the mid-1980s, 
+so any significant deviation from the natural sex ratio before that time is likely the 
+result of recall error.
+The second approach is to compare births that took place during the same period but
+where captured in different surveys.
+Recall error is likely to increase with time, so births and deaths that took place earlier 
+are more likely to be subject to recall error than more recent events.
+
+Table \ref{tab:recallBirthBO1} shows the sex ratios of children recorded as first-born by 
+year of birth, together with tests for whether the observed sex ratio is significantly 
+higher than the natural sex ratio and whether more recent surveys have a higher sex ratio 
+for the cohort than earlier surveys for the same period births.
+Births are combined into five-year cohorts to achieve sufficient power.
+
+\input{../tables/recallBirthBO1.tex}
+
+% \input{../tables/recallBirthBO2.tex}
+
+The ``first-born'' sex ratios illustrate the systematic recall error problem well.
+In all four surveys around 55 percent of children reported as first-born are boys
+for the first cohort of births observed.
+Given that these cohorts cover from 1960-1964 to 1980-1984, which is before sex selection 
+techniques became available in India, the most likely explanation for the skewed sex ratio 
+is that some children listed as first-borns were not, in fact, the first children born in 
+their families.
+Instead, for a substantial proportion of families, their first-born was a girl who died 
+and went unreported when enumerators asked about birth history.
+
+As expected, the difference between the observed sex ratio and the natural sex ratio is 
+less pronounced the closer to the survey date the cohort is.
+The observed sex ratio for children born just before the NFHS-1 survey and listed as 
+first-born is 0.517, which is not statistically significantly different from the
+natural sex ratio.
+The same general pattern holds for the other three surveys, with cohorts further away
+from the survey date more likely to have a sex ratio skewed male.
+
+% Second births show a pattern very similar to that for first births.
+% An interesting difference is that there is evidence of a U-shaped relationship between
+% time and sex ratio for second births.
+% Cohorts furthest away from the survey year show the highest sex ratios, but declines to the
+% natural sex ratio in the mid-1980s, and the sex ratio is then significantly higher again 
+% for more recent births.
+% This is in line with the results in the main paper that show that sex selective abortions 
+% take place on lower parity births as desired fertility declined.
+
+Finally, across surveys, the same cohort tends to show a higher sex ratio the more recent 
+the survey (births in the cohort took place earlier relatively to the survey date).
+Despite this, few cohorts show significantly different sex ratios across surveys, most 
+likely because of a lack of power.
+The exception is that comparisons involving NFHS-4 are mostly statistically significant
+since the number of surveyed households in NFHS-4 were much larger than in prior surveys.
+
+The problem with the above approach is that the year of birth is affected by recall error; 
+for example, a second born child listed as first-born is born later than the real 
+first born child.
+Recorded year of marriage should, however, be affected neither by parental recall error 
+nor the use of sex-selective abortions.
+Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2}, therefore, shows sex 
+ratios of children recorded as first-born and second-born by year of parents' marriage, 
+together with tests for whether the observed sex ratio is significantly higher than the 
+natural sex ratio and whether more recent surveys show a higher sex ratio for the cohort 
+than earlier surveys.
+
+The basic recall error pattern remains with women married longer ago more
+likely to report that their first-born is a boy.
+If anything the pattern is more consistent when using year of marriage than 
+year of birth. 
+Before the introduction of sex selection there are only two instances  across the two 
+parities where the observed sex ratio is lower for women married longer ago than for women 
+married closer to the survey date.%
+\footnote{
+For first-borns it is between 1970--1974 and 1975-1979 for NFHS-3 and for second-borns
+it is between 1975--1979 and 1980--1984 for NFHS-1.
+}
+Similarly, comparing women married in the same five-year period across surveys shows
+that women married longer ago are more likely to report having a son.
+
+\input{../tables/recallMarriageBO1.tex}
+
+\input{../tables/recallMarriageBO2.tex}
+
+The relationship between length of marriage and recall error can also seen in 
+Figure \ref{fig:sexRatioMarriage}, which shows the observed sex ratio for children reported
+as first born as a function of duration of marriage at the time of the survey combining 
+all four surveys.
+The solid line is the sex ratio of children reported 
+as first born by the number of years between the survey and marriage, 
+the dashed lines indicate the 95 percent confidence interval 
+and the horizontal line the natural sex ratio (approximately 0.512).
+To ensure sufficient cell sizes the years are grouped in twos.
+In line with the results from Tables \ref{tab:recallMarriageBO1} and 
+\ref{tab:recallMarriageBO2}, the observed ratio of boys 
+is increasingly above the expected value the longer ago the parents were married.%
+\footnote{
+The graph for second births shows a similar pattern with the
+likelihood of the second child being a boy going up with increasing marriage duration.
+The graphs for the second births and the individual survey rounds are available upon request.
+}
+
+\begin{figure}[htp]%
+\centering
+\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
+\caption{Sex ratio of ``first'' births by duration of marriage}
+\label{fig:sexRatioMarriage}}
+\end{figure}
+
+The increasingly unequal sex ratio with increasing marriage duration suggests that
+a solution to the recall error problem is to drop observations for 
+women who were married ``too far'' from the survey year.
+The main problem is establishing what the best cut-off point should be.
+As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} shows there are 
+differences in recall error across the three surveys and between parities.
+One possibility is simply to drop all women married in cohorts where the observed
+sex ratio is substantially higher than the natural sex ratio, but even this is not
+straightforward.
+For ``first'' born this would imply dropping all women married before 1980, but
+for ``second'' born it would be imply dropping all married before 1970 for NFHS-1, before 1975 
+for NFHS-2, and before 1980 NFHS-3.
+Because of the differences between ``first'' and ``second'' born in the different surveys
+I vary the cut-off point by survey round.
+
+NFHS-3 is the most straightforward in that the implied cut-off point is the same for
+both first and second born.
+Based on Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2}, women in 
+NFHS-3 who were married 26 years or
+more before the survey date are dropped.
+For NFHS-1 and NFHS-2 the trade-off is between ensuring enough information and not bias 
+the results unduly.
+Given that sex selective abortions are more likely in higher parity birth I base the
+cut-off point on the second births instead of the first births.
+Hence, for NFHS-1 women who were married 22 years or more before the survey date 
+were dropped and for NFHS-2 women who were married 23 year or more before the survey date 
+were dropped.
+
+% \begin{figure}
+% \centering
+% \subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r1}}
+% \subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r2}} \\
+% \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r3}} 
+% \caption{Ratio of Boys for ``First'' Births by Survey Round}
+% \label{fig:sex_ratio_recall_rounds}
+% \end{figure}
+
+\clearpage
+\newpage
+
 \section{Descriptive Statistics}

### 2019-01-08 paper/sex_selection_spacing-ver2.tex
Reorder packages to run and minor edits in recall section

@@
 
+\usepackage{amsmath}
 \usepackage{fontspec}
@@
 \setmathfont{TeX Gyre Pagella Math}
-\usepackage{amsmath}
 \usepackage[title]{appendix}
@@
 \ref{tab:recallMarriageBO2}, the observed ratio of boys 
-is increasingly above the expected value the longer ago the parents were married.%
-\footnote{
-The graph for second births shows a similar pattern with the
-likelihood of the second child being a boy going up with increasing marriage duration.
-The graphs for the second births and the individual survey rounds are available upon request.
-}
+is increasingly above the expected value the longer ago the parents were married.
 
@@
 \caption{Sex ratio of ``first'' births by duration of marriage}
-\label{fig:sexRatioMarriage}}
+\label{fig:sexRatioMarriage}
 \end{figure}
@@
 
-% \begin{figure}
-% \centering
-% \subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r1}}
-% \subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r2}} \\
-% \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r3}} 
-% \caption{Ratio of Boys for ``First'' Births by Survey Round}
-% \label{fig:sex_ratio_recall_rounds}
-% \end{figure}
+\begin{figure}
+\centering
+\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1}}
+\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2}} \\
+\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
+\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
+\caption{Ratio of Boys for ``First'' Births by Survey Round}
+\label{fig:sex_ratio_recall_rounds}
+\end{figure}
 

### 2019-01-09 paper/sex_selection_spacing-ver2.tex
Add graphs for second births

@@
 \centering
-\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
+\includegraphics[width=0.9\textwidth]{recall_sex_ratio_marriage}
 \caption{Sex ratio of ``first'' births by duration of marriage}
@@
 \caption{Ratio of Boys for ``First'' Births by Survey Round}
-\label{fig:sex_ratio_recall_rounds}
+\label{fig:sex_ratio_recall_rounds_bo1}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1_bo2}}
+\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2_bo2}} \\
+\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3_bo2}} 
+\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4_bo2}} 
+\caption{Ratio of Boys for ``Second'' Births by Survey Round}
+\label{fig:sex_ratio_recall_rounds_bo2}
 \end{figure}

### 2019-01-09 paper/sex_selection_spacing-ver2.tex
Add graphs on recall error and simply cut-off to 22 years or more.

@@
 NFHS enumerators probe for any missed births, although the method depends on the survey.
-NFHS-1 probe for each calendar birth interval that is 4 or more years.
+NFHS-1 probe for each calendar birth interval that is four or more years.
 NFHS-2 asked for stillbirths, spontaneous and induced abortions and also probed 
-for each calendar birth interval 4 or more years.
-NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether were there any 
+for each calendar birth interval four or more years.
+NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether there were any 
 other live births between (name of previous birth) and (name), including any children who 
@@
 The problem with the above approach is that the year of birth is affected by recall error; 
-for example, a second born child listed as first-born is born later than the real 
-first born child.
-Recorded year of marriage should, however, be affected neither by parental recall error 
+a second born child listed as first-born is born later than the real first born child.
+Year of marriage should, however, be affected neither by parental recall error 
 nor the use of sex-selective abortions.
@@
 than earlier surveys.
-
-The basic recall error pattern remains with women married longer ago more
+The basic recall error pattern remains, with women married longer ago more
 likely to report that their first-born is a boy.
-If anything the pattern is more consistent when using year of marriage than 
-year of birth. 
-Before the introduction of sex selection there are only two instances  across the two 
-parities where the observed sex ratio is lower for women married longer ago than for women 
-married closer to the survey date.%
-\footnote{
-For first-borns it is between 1970--1974 and 1975-1979 for NFHS-3 and for second-borns
-it is between 1975--1979 and 1980--1984 for NFHS-1.
-}
 Similarly, comparing women married in the same five-year period across surveys shows
@@
 The relationship between length of marriage and recall error can also seen in 
-Figure \ref{fig:sexRatioMarriage}, which shows the observed sex ratio for children reported
-as first born as a function of duration of marriage at the time of the survey combining 
-all four surveys.
-The solid line is the sex ratio of children reported 
-as first born by the number of years between the survey and marriage, 
-the dashed lines indicate the 95 percent confidence interval 
-and the horizontal line the natural sex ratio (approximately 0.512).
+Figures \ref{fig:sex_ratio_recall_rounds_bo1} and \ref{fig:sex_ratio_recall_rounds_bo2}, 
+which show the observed sex ratio for children reported as first born as a function of 
+duration of marriage at the time of the survey.
+The solid line is the sex ratio of children reported as first born by the number of years 
+between the survey and marriage, the dashed lines indicate the 95 percent confidence 
+interval and the horizontal line the natural sex ratio (approximately 0.512).
 To ensure sufficient cell sizes the years are grouped in twos.
 In line with the results from Tables \ref{tab:recallMarriageBO1} and 
-\ref{tab:recallMarriageBO2}, the observed ratio of boys 
-is increasingly above the expected value the longer ago the parents were married.
-
-\begin{figure}[htp]%
-\centering
-\includegraphics[width=0.9\textwidth]{recall_sex_ratio_marriage}
-\caption{Sex ratio of ``first'' births by duration of marriage}
-\label{fig:sexRatioMarriage}
-\end{figure}
-
-The increasingly unequal sex ratio with increasing marriage duration suggests that
-a solution to the recall error problem is to drop observations for 
-women who were married ``too far'' from the survey year.
-The main problem is establishing what the best cut-off point should be.
-As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} shows there are 
-differences in recall error across the three surveys and between parities.
-One possibility is simply to drop all women married in cohorts where the observed
-sex ratio is substantially higher than the natural sex ratio, but even this is not
-straightforward.
-For ``first'' born this would imply dropping all women married before 1980, but
-for ``second'' born it would be imply dropping all married before 1970 for NFHS-1, before 1975 
-for NFHS-2, and before 1980 NFHS-3.
-Because of the differences between ``first'' and ``second'' born in the different surveys
-I vary the cut-off point by survey round.
-
-NFHS-3 is the most straightforward in that the implied cut-off point is the same for
-both first and second born.
-Based on Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2}, women in 
-NFHS-3 who were married 26 years or
-more before the survey date are dropped.
-For NFHS-1 and NFHS-2 the trade-off is between ensuring enough information and not bias 
-the results unduly.
-Given that sex selective abortions are more likely in higher parity birth I base the
-cut-off point on the second births instead of the first births.
-Hence, for NFHS-1 women who were married 22 years or more before the survey date 
-were dropped and for NFHS-2 women who were married 23 year or more before the survey date 
-were dropped.
+\ref{tab:recallMarriageBO2}, the observed ratio of boys is increasingly above the expected 
+value the longer ago the parents were married.
 
@@
 \end{figure}
+
+The increasingly unequal sex ratio with increasing marriage duration suggests that
+a solution to the recall error problem is to drop observations for 
+women who were married ``too far'' from the survey year.
+The main problem is establishing what the best cut-off point should be, with the
+trade-off between retaining enough observations and the correctness of the information.
+As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} show, there are 
+differences in recall error across the three surveys and between parities, although
+this may simply be the result of differences in number of observations across surveys.
+Furthermore, the recall error pattern is not entirely consistent across observed birth 
+orders.
+Since most of the surveys start showing significantly biased sex ratio from around 22
+years of marriage on, I drop all observations where the marriage took place 22 years
+or more.
 

### 2019-01-09 paper/sex_selection_spacing-ver2.tex
Minor edits

@@
 Finally, across surveys, the same cohort tends to show a higher sex ratio the more recent 
-the survey (births in the cohort took place earlier relatively to the survey date).
+the survey (births in the cohort took place earlier relative to the survey date).
 Despite this, few cohorts show significantly different sex ratios across surveys, most 
@@
 
-The relationship between length of marriage and recall error can also seen in 
+The relationship between the length of marriage and recall error can also be seen in 
 Figures \ref{fig:sex_ratio_recall_rounds_bo1} and \ref{fig:sex_ratio_recall_rounds_bo2}, 
 which show the observed sex ratio for children reported as first born as a function of 
-duration of marriage at the time of the survey.
-The solid line is the sex ratio of children reported as first born by the number of years 
-between the survey and marriage, the dashed lines indicate the 95 percent confidence 
+the duration of marriage at the time of the survey.
+The solid line is the sex ratio of children reported as first-born by the number of years 
+between the survey and marriage, while the dashed lines indicate the 95 percent confidence 
 interval and the horizontal line the natural sex ratio (approximately 0.512).
-To ensure sufficient cell sizes the years are grouped in twos.
+To ensure sufficient cell sizes I group years into twos.
 In line with the results from Tables \ref{tab:recallMarriageBO1} and 
@@
 As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} show, there are 
-differences in recall error across the three surveys and between parities, although
-this may simply be the result of differences in number of observations across surveys.
+differences in recall error across the three surveys and between the two birth
+orders, although this may be the result of differences in the number of observations 
+across surveys.
 Furthermore, the recall error pattern is not entirely consistent across observed birth 

### 2019-02-01 response/response-demography-1.tex
Minor edits
Respond to questions on marriage cut-off year
Discuss regions and imputed spacing to first birth

@@
 
+[Make the paper about spacing; need to emphasize why spacing is interesting]
+
 5. The use of competing hazard models is not new in demographic research
@@
 
-[Maybe run regression only on those birth intervals that does not
-involve imputations on either end of the spacing.
-This could be presented in the Appendix, unless very different from
-results.]
+For both NFHS-1 and NFHS-2, the only information collected on marriage timing is age at 
+marriage and age starting living with husband.
+For NFHS-1, I, therefore, used the date of birth of the respondent in CMC and added the 
+age at marriage multiplied by 12 to get the earliest data of marriage in CMC possible.
+Using this definition, 10.73 percent have duration of less than eight months or fewer, and
+0.71 percent have a negative duration.
+For NFHS-2, I used the imputed duration provided in the recode data set, which leads to 
+24.65 with an eight months or fewer duration between marriage and first birth, and 0.95 
+percent with a negative duration.
+
+Both NFHS-3 and NFHS-4 ask for specific month and year of first marriage, but a number of
+respondent did not provide complete information.
+One approach to understanding the impact on spacing to first birth is to split spacing 
+from marriage to first birth by completeness of date of marriage.
+In NFHS-3, 2.55 percent of the 39,213 women with complete information on date of 
+marriage show a spacing from marriage to first birth of 8 months or less and that 0.6 
+percent show a negative spacing. 
+For the 19,403 women with incomplete information on date of marriage 27.36 percent show
+a spacing from marriage to first birth of 8 months or less and that 3.37 percent show a 
+negative duration.
+In NFHS-4, 3.8 percent of women with complete information report a birth 8 or fewer months
+after marriage and 2.35 report a negative duration.
+For women with imputed information, 14.99 percent report a birth 8 or fewer months
+after marriage with 11.02 percent reporting a negative duration.
+The main difference between NFHS-3 and NFHS-4 is that only just below four percent of 
+women in NFHS-4 have imputed information whereas more than 33 percent did in NFHS-3.
+
+[Maybe it makes the most sense to simply drop the analysis of first spell]
+
+[What to do with fecundity variable?]
 
@@
 [Response:]
-
-[Add this discussion back into Appendix]
+I have added a detailed discussion of recall error in the Appendices intended for online 
+publication.
+Furthermore, I have changed the cut-off to be 22 years of marriage or more for all surveys 
+to simplify.
+Even with the stricter cut-off there are still some evidence of recall error,
+especially in region TK, where the sex ratio was substantially biased against females 
+before sex selection became available.
 
@@
 
-[Check for broad regions to incorporate. Check how to do this for the non-proportional
-hazard specification.]
+I have divided India into four broad regions depending on degree of son preference and
+initial fertility level (inspired by the categories in \citep{retherford03b}, but
+expanded to include all states in the surveys).
+In addition to the potential power problem, the division also means that there now are 
+four times as many tables and graphs, which exacerbate the concern in comment 9 below.
+I have, therefore, selected what I consider the most important results and presented
+those in graphical format.
 

### 2019-02-04 response/response-demography-1.tex
Explain response to imputed first spell values

@@
 
+This is, indeed, an important concern.
 For both NFHS-1 and NFHS-2, the only information collected on marriage timing is age at 
@@
 For NFHS-2, I used the imputed duration provided in the recode data set, which leads to 
-24.65 with an eight months or fewer duration between marriage and first birth, and 0.95 
-percent with a negative duration.
+24.65 percent with an eight months or fewer duration between marriage and first birth, 
+and 0.95 percent with a negative duration.
+Other people seem to have caught by the same problem, such as \citet{Padmadas2004}.
 
@@
 
-[Maybe it makes the most sense to simply drop the analysis of first spell]
+Given the substantial problems with the first spell data for all but the very last
+survey and that the first spell analysis adds relatively little to the central question, 
+I have dropped the analysis of first spells.
+Removing the first spell also helps keeping the paper within the word limit.
+Because of the large number of imputed observations for the first spell, I have also
+remove the first spell duration and its square as explanatory variables for the second
+through fourth spells.
 
-[What to do with fecundity variable?]
+[TK still needs to be removed from the paper]
 

### 2019-02-05 response/response-demography-1.tex
Some region bootstrap analyses do not converge, so limit to high education
The problem is mainly for the medium education women, where there are a low number
of observations, especially for the southern parts of India. Since high education
women are more likely to use sex selection focus is now on them.

Also has the advantage of cutting down on run time.

@@
 [Response:]
-
-I have divided India into four broad regions depending on degree of son preference and
-initial fertility level (inspired by the categories in \citep{retherford03b}, but
-expanded to include all states in the surveys).
-In addition to the potential power problem, the division also means that there now are 
-four times as many tables and graphs, which exacerbate the concern in comment 9 below.
-I have, therefore, selected what I consider the most important results and presented
-those in graphical format.
+I agree completely that the regional differences in fertility, son preference, and use 
+of sex selection are important.
+To try to capture these differences, I have divided India into four broad regions 
+depending on degree of son preference and initial fertility level as in 
+\citep{retherford03b}, although expanded to include all states in the surveys.
+In addition to the power problem, some education/region/spell/period combinations have too 
+small sample sizes for the estimations to converge.
+The lack of convergence is especially an issue for the middle-education group at the
+higher spells.
+I, therefore, first present the all-India results and then focus on regional differences
+for the most educated women.
 

### 2019-02-06 paper/birth_spacing_lit.tex
Initial commit of possible lit and write-up

To read:

In birth_spacing:

In collection.bib
\citep{Rafalitnanana2000} 
\citep{Rahman1993}
\citep{Jayachandran2017}
\citep{Jayachandran2017a}
\citep{Lambert2016}

In collection.bib but maybe not that relevant
\citep{Basu2010} 
\citep{dasgupta95} 
\citep{Kugler2017}

### 2019-02-12 paper/birth_spacing_lit.tex
Add notes on papers read

@@
 \citep{Kugler2017}
+
+\citet{Dewey2007}
+
+Review study
+
+The three conceptual models demonstrate that the relationship between
+interpregnancy interval and maternal or child nutritional status is by
+no means simple.
+
+The studies on child nutrition outcomes indicate that a longer birth
+interval is associated with a lower risk of malnutrition in some
+populations, but not all.
+
+The studies on maternal anthropometric outcomes yielded mixed results.
+Because the nutritional burden on the mother between pregnancies depends
+on the extent of breastfeeding, the interpregnancy interval is not the
+best measure of whether the mother has had a chance to recover from the
+pregnancy, in terms of repleting her nutritional status. Therefore, some
+studies examined the ‘recuperative interval’ (duration of the
+non-pregnant, non-lactating interval) instead.
+
+Lactation represents a greater nutritional burden than pregnancy,
+
+[link with paper on shorter breastfeeding for girls than for boys]
+
+Important methodological limitations in papers used.
+
+Mechanisms: 
+- new pregnancy can lead to reduction is breastfeeding (reduced volume of breastmilk), which
+can be hazardous both nutritionally and in terms of resistance to infection.
+(lower breastfeeding -> less contraceptive effect -> shorter birth intervals)
+
+- care of new infant affects prior child; might even happen before birth of new child
+
+\citet{Gribble2009}
+
+El Salvadore NFHS 2002-2003
+
+Our objectives are to explore how short birth intervals may increase the
+risk of stunting and underweight, and to identify policy and
+programmatic efforts that can contribute to reducing the risk of
+undernutrition, including healthy timing and spacing of pregnancies.
+
+Nevertheless, the ﬁndings do suggest that birth intervals of less than 3
+years are either directly related to stunting or act as a proxy for a
+risk factor that is either unobserved or not included in the analysis.
+
+(no attempt to estimate what determines birth spacing, although do acknowledge that
+causality is difficult to establish)
+
+\citet{Soest2018}
+
+The main novelty compared to [14] is that our application concerns
+infant mortality in rural Bangladesh. While Bhalotra and van Soest used
+retrospective data to analyse neonatal mortality in India, we use
+prospective data from the Demographic and Health Surveillance System,
+Matlab, following mothers residing in the study area over time.
+
+Many studies also found an association between a short birth interval
+and infant death of the next child, particularly when the preceding
+sibling survived [21–23]. An explanation for this is that the mother has
+not recuperated physiologically from the previous birth [24–25].
+
+(!this is an important point. In the literature, the mortality effect discussed
+generally comes from the subsequent child, not the prior one. 
+Hence, longer spacing should be beneficial for the boy born next if 
+sex selection has been used.
+This could explain part of the reduction in female mortality: The
+girls that would "normally" have been born relatively soon after the
+prior birth, and, therefore, have higher mortality risk, now are no
+longer born.
+)
+
+Sibling competition may also explain why short birth intervals and high
+fertility increase death risk: sources of food and care per head
+diminish as the number of dependent members of a family increases [5].
+
+(this effect can be used to explain any reductions in mortality for
+the prior girls.
+
+A type of this would be cession of breastfeeding because of a short
+birth interval - see Conde et al. paper below for discussion of 
+breastfeeding. 
+)
+
+(This might be something to test in a new paper. Mortality risk should
+go down differentially across parities with access to sex selection,
+depending on the sex of the prior child. This effect should be larger
+for families more likely to use sex selection, i.e. higher education
+women.
+Since we do not know actual use of sex selection, one possibility
+would be to used the area's sex ratio for the type of family.
+A caveat is that sibling competition is less likely to occur, which
+would also reduce mortality for the prior child, although possibly
+less.
+A first step would be to check on mortality levels among the
+well-educated women.
+)
+
+We assume gender of each birth is exogenous and thus do not incorporate
+the possibility of selective abortion. Descriptive statistics confirm
+that this is not an issue in these data, revealing no relation at all
+between gender of a newborn child and gender composition of the older
+children in the family.
+
+keeping other covariates and unobserved mother specific factors
+constant, if the previous child survived its infancy, the mortality
+probability falls with the length of the birth interval as long as the
+birth interval is less than 63.3 months
+
+If the previous child died, mortality falls with birth interval length
+for intervals up to 52.5 months, still much beyond the median.
+
+In the comparison area, death at infancy of the previous child shortens
+the subsequent birth interval by about 46\%.
+
+Having at least one boy has a stronger positive effect on the birth
+interval than having a girl. The same applies to each additional boy.
+
+Birth intervals increase with the mother’s education level, in line with
+the positive relation between birth intervals and socioeconomic status.
+This is in line with the finding that the use of contraception is more
+common among higher socioeconomic status groups [38].
+
+A large negative correlation is observed between unobserved
+heterogeneity in birth interval and fertility equations, confirming that
+both equations are strongly related: mothers who desire many children
+also tend to use shorter birth intervals. This is consistent with the
+target fertility model of Wolpin [4] and in line with the findings in
+[14].
+
+\citet{Zimmermann2018}
+
+Son preference is widespread in a number of developing countries despite
+substantial improvements in education levels and economic development.
+One potential explanation for the persistence of this phenomenon is that
+individual household members like the mother derive large non-monetary
+beneﬁts from giving birth to a son and therefore prefer boys to girls.
+
+I focus on ﬁrst-born children for whom the sex ratio of girls relative to boys is normal.
+
+The results show little evidence of consistently large female beneﬁts
+shortly after birth, and any positive impacts of having a son disappear
+after the ﬁrst six months. There are also no large beneﬁts for adult
+sons. These empirical patterns do not support qualitative evidence
+suggesting that women beneﬁt from the birth of a son through larger
+decision-making powers in the household because of increased respect by
+other household members.
+
+(Li and Wu (2011) is the paper on China that found positive effects on
+bargaining power of a first born son)
+
+(does not seem directly relevant for this paper.)
+
+\citet{Conde-Agudelo2012}
+
+The following hypothetical causal mechanisms for explaining the
+association between short intervals and adverse outcomes were
+identified: maternal nutritional depletion, folate depletion, cervical
+insufficiency, vertical transmission of infections, suboptimal lactation
+related to breastfeeding–pregnancy overlap, sibling competition,
+transmission of infectious diseases among siblings, incomplete healing
+of uterine scar from previous cesarean delivery, and abnormal remodeling
+of endometrial blood vessels.
+
+Interpregnancy intervals shorter than 18 months and longer than 59
+months are significantly associated with increased risk of adverse
+perinatal outcomes such as preterm birth, low birth-weight, and small
+for gestational age (Conde-Agudelo, Rosas-Bermudez, and Kafury-Goeta
+2006).
+
+Preceding interpregnancy intervals shorter than 36 months are
+significantly associated with a greater risk of child and
+under-five-years mortality, and intervals shorter than 24 months
+significantly increase risk of early neonatal, neonatal, and infant
+mortality (Rutstein 2008).
+
+Hypotheses generally adopt either biological or behavioral orientations,
+but no one framework or hypothesis has emerged as dominant (Erickson and
+Bjerkedal 1979; Winikoff 1983; Klebanoff 1999).
+
+The current maternal nutritional depletion hypothesis states that a
+close succession of pregnancies and of periods of lactation worsens the
+mother’s nutritional status because of inadequate time to recover from
+the physiological stresses of the preceding pregnancy before becoming
+subject to the stresses of the next pregnancy (Winkvist, Rasmussen, and
+Habicht 1992; King 2003).
+
+In summary, the studies that evaluated the effects of birth spacing on
+maternal anthropometric status, anemia, and micronutrient status did not
+provide clear evidence to support the maternal nutritional depletion
+hypothesis.
+
+(if parents know that/believe that there are substantially negative 
+effects of short spacing, why would they engage in it. It would put
+they subsequent son at an disadvantage. Unless the compensatory effects
+are so large that it balances out the negative effects.)
+
+if a new pregnancy starts before complete folate restoration, the woman
+will be at higher risk of maternal folate deficiency and subsequent
+adverse perinatal outcomes such as low birthweight, preterm birth, and
+small for gestational age.
+
+Strong evidence exists that folate depletion occurs in women during the
+first three to four months postpartum, and growing evidence supports the
+hypothesis that this depletion constitutes a hypothetical causal
+mechanism that explains the increased risk of adverse perinatal outcomes
+in women with short interpregnancy intervals.
+
+Haaga (1988) proposed that inadequate time to regain muscle tone in
+reproductive tissues after a pregnancy might lead to increased incidence
+of cervical insufficiency (formerly called cervical incompetence) toward
+the end of the next pregnancy, resulting in increased incidence of
+preterm birth. Cervical insufficiency is described as the inability of
+the uterine cervix to retain a pregnancy in the absence of contractions
+or labor.
+
+Strong evidence suggests that cervical insufficiency is a cause of
+spontaneous preterm birth (Romero et al. 2006).
+
+Adverse perinatal outcomes associated with maternal infections can occur
+because of direct infections of the fetus or neonate, or because of
+infections that cause early delivery without directly involving the
+fetus. For organisms that attack the fetus directly, transmission may
+occur within the uterus via transplacental or ascending infection, or in
+the intrapartum period secondary to fetal contact with infected genital
+secretions or maternal blood (vertical transmission).
+
+emerging evidence supports the hypothesis that the association between
+short intervals and adverse perinatal outcomes could also be mediated by
+vertical transmission of infections.
+
+Breastfeeding–pregnancy overlap is defined as the continuation of
+breastfeeding into the first, second, or even third trimester of
+pregnancy.
+
+short intervals could indirectly increase the risk of adverse
+neonatal/infant outcomes through changes in breastfeeding patterns or
+the composition and/or quantity of breast milk secondary to
+breastfeeding–pregnancy overlap.
+
+Although we did not identify any studies that specifically evaluated
+suboptimal lactation related to the breastfeeding–pregnancy overlap
+hypothesis for explaining the association between short intervals and
+neonatal/infant health, some evidence presented above supports this
+hypothetical causal mechanism.
+
+the relationship between short interpregnancy or birth intervals and
+infant and child mortality may be explained by sibling competition,
+which may interact with other proposed mechanisms such as the
+transmission of infectious diseases among closely spaced siblings. If
+two or more young children within a family are close in age, they may
+compete for resources and for parental care and attention.
+
+although the results are conflicting, they suggest that the effects of
+preceding short birth intervals on neonatal and infant mortality seem to
+be stronger when the preceding sibling dies than when she/he survives.
+This finding suggests that neither competition nor transmission of
+infectious diseases among siblings is the main mechanism by which short
+birth intervals may affect neonatal and infant mortality. The effects of
+preceding short birth intervals on post-neonatal mortality seem to be
+stronger when the preceding sibling survives than when she/he dies,
+which is consistent with both the sibling competition hypothesis and the
+hypothesis of transmission of infectious diseases among siblings.
+Evidence regarding the effects of preceding short birth intervals on
+child and under-five-years mortality according to survival status of the
+preceding sibling is inconclusive.
+
+Interpregnancy intervals longer than five years are associated with an
+increased risk of adverse perinatal outcomes, such as preterm birth, low
+birth-weight, small for gestational age (Conde-Agudelo, Rosas-Bermudez
+and Kafury-Goeta 2006), and preeclampsia (Conde-Agudelo, Rosas-Bermudez,
+and Kafury-Goeta 2007).
+
+According to this hypothesis, the mother’s physiological processes are
+primed for fetal growth during pregnancy and decline gradually after
+delivery. The benefit gained during pregnancy declines gradually
+postpartum if the mother does not become pregnant again.
+
+\citet{Buckles2012}
+
+US analysis.
+
+Using the NLSY79 and NLSY79 Child and Young Adult Surveys we investigate 
+the effect of the age difference between between siblings (spacing) on
+educational achievement. Because spacing may be endogenous, we use an
+instrumental variables strategy that exploits variation in spacing driven
+by miscarriages. The IV results indicate that a one-year increases in
+spacing increases test scores for older siblings by about 0.17 standard
+deviations. These results are larger than the OLS estimates, suggesting
+that failing to account for the endogeneity of spacing may understate
+its benefits. For younger siblings, we find no causal impact of spacing
+on test scores.
+
+The identification strategy exploits variation in spacing driven by 
+miscarriages that occur between two live births; there are several caveats to 
+consider when using this instrument, which will be discussed in detail in Section V. 
+We show that a miscarriage between siblings is associated with an increase in 
+spacing of about eight months, and decreases the likelihood that the siblings 
+are less than two years apart by 19 percentage points.
+
+Among economists, Rosenzweig (1986) develops a model of optimal child spacing
+in which spacing is an input into child quality. An important feature of the model
+is that the endowments of older children affect the optimal timing of subsequent
+births.
+Rosenzweig, Mark R. 1986. "Birth Spacing and Sibling Inequality: Asymmetric Information
+Within the Household. "International Economic Review 27(l):55-76.
+
+Heckman and Walker (1990) consider the effects of female labor market outcomes
+on fertility timing and birth spacing and found that higher female wages led to
+delayed childbearing and greater spacing between children. Troske and Voicu (2009)
+show that women who delay the birth of a second child reduce their labor force
+participation by less than women with closely spaced children, but are more likely
+to work part-time.
+
+Estimates of average time to conception for women who conceived within one year of 
+a miscarriage range from 17.35 weeks (Goldstein, Croughan, and Robertson 2002) to 23.2
+weeks (Wyss, Biedermann, and Huch 1994).
+
+\citet{Saha2013}
+
+Matlab, Bangladesh
+
+this study analyzes the causal effects of birth spacing on subsequent
+infant mortality and of infant mortality on the use of contraceptives
+and the length of the next birth interval.
+
+Our main finding is that complete contraceptive use could reduce infant
+mortality of birth order two and higher by 7.9 percent. The net effect
+of complete contraceptive use on the total infant mortality rate is
+small (2.9 percent), however, because the favorable effect on higher
+order births is partly offset by the rise in the proportion of high-risk
+first births.

### 2019-02-12 paper/birth_spacing_lit.tex
Add notes on papers

@@
 breastfeeding. 
-)
-
-(This might be something to test in a new paper. Mortality risk should
-go down differentially across parities with access to sex selection,
-depending on the sex of the prior child. This effect should be larger
-for families more likely to use sex selection, i.e. higher education
-women.
-Since we do not know actual use of sex selection, one possibility
-would be to used the area's sex ratio for the type of family.
-A caveat is that sibling competition is less likely to occur, which
-would also reduce mortality for the prior child, although possibly
-less.
-A first step would be to check on mortality levels among the
-well-educated women.
 )
@@
 first births.
+
+we use the estimates to perform simulations that show how the use of
+contraceptives is linked to the infant mortality rate in two ways: (1)
+by reducing mortality among higher order births by lengthening birth
+intervals, and (2) through a composition effect: reducing the number of
+higher order births leads to a larger proportion of relatively
+vulnerable first order births, thereby increasing the average mortality
+rate for all birth orders.
+
+keeping other factors constant (including the decision to use
+contraceptives at any time after the previous birth), birth intervals
+tend to be shorter for higher birth orders, which is consistent with the
+association between short birth intervals and high fertility.
+
+\citep{Jayachandran2011}
+
+If son preference exists, girls will be weaned earlier than boys because
+parents want to try again for a son. Given the large health benefits of
+breastfeeding in environments with contaminated food and water (Feachem
+and Koblinsky 1984; Palloni and Millman 1986; Habicht, DaVanzo, and Butz
+1988), such behaviorcanleadtogenderdisparities inchildhealth. Incontrast
+to the standard explanation of gender health disparities—that parents
+actively invest more in sons’ health—we show that if parents merely
+prefer to have sons, then mothers will breastfeed daughters less,
+causing a gender gapin health even when parents
+equallyvaluethehealthofall theirchildren. Ourresults highlight how
+health disparities can arise “passively” from fertility preferences, and
+relate to earlier work (Yamaguchi 1989; Clark 2000; Jensen 2003) showing
+that a “try until you have a son” fertility rule results in girls, on
+average, having more siblings and thus more competition for household
+resources.
+
+Model predictions:
+First, breastfeeding duration increases with birth order, as demand for
+breastfeeding’s contraceptive properties should rise as couples approach
+or exceed their ideal family size, andin fact shouldincrease
+discontinuously once ideal family size is met.
+Second, as explained, as long as some son preference exists, girls are
+breastfed less than boys.
+Third, by the same logic, children with older brothers are breastfed more.
+Fourth, the gender effect is largest when a couple approaches its target
+family size since, at that point, their decision to have another child
+is highly marginal and thus most sensitive to sex composition; the
+effect is smallest for children whose birth order is either
+significantly below or above ideal family size because couples will want
+to, respectively, wean or nurse such children regardless of gender.
+
+several papers show empirically that in settings with son preference, a
+couple that just had a son is more likely to stop having children (Das
+1987) or wait longer to have the next child (Rindfuss et al. 1982;
+Trussell et al. 1985; Arnold, Choe, and Roy 1998; RetherfordandRoy
+2003). Hemochandra, Singh, and Singh (2010) show that birth intervals
+are shorter if parents have not reached their self-reported ideal number
+of sons. Second, Nemeth and Bowling (1985) examine whether having nosons
+shortens the duration of breastfeeding.
+
+Muhuri and Menken (1997) show that birth spacing and the sex of older
+siblings affect mortality and state that shorter birth intervals after
+girls are one potential cause of excess female mortality. In unreported
+results, Arnold, Choe, and Roy (1998) examine whether the gender gap in
+mortality in India is due to birth spacing; they donot findevidence
+tosupport the hypothesis. Finally, Mutharayappa et al. (1997) show that
+there is a gender gap in breastfeeding in India and conjecture that it
+is related to son-biased fertility patterns.
+
+((Bhatia 1978; Basu 1992) on lower son preference in the south)
+
+Retherford et al. (1989) find that controlling for breastfeeding largely
+eliminates the negative correlation between infant mortality and
+subsequent birth spacing in Nepal.
+
+\citep{Whitworth2002}
+
+This paper examines the impact of the length of the preceding birth
+interval on under-two mortality in India, and examines the pathways
+through which short preceding birth intervals may lead to an increased
+risk of mortality
+
+1992 NFHS
+
+Three mortality periods are examined: neonatal, early post neonatal and
+late post-neonatal and toddler
+
+short preceding birth intervals (< 18 months) are associated with an
+increased risk of mortality in all three age groups, and the effect is
+particularly marked in the early post-neonatal period.
+
+diluting effect that a higher level of maternal education has on the
+relationship between short preceding birth intervals and mortality risk
+
+There is evidence to suggest that sibling rivalry is a pathway through
+which short birth intervals inﬂuence mortality, with the death of the
+previous sibling removing the competition for scarce resources, and
+resulting in lower risks of mortality than if the previous sibling was
+still alive.
+
+\citep{Bhalotra2008}

### 2019-02-12 paper/birth_spacing_lit.tex
Add notes

@@
 \citep{Bhalotra2008}
+
+NFHS-2 1998-99
+
+We use data for Uttar Pradesh (UP), the largest Indian state, which, in
+the year 2000, contained 17.1\% of the country’s population
+(approximately 165 million people). It has social and demographic
+indicators that put it well below the Indian average (Dreze and Sen,
+1997).
+
+Birth intervals explain only a limited share of the correlation between
+neonatal mortality of successive children in a family.
+
+The main contribution of this paper is to use panel data based on
+retrospective fertility histories to estimate causal effects of birth
+interval length on subsequent neonatal mortality risk and of neonatal
+mortality on subsequent birth interval length, controlling for
+unobserved heterogeneity in both processes (referred to as frailty and
+fecundity, respectively)

### 2019-02-14 response/response-demography-1.tex
Add notes on spacing literature

@@
 I, therefore, first present the all-India results and then focus on regional differences
-for the most educated women.
+for only the most educated women, who are the main users of sex selection.
+
+[Part of the reason is the very low fertility in the southern areas. See Guilmoto
+and Rajan 2001 and IIPS 2006 and check latest NFHS report on, for example, Tamil Nadu.
+TFR of less than 2 is likely.]
+
+It is also worthwhile to note that even some of the southern states appear to have
+seen an increase in son preference over time, or, rather, daughter aversion
+\citep{DiamondSmith2008}.
 

### 2019-02-14 paper/birth_spacing_lit.tex
Add notes on spacing literature

@@
-To read:
-
-In birth_spacing:
-
-In collection.bib
-\citep{Rafalitnanana2000} 
-\citep{Rahman1993}
-\citep{Jayachandran2017}
-\citep{Jayachandran2017a}
-\citep{Lambert2016}
-
-In collection.bib but maybe not that relevant
-\citep{Basu2010} 
-\citep{dasgupta95} 
-\citep{Kugler2017}
-
 \citet{Dewey2007}
@@
 fecundity, respectively)
+
+The gender of the last-born child is signiﬁcant and its sign is
+consistent with son-preference. If the last birth was a girl, the
+expected birth interval is about 3\% shorter than if it was a boy.
+
+There is a signiﬁcant humpshaped trend in birth-spacing, with a maximum
+in 1980. That birth intervals got shorter in the last 20 years might be
+because rising nutritional standards for mothers allow them to support
+shorter intervals. Alternatively, the rise in women’s labour force
+participation may have encouraged clustering of fertility.
+
+birth intervals increase until the sixth child is born.
+
+Other things equal, birth-order exhibits a non-monotonic pattern, with
+the shortest birth intervals preceding the birth of the fourth child.
+
+Maternal education decreases both mortality and fertility, but has no
+effect on birth-spacing.
+
+Fertility decline in India seems to have set in from 1981. Despite this,
+birth intervals have got shorter since about then.
+
+\citep{Zavier2000}
+
+NFHS 92-93 Kerala
+
+Many couples in India never use a reversible method to delay or space births, and in-
+stead adopt sterilization as their first and only method.
+
+higher educational attainment (of either partner) independently increases the likelihood 
+that a couple will have used a method to delay or space births, as does middle 
+socioeconomic status.
+
+\citep{Maitra2008}
+
+We ﬁnd that the estimates of birth spacing on child mortality are different when we do not account for fertility selection.
+
+Our analysis is based on the National Family Health Survey (NFHS) 1992–1993 data from the Indian province of the Punjab and the Demographic and Health Survey (DHS) 1991–1992 data from the Pakistani province of the Punjab.
+
+India: There is evidence of a statistically signiﬁcant effect of birth spacing on child survival: an increase in the duration between child i and child i + 1 signiﬁcantly reduces the hazard of mortality of child i (equivalently increases the survival chances of the child).
+for the sample of Pakistani households.
+As with the Indian case, there is evidence of maternal depletion/sibling competition effect in the Pakistani sample: an increase in the duration between child i and child i + 1 signiﬁcantly reduces the hazard of mortality of child i.
+
+early child death may also result in a reduction in the duration between successive children because parents want to replace children that have died.
+Our results show that the child replacement effect is signiﬁcant in the Indian sample, but not in the Pakistani sample.
+In other words, increased child survival increases birth spacing in India but not in Pakistan.
+
+\citep{Makepeace2008}
+
+NFHS 1992-1993 West Bengal
+
+Our central result is that child mortality decreases with increases in
+either prior or posterior spacing (although the size of the fall is
+different).
+
+There is evidence that uncorrected estimates under-estimate the effects
+of prior and posterior spacing on child mortality.
+
+the spacing between consecutive children, i.e. the age composition of
+siblings, could capture the intensity of competition between successive
+siblings better,
+
+\citep{Bhargava2003}
+
+NFHS 1992-93: Uttar Pradesh
+
+indicator variables constructed on the basis of the stated preferences for sons and daughters indicated that unwanted fertility contributes to excess mortality of higher order births, especially of girls.
+
+\citep{Davanzo2008}
+
+Matlab
+
+Shorter intervals are associated with higher mortality. Interval effects are greater if the
+interval began with a live birth than with another pregnancy outcome.
+
+previous studies have generally considered the preceding interval between births* the interbirth interval*as their measure of spacing
+
+the appropriate measure to use when considering the effect of competition or disease transmission from another young child in the family
+
+sometimes there is a pregnancy that resulted in an outcome other than a live birth (NLB) between two live births, in which case the interbirth interval will include two (or more) interpregnancy intervals.
+
+Some of the hypotheses about why reproductive spacing may affect infant and child health and survival are related to the interpregnancy interval
+
+Furthermore, an intervening NLB may reflect something about the mother’s health that may affect the health of her children
+
+Some, but very little, of the effect is explained by the fact that shorter interbirth and inter-outcome intervals are associated with shorter gestations of pregnancy.
+
+Our results give some credence to the maternal depletion hypothesis.
+We see that very short inter-outcome intervals are generally more detrimental when they follow a live birth or stillbirth than when they follow a preceding miscarriage or induced abortion.
+Because of their longer gestation, live births and stillbirths should be more depleting than miscarriages or induced abortions.
+The breastfeeding that follows a live birth leads to further maternal depletion.
+Indeed we find that the effects of short inter-outcome intervals are greatest when the preceding outcome was a live birth.
+
+We also find significant negative effects of subsequent short interpregnancy intervals on child survival (and have investigated this in a way that avoids reverse causality): a child is much more likely to die between ages 1 and 5 if the mother became pregnant again before this index child’s first birthday (RR02.31, pB0.001).
+
+\citep{Haughton1995}
+
+Vietnam Living Standards Survey (VLSS) 1992-1993
+
+This article assesses the strength of son preference in Vietnam, as reflected infertility behavior. It
+formulates and estimates a proportional hazards model applied to birth intervals, and a contraceptive
+prevalence model, using household survey datafrom 2,636 ever-married women aged 15-49 with at
+least one living child who were interviewedfor the Vietnam Living Standards Survey 1992-1993.
+
+ Two tests are applied to the data in an attempt to discern the presence of son preference. The hazard
+model test estimates the risk (hazard) of having another
+child at any point in time; if the hazard is lower for families with a son (or sons),
+the implication is that son preference is present. The contraceptive prevalence test
+determines whether families with a son (or sons) are significantly more likely to use
+contraceptives; if the answer is yer, a presumption may be made that son preference is present.
+
+The central finding of this study is that son preference,
+as reflected in household behavior, is strong in Vietnam.
+This finding is surprising in the sense that Vietnamese
+women are not secluded but are major participants in
+the labor force and are relatively well educated.
+
+\citep{Milazzo2018}
+
+This paper is the ﬁrst to show that morbidity and mortality among adult women in India can be partially explained by son preference.
+First, I show suggestive evidence that women with a ﬁrst-born girl have lower survival.
+Second, consistent with prior literature, I ﬁnd that having a ﬁrst-born girl leads to fertility behaviors medically known to hurt women’s survival.
+Third, I show new evidence of eﬀects of a ﬁrst-born girl on a mother’s likelihood and severity of anemia.
+These outcomes are severely aggravated with each successive female birth
+
+I pool the three available rounds of the India National Family Health Survey (NFHS) conducted in 1992/93, 1998/99, 2005/06, and consider the cross-sectional sample of women ages 15 to 39.
+
+I show nonparametric evidence that the share of living women whose ﬁrst birth is female is a decreasing function of their age (or, alternatively, of the number of years since ﬁrst birth).
+This decreasing pattern starts around age 24 and continues to decrease below the biological range, stabilizing for women in their mid-30s
+
+Although indirect, this evidence is suggestive of lower survival among women with ﬁrst girls due, at least partly, to son preference.
+
+I estimate the eﬀects of having a ﬁrst-born girl on several fertility-related outcomes, including the probability of desiring more children, being sterilized, having undergone ultrasound, having had a terminated pregnancy, short birth spacing, and the number of children ever born.
+
+I provide original evidence that women with ﬁrst-born girls are more likely to develop anemia.
+Speciﬁcally, a ﬁrst-born daughter increases the probability of being moderately or severely anemic by 5.4 percent.
+The additional eﬀect of a second and third-born girl (conditional on previous female births) is equivalent to 9 and 17.6 percent, respectively.
+Predetermined health or current pregnancy or breastfeeding status do not appear to drive these results.
+
+\citep{Gangadharan2003}
+
+We use an accelerated hazard model to estimate the duration between successive births and our results indicate that son preference exists only for the Indian community in South Africa.
+
+Indian households are observed to have a higher duration between children following the birth of a son, irrespective of the number of children they already have.
+For the rest of the population, there is very little evidence of son preference.
+
+For the Indian households, regardless of the number of existing sons, the duration is higher after a son.
+Additionally, an increase in the number of sons also significantly increases the duration between the second and the third children.
+
+\citep{Kim2010}
+
+Indonesia
+
+among earlier cohorts, women who are more educated tend to have shorter birth intervals than those who are less educated and that the opposite is true among later cohorts.
+
+The empirical results based on the ﬁrst hypothesis show that the level of industrialization of the local economy does not have a differential effect on birth spacing across educational groups.
+However, empirical results using measures of the availability of a family planning program show a differential effect on delaying births across educational groups.
+
+women’s education had an impact on the second birth interval mainly through changing the availability of contraceptives rather than through change in the demand for children over the period 1974–90.
+
+My ﬁndings are consistent with the hypothesis that more educated women are better at adopting new contraceptive technology.
+
+\citep{Teachman1989}
+
+USA
+
+Our findings suggest
+that a preference to balance the gender of children affects the timing of births, not a
+preference for either sons or daughters. At parity 2, women with children of the same
+sex time a third birth more rapidly than women with a boy and a girl. At parity 1,
+women with a boy time second births more rapidly than women with a girl. This
+seemingly anomalous finding is explained, however, by the fact that women with boys
+are more likely than women with girls to be married at any point in time and thus
+less likely to have disrupted fertility careers.
+
+\citep{DiamondSmith2008}
+
+Tamil Nadu, India
+
+The southern Indian state of Tamil Nadu has experienced a dramatic decline in fertility, accompanied by a trend of increased son preference.
+
+Findings suggest that daughter aversion, fuelled primarily by the perceived economic burden of daughters due to the proliferation of dowry, is playing a larger role in fertility decision-making than son preference.
+The desire for a son is often trumped by the worry over having many daughters.
+Women use various means of controlling the sex of their children, which in this study appear to be primarily female infanticide.
+It is important to distinguish between son preference and daughter aversion and to examine repercussions of low fertility within this setting.
+
+In the last decade, Tamil Nadu – along with its neighbouring southern states – has achieved very low fertility.
+In the year 2005–2006, the Total Fertility Rate (TFR, the average number of children born to a woman over her lifetime) was estimated at 1.80, down from a TFR of 4.97 in 1974 (Dyson and Moore 1983, Guilmoto and Rajan 2001, International Institute for Population Sciences and ORC Macro 2006).
+
+This impressive decline in fertility has been accompanied by worrisome evidence of the emergence of son preference in the past decade, which is reflected in increasingly disproportional sex ratios at birth and younger ages (Das Gupta and Bhat 1997, Basu 1999, Srinivasan 2005).
+
+If strong daughter aversion is a prime driver of fertility limitation, it may put downward pressure on population growth, possibly helping to explain the recent trend toward very low fertility rates in Tamil Nadu.
+Although the phenomenon of daughter aversion has received less attention than son preference, there are a few past studies on it, primarily in Northern India, some which suggest that it may differ by religious group (Khanna 1997, Borooah and Iyer 2004).
+Our work here supports the idea that daughter avoidance, often described inaccurately as son preference, is increasing in rural Tamil Nadu and suggests that economic constraints, primarily due to increased use of dowry, are the cause.
+
+\citep{Kishor1993}
+
+India
+
+Gender differentials in early childhood
+mortality are best modeled by simultaneously
+considering kinship structures and female labor force participation.
+
+the analysis suggests that cultural factors may contribute more to explaining gender
+differences in mortality across India than does female labor force participation.
+
+this analysis unequivocally suggests that excess fe-
+male mortality in India has both economic and
+cultural roots and any explanation must con-
+sider both economic and cultural factors.
+
+\citep{Curtis1993}
+
+Brazil
+
+In this paper random-effects logistic models are used to analyze the effects of the
+preceding birth interval on postneonatal mortality in Brazil, controlling for the
+correlation of survival outcomes between siblings. The results are compared to those
+obtained by using ordinary logistic regression. Family effects are found to be highly
+significant in the random-effects model, but the substantive conclusions of the
+ordinary logistic model are preserved. In particular, birth interval effects remain
+highly significant
+
+Birth interval effects are highly significant in Brazil, particularly in the less developed
+Northeast region. This point is important because short birth intervals are relatively common
+in Brazil, particularly in the Northeast.
+
+\citep{Rahman1993}
+
+Matlab, Bangladesh
+
+We hypothesize that mothers in Matlab have a strong preference about the gender composition of their surviving children; in particular, they want several surviving sons and at least one surviving daughter.
+
+the basic premise of this paper is that gender preference will have a greater influence on fertility where contraception is readily available and widely used; we expect to see little or no effect of gender preference on fertility in a population that does not use contraception.
+
+In the earlier stages of family formation (i.e., in families with three or fewer surviving children), the number of surviving sons is a significant (negative) predictor of subsequent fertility.
+In the later stages (i.e., in families with four or more surviving children), the subsequent pace of reproduction is affected significantly not only by the number of sons but also by whether there is a son and by whether there is a daughter in the family.
+Our results show not only a very strong desire for sons, which is seen early in the family formation process, but also a desire for at least one daughter, which is seen at a more advanced stage.
+
+The effect of gender composition of children is significantly stronger in the treatment area than in the comparison area.
+Moreover, whether the family has children of both genders seems to be more important in the treatment area than in the comparison area.
+
+These differentials in the impact of gender preference on fertility as a result of the availability and use of contraception imply strongly that gender preference effects become more important when contraception is readily availableand when a population is more able to control its fertility, other things being equal.
+
+\citep{Rafalitnanana2000}
+
+Sub-Saharan Africa 20 countries
+
+Examines preferred spacing as compared to observed spacing. In 5 of 20 countries the
+actual spacing is significantly longer than the preferred spacing.
+
+\citep{Lambert2016}
+
+Exploiting original data from a Senegalese household survey, we provide evidence that fertility choices are partly driven by women's needs for widowhood insurance.
+We use a duration model of birth intervals to show that women most at risk in case of widowhood intensify their fertility, shortening birth spacing, until they get a son.
+Insurance through sons might entail substantial health costs since short birth spacing raises maternal and infant mortality rates.
+
+\citep{Jayachandran2017}
+
+This paper’s contribution is to directly estimate the causal relationship between family size and the desired sex ratio and to quantify an important cause of rising sex ratios.
+The challenge in estimating this effect is to isolate exogenous variation in the fertility level.
+The approach I use is to elicit sex composition preferences at different fertility levels: a hypothetical fertility level is specified to the survey respondent, and she is asked, given that fertility level, what is her preferred composition of boys and
+girls. 5 By imposing the total number of children, one can characterize the respondents’ sex ratio preferences at different exogenously determined fertility levels.
+
+\citep{Basu2010}
+
+This article draws out some implications of son targeting fertility behavior and studies its determinants.
+We demonstrate that such behavior has two notable implications at the aggregate level: (a) girls have a larger number of siblings (sibling effect), and (b) girls are born at relatively earlier parities within families (birth-order effect).
+Empirically testing for these effects, we find that both are present in many countries in South Asia, Southeast Asia, and North Africa but are absent in the countries of sub-Saharan Africa.
+Using maximum likelihood estimation, we study the effect of covariates on son targeting fertility behavior in India, a country that displays significant sibling and birth-order effects.
+We find that income and geographic location of families significantly affect son targeting behavior.
+
+\citep{Kugler2017}
+
+Using data from nationally representative household surveys, we test whether Indian parents make trade-offs between the number of children and investments in education.
+To address the endogeneity due to the joint determination of quantity and quality of children, we instrument family size with the gender of the first child, which is plausibly random.
+Given a strong son preference in India, parents tend to have more children if the firstborn is a girl.
+Our instrumental variable results show that children from larger families have lower educational attainment and are less likely to be enrolled in school, with larger effects for rural, poorer, and low-caste families as well as for families with illiterate mothers.
+
+\citep{Hotz1997}
+
+This hazard approach provides a natural way to model incomplete histories, nonoccurrence of the event (a subsequent birth) and a natural set of covariates (current period values).
+It, however, does not solve several other problems.
+First, it provides
+little insight into how to summarize the information in past and future covariates.
+Second, it does not solve the dynamic selection problem.
+To be in the sample of individuals on which we estimate the time between the first and second birth, one must have had a first birth.
+This is a selected sample.
+This simple hazard model provides no insight into the effects of that selection.
+Finally, this model has the unfortunate characteristic of mixing the parameters for the speed with which the event occurs with the parameters for whether or not the event occurs.

### 2019-02-15 paper/birth_spacing_lit.tex
Update lit notes

@@
 \citet{Soest2018}
+
+we use dynamic panel data techniques to analyse the causal effects of infant mortality on birth intervals and fertility, as well as the causal effects of birth intervals on mortality in rural Bangladesh, accounting for unobserved heterogeneity and reverse causality
 
@@
 [14].
+
+We find evidence of causal effects in two directions: a short preceding birth interval reduces survival chances of infants, and an infant death increases the probability of a next birth and shortens the time until the next birth (replacement behaviour)
+
+Estimates of reproductive behaviour are consistent with gender preference: having more surviving boys significantly reduces the probability of having a next child and this effect is strongest in the comparison area
 
@@
 are shorter if parents have not reached their self-reported ideal number
-of sons. Second, Nemeth and Bowling (1985) examine whether having nosons
+of sons. Second, Nemeth and Bowling (1985) examine whether having no sons
 shortens the duration of breastfeeding.
@@
 
-We ﬁnd that the estimates of birth spacing on child mortality are different when we do not account for fertility selection.
+We find that the estimates of birth spacing on child mortality are
+different when we do not account for fertility selection.
 
-Our analysis is based on the National Family Health Survey (NFHS) 1992–1993 data from the Indian province of the Punjab and the Demographic and Health Survey (DHS) 1991–1992 data from the Pakistani province of the Punjab.
+Our analysis is based on the National Family Health Survey (NFHS)
+1992–1993 data from the Indian province of the Punjab and the
+Demographic and Health Survey (DHS) 1991–1992 data from the Pakistani
+province of the Punjab.
 
-India: There is evidence of a statistically signiﬁcant effect of birth spacing on child survival: an increase in the duration between child i and child i + 1 signiﬁcantly reduces the hazard of mortality of child i (equivalently increases the survival chances of the child).
-for the sample of Pakistani households.
-As with the Indian case, there is evidence of maternal depletion/sibling competition effect in the Pakistani sample: an increase in the duration between child i and child i + 1 signiﬁcantly reduces the hazard of mortality of child i.
+India: There is evidence of a statistically signifiant effect of birth
+spacing on child survival: an increase in the duration between child i
+and child i + 1 significantly reduces the hazard of mortality of child i
+(equivalently increases the survival chances of the child).
+for the sample of Pakistani households. As with the Indian case, there
+is evidence of maternal depletion/sibling competition effect in the
+Pakistani sample: an increase in the duration between child i and child
+i + 1 significantly reduces the hazard of mortality of child i.
 
-early child death may also result in a reduction in the duration between successive children because parents want to replace children that have died.
-Our results show that the child replacement effect is signiﬁcant in the Indian sample, but not in the Pakistani sample.
-In other words, increased child survival increases birth spacing in India but not in Pakistan.
+early child death may also result in a reduction in the duration between
+successive children because parents want to replace children that have
+died.
+Our results show that the child replacement effect is signiﬁcant in the
+Indian sample, but not in the Pakistani sample. In other words,
+increased child survival increases birth spacing in India but not in
+Pakistan.
 
@@
 
-indicator variables constructed on the basis of the stated preferences for sons and daughters indicated that unwanted fertility contributes to excess mortality of higher order births, especially of girls.
+indicator variables constructed on the basis of the stated preferences
+for sons and daughters indicated that unwanted fertility contributes to
+excess mortality of higher order births, especially of girls.
 
@@
 
-Shorter intervals are associated with higher mortality. Interval effects are greater if the
+Shorter intervals are associated with higher mortality. Interval effects
+are greater if the
 interval began with a live birth than with another pregnancy outcome.
 
-previous studies have generally considered the preceding interval between births* the interbirth interval*as their measure of spacing
+previous studies have generally considered the preceding interval
+between births* the interbirth interval*as their measure of spacing
 
-the appropriate measure to use when considering the effect of competition or disease transmission from another young child in the family
+the appropriate measure to use when considering the effect of
+competition or disease transmission from another young child in the
+family
 
-sometimes there is a pregnancy that resulted in an outcome other than a live birth (NLB) between two live births, in which case the interbirth interval will include two (or more) interpregnancy intervals.
+sometimes there is a pregnancy that resulted in an outcome other than a
+live birth (NLB) between two live births, in which case the interbirth
+interval will include two (or more) interpregnancy intervals.
 
-Some of the hypotheses about why reproductive spacing may affect infant and child health and survival are related to the interpregnancy interval
+Some of the hypotheses about why reproductive spacing may affect infant
+and child health and survival are related to the interpregnancy interval
 
-Furthermore, an intervening NLB may reflect something about the mother’s health that may affect the health of her children
+Furthermore, an intervening NLB may reflect something about the mother’s
+health that may affect the health of her children
 
-Some, but very little, of the effect is explained by the fact that shorter interbirth and inter-outcome intervals are associated with shorter gestations of pregnancy.
+Some, but very little, of the effect is explained by the fact that
+shorter interbirth and inter-outcome intervals are associated with
+shorter gestations of pregnancy.
 
 Our results give some credence to the maternal depletion hypothesis.
-We see that very short inter-outcome intervals are generally more detrimental when they follow a live birth or stillbirth than when they follow a preceding miscarriage or induced abortion.
-Because of their longer gestation, live births and stillbirths should be more depleting than miscarriages or induced abortions.
-The breastfeeding that follows a live birth leads to further maternal depletion.
-Indeed we find that the effects of short inter-outcome intervals are greatest when the preceding outcome was a live birth.
+We see that very short inter-outcome intervals are generally more
+detrimental when they follow a live birth or stillbirth than when they
+follow a preceding miscarriage or induced abortion. Because of their
+longer gestation, live births and stillbirths should be more depleting
+than miscarriages or induced abortions.
+The breastfeeding that follows a live birth leads to further maternal
+depletion. Indeed we find that the effects of short inter-outcome
+intervals are greatest when the preceding outcome was a live birth.
 
-We also find significant negative effects of subsequent short interpregnancy intervals on child survival (and have investigated this in a way that avoids reverse causality): a child is much more likely to die between ages 1 and 5 if the mother became pregnant again before this index child’s first birthday (RR02.31, pB0.001).
+We also find significant negative effects of subsequent short
+interpregnancy intervals on child survival (and have investigated this
+in a way that avoids reverse causality): a child is much more likely to
+die between ages 1 and 5 if the mother became pregnant again before this
+index child’s first birthday (RR02.31, pB0.001).
 
@@
 
-This article assesses the strength of son preference in Vietnam, as reflected infertility behavior. It
+This article assesses the strength of son preference in Vietnam, as reflected in fertility behavior. It
 formulates and estimates a proportional hazards model applied to birth intervals, and a contraceptive
-prevalence model, using household survey datafrom 2,636 ever-married women aged 15-49 with at
+prevalence model, using household survey data from 2,636 ever-married women aged 15-49 with at
 least one living child who were interviewedfor the Vietnam Living Standards Survey 1992-1993.
@@
 
-This paper is the ﬁrst to show that morbidity and mortality among adult women in India can be partially explained by son preference.
-First, I show suggestive evidence that women with a ﬁrst-born girl have lower survival.
-Second, consistent with prior literature, I ﬁnd that having a ﬁrst-born girl leads to fertility behaviors medically known to hurt women’s survival.
-Third, I show new evidence of eﬀects of a ﬁrst-born girl on a mother’s likelihood and severity of anemia.
-These outcomes are severely aggravated with each successive female birth
+This paper is the ﬁrst to show that morbidity and mortality among adult
+women in India can be partially explained by son preference. First, I
+show suggestive evidence that women with a ﬁrst-born girl have lower
+survival. Second, consistent with prior literature, I ﬁnd that having a
+ﬁrst-born girl leads to fertility behaviors medically known to hurt
+women’s survival. Third, I show new evidence of eﬀects of a ﬁrst-born
+girl on a mother’s likelihood and severity of anemia. These outcomes are
+severely aggravated with each successive female birth
 
-I pool the three available rounds of the India National Family Health Survey (NFHS) conducted in 1992/93, 1998/99, 2005/06, and consider the cross-sectional sample of women ages 15 to 39.
+I pool the three available rounds of the India National Family Health
+Survey (NFHS) conducted in 1992/93, 1998/99, 2005/06, and consider the
+cross-sectional sample of women ages 15 to 39.
 
-I show nonparametric evidence that the share of living women whose ﬁrst birth is female is a decreasing function of their age (or, alternatively, of the number of years since ﬁrst birth).
-This decreasing pattern starts around age 24 and continues to decrease below the biological range, stabilizing for women in their mid-30s
+I show nonparametric evidence that the share of living women whose ﬁrst
+birth is female is a decreasing function of their age (or,
+alternatively, of the number of years since ﬁrst birth). This decreasing
+pattern starts around age 24 and continues to decrease below the
+biological range, stabilizing for women in their mid-30s
 
-Although indirect, this evidence is suggestive of lower survival among women with ﬁrst girls due, at least partly, to son preference.
+Although indirect, this evidence is suggestive of lower survival among
+women with ﬁrst girls due, at least partly, to son preference.
 
-I estimate the eﬀects of having a ﬁrst-born girl on several fertility-related outcomes, including the probability of desiring more children, being sterilized, having undergone ultrasound, having had a terminated pregnancy, short birth spacing, and the number of children ever born.
+I estimate the eﬀects of having a ﬁrst-born girl on several
+fertility-related outcomes, including the probability of desiring more
+children, being sterilized, having undergone ultrasound, having had a
+terminated pregnancy, short birth spacing, and the number of children
+ever born.
 
-I provide original evidence that women with ﬁrst-born girls are more likely to develop anemia.
-Speciﬁcally, a ﬁrst-born daughter increases the probability of being moderately or severely anemic by 5.4 percent.
-The additional eﬀect of a second and third-born girl (conditional on previous female births) is equivalent to 9 and 17.6 percent, respectively.
-Predetermined health or current pregnancy or breastfeeding status do not appear to drive these results.
+I provide original evidence that women with ﬁrst-born girls are more
+likely to develop anemia. Speciﬁcally, a ﬁrst-born daughter increases
+the probability of being moderately or severely anemic by 5.4 percent.
+The additional eﬀect of a second and third-born girl (conditional on
+previous female births) is equivalent to 9 and 17.6 percent,
+respectively. Predetermined health or current pregnancy or breastfeeding
+status do not appear to drive these results.
 

### 2019-02-20 paper/birth_spacing_lit.tex
Update spacing lit notes

@@
 Mechanisms: 
-- new pregnancy can lead to reduction is breastfeeding (reduced volume of breastmilk), which
-can be hazardous both nutritionally and in terms of resistance to infection.
-(lower breastfeeding -> less contraceptive effect -> shorter birth intervals)
+- new pregnancy can lead to reduction is breastfeeding (reduced volume
+of breastmilk), which
+can be hazardous both nutritionally and in terms of resistance to
+infection.
+(lower breastfeeding -> less contraceptive effect -> shorter birth
+intervals)
 
-- care of new infant affects prior child; might even happen before birth of new child
+- care of new infant affects prior child; might even happen before birth
+of new child
 
@@
 
-(no attempt to estimate what determines birth spacing, although do acknowledge that
+(no attempt to estimate what determines birth spacing, although do
+acknowledge that
 causality is difficult to establish)
@@
 
-we use dynamic panel data techniques to analyse the causal effects of infant mortality on birth intervals and fertility, as well as the causal effects of birth intervals on mortality in rural Bangladesh, accounting for unobserved heterogeneity and reverse causality
+we use dynamic panel data techniques to analyse the causal effects of
+infant mortality on birth intervals and fertility, as well as the causal
+effects of birth intervals on mortality in rural Bangladesh, accounting
+for unobserved heterogeneity and reverse causality
 
@@
 
-(!this is an important point. In the literature, the mortality effect discussed
+(!this is an important point. In the literature, the mortality effect
+discussed
 generally comes from the subsequent child, not the prior one. 
@@
 
-We find evidence of causal effects in two directions: a short preceding birth interval reduces survival chances of infants, and an infant death increases the probability of a next birth and shortens the time until the next birth (replacement behaviour)
+We find evidence of causal effects in two directions: a short preceding
+birth interval reduces survival chances of infants, and an infant death
+increases the probability of a next birth and shortens the time until
+the next birth (replacement behaviour)
 
-Estimates of reproductive behaviour are consistent with gender preference: having more surviving boys significantly reduces the probability of having a next child and this effect is strongest in the comparison area
+Estimates of reproductive behaviour are consistent with gender
+preference: having more surviving boys significantly reduces the
+probability of having a next child and this effect is strongest in the
+comparison area
 
@@
 
-I focus on ﬁrst-born children for whom the sex ratio of girls relative to boys is normal.
+I focus on ﬁrst-born children for whom the sex ratio of girls relative
+to boys is normal.
 
@@
 Using the NLSY79 and NLSY79 Child and Young Adult Surveys we investigate
+
 the effect of the age difference between between siblings (spacing) on
 educational achievement. Because spacing may be endogenous, we use an
-instrumental variables strategy that exploits variation in spacing driven
+instrumental variables strategy that exploits variation in spacing
+driven
 by miscarriages. The IV results indicate that a one-year increases in
@@
 The identification strategy exploits variation in spacing driven by 
-miscarriages that occur between two live births; there are several caveats to 
-consider when using this instrument, which will be discussed in detail in Section V. 
-We show that a miscarriage between siblings is associated with an increase in 
-spacing of about eight months, and decreases the likelihood that the siblings 
+miscarriages that occur between two live births; there are several
+caveats to 
+consider when using this instrument, which will be discussed in detail
+in Section V. 
+We show that a miscarriage between siblings is associated with an
+increase in 
+spacing of about eight months, and decreases the likelihood that the
+siblings 
 are less than two years apart by 19 percentage points.
 
-Among economists, Rosenzweig (1986) develops a model of optimal child spacing
-in which spacing is an input into child quality. An important feature of the model
-is that the endowments of older children affect the optimal timing of subsequent
+Among economists, Rosenzweig (1986) develops a model of optimal child
+spacing
+in which spacing is an input into child quality. An important feature of
+the model
+is that the endowments of older children affect the optimal timing of
+subsequent
 births.
-Rosenzweig, Mark R. 1986. "Birth Spacing and Sibling Inequality: Asymmetric Information
+Rosenzweig, Mark R. 1986. "Birth Spacing and Sibling Inequality:
+Asymmetric Information
 Within the Household. "International Economic Review 27(l):55-76.
 
-Heckman and Walker (1990) consider the effects of female labor market outcomes
-on fertility timing and birth spacing and found that higher female wages led to
-delayed childbearing and greater spacing between children. Troske and Voicu (2009)
-show that women who delay the birth of a second child reduce their labor force
-participation by less than women with closely spaced children, but are more likely
+Heckman and Walker (1990) consider the effects of female labor market
+outcomes
+on fertility timing and birth spacing and found that higher female wages
+led to
+delayed childbearing and greater spacing between children. Troske and
+Voicu (2009)
+show that women who delay the birth of a second child reduce their labor
+force
+participation by less than women with closely spaced children, but are
+more likely
 to work part-time.
 
-Estimates of average time to conception for women who conceived within one year of 
-a miscarriage range from 17.35 weeks (Goldstein, Croughan, and Robertson 2002) to 23.2
+Estimates of average time to conception for women who conceived within
+one year of 
+a miscarriage range from 17.35 weeks (Goldstein, Croughan, and Robertson
+2002) to 23.2
 weeks (Wyss, Biedermann, and Huch 1994).
@@
 breastfed less than boys.
-Third, by the same logic, children with older brothers are breastfed more.
+Third, by the same logic, children with older brothers are breastfed
+more.
 Fourth, the gender effect is largest when a couple approaches its target
@@
 are shorter if parents have not reached their self-reported ideal number
-of sons. Second, Nemeth and Bowling (1985) examine whether having no sons
+of sons. Second, Nemeth and Bowling (1985) examine whether having no
+sons
 shortens the duration of breastfeeding.
@@
 
-Many couples in India never use a reversible method to delay or space births, and in-
+Many couples in India never use a reversible method to delay or space
+births, and in-
 stead adopt sterilization as their first and only method.
 
-higher educational attainment (of either partner) independently increases the likelihood 
-that a couple will have used a method to delay or space births, as does middle 
+higher educational attainment (of either partner) independently
+increases the likelihood 
+that a couple will have used a method to delay or space births, as does
+middle 
 socioeconomic status.
@@
 
-This article assesses the strength of son preference in Vietnam, as reflected in fertility behavior. It
-formulates and estimates a proportional hazards model applied to birth intervals, and a contraceptive
-prevalence model, using household survey data from 2,636 ever-married women aged 15-49 with at
-least one living child who were interviewedfor the Vietnam Living Standards Survey 1992-1993.
+This article assesses the strength of son preference in Vietnam, as
+reflected in fertility behavior. It
+formulates and estimates a proportional hazards model applied to birth
+intervals, and a contraceptive
+prevalence model, using household survey data from 2,636 ever-married
+women aged 15-49 with at
+least one living child who were interviewedfor the Vietnam Living
+Standards Survey 1992-1993.
 
- Two tests are applied to the data in an attempt to discern the presence of son preference. The hazard
+ Two tests are applied to the data in an attempt to discern the presence
+of son preference. The hazard
 model test estimates the risk (hazard) of having another
-child at any point in time; if the hazard is lower for families with a son (or sons),
-the implication is that son preference is present. The contraceptive prevalence test
-determines whether families with a son (or sons) are significantly more likely to use
-contraceptives; if the answer is yer, a presumption may be made that son preference is present.
+child at any point in time; if the hazard is lower for families with a
+son (or sons),
+the implication is that son preference is present. The contraceptive
+prevalence test
+determines whether families with a son (or sons) are significantly more
+likely to use
+contraceptives; if the answer is yer, a presumption may be made that son
+preference is present.
 
@@
 
-We use an accelerated hazard model to estimate the duration between successive births and our results indicate that son preference exists only for the Indian community in South Africa.
+We use an accelerated hazard model to estimate the duration between
+successive births and our results indicate that son preference exists
+only for the Indian community in South Africa.
 
-Indian households are observed to have a higher duration between children following the birth of a son, irrespective of the number of children they already have.
-For the rest of the population, there is very little evidence of son preference.
+Indian households are observed to have a higher duration between
+children following the birth of a son, irrespective of the number of
+children they already have. For the rest of the population, there is
+very little evidence of son preference.
 
-For the Indian households, regardless of the number of existing sons, the duration is higher after a son.
-Additionally, an increase in the number of sons also significantly increases the duration between the second and the third children.
+For the Indian households, regardless of the number of existing sons,
+the duration is higher after a son. Additionally, an increase in the
+number of sons also significantly increases the duration between the
+second and the third children.
 
@@
 
-among earlier cohorts, women who are more educated tend to have shorter birth intervals than those who are less educated and that the opposite is true among later cohorts.
+among earlier cohorts, women who are more educated tend to have shorter
+birth intervals than those who are less educated and that the opposite
+is true among later cohorts.
 
-The empirical results based on the ﬁrst hypothesis show that the level of industrialization of the local economy does not have a differential effect on birth spacing across educational groups.
-However, empirical results using measures of the availability of a family planning program show a differential effect on delaying births across educational groups.
+The empirical results based on the ﬁrst hypothesis show that the level
+of industrialization of the local economy does not have a differential
+effect on birth spacing across educational groups. However, empirical
+results using measures of the availability of a family planning program
+show a differential effect on delaying births across educational groups.
 
-women’s education had an impact on the second birth interval mainly through changing the availability of contraceptives rather than through change in the demand for children over the period 1974–90.
+women’s education had an impact on the second birth interval mainly
+through changing the availability of contraceptives rather than through
+change in the demand for children over the period 1974–90.
 
-My ﬁndings are consistent with the hypothesis that more educated women are better at adopting new contraceptive technology.
+My ﬁndings are consistent with the hypothesis that more educated women
+are better at adopting new contraceptive technology.
 
@@
 Our findings suggest
-that a preference to balance the gender of children affects the timing of births, not a
-preference for either sons or daughters. At parity 2, women with children of the same
-sex time a third birth more rapidly than women with a boy and a girl. At parity 1,
-women with a boy time second births more rapidly than women with a girl. This
-seemingly anomalous finding is explained, however, by the fact that women with boys
-are more likely than women with girls to be married at any point in time and thus
+that a preference to balance the gender of children affects the timing
+of births, not a
+preference for either sons or daughters. At parity 2, women with
+children of the same
+sex time a third birth more rapidly than women with a boy and a girl. At
+parity 1,
+women with a boy time second births more rapidly than women with a girl.
+This
+seemingly anomalous finding is explained, however, by the fact that
+women with boys
+are more likely than women with girls to be married at any point in time
+and thus
 less likely to have disrupted fertility careers.
@@
 
-The southern Indian state of Tamil Nadu has experienced a dramatic decline in fertility, accompanied by a trend of increased son preference.
+The southern Indian state of Tamil Nadu has experienced a dramatic
+decline in fertility, accompanied by a trend of increased son
+preference.
 
-Findings suggest that daughter aversion, fuelled primarily by the perceived economic burden of daughters due to the proliferation of dowry, is playing a larger role in fertility decision-making than son preference.
-The desire for a son is often trumped by the worry over having many daughters.
-Women use various means of controlling the sex of their children, which in this study appear to be primarily female infanticide.
-It is important to distinguish between son preference and daughter aversion and to examine repercussions of low fertility within this setting.
+Findings suggest that daughter aversion, fuelled primarily by the
+perceived economic burden of daughters due to the proliferation of
+dowry, is playing a larger role in fertility decision-making than son
+preference. The desire for a son is often trumped by the worry over
+having many daughters. Women use various means of controlling the sex of
+their children, which in this study appear to be primarily female
+infanticide. It is important to distinguish between son preference and
+daughter aversion and to examine repercussions of low fertility within
+this setting.
 
-In the last decade, Tamil Nadu – along with its neighbouring southern states – has achieved very low fertility.
-In the year 2005–2006, the Total Fertility Rate (TFR, the average number of children born to a woman over her lifetime) was estimated at 1.80, down from a TFR of 4.97 in 1974 (Dyson and Moore 1983, Guilmoto and Rajan 2001, International Institute for Population Sciences and ORC Macro 2006).
+In the last decade, Tamil Nadu – along with its neighbouring southern
+states – has achieved very low fertility. In the year 2005–2006, the
+Total Fertility Rate (TFR, the average number of children born to a
+woman over her lifetime) was estimated at 1.80, down from a TFR of 4.97
+in 1974 (Dyson and Moore 1983, Guilmoto and Rajan 2001, International
+Institute for Population Sciences and ORC Macro 2006).
 
-This impressive decline in fertility has been accompanied by worrisome evidence of the emergence of son preference in the past decade, which is reflected in increasingly disproportional sex ratios at birth and younger ages (Das Gupta and Bhat 1997, Basu 1999, Srinivasan 2005).
+This impressive decline in fertility has been accompanied by worrisome
+evidence of the emergence of son preference in the past decade, which is
+reflected in increasingly disproportional sex ratios at birth and
+younger ages (Das Gupta and Bhat 1997, Basu 1999, Srinivasan 2005).
 
-If strong daughter aversion is a prime driver of fertility limitation, it may put downward pressure on population growth, possibly helping to explain the recent trend toward very low fertility rates in Tamil Nadu.
-Although the phenomenon of daughter aversion has received less attention than son preference, there are a few past studies on it, primarily in Northern India, some which suggest that it may differ by religious group (Khanna 1997, Borooah and Iyer 2004).
-Our work here supports the idea that daughter avoidance, often described inaccurately as son preference, is increasing in rural Tamil Nadu and suggests that economic constraints, primarily due to increased use of dowry, are the cause.
+If strong daughter aversion is a prime driver of fertility limitation,
+it may put downward pressure on population growth, possibly helping to
+explain the recent trend toward very low fertility rates in Tamil Nadu.
+Although the phenomenon of daughter aversion has received less attention
+than son preference, there are a few past studies on it, primarily in
+Northern India, some which suggest that it may differ by religious group
+(Khanna 1997, Borooah and Iyer 2004). Our work here supports the idea
+that daughter avoidance, often described inaccurately as son preference,
+is increasing in rural Tamil Nadu and suggests that economic
+constraints, primarily due to increased use of dowry, are the cause.
 
@@
 
-the analysis suggests that cultural factors may contribute more to explaining gender
-differences in mortality across India than does female labor force participation.
+the analysis suggests that cultural factors may contribute more to
+explaining gender
+differences in mortality across India than does female labor force
+participation.
 
-this analysis unequivocally suggests that excess fe-
-male mortality in India has both economic and
-cultural roots and any explanation must con-
-sider both economic and cultural factors.
+this analysis unequivocally suggests that excess female mortality in
+India has both 
+economic and cultural roots and any explanation must consider both
+economic and cultural 
+factors.
 
@@
 
-In this paper random-effects logistic models are used to analyze the effects of the
-preceding birth interval on postneonatal mortality in Brazil, controlling for the
-correlation of survival outcomes between siblings. The results are compared to those
-obtained by using ordinary logistic regression. Family effects are found to be highly
-significant in the random-effects model, but the substantive conclusions of the
-ordinary logistic model are preserved. In particular, birth interval effects remain
+In this paper random-effects logistic models are used to analyze the
+effects of the
+preceding birth interval on postneonatal mortality in Brazil,
+controlling for the
+correlation of survival outcomes between siblings. The results are
+compared to those
+obtained by using ordinary logistic regression. Family effects are found
+to be highly
+significant in the random-effects model, but the substantive conclusions
+of the
+ordinary logistic model are preserved. In particular, birth interval
+effects remain
 highly significant
 
-Birth interval effects are highly significant in Brazil, particularly in the less developed
-Northeast region. This point is important because short birth intervals are relatively common
+Birth interval effects are highly significant in Brazil, particularly in
+the less developed
+Northeast region. This point is important because short birth intervals
+are relatively common
 in Brazil, particularly in the Northeast.
@@
 
-We hypothesize that mothers in Matlab have a strong preference about the gender composition of their surviving children; in particular, they want several surviving sons and at least one surviving daughter.
+We hypothesize that mothers in Matlab have a strong preference about the
+gender composition of their surviving children; in particular, they want
+several surviving sons and at least one surviving daughter.
 
-the basic premise of this paper is that gender preference will have a greater influence on fertility where contraception is readily available and widely used; we expect to see little or no effect of gender preference on fertility in a population that does not use contraception.
+the basic premise of this paper is that gender preference will have a
+greater influence on fertility where contraception is readily available
+and widely used; we expect to see little or no effect of gender
+preference on fertility in a population that does not use contraception.
 
-In the earlier stages of family formation (i.e., in families with three or fewer surviving children), the number of surviving sons is a significant (negative) predictor of subsequent fertility.
-In the later stages (i.e., in families with four or more surviving children), the subsequent pace of reproduction is affected significantly not only by the number of sons but also by whether there is a son and by whether there is a daughter in the family.
-Our results show not only a very strong desire for sons, which is seen early in the family formation process, but also a desire for at least one daughter, which is seen at a more advanced stage.
+In the earlier stages of family formation (i.e., in families with three
+or fewer surviving children), the number of surviving sons is a
+significant (negative) predictor of subsequent fertility. In the later
+stages (i.e., in families with four or more surviving children), the
+subsequent pace of reproduction is affected significantly not only by
+the number of sons but also by whether there is a son and by whether
+there is a daughter in the family. Our results show not only a very
+strong desire for sons, which is seen early in the family formation
+process, but also a desire for at least one daughter, which is seen at a
+more advanced stage.
 
-The effect of gender composition of children is significantly stronger in the treatment area than in the comparison area.
-Moreover, whether the family has children of both genders seems to be more important in the treatment area than in the comparison area.
+The effect of gender composition of children is significantly stronger
+in the treatment area than in the comparison area. Moreover, whether the
+family has children of both genders seems to be more important in the
+treatment area than in the comparison area.
 
-These differentials in the impact of gender preference on fertility as a result of the availability and use of contraception imply strongly that gender preference effects become more important when contraception is readily availableand when a population is more able to control its fertility, other things being equal.
+These differentials in the impact of gender preference on fertility as a
+result of the availability and use of contraception imply strongly that
+gender preference effects become more important when contraception is
+readily availableand when a population is more able to control its
+fertility, other things being equal.
 
@@
 
-Examines preferred spacing as compared to observed spacing. In 5 of 20 countries the
-actual spacing is significantly longer than the preferred spacing.
+Examines preferred spacing as compared to observed spacing. In 5 of 20
+countries the
+actual spacing is significantly shorter than the preferred spacing.
 
@@
 
-Exploiting original data from a Senegalese household survey, we provide evidence that fertility choices are partly driven by women's needs for widowhood insurance.
-We use a duration model of birth intervals to show that women most at risk in case of widowhood intensify their fertility, shortening birth spacing, until they get a son.
-Insurance through sons might entail substantial health costs since short birth spacing raises maternal and infant mortality rates.
+Exploiting original data from a Senegalese household survey, we provide
+evidence that fertility choices are partly driven by women's needs for
+widowhood insurance. We use a duration model of birth intervals to show
+that women most at risk in case of widowhood intensify their fertility,
+shortening birth spacing, until they get a son. Insurance through sons
+might entail substantial health costs since short birth spacing raises
+maternal and infant mortality rates.
 
@@
 
-This paper’s contribution is to directly estimate the causal relationship between family size and the desired sex ratio and to quantify an important cause of rising sex ratios.
-The challenge in estimating this effect is to isolate exogenous variation in the fertility level.
-The approach I use is to elicit sex composition preferences at different fertility levels: a hypothetical fertility level is specified to the survey respondent, and she is asked, given that fertility level, what is her preferred composition of boys and
-girls. 5 By imposing the total number of children, one can characterize the respondents’ sex ratio preferences at different exogenously determined fertility levels.
+This paper’s contribution is to directly estimate the causal
+relationship between family size and the desired sex ratio and to
+quantify an important cause of rising sex ratios. The challenge in
+estimating this effect is to isolate exogenous variation in the
+fertility level. The approach I use is to elicit sex composition
+preferences at different fertility levels: a hypothetical fertility
+level is specified to the survey respondent, and she is asked, given
+that fertility level, what is her preferred composition of boys and
+girls. By imposing the total number of children, one can characterize
+the respondents’ sex ratio preferences at different exogenously
+determined fertility levels.
 
@@
 
-This article draws out some implications of son targeting fertility behavior and studies its determinants.
-We demonstrate that such behavior has two notable implications at the aggregate level: (a) girls have a larger number of siblings (sibling effect), and (b) girls are born at relatively earlier parities within families (birth-order effect).
-Empirically testing for these effects, we find that both are present in many countries in South Asia, Southeast Asia, and North Africa but are absent in the countries of sub-Saharan Africa.
-Using maximum likelihood estimation, we study the effect of covariates on son targeting fertility behavior in India, a country that displays significant sibling and birth-order effects.
-We find that income and geographic location of families significantly affect son targeting behavior.
+This article draws out some implications of son targeting fertility
+behavior and studies its determinants. We demonstrate that such behavior
+has two notable implications at the aggregate level: (a) girls have a
+larger number of siblings (sibling effect), and (b) girls are born at
+relatively earlier parities within families (birth-order effect).
+Empirically testing for these effects, we find that both are present in
+many countries in South Asia, Southeast Asia, and North Africa but are
+absent in the countries of sub-Saharan Africa. Using maximum likelihood
+estimation, we study the effect of covariates on son targeting fertility
+behavior in India, a country that displays significant sibling and
+birth-order effects. We find that income and geographic location of
+families significantly affect son targeting behavior.
 
@@
 
-Using data from nationally representative household surveys, we test whether Indian parents make trade-offs between the number of children and investments in education.
-To address the endogeneity due to the joint determination of quantity and quality of children, we instrument family size with the gender of the first child, which is plausibly random.
-Given a strong son preference in India, parents tend to have more children if the firstborn is a girl.
-Our instrumental variable results show that children from larger families have lower educational attainment and are less likely to be enrolled in school, with larger effects for rural, poorer, and low-caste families as well as for families with illiterate mothers.
+Using data from nationally representative household surveys, we test
+whether Indian parents make trade-offs between the number of children
+and investments in education. To address the endogeneity due to the
+joint determination of quantity and quality of children, we instrument
+family size with the gender of the first child, which is plausibly
+random. Given a strong son preference in India, parents tend to have
+more children if the firstborn is a girl. Our instrumental variable
+results show that children from larger families have lower educational
+attainment and are less likely to be enrolled in school, with larger
+effects for rural, poorer, and low-caste families as well as for
+families with illiterate mothers.
 
@@
 
-This hazard approach provides a natural way to model incomplete histories, nonoccurrence of the event (a subsequent birth) and a natural set of covariates (current period values).
-It, however, does not solve several other problems.
-First, it provides
-little insight into how to summarize the information in past and future covariates.
-Second, it does not solve the dynamic selection problem.
-To be in the sample of individuals on which we estimate the time between the first and second birth, one must have had a first birth.
-This is a selected sample.
-This simple hazard model provides no insight into the effects of that selection.
-Finally, this model has the unfortunate characteristic of mixing the parameters for the speed with which the event occurs with the parameters for whether or not the event occurs.
+This hazard approach provides a natural way to model incomplete
+histories, nonoccurrence of the event (a subsequent birth) and a natural
+set of covariates (current period values). It, however, does not solve
+several other problems. First, it provides
+little insight into how to summarize the information in past and future
+covariates. Second, it does not solve the dynamic selection problem. To
+be in the sample of individuals on which we estimate the time between
+the first and second birth, one must have had a first birth. This is a
+selected sample. This simple hazard model provides no insight into the
+effects of that selection. Finally, this model has the unfortunate
+characteristic of mixing the parameters for the speed with which the
+event occurs with the parameters for whether or not the event occurs.

### 2019-02-20 paper/sex_selection_spacing-ver2-new-intro.tex
Initial commit of files for rewrite of introduction

--- 2019-01-09 paper/sex_selection_spacing-ver2.tex
@@
 
-%------------------------------------------------------------------------------------
-
-\section{Estimation Strategy\label{sec:strategy}}
-
-% Requirements for method and the intuition behind each:  
-%  - Account for censoring (hazard model)
-%  - Work both with and without sex selection (competing risk part)
-%  - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
-%  - Capture that the shape of the hazard function differ across groups
-%    (non-proportionality); needs a better description, maybe using example
-%    of shorter spacing and/or use of sex selection. Differences in parity
-%    progression likelihood.
-
-The unit of analysis is a spell, the period from one birth---or for the first spell from 
-marriage---to the next birth.
-The model is a discrete time, non-proportional, competing risk hazard model with two exit 
-states: either a boy or a girl is born.
-The standard approach in the spacing literature is to use a single-exit model, but with
-access to sex selection the sex of the next child is not random and parents' choices 
-will impact the spacing to a girl or a boy differentially.%
-\footnote{
-\cite{Merli2000} used a discrete hazard model to examine whether 
-there were under-reporting of births in rural China, although they 
-estimated separate waiting time regressions for boys and girls.
-}
-Both the non-randomness and differential spacing can be captured with a competing risk set 
-up.
-
-I use a non-proportional hazard specification, which allows the shape of the hazard 
-functions to vary across groups, rather than the standard proportional hazard function 
-for three reasons.
-First, it is unlikely---even in the absence of prenatal sex determination---that the 
-effect of household characteristics such as the sex composition of previous births have 
-the same effect throughout the entire spell.%
-\footnote{
-Assuming that the effect of sex composition is the same throughout a spell is especially 
-problematic for higher-order spells where different sex composition of previous births can 
-lead to substantial differences both in the likelihood of progressing to the next birth and
-how soon couples want their next child if they are going to have one.
-}
-Second, the introduction of prenatal sex determination likely exacerbates any bias 
-from the proportionality assumption since sex-selective abortion use varies across groups,
-which affects birth spacing, and because a household's use of sex selection may vary 
-within a spell, which means that the effects of covariates vary within the spell as well.
-Finally, the use of a non-proportional specification mitigates any potential effects 
-of unobserved heterogeneity when used in conjunction with a flexible baseline hazard 
-\citep{Dolton1995}.
-
-For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
-the spell continues until time $t_i$, when either a birth occurs or the spell 
-is censored.%
-\footnote{
-The time of censoring is assumed independent of the hazard rate,
-as is standard in the literature.
-}
-There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
-$J_i$ is a random variable indicating which event took place.
-The discrete time hazard rate $h_{ijt}$ is specified as
-\begin{equation}
- h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
- {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
- \label{eq:hazard}
-\end{equation}
-where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
-individual, household, and community characteristics discussed below,
-and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
-by dummies and the associated coefficients,
-\begin{equation}
-D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
-\end{equation}
-with $D_m = 1$ if $t=m$ and zero otherwise.
-This approach to modeling the baseline hazard is flexible and does not place 
-overly strong restrictions on the baseline hazard.
-
-The explanatory variables in $\mathbf{Z}$ and the interactions between them 
-are the non-proportional part of the model, which means that they are
-interacted with the baseline hazard:
-\begin{equation}
- \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
-\end{equation}
-where $D_j(t)$ is the piece-wise linear baseline hazard and $\mathbf{Z}_1$ captures sex 
-composition of previous children, if any, and $Z_2$ captures area of residence.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
-but to further minimize any potential bias from assuming proportionality, estimations 
-are done separately for different levels of mothers' education and for different 
-time periods.
-
-Equation (\ref{eq:hazard}) is equivalent to the logistic hazard model and has the same 
-likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, transforming the data, so each observation is an interval---here equal
-to three months---the model can be estimated using a standard multinomial logit model.%
-\footnote{
-The multinomial model assumes that alternative exit states are stochastically independent
-(Independence of Irrelevant Alternatives or IIA), which rules out any individual-specific 
-unmeasured or unobservable factors that affect both the hazard of having a girl and the 
-hazard of having a boy.
-I, therefore, include a proxy for fecundity discussed in Section \ref{sec:data}.
-Also, the multivariate probit model can be used as an alternative because the IIA is not 
-imposed \citep{han90}.
-The results are substantially identical between these two models and
-available upon request.
-}
-In the reorganized data the outcome variable is 0 if the woman does not have a child in a 
-given interval (the base outcome), 1 if she gives birth to a son in that interval, and 2 
-if she gives birth to a daughter in that interval.
-
-The distribution of spacing is captured by the survival curve, which shows the probability 
-of not having had a birth yet by spell duration, for a given set of explanatory variables.
-The survival curve at time $t$ is 
-\begin{equation}
-\label{eq:survival}
-S_{t} 
-= 
-\prod_{d=1}^t
-\left(
-\frac{ 1 }
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
-\right).
-\end{equation}
-
-Because the probability of ever having a next birth likely varies across groups, a direct 
-comparison of standard survival curves tells us little about how the spread of sex selection 
-affects birth spacing across groups.
-I, therefore, condition on the predicted likelihood of parity progression when examining 
-birth spacing measures, such as the median duration to a birth.
-The reliability of this approach depends on whether the spell length covered is 
-sufficiently long that few women are likely to give birth after the spell cut-off.
-I discuss the choice of spell length below.%
-\footnote{
-It is important to note that the approach is not the same as merely calculating 
-the birth spacing measures for women who already have a given 
-parity child in the survey because that number does not take into account
-the censoring of spells that will eventually lead to a birth.
-}
-In addition, I also present graphs of both standard survival curves and
-survival curves conditional on parity progression (which therefore
-begin at 100\% and end at 0\%).
-
-Interpretation of the model coefficients is challenging \citep{thomas96}.
-It is, however, possible to calculate the predicted probabilities of 
-having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
-a set of explanatory variables and not having had a child before that period, as
-\begin{align}
-P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
-& =  
-\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
-{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
-\label{eq:probability_boy} \\
-P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
-& =  
-\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
-\label{eq:probability_girl}
-\end{align}
-It is then straightforward to calculate the estimated percentage of children born that 
-are boys, $\hat{Y}$, at each $t$:  
-\begin{equation}
-\hat{Y}_t 
-= 
-\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-\times 100.
-\label{eq:probability_son}
-\end{equation}
-Combining the percentage boys and the likelihood of exiting the spell 
-across all $t$ gives the predicted percent boys born over the entire spell.
-In addition to the predicted percent boys over the entire spell, 
-I also present graphs of how the percentage boys born vary across time
-within a spell, together with the associated confidence interval for given 
-values of explanatory variables calculated using the Delta method.
-
-\section{Data\label{sec:data}}
-
-The data come from the four rounds of the National Family Health Survey 
-(NFHS-1, NFHS-2, NFHS-3, and NFHS-4),
-collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.%
-\footnote{
-A delay in the survey for Tripura means that NFHS-2 has some observation 
-collected in 2000.
-}
-The surveys are large: NFHS-1 covered 89,777 ever-married women 
-aged 13--49 from 88,562 households;
-NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households;
-NFHS-3 covered 124,385 never-married and ever-married women aged 
-15--49 from 109,041 households;
-and 
-NFHS-4 covered 699,686 never-married and ever-married women aged
-15--49 from 601,509 households surveyed.
-
-I exclude visitors to the household, as well as
-women who have been married more than once, divorced, or who are 
-not living with their husband,
-women with inconsistent age at marriage,
-and those with missing information on education.
-Women interviewed in NFHS-3 or NFHS-4 who were never married or where Gauna 
-had not yet been performed were also dropped.
-The same goes for women who had at least one multiple births,
-reported having a birth before age 12, had a birth before marriage, or
-duration between births of less than nine months.
-Women who reported less than nine months between marriage and first birth
-remain in the sample---unless they are dropped for another reason---because 
-8.5\% fall into this category across the four surveys.
-Although it is possible that some of these births are premature, the high number of
-women who report a birth less than six months after their marriage indicates that for
-a majority conception likely occurred before marriage.
-
-Finally, I restrict the sample to Hindus,
-who constitute about 80\% of India's population.
-If the use of sex selection differ between Hindu and other religions, such 
-as Sikhs, assuming that the baseline hazard is the same would lead to bias.
-The other groups are each so small relative to Hindus that it is not
-possible to estimate different baseline hazards for each group.
-Furthermore, the other groups are so different in background and son 
-preference that combining them into one group would not make sense.
-
-There are four advantages to using the NFHS.
-First, surveys enumerators pay careful attention to spacing between births and
-probe for ``missed'' births.
-Second, no other surveys cover as extended a period in the same amount of detail.
-The four NFHS rounds allow me to show how spacing and 
-sex ratio changed from before sex-selective abortions were available until 2016.
-Third, NFHS has birth histories for a large number of women.
-% %
-% \footnote{
-% The Special Fertility and Mortality Survey appears to cover a much large number of households
-% than the three rounds of the NFHS combined, but \citet{jha06} only use the births that 
-% took place in 1997 making their sample sizes by parity smaller than here.
-% Their sample consists of 133,738 births of which 38,177 were first-born, 
-% 36,241 second-born, and 23,756 were third-born.
-% }
-Finally, even if probing for missing births does not eliminate recall error,   
-the overlap in cohorts covered and the large sample size makes it possible 
-to establish where recall error remains a problem.
-
-Recall error arises mainly from child mortality when respondents are 
-reluctant to discuss deceased children.
-Systematic recall error, where the likelihood of reporting a deceased 
-child depends on the sex of the child, is especially problematic because 
-it biases both spacing and sex ratios.
-Probing catches many missed births, but systematic recall error is 
-still a potentially substantial problem.
-
-Three factors contribute to the problem here.
-First, girls have significantly higher mortality risk than boys.
-Second, son preference may increase the probability that parents recall boys 
-more readily than girls.
-Finally, in NFHS-1 and NFHS-2 enumerators probed only for a missed birth if the
-initially reported birth interval was four calendar years or more,
-but, given short durations between births, especially after the birth of a girl,
-that procedure is unlikely to pick up all missed children.
-
-Recall error is heavily dependent on how long ago a woman was married 
-\citep{Portner2018b}.
-I, therefore, drop women married 22 years or more 
-for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
-and 25 years for NFHS-3 and NFHS-4.
-The final sample consists of 
-\input{../tables/num_women.tex}
-% [number] women, with [number] parity one through four births.
-
-\subsection{Spell Definition\label{sec:spell_def}}
-
-As mentioned above, 8.5\% of women gave birth less than nine months
-after they were married, and the first spell, therefore, begins at the 
-month of marriage.
-The exception is for women married very young, where I use the month they 
-turned 12.
-The second and subsequent spells begin nine months after the previous birth 
-because that is the earliest we should expect to observe a new birth.
-A few women report births that occurred less than nine months 
-after the previous birth; I drop those women from the sample as mentioned above.
-
-All spells continue until either a child is born or censoring occurs.
-Censoring can happen for three reasons:
-the survey takes place;
-sterilization of the woman or her husband;
-or too few births are observed for the method to work.
-For the first spell I set censoring because of too few births to 108 months 
-(nine years) after marriage,
-while for the second, third, and fourth spells censoring is at 96 months 
-(eight years) after a birth can occur.
-With these cut-offs, less than one percent of observed births occur after
-the spell cut-off.%
-\footnote{
-\input{../tables/num_missed.tex}
-Recall also that these numbers are totals across all 36 separate regressions.
-}
-
-I group spells into four periods based on the year of marriage
-or year of the previous birth:
-1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The periods follow the main changes in availability and legality of 
-prenatal sex determination discussed in the Introduction.
-The allocation into periods is determined by when conception and therefore 
-decisions on sex selection can begin, even if we do not observe
-any births until nine months later.
-
-The allocation into periods means that some spells cover two periods.
-A couple may, for example, be married in 1984, but not have their first 
-child until 1986.
-That couple's first spell will be in the 1972--1984 period, even though 
-most of the interval falls in the 1985--1994 period.
-Hence, prenatal sex determination was likely available when some
-children from spells that began in the 1972--1984 period were conceived,
-which could result in evidence of sex-selective abortions even for this
-period.
-Similarly, a spell that started in the 1985--1994 period may have been partly 
-or mostly under the PDNT act.
-The effect is a downward bias in the differences between the periods.
-
-\subsection{Explanatory Variables}
-
-I divide the explanatory variables into two groups.
-The first group consists of variables expected to affect the shape of the hazard function
-(the $\mathbf{Z}$ variables): 
-mother's education, sex composition of previous children, and area of residence.
-I chose these variables because the prior literature shows that they affect 
-spacing choices and correlate with sex selection.
-Increasing the number of variables interacted with the baseline hazard would
-further lower the risk of bias but at the cost of requiring more data to 
-precisely estimate.
-
-I divide women into three groups based on education attainment: no
-education, one to seven years of education, and eight and more years of education.
-The models are estimated separately for each education level to reduce
-the potential problem of including other variables as proportional.
-Increasing education of mothers correlates closely with lower fertility 
-\citep{schultz97}, and 
-we should expect lower fertility to lead to more use of sex selection.%
-\footnote{
-Fathers' education has two opposite predicted effects: the associated higher income
-should increase fertility and therefore lower the pressure to use sex selection, but
-the higher income also makes the use of sex selection cheaper.
-In practice, fathers' education had little effect on the hazards and the use of 
-sex-selective abortions, and I, therefore, do not include it.
-}
-
-I capture sex composition with dummy variables for the
-possible combinations for the specific spell, ignoring the ordering of births.
-As an example, for the third spell, three groups are used: Two boys,
-one girl and one boy, and two girls.
-It is, in principle, possible to estimate the model taking into account
-the ordering of children, but this would further lower the power of the
-test, by adding one additional group for the third spell and four
-additional groups for the fourth spell. 
-As discussed, the sex composition of previous children affects both the timing
-of births and the use of sex-selective abortions.
-
-Area of residence is a dummy variable for the household living in
-an urban area.
-The cost of children is higher in urban areas than in rural areas, and 
-there is easier access to prenatal sex determination in urban areas.
-Both factors are likely to lead to higher use of sex-selective abortions
-in urban than in rural areas.
-
-The second group of variables consists of those expected to have an 
-approximately proportional effect on the hazard.
-These include the length of the first spell 
-(for the second and higher-order spells to capture fecundity), 
-the age of the mother at the beginning of the spell, 
-whether the household owns any land, 
-and whether the household belongs to a scheduled tribe or caste.
-We cannot observe fecundity directly, but the time from marriage until 
-first birth is a suitable proxy because most Indian women do not use 
-contraception before the first birth and there is pressure to show that 
-a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
-The absence of contraception before the first birth is confirmed below by the 
-very short spells between marriage and first birth, even among the most educated.
-Hence, a long spell between marriage and first birth is likely due to low fecundity.
-For both duration from marriage to first birth and the age of the mother at the 
-beginning of the spell, I also include their squares.
-The remaining variables are dummies for household ownership of land and membership
-of a scheduled caste or tribe.
-
-\subsection{Descriptive Statistics}
-
-Appendix Table \ref{tab:des_stat1} presents descriptive statistics for
-the spells by education level and period they began.
-There is a substantial number of censored observations.
-As an example, for highly educated women who had their first child in the 2005--2016
-period, more than 40\% did not have their second child by the time of the survey.
-Censoring becomes even more important for the third and fourth
-spells, with around 70\% of the observations censored.
-The level of censoring also increases with parity and time,
-which reflects a combination of factors: timing of the surveys
-relative to the periods of interest, later beginning of childbearing, 
-falling fertility, and the increase in spell lengths from 
-sex-selective abortions.
-
-The share of urban women in the sample has fallen slightly over the
-periods, even though India's population has become progressively more urbanized.
-For the first and second periods, over 32\% of the women 
-entering the first spell lived in urban areas, falling to 
-30\% for the third period and 26\% in the last period.
-The most likely explanation is that the age of marriage has increased
-faster in urban areas than in rural areas.
-Hence, there are relatively more urban women, but fewer show up in the
-sample because they are not yet married.
-
-The population has become substantially better educated over time.
-Women with no education constituted almost 60\% 
-in the first period, but less than twenty percent in the last period.
-Correspondingly, in the first period just over twenty percent had eight or more 
-years of education, whereas in the last period more than 60\% did.
-These changes are an underestimate of the increase in female
-education overall because many of the younger women with more education
-have not yet married than therefore are not in the sample.%
-\footnote{
-Women with eight or more years of education accounted for 65.9\% of
-unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4.
-See \citet[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
-and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
-for more information.
- }
-
-Age at marriage increased over time across all three education groups.
-The most substantial increase was for women without any education, where
-the average went from below 16 years of age to 18.5.
-The smallest change is for the most educated women where the average age
-at marriage went up by less than a year---from 19.6 to 20.4---across the 
-four periods.
-
-\section{Results\label{sec:results}}
-
-% [Hypotheses / questions]
-
-The overall hypothesis is that spacing patterns significantly changed 
-as prenatal sex determination became available.
-To address this, I examine three questions in order of importance.
-
-First, did the spacing after girls increase relative to the spacing
-after boys?
-The underlying hypothesis is that in the absence of sex selection son 
-preference leads to shorter spacing after the birth of a girl than after the 
-birth of a boy, whereas son preference increases the spacing after the birth 
-of a girl relative to after the birth of a boy when prenatal sex selection is 
-available.
-I still expect parents to \emph{try} to conceive earlier after the birth 
-of a girl than after a boy, but the abortions will increase the 
-duration between births, and may even lead to longer spacing after the
-birth of girls than after boys.
-
-Second, have the shapes of the survival curves changed?
-The shapes of the survival curves provide information both on general
-changes in birth spacing and whether parents are
-still trying to conceive earlier after girls than boys.
-I expect this to be the case if there is still a strong preference for
-boys, and, as discussed above, this behavior may even become more pronounced
-with access to sex selection.
-
-Finally, does the sex ratio change within a spell?
-There are two reasons why this is interesting.
-First, if the sex ratio changes within a spell, relying on the observed sex
-ratio at birth---as is standard practice in the literature---will not provide
-correct estimates of the use of sex selection or the sex ratio at
-the conclusion of childbearing.
-Second, any changes in the sex ratio within a spell provides clues
-to parents' preferences over the ideal spacing between births and the
-distribution of son preference in the sample.
-
-% [How to read tables]
-Tables \ref{tab:median_sex_ratio_low}, \ref{tab:median_sex_ratio_med}, and
-\ref{tab:median_sex_ratio_high}
-show the predicted median duration and sex ratios by period, spell, and sex 
-composition for the three education levels separated by area of residence.%
-\footnote{
-Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
-\ref{tab:p25_p75_high} show 25th and 75th percentiles durations.
-} 
-For each subsample, I first estimate the model described in Section 
-\ref{sec:strategy} and then use the estimated coefficients to predict 
-median duration and sex ratio.
-For the standard errors, I use bootstrapping for both measures,
-where the model is repeatedly estimated using resampling with replacement.
-
-The predicted median duration is the weighted average over the women in the 
-subsample, using the individual probabilities of giving birth as weights.
-For each woman in a sample, I calculate her probability of ending the spell 
-with a birth, and her contribution to median spacing is how long it will take
-from the beginning of the spell to where she is predicted to reach half of that probability.
-For example, if a woman has an 80\% probability of having a birth by the end of 
-the spell, her median duration is the number of months it takes to reach
-40\% probability of having exited with a birth.
-The 40\% is equivalent to the 60\% point on a standard survival curve because that 
-captures how many have not yet exited.
-
-For the second through the fourth spell, I show whether durations for sex 
-composition other than only girls are statistically significantly different 
-from the duration with only girls.
-To calculate the level of statistical significance, I bootstrap the
-difference in spacing.
-
-The cleanest test is comparing durations after only boys with durations after
-only girls, but the number of births to women with only sons becomes small 
-in the later periods.
-Hence, it is possible to have substantial differences in spacing that are
-not statistically significant because of low power, especially for the third 
-and fourth spell.
-
-The predicted sex ratio is the weighted average over the women in the sample's 
-individual predicted sex ratios, using the individual probabilities of having
-given birth by the end of the spell as weights.
-Each woman's predicted sex ratio is the weighted average of the predicted
-percentage boys over the months in the spell calculated using equation 
-(\ref{eq:probability_son}) and the probability of giving birth in each month 
-as weights.%
-\footnote{
-Imagine a spell has two periods and that the estimated percentage boys for a
-woman are 54\% and 66\% and that the likelihood of having a birth is 20\% and 40\%.
-The likelihood of having a birth is the change in the survival curve; 
-in other words, there is 40\% chance that she will not have given birth by the end of 
-this spell.
-This woman's percentage boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
-}
-The predicted sex ratio captures the percent boys that will have been born to women 
-in the sample when childbearing for that spell is over.
-
-Each predicted percent boys is tested against the natural percentage 
-boys using the bootstrapped standard errors.
-The natural sex ratio is approximately 105 boys to 100 girls or
-51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
-The predicted percentage boys may differ from the natural rate because of 
-natural variation, any remaining recall error not corrected for, or 
-sex selection.
-
-\subsection{No Education Women}
-
-\input{../tables/bootstrap_duration_sex_ratio_low.tex}
-
-Women with no education follow a pattern consistent with son
-preference with shorter spacing when they have only girls compared 
-to when they have one or more sons, and the differences are often 
-statistically significant as shown in Table \ref{tab:median_sex_ratio_low}.
-Most of the women without education live in rural areas,
-whereas there are relatively few urban women with no education.
-There are especially very few urban women to based the third
-and fourth spell results on, and I therefore focus on rural women.
-
-Predicted median duration has increased over time within
-each sex composition.
-The exception is for the first spell, where there is little
-change, and possibly even a small decline.
-
-The differences in duration across sex compositions increase with 
-spell number.
-For the second spell, the difference in median duration between
-having a girl or a boy as the first-born are mostly between a half
-and one month.
-For the third spell, the difference in duration between only girls 
-and only boys is, on average, slightly over one month and statistically 
-significant in all periods.
-The differences for the fourth spell are between two and three months, 
-except for the 1972--1984 period, which is also the only period where 
-the difference is not statistically significant.
-
-There are no clear time trends in the differences in median duration
-across sex compositions or the predicted sex ratios across the four periods.
-Despite that some sex ratios are statistically significantly higher 
-than the natural sex ratio there is therefore little consistent evidence 
-for the use of sex selection for women without education.
-There has, for example, been relatively little change in the length
-of spacing for rural women with two girls in the third spell and 
-the predicted sex ratio was higher in the 1985--1994 period
-than in the 2005--2016 period.
-The possible exception is the fourth spell, where both duration 
-and sex ratio has increased for women with three girls, although
-the \emph{difference} across sex compositions has remained almost
-the same.
-
-\subsection{Middle Education Women}
-
-\input{../tables/bootstrap_duration_sex_ratio_med.tex}
-
-Women with one to seven years of education follow a pattern
-broadly similar to those with no education as 
-Table \ref{tab:median_sex_ratio_med} shows.
-The sample size is more evenly distributed across urban and rural 
-for this education group than for the no education women.
-As a result, the only spells where there are few women to base 
-results on are for the fourth spell for urban women and the first 
-period of the fourth spell for rural women.
-
-The spacing between births increased over the four decades.
-On average, the increase is approximately three to four months.
-The exception is again the first spell, where the time from
-marriage to first birth remained the same or fell slightly.
-
-In the period before sex selection became available, 1972--1985,
-the differences in spacing between only girls and only boys
-increase with between the second and third spell.
-For both urban and rural women, the difference in duration is just over
-a month for the second spell, but it is 1.4 and 2.8 months for urban and
-rural women, respectively, for the third spell.
-In the three later periods, there is no clear pattern
-in the differences across sex compositions.
-
-The differences in duration between only girls and only boys 
-appear to decrease over time.
-The exception is for the two later periods where the
-differences are slightly larger in the last period compared
-with the second-to-last period.
-
-The decreases in differences are accompanied by increases
-in predicted sex ratios, some of which are statistically 
-significantly different from the natural sex ratio.
-Hence, even though the evidence is not substantial, it does
-appear that women with one to seven years of education 
-have begun to use sex selection at higher-order spells.
-
-\subsection{High Education Women}
-
-\input{../tables/bootstrap_duration_sex_ratio_high.tex}
-
-Women with eight or more year of education mostly followed 
-the traditional spacing pattern before sex selection became 
-available as shown in Table \ref{tab:median_sex_ratio_high}.
-Compared to the two other education groups there are,
-however, more situations where the pattern is less clear.
-Part of the problem may be that there are few women in
-this group for the 1972--1984 period, and, hence, only 
-the results for the first and second spells in both urban 
-and rural areas are likely reliable.
-
-Birth spacing increases substantially over time, 
-especially for urban women. 
-The median duration for urban women increases between a half
-and a full year, whereas the increase for rural women 
-is between a quarter and half a year.
-The spacing between marriage and the first birth is still the
-exception, and for this group of women, there is a decline of
-about a month for both urban and rural areas.
-
-In urban areas, the increase in spacing with only girls is so 
-substantial that women with only girls have longer spacing to the 
-next birth than any of the other sex compositions from 1985 onward.%
-\footnote{
-The exception is the second spell for the 1985--1994 period, where women
-with one girl have 0.1 months shorter spacing the women with one boy.
-}
-This reversal in the standard spacing pattern is substantial, 
-especially for the third and fourth spells.
-For the latest period, the difference between only girls than the
-other sex compositions is between 4.8 and 9.1 months for the third
-and fourth spell.
-Furthermore, the differences are statistically significant, except
-for only boys for the fourth spell because few women have a fourth
-birth if they have three boys already.
-
-Rural women also show a reversal of the typical spacing pattern,
-although the changes are less pronounced than for urban women.
-The third spell shows that spacing for women with only girls become
-increasing longer compared to the other two sex compositions.
-Most of the differences are statistically significant, although they are 
-smaller than for urban women.
-For the second spell, there is little difference in spacing for
-women with one girl and women with one boy.
-
-The predicted sex ratios at the end of the spells show that
-the reversal in spacing patterns is not the result of a declining son
-preference but instead corresponds to a substantially more male-biased 
-sex ratio.
-For urban women, the predicted sex ratio with only girls 
-is consistently above 60\% boys for the third and fourth spells.
-For rural women, the predicted sex ratios are lower than for urban
-women but still substantial and statistically significant at close 
-to 60\%.
-The high predicted sex ratios are presumably the result of increased 
-use of sex selection.
-
-When trying to understand the strength of son preference, it is interesting
-that the sex ratio is also statistically significantly different
-from the natural rate in the case where women already have one
-son for the third and fourth spells.
-Again, the sex ratio in the presence of one son for the third and
-fourth spells are higher in urban areas than rural areas, although
-the difference is less than for women with only girls.
-Hence, it is possible that women are still willing to use sex selection
-even after giving birth to one, although this behavior may also 
-be in response to either experienced
-or expected mortality of the first son born.
-
-It also appears that there is a slightly elevated sex ratio among 
-first-born for urban women. 
-There is, however, no corresponding increase in spacing; instead,
-the median duration has fallen over time and is the lowest among
-the three education groups.
-Hence, unless duration between marriage and first birth has decreased 
-substantially by itself, for example, because of improved health, it
-is not clear how much stock to place on the increased sex ratio
-among first-borns as evidence for sex selection among first-borns.
-
-Both of the last two results are different from prior studies using NFHS data.
-There are two potential explanations.
-First, the NFHS-4 is substantially larger than the three prior surveys.
-Hence, it is possible that the effects have been there all along, but 
-we did not have the power to detect them.
-Second, it is possible that at least the first-born results are an
-artifact of any recall error not captured by the data restrictions.
-Certain types of recall error would also explain why the sex ratio for
-the second spell and one boy is statistically significantly \emph{below} 
-the natural sex ratio \citep{Portner2018b}.
-
-\subsection{Distribution of Birth Spacing Across Sex Compositions and Time}
-
-Median spacing is a convenient way to understand the overall changes but
-may hide important differences in the distribution of spacing.
-This section, therefore, provides more detail on how spacing is distributed
-over time and sex compositions using a graphical approach.
-
-I show survival curves conditional on predicted parity progression rather than
-standard survival curves. 
-The advantage of this approach is that it is possible to directly compare 
-the distribution of spacing to next birth across groups, independently of 
-differences in how likely the next birth is.
-Because the conditional survival curves are independent of the likelihood
-of final parity progression, they all begin at 100\% and end at 0\%.
-
-Instead of averaging across the entire sample, I calculate the conditional
-survival curves for an average woman using the method detailed in 
-Section \ref{sec:strategy}.
-For each combination of education and spell, I use values based on the
-average age at the start of the spell and, for the second and higher
-spells, the average duration of the first spell.
-Furthermore, I use the majority categories for the categorical explanatory 
-variables, which means no ownership of land and not in a scheduled caste or 
-tribe.
-The characteristics used do not change across period to ensure that 
-composition effects do not drive the changes.
-
-In the interest of brevity, I discuss only a select set of subsamples.
-Figure \ref{fig:pps_spell1} shows spacing for the first spell across the
-four periods for rural women with no education and urban women with 
-eight or more years of education.
-Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex
-compositions for the second, third, and fourth spells for the first period, 
-1972--1984, and the last period, 2005--2016, for rural women with no 
-education and for urban women with eight or more years of education.
-The Appendix shows standard and conditional survival curves for all groups and 
-time periods, and I discuss some examples of standard survival
-curves in the following section.%
-\footnote{
-To ease legibility of the graphs some three months intervals are combined
-into longer ones when there are few births available in the sample.
-}
-
-% First spell for low and high education women
-
-\begin{figure}[htpb]
-\centering
-\setcounter{subfigure}{-1}
-\subfloat[Rural Women with No Education]{
-    \begin{minipage}{0.48\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Urban Women with 8 or More Years of Education]{
-    \begin{minipage}{0.48\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{
-Survival curves conditional on progression to first birth; start point is month of marriage
-}
-\label{fig:pps_spell1}
-\end{figure}
-
-The biased sex ratio for the first spell for the most educated 
-women suggests that there might be sex selection on the first birth.
-I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
-of spacing has changed over time for rural women with no education and urban women 
-with eight or more years of education.
-What is most striking is how similar the distribution of spacing is across the
-two groups.
-
-Both groups show little change in median spacing, but that masks a substantial
-compression of when most of the births occur.
-In the 1972--1984 period, the middle 80\% of births for women with no education 
-are predicted to occur between approximately 6 and 64 months, whereas in the 
-2005--2016 period it is between 12 and 54 months.
-Hence, the compression is equivalent to more than a full year.
-Women with eight or more years of education show a slightly smaller compression:
-in the 1972--1984 period, the middle 80\% of births are predicted to occur between
-approximately 6 and 48 months, whereas in the 2005--2016 period it is between
-12 and 46 months.
-Hence, the compression is eight months.
-
-Women became less likely to conceive before marriage over time.
-In the first two periods there was a relatively smooth decline in the number of
-women without a birth starting at the time of marriage, but in the last two
-periods, there are few women who exit early after marriage and
-instead there is a substantial dip between 9 and 12 months after
-marriage.
-
-It is likely that the compressed spacing, beginning at nine months
-after marriage in the later periods, is associated with better health
-and higher age at marriage.
-For example, women without education have seen an increase in the average 
-age at marriage from below 16 to 18.5 from the first period to the last 
-while women with the most education increased from 19.5 to 20.4.
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{
-Survival curves conditional on progression to next birth for rural women without
-education; start point for each spell is nine months after prior birth
-}
-\label{fig:pps_low}
-\end{figure}
-
-For women with no education, Figure \ref{fig:pps_low} shows that the median results
-above are consistent with the distribution of spacing within a spell with spacing 
-after only girls consistently shorter than after only boys.
-There are slight variations in how strong this effect is across the three spells.
-On the one hand, for the second spell the difference in spacing between
-when the first child is a girl versus when the first child is a boy as
-first-born remains almost the same across the four decades.
-On the other hand, for the third spell the differences between two girls and 
-the other sex compositions become more pronounced over time, and especially
-the difference between two girls and two boys have become substantially larger.
-The fourth spell results are based on relatively few observations but do
-indicate that women with either only girls or two girls and one boy have
-shorter spacing than women with only boys or one girl and two boys.
-Although the evidence is not substantial, it does appear that there is a slight
-preference for two boys in the sense that spacing becomes longer once the couple
-has at least two boys than for the other sex compositions.
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{
-Survival curves conditional on progression to next birth for urban women with eight or
-more years of education; start point is nine months after prior birth
-}
-\label{fig:pps_high}
-\end{figure}
-
-The distribution of spacing for the second spell is almost indistinguishable 
-between urban women with eight or more years of education and rural women 
-with no education for the 1972--1984 period, as shown in Figure \ref{fig:pps_high}.
-The small difference points to these two very different groups of women behaving similarly
-in response to son preference in a situation where there was little access to
-prenatal sex determination or little incentive to use it early even for those 
-who might have had access.
-
-Whereas the no education group show almost no change across the four decades,
-the high education women show a rightward shift if the spacing pattern when
-the first child is a girl.
-The result is that the spacing patterns are close to identical after first-born 
-girls and after first-born boys.
-Given the elevated predicted percentage boys in Table \ref{tab:median_sex_ratio_high},
-this change is consistent with the use of sex selection for women with a girl 
-as their first child.
-
-The hypothesized correlation between use of sex selection and reversal of 
-the standard spacing pattern show up clearly in the 2005--2016 period for the 
-third spell with spacing to the third child consistently longer with two girls 
-than with either two girls or one boy and one girl.
-The rightward movement for only girls from the, mostly, standard pattern in 
-the 1972--1984 period to the new pattern in the 2005--2016 period is substantial.
-There are also indications that the spacing distribution has moved rightward
-for women with one boy and one girl relatively to women with two boys, which
-provides some evidence for the use of sex selection for this group.
-The caveat is that the 1972--1985 period also had a biased sex ratio, which
-points to uncorrected recall error for this group.
-
-There is an even more pronounced rightward shift for spacing after only
-girls in the fourth spell for the first years of the spell. 
-The caveat is that there are few births to base the results on,
-especially for women with two or more sons.%
-\footnote{
-As mentioned, it is possible that some women had access to sex selection even
-in the first period.
-I would expect well educated urban women with more children to be the
-most likely to know about and use this early access to prenatal sex determination.
-}
-Furthermore, the differences are substantial across most of the distribution.
-Twelve months after the beginning of the spell there is a more than ten 
-percentage points difference in the conditional survival curves for only girls
-and only boys.
-That is, of the women who are predicted to have a fourth child just over 30\%
-of women with three boys have had their fourth child, while less than 20\% of
-those with three girls have had theirs.
-Even at three years after the beginning of the spell, there is a more than 
-five percentage points difference.
-
-As discussed above there is some evidence of a two-son preference with
-the spacing pattern almost the same for women with three boys and with
-two boys and one girl.
-The conditional survival curve for women with one boy and two girls is
-consistently above those for women with two or more son, but below those 
-with three girls.
-The pattern fit the predicted sex ratios shown above where the highest
-predicted sex ratio is for women with only girls, followed by those
-with one son and two girls, and those with two or more boys having
-almost the same sex ratio.
-
-\subsection{Does Sex Selection Change within Spells?}
-
-The above results show that length of birth spacing increased 
-more for women with only girls than for other sex compositions
-as sex ratios became more male-biased, presumably because
-of increased use of sex selection.
-Neither the median spacing or the conditional survival curves,
-however, can tell us whether sex selection varies \emph{within}
-a spell or provide any information about the likelihood of
-exiting a spell with a birth.
-To understand both, I now turn to the standard survival curves
-and predicted sex ratios by spell duration.
-
-\begin{figure}[htpb!]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Urban}}
-\setcounter{subfigure}{-2}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Rural}}
-\setcounter{subfigure}{0}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of 
-no birth yet from nine months after first birth for women with a girl
-as their first child and eight or more years of education 
-for the 1995--2004 and 2005--2016 periods
-} 
-\label{fig:decreasing_sex_ratio} 
-\end{figure}
-
-\begin{figure}[htpb!]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
-\setcounter{subfigure}{-2}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
-\setcounter{subfigure}{0}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of 
-no birth yet from nine months after second birth for urban women with
-eight or more years of education 
-for the 1995--2004 and 2005--2016 periods
-} 
-\label{fig:increasing_sex_ratio} 
-\end{figure}
-
-The predicted sex ratio may change within a spell for, at
-least, two reasons.
-First, parents may stop using prenatal sex determination within
-a spell once the duration from the previous birth becomes long enough.
-The desire for short spacing could, for example, arise from 
-economies of scale in childbearing and rearing that parents lose 
-if children are born too far apart \citep[p 374]{schultz97}. 
-In this case, we should observe the predicted sex ratio decline
-with spell length.
-
-Second, if the degree of son preference varies across women within 
-the sample, but their behavior is not affected by duration from the 
-previous birth, we should observe an increasing share of births come from 
-parents with stronger son preference as the duration from the
-previous birth increases.
-Whereas the early births are a combination of births to
-people with lower son preference and those with stronger son
-preference who conceived a son in the first or second pregnancy,
-births later in the spell are then predominately from those with stronger
-son preference who have not yet conceived a son.
-In this case, we should see an increase in the sex ratio 
-as duration increases.
-
-Figures \ref{fig:decreasing_sex_ratio} and \ref{fig:increasing_sex_ratio} show
-examples of how sex ratio behave within spells.
-Both are for women with eight or more education since the results above indicate
-that they are the most likely to use sex selection or other means of achieving 
-an unequal sex ratio.
-Figure \ref{fig:decreasing_sex_ratio} shows results for the second spell for
-the 1995--2004 and 2005--2016 periods for women with a girl as their first
-child by area of residence.
-Figure \ref{fig:increasing_sex_ratio} shows results for the third spell for
-the same two periods for urban women with either two girls or one boy and one
-girl as their first two children.
-
-Within the second spell, both urban and rural women show a declining
-sex ratio as duration increases for the 1995--2004 period, whereas there
-is little change, or possibly a small increase, with duration for the 
-2005--2016 period.
-These results are consistent with a situation where fertility is declining
-over time leaving less room for a change in the decision to use sex selection.
-Fertility decline is not immediately apparent from the second spell 
-results, but the third spell shows that the likelihood of progressing from
-two to third children declines by approximately 15 percentage points if
-the woman has given birth to a boy.
-
-The third spell figures show a very different situation with substantial 
-increases in sex ratios.
-The high sex ratio for women with two girls is likely 
-motivated by the combined desire to limit fertility and ensure a son;
-similarly to the situation for the second spell as shown in 
-Figure \ref{fig:decreasing_sex_ratio} (b) and (d).
-
-The increase in sex ratio with duration for women who already have
-given birth to a boy likely illustrates the case where there is a
-combination of degrees of son preference.
-Say that one group wants one son and after that will not use sex
-selection, whereas another group has a strong preference for two
-sons (or either have or expect to lose the boy they already have)
-and that the two groups conceive at the same rate.
-In that case, we should expect precisely the increasing sex ratios
-we observe, especially given the declining fertility over time.
-
-\section{Conclusion\label{sec:conclusion}}
-
-The central question addressed here is the extent to which spacing patterns 
-significantly changed as prenatal sex determination became available.
-Specifically, did the spacing after girls increase relative to the spacing
-after boys?
-The underlying idea is that in the absence of sex selection son 
-preference leads to shorter spacing after the birth of a girl than after the 
-birth of a boy, whereas son preference increases the spacing after the birth 
-of a girl relative to after the birth of a boy when prenatal sex selection is 
-available.
-I introduce a new method that simultaneously accounts for spacing
-between births and the potential use of sex selection. 
-I apply the method to over four decades of data from India's NFHS.
-The results show two very different approaches to son preference.
-
-At one extreme, women without education mostly follow the standard 
-pattern of shorter spacing when a woman does not have the desired number of 
-sons.
-There is also limited evidence of biased sex ratios and the increases in
-spacing that should follow from the use of sex selection.
- In the situations where there are elevated sex ratios for women without
-education, the spacing patterns are close to those with more regular sex
-ratios. 
-Hence, it is difficult to conclude that the changes in sex
-ratios indicate sex selection rather than normal variation or problems
-with recall errors.
-
-At the other extreme, women with eight or more years of education have
-experienced an almost complete reversal of the traditional spacing patterns.
-Rather than having the next birth sooner as they mostly did before 
-sex selection became available, women with either no or one son now 
-have substantially longer spacing than if they have two or more sons.
-As shown by the increasingly significant deviations in the sex ratio
-from the natural sex ratio, these changes are likely due to increased
-use of sex selection rather than changes in son preference. 
-Banning prenatal sex determination has not been able to
-reverse the use, although it is possible that it has slowed the rate 
-of increase.
-
-Over the last 40 years, there has been a general increase in median
-spacing for all education groups, but especially for the most 
-educated women.
-The exception is for the spacing between marriage and first birth
-where there are two counteracting forces: women have become less likely 
-to conceive before marriage, and there has been a substantial compression 
-in the variation of spacing.
-The result is that median spacing from marriage to first birth
-has changed little or even declined for the best-educated women.
-Both the decrease for the first spell and the increase for higher-order
-spells are consistent with increased access to contraceptives over
-time \citep{Yeakey2009}.
-
-The empirical model allows for the effects of covariates
-to vary within the spell. 
-Non-proportionality is essential because the use of sex selection may 
-vary within a spell. 
-The use of sex selection may change either because preferences for not 
-too long spacing between births override the preference for sons or 
-because of selection, where
-the women who remain in a spell are those with the strongest son
-preference who have been through multiple pregnancies because the
-fetuses were female. 
-Because these move in opposite directions, I cannot
-directly establish the extent to which they affect the results. 
-Both are, however, present, as can be seen from the cases where there is
-either a decline in sex ratio with spell duration or a substantial
-increase with spell duration. 
-The first case is most likely at lower
-parities where there is still less pressure to ensure a son, which
-allows any preference for shorter spacing to play more of a role. 
-The second is most likely for higher
-parities where the desire to limit further childbearing and ensure a son
-dominates any preferences for shorter spacing.
-
-The potential for changes in sex ratio within a spell means that
-censoring is an important issue when trying to understand how the sex
-ratio changes over time, and especially when it comes to establishing
-whether the use of sex selection is increasing or decreasing.
-Take, for example, the case of women with eight or more years of
-education in the last period. 
-If we look at women who started their third spell in either the
-2005--2009 or the 2010--2014 periods and we treat end of 2015
-as the cut-off point, then the observed sex ratio for the 2005--2009
-women is 55.99\% boys while it is 55.38\% for women who started 
-in the 2010--2014 period.%
-\footnote{
-The calculations combines urban and rural women; the basis result 
-changes little if I split by area of residence.
-I chose the 2014 cut-off to ensure that both groups cover 
-five years, even though NFHS-4 took place in 2015 and 2016.
-}
-It would, therefore, appear that the use of sex selection for
-this spell is slightly decreasing over time.
-This interpretation, however, ignores the role of censoring.
-If we use the estimation results to predict final sex ratio
-once childbearing for the third spell is over, the predicted
-sex ratios are 56.10\% boys and 56.08\% boys for the 
-2005--2009 and the 2010--2015 starts, which indicates
-virtually no change over time.
-The reason for the difference is that while we would have 
-observed 7,134 birth out of a predicted 7,451 total number 
-of births for the 2005--2009 start, we would only have observed 
-3,348 births out of a predicted 8,842 for the 2010--2014 group.
-
-Although it is not possible to directly observe whether sex selection
-causes the unequal sex ratio and longer spacing the results are
-consistent with a general increase in sex selection over time. 
-The apparent increase in the use of sex selection is mainly found among
-women with more education and more so in urban than in rural areas,
-although the differences between urban and rural areas are relatively
-minor. 
-Compared to previous research one result stands out. 
-It appears that the use of sex selection is spreading to women with lower 
-levels of education.
-Even women with one to seven years of education show unequal sex ratios 
-and longer spacing for their higher-order spells.
-
-The results here point to two important, interconnected, questions 
-for future research:
-What is the connection between falling fertility and the 
-use of sex selection and is the use of sex selection increasing 
-or decreasing over time?
-It is clear that fertility has been declining over time in India,
-although it is important to note that the decline might be
-overstated precisely because of increased use of sex selection and
-the resulting longer spacing between births makes it less likely 
-that we will observe births to women, even though they eventually
-will happen.
-The fact that biased sex ratio occurs at lower-order spells over
-time and is starting to show up for women with less education 
-all indicate that lower fertility and use of sex selection are
-related, but a more detailed analysis is needed.
-Furthermore, although examining spells separately, as done here, is a useful
-first step in understanding how sex selection changes over time,
-it does not lend itself easily to examine the degree to which
-sex selection changes over time.
-For both, a combined model that incorporates the full fertility
-history of women would be more appropriate.
-
-The results here also lead to a set of broader questions that
-future research should address.
-First, to what extent are the improvements in health for girls
-relative to boys the result of selection, the longer spacing between
-births, or changing son preference?
-There is some early evidence that sample selection can make it appear that
-girls are healthier, even though the underlying cause is a combination
-of sex selection and higher mortality together with recall 
-error \citep{Portner2018a}. 
-Understanding what role these factors play in better health for
-girls is especially important when evaluating policies that 
-aim to directly limit the use of sex selection rather than 
-changing preferences or incentives.
-If the better health outcomes for girls are, for example, an unintended 
-side-effect of the longer spacing that arises from sex-selective 
-abortions, then an effective ban on sex selection may, at least
-temporarily, worsen health outcomes for girls.
-
-Second, we need to understand how female labor force participation
-interacts with the use of sex selection.
-Increased autonomy for women, arising, for example, from better opportunities
-for working outside the home, has been suggested as a way to increase
-women's status and thereby lower the use of sex selection \citep{Das-Gupta2016}.
-This may, however, be a double-edged sword.
-On the one hand, it is a clear benefit to the women who gain  
-bargaining power, and it increases the cost of repeated 
-sex-selective abortions because the increased duration between births
-would cause a stronger disruption in labor market participation.
-On the other hand, it may further lower desired fertility, and 
-that may, everything else equal, lead to higher use of sex selection.
-Understanding the trade-off between long-term benefits from improvements in
-women's labor force participation and short-term costs from potential 
-increases in sex selection is of paramount importance.
-
 \clearpage
@@
 
-\clearpage
-\newpage
-
-\appendix
-
-% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
-\renewcommand\thefigure{\thesection.\arabic{figure}}    
-\renewcommand\thetable{\thesection.\arabic{table}}
-
-\section*{Appendices for Online Publication}
-
-These appendices are intended for online publication.
-They provide the descriptive statistics, additional
-estimated duration tables, and graphs for all 
-education groups and spells.
-
-\clearpage
-\newpage
-
-\section{Recall Error and the Sex Ratio}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-The reliability of the results depends on the correctness of the birth histories
-provided by the respondents.
-A significant concern here is underreporting of child mortality, especially a systematic
-recall error where respondents' likelihood of reporting a deceased child depends on the 
-sex of that child. 
-This section assesses the degree of recall error across the surveys and discusses methods
-to address it.
-
-NFHS enumerators probe for any missed births, although the method depends on the survey.
-NFHS-1 probe for each calendar birth interval that is four or more years.
-NFHS-2 asked for stillbirths, spontaneous and induced abortions and also probed 
-for each calendar birth interval four or more years.
-NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether there were any 
-other live births between (name of previous birth) and (name), including any children who 
-died after birth, and asked for births before the birth listed as first birth and
-after the last birth listed as the last birth.
-
-Probing catches many initially missed births, but systematic recall error based on son
-preference may still be a problem.
-First, son preference leads to significantly higher mortality for girls than boys.
-Secondly, son preference makes it more likely that parents will remember deceased boys 
-than deceased girls.
-Finally, in the absence of sex-selective abortions, parents with a preference for sons may
-have the next birth sooner if the last child was a girl than if it was a boy.
-If this girl subsequently dies, she is more likely to be missed if probing for missed 
-births is only done for long intervals as in NFHS-1 and NFHS-2.
-
-I use two approaches to examine the degree of recall error.
-The first approach is to test whether the observed sex ratio is significantly different
-from the natural sex ratio.
-Prenatal sex determination techniques did not become widely available until the mid-1980s, 
-so any significant deviation from the natural sex ratio before that time is likely the 
-result of recall error.
-The second approach is to compare births that took place during the same period but
-where captured in different surveys.
-Recall error is likely to increase with time, so births and deaths that took place earlier 
-are more likely to be subject to recall error than more recent events.
-
-Table \ref{tab:recallBirthBO1} shows the sex ratios of children recorded as first-born by 
-year of birth, together with tests for whether the observed sex ratio is significantly 
-higher than the natural sex ratio and whether more recent surveys have a higher sex ratio 
-for the cohort than earlier surveys for the same period births.
-Births are combined into five-year cohorts to achieve sufficient power.
-
-\input{../tables/recallBirthBO1.tex}
-
-% \input{../tables/recallBirthBO2.tex}
-
-The ``first-born'' sex ratios illustrate the systematic recall error problem well.
-In all four surveys around 55 percent of children reported as first-born are boys
-for the first cohort of births observed.
-Given that these cohorts cover from 1960-1964 to 1980-1984, which is before sex selection 
-techniques became available in India, the most likely explanation for the skewed sex ratio 
-is that some children listed as first-borns were not, in fact, the first children born in 
-their families.
-Instead, for a substantial proportion of families, their first-born was a girl who died 
-and went unreported when enumerators asked about birth history.
-
-As expected, the difference between the observed sex ratio and the natural sex ratio is 
-less pronounced the closer to the survey date the cohort is.
-The observed sex ratio for children born just before the NFHS-1 survey and listed as 
-first-born is 0.517, which is not statistically significantly different from the
-natural sex ratio.
-The same general pattern holds for the other three surveys, with cohorts further away
-from the survey date more likely to have a sex ratio skewed male.
-
-% Second births show a pattern very similar to that for first births.
-% An interesting difference is that there is evidence of a U-shaped relationship between
-% time and sex ratio for second births.
-% Cohorts furthest away from the survey year show the highest sex ratios, but declines to the
-% natural sex ratio in the mid-1980s, and the sex ratio is then significantly higher again 
-% for more recent births.
-% This is in line with the results in the main paper that show that sex selective abortions 
-% take place on lower parity births as desired fertility declined.
-
-Finally, across surveys, the same cohort tends to show a higher sex ratio the more recent 
-the survey (births in the cohort took place earlier relatively to the survey date).
-Despite this, few cohorts show significantly different sex ratios across surveys, most 
-likely because of a lack of power.
-The exception is that comparisons involving NFHS-4 are mostly statistically significant
-since the number of surveyed households in NFHS-4 were much larger than in prior surveys.
-
-The problem with the above approach is that the year of birth is affected by recall error; 
-a second born child listed as first-born is born later than the real first born child.
-Year of marriage should, however, be affected neither by parental recall error 
-nor the use of sex-selective abortions.
-Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2}, therefore, shows sex 
-ratios of children recorded as first-born and second-born by year of parents' marriage, 
-together with tests for whether the observed sex ratio is significantly higher than the 
-natural sex ratio and whether more recent surveys show a higher sex ratio for the cohort 
-than earlier surveys.
-The basic recall error pattern remains, with women married longer ago more
-likely to report that their first-born is a boy.
-Similarly, comparing women married in the same five-year period across surveys shows
-that women married longer ago are more likely to report having a son.
-
-\input{../tables/recallMarriageBO1.tex}
-
-\input{../tables/recallMarriageBO2.tex}
-
-The relationship between length of marriage and recall error can also seen in 
-Figures \ref{fig:sex_ratio_recall_rounds_bo1} and \ref{fig:sex_ratio_recall_rounds_bo2}, 
-which show the observed sex ratio for children reported as first born as a function of 
-duration of marriage at the time of the survey.
-The solid line is the sex ratio of children reported as first born by the number of years 
-between the survey and marriage, the dashed lines indicate the 95 percent confidence 
-interval and the horizontal line the natural sex ratio (approximately 0.512).
-To ensure sufficient cell sizes the years are grouped in twos.
-In line with the results from Tables \ref{tab:recallMarriageBO1} and 
-\ref{tab:recallMarriageBO2}, the observed ratio of boys is increasingly above the expected 
-value the longer ago the parents were married.
-
-\begin{figure}
-\centering
-\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1}}
-\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2}} \\
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
-\caption{Ratio of Boys for ``First'' Births by Survey Round}
-\label{fig:sex_ratio_recall_rounds_bo1}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1_bo2}}
-\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2_bo2}} \\
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3_bo2}} 
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4_bo2}} 
-\caption{Ratio of Boys for ``Second'' Births by Survey Round}
-\label{fig:sex_ratio_recall_rounds_bo2}
-\end{figure}
-
-The increasingly unequal sex ratio with increasing marriage duration suggests that
-a solution to the recall error problem is to drop observations for 
-women who were married ``too far'' from the survey year.
-The main problem is establishing what the best cut-off point should be, with the
-trade-off between retaining enough observations and the correctness of the information.
-As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} show, there are 
-differences in recall error across the three surveys and between parities, although
-this may simply be the result of differences in number of observations across surveys.
-Furthermore, the recall error pattern is not entirely consistent across observed birth 
-orders.
-Since most of the surveys start showing significantly biased sex ratio from around 22
-years of marriage on, I drop all observations where the marriage took place 22 years
-or more.
-
-\clearpage
-\newpage
-
-\section{Descriptive Statistics}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% Descriptive statistics tables
-\input{../tables/des_stat.tex}
-
-\clearpage
-\newpage
-
-\section{Additional Duration Results}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\vspace*{-0.51cm}
-
-\input{../tables/bootstrap_duration_p25_p75_low.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_med.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high.tex}
-
-\clearpage
-
-\section{Graphs for All Education and Spell Groups}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% [FIRST SPELL]
-
-\subsection{First Spell}
-
-\input{../figures/appendix_spell1_low.tex}
-
-\input{../figures/appendix_spell1_med.tex}
-
-\input{../figures/appendix_spell1_high.tex}
-
-\begin{figure}[htpb]
-\centering
-\caption*{No Education}
-\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
-\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
-\caption*{1-7 Years of Education}
-\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
-\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
-\caption*{8 or more Years of Education}
-\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
-\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
-\caption{Survival curves conditional on progression to first birth; start point is month of marriage}
-\label{fig:results_spell1_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Second Spell}
-
-\input{../figures/appendix_spell2_low.tex}
-
-% PARITY PROGRESSION SURVIVAL CURVES - Low
-
-% Low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2005]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_low_pps}
-\end{figure}
-
-% SPELL 2 - URBAN - MEDIUM
-
-\input{../figures/appendix_spell2_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-% Low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1-7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_med_pps}
-\end{figure}
-
-% High education
-
-\input{../figures/appendix_spell2_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_high_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Third Spell}
-
-% low education
-\input{../figures/appendix_spell3_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_low_pps}
-\end{figure}
-
-% Medium education
-
-\input{../figures/appendix_spell3_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_med_pps}
-\end{figure}
-
-% High education
-
-\input{../figures/appendix_spell3_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - high
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_high_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Fourth Spell}
-
-% low education
-
-\input{../figures/appendix_spell4_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_low_pps}
-\end{figure}
-
-% Medium education
-
-\input{../figures/appendix_spell4_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_med_pps}
-\end{figure}
-
-% High education
-
-\input{../figures/appendix_spell4_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - high
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_high_pps}
-\end{figure}
-
 \end{document}

### 2019-02-21 paper/intro-notes.tex
Recast first couple of paragraphs

Birth spacing has long served as a measure of son preference, with strong
son preference typically associated with shorter birth intervals the
fewer sons a family has \citep{ben-porath76b,Leung1988}.
However, the introduction of prenatal sex determination has the potential to 
change the relationship between son preference and birth spacing fundamentally.
Some of the couples who before had shorter birth spacing because of son preference,
might instead resort to sex-selective abortions, and each abortion naturally 
increases the interval between births.
As a result, we may now observe \emph{longer} average spacing for families with strong son 
preference, precisely because it leads them to use sex selection.
To further complicate matters, families who---for one reason or another---do 
not use prenatal sex selection but still have a preference for son may continue to have 
shorter birth spacing than those with a lower preference for sons.

In this paper, I examine how birth spacing in India has changed over time and across 
groups with the introduction of sex selection.
I introduce and apply an empirical method that directly incorporates the effects of 
sex-selective abortions on the duration between births 
\emph{and} 
the likelihood of a son. 
The method can be used to analyze both situations with and without prenatal
sex selection.
I apply the method to birth histories of Hindu women, using data from the four
India's National Family and Health Surveys (NFHS), covering the period 
1972 to 2016.

India is a particularly compelling case.
India has long shown a strong preference for boys, especially in the northern 
states \citep{Kishor1993,murthi95,arnold98}.%
\footnote{
The proportion of couples who ideally wants more boys than girls does, however,
appear to be decreasing over time and with higher education \citep{bhat03,pande07}.
}
As a result, mortality risk is higher for females than males, leading to an almost
continuous increase in India's overall ratio of males to females over the last century 
\citep{dyson01,Navaneetham2011}.
India has also seen dramatic increases in the males-to-females ratio 
at birth over the last three decades as access to prenatal sex determination 
expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06}.
In addition, fertility has declined substantially, to the point where it is now
at, or even below, replacement in some areas 
\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
This decline in fertility, combined with son preference, has lead to an intensified
pressure to use sex selection.

 families are more likely to cease childbearing after the birth of 
a son than after a daughter \citep{Das1987,Arnold1997,arnold98,clark00,dreze01,Basu2010}.

My proposed method allows for the time since the previous 
birth to affect the decision on sex selection.
By examining under what circumstances sex selection decisions change with 
spacing, we can draw a more nuanced picture of the degree of son preference.

[how much longer intervals]
 by six months to a year.
The increase consists of three parts.
First, starting from the time of the abortion, the uterus needs at 
least two menstrual cycles to recover;  otherwise, the likelihood 
of spontaneous abortion increases substantially \citep{zhou00b}.
The second part is the waiting time to conception, which is between 
one and six months \citep{Wang2003}.
Finally, sex determination tests are reliable only from three months 
of gestation onwards.

[son preference and spacing - evidence]

[spacing and outcomes - children]

[spacing and outcomes - mothers]

[falling fertility and introduction of sex selection]

[Predicted changes in spacing]

[Other reasons for studying spacing]

### 2019-02-21 paper/intro-notes.tex
Add references to discussion on fertility decline

@@
 continuous increase in India's overall ratio of males to females over the last century 
-\citep{dyson01,Navaneetham2011}.
+\citep{dyson01,Navaneetham2011,Bongaarts2015}.
 India has also seen dramatic increases in the males-to-females ratio  
 at birth over the last three decades as access to prenatal sex determination 
-expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06}.
+expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012}.
 In addition, fertility has declined substantially, to the point where it is now
@@
 \citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-This decline in fertility, combined with son preference, has lead to an intensified
-pressure to use sex selection.
+This decline in fertility, combined with the strong preference for sons, has lead to an 
+intensified pressure to use sex selection \citet{Guilmoto2009a,Jayachandran2017}.%
+\footnote{
+In some instances, however, the fertility decline appears to have created a stronger 
+aversion to daughters rather than a stronger preference for son \citet{DiamondSmith2008}.
+}
 

### 2019-02-21 paper/intro-notes.tex
Update spacing and DSR lit

@@
 This decline in fertility, combined with the strong preference for sons, has lead to an 
-intensified pressure to use sex selection \citet{Guilmoto2009a,Jayachandran2017}.%
+intensified pressure to use sex selection \citet{Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
 \footnote{
@@
 a son than after a daughter \citep{Das1987,Arnold1997,arnold98,clark00,dreze01,Basu2010}.
+
+Parents are also more likely to cease childbearing after the birth of 
+a son than after a daughter 
+\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
+}
 

### 2019-02-22 paper/intro-notes.tex
Write up on differential stopping behavior

@@
 
- families are more likely to cease childbearing after the birth of 
-a son than after a daughter \citep{Das1987,Arnold1997,arnold98,clark00,dreze01,Basu2010}.
+There is amble evidence that son preference has affected individual families' fertility
+decisions in India and elsewhere.
+It is, for example, clear that a significant proportion of Indian families follow a
+son preference based differential stopping behavior, where, for a given number of
+children, they are more likely to have an additional child if they have not yet
+reached their preferred number of sons 
+\citep{repetto72,Das1987,Arnold1997,clark00,Basu2010,Barcellos2014}.
+A smilar pattern is found in many other countries 
+\citep[see, for example][]{larsen98,filmer09,Altindag2016}.%
+\footnote{
+One potential effect of this behavior is that girls tend to end up in larger families, 
+which may have negative impacts on survival and human capital investments, even in 
+the absence of direct discrimination \citet{Jensen2003,Kugler2017}.
+}
 
-Parents are also more likely to cease childbearing after the birth of 
-a son than after a daughter 
-\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
-}
+Of more direct interest here is differential \emph{spacing} behavior, both because 
+it has been used as a measure for son preference and because birth spacing may directly
+impact health and other outcomes for both children and mother.
 

### 2019-02-25 paper/intro-notes.tex
Add paragraph on son preference and spacing research

@@
 fewer sons a family has \citep{ben-porath76b,Leung1988}.
-However, the introduction of prenatal sex determination has the potential to 
-change the relationship between son preference and birth spacing fundamentally.
-Some of the couples who before had shorter birth spacing because of son preference,
-might instead resort to sex-selective abortions, and each abortion naturally 
-increases the interval between births.
-As a result, we may now observe \emph{longer} average spacing for families with strong son 
-preference, precisely because it leads them to use sex selection.
-To further complicate matters, families who---for one reason or another---do 
-not use prenatal sex selection but still have a preference for son may continue to have 
-shorter birth spacing than those with a lower preference for sons.
+However, the introduction of prenatal sex determination potentially  
+changed the relationship between son preference and birth spacing fundamentally.
+The stronger the son preference, the more likely couples are to resort to sex-selective 
+abortions, and each abortion naturally increases the interval between births.
+As a result, we may now observe \emph{longer} average spacing for families with stronger 
+son preference, precisely because it makes them more likely to use sex selection.
+To further complicate matters, families with a preference for son who---for one reason or 
+another---do not use prenatal sex selection may continue to have shorter birth spacing 
+than those with a lower preference for sons.
 
@@
 
-There is amble evidence that son preference has affected individual families' fertility
-decisions in India and elsewhere.
+There is amble evidence that son preference has affected fertility decisions in India and 
+elsewhere.
 It is, for example, clear that a significant proportion of Indian families follow a
@@
 reached their preferred number of sons 
-\citep{repetto72,Das1987,Arnold1997,clark00,Basu2010,Barcellos2014}.
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
 A smilar pattern is found in many other countries 
@@
 
-Of more direct interest here is differential \emph{spacing} behavior, both because 
-it has been used as a measure for son preference and because birth spacing may directly
-impact health and other outcomes for both children and mother.
+[emphasize that birth spacing is a superset of DSB?]
+Of more direct interest here is, however, the potential for differential \emph{spacing} 
+behavior, 
+both because it has been used as a measure for son preference and because birth spacing 
+may directly impact health and other outcomes for both children and mother.
+In India the sex of the last-born child significantly impact the duration to next birth,
+with the expected birth interval about three percent longer if the last-born was son than
+if it was a daughter \citep{Bhalotra2008,Kumar2016}.
+Similarly, ethic Indians in South Africa also show a longer duration after the birth of a 
+son than after a daughter \citep{Gangadharan2003}.%
+\footnote{
+Ethic Indians in Malaysia do, however, show little evidence of son preference, although
+the sample sizes are very small \citep{Pong1994}.
+}
+India is not alone in showing an effect of sex composition on subsequent birth spacing.
+In both Bangladesh and Vietnam the more boys a family has the longer the expected duration 
+to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
+Outside Asia the evidence is more mixed.
+North Africa shows shorter spacing in the absense of sons, while a similar pattern does
+not exists in Sub-Saharan Africa \citep{Rossi2015}.%
+\footnote{
+A possible exception is Senegal, where women with a higher risk of widowhood show
+shorter birth spacing until they have secured a son \citep{Lambert2016}.
+}
 
-My proposed method allows for the time since the previous 
-birth to affect the decision on sex selection.
-By examining under what circumstances sex selection decisions change with 
-spacing, we can draw a more nuanced picture of the degree of son preference.
+[how is spacing achieved?]
+This longer spacing 
+\citep{Rahman1993}
+\citep{Jayachandran2011}
+
+[Education and socio-economic status and spacing]
+
+[spacing and outcomes - children]
+
+[spacing and outcomes - mothers]
+
+[Other reasons for studying spacing]
+
+[Predicted changes in spacing with sex selection]
 
@@
 of gestation onwards.
-
-[son preference and spacing - evidence]
-
-[spacing and outcomes - children]
-
-[spacing and outcomes - mothers]
-
-[falling fertility and introduction of sex selection]
-
-[Predicted changes in spacing]
-
-[Other reasons for studying spacing]

### 2019-02-25 paper/intro-notes.tex
Add paragraphs on spacing and health outcomes

@@
 [emphasize that birth spacing is a superset of DSB?]
-Of more direct interest here is, however, the potential for differential \emph{spacing} 
+Of particular interest here is, however, the potential for differential \emph{spacing} 
 behavior, 
@@
 }
-India is not alone in showing an effect of sex composition on subsequent birth spacing.
+India is not alone in sex composition affecting subsequent birth spacing.
 In both Bangladesh and Vietnam the more boys a family has the longer the expected duration 
@@
 }
+
+There is an even more substantial literature addressing the potential effects of birth 
+spacing on health outcomes, but, although most of the research finds a negative impact of 
+short spacing on health, identifying the causal mechanisms have proven more difficult
+\citep{Conde-Agudelo2006,Conde-Agudelo2012}.
+Broadly speaking, there are three pathways that birth intervals can affect health.
+First, maternal depletion, where the mother does not have sufficient
+time to recover after a pregnancy.%
+\footnote{
+This depletion can take the form of nutrition, folate, or cervical insufficiency.
+}
+Second, disease transmission both from mother to child and between children close in age.
+Third, sibling competition, where siblings close in age compete for scarce resources and
+parental care.
+Which mechanism dominates is especially of interest when spacing decisions are driven by 
+son preference.
+Both the maternal depletion and the transmission of disease explanations predominately
+affect the subsequent child and the mother.
+Only sibling competition has the potential to negatively affect the older child.
+
+In India, there is evidence that both the prior and the subsequent child have higher
+likelihood of dying the closer they are spaced, although the effect is not symmetrical
+\citep{Whitworth2002,Bhargava2003,Maitra2008,Makepeace2008}.%
+\footnote{
+\cite{Bhalotra2008}, however, find that birth spacing only explain a limited amount
+of neonatal mortality.
+In other countries, focus has been mostly on the subsequent birth, but there is evidence 
+in countries as diverse as Bangladesh, Brazil, and El Salvadore that
+short intervals between birth has negative health effects
+\citep{Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
+}
+The increased mortality risk for prior children may come from shorter breastfeeding of 
+girls to ensure that the mother can conceive again quicker, and with poor water
+quality this shorter breastfeeding may result both in higher risk of dying and shorter
+stature if the child survives \citep{Jayachandran2011,Jayachandran2017a}.
 
@@
 
+What is common in the literature reviewed above it that the potential effects of 
+sex selection on spacing has not been incorporated.
+
 [how much longer intervals]

### 2019-02-27 paper/intro-notes.tex
Work on long-term effects of spacing
Combine intro

@@
 elsewhere.
-It is, for example, clear that a significant proportion of Indian families follow a
-son preference based differential stopping behavior, where, for a given number of
-children, they are more likely to have an additional child if they have not yet
-reached their preferred number of sons 
+A significant proportion of Indian families follow a son preference based differential 
+stopping behavior, where, for a given number of children, they are more likely to have an 
+additional child if they have not yet reached their preferred number of sons 
 \citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
@@
 of neonatal mortality.
-In other countries, focus has been mostly on the subsequent birth, but there is evidence 
-in countries as diverse as Bangladesh, Brazil, and El Salvadore that
-short intervals between birth has negative health effects
-\citep{Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
 }
@@
 stature if the child survives \citep{Jayachandran2011,Jayachandran2017a}.
+In other countries, focus has been mostly on the subsequent birth, but there is evidence 
+in countries as diverse as Bangladesh, Brazil, and El Salvadore that
+short intervals between birth has negative health effects
+\citep{Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
+
+The potential effects of spacing are not restricted to child outcomes, although
+there is less evidence on longer term effects, and most of what we have comes from
+Western countries.
+In the US, for example, longer spacing between births increases the older sibling's
+test scores on the Peabody Individual Achievement Test, although there is no
+statistically significant effect on the younger sibling \citep{Buckles2012}.
+In line with this, close spacing appears to increase the risk of dropping out of
+high school and lower the probability of attending a post-secondary school in both the
+US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.
+These results are, however, not uniformly supported, with recent results from Sweden 
+showing no relationship between birth spacing, even if very short, and outcomes such as 
+years of education completed, earnings, and unemployment \citep{Barclay2017}.
+
+The effect of spacing on mother's outcomes have received less attention than the
+effect on children, and reviews of the literature show mixed results on mother's 
+anthropometric status \citep{Dewey2007,Conde-Agudelo2012}.
+For India, there is, however, evidence that women with first-born girls are both
+more likely to have short birth spacing and more likely to have anemia, possibly as
+the result of the short spacing resulting in maternal depletion \citep{Milazzo2018}.
+In Western countries, having a longer interval between births appear to have positive
+effects on long-term labor market outcomes, such as participation and 
+income \citep{Gough2017,Karimi2014}.
 
 [how is spacing achieved?]
-This longer spacing 
 \citep{Rahman1993}
 \citep{Jayachandran2011}
+\citep{Alam2018}
 
 [Education and socio-economic status and spacing]
-
-[spacing and outcomes - children]
-
-[spacing and outcomes - mothers]
 

### 2019-02-27 paper/sex_selection_spacing-ver2-new-intro.tex
Combine intro

@@
 
-Parents' spacing of births has long served as a measure of son preference 
-\citep{Leung1988}.
-Before prenatal sex determination became available, the only recourse for 
-parents who wanted a son---but did not yet have one---was to have the next 
-birth sooner.
-Son preference is therefore often associated with shorter spacing after the 
-births of girls than boys 
-\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012,Rossi2015}.
-Shorter spacing is, in turn, associated with worse health outcomes for girls 
-and mothers 
-\citep{arnold98,Conde-Agudelo2000,Whitworth2002,Razzaque2005,Rutstein2005,Conde-Agudelo2006}.%
+Birth spacing has long served as a measure of son preference, with strong
+son preference typically associated with shorter birth intervals the
+fewer sons a family has \citep{ben-porath76b,Leung1988}.
+However, the introduction of prenatal sex determination has the potential to
+fundamentally change the relationship between son preference and birth spacing.
+The stronger the son preference, the more likely couples are to resort to sex-selective 
+abortions, and each abortion increases the interval between births.
+As a result, we may now observe \emph{longer} average spacing for families with stronger 
+son preference, precisely because it makes them more likely to use sex selection.
+To further complicate matters, families with son preference who---for one reason or 
+another---do not use prenatal sex selection may continue to have shorter birth spacing 
+than those with a lower preference for sons.
+
+In this paper, I examine how birth spacing in India has changed over time and across 
+groups with the introduction of sex selection.
+I introduce and apply an empirical method that directly incorporates the effects of 
+sex-selective abortions on the duration between births 
+\emph{and} 
+the likelihood of a son. 
+The method can be used to analyze both situations with and without prenatal
+sex selection.
+I apply the method to birth histories of Hindu women, using data from the four
+India's National Family and Health Surveys (NFHS), covering the period 
+1972 to 2016.
+
+% [Why India?]
+India is a particularly compelling case.
+India has long shown a strong male preference, especially in the northern states 
+\citep{Kishor1993,murthi95,arnold98}.%
 \footnote{
-Parents are also more likely to cease childbearing after the birth of 
-a son than after a daughter 
-\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
+The proportion of couples who ideally wants more boys than girls does, however,
+appear to be decreasing over time and with higher education \citep{bhat03,pande07}.
+}
+As a result, a significant proportion of Indian families follow a son preference based 
+differential stopping behavior, where, for a given number of children, they are more 
+likely to have an additional child if they have not yet reached their preferred number of 
+sons \citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
+\footnote{
+A smilar pattern is found in many other countries 
+\citep[see, for example][]{larsen98,filmer09,Altindag2016}.
+}
+Furthermore, higher mortality risk for females than males at most ages has lead to an 
+almost continuous increase in India's overall ratio of males to females over the last 
+century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
+Over the last three decades, India has also seen dramatic increases in the 
+males-to-females ratio at birth as access to prenatal sex determination 
+expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012}.
+In addition, fertility has declined substantially, to the point where it is now
+at, or even below, replacement in some areas 
+\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
+This decline in fertility, combined with the strong preference for sons, has lead to an 
+intensified pressure to use sex selection \citep{Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
+\footnote{
+In some instances, however, the fertility decline appears to have created a stronger 
+aversion to daughters rather than a stronger preference for son \citet{DiamondSmith2008}.
 }
 
-However, the introduction of prenatal sex determination fundamentally changed the 
-relationship between son preference and birth spacing.
-Couples, who had shorter birth spacing before because of son preference,
-now have access to prenatal sex determination and sex-selective abortions,
-and each abortion increases birth spacing by six months to a year.
-The increase consists of three parts.
-First, starting from the time of the abortion, the uterus needs at 
-least two menstrual cycles to recover;  otherwise, the likelihood 
-of spontaneous abortion increases substantially \citep{zhou00b}.
-The second part is the waiting time to conception, which is between 
-one and six months \citep{Wang2003}.
-Finally, sex determination tests are reliable only from three months 
-of gestation onwards.
+% [Why spacing?] 
+There are four main reasons for examining birth spacing and how it changes with 
+access to sex selection.
+First, it has been widely used as a measure of son preference.
+In India the sex of the last-born child significantly impact the duration to next birth,
+with the expected birth interval about three percent longer if the last-born was son than
+if it was a daughter \citep{Bhalotra2008,Kumar2016}.
+Similarly, ethic Indians in South Africa also show a longer duration after the birth of a 
+son than after a daughter \citep{Gangadharan2003}.%
+\footnote{
+Ethic Indians in Malaysia do, however, show little evidence of son preference, although
+the sample sizes are very small \citep{Pong1994}.
+}
+India is not alone in sex composition affecting subsequent birth spacing.
+In both Bangladesh and Vietnam the more boys a family has the longer the expected duration 
+to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
+Outside Asia the evidence is more mixed.
+North Africa shows shorter spacing in the absense of sons, while a similar pattern does
+not exists in Sub-Saharan Africa \citep{Rossi2015}.%
+\footnote{
+A possible exception is Senegal, where women with a higher risk of widowhood show
+shorter birth spacing until they have secured a son \citep{Lambert2016}.
+}
 
-As a result, we now have a situation where we may observer \emph{longer} spacing
-for families with daughters than for families with sons, precisely because
-strong son preference leads them to use sex selection.
-Working in the opposite direction, couples with strong son preference
-will likely still try to conceive earlier in the absence of sons. 
-They may even shorten the time until conception, knowing that they might
-have to go through multiple pregnancies and abortions before they
-conceive a son.
-To further complicate matters, we can still observe shorter birth spacing 
-after the births of daughters as a representation of son preference for 
-families who---for one reason or another---do not use prenatal sex selection.
+Second, birth spacing can have substantial impact on children's outcomes.
+Most of the research finds a negative impact of short spacing on child health, although 
+identifying the causal mechanisms have proven more difficult
+\citep{Conde-Agudelo2006,Conde-Agudelo2012}.
+Broadly speaking, there are three pathways that birth intervals can affect health.
+First, maternal depletion, where the mother does not have sufficient
+time to recover after a pregnancy.%
+\footnote{
+This depletion can take the form of nutrition, folate, or cervical insufficiency.
+}
+Second, disease transmission both from mother to child and between children close in age.
+Third, sibling competition, where siblings close in age compete for scarce resources and
+parental care.
+Which mechanism dominates is especially of interest when spacing decisions are driven by 
+son preference.
+Both the maternal depletion and the transmission of disease explanations predominately
+affect the subsequent child and the mother.
+Only sibling competition has the potential to negatively affect the older child.
 
-Spacing, by itself, can therefore no longer be used as a direct measure of 
-son preference, but understanding birth spacing remains a critical undertaking.
-First, 
-birth spacing is still useful in understanding son preference, 
-if combined with the likelihood of observing a boy or a girl.
-Second, 
-the duration between births may be an important factor in parents' 
-decisions, either for preference or economic reasons.
-It is, for example, possible that even parents with strong son preference 
-may reverse their decision to use prenatal sex determination---and carry 
-the next pregnancy to term whether male or female---as the duration from 
-the previous birth becomes sufficiently long.
+In India, there is evidence that both the prior and the subsequent child have higher
+likelihood of dying the closer they are spaced, although the effect is not symmetrical
+\citep{Whitworth2002,Bhargava2003,Rutstein2005,Maitra2008,Makepeace2008}.%
+\footnote{
+\cite{Bhalotra2008}, however, find that birth spacing only explain a limited amount
+of neonatal mortality.
+}
+The increased mortality risk for prior children may come from shorter breastfeeding of 
+girls to ensure that the mother can conceive again quicker, and with poor water
+quality this shorter breastfeeding may result both in higher risk of dying and shorter
+stature if the child survives \citep{Jayachandran2011,Jayachandran2017a}.
+In other countries, focus has been mostly on the subsequent birth, but there is evidence 
+in countries as diverse as Bangladesh, Brazil, and El Salvadore that
+short intervals between birth has negative health effects
+\citep{Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
 
-At a broader level, we know less about what determines spacing behavior in 
-developing countries than in developed countries.%
-\footnote{
+The potential effects of spacing are not restricted to early outcomes, although
+there is less evidence on longer term effects, and most of what we have comes from
+Western countries.
+In the US, for example, longer spacing between births increases the older sibling's
+test scores on the Peabody Individual Achievement Test, although there is no
+statistically significant effect on the younger sibling \citep{Buckles2012}.
+In line with this, close spacing appears to increase the risk of dropping out of
+high school and lower the probability of attending a post-secondary school in both the
+US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.
+These results are, however, not uniformly supported, with recent results from Sweden 
+showing no relationship between birth spacing, even if very short, and outcomes such as 
+years of education completed, earnings, and unemployment \citep{Barclay2017}.
+
+Third, the mother may also be affected by the length of the birth intervals.
+The effect of spacing on mother's outcomes have received less attention than the
+effect on children, and reviews of the literature show mixed results on mother's 
+anthropometric status \citep{Dewey2007,Conde-Agudelo2012}.
+For India, there is, however, evidence that women with first-born girls are both
+more likely to have short birth spacing and more likely to have anemia, possibly as
+the result of the short spacing resulting in maternal depletion \citep{Milazzo2018}.
+In Western countries, having a longer interval between births appear to have positive
+effects on long-term labor market outcomes, such as participation and 
+income \citep{Gough2017,Karimi2014}.
+
+[Other reasons for studying spacing]
+[Education and socio-economic status and spacing]
+Finally, we know less about what determines spacing behavior in 
+developing countries than in developed countries.
 Even the effects of access to contraceptive on spacing are uncertain.
@@
 difficult \citep{Yeakey2009}.
-}
 With increasing numbers of women entering the labor force in developing
@@
 for the design of suitable policies \citep{Portner2018}.
-Furthermore, if spacing does affect health outcomes for mother and children, it is 
-essential to understand what drives changes in spacing.
-We know, for example, that health outcomes for girls appear to improve
-in the presence of sex selection \citep{Lin2014,Hu2015}.
-It is possible that these improvements are an unintended side-effect of
-the longer spacing that arises from sex-selective abortions, rather than
-because the smaller number of girls makes them more valued as is often
-assumed.
 
-In this paper, I introduce and apply a novel empirical method that directly incorporates 
-the effects of sex-selective abortions on 
-the duration between births
-\emph{and} 
-the likelihood of a son. 
-The method can be used to analyze both situations with and without prenatal
-sex selection.
-My proposed method allows for the time since the previous 
-birth to affect the decision on sex selection.
-By examining under what circumstances sex selection decisions change with 
-spacing, we can draw a more nuanced picture of the degree of son preference.
+[how is spacing achieved?]
+\citep{Rahman1993}
+\citep{Jayachandran2011}
+\citep{Alam2018}
 
-% [Why India?]
-I apply the method to birth histories of Hindu women, using data from 
-India's National Family and Health Surveys (NFHS), covering the period 
-1972 to 2016. 
-India is a particularly compelling case.
-On the one hand, India has seen dramatic increases in the males-to-females ratio 
-at birth over the last three decades as access to prenatal sex determination 
-expanded 
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06}.%
-\footnote{
-India is not alone; both China and South Korea saw
-significant changes in the sex ratio at birth over the same period 
-\citep{Yi1993,park95}.
-}
-On the other hand, research suggests that son preference in 
-India, when measured as ideally having more boys than girls, is decreasing 
-over time and with higher education \citep{bhat03,pande07}.
-% %
-% \footnote{
-% This measure of son preference is commonly used in the literature. 
-% See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-% }
+Despite the potential important impact of birth spacing on outcomes for both
+mother and children, there has so far been no examination of what effect access to
+sex selection has had on spacing.
+We know that health outcomes for girls appear to improve in the presence of sex 
+selection \citep{Lin2014,Hu2015}.
+It is possible that these improvements are an unintended side-effect of the longer spacing 
+that arises from sex-selective abortions, rather than because the smaller number of girls 
+makes them more valued as is often assumed.
+A first step
 
-There have also been substantial changes in access and legality of
-prenatal sex determination in India over the period covered.
+[Predicted changes in spacing with sex selection]
+
+[how much longer intervals]
+ by six months to a year.
+The increase consists of three parts.
+First, starting from the time of the abortion, the uterus needs at 
+least two menstrual cycles to recover;  otherwise, the likelihood 
+of spontaneous abortion increases substantially \citep{zhou00b}.
+The second part is the waiting time to conception, which is between 
+one and six months \citep{Wang2003}.
+Finally, sex determination tests are reliable only from three months 
+of gestation onwards.
+
+Direct information on the use of sex selection is not available, but it is possible
+to compare different periods as a proxy since there has been substantial changes in access 
+and legality of prenatal sex determination in India.
 Abortion has been legal in India since 1971 and still is.
@@
 }
-% Hence, the data make it possible to show how the spacing between births and
-% sex ratios have changed with the introduction of prenatal sex determination,
-% and whether the ban affected the relationship between birth spacing and sex 
-% ratios.
+[TK something on split 1995 to 2016 into two groups?]
+
+[OLD VERSION FROM HERE]
+
+Spacing, by itself, can therefore no longer be used as a direct measure of 
+son preference, but understanding birth spacing remains a critical undertaking.
+First, 
+birth spacing is still useful in understanding son preference, 
+if combined with the likelihood of observing a boy or a girl.
+Second, 
+the duration between births may be an important factor in parents' 
+decisions, either for preference or economic reasons.
+It is, for example, possible that even parents with strong son preference 
+may reverse their decision to use prenatal sex determination---and carry 
+the next pregnancy to term whether male or female---as the duration from 
+the previous birth becomes sufficiently long.
 

### 2019-02-28 paper/sex_selection_spacing-ver2-new-intro.tex
Minor edits

@@
 The stronger the son preference, the more likely couples are to resort to sex-selective 
-abortions, and each abortion increases the interval between births.
+abortions, and each abortion automatically increases the interval between births by six 
+months to a year.%
+\footnote{
+The increase consists of three parts.
+First, starting from the time of the abortion, the uterus needs at 
+least two menstrual cycles to recover;  otherwise, the likelihood 
+of spontaneous abortion increases substantially \citep{zhou00b}.
+The second part is the waiting time to conception, which is between 
+one and six months \citep{Wang2003}.
+Finally, sex determination tests are reliable only from three months 
+of gestation onwards.
+}
 As a result, we may now observe \emph{longer} average spacing for families with stronger 
@@
 [Education and socio-economic status and spacing]
-Finally, we know less about what determines spacing behavior in 
-developing countries than in developed countries.
+Finally, we know less about what determines spacing behavior in developing countries than 
+in developed countries, and with increasing numbers of women entering the labor force in 
+developing countries, understanding how couples make timing decisions will be necessary
+for the design of suitable policies \citep{Portner2018}.
+
 Even the effects of access to contraceptive on spacing are uncertain.
@@
 difficult \citep{Yeakey2009}.
-With increasing numbers of women entering the labor force in developing
-countries, understanding how couples make timing decisions will be necessary
-for the design of suitable policies \citep{Portner2018}.
 
@@
 A first step
-
-[Predicted changes in spacing with sex selection]
-
-[how much longer intervals]
- by six months to a year.
-The increase consists of three parts.
-First, starting from the time of the abortion, the uterus needs at 
-least two menstrual cycles to recover;  otherwise, the likelihood 
-of spontaneous abortion increases substantially \citep{zhou00b}.
-The second part is the waiting time to conception, which is between 
-one and six months \citep{Wang2003}.
-Finally, sex determination tests are reliable only from three months 
-of gestation onwards.
 
@@
 [TK something on split 1995 to 2016 into two groups?]
+
+[What do we know about use of sex selection?]
 

### 2019-03-01 paper/sex_selection_spacing-ver2-new-intro.tex
Add discussion of sex selection research and minor grammar edits

@@
 }
-As a result, we may now observe \emph{longer} average spacing for families with stronger 
-son preference, precisely because it makes them more likely to use sex selection.
-To further complicate matters, families with son preference who---for one reason or 
-another---do not use prenatal sex selection may continue to have shorter birth spacing 
-than those with a lower preference for sons.
+As a result, we may now observe \emph{longer} average spacing for families with the
+strongest son preference, precisely because it makes them more likely to use sex selection.
+% To further complicate matters, families with son preference who---for one reason or 
+% another---do not use prenatal sex selection may continue to have shorter birth spacing 
+% than those with a lower preference for sons.
 
@@
 India is a particularly compelling case.
-India has long shown a strong male preference, especially in the northern states 
+India has long shown a male preference, especially in the northern states 
 \citep{Kishor1993,murthi95,arnold98}.%
@@
 }
-As a result, a significant proportion of Indian families follow a son preference based 
+A significant proportion of Indian families exhibit a son preference based 
 differential stopping behavior, where, for a given number of children, they are more 
@@
 \footnote{
-A smilar pattern is found in many other countries 
-\citep[see, for example][]{larsen98,filmer09,Altindag2016}.
+Other countries show a similar pattern
+\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
 }
-Furthermore, higher mortality risk for females than males at most ages has lead to an 
-almost continuous increase in India's overall ratio of males to females over the last 
-century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
-Over the last three decades, India has also seen dramatic increases in the 
-males-to-females ratio at birth as access to prenatal sex determination 
-expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012}.
-In addition, fertility has declined substantially, to the point where it is now
+Furthermore, mortality risk for it higher for females than males at most ages, 
+resulting in an almost continuous increase in India's overall ratio of males to females 
+over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
+
+% [What do we know about use of sex selection?]
+Over the last three decades, India has seen dramatic increases in the males-to-females 
+ratio at birth as access to prenatal sex determination expanded 
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012,Portner2015b}.
+Also, fertility has declined substantially, to the point where it is now
 at, or even below, replacement in some areas 
 \citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-This decline in fertility, combined with the strong preference for sons, has lead to an 
-intensified pressure to use sex selection \citep{Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
+This decline in fertility, combined with a strong preference for sons, has intensified 
+the pressure to use sex selection \citep{Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
 \footnote{
@@
 }
+Within families, the strongest predictor of the use of sex selection at a given parity is 
+the sex composition of previous children \citep{retherford03b,jha06,abrevaya09,Portner2015b}.
+For families without a son, the higher the parity is, the higher is the probability
+of having a son as the next birth.
+The use of sex selection also increases with socioeconomic status, especially 
+education, and is more prevalent in cities than in rural areas, both possibly because 
+of lower desired fertility \citep{retherford03b,jha06,Portner2015b}.
 
@@
 access to sex selection.
-First, it has been widely used as a measure of son preference.
-In India the sex of the last-born child significantly impact the duration to next birth,
-with the expected birth interval about three percent longer if the last-born was son than
+First, researchers have made extensive use of birth spacing as a measure of son preference, 
+and it is critical to understand to what extent spacing is still useful as a measure of son 
+preference and develop new methods if needed.
+In India, the sex of the last-born child significantly impacts the duration to next birth,
+with the expected birth interval about three percent longer if the last-born was a son than
 if it was a daughter \citep{Bhalotra2008,Kumar2016}.
-Similarly, ethic Indians in South Africa also show a longer duration after the birth of a 
+Similarly, ethnic Indians in South Africa also show a longer duration after the birth of a 
 son than after a daughter \citep{Gangadharan2003}.%
 \footnote{
-Ethic Indians in Malaysia do, however, show little evidence of son preference, although
-the sample sizes are very small \citep{Pong1994}.
+Ethnic Indians in Malaysia do, however, show little evidence of son preference, although
+the sample sizes are small \citep{Pong1994}.
 }
-India is not alone in sex composition affecting subsequent birth spacing.
 In both Bangladesh and Vietnam the more boys a family has the longer the expected duration 
 to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
-Outside Asia the evidence is more mixed.
-North Africa shows shorter spacing in the absense of sons, while a similar pattern does
-not exists in Sub-Saharan Africa \citep{Rossi2015}.%
+Outside Asia, the evidence is more mixed.
+North Africa shows shorter spacing in the absence of sons, while a similar pattern does
+not exist in Sub-Saharan Africa \citep{Rossi2015}.%
 \footnote{
@@
 
-Second, birth spacing can have substantial impact on children's outcomes.
+Second, birth spacing can have a substantial impact on children's outcomes.
 Most of the research finds a negative impact of short spacing on child health, although 
@@
 \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
-Broadly speaking, there are three pathways that birth intervals can affect health.
-First, maternal depletion, where the mother does not have sufficient
-time to recover after a pregnancy.%
+There are three pathways that birth intervals can affect health.
+First, there is maternal depletion, where the mother does not have sufficient time to 
+recover after her last pregnancy before she become pregnant again.%
 \footnote{
@@
 parental care.
-Which mechanism dominates is especially of interest when spacing decisions are driven by 
-son preference.
+Which mechanism dominates is of particular interest when son preference drives spacing 
+decisions.
 Both the maternal depletion and the transmission of disease explanations predominately
@@
 
-In India, there is evidence that both the prior and the subsequent child have higher
-likelihood of dying the closer they are spaced, although the effect is not symmetrical
-\citep{Whitworth2002,Bhargava2003,Rutstein2005,Maitra2008,Makepeace2008}.%
+In India, there is evidence that both the prior and the subsequent child have worse health 
+outcomes and a higher likelihood of dying the shorter the interval between them, although 
+the effect is not symmetrical
+\citep{Whitworth2002,Bhargava2003,Rutstein2005,Maitra2008,Makepeace2008,Ghosh2018}.%
 \footnote{
-\cite{Bhalotra2008}, however, find that birth spacing only explain a limited amount
+\cite{Bhalotra2008}, however, find that birth spacing only explains a limited amount
 of neonatal mortality.
@@
 in countries as diverse as Bangladesh, Brazil, and El Salvadore that
-short intervals between birth has negative health effects
+short intervals between births have adverse health effects
 \citep{Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
@@
 The potential effects of spacing are not restricted to early outcomes, although
-there is less evidence on longer term effects, and most of what we have comes from
-Western countries.
-In the US, for example, longer spacing between births increases the older sibling's
+there is less evidence on longer-term effects, and most comes from Western countries.
+In the US, for example, a longer spacing between births increases the older sibling's
 test scores on the Peabody Individual Achievement Test, although there is no
@@
 Third, the mother may also be affected by the length of the birth intervals.
-The effect of spacing on mother's outcomes have received less attention than the
-effect on children, and reviews of the literature show mixed results on mother's 
-anthropometric status \citep{Dewey2007,Conde-Agudelo2012}.
+The effect of spacing on mothers have received less attention than the effect on children, 
+and reviews of the literature show mixed results on mother's anthropometric status 
+\citep{Dewey2007,Conde-Agudelo2012}.
 For India, there is, however, evidence that women with first-born girls are both
@@
 
-[Other reasons for studying spacing]
-[Education and socio-economic status and spacing]
 Finally, we know less about what determines spacing behavior in developing countries than 
-in developed countries, and with increasing numbers of women entering the labor force in 
-developing countries, understanding how couples make timing decisions will be necessary
-for the design of suitable policies \citep{Portner2018}.
+in developed countries, and with declining fertility and increasing numbers of women 
+entering the labor force in developing countries, understanding how couples make timing 
+decisions will be necessary for the design of suitable policies \citep{Portner2018}.%
+\footnote{
+It is clear that birth spacing does respond to policies in both developed and 
+developing countries \citep{Pettersson-Lidbom2009,Todd2012,Meckel2015,Ghosh2018}.
+}
+For example, the evidence on the effects of education and socio-economic status on
+birth intervals is mixed, with some research showing either a positive association, no
+association, or one that is changing over time 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
 
-Even the effects of access to contraceptive on spacing are uncertain.
-On the one hand, access to contraceptives allows women to avoid too 
-short spacing between birth, which would increase birth spacing.
-On the other hand, increased reliability of access and effectiveness of
-contraceptives can lead to shorter spacing between births 
-\citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level 
-of contraception, which results in longer spacing, to avoid having 
-too many children by accident.
-But, as contraception becomes more effective parents can more
-easily avoid future births, allowing them to reduce the spacing 
-between births without having to worry about overshooting their 
-preferred number of children.
-This idea may explain why better-educated women have
-shorter spacing than less educated women in some instances
- \citep{Tulasidhar1993,Whitworth2002}.
-These two counteracting effects may explain why finding statistically 
-significant effects of contraception use on birth spacing is 
-difficult \citep{Yeakey2009}.
+Even the effects of access to contraceptive on spacing are unclear.
+On the one hand, access to contraceptives allows women to avoid too short spacing between 
+birth, which would increase birth spacing.
+On the other hand, increased reliability of access and effectiveness of contraceptives can 
+lead to shorter intervals between births  \citep{Keyfitz1971,Heckman1976}.
+With less reliable contraception parents choose a higher level of contraception, which 
+results in longer spacing, to avoid having too many children by accident.
+However, as contraception becomes more effective parents can more easily avoid future 
+births, allowing them to reduce the spacing between births without having to worry about 
+overshooting their preferred number of children.
+This idea may explain why better-educated women have shorter spacing than less educated 
+women in some instances but not in others.
+These two counteracting effects may explain why finding statistically significant effects 
+of contraception use on birth spacing is difficult \citep{Yeakey2009}.%
+\footnote{
+There is evidence in Matlab that the effect of son preference on birth spacing is
+stronger in areas with better access to family planning \citep{Rahman1993}.
+Other evidence, however, points to families ability to time birth, even in the absence
+of modern contraceptives \citep{Jayachandran2011,Alam2018}.
+}
 
-[how is spacing achieved?]
-\citep{Rahman1993}
-\citep{Jayachandran2011}
-\citep{Alam2018}
+TK spacing and decline in fertility (with and without sex selection)
 
@@
 sex selection has had on spacing.
-We know that health outcomes for girls appear to improve in the presence of sex 
-selection \citep{Lin2014,Hu2015}.
-It is possible that these improvements are an unintended side-effect of the longer spacing 
-that arises from sex-selective abortions, rather than because the smaller number of girls 
-makes them more valued as is often assumed.
-A first step
+
+TK What questions I am asking
+
+TK How I am answering them
 
@@
 
-[What do we know about use of sex selection?]
-
-[OLD VERSION FROM HERE]
-
-Spacing, by itself, can therefore no longer be used as a direct measure of 
-son preference, but understanding birth spacing remains a critical undertaking.
-First, 
-birth spacing is still useful in understanding son preference, 
-if combined with the likelihood of observing a boy or a girl.
-Second, 
-the duration between births may be an important factor in parents' 
-decisions, either for preference or economic reasons.
-It is, for example, possible that even parents with strong son preference 
-may reverse their decision to use prenatal sex determination---and carry 
-the next pregnancy to term whether male or female---as the duration from 
-the previous birth becomes sufficiently long.
+We know that health outcomes for girls appear to improve in the presence of sex 
+selection \citep{Lin2014,Hu2015}.
+It is possible that these improvements are an unintended side-effect of the longer spacing 
+that arises from sex-selective abortions, rather than because the smaller number of girls 
+makes them more valued as is often assumed.
+A first step
 
 % [Results]
-There are four main results.
+There are three main results.
 First, there has been a general increase in the length of spacing between births
 over the four decades covered by the data.
-The exception is for first births, where the median duration has either
-remained the same or slightly declined, although this hides a
-significant compression of the variation in spell length.
 Second, the most substantial increase in spacing is for the women who
@@
 son through higher fertility rather than the use of sex selection.
-Finally, sex ratios are the most likely to decline within spells at
-lower-order spells, where the pressure to provide a son is smaller, and
-are more likely to increase or remain consistently high for higher-order
-spells, where the pressure to ensure a son is high.
 

### 2019-03-02 paper/sex_selection_spacing-ver2-new-intro.tex
Minor edits

@@
 This decline in fertility, combined with a strong preference for sons, has intensified 
-the pressure to use sex selection \citep{Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
+the pressure to use sex selection 
+\citep{das_gupta97,Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
 \footnote{
@@
 
-Despite the potential important impact of birth spacing on outcomes for both
-mother and children, there has so far been no examination of what effect access to
-sex selection has had on spacing.
+Despite the increasing use of sex selection, the extensive use of spacing to measure son 
+preference, and the important impacts of spacing on outcomes for both mother and children  
+there has so far been no examination of what effect access to sex selection has had on 
+spacing.
 
@@
 
+[move to conclusion?]
 We know that health outcomes for girls appear to improve in the presence of sex 
@@
 
-% [Results]
+% [Results - need updating]
 There are three main results.

### 2019-03-03 paper/sex_selection_spacing-ver2.tex
Minor edits
Make all code and paper run without breaking

@@
 \usepackage{xfrac}
+\usepackage{placeins}
 
@@
 
-\date{November 2018}
+\date{March 2018}
 
@@
 \noindent
+
+[TK rewrite with region results]
 
@@
 twelve months. 
-I introduce a statistical method that simultaneously
-accounts for how sex selection increases the spacing between 
-births and the likelihood of a son. 
-Using four rounds of India's National
-Family and Health Surveys, I show that, except for first births,
+I introduce a statistical method that simultaneously accounts for how sex selection 
+increases both the spacing between births and the likelihood of a son. 
+Using the four rounds of India's National Family and Health Surveys, I show that
 the spacing between births increased substantially over the last four
@@
 selection, with medium-educated women showing mixed results.
-Finally,
-sex ratios are more likely to decline within spells at lower parities,
-where there is less pressure to ensure a son, and more likely to
-increase or remain consistently high for higher-order spells, where the
-pressure to provide a son is high.
 
@@
 
-Parents' spacing of births has long served as a measure of son preference 
-\citep{Leung1988}.
-Before prenatal sex determination became available, the only recourse for 
-parents who wanted a son---but did not yet have one---was to have the next 
-birth sooner.
-Son preference is therefore often associated with shorter spacing after the 
-births of girls than boys 
-\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997,Soest2012,Rossi2015}.
-Shorter spacing is, in turn, associated with worse health outcomes for girls 
-and mothers 
-\citep{arnold98,Conde-Agudelo2000,Whitworth2002,Razzaque2005,Rutstein2005,Conde-Agudelo2006}.%
+Birth spacing has long served as a measure of son preference, with strong
+son preference typically associated with shorter birth intervals the
+fewer sons a family has \citep{ben-porath76b,Leung1988}.
+However, the introduction of prenatal sex determination has the potential to
+fundamentally change the relationship between son preference and birth spacing.
+The stronger the son preference, the more likely couples are to resort to sex-selective 
+abortions, and each abortion automatically increases the interval between births by six 
+months to a year.%
 \footnote{
-Parents are also more likely to cease childbearing after the birth of 
-a son than after a daughter 
-\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
-}
-
-However, the introduction of prenatal sex determination fundamentally changed the 
-relationship between son preference and birth spacing.
-Couples, who had shorter birth spacing before because of son preference,
-now have access to prenatal sex determination and sex-selective abortions,
-and each abortion increases birth spacing by six months to a year.
 The increase consists of three parts.
@@
 of gestation onwards.
-
-As a result, we now have a situation where we may observer \emph{longer} spacing
-for families with daughters than for families with sons, precisely because
-strong son preference leads them to use sex selection.
-Working in the opposite direction, couples with strong son preference
-will likely still try to conceive earlier in the absence of sons. 
-They may even shorten the time until conception, knowing that they might
-have to go through multiple pregnancies and abortions before they
-conceive a son.
-To further complicate matters, we can still observe shorter birth spacing 
-after the births of daughters as a representation of son preference for 
-families who---for one reason or another---do not use prenatal sex selection.
-
-Spacing, by itself, can therefore no longer be used as a direct measure of 
-son preference, but understanding birth spacing remains a critical undertaking.
-First, 
-birth spacing is still useful in understanding son preference, 
-if combined with the likelihood of observing a boy or a girl.
-Second, 
-the duration between births may be an important factor in parents' 
-decisions, either for preference or economic reasons.
-It is, for example, possible that even parents with strong son preference 
-may reverse their decision to use prenatal sex determination---and carry 
-the next pregnancy to term whether male or female---as the duration from 
-the previous birth becomes sufficiently long.
-
-At a broader level, we know less about what determines spacing behavior in 
-developing countries than in developed countries.%
-\footnote{
-Even the effects of access to contraceptive on spacing are uncertain.
-On the one hand, access to contraceptives allows women to avoid too 
-short spacing between birth, which would increase birth spacing.
-On the other hand, increased reliability of access and effectiveness of
-contraceptives can lead to shorter spacing between births 
-\citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level 
-of contraception, which results in longer spacing, to avoid having 
-too many children by accident.
-But, as contraception becomes more effective parents can more
-easily avoid future births, allowing them to reduce the spacing 
-between births without having to worry about overshooting their 
-preferred number of children.
-This idea may explain why better-educated women have
-shorter spacing than less educated women in some instances
- \citep{Tulasidhar1993,Whitworth2002}.
-These two counteracting effects may explain why finding statistically 
-significant effects of contraception use on birth spacing is 
-difficult \citep{Yeakey2009}.
-}
-With increasing numbers of women entering the labor force in developing
-countries, understanding how couples make timing decisions will be necessary
-for the design of suitable policies \citep{Portner2018}.
-Furthermore, if spacing does affect health outcomes for mother and children, it is 
-essential to understand what drives changes in spacing.
-We know, for example, that health outcomes for girls appear to improve
-in the presence of sex selection \citep{Lin2014,Hu2015}.
-It is possible that these improvements are an unintended side-effect of
-the longer spacing that arises from sex-selective abortions, rather than
-because the smaller number of girls makes them more valued as is often
-assumed.
-
-In this paper, I introduce and apply a novel empirical method that directly incorporates 
-the effects of sex-selective abortions on 
-the duration between births
+}
+As a result, we may now observe \emph{longer} average spacing for families with the
+strongest son preference, precisely because it makes them more likely to use sex selection.
+% To further complicate matters, families with son preference who---for one reason or 
+% another---do not use prenatal sex selection may continue to have shorter birth spacing 
+% than those with a lower preference for sons.
+
+In this paper, I examine how birth spacing in India has changed over time and across 
+groups with the introduction of sex selection.
+I introduce and apply an empirical method that directly incorporates the effects of 
+sex-selective abortions on the duration between births 
 \emph{and} 
@@
 sex selection.
-My proposed method allows for the time since the previous 
-birth to affect the decision on sex selection.
-By examining under what circumstances sex selection decisions change with 
-spacing, we can draw a more nuanced picture of the degree of son preference.
-
-% [Why India?]
-I apply the method to birth histories of Hindu women, using data from 
+I apply the method to birth histories of Hindu women, using data from the four
 India's National Family and Health Surveys (NFHS), covering the period 
 1972 to 2016.
+
+% [Why India?]
 India is a particularly compelling case.
-On the one hand, India has seen dramatic increases in the males-to-females ratio 
-at birth over the last three decades as access to prenatal sex determination 
-expanded 
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06}.%
+India has a long history of male preference, especially in the northern states 
+\citep{Kishor1993,murthi95,arnold98}.
+A significant proportion of Indian families exhibit a son preference based 
+differential stopping behavior, where, for a given number of children, they are more 
+likely to have an additional child if they have not yet reached their preferred number of 
+sons \citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
 \footnote{
-India is not alone; both China and South Korea saw
-significant changes in the sex ratio at birth over the same period 
-\citep{Yi1993,park95}.
-}
-On the other hand, research suggests that son preference in 
-India, when measured as ideally having more boys than girls, is decreasing 
-over time and with higher education \citep{bhat03,pande07}.
-% %
-% \footnote{
-% This measure of son preference is commonly used in the literature. 
-% See, for example, \citet{clark00}, \citet{Jensen2009}, and \cite{Hu2015}.
-% }
-
-There have also been substantial changes in access and legality of
-prenatal sex determination in India over the period covered.
+Other countries show a similar pattern
+\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
+}
+Moreover, mortality risk is higher for females than males for most ages groups, and
+there has been an almost continuous increase in India's overall ratio of males to females 
+over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
+
+% [What do we know about use of sex selection?]
+Over the last three decades, India has seen dramatic increases in the males-to-females 
+ratio at birth as access to prenatal sex determination expanded 
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012,Portner2015b}.
+Simultaneously, fertility has declined substantially, to the point where it is now at, or 
+even below, replacement in some areas 
+\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
+This decline in fertility, combined with a continued strong preference for sons, has 
+intensified the pressure to use sex selection 
+\citep{das_gupta97,Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
+\footnote{
+In some instances, however, the fertility decline appears to have created a stronger 
+aversion to daughters rather than a stronger preference for son \citet{DiamondSmith2008}.
+}
+At household level the strongest predictor of the use of sex selection is the sex 
+composition of previous children \citep{retherford03b,jha06,abrevaya09,Portner2015b}.
+For families without a son, the higher the parity, the higher is the probability
+of having a son as the next birth.
+The use of sex selection also increases with socioeconomic status, especially 
+education, and is more prevalent in cities than in rural areas, both possibly because 
+of lower desired fertility \citep{retherford03b,jha06,Portner2015b}.
+
+% [Why spacing?] 
+There are four main reasons for examining birth spacing and how it changes with 
+access to sex selection.
+First, researchers have made extensive use of birth spacing as a measure of son preference, 
+and it is critical to understand to what extent spacing is still useful as a measure of son 
+preference and develop new methods if needed.
+In India, the sex of the last-born child significantly impacts the duration to next birth,
+with the expected birth interval about three percent longer if the last-born was a son than
+if it was a daughter \citep{Bhalotra2008,Kumar2016}.
+Similarly, ethnic Indians in South Africa also show a longer duration after the birth of a 
+son than after a daughter \citep{Gangadharan2003}.%
+\footnote{
+Ethnic Indians in Malaysia do, however, show little evidence of son preference, although
+the sample sizes are small \citep{Pong1994}.
+}
+In both Bangladesh and Vietnam the more boys a family has the longer the expected duration 
+to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
+Outside Asia, the evidence is more mixed.
+North Africa shows shorter spacing in the absence of sons, while a similar pattern does
+not exist in Sub-Saharan Africa \citep{Rossi2015}.%
+\footnote{
+A possible exception is Senegal, where women with a higher risk of widowhood show
+shorter birth spacing until they have secured a son \citep{Lambert2016}.
+}
+
+Second, birth spacing can have a substantial impact on children's outcomes.
+Most of the research finds a negative impact of short spacing on child health, although 
+identifying the causal mechanisms have proven more difficult
+\citep{Conde-Agudelo2006,Conde-Agudelo2012}.
+There are three pathways that birth intervals can affect health.
+First, there is maternal depletion, where the mother does not have sufficient time to 
+recover after her last pregnancy before she become pregnant again.%
+\footnote{
+This depletion can take the form of nutrition, folate, or cervical insufficiency.
+}
+Second, disease transmission both from mother to child and between children close in age.
+Third, sibling competition, where siblings close in age compete for scarce resources and
+parental care.
+Which mechanism dominates is of particular interest when son preference drives spacing 
+decisions.
+Both the maternal depletion and the transmission of disease explanations predominately
+affect the subsequent child and the mother.
+Only sibling competition has the potential to negatively affect the older child.
+
+In India, there is evidence that both the prior and the subsequent child have worse health 
+outcomes and a higher likelihood of dying the shorter the interval between them, although 
+the effect is not symmetrical
+\citep{Whitworth2002,Bhargava2003,Rutstein2005,Maitra2008,Makepeace2008,Ghosh2018}.%
+\footnote{
+\cite{Bhalotra2008}, however, find that birth spacing only explains a limited amount
+of neonatal mortality.
+}
+The increased mortality risk for prior children may come from shorter breastfeeding of 
+girls to ensure that the mother can conceive again quicker, and with poor water
+quality this shorter breastfeeding may result both in higher risk of dying and shorter
+stature if the child survives \citep{Jayachandran2011,Jayachandran2017a}.
+In other countries, focus has been mostly on the subsequent birth, but there is evidence 
+in countries as diverse as Bangladesh, Brazil, El Salvadore, and Pakistan that
+short intervals between births have adverse health effects
+\citep{Cleland1984,Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
+
+The potential effects of spacing are not restricted to early outcomes, although
+there is less evidence on longer-term effects, and most comes from Western countries.
+In the US, for example, a longer spacing between births increases the older sibling's
+test scores on the Peabody Individual Achievement Test, although there is no
+statistically significant effect on the younger sibling \citep{Buckles2012}.
+In line with this, close spacing appears to increase the risk of dropping out of
+high school and lower the probability of attending a post-secondary school in both the
+US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.
+These results are, however, not uniformly supported, with recent results from Sweden 
+showing no relationship between birth spacing, even if very short, and outcomes such as 
+years of education completed, earnings, and unemployment \citep{Barclay2017}.
+
+Third, the mother may also be affected by the length of the birth intervals.
+The effect of spacing on mothers have received less attention than the effect on children, 
+and reviews of the literature show mixed results on mother's anthropometric status 
+\citep{Dewey2007,Conde-Agudelo2012}.
+For India, there is, however, evidence that women with first-born girls are both
+more likely to have short birth spacing and more likely to have anemia, possibly as
+the result of the short spacing resulting in maternal depletion \citep{Milazzo2018}.
+In Western countries, having a longer interval between births appear to have positive
+effects on long-term labor market outcomes, such as participation and 
+income \citep{Gough2017,Karimi2014}.
+
+Finally, we know less about what determines spacing behavior in developing countries than 
+in developed countries, and with declining fertility and increasing numbers of women 
+entering the labor force in developing countries, understanding how couples make timing 
+decisions will be necessary for the design of suitable policies \citep{Portner2018}.%
+\footnote{
+It is clear that birth spacing does respond to policies in both developed and 
+developing countries \citep{Pettersson-Lidbom2009,Todd2012,Meckel2015,Ghosh2018}.
+}
+For example, the evidence on the effects of education and socio-economic status on
+birth intervals is mixed, with some research showing either a positive association, no
+association, or one that is changing over time 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
+
+Even the effects of access to contraceptive on spacing are unclear.
+On the one hand, access to contraceptives allows women to avoid too short spacing between 
+birth, which would increase birth spacing.
+On the other hand, increased reliability of access and effectiveness of contraceptives can 
+lead to shorter intervals between births  \citep{Keyfitz1971,Heckman1976}.
+With less reliable contraception parents choose a higher level of contraception, which 
+results in longer spacing, to avoid having too many children by accident.
+However, as contraception becomes more effective parents can more easily avoid future 
+births, allowing them to reduce the spacing between births without having to worry about 
+overshooting their preferred number of children.
+This idea may explain why better-educated women have shorter spacing than less educated 
+women in some instances but not in others.
+These two counteracting effects may explain why finding statistically significant effects 
+of contraception use on birth spacing is difficult \citep{Yeakey2009}.%
+\footnote{
+There is evidence in Matlab that the effect of son preference on birth spacing is
+stronger in areas with better access to family planning \citep{Rahman1993}.
+Other evidence, however, points to families ability to time birth, even in the absence
+of modern contraceptives \citep{Jayachandran2011,Alam2018}.
+}
+
+TK spacing and decline in fertility (with and without sex selection)
+
+Despite the increasing use of sex selection, the extensive use of spacing to measure son 
+preference, and the important impacts of spacing on outcomes for both mother and children  
+there has so far been no examination of what effect access to sex selection has had on 
+spacing.
+
+TK What questions I am asking
+
+TK How I am answering them
+
+Direct information on the use of sex selection is not available, but it is possible
+to compare different periods as a proxy since there has been substantial changes in access 
+and legality of prenatal sex determination in India.
 Abortion has been legal in India since 1971 and still is.
@@
 }
-% Hence, the data make it possible to show how the spacing between births and
-% sex ratios have changed with the introduction of prenatal sex determination,
-% and whether the ban affected the relationship between birth spacing and sex 
-% ratios.
-
-% [Results]
-There are four main results.
+[TK something on split 1995 to 2016 into two groups?]
+
+% [Results - need updating]
+There are three main results.
 First, there has been a general increase in the length of spacing between births
 over the four decades covered by the data.
-The exception is for first births, where the median duration has either
-remained the same or slightly declined, although this hides a
-significant compression of the variation in spell length.
 Second, the most substantial increase in spacing is for the women who
@@
 
-The unit of analysis is a spell, the period from one birth---or for the first spell from 
-marriage---to the next birth.
+The unit of analysis is a spell, the period from one birth to the next.
 The model is a discrete time, non-proportional, competing risk hazard model with two exit 
@@
 }
-Both the non-randomness and differential spacing can be captured with a competing risk set 
-up.
+Both the non-randomness and differential spacing can be captured with a competing risk 
+set up.
 
@@
 }
-Second, the introduction of prenatal sex determination likely exacerbates any bias 
-from the proportionality assumption since sex-selective abortion use varies across groups,
+Second, the introduction of prenatal sex determination exacerbates any bias from the 
+proportionality assumption since sex-selective abortion use varies across groups,
 which affects birth spacing, and because a household's use of sex selection may vary 
@@
 
-\input{../tables/bootstrap_duration_sex_ratio_low.tex}
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_urban_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_urban_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_urban_all}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_rural_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_rural_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_rural_all}} 
+\caption{low education}
+\end{figure}
+
+\input{../tables/bootstrap_duration_sex_ratio_low_all.tex}
 
@@
 
-\subsection{Middle Education Women}
-
-\input{../tables/bootstrap_duration_sex_ratio_med.tex}
+\subsection{Low to Medium Education Women}
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_urban_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_urban_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_urban_all}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_rural_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_rural_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_rural_all}} 
+\caption{med education}
+\end{figure}
+
+\input{../tables/bootstrap_duration_sex_ratio_med_all.tex}
 
@@
 
-\input{../tables/bootstrap_duration_sex_ratio_high.tex}
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
+\caption{high education}
+\end{figure}
+
+\input{../tables/bootstrap_duration_sex_ratio_high_all.tex}
 
@@
 
-\begin{figure}[htpb]
-\centering
-\setcounter{subfigure}{-1}
-\subfloat[Rural Women with No Education]{
-    \begin{minipage}{0.48\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[Urban Women with 8 or More Years of Education]{
-    \begin{minipage}{0.48\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{
-Survival curves conditional on progression to first birth; start point is month of marriage
-}
-\label{fig:pps_spell1}
-\end{figure}
+% \begin{figure}[htpb]
+% \centering
+% \setcounter{subfigure}{-1}
+% \subfloat[Rural Women with No Education]{
+%     \begin{minipage}{0.48\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_low_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{0}
+% \subfloat[Urban Women with 8 or More Years of Education]{
+%     \begin{minipage}{0.48\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_high_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{
+% Survival curves conditional on progression to first birth; start point is month of marriage
+% }
+% \label{fig:pps_spell1}
+% \end{figure}
 
@@
 
-\subsection{Does Sex Selection Change within Spells?}
-
-The above results show that length of birth spacing increased 
-more for women with only girls than for other sex compositions
-as sex ratios became more male-biased, presumably because
-of increased use of sex selection.
-Neither the median spacing or the conditional survival curves,
-however, can tell us whether sex selection varies \emph{within}
-a spell or provide any information about the likelihood of
-exiting a spell with a birth.
-To understand both, I now turn to the standard survival curves
-and predicted sex ratios by spell duration.
-
-\begin{figure}[htpb!]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Urban}}
-\setcounter{subfigure}{-2}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Rural}}
-\setcounter{subfigure}{0}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of 
-no birth yet from nine months after first birth for women with a girl
-as their first child and eight or more years of education 
-for the 1995--2004 and 2005--2016 periods
-} 
-\label{fig:decreasing_sex_ratio} 
-\end{figure}
-
-\begin{figure}[htpb!]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
-\setcounter{subfigure}{-2}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{-1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
-\setcounter{subfigure}{0}
-\subfloat[1995--2004]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_bg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\setcounter{subfigure}{1}
-\subfloat[2005--2016]{
-   \begin{minipage}{0.39\textwidth}
-       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_pc}}\\
-       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_bg_s}}
-       \captionsetup[subfigure]{labelformat=parens}
-   \end{minipage}
-}
-\caption{Predicted probability of having a boy and probability of 
-no birth yet from nine months after second birth for urban women with
-eight or more years of education 
-for the 1995--2004 and 2005--2016 periods
-} 
-\label{fig:increasing_sex_ratio} 
-\end{figure}
-
-The predicted sex ratio may change within a spell for, at
-least, two reasons.
-First, parents may stop using prenatal sex determination within
-a spell once the duration from the previous birth becomes long enough.
-The desire for short spacing could, for example, arise from 
-economies of scale in childbearing and rearing that parents lose 
-if children are born too far apart \citep[p 374]{schultz97}. 
-In this case, we should observe the predicted sex ratio decline
-with spell length.
-
-Second, if the degree of son preference varies across women within 
-the sample, but their behavior is not affected by duration from the 
-previous birth, we should observe an increasing share of births come from 
-parents with stronger son preference as the duration from the
-previous birth increases.
-Whereas the early births are a combination of births to
-people with lower son preference and those with stronger son
-preference who conceived a son in the first or second pregnancy,
-births later in the spell are then predominately from those with stronger
-son preference who have not yet conceived a son.
-In this case, we should see an increase in the sex ratio 
-as duration increases.
-
-Figures \ref{fig:decreasing_sex_ratio} and \ref{fig:increasing_sex_ratio} show
-examples of how sex ratio behave within spells.
-Both are for women with eight or more education since the results above indicate
-that they are the most likely to use sex selection or other means of achieving 
-an unequal sex ratio.
-Figure \ref{fig:decreasing_sex_ratio} shows results for the second spell for
-the 1995--2004 and 2005--2016 periods for women with a girl as their first
-child by area of residence.
-Figure \ref{fig:increasing_sex_ratio} shows results for the third spell for
-the same two periods for urban women with either two girls or one boy and one
-girl as their first two children.
-
-Within the second spell, both urban and rural women show a declining
-sex ratio as duration increases for the 1995--2004 period, whereas there
-is little change, or possibly a small increase, with duration for the 
-2005--2016 period.
-These results are consistent with a situation where fertility is declining
-over time leaving less room for a change in the decision to use sex selection.
-Fertility decline is not immediately apparent from the second spell 
-results, but the third spell shows that the likelihood of progressing from
-two to third children declines by approximately 15 percentage points if
-the woman has given birth to a boy.
-
-The third spell figures show a very different situation with substantial 
-increases in sex ratios.
-The high sex ratio for women with two girls is likely 
-motivated by the combined desire to limit fertility and ensure a son;
-similarly to the situation for the second spell as shown in 
-Figure \ref{fig:decreasing_sex_ratio} (b) and (d).
-
-The increase in sex ratio with duration for women who already have
-given birth to a boy likely illustrates the case where there is a
-combination of degrees of son preference.
-Say that one group wants one son and after that will not use sex
-selection, whereas another group has a strong preference for two
-sons (or either have or expect to lose the boy they already have)
-and that the two groups conceive at the same rate.
-In that case, we should expect precisely the increasing sex ratios
-we observe, especially given the declining fertility over time.
-
+\FloatBarrier
 \section{Conclusion\label{sec:conclusion}}
@@
 time \citep{Yeakey2009}.
-
-The empirical model allows for the effects of covariates
-to vary within the spell. 
-Non-proportionality is essential because the use of sex selection may 
-vary within a spell. 
-The use of sex selection may change either because preferences for not 
-too long spacing between births override the preference for sons or 
-because of selection, where
-the women who remain in a spell are those with the strongest son
-preference who have been through multiple pregnancies because the
-fetuses were female. 
-Because these move in opposite directions, I cannot
-directly establish the extent to which they affect the results. 
-Both are, however, present, as can be seen from the cases where there is
-either a decline in sex ratio with spell duration or a substantial
-increase with spell duration. 
-The first case is most likely at lower
-parities where there is still less pressure to ensure a son, which
-allows any preference for shorter spacing to play more of a role. 
-The second is most likely for higher
-parities where the desire to limit further childbearing and ensure a son
-dominates any preferences for shorter spacing.
-
-The potential for changes in sex ratio within a spell means that
-censoring is an important issue when trying to understand how the sex
-ratio changes over time, and especially when it comes to establishing
-whether the use of sex selection is increasing or decreasing.
-Take, for example, the case of women with eight or more years of
-education in the last period. 
-If we look at women who started their third spell in either the
-2005--2009 or the 2010--2014 periods and we treat end of 2015
-as the cut-off point, then the observed sex ratio for the 2005--2009
-women is 55.99\% boys while it is 55.38\% for women who started 
-in the 2010--2014 period.%
-\footnote{
-The calculations combines urban and rural women; the basis result 
-changes little if I split by area of residence.
-I chose the 2014 cut-off to ensure that both groups cover 
-five years, even though NFHS-4 took place in 2015 and 2016.
-}
-It would, therefore, appear that the use of sex selection for
-this spell is slightly decreasing over time.
-This interpretation, however, ignores the role of censoring.
-If we use the estimation results to predict final sex ratio
-once childbearing for the third spell is over, the predicted
-sex ratios are 56.10\% boys and 56.08\% boys for the 
-2005--2009 and the 2010--2015 starts, which indicates
-virtually no change over time.
-The reason for the difference is that while we would have 
-observed 7,134 birth out of a predicted 7,451 total number 
-of births for the 2005--2009 start, we would only have observed 
-3,348 births out of a predicted 8,842 for the 2010--2014 group.
 
@@
 births, or changing son preference?
-There is some early evidence that sample selection can make it appear that
-girls are healthier, even though the underlying cause is a combination
-of sex selection and higher mortality together with recall 
-error \citep{Portner2018a}. 
+There is some evidence that sample selection can make it appear that girls are healthier, 
+even though the underlying cause is a combination of sex selection and higher mortality 
+together with recall error \citep{Portner2018a}. 
 Understanding what role these factors play in better health for
@@
 temporarily, worsen health outcomes for girls.
+
+[move to conclusion?]
+We know that health outcomes for girls appear to improve in the presence of sex 
+selection \citep{Lin2014,Hu2015}.
+It is possible that these improvements are an unintended side-effect of the longer spacing 
+that arises from sex-selective abortions, rather than because the smaller number of girls 
+makes them more valued as is often assumed.
+A first step
 
@@
 
+\section{[Bootstrap Results by Region]}
+
+\clearpage
+\newpage
+
 \section{Additional Duration Results}
@@
 
-\input{../tables/bootstrap_duration_p25_p75_low.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_med.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high.tex}
+\input{../tables/bootstrap_duration_p25_p75_low_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_med_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_all.tex}
 
@@
 
-\subsection{First Spell}
-
-\input{../figures/appendix_spell1_low.tex}
-
-\input{../figures/appendix_spell1_med.tex}
-
-\input{../figures/appendix_spell1_high.tex}
-
-\begin{figure}[htpb]
-\centering
-\caption*{No Education}
-\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
-\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
-\caption*{1-7 Years of Education}
-\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
-\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
-\caption*{8 or more Years of Education}
-\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
-\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
-\caption{Survival curves conditional on progression to first birth; start point is month of marriage}
-\label{fig:results_spell1_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
+% \subsection{First Spell}
+% 
+% \input{../figures/appendix_spell1_low.tex}
+% 
+% \input{../figures/appendix_spell1_med.tex}
+% 
+% \input{../figures/appendix_spell1_high.tex}
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{No Education}
+% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
+% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
+% \caption*{1-7 Years of Education}
+% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
+% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
+% \caption*{8 or more Years of Education}
+% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
+% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
+% \caption{Survival curves conditional on progression to first birth; start point is month of marriage}
+% \label{fig:results_spell1_pps}
+% \end{figure}
+% 
+% 
+% \clearpage
+% \newpage
+% 
 \subsection{Second Spell}

### 2019-03-05 paper/sex_selection_spacing-ver2.tex
Change to average spacing in tables and graphs

@@
 
-\input{../tables/bootstrap_duration_sex_ratio_low_all.tex}
+\input{../tables/bootstrap_duration_avg_sex_ratio_low_all.tex}
 
@@
 
-\input{../tables/bootstrap_duration_sex_ratio_med_all.tex}
+\input{../tables/bootstrap_duration_avg_sex_ratio_med_all.tex}
 
@@
 
-\input{../tables/bootstrap_duration_sex_ratio_high_all.tex}
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
 

### 2019-03-06 paper/sex_selection_spacing-ver2.tex
Update explanation of effect of sex selection in intro

@@
 }
-As a result, we may now observe \emph{longer} average spacing for families with the
-strongest son preference, precisely because it makes them more likely to use sex selection.
+As a result, we may observe the largest increases in average birth intervals for families 
+with the strongest son preference, precisely because their preference for sons makes them 
+more likely to use sex selection.
 % To further complicate matters, families with son preference who---for one reason or 

### 2019-03-06 paper/sex_selection_spacing-ver2.tex
Update 1st paragraph in Introduction

--- 2019-03-05 paper/sex_selection_spacing-ver2.tex
@@
 }
-As a result, we may now observe \emph{longer} average spacing for families with the
-strongest son preference, precisely because it makes them more likely to use sex selection.
+Longer birth intervals may, therefore, no longer be an indication of declining son
+preference, but could instead come about precisely because strong son preference makes
+couples more likely to use sex selection.
 % To further complicate matters, families with son preference who---for one reason or 
@@
 First, there is maternal depletion, where the mother does not have sufficient time to 
-recover after her last pregnancy before she become pregnant again.%
+recover after her last pregnancy before she becomes pregnant again.%
 \footnote{
@@
 
-\input{../figures/appendix_spell2_low.tex}
+% \input{../figures/appendix_spell2_low.tex}
 
@@
 
-\input{../figures/appendix_spell2_med.tex}
+% \input{../figures/appendix_spell2_med.tex}
 
@@
 
-\input{../figures/appendix_spell2_high.tex}
+% \input{../figures/appendix_spell2_high.tex}
 
@@
 % low education
-\input{../figures/appendix_spell3_low.tex}
+% \input{../figures/appendix_spell3_low.tex}
 
@@
 
-\input{../figures/appendix_spell3_med.tex}
+% \input{../figures/appendix_spell3_med.tex}
 
@@
 
-\input{../figures/appendix_spell3_high.tex}
+% \input{../figures/appendix_spell3_high.tex}
 
@@
 
-\input{../figures/appendix_spell4_low.tex}
+% \input{../figures/appendix_spell4_low.tex}
 
@@
 
-\input{../figures/appendix_spell4_med.tex}
+% \input{../figures/appendix_spell4_med.tex}
 
@@
 
-\input{../figures/appendix_spell4_high.tex}
+% \input{../figures/appendix_spell4_high.tex}
 

### 2019-03-06 paper/sex_selection_spacing-ver2.tex
Minor edits for grammar/clarity in Introduction

@@
 and it is critical to understand to what extent spacing is still useful as a measure of son 
-preference and develop new methods if needed.
+preference.
 In India, the sex of the last-born child significantly impacts the duration to next birth,
@@
 \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
-There are three pathways that birth intervals can affect health.
+There are three pathways through which birth intervals can affect health.
 First, there is maternal depletion, where the mother does not have sufficient time to 
@@
 }
-Second, disease transmission both from mother to child and between children close in age.
+Second, disease transmission either from mother to child or between children.
 Third, sibling competition, where siblings close in age compete for scarce resources and
@@
 affect the subsequent child and the mother.
-Only sibling competition has the potential to negatively affect the older child.
+Only sibling competition has the potential to affect the older child negatively.
 
@@
 The increased mortality risk for prior children may come from shorter breastfeeding of 
-girls to ensure that the mother can conceive again quicker, and with poor water
+girls to ensure that the mother can conceive again sooner, and with poor water
 quality this shorter breastfeeding may result both in higher risk of dying and shorter
@@
 The potential effects of spacing are not restricted to early outcomes, although
-there is less evidence on longer-term effects, and most comes from Western countries.
-In the US, for example, a longer spacing between births increases the older sibling's
+there is less evidence on longer-term effects and most comes from Western countries.
+In the US, for example, a longer interval between births increases the older sibling's
 test scores on the Peabody Individual Achievement Test, although there is no
@@
 
-\section{Results\label{sec:results}}
+\section{ }
 

### 2019-03-06 response/response-demography-1.tex
Begin response to editor on Introduction
Need better description of why my estimation method better

@@
 
+I have completely rewritten the introduction to better situate the paper in the literature
+and to highlight the contributions of the paper.
+
 - Spacing as an indicator for son preference
@@
 - Women's role in general
+
+- complete rewrite of introduction
+- highlight how method is different in ``Estimation Strategy'' section.
 
@@
 pages long, while the revised section is less than 3.5).
+The first two paragraphs in the section now highlight how my approach is different from
+prior research, especially the non-randomness of birth outcome and non-proportionality
+assumption.
+
 There are three important differences between my approach and what is standard

### 2019-03-06 paper/sex_selection_spacing-ver2.tex
Minor edits
Need better description of why my estimation method better

@@
 
-The unit of analysis is a spell, the period from one birth to the next.
-The model is a discrete time, non-proportional, competing risk hazard model with two exit 
-states: either a boy or a girl is born.
-The standard approach in the spacing literature is to use a single-exit model, but with
-access to sex selection the sex of the next child is not random and parents' choices 
-will impact the spacing to a girl or a boy differentially.%
+The standard approach in the birth spacing literature is to use proportional hazard
+models with a single exit, the birth of a child.
+There are two problems with the standard approach in this setting.
+First, and most importantly, the introduction of sex selection means that the sex of the 
+next child is no longer necessarily random and that parents' choices will impact the 
+spacing to the birth of a girl or a boy differentially.
+I, therefore, use a competing risk set-up, which can capture both the non-randomness of
+the birth outcome and the differential spacing to the birth of a girl or a boy.
+To my knowledge, this is the first application of competing risk models to birth
+spacing.%
 \footnote{
@@
 }
-Both the non-randomness and differential spacing can be captured with a competing risk 
-set up.
-
-I use a non-proportional hazard specification, which allows the shape of the hazard 
-functions to vary across groups, rather than the standard proportional hazard function 
-for three reasons.
-First, it is unlikely---even in the absence of prenatal sex determination---that the 
+
+Second, it is unlikely---even in the absence of prenatal sex determination---that the 
 effect of household characteristics such as the sex composition of previous births have 
-the same effect throughout the entire spell.%
-\footnote{
+the same effect throughout the entire spell as is assumed by the proportional hazard
+model.
 Assuming that the effect of sex composition is the same throughout a spell is especially 
 problematic for higher-order spells where different sex composition of previous births can 
-lead to substantial differences both in the likelihood of progressing to the next birth and
-how soon couples want their next child if they are going to have one.
-}
-Second, the introduction of prenatal sex determination exacerbates any bias from the 
+lead to substantial differences both in the likelihood of progressing to the next birth 
+and how soon couples want their next child if they are going to have one.
+The introduction of prenatal sex determination exacerbates any bias from the 
 proportionality assumption since sex-selective abortion use varies across groups,
@@
 within a spell, which means that the effects of covariates vary within the spell as well.
-Finally, the use of a non-proportional specification mitigates any potential effects 
+I, therefore, use a non-proportional hazard specification, which allows the shape of the 
+hazard functions to vary across groups.
+The use of a non-proportional specification also mitigates any potential effects 
 of unobserved heterogeneity when used in conjunction with a flexible baseline hazard 
@@
 
+The model is a discrete time, non-proportional, competing risk hazard model with two exit 
+states: either a boy or a girl is born.
+The unit of analysis is a spell, the period from one birth to the next.
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
@@
 
-\section{ }
+\section{Results\label{sec:results}}
 

### 2019-03-06 paper/sex_selection_spacing-ver2.tex
Minor edit of intro paragraph

@@
 }
-Longer birth intervals may, therefore, no longer be an indication of declining son
+Longer birth intervals may, therefore, cease to be an indication of declining son
 preference, but could instead come about precisely because strong son preference makes

### 2019-03-07 paper/sex_selection_spacing-ver2.tex
Edits of Data section

@@
 duration between births of less than nine months.
-Women who reported less than nine months between marriage and first birth
-remain in the sample---unless they are dropped for another reason---because 
-8.5\% fall into this category across the four surveys.
-Although it is possible that some of these births are premature, the high number of
-women who report a birth less than six months after their marriage indicates that for
-a majority conception likely occurred before marriage.
 
@@
 
-Recall error is heavily dependent on how long ago a woman was married 
-\citep{Portner2018b}.
-I, therefore, drop women married 22 years or more 
-for NFHS-1, with the corresponding cut-off points 23 years for NFHS-2, 
-and 25 years for NFHS-3 and NFHS-4.
+Recall error is heavily dependent on how long ago a woman was married.%
+\footnote{
+See the discussion in the online Appendix.
+}
+I, therefore, drop women married 22 years or more.
 The final sample consists of 
@@
 approximately proportional effect on the hazard.
-These include the length of the first spell 
-(for the second and higher-order spells to capture fecundity), 
+These include
 the age of the mother at the beginning of the spell, 
@@
 and whether the household belongs to a scheduled tribe or caste.
-We cannot observe fecundity directly, but the time from marriage until 
-first birth is a suitable proxy because most Indian women do not use 
-contraception before the first birth and there is pressure to show that 
-a newly married woman can conceive \citep{dyson83,Sethuraman2007,Dommaraju2009}.
-The absence of contraception before the first birth is confirmed below by the 
-very short spells between marriage and first birth, even among the most educated.
-Hence, a long spell between marriage and first birth is likely due to low fecundity.
-For both duration from marriage to first birth and the age of the mother at the 
-beginning of the spell, I also include their squares.
-The remaining variables are dummies for household ownership of land and membership
-of a scheduled caste or tribe.
 

### 2019-03-07 paper/sex_selection_spacing-ver2.tex
Need earlier highlight of main questions

@@
 couples more likely to use sex selection.
-% To further complicate matters, families with son preference who---for one reason or 
-% another---do not use prenatal sex selection may continue to have shorter birth spacing 
-% than those with a lower preference for sons.
 
@@
 
-Even the effects of access to contraceptive on spacing are unclear.
+Even the effects of access to contraceptive and declining fertility on spacing are unclear.
 On the one hand, access to contraceptives allows women to avoid too short spacing between 
@@
 
-TK spacing and decline in fertility (with and without sex selection)
-
-Despite the increasing use of sex selection, the extensive use of spacing to measure son 
-preference, and the important impacts of spacing on outcomes for both mother and children  
-there has so far been no examination of what effect access to sex selection has had on 
-spacing.
-
-TK What questions I am asking
+% [Hypotheses / questions]
+Despite the increasing use of sex selection, the important impacts of spacing on outcomes 
+for both mother and children, and the extensive use of spacing to measure son 
+preference in the literature, there has so far been no examination of what effect access 
+to sex selection has had on spacing.
+The overall hypothesis I examine here is that spacing patterns significantly changed 
+as prenatal sex determination became available.
+I address three questions in order of importance.
+
+First, how did birth intervals change over time for different groups and how are those 
+changes related to the likely use of sex selection?
+The underlying hypothesis is that in the absence of sex selection son preference leads to 
+shorter spacing the fewer boys a family has for a given parity, whereas son preference 
+increases the spacing the fewer boys a family has when prenatal sex selection is available.
+Families with son preference who---for one reason or another---do not use prenatal sex 
+selection may continue to have shorter birth spacing.
+Based on the prior literature on sex selection, I focus on how birth intervals have
+changed for different education levels, whether urban or rural, and the sex composition of 
+prior children.
+
+Second, have the shapes of the survival curves changed?
+The shapes of the survival curves provide information both on general changes in birth 
+spacing and whether parents are still trying to conceive earlier after girls than boys.
+I still expect parents to \emph{try} to conceive earlier after the birth 
+of a girl than after a boy, but the abortions will increase the duration between births, 
+and may even lead to longer average spacing after the birth of girls than after boys.
+I expect this to be the case if there is still a strong preference for boys, and this 
+behavior may even become more pronounced with access to sex selection.
+
+Finally, how are the changes in birth intervals with increasing access to sex selection 
+distributed geographically?
+Given the size and cultural differences within India, it is unlikely that the effect of
+increasing access to sex selection will have had the same effect throughout 
+\citep{retherford03b}.
+I, therefore, examine how birth intervals have changed across four broad regions.
+[TK only some groups]
 
@@
 
-% [Hypotheses / questions]
-
-The overall hypothesis is that spacing patterns significantly changed 
-as prenatal sex determination became available.
-To address this, I examine three questions in order of importance.
-
-First, did the spacing after girls increase relative to the spacing
-after boys?
-The underlying hypothesis is that in the absence of sex selection son 
-preference leads to shorter spacing after the birth of a girl than after the 
-birth of a boy, whereas son preference increases the spacing after the birth 
-of a girl relative to after the birth of a boy when prenatal sex selection is 
-available.
-I still expect parents to \emph{try} to conceive earlier after the birth 
-of a girl than after a boy, but the abortions will increase the 
-duration between births, and may even lead to longer spacing after the
-birth of girls than after boys.
-
-Second, have the shapes of the survival curves changed?
-The shapes of the survival curves provide information both on general
-changes in birth spacing and whether parents are
-still trying to conceive earlier after girls than boys.
-I expect this to be the case if there is still a strong preference for
-boys, and, as discussed above, this behavior may even become more pronounced
-with access to sex selection.
-
-Finally, does the sex ratio change within a spell?
-There are two reasons why this is interesting.
-First, if the sex ratio changes within a spell, relying on the observed sex
-ratio at birth---as is standard practice in the literature---will not provide
-correct estimates of the use of sex selection or the sex ratio at
-the conclusion of childbearing.
-Second, any changes in the sex ratio within a spell provides clues
-to parents' preferences over the ideal spacing between births and the
-distribution of son preference in the sample.
-
 % [How to read tables]
@@
 
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
+
 \begin{figure}[htpb]
@@
 \end{figure}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
 
@@
 almost the same sex ratio.
+
+\subsection{Regional Differences\label{sec:regional}}
 

### 2019-03-07 paper/sex_selection_spacing-ver2.tex
Explain why no first spell analysis

@@
 
-As mentioned above, 8.5\% of women gave birth less than nine months
-after they were married, and the first spell, therefore, begins at the 
-month of marriage.
-The exception is for women married very young, where I use the month they 
-turned 12.
+I focus here on the second through fourth spells, that is, from the second birth until
+at most the fourth birth.
+The first spell from marriage to the first spell is excluded because of data issues.
+In NFHS-1 and NFHS-2 the only information on marriage timing is age at marriage and all
+spell durations are therefore imputed.
+In NFHS-3 about a third of respondent did not provide complete information on the
+timing of marriage and therefore had the length of their first spell imputed using only
+the age at marriage.
+The result of the imputation is that very large numbers of women end up with very short,
+i.e. less than 9 months, or negative spells and that comparing spell duration over time
+for the first spell is subject to an excessive amount of noise.
+
 The second and subsequent spells begin nine months after the previous birth 
 because that is the earliest we should expect to observe a new birth.
-A few women report births that occurred less than nine months 
-after the previous birth; I drop those women from the sample as mentioned above.
-
 All spells continue until either a child is born or censoring occurs.
@@
 or too few births are observed for the method to work.
-For the first spell I set censoring because of too few births to 108 months 
-(nine years) after marriage,
-while for the second, third, and fourth spells censoring is at 96 months 
-(eight years) after a birth can occur.
+For all spells censoring is set at 96 months (eight years) after a birth can occur.
 With these cut-offs, less than one percent of observed births occur after
@@
 \input{../tables/num_missed.tex}
-Recall also that these numbers are totals across all 36 separate regressions.
-}
-
-I group spells into four periods based on the year of marriage
-or year of the previous birth:
+}
+
+I group spells into four periods based on the year of the previous birth:
 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
@@
 The allocation into periods means that some spells cover two periods.
-A couple may, for example, be married in 1984, but not have their first 
+A couple may, for example, have their first child in 1984, but not have their second 
 child until 1986.
-That couple's first spell will be in the 1972--1984 period, even though 
+That couple's second spell will be in the 1972--1984 period, even though 
 most of the interval falls in the 1985--1994 period.

### 2019-03-08 paper/sex_selection_spacing-ver2.tex
Add region bootstrap graphs

@@
 
+\FloatBarrier
+
 \subsection{Regional Differences\label{sec:regional}}
 
-\FloatBarrier
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
+\caption{high education - r1}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
+\caption{high education - r2}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
+\caption{high education - r3}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
+\\
+\caption*{Rural}
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
+\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
+\caption{high education - r4}
+\end{figure}
+
 \section{Conclusion\label{sec:conclusion}}

### 2019-03-08 paper/sex_selection_spacing-ver2.tex
Show 25, 50, and 75 percentiles spacing in one graph
This also introduces \mcth to cover multicolumn{3}{c}{} in LaTeX
Remove reference to non-existing paper

@@
 \newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
+\newcommand{\mcth}[1]{\multicolumn{3}{c}{#1}}
 \newcommand{\X}{$\times$ }
@@
 the second spell and one boy is statistically significantly \emph{below} 
-the natural sex ratio \citep{Portner2018b}.
+the natural sex ratio.
 

### 2019-03-09 paper/sex_selection_spacing-ver2.tex
Prettier main results graphs with proper information

@@
 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_urban_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_urban_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_urban_all}} 
+% \\
+% \caption*{Rural}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_rural_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_rural_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_rural_all}} 
+% \caption{low education}
+% \label{fig:bootstrap_low}
+% \end{figure}
+
 \begin{figure}[htpb]
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_urban_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_urban_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_urban_all}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_rural_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_rural_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_rural_all}} 
-\caption{low education}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with no education}
+\label{fig:bootstrap_low}
 \end{figure}
@@
 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_urban_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_urban_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_urban_all}} 
+% \\
+% \caption*{Rural}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_rural_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_rural_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_rural_all}} 
+% \caption{med education}
+% \label{fig:bootstrap_med}
+% \end{figure}
+
 \begin{figure}[htpb]
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_urban_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_urban_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_urban_all}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_rural_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_rural_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_rural_all}} 
-\caption{med education}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with one to seven years of education}
+\label{fig:bootstrap_med}
 \end{figure}
@@
 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
+% \\
+% \caption*{Rural}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
+% \caption{high education}
+% \label{fig:bootstrap_high}
+% \end{figure}
+
+% \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
+\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
+
 \begin{figure}[htpb]
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
-\caption{high education}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight or more years of education}
+\label{fig:bootstrap_high}
 \end{figure}

### 2019-03-10 paper/sex_selection_spacing-ver2.tex
Initial rewrite of result introduction

@@
 % [How to read tables]
-Tables \ref{tab:median_sex_ratio_low}, \ref{tab:median_sex_ratio_med}, and
-\ref{tab:median_sex_ratio_high}
-show the predicted median duration and sex ratios by period, spell, and sex 
-composition for the three education levels separated by area of residence.%
-\footnote{
-Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
-\ref{tab:p25_p75_high} show 25th and 75th percentiles durations.
-} 
+Figures \ref{fig:bootstrap_low}, \ref{fig:bootstrap_med}, and  \ref{fig:bootstrap_high} 
+show predicted average birth intervals, sex ratios, and probabilities of having
+a birth by decade, spell, and sex composition for the three education levels separated 
+by area of residence.
 For each subsample, I first estimate the model described in Section 
 \ref{sec:strategy} and then use the estimated coefficients to predict 
-median duration and sex ratio.
-For the standard errors, I use bootstrapping for both measures,
-where the model is repeatedly estimated using resampling with replacement.
-
-The predicted median duration is the weighted average over the women in the 
-subsample, using the individual probabilities of giving birth as weights.
-For each woman in a sample, I calculate her probability of ending the spell 
-with a birth, and her contribution to median spacing is how long it will take
-from the beginning of the spell to where she is predicted to reach half of that probability.
-For example, if a woman has an 80\% probability of having a birth by the end of 
-the spell, her median duration is the number of months it takes to reach
-40\% probability of having exited with a birth.
-The 40\% is equivalent to the 60\% point on a standard survival curve because that 
-captures how many have not yet exited.
-
-For the second through the fourth spell, I show whether durations for sex 
-composition other than only girls are statistically significantly different 
-from the duration with only girls.
-To calculate the level of statistical significance, I bootstrap the
-difference in spacing.
-
-The cleanest test is comparing durations after only boys with durations after
-only girls, but the number of births to women with only sons becomes small 
-in the later periods.
-Hence, it is possible to have substantial differences in spacing that are
-not statistically significant because of low power, especially for the third 
-and fourth spell.
+average spell length, sex ratio, and the probability of having a birth in that spell.
+
+The expected average duration is calculated as follows.
+For each woman in a sample, I calculate her probability of giving birth for each period
+in the spell and use these probabilities as weights to calculated her expected duration 
+for that spell.
+I then take the average of these expected durations using her probability of having a
+birth by the end of the spell as weights.
 
@@
 Each woman's predicted sex ratio is the weighted average of the predicted
-percentage boys over the months in the spell calculated using equation 
-(\ref{eq:probability_son}) and the probability of giving birth in each month 
+percentage boys over each period in the spell calculated using equation 
+(\ref{eq:probability_son}) and the probability of giving birth in each period 
 as weights.%
@@
 in the sample when childbearing for that spell is over.
+
+For legibility none of the graphs show standard errors.
+Instead, the standard errors, together with the graphed values, are shown in Appendix 
+Tables TK, TK, and TK.%
+\footnote{
+Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
+\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
+bootstrapped standard errors.
+} 
+The standard errors are based on bootstrapping for all three measures,
+where the model is repeatedly estimated using resampling with replacement.
+
+I also show whether durations for sex composition other than only girls are statistically 
+significantly different from the duration with only girls based on bootstrapped 
+differences. 
+The cleanest test is comparing durations after only boys with durations after
+only girls, but the number of births to women with only sons becomes small 
+in the later periods.
+Hence, it is possible to have substantial differences in spacing that are
+not statistically significant because of low power, especially for the third 
+and fourth spell.
 
@@
 
+% \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
+\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
+
 \begin{figure}[htpb]
@@
 % \end{figure}
-
-% \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
-\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
 

### 2019-03-10 paper/sex_selection_spacing-ver2.tex
Remove discussion of methods not shown in paper

@@
 
-Because the probability of ever having a next birth likely varies across groups, a direct 
-comparison of standard survival curves tells us little about how the spread of sex selection 
-affects birth spacing across groups.
+Because the probability of ever having a next birth varies across groups, a direct 
+comparison of standard survival curves tells us little about how the spread of sex 
+selection affects birth spacing across groups.
 I, therefore, condition on the predicted likelihood of parity progression when examining 
-birth spacing measures, such as the median duration to a birth.
+birth spacing measures, such as the average duration to a birth.
 The reliability of this approach depends on whether the spell length covered is 
@@
 }
-In addition, I also present graphs of both standard survival curves and
-survival curves conditional on parity progression (which therefore
-begin at 100\% and end at 0\%).
+In addition, I present graphs of survival curves conditional on parity progression,
+which therefore begin at 100\% and end at 0\%.
 
@@
 across all $t$ gives the predicted percent boys born over the entire spell.
-In addition to the predicted percent boys over the entire spell, 
-I also present graphs of how the percentage boys born vary across time
-within a spell, together with the associated confidence interval for given 
-values of explanatory variables calculated using the Delta method.
 

### 2019-03-10 paper/sex_selection_spacing-ver2.tex
Prettier set-up for regional graphs

@@
 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
+% \\
+% \caption*{Rural}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
+% \caption{high education - r1}
+% \end{figure}
+
 \begin{figure}[htpb]
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r1}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r1} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_high_urban_r1}
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
-\caption{high education - r1}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r1}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r1} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_high_rural_r1} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight or more years of education - r1}
+\label{fig:bootstrap_high_r1}
 \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
+% \\
+% \caption*{Rural}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
+% \caption{high education - r2}
+% \end{figure}
 
@@
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r2}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r2} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_high_urban_r2}
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
-\caption{high education - r2}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r2}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r2} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_high_rural_r2} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight or more years of education - r2}
+\label{fig:bootstrap_high_r2}
 \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
+% \\
+% \caption*{Rural}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
+% \caption{high education - r3}
+% \end{figure}
 
@@
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r3}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r3} 
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
-\caption{high education - r3}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r3}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r3} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight or more years of education - r3}
+\label{fig:bootstrap_high_r3}
 \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
+% \\
+% \caption*{Rural}
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
+% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
+% \caption{high education - r4}
+% \end{figure}
 
@@
 \centering
-\caption*{Urban}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r4}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r4} 
+    \end{minipage}
+}
 \\
-\caption*{Rural}
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
-\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
-\caption{high education - r4}
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r4}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r4} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight or more years of education - r4}
+\label{fig:bootstrap_high_r4}
 \end{figure}

### 2019-03-11 paper/sex_selection_spacing-ver2.tex
Add regional bootstrap tables
Add table with state names by region
Explain region creation

@@
 
-\FloatBarrier
-
 \subsection{Regional Differences\label{sec:regional}}
+
+To examine the effect of differences in son preference, fertility, and use of sex 
+selection on birth spacing, I divide India into four broad regions based on degree of 
+son preference and initial fertility levels as in  \citet{retherford03b}, although 
+expanded to include all states in the surveys.
+Table \ref{tab:regions} shows the four regions and the states that they contain.%
+\footnote{
+The geographical names do not perfectly reflect the geography of India, and mainly
+serves as mnemonic short-hands.
+}
+The state names are based on the states in existence when NFHS-1 was collected.
+States that are formed later are allocated as closely as possible to the original state.
+
+\input{../tables/desc_region.tex}
+
+The West contains states with a high degree of son preference and use of sex selection.
+The North consists of states that also have a strong son preference, but initially had
+higher fertility and therefore lower likelihood of using sex selection.
+The East states generally have only a moderate level of son preference.
+Finally, the South contains states with traditionally low son preference and lower
+fertility than the rest of India.
 
@@
 
-\section{[Bootstrap Results by Region]}
+\section{Additional Duration Results}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\vspace*{-0.51cm}
+
+\input{../tables/bootstrap_duration_p25_p75_low_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_med_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_all.tex}
+
+\clearpage
+
+\section{Results by Region}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\vspace*{-0.51cm}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_r1.tex}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_r2.tex}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_r3.tex}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_r4.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_r1.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_r2.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_r3.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_r4.tex}
 
@@
 \newpage
-
-\section{Additional Duration Results}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\vspace*{-0.51cm}
-
-\input{../tables/bootstrap_duration_p25_p75_low_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_med_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_all.tex}
-
-\clearpage
 

### 2019-03-11 response/response-demography-1.tex
Minor edit
Notes on selection bias from changes in education

@@
 [Response:]
+
+[selection]
+
+There are two possible explanations, economics and cultural.
+
+For the economics one, the use of sex selection is mainly driven by the lower fertility
+that comes from higher opportunity cost of time and the higher income that allow those
+with higher education to use sex selection.
+Here there is essentially no selection bias since the use of sex selection is driven
+by factors that are identical across those with the same level of education.
+
+The cultural explanation is that originally those with higher education where also those
+groups with the strongest son preference (presumably those who are also higher caste).
+The expansion of access to education brought other groups/castes into connection with
+the higher castes and assimilation of their son preference norms.
+Presumably the assimilation is not complete and those newer to higher education would
+therefore have lower son preference and therefore lower use of sex selection.
+This means that any appearance of lower use of sex selection could be a selection story,
+and that the initial group's son preference is just as strong.
+
+The cultural explanation also suggests a reason for why the states son preference 
+appear to decline over time.
+The ``newer'' entrants have lower initial son preference and therefore the average
+son preference for high education women will decline over time.
+\citep{bhat03}, \citep{pande07}.
 
@@
 depending on degree of son preference and initial fertility level as in 
-\citep{retherford03b}, although expanded to include all states in the surveys.
+\citet{retherford03b}, although expanded to include all states in the surveys.
 In addition to the power problem, some education/region/spell/period combinations have too 

### 2019-03-11 response/response-demography-1.tex
Minor edits
Respond to R1's suggestion on results graphs

@@
 Third, the sex ratio calculations is a new way to use competing risk estimates and is 
-required to understand whether the use of sex selection vary within spells.
+required to understand the use of sex selection.
 
@@
 
+Using graphs is an excellent suggestion.
+Instead of the tables, I now show graphs for each of the education levels.
+For each spell, I show the predicted average spacing, the predicted sex ratio, and the 
+probability of having a birth by the end of the spell for each decade.
+Including the probability of having a birth allows me to discuss the falling fertility 
+more organically as requested by the editor.
+
+The only downside is that I had to remove the confidence intervals for legibility. 
+I, therefore, still include Tables 1-3, but have moved them to the Appendix, and I have 
+added the probability of a birth to the tables.
+I have also combined the 75th, 50th, and 25th percentiles results tables in the Appendix.
+
 10. As sex composition and sex ratios has been examined in the literature, I think

### 2019-03-11 paper/sex_selection_spacing-ver2.tex
Respond to R1's suggestion on results graphs
Discuss no education results

@@
 
-\input{../tables/bootstrap_duration_avg_sex_ratio_low_all.tex}
-
-Women with no education follow a pattern consistent with son
-preference with shorter spacing when they have only girls compared 
-to when they have one or more sons, and the differences are often 
-statistically significant as shown in Table \ref{tab:median_sex_ratio_low}.
-Most of the women without education live in rural areas,
-whereas there are relatively few urban women with no education.
-There are especially very few urban women to based the third
-and fourth spell results on, and I therefore focus on rural women.
-
-Predicted median duration has increased over time within
-each sex composition.
-The exception is for the first spell, where there is little
-change, and possibly even a small decline.
-
-The differences in duration across sex compositions increase with 
-spell number.
-For the second spell, the difference in median duration between
-having a girl or a boy as the first-born are mostly between a half
-and one month.
-For the third spell, the difference in duration between only girls 
-and only boys is, on average, slightly over one month and statistically 
-significant in all periods.
-The differences for the fourth spell are between two and three months, 
-except for the 1972--1984 period, which is also the only period where 
-the difference is not statistically significant.
-
-There are no clear time trends in the differences in median duration
-across sex compositions or the predicted sex ratios across the four periods.
-Despite that some sex ratios are statistically significantly higher 
-than the natural sex ratio there is therefore little consistent evidence 
-for the use of sex selection for women without education.
-There has, for example, been relatively little change in the length
-of spacing for rural women with two girls in the third spell and 
-the predicted sex ratio was higher in the 1985--1994 period
-than in the 2005--2016 period.
-The possible exception is the fourth spell, where both duration 
-and sex ratio has increased for women with three girls, although
-the \emph{difference} across sex compositions has remained almost
-the same.
+The previous literature finds that women with no education are the least likely to use 
+sex selection, which suggests that they would instead follow a traditional strategy to son 
+preference with higher fertility and shorter birth intervals the fewer sons they have.
+This pattern is supported by Figure \ref{fig:bootstrap_low}, but with important
+differences across spells.
+Most of the women without education live in rural areas, and I therefore focus on rural 
+women.
+
+The initial high fertility of women with no education shows clearly in the results.
+In the 1972--1984 period almost all women had at least four children, irrespectively
+of the sex composition of the children.
+Over time, however, the likelihood of having a third or fourth child decreased for women 
+with at least one son, and more so the more sons they had.
+Hence, fertility have begun to fall even among women with no education, as long as they 
+have at least one son.
+Two additional fertility trends stand out.
+First, essentially all women still have a second birth, whether the first child was
+a boy or a girl.
+Second, for women with only girls there is almost no reduction in the probability of 
+having a birth across time and across spells.
+
+Birth intervals have increased in length over time, although the increases are not
+uniform over spells and sex compositions of prior children.
+The smallest increases have been for the second spell, with most increases between one
+and two months.
+Interestingly, son preference appear to have little effect on spacing for the second
+spell, with very small, albeit statistically significant, differences in birth intervals 
+depending on the sex of the first child.
+This small difference is in line with the high likelihood of having a second child.
+The second spell also shows convergence in birth intervals, especially in the urban
+areas where the predicted average duration is now the same whether the first child was
+a boy or a girl.
+
+Where son preference in birth intervals shows most clearly is for the fourth spell.
+Despite the increase in spacing even for those with three girls, the increases in 
+spacing have been substantially larger for families with at least one son.
+As for fertility, the differences are larger the more sons a family has.
+
+Despite the general finding that use of sex selection is confined to higher education
+women, the predicted sex ratios for those with only girls is statistically significantly
+higher than the natural ratio for the third and fourth spell.
+Hence, it is possible that at least part of the increased  birth intervals for those
+with only girls comes from the use of sex selection and that the differences in
+birth spacing across sex compositions would be even larger in the absense of sex selection.
 
@@
 
-\input{../tables/bootstrap_duration_avg_sex_ratio_med_all.tex}
-
 Women with one to seven years of education follow a pattern
 broadly similar to those with no education as 
-Table \ref{tab:median_sex_ratio_med} shows.
+Figure \ref{fig:bootstrap_med} shows.
 The sample size is more evenly distributed across urban and rural 
@@
 \subsection{High Education Women}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
 
@@
 
-\section{Additional Duration Results}
+\section{Duration Results Tables}
 
@@
 \vspace*{-0.51cm}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_low_all.tex}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_med_all.tex}
+
+\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
 

### 2019-03-12 paper/sex_selection_spacing-ver2.tex
Discuss middle education results

@@
 Most of the women without education live in rural areas, and I therefore focus on rural 
-women.
+women.%
+\footnote{
+Only between ten and twenty percent of the surveyed women without education live in urban 
+areas, and this proportion has been decreasing over time.
+}
 
@@
 
-Women with one to seven years of education follow a pattern
-broadly similar to those with no education as 
-Figure \ref{fig:bootstrap_med} shows.
-The sample size is more evenly distributed across urban and rural 
-for this education group than for the no education women.
-As a result, the only spells where there are few women to base 
-results on are for the fourth spell for urban women and the first 
-period of the fourth spell for rural women.
-
-The spacing between births increased over the four decades.
-On average, the increase is approximately three to four months.
-The exception is again the first spell, where the time from
-marriage to first birth remained the same or fell slightly.
-
-In the period before sex selection became available, 1972--1985,
-the differences in spacing between only girls and only boys
-increase with between the second and third spell.
-For both urban and rural women, the difference in duration is just over
-a month for the second spell, but it is 1.4 and 2.8 months for urban and
-rural women, respectively, for the third spell.
-In the three later periods, there is no clear pattern
-in the differences across sex compositions.
-
-The differences in duration between only girls and only boys 
-appear to decrease over time.
-The exception is for the two later periods where the
-differences are slightly larger in the last period compared
-with the second-to-last period.
-
-The decreases in differences are accompanied by increases
-in predicted sex ratios, some of which are statistically 
-significantly different from the natural sex ratio.
-Hence, even though the evidence is not substantial, it does
-appear that women with one to seven years of education 
-have begun to use sex selection at higher-order spells.
+Figure \ref{fig:bootstrap_med} shows that women with one to seven years of education 
+follow a fertility pattern broadly similar to those with no education.
+As expected, fertility is lower than for women with no education, but still show
+substantial son preference in the parity progression behavior.
+Except for the second spell, the likelihood of having a birth by the end of spell is
+substantially lower if there has been at least one male birth than if there are only girls.
+Despite this, the probability of a birth in the third and fourth spells has also been 
+falling for those with only girls.
+Having a second birth is still close to universal, although in urban areas it is down to
+just over 85 percent for those with a son as their first child.
+
+The spacing between births has increased over the four decades, and the increases are 
+larger than for women without any education across all spells.
+Contrary to women without education, however, there has not been an increased divergence 
+in birth intervals lengths across sex compositions for the third and fourth spells.
+On the contrary, for the third spell the largest increases in birth intervals are for women with
+two daughters and no sons, with an increase of about seven months across the four decades.
+The results is that for urban women the standard spacing pattern reversed, so the longest 
+predicted spacing is now for those with only girls, while for rural women the predicted 
+average birth intervals are now almost identical across sex compositions of prior children.
+For the fourth spell, the increases in spacing for women with only girls have kept pace
+with the other sex compositions in rural areas.%
+\footnote{
+Because of low number of observations the pattern for the fourth spell is more noisy for 
+urban women.
+}
+
+The substantial increases in spacing for women with only girls is not evidence of lower
+son preference as the changes in the predicted sex ratios show.
+For both the third and fourth spell the predicted sex ratio in both urban and rural
+areas is statistically significantly above the natural sex ratio at between 55.5 and 57.7 
+percent boys.
+The elevated sex ratios strongly suggests that sex selection is driving the increases in
+birth intervals for women with only girls, and that without sex selection we would 
+instead have observed a diverging pattern in birth intervals across sex composition as
+for women without education.
 

### 2019-03-12 paper/sex_selection_spacing-ver2.tex
Minor edits

@@
 Instead, the standard errors, together with the graphed values, are shown in Appendix 
-Tables TK, TK, and TK.%
-\footnote{
-Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
-\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
-bootstrapped standard errors.
-} 
+Tables TK, TK, and TK.
 The standard errors are based on bootstrapping for all three measures,
@@
 the traditional spacing pattern before sex selection became 
-available as shown in Table \ref{tab:median_sex_ratio_high}.
+available as shown in Figure \ref{fig:bootstrap_high}.
 Compared to the two other education groups there are,
@@
 
-\subsection{Distribution of Birth Spacing Across Sex Compositions and Time}
+\subsection{How the Distribution of Birth Spacing Varies Across Sex Compositions and Time}
 
@@
 This section, therefore, provides more detail on how spacing is distributed
-over time and sex compositions using a graphical approach.
+over time and sex compositions using a graphical approach.%
+\footnote{
+Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
+\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
+bootstrapped standard errors.
+}
 

### 2019-03-12 paper/sex_selection_spacing-ver2.tex
Begin editing high education results

@@
 
+Women with eight or more years of education are those expected to have the lowest 
+fertility and the highest use of sex selection based on the prior literature.
+Figure \ref{fig:bootstrap_high} shows that not only do this group, indeed, have lower 
+fertility than the two prior groups, it is also falling rapidly over time.
+Of women with one birth, the probability of having a second birth when the first-born
+is a son is only around 70 percent for urban women and around 80 percent for rural women,
+and for those with a first-born daughter it is around 80 percent for urban women and 90 
+percent for rural women.
+The falling fertility is even more clear for the third and fourth spells when the woman
+has given birth to at least one son.
+At the beginning of the sample, urban women with at least one boy had a close to 75
+percent likelihood of having a birth, but that has fallen to only around 25 percent.
+However, son preference still shows clearly in the parity progression probability for 
+women without a son, with the decline for the third and fourth spell substantially
+slower for both urban and rural women without a son than for those with at least one son.
+
 Women with eight or more year of education mostly followed 
@@
 or expected mortality of the first son born.
-
-It also appears that there is a slightly elevated sex ratio among 
-first-born for urban women. 
-There is, however, no corresponding increase in spacing; instead,
-the median duration has fallen over time and is the lowest among
-the three education groups.
-Hence, unless duration between marriage and first birth has decreased 
-substantially by itself, for example, because of improved health, it
-is not clear how much stock to place on the increased sex ratio
-among first-borns as evidence for sex selection among first-borns.
-
-Both of the last two results are different from prior studies using NFHS data.
-There are two potential explanations.
-First, the NFHS-4 is substantially larger than the three prior surveys.
-Hence, it is possible that the effects have been there all along, but 
-we did not have the power to detect them.
-Second, it is possible that at least the first-born results are an
-artifact of any recall error not captured by the data restrictions.
-Certain types of recall error would also explain why the sex ratio for
-the second spell and one boy is statistically significantly \emph{below} 
-the natural sex ratio.
+This result is different from prior studies using NFHS data.
+The NFHS-4 sample is substantially larger than the three prior surveys.
+Hence, it is possible that the effect has been there all along, but 
+we did not have the power to detect it.
 

### 2019-03-13 paper/sex_selection_spacing-ver2.tex
Write up of high education results

@@
 percent for rural women.
-The falling fertility is even more clear for the third and fourth spells when the woman
-has given birth to at least one son.
+
+The rapid decline in fertility for the most educated women is even more clear for the 
+third and fourth spells when the woman has given birth to at least one son.
 At the beginning of the sample, urban women with at least one boy had a close to 75
@@
 slower for both urban and rural women without a son than for those with at least one son.
-
-Women with eight or more year of education mostly followed 
-the traditional spacing pattern before sex selection became 
-available as shown in Figure \ref{fig:bootstrap_high}.
-Compared to the two other education groups there are,
-however, more situations where the pattern is less clear.
-Part of the problem may be that there are few women in
-this group for the 1972--1984 period, and, hence, only 
-the results for the first and second spells in both urban 
-and rural areas are likely reliable.
-
-Birth spacing increases substantially over time, 
-especially for urban women. 
-The median duration for urban women increases between a half
-and a full year, whereas the increase for rural women 
-is between a quarter and half a year.
-The spacing between marriage and the first birth is still the
-exception, and for this group of women, there is a decline of
-about a month for both urban and rural areas.
-
-In urban areas, the increase in spacing with only girls is so 
-substantial that women with only girls have longer spacing to the 
-next birth than any of the other sex compositions from 1985 onward.%
-\footnote{
-The exception is the second spell for the 1985--1994 period, where women
-with one girl have 0.1 months shorter spacing the women with one boy.
-}
-This reversal in the standard spacing pattern is substantial, 
-especially for the third and fourth spells.
-For the latest period, the difference between only girls than the
-other sex compositions is between 4.8 and 9.1 months for the third
-and fourth spell.
-Furthermore, the differences are statistically significant, except
-for only boys for the fourth spell because few women have a fourth
-birth if they have three boys already.
-
-Rural women also show a reversal of the typical spacing pattern,
-although the changes are less pronounced than for urban women.
-The third spell shows that spacing for women with only girls become
-increasing longer compared to the other two sex compositions.
-Most of the differences are statistically significant, although they are 
-smaller than for urban women.
-For the second spell, there is little difference in spacing for
-women with one girl and women with one boy.
-
-The predicted sex ratios at the end of the spells show that
-the reversal in spacing patterns is not the result of a declining son
-preference but instead corresponds to a substantially more male-biased 
-sex ratio.
-For urban women, the predicted sex ratio with only girls 
-is consistently above 60\% boys for the third and fourth spells.
-For rural women, the predicted sex ratios are lower than for urban
-women but still substantial and statistically significant at close 
-to 60\%.
-The high predicted sex ratios are presumably the result of increased 
-use of sex selection.
-
-When trying to understand the strength of son preference, it is interesting
-that the sex ratio is also statistically significantly different
-from the natural rate in the case where women already have one
-son for the third and fourth spells.
-Again, the sex ratio in the presence of one son for the third and
-fourth spells are higher in urban areas than rural areas, although
-the difference is less than for women with only girls.
-Hence, it is possible that women are still willing to use sex selection
-even after giving birth to one, although this behavior may also 
-be in response to either experienced
+The falling fertility means that relatively few women makes it to the fourth spell,
+which, therefore, has more noise than the other spells.
+
+Average birth spacing for the second spell is almost identically across sex compositions 
+for both urban and rural women, and increased by around five months for rural women and
+by almost ten months for urban women over the four decades.
+These similarities hides, however, what would have been a standard son preference spacing 
+pattern with significantly shorter spacing after a first-born girl than after a first-born 
+boy if there had not been a substantial amount of sex selection.
+For both of the last two periods the predicted sex ratio for women with a daughter as 
+their first-born child is above 55 percent for both urban and rural areas.
+
+The tremendous impact that sex selection can have on birth spacing is illustrated 
+particularly vividly by the changes over time for the third spell.
+In the 1972-1984 period the predicted average birth intervals for the three possible sex 
+compositions were less than two months apart.
+For the later periods, however, the highest predicted average spacing was for women
+with only daughters with most of the differences to the other sex compositions 
+statistically significant.
+In urban areas the predicted average birth interval for a woman with only daughters 
+increased by almost a full year from 26.8 to 38.3 months.
+What is more, this increase is likely an underestimate.
+The sex ratios for the 1972-84 period are substantially higher than the natural sex ratio 
+despite sex selection not being widely available until around 1985.
+If this early elevated sex ratio is because of recall error it means that the actual birth 
+intervals would have been substantially shorter than the ones predicted here and the
+increase over time larger.
+
+The reversal pattern also shows for the fourth spell for urban women, although not for
+rural women.
+An important caveat is that because of the falling fertility relatively few women make
+it to the fourth spell, and even if they do we do not observe a birth by the time of the
+survey.
+Of the 11,886 women across urban and rural areas observed for the fourth spell for the 
+2005-2016 period more than 70 percent did not have a birth at the time of the survey.
+Even though the censoring is less prevalent for the earlier periods this is countered by
+those samples being substantially smaller.
+Despite this, the pattern for the fourth spell is similar to that of the third spell.
+
+The predicted sex ratios at the end of the spells show that this reversal in spacing 
+patterns is not the result of a declining son preference but instead corresponds to a 
+substantially more male-biased sex ratio as use of sex selection spread.
+For urban women, the predicted sex ratio with only girls is consistently above 60\% boys 
+for the third and fourth spells.
+For rural women, the predicted sex ratios are lower than for urban women but still 
+substantial and statistically significant at close to 60\%.
+
+When trying to understand the strength of son preference, it is interesting that the sex 
+ratio is also statistically significantly different from the natural rate in the case 
+where women already have one son for the third and fourth spells.
+Again, the sex ratio in the presence of one son for the third and fourth spells are higher 
+in urban areas than rural areas, although the difference is less than for women with only 
+girls.
+Hence, it is possible that women are still willing to use sex selection even after giving 
+birth to one, although this behavior may also be in response to either experienced
 or expected mortality of the first son born.
@@
 The NFHS-4 sample is substantially larger than the three prior surveys.
-Hence, it is possible that the effect has been there all along, but 
-we did not have the power to detect it.
+Hence, it is possible that the effect has been there all along, but we did not have the 
+power to detect it.
 

### 2019-03-13 paper/sex_selection_spacing-ver2.tex
Initial work on distribution of spacing results

@@
 
-\subsection{How the Distribution of Birth Spacing Varies Across Sex Compositions and Time}
-
-Median spacing is a convenient way to understand the overall changes but
-may hide important differences in the distribution of spacing.
-This section, therefore, provides more detail on how spacing is distributed
-over time and sex compositions using a graphical approach.%
+\subsection{Distribution of Birth Spacing Within Spells and Across Sex Compositions}
+
+Average spacing is a convenient way to understand the overall changes but may hide 
+important differences in the distribution of spacing.
+Specifically, a concern is that the increases in average spacing that I show above may 
+mask an increased variance in birth spacing with families with fewer sons both more likely 
+to have a very pregnancy and to continue through pregnancies and sex-selective abortions 
+until they conceive a son.
+This section, therefore, provides more detail on how spacing is distributed within a spell 
+and across sex compositions using a graphical approach.
+
+I show survival curves conditional on predicted parity progression rather than standard 
+survival curves. 
+The advantage of this approach is that it is possible to directly compare the distribution 
+of spacing to next birth across groups, independently of differences in how likely the 
+next birth is.
+Because the conditional survival curves are independent of the likelihood of parity 
+progression within the spell, they all begin at 100\% and end at 0\%.
+
+Instead of averaging across the entire sample, I calculate the conditional survival curves 
+for an average woman using the method detailed in Section \ref{sec:strategy}.%
 \footnote{
-Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
-\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
-bootstrapped standard errors.
-}
-
-I show survival curves conditional on predicted parity progression rather than
-standard survival curves. 
-The advantage of this approach is that it is possible to directly compare 
-the distribution of spacing to next birth across groups, independently of 
-differences in how likely the next birth is.
-Because the conditional survival curves are independent of the likelihood
-of final parity progression, they all begin at 100\% and end at 0\%.
-
-Instead of averaging across the entire sample, I calculate the conditional
-survival curves for an average woman using the method detailed in 
-Section \ref{sec:strategy}.
-For each combination of education and spell, I use values based on the
-average age at the start of the spell and, for the second and higher
-spells, the average duration of the first spell.
-Furthermore, I use the majority categories for the categorical explanatory 
-variables, which means no ownership of land and not in a scheduled caste or 
-tribe.
-The characteristics used do not change across period to ensure that 
-composition effects do not drive the changes.
+To complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
+\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
+percentiles durations with bootstrapped standard errors based on averages across all women 
+in the each subsample as for the results above.
+} 
+For each combination of education and spell, I use values based on the average age at the 
+start of the spell.
+Furthermore, I use the majority categories for the categorical explanatory  variables, 
+which means no ownership of land and not in a scheduled caste or tribe.
+The characteristics used do not change across the four decades to ensure that composition 
+effects do not drive any changes.
 
 In the interest of brevity, I discuss only a select set of subsamples.
-Figure \ref{fig:pps_spell1} shows spacing for the first spell across the
-four periods for rural women with no education and urban women with 
-eight or more years of education.
-Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex
-compositions for the second, third, and fourth spells for the first period, 
-1972--1984, and the last period, 2005--2016, for rural women with no 
-education and for urban women with eight or more years of education.
-The Appendix shows standard and conditional survival curves for all groups and 
-time periods, and I discuss some examples of standard survival
-curves in the following section.%
-\footnote{
-To ease legibility of the graphs some three months intervals are combined
-into longer ones when there are few births available in the sample.
-}
+Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex compositions for 
+the second, third, and fourth spells for the first period, 1972--1984, and the last 
+period, 2005--2016, for rural women with no education and for urban women with eight or 
+more years of education.
+The Appendix shows conditional survival curves for all groups and decades.
 
@@
 
-The biased sex ratio for the first spell for the most educated 
-women suggests that there might be sex selection on the first birth.
-I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
-of spacing has changed over time for rural women with no education and urban women 
-with eight or more years of education.
-What is most striking is how similar the distribution of spacing is across the
-two groups.
-
-Both groups show little change in median spacing, but that masks a substantial
-compression of when most of the births occur.
-In the 1972--1984 period, the middle 80\% of births for women with no education 
-are predicted to occur between approximately 6 and 64 months, whereas in the 
-2005--2016 period it is between 12 and 54 months.
-Hence, the compression is equivalent to more than a full year.
-Women with eight or more years of education show a slightly smaller compression:
-in the 1972--1984 period, the middle 80\% of births are predicted to occur between
-approximately 6 and 48 months, whereas in the 2005--2016 period it is between
-12 and 46 months.
-Hence, the compression is eight months.
-
-Women became less likely to conceive before marriage over time.
-In the first two periods there was a relatively smooth decline in the number of
-women without a birth starting at the time of marriage, but in the last two
-periods, there are few women who exit early after marriage and
-instead there is a substantial dip between 9 and 12 months after
-marriage.
-
-It is likely that the compressed spacing, beginning at nine months
-after marriage in the later periods, is associated with better health
-and higher age at marriage.
-For example, women without education have seen an increase in the average 
-age at marriage from below 16 to 18.5 from the first period to the last 
-while women with the most education increased from 19.5 to 20.4.
+% The biased sex ratio for the first spell for the most educated 
+% women suggests that there might be sex selection on the first birth.
+% I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
+% of spacing has changed over time for rural women with no education and urban women 
+% with eight or more years of education.
+% What is most striking is how similar the distribution of spacing is across the
+% two groups.
+% 
+% Both groups show little change in median spacing, but that masks a substantial
+% compression of when most of the births occur.
+% In the 1972--1984 period, the middle 80\% of births for women with no education 
+% are predicted to occur between approximately 6 and 64 months, whereas in the 
+% 2005--2016 period it is between 12 and 54 months.
+% Hence, the compression is equivalent to more than a full year.
+% Women with eight or more years of education show a slightly smaller compression:
+% in the 1972--1984 period, the middle 80\% of births are predicted to occur between
+% approximately 6 and 48 months, whereas in the 2005--2016 period it is between
+% 12 and 46 months.
+% Hence, the compression is eight months.
+% 
+% Women became less likely to conceive before marriage over time.
+% In the first two periods there was a relatively smooth decline in the number of
+% women without a birth starting at the time of marriage, but in the last two
+% periods, there are few women who exit early after marriage and
+% instead there is a substantial dip between 9 and 12 months after
+% marriage.
+% 
+% It is likely that the compressed spacing, beginning at nine months
+% after marriage in the later periods, is associated with better health
+% and higher age at marriage.
+% For example, women without education have seen an increase in the average 
+% age at marriage from below 16 to 18.5 from the first period to the last 
+% while women with the most education increased from 19.5 to 20.4.
 
@@
 % Low education
+\vspace*{-0.75cm}
+\begin{figure}[hp!]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2005]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.32\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_low_pps}
+\end{figure}
+
+% SPELL 2 - URBAN - MEDIUM
+
+% \input{../figures/appendix_spell2_med.tex}
+
+% PARITY PROGRESSION SURVIVAL - MEDIUM
+
+% Low education
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \setcounter{subfigure}{1}
-\subfloat[1995--2005]{
+\subfloat[1995--2004]{
     \begin{minipage}{0.32\textwidth}
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_low_pps}
+for women with 1-7 years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_med_pps}
 \end{figure}
 
-% SPELL 2 - URBAN - MEDIUM
-
-% \input{../figures/appendix_spell2_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-% Low education
+% High education
+
+% \input{../figures/appendix_spell2_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - High education
 
@@
 \subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \caption{Survival curves conditional on parity progression
-for women with 1-7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_med_pps}
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_high_pps}
 \end{figure}
 
-% High education
-
-% \input{../figures/appendix_spell2_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - High education
+\clearpage
+\newpage
+
+\subsection{Third Spell}
+
+% low education
+% \input{../figures/appendix_spell3_low.tex}
+
+% PARITY PROGRESSION SURVIVAL - LOW
+\vspace*{-0.75cm}
+\begin{figure}[hp!]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with no education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_low_pps}
+\end{figure}
+
+% Medium education
+
+% \input{../figures/appendix_spell3_med.tex}
+
+% PARITY PROGRESSION SURVIVAL - MEDIUM
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 \caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_high_pps}
+for women with 1 to 7 years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_med_pps}
 \end{figure}
 
-\clearpage
-\newpage
-
-\subsection{Third Spell}
-
-% low education
-% \input{../figures/appendix_spell3_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
+% High education
+
+% \input{../figures/appendix_spell3_high.tex}
+
+% PARITY PROGRESSION SURVIVAL - high
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with 8 or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_high_pps}
+\end{figure}
+
+\clearpage
+\newpage
+
+\subsection{Fourth Spell}
+
+% low education
+
+% \input{../figures/appendix_spell4_low.tex}
+
+% PARITY PROGRESSION SURVIVAL - LOW
+\vspace*{-0.75cm}
+\begin{figure}[hp!]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 
-% \input{../figures/appendix_spell3_med.tex}
+% \input{../figures/appendix_spell4_med.tex}
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 
-% \input{../figures/appendix_spell3_high.tex}
+% \input{../figures/appendix_spell4_high.tex}
 
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
         \captionsetup[subfigure]{labelformat=parens}
@@
 }
-\label{fig:results_spell3_high_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Fourth Spell}
-
-% low education
-
-% \input{../figures/appendix_spell4_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_low_pps}
-\end{figure}
-
-% Medium education
-
-% \input{../figures/appendix_spell4_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_med_pps}
-\end{figure}
-
-% High education
-
-% \input{../figures/appendix_spell4_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - high
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
-}
 \label{fig:results_spell4_high_pps}

### 2019-03-15 paper/sex_selection_spacing-ver2.tex
Write-up of distribution results

@@
 important differences in the distribution of spacing.
-Specifically, a concern is that the increases in average spacing that I show above may 
-mask an increased variance in birth spacing with families with fewer sons both more likely 
-to have a very pregnancy and to continue through pregnancies and sex-selective abortions 
-until they conceive a son.
+Specifically, a concern is that the increases in average spacing that I find above may 
+mask an increased variance in birth spacing for families with fewer sons if they are both 
+more likely to have a very early pregnancy and to continue through pregnancies and 
+sex-selective abortions until they conceive a son.
 This section, therefore, provides more detail on how spacing is distributed within a spell 
@@
 Because the conditional survival curves are independent of the likelihood of parity 
-progression within the spell, they all begin at 100\% and end at 0\%.
+progression, they all begin at 100\% and end at 0\%.
 
@@
 
-For women with no education, Figure \ref{fig:pps_low} shows that the median results
-above are consistent with the distribution of spacing within a spell with spacing 
-after only girls consistently shorter than after only boys.
-There are slight variations in how strong this effect is across the three spells.
-On the one hand, for the second spell the difference in spacing between
-when the first child is a girl versus when the first child is a boy as
-first-born remains almost the same across the four decades.
-On the other hand, for the third spell the differences between two girls and 
-the other sex compositions become more pronounced over time, and especially
-the difference between two girls and two boys have become substantially larger.
-The fourth spell results are based on relatively few observations but do
-indicate that women with either only girls or two girls and one boy have
-shorter spacing than women with only boys or one girl and two boys.
-Although the evidence is not substantial, it does appear that there is a slight
-preference for two boys in the sense that spacing becomes longer once the couple
-has at least two boys than for the other sex compositions.
+Figure \ref{fig:pps_low} shows the distribution of birth within a spell for women with no 
+education.
+For the second spell, what is most interesting is that there is almost no difference 
+between those with a first-born boy and those with a first-born girl.
+For the 1972--1984 period the two conditional survival curves only begin to diverge 
+at around 18 months (corresponding to 27 months after the first birth took place), and
+at that point close to 50 percent of the women have already had their second child.
+The literature on birth spacing and child health suggests that an interpregnancy interval
+of less than 18 months is associated with a higher risk of adverse health outcomes and
+mortality \citep{Conde-Agudelo2012}.
+With a nine-month pregnancy this means that almost 50 percent of the children born fall
+in this category, and, somewhat surprisingly, that there do not appear to be any particular 
+disadvantage for the child born after a girl than after a boy.%
+\footnote{
+Note that this does not imply that the first-born girl is not in a more adverse position
+than a first-born boy when the second child arrives.
+}
+The difference in spacing between a first-born girl and a first-born boy first-born 
+remains almost the same across the four decades.
+Furthermore, the proportion with very short spacing remains almost the same.
+
+For the third spell the son preference driven short spacing is evident throughout the
+distribution and becomes more pronounced over the four decades.
+Families with two girls are especially likely to have a birth early with 25 percent
+having a child within 12 months of the beginning of the spell (21 months after the prior
+second birth).
+That number is only slightly smaller four decades later. 
+The fourth spell shows changes in the distribution that appear to be more pronounced
+than for the third spell, although these results are based on fewer observed births.
+For families with three girls, 75 percent have had their fourth child within 36 months 
+after the beginning of the spell, but this occurs more than a year later for families
+with two or more boys.
 
@@
 with no education for the 1972--1984 period, as shown in Figure \ref{fig:pps_high}.
-The small difference points to these two very different groups of women behaving similarly
+The small differences point to these two very different groups of women behaving similarly
 in response to son preference in a situation where there was little access to
@@
 who might have had access.
-
-Whereas the no education group show almost no change across the four decades,
-the high education women show a rightward shift if the spacing pattern when
-the first child is a girl.
+However, whereas the no education group shows almost no change across the four decades for 
+the second spell, the high education women show an upward shift and a relatively even
+distribution of births within the spell for both women with a first-born son and women
+with a first-born girl.
 The result is that the spacing patterns are close to identical after first-born 
-girls and after first-born boys.
-Given the elevated predicted percentage boys in Table \ref{tab:median_sex_ratio_high},
-this change is consistent with the use of sex selection for women with a girl 
-as their first child.
-
-The hypothesized correlation between use of sex selection and reversal of 
-the standard spacing pattern show up clearly in the 2005--2016 period for the 
-third spell with spacing to the third child consistently longer with two girls 
-than with either two girls or one boy and one girl.
-The rightward movement for only girls from the, mostly, standard pattern in 
-the 1972--1984 period to the new pattern in the 2005--2016 period is substantial.
-There are also indications that the spacing distribution has moved rightward
-for women with one boy and one girl relatively to women with two boys, which
-provides some evidence for the use of sex selection for this group.
-The caveat is that the 1972--1985 period also had a biased sex ratio, which
-points to uncorrected recall error for this group.
-
-There is an even more pronounced rightward shift for spacing after only
-girls in the fourth spell for the first years of the spell. 
+girls and after first-born boys until after approximately 80 percent have had their 
+second child, although as mentioned above, this is driven in large part by the significant
+use of sex selection among women with a first-born girl.
+
+The correlation between the increased use of sex selection and the reversal of the 
+standard spacing pattern show up clearly in the 2005--2016 period for the third spell with 
+spacing to the third child consistently longer with two girls than with either two boys 
+or one boy and one girl throughout the entire spell.%
+\footnote{
+For the third spell, the 1972--1984 period show a close to standard pattern throughout, 
+although, as mentioned above, the sex ratios for women without girls was substantially 
+higher than the natural sex ratio either because of recall error or early use of 
+sex selection.
+}
+There is an even more pronounced rightward and upward shift for spacing after only
+girls in the fourth spell for the first years of the spell.%
+\footnote{
 The caveat is that there are few births to base the results on,
-especially for women with two or more sons.%
-\footnote{
-As mentioned, it is possible that some women had access to sex selection even
-in the first period.
-I would expect well educated urban women with more children to be the
-most likely to know about and use this early access to prenatal sex determination.
+especially for women with two or more sons.
 } 
@@
 and only boys.
-That is, of the women who are predicted to have a fourth child just over 30\%
-of women with three boys have had their fourth child, while less than 20\% of
-those with three girls have had theirs.
-Even at three years after the beginning of the spell, there is a more than 
-five percentage points difference.
-
-As discussed above there is some evidence of a two-son preference with
-the spacing pattern almost the same for women with three boys and with
-two boys and one girl.
-The conditional survival curve for women with one boy and two girls is
-consistently above those for women with two or more son, but below those 
-with three girls.
-The pattern fit the predicted sex ratios shown above where the highest
-predicted sex ratio is for women with only girls, followed by those
-with one son and two girls, and those with two or more boys having
-almost the same sex ratio.
+Both of the spells therefore show changes in the distribution of births that is in line
+with extensive use of sex selection among families with no or one son.
+
+% Even with sex selection, however, the observed pattern for the third and fourth spells
+% is not preordained.
+% We should expect 51.2 percent of the women to conceive a boy when they have their first 
+% pregnancy in the spell, which means that they do not need to use sex selection to have
+% a son.
+% Hence, even with sex selection, we might expect to observe a very short interval for the 
+% initial births if families with strong son preference still try to conceive sooner than 
+% those with lower son preference.
+% That we do not observe a short intervals for the early births calls into question the 
+% assumption that son preference leads to very early births with fewer sons even in 
+% situations when there is access to sex selection.
+% If, however, parents know that children born after short interpregnancy periods suffer 
+% from worse health outcomes it makes sense to wait longer before conceiving again in
+% this situation, precisely because they know that with sex selection the next child they 
+% carry to term will be a boy.
+% 
+% Hence, there are two potential reasons why son preference combined with access to
+% sex selection can lead to longer birth intervals.
+% First, the ``abortion'' effect, where each abortion extend birth spacing by between six
+% and twelve months.
+% Second, a ``delay'' effect, where parents conceive later because they know that short
+% spacing is detrimental to the next child's health, and that the next child is more likely
+% to be a boy because of access to sex selection.
+% The ``delay'' effect may explain why the twenty-five percentile birth intervals for the
+% second spell increase more for families with two girls than either of the other two
+% sex compositions, even though there should be few if any sex-selective abortions among
+% these births.%
+% \footnote{
+% See Appendix Table \ref{tab:p25_p50_p75_high}.
+% }
 
@@
 
-The West contains states with a high degree of son preference and use of sex selection.
-The North consists of states that also have a strong son preference, but initially had
+The ``West'' contains states with a high degree of son preference and use of sex selection.
+The ``North'' consists of states that also have a strong son preference, but initially had
 higher fertility and therefore lower likelihood of using sex selection.
-The East states generally have only a moderate level of son preference.
-Finally, the South contains states with traditionally low son preference and lower
+The ``East'' states generally have only a moderate level of son preference.
+Finally, the ``South'' contains states with traditionally low son preference and lower
 fertility than the rest of India.

### 2019-03-15 paper/sex_selection_spacing-ver2.tex
Need names in region graphs

@@
 \caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education - r1}
+a next birth for women with eight or more years of education in the ``West''}
 \label{fig:bootstrap_high_r1}
@@
 \caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education - r2}
+a next birth for women with eight or more years of education in the ``North''}
 \label{fig:bootstrap_high_r2}
@@
 \caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education - r3}
+a next birth for women with eight or more years of education in the ``East''}
 \label{fig:bootstrap_high_r3}
@@
 \caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education - r4}
+a next birth for women with eight or more years of education in the ``South''}
 \label{fig:bootstrap_high_r4}

### 2019-03-15 paper/sex_selection_spacing-ver2.tex
Initial commit of all region results

@@
 
-To examine the effect of differences in son preference, fertility, and use of sex 
-selection on birth spacing, I divide India into four broad regions based on degree of 
-son preference and initial fertility levels as in  \citet{retherford03b}, although 
-expanded to include all states in the surveys.
+\input{../tables/desc_region.tex}
+
+To understand how regional differences in son preference, fertility, and use of sex 
+selection affect birth spacing, I divide India into four broad regions based on degree of 
+son preference and initial fertility levels.
+Focus is on the most educated women since they are the main users of sex selection.
+The four regions are based on \citet{retherford03b}, although expanded to include all 
+states in the surveys.
 Table \ref{tab:regions} shows the four regions and the states that they contain.%
@@
 States that are formed later are allocated as closely as possible to the original state.
-
-\input{../tables/desc_region.tex}
-
 The ``West'' contains states with a high degree of son preference and use of sex selection.
 The ``North'' consists of states that also have a strong son preference, but initially had
-higher fertility and therefore lower likelihood of using sex selection.
+higher fertility and, therefore, lower likelihood of using sex selection.
 The ``East'' states generally have only a moderate level of son preference.
@@
 
+Figure \ref{fig:bootstrap_high_r1} shows the predicted average birth intervals, sex 
+ratios, and likelihoods of having a child by the end of the spell over time for the three 
+spells.
+What most stands out is how close to the national estimates the ``West'' estimates are.
+The predicted second spell average birth spacing is similar across families with a girl
+or a boy, and the average spacing substantially higher in the absence of boys than when
+there is at least one boy for the third spell.
+The main difference is that the very high predicted sex ratios reflect the expected higher 
+use of sex selection.
+For the second spell, the predicted sex ratios are around 60 percent for both urban and
+rural women, and for the third spell it it around 70 percent for urban women and 
+consistently above 60 percent for rural women.
+This higher use of sex selection, in turn, translates into longer average spacing.
+Furthermore, fertility has fallen faster than the national trend, especially for women
+with one or more sons.
+
 % \begin{figure}[htpb]
@@
 
+Figure \ref{fig:bootstrap_high_r2} shows the same outcomes for the ``North'' region. 
+Despite the idea that the ``North'' is characterized by high fertility and lower 
+likelihood of sex selection the differences to the ``West'' region is surprisingly small,
+at least in the urban areas.
+Fertility is, indeed, higher than in the ``West'' region, but the declines in the 
+probability of parity progression has been relatively rapid and mirrors the national one.
+The use of sex selection is also close to the ``West'', and there is the same reversal of
+spacing pattern as there.
+The rural areas of the ``North'' are a slightly different story.
+Fertility is substantially higher, and the use of sex selection much lower than in the
+rural areas of the ``West''. 
+That said, there still is clear evidence that the sex ratio is substantially above normal
+at close to 60 percent for the latest decade.
+
 % \begin{figure}[htpb]
@@
 
+The results for the ``East'' region of India are shown in Figure 
+\ref{fig:bootstrap_high_r3}, although the fourth spell results are not included because 
+the sample size is smaller for this region and the fourth spell results very noisy.
+Despite the ``South'' region generally considered to be the low fertility region, the
+reduction in fertility has been even faster in the ``East''.
+For the last decade only half of urban women with a first-born son are predicted to have
+a second child by the end of the spell period covered, which means almost nine years after
+the first birth.
+The probability is only slightly higher for those in urban areas with a first-born 
+daughter and still less than 70 percent.
+Not surprisingly, the probabilities are higher in rural areas, but still below the 
+national pattern.
+Similarly, conditionally on having a second child, the probabilities of having a third
+child are low, even in the absence of sons.
+In urban areas a woman with two girls have only around a 40 percent likelihood of 
+having a third child.
+
+What really stands out, however, is the rapid increase in the lengths of birth intervals,
+especially for the second spell.
+In both urban and rural areas, the predicted average birth intervals have gone up by
+more than a year across the four decade, and that is independent of whether the first-born
+was a boy or a girl.
+The increases in birth intervals are slightly smaller for third spell, but still 
+substantial.
+Although spacing pattern is consistently with some son preference with the average
+spacing slightly shorter in the absence of boys than when at least one boy is present,
+there is little evidence of sex-selective abortions.
+The sex ratios after a first-born daughter is slightly elevated, but much lower than 
+the prior two regions.
+There is more evidence for the third spell, where the sex ratio is close to 60 percent
+in the last period for urban women and the last two for rural women, but recall that 
+there is a much smaller likelihood of even making it to the third spell for this region
+than the other or the national average.
+
 % \begin{figure}[htpb]
@@
 \end{figure}
+
+The final region is the ``South'', shown in Figure \ref{fig:bootstrap_high_r4}.
+This region is historically thought to have the lowest degree of son preference of the
+regions of India.
+As for the ``East'', I do not show the fourth spell results because of the small sample 
+size and the associated noisy estimates.
+Judging from the second spell progression rate and the associated spacing pattern, it
+does, indeed, appear that there is little son preference in this region.
+The likelihood of having a second birth is relatively high at around 80 to 90 percent,
+and is close to independent of the sex of the first birth in both urban and rural areas.
+The predicted average spacing also show no sign of son preference, and the predicted
+sex ratios are close to the natural rate.
+The average birth spacing started high relatively to the other regions, and with little 
+change in fertility and no significant use of sex selection, it has increased only 
+slightly over time.
+
+With the high likelihood of a second birth and lower decline in the likelihood of a third
+birth, the ``South'' has a higher predicted fertility than the ``East''.
+What is more, for urban areas the average birth interval have increased substantially
+for those with only girls relative to those with a boy and a girl, corresponding to
+a predicted sex ratio close to 60 percent with only girls. 
+The signs of the use of sex selection also show up for rural women with no sons.
+Furthermore, over the four decades the likelihood of having a third birth has decreased
+much less than for either a boy and a girl or two boys.%
+\footnote{
+The relatively high parity progression for women without son does raise the question
+whether ``daughter avoidance'' is behind the fertility behavior in this region as
+suggested by \citet{DiamondSmith2008}.
+}
+The differences in parity progression and the sex ratios suggests that despite originally
+having less son preference, the ``South'' now appears to have the longer average spacing 
+in absence of son and the higher sex ratio associated with the use of sex selection.
 

### 2019-03-18 response/response-demography-1.tex
Address editor comments on literature review and weight of different sections

@@
 and to highlight the contributions of the paper.
-
-- Spacing as an indicator for son preference
-- The relationship between spacing and child health
-- The relationship between spacing and women's health
-- Important for understanding how spacing in general behaves. See last point from
-editor: if lower fertility, better health, and increased female labor market participation 
-are all is associated with a compression of spacing, the use of sex selection would
-work against this trend and make it look like India is not behaving like other countries.
-- Women's role in general
-
-- complete rewrite of introduction
-- highlight how method is different in ``Estimation Strategy'' section.
+I now cover the research on using spacing as a measure of son preference, the 
+relationship between spacing and child health (both older and younger child), the 
+effect on women's health and other outcomes, and, finally, the limited and mixed results
+on what determines birth spacing behavior in developing countries compared to developed 
+countries.
+I use these to motivate why examining how birth spacing has been affected by the use of
+sex selection is important, and, in addition, highlight the three main questions I address 
+in the paper: the effect of sex selection on birth intervals, the effect of sex selection
+on the distribution of births within spells, and, finally, how the effects have varied
+with geographical region.
 
@@
 maternal education. Does maternal education proxy for access to sex
-selective technology, preferences for sons, etc.? In addition, how does
+selective technology, preferences for sons, etc.?
+
+[Response:]
+
+In addition, how does
 selection into the highest/lowest educated categories change over the 45
@@
 [Response:]
+
+As detailed below, I have substantially shorten the ``Estimation Strategy'' section.
+The results section is not necessarily shorter, but is better focused on the spacing
+results, guided by the three main questions.
+There is also less focus on the sex selection results.
+Specifically, I have removed the section on how the use of sex-selective abortions changes 
+within a spell since it, as originally written, was more focused on sex selection than
+the spacing, and that the spacing question is better addressed in the section on the
+distribution of births within spells.
+Obviously I still need to discuss how sex selection has changed to tie those to the 
+changes in spacing, but I have tried to make these result mainly serve the overall
+spacing analysis.
 

### 2019-03-19 response/response-demography-1.tex
Add discussion of expanded discussion of fertility

@@
 
-First, the description of the problem and literature review are sparse.
+\begin{enumerate}
+
+\item First, the description of the problem and literature review are sparse.
 The front end of the paper should be revised to situate the study in the
@@
 
-Second, a conceptual framework or theoretical argument is needed to
+\item Second, a conceptual framework or theoretical argument is needed to
 motivate the decision to examine birth intervals and sex composition by
@@
 selective technology, preferences for sons, etc.? 
-
-[Response:]
-
 In addition, how does
@@
 
-Third, the paper is heavy on the description of methods and results.
+\item Third, the paper is heavy on the description of methods and results.
 These sections could be shortened and reorganized to focus on the most
@@
 
-Fourth, discussion of the fertility transition is neglected and only
+\item Fourth, discussion of the fertility transition is neglected and only
 discussed in the conclusion. At a minimum, you should consider providing
@@
 
-[Generically, spacing tend to decline with lower fertility (check this). 
-Presumably the decline in spacing is because part of the cause is higher female labor 
-market participation, which makes it more attractive to space children closer together.
-Not clear whether this is the case for India - The R1 suggested paper might be a good
-starting point with a tie-in to compression.
-Compression can also come from improved health and/or less migration.
+I address this a number of different ways.
+First, in the Introduction, I discuss the decline in fertility when introducing why India 
+is an interesting case, with special focus on the relationship between declining fertility 
+and increased use of sex selection and, hence, by my hypothesis on birth spacing.
+Second, the suggestion by Referee 1 to use graphical presentation of the results made it 
+possible to include the likelihood of parity progression for each of the three spells, 
+which allows me to discuss how fertility has decreased across the three education groups
+and by urban and rural areas.
+I have also added the parity progression likelihood to the original tables, which are now
+included in the online Appendix.
+Third, I discuss the changes in fertility directly in the Results section.
 
-On the flip side, lower fertility place additional pressure on women to use
-sex selection, which lead to *less* compression.
-]
+% [Generically, spacing tend to decline with lower fertility (check this). 
+% Presumably the decline in spacing is because part of the cause is higher female labor 
+% market participation, which makes it more attractive to space children closer together.
+% Not clear whether this is the case for India - The R1 suggested paper might be a good
+% starting point with a tie-in to compression.
+% Compression can also come from improved health and/or less migration.
+% 
+% On the flip side, lower fertility place additional pressure on women to use
+% sex selection, which lead to *less* compression.
+% ]
+
+\end{enumerate}
 
@@
 
-1. The key contribution of the paper is the use of birth spacing and sex
+\begin{enumerate}
+\item 1. The key contribution of the paper is the use of birth spacing and sex
 ratios to examine changes and differentials in possible sex-selective
@@
 
-2. The paper would need to articulate its contribution clearly. The
+\item 2. The paper would need to articulate its contribution clearly. The
 paper seems to be focussed too much on methodology and less on
@@
 
-3. The literature review must be systematic. The paper seems to move too
+\item 3. The literature review must be systematic. The paper seems to move too
 quickly to estimation strategy. Before presenting this, the literature
@@
 
-4. The demographic literature, for example, by works from Christophe Z
+\item 4. The demographic literature, for example, by works from Christophe Z
 Guilmoto, doesn’t seem to be consulted. Guilmoto and colleagues many
@@
 
-5. The use of competing hazard models is not new in demographic research
+\item 5. The use of competing hazard models is not new in demographic research
 and doesn’t require long exposition. This section can be cut
@@
 
-6. The use of NFHS data including the most recent data are welcome. An
+\item 6. The use of NFHS data including the most recent data are welcome. An
 additional limitation to those addressed in the paper is the issue of
@@
 
-7. It is not clear why exactly 22, 23, 25 years are used a cut-off
+\item 7. It is not clear why exactly 22, 23, 25 years are used a cut-off
 points.
@@
 
-8. I understand the empirical reason for not increasing the number of
+\item 8. I understand the empirical reason for not increasing the number of
 variables. However, a key variable that is essential to consider is
@@
 
-9. The three tables are logically organized and contain a wealth of
+\item 9. The three tables are logically organized and contain a wealth of
 information. But there are too many comparisons to make in each of the
@@
 
-10. As sex composition and sex ratios has been examined in the literature, I think
+\item 10. As sex composition and sex ratios has been examined in the literature, I think
 it would make sense to not present findings on that in great detail. As
@@
 
-11. The results talk about compression of spacing. This is important and
+\item 11. The results talk about compression of spacing. This is important and
 literature on it should be presented in the intro or lit review section.
@@
 
-12. As there are many results presented, it would make sense to have a
+\item 12. As there are many results presented, it would make sense to have a
 paragraph at the beginning of the conclusion highlighting the key
@@
 
-13. Overall, the paper is empirically strong but needs to build on the
+\item 13. Overall, the paper is empirically strong but needs to build on the
 contextual, theoretical, and prior demographic literature. As the
@@
 [Response:]
+
+\end{enumerate}
 

### 2019-03-19 paper/sex_selection_spacing-ver2.tex
Edit Introduction

@@
 }
-Longer birth intervals may, therefore, cease to be an indication of declining son
-preference, but could instead come about precisely because strong son preference makes
-couples more likely to use sex selection.
+Longer birth intervals in the absence of sons, which previously would be taken to indicate 
+a lower son preference, now may arise precisely because a sufficiently strong son 
+preference makes couples use sex selection.
 
@@
 % [Why India?]
-India is a particularly compelling case.
-India has a long history of male preference, especially in the northern states 
-\citep{Kishor1993,murthi95,arnold98}.
-A significant proportion of Indian families exhibit a son preference based 
-differential stopping behavior, where, for a given number of children, they are more 
-likely to have an additional child if they have not yet reached their preferred number of 
-sons \citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
+India is a particularly compelling case since it has a long history of male preference, 
+especially in the northern states \citep{Kishor1993,murthi95,arnold98}.
+A significant proportion of Indian families exhibit differential stopping behavior, where, 
+for a given number of children, they are more likely to have an additional child if they 
+have not yet reached their preferred number of sons 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
 \footnote{
@@
 In some instances, however, the fertility decline appears to have created a stronger 
-aversion to daughters rather than a stronger preference for son \citet{DiamondSmith2008}.
-}
-At household level the strongest predictor of the use of sex selection is the sex 
-composition of previous children \citep{retherford03b,jha06,abrevaya09,Portner2015b}.
-For families without a son, the higher the parity, the higher is the probability
-of having a son as the next birth.
+aversion to daughters rather than a stronger preference for son \citep{DiamondSmith2008}.
+}
+The strongest predictor of the use of sex selection is the sex composition of previous 
+children; for families without a son, the higher the parity, the higher is the probability
+of having a son as the next birth \citep{retherford03b,jha06,abrevaya09,Portner2015b}.
 The use of sex selection also increases with socioeconomic status, especially 
@@
 overshooting their preferred number of children.
-This idea may explain why better-educated women have shorter spacing than less educated 
-women in some instances but not in others.
-These two counteracting effects may explain why finding statistically significant effects 
-of contraception use on birth spacing is difficult \citep{Yeakey2009}.%
+These two counteracting effects may explain why better-educated women have shorter spacing 
+than less educated women in some instances but not in others and why finding statistically 
+significant effects of contraception use on birth spacing is difficult \citep{Yeakey2009}.%
 \footnote{
@@
 
+[TK change based on rewrite of section]
 Second, have the shapes of the survival curves changed?
@@
 
-% [Results - need updating]
+% [TK Results - need updating]
 There are three main results.

### 2019-03-20 paper/sex_selection_spacing-ver2.tex
Restructuring Results section
Still missing distributional results and regional results.

@@
 
-The central question addressed here is the extent to which spacing patterns 
-significantly changed as prenatal sex determination became available.
-Specifically, did the spacing after girls increase relative to the spacing
-after boys?
-The underlying idea is that in the absence of sex selection son 
-preference leads to shorter spacing after the birth of a girl than after the 
-birth of a boy, whereas son preference increases the spacing after the birth 
-of a girl relative to after the birth of a boy when prenatal sex selection is 
-available.
-I introduce a new method that simultaneously accounts for spacing
-between births and the potential use of sex selection. 
+The central question addressed here is the extent to which spacing patterns significantly 
+changed as prenatal sex determination became available.
+The underlying idea is that in the absence of sex selection son preference leads to shorter 
+spacing after the birth of a girl than after the birth of a boy, whereas when prenatal sex 
+selection is available son preference increases the spacing after the birth of a girl 
+relative to after the birth of a boy.
+I introduce an empirical method that simultaneously accounts for spacing between births 
+and the potential use of sex selection. 
 I apply the method to over four decades of data from India's NFHS.
-The results show two very different approaches to son preference.
-
-At one extreme, women without education mostly follow the standard 
-pattern of shorter spacing when a woman does not have the desired number of 
-sons.
-There is also limited evidence of biased sex ratios and the increases in
-spacing that should follow from the use of sex selection.
- In the situations where there are elevated sex ratios for women without
-education, the spacing patterns are close to those with more regular sex
-ratios. 
-Hence, it is difficult to conclude that the changes in sex
-ratios indicate sex selection rather than normal variation or problems
-with recall errors.
-
-At the other extreme, women with eight or more years of education have
-experienced an almost complete reversal of the traditional spacing patterns.
-Rather than having the next birth sooner as they mostly did before 
-sex selection became available, women with either no or one son now 
-have substantially longer spacing than if they have two or more sons.
-As shown by the increasingly significant deviations in the sex ratio
-from the natural sex ratio, these changes are likely due to increased
-use of sex selection rather than changes in son preference. 
-Banning prenatal sex determination has not been able to
-reverse the use, although it is possible that it has slowed the rate 
-of increase.
-
-Over the last 40 years, there has been a general increase in median
-spacing for all education groups, but especially for the most 
-educated women.
-The exception is for the spacing between marriage and first birth
-where there are two counteracting forces: women have become less likely 
-to conceive before marriage, and there has been a substantial compression 
-in the variation of spacing.
-The result is that median spacing from marriage to first birth
-has changed little or even declined for the best-educated women.
-Both the decrease for the first spell and the increase for higher-order
-spells are consistent with increased access to contraceptives over
-time \citep{Yeakey2009}.
-
-Although it is not possible to directly observe whether sex selection
-causes the unequal sex ratio and longer spacing the results are
-consistent with a general increase in sex selection over time. 
-The apparent increase in the use of sex selection is mainly found among
-women with more education and more so in urban than in rural areas,
-although the differences between urban and rural areas are relatively
-minor. 
-Compared to previous research one result stands out. 
-It appears that the use of sex selection is spreading to women with lower 
-levels of education.
-Even women with one to seven years of education show unequal sex ratios 
-and longer spacing for their higher-order spells.
-
-The results here point to two important, interconnected, questions 
-for future research:
-What is the connection between falling fertility and the 
-use of sex selection and is the use of sex selection increasing 
-or decreasing over time?
-It is clear that fertility has been declining over time in India,
-although it is important to note that the decline might be
-overstated precisely because of increased use of sex selection and
-the resulting longer spacing between births makes it less likely 
-that we will observe births to women, even though they eventually
-will happen.
-The fact that biased sex ratio occurs at lower-order spells over
-time and is starting to show up for women with less education 
-all indicate that lower fertility and use of sex selection are
-related, but a more detailed analysis is needed.
-Furthermore, although examining spells separately, as done here, is a useful
-first step in understanding how sex selection changes over time,
-it does not lend itself easily to examine the degree to which
-sex selection changes over time.
-For both, a combined model that incorporates the full fertility
-history of women would be more appropriate.
-
-The results here also lead to a set of broader questions that
-future research should address.
-First, to what extent are the improvements in health for girls
-relative to boys the result of selection, the longer spacing between
-births, or changing son preference?
-There is some evidence that sample selection can make it appear that girls are healthier, 
-even though the underlying cause is a combination of sex selection and higher mortality 
-together with recall error \citep{Portner2018a}. 
-Understanding what role these factors play in better health for
-girls is especially important when evaluating policies that 
-aim to directly limit the use of sex selection rather than 
-changing preferences or incentives.
-If the better health outcomes for girls are, for example, an unintended 
-side-effect of the longer spacing that arises from sex-selective 
-abortions, then an effective ban on sex selection may, at least
-temporarily, worsen health outcomes for girls.
-
-[move to conclusion?]
-We know that health outcomes for girls appear to improve in the presence of sex 
-selection \citep{Lin2014,Hu2015}.
-It is possible that these improvements are an unintended side-effect of the longer spacing 
-that arises from sex-selective abortions, rather than because the smaller number of girls 
-makes them more valued as is often assumed.
-A first step
-
-Second, we need to understand how female labor force participation
-interacts with the use of sex selection.
-Increased autonomy for women, arising, for example, from better opportunities
-for working outside the home, has been suggested as a way to increase
-women's status and thereby lower the use of sex selection \citep{Das-Gupta2016}.
+
+The results show three major, interrelated trends over the last 40 years.
+First, fertility has declined for all groups, as shown by the parity progression
+probabilities, with a larger decline the more educated the woman.
+Across all groups, the likelihood of having an additional child in each spell depends 
+strongly on how many sons you already have, with women with none or only one son having
+the highest probability of a birth.
+Second, there has been a general increase in the length of average birth 
+intervals for all education groups.
+The increase in average birth interval is larger the higher the spell and the higher the 
+education group.
+Finally, as shown by the increasing sex ratios for women with no or only one son there
+has been a substantial increase in the use of sex selection over time.
+As for fertility and birth intervals, this increase is larger the higher the spell and
+with higher education.
+
+The results also show two very different approaches to son preference with important
+impacts on spacing patterns.
+At one extreme, rural women without education mostly follow the standard pattern of 
+shorter spacing when a woman does not have the desired number of sons.
+The strength of this pattern does, however, depend critically on spell number.
+For the second spell, although the average interval after a first-born girl is shorter
+than the average interval after a first-born boy, the difference is small.
+The differences in spacing is larger for the third spell and largest for the fourth.
+For the the fourth spell, the divergence in intervals across sex compositions have 
+increased over time, with the largest increases in average intervals for women with 
+two or three boys.
+There has also been an increase in average spacing for women with only girls, and there
+is some limited evidence of biased sex ratios, which suggests that this increases in
+spacing follow from the use of sex selection.
+
+At the other extreme, urban women with eight or more years of education have experienced 
+an almost complete reversal of the traditional spacing patterns as a result of falling
+fertility and the associated extensive use of sex selection.
+Rather than having the next birth sooner as they mostly did before sex selection became 
+available, women with either no or one son now have substantially longer spacing than if 
+they have two or more sons.
+As shown by the increasingly significant deviations in the sex ratio from the natural sex 
+ratio, these changes are likely due to increased use of sex selection rather than sudden
+reversal in son preference.%
+\footnote{
+Banning prenatal sex determination has not been able to reverse the use, although it is 
+possible that it has slowed the rate of increase.
+}
+Only the second spell has not seen a reversal despite a substantial increased use of
+sex selection, mainly because the average spacing with a first-born boy has increased 
+independently by more than nine months.
+
+TK Distribution results
+
+TK Regional differences
+
+The results here lead to a set of broader questions that future research should address.
+First, what is behind the substantial increases in spacing even for women who are unlikely 
+to use sex selection, and, related, why does spacing appear to increase with declining 
+parity progression probabilities?
+The distributional results provide an initial indication that most of the increases in 
+average birth intervals come from the upper end of the birth intervals rather an generic
+increase across the distribution.
+It is, however, unclear why we are seeing relatively more very long birth intervals over
+time, and the longer average spacing seem to run counter to a general reduction in the 
+length of women's reproductive spans found in earlier research \citep{Padmadas2004}.
+Understanding whether the longer average spacing is by choice at the beginning of the 
+spell, because of unplanned pregnancies, or because of changes in economic circumstances 
+that allow families to have an additional child later has important implications for both 
+policy design and outcomes for mother and children.
+
+Second, to what extent are the improvements in health for girls relative to boys the result 
+of selection, the longer spacing between births, or changing son preference?
+We know that health outcomes for girls appear to improve in the presence of sex selection 
+\citep{Lin2014,Hu2015}.
+Furthermore, there is some evidence that sample selection can make it appear that girls 
+are healthier, even though the underlying cause is a combination of sex selection and 
+higher mortality together with recall error \citep{Portner2018a}. 
+Understanding what role these factors play in better health for girls is especially 
+important when evaluating policies that aim to directly limit the use of sex selection 
+rather than changing preferences or incentives.
+If the better health outcomes for girls are, for example, an unintended side-effect of the 
+longer spacing that arises from sex-selective abortions, rather than because the smaller 
+number of girls makes them more valued as is often assumed, then an effective ban on sex 
+selection may, at least temporarily, worsen health outcomes for girls.
+
+Finally, we need to understand how female labor force participation interacts with the use 
+of sex selection.
+Increased autonomy for women, arising, for example, from better opportunities for working 
+outside the home, has been suggested as a way to increase women's status and thereby lower 
+the use of sex selection \citep{Das-Gupta2016}.
 This may, however, be a double-edged sword.
-On the one hand, it is a clear benefit to the women who gain  
-bargaining power, and it increases the cost of repeated 
-sex-selective abortions because the increased duration between births
-would cause a stronger disruption in labor market participation.
-On the other hand, it may further lower desired fertility, and 
-that may, everything else equal, lead to higher use of sex selection.
-Understanding the trade-off between long-term benefits from improvements in
-women's labor force participation and short-term costs from potential 
-increases in sex selection is of paramount importance.
+On the one hand, it is a clear benefit to the women who gain bargaining power, and it 
+increases the cost of repeated sex-selective abortions because the increased duration 
+between births would cause a stronger disruption in labor market participation.
+On the other hand, it may further lower desired fertility, and that may, everything else 
+equal, lead to higher use of sex selection.
+Understanding the trade-off between long-term benefits from improvements in women's labor 
+force participation and short-term costs from potential increases in sex selection is of 
+paramount importance.
 

### 2019-03-20 response/response-demography-1.tex
Add compression and reduced focus on sex ratios

@@
 
+As detailed above, I have refocused the Results section to focus mainly on birth spacing
+and how that is affected by the increased use of sex selection over time.
+I now instead refer to the previous literature on sex ratios and use that as a guide for
+structuring the analysis of birth spacing.
+
 \item 11. The results talk about compression of spacing. This is important and
@@
 [Response:]
-
-[Compression is only for first birth as far as I remember. Need to check that.
-Check on paper for their analysis.]
+Compression in the original manuscript was only for first birth, and I no longer cover 
+those because of the data issues discussed above.
+I do, however, agree that this is an important question, even if I cannot directly
+address it here.
+I, therefore, have added this to the conclusion when I discuss areas of future research.
 

### 2019-03-21 paper/sex_selection_spacing-ver2.tex
Minor edits

@@
 Note that this does not imply that the first-born girl is not in a more adverse position
-than a first-born boy when the second child arrives.
+than a first-born boy when the second child arrives, just that this is not directly
+related to a short birth interval.
 }

### 2019-03-21 response/response-demography-1.tex
Respond to Editor's question on proportionality variables, especially education

@@
 
-[selection]
+I have substantially expanded the discussion of the choice of non-proportionality 
+variables in the ``Explanatory Variables'' section (and added a footnote to that effect 
+in the ``Estimation Strategy'' section).
+This now covers education, sex composition, and area of residence in more detail.
+If there is a more appropriate place for this discussion, I am open to moving it.
 
-There are two possible explanations, economics and cultural.
+When it comes to selection, there are two possible explanations: one economic and one 
+cultural.
+In the ``economic'' explanation, the use of sex selection is mainly driven by the lower 
+fertility that comes from higher opportunity cost of time and the higher income that allow 
+those with higher education to use sex selection.
+In that case, there is essentially no selection bias since the use of sex selection is 
+driven by factors that are identical across those with the same level of education.
 
-For the economics one, the use of sex selection is mainly driven by the lower fertility
-that comes from higher opportunity cost of time and the higher income that allow those
-with higher education to use sex selection.
-Here there is essentially no selection bias since the use of sex selection is driven
-by factors that are identical across those with the same level of education.
-
-The cultural explanation is that originally those with higher education where also those
-groups with the strongest son preference (presumably those who are also higher caste).
+The ``cultural'' explanation is that originally those with higher education where also 
+those groups with the strongest son preference (presumably also higher caste).
 The expansion of access to education brought other groups/castes into connection with
-the higher castes and assimilation of their son preference norms.
-Presumably the assimilation is not complete and those newer to higher education would
-therefore have lower son preference and therefore lower use of sex selection.
+the higher castes and lead to assimilation of the high caste son preference norms.
+Presumably this assimilation would not be complete and those groups newer to higher 
+education would therefore have lower son preference and therefore lower use of sex 
+selection.
 This means that any appearance of lower use of sex selection could be a selection story,
 and that the initial group's son preference is just as strong.
+The cultural explanation also suggests a reason for why the stated son preference appear 
+to decline over time: the ``newer'' entrants have lower initial son preference and, 
+therefore, the average son preference for high education women will decline over time.
+\citep{bhat03}, \citep{pande07}.
 
-The cultural explanation also suggests a reason for why the states son preference 
-appear to decline over time.
-The ``newer'' entrants have lower initial son preference and therefore the average
-son preference for high education women will decline over time.
-\citep{bhat03}, \citep{pande07}.
+Since I have no way of separating out these two possible explanation with the available
+data and set up, I have not included this discussion in the paper itself. 
+One possible approach would be to included this as a question for future research in the
+Conclusion.
+If you think it will make the paper stronger, I am, of course, open to including the
+discussion there or anywhere else it might fit better.
 

### 2019-03-21 paper/sex_selection_spacing-ver2.tex
Respond to Editor's question on proportionality variables, especially education

@@
 are done separately for different levels of mothers' education and for different 
-time periods.
+time periods.%
+\footnote{
+The choice of which variables to use for non-proportionality is discussed in more detail
+in the ``Explanatory Variables'' section.
+}
 
@@
 I chose these variables because the prior literature shows that they affect 
-spacing choices and correlate with sex selection.
+spacing choices and the likelihood of using sex selection.%
+\footnote{
 Increasing the number of variables interacted with the baseline hazard would
@@
 precisely estimate.
+}
+
+The first variable that is likely to affect the hazard rate in a non-proportional manner
+is education.
+First, there is evidence, even in the absence of sex selection, that women with
+different education levels have different hazard profiles, although the size and direction
+of the effect vary across areas and time 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
+Second, as discussed above, the use of sex selection increases with socioeconomic 
+status, especially education, and the use of sex selection is unlikely to be the
+same throughout a spell, which means that education cannot enter in a proportional
+fashion. \citep{retherford03b,jha06,Portner2015b}.
+One potential reason for the correlation between education and sex selection is that
+increasing education of mothers correlates closely with lower fertility 
+\citep{schultz97}.
+This lower fertility leads, in turn, to a higher likelihood of using sex selection
+\citep{das_gupta97,Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
+\footnote{
+In principle, it is possible that part of the higher likelihood is driven by a stronger
+preference for son, independently of desired fertility.
+There is, however, evidence that higher education women have shown a decline in
+son preference \citep{bhat03,pande07}
+}
+Another reasons is that having more education is closely associated with higher income and 
+wealth, which makes it easier to access illegal services such as prenatal sex 
+determination.
+It is not possible to separate these two effects here.
 
@@
 The models are estimated separately for each education level to reduce
-the potential problem of including other variables as proportional.
-Increasing education of mothers correlates closely with lower fertility 
-\citep{schultz97}, and 
-we should expect lower fertility to lead to more use of sex selection.%
+the potential problem of including other variables as proportional.%
 \footnote{
@@
 
+As discussed, the sex composition of previous children affects both the timing
+of births and the use of sex-selective abortions 
+\citep{retherford03b,jha06,Bhalotra2008,abrevaya09,Portner2015b,Kumar2016,Soest2018}.
 I capture sex composition with dummy variables for the
@@
 additional groups for the fourth spell.
-As discussed, the sex composition of previous children affects both the timing
-of births and the use of sex-selective abortions.
-
+
+Whether a woman lives in an urban or rural area affect both her fertility level and
+her access to sex selection \citep{retherford03b,jha06,Portner2015b}.
 Area of residence is a dummy variable for the household living in

### 2019-03-21 paper/sex_selection_spacing-ver2.tex
First spell no longer covered

@@
 periods, even though India's population has become progressively more urbanized.
-For the first and second periods, over 32\% of the women 
-entering the first spell lived in urban areas, falling to 
-30\% for the third period and 26\% in the last period.
 The most likely explanation is that the age of marriage has increased
@@
 
-Age at marriage increased over time across all three education groups.
-The most substantial increase was for women without any education, where
-the average went from below 16 years of age to 18.5.
-The smallest change is for the most educated women where the average age
-at marriage went up by less than a year---from 19.6 to 20.4---across the 
-four periods.
+% Age at marriage increased over time across all three education groups.
+% The most substantial increase was for women without any education, where
+% the average went from below 16 years of age to 18.5.
+% The smallest change is for the most educated women where the average age
+% at marriage went up by less than a year---from 19.6 to 20.4---across the 
+% four periods.
 

### 2019-03-21 paper/sex_selection_spacing-ver2.tex
Expand on distribution results section and update distribution part of Introduction

@@
 to sex selection has had on spacing.
-The overall hypothesis I examine here is that spacing patterns significantly changed 
-as prenatal sex determination became available.
-I address three questions in order of importance.
-
-First, how did birth intervals change over time for different groups and how are those 
-changes related to the likely use of sex selection?
+The overall hypothesis is that spacing patterns significantly changed as prenatal sex 
+determination became available.
+Specifically, I address three questions.
+
+First, how did average birth intervals change over time for different groups and how are 
+those changes related to the likely use of sex selection?
 The underlying hypothesis is that in the absence of sex selection son preference leads to 
@@
 increases the spacing the fewer boys a family has when prenatal sex selection is available.
+I still expect parents to \emph{try} to conceive earlier after the birth of a girl than 
+after a boy, but the abortions will increase the duration between births, and may even 
+lead to longer average spacing after the birth of girls than after boys.
 Families with son preference who---for one reason or another---do not use prenatal sex 
@@
 
-[TK change based on rewrite of section]
 Second, have the shapes of the survival curves changed?
-The shapes of the survival curves provide information both on general changes in birth 
-spacing and whether parents are still trying to conceive earlier after girls than boys.
-I still expect parents to \emph{try} to conceive earlier after the birth 
-of a girl than after a boy, but the abortions will increase the duration between births, 
-and may even lead to longer average spacing after the birth of girls than after boys.
-I expect this to be the case if there is still a strong preference for boys, and this 
-behavior may even become more pronounced with access to sex selection.
+Very short birth intervals are associated with worse health outcomes and increasing 
+mortality risk \citep{Conde-Agudelo2012}.
+Hence, understanding how the distribution of birth intervals changes help us understand to 
+what extent we can expect improvements in health outcomes.
+We should, for example, expect different impacts on the distribution of birth intervals
+depending on whether parents change their spacing behavior based on an increasing 
+concern for child health or from a strong son preference leading to continued pregnancies
+until a son is conceive.
 
@@
 
-Average spacing is a convenient way to understand the overall changes but may hide 
-important differences in the distribution of spacing.
-Specifically, a concern is that the increases in average spacing that I find above may 
-mask an increased variance in birth spacing for families with fewer sons if they are both 
-more likely to have a very early pregnancy and to continue through pregnancies and 
-sex-selective abortions until they conceive a son.
+The results above show consistent increases in average spacing across the board.
+Average spacing is a convenient way to understand the overall changes in behavior but may 
+hide important differences in the distribution of spacing.
+Specifically, whether these increases in average spacing come from fewer births after 
+very short intervals, because of even longer spacing from births with already long 
+spacing, or a general increase in spacing have important implications for what effects the
+increase in average spacing are likely to have and how to interpret the motivation for
+the changes.
+On one hand, if there still are many births that occur after very short intervals, the 
+increase in average spacing is unlikely to have a substantial impact on health outcomes
+since the literature on birth spacing and child health suggests that an interpregnancy 
+interval of less than 18 months is associated with a higher risk of adverse health 
+outcomes and mortality \citep{Conde-Agudelo2012}.
+On the other hand, we may see a reduction in early observed births and more long spells if 
+families with fewer sons are both more likely to have a very early pregnancy and to 
+continue through pregnancies and sex-selective abortions until they conceive a son.%
+\footnote{
+It is unclear what the optimal response in timing of pregnancies to the availability of 
+sex selection should be.
+The expected birth intervals become longer with the use of sex selection, which may be 
+costly for parents leading them to try to conceive even earlier than previously.
+Conversely, if parents know that short birth intervals are detrimental to the next child's
+health, and with sex selection the next child is likely be a boy, it might make sense to 
+wait longer before conceiving.
+}
+
 This section, therefore, provides more detail on how spacing is distributed within a spell 
 and across sex compositions using a graphical approach.
-
 I show survival curves conditional on predicted parity progression rather than standard 
@@
 Instead of averaging across the entire sample, I calculate the conditional survival curves 
-for an average woman using the method detailed in Section \ref{sec:strategy}.%
-\footnote{
-To complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
-\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
-percentiles durations with bootstrapped standard errors based on averages across all women 
-in the each subsample as for the results above.
-} 
+for an average woman using the method detailed in Section \ref{sec:strategy}.
 For each combination of education and spell, I use values based on the average age at the 
@@
 effects do not drive any changes.
-
-In the interest of brevity, I discuss only a select set of subsamples.
+To complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
+\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
+percentiles durations with bootstrapped standard errors based on averages across all women 
+in the each subsample as for the results above.
+
+In the interest of brevity, I discuss only two subsamples.
 Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex compositions for 
@@
 at that point close to 50 percent of the women have already had their second child.
-The literature on birth spacing and child health suggests that an interpregnancy interval
-of less than 18 months is associated with a higher risk of adverse health outcomes and
-mortality \citep{Conde-Agudelo2012}.
-With a nine-month pregnancy this means that almost 50 percent of the children born fall
-in this category, and, somewhat surprisingly, that there do not appear to be any particular 
-disadvantage for the child born after a girl than after a boy.%
+With a nine-month pregnancy, this means that almost 50 percent of the children born are
+born within the interpregnancy interval associated with a higher risk of adverse health
+outcomes and mortality, and, somewhat surprisingly, that there do not appear to be any 
+particular disadvantage for the child born after a girl than after a boy.%
 \footnote{
@@
 
-The correlation between the increased use of sex selection and the reversal of the 
-standard spacing pattern show up clearly in the 2005--2016 period for the third spell with 
-spacing to the third child consistently longer with two girls than with either two boys 
-or one boy and one girl throughout the entire spell.%
-\footnote{
 For the third spell, the 1972--1984 period show a close to standard pattern throughout, 
@@
 sex selection.
-}
+The correlation between the increased use of sex selection and the reversal of the 
+standard spacing pattern show up clearly in the 2005--2016 period for the third spell with 
+spacing to the third child consistently longer with two girls than with either two boys 
+or one boy and one girl throughout the entire spell.
+This pattern is most consistent with early and continued use of sex selection, rather 
+than a general reduction in the likelihood of very short birth intervals.
+It also means, that previous girls can expect a longer period without a younger sibling,
+which may reduce the sibling competition for resources.
+
 There is an even more pronounced rightward and upward shift for spacing after only
@@
 
-% Even with sex selection, however, the observed pattern for the third and fourth spells
-% is not preordained.
 % We should expect 51.2 percent of the women to conceive a boy when they have their first 
@@
 % those with lower son preference.
-% That we do not observe a short intervals for the early births calls into question the 
-% assumption that son preference leads to very early births with fewer sons even in 
-% situations when there is access to sex selection.
 % If, however, parents know that children born after short interpregnancy periods suffer 
@@
 % to be a boy because of access to sex selection.
-% The ``delay'' effect may explain why the twenty-five percentile birth intervals for the
-% second spell increase more for families with two girls than either of the other two
-% sex compositions, even though there should be few if any sex-selective abortions among
-% these births.%
-% \footnote{
-% See Appendix Table \ref{tab:p25_p50_p75_high}.
-% }
 

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Need discussion of distribution results in Conclusion

@@
 
-\subsection{Distribution of Birth Spacing Within Spells and Across Sex Compositions}
+\subsection{Distribution of Birth Spacing Within Spells}
 
@@
 
-\input{../tables/desc_region.tex}
-
 To understand how regional differences in son preference, fertility, and use of sex 
@@
 fertility than the rest of India.
+
+\input{../tables/desc_region.tex}
 
@@
 
-The results show three major, interrelated trends over the last 40 years.
+Three major, interrelated trends emerge from the data over the four decades.
 First, fertility has declined for all groups, as shown by the parity progression
@@
 
-The results also show two very different approaches to son preference with important
+The results show two very different approaches to son preference with important
 impacts on spacing patterns.
@@
 
-TK Distribution results
+Despite the differences in average spacing across sex compositions of prior children,
+the picture of how son preference affects spacing is more complicated than excepted.
+First, for the second spell the differences in birth intervals for the first 25 percent of 
+births are negligible across sex compositions, despite that these birth intervals are
+clearly within the durations considered the most likely to generate adverse outcomes.
+Furthermore, there is little difference in this spacing patterns across education.
+Hence, most of the divergence in spacing patterns across sex compositions arise from
+longer spells, which are likely to have less negative impacts on children and the mother.
+Second, one of the side-effects of the extensive use of sex selection for women with eight
+or more years of education for the third and fourth spell is that only-girls families
+not only end up with longer average intervals to the birth of the next, they also are now
+much less likely to have a short, i.e. less than 18 months, interpregnancy interval,
+which may reduce the sibling competition for resources.
 

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Updata regional results in Conclusion; explain periods used in Introduction

@@
 I, therefore, examine how birth intervals have changed across four broad regions.
-[TK only some groups]
-
-TK How I am answering them
 
@@
 Abortion has been legal in India since 1971 and still is.
-The first reports of sex determination appeared around 
-1982--83 \citep{Sudha1999,bhat06,Grover2006}.
-The number of clinics quickly increased, and knowledge about sex selection 
-became widespread after a senior government official's wife aborted a 
-fetus that turned out to be male \citep[p.\ 598]{Sudha1999}.
-In 1994, the Central Government passed the Prenatal Diagnostic Techniques 
-(PNDT) Act, making determining and communicating the sex of a fetus illegal.%
+The first reports of sex determination appeared around 1982--83 
+\citep{Sudha1999,bhat06,Grover2006}.
+The number of clinics quickly increased, and knowledge about sex selection became 
+widespread after a senior government official's wife aborted a fetus that turned out to be 
+male \citep[p.\ 598]{Sudha1999}.
+In 1994, the Central Government passed the Prenatal Diagnostic Techniques (PNDT) Act, 
+making determining and communicating the sex of a fetus illegal.%
 \footnote{
@@
 }
-[TK something on split 1995 to 2016 into two groups?]
+
+Based on these development, I split the four decades into four periods.
+The first period cover until prenatal sex determination became widely available, 
+1972--1984.
+The second period saw (mostly) unrestricted access to sex selection, 1985--1994.
+Although, as reviewed above, there is evidence that there has been a substantial 
+increase in the use of sex selection, some researchers argue that we might be close to or 
+have already passed a turning-point in the use of sex selection 
+\citep{Das_Gupta2009,Diamond-Smith2015}.
+I, therefore, split the period from the implementation of the PNDT Act until the last 
+survey into two, 1995--2004, and 2005--2016.
 
@@
 
-Three major, interrelated trends emerge from the data over the four decades.
+Three major, interrelated trends over the the four decades emerge from the data.
 First, fertility has declined for all groups, as shown by the parity progression
@@
 
-TK Regional differences
+With a country as large as India, it is natural to expect variation in both fertility
+behavior, spacing patterns, and the degree of son preference.
+The regional results confirm this, although differences are less apparent than one would
+expect given the prior research on regional differences.
+The ``North'' and the ``West'' regions have relatively similar spacing patterns, likely
+precipitated by rapidly declining fertility and substantial use of sex selection.
+The exception is that the rural areas of the ``North'' still has higher fertility and
+consequently less use of sex selection and have, therefore, not yet experienced the
+same reversal of spacing patterns.
+Even the ``South'', which is otherwise considered the area with the least son preference,
+has has seen a substantial increase in the use of sex selection and the associated changes 
+in the spacing patterns.
+Even though the ``South'' is often mentioned as the low-fertility region of India, 
+fertility has declined fastest in the ``East'' region, although this does not appear to 
+have translated into the use of sex selection.
 

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Rewrite Introduction with four main results

@@
 Second, birth spacing can have a substantial impact on children's outcomes.
-Most of the research finds a negative impact of short spacing on child health, although 
-identifying the causal mechanisms have proven more difficult
-\citep{Conde-Agudelo2006,Conde-Agudelo2012}.
+Most of the research finds a negative impact of short spacing on child health---especially 
+for very short intervals of 18 months or less---although identifying the causal mechanisms 
+have proven more difficult \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
 There are three pathways through which birth intervals can affect health.
@@
 
-% [TK Results - need updating]
-There are three main results.
-First, there has been a general increase in the length of spacing between births
-over the four decades covered by the data.
-Second, the most substantial increase in spacing is for the women who
-are most likely to use sex selection.
-Specifically, among the best-educated women, those with no boys now has 
-significantly longer spacing---and a more male-biased sex ratio---than 
-similar women with boys.
-Third, women with no education still follow the standard pattern of
-short spacing when they have girls and little evidence of the use of sex
-selection.
-In other words, these women adhere to a strategy where they achieve a
-son through higher fertility rather than the use of sex selection.
+There are four main results.
+First, there has been a general increase in the intervals between births for all education 
+groups over the four decades covered by the data.
+These increases are larger the higher the parity and the higher the education level.
+Second, those women who are most likely to use sex selection, well-educated women with no
+sons, have seen the largest increases in birth intervals.
+As a result, we now have a complete reversal of the traditional spacing pattern for
+well-educated women, and instead observe the longest spacing for women with no sons.
+Third, women who are least likely to use sex selection, those with no education in
+rural areas, still follow the standard pattern of short spacing when they have girls and 
+little evidence of the use of sex selection.
+In other words, these women adhere to a strategy where they achieve a son through higher 
+fertility rather than the use of sex selection.
+Fourth, the traditional pattern of longer average spacing when women have one or more sons
+appear to arise from more very long intervals, rather than from fewer very short birth 
+intervals; across education groups there appear to be little difference in the likelihood
+of having a very short birth interval across sex compositions, especially for lower
+parities.
 

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
No need to discuss ban's effect

@@
 ratio, these changes are likely due to increased use of sex selection rather than sudden
-reversal in son preference.%
-\footnote{
-Banning prenatal sex determination has not been able to reverse the use, although it is 
-possible that it has slowed the rate of increase.
-}
+reversal in son preference.
 Only the second spell has not seen a reversal despite a substantial increased use of

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Update Abstract

@@
 
-[TK rewrite with region results]
-
-Strong son preference is typically associated with shorter birth spacing
-in the absence of sons, but access to sex selection has the potential to
-reverse this pattern because each abortion extends spacing by six to
-twelve months. 
-I introduce a statistical method that simultaneously accounts for how sex selection 
-increases both the spacing between births and the likelihood of a son. 
-Using the four rounds of India's National Family and Health Surveys, I show that
-the spacing between births increased substantially over the last four
-decades, with the most substantial increases among women most 
-likely to use sex selection.
-Specifically, well-educated women with no boys now
-exhibit significantly longer spacing and more male-biased sex ratios
-than similar women with boys. 
-Women with no education still follow the standard
-pattern of short spacing when they have girls and little evidence of sex
-selection, with medium-educated women showing mixed results.
+Strong son preference is typically associated with shorter birth spacing in the absence of 
+sons, but access to sex selection has the potential to reverse this pattern because each 
+abortion extends spacing by six to twelve months. 
+I introduce an empirical method that simultaneously accounts for how sex selection 
+increases both birth spacing and the likelihood of a son. 
+Using the four rounds of India's National Family and Health Surveys, I show that birth 
+intervals increased substantially over the last four decades, most substantially among 
+women most likely to use sex selection.
+Specifically, well-educated women with no boys now exhibit significantly longer spacing, 
+and more male-biased sex ratios, than similar women with boys. 
+Women with no education still follow the standard pattern of short average spacing when 
+they have girls and little evidence of sex selection, with medium-educated women showing 
+mixed results.
+Furthermore, the traditional pattern of longer average spacing with sons appears to arise 
+not from fewer very short birth intervals, but rather from the upper end of the distribution.
+Finally, northern and western India are responsible for most of the spacing pattern 
+reversal, although even the south experienced substantial increased intervals from
+sex selection.
 
 \noindent JEL: J1, O12, I1
-\noindent Keywords: India, prenatal sex determination, censoring, competing risk
+\noindent Keywords: India, prenatal sex determination, censoring, competing risk, non-proportional hazard
 \end{abstract}

### 2019-03-22 response/response-demography-1.tex
Minor edit
General edits

@@
 
-I have completely rewritten the introduction to better situate the paper in the literature
+I have completely rewritten the Introduction to better situate the paper in the literature
 and to highlight the contributions of the paper.
@@
 sex selection is important, and, in addition, highlight the three main questions I address 
-in the paper: the effect of sex selection on birth intervals, the effect of sex selection
-on the distribution of births within spells, and, finally, how the effects have varied
-with geographical region.
+in the paper: the effect of sex selection on birth intervals, the distribution of births 
+within spells, and, finally, differences across geographical regions.
 
@@
 
-[See response to Editor]
+Please see my response to the Editor's first comment above.
 
@@
 
-[I should have those somewhere already. I think they were in the original version.]
-
-[Make the paper about spacing; need to emphasize why spacing is interesting]
+As mentioned above, I have refocused the paper to examine how birth spacing has changed
+over time in India, and, especially, how the spread of prenatal sex determination can
+lead to longer spacing.
+As part of this rewrite, I have incorporated the suggested references and other works into 
+the Introduction as part of the motivation for why examining the changes in birth 
+intervals that arise from the use of sex selection is important.
 
@@
 There are three important differences between my approach and what is standard
-in the literature, and I believe further shortening would negatively impact readers'
+in the literature, and I believe further shortening would negatively impact readers's
 ability to understand the results.
@@
 Third, the sex ratio calculations is a new way to use competing risk estimates and is 
-required to understand the use of sex selection.
+required to understand how the use of sex selection impact birth intervals.
 
@@
 and 0.95 percent with a negative duration.
-Other people seem to have caught by the same problem, such as \citet{Padmadas2004}.
+Other people seem to have been caught by the same problem, such as \citet{Padmadas2004}.
 
@@
 respondent did not provide complete information.
-One approach to understanding the impact on spacing to first birth is to split spacing 
-from marriage to first birth by completeness of date of marriage.
+One approach to understanding the impact of imputation on spacing to first birth is to 
+split spacing from marriage to first birth by completeness of date of marriage.
 In NFHS-3, 2.55 percent of the 39,213 women with complete information on date of 
@@
 
-[TK still needs to be removed from the paper]
-
 \item 7. It is not clear why exactly 22, 23, 25 years are used a cut-off
@@
 [Response:]
+
 I have added a detailed discussion of recall error in the Appendices intended for online 
@@
 to simplify.
-Even with the stricter cut-off there are still some evidence of recall error,
-especially in region TK, where the sex ratio was substantially biased against females 
-before sex selection became available.
+Even with the stricter cut-off there are, however, still some evidence of recall error 
+where the sex ratio was substantially biased against females  before sex selection became 
+available.
 
@@
 [Response:]
+
 I agree completely that the regional differences in fertility, son preference, and use 
@@
 small sample sizes for the estimations to converge.
-The lack of convergence is especially an issue for the middle-education group at the
-higher spells.
+The lack of convergence is especially an issue for the lower and middle-education groups.
 I, therefore, first present the all-India results and then focus on regional differences
 for only the most educated women, who are the main users of sex selection.
-
-[Part of the reason is the very low fertility in the southern areas. See Guilmoto
-and Rajan 2001 and IIPS 2006 and check latest NFHS report on, for example, Tamil Nadu.
-TFR of less than 2 is likely.]
-
-It is also worthwhile to note that even some of the southern states appear to have
-seen an increase in son preference over time, or, rather, daughter aversion
-\citep{DiamondSmith2008}.
 
@@
 
-As detailed above, I have refocused the Results section to focus mainly on birth spacing
-and how that is affected by the increased use of sex selection over time.
+As detailed above, I have refocused the Results section to focus on birth spacing and how 
+that is affected by the increased use of sex selection over time.
 I now instead refer to the previous literature on sex ratios and use that as a guide for
@@
 [Response:]
-Compression in the original manuscript was only for first birth, and I no longer cover 
-those because of the data issues discussed above.
+
+Compression in the original manuscript was only for first birth interval, and I no longer 
+cover that because of the data issues discussed above.
 I do, however, agree that this is an important question, even if I cannot directly
 address it here.
-I, therefore, have added this to the conclusion when I discuss areas of future research.
+I, therefore, have added this, together with the reference, to the conclusion when I 
+discuss areas of future research.
 
@@
 
-[Add discussion when other parts are done]
+With the refocus on birth intervals there should be more coherence in the results.
+I have, however, highlighted what I consider the main results in the Conclusion.
 
@@
 
+As part of the rewrite of the paper, I have redone the abstract and removed the
+reference to spells.
+
 \newpage

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Minor edits of Abstract

@@
 women most likely to use sex selection.
-Specifically, well-educated women with no boys now exhibit significantly longer spacing, 
-and more male-biased sex ratios, than similar women with boys. 
+Specifically, well-educated women with no boys now have significantly longer birth
+intervals, and more male-biased sex ratios, than similar women with boys. 
 Women with no education still follow the standard pattern of short average spacing when 
@@
 Finally, northern and western India are responsible for most of the spacing pattern 
-reversal, although even the south experienced substantial increased intervals from
+reversal, although even the south experienced substantially increased intervals from
 sex selection.

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Grammar edits of Introduction

@@
 However, the introduction of prenatal sex determination has the potential to
-fundamentally change the relationship between son preference and birth spacing.
+change the relationship between son preference and birth spacing.
 The stronger the son preference, the more likely couples are to resort to sex-selective 
@@
 }
-In both Bangladesh and Vietnam the more boys a family has the longer the expected duration 
-to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
+In both Bangladesh and Vietnam the more boys a family has the longer is the expected 
+duration to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
 Outside Asia, the evidence is more mixed.
@@
 % [Hypotheses / questions]
-Despite the increasing use of sex selection, the important impacts of spacing on outcomes 
+Despite the increasing use of sex selection, the critical impacts of spacing on outcomes 
 for both mother and children, and the extensive use of spacing to measure son 
@@
 Based on the prior literature on sex selection, I focus on how birth intervals have
-changed for different education levels, whether urban or rural, and the sex composition of 
+changed for different education levels, urban or rural, and the sex composition of 
 prior children.
@@
 Second, have the shapes of the survival curves changed?
-Very short birth intervals are associated with worse health outcomes and increasing 
+Very short birth intervals are associated with worse health outcomes and increased 
 mortality risk \citep{Conde-Agudelo2012}.
@@
 concern for child health or from a strong son preference leading to continued pregnancies
-until a son is conceive.
+until they conceive a son.
 
@@
 
-Direct information on the use of sex selection is not available, but it is possible
-to compare different periods as a proxy since there has been substantial changes in access 
+Direct information on the use of sex selection is not available, but it is possible to 
+compare different periods as a proxy since there have been substantial changes in access 
 and legality of prenatal sex determination in India.
@@
 It took until January 2008 for the first state, Haryana, to reach five convictions.
-Hence, private clinics apparently operate with little risk of legal action 
-\citep{Sudha1999}.
+Hence, private clinics operate with little risk of legal action \citep{Sudha1999}.
 Furthermore, there is little evidence that bans like this significantly
@@
 
-Based on these development, I split the four decades into four periods.
-The first period cover until prenatal sex determination became widely available, 
+Based on these developments, I split the four decades into four periods.
+The first period covers until prenatal sex determination became widely available, 
 1972--1984.
@@
 groups over the four decades covered by the data.
-These increases are larger the higher the parity and the higher the education level.
+These increases are larger the higher the parity and the higher the education 
+level.
 Second, those women who are most likely to use sex selection, well-educated women with no
@@
 As a result, we now have a complete reversal of the traditional spacing pattern for
-well-educated women, and instead observe the longest spacing for women with no sons.
+well-educated women, and instead, observe the longest birth intervals for women with no 
+sons.
 Third, women who are least likely to use sex selection, those with no education in

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Grammar edits of Estimation Strategy

@@
 $J_i$ is a random variable indicating which event took place.
-The discrete time hazard rate $h_{ijt}$ is specified as
+The discrete time hazard rate $h_{ijt}$ is 
 \begin{equation}
@@
 but to further minimize any potential bias from assuming proportionality, estimations 
-are done separately for different levels of mothers' education and for different 
-time periods.%
+are done separately for different levels of mothers' education and different 
+periods.%
 \footnote{
-The choice of which variables to use for non-proportionality is discussed in more detail
+I discuss the choice of which variables to use for non-proportionality in more detail
 in the ``Explanatory Variables'' section.

### 2019-03-22 paper/sex_selection_spacing-ver2.tex
Edit Data section for grammar

@@
 Three factors contribute to the problem here.
-First, girls have significantly higher mortality risk than boys.
+First, girls have a significantly higher mortality risk than boys.
 Second, son preference may increase the probability that parents recall boys 
@@
 
-I focus here on the second through fourth spells, that is, from the second birth until
-at most the fourth birth.
-The first spell from marriage to the first spell is excluded because of data issues.
-In NFHS-1 and NFHS-2 the only information on marriage timing is age at marriage and all
-spell durations are therefore imputed.
+I focus here on the second through fourth spells, that is, on the intervals from the first 
+birth until at most the fourth birth.%
+\footnote{
+I exclude the first spell from marriage to the first spell because of data issues.
+In NFHS-1 and NFHS-2 the only information on marriage timing is the age at marriage, and 
+all spell durations are therefore imputed.
 In NFHS-3 about a third of respondent did not provide complete information on the
@@
 the age at marriage.
-The result of the imputation is that very large numbers of women end up with very short,
-i.e. less than 9 months, or negative spells and that comparing spell duration over time
-for the first spell is subject to an excessive amount of noise.
-
-The second and subsequent spells begin nine months after the previous birth 
-because that is the earliest we should expect to observe a new birth.
-All spells continue until either a child is born or censoring occurs.
+The result of the imputation is that large numbers of women end up with very short,
+i.e., less than nine months, or negative spells and that comparison of spell duration over 
+time is subject to an excessive amount of noise.
+}
+The spells all begin nine months after the previous birth 
+because that is the earliest we should expect to observe a new birth, which also means 
+that they capture the interpregnancy interval for pregnancies carried to term.
+A spell continues until either a child is born or censoring occurs.
 Censoring can happen for three reasons:
@@
 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The periods follow the main changes in availability and legality of 
+The periods follow the main changes in the availability and legality of 
 prenatal sex determination discussed in the Introduction.
@@
 status, especially education, and the use of sex selection is unlikely to be the
-same throughout a spell, which means that education cannot enter in a proportional
-fashion. \citep{retherford03b,jha06,Portner2015b}.
+same throughout a spell, which means that education cannot enter proportionally 
+\citep{retherford03b,jha06,Portner2015b}.
 One potential reason for the correlation between education and sex selection is that
@@
 In principle, it is possible that part of the higher likelihood is driven by a stronger
-preference for son, independently of desired fertility.
+son preference, independently of desired fertility.
 There is, however, evidence that higher education women have shown a decline in
-son preference \citep{bhat03,pande07}
-}
-Another reasons is that having more education is closely associated with higher income and 
+son preference \citep{bhat03,pande07}.
+}
+Another reason is that having more education is closely associated with higher income and 
 wealth, which makes it easier to access illegal services such as prenatal sex 

### 2019-03-23 paper/sex_selection_spacing-ver2.tex
Edit first part of Results section for grammar

@@
 a birth by decade, spell, and sex composition for the three education levels separated 
-by area of residence.
+by the area of residence.
 For each subsample, I first estimate the model described in Section 
@@
 
-The expected average duration is calculated as follows.
+I calculate the expected average duration as follows.
 For each woman in a sample, I calculate her probability of giving birth for each period
@@
 Each woman's predicted sex ratio is the weighted average of the predicted
-percentage boys over each period in the spell calculated using equation 
+percentage of boys over each period in the spell calculated using equation 
 (\ref{eq:probability_son}) and the probability of giving birth in each period 
@@
 \footnote{
-Imagine a spell has two periods and that the estimated percentage boys for a
+Imagine a spell has two periods and that the estimated percentages of boys for a
 woman are 54\% and 66\% and that the likelihood of having a birth is 20\% and 40\%.
 The likelihood of having a birth is the change in the survival curve; 
-in other words, there is 40\% chance that she will not have given birth by the end of 
+in other words, there is a 40\% chance that she will not have given birth by the end of 
 this spell.
-This woman's percentage boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
+This woman's percentage of boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
 }
@@
 
-For legibility none of the graphs show standard errors.
+For legibility, none of the graphs show standard errors.
 Instead, the standard errors, together with the graphed values, are shown in Appendix 
-Tables TK, TK, and TK.
+Tables 
+\ref{tab:bootstrap_duration_avg_sex_ratio_low_all}, 
+\ref{tab:bootstrap_duration_avg_sex_ratio_med_all}, and 
+\ref{tab:bootstrap_duration_avg_sex_ratio_high_all}.
 The standard errors are based on bootstrapping for all three measures,
@@
 
-Each predicted percent boys is tested against the natural percentage 
+Each predicted percent of boys is tested against the natural percentage of
 boys using the bootstrapped standard errors.
@@
 preference with higher fertility and shorter birth intervals the fewer sons they have.
-This pattern is supported by Figure \ref{fig:bootstrap_low}, but with important
+This pattern is supported by Figure \ref{fig:bootstrap_low}, but with significant
 differences across spells.
-Most of the women without education live in rural areas, and I therefore focus on rural 
+Most of the women without education live in rural areas, and I, therefore, focus on rural 
 women.%
@@
 with at least one son, and more so the more sons they had.
-Hence, fertility have begun to fall even among women with no education, as long as they 
+Hence, fertility has begun to fall even among women with no education, as long as they 
 have at least one son.
 Two additional fertility trends stand out.
-First, essentially all women still have a second birth, whether the first child was
+First, virtually all women still have a second birth, whether the first child was
 a boy or a girl.
-Second, for women with only girls there is almost no reduction in the probability of 
-having a birth across time and across spells.
+Second, for women with only girls, there is almost no reduction in the probability of 
+having a birth across time and spells.
 
@@
 and two months.
-Interestingly, son preference appear to have little effect on spacing for the second
+Interestingly, son preference appears to have little effect on spacing for the second
 spell, with very small, albeit statistically significant, differences in birth intervals 
@@
 Despite the increase in spacing even for those with three girls, the increases in 
-spacing have been substantially larger for families with at least one son.
-As for fertility, the differences are larger the more sons a family has.
-
-Despite the general finding that use of sex selection is confined to higher education
-women, the predicted sex ratios for those with only girls is statistically significantly
-higher than the natural ratio for the third and fourth spell.
+spacing have been substantially stronger for families with at least one son.
+As for fertility, the more sons a family has, the more significant are the differences.
+
+Despite the prior literature finding that women with higher education are the primary user 
+of sex selection, the predicted sex ratios for those with only girls are statistically 
+significantly higher than the natural ratio for the third and fourth spell.
 Hence, it is possible that at least part of the increased  birth intervals for those
-with only girls comes from the use of sex selection and that the differences in
-birth spacing across sex compositions would be even larger in the absense of sex selection.
+with only girls comes from the use of sex selection and that the differences in birth 
+spacing across sex compositions would be even more substantial in the absence of sex 
+selection.
 
@@
 follow a fertility pattern broadly similar to those with no education.
-As expected, fertility is lower than for women with no education, but still show
-substantial son preference in the parity progression behavior.
-Except for the second spell, the likelihood of having a birth by the end of spell is
+As expected, fertility is lower than for women with no education, but still a
+strong son preference in the parity progression behavior.
+Except for the second spell, the likelihood of having a birth by the end of the spell is
 substantially lower if there has been at least one male birth than if there are only girls.
@@
 in birth intervals lengths across sex compositions for the third and fourth spells.
-On the contrary, for the third spell the largest increases in birth intervals are for women with
-two daughters and no sons, with an increase of about seven months across the four decades.
-The results is that for urban women the standard spacing pattern reversed, so the longest 
+On the contrary, for the third spell, the most substantial increases in birth intervals are for 
+women with two daughters and no sons, with an increase of about seven months across the 
+four decades.
+The result is that for urban women the standard spacing pattern reversed, so the longest 
 predicted spacing is now for those with only girls, while for rural women the predicted 
@@
 \footnote{
-Because of low number of observations the pattern for the fourth spell is more noisy for 
-urban women.
+Because of the low number of observations, the pattern for the fourth spell is noisier 
+for urban women.
 }
@@
 percent boys.
-The elevated sex ratios strongly suggests that sex selection is driving the increases in
-birth intervals for women with only girls, and that without sex selection we would 
+The elevated sex ratios strongly suggest that sex selection is driving the increases in
+birth intervals for women with only girls and that without sex selection we would 
 instead have observed a diverging pattern in birth intervals across sex composition as
@@
 fertility and the highest use of sex selection based on the prior literature.
-Figure \ref{fig:bootstrap_high} shows that not only do this group, indeed, have lower 
-fertility than the two prior groups, it is also falling rapidly over time.
+Figure \ref{fig:bootstrap_high} shows that this group not only have lower fertility than 
+the two previous groups; fertility is also falling rapidly over time.
 Of women with one birth, the probability of having a second birth when the first-born
 is a son is only around 70 percent for urban women and around 80 percent for rural women,
-and for those with a first-born daughter it is around 80 percent for urban women and 90 
+and for those with a first-born daughter, it is around 80 percent for urban women and 90 
 percent for rural women.
@@
 slower for both urban and rural women without a son than for those with at least one son.
-The falling fertility means that relatively few women makes it to the fourth spell,
+The falling fertility means that relatively few women make it to the fourth spell,
 which, therefore, has more noise than the other spells.
@@
 Average birth spacing for the second spell is almost identically across sex compositions 
-for both urban and rural women, and increased by around five months for rural women and
+for both urban and rural women and increased by around five months for rural women and
 by almost ten months for urban women over the four decades.
-These similarities hides, however, what would have been a standard son preference spacing 
+These similarities hide, however, what would have been a standard son preference spacing 
 pattern with significantly shorter spacing after a first-born girl than after a first-born 
 boy if there had not been a substantial amount of sex selection.
-For both of the last two periods the predicted sex ratio for women with a daughter as 
+For both of the last two periods, the predicted sex ratio for women with a daughter as 
 their first-born child is above 55 percent for both urban and rural areas.
@@
 particularly vividly by the changes over time for the third spell.
-In the 1972-1984 period the predicted average birth intervals for the three possible sex 
+In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
 compositions were less than two months apart.
@@
 statistically significant.
-In urban areas the predicted average birth interval for a woman with only daughters 
+In urban areas, the predicted average birth interval for a woman with only daughters 
 increased by almost a full year from 26.8 to 38.3 months.
@@
 despite sex selection not being widely available until around 1985.
-If this early elevated sex ratio is because of recall error it means that the actual birth 
+If this early, elevated sex ratio is because of recall error, it means that the actual birth 
 intervals would have been substantially shorter than the ones predicted here and the
@@
 An important caveat is that because of the falling fertility relatively few women make
-it to the fourth spell, and even if they do we do not observe a birth by the time of the
+it to the fourth spell, and even if they do, we do not observe a birth by the time of the
 survey.
@@
 2005-2016 period more than 70 percent did not have a birth at the time of the survey.
-Even though the censoring is less prevalent for the earlier periods this is countered by
+Even though the censoring is less prevalent for the earlier periods, this is countered by
 those samples being substantially smaller.
@@
 patterns is not the result of a declining son preference but instead corresponds to a 
-substantially more male-biased sex ratio as use of sex selection spread.
+substantially more male-biased sex ratio as the use of sex selection spread.
 For urban women, the predicted sex ratio with only girls is consistently above 60\% boys 

### 2019-03-23 paper/sex_selection_spacing-ver2.tex
Edit distributional results section for grammar

@@
 since the literature on birth spacing and child health suggests that an interpregnancy 
-interval of less than 18 months is associated with a higher risk of adverse health 
+interval of fewer than 18 months is associated with a higher risk of adverse health 
 outcomes and mortality \citep{Conde-Agudelo2012}.
@@
 \footnote{
-It is unclear what the optimal response in timing of pregnancies to the availability of 
-sex selection should be.
+It is unclear what the optimal response in the timing of pregnancies to the availability 
+of sex selection should be.
 The expected birth intervals become longer with the use of sex selection, which may be 
@@
 Conversely, if parents know that short birth intervals are detrimental to the next child's
-health, and with sex selection the next child is likely be a boy, it might make sense to 
+health, and with sex selection, the next child is likely a boy, it might make sense to 
 wait longer before conceiving.
@@
 percentiles durations with bootstrapped standard errors based on averages across all women 
-in the each subsample as for the results above.
+in each subsample as for the results above.
 
@@
 the second, third, and fourth spells for the first period, 1972--1984, and the last 
-period, 2005--2016, for rural women with no education and for urban women with eight or 
+period, 2005--2016, for rural women with no education and urban women with eight or 
 more years of education.
@@
 
-For the third spell the son preference driven short spacing is evident throughout the
+For the third spell, the son preference driven short spacing is evident throughout the
 distribution and becomes more pronounced over the four decades.
@@
 than a general reduction in the likelihood of very short birth intervals.
-It also means, that previous girls can expect a longer period without a younger sibling,
+It also means, that previous girls can expect more time without a younger sibling,
 which may reduce the sibling competition for resources.
@@
 and only boys.
-Both of the spells therefore show changes in the distribution of births that is in line
+Both of the spells, therefore, show changes in the distribution of births that is in line
 with extensive use of sex selection among families with no or one son.

### 2019-03-23 paper/sex_selection_spacing-ver2.tex
Edit regional results for grammar

@@
 To understand how regional differences in son preference, fertility, and use of sex 
-selection affect birth spacing, I divide India into four broad regions based on degree of 
-son preference and initial fertility levels.
-Focus is on the most educated women since they are the main users of sex selection.
+selection affect birth spacing, I divide India into four broad regions based on the degree 
+of son preference and initial fertility levels.
+The focus is on the most educated women since they are the primary users of sex selection.
 The four regions are based on \citet{retherford03b}, although expanded to include all 
@@
 \footnote{
-The geographical names do not perfectly reflect the geography of India, and mainly
+The geographical names do not entirely reflect the geography of India, and mainly
 serves as mnemonic short-hands.
 }
-The state names are based on the states in existence when NFHS-1 was collected.
-States that are formed later are allocated as closely as possible to the original state.
+The state names are those in existence at the time of the NFHS-1 data collection.
+States formed later are allocated as close as possible to the original state.
 The ``West'' contains states with a high degree of son preference and use of sex selection.
@@
 ratios, and likelihoods of having a child by the end of the spell over time for the three 
-spells.
+spells in the ``West.''
 What most stands out is how close to the national estimates the ``West'' estimates are.
@@
 For the second spell, the predicted sex ratios are around 60 percent for both urban and
-rural women, and for the third spell it it around 70 percent for urban women and 
+rural women, and for the third spell it is around 70 percent for urban women and 
 consistently above 60 percent for rural women.
@@
 Figure \ref{fig:bootstrap_high_r2} shows the same outcomes for the ``North'' region. 
-Despite the idea that the ``North'' is characterized by high fertility and lower 
+Despite the idea that the ``North'' has high fertility and lower 
 likelihood of sex selection the differences to the ``West'' region is surprisingly small,
@@
 Fertility is, indeed, higher than in the ``West'' region, but the declines in the 
-probability of parity progression has been relatively rapid and mirrors the national one.
-The use of sex selection is also close to the ``West'', and there is the same reversal of
+probability of parity progression have been relatively rapid and mirror the national one.
+The use of sex selection is also close to the ``West,'' and there is the same reversal of
 spacing pattern as there.
@@
 Fertility is substantially higher, and the use of sex selection much lower than in the
-rural areas of the ``West''. 
+rural areas of the ``West.'' 
 That said, there still is clear evidence that the sex ratio is substantially above normal
@@
 The results for the ``East'' region of India are shown in Figure 
-\ref{fig:bootstrap_high_r3}, although the fourth spell results are not included because 
+\ref{fig:bootstrap_high_r3}, although it does not include the fourth spell results because 
 the sample size is smaller for this region and the fourth spell results very noisy.
 Despite the ``South'' region generally considered to be the low fertility region, the
-reduction in fertility has been even faster in the ``East''.
-For the last decade only half of urban women with a first-born son are predicted to have
-a second child by the end of the spell period covered, which means almost nine years after
-the first birth.
+reduction in fertility has been even faster in the ``East.''
+For the last decade, only half of the urban women with a first-born son are predicted to 
+have a second child by the end of the spell, which means almost nine years after the first 
+birth.
 The probability is only slightly higher for those in urban areas with a first-born 
@@
 child are low, even in the absence of sons.
-In urban areas a woman with two girls have only around a 40 percent likelihood of 
+In urban areas, a woman with two girls has only around a 40 percent likelihood of 
 having a third child.
 
-What really stands out, however, is the rapid increase in the lengths of birth intervals,
+What stands out, however, is the rapid increase in the lengths of birth intervals,
 especially for the second spell.
 In both urban and rural areas, the predicted average birth intervals have gone up by
-more than a year across the four decade, and that is independent of whether the first-born
+more than a year across the four decades, and that is independent of whether the first-born
 was a boy or a girl.
-The increases in birth intervals are slightly smaller for third spell, but still 
+The increases in birth intervals are slightly smaller for the third spell but still 
 substantial.
-Although spacing pattern is consistently with some son preference with the average
+Although the spacing pattern is consistent with some son preference, with the average
 spacing slightly shorter in the absence of boys than when at least one boy is present,
 there is little evidence of sex-selective abortions.
-The sex ratios after a first-born daughter is slightly elevated, but much lower than 
+The sex ratios after a first-born daughter are slightly elevated but much lower than 
 the prior two regions.
@@
 
-The final region is the ``South'', shown in Figure \ref{fig:bootstrap_high_r4}.
+The final region is the ``South,'' shown in Figure \ref{fig:bootstrap_high_r4}.
 This region is historically thought to have the lowest degree of son preference of the
 regions of India.
-As for the ``East'', I do not show the fourth spell results because of the small sample 
+As for the ``East,'' I do not show the fourth spell results because of the small sample 
 size and the associated noisy estimates.
@@
 does, indeed, appear that there is little son preference in this region.
-The likelihood of having a second birth is relatively high at around 80 to 90 percent,
+The likelihood of having a second birth is relatively high at around 80 to 90 percent
 and is close to independent of the sex of the first birth in both urban and rural areas.
@@
 sex ratios are close to the natural rate.
-The average birth spacing started high relatively to the other regions, and with little 
+The average birth spacing started high relative to the other regions, and with little 
 change in fertility and no significant use of sex selection, it has increased only 
@@
 With the high likelihood of a second birth and lower decline in the likelihood of a third
-birth, the ``South'' has a higher predicted fertility than the ``East''.
-What is more, for urban areas the average birth interval have increased substantially
+birth, the ``South'' has higher predicted fertility than the ``East.''
+What is more, for urban areas the average birth interval has increased substantially
 for those with only girls relative to those with a boy and a girl, corresponding to
@@
 The signs of the use of sex selection also show up for rural women with no sons.
-Furthermore, over the four decades the likelihood of having a third birth has decreased
+Furthermore, over the four decades, the likelihood of having a third birth has decreased
 much less than for either a boy and a girl or two boys.%
 \footnote{
-The relatively high parity progression for women without son does raise the question
+The relatively high parity progression for women without son does raise the question of
 whether ``daughter avoidance'' is behind the fertility behavior in this region as
@@
 }
-The differences in parity progression and the sex ratios suggests that despite originally
-having less son preference, the ``South'' now appears to have the longer average spacing 
-in absence of son and the higher sex ratio associated with the use of sex selection.
+The differences in parity progression and the sex ratios suggest that despite originally
+having less son preference, the ``South'' now appears to have longer average spacing 
+in the absence of sons and the higher sex ratio associated with the use of sex selection.
 

### 2019-03-23 paper/sex_selection_spacing-ver2.tex
Edit Conclusion for grammar

@@
 
-Three major, interrelated trends over the the four decades emerge from the data.
+Three major, interrelated trends over the four decades emerge from the data.
 First, fertility has declined for all groups, as shown by the parity progression
@@
 Across all groups, the likelihood of having an additional child in each spell depends 
-strongly on how many sons you already have, with women with none or only one son having
+strongly on the number of sons, with women with none or only one son having
 the highest probability of a birth.
@@
 intervals for all education groups.
-The increase in average birth interval is larger the higher the spell and the higher the 
+The increase in the average birth interval is larger the higher the spell and the higher the 
 education group.
@@
 
-The results show two very different approaches to son preference with important
+The results show two very different approaches to son preference with significant
 impacts on spacing patterns.
@@
 than the average interval after a first-born boy, the difference is small.
-The differences in spacing is larger for the third spell and largest for the fourth.
-For the the fourth spell, the divergence in intervals across sex compositions have 
+The differences in spacing are larger for the third spell and largest for the fourth.
+For the fourth spell, the divergence in intervals across sex compositions has 
 increased over time, with the largest increases in average intervals for women with 
@@
 As shown by the increasingly significant deviations in the sex ratio from the natural sex 
-ratio, these changes are likely due to increased use of sex selection rather than sudden
+ratio, these changes are likely due to increased use of sex selection rather than a sudden
 reversal in son preference.
-Only the second spell has not seen a reversal despite a substantial increased use of
+Only the second spell has not seen a reversal despite a substantially increased use of
 sex selection, mainly because the average spacing with a first-born boy has increased 
@@
 the picture of how son preference affects spacing is more complicated than excepted.
-First, for the second spell the differences in birth intervals for the first 25 percent of 
+First, for the second spell, the differences in birth intervals for the first 25 percent of 
 births are negligible across sex compositions, despite that these birth intervals are
@@
 longer spells, which are likely to have less negative impacts on children and the mother.
-Second, one of the side-effects of the extensive use of sex selection for women with eight
-or more years of education for the third and fourth spell is that only-girls families
-not only end up with longer average intervals to the birth of the next, they also are now
-much less likely to have a short, i.e. less than 18 months, interpregnancy interval,
-which may reduce the sibling competition for resources.
+Second, one of the side-effects of the extensive use of sex selection for third and fourth 
+spells is that only-girls families are much less likely to have a short, i.e., less than 
+18 months, interpregnancy interval, which may reduce the sibling competition for resources.
 
@@
 precipitated by rapidly declining fertility and substantial use of sex selection.
-The exception is that the rural areas of the ``North'' still has higher fertility and
+The exception is that the rural areas of the ``North'' still have higher fertility and
 consequently less use of sex selection and have, therefore, not yet experienced the
 same reversal of spacing patterns.
-Even the ``South'', which is otherwise considered the area with the least son preference,
-has has seen a substantial increase in the use of sex selection and the associated changes 
+Even the ``South,'' which is otherwise considered the area with the least son preference,
+has seen a substantial increase in the use of sex selection and the associated changes 
 in the spacing patterns.
@@
 The distributional results provide an initial indication that most of the increases in 
-average birth intervals come from the upper end of the birth intervals rather an generic
+average birth intervals come from the upper end of the birth intervals rather a general
 increase across the distribution.
 It is, however, unclear why we are seeing relatively more very long birth intervals over
-time, and the longer average spacing seem to run counter to a general reduction in the 
+time, and the longer average spacing seems to run counter to a general reduction in the 
 length of women's reproductive spans found in earlier research \citep{Padmadas2004}.
@@
 the use of sex selection \citep{Das-Gupta2016}.
-This may, however, be a double-edged sword.
+This approach may, however, be a double-edged sword.
 On the one hand, it is a clear benefit to the women who gain bargaining power, and it 

### 2019-03-24 paper/sex_selection_spacing-ver2.tex
Minor edits after final read-through

@@
 preference.
-In India, the sex of the last-born child significantly impacts the duration to next birth,
-with the expected birth interval about three percent longer if the last-born was a son than
-if it was a daughter \citep{Bhalotra2008,Kumar2016}.
-Similarly, ethnic Indians in South Africa also show a longer duration after the birth of a 
+In India, the sex of the last-born child has in the past significantly affected the 
+duration to next birth, with the expected birth interval about three percent longer if the 
+last-born was a son than if it was a daughter \citep{Bhalotra2008,Kumar2016}.
+Ethnic Indians in South Africa also show a longer duration after the birth of a 
 son than after a daughter \citep{Gangadharan2003}.%
@@
 }
-In both Bangladesh and Vietnam the more boys a family has the longer is the expected 
+In both Bangladesh and Vietnam, the more boys a family has the longer is the expected 
 duration to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
@@
 \footnote{
-This depletion can take the form of nutrition, folate, or cervical insufficiency.
+This depletion can take the form of nutrition, folate, or cervical insufficiencies.
 }
@@
 outcomes and a higher likelihood of dying the shorter the interval between them, although 
-the effect is not symmetrical
+the effects are not symmetrical
 \citep{Whitworth2002,Bhargava2003,Rutstein2005,Maitra2008,Makepeace2008,Ghosh2018}.%
@@
 Second, have the shapes of the survival curves changed?
-Very short birth intervals are associated with worse health outcomes and increased 
-mortality risk \citep{Conde-Agudelo2012}.
-Hence, understanding how the distribution of birth intervals changes help us understand to 
+Very short birth intervals are, as mentioned, associated with worse health outcomes and 
+increased mortality risk \citep{Conde-Agudelo2012}.
+Hence, understanding how the distribution of birth intervals changes can help us understand to 
 what extent we can expect improvements in health outcomes.
@@
 distributed geographically?
-Given the size and cultural differences within India, it is unlikely that the effect of
-increasing access to sex selection will have had the same effect throughout 
-\citep{retherford03b}.
-I, therefore, examine how birth intervals have changed across four broad regions.
+Given the size and cultural differences within India, it is unlikely that the increasing 
+access to sex selection will have had the same effects throughout \citep{retherford03b}.
+I, therefore, examine how birth intervals have changed across four regions.
 
@@
 next child is no longer necessarily random and that parents' choices will impact the 
-spacing to the birth of a girl or a boy differentially.
+spacing to the birth of a girl or a boy differently.
 I, therefore, use a competing risk set-up, which can capture both the non-randomness of
@@
 
-Second, it is unlikely---even in the absence of prenatal sex determination---that the 
-effect of household characteristics such as the sex composition of previous births have 
-the same effect throughout the entire spell as is assumed by the proportional hazard
-model.
+Second, it is unlikely---even in the absence of prenatal sex determination---that 
+characteristics, such as the sex composition of previous births, have the same effects 
+throughout the entire spell as is assumed by the proportional hazard model.
 Assuming that the effect of sex composition is the same throughout a spell is especially 
@@
 states: either a boy or a girl is born.
-The unit of analysis is a spell, the period from one birth to the next.
+The unit of analysis is a spell, the period from nine months after one birth to the next.
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
@@
 
-The explanatory variables in $\mathbf{Z}$ and the interactions between them 
-are the non-proportional part of the model, which means that they are
+The explanatory variables in $\mathbf{Z}$, and the interactions between them, 
+constitute the non-proportional part of the model, which means that they are
 interacted with the baseline hazard:
@@
 \end{equation}
-where $D_j(t)$ is the piece-wise linear baseline hazard and $\mathbf{Z}_1$ captures sex 
+where $D_j(t)$ is the piece-wise linear baseline hazard, $\mathbf{Z}_1$ captures sex 
 composition of previous children, if any, and $Z_2$ captures area of residence.
@@
 The same goes for women who had at least one multiple births,
-reported having a birth before age 12, had a birth before marriage, or
-duration between births of less than nine months.
+reported having a birth before age 12, had a birth before marriage, or an interval between 
+births of less than nine months.
 
@@
 a birth by decade, spell, and sex composition for the three education levels separated 
-by the area of residence.
+by the area of residence.%
+\footnote{
+For legibility, none of the graphs show standard errors.
+Instead, the standard errors, together with the graphed values, are shown in Appendix 
+Tables 
+\ref{tab:avg_sex_ratio_low}, 
+\ref{tab:avg_sex_ratio_med}, and 
+\ref{tab:avg_sex_ratio_high}.
+The standard errors are based on bootstrapping for all three measures,
+where the model is repeatedly estimated using resampling with replacement.
+}
 For each subsample, I first estimate the model described in Section 
 \ref{sec:strategy} and then use the estimated coefficients to predict 
-average spell length, sex ratio, and the probability of having a birth in that spell.
+average birth spacing, sex ratio, and the probability of having a birth in that spell.
 
@@
 in the sample when childbearing for that spell is over.
-
-For legibility, none of the graphs show standard errors.
-Instead, the standard errors, together with the graphed values, are shown in Appendix 
-Tables 
-\ref{tab:bootstrap_duration_avg_sex_ratio_low_all}, 
-\ref{tab:bootstrap_duration_avg_sex_ratio_med_all}, and 
-\ref{tab:bootstrap_duration_avg_sex_ratio_high_all}.
-The standard errors are based on bootstrapping for all three measures,
-where the model is repeatedly estimated using resampling with replacement.
-
-I also show whether durations for sex composition other than only girls are statistically 
-significantly different from the duration with only girls based on bootstrapped 
-differences. 
-The cleanest test is comparing durations after only boys with durations after
-only girls, but the number of births to women with only sons becomes small 
-in the later periods.
-Hence, it is possible to have substantial differences in spacing that are
-not statistically significant because of low power, especially for the third 
-and fourth spell.
-
-Each predicted percent of boys is tested against the natural percentage of
-boys using the bootstrapped standard errors.
-The natural sex ratio is approximately 105 boys to 100 girls or
-51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
-The predicted percentage boys may differ from the natural rate because of 
-natural variation, any remaining recall error not corrected for, or 
-sex selection.
 
@@
 
-Where son preference in birth intervals shows most clearly is for the fourth spell.
+Son preference in birth intervals shows most clearly for the fourth spell.
 Despite the increase in spacing even for those with three girls, the increases in 
@@
 follow a fertility pattern broadly similar to those with no education.
-As expected, fertility is lower than for women with no education, but still a
+As expected, fertility is lower than for women with no education, but there is still a
 strong son preference in the parity progression behavior.
@@
 percent likelihood of having a birth, but that has fallen to only around 25 percent.
-However, son preference still shows clearly in the parity progression probability for 
-women without a son, with the decline for the third and fourth spell substantially
+Son preference still shows clearly in the parity progression probabilities for 
+women without a son, with the declines for the third and fourth spells substantially
 slower for both urban and rural women without a son than for those with at least one son.
@@
 The tremendous impact that sex selection can have on birth spacing is illustrated 
-particularly vividly by the changes over time for the third spell.
+particularly vividly by the changes over time for the third spell, which led to a complete 
+reversal of the standard spacing pattern.
 In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
@@
 For the later periods, however, the highest predicted average spacing was for women
-with only daughters with most of the differences to the other sex compositions 
+\emph{with only daughters}, with most of the differences to the other sex compositions 
 statistically significant.
@@
 An important caveat is that because of the falling fertility relatively few women make
-it to the fourth spell, and even if they do, we do not observe a birth by the time of the
-survey.
+it to the fourth spell, and even if they do, we often do not observe a birth by the time 
+of the survey.
 Of the 11,886 women across urban and rural areas observed for the fourth spell for the 
@@
 spacing, or a general increase in spacing have important implications for what effects the
-increase in average spacing are likely to have and how to interpret the motivation for
+increases in average spacing are likely to have and how to interpret the motivation for
 the changes.
@@
 Conversely, if parents know that short birth intervals are detrimental to the next child's
-health, and with sex selection, the next child is likely a boy, it might make sense to 
+health, and that, with sex selection, the next child is likely a boy, it might make sense to 
 wait longer before conceiving.
@@
 }
-The difference in spacing between a first-born girl and a first-born boy first-born 
-remains almost the same across the four decades.
+The difference in spacing after a first-born girl and a first-born boy remains almost 
+the same across the four decades.
 Furthermore, the proportion with very short spacing remains almost the same.
@@
 Families with two girls are especially likely to have a birth early with 25 percent
-having a child within 12 months of the beginning of the spell (21 months after the prior
-second birth).
+having a child within 12 months of the beginning of the spell (21 months after the second 
+birth).
 That number is only slightly smaller four decades later. 
@@
 
-For the third spell, the 1972--1984 period show a close to standard pattern throughout, 
+For the third spell, the 1972--1984 period shows a close to standard pattern throughout, 
 although, as mentioned above, the sex ratios for women without girls was substantially 
@@
 than a general reduction in the likelihood of very short birth intervals.
-It also means, that previous girls can expect more time without a younger sibling,
+It also means that the previously born girls can expect more time without a younger sibling,
 which may reduce the sibling competition for resources.
@@
 Despite the idea that the ``North'' has high fertility and lower 
-likelihood of sex selection the differences to the ``West'' region is surprisingly small,
+likelihood of sex selection the differences to the ``West'' region are surprisingly small,
 at least in the urban areas.
@@
 Judging from the second spell progression rate and the associated spacing pattern, it
-does, indeed, appear that there is little son preference in this region.
+does, initially, appear that there is little son preference in this region.
 The likelihood of having a second birth is relatively high at around 80 to 90 percent
@@
 
-With the high likelihood of a second birth and lower decline in the likelihood of a third
-birth, the ``South'' has higher predicted fertility than the ``East.''
-What is more, for urban areas the average birth interval has increased substantially
-for those with only girls relative to those with a boy and a girl, corresponding to
+Despite the second spell's apparent lack of son preference behavior, for the third spell 
+in urban areas the average birth interval has increased substantially for those with only 
+girls relative to those with a boy and a girl, corresponding to
 a predicted sex ratio close to 60 percent with only girls. 
@@
 fertility and the associated extensive use of sex selection.
-Rather than having the next birth sooner as they mostly did before sex selection became 
-available, women with either no or one son now have substantially longer spacing than if 
-they have two or more sons.
+Women with either no or one son now have substantially longer spacing than if they have 
+two or more sons, rather than having the next birth sooner as they mostly did before sex 
+selection became available.
 As shown by the increasingly significant deviations in the sex ratio from the natural sex 
-ratio, these changes are likely due to increased use of sex selection rather than a sudden
+ratio, these changes are due to increased use of sex selection rather than a sudden
 reversal in son preference.
@@
 
-\vspace*{-0.51cm}
+The first set of tables, Tables \ref{tab:avg_sex_ratio_low}, \ref{tab:avg_sex_ratio_med}, 
+and \ref{tab:avg_sex_ratio_high}, show predicted average birth intervals, sex ratios, and 
+probabilities of having a birth by decade, spell, and sex composition for the three 
+education levels separated by the area of residence, together with standard errors for all 
+three outcomes.
+The standard errors are based on bootstrapping for all three measures,
+where the model is repeatedly estimated using resampling with replacement.
+
+I also show whether durations for sex composition other than only girls are statistically 
+significantly different from the duration with only girls based on bootstrapped 
+differences. 
+The cleanest test is comparing durations after only boys with durations after
+only girls, but the number of births to women with only sons becomes small 
+in the later periods.
+Hence, it is possible to have substantial differences in spacing that are
+not statistically significant because of low power, especially for the third 
+and fourth spell.
+
+Each predicted percent of boys is tested against the natural percentage of
+boys using the bootstrapped standard errors.
+The natural sex ratio is approximately 105 boys to 100 girls or
+51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
+The predicted percentage boys may differ from the natural rate because of 
+natural variation, any remaining recall error not corrected for, or 
+sex selection.
 

### 2019-03-25 response/response-demography-1.tex
Add caveat on Introduction too long now
Final grammar edits of response

@@
 
-\begin{center} Response to Editor and Referee Comments \end{center}
+\begin{center} Response to Editor and Reviewer Comments \end{center}
 
@@
 India's Experience over Four Decades.''
-I would like to thank the two referees and the editor for the very useful comments and 
+I want to thank the two reviewers and the editor for the very helpful comments and 
 suggestions, which I believe substantially improved the paper.
@@
 
-I have completely rewritten the Introduction to better situate the paper in the literature
-and to highlight the contributions of the paper.
-I now cover the research on using spacing as a measure of son preference, the 
+I have rewritten the Introduction entirely to situate the paper in the literature 
+and better highlight the contributions of the paper.
+I now cover the research on spacing as a measure of son preference, the 
 relationship between spacing and child health (both older and younger child), the 
 effect on women's health and other outcomes, and, finally, the limited and mixed results
-on what determines birth spacing behavior in developing countries compared to developed 
-countries.
-I use these to motivate why examining how birth spacing has been affected by the use of
-sex selection is important, and, in addition, highlight the three main questions I address 
+on what determines birth spacing behavior in developing countries.
+I use these to motivate why it is essential to examine how birth spacing has been affected 
+by the use of sex selection, and, in addition, highlight the three main questions I address 
 in the paper: the effect of sex selection on birth intervals, the distribution of births 
 within spells, and, finally, differences across geographical regions.
+
+My one concern with the rewrite is that the review of the relevant literature might have 
+gotten a little too detailed, making the Introduction too long. 
+If there are parts that might fit better somewhere else or that needs to be shortened or
+removed, I am open to suggestions.
 
@@
 in the ``Estimation Strategy'' section).
-This now covers education, sex composition, and area of residence in more detail.
-If there is a more appropriate place for this discussion, I am open to moving it.
+The discussion now covers education, sex composition, and area of residence in more detail.
+If there is a more appropriate place for this discussion, I am happy to move it.
 
-When it comes to selection, there are two possible explanations: one economic and one 
+When it comes to selection, I see two possible explanations: one economic and one 
 cultural.
-In the ``economic'' explanation, the use of sex selection is mainly driven by the lower 
-fertility that comes from higher opportunity cost of time and the higher income that allow 
-those with higher education to use sex selection.
-In that case, there is essentially no selection bias since the use of sex selection is 
-driven by factors that are identical across those with the same level of education.
+In the ``economic'' explanation, well-educated women's use of sex selection is mainly 
+driven by the lower fertility that comes from their higher opportunity cost of time and 
+the higher income that allow them to use sex selection.
+In that case, there is no selection bias since the use of sex selection is driven by 
+factors that are identical across those with the same level of education.
 
-The ``cultural'' explanation is that originally those with higher education where also 
+My ``cultural'' explanation assumes that, originally, those with higher education were also 
 those groups with the strongest son preference (presumably also higher caste).
 The expansion of access to education brought other groups/castes into connection with
-the higher castes and lead to assimilation of the high caste son preference norms.
-Presumably this assimilation would not be complete and those groups newer to higher 
-education would therefore have lower son preference and therefore lower use of sex 
+the higher castes and led them to assimilate the high caste son preference norms.
+Presumably, this assimilation would not be complete, and those groups newer to higher 
+education would, therefore, have lower son preference and therefore lower use of sex 
 selection.
-This means that any appearance of lower use of sex selection could be a selection story,
+Hence, any appearance of lower use of sex selection could be a selection story,
 and that the initial group's son preference is just as strong.
-The cultural explanation also suggests a reason for why the stated son preference appear 
+The cultural explanation also suggests a reason for why the stated son preference appears 
 to decline over time: the ``newer'' entrants have lower initial son preference and, 
-therefore, the average son preference for high education women will decline over time.
-\citep{bhat03}, \citep{pande07}.
+therefore, the average son preference for high education women will decline over time
+\citep{bhat03,pande07}.
 
-Since I have no way of separating out these two possible explanation with the available
+Since I have no way of separating these two possible explanations with the available
 data and set up, I have not included this discussion in the paper itself. 
-One possible approach would be to included this as a question for future research in the
+One possible approach would be to include this as a question for future research in the
 Conclusion.
@@
 
-As detailed below, I have substantially shorten the ``Estimation Strategy'' section.
-The results section is not necessarily shorter, but is better focused on the spacing
-results, guided by the three main questions.
-There is also less focus on the sex selection results.
-Specifically, I have removed the section on how the use of sex-selective abortions changes 
+As detailed below in my response to Reviewer 1, I have substantially shortened the 
+``Estimation Strategy'' section.
+The results section now focuses on the spacing results, guided by the three main 
+questions.
+Also, I have removed the section on how the use of sex-selective abortions changes 
 within a spell since it, as originally written, was more focused on sex selection than
-the spacing, and that the spacing question is better addressed in the section on the
+the spacing, and because I can better address the spacing question in the section on the 
 distribution of births within spells.
-Obviously I still need to discuss how sex selection has changed to tie those to the 
+I still need to discuss how sex selection has changed to tie those to the 
 changes in spacing, but I have tried to make these result mainly serve the overall
-spacing analysis.
+analysis of spacing.
+In response to Reviewer 1's comments, I have added a section on regional differences,
+using information on well-educated women.
 
@@
 
-I address this a number of different ways.
+I address fertility changes three different ways.
 First, in the Introduction, I discuss the decline in fertility when introducing why India 
-is an interesting case, with special focus on the relationship between declining fertility 
-and increased use of sex selection and, hence, by my hypothesis on birth spacing.
-Second, the suggestion by Referee 1 to use graphical presentation of the results made it 
+is a compelling case, with a particular focus on the relationship between declining fertility 
+and increased use of sex selection and, hence, by my hypothesis, on birth spacing.
+Second, the suggestion by Reviewer 1 to use a graphical presentation of the results made it 
 possible to include the likelihood of parity progression for each of the three spells, 
@@
 and by urban and rural areas.
-I have also added the parity progression likelihood to the original tables, which are now
-included in the online Appendix.
+I have also added the parity progression likelihood to the original tables, which I now
+include in the online Appendix.
 Third, I discuss the changes in fertility directly in the Results section.
@@
 \begin{enumerate}
-\item 1. The key contribution of the paper is the use of birth spacing and sex
+\item The key contribution of the paper is the use of birth spacing and sex
 ratios to examine changes and differentials in possible sex-selective
@@
 
-\item 2. The paper would need to articulate its contribution clearly. The
+\item The paper would need to articulate its contribution clearly. The
 paper seems to be focussed too much on methodology and less on
@@
 
-\item 3. The literature review must be systematic. The paper seems to move too
+I have rewritten the paper completely, so the focus is now directly on spacing 
+changes, especially how access to sex selection changes birth intervals differently across 
+sex compositions.
+As part of the rewrite, I now include a substantially expanded review of the literature
+on sex selection, son preference, and spacing.
+I use this literature review to guide my discussion of the changes in spacing throughout
+the paper.
+
+\item The literature review must be systematic. The paper seems to move too
 quickly to estimation strategy. Before presenting this, the literature
@@
 
-\item 4. The demographic literature, for example, by works from Christophe Z
+\item The demographic literature, for example, by works from Christophe Z
 Guilmoto, doesn’t seem to be consulted. Guilmoto and colleagues many
@@
 lead to longer spacing.
-As part of this rewrite, I have incorporated the suggested references and other works into 
-the Introduction as part of the motivation for why examining the changes in birth 
-intervals that arise from the use of sex selection is important.
+As part of this rewrite, I have incorporated the suggested references and other relevant
+works into the Introduction as part of the motivation for why examining the changes in 
+birth  intervals that arise from the use of sex selection is essential.
 
-\item 5. The use of competing hazard models is not new in demographic research
+\item The use of competing hazard models is not new in demographic research
 and doesn’t require long exposition. This section can be cut
@@
 
-I have reduced the length of the section by more than 1/4 (the original section was 5
+I have reduced the length of the section by more than 1/4 (the original section was five
 pages long, while the revised section is less than 3.5).
@@
 
-There are three important differences between my approach and what is standard
-in the literature, and I believe further shortening would negatively impact readers's
+There are three essential differences between my approach and what is standard
+in the literature, and I believe further shortening would negatively impact readers'
 ability to understand the results.
-First, most research that use survival models employ proportional hazard models, so 
-motivating and providing more information on the non-proportional set-up is important.
+First, most research that uses survival models employ proportional hazard models, so 
+motivating and providing more information on the non-proportional set-up is essential.
 Second, the use of conditional survival curves is, to my knowledge, new, and, therefore,
@@
 Third, the sex ratio calculations is a new way to use competing risk estimates and is 
-required to understand how the use of sex selection impact birth intervals.
+required to understand how the use of sex selection impacts birth intervals.
 
-\item 6. The use of NFHS data including the most recent data are welcome. An
+\item The use of NFHS data including the most recent data are welcome. An
 additional limitation to those addressed in the paper is the issue of
@@
 
-This is, indeed, an important concern.
-For both NFHS-1 and NFHS-2, the only information collected on marriage timing is age at 
-marriage and age starting living with husband.
+Date imputation is, indeed, a significant concern.
+For both NFHS-1 and NFHS-2, the only information collected on marriage timing is the age 
+at marriage and age starting living with husband.
 For NFHS-1, I, therefore, used the date of birth of the respondent in CMC and added the 
-age at marriage multiplied by 12 to get the earliest data of marriage in CMC possible.
-Using this definition, 10.73 percent have duration of less than eight months or fewer, and
-0.71 percent have a negative duration.
+age at marriage multiplied by 12 to get the earliest date of marriage in CMC possible.
+If I use this definition, 10.73 percent have a duration of eight months or fewer, 
+and 0.71 percent have a negative duration.
 For NFHS-2, I used the imputed duration provided in the recode data set, which leads to 
-24.65 percent with an eight months or fewer duration between marriage and first birth, 
+24.65 percent with a duration of eight months or fewer between marriage and first birth, 
 and 0.95 percent with a negative duration.
-Other people seem to have been caught by the same problem, such as \citet{Padmadas2004}.
+Other people seem to have been caught by the same problem 
+\citep[See, for example, ][]{Padmadas2004}.
 
-Both NFHS-3 and NFHS-4 ask for specific month and year of first marriage, but a number of
-respondent did not provide complete information.
+Both NFHS-3 and NFHS-4 ask for the specific month and year of first marriage, but some
+respondents did not provide complete information.
 One approach to understanding the impact of imputation on spacing to first birth is to 
 split spacing from marriage to first birth by completeness of date of marriage.
-In NFHS-3, 2.55 percent of the 39,213 women with complete information on date of 
-marriage show a spacing from marriage to first birth of 8 months or less and that 0.6 
+In NFHS-3, 2.55 percent of the 39,213 women with complete information on the date of 
+marriage shows a spacing from marriage to first birth of 8 months or less and that 0.6 
 percent show a negative spacing. 
-For the 19,403 women with incomplete information on date of marriage 27.36 percent show
-a spacing from marriage to first birth of 8 months or less and that 3.37 percent show a 
+For the 19,403 women with incomplete information on the date of marriage, 27.36 percent show
+a spacing from marriage to first birth of eight months or fewer and that 3.37 percent show a 
 negative duration.
-In NFHS-4, 3.8 percent of women with complete information report a birth 8 or fewer months
+In NFHS-4, 3.8 percent of women with complete information report a birth eight or fewer months
 after marriage and 2.35 report a negative duration.
-For women with imputed information, 14.99 percent report a birth 8 or fewer months
+For women with imputed information, 14.99 percent report a birth eight or fewer months
 after marriage with 11.02 percent reporting a negative duration.
@@
 I have dropped the analysis of first spells.
-Removing the first spell also helps keeping the paper within the word limit.
+Removing the first spell also helps to keep the paper from getting excessively long.
 Because of the large number of imputed observations for the first spell, I have also
@@
 
-\item 7. It is not clear why exactly 22, 23, 25 years are used a cut-off
+\item It is not clear why exactly 22, 23, 25 years are used a cut-off
 points.
@@
 to simplify.
-Even with the stricter cut-off there are, however, still some evidence of recall error 
+Even with the stricter cut-off, there is, however, still some evidence of recall error 
 where the sex ratio was substantially biased against females  before sex selection became 
@@
 
-\item 8. I understand the empirical reason for not increasing the number of
+\item I understand the empirical reason for not increasing the number of
 variables. However, a key variable that is essential to consider is
@@
 
-I agree completely that the regional differences in fertility, son preference, and use 
-of sex selection are important.
+I agree that the regional differences in fertility, son preference, and use 
+of sex selection are essential to examine.
 To try to capture these differences, I have divided India into four broad regions 
-depending on degree of son preference and initial fertility level as in 
+depending on the degree of son preference and initial fertility level as in 
 \citet{retherford03b}, although expanded to include all states in the surveys.
@@
 small sample sizes for the estimations to converge.
-The lack of convergence is especially an issue for the lower and middle-education groups.
+The lack of convergence is primarily an issue for the lower and middle-education groups.
 I, therefore, first present the all-India results and then focus on regional differences
@@
 
-\item 9. The three tables are logically organized and contain a wealth of
+\item The three tables are logically organized and contain a wealth of
 information. But there are too many comparisons to make in each of the
@@
 I, therefore, still include Tables 1-3, but have moved them to the Appendix, and I have 
-added the probability of a birth to the tables.
+added the probability of having a birth by the end of the spell to the tables.
 I have also combined the 75th, 50th, and 25th percentiles results tables in the Appendix.
 
-\item 10. As sex composition and sex ratios has been examined in the literature, I think
+\item As sex composition and sex ratios has been examined in the literature, I think
 it would make sense to not present findings on that in great detail. As
@@
 structuring the analysis of birth spacing.
+I have also removed the section on how sex ratios change within spells since that is
+more relevant when examining sex selection.
+I can better address birth spacing changes using the results on the distribution of 
+births within a spell.
 
-\item 11. The results talk about compression of spacing. This is important and
+\item The results talk about compression of spacing. This is important and
 literature on it should be presented in the intro or lit review section.
@@
 
-Compression in the original manuscript was only for first birth interval, and I no longer 
+Compression in the original manuscript was only for the first birth interval, and I no longer 
 cover that because of the data issues discussed above.
@@
 
-\item 12. As there are many results presented, it would make sense to have a
+\item As there are many results presented, it would make sense to have a
 paragraph at the beginning of the conclusion highlighting the key
@@
 
-With the refocus on birth intervals there should be more coherence in the results.
+With the refocus on birth intervals, there should be more coherence in the results and
+how I present them.
 I have, however, highlighted what I consider the main results in the Conclusion.
@@
 [Response:]
+
+As mentioned, I have substantially expanded the review of the literature, and use the 
+review to guide the main questions I ask, and I refer back to the main previous finding 
+throughout to place my results in perspective.
+With the restructuring of the Results section, including the added discussion of regional 
+differences, and the rewrite of the Conclusion, I hope that the paper is now more 
+balanced. 
+I also trust that it is clearer how it fits into the literature.
 

### 2019-03-25 paper/sex_selection_spacing-ver2.tex
Minor edits

@@
 \noindent 
-
 Strong son preference is typically associated with shorter birth spacing in the absence of 
@@
 Using the four rounds of India's National Family and Health Surveys, I show that birth 
-intervals increased substantially over the last four decades, most substantially among 
-women most likely to use sex selection.
+intervals increased substantially over the last four decades, with the most significant
+increase among women most likely to use sex selection.
 Specifically, well-educated women with no boys now have significantly longer birth

### 2019-03-25 paper/sex_selection_spacing-ver2-demography.tex
Cannot have identifiable information on submission

--- 2019-03-25 paper/sex_selection_spacing-ver2.tex
@@
 India's Experience over Four Decades%
-\protect\thanks{%
-I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-University of Washington, University of Aarhus, the Fourth 
-Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful 
-suggestions and comments.
-I would also like to thank Nalina Varanasi for research assistance.
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
-The views and findings expressed here are those of the author and
-should not be attributed to the World Bank or any of its member countries.
-Partial support for this research came from a Eunice Kennedy Shriver National
-Institute of Child Health and Human Development research infrastructure grant,
-5R24HD042828, to the Center for Studies in Demography and Ecology at the
-University of Washington.
-}
-}
-
-\author{Claus C P\"ortner\\
-    Department of Economics\\
-    Albers School of Business and Economics\\
-    Seattle University, P.O. Box 222000\\
-    Seattle, WA 98122\\
-    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
-    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
-    \& \\
-    Center for Studies in Demography and Ecology \\
-    University of Washington\\ \vspace{2cm}
-    }
+% \protect\thanks{%
+% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
+% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
+% University of Washington, University of Aarhus, the Fourth 
+% Annual Conference on Population, Reproductive Health, 
+% and Economic Development, and the Economic Demography Workshop for helpful 
+% suggestions and comments.
+% I would also like to thank Nalina Varanasi for research assistance.
+% Support for development of the method from the University of Washington Royalty 
+% Research Fund and the Development Research Group of the World Bank is gratefully 
+% acknowledged.
+% The views and findings expressed here are those of the author and
+% should not be attributed to the World Bank or any of its member countries.
+% Partial support for this research came from a Eunice Kennedy Shriver National
+% Institute of Child Health and Human Development research infrastructure grant,
+% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
+% University of Washington.
+% }
+}
+
+\author{}
+% \author{Claus C P\"ortner\\
+%     Department of Economics\\
+%     Albers School of Business and Economics\\
+%     Seattle University, P.O. Box 222000\\
+%     Seattle, WA 98122\\
+%     \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
+%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
+%     \& \\
+%     Center for Studies in Demography and Ecology \\
+%     University of Washington\\ \vspace{2cm}
+%     }
 
@@
 
-\setcounter{page}{-1}
+% \setcounter{page}{-1}
 \maketitle
@@
 
-% \setcounter{page}{0}
-
-\newpage
+\setcounter{page}{0}
+
+% \newpage
 \thispagestyle{empty}

### 2019-03-28 paper/sex_selection_spacing-ver2.tex
Shorten first half of paper

@@
 Birth spacing has long served as a measure of son preference, with strong
-son preference typically associated with shorter birth intervals the
+son preference associated with shorter birth intervals the
 fewer sons a family has \citep{ben-porath76b,Leung1988}.
-However, the introduction of prenatal sex determination has the potential to
-change the relationship between son preference and birth spacing.
+However, the introduction of prenatal sex determination potentially 
+changed the relationship between son preference and birth spacing.
 The stronger the son preference, the more likely couples are to resort to sex-selective 
-abortions, and each abortion automatically increases the interval between births by six 
-months to a year.%
+abortions, and each abortion increases the interval between births by six to twelve 
+months.%
 \footnote{
 The increase consists of three parts.
-First, starting from the time of the abortion, the uterus needs at 
+First, starting from the abortion, the uterus needs at 
 least two menstrual cycles to recover;  otherwise, the likelihood 
@@
 }
-Longer birth intervals in the absence of sons, which previously would be taken to indicate 
-a lower son preference, now may arise precisely because a sufficiently strong son 
-preference makes couples use sex selection.
-
-In this paper, I examine how birth spacing in India has changed over time and across 
+Hence, longer birth intervals in the absence of sons, which previously would be taken to 
+indicate a lower son preference, now may instead arise because couples with a strong son 
+preference use sex selection.
+
+Here, I examine how birth spacing in India has changed over time and across 
 groups with the introduction of sex selection.
-I introduce and apply an empirical method that directly incorporates the effects of 
+I introduce an empirical method that directly incorporates the effects of 
 sex-selective abortions on the duration between births 
@@
 % [Why India?]
-India is a particularly compelling case since it has a long history of male preference, 
+India is a particularly compelling case with its long history of male preference, 
 especially in the northern states \citep{Kishor1993,murthi95,arnold98}.
-A significant proportion of Indian families exhibit differential stopping behavior, where, 
-for a given number of children, they are more likely to have an additional child if they 
-have not yet reached their preferred number of sons 
+Mortality risk is higher for females than males for most ages groups, resulting in
+an almost continuous increase in India's overall ratio of males to females 
+over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
+Differential stopping behavior is widespread, with an additional child more likely the
+fewer sons a family has 
 \citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
@@
 }
-Moreover, mortality risk is higher for females than males for most ages groups, and
-there has been an almost continuous increase in India's overall ratio of males to females 
-over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
-
-% [What do we know about use of sex selection?]
-Over the last three decades, India has seen dramatic increases in the males-to-females 
-ratio at birth as access to prenatal sex determination expanded 
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012,Portner2015b}.
-Simultaneously, fertility has declined substantially, to the point where it is now at, or 
-even below, replacement in some areas 
+Furthermore, fertility has declined substantially, to the point where it is now at, or even 
+below, replacement in some areas 
 \citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-This decline in fertility, combined with a continued strong preference for sons, has 
-intensified the pressure to use sex selection 
-\citep{das_gupta97,Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
-\footnote{
-In some instances, however, the fertility decline appears to have created a stronger 
-aversion to daughters rather than a stronger preference for son \citep{DiamondSmith2008}.
-}
-The strongest predictor of the use of sex selection is the sex composition of previous 
-children; for families without a son, the higher the parity, the higher is the probability
-of having a son as the next birth \citep{retherford03b,jha06,abrevaya09,Portner2015b}.
-The use of sex selection also increases with socioeconomic status, especially 
-education, and is more prevalent in cities than in rural areas, both possibly because 
-of lower desired fertility \citep{retherford03b,jha06,Portner2015b}.
+The combination of falling fertility, strong son preference, and expanding access to 
+prenatal sex determination has lead to dramatic increases in the males-to-females ratio at 
+birth in India from sex selection over the last three decades
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,Bongaarts2013,Portner2015b,Jayachandran2017}.
 
@@
 First, researchers have made extensive use of birth spacing as a measure of son preference, 
-and it is critical to understand to what extent spacing is still useful as a measure of son 
+and it is critical to understand to what extent spacing is still a useful measure of son 
 preference.
-In India, the sex of the last-born child has in the past significantly affected the 
-duration to next birth, with the expected birth interval about three percent longer if the 
-last-born was a son than if it was a daughter \citep{Bhalotra2008,Kumar2016}.
+For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
+a boy as the last-born child, significantly increase the duration to next birth,
+\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
+\footnote{
 Ethnic Indians in South Africa also show a longer duration after the birth of a 
-son than after a daughter \citep{Gangadharan2003}.%
+son than after a daughter \citep{Gangadharan2003}.
+}
+Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
+absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
+\citep{Rossi2015}.
+
+Second, birth spacing can affect children's short and long-term outcomes.
+Most of the research finds a negative impact of short spacing on child health, especially 
+for very short intervals of 18 months or less \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
+There is evidence in countries as diverse as Bangladesh, Brazil, El Salvadore, India,
+and Pakistan of worse health outcomes and a higher mortality risk the shorter the birth
+interval
+\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,Ghosh2018}.
+Most of the evidence on longer-term outcomes come from Western countries.
+In the US, for example, a longer interval between births increases the older, but not the
+younger, sibling's test scores \citep{Buckles2012}.
+Furthermore, close spacing appears to increase the risk of dropping out of
+high school and lower the probability of attending a post-secondary school in both the
+US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.%
 \footnote{
-Ethnic Indians in Malaysia do, however, show little evidence of son preference, although
-the sample sizes are small \citep{Pong1994}.
-}
-In both Bangladesh and Vietnam, the more boys a family has the longer is the expected 
-duration to the next birth \citep{Haughton1995,Haughton1996,Rahman1993,Soest2018}.
-Outside Asia, the evidence is more mixed.
-North Africa shows shorter spacing in the absence of sons, while a similar pattern does
-not exist in Sub-Saharan Africa \citep{Rossi2015}.%
-\footnote{
-A possible exception is Senegal, where women with a higher risk of widowhood show
-shorter birth spacing until they have secured a son \citep{Lambert2016}.
-}
-
-Second, birth spacing can have a substantial impact on children's outcomes.
-Most of the research finds a negative impact of short spacing on child health---especially 
-for very short intervals of 18 months or less---although identifying the causal mechanisms 
-have proven more difficult \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
-There are three pathways through which birth intervals can affect health.
-First, there is maternal depletion, where the mother does not have sufficient time to 
-recover after her last pregnancy before she becomes pregnant again.%
-\footnote{
-This depletion can take the form of nutrition, folate, or cervical insufficiencies.
-}
-Second, disease transmission either from mother to child or between children.
-Third, sibling competition, where siblings close in age compete for scarce resources and
-parental care.
-Which mechanism dominates is of particular interest when son preference drives spacing 
-decisions.
-Both the maternal depletion and the transmission of disease explanations predominately
-affect the subsequent child and the mother.
-Only sibling competition has the potential to affect the older child negatively.
-
-In India, there is evidence that both the prior and the subsequent child have worse health 
-outcomes and a higher likelihood of dying the shorter the interval between them, although 
-the effects are not symmetrical
-\citep{Whitworth2002,Bhargava2003,Rutstein2005,Maitra2008,Makepeace2008,Ghosh2018}.%
-\footnote{
-\cite{Bhalotra2008}, however, find that birth spacing only explains a limited amount
-of neonatal mortality.
-}
-The increased mortality risk for prior children may come from shorter breastfeeding of 
-girls to ensure that the mother can conceive again sooner, and with poor water
-quality this shorter breastfeeding may result both in higher risk of dying and shorter
-stature if the child survives \citep{Jayachandran2011,Jayachandran2017a}.
-In other countries, focus has been mostly on the subsequent birth, but there is evidence 
-in countries as diverse as Bangladesh, Brazil, El Salvadore, and Pakistan that
-short intervals between births have adverse health effects
-\citep{Cleland1984,Curtis1993,Davanzo2008,Gribble2009,Saha2013}.
-
-The potential effects of spacing are not restricted to early outcomes, although
-there is less evidence on longer-term effects and most comes from Western countries.
-In the US, for example, a longer interval between births increases the older sibling's
-test scores on the Peabody Individual Achievement Test, although there is no
-statistically significant effect on the younger sibling \citep{Buckles2012}.
-In line with this, close spacing appears to increase the risk of dropping out of
-high school and lower the probability of attending a post-secondary school in both the
-US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.
-These results are, however, not uniformly supported, with recent results from Sweden 
-showing no relationship between birth spacing, even if very short, and outcomes such as 
-years of education completed, earnings, and unemployment \citep{Barclay2017}.
-
-Third, the mother may also be affected by the length of the birth intervals.
-The effect of spacing on mothers have received less attention than the effect on children, 
-and reviews of the literature show mixed results on mother's anthropometric status 
+However, recent results from Sweden show no relationship between birth spacing, even if 
+very short, and outcomes such as years of education completed, earnings, and unemployment 
+\citep{Barclay2017}.
+}
+
+Third, the mother may also be affected by the length of the birth intervals, although 
+reviews of the literature show mixed results on mother's anthropometric status 
 \citep{Dewey2007,Conde-Agudelo2012}.
-For India, there is, however, evidence that women with first-born girls are both
-more likely to have short birth spacing and more likely to have anemia, possibly as
-the result of the short spacing resulting in maternal depletion \citep{Milazzo2018}.
-In Western countries, having a longer interval between births appear to have positive
-effects on long-term labor market outcomes, such as participation and 
-income \citep{Gough2017,Karimi2014}.
+For India, there is, however, evidence that women with first-born girls are more likely to 
+have anemia, possibly because short birth spacing can resulting in maternal depletion 
+\citep{Milazzo2018}.
+In Western countries, a longer interval between births has positive effects on long-term 
+labor market outcomes, such as participation and income \citep{Gough2017,Karimi2014}.
 
@@
 in developed countries, and with declining fertility and increasing numbers of women 
-entering the labor force in developing countries, understanding how couples make timing 
-decisions will be necessary for the design of suitable policies \citep{Portner2018}.%
+entering the labor force, understanding how couples make timing decisions is necessary 
+for the design of suitable policies \citep{Portner2018}.%
 \footnote{
@@
 }
-For example, the evidence on the effects of education and socio-economic status on
-birth intervals is mixed, with some research showing either a positive association, no
-association, or one that is changing over time 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
-
 Even the effects of access to contraceptive and declining fertility on spacing are unclear.
 On the one hand, access to contraceptives allows women to avoid too short spacing between 
-birth, which would increase birth spacing.
+birth.
 On the other hand, increased reliability of access and effectiveness of contraceptives can 
-lead to shorter intervals between births  \citep{Keyfitz1971,Heckman1976}.
-With less reliable contraception parents choose a higher level of contraception, which 
-results in longer spacing, to avoid having too many children by accident.
-However, as contraception becomes more effective parents can more easily avoid future 
-births, allowing them to reduce the spacing between births without having to worry about 
-overshooting their preferred number of children.
+lead to shorter intervals between births if women used to have longer spacing to avoid
+having too many children by accident \citep{Keyfitz1971,Heckman1976}.
 These two counteracting effects may explain why better-educated women have shorter spacing 
 than less educated women in some instances but not in others and why finding statistically 
-significant effects of contraception use on birth spacing is difficult \citep{Yeakey2009}.%
+significant effects of contraception use on birth spacing is difficult 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.%
 \footnote{
-There is evidence in Matlab that the effect of son preference on birth spacing is
-stronger in areas with better access to family planning \citep{Rahman1993}.
-Other evidence, however, points to families ability to time birth, even in the absence
+In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
+access to family planning \citep{Rahman1993}.
+Other evidence, however, points to families ability to time births, even in the absence
 of modern contraceptives \citep{Jayachandran2011,Alam2018}.
@@
 Despite the increasing use of sex selection, the critical impacts of spacing on outcomes 
-for both mother and children, and the extensive use of spacing to measure son 
-preference in the literature, there has so far been no examination of what effect access 
-to sex selection has had on spacing.
-The overall hypothesis is that spacing patterns significantly changed as prenatal sex 
-determination became available.
-Specifically, I address three questions.
-
-First, how did average birth intervals change over time for different groups and how are 
-those changes related to the likely use of sex selection?
-The underlying hypothesis is that in the absence of sex selection son preference leads to 
-shorter spacing the fewer boys a family has for a given parity, whereas son preference 
-increases the spacing the fewer boys a family has when prenatal sex selection is available.
-I still expect parents to \emph{try} to conceive earlier after the birth of a girl than 
-after a boy, but the abortions will increase the duration between births, and may even 
-lead to longer average spacing after the birth of girls than after boys.
+for both mother and children, and the extensive use of spacing to measure son preference, 
+there has so far been no systematic examination of what effect access to sex selection 
+have on spacing.
+I address three questions to remedy this shortcoming.
+
+First, how did average birth intervals change over time for different groups and how do 
+these changes relate to the use of sex selection?
+The hypothesis is that in the absence of sex selection son preference leads to shorter 
+spacing the fewer boys a family has, whereas son preference increases spacing the fewer 
+boys a family has when prenatal sex selection is available, possibly to the point where
+we observe a reversal of the standard spacing pattern.
 Families with son preference who---for one reason or another---do not use prenatal sex 
-selection may continue to have shorter birth spacing.
+selection likely continue to have shorter birth spacing.
 Based on the prior literature on sex selection, I focus on how birth intervals have
@@
 Second, have the shapes of the survival curves changed?
-Very short birth intervals are, as mentioned, associated with worse health outcomes and 
-increased mortality risk \citep{Conde-Agudelo2012}.
-Hence, understanding how the distribution of birth intervals changes can help us understand to 
-what extent we can expect improvements in health outcomes.
-We should, for example, expect different impacts on the distribution of birth intervals
-depending on whether parents change their spacing behavior based on an increasing 
-concern for child health or from a strong son preference leading to continued pregnancies
-until they conceive a son.
-
-Finally, how are the changes in birth intervals with increasing access to sex selection 
-distributed geographically?
-Given the size and cultural differences within India, it is unlikely that the increasing 
+Although examining average birth intervals helps us understand the overall changes in 
+spacing behavior, it tells us little about how these changes came about.
+For example, the motivation behind an increase in average spacing is different if it
+comes mainly from parents trying to avoid very short birth intervals, which, as mentioned,
+are associated with worse child outcomes, or from continued use of sex selection to
+ensure a son.
+
+Finally, how are the changes in birth intervals distributed geographically?
+Given the cultural differences within India, it is unlikely that the increasing 
 access to sex selection will have had the same effects throughout \citep{retherford03b}.
@@
 
-Direct information on the use of sex selection is not available, but it is possible to 
-compare different periods as a proxy since there have been substantial changes in access 
-and legality of prenatal sex determination in India.
-Abortion has been legal in India since 1971 and still is.
-The first reports of sex determination appeared around 1982--83 
-\citep{Sudha1999,bhat06,Grover2006}.
-The number of clinics quickly increased, and knowledge about sex selection became 
-widespread after a senior government official's wife aborted a fetus that turned out to be 
-male \citep[p.\ 598]{Sudha1999}.
-In 1994, the Central Government passed the Prenatal Diagnostic Techniques (PNDT) Act, 
-making determining and communicating the sex of a fetus illegal.%
-\footnote{
-Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
-The number of convictions has been low.
-It took until January 2008 for the first state, Haryana, to reach five convictions.
-Hence, private clinics operate with little risk of legal action \citep{Sudha1999}.
-Furthermore, there is little evidence that bans like this significantly
-affect sex ratios \citep{Das-Gupta2016}.
-}
-
-Based on these developments, I split the four decades into four periods.
-The first period covers until prenatal sex determination became widely available, 
-1972--1984.
-The second period saw (mostly) unrestricted access to sex selection, 1985--1994.
-Although, as reviewed above, there is evidence that there has been a substantial 
-increase in the use of sex selection, some researchers argue that we might be close to or 
-have already passed a turning-point in the use of sex selection 
-\citep{Das_Gupta2009,Diamond-Smith2015}.
-I, therefore, split the period from the implementation of the PNDT Act until the last 
-survey into two, 1995--2004, and 2005--2016.
-
 There are four main results.
-First, there has been a general increase in the intervals between births for all education 
-groups over the four decades covered by the data.
+First, the intervals between births have increased for all education groups over the four 
+decades.
 These increases are larger the higher the parity and the higher the education 
 level.
-Second, those women who are most likely to use sex selection, well-educated women with no
-sons, have seen the largest increases in birth intervals.
-As a result, we now have a complete reversal of the traditional spacing pattern for
-well-educated women, and instead, observe the longest birth intervals for women with no 
-sons.
+Second, those women who are most likely to use sex selection---well-educated women with no
+sons---have seen the largest increases in birth intervals.
+As a result, well-educated women now show a complete reversal of the traditional spacing 
+pattern, with the longest birth intervals for women with no sons.
 Third, women who are least likely to use sex selection, those with no education in
@@
 little evidence of the use of sex selection.
-In other words, these women adhere to a strategy where they achieve a son through higher 
-fertility rather than the use of sex selection.
-Fourth, the traditional pattern of longer average spacing when women have one or more sons
-appear to arise from more very long intervals, rather than from fewer very short birth 
-intervals; across education groups there appear to be little difference in the likelihood
-of having a very short birth interval across sex compositions, especially for lower
-parities.
+Fourth, the traditional pattern of longer average spacing with sons appear to arise from 
+more very long intervals, rather than from fewer very short birth intervals; across 
+education groups, there appears to be little difference in the likelihood of having a very 
+short birth interval across sex compositions, especially for lower parities.
 
@@
 models with a single exit, the birth of a child.
-There are two problems with the standard approach in this setting.
+There are two problems with this approach in this setting.
 First, and most importantly, the introduction of sex selection means that the sex of the 
@@
 I, therefore, use a competing risk set-up, which can capture both the non-randomness of
-the birth outcome and the differential spacing to the birth of a girl or a boy.
+the birth outcome and the differential spacing.
 To my knowledge, this is the first application of competing risk models to birth
@@
 throughout the entire spell as is assumed by the proportional hazard model.
-Assuming that the effect of sex composition is the same throughout a spell is especially 
-problematic for higher-order spells where different sex composition of previous births can 
-lead to substantial differences both in the likelihood of progressing to the next birth 
-and how soon couples want their next child if they are going to have one.
+The proportionality assumption is especially problematic for higher-order spells where 
+there are substantial differences across groups both in the likelihood of progressing to 
+the next birth and how soon couples want their next child if they are going to have one.
 The introduction of prenatal sex determination exacerbates any bias from the 
@@
 Hence, transforming the data, so each observation is an interval---here equal
-to three months---the model can be estimated using a standard multinomial logit model.%
-\footnote{
-The multinomial model assumes that alternative exit states are stochastically independent
-(Independence of Irrelevant Alternatives or IIA), which rules out any individual-specific 
-unmeasured or unobservable factors that affect both the hazard of having a girl and the 
-hazard of having a boy.
-I, therefore, include a proxy for fecundity discussed in Section \ref{sec:data}.
-Also, the multivariate probit model can be used as an alternative because the IIA is not 
-imposed \citep{han90}.
-The results are substantially identical between these two models and
-available upon request.
-}
+to three months---the model can be estimated using a standard multinomial logit model.
+%
+% \footnote{
+% The multinomial model assumes that alternative exit states are stochastically independent
+% (Independence of Irrelevant Alternatives or IIA), which rules out any individual-specific 
+% unmeasured or unobservable factors that affect both the hazard of having a girl and the 
+% hazard of having a boy.
+% I, therefore, include a proxy for fecundity discussed in Section \ref{sec:data}.
+% Also, the multivariate probit model can be used as an alternative because the IIA is not 
+% imposed \citep{han90}.
+% The results are substantially identical between these two models and
+% available upon request.
+% }
 In the reorganized data the outcome variable is 0 if the woman does not have a child in a 
@@
 The data come from the four rounds of the National Family Health Survey
-(NFHS-1, NFHS-2, NFHS-3, and NFHS-4),
 collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.%
@@
 
-I exclude visitors to the household, as well as
-women who have been married more than once, divorced, or who are 
-not living with their husband,
-women with inconsistent age at marriage,
-and those with missing information on education.
-Women interviewed in NFHS-3 or NFHS-4 who were never married or where Gauna 
-had not yet been performed were also dropped.
-The same goes for women who had at least one multiple births,
-reported having a birth before age 12, had a birth before marriage, or an interval between 
-births of less than nine months.
-
-Finally, I restrict the sample to Hindus,
-who constitute about 80\% of India's population.
-If the use of sex selection differ between Hindu and other religions, such 
-as Sikhs, assuming that the baseline hazard is the same would lead to bias.
-The other groups are each so small relative to Hindus that it is not
-possible to estimate different baseline hazards for each group.
-Furthermore, the other groups are so different in background and son 
-preference that combining them into one group would not make sense.
-
-There are four advantages to using the NFHS.
-First, surveys enumerators pay careful attention to spacing between births and
-probe for ``missed'' births.
-Second, no other surveys cover as extended a period in the same amount of detail.
-The four NFHS rounds allow me to show how spacing and 
-sex ratio changed from before sex-selective abortions were available until 2016.
-Third, NFHS has birth histories for a large number of women.
-% %
-% \footnote{
-% The Special Fertility and Mortality Survey appears to cover a much large number of households
-% than the three rounds of the NFHS combined, but \citet{jha06} only use the births that 
-% took place in 1997 making their sample sizes by parity smaller than here.
-% Their sample consists of 133,738 births of which 38,177 were first-born, 
-% 36,241 second-born, and 23,756 were third-born.
-% }
-Finally, even if probing for missing births does not eliminate recall error,   
-the overlap in cohorts covered and the large sample size makes it possible 
-to establish where recall error remains a problem.
-
-Recall error arises mainly from child mortality when respondents are 
-reluctant to discuss deceased children.
-Systematic recall error, where the likelihood of reporting a deceased 
-child depends on the sex of the child, is especially problematic because 
-it biases both spacing and sex ratios.
-Probing catches many missed births, but systematic recall error is 
-still a potentially substantial problem.
-
-Three factors contribute to the problem here.
-First, girls have a significantly higher mortality risk than boys.
-Second, son preference may increase the probability that parents recall boys 
-more readily than girls.
-Finally, in NFHS-1 and NFHS-2 enumerators probed only for a missed birth if the
-initially reported birth interval was four calendar years or more,
-but, given short durations between births, especially after the birth of a girl,
-that procedure is unlikely to pick up all missed children.
-
-Recall error is heavily dependent on how long ago a woman was married.%
+I exclude visitors to the household, as well as women who fall into any of the following 
+categories: never married; no gauna yet; married more than once; divorced; 
+not living with husband; inconsistent age at marriage; or education information missing.  
+The same goes for women who had at least one multiple births, reported having a birth 
+before age 12, had a birth before marriage, or an interval between births of less than 
+nine months. 
+Finally, I restrict the sample to Hindus, who constitute about 80\% of India’s population.%
 \footnote{
-See the discussion in the online Appendix.
-}
-I, therefore, drop women married 22 years or more.
+If the use of sex selection differ between Hindu and other groups assuming
+that the baseline hazard is the same would lead to bias. The other
+groups are each so small that it is not possible to estimate different
+baseline hazards for each group, and are so different that combining
+them into one group would not make sense.
+}
+
+In addition to the large number of women surveyed and the long period covered, one of the
+benefits of the NFHS is that surveys enumerators pay careful attention to spacing between 
+births and probe for ``missed'' births.
+Nevertheless, systematic recall error, where the likelihood of reporting a deceased 
+child depends on the sex of the child, is still a potentially substantial problem and
+will bias both spacing and sex ratios.
+As I show in the online Appendix, recall error is heavily dependent on how long ago a 
+woman was married, and I, therefore, drop women married 22 years or more.
 The final sample consists of 
@@
 
-\subsection{Spell Definition\label{sec:spell_def}}
+Direct information on the use of sex selection is not available, so I compare different 
+periods as a proxy, based on the changes in access and legality of prenatal sex 
+determination in India.
+Abortion has been legal in India since 1971.
+Reports of sex determination appeared around 1982--83, and the number of clinics 
+quickly increased \citep{Sudha1999,bhat06,Grover2006}.
+In 1994, the Prenatal Diagnostic Techniques (PNDT) Act made determining and communicating 
+the sex of a fetus illegal.%
+\footnote{
+Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
+There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2016}.
+}
+Although the use of sex selection increased even after 1994, some researchers argue that 
+we have passed a turning point in its use \citep{Das_Gupta2009,Diamond-Smith2015}.
+I, therefore, use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
+The allocation of spells into periods is determined by when conception, and therefore 
+decisions on sex selection, can begin, even if we do not observe any births until nine 
+months later. 
+This allocation mechanism means that some spells cover two periods, which may bias 
+downward the differences between the periods.
 
 I focus here on the second through fourth spells, that is, on the intervals from the first 
-birth until at most the fourth birth.%
-\footnote{
-I exclude the first spell from marriage to the first spell because of data issues.
-In NFHS-1 and NFHS-2 the only information on marriage timing is the age at marriage, and 
-all spell durations are therefore imputed.
+birth until at most the fourth birth.
+I exclude the spell from marriage to the first birth because of data issues.
+In NFHS-1 and NFHS-2 the only information on marriage is the age at marriage, and 
+all first spell durations are therefore imputed.
 In NFHS-3 about a third of respondent did not provide complete information on the
-timing of marriage and therefore had the length of their first spell imputed using only
-the age at marriage.
-The result of the imputation is that large numbers of women end up with very short,
-i.e., less than nine months, or negative spells and that comparison of spell duration over 
-time is subject to an excessive amount of noise.
-}
-The spells all begin nine months after the previous birth 
-because that is the earliest we should expect to observe a new birth, which also means 
-that they capture the interpregnancy interval for pregnancies carried to term.
+timing of marriage and had the length of their first spell imputed using the age at 
+marriage.
+The imputation results in large numbers of women with spells that are either negative or 
+less than nine months and makes a comparison of spell duration over time subject to an 
+excessive amount of noise.
+
+The spells all begin nine months after the previous birth, which is the earliest we should 
+expect to observe a new birth.
 A spell continues until either a child is born or censoring occurs.
@@
 
-I group spells into four periods based on the year of the previous birth:
-1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The periods follow the main changes in the availability and legality of 
-prenatal sex determination discussed in the Introduction.
-The allocation into periods is determined by when conception and therefore 
-decisions on sex selection can begin, even if we do not observe
-any births until nine months later.
-
-The allocation into periods means that some spells cover two periods.
-A couple may, for example, have their first child in 1984, but not have their second 
-child until 1986.
-That couple's second spell will be in the 1972--1984 period, even though 
-most of the interval falls in the 1985--1994 period.
-Hence, prenatal sex determination was likely available when some
-children from spells that began in the 1972--1984 period were conceived,
-which could result in evidence of sex-selective abortions even for this
-period.
-Similarly, a spell that started in the 1985--1994 period may have been partly 
-or mostly under the PDNT act.
-The effect is a downward bias in the differences between the periods.
-
 \subsection{Explanatory Variables}
@@
 I divide the explanatory variables into two groups.
-The first group consists of variables expected to affect the shape of the hazard function
-(the $\mathbf{Z}$ variables): 
+The first group consists of characteristics that the prior literature finds affect 
+spacing choice and the use of sex selection:
 mother's education, sex composition of previous children, and area of residence.
-I chose these variables because the prior literature shows that they affect 
-spacing choices and the likelihood of using sex selection.%
+The second group of variables consists of those expected to have an approximately 
+proportional effect on the hazard.
+These include the age of the mother at the beginning of the spell, whether the household 
+owns any land, and whether the household belongs to a scheduled tribe or caste.
+
+Women with different education levels have different hazard profiles, although the size 
+and direction of the effect vary across areas and time 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
+Furthermore, the use of sex selection increases with education, either because of the 
+associated lower fertility or because higher income enables them to access and
+afford prenatal sex determination
+\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.%
 \footnote{
-Increasing the number of variables interacted with the baseline hazard would
-further lower the risk of bias but at the cost of requiring more data to 
-precisely estimate.
-}
-
-The first variable that is likely to affect the hazard rate in a non-proportional manner
-is education.
-First, there is evidence, even in the absence of sex selection, that women with
-different education levels have different hazard profiles, although the size and direction
-of the effect vary across areas and time 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
-Second, as discussed above, the use of sex selection increases with socioeconomic 
-status, especially education, and the use of sex selection is unlikely to be the
-same throughout a spell, which means that education cannot enter proportionally 
-\citep{retherford03b,jha06,Portner2015b}.
-One potential reason for the correlation between education and sex selection is that
-increasing education of mothers correlates closely with lower fertility 
-\citep{schultz97}.
-This lower fertility leads, in turn, to a higher likelihood of using sex selection
-\citep{das_gupta97,Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
-\footnote{
-In principle, it is possible that part of the higher likelihood is driven by a stronger
-son preference, independently of desired fertility.
-There is, however, evidence that higher education women have shown a decline in
-son preference \citep{bhat03,pande07}.
-}
-Another reason is that having more education is closely associated with higher income and 
-wealth, which makes it easier to access illegal services such as prenatal sex 
-determination.
-It is not possible to separate these two effects here.
-
+It is also possible that the effect is driven by a stronger son preference, although 
+higher education women have shown declining son preference \citep{bhat03,pande07}.
+}
 I divide women into three groups based on education attainment: no
 education, one to seven years of education, and eight and more years of education.
-The models are estimated separately for each education level to reduce
-the potential problem of including other variables as proportional.%
-\footnote{
-Fathers' education has two opposite predicted effects: the associated higher income
-should increase fertility and therefore lower the pressure to use sex selection, but
-the higher income also makes the use of sex selection cheaper.
-In practice, fathers' education had little effect on the hazards and the use of 
-sex-selective abortions, and I, therefore, do not include it.
-}
-
-As discussed, the sex composition of previous children affects both the timing
-of births and the use of sex-selective abortions 
+The models are estimated separately for each education level to reduce the potential 
+problem of including other variables as proportional.
+
+The sex composition of previous children affects both the timing of births and the use of 
+sex-selective abortions 
 \citep{retherford03b,jha06,Bhalotra2008,abrevaya09,Portner2015b,Kumar2016,Soest2018}.
@@
 possible combinations for the specific spell, ignoring the ordering of births.
-As an example, for the third spell, three groups are used: Two boys,
-one girl and one boy, and two girls.
-It is, in principle, possible to estimate the model taking into account
-the ordering of children, but this would further lower the power of the
-test, by adding one additional group for the third spell and four
-additional groups for the fourth spell.
-
-Whether a woman lives in an urban or rural area affect both her fertility level and
-her access to sex selection \citep{retherford03b,jha06,Portner2015b}.
-Area of residence is a dummy variable for the household living in
-an urban area.
-The cost of children is higher in urban areas than in rural areas, and 
-there is easier access to prenatal sex determination in urban areas.
-Both factors are likely to lead to higher use of sex-selective abortions
-in urban than in rural areas.
-
-The second group of variables consists of those expected to have an 
-approximately proportional effect on the hazard.
-These include
-the age of the mother at the beginning of the spell, 
-whether the household owns any land, 
-and whether the household belongs to a scheduled tribe or caste.
+Finally, urban women have both lower fertility and, presumably, better access to
+sex selection, both of which lead to higher use of sex-selective abortions than in 
+rural areas \citep{retherford03b,jha06,Portner2015b}.
+Area of residence is a dummy variable for the household living in an urban area.
+
+% %
+% \footnote{
+% Fathers' education has two opposite predicted effects: the associated higher income
+% should increase fertility and therefore lower the pressure to use sex selection, but
+% the higher income also makes the use of sex selection cheaper.
+% In practice, fathers' education had little effect on the hazards and the use of 
+% sex-selective abortions, and I, therefore, do not include it.
+% }
 
@@
 Appendix Table \ref{tab:des_stat1} presents descriptive statistics for
-the spells by education level and period they began.
-There is a substantial number of censored observations.
-As an example, for highly educated women who had their first child in the 2005--2016
-period, more than 40\% did not have their second child by the time of the survey.
-Censoring becomes even more important for the third and fourth
-spells, with around 70\% of the observations censored.
-The level of censoring also increases with parity and time,
-which reflects a combination of factors: timing of the surveys
-relative to the periods of interest, later beginning of childbearing, 
-falling fertility, and the increase in spell lengths from 
+the spells by education level and period.
+The level of censoring increases with parity and time, as we should expect with later 
+childbearing, falling fertility, and the hypothesized increases in birth intervals from 
 sex-selective abortions.
@@
 The share of urban women in the sample has fallen slightly over the
-periods, even though India's population has become progressively more urbanized.
-The most likely explanation is that the age of marriage has increased
-faster in urban areas than in rural areas.
+periods, even though India's population has become more urbanized, presumably because the 
+age of marriage has increased faster in urban than in rural areas.
 Hence, there are relatively more urban women, but fewer show up in the
@@
 
-The population has become substantially better educated over time.
-Women with no education constituted almost 60\% 
-in the first period, but less than twenty percent in the last period.
-Correspondingly, in the first period just over twenty percent had eight or more 
-years of education, whereas in the last period more than 60\% did.
-These changes are an underestimate of the increase in female
-education overall because many of the younger women with more education
-have not yet married than therefore are not in the sample.%
+Finally, the population has become substantially better educated over time.
+In the first period, almost 60\% of women had no education, and only twenty percent had
+eight or more years, while in the last period the reverse was the case.
+These changes underestimate the increase in education because many of the younger women 
+with more education are not yet married and therefore not in the sample.%
 \footnote{
 Women with eight or more years of education accounted for 65.9\% of
-unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4.
-See \citet[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
-and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
-for more information.
- }
+unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4
+\citep{International-Institute-for-Population-Sciences-IIPS2007,International-Institute-for-Population-Sciences-IIPS2017}.
+}
+
+% \citep[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
+% and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
+% for more information.
 
@@
 sex of that child. 
-This section assesses the degree of recall error across the surveys and discusses methods
-to address it.
+This Appendix section assesses the degree of recall error across the surveys and discusses 
+methods to address it.
 
@@
 from the natural sex ratio.
+The natural sex ratio is approximately 105 boys to 100 girls or
+51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
 Prenatal sex determination techniques did not become widely available until the mid-1980s, 

### 2019-03-28 paper/sex_selection_spacing-ver2.tex
Edits to shorten paper

@@
 % [How to read tables]
+I estimate the model for each spell/education/period subsample, the results of which I use 
+to predict average birth spacing, sex ratio, and the probability of having a birth in that 
+spell.
 Figures \ref{fig:bootstrap_low}, \ref{fig:bootstrap_med}, and  \ref{fig:bootstrap_high} 
-show predicted average birth intervals, sex ratios, and probabilities of having
-a birth by decade, spell, and sex composition for the three education levels separated 
-by the area of residence.%
+show these predicted outcomes for the three education levels separated by the area of 
+residence.%
 \footnote{
-For legibility, none of the graphs show standard errors.
-Instead, the standard errors, together with the graphed values, are shown in Appendix 
-Tables 
+For legibility, none of the graphs show standard errors, which, together with the graphed 
+values, are shown in Appendix Tables 
 \ref{tab:avg_sex_ratio_low}, 
@@
 \ref{tab:avg_sex_ratio_high}.
-The standard errors are based on bootstrapping for all three measures,
-where the model is repeatedly estimated using resampling with replacement.
-}
-For each subsample, I first estimate the model described in Section 
-\ref{sec:strategy} and then use the estimated coefficients to predict 
-average birth spacing, sex ratio, and the probability of having a birth in that spell.
-
-I calculate the expected average duration as follows.
-For each woman in a sample, I calculate her probability of giving birth for each period
-in the spell and use these probabilities as weights to calculated her expected duration 
-for that spell.
-I then take the average of these expected durations using her probability of having a
-birth by the end of the spell as weights.
-
-The predicted sex ratio is the weighted average over the women in the sample's 
-individual predicted sex ratios, using the individual probabilities of having
-given birth by the end of the spell as weights.
-Each woman's predicted sex ratio is the weighted average of the predicted
-percentage of boys over each period in the spell calculated using equation 
-(\ref{eq:probability_son}) and the probability of giving birth in each period 
-as weights.%
-\footnote{
-Imagine a spell has two periods and that the estimated percentages of boys for a
-woman are 54\% and 66\% and that the likelihood of having a birth is 20\% and 40\%.
-The likelihood of having a birth is the change in the survival curve; 
-in other words, there is a 40\% chance that she will not have given birth by the end of 
-this spell.
-This woman's percentage of boys is then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
-}
+}
+The predicted probability of having a birth by the end of the spell (parity progression
+probability) is $1-S_{T}$, that is the likelihood of having had a birth by 96 months after 
+the beginning of the spell.
+To find the expected average duration I first calculate for each woman the probability 
+of giving birth in each time $t$, which I use as weights to calculated her expected duration. 
+I then average the individual expected durations across women using the parity progression
+probabilities as weights.
+
 The predicted sex ratio captures the percent boys that will have been born to women 
 in the sample when childbearing for that spell is over.
+A woman's predicted sex ratio is the weighted average of the predicted percentage boys 
+over each $t$ in the spell, calculated using equation (\ref{eq:probability_son}), using
+the probability of giving birth at time $t$ as weights.%
+\footnote{
+If T=2 with the estimated percent boys 54\% and 66\% and the likelihoods of giving 
+birth 20\% and 40\%, the percent boys is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
+}
+The predicted sex ratio shown is the weighted average of the individual predicted sex 
+ratios, using the parity progression probabilities as weights.
+For comparison, the graphs also show the natural sex ratio, approximately 51.2\% 
+\citep{ben-porath76b,jacobsen99,Portner2015b}.
 
@@
 
-The previous literature finds that women with no education are the least likely to use 
-sex selection, which suggests that they would instead follow a traditional strategy to son 
-preference with higher fertility and shorter birth intervals the fewer sons they have.
-This pattern is supported by Figure \ref{fig:bootstrap_low}, but with significant
-differences across spells.
-Most of the women without education live in rural areas, and I, therefore, focus on rural 
-women.%
-\footnote{
-Only between ten and twenty percent of the surveyed women without education live in urban 
-areas, and this proportion has been decreasing over time.
-}
-
-The initial high fertility of women with no education shows clearly in the results.
-In the 1972--1984 period almost all women had at least four children, irrespectively
-of the sex composition of the children.
-Over time, however, the likelihood of having a third or fourth child decreased for women 
-with at least one son, and more so the more sons they had.
-Hence, fertility has begun to fall even among women with no education, as long as they 
-have at least one son.
-Two additional fertility trends stand out.
-First, virtually all women still have a second birth, whether the first child was
-a boy or a girl.
-Second, for women with only girls, there is almost no reduction in the probability of 
-having a birth across time and spells.
-
-Birth intervals have increased in length over time, although the increases are not
-uniform over spells and sex compositions of prior children.
-The smallest increases have been for the second spell, with most increases between one
-and two months.
-Interestingly, son preference appears to have little effect on spacing for the second
-spell, with very small, albeit statistically significant, differences in birth intervals 
-depending on the sex of the first child.
-This small difference is in line with the high likelihood of having a second child.
-The second spell also shows convergence in birth intervals, especially in the urban
-areas where the predicted average duration is now the same whether the first child was
-a boy or a girl.
-
-Son preference in birth intervals shows most clearly for the fourth spell.
-Despite the increase in spacing even for those with three girls, the increases in 
-spacing have been substantially stronger for families with at least one son.
-As for fertility, the more sons a family has, the more significant are the differences.
-
-Despite the prior literature finding that women with higher education are the primary user 
-of sex selection, the predicted sex ratios for those with only girls are statistically 
-significantly higher than the natural ratio for the third and fourth spell.
+Based on the literature, I expect women with no education to follow a traditional approach
+to son preference with high fertility, shorter birth intervals with fewer son, and  
+minimal use of sex selection.
+This pattern is supported by Figure \ref{fig:bootstrap_low}, but with crucial differences 
+across spells.
+Since only between ten and twenty percent of women without education live in urban areas, 
+I focus on rural women.
+
+Birth intervals have increased in length over time and are longer the higher the spell.
+The smallest increases in birth intervals have been for the second spell, with most 
+increases only between one and two months.
+Interestingly, son preference has little effect on spacing for the second spell, with 
+very small, albeit statistically significant, differences in birth intervals depending on 
+the sex of the first child and virtually all women still have a second birth.
+
+Son preference in birth intervals shows up more clearly for the third, and, particularly, 
+the fourth spell.
+For the fourth spell, the difference across sex compositions are more pronounced over time, 
+and the likelihood of having a child has decreased for women with at least one son.
+Women with only girls, show almost no reduction in the probability of having a birth 
+across time and spells.
+Despite the expectation that this group of women does not use sex selection, the predicted 
+sex ratios for those with only girls are statistically significantly higher than the 
+natural ratio for the third and fourth spell.
 Hence, it is possible that at least part of the increased  birth intervals for those
@@
 
-Figure \ref{fig:bootstrap_med} shows that women with one to seven years of education 
-follow a fertility pattern broadly similar to those with no education.
-As expected, fertility is lower than for women with no education, but there is still a
-strong son preference in the parity progression behavior.
-Except for the second spell, the likelihood of having a birth by the end of the spell is
-substantially lower if there has been at least one male birth than if there are only girls.
-Despite this, the probability of a birth in the third and fourth spells has also been 
-falling for those with only girls.
-Having a second birth is still close to universal, although in urban areas it is down to
-just over 85 percent for those with a son as their first child.
-
-The spacing between births has increased over the four decades, and the increases are 
-larger than for women without any education across all spells.
+Figure \ref{fig:bootstrap_med} shows that for women with one to seven years of education
+birth intervals have increased over the four decades, and the increases are larger than 
+for women without any education.
 Contrary to women without education, however, there has not been an increased divergence 
-in birth intervals lengths across sex compositions for the third and fourth spells.
-On the contrary, for the third spell, the most substantial increases in birth intervals are for 
-women with two daughters and no sons, with an increase of about seven months across the 
-four decades.
-The result is that for urban women the standard spacing pattern reversed, so the longest 
-predicted spacing is now for those with only girls, while for rural women the predicted 
-average birth intervals are now almost identical across sex compositions of prior children.
+in birth intervals across sex compositions for the third and fourth spells.
+Instead, for the third spell, the most substantial increases in birth intervals 
+are for women with two daughters and no sons, with an increase of about seven months.
+The result is that the standard spacing pattern reversed for urban women, so the longest 
+predicted spacing is now for those with only girls, while rural women's predicted average 
+birth intervals are now almost identical across sex compositions of prior children.
 For the fourth spell, the increases in spacing for women with only girls have kept pace
@@
 \footnote{
-Because of the low number of observations, the pattern for the fourth spell is noisier 
-for urban women.
+The pattern for the urban fourth spell is noisier because a low number of observations.
 }
@@
 The substantial increases in spacing for women with only girls is not evidence of lower
-son preference as the changes in the predicted sex ratios show.
-For both the third and fourth spell the predicted sex ratio in both urban and rural
-areas is statistically significantly above the natural sex ratio at between 55.5 and 57.7 
-percent boys.
-The elevated sex ratios strongly suggest that sex selection is driving the increases in
-birth intervals for women with only girls and that without sex selection we would 
-instead have observed a diverging pattern in birth intervals across sex composition as
-for women without education.
+son preference as shown by the changes in the predicted sex ratios and the parity 
+progression behavior.
+For both the third and fourth spell the predicted sex ratios in urban and rural areas are
+statistically significantly above the natural sex ratio at between 55.5\% and 57.7\% boys.
+The elevated sex ratios strongly suggest that sex selection, possibly precipitated by
+declining fertility, drove the increases in birth intervals for women with only girls and 
+that without sex selection we would instead have observed a diverging pattern in birth 
+intervals across sex composition similar to what we saw for women without education.
 
@@
 
-Women with eight or more years of education are those expected to have the lowest 
-fertility and the highest use of sex selection based on the prior literature.
-Figure \ref{fig:bootstrap_high} shows that this group not only have lower fertility than 
-the two previous groups; fertility is also falling rapidly over time.
-Of women with one birth, the probability of having a second birth when the first-born
-is a son is only around 70 percent for urban women and around 80 percent for rural women,
-and for those with a first-born daughter, it is around 80 percent for urban women and 90 
-percent for rural women.
-
-The rapid decline in fertility for the most educated women is even more clear for the 
-third and fourth spells when the woman has given birth to at least one son.
-At the beginning of the sample, urban women with at least one boy had a close to 75
-percent likelihood of having a birth, but that has fallen to only around 25 percent.
-Son preference still shows clearly in the parity progression probabilities for 
-women without a son, with the declines for the third and fourth spells substantially
-slower for both urban and rural women without a son than for those with at least one son.
-The falling fertility means that relatively few women make it to the fourth spell,
-which, therefore, has more noise than the other spells.
-
-Average birth spacing for the second spell is almost identically across sex compositions 
-for both urban and rural women and increased by around five months for rural women and
-by almost ten months for urban women over the four decades.
-These similarities hide, however, what would have been a standard son preference spacing 
-pattern with significantly shorter spacing after a first-born girl than after a first-born 
-boy if there had not been a substantial amount of sex selection.
-For both of the last two periods, the predicted sex ratio for women with a daughter as 
-their first-born child is above 55 percent for both urban and rural areas.
+Women with eight or more years of education are expected to have the lowest fertility and 
+the highest use of sex selection, and we should, therefore, see the most substantial 
+effects on spacing.
+At first blush, it appears from Figure \ref{fig:bootstrap_high} that the second spell 
+spacing pattern looks remarkably similar to the two other education groups with little 
+difference in average birth spacing across sex composition.
+This similarity hides, however, a much faster decline in the likelihood of having a second 
+birth, substantial increases in spacing, and predicted sex ratios for women with a 
+first-born daughter above 55 percent for both urban and rural areas for the last two 
+periods.
+Hence, where it not for a substantial amount of sex selection brought on by falling
+fertility we would now have seen a standard son preference spacing pattern with 
+significantly shorter spacing after a first-born girl than after a first-born boy.
 
 The tremendous impact that sex selection can have on birth spacing is illustrated 
-particularly vividly by the changes over time for the third spell, which led to a complete 
-reversal of the standard spacing pattern.
+particularly vividly by the changes for the third spell, where we see a complete reversal 
+of the standard spacing pattern.
 In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
@@
 In urban areas, the predicted average birth interval for a woman with only daughters 
-increased by almost a full year from 26.8 to 38.3 months.
-What is more, this increase is likely an underestimate.
-The sex ratios for the 1972-84 period are substantially higher than the natural sex ratio 
-despite sex selection not being widely available until around 1985.
-If this early, elevated sex ratio is because of recall error, it means that the actual birth 
-intervals would have been substantially shorter than the ones predicted here and the
-increase over time larger.
-
-The reversal pattern also shows for the fourth spell for urban women, although not for
-rural women.
-An important caveat is that because of the falling fertility relatively few women make
-it to the fourth spell, and even if they do, we often do not observe a birth by the time 
-of the survey.
-Of the 11,886 women across urban and rural areas observed for the fourth spell for the 
-2005-2016 period more than 70 percent did not have a birth at the time of the survey.
-Even though the censoring is less prevalent for the earlier periods, this is countered by
-those samples being substantially smaller.
-Despite this, the pattern for the fourth spell is similar to that of the third spell.
-
-The predicted sex ratios at the end of the spells show that this reversal in spacing 
-patterns is not the result of a declining son preference but instead corresponds to a 
-substantially more male-biased sex ratio as the use of sex selection spread.
-For urban women, the predicted sex ratio with only girls is consistently above 60\% boys 
-for the third and fourth spells.
-For rural women, the predicted sex ratios are lower than for urban women but still 
-substantial and statistically significant at close to 60\%.
-
-When trying to understand the strength of son preference, it is interesting that the sex 
-ratio is also statistically significantly different from the natural rate in the case 
-where women already have one son for the third and fourth spells.
-Again, the sex ratio in the presence of one son for the third and fourth spells are higher 
-in urban areas than rural areas, although the difference is less than for women with only 
-girls.
-Hence, it is possible that women are still willing to use sex selection even after giving 
-birth to one, although this behavior may also be in response to either experienced
-or expected mortality of the first son born.
-This result is different from prior studies using NFHS data.
-The NFHS-4 sample is substantially larger than the three prior surveys.
-Hence, it is possible that the effect has been there all along, but we did not have the 
-power to detect it.
+increased by almost a full year from 26.8 to 38.3 months, while it ``only'' increased
+by around six months with only sons.
+Consistent with the rapidly falling fertility leading to increased use of sex selection, 
+women with no sons have around 65\% and 60\% boys in urban and rural areas, respectively.
+
+The reversal pattern also shows up for the fourth spell for urban women, but not for rural 
+women.
+An important caveat is that the falling fertility means that few women make it to the 
+fourth spell, and even if they do, we are unlikely to observe a birth by the survey making 
+the estimates noisy.
+Son preference, however, still shows clearly in the parity progression probabilities for 
+women without a son, with the declines for the third and fourth spells substantially
+slower for both urban and rural women without a son than for those with at least one son.
+
+% When trying to understand the strength of son preference, it is interesting that the sex 
+% ratio is also statistically significantly different from the natural rate in the case 
+% where women already have one son for the third and fourth spells.
+% Again, the sex ratio in the presence of one son for the third and fourth spells are higher 
+% in urban areas than rural areas, although the difference is less than for women with only 
+% girls.
+% Hence, it is possible that women are still willing to use sex selection even after giving 
+% birth to one, although this behavior may also be in response to either experienced
+% or expected mortality of the first son born.
+% This result is different from prior studies using NFHS data.
+% The NFHS-4 sample is substantially larger than the three prior surveys.
+% Hence, it is possible that the effect has been there all along, but we did not have the 
+% power to detect it.
 
@@
 
-The results above show consistent increases in average spacing across the board.
 Average spacing is a convenient way to understand the overall changes in behavior but may 
 hide important differences in the distribution of spacing.
-Specifically, whether these increases in average spacing come from fewer births after 
-very short intervals, because of even longer spacing from births with already long 
-spacing, or a general increase in spacing have important implications for what effects the
-increases in average spacing are likely to have and how to interpret the motivation for
-the changes.
-On one hand, if there still are many births that occur after very short intervals, the 
-increase in average spacing is unlikely to have a substantial impact on health outcomes
-since the literature on birth spacing and child health suggests that an interpregnancy 
-interval of fewer than 18 months is associated with a higher risk of adverse health 
-outcomes and mortality \citep{Conde-Agudelo2012}.
-On the other hand, we may see a reduction in early observed births and more long spells if 
-families with fewer sons are both more likely to have a very early pregnancy and to 
-continue through pregnancies and sex-selective abortions until they conceive a son.%
-\footnote{
-It is unclear what the optimal response in the timing of pregnancies to the availability 
-of sex selection should be.
-The expected birth intervals become longer with the use of sex selection, which may be 
-costly for parents leading them to try to conceive even earlier than previously.
-Conversely, if parents know that short birth intervals are detrimental to the next child's
-health, and that, with sex selection, the next child is likely a boy, it might make sense to 
-wait longer before conceiving.
-}
-
-This section, therefore, provides more detail on how spacing is distributed within a spell 
-and across sex compositions using a graphical approach.
+Specifically, whether increases in average spacing come from fewer births after very short 
+intervals, from even longer spacing of births with already long spacing, or from a general 
+increase in spacing have important implications for what effects the increases in average 
+spacing are likely to have and how to interpret the motivation for the changes.
+This section, therefore, examines how spacing is distributed within spells.
 I show survival curves conditional on predicted parity progression rather than standard 
-survival curves. 
-The advantage of this approach is that it is possible to directly compare the distribution 
-of spacing to next birth across groups, independently of differences in how likely the 
-next birth is.
-Because the conditional survival curves are independent of the likelihood of parity 
-progression, they all begin at 100\% and end at 0\%.
-
-Instead of averaging across the entire sample, I calculate the conditional survival curves 
-for an average woman using the method detailed in Section \ref{sec:strategy}.
-For each combination of education and spell, I use values based on the average age at the 
-start of the spell.
-Furthermore, I use the majority categories for the categorical explanatory  variables, 
-which means no ownership of land and not in a scheduled caste or tribe.
+survival curves, which allows direct comparisons of the distribution of spacing across 
+groups, independent of differences in parity progression probabilities.
+
+% Because the conditional survival curves are independent of the likelihood of parity 
+% progression, they all begin at 100\% and end at 0\%.
+
+% On one hand, if there still are many births that occur after very short intervals, the 
+% increase in average spacing is unlikely to have a substantial impact on health outcomes
+% since the literature on birth spacing and child health suggests that an interpregnancy 
+% interval of fewer than 18 months is associated with a higher risk of adverse health 
+% outcomes and mortality \citep{Conde-Agudelo2012}.
+% On the other hand, we may see a reduction in early observed births and more long spells if 
+% families with fewer sons are both more likely to have a very early pregnancy and to 
+% continue through pregnancies and sex-selective abortions until they conceive a son.%
+% \footnote{
+% It is unclear what the optimal response in the timing of pregnancies to the availability 
+% of sex selection should be.
+% The expected birth intervals become longer with the use of sex selection, which may be 
+% costly for parents leading them to try to conceive even earlier than previously.
+% Conversely, if parents know that short birth intervals are detrimental to the next child's
+% health, and that, with sex selection, the next child is likely a boy, it might make sense to 
+% wait longer before conceiving.
+% }
+
+Instead of averaging across the entire sample, for each spell/education combination I 
+calculate the conditional survival curves using average values and the majority of
+categories, which means no ownership of land and not in a scheduled caste or tribe.
 The characteristics used do not change across the four decades to ensure that composition 
-effects do not drive any changes.
-To complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
-\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
-percentiles durations with bootstrapped standard errors based on averages across all women 
-in each subsample as for the results above.
-
+effects do not drive the changes.
 In the interest of brevity, I discuss only two subsamples.
@@
 more years of education.
-The Appendix shows conditional survival curves for all groups and decades.
+The Appendix shows conditional survival curves for all groups and decades and to 
+complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
+\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
+percentiles durations with bootstrapped standard errors based on averages across all women.
 

### 2019-03-29 paper/sex_selection_spacing-ver2.tex
Finish shortening paper to < 8,000 words

@@
 Average spacing is a convenient way to understand the overall changes in behavior but may 
-hide important differences in the distribution of spacing.
+hide crucial differences in the distribution of spacing.
 Specifically, whether increases in average spacing come from fewer births after very short 
-intervals, from even longer spacing of births with already long spacing, or from a general 
+intervals, from an even longer spacing of births with already long spacing, or a general 
 increase in spacing have important implications for what effects the increases in average 
 spacing are likely to have and how to interpret the motivation for the changes.
-This section, therefore, examines how spacing is distributed within spells.
+This section, therefore, examines the distribution of spacing within spells.
 I show survival curves conditional on predicted parity progression rather than standard 
@@
 
-Figure \ref{fig:pps_low} shows the distribution of birth within a spell for women with no 
-education.
-For the second spell, what is most interesting is that there is almost no difference 
-between those with a first-born boy and those with a first-born girl.
-For the 1972--1984 period the two conditional survival curves only begin to diverge 
-at around 18 months (corresponding to 27 months after the first birth took place), and
-at that point close to 50 percent of the women have already had their second child.
-With a nine-month pregnancy, this means that almost 50 percent of the children born are
-born within the interpregnancy interval associated with a higher risk of adverse health
-outcomes and mortality, and, somewhat surprisingly, that there do not appear to be any 
-particular disadvantage for the child born after a girl than after a boy.%
-\footnote{
-Note that this does not imply that the first-born girl is not in a more adverse position
-than a first-born boy when the second child arrives, just that this is not directly
-related to a short birth interval.
-}
-The difference in spacing after a first-born girl and a first-born boy remains almost 
-the same across the four decades.
-Furthermore, the proportion with very short spacing remains almost the same.
-
-For the third spell, the son preference driven short spacing is evident throughout the
-distribution and becomes more pronounced over the four decades.
-Families with two girls are especially likely to have a birth early with 25 percent
-having a child within 12 months of the beginning of the spell (21 months after the second 
-birth).
-That number is only slightly smaller four decades later. 
-The fourth spell shows changes in the distribution that appear to be more pronounced
-than for the third spell, although these results are based on fewer observed births.
-For families with three girls, 75 percent have had their fourth child within 36 months 
-after the beginning of the spell, but this occurs more than a year later for families
-with two or more boys.
+The most striking results for women with no education are that, in both periods, close to 
+50\% had their second child by 18 months and that there are minimal differences in the 
+probability of very short intervals whether the first-born was a boy or a girl.
+Hence, almost 50\% of second-borns are born within an interval associated with a higher 
+risk of adverse outcomes, and, surprisingly, there do not appear to be any particular 
+disadvantage for the child born after a girl than after a boy.
+There is more evidence of son-preference driven short spacing for the third and fourth
+spells, but a large number of women still have very short intervals whether they have boys 
+or girls already.
+For both spells, the difference in average spacing mainly come from the upper end of the
+distribution; for example, the 75th percentile show a twelve months difference between 
+families with three girls and families with two or more boys.
 
@@
 
-The distribution of spacing for the second spell is almost indistinguishable 
-between urban women with eight or more years of education and rural women 
-with no education for the 1972--1984 period, as shown in Figure \ref{fig:pps_high}.
-The small differences point to these two very different groups of women behaving similarly
-in response to son preference in a situation where there was little access to
-prenatal sex determination or little incentive to use it early even for those 
-who might have had access.
-However, whereas the no education group shows almost no change across the four decades for 
-the second spell, the high education women show an upward shift and a relatively even
-distribution of births within the spell for both women with a first-born son and women
-with a first-born girl.
-The result is that the spacing patterns are close to identical after first-born 
-girls and after first-born boys until after approximately 80 percent have had their 
-second child, although as mentioned above, this is driven in large part by the significant
-use of sex selection among women with a first-born girl.
-
-For the third spell, the 1972--1984 period shows a close to standard pattern throughout, 
-although, as mentioned above, the sex ratios for women without girls was substantially 
-higher than the natural sex ratio either because of recall error or early use of 
-sex selection.
-The correlation between the increased use of sex selection and the reversal of the 
-standard spacing pattern show up clearly in the 2005--2016 period for the third spell with 
-spacing to the third child consistently longer with two girls than with either two boys 
-or one boy and one girl throughout the entire spell.
+Another remarkable result is the similarity in the lower end of the distribution of
+spacing for the second spell between urban women with eight or more years of education and 
+rural women with no education for the 1972--1984 period with little difference across
+sex composition and close to 50\% with very short birth intervals.
+However, the high education women show an upward shift over time and spacing patterns that
+are close to identical after first-born girls and after first-born boys until after 
+approximately 80 percent have had their second child, driven by the significant use of sex 
+selection among women with a first-born girl.
+
+The sex selection induced reversal of the standard spacing pattern shows up clearly in the 
+2005--2016 period for the third and fourth spells, with spacing to the next child 
+consistently longer with only girls than with the other sex compositions.
 This pattern is most consistent with early and continued use of sex selection, rather 
 than a general reduction in the likelihood of very short birth intervals.
-It also means that the previously born girls can expect more time without a younger sibling,
-which may reduce the sibling competition for resources.
-
-There is an even more pronounced rightward and upward shift for spacing after only
-girls in the fourth spell for the first years of the spell.%
-\footnote{
-The caveat is that there are few births to base the results on,
-especially for women with two or more sons.
-} 
-Furthermore, the differences are substantial across most of the distribution.
-Twelve months after the beginning of the spell there is a more than ten 
-percentage points difference in the conditional survival curves for only girls
-and only boys.
-Both of the spells, therefore, show changes in the distribution of births that is in line
-with extensive use of sex selection among families with no or one son.
+It also means that the previously born girls can expect more time without a younger 
+sibling, which may reduce the sibling competition for resources.
+
+% Furthermore, the differences are substantial across most of the distribution.
+% Twelve months after the beginning of the spell there is a more than ten 
+% percentage points difference in the conditional survival curves for only girls
+% and only boys.
+% Both of the spells, therefore, show changes in the distribution of births that is in line
+% with extensive use of sex selection among families with no or one son.
 
@@
 To understand how regional differences in son preference, fertility, and use of sex 
-selection affect birth spacing, I divide India into four broad regions based on the degree 
-of son preference and initial fertility levels.
-The focus is on the most educated women since they are the primary users of sex selection.
-The four regions are based on \citet{retherford03b}, although expanded to include all 
-states in the surveys.
-Table \ref{tab:regions} shows the four regions and the states that they contain.%
+selection affect birth spacing, I divide India into four regions, shown in Table 
+\ref{tab:regions}, based on the degree  of son preference and initial fertility 
+levels \citep{retherford03b}.%
 \footnote{
-The geographical names do not entirely reflect the geography of India, and mainly
-serves as mnemonic short-hands.
-}
-The state names are those in existence at the time of the NFHS-1 data collection.
-States formed later are allocated as close as possible to the original state.
+The state names are those used in NFHS-1, with states formed later allocated as close as 
+possible to the original state.
+}
 The ``West'' contains states with a high degree of son preference and use of sex selection.
@@
 \input{../tables/desc_region.tex}
+
+I focus on the most educated women as the primary users of sex selection.
+Figures \ref{fig:bootstrap_high_r1}, \ref{fig:bootstrap_high_r2}, 
+\ref{fig:bootstrap_high_r3}, and \ref{fig:bootstrap_high_r4} show the predicted average 
+birth intervals, sex ratios, and parity progression probabilities for the ``West,''
+``North,'' ``East,'' and ``South,'' respectively.
+The ``East'' and ``South'' do not include the fourth spell because of small sample sizes 
+and very noisy results.
 
@@
 
-Figure \ref{fig:bootstrap_high_r1} shows the predicted average birth intervals, sex 
-ratios, and likelihoods of having a child by the end of the spell over time for the three 
-spells in the ``West.''
-What most stands out is how close to the national estimates the ``West'' estimates are.
-The predicted second spell average birth spacing is similar across families with a girl
-or a boy, and the average spacing substantially higher in the absence of boys than when
-there is at least one boy for the third spell.
-The main difference is that the very high predicted sex ratios reflect the expected higher 
-use of sex selection.
-For the second spell, the predicted sex ratios are around 60 percent for both urban and
-rural women, and for the third spell it is around 70 percent for urban women and 
-consistently above 60 percent for rural women.
-This higher use of sex selection, in turn, translates into longer average spacing.
-Furthermore, fertility has fallen faster than the national trend, especially for women
-with one or more sons.
+Despite the idea that the ``West'' and ``North'' differ in fertility and likelihood of 
+using sex selection, the differences are surprisingly small, at least for urban areas.
+Furthermore, both are close to the national averages presented above, with the main 
+difference that the very high sex ratios reflect a higher use of sex selection, 
+presumably as a result of fertility falling faster than the national trend.
+The predicted sex ratios in urban areas are around 60\% for the second spell and
+around 70\% for the third spell.
+This higher use of sex selection, in turn, translates into the reversal of standard
+spacing pattern.
+
+The two regions are further apart for the rural areas.
+In the ``West'' the rural areas show only slightly lower use of sex selection and 
+therefore a less pronounced reversal in spacing patterns than in the urban areas.
+In the rural ``North,'' fertility is substantially higher, and the use of sex selection 
+subsequently lower, but the sex ratio is still substantially above normal at close to 60 
+percent for the latest decade.
 
@@
 
-Figure \ref{fig:bootstrap_high_r2} shows the same outcomes for the ``North'' region. 
-Despite the idea that the ``North'' has high fertility and lower 
-likelihood of sex selection the differences to the ``West'' region are surprisingly small,
-at least in the urban areas.
-Fertility is, indeed, higher than in the ``West'' region, but the declines in the 
-probability of parity progression have been relatively rapid and mirror the national one.
-The use of sex selection is also close to the ``West,'' and there is the same reversal of
-spacing pattern as there.
-The rural areas of the ``North'' are a slightly different story.
-Fertility is substantially higher, and the use of sex selection much lower than in the
-rural areas of the ``West.'' 
-That said, there still is clear evidence that the sex ratio is substantially above normal
-at close to 60 percent for the latest decade.
-
 % \begin{figure}[htpb]
@@
 
-The results for the ``East'' region of India are shown in Figure 
-\ref{fig:bootstrap_high_r3}, although it does not include the fourth spell results because 
-the sample size is smaller for this region and the fourth spell results very noisy.
-Despite the ``South'' region generally considered to be the low fertility region, the
-reduction in fertility has been even faster in the ``East.''
-For the last decade, only half of the urban women with a first-born son are predicted to 
-have a second child by the end of the spell, which means almost nine years after the first 
-birth.
-The probability is only slightly higher for those in urban areas with a first-born 
-daughter and still less than 70 percent.
-Not surprisingly, the probabilities are higher in rural areas, but still below the 
-national pattern.
-Similarly, conditionally on having a second child, the probabilities of having a third
-child are low, even in the absence of sons.
-In urban areas, a woman with two girls has only around a 40 percent likelihood of 
-having a third child.
-
-What stands out, however, is the rapid increase in the lengths of birth intervals,
-especially for the second spell.
-In both urban and rural areas, the predicted average birth intervals have gone up by
-more than a year across the four decades, and that is independent of whether the first-born
-was a boy or a girl.
+What stands out for the ``East'' is the rapid increase in the lengths of birth intervals,
+especially for the second spell, where the increases have been more
+than a year, independently of whether the first-born was a boy or a girl.
 The increases in birth intervals are slightly smaller for the third spell but still 
 substantial.
-Although the spacing pattern is consistent with some son preference, with the average
-spacing slightly shorter in the absence of boys than when at least one boy is present,
-there is little evidence of sex-selective abortions.
-The sex ratios after a first-born daughter are slightly elevated but much lower than 
-the prior two regions.
-There is more evidence for the third spell, where the sex ratio is close to 60 percent
-in the last period for urban women and the last two for rural women, but recall that 
-there is a much smaller likelihood of even making it to the third spell for this region
-than the other or the national average.
+Although the spacing pattern is consistent with some son preference, there is little 
+evidence of sex-selective abortions.
+Furthermore, despite the ``South'' is generally considered the low fertility region, 
+the reduction in fertility has been even faster in the ``East.''
+For example, only half of the urban women with a first-born son are now predicted to 
+have a second child by the end of the spell.
 
@@
 
-The final region is the ``South,'' shown in Figure \ref{fig:bootstrap_high_r4}.
-This region is historically thought to have the lowest degree of son preference of the
-regions of India.
-As for the ``East,'' I do not show the fourth spell results because of the small sample 
-size and the associated noisy estimates.
-Judging from the second spell progression rate and the associated spacing pattern, it
-does, initially, appear that there is little son preference in this region.
-The likelihood of having a second birth is relatively high at around 80 to 90 percent
-and is close to independent of the sex of the first birth in both urban and rural areas.
-The predicted average spacing also show no sign of son preference, and the predicted
-sex ratios are close to the natural rate.
-The average birth spacing started high relative to the other regions, and with little 
-change in fertility and no significant use of sex selection, it has increased only 
-slightly over time.
-
-Despite the second spell's apparent lack of son preference behavior, for the third spell 
-in urban areas the average birth interval has increased substantially for those with only 
-girls relative to those with a boy and a girl, corresponding to
-a predicted sex ratio close to 60 percent with only girls. 
+The ``South'' is historically thought to have the lowest degree of son preference,
+which has initial support from the second spell's progression rates, spacing pattern, and 
+sex ratios.
+However, for the third spell in urban areas, the average birth interval has increased 
+substantially, and the predicted sex ratio is close to 60\% for those with only girls. 
 The signs of the use of sex selection also show up for rural women with no sons.
-Furthermore, over the four decades, the likelihood of having a third birth has decreased
-much less than for either a boy and a girl or two boys.%
+Furthermore, the likelihood of having a third birth has decreased much less with no sons 
+than the other sex compositions.%
 \footnote{
-The relatively high parity progression for women without son does raise the question of
-whether ``daughter avoidance'' is behind the fertility behavior in this region as
+The relatively high parity progression for women without son runs counter to what we
+should expect if ``daughter avoidance'' is behind the fertility behavior as
 suggested by \citet{DiamondSmith2008}.
 }
-The differences in parity progression and the sex ratios suggest that despite originally
-having less son preference, the ``South'' now appears to have longer average spacing 
-in the absence of sons and the higher sex ratio associated with the use of sex selection.
+Hence, the ``South'' now also shows the longer average spacing in the absence of sons and 
+the higher sex ratio associated with the use of sex selection.
 
@@
 I introduce an empirical method that simultaneously accounts for spacing between births 
-and the potential use of sex selection. 
-I apply the method to over four decades of data from India's NFHS.
-
-Three major, interrelated trends over the four decades emerge from the data.
-First, fertility has declined for all groups, as shown by the parity progression
-probabilities, with a larger decline the more educated the woman.
-Across all groups, the likelihood of having an additional child in each spell depends 
-strongly on the number of sons, with women with none or only one son having
-the highest probability of a birth.
-Second, there has been a general increase in the length of average birth 
-intervals for all education groups.
-The increase in the average birth interval is larger the higher the spell and the higher the 
-education group.
-Finally, as shown by the increasing sex ratios for women with no or only one son there
-has been a substantial increase in the use of sex selection over time.
-As for fertility and birth intervals, this increase is larger the higher the spell and
+and the potential use of sex selection, and apply the method to four decades of data 
+from India's NFHS.
+
+Three major, interrelated trends emerge.
+First, 
+the length of average birth intervals have increased for all education groups, and
+the increases are larger the higher the spell and the higher the education group.
+Second, fertility has declined for all groups with larger declines the more educated the 
+woman.
+Across all groups, the likelihood of having an additional child depends strongly on the 
+number of sons, with women with none or only one son having the highest probabilities.
+Finally, as shown by the increasing sex ratios for women with no or only one son, there
+has been a substantial increase in the use of sex selection.
+As for fertility and birth intervals, the increases are larger the higher the spell and
 with higher education.
 
-The results show two very different approaches to son preference with significant
-impacts on spacing patterns.
+The results show two very different spacing patterns in response to son preference.
 At one extreme, rural women without education mostly follow the standard pattern of 
-shorter spacing when a woman does not have the desired number of sons.
+shorter spacing in the absence of sons.
 The strength of this pattern does, however, depend critically on spell number.
 For the second spell, although the average interval after a first-born girl is shorter
-than the average interval after a first-born boy, the difference is small.
+than after a first-born boy, the difference is small.
 The differences in spacing are larger for the third spell and largest for the fourth.
-For the fourth spell, the divergence in intervals across sex compositions has 
-increased over time, with the largest increases in average intervals for women with 
-two or three boys.
-There has also been an increase in average spacing for women with only girls, and there
-is some limited evidence of biased sex ratios, which suggests that this increases in
-spacing follow from the use of sex selection.
+For the fourth spell, the divergence in intervals has increased over time; the largest 
+increases are for women with two or three boys, but there has also been an increase for 
+women with only girls, likely because of an emerging use of sex selection.
 
 At the other extreme, urban women with eight or more years of education have experienced 
-an almost complete reversal of the traditional spacing patterns as a result of falling
+an almost complete reversal of the traditional spacing patterns as the result of falling
 fertility and the associated extensive use of sex selection.
 Women with either no or one son now have substantially longer spacing than if they have 
-two or more sons, rather than having the next birth sooner as they mostly did before sex 
-selection became available.
+two or more sons.
 As shown by the increasingly significant deviations in the sex ratio from the natural sex 
@@
 
-Despite the differences in average spacing across sex compositions of prior children,
-the picture of how son preference affects spacing is more complicated than excepted.
-First, for the second spell, the differences in birth intervals for the first 25 percent of 
-births are negligible across sex compositions, despite that these birth intervals are
-clearly within the durations considered the most likely to generate adverse outcomes.
-Furthermore, there is little difference in this spacing patterns across education.
-Hence, most of the divergence in spacing patterns across sex compositions arise from
-longer spells, which are likely to have less negative impacts on children and the mother.
-Second, one of the side-effects of the extensive use of sex selection for third and fourth 
-spells is that only-girls families are much less likely to have a short, i.e., less than 
-18 months, interpregnancy interval, which may reduce the sibling competition for resources.
+The picture of how son preference affects spacing is, however, more complicated than 
+excepted.
+First, the differences in birth intervals for the first 50 percent of second births are 
+negligible across sex compositions, despite these births clearly within the 
+durations most likely to generate adverse outcomes.
+Hence, most of the divergence in spacing patterns arise from longer spells.
+Second, a side-effect of the extensive use of sex selection for third and fourth 
+spells is that only-girls families are much less likely to have a very short birth 
+interval, which may reduce the sibling competition for resources.
 
@@
 behavior, spacing patterns, and the degree of son preference.
-The regional results confirm this, although differences are less apparent than one would
-expect given the prior research on regional differences.
-The ``North'' and the ``West'' regions have relatively similar spacing patterns, likely
-precipitated by rapidly declining fertility and substantial use of sex selection.
-The exception is that the rural areas of the ``North'' still have higher fertility and
-consequently less use of sex selection and have, therefore, not yet experienced the
-same reversal of spacing patterns.
-Even the ``South,'' which is otherwise considered the area with the least son preference,
-has seen a substantial increase in the use of sex selection and the associated changes 
+Although the regional results confirm this, the differences are less apparent than one would
+expect given the prior research.
+The ``North'' and the ``West'' regions have relatively similar spacing patterns, both
+the result of rapidly falling fertility and substantial use of sex selection.
+The exception is that the rural ``North'' still have higher fertility and
+consequently less use of sex selection.
+Even the ``South,'' otherwise considered to have the least son preference, has 
+seen a substantial increase in the use of sex selection and associated changes 
 in the spacing patterns.
-Even though the ``South'' is often mentioned as the low-fertility region of India, 
-fertility has declined fastest in the ``East'' region, although this does not appear to 
-have translated into the use of sex selection.
-
-The results here lead to a set of broader questions that future research should address.
-First, what is behind the substantial increases in spacing even for women who are unlikely 
-to use sex selection, and, related, why does spacing appear to increase with declining 
+Finally, fertility has declined fastest in the ``East'' region, but this has not 
+translated into the use of sex selection.
+
+The results here lead to three questions that future research should address.
+First, what is behind the substantial increases in spacing even for women unlikely to use 
+sex selection, and, related, why does spacing appear to increase with declining 
 parity progression probabilities?
-The distributional results provide an initial indication that most of the increases in 
-average birth intervals come from the upper end of the birth intervals rather a general
-increase across the distribution.
-It is, however, unclear why we are seeing relatively more very long birth intervals over
-time, and the longer average spacing seems to run counter to a general reduction in the 
-length of women's reproductive spans found in earlier research \citep{Padmadas2004}.
-Understanding whether the longer average spacing is by choice at the beginning of the 
-spell, because of unplanned pregnancies, or because of changes in economic circumstances 
-that allow families to have an additional child later has important implications for both 
-policy design and outcomes for mother and children.
+The distributional results suggest that most of the increases in average birth intervals 
+come from the upper end rather than from a general increase across the distribution.
+The longer average spacing and the relatively higher number of very long birth intervals 
+seem to run counter to a general reduction in the length of women's reproductive spans 
+found in earlier research \citep{Padmadas2004}.
+Understanding whether the longer average spacing is by choice, because of unplanned 
+pregnancies, or because of changes in economic circumstances that allow families to have 
+an additional child later has important implications for both policy design and outcomes 
+for mother and children.
 
@@
 \citep{Lin2014,Hu2015}.
-Furthermore, there is some evidence that sample selection can make it appear that girls 
-are healthier, even though the underlying cause is a combination of sex selection and 
-higher mortality together with recall error \citep{Portner2018a}. 
+Furthermore, sample selection can make it appear that girls are healthier, even though the 
+underlying cause is a combination of sex selection and higher mortality together with 
+recall error \citep{Portner2018a}. 
 Understanding what role these factors play in better health for girls is especially 
@@
 between births would cause a stronger disruption in labor market participation.
-On the other hand, it may further lower desired fertility, and that may, everything else 
-equal, lead to higher use of sex selection.
+On the other hand, it may further lower desired fertility, which, everything else equal, 
+may lead to higher use of sex selection.
 Understanding the trade-off between long-term benefits from improvements in women's labor 

### 2019-03-31 paper/sex_selection_spacing-ver2.tex
Minor edits

@@
 intervals increased substantially over the last four decades, with the most significant
-increase among women most likely to use sex selection.
+increases among women most likely to use sex selection.
 Specifically, well-educated women with no boys now have significantly longer birth
@@
 }
-Hence, longer birth intervals in the absence of sons, which previously would be taken to 
-indicate a lower son preference, now may instead arise because couples with a strong son 
-preference use sex selection.
+Hence, longer birth intervals in the absence of sons, which previously would be taken as 
+an indicator of lower son preference, may now instead arise because couples with a strong 
+son preference use sex selection.
 
@@
 I introduce an empirical method that directly incorporates the effects of 
-sex-selective abortions on the duration between births 
+sex-selective abortions on birth intervals
 \emph{and} 
@@
 prenatal sex determination has lead to dramatic increases in the males-to-females ratio at 
-birth in India from sex selection over the last three decades
+birth over the last three decades
 \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,Bongaarts2013,Portner2015b,Jayachandran2017}.
@@
 have on spacing.
-I address three questions to remedy this shortcoming.
+I address three questions to remedy this shortcoming in the literature.
 
@@
 spacing behavior, it tells us little about how these changes came about.
-For example, the motivation behind an increase in average spacing is different if it
-comes mainly from parents trying to avoid very short birth intervals, which, as mentioned,
-are associated with worse child outcomes, or from continued use of sex selection to
-ensure a son.
+For example, the motivations that lead to an increase in average spacing are different if 
+the increase comes mainly from parents trying to avoid very short birth intervals or from 
+continued use of sex selection to ensure a son.
 
@@
 sons---have seen the largest increases in birth intervals.
-As a result, well-educated women now show a complete reversal of the traditional spacing 
+As a result, well-educated women now show a reversal of the traditional spacing 
 pattern, with the longest birth intervals for women with no sons.
@@
 little evidence of the use of sex selection.
-Fourth, the traditional pattern of longer average spacing with sons appear to arise from 
+Finally, the traditional pattern of longer average spacing with sons appear to arise from 
 more very long intervals, rather than from fewer very short birth intervals; across 
@@
 models with a single exit, the birth of a child.
-There are two problems with this approach in this setting.
+There are two problems with the standard approach in this setting.
 First, and most importantly, the introduction of sex selection means that the sex of the 
@@
 Specifically, whether increases in average spacing come from fewer births after very short 
-intervals, from an even longer spacing of births with already long spacing, or a general 
-increase in spacing have important implications for what effects the increases in average 
-spacing are likely to have and how to interpret the motivation for the changes.
+intervals, from an even longer spacing of births with already long spacing, or from a 
+general increase in spacing have important implications for what effects the increases in 
+average spacing are likely to have and how to interpret the motivation for the changes.
 This section, therefore, examines the distribution of spacing within spells.
-I show survival curves conditional on predicted parity progression rather than standard 
-survival curves, which allows direct comparisons of the distribution of spacing across 
-groups, independent of differences in parity progression probabilities.
+I show survival curves conditional on predicted parity progression, which allows direct 
+comparisons of the distribution of spacing across groups independent of differences in 
+parity progression probabilities, rather than standard survival curves.
 
@@
 evidence of sex-selective abortions.
-Furthermore, despite the ``South'' is generally considered the low fertility region, 
+Furthermore, despite the ``South'' generally considered the low fertility region, 
 the reduction in fertility has been even faster in the ``East.''

### 2019-03-31 response/response-demography-1.tex
Minor edits

@@
 
-My one concern with the rewrite is that the review of the relevant literature might have 
-gotten a little too detailed, making the Introduction too long. 
-If there are parts that might fit better somewhere else or that needs to be shortened or
-removed, I am open to suggestions.
-
 \item Second, a conceptual framework or theoretical argument is needed to
@@
 
-I have substantially expanded the discussion of the choice of non-proportionality 
-variables in the ``Explanatory Variables'' section (and added a footnote to that effect 
-in the ``Estimation Strategy'' section).
-The discussion now covers education, sex composition, and area of residence in more detail.
+I have expanded the discussion of the choice of non-proportionality variables in the 
+``Explanatory Variables'' section (and added a footnote to that effect in the ``Estimation 
+Strategy'' section).
+The discussion now covers education, sex composition, and area of residence in more detail,
+although given that I need to keep the paper below 8,000 words there is a limit to how
+detailed the discussion is.
 If there is a more appropriate place for this discussion, I am happy to move it.
@@
 Since I have no way of separating these two possible explanations with the available
-data and set up, I have not included this discussion in the paper itself. 
+data and set up and because of the need to keep the paper short, I have not included this 
+discussion in the paper itself. 
 One possible approach would be to include this as a question for future research in the
@@
 I have dropped the analysis of first spells.
-Removing the first spell also helps to keep the paper from getting excessively long.
+Removing the first spell also helps to keep the paper within the word limit.
 Because of the large number of imputed observations for the first spell, I have also
@@
 for only the most educated women, who are the main users of sex selection.
+This new section substitutes for the removed section on how sex ratios change within 
+a spell.
 
@@
 
-Compression in the original manuscript was only for the first birth interval, and I no longer 
-cover that because of the data issues discussed above.
+Compression in the original manuscript was only for the first birth interval, and I no 
+longer cover that because of the data issues discussed above.
 I do, however, agree that this is an important question, even if I cannot directly

### 2019-04-01 paper/sex_selection_spacing-ver2-demography.tex
Shorten version for Demography

@@
 \author{}
+
 % \author{Claus C P\"ortner\\
@@
 }
-Longer birth intervals in the absence of sons, which previously would be taken to indicate 
-a lower son preference, now may arise precisely because a sufficiently strong son 
-preference makes couples use sex selection.
-
-In this paper, I examine how birth spacing in India has changed over time and across 
+Hence, longer birth intervals in the absence of sons, which previously would be taken as 
+an indicator of lower son preference, may now instead arise because couples with a strong 
+son preference use sex selection.
+
+Here, I examine how birth spacing in India has changed over time and across 
 groups with the introduction of sex selection.
-I introduce and apply an empirical method that directly incorporates the effects of 
-sex-selective abortions on the duration between births 
+I introduce an empirical method that directly incorporates the effects of 
+sex-selective abortions on birth intervals
 \emph{and} 
@@
 }
-Moreover, mortality risk is higher for females than males for most ages groups, and
-there has been an almost continuous increase in India's overall ratio of males to females 
-over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
-
-% [What do we know about use of sex selection?]
-Over the last three decades, India has seen dramatic increases in the males-to-females 
-ratio at birth as access to prenatal sex determination expanded 
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012,Portner2015b}.
-Simultaneously, fertility has declined substantially, to the point where it is now at, or 
-even below, replacement in some areas 
+Furthermore, fertility has declined substantially, to the point where it is now at, or even 
+below, replacement in some areas 
 \citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-This decline in fertility, combined with a continued strong preference for sons, has 
-intensified the pressure to use sex selection 
-\citep{das_gupta97,Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
-\footnote{
-In some instances, however, the fertility decline appears to have created a stronger 
-aversion to daughters rather than a stronger preference for son \citep{DiamondSmith2008}.
-}
-The strongest predictor of the use of sex selection is the sex composition of previous 
-children; for families without a son, the higher the parity, the higher is the probability
-of having a son as the next birth \citep{retherford03b,jha06,abrevaya09,Portner2015b}.
-The use of sex selection also increases with socioeconomic status, especially 
-education, and is more prevalent in cities than in rural areas, both possibly because 
-of lower desired fertility \citep{retherford03b,jha06,Portner2015b}.
+The combination of falling fertility, strong son preference, and expanding access to 
+prenatal sex determination has lead to dramatic increases in the males-to-females ratio at 
+birth over the last three decades
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,Bongaarts2013,Portner2015b,Jayachandran2017}.
 
@@
 Despite the increasing use of sex selection, the critical impacts of spacing on outcomes 
-for both mother and children, and the extensive use of spacing to measure son 
-preference in the literature, there has so far been no examination of what effect access 
-to sex selection has had on spacing.
-The overall hypothesis is that spacing patterns significantly changed as prenatal sex 
-determination became available.
-Specifically, I address three questions.
-
-First, how did average birth intervals change over time for different groups and how are 
-those changes related to the likely use of sex selection?
-The underlying hypothesis is that in the absence of sex selection son preference leads to 
-shorter spacing the fewer boys a family has for a given parity, whereas son preference 
-increases the spacing the fewer boys a family has when prenatal sex selection is available.
-I still expect parents to \emph{try} to conceive earlier after the birth of a girl than 
-after a boy, but the abortions will increase the duration between births, and may even 
-lead to longer average spacing after the birth of girls than after boys.
+for both mother and children, and the extensive use of spacing to measure son preference, 
+there has so far been no systematic examination of what effect access to sex selection 
+have on spacing.
+I address three questions to remedy this shortcoming in the literature.
+
+First, how did average birth intervals change over time for different groups and how do 
+these changes relate to the use of sex selection?
+The hypothesis is that in the absence of sex selection son preference leads to shorter 
+spacing the fewer boys a family has, whereas son preference increases spacing the fewer 
+boys a family has when prenatal sex selection is available, possibly to the point where
+we observe a reversal of the standard spacing pattern.
 Families with son preference who---for one reason or another---do not use prenatal sex 
-selection may continue to have shorter birth spacing.
+selection likely continue to have shorter birth spacing.
 Based on the prior literature on sex selection, I focus on how birth intervals have
@@
 Second, have the shapes of the survival curves changed?
-Very short birth intervals are, as mentioned, associated with worse health outcomes and 
-increased mortality risk \citep{Conde-Agudelo2012}.
-Hence, understanding how the distribution of birth intervals changes can help us understand to 
-what extent we can expect improvements in health outcomes.
-We should, for example, expect different impacts on the distribution of birth intervals
-depending on whether parents change their spacing behavior based on an increasing 
-concern for child health or from a strong son preference leading to continued pregnancies
-until they conceive a son.
-
-Finally, how are the changes in birth intervals with increasing access to sex selection 
-distributed geographically?
-Given the size and cultural differences within India, it is unlikely that the increasing 
+Although examining average birth intervals helps us understand the overall changes in 
+spacing behavior, it tells us little about how these changes came about.
+For example, the motivations that lead to an increase in average spacing are different if 
+the increase comes mainly from parents trying to avoid very short birth intervals or from 
+continued use of sex selection to ensure a son.
+
+Finally, how are the changes in birth intervals distributed geographically?
+Given the cultural differences within India, it is unlikely that the increasing 
 access to sex selection will have had the same effects throughout \citep{retherford03b}.
@@
 
-Direct information on the use of sex selection is not available, but it is possible to 
-compare different periods as a proxy since there have been substantial changes in access 
-and legality of prenatal sex determination in India.
-Abortion has been legal in India since 1971 and still is.
-The first reports of sex determination appeared around 1982--83 
-\citep{Sudha1999,bhat06,Grover2006}.
-The number of clinics quickly increased, and knowledge about sex selection became 
-widespread after a senior government official's wife aborted a fetus that turned out to be 
-male \citep[p.\ 598]{Sudha1999}.
-In 1994, the Central Government passed the Prenatal Diagnostic Techniques (PNDT) Act, 
-making determining and communicating the sex of a fetus illegal.%
-\footnote{
-Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
-The number of convictions has been low.
-It took until January 2008 for the first state, Haryana, to reach five convictions.
-Hence, private clinics operate with little risk of legal action \citep{Sudha1999}.
-Furthermore, there is little evidence that bans like this significantly
-affect sex ratios \citep{Das-Gupta2016}.
-}
-
-Based on these developments, I split the four decades into four periods.
-The first period covers until prenatal sex determination became widely available, 
-1972--1984.
-The second period saw (mostly) unrestricted access to sex selection, 1985--1994.
-Although, as reviewed above, there is evidence that there has been a substantial 
-increase in the use of sex selection, some researchers argue that we might be close to or 
-have already passed a turning-point in the use of sex selection 
-\citep{Das_Gupta2009,Diamond-Smith2015}.
-I, therefore, split the period from the implementation of the PNDT Act until the last 
-survey into two, 1995--2004, and 2005--2016.
-
 There are four main results.
-First, there has been a general increase in the intervals between births for all education 
-groups over the four decades covered by the data.
+First, the intervals between births have increased for all education groups over the four 
+decades.
 These increases are larger the higher the parity and the higher the education 
 level.
-Second, those women who are most likely to use sex selection, well-educated women with no
-sons, have seen the largest increases in birth intervals.
-As a result, we now have a complete reversal of the traditional spacing pattern for
-well-educated women, and instead, observe the longest birth intervals for women with no 
-sons.
+Second, those women who are most likely to use sex selection---well-educated women with no
+sons---have seen the largest increases in birth intervals.
+As a result, well-educated women now show a reversal of the traditional spacing 
+pattern, with the longest birth intervals for women with no sons.
 Third, women who are least likely to use sex selection, those with no education in
@@
 little evidence of the use of sex selection.
-In other words, these women adhere to a strategy where they achieve a son through higher 
-fertility rather than the use of sex selection.
-Fourth, the traditional pattern of longer average spacing when women have one or more sons
-appear to arise from more very long intervals, rather than from fewer very short birth 
-intervals; across education groups there appear to be little difference in the likelihood
-of having a very short birth interval across sex compositions, especially for lower
-parities.
+Finally, the traditional pattern of longer average spacing with sons appear to arise from 
+more very long intervals, rather than from fewer very short birth intervals; across 
+education groups, there appears to be little difference in the likelihood of having a very 
+short birth interval across sex compositions, especially for lower parities.
 
@@
 
-The results above show consistent increases in average spacing across the board.
 Average spacing is a convenient way to understand the overall changes in behavior but may 
-hide important differences in the distribution of spacing.
-Specifically, whether these increases in average spacing come from fewer births after 
-very short intervals, because of even longer spacing from births with already long 
-spacing, or a general increase in spacing have important implications for what effects the
-increases in average spacing are likely to have and how to interpret the motivation for
-the changes.
-On one hand, if there still are many births that occur after very short intervals, the 
-increase in average spacing is unlikely to have a substantial impact on health outcomes
-since the literature on birth spacing and child health suggests that an interpregnancy 
-interval of fewer than 18 months is associated with a higher risk of adverse health 
-outcomes and mortality \citep{Conde-Agudelo2012}.
-On the other hand, we may see a reduction in early observed births and more long spells if 
-families with fewer sons are both more likely to have a very early pregnancy and to 
-continue through pregnancies and sex-selective abortions until they conceive a son.%
-\footnote{
-It is unclear what the optimal response in the timing of pregnancies to the availability 
-of sex selection should be.
-The expected birth intervals become longer with the use of sex selection, which may be 
-costly for parents leading them to try to conceive even earlier than previously.
-Conversely, if parents know that short birth intervals are detrimental to the next child's
-health, and that, with sex selection, the next child is likely a boy, it might make sense to 
-wait longer before conceiving.
-}
-
-This section, therefore, provides more detail on how spacing is distributed within a spell 
-and across sex compositions using a graphical approach.
-I show survival curves conditional on predicted parity progression rather than standard 
-survival curves. 
-The advantage of this approach is that it is possible to directly compare the distribution 
-of spacing to next birth across groups, independently of differences in how likely the 
-next birth is.
-Because the conditional survival curves are independent of the likelihood of parity 
-progression, they all begin at 100\% and end at 0\%.
-
-Instead of averaging across the entire sample, I calculate the conditional survival curves 
-for an average woman using the method detailed in Section \ref{sec:strategy}.
-For each combination of education and spell, I use values based on the average age at the 
-start of the spell.
-Furthermore, I use the majority categories for the categorical explanatory  variables, 
-which means no ownership of land and not in a scheduled caste or tribe.
+hide crucial differences in the distribution of spacing.
+Specifically, whether increases in average spacing come from fewer births after very short 
+intervals, from an even longer spacing of births with already long spacing, or from a 
+general increase in spacing have important implications for what effects the increases in 
+average spacing are likely to have and how to interpret the motivation for the changes.
+This section, therefore, examines the distribution of spacing within spells.
+I show survival curves conditional on predicted parity progression, which allows direct 
+comparisons of the distribution of spacing across groups independent of differences in 
+parity progression probabilities, rather than standard survival curves.
+
+% Because the conditional survival curves are independent of the likelihood of parity 
+% progression, they all begin at 100\% and end at 0\%.
+
+% On one hand, if there still are many births that occur after very short intervals, the 
+% increase in average spacing is unlikely to have a substantial impact on health outcomes
+% since the literature on birth spacing and child health suggests that an interpregnancy 
+% interval of fewer than 18 months is associated with a higher risk of adverse health 
+% outcomes and mortality \citep{Conde-Agudelo2012}.
+% On the other hand, we may see a reduction in early observed births and more long spells if 
+% families with fewer sons are both more likely to have a very early pregnancy and to 
+% continue through pregnancies and sex-selective abortions until they conceive a son.%
+% \footnote{
+% It is unclear what the optimal response in the timing of pregnancies to the availability 
+% of sex selection should be.
+% The expected birth intervals become longer with the use of sex selection, which may be 
+% costly for parents leading them to try to conceive even earlier than previously.
+% Conversely, if parents know that short birth intervals are detrimental to the next child's
+% health, and that, with sex selection, the next child is likely a boy, it might make sense to 
+% wait longer before conceiving.
+% }
+
+Instead of averaging across the entire sample, for each spell/education combination I 
+calculate the conditional survival curves using average values and the majority of
+categories, which means no ownership of land and not in a scheduled caste or tribe.
 The characteristics used do not change across the four decades to ensure that composition 
-effects do not drive any changes.
-To complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
-\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
-percentiles durations with bootstrapped standard errors based on averages across all women 
-in each subsample as for the results above.
-
+effects do not drive the changes.
 In the interest of brevity, I discuss only two subsamples.
@@
 
-The results for the ``East'' region of India are shown in Figure 
-\ref{fig:bootstrap_high_r3}, although it does not include the fourth spell results because 
-the sample size is smaller for this region and the fourth spell results very noisy.
-Despite the ``South'' region generally considered to be the low fertility region, the
-reduction in fertility has been even faster in the ``East.''
-For the last decade, only half of the urban women with a first-born son are predicted to 
-have a second child by the end of the spell, which means almost nine years after the first 
-birth.
-The probability is only slightly higher for those in urban areas with a first-born 
-daughter and still less than 70 percent.
-Not surprisingly, the probabilities are higher in rural areas, but still below the 
-national pattern.
-Similarly, conditionally on having a second child, the probabilities of having a third
-child are low, even in the absence of sons.
-In urban areas, a woman with two girls has only around a 40 percent likelihood of 
-having a third child.
-
-What stands out, however, is the rapid increase in the lengths of birth intervals,
-especially for the second spell.
-In both urban and rural areas, the predicted average birth intervals have gone up by
-more than a year across the four decades, and that is independent of whether the first-born
-was a boy or a girl.
+What stands out for the ``East'' is the rapid increase in the lengths of birth intervals,
+especially for the second spell, where the increases have been more
+than a year, independently of whether the first-born was a boy or a girl.
 The increases in birth intervals are slightly smaller for the third spell but still 
 substantial.
-Although the spacing pattern is consistent with some son preference, with the average
-spacing slightly shorter in the absence of boys than when at least one boy is present,
-there is little evidence of sex-selective abortions.
-The sex ratios after a first-born daughter are slightly elevated but much lower than 
-the prior two regions.
-There is more evidence for the third spell, where the sex ratio is close to 60 percent
-in the last period for urban women and the last two for rural women, but recall that 
-there is a much smaller likelihood of even making it to the third spell for this region
-than the other or the national average.
+Although the spacing pattern is consistent with some son preference, there is little 
+evidence of sex-selective abortions.
+Furthermore, despite the ``South'' generally considered the low fertility region, 
+the reduction in fertility has been even faster in the ``East.''
+For example, only half of the urban women with a first-born son are now predicted to 
+have a second child by the end of the spell.
 

### 2019-10-18 paper/conceptual_framework.tex
Initial commit of conceptual framework
Just the comments from the editors at the moment

Second, the paper lacks a conceptual framework to organize (and motivate) the analysis. Following on the comments of one reviewer, one suggestion would be to focus on the role of women’s education, with a more thorough description of the context of changing education in India over the last half century and clearly lay out a framework for the mechanisms through which birth spacing is affected by educational expansion.

### 2019-10-22 paper/conceptual_framework.tex
Add notes from paper

@@
-Second, the paper lacks a conceptual framework to organize (and motivate) the analysis.
-Following on the comments of one reviewer, one suggestion would be to focus on the role of women’s education, with a more thorough description of the context of changing education in India over the last half century and clearly lay out a framework for the mechanisms through which birth spacing is affected by educational expansion.
+Second, the paper lacks a conceptual framework to organize (and
+motivate) the analysis. Following on the comments of one reviewer, one
+suggestion would be to focus on the role of women’s education, with a
+more thorough description of the context of changing education in India
+over the last half century and clearly lay out a framework for the
+mechanisms through which birth spacing is affected by educational
+expansion.
+
+\section{Conceptual Framework}
+
+% How education has changed in India
+
+son preference and investment in education
+
+Finally, the population has become substantially better educated over time.
+In the first period, almost 60\% of women had no education, and only twenty percent had
+eight or more years, while in the last period the reverse was the case.
+These changes underestimate the increase in education because many of the younger women 
+with more education are not yet married and therefore not in the sample.%
+\footnote{
+Women with eight or more years of education accounted for 65.9\% of
+unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4
+\citep{International-Institute-for-Population-Sciences-IIPS2007,International-Institute-for-Population-Sciences-IIPS2017}.
+}
+
+% \citep[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
+% and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
+% for more information.
+
+% Age at marriage increased over time across all three education groups.
+% The most substantial increase was for women without any education, where
+% the average went from below 16 years of age to 18.5.
+% The smallest change is for the most educated women where the average age
+% at marriage went up by less than a year---from 19.6 to 20.4---across the 
+% four periods.
+
+% How does educational expansion affect birth spacing
+
+Women with different education levels have different hazard profiles, although the size 
+and direction of the effect vary across areas and time 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
+Furthermore, the use of sex selection increases with education, either because of the 
+associated lower fertility or because higher income enables them to access and
+afford prenatal sex determination
+\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.%
+\footnote{
+It is also possible that the effect is driven by a stronger son preference, although 
+higher education women have shown declining son preference \citep{bhat03,pande07}.
+}
+
+The sex composition of previous children affects both the timing of births and the use of 
+sex-selective abortions 
+\citep{retherford03b,jha06,Bhalotra2008,abrevaya09,Portner2015b,Kumar2016,Soest2018}.
+I capture sex composition with dummy variables for the
+possible combinations for the specific spell, ignoring the ordering of births.
+Finally, urban women have both lower fertility and, presumably, better access to
+sex selection, both of which lead to higher use of sex-selective abortions than in 
+rural areas \citep{retherford03b,jha06,Portner2015b}.
+
+The longer average spacing and the relatively higher number of very long birth intervals 
+seem to run counter to a general reduction in the length of women's reproductive spans 
+found in earlier research \citep{Padmadas2004}.
+
+Differential stopping behavior is widespread, with an additional child more likely the
+fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
+\footnote{
+Other countries show a similar pattern
+\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
+}
+
+For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
+a boy as the last-born child, significantly increase the duration to next birth,
+\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
+\footnote{
+Ethnic Indians in South Africa also show a longer duration after the birth of a 
+son than after a daughter \citep{Gangadharan2003}.
+}
+Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
+absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
+\citep{Rossi2015}.
+
+Finally, we know less about what determines spacing behavior in developing countries than 
+in developed countries, and with declining fertility and increasing numbers of women 
+entering the labor force, understanding how couples make timing decisions is necessary 
+for the design of suitable policies \citep{Portner2018}.%
+\footnote{
+It is clear that birth spacing does respond to policies in both developed and 
+developing countries \citep{Pettersson-Lidbom2009,Todd2012,Meckel2015,Ghosh2018}.
+}
+Even the effects of access to contraceptive and declining fertility on spacing are unclear.
+On the one hand, access to contraceptives allows women to avoid too short spacing between 
+birth.
+On the other hand, increased reliability of access and effectiveness of contraceptives can 
+lead to shorter intervals between births if women used to have longer spacing to avoid
+having too many children by accident \citep{Keyfitz1971,Heckman1976}.
+These two counteracting effects may explain why better-educated women have shorter spacing 
+than less educated women in some instances but not in others and why finding statistically 
+significant effects of contraception use on birth spacing is difficult 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.%
+\footnote{
+In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
+access to family planning \citep{Rahman1993}.
+Other evidence, however, points to families ability to time births, even in the absence
+of modern contraceptives \citep{Jayachandran2011,Alam2018}.
+}

### 2019-11-07 paper/conceptual_framework.tex
Add drafts of biological, contraception, and quality discussions

@@
 
-\section{Conceptual Framework}
+\section{Birth Spacing and Education: Mechanisms and Findings}
 
-% How education has changed in India
+This section provides a conceptual framework for understanding what determines spacing 
+between births.
+Since education is closely linked to the use of sex selection, I focus especially on the
+the effects of education on spacing.
+I first discuss generic spacing decisions frameworks, and then turn to how son preference
+and sex selection fits into the decisions on spacing.
 
-son preference and investment in education
+In the simplest possible dynamic model of fertility there are no real spacing decisions.
+Assume that parents derive benefits from having their children around, rather than from 
+the births themselves, that spacing of children by itself does impact parental utility, 
+and that the parents perfectly control when to have children. 
+In this set up, the optimal decision is then to have the children as early as possible 
+\citep{Newman1988}.
+The simplest model clearly does not fit the observed spacing patterns, but the question 
+is why.
 
-Finally, the population has become substantially better educated over time.
-In the first period, almost 60\% of women had no education, and only twenty percent had
-eight or more years, while in the last period the reverse was the case.
-These changes underestimate the increase in education because many of the younger women 
-with more education are not yet married and therefore not in the sample.%
+First, parents do not perfectly control the timing of births, but instead decide on their
+levels of sexual activity and contraceptive effort, which, in turn, affect their likelihood 
+of conceiving.
+
+The decisions on sexual activity and contraceptive effort are constrained by biological 
+factors, such as fecundity, age, and health of the mother, and the knowledge of and access
+to contraceptive technology.
+There is evidence from ``natural fertility'' populations that increasing number of 
+children is associated with shorter spacing and that birth intervals increase 
+with parity \citep{Henry1961,Leridon1977}.
+
+Biological factors are unlikely to be an important factor in differences in spacing over 
+time or across education levels in India for the period covered.
+Outside of direct famine conditions, there is little evidence that women's health and 
+nutritional status substantially affects spacing \citep{Huffman1987,John1987,lindstrom99}.
+The Maharashtra drought occurred in 1970-1973 and, therefore, would only affect the first
+year or two of the data.
+Hence, although there are still differences in individual fecundity across women, it is
+unlikely that we should see systematic differences across education groups and over time
+in the data because of health status.
+Furthermore, I only examine spacing up to parity fourth, and age of the mother is,
+therefore, unlikely to be a concern when it comes to fecundity, when though better 
+educated women are, on average, older when they marry.
+
+TK contraception
+
+There is no clear relationship between contraception use and birth spacing in the 
+literature, and better-educated women have shorter spacing than less educated women in 
+some instances but not in others 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+
+Even the effects of access to contraceptive and declining fertility on spacing are unclear.
+On the one hand, access to contraceptives allows women to avoid too short spacing between 
+birth.
+On the other hand, increased reliability of access and effectiveness of contraceptives can 
+lead to shorter intervals between births if women used to have longer spacing to avoid
+having too many children by accident \citep{Keyfitz1971,Heckman1976}.
+%
 \footnote{
-Women with eight or more years of education accounted for 65.9\% of
-unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4
-\citep{International-Institute-for-Population-Sciences-IIPS2007,International-Institute-for-Population-Sciences-IIPS2017}.
+In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
+access to family planning \citep{Rahman1993}.
+Other evidence, however, points to families ability to time births, even in the absence
+of modern contraceptives \citep{Jayachandran2011,Alam2018}.
 }
 
-% \citep[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
-% and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
-% for more information.
+Second, parents possibly care about the spacing between birth either in its own right or, 
+more likely, because of the potential effects of spacing on the children and the mother.
 
-% Age at marriage increased over time across all three education groups.
-% The most substantial increase was for women without any education, where
-% the average went from below 16 years of age to 18.5.
-% The smallest change is for the most educated women where the average age
-% at marriage went up by less than a year---from 19.6 to 20.4---across the 
-% four periods.
+It has, for example, been suggested that child ``quality'' might increases with spacing 
+because the amount of parental attention increases with spacing
+\citep{Zajonc1975,Zajonc1976,Razin1980}.
+In this case, birth spacing should increase in family income, while the effect of maternal 
+education is ambiguous since higher education on one hand makes the mother's time spent 
+out of the labor market more costly and on the other hand increases how productive the 
+mother is in childrearing. [TK Behrman et al. paper on mother's education in India]
 
-% How does educational expansion affect birth spacing
+Most of the research finds a negative impact of short spacing on child health, especially 
+for very short intervals of 24 months or less 
+\citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
+There is evidence in countries as diverse as Bangladesh, Brazil, El Salvadore, India,
+and Pakistan of worse health outcomes and a higher mortality risk the shorter the birth
+interval
+\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,Ghosh2018}.
+The effects of short spacing on child mortality are, however, strongly moderated by
+maternal education, and even very short spacing has relatively low mortality for women
+with secondary or tertiary education \citep{Molitoris2019}.
+
+The mother may also be affected by the length of the birth intervals, although the
+results on mother's anthropometric status are mixed \citep{Dewey2007,Conde-Agudelo2012}.
+For India, there is, however, evidence that women with first-born girls are more likely to 
+have anemia, possibly because short birth spacing can resulting in maternal depletion 
+\citep{Milazzo2018}.
+
+Hence, the determinants of the durations between births are an amalgam of biological 
+factors, economic considerations, and individual preferences.
+
+Education affects a number of factors related to birth spacing.
+First, it affects the cost of time and the associated income profile over time.
+Second, it affects the cost of using contraceptives (independently of the lower fertility
+and changes in spacing). This could also include how good women are to use new 
+contraceptive technology \citep{Kim2010}.
+[I find this argument weird. \citep{Rosenzweig1989} shows that better educated women
+are better at using more difficult ``technologies'' but those do not include most common
+forms of modern contraceptives such as pills or injectables.]
+
+First, if parents realize that having children close together increase the children's
+mortality risk, they would prefer to space births further apart to lower mortality risk
+(although possibly not very long since the mortality risk involves a trade-off between the
+cost of births and the benefit of having a child).
+Second, if there is a risk of ``overshooting'' the ideal number of children because of
+imperfect fertility control and overshooting is sufficiently costly.
+Parents would select a higher level of contraception than if they had perfect control and,
+consequently, space children far apart on average [this is presumably
+the \citep{Keyfitz1971,Heckman1976} arguments]
+Third, if capital markets are not perfect and giving birth or rearing a child is costly
+parents are forced to wait until they have enough income/wealth to have the next child
+(this works through consumption; with low levels of consumption the cost of giving up
+any will be higher so parents will want to wait until they have higher income and the
+marginal cost of giving up consumption will be lower).
+[would the opportunity cost of time work in the opposite direction? If women's 
+opportunity cost of time goes up over time it would make sense to have the children
+earlier]
+
+Is there an expected mortality effect here as well?
+If you expect a certain proportion of your children to die, it would probably make sense
+to have your births earlier, everything else equal.
+That way, you would get to the ideal number of children earlier.
+
+Effect of son preference on birth spacing?
+Do we have any theoretical results on this?
+
+Biological/health effects on spacing that might change with education (or rather the
+health improvements that come with higher education/income either from the women
+herself or her husband)?
+As better health leads to shorter post-partum amenorrhoea, we should expect shorter
+spacing rather than longer with better health.
+The evidence suggests that there is relatively little effect of health status on 
+fecundity once nutrition is above famine or starvation levels \citep{Huffman1987,John1987,lindstrom99}
+
+Breastfeeding would be part of this.
+An healthier mother is more likely to successfully breastfeed and that would increase the
+spacing between births.
+
+Steeper income profile over time results in longer spacing in the absence of perfect
+capital markets.
+There are two effects of this theoretical results.
+First, we should see an general increase in spacing across education groups because
+development lead to a steeper income profile.
+[This does require that economic development is associated with steeper income profiles;
+not sure if anybody looked at this.
+The lower fertility even for low education women does suggest that income is higher,
+but does not, by itself, say anything about the age profile in income.]
+Second, the increase in spacing should be stronger the higher the education level is.
+In other words, we should see a general increase in spacing, and this increase should be
+longer the higher the education level.
+
+[Notes/lit review from paper]
 
@@
 }
-Even the effects of access to contraceptive and declining fertility on spacing are unclear.
-On the one hand, access to contraceptives allows women to avoid too short spacing between 
-birth.
-On the other hand, increased reliability of access and effectiveness of contraceptives can 
-lead to shorter intervals between births if women used to have longer spacing to avoid
-having too many children by accident \citep{Keyfitz1971,Heckman1976}.
-These two counteracting effects may explain why better-educated women have shorter spacing 
-than less educated women in some instances but not in others and why finding statistically 
-significant effects of contraception use on birth spacing is difficult 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.%
+
+\subsection{How Education Has Changed in India}
+
+son preference and investment in female education (Behrman et al. paper)
+
+labor force participation of women in India
+
+returns to education in India (men and women)
+
+[Notes/lit review paper from paper]
+
+[Update with numbers from household module instead of individual recode using cohorts]
+
+Finally, the population has become substantially better educated over time.
+In the first period, almost 60\% of women had no education, and only twenty percent had
+eight or more years, while in the last period the reverse was the case.
+These changes underestimate the increase in education because many of the younger women 
+with more education are not yet married and therefore not in the sample.%
 \footnote{
-In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
-access to family planning \citep{Rahman1993}.
-Other evidence, however, points to families ability to time births, even in the absence
-of modern contraceptives \citep{Jayachandran2011,Alam2018}.
+Women with eight or more years of education accounted for 65.9\% of
+unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4
+\citep{International-Institute-for-Population-Sciences-IIPS2007,International-Institute-for-Population-Sciences-IIPS2017}.
 }
+
+% \citep[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
+% and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
+% for more information.
+
+% Age at marriage increased over time across all three education groups.
+% The most substantial increase was for women without any education, where
+% the average went from below 16 years of age to 18.5.
+% The smallest change is for the most educated women where the average age
+% at marriage went up by less than a year---from 19.6 to 20.4---across the 
+% four periods.
+
+What factors have changed over time:
+    - education levels / desired fertility
+    - access to contraceptives
+    - return to women's education
+    - access to sex selection
+    - breastfeeding patterns (?)
+    - labor force participation (?)

### 2019-11-08 paper/conceptual_framework.tex
Add contraception and spacing discussion

@@
 
-The decisions on sexual activity and contraceptive effort are constrained by biological 
-factors, such as fecundity, age, and health of the mother, and the knowledge of and access
-to contraceptive technology.
+The decisions on sexual activity and contraceptive effort are moderated by fecundity,
+determined by biological factors such as age and health of the mother, and the knowledge of and 
+access to contraceptive technology.
 There is evidence from ``natural fertility'' populations that increasing number of 
@@
 
-TK contraception
+Empirically, there is no clear relationship between contraception use and birth 
+spacing or between education level and birth spacing
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+The lack of evidence is consistent with the ambiguous theoretical effect of introducing 
+modern contraceptives on birth spacing.
+On one hand, when contraceptive technologies are less effective, 
+parents may try to avoid overshooting their desired number of children by spacing their 
+children further apart.
+Increased reliability of access to and effectiveness of contraceptives can then lead to 
+shorter intervals between births because parents are more certain of effectively
+stopping childbearing when they reach their preferred number of children and having
+the children closer together provide higher utility because parents get to enjoy the
+children for longer as discussed above \citep{Keyfitz1971,Heckman1976}.
+On the other hand, when contraceptives are less effective we would expect, through 
+random variation, some birth intervals to be shorter than ideal for the reasons 
+discussed below.
+With increased reliability of access to and effectiveness of contraceptives, parents 
+would better be able to avoid too short spacing between birth and average spacing
+should go up.
 
-There is no clear relationship between contraception use and birth spacing in the 
-literature, and better-educated women have shorter spacing than less educated women in 
-some instances but not in others 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
-
-Even the effects of access to contraceptive and declining fertility on spacing are unclear.
-On the one hand, access to contraceptives allows women to avoid too short spacing between 
-birth.
-On the other hand, increased reliability of access and effectiveness of contraceptives can 
-lead to shorter intervals between births if women used to have longer spacing to avoid
-having too many children by accident \citep{Keyfitz1971,Heckman1976}.
-%
-\footnote{
-In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
-access to family planning \citep{Rahman1993}.
-Other evidence, however, points to families ability to time births, even in the absence
-of modern contraceptives \citep{Jayachandran2011,Alam2018}.
-}
+To further complicate the relationship between contraception access and spacing,
+the ability to successfully use ``low efficacy'' contraceptive methods, such as 
+the rhythm method, is increasing in education, while there is no difference across education 
+leves when it comes to modern contraceptives such as pills or injectables 
+\citep{Rosenzweig1989}.
+Furthermore, even in the absence of modern contraceptives, families appear able to time or 
+at least postpone births when faced with strong enough incentives 
+\citep{Jayachandran2011,Alam2018}.
+[Does this need a tie-in to the paragraph above?]
 
@@
 
+In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
+access to family planning \citep{Rahman1993}.
+
 \subsection{How Education Has Changed in India}

### 2019-11-09 paper/conceptual_framework.tex
Add draft of economic factors to conceptual framework
Covers economies of scale, income profile over time, and shocks to
prices and income.

@@
 
-In the simplest possible dynamic model of fertility there are no real spacing decisions.
+In the simplest possible dynamic model of fertility the spacing decisions is trivial.
 Assume that parents derive benefits from having their children around, rather than from 
@@
 
-Biological factors are unlikely to be an important factor in differences in spacing over 
+Biological factors are, however, unlikely to be an important factor in differences in spacing over 
 time or across education levels in India for the period covered.
@@
 [Does this need a tie-in to the paragraph above?]
+[Can use "less effective" contraception and still have low fertility]
+[Do parents move afway from certain contraceptive choices with education?]
 
@@
 
-Hence, the determinants of the durations between births are an amalgam of biological 
-factors, economic considerations, and individual preferences.
+Third, having and rearing children involves both direct and time costs, and economic factors 
+can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
+These economic factors can broadly be divided into 
+the effects of price and income shocks,
+the expected income trajectory of the husband and wife,
+and economies of scale considerations.
+There is a substantial amount of research on all these areas, although the majority is for
+developed countries.
+
+The expected effect of economies of scale in childrearing is to shorten the interval between 
+births.
+Childbearing and rearing is intensive in the mother's time, but taking care of two young
+children is not twice as time consuming as taking care of one child 
+\citep{Vijverberg1982,Espenshade1984}.
+Hence, if childbearing and rearing requires the mother to reduce her participation in productive 
+activities, parents can lower the cost of children by shorten birth spacing and, thereby, reduce
+the amount of time the mother has to be away from productive activities.
+In this set-up women with higher education will both have lower fertility and shorter
+spacing than women with lower education because of the higher opportunity cost of time 
+\citep{Ross1974,Newman1981}.
+The extent to which this type of economies of scale is important depends on the extent to
+which having children affects the mother's productive activities.
+If she mainly works at home there likely is going to be less of an incentive to space 
+children for this reason than if she is part of the labor force outside the home.
+Similarly, higher household income, holding the mother's income contanst, reduces the incentive 
+to space births for this reason.
+
+In the absense of perfect capital markets, theory suggests that the steeper the parents' income 
+profile over time, the longer the spacing between births 
+\citep{Heckman1975,Wolpin1984,Newman1988}.
+The idea is that although parents would prefer to have their children as early as possible to
+enjoy them for longer there is also a direct cost to children.
+At the early stage of life income is low, which means that the marginal utility of consumption 
+is higher making parents less willing to give up consumption now to have a child, compare to 
+later when they know that their income will be higher.
+There is evidence that---at least for first births---there is, indeed, an effect of the income
+profile over time \citep{Newman1984,Happel1984}.
+
+There are two effects of this theoretical results.
+First, we should see an general increase in spacing across education groups to the extent that
+development lead to a steeper income profile.
+[This does require that economic development is associated with steeper income profiles;
+not sure if anybody looked at this.
+The lower fertility even for low education women does suggest that income is higher,
+but does not, by itself, say anything about the age profile in income.]
+Second, the increase in spacing should be stronger with increasing education levels.
+In other words, we should see a general increase in spacing, and this increase should be
+larger the higher the education level.
+
+The income profile argument assumes that parents know their future income, but 
+shocks to income and prices may also affect spacing, with temporary higher cost of women's time
+and other inputs into children together with lower income temporarily decreasing fertility 
+and, thereby, increase spacing between births \citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
+It is likely that the risk of income shocks decrease with increasing education, although it
+is unclear the extent to which exposure to other types of shocks that might impact the timing
+of birth is affected by education.
 
@@
 spacing between births.
-
-Steeper income profile over time results in longer spacing in the absence of perfect
-capital markets.
-There are two effects of this theoretical results.
-First, we should see an general increase in spacing across education groups because
-development lead to a steeper income profile.
-[This does require that economic development is associated with steeper income profiles;
-not sure if anybody looked at this.
-The lower fertility even for low education women does suggest that income is higher,
-but does not, by itself, say anything about the age profile in income.]
-Second, the increase in spacing should be stronger the higher the education level is.
-In other words, we should see a general increase in spacing, and this increase should be
-longer the higher the education level.
 

### 2019-11-09 paper/conceptual_framework.tex
Expand on mortality risk on spacing and clean up of notes

@@
 Outside of direct famine conditions, there is little evidence that women's health and 
-nutritional status substantially affects spacing \citep{Huffman1987,John1987,lindstrom99}.
+nutritional status substantially affects spacing \citep{Huffman1987,John1987,lindstrom99}.%
+\footnote{
+On one hand, with better health we should expect shorter post-partum amenorrhoea and a higher
+likelihood of carrying a pregnancy to term, both of which lead to shorter spacing with better health.
+On the other hand, an healthier mother is more likely to successfully breastfeed and that would 
+increase the spacing between births, although if she is a strong producer of breastmilk the 
+suckling relative to production is lower, which, in turn, lower the conceptraceptive effect
+of breastfeeding.
+}
 The Maharashtra drought occurred in 1970-1973 and, therefore, would only affect the first
@@
 modern contraceptives on birth spacing.
-On one hand, when contraceptive technologies are less effective, 
-parents may try to avoid overshooting their desired number of children by spacing their 
-children further apart.
+On one hand, when contraceptive technologies are less effective, parents may try to avoid 
+overshooting their desired number of children by spacing their children further apart.
 Increased reliability of access to and effectiveness of contraceptives can then lead to 
@@
 
-Most of the research finds a negative impact of short spacing on child health, especially 
-for very short intervals of 24 months or less 
-\citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
+One aspect of child ``quality'' where is is a strong effect of spacing is child health
+and mortality, with most of the research finding that shorter spacing leads to worse
+health and higher mortality for children, especially for very short intervals of 24 months 
+or less \citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
+\footnote{
 There is evidence in countries as diverse as Bangladesh, Brazil, El Salvadore, India,
@@
 \citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,Ghosh2018}.
-The effects of short spacing on child mortality are, however, strongly moderated by
+This is different from the effect of the underlying mortality risk on birth spacing.
+The expected effect of mortality risk---ignoring the effect of shorter spacing on mortality 
+risk---is to shorten birth spacing to get to the ideal number of children earlier.
+There is little empirical evidence for this type of effect 
+\citep{Newman1983,Newman1988,Bhalotra2008}.
+}
+Hence, if parents realize that having children close together increase the children's
+mortality risk, they would prefer to space births further apart to lower mortality risk
+(although possibly not very long since the mortality risk involves a trade-off between the
+cost of births and the benefit of having a child).
+Furthermore, the effects of short spacing on child mortality are strongly moderated by
 maternal education, and even very short spacing has relatively low mortality for women
@@
 
-Education affects a number of factors related to birth spacing.
-First, it affects the cost of time and the associated income profile over time.
-Second, it affects the cost of using contraceptives (independently of the lower fertility
-and changes in spacing). This could also include how good women are to use new 
-contraceptive technology \citep{Kim2010}.
-[I find this argument weird. \citep{Rosenzweig1989} shows that better educated women
-are better at using more difficult ``technologies'' but those do not include most common
-forms of modern contraceptives such as pills or injectables.]
-
-First, if parents realize that having children close together increase the children's
-mortality risk, they would prefer to space births further apart to lower mortality risk
-(although possibly not very long since the mortality risk involves a trade-off between the
-cost of births and the benefit of having a child).
-Second, if there is a risk of ``overshooting'' the ideal number of children because of
-imperfect fertility control and overshooting is sufficiently costly.
-Parents would select a higher level of contraception than if they had perfect control and,
-consequently, space children far apart on average [this is presumably
-the \citep{Keyfitz1971,Heckman1976} arguments]
-Third, if capital markets are not perfect and giving birth or rearing a child is costly
-parents are forced to wait until they have enough income/wealth to have the next child
-(this works through consumption; with low levels of consumption the cost of giving up
-any will be higher so parents will want to wait until they have higher income and the
-marginal cost of giving up consumption will be lower).
-[would the opportunity cost of time work in the opposite direction? If women's 
-opportunity cost of time goes up over time it would make sense to have the children
-earlier]
-
-Is there an expected mortality effect here as well?
-If you expect a certain proportion of your children to die, it would probably make sense
-to have your births earlier, everything else equal.
-That way, you would get to the ideal number of children earlier.
-
 Effect of son preference on birth spacing?
 Do we have any theoretical results on this?
-
-Biological/health effects on spacing that might change with education (or rather the
-health improvements that come with higher education/income either from the women
-herself or her husband)?
-As better health leads to shorter post-partum amenorrhoea, we should expect shorter
-spacing rather than longer with better health.
-The evidence suggests that there is relatively little effect of health status on 
-fecundity once nutrition is above famine or starvation levels \citep{Huffman1987,John1987,lindstrom99}
-
-Breastfeeding would be part of this.
-An healthier mother is more likely to successfully breastfeed and that would increase the
-spacing between births.
 

### 2019-11-12 paper/conceptual_framework.tex
Add draft discussion of son preference and sex selection
Very much a draft at the moment.
Need to add sex selection theory predictions

@@
 maternal education, and even very short spacing has relatively low mortality for women
-with secondary or tertiary education \citep{Molitoris2019}.
+with secondary or tertiary education \citep{Whitworth2002,Molitoris2019}.
 
@@
 
-Effect of son preference on birth spacing?
-Do we have any theoretical results on this?
+Finally, the discussion has so far assumed that children are identical, except for any potential
+differences that arise from differences in spacing, but there is substantial evidence that the 
+sex composition of previous children affect birth spacing.
+For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
+a boy as the last-born child, significantly increase the duration to next birth,
+\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
+\footnote{
+There is also evidence of differential stopping behavior, with an additional child more likely the
+fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
+Other countries show a similar pattern
+\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
+Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
+absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
+\citep{Rossi2015}.
+}
+
+It is not immediately obvious that we should expect a result like this from a theoretical
+standpoint.
+If, as discussed above, there are potentially significant negative effects of short spacing
+parents who choose short spacing in the absence of a boy lowers the survival probabilty of
+the next child, including a boy if the next child is a boy.
+There are two possibilities for why parents might still try to conceive sooner in the 
+absence of boys.%
+\footnote{
+The fact that there are significant differences in spacing by sex composition indicates that
+parents have---at least some---control over the timing of birth.
+Hence, it is unlikely that the differences in spacing come about by random chance.
+In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
+access to family planning \citep{Rahman1993}.
+}
+First, it is possible that parents do not, in fact, realize that short spacing is potentially
+detrimental to the next child's health.
+Second, parents realize that short spacing has negative health effects, but have a strong
+enough son preference that they are willing to divert substantial resources to investing
+in the next child's health if it is a boy and that these investments can compensate for 
+the negative effects.
+[Are there any other ones that might explain the pattern?
+    - biological? this would have to work off the sex of only the last child, so that
+    spacing after girls is naturally shorter.
+    - parents care so much about having a son sooner that they are willing to accept a 
+    higher mortality risk.
+    - ??
+    ]
+
+[has anyone actual done the theory behind the short spacing?
+It would seem that it requires fairly strong assumptions to make it attractive to
+have short spacing.
+Maybe check the Jensen paper on equal treatment]
+
+[can I say anything about which one is true?]
+It is worthwhile thinking a bit about under what circumstances it would be possible to
+identify which of these explanations hold.
+If the first one holds, we should see high mortality for both boys and girls born
+after short spacing across all households whether or not they have a strong son preference.
+In fact, it is possible that we see higher mortality for sons than girls given that boys 
+have naturally higher mortality in the absense of any preference for a given sex.
+
+If the second one holds, we should see substantial differences in mortality across
+sex for short spacing children, with the boys having substantially lower mortality risk
+than expected for the spacing length.
+
+If a son is born next:
+The boy should have substantially lower mortality risk than expected for the spacing
+duration.
+Because this argument relies on a redistribution of resources, we should expect to see
+worse outcomes for all the other children in the family.
+This means that the other children (all girls) should do substantially worse.
+
+If a girl is born next:
+there are a couple of possible outcomes.
+If all children/girls are treated equally, we should see somewhat of a worsening in 
+health outcomes because the available resources are now distributed across more children.
+If children are not treated equally, we should see much worse outcomes for the last
+girl because the parents have an incentive to keep investing in the children they have
+already rather than the new child.
+
+How does education play into this?
+The negative effects of shorter spacing is strongly mitigated by higher education.
+Hence, women with more education are in the position that they can better tolerate short 
+spacing in the absence of a boy and that the potential negative effects on the next child 
+should be much less pronounced.
+Furthermore, the lower mortality risk should show up whether the next child is a boy 
+or a girl.
+It is clearly still possible that there would some difference in mortality outcomes 
+across boys and girls because of a larger investment in the boy once born, but it should
+not be as large.
+
+What are the effects of the introduction of sex selection?
+The introduction of sex selection means that parents now have the option to avoid
+birth of children with an undesired sex.
+This impacts the observed birth spacing since, as discussed above, each sex-selective 
+abortions increases the interval between births by six to twelve months.
+The question is who is likely to use sex selection, when, and why?
+
+[could I simply copy the results from my WB paper's theory section?]
+
+There is clear evidence that in India the use of sex selection increases with education
+\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.
+There are two potential reasons for this.%
+\footnote{
+It is also possible that the effect is driven by a stronger son preference, although 
+higher education women have shown declining stated son preference \citep{bhat03,pande07}.
+}
+First, women with more education generally have lower fertility either because of the
+higher opportunity cost of time or because of other changes in the preferred number of
+children.
+Second, women with more education also tend to live in households with higher income,
+which better enables them to access prenatal sex determination.
+[It does not seem possible to cleanly separate out these differences]
+
+should have something about how short spacing to conception could still be important.
+Maybe even more so since health outcomes for short spacing birth likely has improved
+over time.
 
 [Notes/lit review from paper]
-
-Women with different education levels have different hazard profiles, although the size 
-and direction of the effect vary across areas and time 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
-Furthermore, the use of sex selection increases with education, either because of the 
-associated lower fertility or because higher income enables them to access and
-afford prenatal sex determination
-\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.%
-\footnote{
-It is also possible that the effect is driven by a stronger son preference, although 
-higher education women have shown declining son preference \citep{bhat03,pande07}.
-}
 
@@
 
-Differential stopping behavior is widespread, with an additional child more likely the
-fewer sons a family has 
-\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
-\footnote{
-Other countries show a similar pattern
-\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
-}
-
-For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
-a boy as the last-born child, significantly increase the duration to next birth,
-\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
-\footnote{
-Ethnic Indians in South Africa also show a longer duration after the birth of a 
-son than after a daughter \citep{Gangadharan2003}.
-}
-Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
-absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
-\citep{Rossi2015}.
-
 Finally, we know less about what determines spacing behavior in developing countries than 
@@
 }
-
-In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
-access to family planning \citep{Rahman1993}.
 

### 2019-11-13 paper/conceptual_framework.tex
Discuss the role of sex selection in spacing
Focus is on the trade-off that parents face when deciding whether to engage in
sex selection, especially relating to birth spacing.

Discuss how education is related to sex selection.

Remove notes from paper no longer needed.

@@
 between births.
-Since education is closely linked to the use of sex selection, I focus especially on the
+Since sex selection is closely linked to education, I focus especially on the
 the effects of education on spacing.
-I first discuss generic spacing decisions frameworks, and then turn to how son preference
-and sex selection fits into the decisions on spacing.
+I first discuss a generic spacing decisions frameworks, and then turn to how son 
+preference and sex selection fits into the decisions on spacing.
 
-In the simplest possible dynamic model of fertility the spacing decisions is trivial.
+In the simplest possible dynamic model of fertility the spacing decision is trivial.
 Assume that parents derive benefits from having their children around, rather than from 
@@
 spacing than women with lower education because of the higher opportunity cost of time 
-\citep{Ross1974,Newman1981}.
+\citep{Ross1974,Newman1981,Newman1984}.
 The extent to which this type of economies of scale is important depends on the extent to
@@
 profile over time, the longer the spacing between births 
-\citep{Heckman1975,Wolpin1984,Newman1988}.
+\citep{Heckman1976,Wolpin1984,Newman1988}.
 The idea is that although parents would prefer to have their children as early as possible to
@@
 
-What are the effects of the introduction of sex selection?
-The introduction of sex selection means that parents now have the option to avoid
-birth of children with an undesired sex.
-This impacts the observed birth spacing since, as discussed above, each sex-selective 
-abortions increases the interval between births by six to twelve months.
+With the introduction of sex selection parents can now avoid the birth of children with 
+an undesired sex, although at the cost of the procedure and having to wait longer until 
+the next child if the fetus is aborted.
+The use of sex selection impacts the observed birth spacing since, as discussed 
+above, each sex-selective abortions increases the interval between births by six 
+to twelve months.
 The question is who is likely to use sex selection, when, and why?
 
-[could I simply copy the results from my WB paper's theory section?]
+Theory suggests that the lower the desired fertility the more likely is the use of sex 
+selection \citep{Portner2015b}.
+This is driven by simple probabilities:
+without use of sex selection, the probability of not having a son are 48.8 percent when
+only having one child, 23.8 percent for two children, 11.6 percent for three children, 
+5.7 percent for four children, 2.8 percent for five children, and 1.4 percent for six 
+children.
+Furthermore, given a desired level of fertility, the higher the parity, the higher the
+likelihood of using sex selection.
+Unless parents have a specific preference for a first-born boy, the costs associated with 
+sex selection means that it is better to try for a boy without sex selection first and 
+then use at later parities in the absence of a son as you get closer to the desired 
+fertility.
 
-There is clear evidence that in India the use of sex selection increases with education
-\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.
-There are two potential reasons for this.%
+The higher the cost of prenatal sex determination and the abortion, both in direct cost
+and the possibility of criminal charges, the less use we should see.
+Similarly, any potentially negative effects on the mother and offspring from repeated
+abortions would also tend to reduce the use of sex selection---provided, obviously, that
+parents are aware of these costs.
+Finally, the more abortions between births, the less the opportunity there is to take
+advantage of any economies of scale in childrearing.
+
+The use of sex selection in India increases with education and is higher in urban
+areas than in rural
+\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
+Jayachandran2017}.
+Women with more education generally have lower desired fertility, either because of the
+higher opportunity cost of time or because of other changes in the preferred number of
+children.%
 \footnote{
@@
 }
-First, women with more education generally have lower fertility either because of the
-higher opportunity cost of time or because of other changes in the preferred number of
-children.
-Second, women with more education also tend to live in households with higher income,
-which better enables them to access prenatal sex determination.
-[It does not seem possible to cleanly separate out these differences]
+Women with more education also tend to live in households with higher income,
+which better enables them to access prenatal sex determination and lowers the relative
+costs of using sex selection (both direct and indirect, such the decline in 
+economies of scale with repeated abortions).
 
-should have something about how short spacing to conception could still be important.
-Maybe even more so since health outcomes for short spacing birth likely has improved
-over time.
+Given that each abortion increases the spacing between births, it is possible that
+parents may try to conceive even sooner than in the absence of sex selection.
+By conceiving sooner, they would lower the expected cost of foregone economies of scale in 
+childrearing.
+This is especially relevant for better educated women, who, as discussed above, have
+lower mortality risk for offspring born after short spacing.
+If health outcomes for short spacing births has improved over time---as is likely---we
+should see an even stronger push toward shorter spacing for women using sex selection.
 
-[Notes/lit review from paper]
-
-The sex composition of previous children affects both the timing of births and the use of 
-sex-selective abortions 
-\citep{retherford03b,jha06,Bhalotra2008,abrevaya09,Portner2015b,Kumar2016,Soest2018}.
-I capture sex composition with dummy variables for the
-possible combinations for the specific spell, ignoring the ordering of births.
-Finally, urban women have both lower fertility and, presumably, better access to
-sex selection, both of which lead to higher use of sex-selective abortions than in 
-rural areas \citep{retherford03b,jha06,Portner2015b}.
-
-The longer average spacing and the relatively higher number of very long birth intervals 
-seem to run counter to a general reduction in the length of women's reproductive spans 
-found in earlier research \citep{Padmadas2004}.
-
-Finally, we know less about what determines spacing behavior in developing countries than 
-in developed countries, and with declining fertility and increasing numbers of women 
-entering the labor force, understanding how couples make timing decisions is necessary 
-for the design of suitable policies \citep{Portner2018}.%
-\footnote{
-It is clear that birth spacing does respond to policies in both developed and 
-developing countries \citep{Pettersson-Lidbom2009,Todd2012,Meckel2015,Ghosh2018}.
-}
+[Need some kind of summary of spacing decisions and how they are likely to change
+over time and with increased education]
 

### 2019-11-13 paper/conceptual_framework.tex
First go at summary of spacing framework

@@
 interval
-\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,Ghosh2018}.
+\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,
+Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,
+Ghosh2018}.
 This is different from the effect of the underlying mortality risk on birth spacing.
@@
 The mother may also be affected by the length of the birth intervals, although the
-results on mother's anthropometric status are mixed \citep{Dewey2007,Conde-Agudelo2012}.
+results on mother's anthropometric status are mixed and there appear to be no
+effect on maternal mortality \citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
 For India, there is, however, evidence that women with first-born girls are more likely to 
@@
 
-There are two effects of this theoretical results.
+There are two implications of this theoretical results.
 First, we should see an general increase in spacing across education groups to the extent that
@@
 
+The question is how birth spacing is likely to change over time and with increasing
+education in India.
+As other countries like the US have developed, they have seen a progressively longer 
+spacing between births as the proportion of births with very short intervals---less than 
+24 months---have declined substantially \citep{Hotz1997}.
+Most of the these countries do, however, not have the same degree of son preference that
+we see in India.
+
+What are the important factors that determine spacing?
+
+- household income
+- education
+- labor force participation
+- sex selection
+- health (improvements, campaigns)
+
+The main drivers of birth spacing of interest for India are female education and
+development together with son preference and the increased availability of sex selection.
+
 \subsection{How Education Has Changed in India}
@@
 labor force participation of women in India
+
+\citep{Jensen2012}
+\citep{Behrman2017}
+\citep{Chatterjee2018}
+
+On the U-shaped relationship between development and women's labor force participation \citep{Goldin1994}
 

### 2019-11-13 paper/conceptual_framework.tex
Move descriptive section to new branch

@@
 development together with son preference and the increased availability of sex selection.
-
-\subsection{How Education Has Changed in India}
-
-son preference and investment in female education (Behrman et al. paper)
-
-labor force participation of women in India
-
-\citep{Jensen2012}
-\citep{Behrman2017}
-\citep{Chatterjee2018}
-
-On the U-shaped relationship between development and women's labor force participation \citep{Goldin1994}
-
-returns to education in India (men and women)
-
-[Notes/lit review paper from paper]
-
-[Update with numbers from household module instead of individual recode using cohorts]
-
-Finally, the population has become substantially better educated over time.
-In the first period, almost 60\% of women had no education, and only twenty percent had
-eight or more years, while in the last period the reverse was the case.
-These changes underestimate the increase in education because many of the younger women 
-with more education are not yet married and therefore not in the sample.%
-\footnote{
-Women with eight or more years of education accounted for 65.9\% of
-unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4
-\citep{International-Institute-for-Population-Sciences-IIPS2007,International-Institute-for-Population-Sciences-IIPS2017}.
-}
-
-% \citep[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
-% and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
-% for more information.
-
-% Age at marriage increased over time across all three education groups.
-% The most substantial increase was for women without any education, where
-% the average went from below 16 years of age to 18.5.
-% The smallest change is for the most educated women where the average age
-% at marriage went up by less than a year---from 19.6 to 20.4---across the 
-% four periods.
-
-What factors have changed over time:
-    - education levels / desired fertility
-    - access to contraceptives
-    - return to women's education
-    - access to sex selection
-    - breastfeeding patterns (?)
-    - labor force participation (?)

### 2019-11-13 paper/conceptual_framework.tex
Minor edits

@@
 
-The question is how birth spacing is likely to change over time and with increasing
-education in India.
 As other countries like the US have developed, they have seen a progressively longer 
@@
 
-The main drivers of birth spacing of interest for India are female education and
-development together with son preference and the increased availability of sex selection.
+In summary, female education affects birth spacing through a variety of pathways.
+The main pathway of interest here is the effect of sex selection on spacing.
+However, to understand the effects of the increased use of sex selection over time it
+is important to also understand the other changes that affect birth spacing.
+The most likely factors are the changes in household income/wealth and the improvements
+in health as India has developed.
+I, therefore, now look at how female education and labor force participation has changed
+over time in India.

### 2019-11-19 paper/conceptual_framework.tex
Edit and shorten conceptual framework

@@
 between births.
-Since sex selection is closely linked to education, I focus especially on the
+I first discuss the main determinants of spacing discussed in the prior research, and 
+then turn to how son preference and sex selection fits into the decisions on spacing.
+Since sex selection is closely linked to education, I pay special attention to the
 the effects of education on spacing.
-I first discuss a generic spacing decisions frameworks, and then turn to how son 
-preference and sex selection fits into the decisions on spacing.
 
 In the simplest possible dynamic model of fertility the spacing decision is trivial.
-Assume that parents derive benefits from having their children around, rather than from 
+Assume that parents derive benefits from the presence of children, rather than from 
 the births themselves, that spacing of children by itself does impact parental utility, 
@@
 \citep{Newman1988}.
-The simplest model clearly does not fit the observed spacing patterns, but the question 
-is why.
+The simplest model clearly does not fit the observed spacing patterns, which suggests 
+that one or more of the assumptions in the simple model are wrong.
 
-First, parents do not perfectly control the timing of births, but instead decide on their
-levels of sexual activity and contraceptive effort, which, in turn, affect their likelihood 
-of conceiving.
+First, parents do not perfectly control the timing of births, but instead decide on the
+levels of sexual activity and contraceptive effort, which, in turn, affect the 
+likelihood of conceiving.
 
 The decisions on sexual activity and contraceptive effort are moderated by fecundity,
-determined by biological factors such as age and health of the mother, and the knowledge of and 
+determined by factors such as age and health of the mother, and the knowledge of and 
 access to contraceptive technology.
@@
 
-Biological factors are, however, unlikely to be an important factor in differences in spacing over 
-time or across education levels in India for the period covered.
-Outside of direct famine conditions, there is little evidence that women's health and 
-nutritional status substantially affects spacing \citep{Huffman1987,John1987,lindstrom99}.%
-\footnote{
-On one hand, with better health we should expect shorter post-partum amenorrhoea and a higher
-likelihood of carrying a pregnancy to term, both of which lead to shorter spacing with better health.
-On the other hand, an healthier mother is more likely to successfully breastfeed and that would 
-increase the spacing between births, although if she is a strong producer of breastmilk the 
-suckling relative to production is lower, which, in turn, lower the conceptraceptive effect
-of breastfeeding.
-}
-The Maharashtra drought occurred in 1970-1973 and, therefore, would only affect the first
+Age and health of the mother are, however, unlikely to be important factors in changes
+in spacing over time or across education levels in India for the period covered, since
+there is little evidence that women's health and nutritional status substantially affects 
+spacing, outside of direct famine conditions \citep{Huffman1987,John1987,lindstrom99}.
+The Maharashtra drought occurred in 1970--1973 and would, therefore, only affect the first
 year or two of the data.
-Hence, although there are still differences in individual fecundity across women, it is
-unlikely that we should see systematic differences across education groups and over time
-in the data because of health status.
 Furthermore, I only examine spacing up to parity fourth, and age of the mother is,
-therefore, unlikely to be a concern when it comes to fecundity, when though better 
+therefore, unlikely to be a concern when it comes to fecundity, even though better 
 educated women are, on average, older when they marry.
 
-Empirically, there is no clear relationship between contraception use and birth 
-spacing or between education level and birth spacing
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
-The lack of evidence is consistent with the ambiguous theoretical effect of introducing 
+Despite a general belief that better access to and knowledge of contraception should lead
+to longer average spacing, the empirical relationship between contraception use and birth 
+spacing is ambiguous \citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+This lack of evidence is consistent with the ambiguous theoretical effect of introducing 
 modern contraceptives on birth spacing.
-On one hand, when contraceptive technologies are less effective, parents may try to avoid 
-overshooting their desired number of children by spacing their children further apart.
-Increased reliability of access to and effectiveness of contraceptives can then lead to 
+On one hand, in the absence of modern contraceptive technologies, parents may try to 
+avoid overshooting their desired number of children by spacing their children further apart.
+Increased reliability of access to and effectiveness of contraceptives then lead to 
 shorter intervals between births because parents are more certain of effectively
 stopping childbearing when they reach their preferred number of children and having
-the children closer together provide higher utility because parents get to enjoy the
-children for longer as discussed above \citep{Keyfitz1971,Heckman1976}.
-On the other hand, when contraceptives are less effective we would expect, through 
-random variation, some birth intervals to be shorter than ideal for the reasons 
-discussed below.
+the children closer together provide higher utility because parents benefit from the
+presence of children for longer as discussed above \citep{Keyfitz1971,Heckman1976}.
+On the other hand, when contraceptives are effective we would expect some birth 
+intervals to be shorter than ideal in the sense discussed below through simple random
+variation.
 With increased reliability of access to and effectiveness of contraceptives, parents 
@@
 
-To further complicate the relationship between contraception access and spacing,
-the ability to successfully use ``low efficacy'' contraceptive methods, such as 
-the rhythm method, is increasing in education, while there is no difference across education 
-leves when it comes to modern contraceptives such as pills or injectables 
-\citep{Rosenzweig1989}.
+To further complicate the relationship between contraception and spacing, the ability to 
+successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, is 
+increasing in education, while there is no difference across education levels 
+when it comes to modern contraceptives such as pills or injectables \citep{Rosenzweig1989}.
 Furthermore, even in the absence of modern contraceptives, families appear able to time or 
@@
 \citep{Jayachandran2011,Alam2018}.
-[Does this need a tie-in to the paragraph above?]
-[Can use "less effective" contraception and still have low fertility]
-[Do parents move afway from certain contraceptive choices with education?]
 
-Second, parents possibly care about the spacing between birth either in its own right or, 
-more likely, because of the potential effects of spacing on the children and the mother.
-
+Second, parents may care about the spacing between birth either in its own right or, 
+more likely, because of the potential effects of spacing on the children.%
+\footnote{
+In principle, the mother could also be affected, but the results on mother's 
+anthropometric status are mixed and there appear to be no effect on mortality 
+\citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
+}
 It has, for example, been suggested that child ``quality'' might increases with spacing 
@@
 out of the labor market more costly and on the other hand increases how productive the 
-mother is in childrearing. [TK Behrman et al. paper on mother's education in India]
+mother is in childrearing. 
+For child quality measures such as IQ and education there is, to my knowledge, no evidence 
+from developing countries.%
+\footnote{
+The evidence from developed countries is mixed
+\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
+}
 
-One aspect of child ``quality'' where is is a strong effect of spacing is child health
-and mortality, with most of the research finding that shorter spacing leads to worse
-health and higher mortality for children, especially for very short intervals of 24 months 
-or less \citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
+For one crucial aspect of child quality---health and mortality---shorter spacing 
+do lead to worse outcomes, especially for very short intervals of 24 months or less,
+although this effect is strongly moderated by maternal education
+\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
 \footnote{
-There is evidence in countries as diverse as Bangladesh, Brazil, El Salvadore, India,
-and Pakistan of worse health outcomes and a higher mortality risk the shorter the birth
-interval
-\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,
-Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,
-Ghosh2018}.
-This is different from the effect of the underlying mortality risk on birth spacing.
-The expected effect of mortality risk---ignoring the effect of shorter spacing on mortality 
-risk---is to shorten birth spacing to get to the ideal number of children earlier.
-There is little empirical evidence for this type of effect 
-\citep{Newman1983,Newman1988,Bhalotra2008}.
+This is different from the potential effect of the underlying mortality risk on birth 
+spacing, which---ignoring the effect of shorter spacing on mortality risk---is to shorten 
+birth spacing to get to the ideal number of children earlier.
+There is little empirical evidence for this effect \citep{Newman1983,Newman1988,Bhalotra2008}.
 }
-Hence, if parents realize that having children close together increase the children's
-mortality risk, they would prefer to space births further apart to lower mortality risk
-(although possibly not very long since the mortality risk involves a trade-off between the
-cost of births and the benefit of having a child).
-Furthermore, the effects of short spacing on child mortality are strongly moderated by
-maternal education, and even very short spacing has relatively low mortality for women
-with secondary or tertiary education \citep{Whitworth2002,Molitoris2019}.
+Hence, if parents realize short birth spacing increase their children's mortality risk, 
+they likely prefer to space births further apart.
+However, since women with secondary or tertiary education show relatively low mortality 
+risk for their children, even with very short spacing is associated, this effect should
+diminish with education level.
 
-The mother may also be affected by the length of the birth intervals, although the
-results on mother's anthropometric status are mixed and there appear to be no
-effect on maternal mortality \citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
-For India, there is, however, evidence that women with first-born girls are more likely to 
-have anemia, possibly because short birth spacing can resulting in maternal depletion 
-\citep{Milazzo2018}.
-
-Third, having and rearing children involves both direct and time costs, and economic factors 
-can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
-These economic factors can broadly be divided into 
+Third, having and rearing children involves both direct and time costs, and economic 
+factors can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
+The economic factors can broadly be divided into 
 the effects of price and income shocks,
@@
 and economies of scale considerations.
-There is a substantial amount of research on all these areas, although the majority is for
-developed countries.
 
-The expected effect of economies of scale in childrearing is to shorten the interval between 
-births.
-Childbearing and rearing is intensive in the mother's time, but taking care of two young
-children is not twice as time consuming as taking care of one child 
+The expected effect of economies of scale in childrearing---childbearing and rearing is
+time intensive, but taking care of two young children is not twice as time consuming as 
+taking care of one child---is to shorten the interval between births
 \citep{Vijverberg1982,Espenshade1984}.
-Hence, if childbearing and rearing requires the mother to reduce her participation in productive 
-activities, parents can lower the cost of children by shorten birth spacing and, thereby, reduce
-the amount of time the mother has to be away from productive activities.
-In this set-up women with higher education will both have lower fertility and shorter
+To the extent that childbearing and rearing requires the mother to reduce her participation 
+in productive activities, parents can lower the cost of children by shorten birth spacing 
+thereby reducing the amount of time the mother is away from productive activities.
+In this set-up, women with higher education will both have lower fertility and shorter
 spacing than women with lower education because of the higher opportunity cost of time 
 \citep{Ross1974,Newman1981,Newman1984}.
-The extent to which this type of economies of scale is important depends on the extent to
-which having children affects the mother's productive activities.
-If she mainly works at home there likely is going to be less of an incentive to space 
-children for this reason than if she is part of the labor force outside the home.
-Similarly, higher household income, holding the mother's income contanst, reduces the incentive 
-to space births for this reason.
+If the mother mainly works at home there is less incentive to space children for this 
+reason and, similarly, higher household income, holding the mother's income contanst, 
+reduces the incentive to space births for this reason.
 
-In the absense of perfect capital markets, theory suggests that the steeper the parents' income 
-profile over time, the longer the spacing between births 
+In the absense of perfect capital markets, theory predicts that the steeper the parents'
+life-time income profile, the longer the spacing between births, which suggests that 
+with development we should see a general increase in spacing across education 
+groups and that this increase in spacing should be stronger with increasing education levels
 \citep{Heckman1976,Wolpin1984,Newman1988}.
-The idea is that although parents would prefer to have their children as early as possible to
-enjoy them for longer there is also a direct cost to children.
-At the early stage of life income is low, which means that the marginal utility of consumption 
-is higher making parents less willing to give up consumption now to have a child, compare to 
-later when they know that their income will be higher.
-There is evidence that---at least for first births---there is, indeed, an effect of the income
-profile over time \citep{Newman1984,Happel1984}.
-
-There are two implications of this theoretical results.
-First, we should see an general increase in spacing across education groups to the extent that
-development lead to a steeper income profile.
-[This does require that economic development is associated with steeper income profiles;
-not sure if anybody looked at this.
-The lower fertility even for low education women does suggest that income is higher,
-but does not, by itself, say anything about the age profile in income.]
-Second, the increase in spacing should be stronger with increasing education levels.
-In other words, we should see a general increase in spacing, and this increase should be
-larger the higher the education level.
+The idea is that although parents would prefer to have their children as early as possible 
+to enjoy them for longer, there is also a direct cost to children.
+Early on income is low, which means that the marginal utility of consumption is higher 
+making parents less willing to give up consumption now to have a child, compare to later 
+when they know that their income will be higher \citep{Newman1984,Happel1984}.
 
@@
 
-Finally, the discussion has so far assumed that children are identical, except for any potential
-differences that arise from differences in spacing, but there is substantial evidence that the 
-sex composition of previous children affect birth spacing.
-For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
-a boy as the last-born child, significantly increase the duration to next birth,
+Finally, the discussion has so far assumed that children are identical---except for any 
+potential differences that arise from differences in spacing---but there is substantial 
+evidence that the sex composition of previous children affect birth spacing, with the
+absence of boys significantly decreasing the duration to next birth
 \citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
 \footnote{
-There is also evidence of differential stopping behavior, with an additional child more likely the
-fewer sons a family has 
-\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
-Other countries show a similar pattern
-\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
-Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
-absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
-\citep{Rossi2015}.
+There is also evidence of differential stopping behavior, with an additional child more 
+likely the fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
 }
 
-It is not immediately obvious that we should expect a result like this from a theoretical
-standpoint.
+It is not obvious that we should expect this result from a theoretical standpoint.
 If, as discussed above, there are potentially significant negative effects of short spacing
@@
 
-[Need some kind of summary of spacing decisions and how they are likely to change
-over time and with increased education]
-
-As other countries like the US have developed, they have seen a progressively longer 
-spacing between births as the proportion of births with very short intervals---less than 
-24 months---have declined substantially \citep{Hotz1997}.
-Most of the these countries do, however, not have the same degree of son preference that
-we see in India.
-
-What are the important factors that determine spacing?
-
-- household income
-- education
-- labor force participation
-- sex selection
-- health (improvements, campaigns)
-
 In summary, female education affects birth spacing through a variety of pathways.
-The main pathway of interest here is the effect of sex selection on spacing.
-However, to understand the effects of the increased use of sex selection over time it
-is important to also understand the other changes that affect birth spacing.
-The most likely factors are the changes in household income/wealth and the improvements
-in health as India has developed.
+The main pathway of interest here is the effect of sex selection on spacing, but 
+to fully understand how sex selection affects spacing we also need to understand 
+the other changes that affect birth spacing over time.
+The most likely factors are the changes in household income and wealth and the 
+improvements in health as India has developed.
 I, therefore, now look at how female education and labor force participation has changed

### 2019-11-25 paper/conceptual_framework.tex
Shorten and edit conceptual framework
Still more than 2,100 words so probably needs to be shorten further.

@@
 
-This section provides a conceptual framework for understanding what determines spacing 
+This section provides a conceptual framework for understanding what determines the  spacing 
 between births.
@@
 then turn to how son preference and sex selection fits into the decisions on spacing.
-Since sex selection is closely linked to education, I pay special attention to the
-the effects of education on spacing.
+Since sex selection and education are closely linked, I pay special attention to how education affects spacing.
 
-In the simplest possible dynamic model of fertility the spacing decision is trivial.
+In the simplest possible dynamic model of fertility, the spacing decision is trivial.
 Assume that parents derive benefits from the presence of children, rather than from 
-the births themselves, that spacing of children by itself does impact parental utility, 
+the births themselves, that spacing of children by itself does impact the parental utility, 
 and that the parents perfectly control when to have children. 
-In this set up, the optimal decision is then to have the children as early as possible 
+In this model, the optimal decision is then to have the children as early as possible 
 \citep{Newman1988}.
-The simplest model clearly does not fit the observed spacing patterns, which suggests 
+The simplest model does not fit the observed spacing patterns, which suggests 
 that one or more of the assumptions in the simple model are wrong.
 
-First, parents do not perfectly control the timing of births, but instead decide on the
+First, parents do not entirely control the timing of births, but rather decide on the
 levels of sexual activity and contraceptive effort, which, in turn, affect the 
@@
 
-The decisions on sexual activity and contraceptive effort are moderated by fecundity,
-determined by factors such as age and health of the mother, and the knowledge of and 
-access to contraceptive technology.
-There is evidence from ``natural fertility'' populations that increasing number of 
-children is associated with shorter spacing and that birth intervals increase 
+Couples make decisions on sexual activity and contraception, taking into account fecundity, determined by factors such as age and health of the mother, and their knowledge of and access to contraceptive technology.
+There is evidence from ``natural fertility'' populations that higher fertility is associated with shorter spacing and that birth intervals increase 
 with parity \citep{Henry1961,Leridon1977}.
 
-Age and health of the mother are, however, unlikely to be important factors in changes
+Age and health of the mother are, however, unlikely to be significant factors in changes
 in spacing over time or across education levels in India for the period covered, since
-there is little evidence that women's health and nutritional status substantially affects 
+there is little evidence that women's health and nutritional status substantially affect 
 spacing, outside of direct famine conditions \citep{Huffman1987,John1987,lindstrom99}.
-The Maharashtra drought occurred in 1970--1973 and would, therefore, only affect the first
+The Maharashtra drought occurred in 1970--1973 and would, therefore, only impact the first
 year or two of the data.
-Furthermore, I only examine spacing up to parity fourth, and age of the mother is,
-therefore, unlikely to be a concern when it comes to fecundity, even though better 
-educated women are, on average, older when they marry.
+Furthermore, I only examine spacing up to parity fourth, and the age of the mother is,
+therefore, unlikely to be a concern when it comes to fecundity, even though better -educated women are, on average, older when they marry.
 
@@
 modern contraceptives on birth spacing.
-On one hand, in the absence of modern contraceptive technologies, parents may try to 
+On the one hand, in the absence of modern contraceptive technologies, parents may try to 
 avoid overshooting their desired number of children by spacing their children further apart.
-Increased reliability of access to and effectiveness of contraceptives then lead to 
-shorter intervals between births because parents are more certain of effectively
+Increased reliability of the access to and effectiveness of contraceptives then lead to 
+shorter intervals between births because parents are more confident of effectively
 stopping childbearing when they reach their preferred number of children and having
@@
 presence of children for longer as discussed above \citep{Keyfitz1971,Heckman1976}.
-On the other hand, when contraceptives are effective we would expect some birth 
-intervals to be shorter than ideal in the sense discussed below through simple random
+On the other hand, when contraceptives are effective, we would expect some birth 
+intervals to be shorter than ideal, as discussed below, through simple random
 variation.
-With increased reliability of access to and effectiveness of contraceptives, parents 
+With increased reliability of the  access to and effectiveness of contraceptives, parents 
 would better be able to avoid too short spacing between birth and average spacing
@@
 Furthermore, even in the absence of modern contraceptives, families appear able to time or 
-at least postpone births when faced with strong enough incentives 
+at least postpone births when they have substantial enough incentive 
 \citep{Jayachandran2011,Alam2018}.
 
-Second, parents may care about the spacing between birth either in its own right or, 
-more likely, because of the potential effects of spacing on the children.%
+Second, parents may care about the spacing between birth because of the potential effects of spacing on the children.%
 \footnote{
-In principle, the mother could also be affected, but the results on mother's 
-anthropometric status are mixed and there appear to be no effect on mortality 
+In principle, the mother could also be affected, but the results
+so are mixed on mothers' 
+anthropometric status, and there appears to be no effect on mortality 
 \citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
 }
-It has, for example, been suggested that child ``quality'' might increases with spacing 
+One theory is that child ``quality'' might increases with spacing 
 because the amount of parental attention increases with spacing
@@
 In this case, birth spacing should increase in family income, while the effect of maternal 
-education is ambiguous since higher education on one hand makes the mother's time spent 
+education is ambiguous since higher education, on the one hand, makes the mother's time spent 
 out of the labor market more costly and on the other hand increases how productive the 
 mother is in childrearing. 
-For child quality measures such as IQ and education there is, to my knowledge, no evidence 
+For child quality measures such as IQ and education, there is, to my knowledge, no evidence 
 from developing countries.%
@@
 For one crucial aspect of child quality---health and mortality---shorter spacing 
-do lead to worse outcomes, especially for very short intervals of 24 months or less,
-although this effect is strongly moderated by maternal education
+does lead to worse outcomes, especially for very short intervals of 24 months or less,
+although this effect decreases with maternal education
 \citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
 \footnote{
-This is different from the potential effect of the underlying mortality risk on birth 
-spacing, which---ignoring the effect of shorter spacing on mortality risk---is to shorten 
+It is also possible the underlying mortality risk affects birth 
+spacing.
+The predicted outcome then---ignoring the effect of shorter spacing on mortality risk---would be to shorten 
 birth spacing to get to the ideal number of children earlier.
@@
 }
-Hence, if parents realize short birth spacing increase their children's mortality risk, 
+Hence, if parents realize short birth spacing increases their children's mortality risk, 
 they likely prefer to space births further apart.
@@
 factors can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
-The economic factors can broadly be divided into 
-the effects of price and income shocks,
+I divide the economic factors into the effects of price and income shocks,
 the expected income trajectory of the husband and wife,
@@
 
-The expected effect of economies of scale in childrearing---childbearing and rearing is
-time intensive, but taking care of two young children is not twice as time consuming as 
-taking care of one child---is to shorten the interval between births
+The expected effect of economies of scale in childrearing, which can arise, for example, because
+childbearing and rearing are time-intensive, but taking care of two young children does not take 
+twice as much time as taking care of one child, is shorter intervals between births
 \citep{Vijverberg1982,Espenshade1984}.
-To the extent that childbearing and rearing requires the mother to reduce her participation 
-in productive activities, parents can lower the cost of children by shorten birth spacing 
+To the extent that children require the mother to reduce her participation 
+in productive activities, parents can lower the cost of children by shortening birth spacing, 
 thereby reducing the amount of time the mother is away from productive activities.
-In this set-up, women with higher education will both have lower fertility and shorter
+In this case, women with higher education will both have lower fertility and shorter
 spacing than women with lower education because of the higher opportunity cost of time 
 \citep{Ross1974,Newman1981,Newman1984}.
-If the mother mainly works at home there is less incentive to space children for this 
-reason and, similarly, higher household income, holding the mother's income contanst, 
+If the mother mainly works at home, there is less incentive to space children for this 
+reason and, similarly, higher household income, holding the mother's income constant, 
 reduces the incentive to space births for this reason.
 
-In the absense of perfect capital markets, theory predicts that the steeper the parents'
-life-time income profile, the longer the spacing between births, which suggests that 
-with development we should see a general increase in spacing across education 
+In the absence of perfect capital markets, theory predicts that the steeper the parents'
+lifetime income profile, the longer the spacing between births, which suggests that 
+with economic development we should see a general increase in spacing across education 
 groups and that this increase in spacing should be stronger with increasing education levels
@@
 to enjoy them for longer, there is also a direct cost to children.
-Early on income is low, which means that the marginal utility of consumption is higher 
+Early on income is low, which means that the marginal utility of consumption is higher, 
 making parents less willing to give up consumption now to have a child, compare to later 
@@
 
-The income profile argument assumes that parents know their future income, but 
-shocks to income and prices may also affect spacing, with temporary higher cost of women's time
+The income profile argument assumes that parents know their future income, but income and price shocks may also affect spacing. A temporary, higher cost of women's time
 and other inputs into children together with lower income temporarily decreasing fertility 
-and, thereby, increase spacing between births \citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
-It is likely that the risk of income shocks decrease with increasing education, although it
-is unclear the extent to which exposure to other types of shocks that might impact the timing
-of birth is affected by education.
+and, thereby, increase the spacing between births \citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
+Increasing education likely reduces the risk of income shocks, but the effect on other types of shocks that might impact the spacing is unclear.
 
 Finally, the discussion has so far assumed that children are identical---except for any 
-potential differences that arise from differences in spacing---but there is substantial 
-evidence that the sex composition of previous children affect birth spacing, with the
+potential differences that arise from spacing---but there is substantial 
+evidence that the sex composition of previous children affects birth spacing, with the
 absence of boys significantly decreasing the duration to next birth
@@
 
-It is not obvious that we should expect this result from a theoretical standpoint.
-If, as discussed above, there are potentially significant negative effects of short spacing
-parents who choose short spacing in the absence of a boy lowers the survival probabilty of
-the next child, including a boy if the next child is a boy.
+It is not, however, immediately apparent that we should expect shorter spacing in the absence 
+of boys, if, as discussed above, short spacing lowers the survival probability of the next child.
 There are two possibilities for why parents might still try to conceive sooner in the 
@@
 parents have---at least some---control over the timing of birth.
-Hence, it is unlikely that the differences in spacing come about by random chance.
+Hence, it is unlikely that the variations in spacing come about by random chance.
 In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
@@
 }
-First, it is possible that parents do not, in fact, realize that short spacing is potentially
-detrimental to the next child's health.
-Second, parents realize that short spacing has negative health effects, but have a strong
-enough son preference that they are willing to divert substantial resources to investing
-in the next child's health if it is a boy and that these investments can compensate for 
-the negative effects.
-[Are there any other ones that might explain the pattern?
-    - biological? this would have to work off the sex of only the last child, so that
-    spacing after girls is naturally shorter.
-    - parents care so much about having a son sooner that they are willing to accept a 
-    higher mortality risk.
-    - ??
-    ]
+One possibility is that parents do not realize that short spacing is potentially
+detrimental to the next child's health, resulting in high mortality for both boys and girls 
+born after short spacing across all households whether or not they have a son preference.%
+\footnote{
+We may even see a higher likelihood of dying for sons than girls, given that boys 
+have naturally higher mortality.
+}
 
-[has anyone actual done the theory behind the short spacing?
-It would seem that it requires fairly strong assumptions to make it attractive to
-have short spacing.
-Maybe check the Jensen paper on equal treatment]
+The other possibility is that parents realize that short spacing has adverse health effects, 
+but their son-preference is so strong that they are willing to divert substantial resources 
+to the next child's health if it is a boy \emph{and} that these investments can 
+compensate for the adverse effects.
+In this scenario, we should see substantial differences in mortality across sex for short spacing 
+children in the absence of any other boys.
+If a son is born next, his mortality risk should be substantially lower than expected for 
+the spacing duration, and, because this argument relies on redistribution of resources, we should 
+expect to see worse outcomes for all the other children (all girls) in the family.
+If a girl is born next, there are two possible outcomes.
+If parents treat all children/girls the same, we should see a slight worsening in health 
+outcomes because fewer resources are available per child; 
+if they do not, the last girl will have a much lower likelihood of surviving because the 
+parents' incentive is to invest in their prior children rather than the new child.
 
-[can I say anything about which one is true?]
-It is worthwhile thinking a bit about under what circumstances it would be possible to
-identify which of these explanations hold.
-If the first one holds, we should see high mortality for both boys and girls born
-after short spacing across all households whether or not they have a strong son preference.
-In fact, it is possible that we see higher mortality for sons than girls given that boys 
-have naturally higher mortality in the absense of any preference for a given sex.
+As mentioned above, the adverse effects of shorter spacing are strongly mitigated by higher 
+education, which, in theory, allows better-educated women
+to have shorter spacing in the 
+absence of a boy without substantial increasing mortality risk.
+Differences in mortality outcomes across boys and girls are still possible,
+but should not be as large as for less-educated women.
 
-If the second one holds, we should see substantial differences in mortality across
-sex for short spacing children, with the boys having substantially lower mortality risk
-than expected for the spacing length.
+With the introduction of sex selection, parents can avoid the birth of girls, although at the cost of the procedure and having to wait longer until 
+the next child if they abort the fetus.
+The question is, who is likely to use sex selection, when, and why?
 
-If a son is born next:
-The boy should have substantially lower mortality risk than expected for the spacing
-duration.
-Because this argument relies on a redistribution of resources, we should expect to see
-worse outcomes for all the other children in the family.
-This means that the other children (all girls) should do substantially worse.
+Theory suggests that the lower the desired fertility, the 
+higher the likelihood of sex selection \citep{Portner2015b}.
+Simple probabilities drive this prediction:
+in the absence of sex selection, 
+48.8 percent will not have a son when only having one child, 
+23.8 percent for two children, 11.6 percent for three children, 
+5.7 percent for four children, 2.8 percent for five children, 
+and 1.4 percent for six children.
+Furthermore, for a given level of desired fertility, the higher
+the parity, the higher is the likelihood of using sex selection.
 
-If a girl is born next:
-there are a couple of possible outcomes.
-If all children/girls are treated equally, we should see somewhat of a worsening in 
-health outcomes because the available resources are now distributed across more children.
-If children are not treated equally, we should see much worse outcomes for the last
-girl because the parents have an incentive to keep investing in the children they have
-already rather than the new child.
-
-How does education play into this?
-The negative effects of shorter spacing is strongly mitigated by higher education.
-Hence, women with more education are in the position that they can better tolerate short 
-spacing in the absence of a boy and that the potential negative effects on the next child 
-should be much less pronounced.
-Furthermore, the lower mortality risk should show up whether the next child is a boy 
-or a girl.
-It is clearly still possible that there would some difference in mortality outcomes 
-across boys and girls because of a larger investment in the boy once born, but it should
-not be as large.
-
-With the introduction of sex selection parents can now avoid the birth of children with 
-an undesired sex, although at the cost of the procedure and having to wait longer until 
-the next child if the fetus is aborted.
-The use of sex selection impacts the observed birth spacing since, as discussed 
-above, each sex-selective abortions increases the interval between births by six 
-to twelve months.
-The question is who is likely to use sex selection, when, and why?
-
-Theory suggests that the lower the desired fertility the more likely is the use of sex 
-selection \citep{Portner2015b}.
-This is driven by simple probabilities:
-without use of sex selection, the probability of not having a son are 48.8 percent when
-only having one child, 23.8 percent for two children, 11.6 percent for three children, 
-5.7 percent for four children, 2.8 percent for five children, and 1.4 percent for six 
-children.
-Furthermore, given a desired level of fertility, the higher the parity, the higher the
-likelihood of using sex selection.
-Unless parents have a specific preference for a first-born boy, the costs associated with 
-sex selection means that it is better to try for a boy without sex selection first and 
-then use at later parities in the absence of a son as you get closer to the desired 
-fertility.
-
-The higher the cost of prenatal sex determination and the abortion, both in direct cost
-and the possibility of criminal charges, the less use we should see.
-Similarly, any potentially negative effects on the mother and offspring from repeated
-abortions would also tend to reduce the use of sex selection---provided, obviously, that
-parents are aware of these costs.
+The higher the cost of prenatal sex determination and abortion,
+the less use we should see.
+Similarly, any potential adverse effects on the mother and 
+offspring from repeated
+abortions would also tend to reduce the use of sex selection---
+provided that parents are aware of these costs.
 Finally, the more abortions between births, the less the opportunity there is to take
@@
 }
-Women with more education also tend to live in households with higher income,
-which better enables them to access prenatal sex determination and lowers the relative
-costs of using sex selection (both direct and indirect, such the decline in 
-economies of scale with repeated abortions).
+Better-educated women also tend to live in households with higher 
+income, which better enables them to access prenatal sex determination and lowers the relative
+costs of using sex selection.
 
-Given that each abortion increases the spacing between births, it is possible that
-parents may try to conceive even sooner than in the absence of sex selection.
-By conceiving sooner, they would lower the expected cost of foregone economies of scale in 
-childrearing.
-This is especially relevant for better educated women, who, as discussed above, have
-lower mortality risk for offspring born after short spacing.
-If health outcomes for short spacing births has improved over time---as is likely---we
-should see an even stronger push toward shorter spacing for women using sex selection.
+Given the increase in birth spacing with each abortion, parents may try to conceive even sooner to compensate for the potentially longer spacing and, thereby, still take advantage of economies of scale in childrearing.
+By conceiving sooner, they are more likely to be able to take advantage of economies of
+scale in childrearing, even if they have to go through one or more abortions.
+Furthermore, if health outcomes for short spacing births has improved over time---as is 
+likely---we should see an even stronger push toward shorter spacing for women using sex 
+selection.
 
-In summary, female education affects birth spacing through a variety of pathways.
-The main pathway of interest here is the effect of sex selection on spacing, but 
-to fully understand how sex selection affects spacing we also need to understand 
-the other changes that affect birth spacing over time.
-The most likely factors are the changes in household income and wealth and the 
-improvements in health as India has developed.
-I, therefore, now look at how female education and labor force participation has changed
-over time in India.
+In summary, birth spacing is affected by female education through 
+multiple pathways, with the main one of interest here the use of 
+sex selection. But, to fully understand how sex selection affects 
+spacing, we also need to understand the other changes that affect 
+birth spacing over time.
+The most likely factors are the changes in household income and 
+wealth and the improvements in health as India has developed.
+I, therefore, now look at how female education and labor force 
+participation has changed over time in India.

### 2019-11-27 paper/conceptual_framework.tex
Edit and shorten conceptual framework
Below 2,000 words now. Still seems too long.

@@
 
-This section provides a conceptual framework for understanding what determines the  spacing 
-between births.
-I first discuss the main determinants of spacing discussed in the prior research, and 
+This section provides a conceptual framework for understanding what determines  
+birth spacing.
+I first discuss the main determinants of spacing examined in the prior research, and 
 then turn to how son preference and sex selection fits into the decisions on spacing.
-Since sex selection and education are closely linked, I pay special attention to how education affects spacing.
+Since sex selection and education are closely linked, I pay special attention to how 
+education affects spacing.
 
@@
 and that the parents perfectly control when to have children. 
-In this model, the optimal decision is then to have the children as early as possible 
+The optimal decision is then to have the children as early as possible 
 \citep{Newman1988}.
 The simplest model does not fit the observed spacing patterns, which suggests 
-that one or more of the assumptions in the simple model are wrong.
+that one or more of the assumptions are wrong.
 
-First, parents do not entirely control the timing of births, but rather decide on the
-levels of sexual activity and contraceptive effort, which, in turn, affect the 
-likelihood of conceiving.
+First, parents do not entirely control the timing of births, but rather decide on 
+the levels of sexual activity and contraceptive effort, which, in turn, affect the 
+likelihood of conceiving, while taking into account fecundity and their knowledge 
+of and access to contraceptive technology.
 
-Couples make decisions on sexual activity and contraception, taking into account fecundity, determined by factors such as age and health of the mother, and their knowledge of and access to contraceptive technology.
-There is evidence from ``natural fertility'' populations that higher fertility is associated with shorter spacing and that birth intervals increase 
-with parity \citep{Henry1961,Leridon1977}.
-
-Age and health of the mother are, however, unlikely to be significant factors in changes
-in spacing over time or across education levels in India for the period covered, since
-there is little evidence that women's health and nutritional status substantially affect 
-spacing, outside of direct famine conditions \citep{Huffman1987,John1987,lindstrom99}.
+Fecundity determinants, such as age and health of the mother, are, however, unlikely 
+to be significant factors in how spacing changed over time or across education levels 
+in India for the period covered.
+Outside of direct famine conditions, women's health and nutritional status do not 
+appear to affect spacing substantially \citep{Huffman1987,John1987,lindstrom99}.
 The Maharashtra drought occurred in 1970--1973 and would, therefore, only impact the first
@@
 Furthermore, I only examine spacing up to parity fourth, and the age of the mother is,
-therefore, unlikely to be a concern when it comes to fecundity, even though better -educated women are, on average, older when they marry.
+therefore, unlikely to be a concern when it comes to fecundity, even though 
+better-educated women are, on average, older when they marry.
 
-Despite a general belief that better access to and knowledge of contraception should lead
-to longer average spacing, the empirical relationship between contraception use and birth 
-spacing is ambiguous \citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+Despite a general belief that better access to and knowledge of contraception 
+should lead to longer average spacing, the empirical relationship between contraception 
+use and birth spacing is ambiguous 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
 This lack of evidence is consistent with the ambiguous theoretical effect of introducing 
 modern contraceptives on birth spacing.
-On the one hand, in the absence of modern contraceptive technologies, parents may try to 
-avoid overshooting their desired number of children by spacing their children further apart.
+On the one hand, in the absence of high-efficacy contraceptive technologies, parents may try to 
+avoid overshooting their desired number of children by spacing their children further apart
+than they would otherwise do.
 Increased reliability of the access to and effectiveness of contraceptives then lead to 
-shorter intervals between births because parents are more confident of effectively
-stopping childbearing when they reach their preferred number of children and having
-the children closer together provide higher utility because parents benefit from the
-presence of children for longer as discussed above \citep{Keyfitz1971,Heckman1976}.
-On the other hand, when contraceptives are effective, we would expect some birth 
-intervals to be shorter than ideal, as discussed below, through simple random
-variation.
-With increased reliability of the  access to and effectiveness of contraceptives, parents 
-would better be able to avoid too short spacing between birth and average spacing
-should go up.
+shorter birth intervals because parents are more confident they can effectively
+stop childbearing when they want \citep{Keyfitz1971,Heckman1976}.
+On the other hand, when contraceptives are ineffective, some birth intervals will
+be shorter than ideal, in the way discussed below, through simple random variation.
+With increased reliability of contraceptive efforts, parents can better avoid too short 
+birth spacing, and average spacing should go up.
 
-To further complicate the relationship between contraception and spacing, the ability to 
-successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, is 
-increasing in education, while there is no difference across education levels 
+To further complicate the relationship between contraception and spacing, the ability 
+to successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, 
+is increasing in education, while there is no difference across education levels 
 when it comes to modern contraceptives such as pills or injectables \citep{Rosenzweig1989}.
-Furthermore, even in the absence of modern contraceptives, families appear able to time or 
-at least postpone births when they have substantial enough incentive 
+Additionally, even in the absence of modern contraceptives, families appear able to 
+time or at least postpone births when they have substantial enough incentive 
 \citep{Jayachandran2011,Alam2018}.
 
-Second, parents may care about the spacing between birth because of the potential effects of spacing on the children.%
+Second, parents may care about the spacing between birth because of the 
+potential effects of spacing on the children.%
 \footnote{
-In principle, the mother could also be affected, but the results
-so are mixed on mothers' 
-anthropometric status, and there appears to be no effect on mortality 
+In principle, the mother could also be affected, but the estimated impact on 
+mothers' anthropometric status is mixed, and there appears to be no 
+effect on mortality 
 \citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
 }
-One theory is that child ``quality'' might increases with spacing 
-because the amount of parental attention increases with spacing
+One theory is that child ``quality'' increases with spacing 
+since parental attention per child increases
 \citep{Zajonc1975,Zajonc1976,Razin1980}.
-In this case, birth spacing should increase in family income, while the effect of maternal 
-education is ambiguous since higher education, on the one hand, makes the mother's time spent 
-out of the labor market more costly and on the other hand increases how productive the 
-mother is in childrearing. 
-For child quality measures such as IQ and education, there is, to my knowledge, no evidence 
-from developing countries.%
-\footnote{
-The evidence from developed countries is mixed
+In this case, birth spacing should increase in family income, while the 
+effect of maternal education is ambiguous since higher education, on the 
+one hand, makes the mother's time spent out of the labor market more 
+costly and on the other hand increases how productive the mother is 
+in childrearing.
+The evidence on spacing's effect on child quality measures such as IQ 
+and education is, however, mixed for developed countries and non-existing 
+for developing countries
 \citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-}
 
 For one crucial aspect of child quality---health and mortality---shorter spacing 
-does lead to worse outcomes, especially for very short intervals of 24 months or less,
-although this effect decreases with maternal education
+does lead to worse outcomes, especially for very short intervals of 24 months 
+or less, although this effect decreases with maternal education
 \citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
 \footnote{
-It is also possible the underlying mortality risk affects birth 
-spacing.
-The predicted outcome then---ignoring the effect of shorter spacing on mortality risk---would be to shorten 
-birth spacing to get to the ideal number of children earlier.
-There is little empirical evidence for this effect \citep{Newman1983,Newman1988,Bhalotra2008}.
+The underlying mortality risk could also affect birth spacing, but
+there is little empirical evidence for this 
+\citep{Newman1983,Newman1988,Bhalotra2008}.
 }
-Hence, if parents realize short birth spacing increases their children's mortality risk, 
+If parents realize short birth spacing increases their children's mortality risk, 
 they likely prefer to space births further apart.
-However, since women with secondary or tertiary education show relatively low mortality 
-risk for their children, even with very short spacing is associated, this effect should
-diminish with education level.
+However, this effect should diminish with education level since women with 
+secondary or tertiary education experience relatively low mortality risk for 
+their children, even with very short spacing is associated.
 
-Third, having and rearing children involves both direct and time costs, and economic 
-factors can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
+Third, parents incur both direct and time costs when they have children, 
+and economic factors can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
 I divide the economic factors into the effects of price and income shocks,
@@
 
-The expected effect of economies of scale in childrearing, which can arise, for example, because
-childbearing and rearing are time-intensive, but taking care of two young children does not take 
-twice as much time as taking care of one child, is shorter intervals between births
+The expected effect of economies of scale in childrearing, which, for example, 
+can arise because taking care of two young children does not take twice as much 
+time as taking care of one child, is to shorten intervals between births
 \citep{Vijverberg1982,Espenshade1984}.
-To the extent that children require the mother to reduce her participation 
-in productive activities, parents can lower the cost of children by shortening birth spacing, 
-thereby reducing the amount of time the mother is away from productive activities.
-In this case, women with higher education will both have lower fertility and shorter
-spacing than women with lower education because of the higher opportunity cost of time 
+To the extent that children require the mother to do less market work, parents 
+can lower the cost of children by reducing birth spacing.
+In this case, better-educated women will both have lower fertility and shorter
+spacing than less-educated women because of their higher opportunity cost of time 
 \citep{Ross1974,Newman1981,Newman1984}.
-If the mother mainly works at home, there is less incentive to space children for this 
-reason and, similarly, higher household income, holding the mother's income constant, 
-reduces the incentive to space births for this reason.
+However, if the mother mainly works at home or as household income increases, there 
+is less incentive to space children for this reason.
 
-In the absence of perfect capital markets, theory predicts that the steeper the parents'
-lifetime income profile, the longer the spacing between births, which suggests that 
-with economic development we should see a general increase in spacing across education 
-groups and that this increase in spacing should be stronger with increasing education levels
+In the absence of perfect capital markets, theory predicts that the steeper 
+the parents' lifetime income profile, the longer the spacing between births, 
+which suggests that with economic development we should see a general increase 
+in spacing across education groups and that this increase in spacing should be 
+stronger with increasing education levels
 \citep{Heckman1976,Wolpin1984,Newman1988}.
-The idea is that although parents would prefer to have their children as early as possible 
-to enjoy them for longer, there is also a direct cost to children.
-Early on income is low, which means that the marginal utility of consumption is higher, 
-making parents less willing to give up consumption now to have a child, compare to later 
-when they know that their income will be higher \citep{Newman1984,Happel1984}.
+The idea is that although parents would prefer to have their children as early 
+as possible to enjoy them for longer, there is also a direct cost to children.
+Early on income is low, which means that the marginal utility of consumption is 
+higher, making parents less willing to give up consumption now to have a child, 
+compare to later when they know that their income will be higher 
+\citep{Newman1984,Happel1984}.
 
-The income profile argument assumes that parents know their future income, but income and price shocks may also affect spacing. A temporary, higher cost of women's time
-and other inputs into children together with lower income temporarily decreasing fertility 
-and, thereby, increase the spacing between births \citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
-Increasing education likely reduces the risk of income shocks, but the effect on other types of shocks that might impact the spacing is unclear.
+The income profile argument assumes that parents know their future income, 
+but income and price shocks may also affect spacing. 
+A temporary, higher cost of women's time or a lower household income, will 
+temporarily decrease fertility and, thereby, increase birth spacing 
+\citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
+Increasing education likely reduces the risk of income shocks, but the 
+effect on other types of shocks that might impact the spacing is unclear.
 
-Finally, the discussion has so far assumed that children are identical---except for any 
-potential differences that arise from spacing---but there is substantial 
-evidence that the sex composition of previous children affects birth spacing, with the
+Finally, the discussion has so far assumed that children are identical---except 
+for any differences that arise from spacing---but there is substantial evidence 
+that the sex composition of previous children affects birth spacing, with the
 absence of boys significantly decreasing the duration to next birth
-\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
+\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.
+There is also evidence of differential stopping behavior, with an additional child 
+more likely the fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
+
+It is not, however, immediately apparent that we should expect shorter spacing in 
+the absence of boys, if short spacing lowers the survival probability of the 
+next child, as discussed above.
+There are two potential reasons why parents might still try to conceive sooner 
+in the absence of boys.%
 \footnote{
-There is also evidence of differential stopping behavior, with an additional child more 
-likely the fewer sons a family has 
-\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
-}
-
-It is not, however, immediately apparent that we should expect shorter spacing in the absence 
-of boys, if, as discussed above, short spacing lowers the survival probability of the next child.
-There are two possibilities for why parents might still try to conceive sooner in the 
-absence of boys.%
-\footnote{
-The fact that there are significant differences in spacing by sex composition indicates that
-parents have---at least some---control over the timing of birth.
-Hence, it is unlikely that the variations in spacing come about by random chance.
-In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
-access to family planning \citep{Rahman1993}.
+The significant differences in spacing by sex composition indicate that
+parents control the timing of birth, at least to some extent.
+In Matlab, the effect of son preference on birth spacing is stronger in 
+areas with better access to family planning \citep{Rahman1993}.
 }
 One possibility is that parents do not realize that short spacing is potentially
-detrimental to the next child's health, resulting in high mortality for both boys and girls 
-born after short spacing across all households whether or not they have a son preference.%
+detrimental to the next child's health, resulting in high mortality for both boys 
+and girls born after short spacing across all households whether or not they have 
+a son preference.%
 \footnote{
@@
 
-The other possibility is that parents realize that short spacing has adverse health effects, 
-but their son-preference is so strong that they are willing to divert substantial resources 
-to the next child's health if it is a boy \emph{and} that these investments can 
-compensate for the adverse effects.
-In this scenario, we should see substantial differences in mortality across sex for short spacing 
-children in the absence of any other boys.
-If a son is born next, his mortality risk should be substantially lower than expected for 
-the spacing duration, and, because this argument relies on redistribution of resources, we should 
-expect to see worse outcomes for all the other children (all girls) in the family.
-If a girl is born next, there are two possible outcomes.
-If parents treat all children/girls the same, we should see a slight worsening in health 
-outcomes because fewer resources are available per child; 
-if they do not, the last girl will have a much lower likelihood of surviving because the 
-parents' incentive is to invest in their prior children rather than the new child.
+The other possibility is that parents realize that short spacing has adverse 
+health effects, but their son-preference is so strong that they are willing to 
+divert substantial resources to the next child if it is a boy.
+Assuming that these investments can compensate for the adverse effects,
+we should see significant differences in mortality across sex for short-spacing 
+children in the absence of boys.
+If a son is born, his mortality risk should be substantially lower than expected 
+for the spacing duration, and we should expect worse outcomes for the other 
+children (all girls).
+If a girl is born, there are two possible outcomes.
+If parents treat all children/girls the same, we should see a slight worsening in 
+health outcomes because fewer resources are available per child; 
+if they do not, the last girl will have a much lower likelihood of surviving 
+because the parents' incentive is to invest in their prior children rather than 
+the new child.
 
-As mentioned above, the adverse effects of shorter spacing are strongly mitigated by higher 
-education, which, in theory, allows better-educated women
-to have shorter spacing in the 
-absence of a boy without substantial increasing mortality risk.
+As mentioned above, the adverse effects of shorter spacing are strongly mitigated 
+by higher education, which, in theory, allows better-educated women to have shorter
+spacing in the absence of a boy without substantial increasing mortality risk.
 Differences in mortality outcomes across boys and girls are still possible,
@@
 
-With the introduction of sex selection, parents can avoid the birth of girls, although at the cost of the procedure and having to wait longer until 
+With the introduction of sex selection, parents can avoid the birth of girls, 
+although at the cost of the procedure and having to wait longer until 
 the next child if they abort the fetus.
@@
 the less use we should see.
-Similarly, any potential adverse effects on the mother and 
-offspring from repeated
-abortions would also tend to reduce the use of sex selection---
-provided that parents are aware of these costs.
-Finally, the more abortions between births, the less the opportunity there is to take
-advantage of any economies of scale in childrearing.
+Similarly, any potential adverse effects on the mother and offspring 
+from repeated abortions would also tend to reduce the use of sex 
+selection---provided that parents are aware of these costs.
+Finally, the more abortions between births, the less the opportunity 
+there is to take advantage of any economies of scale in childrearing.
 
-The use of sex selection in India increases with education and is higher in urban
-areas than in rural
+The use of sex selection in India increases with education and is higher 
+in urban areas than in rural
 \citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
 Jayachandran2017}.
-Women with more education generally have lower desired fertility, either because of the
-higher opportunity cost of time or because of other changes in the preferred number of
-children.%
+Women with more education generally have lower desired fertility, either 
+because of the higher opportunity cost of time or because of other changes 
+in the preferred number of children.%
 \footnote{
@@
 Better-educated women also tend to live in households with higher 
-income, which better enables them to access prenatal sex determination and lowers the relative
-costs of using sex selection.
+income, which better enables them to access prenatal sex determination 
+and lowers the relative costs of using sex selection.
 
-Given the increase in birth spacing with each abortion, parents may try to conceive even sooner to compensate for the potentially longer spacing and, thereby, still take advantage of economies of scale in childrearing.
-By conceiving sooner, they are more likely to be able to take advantage of economies of
-scale in childrearing, even if they have to go through one or more abortions.
-Furthermore, if health outcomes for short spacing births has improved over time---as is 
-likely---we should see an even stronger push toward shorter spacing for women using sex 
-selection.
+Given the increase in birth spacing with each abortion, parents may try to 
+conceive even sooner to compensate for the potentially longer spacing and, 
+thereby, still take advantage of economies of scale in childrearing.
+Furthermore, if health outcomes for short spacing births have improved over 
+time---as is likely---we should see an even stronger push toward shorter 
+spacing for women using sex selection.
 
@@
 multiple pathways, with the main one of interest here the use of 
-sex selection. But, to fully understand how sex selection affects 
-spacing, we also need to understand the other changes that affect 
-birth spacing over time.
+sex selection. 
+But, to fully understand how sex selection affects spacing, we also 
+need to understand the other changes that affect birth spacing over time.
 The most likely factors are the changes in household income and 

### 2019-12-07 paper/sex_selection_spacing-ver3.tex
Initial add of conceptual framework to main paper

--- 2019-03-31 paper/sex_selection_spacing-ver2.tex
@@
 %------------------------------------------------------------------------------------
+
+\section{Birth Spacing: Mechanisms and Findings}
+
+This section provides a conceptual framework for understanding what determines  
+birth spacing.
+I first discuss the main determinants of spacing examined in the prior research, and 
+then how son preference and sex selection fits into the spacing decisions.
+Since sex selection and education are closely linked, I pay special attention to how 
+education affects spacing.
+
+In the simplest possible dynamic model of fertility, the spacing decision is trivial.
+Assume that parents derive benefits from the presence of children, not their births, 
+that spacing of children does impact parents' utility, 
+and that the parents fully control when to have children. 
+The optimal decision then is to have the children as early as possible 
+\citep{Newman1988}.
+The simplest model does not fit the observed spacing patterns, which suggests 
+that one or more of the assumptions are wrong.
+
+First, parents do not entirely control the timing of births, but rather decide on 
+the levels of sexual activity and contraceptive effort, which, in turn, affect the 
+likelihood of conceiving, while taking into account fecundity and their knowledge 
+of and access to contraceptive technology.
+
+Fecundity determinants, such as age and health of the mother, are, however, unlikely 
+to be significant factors in how spacing changed over time or across education levels 
+in India for the period covered.
+Outside of direct famine conditions, women's health and nutritional status do not 
+appear to affect spacing substantially \citep{Huffman1987,John1987,lindstrom99}.
+The Maharashtra drought occurred in 1970--1973 and would, therefore, only impact the first
+year or two of the data.
+Furthermore, I only examine spacing up to parity fourth, and the age of the mother is,
+therefore, unlikely to be a concern when it comes to fecundity, even though 
+better-educated women are, on average, older when they marry.
+
+Despite a general belief that better access to and knowledge of contraception 
+should lengthen average spacing, the empirical relationship between contraception 
+use and birth spacing is ambiguous 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+This lack of evidence is consistent with the ambiguous theoretical effect of introducing 
+modern contraceptives on birth spacing.
+On the one hand, in the absence of high-efficacy contraceptive technologies, parents may 
+try to avoid overshooting their desired number of children by spacing their children 
+further apart than they would otherwise do.
+Increased reliability of the access to and effectiveness of contraceptives then lead to 
+shorter birth intervals because parents are more confident they can effectively
+stop childbearing when they want \citep{Keyfitz1971,Heckman1976}.
+On the other hand, through simple random variation, when contraceptives are ineffective, 
+some birth intervals will be shorter than ideal, in the way discussed below.
+With increased reliability of contraceptive efforts, parents can better avoid too short 
+birth spacing, and average spacing should go up.
+
+To further complicate the relationship between contraception and spacing, the ability 
+to successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, 
+is increasing in education, while there is no difference across education levels 
+when it comes to modern contraceptives such as pills or injectables \citep{Rosenzweig1989}.
+Additionally, even in the absence of modern contraceptives, families appear able to 
+time or at least postpone births when they have substantial enough incentive 
+\citep{Jayachandran2011,Alam2018}.
+
+Second, parents may care about the spacing between birth because of the 
+potential effects of spacing on the children.%
+\footnote{
+In principle, the mother could also be affected, but the estimated impact on 
+mothers' anthropometric status is mixed, and there appears to be no 
+effect on mortality 
+\citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
+}
+One theory is that child ``quality'' increases with spacing 
+since parental attention per child increases
+\citep{Zajonc1975,Zajonc1976,Razin1980}.
+In this case, birth spacing should increase in family income, while the 
+effect of maternal education is ambiguous since higher education, on the 
+one hand, makes the mother's time spent out of the labor market more 
+costly and on the other hand increases how productive the mother is 
+in childrearing.
+The evidence on spacing's effect on child quality measures such as IQ 
+and education is, however, mixed for developed countries and non-existing 
+for developing countries
+\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
+
+For one crucial aspect of child quality---health and mortality---shorter spacing 
+does lead to worse outcomes, especially for very short intervals of 24 months 
+or less, although this effect decreases with maternal education
+\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
+\footnote{
+The underlying mortality risk could also affect birth spacing, but
+there is little empirical evidence for this 
+\citep{Newman1983,Newman1988,Bhalotra2008}.
+}
+If parents realize short birth spacing increases their children's mortality risk, 
+they likely prefer to space births further apart.
+However, this effect should diminish with education level since women with 
+secondary or tertiary education experience relatively low mortality risk for 
+their children, even with very short spacing is associated.
+
+Third, parents incur both direct and time costs when they have children, 
+and economic considerations can, therefore, affect birth spacing 
+\citep{Hotz1997,Schultz1997}.
+I divide the economic factors into the effects of economies of scale and
+the expected income trajectory of the husband and wife.
+
+The expected effect of economies of scale in childrearing, which, for example, 
+can arise because taking care of two young children does not take twice as much 
+time as taking care of one child, is to shorten intervals between births
+\citep{Vijverberg1982,Espenshade1984}.
+To the extent that children require the mother to do less market work, parents 
+can lower the cost of children by reducing birth spacing.
+In this case, better-educated women will both have lower fertility and shorter
+spacing than less-educated women because of their higher opportunity cost of time 
+\citep{Ross1974,Newman1981,Newman1984}.
+However, if the mother mainly works at home or as household income increases, there 
+is less incentive to space children for this reason.
+
+In the absence of perfect capital markets, theory predicts that the steeper 
+the parents' lifetime income profile, the longer the spacing between births, 
+which suggests that with economic development we should see a general increase 
+in spacing across education groups and that this increase in spacing should be 
+stronger with increasing education levels
+\citep{Heckman1976,Wolpin1984,Newman1988}.
+The idea is that although parents would prefer to have their children as early 
+as possible to enjoy them for longer, there is also a direct cost to children.
+Income is low early on, which means that the marginal utility of consumption is 
+higher, making parents less willing to give up consumption to have a child, 
+compare to later when they know that their income will be higher 
+\citep{Newman1984,Happel1984}.
+
+Finally, the discussion has so far assumed that children are identical---except 
+for any differences that arise from spacing---but there is substantial evidence 
+that the sex composition of previous children affects birth spacing, with the
+absence of boys significantly decreasing the duration to next birth
+\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.
+There is also evidence of differential stopping behavior, with an additional child 
+more likely the fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
+
+If short spacing lowers the survival probability of the next child, as discussed above,
+it is not, however, apparent that we should expect shorter spacing in the absence of boys.
+There are two potential reasons why parents might still try to conceive sooner 
+in the absence of boys.%
+\footnote{
+The significant differences in spacing by sex composition indicate that
+parents control the timing of birth, at least to some extent.
+In Matlab, the effect of son preference on birth spacing is stronger in 
+areas with better access to family planning \citep{Rahman1993}.
+}
+One possibility is that parents do not realize that short spacing is potentially
+detrimental to the next child's health, resulting in high mortality for both boys 
+and girls born after short spacing across all households.
+
+The other possibility is that parents realize that short spacing has adverse 
+health effects, but their preference for sons is so strong that they are willing to 
+divert substantial resources to the next child if it is a boy.
+Assuming that these investments can compensate for the adverse effects,
+we should see significant differences in mortality across sex for short-spacing 
+children in the absence of boys.
+If a son is born, his mortality risk should be substantially lower than expected 
+for the spacing duration, and we should expect worse outcomes for the other 
+children (all girls).
+If a girl is born, there are two possible outcomes.
+If parents treat all children/girls the same, we should see a slight worsening in 
+health outcomes because fewer resources are available per child; 
+if they do not, the last girl will have a much lower likelihood of surviving 
+because the parents' incentive is to invest in their prior children rather than 
+the new child.
+
+With the adverse effects of shorter spacing strongly mitigated by higher education,
+better-educated women can, in theory, have shorter spacing in the absence of a boy 
+without substantial increasing mortality risk.
+Differences in mortality outcomes across boys and girls are still possible,
+but should not be as large as for less-educated women.
+
+With the introduction of sex selection, parents can avoid the birth of girls, 
+although at the cost of the procedure and having to wait longer until 
+the next child if they abort the fetus.
+
+Theory suggests that sex selection increases with lower desired fertility, and, for a 
+given desired number of children, the higher the parity \citep{Portner2015b}.
+The increased use of sex selection in India with education and in urban
+areas is consistent with a lower desired fertility for both groups,
+either because of the higher cost of children or because of other
+changes in the preferred number of children
+\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
+Jayachandran2017}.%
+\footnote{
+Stronger son preference could also contribute, but better-educated women 
+have declining stated son preference over time \citep{bhat03,pande07}.
+}
+
+The higher the cost of prenatal sex determination and abortion, the less use we should 
+see.
+Similarly, any potential adverse effects on the mother and offspring 
+from repeated abortions should also reduce the use of sex selection---provided that 
+parents are aware of these costs.
+Furthermore, the more abortions between births, the less the parents can take advantage 
+of economies of scale.
+Better-educated women tend to live in households with higher income, which better enables 
+them to access prenatal sex determination and lowers the relative costs of using sex 
+selection.
+
+Given the increase in birth spacing with each abortion, parents may try to 
+conceive even sooner to compensate for the potentially longer spacing and, 
+thereby, still take advantage of economies of scale in childrearing.
+Furthermore, if health outcomes for short spacing births have improved over 
+time---as is likely---we should see an even stronger push toward shorter 
+spacing for women using sex selection.
+
+In summary, birth spacing is affected by female education through 
+multiple pathways, with the main one of interest here the use of 
+sex selection. 
+But, to fully understand how sex selection affects spacing, we also 
+need to understand the other changes that affect birth spacing over time.
+The most likely factors are the changes in household income and 
+wealth and the improvements in health as India has developed.
+I, therefore, examine how female education and labor force 
+participation has changed over time in India.
 

### 2019-12-12 paper/educ_work_over_time.tex
Initial commit of discussion of changes in female education and labor force participation

Female Education and Labor Force Participation in India

There has been substantial improvements in female educational attainment over time.
Figure XX shows the distribution of schooling by birth cohort for urban and rural women 
twenty years or older whether married or not.
The education groups are no education, one to seven years, and eight years or
above.

For rural areas, the percentage of women with no education has gone from around 90 percent
for the 1930s cohorts to less than 20 percent for 1990s cohorts. 
The proportion of women with one to seven years of education has remained remarkably
constant at around ten percent.
The difference is made up by the women with eight or more years of education, who have
gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts.

Female education is higher in urban areas than in rural areas.
Around sixty percent of urban women born in the 1930s had no education, 25 percent had
between one and seven years, and about 15 had eight or more years of education.
The proportion with no education has declined almost to five percent for the latest
cohort, and the proportion with one to seven years of education has shrunk to just over
ten percent.
The result is that close to 80 percent of urban women now have eight or more years of
education.

Despite the increasing level of female education the female labor force participation has
decreased over time.

### 2019-12-17 paper/educ_work_over_time.tex
Begin discussion of falling female labor force participation

@@
 
-Despite the increasing level of female education the female labor force participation has
-decreased over time.
+Even as the level of female education has increased the female labor force participation 
+has decreased over time [should this be by level of education?].
+
+[Discuss recent papers on labor supply in India]
+
+To place my results in context, Figure XX shows the percent of married women who are 
+working at the time of the survey by age group.%
+\footnote{
+This question is the only question on labor force participation consistently available 
+across all four surveys.
+Since the question is asked only of married women it is possible that the overall
+female labor force participation might have developed differently, especially since
+many young, unmarried women have begun working in, for example, the business process 
+outsourcing industry [TK cite Jensen 2012 QJE].
+}
+
+The declines over the the four rounds of the NFHS are in line with what previous
+research has found using other data sets [TK cite Bhargava 2018 and 2019, Chatterjee 2018].
+Finding a decline in labor force participation in the beginning of development is
+in line with the hypothesis of a U-shaped labor force participation as a country
+develop [TK cite Goldin 1994, Chatterjee 2018].
+
+The theories on the relationship between education and birth spacing often works 
+through the changes in the opportunity cost of time. 
+If women are unlikely to work, this makes the predictions that are based on
+opportunity cost less relevant. 
+instead, theories that emphasize income effects or effects of spacing become
+more relevant.

### 2019-12-20 paper/educ_work_over_time.tex
Discuss literature on female labor force participation

--- 2019-12-12 paper/educ_work_over_time.tex
@@
 
-Despite the increasing level of female education the female labor force participation has
-decreased over time.
+Even as the level of female education has increased, the female labor force participation 
+in both urban and rural areas has stagnated or decreased
+\citep{Klasen2015,Afridi2018,Bhargava2018, Chatterjee2018, Bhargava2019}.
+A decline in female labor force participation in the beginning of development is
+consistent with the hypothesis of a U-shaped labor force participation as a country
+develop, although India's female labor force participation is lower than most other
+countries and more in line with countries in the Middle East and North Africa  
+\citep{Goldin1994,Klasen2015,Chatterjee2018}.
+
+[men and women's wages]
+
+Klasen2015
+In line with India’s high growth rates, earnings data form the NSS
+surveys show that real wages roughly doubled between 1987 and 2011 (see
+Fig. S1.1 in the supplemental appendix). In absolute terms, real wages
+increased almost equally for men and women, but the ratio of male to
+female average weekly earnings declined from 1.6 in 1987 to 1.3 in 2011.
+
+[Discuss recent papers on labor supply in India]
+
+To place my results in context, Figure XX shows the percent of married women who are 
+working at the time of the survey by age group.%
+\footnote{
+This question is the only question on labor force participation consistently available 
+across all four surveys.
+For the NFHS-4, it is only asked of women selected for the state samples, so the
+sample size is comparable across all four surveys.
+Furthermore, because the question refers to currently the percentages will be lower than
+what other studies have found.
+Finally, since the question is asked only of married women it is possible that the overall
+female labor force participation might have developed differently, especially since
+many young, unmarried women have begun working in, for example, the business process 
+outsourcing industry, which, in turn, has increased girls' schooling investments
+\citep{Jensen2012}.
+}
+
+The theories on the relationship between education and birth spacing often works 
+through the changes in the opportunity cost of time. 
+If women are unlikely to work, this makes the predictions that are based on
+opportunity cost less relevant. 
+instead, theories that emphasize income effects or effects of spacing become
+more relevant.

### 2019-12-20 paper/educ_work_over_time.tex
Minor edits

@@
 consistent with the hypothesis of a U-shaped labor force participation as a country
-develop, although India's female labor force participation is lower than most other
-countries and more in line with countries in the Middle East and North Africa  
-\citep{Goldin1994,Klasen2015,Chatterjee2018}.
+develop \citep{Goldin1994}
+India's female labor force participation is, however,  lower than most other
+countries and more in line with countries in the Middle East and North Africa and
+does not yet show any signs of increasing.
+\citep{Klasen2015,Chatterjee2018}.
+
+India has experience substantial economic growth since the mid-seventies with
+an average growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
 

### 2019-12-23 paper/educ_work_over_time.tex
Expand discussion of female labor supply theory and findings

--- 2019-12-17 paper/educ_work_over_time.tex
@@
 
-Even as the level of female education has increased the female labor force participation 
-has decreased over time [should this be by level of education?].
+Even as the level of female education has increased, the female labor force participation 
+in both urban and rural areas has stagnated or decreased
+\citep{Klasen2015,Afridi2018,Bhargava2018, Chatterjee2018, Bhargava2019}.
+A decline in female labor force participation in the beginning of development is
+consistent with the hypothesis of a U-shaped labor force participation as a country
+develop \citep{Goldin1994}.
+India's female labor force participation is, however, lower than most other
+countries and more in line with countries in the Middle East and North Africa and
+does not yet show any signs of increasing.
+\citep{Klasen2015,Chatterjee2018}.
 
-[Discuss recent papers on labor supply in India]
+Theory predicts that increasing women's wage leads to higher labor force participation, 
+while both a higher male income and social restrictions on working, possibly in 
+specific industries or jobs, reduce female labor supply \citep{Goldin1994}.
+India's economy has grown substantially since the mid-seventies with
+an average annual growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
+As a result, real wages for both men and women have almost doubled between 1987 and 2011 
+\citep{Klasen2015}.
+Despite the increases in wages and the higher female education, the mean male wage is
+still close to 70 percent higher than the mean female wage \citep{Bhargava2018}.
+Furthermore, the development in women's wage is not uniform across education levels.
+The real wages for women with middle school education or below has converged, 
+for women with secondary education, the change over time depends on the sample used
+with some showing a relative strong decline and others a modest increase,
+and women with more than secondary education experienced an increased in their real 
+wage, especially in cities \citep{Klasen2015,Bhargava2018}.
+
+After controlling for household characteristics and husband income, there is
+still a U-shaped relationship between female education and labor supply with the
+lowest labor force participation for women with secondary education \citep{Chatterjee2018}.
+There are two possible explanations for this effect, both directly related to the strong
+pro-male bias in India.
+First, it becomes less socially acceptable for women to work in manual labor as their
+education increases, but women are still mostly excluded from white-collar
+employment despite the strong economic growth \citep{Klasen2015,Chatterjee2018}.
+Second, with increasing education, women's productivity at home increases, especially
+in the production of offspring human capital, and with access to sex selective abortions
+leading to relatively more boys being born and an increasing return to male education 
+there can be an increased demand for women with more education, even though they do not 
+participate in the labor market \citep{Behrman1999}.
 
 To place my results in context, Figure XX shows the percent of married women who are 
-working at the time of the survey by age group.%
-\footnote{
+working at the time of the survey by age group.
 This question is the only question on labor force participation consistently available 
-across all four surveys.
-Since the question is asked only of married women it is possible that the overall
-female labor force participation might have developed differently, especially since
-many young, unmarried women have begun working in, for example, the business process 
-outsourcing industry [TK cite Jensen 2012 QJE].
-}
+across all four surveys, and because the question refers to currently working the 
+percentages will be lower than what other studies have found.
+Furthermore, since the question is asked only of married women, the overall female labor 
+force participation might have developed differently, especially since many young, 
+unmarried women have begun working in, for example, the business process 
+outsourcing industry, which, in turn, has increased girls' schooling investments
+\citep{Jensen2012}.
 
-The declines over the the four rounds of the NFHS are in line with what previous
-research has found using other data sets [TK cite Bhargava 2018 and 2019, Chatterjee 2018].
-Finding a decline in labor force participation in the beginning of development is
-in line with the hypothesis of a U-shaped labor force participation as a country
-develop [TK cite Goldin 1994, Chatterjee 2018].
+Women in their twenties have the lowest labor force participation, consistent with
+that age being the prime age bearing period.
+As a result, there is little change in the percent women who currently work, except
+that rural women with no education has seen a 15 percentage points decline.
 
@@
 opportunity cost less relevant. 
-instead, theories that emphasize income effects or effects of spacing become
-more relevant.
+Instead, theories that emphasize income effects or effects of spacing on child
+outcomes become more relevant.

### 2019-12-26 paper/educ_work_over_time.tex
Discuss NFHS data on working

@@
 India's female labor force participation is, however, lower than most other
-countries and more in line with countries in the Middle East and North Africa and
+countries and more in line with countries in the Middle East and North Africa, and
 does not yet show any signs of increasing.
@@
 Theory predicts that increasing women's wage leads to higher labor force participation, 
-while both a higher male income and social restrictions on working, possibly in 
+while both a higher male income and stronger social restrictions on working, possibly in 
 specific industries or jobs, reduce female labor supply \citep{Goldin1994}.
@@
 To place my results in context, Figure XX shows the percent of married women who are 
-working at the time of the survey by age group.
-This question is the only question on labor force participation consistently available 
+currently working at the time of the survey by age group and education level.
+This is the only question on labor force participation consistently available 
 across all four surveys, and because the question refers to currently working the 
@@
 
-Women in their twenties have the lowest labor force participation, consistent with
-that age being the prime age bearing period.
-As a result, there is little change in the percent women who currently work, except
-that rural women with no education has seen a 15 percentage points decline.
+Women are more likely to report working if they live in rural than urban areas
+and the older they are, and the U-shaped relationship between education and working
+holds in most cases with the highest percent working for women with either no education
+or with twelve or more years and the lowest for women with eight to eleven years 
+of education.
+Comparing 1992 and 2015, the percent who currently work has either remained roughly 
+the same or decreased.
+The cases were the numbers were higher in 1999 and 2006 than 1992 and 2015 are mostly
+based on small samples, such as rural women with twelve or more years of education
+in rural areas.
 
-The theories on the relationship between education and birth spacing often works 
-through the changes in the opportunity cost of time. 
-If women are unlikely to work, this makes the predictions that are based on
-opportunity cost less relevant. 
+Almost all of the urban women working are paid either cash or a combination of
+cash and in-kind for their work (see Appendix Figure XX).
+Rural women have become more likely to receive cash for their labor over time and
+the better educated the more likely they are to receive cash.
+Despite this, women across all groups have become substantially more likely to 
+work for a family member rather than for themselves or somebody else
+(see Appendix Figure XX).
+Hence, most of the reduction in the likelihood of working appear have come from 
+a retraction from the general labor market and self-employment.
+
+As shown above, some of the theories on the relationship between education and birth 
+spacing works through the changes in the opportunity cost of time. 
+For those women unlikely to work, the predictions based on opportunity cost are 
+less relevant. 
 Instead, theories that emphasize income effects or effects of spacing on child
 outcomes become more relevant.
+
+With substantial increases in husband income and a declining female labor force 
+participation, I expect a push toward longer birth spacing over time, independent
+of education levels.
+Even lower desired fertility with increasing education, I would, however, expect
+the most substantial increase in birth spacing among the best educated because
+of their use of sex selection.
+Working in the opposite direction is that women with more education can space
+their children closer together without substantially increasing child mortality risk.
+
+[How would education levels behave relative to each other?
+- longer among better educated because of sex selection
+- convergence because better educated can space children closer together without 
+  substantially increased child mortality risk.
+- Sanskritization (?) would mean that lower caste caste women try to mimic 
+  and with increasing education that becomes easier]

### 2019-12-26 paper/educ_work_over_time.tex
Add initial Sanskritization discussion

@@
 the better educated the more likely they are to receive cash.
+
 Despite this, women across all groups have become substantially more likely to 
@@
 
-[How would education levels behave relative to each other?
-- longer among better educated because of sex selection
-- convergence because better educated can space children closer together without 
-  substantially increased child mortality risk.
 - Sanskritization (?) would mean that lower caste caste women try to mimic 
   and with increasing education that becomes easier]
+
+A major question is how the dramatic changes in educational attainment for women, the
+changes in labor force participation, and declining fertility interact.
+Especially, in many countries increasing female education is associated with 
+improved status in the household and lower fertility.
+However, with the increase in male education and income in India over time, 
+``Sanskritization'' imply that as lower castes females gain access to education we 
+instead observe the adoption of higher caste norms such as stronger son preference
+and a retraction from the formal labor market for women 
+\citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
+In addition, ``Sanskritization'' may lead to not just an increased preference for sons,
+but also an increased aversion to daughters, and, in turn, to lower desired fertility
+\citep{Borooah2004}.

### 2019-12-27 paper/educ_work_over_time.tex
Edits for grammar and clarity

--- 2019-12-23 paper/educ_work_over_time.tex
@@
 
-There has been substantial improvements in female educational attainment over time.
-Figure XX shows the distribution of schooling by birth cohort for urban and rural women 
-twenty years or older whether married or not.
-The education groups are no education, one to seven years, and eight years or
-above.
+Female educational attainment has increased substantially over time.
+Figure XX shows the distribution of schooling by birth cohort for urban and rural women, 
+twenty years or older, whether married or not, based on the four rounds of the NFHS.
+The education groups are no education, one to seven years, and eight to eleven years,
+and twelve years and above.
 
 For rural areas, the percentage of women with no education has gone from around 90 percent
-for the 1930s cohorts to less than 20 percent for 1990s cohorts. 
+for the 1930s cohorts to less than 20 percent for the 1990s cohorts. 
 The proportion of women with one to seven years of education has remained remarkably
@@
 The difference is made up by the women with eight or more years of education, who have
-gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts.
+gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts,
+with about half in the eight to eleven years group and 
+the other half in the twelve years or more group.
 
@@
 Around sixty percent of urban women born in the 1930s had no education, 25 percent had
-between one and seven years, and about 15 had eight or more years of education.
-The proportion with no education has declined almost to five percent for the latest
-cohort, and the proportion with one to seven years of education has shrunk to just over
-ten percent.
-The result is that close to 80 percent of urban women now have eight or more years of
-education.
+between one and seven years, about 10 had eight or more years of education, and only
+five percent has twelve years or more.
+The proportions with no education and one to seven years have both declined to just below 
+ten percent for the latest cohort.
+Although the proportion of women with eight to eleven years of education has increased
+to about twenty, most of the increase in urban female education has come from the 
+twelve plus group, which now account for more than half of all urban women.
 
@@
 \citep{Klasen2015,Afridi2018,Bhargava2018, Chatterjee2018, Bhargava2019}.
-A decline in female labor force participation in the beginning of development is
+A decline in female labor force participation at the beginning of development is
 consistent with the hypothesis of a U-shaped labor force participation as a country
-develop \citep{Goldin1994}.
+develops \citep{Goldin1994}.
 India's female labor force participation is, however, lower than most other
-countries and more in line with countries in the Middle East and North Africa and
-does not yet show any signs of increasing.
+countries and more in line with countries in the Middle East and North Africa, and
+does not yet show any signs of increasing
 \citep{Klasen2015,Chatterjee2018}.
 
-Theory predicts that increasing women's wage leads to higher labor force participation, 
-while both a higher male income and social restrictions on working, possibly in 
+Theory predicts that increasing women's wages leads to higher labor force participation, 
+while both a higher male income and stronger social restrictions on working, possibly in 
 specific industries or jobs, reduce female labor supply \citep{Goldin1994}.
-India's economy has grown substantially since the mid-seventies with
+India's economy has grown substantially since the mid-seventies, with
 an average annual growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
@@
 still close to 70 percent higher than the mean female wage \citep{Bhargava2018}.
-Furthermore, the development in women's wage is not uniform across education levels.
-The real wages for women with middle school education or below has converged, 
-for women with secondary education, the change over time depends on the sample used
-with some showing a relative strong decline and others a modest increase,
-and women with more than secondary education experienced an increased in their real 
-wage, especially in cities \citep{Klasen2015,Bhargava2018}.
+Furthermore, the development in women's wages is not uniform across education 
+levels \citep{Klasen2015,Bhargava2018}.
+The real wages for women with middle school education or below have converged. 
+For women with secondary education, the change over time depends on the sample used,
+with some showing a substantial decline and others a modest increase.
+Women with more than secondary education experienced an increased in their real 
+wages, especially in cities.
 
@@
 First, it becomes less socially acceptable for women to work in manual labor as their
-education increases, but women are still mostly excluded from white-collar
-employment despite the strong economic growth \citep{Klasen2015,Chatterjee2018}.
-Second, with increasing education, women's productivity at home increases, especially
-in the production of offspring human capital, and with access to sex selective abortions
-leading to relatively more boys being born and an increasing return to male education 
-there can be an increased demand for women with more education, even though they do not 
-participate in the labor market \citep{Behrman1999}.
+education increases, and women are still mostly excluded from white-collar
+employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
+Second, with increasing education, women's productivity at home also increases, especially
+in the production of offspring human capital.
+With relatively more boys born because of increased access to sex-selective 
+abortions and an increasing male income, demand for better-educated women can 
+increase, even if they do not participate in the labor market \citep{Behrman1999}.
 
-To place my results in context, Figure XX shows the percent of married women who are 
-working at the time of the survey by age group.
-This question is the only question on labor force participation consistently available 
-across all four surveys, and because the question refers to currently working the 
-percentages will be lower than what other studies have found.
+Figure XX shows the percent of married women who are 
+currently working at the time of the survey by age group and education level.
+No other labor force participation question is consistently available across all 
+four surveys. 
+Because the question refers to currently working, the percentages will be lower 
+than what other studies have found. 
 Furthermore, since the question is asked only of married women, the overall female labor 
@@
 
-Women in their twenties have the lowest labor force participation, consistent with
-that age being the prime age bearing period.
-As a result, there is little change in the percent women who currently work, except
-that rural women with no education has seen a 15 percentage points decline.
+The U-shaped relationship between education and working holds in most cases with 
+the highest percent working for women with either no education or with twelve or 
+more years and the lowest for women with eight to eleven years of education.
+Women are more likely to report working if they live in rural than urban areas 
+and the older they are.
+Comparing 1992 and 2015, the percent of women who currently work has either 
+remained roughly the same or decreased.
+The cases were the numbers were higher in 1999 and 2006 than in 1992 or 2015 
+are mostly based on small samples, such as rural women with twelve or more 
+years of education in rural areas.
 
-The theories on the relationship between education and birth spacing often works 
-through the changes in the opportunity cost of time. 
-If women are unlikely to work, this makes the predictions that are based on
-opportunity cost less relevant. 
-Instead, theories that emphasize income effects or effects of spacing on child
-outcomes become more relevant.
+Almost all of the urban women who work receive either cash or a combination of 
+cash and in-kind for their work (see Appendix Figure XX). 
+Rural women have become more likely to receive cash for their labor over time, 
+and the better educated, the more likely they are to receive cash.
+
+Despite this, women across all groups have become substantially more likely to 
+work for a family member rather than for themselves or somebody else
+(see Appendix Figure XX).
+Hence, the lower likelihood of working stems mostly from women retracting from 
+the general labor market and self-employment.
+
+The increases in female educational attainment imply that access to education 
+has expanded beyond the higher castes. 
+However, ``Sanskritization'' implies that as lower castes females gain access to 
+education and their husbands' income increases, the women adopt higher caste 
+norms such as stronger son preference and a retraction from the formal labor 
+market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}. 
+``Sanskritization'' may also lead to an increased aversion to daughters, rather 
+than just an increased preference for sons, which, in turn, lowers desired 
+fertility \citep{Borooah2004}.
+
+Hence, with substantial increases in husband income and a declining female labor force 
+participation, I expect a push toward longer birth spacing over time, independent
+of education levels, based on the income effects and the effects of spacing
+on child outcomes in the theories above.
+The declining percentage of women working suggests that the opportunity cost
+effects with increasing education will not be strong enough to shorten the
+birth spacing.
+
+As desired fertility decreases with increasing education, I, furthermore, expect 
+birth spacing to increase the most among the best-educated because of their 
+use of sex selection and because of "Sanskritization" the changing composition 
+of women in the better-educated group does not substantially change this 
+group's use of sex selection.
+Working in the opposite direction is that women with more education can space
+their children closer together without substantially increasing child mortality risk.

### 2019-12-27 paper/birth_spacing_lit.tex

@@
 
-The empirical results based on the ﬁrst hypothesis show that the level
+The empirical results based on the first hypothesis show that the level
 of industrialization of the local economy does not have a differential
@@
 
-My ﬁndings are consistent with the hypothesis that more educated women
+My findings are consistent with the hypothesis that more educated women
 are better at adopting new contraceptive technology.

### 2019-12-27 paper/conceptual_framework.tex

@@
 I first discuss the main determinants of spacing examined in the prior research, and 
-then turn to how son preference and sex selection fits into the decisions on spacing.
+then how son preference and sex selection fits into the spacing decisions.
 Since sex selection and education are closely linked, I pay special attention to how 
@@
 In the simplest possible dynamic model of fertility, the spacing decision is trivial.
-Assume that parents derive benefits from the presence of children, rather than from 
-the births themselves, that spacing of children by itself does impact the parental utility, 
-and that the parents perfectly control when to have children. 
-The optimal decision is then to have the children as early as possible 
+Assume that parents derive benefits from the presence of children, not their births, 
+that spacing of children does impact parents' utility, 
+and that the parents fully control when to have children. 
+The optimal decision then is to have the children as early as possible 
 \citep{Newman1988}.
@@
 Despite a general belief that better access to and knowledge of contraception 
-should lead to longer average spacing, the empirical relationship between contraception 
+should lengthen average spacing, the empirical relationship between contraception 
 use and birth spacing is ambiguous 
@@
 modern contraceptives on birth spacing.
-On the one hand, in the absence of high-efficacy contraceptive technologies, parents may try to 
-avoid overshooting their desired number of children by spacing their children further apart
-than they would otherwise do.
+On the one hand, in the absence of high-efficacy contraceptive technologies, parents may 
+try to avoid overshooting their desired number of children by spacing their children 
+further apart than they would otherwise do.
 Increased reliability of the access to and effectiveness of contraceptives then lead to 
@@
 stop childbearing when they want \citep{Keyfitz1971,Heckman1976}.
-On the other hand, when contraceptives are ineffective, some birth intervals will
-be shorter than ideal, in the way discussed below, through simple random variation.
+On the other hand, through simple random variation, when contraceptives are ineffective, 
+some birth intervals will be shorter than ideal, in the way discussed below.
 With increased reliability of contraceptive efforts, parents can better avoid too short 
@@
 Third, parents incur both direct and time costs when they have children, 
-and economic factors can, therefore, affect birth spacing \citep{Hotz1997,Schultz1997}.
-I divide the economic factors into the effects of price and income shocks,
-the expected income trajectory of the husband and wife,
-and economies of scale considerations.
+and economic considerations can, therefore, affect birth spacing 
+\citep{Hotz1997,Schultz1997}.
+I divide the economic factors into the effects of economies of scale and
+the expected income trajectory of the husband and wife.
 
@@
 as possible to enjoy them for longer, there is also a direct cost to children.
-Early on income is low, which means that the marginal utility of consumption is 
-higher, making parents less willing to give up consumption now to have a child, 
+Income is low early on, which means that the marginal utility of consumption is 
+higher, making parents less willing to give up consumption to have a child, 
 compare to later when they know that their income will be higher 
 \citep{Newman1984,Happel1984}.
-
-The income profile argument assumes that parents know their future income, 
-but income and price shocks may also affect spacing. 
-A temporary, higher cost of women's time or a lower household income, will 
-temporarily decrease fertility and, thereby, increase birth spacing 
-\citep{Moffitt1984,Hotz1988,Portner2001,Alam2018}.
-Increasing education likely reduces the risk of income shocks, but the 
-effect on other types of shocks that might impact the spacing is unclear.
 
@@
 
-It is not, however, immediately apparent that we should expect shorter spacing in 
-the absence of boys, if short spacing lowers the survival probability of the 
-next child, as discussed above.
+If short spacing lowers the survival probability of the next child, as discussed above,
+it is not, however, apparent that we should expect shorter spacing in the absence of boys.
 There are two potential reasons why parents might still try to conceive sooner 
@@
 detrimental to the next child's health, resulting in high mortality for both boys 
-and girls born after short spacing across all households whether or not they have 
-a son preference.%
-\footnote{
-We may even see a higher likelihood of dying for sons than girls, given that boys 
-have naturally higher mortality.
-}
+and girls born after short spacing across all households.
 
 The other possibility is that parents realize that short spacing has adverse 
-health effects, but their son-preference is so strong that they are willing to 
+health effects, but their preference for sons is so strong that they are willing to 
 divert substantial resources to the next child if it is a boy.
@@
 
-As mentioned above, the adverse effects of shorter spacing are strongly mitigated 
-by higher education, which, in theory, allows better-educated women to have shorter
-spacing in the absence of a boy without substantial increasing mortality risk.
+With the adverse effects of shorter spacing strongly mitigated by higher education,
+better-educated women can, in theory, have shorter spacing in the absence of a boy 
+without substantial increasing mortality risk.
 Differences in mortality outcomes across boys and girls are still possible,
@@
 the next child if they abort the fetus.
-The question is, who is likely to use sex selection, when, and why?
 
-Theory suggests that the lower the desired fertility, the 
-higher the likelihood of sex selection \citep{Portner2015b}.
-Simple probabilities drive this prediction:
-in the absence of sex selection, 
-48.8 percent will not have a son when only having one child, 
-23.8 percent for two children, 11.6 percent for three children, 
-5.7 percent for four children, 2.8 percent for five children, 
-and 1.4 percent for six children.
-Furthermore, for a given level of desired fertility, the higher
-the parity, the higher is the likelihood of using sex selection.
+Theory suggests that sex selection increases with lower desired fertility, and, for a 
+given desired number of children, the higher the parity \citep{Portner2015b}.
+The increased use of sex selection in India with education and in urban
+areas is consistent with a lower desired fertility for both groups,
+either because of the higher cost of children or because of other
+changes in the preferred number of children
+\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
+Jayachandran2017}.%
+\footnote{
+Stronger son preference could also contribute, but better-educated women 
+have declining stated son preference over time \citep{bhat03,pande07}.
+}
 
-The higher the cost of prenatal sex determination and abortion,
-the less use we should see.
+The higher the cost of prenatal sex determination and abortion, the less use we should 
+see.
 Similarly, any potential adverse effects on the mother and offspring 
-from repeated abortions would also tend to reduce the use of sex 
-selection---provided that parents are aware of these costs.
-Finally, the more abortions between births, the less the opportunity 
-there is to take advantage of any economies of scale in childrearing.
-
-The use of sex selection in India increases with education and is higher 
-in urban areas than in rural
-\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
-Jayachandran2017}.
-Women with more education generally have lower desired fertility, either 
-because of the higher opportunity cost of time or because of other changes 
-in the preferred number of children.%
-\footnote{
-It is also possible that the effect is driven by a stronger son preference, although 
-higher education women have shown declining stated son preference \citep{bhat03,pande07}.
-}
-Better-educated women also tend to live in households with higher 
-income, which better enables them to access prenatal sex determination 
-and lowers the relative costs of using sex selection.
+from repeated abortions should also reduce the use of sex selection---provided that 
+parents are aware of these costs.
+Furthermore, the more abortions between births, the less the parents can take advantage 
+of economies of scale.
+Better-educated women tend to live in households with higher income, which better enables 
+them to access prenatal sex determination and lowers the relative costs of using sex 
+selection.
 
@@
 wealth and the improvements in health as India has developed.
-I, therefore, now look at how female education and labor force 
+I, therefore, examine how female education and labor force 
 participation has changed over time in India.

### 2019-12-27 paper/sex_selection_spacing-ver3.tex

@@
 and economic considerations can, therefore, affect birth spacing 
-\citep{Hotz1997,Schultz1997}.
+\citep{Hotz1997,schultz97}.
 I divide the economic factors into the effects of economies of scale and
@@
 time as taking care of one child, is to shorten intervals between births
-\citep{Vijverberg1982,Espenshade1984}.
+\citep{Vijverberg1982}.
 To the extent that children require the mother to do less market work, parents 
@@
 spacing than less-educated women because of their higher opportunity cost of time 
-\citep{Ross1974,Newman1981,Newman1984}.
+\citep{Ross1974,Newman1984}.
 However, if the mother mainly works at home or as household income increases, there 
@@
 stronger with increasing education levels
-\citep{Heckman1976,Wolpin1984,Newman1988}.
+\citep{Heckman1976,wolpin84,Newman1988}.
 The idea is that although parents would prefer to have their children as early 
@@
 participation has changed over time in India.
+
+%------------------------------------------------------------------------------------
+
+\section{Female Education and Labor Force Participation in India}
+
+Female educational attainment has increased substantially over time.
+Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
+cohort for urban and rural women, 
+twenty years or older, whether married or not, based on the four rounds of the NFHS.
+The education groups are no education, one to seven years, and eight to eleven years,
+and twelve years and above.
+
+\begin{figure}[htpb]
+\centering
+\subfloat[Rural]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_rural}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_urban} 
+    \end{minipage}
+}
+\caption{Distribution of education by cohort for women twenty years or older at survey}
+\label{fig:education_over_time}
+\end{figure}
+
+For rural areas, the percentage of women with no education has gone from around 90 percent
+for the 1930s cohorts to less than 20 percent for the 1990s cohorts. 
+The proportion of women with one to seven years of education has remained remarkably
+constant at around ten percent.
+The difference is made up by the women with eight or more years of education, who have
+gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts,
+with about half in the eight to eleven years group and 
+the other half in the twelve years or more group.
+
+Female education is higher in urban areas than in rural areas.
+Around sixty percent of urban women born in the 1930s had no education, 25 percent had
+between one and seven years, about 10 had eight or more years of education, and only
+five percent has twelve years or more.
+The proportions with no education and one to seven years have both declined to just below 
+ten percent for the latest cohort.
+Although the proportion of women with eight to eleven years of education has increased
+to about twenty, most of the increase in urban female education has come from the 
+twelve plus group, which now account for more than half of all urban women.
+
+Even as the level of female education has increased, the female labor force participation 
+in both urban and rural areas has stagnated or decreased
+\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018, Bhargava2019}.
+A decline in female labor force participation at the beginning of development is
+consistent with the hypothesis of a U-shaped labor force participation as a country
+develops \citep{Goldin1994}.
+India's female labor force participation is, however, lower than most other
+countries and more in line with countries in the Middle East and North Africa, and
+does not yet show any signs of increasing
+\citep{Klasen2015,Chatterjee2018}.
+
+Theory predicts that increasing women's wages leads to higher labor force participation, 
+while both a higher male income and stronger social restrictions on working, possibly in 
+specific industries or jobs, reduce female labor supply \citep{Goldin1994}.
+India's economy has grown substantially since the mid-seventies, with
+an average annual growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
+As a result, real wages for both men and women have almost doubled between 1987 and 2011 
+\citep{Klasen2015}.
+Despite the increases in wages and the higher female education, the mean male wage is
+still close to 70 percent higher than the mean female wage \citep{Bhargava2018}.
+Furthermore, the development in women's wages is not uniform across education 
+levels \citep{Klasen2015,Bhargava2018}.
+The real wages for women with middle school education or below have converged. 
+For women with secondary education, the change over time depends on the sample used,
+with some showing a substantial decline and others a modest increase.
+Women with more than secondary education experienced an increased in their real 
+wages, especially in cities.
+
+After controlling for household characteristics and husband income, there is
+still a U-shaped relationship between female education and labor supply with the
+lowest labor force participation for women with secondary education \citep{Chatterjee2018}.
+There are two possible explanations for this effect, both directly related to the strong
+pro-male bias in India.
+First, it becomes less socially acceptable for women to work in manual labor as their
+education increases, and women are still mostly excluded from white-collar
+employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
+Second, with increasing education, women's productivity at home also increases, especially
+in the production of offspring human capital.
+With relatively more boys born because of increased access to sex-selective 
+abortions and an increasing male income, demand for better-educated women can 
+increase, even if they do not participate in the labor market \citep{Behrman1999}.
+
+Figure \ref{fig:work_by_survey} shows the percent of married women who are 
+currently working at the time of the survey by age group and education level.
+No other labor force participation question is consistently available across all 
+four surveys. 
+Because the question refers to currently working, the percentages will be lower 
+than what other studies have found. 
+Furthermore, since the question is asked only of married women, the overall female labor 
+force participation might have developed differently, especially since many young, 
+unmarried women have begun working in, for example, the business process 
+outsourcing industry, which, in turn, has increased girls' schooling investments
+\citep{Jensen2012}.
+
+\begin{figure}[!htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{40 Years or Older}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_40}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_40} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_30}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_30} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_20}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_20} 
+    \end{minipage}
+}
+\caption{Percentage of married women who were working at the time of the 
+survey by age group and area of residence}
+\label{fig:work_by_survey}
+\end{figure}
+
+The U-shaped relationship between education and working holds in most cases with 
+the highest percent working for women with either no education or with twelve or 
+more years and the lowest for women with eight to eleven years of education.
+Women are more likely to report working if they live in rural than urban areas 
+and the older they are.
+Comparing 1992 and 2015, the percent of women who currently work has either 
+remained roughly the same or decreased.
+The cases were the numbers were higher in 1999 and 2006 than in 1992 or 2015 
+are mostly based on small samples, such as rural women with twelve or more 
+years of education in rural areas.
+
+Almost all of the urban women who work receive either cash or a combination of 
+cash and in-kind for their work (see Appendix Figure \ref{fig:work_cash_by_survey}). 
+Rural women have become more likely to receive cash for their labor over time, 
+and the better educated, the more likely they are to receive cash.
+
+Despite this, women across all groups have become substantially more likely to 
+work for a family member rather than for themselves or somebody else
+(see Appendix Figure \ref{fig:work_family_by_survey}).
+Hence, the lower likelihood of working stems mostly from women retracting from 
+the general labor market and self-employment.
+
+The increases in female educational attainment imply that access to education 
+has expanded beyond the higher castes. 
+However, ``Sanskritization'' implies that as lower castes females gain access to 
+education and their husbands' income increases, the women adopt higher caste 
+norms such as stronger son preference and a retraction from the formal labor 
+market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}. 
+``Sanskritization'' may also lead to an increased aversion to daughters, rather 
+than just an increased preference for sons, which, in turn, lowers desired 
+fertility \citep{Borooah2004}.
+
+Hence, with substantial increases in husband income and a declining female labor force 
+participation, I expect a push toward longer birth spacing over time, independent
+of education levels, based on the income effects and the effects of spacing
+on child outcomes in the theories above.
+The declining percentage of women working suggests that the opportunity cost
+effects with increasing education will not be strong enough to shorten the
+birth spacing.
+
+As desired fertility decreases with increasing education, I, furthermore, expect 
+birth spacing to increase the most among the best-educated because of their 
+use of sex selection and because of "Sanskritization" the changing composition 
+of women in the better-educated group does not substantially change this 
+group's use of sex selection.
+Working in the opposite direction is that women with more education can space
+their children closer together without substantially increasing child mortality risk.
 
@@
 
+\section{Characteristics of Women Work Experiences}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\begin{figure}[!htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{40 Years or Older}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_cash_rural_40}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_cash_urban_40} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_cash_rural_30}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_cash_urban_30} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_cash_rural_20}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_cash_urban_20} 
+    \end{minipage}
+}
+\caption{Percentage of women paid cash or cash and in-kind of those women who were 
+working at the time of the survey by age group and area of residence}
+\label{fig:work_cash_by_survey}
+\end{figure}
+
+\begin{figure}[!htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{40 Years or Older}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_family_rural_40}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_family_urban_40} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_family_rural_30}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_family_urban_30} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_family_rural_20}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{work_family_urban_20} 
+    \end{minipage}
+}
+\caption{Percentage of women who were working for a family of those women who were
+working at the time of the survey by age group and area of residence}
+\label{fig:work_family_by_survey}
+\end{figure}
+
+\clearpage
+\newpage
+
 \section{Recall Error and the Sex Ratio}

### 2019-12-27 response/response-demography-2.tex
Initial commit of all comments/suggestions from editor and referees

\documentclass[letterpaper,12pt]{article}

% Xetex preamble
\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}

\usepackage[longnamesfirst]{natbib}
%\usepackage[tabhead,nolists,tablesfirst]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{rotating}  
\usepackage{dcolumn} 
\usepackage{setspace}
%\usepackage{flafter} 
%\usepackage{longtable}
%\usepackage[pdftex]{graphicx}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black]{
hyperref} 
\usepackage[margin=1.0in]{geometry} 
\usepackage{multirow}

%opening
\title{} \author{}

\doublespacing

\begin{document}

\begin{center} \textbf{\large Birth Spacing in the Presence of Son
Preference and 
Sex-Selective Abortions: India's Experience over Four Decades}
\end{center}

\begin{center} Response to Editor and Reviewer Comments \end{center}

\noindent Please find attached the revised version of my paper,
``Birth Spacing in the Presence of Son Preference and Sex-Selective
Abortions:
India's Experience over Four Decades.''
I want to thank the three reviewers and the editor for the very helpful comments and 
suggestions, which I believe substantially improved the paper.

\section*{Editor}

\begin{enumerate}

\item First, greater explanation of the unique contributions of this
study is needed. As the reviewers note, the literatures in the areas of
son preference and birth spacing, for example, are extensive, and
clearer and more compelling motivations for the work should be provided.

[Response:]

\item Second, the paper lacks a conceptual framework to organize (and
motivate) the analysis. Following on the comments of one reviewer, one
suggestion would be to focus on the role of women’s education, with a
more thorough description of the context of changing education in India
over the last half century and clearly lay out a framework for the
mechanisms through which birth spacing is affected by educational
expansion.

[Response:]

\item This relates to a third issue, which is space limitations and
decisions regarding what to include in the manuscript. In the last
decision letter you were asked to “reorganized to focus on the most
important issues.” Although the author has done a good job of focusing
the paper in the revision, there are still questions about lack of
detail in some places and perhaps too much in others. One suggestion is
to drop the analysis on regional differences and focus the paper more
centrally on the topic of maternal education, for example (as noted
above).

[Response:]

\end{enumerate}

\newpage

\section*{Reviewer 1}

This paper studies birth variation in birth spacing in relation to son
preference and (access to) sex selective abortion. The data cover four
decades of birth histories in India, but have no direct information on
access to or use of sex selective abortion. Using discrete time
competing risk models, where the “risks” are the birth of a boy and the
birth of a girl, patterns of birth spacing are produced that are
plausibly in line with increasing access and use of sex selective
abortion over time and a strong positive relation between mother’s
education level and the use of sex selective abortion. While many
studies have discussed causes and consequences of the missing girls
problem due to sex selective abortion, the author(s) claim that this is
the first paper that systematically analyzes the link with birth
spacing. If this is indeed the case (I am not following this literature
close enough to be completely sure) then this is an innovative and
important study that will be of interest to readers of Demography. I
have some suggestions for changing the exposition.

\begin{enumerate}

\item The model is well explained, but the paper could be more explicit
on why a model is needed. Some of the conclusions drawn from average
probabilities, sex ratios, etc. (particularly those not conditioning on
specific values of the covariates) might also be directly visible in the
raw data. If so, the data description part could perhaps be extended.

[Response:]

\item Details on the estimation results are not presented. I assume
there are too many of them to be included in the paper. Still, the paper
extensively discusses model specification issues such as the
proportionality assumption and the way that is handled by splitting the
sample. I would like to see some discussion of model specification tests
informing the reader whether this is necessary and whether the resulting
flexible specifications indeed provide a good fit to the data.

[Response:]

\item I found the analysis of geographical differences not very
exciting. It leads to several pages with not so interesting figures of
regional survival curves. I would suggest dropping the details (perhaps
make them available in an online appendix) and briefly summarize the
main findings.

[Response:]

\item The concluding section raises some interesting points but these
are only indirectly related to the content of the paper. The development
of family planning possibilities with increasing availability and use
over time seems to be important for understanding the general decline in
fertility and lengthening of birth intervals. It is mentioned in the
introduction but not in the conclusions. The relation with labor market
participation may be of interest, but what is said about it was not
clear to me. Why would longer birth intervals disrupt labor force
participation (p. 32)

[Response:]

Specific comments:

\item p.7: eq. 2: I would call this a piecewise constant baseline hazard
rather than a piecewise linear one.

[Response:]

\item p.7 after eq. 3: Sex composition of previous children is in
principle endogenous  if there is sex selective abortion (it is
essentially a lagged dependent variable). This is not taken into
account. This is, at least in theory, a limitation of the current model
that should be acknowledged. (I do not think it is easy to remedy
without explicitly incorporating unobserved heterogeneity.)

[Response:]

\item p.7: Why use intervals of three months? Did the author(s) perform
any sensitivity checks?

[Response:]

\item p.9: It might be useful to already mention that Hindus only are
analyzed in the introduction, since religion might play an important
role when choosing sex selective abortion.

[Response:]

\item p.10: Sterilization also seems an endogenous decision in this
context, this should be acknowledged as an additional limitation. How
often does this occur? (It might even be possible to treat this as an
additional competing risk.)

[Response:]

\item p.9: why put the marriage duration threshold at 22 years?
Sensitivity check?

[Response:]

\item Results: The many small figures are hard to read and I did not
find them an attractive way to present the results. Perhaps the
author(s) can come up with an alternative?

[Response:]

\end{enumerate}

\newpage

\section*{Reviewer 2}

\begin{enumerate}

This study uses four waves of the National Family and Health Surveys to
examine the interrelationship between son preference, sex ratios at
birth, and birth spacing in India, how this varies between different
regions, by parity and the sex composition of the children in the
household, by maternal educational level, and over time.

\item On the one hand this feels like a clear and polished piece of
research. On the other hand, I wonder how much we can learn from this
study given that there is already an extensive body of research that
examines son preference and SRBs in India, including how this varies by
parity, sex composition of the children already in the household,
maternal educational level, and over time. It seems to me that the
question is, what is the net contribution of adding birth spacing as an
additional dimension to this whole discussion.

[Response:]

\item The authors attempt to address this point by offering four motivations
for why we should care about spacing as an additional dimension. First,
they say that “researchers have made extensive use of birth spacing as a
measure of son preference, and it is critical to understand to what
extent spacing is still a useful measure of son preference” (page 2). To
my mind, the authors do not offer a particularly compelling explanation
anywhere in the paper for why it is ‘critical to understand’ whether
spacing remains a useful measure of son preference. Understanding son
preference and how that is linked to sex-selective abortions and
differential stopping behaviour (and gender dynamics more generally), is
indeed critical – but I don’t really see that the critical importance of
understanding spacing in relation to this.

[Response:]

\item The second and third motivations offered by the authors are the
potential consequences of (short) birth spacing for maternal health,
child health, and long-term child development. For example, the authors
cite literature showing that short spacing can have severe consequences
for child outcomes, particularly in low-income settings. However,
understanding the potential consequences of birth interval length is
much more confusing when long birth intervals are a consequence of
(sex-selective) abortions. One reason why short birth intervals have a
negative effect on child outcomes is because of maternal nutrient
depletion and insufficient time to recover from the previous pregnancy.
Children born after long birth intervals where those intervals have been
punctuated by multiple abortions will not see the same benefits as a
child born after a long interval that is not punctuated by abortions
since the mother would not be fully recovering in that intervening
period. Likewise the costs and benefits for mothers themselves of
short/long spacing may be overwhelmed by the effects of the abortions
and interrupted pregnancies.

[Response:]

\item The fourth and final motivation offered is that we don’t know what
determines spacing behaviour in low- and middle-income countries.
However, the arguments that the authors develop here are more about 
contraceptive use, declining fertility, and women entering the labor market. 
Those factors don’t seem to be addressed elsewhere in the paper at all.

[Response:]

\item In the end, this study offers a careful descriptive account of how birth
spacing has changed alongside sex ratios at birth, but little more. We
should indeed care about sex ratios at birth – and people do – but there
are many studies published on that topic, and it is not clear that this
one adds something important to that particular debate. If it does, the
authors have not articulated that clearly. I think that understanding
the consequences of birth spacing for maternal and infant health is also
extremely important. But the authors do not study that link empirically.
For these reasons, I find the contribution of the study rather marginal
and confusing.

[Response:]

\end{enumerate}

\newpage

\section*{Reviewer 3}

\begin{enumerate}

The author(s) have considered and addressed reviewers’ comments and have
revised the paper thoughtfully. The changes to the presentation of the
results and added explanations are especially well done. There is much
to be liked in the revised version. While the revised paper is stronger
than the earlier version, there are still some issues that require
further attention.

\item The paper still lacks a stronger narrative on the motivation and
framework for the empirical work. Four reasons are mentioned as
motivations; but, with the exception of the first, all other reasons,
such as the impact of spacing on child and mother’s health, are not
really motivating the empirical work of this paper (they are rather
evidence for importance of spacing).

\item The conceptual framework is not fully developed. The paper suggests
possible explanations at various places but they don’t add up to a
coherent narrative. For instance, it is not clear whether maternal
education acts through access for sex selective technology or preference
for sons. The core idea of the paper that sex selection changes the
relationship between spacing and son preference needs to be developed
further. There is significant amount of good empirical work, but without
proper development of framework it is difficult to evaluate the
contribution and understand the findings, and also to see its
contribution beyond the Indian case.

\item As an illustration, the paper looks at changes over time during which
the access the sex selection has become increasing difficult AND also
almost all groups (by education, religion…) have seen an decline in
fertility. How do we consider the impact of these on spacing, sex
selection and sex ratios? How do we put the findings in the context of
changing educational attainments of women? The paper doesn’t provide us
a framework to think about the broader changes during the time period
under consideration.

\item I’m not fully convinced of the main conclusions of a “substantial
increase in the use of sex selection” or of an “an almost complete
reversal of the traditional spacing patterns” for urban educated women.
They don’t seem to be supported by the findings. For urban women this
seems to apply only for third spell. The substantial increase in sex
selection is also not evident from the findings for all groups or for
all spells. The paper does acknowledge the complexity, but at places
(including in the abstract) seems to stretch the interpretation beyond
what is shown in the findings. The conclusions are presented in way that
implies that they apply to different spells or groups. But the findings
are more limited and differ clearly by spells. This should be presented
accurately in the text.

\item While I really liked the methodology and visual presentation of the
findings, in my reading, I don’t see the paper’s contribution to
methodology. Though the paper makes a claim for methodological novely, I
see it more as an adoption of a widely used technique to spacing rather
than a proposing a new technique. Despite the changes, the paper still
reads as a piece demonstrating a methodology rather than signficant
contribution to the demogrpahic literature.

\item Minor: It might be a disciplinary style, I would recommend cutting down
on the footnotes. I would also not go into the effect of child spacing
in countries that are very dissimilar to the context of India, unless
there is a wider point being made. Some points are not clear: for
instance, “On the other hand, increased reliability of access and
effectiveness of contraceptives can lead to shorter intervals between
births if women used to have longer spacing to avoid having too many
children by accident (Keyfitz, 1971; Heckman and Willis, 1976).”

\end{enumerate}

\newpage
\bibliographystyle{econometrica}
\bibliography{../paper/sex_selection_spacing.bib}
\addcontentsline{toc}{section}{References}

\end{document}

### 2019-12-27 paper/sex_selection_spacing-ver3.tex
Remove region section and add place holders for fertility and mortality sections

@@
 
-\subsection{Regional Differences\label{sec:regional}}
-
-To understand how regional differences in son preference, fertility, and use of sex 
-selection affect birth spacing, I divide India into four regions, shown in Table 
-\ref{tab:regions}, based on the degree  of son preference and initial fertility 
-levels \citep{retherford03b}.%
-\footnote{
-The state names are those used in NFHS-1, with states formed later allocated as close as 
-possible to the original state.
-}
-The ``West'' contains states with a high degree of son preference and use of sex selection.
-The ``North'' consists of states that also have a strong son preference, but initially had
-higher fertility and, therefore, lower likelihood of using sex selection.
-The ``East'' states generally have only a moderate level of son preference.
-Finally, the ``South'' contains states with traditionally low son preference and lower
-fertility than the rest of India.
-
-\input{../tables/desc_region.tex}
-
-I focus on the most educated women as the primary users of sex selection.
-Figures \ref{fig:bootstrap_high_r1}, \ref{fig:bootstrap_high_r2}, 
-\ref{fig:bootstrap_high_r3}, and \ref{fig:bootstrap_high_r4} show the predicted average 
-birth intervals, sex ratios, and parity progression probabilities for the ``West,''
-``North,'' ``East,'' and ``South,'' respectively.
-The ``East'' and ``South'' do not include the fourth spell because of small sample sizes 
-and very noisy results.
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
-% \\
-% \caption*{Rural}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
-% \caption{high education - r1}
-% \end{figure}
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r1}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r1} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_high_urban_r1}
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r1}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r1} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_high_rural_r1} 
-    \end{minipage}
-} 
-\caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education in the ``West''}
-\label{fig:bootstrap_high_r1}
-\end{figure}
-
-Despite the idea that the ``West'' and ``North'' differ in fertility and likelihood of 
-using sex selection, the differences are surprisingly small, at least for urban areas.
-Furthermore, both are close to the national averages presented above, with the main 
-difference that the very high sex ratios reflect a higher use of sex selection, 
-presumably as a result of fertility falling faster than the national trend.
-The predicted sex ratios in urban areas are around 60\% for the second spell and
-around 70\% for the third spell.
-This higher use of sex selection, in turn, translates into the reversal of standard
-spacing pattern.
-
-The two regions are further apart for the rural areas.
-In the ``West'' the rural areas show only slightly lower use of sex selection and 
-therefore a less pronounced reversal in spacing patterns than in the urban areas.
-In the rural ``North,'' fertility is substantially higher, and the use of sex selection 
-subsequently lower, but the sex ratio is still substantially above normal at close to 60 
-percent for the latest decade.
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
-% \\
-% \caption*{Rural}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
-% \caption{high education - r2}
-% \end{figure}
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r2}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r2} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_high_urban_r2}
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r2}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r2} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_high_rural_r2} 
-    \end{minipage}
-} 
-\caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education in the ``North''}
-\label{fig:bootstrap_high_r2}
-\end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
-% \\
-% \caption*{Rural}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
-% \caption{high education - r3}
-% \end{figure}
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r3}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r3} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r3}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r3} 
-    \end{minipage}
-} 
-\caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education in the ``East''}
-\label{fig:bootstrap_high_r3}
-\end{figure}
-
-What stands out for the ``East'' is the rapid increase in the lengths of birth intervals,
-especially for the second spell, where the increases have been more
-than a year, independently of whether the first-born was a boy or a girl.
-The increases in birth intervals are slightly smaller for the third spell but still 
-substantial.
-Although the spacing pattern is consistent with some son preference, there is little 
-evidence of sex-selective abortions.
-Furthermore, despite the ``South'' generally considered the low fertility region, 
-the reduction in fertility has been even faster in the ``East.''
-For example, only half of the urban women with a first-born son are now predicted to 
-have a second child by the end of the spell.
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
-% \\
-% \caption*{Rural}
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
-% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
-% \caption{high education - r4}
-% \end{figure}
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r4}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r4} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r4}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r4} 
-    \end{minipage}
-} 
-\caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education in the ``South''}
-\label{fig:bootstrap_high_r4}
-\end{figure}
-
-The ``South'' is historically thought to have the lowest degree of son preference,
-which has initial support from the second spell's progression rates, spacing pattern, and 
-sex ratios.
-However, for the third spell in urban areas, the average birth interval has increased 
-substantially, and the predicted sex ratio is close to 60\% for those with only girls. 
-The signs of the use of sex selection also show up for rural women with no sons.
-Furthermore, the likelihood of having a third birth has decreased much less with no sons 
-than the other sex compositions.%
-\footnote{
-The relatively high parity progression for women without son runs counter to what we
-should expect if ``daughter avoidance'' is behind the fertility behavior as
-suggested by \citet{DiamondSmith2008}.
-}
-Hence, the ``South'' now also shows the longer average spacing in the absence of sons and 
-the higher sex ratio associated with the use of sex selection.
+\section{Mortality and the Changing Birth Spacing\label{sec:mortality}}
+
+\section{How Much has Fertility Really Fallen?\label{sec:fertility}}
 

### 2019-12-28 paper/sex_selection_spacing-ver3.tex
Delete discussion of regions in paper and region appendix

@@
 
-\date{March 2018}
+\date{December 2018}
 
@@
 not from fewer very short birth intervals, but rather from the upper end of the distribution.
-Finally, northern and western India are responsible for most of the spacing pattern 
-reversal, although even the south experienced substantially increased intervals from
-sex selection.
 
@@
 continued use of sex selection to ensure a son.
-
-Finally, how are the changes in birth intervals distributed geographically?
-Given the cultural differences within India, it is unlikely that the increasing 
-access to sex selection will have had the same effects throughout \citep{retherford03b}.
-I, therefore, examine how birth intervals have changed across four regions.
 
@@
 
-With a country as large as India, it is natural to expect variation in both fertility
-behavior, spacing patterns, and the degree of son preference.
-Although the regional results confirm this, the differences are less apparent than one would
-expect given the prior research.
-The ``North'' and the ``West'' regions have relatively similar spacing patterns, both
-the result of rapidly falling fertility and substantial use of sex selection.
-The exception is that the rural ``North'' still have higher fertility and
-consequently less use of sex selection.
-Even the ``South,'' otherwise considered to have the least son preference, has 
-seen a substantial increase in the use of sex selection and associated changes 
-in the spacing patterns.
-Finally, fertility has declined fastest in the ``East'' region, but this has not 
-translated into the use of sex selection.
-
 The results here lead to three questions that future research should address.
@@
 \input{../tables/bootstrap_duration_p25_p75_high_all.tex}
-
-\clearpage
-
-\section{Results by Region}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\vspace*{-0.51cm}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_r1.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_r2.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_r3.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_r4.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_r1.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_r2.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_r3.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_r4.tex}
 

### 2020-01-10 paper/sex_selection_spacing-ver3.tex
Begin discussion of TFR vs hazard model predictions

@@
 
+One of the effects of the increasing use of sex selection over time is that the total 
+fertility rate will tend to overestimate the decline in fertility.
+``Tempo'' effects, such as those that arise from postpone of childbearing, are studied 
+extensively in the literature \citep{Bongaarts1999}.
+With development, women tend to have their first child later as a result of increasing 
+years spent in school and later marriage, but, as discussed above, spacing between births 
+also tend to shorten as women become more likely to join the labor market, which will 
+tend to counter the downward effect on the TFR.
+
+India has also seen an increasing age of marriage, but birth spacing has also become
+much longer as women leave the labor market and there is substantial use of 
+sex selection.
+The result is that the TFR becomes an increasingly biased measure of cohort fertility
+\citep{Ni-Bhrolchain2011}.
+
+To understand how strong the bias from sex selection on TFR is and how cohort fertility
+has changed, I compare predicted fertility using both TFR and the model results
+presented above.
+
 \section{Conclusion\label{sec:conclusion}}

### 2020-01-13 paper/sex_selection_spacing-ver3.tex
Add notes on prediction set-ups

@@
 
-One of the effects of the increasing use of sex selection over time is that the total 
-fertility rate will tend to overestimate the decline in fertility.
+One of the effects of the increasing use of sex selection is that the total fertility 
+rate will tend to overestimate the decline in fertility.
 ``Tempo'' effects, such as those that arise from postpone of childbearing, are studied 
@@
 India has also seen an increasing age of marriage, but birth spacing has also become
-much longer as women leave the labor market and there is substantial use of 
-sex selection.
-The result is that the TFR becomes an increasingly biased measure of cohort fertility
-\citep{Ni-Bhrolchain2011}.
+much longer as women have become less likely to join the labor market and with the 
+substantial use of sex selection.
+The result is that the TFR may have become an increasingly biased measure of cohort fertility.%
+\footnote{
+I use ``bias'' because what I am interested in is the cohort fertility \citep{Ni-Bhrolchain2011}
+}
 
@@
 presented above.
+
+I calculate TFR by urban/rural and the education groups used above.
+The main difference from the standard TFR measure is that I only use births up to parity
+four.
+Hence, the TFRs are not directly comparable those in the NFHS reports, although the
+differences are smaller the higher the education group and the most recent the survey
+as fertility has fallen over time.
+Otherwise, I follow the procedure used in the NFHS reports and count the number of births
+in months 1 to 36 before the survey month (births in the survey month are not included)
+for five-year age groups.
+
+Because NFHS-1 and NFHS-2 did not interview all women between 15 and 49 about fertility
+the number of women is based on the household rosters, assuming that never-married 
+women have had no children.
+
+To predict cohort fertility based on the models above, I estimate for each spell the 
+probability of progression to the next parity.%
+\footnote{
+This includes the spell from marriage to first birth, even those results are not 
+examined above because of the problems with capturing the exact timing of marriages
+for the first two rounds of the survey.
+The estimated progression probabilities should, however, be less affected by this
+problem.
+}
+
+To make the predictions depend solely on sample composition and the estimate, I
+use the age at marriage for each woman and predict the likelihood of progressing to
+each parity, assuming two years increases in age between each parity.
+For example, for a woman married at age 20, I use age 22 for predicting progression 
+to the second birth, 24 for the third, and 26 for the fourth.
+
+The parity progression depends on the sex composition for prior children for
+parity two and above.
+For example, the likelihood of a second birth is the 
+probability of having a first birth multiplied with
+sum of the 
+probability of having a son as the first child conditional on having a first child 
+multiplied with parity progression probability if the first child is a son 
+and the 
+probability of having a girl as the first child  conditional on having a first child
+multiplied with the parity progression probability if the first child is a girl.
+$$
+prob(2nd) = prob(1st) * (prob(son|1st)*prob(2nd|son) + prob(girl|1st) * prob(2nd|girl)
+$$
+
+The survey rounds do not coincide entirely with the periods I use for the model.
+For the NFHS-4, I use the model results for the 2005--2016 period, 
+for NFHS-3 the 1995-2004, NFHS-2 1985-1994, and for NFHS-1 1972-1984.
 

### 2020-01-15 paper/sex_selection_spacing-ver3.tex
Incorporate predicted fertility file and set up for make run
Write discussion of fertility prediction and results

--- 2019-12-28 paper/sex_selection_spacing-ver3.tex
@@
 
+\section{How Much has Fertility Really Fallen?\label{sec:fertility}}
+
+Birth spacing has increased substantially over time across all education groups, but 
+especially among those women likely to use sex selection.
+One of the potential effects of the increased birth spacing is that the total fertility
+rate may underestimate cohort fertility, at least temporarily.
+Whether tempo effects ``biases'' fertility depends on what the outcome of interest is,
+but since my outcome of interest is cohort fertility I will use ``bias''
+\citep{Ni-Bhrolchain2011}.
+
+Some tempo effects, such as those that arise from postponement of childbearing, are 
+studied extensively in the literature \citep{Bongaarts1999}.
+There are, however, to the best of my knowledge, no other cases where there has been
+as substantial an increasing in spacing as for India.
+
+To understand how cohort fertility has changed over time and how strong the bias in
+TFR is, I compare predicted fertility using both a version of the total fertility
+rate and the hazard model results presented above as shown in Table \ref{tab:fertility}.
+
+\input{../tables/fertility.tex}
+
+The TFR measure uses births up to parity four to make the measure comparable to what I 
+can calculate for the hazard model, and I calculate this four-parity TFR by urban/rural 
+and the education groups used above.
+Hence, the TFRs are not directly comparable to those in the NFHS reports, although the
+differences should be smaller the higher the education group and the most recent the 
+survey provided that cohort fertility has fallen over time.
+Otherwise, I follow the procedure used in the NFHS reports and calculate age specific 
+fertility rates for five-year age groups using the number of births in months 1 to 36 
+before the survey month (births in the survey month are not included) and the number
+of women in each age group.%
+\footnote{
+See \citet{Croft2018} for more detail.
+Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
+is based on the household rosters, assuming that never-married women have had no children.
+Because of the low number of births to women aged 45 to 49 this age group was not
+used for the hazard model estimations and, therefore, is also excluded for the fertility
+rate.
+}
+
+NFHS-1 was collected after sex selection was introduced and it is, therefore, not 
+possible to calculate a fertility rate in exactly the same manner for a period before 
+sex selection was widely available.
+Instead, I calculate the fertility rates for women who was between 15 and 39 years of
+age five years prior to the survey month, again using the number of births three years 
+before that.
+Given the relatively low number of births to women 40 to 45 years of age, this approach 
+provides the best estimate of the fertility rate at the time when sex selection still was 
+not widespread.
+This fertility rate is shown as ``1987--88'' in the table.
+
+To predict cohort fertility based on the models above, I estimate the probability of 
+progression to the next parity for each spell.
+I include the spell from marriage to first birth, even those results are not examined 
+above because of the problems with capturing the exact timing of marriages for the first 
+two rounds of the survey.
+The estimated progression probabilities should, however, be less affected by this
+problem.
+To ensure that the predictions depend solely on sample composition and the estimate, I
+use the age at marriage for each woman and predict the likelihood of progressing to
+each parity, assuming two years increases in age between each parity.
+Hence, for a woman married at age 20, I use age 22 for predicting progression 
+to the second birth, 24 for the third, and 26 for the fourth.
+
+The parity progression depends on the sex composition for prior children for
+parity two and above.
+For example, the likelihood of a second birth is the probability of having a first birth 
+multiplied with
+sum of the 
+probability of having a son as the first child conditional on having a first child 
+multiplied with parity progression probability if the first child is a son 
+and the 
+probability of having a girl as the first child  conditional on having a first child
+multiplied with the parity progression probability if the first child is a girl.
+$$
+prob(2nd) = prob(1st) * (prob(son|1st)*prob(2nd|son) + prob(girl|1st) * prob(2nd|girl)
+$$
+
+The survey rounds do not coincide entirely with the periods I use for the model.
+For the NFHS-4, I use the model results for the 2005--2016 period, 
+for NFHS-3 the 1995-2004, NFHS-2 1985-1994, and for NFHS-1 1972-1984.
+
+The predicted fertility using the hazard model assumes that women in the sample
+follows the parity progression probability based on the given period. 
+For example, for the NFHS-4 the predictions assume that the women in the sample follow
+the estimated behavior for all four spells based on the 2005--2016 sample.
+
+The predicted cohort fertility based on the hazard model is consistently higher and
+declines faster than the predicted fertility based on the four-parity fertility rate.
+
+The faster decline in predicted fertility based on the hazard model is consistent with
+a large bias in the fertility rate measure arising from later marriage, increased use of 
+sex selection, and the general increase in birth spacing shown above.
+
+Consistent with the rapid increase in the use of sex selection from the mid-eighties
+the most substantial differences between the two fertility measures are for higher
+educated women for earlier samples.
+
 \section{Mortality and the Changing Birth Spacing\label{sec:mortality}}
-
-\section{How Much has Fertility Really Fallen?\label{sec:fertility}}
 

### 2020-01-16 paper/sex_selection_spacing-ver3.tex
Continue editing fertility discussion

@@
 problem.
+
 To ensure that the predictions depend solely on sample composition and the estimate, I
 use the age at marriage for each woman and predict the likelihood of progressing to
-each parity, assuming two years increases in age between each parity.
-Hence, for a woman married at age 20, I use age 22 for predicting progression 
-to the second birth, 24 for the third, and 26 for the fourth.
-
-The parity progression depends on the sex composition for prior children for
-parity two and above.
-For example, the likelihood of a second birth is the probability of having a first birth 
-multiplied with
-sum of the 
-probability of having a son as the first child conditional on having a first child 
-multiplied with parity progression probability if the first child is a son 
-and the 
-probability of having a girl as the first child  conditional on having a first child
-multiplied with the parity progression probability if the first child is a girl.
-$$
-prob(2nd) = prob(1st) * (prob(son|1st)*prob(2nd|son) + prob(girl|1st) * prob(2nd|girl)
-$$
-
-The survey rounds do not coincide entirely with the periods I use for the model.
+each parity, assuming three years increases in age between each parity.
+Hence, for a woman married at age 20, I use age 23 for predicting progression 
+to the second birth, 26 for the third, and 29 for the fourth.
+[TK Predicted fertility is higher the younger the women and the shorter the assumed spacing?]
+
+As shown above, the parity progression depends critically on the sex composition for prior 
+children for parity two and above.
+I, therefore, estimate the progression probability for each possible sex composition
+and weigh those probabilities with the likelihood that they will occur based on the
+prior spells.
+
+The survey rounds do not coincide entirely with the periods I use for the hazard model.
 For the NFHS-4, I use the model results for the 2005--2016 period, 
-for NFHS-3 the 1995-2004, NFHS-2 1985-1994, and for NFHS-1 1972-1984.
+for NFHS-3 the 1995--2004 period, 
+for NFHS-2 the 1985--1994 period, 
+and for NFHS-1 the 1972--1984 period.
+Because of the small number of women who had the highest level of education in the
+1972--1984 period, I do not present a predicted fertility for this case.
 
 The predicted fertility using the hazard model assumes that women in the sample
-follows the parity progression probability based on the given period. 
-For example, for the NFHS-4 the predictions assume that the women in the sample follow
-the estimated behavior for all four spells based on the 2005--2016 sample.
+follows the parity progression probability in the period. 
+For example, for the NFHS-4 the predictions I assume that all women in the sample follow
+the estimated behavior for all four spells based on the 2005--2016 results.
 
@@
 
-Consistent with the rapid increase in the use of sex selection from the mid-eighties
-the most substantial differences between the two fertility measures are for higher
-educated women for earlier samples.
+[some TFRs are actually going up!]
+
+[CAVEAT: only first four births, these predicted fertility numbers likely too low,
+especially for the lower education groups]
 

### 2020-01-17 paper/sex_selection_spacing-ver3.tex
Add more discussion of fertility results and edit method description

@@
 
-To predict cohort fertility based on the models above, I estimate the probability of 
-progression to the next parity for each spell.
+To predict cohort fertility based on the hazard models above, I estimate the probability 
+of progression to the next parity for each spell.
 I include the spell from marriage to first birth, even those results are not examined 
@@
 to the second birth, 26 for the third, and 29 for the fourth.
-[TK Predicted fertility is higher the younger the women and the shorter the assumed spacing?]
+Decreasing the increases in age between parities leads to slightly higher predicted 
+fertility.
 
@@
 prior spells.
+
+The predicted fertility using the hazard model assumes that women in the sample
+follows the parity progression probability in the period. 
+For example, for the NFHS-4 the predictions I assume that all women in the sample follow
+the estimated behavior for all four spells based on the 2005--2016 results.
 
@@
 
-The predicted fertility using the hazard model assumes that women in the sample
-follows the parity progression probability in the period. 
-For example, for the NFHS-4 the predictions I assume that all women in the sample follow
-the estimated behavior for all four spells based on the 2005--2016 results.
-
-The predicted cohort fertility based on the hazard model is consistently higher and
-declines faster than the predicted fertility based on the four-parity fertility rate.
-
+The main result is that the predicted cohort fertility based on the hazard model is 
+consistently higher and declines faster than the four-parity fertility rate.
 The faster decline in predicted fertility based on the hazard model is consistent with
@@
 
-[some TFRs are actually going up!]
-
-[CAVEAT: only first four births, these predicted fertility numbers likely too low,
-especially for the lower education groups]
+The potential bias in the fertility rate is also evident in the fact that the 
+fertility rate is increasing over time for some groups.
+For example, urban women with eight to eleven years of education showed 1.84, 1.81, and
+1.87 over the last three surveys and the increase from NFHS-3 to NFHS-4 is even larger
+for rural women with one to seven years of education.
+These increases are likely the result of a stabilization of the age of first birth and
+the spacing between births.%
+\footnote{
+Increases in TFR over time, even in the face of declining fertility is not 
+unusual, as shown by Costa Rica \citep{Bongaarts1999}.
+}
+
+Despite the decline in the predicted cohort fertility based on the hazard model, these 
+are still generally above the generally accepted replacement level of 2.1.
+Only for urban women with twelve or more years of education is the predicted cohort
+fertility below 2.1, and even then it is still more than 0.3 children higher than the 
+fertility rate estimate of 1.5.
+Furthermore, because only the first four births are used, the predicted cohort fertility
+numbers are likely too low, especially for the lower education groups.
 

### 2020-01-17 paper/sex_selection_spacing-ver3.tex
Initial graphs for highest education group

@@
 % power to detect it.
+
+\subsection{Highest Education Women}
+
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
+% \\
+% \caption*{Rural}
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
+% \caption{high education}
+% \label{fig:bootstrap_high}
+% \end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{Urban}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_highest_urban_all}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_highest_rural_all} 
+    \end{minipage}
+} 
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight or more years of education}
+\label{fig:bootstrap_highest}
+\end{figure}
 

### 2020-01-18 paper/sex_selection_spacing-ver3.tex
Ignore 4th spell for highest and add tables

@@
 \caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education}
+a next birth for women with eight to eleven years of education}
 \label{fig:bootstrap_high}
@@
 }
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_highest_urban_all}
-    \end{minipage}
-}
 \\
@@
 } 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_highest_rural_all} 
-    \end{minipage}
-} 
 \caption{Estimated average spell length, sex ratio, and probability of 
-a next birth for women with eight or more years of education}
+a next birth for women with twelve or more years of education}
 \label{fig:bootstrap_highest}
@@
 
-\section{Characteristics of Women Work Experiences}
+\section{Characteristics of Women's Work Experiences}
 
@@
 
+\input{../tables/bootstrap_duration_avg_sex_ratio_highest_all.tex}
+
 \input{../tables/bootstrap_duration_p25_p75_low_all.tex}
@@
 \input{../tables/bootstrap_duration_p25_p75_high_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_highest_all.tex}
 

### 2020-01-18 paper/sex_selection_spacing-ver3.tex
Update table and graphs with 4th education group

@@
 % \caption*{Urban}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_all}} 
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_highest_urban_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_highest_urban_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_highest_urban_all}} 
 % \\
 % \caption*{Rural}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_all}} 
+% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_highest_rural_all}} 
+% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_highest_rural_all}} 
+% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_highest_rural_all}} 
 % \caption{high education}
@@
 %         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_high_urban_pps}} 
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_highest_urban_pps}} 
 %         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}} 
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
         \captionsetup[subfigure]{labelformat=parens}
@@
 Increases in TFR over time, even in the face of declining fertility is not 
-unusual, as shown by Costa Rica \citep{Bongaarts1999}.
+unusual, as shown by Columbia in the early 1990s \citep{Bongaarts1999}.
 }
@@
 The first set of tables, Tables \ref{tab:avg_sex_ratio_low}, \ref{tab:avg_sex_ratio_med}, 
-and \ref{tab:avg_sex_ratio_high}, show predicted average birth intervals, sex ratios, and 
+\ref{tab:avg_sex_ratio_high}, and \ref{tab:avg_sex_ratio_highest}, show predicted average 
+birth intervals, sex ratios, and 
 probabilities of having a birth by decade, spell, and sex composition for the three 
@@
 % \caption*{8 or more Years of Education}
-% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
-% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
+% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_highest_urban_pps}} 
+% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_highest_rural_pps}} 
 % \caption{Survival curves conditional on progression to first birth; start point is month of marriage}
@@
 \caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
+for women with eight to eleven years of education by month beginning 9 months after prior birth.
 }
 \label{fig:results_spell2_high_pps}
+\end{figure}
+
+% Highest education
+
+% PARITY PROGRESSION SURVIVAL - Highest education
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with twelve or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell2_highest_pps}
 \end{figure}
@@
 \caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
+for women with eight to eleven years of education by month beginning 9 months after prior birth.
 }
 \label{fig:results_spell3_high_pps}
+\end{figure}
+
+% Highest education
+
+% PARITY PROGRESSION SURVIVAL - highest
+
+\begin{figure}[htpb]
+\centering
+\caption*{Urban}
+\setcounter{subfigure}{-1}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{-0}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{1}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{2}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption*{Rural}
+\setcounter{subfigure}{3}
+\subfloat[1972--1984]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_rural_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+\setcounter{subfigure}{4}
+\subfloat[1985--1994]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} \\
+\setcounter{subfigure}{5}
+\subfloat[1995--2004]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{6}
+\subfloat[2005--2016]{
+    \begin{minipage}{0.31\textwidth}
+        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_rural_pps}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\caption{Survival curves conditional on parity progression
+for women with twelve or more years of education by month beginning 9 months after prior birth.
+}
+\label{fig:results_spell3_highest_pps}
 \end{figure}
@@
 \caption{Survival curves conditional on parity progression
-for women with 8 or more years of education by month beginning 9 months after prior birth.
+for women with eight to eleven years of education by month beginning 9 months after prior birth.
 }

### 2020-01-20 paper/sex_selection_spacing-ver3.tex
Remove pps graph for 4th spell for highest education

@@
 } 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{
-Survival curves conditional on progression to next birth for urban women with eight or
-more years of education; start point is nine months after prior birth
-}
+% \\
+% \rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.46\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.46\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{
+% Survival curves conditional on progression to next birth for urban women with eight or
+% more years of education; start point is nine months after prior birth
+% }
 \label{fig:pps_high}

### 2020-01-21 paper/sex_selection_spacing-ver3.tex
Reorganizing introduction

--- 2020-01-18 paper/sex_selection_spacing-ver3.tex
@@
 
+% [Why India?]
+India has a long history of pro-male preference \citep{Kishor1993,murthi95,arnold98}.
+Mortality risk is higher for females than males for most ages groups, resulting in
+an almost continuous increase in the ratio of males to females over the last century
+ \citep{dyson01,Navaneetham2011,Bongaarts2015}.
+Differential stopping behavior is widespread, with an additional child more likely the
+fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
+The duration to the next birth is also shorter with fewer sons, likely contributing
+to the higher mortality and morbidity risk for girls
+\citep{Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Maitra2008,Makepeace2008,
+Jayachandran2011,Kumar2016,Jayachandran2017a,Ghosh2018}.
+Furthermore, India's total fertility rate has declined substantially and is now below 
+replacement in some areas [TK more precision] 
+\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
+The combination of falling fertility, strong son preference, and expanding access to 
+prenatal sex determination dramaticly increased the males-to-females ratio at 
+birth over the last three decades
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,
+Bongaarts2013,Portner2015b,Jayachandran2017}.
+
+Highlights:
+- changes in spacing overall
+- much longer spacing with girls
+- biases in TFR
+- effects on mortality
+
 Birth spacing has long served as a measure of son preference, with strong
@@
 1972 to 2016.
-
-% [Why India?]
-India is a particularly compelling case with its long history of male preference, 
-especially in the northern states \citep{Kishor1993,murthi95,arnold98}.
-Mortality risk is higher for females than males for most ages groups, resulting in
-an almost continuous increase in India's overall ratio of males to females 
-over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
-Differential stopping behavior is widespread, with an additional child more likely the
-fewer sons a family has 
-\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
-\footnote{
-Other countries show a similar pattern
-\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
-}
-Furthermore, fertility has declined substantially, to the point where it is now at, or even 
-below, replacement in some areas 
-\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-The combination of falling fertility, strong son preference, and expanding access to 
-prenatal sex determination has lead to dramatic increases in the males-to-females ratio at 
-birth over the last three decades
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,Bongaarts2013,Portner2015b,Jayachandran2017}.
 

### 2020-01-24 paper/sex_selection_spacing-ver3.tex
Thighten up introduction

@@
 abortion extends spacing by six to twelve months. 
-I introduce an empirical method that simultaneously accounts for how sex selection 
+I apply an empirical method that simultaneously accounts for how sex selection 
 increases both birth spacing and the likelihood of a son. 
@@
 
-% [Why India?]
-India has a long history of pro-male preference \citep{Kishor1993,murthi95,arnold98}.
-Mortality risk is higher for females than males for most ages groups, resulting in
-an almost continuous increase in the ratio of males to females over the last century
- \citep{dyson01,Navaneetham2011,Bongaarts2015}.
-Differential stopping behavior is widespread, with an additional child more likely the
-fewer sons a family has 
-\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
-The duration to the next birth is also shorter with fewer sons, likely contributing
-to the higher mortality and morbidity risk for girls
-\citep{Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Maitra2008,Makepeace2008,
-Jayachandran2011,Kumar2016,Jayachandran2017a,Ghosh2018}.
-Furthermore, India's total fertility rate has declined substantially and is now below 
-replacement in some areas [TK more precision] 
-\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-The combination of falling fertility, strong son preference, and expanding access to 
-prenatal sex determination dramaticly increased the males-to-females ratio at 
-birth over the last three decades
+India has changed significantly over the last three decades:
+the economy has grown substantially,
+education has increased for both males and females,
+and the total fertility rate has fallen to the point where, at 2.2, it is just
+above replacement 
+\citep{Bosworth2008,Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
+However, access to prenatal sex determination also expanded rapidly starting in the mid-1980s,
+and, combined with a continued strong son preference, this dramatically increased the 
+males-to-females ratio at birth 
 \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,
@@
 
-Highlights:
-- changes in spacing overall
-- much longer spacing with girls
-- biases in TFR
-- effects on mortality
-
-Birth spacing has long served as a measure of son preference, with strong
-son preference associated with shorter birth intervals the
-fewer sons a family has \citep{ben-porath76b,Leung1988}.
-However, the introduction of prenatal sex determination potentially 
-changed the relationship between son preference and birth spacing.
-The stronger the son preference, the more likely couples are to resort to sex-selective 
-abortions, and each abortion increases the interval between births by six to twelve 
-months.%
+What has not previously been examined is the impact of these changes on birth spacing.
+Economic growth, increasing female education, and falling fertility has been
+shown to significantly affect birth spacing in other countries [TK references].
+India is, however, fundamentally different in at least one respect and that is 
+the substantial use of sex-selective abortions.
+
+The stronger the son preference and the lower the desired fertility, the more likely 
+couples are to resort to sex-selective abortions, and each abortion increases the 
+interval between births by six to twelve months.%
 \footnote{
@@
 }
-Hence, longer birth intervals in the absence of sons, which previously would be taken as 
-an indicator of lower son preference, may now instead arise because couples with a strong 
-son preference use sex selection.
+Hence, the changes in birth spacing may be much larger in India than what we have
+observed in other places as they developed.
+
+Understanding how birth spacing changes is important for three reasons.
+
+First, tempo effects, arising from changes in birth spacing, biases the total fertility 
+rate (TFR), in the sense that the TFR becomes a more biased measure of cohort fertility
+\citep{Bongaarts1999,Ni-Bhrolchain2011}.
+Hence, it is possible that fertility is, in fact, substantially higher than what
+is generally accepted based on the TFR.
+
+Second, longer birth spacing is associated with lower mortality and 
+morbidity risk \citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
+In India, the duration to the next birth has traditionally been shorter with fewer sons, 
+which likely contributed to the higher mortality and morbidity risk for girls
+\citep{Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Maitra2008,Makepeace2008,
+Jayachandran2011,Kumar2016,Jayachandran2017a,Ghosh2018}.
+Longer spacing between births then potentially lowers mortality, although there may
+be a counteracting effect of multiple abortions.
+
+Finally, birth spacing has long served as a measure of son preference, with strong
+son preference associated with shorter birth intervals the fewer sons a family has 
+\citep{ben-porath76b,Leung1988}.
+Instead, longer birth intervals in the absence of sons, which previously would be 
+taken as an indicator of lower son preference, may now instead arise because couples 
+with a strong son preference use sex selection.
 
@@
 groups with the introduction of sex selection.
-I introduce an empirical method that directly incorporates the effects of 
+I apply an empirical method that directly incorporates the effects of 
 sex-selective abortions on birth intervals
@@
 1972 to 2016. 
-
-% [Why spacing?] 
-There are four main reasons for examining birth spacing and how it changes with 
-access to sex selection.
-First, researchers have made extensive use of birth spacing as a measure of son preference, 
-and it is critical to understand to what extent spacing is still a useful measure of son 
-preference.
-For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
-a boy as the last-born child, significantly increase the duration to next birth,
-\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
-\footnote{
-Ethnic Indians in South Africa also show a longer duration after the birth of a 
-son than after a daughter \citep{Gangadharan2003}.
-}
-Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
-absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
-\citep{Rossi2015}.
-
-Second, birth spacing can affect children's short and long-term outcomes.
-Most of the research finds a negative impact of short spacing on child health, especially 
-for very short intervals of 18 months or less \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
-There is evidence in countries as diverse as Bangladesh, Brazil, El Salvadore, India,
-and Pakistan of worse health outcomes and a higher mortality risk the shorter the birth
-interval
-\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,Ghosh2018}.
-Most of the evidence on longer-term outcomes come from Western countries.
-In the US, for example, a longer interval between births increases the older, but not the
-younger, sibling's test scores \citep{Buckles2012}.
-Furthermore, close spacing appears to increase the risk of dropping out of
-high school and lower the probability of attending a post-secondary school in both the
-US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.%
-\footnote{
-However, recent results from Sweden show no relationship between birth spacing, even if 
-very short, and outcomes such as years of education completed, earnings, and unemployment 
-\citep{Barclay2017}.
-}
-
-Third, the mother may also be affected by the length of the birth intervals, although 
-reviews of the literature show mixed results on mother's anthropometric status 
-\citep{Dewey2007,Conde-Agudelo2012}.
-For India, there is, however, evidence that women with first-born girls are more likely to 
-have anemia, possibly because short birth spacing can resulting in maternal depletion 
-\citep{Milazzo2018}.
-In Western countries, a longer interval between births has positive effects on long-term 
-labor market outcomes, such as participation and income \citep{Gough2017,Karimi2014}.
-
-Finally, we know less about what determines spacing behavior in developing countries than 
-in developed countries, and with declining fertility and increasing numbers of women 
-entering the labor force, understanding how couples make timing decisions is necessary 
-for the design of suitable policies \citep{Portner2018}.%
-\footnote{
-It is clear that birth spacing does respond to policies in both developed and 
-developing countries \citep{Pettersson-Lidbom2009,Todd2012,Meckel2015,Ghosh2018}.
-}
-Even the effects of access to contraceptive and declining fertility on spacing are unclear.
-On the one hand, access to contraceptives allows women to avoid too short spacing between 
-birth.
-On the other hand, increased reliability of access and effectiveness of contraceptives can 
-lead to shorter intervals between births if women used to have longer spacing to avoid
-having too many children by accident \citep{Keyfitz1971,Heckman1976}.
-These two counteracting effects may explain why better-educated women have shorter spacing 
-than less educated women in some instances but not in others and why finding statistically 
-significant effects of contraception use on birth spacing is difficult 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.%
-\footnote{
-In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
-access to family planning \citep{Rahman1993}.
-Other evidence, however, points to families ability to time births, even in the absence
-of modern contraceptives \citep{Jayachandran2011,Alam2018}.
-}
+I address three main questions.
 
 % [Hypotheses / questions]
-Despite the increasing use of sex selection, the critical impacts of spacing on outcomes 
-for both mother and children, and the extensive use of spacing to measure son preference, 
-there has so far been no systematic examination of what effect access to sex selection 
-have on spacing.
-I address three questions to remedy this shortcoming in the literature.
 
@@
 in both urban and rural areas has stagnated or decreased
-\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018, Bhargava2019}.
+\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
 A decline in female labor force participation at the beginning of development is

### 2020-01-24 paper/sex_selection_spacing-ver3.tex
Separate out introduction of sex-selection
More concise version of introduction and more upfront discussion of
birth spacing.

@@
 the economy has grown substantially,
-education has increased for both males and females,
+education levels have increased for both males and females,
 and the total fertility rate has fallen to the point where, at 2.2, it is just
 above replacement 
-\citep{Bosworth2008,Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
-However, access to prenatal sex determination also expanded rapidly starting in the mid-1980s,
-and, combined with a continued strong son preference, this dramatically increased the 
-males-to-females ratio at birth 
+\citep{Bosworth2008,Guilmoto2013,Dharmalingam2014,
+International-Institute-for-Population-Sciences-IIPS2017}.
+
+Over the same period, India has, however, also experienced a rapidly expanding 
+access to prenatal sex determination.
+Combined with continued strong son preference, the result has been a dramatic 
+increase in the males-to-females ratio at birth
 \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,
@@
 
-What has not previously been examined is the impact of these changes on birth spacing.
-Economic growth, increasing female education, and falling fertility has been
-shown to significantly affect birth spacing in other countries [TK references].
-India is, however, fundamentally different in at least one respect and that is 
-the substantial use of sex-selective abortions.
-
-The stronger the son preference and the lower the desired fertility, the more likely 
-couples are to resort to sex-selective abortions, and each abortion increases the 
-interval between births by six to twelve months.%
+What the prior research on India has not appreciated is that since each abortion 
+increases the interval between births by six to twelve months, the growing use of 
+sex-selective abortions has the potential to increase birth spacing substantially. %
 \footnote{
@@
 }
-Hence, the changes in birth spacing may be much larger in India than what we have
-observed in other places as they developed.
-
-Understanding how birth spacing changes is important for three reasons.
-
-First, tempo effects, arising from changes in birth spacing, biases the total fertility 
-rate (TFR), in the sense that the TFR becomes a more biased measure of cohort fertility
-\citep{Bongaarts1999,Ni-Bhrolchain2011}.
-Hence, it is possible that fertility is, in fact, substantially higher than what
-is generally accepted based on the TFR.
+Add to this increase that the combination of increasing female education, 
+lower fertility, higher household income, and the low and declining female 
+labor force participation are also likely to impact birth spacing.
+Hence, the changes in birth spacing may be much more substantial in India 
+than what we have observed in other countries as they developed.
+
+Understanding the changes in birth spacing is essential for three reasons.
+
+First, tempo effects, arising from changes in birth spacing, bias the total 
+fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
+of cohort fertility \citep{Bongaarts1999,Ni-Bhrolchain2011}.
+Hence, fertility may be, in fact, substantially higher than what is generally 
+accepted based on the TFR.
 
@@
 Finally, birth spacing has long served as a measure of son preference, with strong
-son preference associated with shorter birth intervals the fewer sons a family has 
+son preference associated with shorter birth intervals, the fewer sons a family has 
 \citep{ben-porath76b,Leung1988}.
-Instead, longer birth intervals in the absence of sons, which previously would be 
-taken as an indicator of lower son preference, may now instead arise because couples 
-with a strong son preference use sex selection.
+Now, longer birth intervals in the absence of sons, rather than an indicator of 
+lower son preference, may instead arise because couples with a strong preference 
+for sons use sex selection.
 
@@
 groups with the introduction of sex selection.
-I apply an empirical method that directly incorporates the effects of 
+I apply a competing risk hazard model that directly incorporates the effects of 
 sex-selective abortions on birth intervals
 \emph{and} 
-the likelihood of a son. 
-The method can be used to analyze both situations with and without prenatal
-sex selection.
+the likelihood of a son, 
+but which also works in cases without prenatal sex selection.
 I apply the method to birth histories of Hindu women, using data from the four
@@
 1972 to 2016.
-I address three main questions.
 
 % [Hypotheses / questions]
+I address four main questions.
+[TK combine questions and highlight of answers here?]
 
@@
 boys a family has when prenatal sex selection is available, possibly to the point where
-we observe a reversal of the standard spacing pattern.
+we observe a reversal of the traditional spacing pattern.
 Families with son preference who---for one reason or another---do not use prenatal sex 
@@
 
-Second, have the shapes of the survival curves changed?
+Second, how has the distribution of birth spacing changed?
 Although examining average birth intervals helps us understand the overall changes in 
@@
 continued use of sex selection to ensure a son.
+
+Third, to what extent does TFR reflect cohort fertility?
+An advantage of the empirical model is that I can predict fertility behavior taking into
+account both the likelihoods of parity progression and having a child of a specific sex.
+I compare those predictions with fertility rate estimates based on the same data to
+show how the increases in birth spacing has led to a substantial overestimate of the
+decline in fertility [TK too imprecise? underestimate of the level, rather?]
+
+Finally, has the relationship between birth spacing and mortality changed over time?
+[TK]
 

### 2020-01-26 paper/sex_selection_spacing-ver3.tex
Combine questions and results in Introduction

@@
 
-India has changed significantly over the last three decades:
+India has changed significantly over the last four decades:
 the economy has grown substantially,
@@
 lower son preference, may instead arise because couples with a strong preference 
-for sons use sex selection.
+for sons use sex selection, possibly to the point where we observe a reversal of 
+the traditional spacing pattern.
+Families with son preference who---for one reason or another---do not use prenatal 
+sex selection likely continue to have shorter birth spacing.
 
@@
 
-First, how did average birth intervals change over time for different groups and how do 
+First, how did average birth intervals change over time for different groups, and how do 
 these changes relate to the use of sex selection?
-The hypothesis is that in the absence of sex selection son preference leads to shorter 
-spacing the fewer boys a family has, whereas son preference increases spacing the fewer 
-boys a family has when prenatal sex selection is available, possibly to the point where
-we observe a reversal of the traditional spacing pattern.
-Families with son preference who---for one reason or another---do not use prenatal sex 
-selection likely continue to have shorter birth spacing.
-Based on the prior literature on sex selection, I focus on how birth intervals have
+To show how sex selection has affected birth spacing, I focus on how birth intervals have
 changed for different education levels, urban or rural, and the sex composition of 
@@
 
+Birth intervals have increased for all education groups over the four decades, 
+with larger increases, the higher the parity and the higher the education level.
+Women who are most likely to use sex selection---well-educated women with no
+sons---have seen the most substantial increases in birth intervals.
+[TK check this!] As a result, well-educated women now show a reversal of the traditional spacing 
+pattern, with the longest intervals for women with no sons.
+Those least likely to use sex selection, women with no education in rural areas, 
+still follow the traditional pattern of short spacing when they have girls and 
+little evidence of the use of sex selection.
+
 Second, how has the distribution of birth spacing changed?
-Although examining average birth intervals helps us understand the overall changes in 
+Although examiniong average birth intervals helps us understand the overall changes in 
 spacing behavior, it tells us little about how these changes came about.
@@
 
+[TK this is unclear]
+The traditional pattern of longer average spacing with sons appears to arise from 
+an increase in the number of very long intervals, rather than from fewer very short 
+birth intervals. 
+Across education groups, there appears to be little difference in the likelihood of 
+having a very short birth interval across sex compositions, especially for lower parities.
+
 Third, to what extent does TFR reflect cohort fertility?
 An advantage of the empirical model is that I can predict fertility behavior taking into
-account both the likelihoods of parity progression and having a child of a specific sex.
+account both the likelihood of parity progression and having a child of a specific sex.
 I compare those predictions with fertility rate estimates based on the same data to
-show how the increases in birth spacing has led to a substantial overestimate of the
-decline in fertility [TK too imprecise? underestimate of the level, rather?]
+show how the increases in birth spacing have led to a substantial overestimate of how 
+fast fertility has declined. [TK too imprecise? underestimate of the level, rather?]
 
@@
 
-There are four main results.
-First, the intervals between births have increased for all education groups over the four 
-decades.
-These increases are larger the higher the parity and the higher the education 
-level.
-Second, those women who are most likely to use sex selection---well-educated women with no
-sons---have seen the largest increases in birth intervals.
-As a result, well-educated women now show a reversal of the traditional spacing 
-pattern, with the longest birth intervals for women with no sons.
-Third, women who are least likely to use sex selection, those with no education in
-rural areas, still follow the standard pattern of short spacing when they have girls and 
-little evidence of the use of sex selection.
-Finally, the traditional pattern of longer average spacing with sons appear to arise from 
-more very long intervals, rather than from fewer very short birth intervals; across 
-education groups, there appears to be little difference in the likelihood of having a very 
-short birth interval across sex compositions, especially for lower parities.
+[TK results]
 

### 2020-01-26 paper/sex_selection_spacing-ver3.tex

@@
         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\caption{
-Survival curves conditional on progression to next birth for urban women with eight or
-more years of education; start point is nine months after prior birth
-}
+        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}} 
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+} 
+% \\
+% \rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.46\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.46\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \caption{
+% Survival curves conditional on progression to next birth for urban women with eight or
+% more years of education; start point is nine months after prior birth
+% }
 \label{fig:pps_high}

### 2020-01-27 paper/infant_mortality.tex
Initial commit of infant mortality discussion
Includes set-up, prior results, and estimation considerations. No
results yet.

\section{Infant Mortality}

The prior literature show that shorter birth spacing, especially very short spacing,
is associated with higher risk of infant mortality.
Hence, it is possible that the increasing use of sex-selective abortions could
directly reduce infant mortality by lengthening the duration from the prior birth.

There are a number of potential issues with understanding to what extent this
has happened.

First, the sex of the next child is no longer random, and boys, in the absence of
differential treatment, have higher infant mortality than girls.

Second, it may be that what matters is not the time between births, but rather 
between pregnancies, in which case multiple abortions followed quickly by new 
pregnancies would lead to shorter real spells of recovery.
The implication is that long spells might have a higher mortality risk since
they are now more likely with multiple abortions.

Third, as I show above the use of sex selection is more prevalent the higher the
education level of the mother.
Higher maternal education is, however, also associated with lower mortality risk
to begin with.
On top of this, with economic growth and better health care, infant mortality
may have fallen across all education groups and areas in the period covered.

I address three questions.

First, does the increased use of sex selection lead to higher mortality risk?

Second, has the negative effects of short spacing changed over time?

Third, how do the effects of short spacing vary by education level in India?

There are a number of problems with estimating the relationship between 
sex-selective abortions and infant mortality.

First, there are potential selection problem.
For example, women who face higher mortality risk of their children might forego 
the use of sex selection to ensure that they reach their desired number of 
children.
If these women also know to avoid very short birth spacing, the precense of 
these women in the sample would inflate the mortality of the "middle" birth
spacing, relative to the very short or very long birth spacing.

[our JDE paper]

An additional selection with the opposite effect is that women who have
difficulties conceiving or carrying a preganancy to term may also have higher 
mortality risk for their offspring, leading to a supriuos correlation
between very long birth spacing and mortality \citep{Kozuki2013}. 
If better health care and higher income means that more of these women are
now able to carry their pregnancy to term we can end up with more births
after long spells that have higher mortality risk but not because of the
increased use of sex selection.

Given the data and that the focus of this paper is mainly on the birth
spacing, a more in-depth treatment of these issue is the topic of future work.
Part of the problem here is also that the method used previously, such
as family fixed effects does not work well when the number of births is
very low as it is for higher education women who use sex 
selection, especially since the spacing from marriage to first birth
does not provide any information \citep{Kozuki2013,Molitoris2019}.

Second, the actual number of abortions are unobserved.
The results above do show, however, how the use of sex selection vary
by education and sex composition of prior children.
I, therefore, estimate infant mortality risk taking into account the
sex composition of the prior children, as well as the index child.

Starting with the sample used for estimating birth spacing, I select, by
parity, children born more than 12 months before the survey month.
The dependent variable is whether the child died within the first twelve
months of life (infant mortality).
As above, I restrict the analysis to parity two through four.

The main set of explanatory variable consists of dummies for birth spacing,
divided into less than 15 months from when conception could realistically
could happen (same definition as above) and based on the finding that 
spacing less than 24 months between birth is associated with higher
infant mortality \citep{Molitoris2019}, and then in 12 months intervals
until TK, where all births after and until 96 months are included.%
\footnote{
\citet{Molitoris2019} has used quartic functions, but the concern is
that with the relatively small number sample here the shape
of the function would be strongly influenced by a small number of
observations.
Using dummies provides a more flexible specification and the standard
error will directly reflect the higher degree of noise for the
spells periods with fewer observations.
}
In addition, I use dummies for sex of the index child (the child whose 
mortality is estimated) and the sex composition of the prior children.
Birth spacing dummies, sex of index child, and sex composition dummies
are all interacted.
The other explanatory variables are the same as above and estimations
are done separately by education level.

I estimate probability of infant mortality using a logit model.
Results are presented as the predicted probability of dying within the
first year at the possible combinations of index child sex, sex composition
of prior children, and the birth spacing dummied.
All other variables are set to their average values.
[TK ehh, did I also do urban/rural?]

Figures TK to TK show the estimated probabilities.
To ease legibility all confidence intervals are suppressed
(graphs with confidence intervals are available on request).

### 2020-01-28 paper/sex_selection_spacing-ver3.tex
Minor edits and additions throughout paper

@@
 
-\date{December 2018}
+\date{January 2019}
 
@@
 increases the interval between births by six to twelve months, the growing use of 
-sex-selective abortions has the potential to increase birth spacing substantially. %
+sex-selective abortions has the potential to substantially increase birth spacing.%
 \footnote{
@@
 fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
-of cohort fertility \citep{Bongaarts1999,Ni-Bhrolchain2011}.
-Hence, fertility may be, in fact, substantially higher than what is generally 
-accepted based on the TFR.
+of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
+If birth spacing increased substantially over time, India's fertility may, in 
+fact, be substantially higher than what is generally accepted based on the TFR.
 
@@
 the traditional spacing pattern.
-Families with son preference who---for one reason or another---do not use prenatal 
-sex selection likely continue to have shorter birth spacing.
+Despite a large literature on son preference and birth spacing, there is, however,
+no prior research has examined how sex selection affects spacing.
 
@@
 groups with the introduction of sex selection.
-I apply a competing risk hazard model that directly incorporates the effects of 
+Using data from the four National Family and Health Surveys (NFHS), I apply
+a competing risk hazard model to the birth histories of Hindu women, covering
+the period 1972 to 2016.
+The competing risk hazard model directly incorporates the effects of 
 sex-selective abortions on birth intervals
@@
 the likelihood of a son, 
-but which also works in cases without prenatal sex selection.
-I apply the method to birth histories of Hindu women, using data from the four
-India's National Family and Health Surveys (NFHS), covering the period 
-1972 to 2016.
+but also works in cases without prenatal sex selection.
 
@@
 I address four main questions.
-[TK combine questions and highlight of answers here?]
 
@@
 The standard approach in the birth spacing literature is to use proportional hazard
-models with a single exit, the birth of a child.
-There are two problems with the standard approach in this setting.
+models with a single exit, the birth of a child.%
+\footnote{
+See \citet{Sheps1970} and \citet{Newman1984} for early discussions of why 
+hazard models are the preferred way to deal with the censoring of birth
+intervals.
+}
+There are, however, two problems with the standard approach in this setting.
 First, and most importantly, the introduction of sex selection means that the sex of the 
@@
 rate.
+The marital total fertility rate lead to unrealistically high numbers and is, therefore,
+not presented \citep{Hoem2011,Laplante2015}.
 }
@@
 
+[TK things to cover:
+- almost everybody marry, so these numbers should reflect cohort fertility relatively well
+- what happens when women begin to join the labor force in larger numbers?
+- better job oppportunities may be a direct way to affect sex selection since it makes 
+it more expensive to have long spacing
+]
+
+[TK future research:
+- health effects of multiple abortions on women and prior children
+- better address selection effects for mortality estimations
+- long-term outcomes for children
+- labor force participation
+- ]
+
 The central question addressed here is the extent to which spacing patterns significantly 
@@
 relative to after the birth of a boy.
-I introduce an empirical method that simultaneously accounts for spacing between births 
-and the potential use of sex selection, and apply the method to four decades of data 
-from India's NFHS.
+I apply an empirical method that simultaneously accounts for spacing between births 
+and the potential use of sex selection to four decades of data from India's NFHS.
 

### 2020-01-29 paper/infant_mortality.tex
Add figures and initial discussion of results

@@
 
+[Our Demography paper shows a different type of selection effect, where the
+use of sex selection biases the effect estimates of other variables that
+vary together with the use of sex selection.]
+
 Given the data and that the focus of this paper is mainly on the birth
@@
 does not provide any information \citep{Kozuki2013,Molitoris2019}.
+However, the fixed effects results and linear probability do not deviate
+substantially.
 
@@
 
-Figures TK to TK show the estimated probabilities.
+Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} show the 
+estimated probabilities.
 To ease legibility all confidence intervals are suppressed
 (graphs with confidence intervals are available on request).
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p1_low_dummies}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_low_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_low_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_low_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_low}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p1_med_dummies}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_med_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_med_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_med_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_med}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p1_high_dummies}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_high_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_high_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_high_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_high}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_highest_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_highest_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_highest_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_highest}
+\end{figure}
+
+For women with twelve or more years of education the results become very noisy
+because of the low number of births, especially for parity three and four, and
+the low mortality rate.
+As above, I do not show results for the 1972--84 period because there were too
+few women with this level of education for this period.
+
+Based on the second parity births, women with twelve or more years of education
+have the lowest infant mortality risk. 
+Even for very short birth intervals the mortality risk is less than five percent,
+and fall to less than half that for longer intervals.
+Given the low mortality there is, not surprisingly, much difference between
+the three periods covered.
+Furthermore, there is no evidence that longer intervals are associated with
+significantly higher mortality, especially for the groups most likely to have
+used sex selection (women with a girl as their first child and a boy as their
+second with a long interval).
+
+Women with eight to eleven years of education have marginally higher mortality
+risk than women with the most education, and also show slightly more evidence
+of increased mortality with very short spacing.
+Mortality risk have decreased slightly between periods, although the changes
+are relatively minor.
+As for women with the most education, there are not any statistically significant 
+differences or increases in mortality with longer spacing.
+Because of the low mortality risk and the relatively small number of births,
+the estimates for the third and fourth parity are noisy.
+
+Infant mortality risk for women with one to seven years of education have
+clearly decreased over time.
+This is also the first group that show increasing mortality risk with longer
+spacing, although this effect mostly disappears for the later periods.
+In other words, it does not appear to be the result of sex selection, but
+rather arise from the selection bias discussed above where women with long
+spells are those who find it difficult to either conceived and/or carry a 
+pregnancy to term and also have higher mortality risk for their offspring.
+
+Finally, women with no education have experienced substantial improvements
+in infant mortality risk over time.
+This decrease is especially pronounced for shorter intervals.
+For the longer intervals, there is surprisingly little difference across
+the education groups for the later periods.

### 2020-01-29 paper/sex_selection_spacing-ver3.tex
Add discussion of mortality to paper

--- 2020-01-26 paper/sex_selection_spacing-ver3.tex
@@
 abortion extends spacing by six to twelve months. 
-I apply an empirical method that simultaneously accounts for how sex selection 
+I introduce an empirical method that simultaneously accounts for how sex selection 
 increases both birth spacing and the likelihood of a son. 
@@
 
-India has changed significantly over the last four decades:
-the economy has grown substantially,
-education levels have increased for both males and females,
-and the total fertility rate has fallen to the point where, at 2.2, it is just
-above replacement 
-\citep{Bosworth2008,Guilmoto2013,Dharmalingam2014,
-International-Institute-for-Population-Sciences-IIPS2017}.
-
-Over the same period, India has, however, also experienced a rapidly expanding 
-access to prenatal sex determination.
-Combined with continued strong son preference, the result has been a dramatic 
-increase in the males-to-females ratio at birth
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,
-Bongaarts2013,Portner2015b,Jayachandran2017}.
-
-What the prior research on India has not appreciated is that since each abortion 
-increases the interval between births by six to twelve months, the growing use of 
-sex-selective abortions has the potential to increase birth spacing substantially. %
+Birth spacing has long served as a measure of son preference, with strong
+son preference associated with shorter birth intervals the
+fewer sons a family has \citep{ben-porath76b,Leung1988}.
+However, the introduction of prenatal sex determination potentially 
+changed the relationship between son preference and birth spacing.
+The stronger the son preference, the more likely couples are to resort to sex-selective 
+abortions, and each abortion increases the interval between births by six to twelve 
+months.%
 \footnote{
@@
 }
-Add to this increase that the combination of increasing female education, 
-lower fertility, higher household income, and the low and declining female 
-labor force participation are also likely to impact birth spacing.
-Hence, the changes in birth spacing may be much more substantial in India 
-than what we have observed in other countries as they developed.
-
-Understanding the changes in birth spacing is essential for three reasons.
-
-First, tempo effects, arising from changes in birth spacing, bias the total 
-fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
-of cohort fertility \citep{Bongaarts1999,Ni-Bhrolchain2011}.
-Hence, fertility may be, in fact, substantially higher than what is generally 
-accepted based on the TFR.
-
-Second, longer birth spacing is associated with lower mortality and 
-morbidity risk \citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
-In India, the duration to the next birth has traditionally been shorter with fewer sons, 
-which likely contributed to the higher mortality and morbidity risk for girls
-\citep{Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Maitra2008,Makepeace2008,
-Jayachandran2011,Kumar2016,Jayachandran2017a,Ghosh2018}.
-Longer spacing between births then potentially lowers mortality, although there may
-be a counteracting effect of multiple abortions.
-
-Finally, birth spacing has long served as a measure of son preference, with strong
-son preference associated with shorter birth intervals, the fewer sons a family has 
-\citep{ben-porath76b,Leung1988}.
-Now, longer birth intervals in the absence of sons, rather than an indicator of 
-lower son preference, may instead arise because couples with a strong preference 
-for sons use sex selection, possibly to the point where we observe a reversal of 
-the traditional spacing pattern.
-Families with son preference who---for one reason or another---do not use prenatal 
-sex selection likely continue to have shorter birth spacing.
+Hence, longer birth intervals in the absence of sons, which previously would be taken as 
+an indicator of lower son preference, may now instead arise because couples with a strong 
+son preference use sex selection.
 
@@
 groups with the introduction of sex selection.
-I apply a competing risk hazard model that directly incorporates the effects of 
+I introduce an empirical method that directly incorporates the effects of 
 sex-selective abortions on birth intervals
 \emph{and} 
-the likelihood of a son, 
-but which also works in cases without prenatal sex selection.
+the likelihood of a son. 
+The method can be used to analyze both situations with and without prenatal
+sex selection.
 I apply the method to birth histories of Hindu women, using data from the four
@@
 
+% [Why India?]
+India is a particularly compelling case with its long history of male preference, 
+especially in the northern states \citep{Kishor1993,murthi95,arnold98}.
+Mortality risk is higher for females than males for most ages groups, resulting in
+an almost continuous increase in India's overall ratio of males to females 
+over the last century \citep{dyson01,Navaneetham2011,Bongaarts2015}.
+Differential stopping behavior is widespread, with an additional child more likely the
+fewer sons a family has 
+\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.%
+\footnote{
+Other countries show a similar pattern
+\citep[see, for example,][]{larsen98,filmer09,Altindag2016}.
+}
+Furthermore, fertility has declined substantially, to the point where it is now at, or even 
+below, replacement in some areas 
+\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
+The combination of falling fertility, strong son preference, and expanding access to 
+prenatal sex determination has lead to dramatic increases in the males-to-females ratio at 
+birth over the last three decades
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,Bongaarts2013,Portner2015b,Jayachandran2017}.
+
+% [Why spacing?] 
+There are four main reasons for examining birth spacing and how it changes with 
+access to sex selection.
+First, researchers have made extensive use of birth spacing as a measure of son preference, 
+and it is critical to understand to what extent spacing is still a useful measure of son 
+preference.
+For example, in Bangladesh, India, and Vietnam, having more boys, and particularly having 
+a boy as the last-born child, significantly increase the duration to next birth,
+\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.%
+\footnote{
+Ethnic Indians in South Africa also show a longer duration after the birth of a 
+son than after a daughter \citep{Gangadharan2003}.
+}
+Outside Asia, the evidence is more mixed, with North Africa showing shorter spacing in the 
+absence of sons, while a similar pattern does not exist in Sub-Saharan Africa 
+\citep{Rossi2015}.
+
+Second, birth spacing can affect children's short and long-term outcomes.
+Most of the research finds a negative impact of short spacing on child health, especially 
+for very short intervals of 18 months or less \citep{Conde-Agudelo2006,Conde-Agudelo2012}.
+There is evidence in countries as diverse as Bangladesh, Brazil, El Salvadore, India,
+and Pakistan of worse health outcomes and a higher mortality risk the shorter the birth
+interval
+\citep{Cleland1984,Curtis1993,Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Davanzo2008,Maitra2008,Makepeace2008,Gribble2009,Jayachandran2011,Saha2013,Jayachandran2017a,Ghosh2018}.
+Most of the evidence on longer-term outcomes come from Western countries.
+In the US, for example, a longer interval between births increases the older, but not the
+younger, sibling's test scores \citep{Buckles2012}.
+Furthermore, close spacing appears to increase the risk of dropping out of
+high school and lower the probability of attending a post-secondary school in both the
+US and Sweden \citep{Powell1993,Pettersson-Lidbom2009}.%
+\footnote{
+However, recent results from Sweden show no relationship between birth spacing, even if 
+very short, and outcomes such as years of education completed, earnings, and unemployment 
+\citep{Barclay2017}.
+}
+
+Third, the mother may also be affected by the length of the birth intervals, although 
+reviews of the literature show mixed results on mother's anthropometric status 
+\citep{Dewey2007,Conde-Agudelo2012}.
+For India, there is, however, evidence that women with first-born girls are more likely to 
+have anemia, possibly because short birth spacing can resulting in maternal depletion 
+\citep{Milazzo2018}.
+In Western countries, a longer interval between births has positive effects on long-term 
+labor market outcomes, such as participation and income \citep{Gough2017,Karimi2014}.
+
+Finally, we know less about what determines spacing behavior in developing countries than 
+in developed countries, and with declining fertility and increasing numbers of women 
+entering the labor force, understanding how couples make timing decisions is necessary 
+for the design of suitable policies \citep{Portner2018}.%
+\footnote{
+It is clear that birth spacing does respond to policies in both developed and 
+developing countries \citep{Pettersson-Lidbom2009,Todd2012,Meckel2015,Ghosh2018}.
+}
+Even the effects of access to contraceptive and declining fertility on spacing are unclear.
+On the one hand, access to contraceptives allows women to avoid too short spacing between 
+birth.
+On the other hand, increased reliability of access and effectiveness of contraceptives can 
+lead to shorter intervals between births if women used to have longer spacing to avoid
+having too many children by accident \citep{Keyfitz1971,Heckman1976}.
+These two counteracting effects may explain why better-educated women have shorter spacing 
+than less educated women in some instances but not in others and why finding statistically 
+significant effects of contraception use on birth spacing is difficult 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.%
+\footnote{
+In Matlab, the effect of son preference on birth spacing is stronger in areas with better 
+access to family planning \citep{Rahman1993}.
+Other evidence, however, points to families ability to time births, even in the absence
+of modern contraceptives \citep{Jayachandran2011,Alam2018}.
+}
+
 % [Hypotheses / questions]
-I address four main questions.
-[TK combine questions and highlight of answers here?]
-
-First, how did average birth intervals change over time for different groups, and how do 
+Despite the increasing use of sex selection, the critical impacts of spacing on outcomes 
+for both mother and children, and the extensive use of spacing to measure son preference, 
+there has so far been no systematic examination of what effect access to sex selection 
+have on spacing.
+I address three questions to remedy this shortcoming in the literature.
+
+First, how did average birth intervals change over time for different groups and how do 
 these changes relate to the use of sex selection?
-To show how sex selection has affected birth spacing, I focus on how birth intervals have
+The hypothesis is that in the absence of sex selection son preference leads to shorter 
+spacing the fewer boys a family has, whereas son preference increases spacing the fewer 
+boys a family has when prenatal sex selection is available, possibly to the point where
+we observe a reversal of the standard spacing pattern.
+Families with son preference who---for one reason or another---do not use prenatal sex 
+selection likely continue to have shorter birth spacing.
+Based on the prior literature on sex selection, I focus on how birth intervals have
 changed for different education levels, urban or rural, and the sex composition of 
@@
 
-Birth intervals have increased for all education groups over the four decades, 
-with larger increases, the higher the parity and the higher the education level.
-Women who are most likely to use sex selection---well-educated women with no
-sons---have seen the most substantial increases in birth intervals.
-[TK check this!] As a result, well-educated women now show a reversal of the traditional spacing 
-pattern, with the longest intervals for women with no sons.
-Those least likely to use sex selection, women with no education in rural areas, 
-still follow the traditional pattern of short spacing when they have girls and 
-little evidence of the use of sex selection.
-
-Second, how has the distribution of birth spacing changed?
-Although examiniong average birth intervals helps us understand the overall changes in 
+Second, have the shapes of the survival curves changed?
+Although examining average birth intervals helps us understand the overall changes in 
 spacing behavior, it tells us little about how these changes came about.
@@
 
-[TK this is unclear]
-The traditional pattern of longer average spacing with sons appears to arise from 
-an increase in the number of very long intervals, rather than from fewer very short 
-birth intervals. 
-Across education groups, there appears to be little difference in the likelihood of 
-having a very short birth interval across sex compositions, especially for lower parities.
-
-Third, to what extent does TFR reflect cohort fertility?
-An advantage of the empirical model is that I can predict fertility behavior taking into
-account both the likelihood of parity progression and having a child of a specific sex.
-I compare those predictions with fertility rate estimates based on the same data to
-show how the increases in birth spacing have led to a substantial overestimate of how 
-fast fertility has declined. [TK too imprecise? underestimate of the level, rather?]
-
-Finally, has the relationship between birth spacing and mortality changed over time?
-[TK]
-
-[TK results]
+There are four main results.
+First, the intervals between births have increased for all education groups over the four 
+decades.
+These increases are larger the higher the parity and the higher the education 
+level.
+Second, those women who are most likely to use sex selection---well-educated women with no
+sons---have seen the largest increases in birth intervals.
+As a result, well-educated women now show a reversal of the traditional spacing 
+pattern, with the longest birth intervals for women with no sons.
+Third, women who are least likely to use sex selection, those with no education in
+rural areas, still follow the standard pattern of short spacing when they have girls and 
+little evidence of the use of sex selection.
+Finally, the traditional pattern of longer average spacing with sons appear to arise from 
+more very long intervals, rather than from fewer very short birth intervals; across 
+education groups, there appears to be little difference in the likelihood of having a very 
+short birth interval across sex compositions, especially for lower parities.
 
@@
 in both urban and rural areas has stagnated or decreased
-\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
+\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018, Bhargava2019}.
 A decline in female labor force participation at the beginning of development is
@@
 
+The prior literature show that shorter birth spacing, especially very short spacing,
+is associated with higher risk of infant mortality.
+Hence, it is possible that the increasing use of sex-selective abortions could
+directly reduce infant mortality by lengthening the duration from the prior birth.
+
+There are a number of potential issues with understanding to what extent this
+has happened.
+
+First, the sex of the next child is no longer random, and boys, in the absence of
+differential treatment, have higher infant mortality than girls.
+
+Second, it may be that what matters is not the time between births, but rather 
+between pregnancies, in which case multiple abortions followed quickly by new 
+pregnancies would lead to shorter real spells of recovery.
+The implication is that long spells might have a higher mortality risk since
+they are now more likely with multiple abortions.
+
+Third, as I show above the use of sex selection is more prevalent the higher the
+education level of the mother.
+Higher maternal education is, however, also associated with lower mortality risk
+to begin with.
+On top of this, with economic growth and better health care, infant mortality
+may have fallen across all education groups and areas in the period covered.
+
+I address three questions.
+
+First, does the increased use of sex selection lead to higher mortality risk?
+
+Second, has the negative effects of short spacing changed over time?
+
+Third, how do the effects of short spacing vary by education level in India?
+
+There are a number of problems with estimating the relationship between 
+sex-selective abortions and infant mortality.
+
+First, there are potential selection problem.
+For example, women who face higher mortality risk of their children might forego 
+the use of sex selection to ensure that they reach their desired number of 
+children.
+If these women also know to avoid very short birth spacing, the precense of 
+these women in the sample would inflate the mortality of the "middle" birth
+spacing, relative to the very short or very long birth spacing.
+
+[our JDE paper]
+
+An additional selection with the opposite effect is that women who have
+difficulties conceiving or carrying a preganancy to term may also have higher 
+mortality risk for their offspring, leading to a supriuos correlation
+between very long birth spacing and mortality \citep{Kozuki2013}. 
+If better health care and higher income means that more of these women are
+now able to carry their pregnancy to term we can end up with more births
+after long spells that have higher mortality risk but not because of the
+increased use of sex selection.
+
+[Our Demography paper shows a different type of selection effect, where the
+use of sex selection biases the effect estimates of other variables that
+vary together with the use of sex selection.]
+
+Given the data and that the focus of this paper is mainly on the birth
+spacing, a more in-depth treatment of these issue is the topic of future work.
+Part of the problem here is also that the method used previously, such
+as family fixed effects does not work well when the number of births is
+very low as it is for higher education women who use sex 
+selection, especially since the spacing from marriage to first birth
+does not provide any information \citep{Kozuki2013,Molitoris2019}.
+However, the fixed effects results and linear probability do not deviate
+substantially.
+
+Second, the actual number of abortions are unobserved.
+The results above do show, however, how the use of sex selection vary
+by education and sex composition of prior children.
+I, therefore, estimate infant mortality risk taking into account the
+sex composition of the prior children, as well as the index child.
+
+Starting with the sample used for estimating birth spacing, I select, by
+parity, children born more than 12 months before the survey month.
+The dependent variable is whether the child died within the first twelve
+months of life (infant mortality).
+As above, I restrict the analysis to parity two through four.
+
+The main set of explanatory variable consists of dummies for birth spacing,
+divided into less than 15 months from when conception could realistically
+could happen (same definition as above) and based on the finding that 
+spacing less than 24 months between birth is associated with higher
+infant mortality \citep{Molitoris2019}, and then in 12 months intervals
+until TK, where all births after and until 96 months are included.%
+\footnote{
+\citet{Molitoris2019} has used quartic functions, but the concern is
+that with the relatively small number sample here the shape
+of the function would be strongly influenced by a small number of
+observations.
+Using dummies provides a more flexible specification and the standard
+error will directly reflect the higher degree of noise for the
+spells periods with fewer observations.
+}
+In addition, I use dummies for sex of the index child (the child whose 
+mortality is estimated) and the sex composition of the prior children.
+Birth spacing dummies, sex of index child, and sex composition dummies
+are all interacted.
+The other explanatory variables are the same as above and estimations
+are done separately by education level.
+
+I estimate probability of infant mortality using a logit model.
+Results are presented as the predicted probability of dying within the
+first year at the possible combinations of index child sex, sex composition
+of prior children, and the birth spacing dummied.
+All other variables are set to their average values.
+[TK ehh, did I also do urban/rural?]
+
+Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} show the 
+estimated probabilities.
+To ease legibility all confidence intervals are suppressed
+(graphs with confidence intervals are available on request).
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p1_low_dummies}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_low_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_low_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_low_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_low}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p1_med_dummies}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_med_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_med_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_med_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_med}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
+    \end{minipage}
+}
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p1_high_dummies}
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_high_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_high_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_high_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_high}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p2_highest_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p3_highest_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.29\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s4_p4_highest_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_highest}
+\end{figure}
+
+For women with twelve or more years of education the results become very noisy
+because of the low number of births, especially for parity three and four, and
+the low mortality rate.
+As above, I do not show results for the 1972--84 period because there were too
+few women with this level of education for this period.
+
+Based on the second parity births, women with twelve or more years of education
+have the lowest infant mortality risk. 
+Even for very short birth intervals the mortality risk is less than five percent,
+and fall to less than half that for longer intervals.
+Given the low mortality there is, not surprisingly, much difference between
+the three periods covered.
+Furthermore, there is no evidence that longer intervals are associated with
+significantly higher mortality, especially for the groups most likely to have
+used sex selection (women with a girl as their first child and a boy as their
+second with a long interval).
+
+Women with eight to eleven years of education have marginally higher mortality
+risk than women with the most education, and also show slightly more evidence
+of increased mortality with very short spacing.
+Mortality risk have decreased slightly between periods, although the changes
+are relatively minor.
+As for women with the most education, there are not any statistically significant 
+differences or increases in mortality with longer spacing.
+Because of the low mortality risk and the relatively small number of births,
+the estimates for the third and fourth parity are noisy.
+
+Infant mortality risk for women with one to seven years of education have
+clearly decreased over time.
+This is also the first group that show increasing mortality risk with longer
+spacing, although this effect mostly disappears for the later periods.
+In other words, it does not appear to be the result of sex selection, but
+rather arise from the selection bias discussed above where women with long
+spells are those who find it difficult to either conceived and/or carry a 
+pregnancy to term and also have higher mortality risk for their offspring.
+
+Finally, women with no education have experienced substantial improvements
+in infant mortality risk over time.
+This decrease is especially pronounced for shorter intervals.
+For the longer intervals, there is surprisingly little difference across
+the education groups for the later periods.
+
 \section{Conclusion\label{sec:conclusion}}

### 2020-01-29 paper/sex_selection_spacing-ver3.tex
Minor edits in paper

@@
 
-Understanding the changes in birth spacing is essential for three reasons.
-
-First, tempo effects, arising from changes in birth spacing, bias the total 
-fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
+Understanding how birth spacing changes is essential for three reasons.
+
+First, tempo effects, here arising from changes in birth spacing, bias 
+the total fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
 of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
 If birth spacing increased substantially over time, India's fertility may, in 
-fact, be substantially higher than what is generally accepted based on the TFR.
+fact, be higher than what is generally accepted based on the TFR.
 
@@
 Despite a large literature on son preference and birth spacing, there is, however,
-no prior research has examined how sex selection affects spacing.
+no prior research that has examined how sex selection affects spacing.
 
@@
 it more expensive to have long spacing
+- Incorporate Newman 1984 discussion (p 947) on income vs substitution effect
+- why has fertility fallen at all? Lower mortality, higher quality children?
 ]

### 2020-01-30 paper/educ_work_over_time.tex
Storage for longer discussion of education and conceptual framework

@@
-Female Education and Labor Force Participation in India
+\section{Female Education and Labor Force Participation in India}
 
 Female educational attainment has increased substantially over time.
-Figure XX shows the distribution of schooling by birth cohort for urban and rural women, 
+Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
+cohort for urban and rural women, 
 twenty years or older, whether married or not, based on the four rounds of the NFHS.
@@
 and twelve years and above.
+
+\begin{figure}[htpb]
+\centering
+\subfloat[Rural]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_rural}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_urban} 
+    \end{minipage}
+}
+\caption{Distribution of education by cohort for women twenty years or older at survey}
+\label{fig:education_over_time}
+\end{figure}
 
@@
 in both urban and rural areas has stagnated or decreased
-\citep{Klasen2015,Afridi2018,Bhargava2018, Chatterjee2018, Bhargava2019}.
+\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
 A decline in female labor force participation at the beginning of development is
@@
 
-Figure XX shows the percent of married women who are 
+Figure \ref{fig:work_by_survey} shows the percent of married women who are 
 currently working at the time of the survey by age group and education level.
@@
 \citep{Jensen2012}.
+
+\begin{figure}[!htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{40 Years or Older}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_40}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_40} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_30}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_30} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_20}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_20} 
+    \end{minipage}
+}
+\caption{Percentage of married women who were working at the time of the 
+survey by age group and area of residence}
+\label{fig:work_by_survey}
+\end{figure}
 
@@
 Almost all of the urban women who work receive either cash or a combination of 
-cash and in-kind for their work (see Appendix Figure XX). 
+cash and in-kind for their work (see Appendix Figure \ref{fig:work_cash_by_survey}). 
 Rural women have become more likely to receive cash for their labor over time, 
@@
 work for a family member rather than for themselves or somebody else
-(see Appendix Figure XX).
+(see Appendix Figure \ref{fig:work_family_by_survey}).
 Hence, the lower likelihood of working stems mostly from women retracting from 

### 2020-01-30 paper/sex_selection_spacing-ver3.tex
Two tables for descriptive stats
Editing education and conceptual framework sections

@@
 education levels have increased for both males and females,
-and the total fertility rate has fallen to the point where, at 2.2, it is just
-above replacement 
-\citep{Bosworth2008,Guilmoto2013,Dharmalingam2014,
+and the total fertility rate has fallen to 2.2, or just above replacement 
+\citep{Bosworth2008,Dharmalingam2014,
 International-Institute-for-Population-Sciences-IIPS2017}.
 
-Over the same period, India has, however, also experienced a rapidly expanding 
+India has, however, also experienced a rapidly expanding 
 access to prenatal sex determination.
@@
 increase in the males-to-females ratio at birth
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2009a,Guilmoto2012,
+\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,Guilmoto2012,
 Bongaarts2013,Portner2015b,Jayachandran2017}.
@@
 }
-Add to this increase that the combination of increasing female education, 
+Furthermore, the combination of increasing female education, 
 lower fertility, higher household income, and the low and declining female 
@@
 
-First, tempo effects, here arising from changes in birth spacing, bias 
+First, tempo effects, such as those arising from changes in birth spacing, bias 
 the total fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
@@
 If birth spacing increased substantially over time, India's fertility may, in 
-fact, be higher than what is generally accepted based on the TFR.
+fact, be higher than generally accepted based on the TFR.
 
 Second, longer birth spacing is associated with lower mortality and 
-morbidity risk \citep{Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
+morbidity risk \citep{Conde-Agudelo2012,Molitoris2019}.
 In India, the duration to the next birth has traditionally been shorter with fewer sons, 
 which likely contributed to the higher mortality and morbidity risk for girls
-\citep{Whitworth2002,Bhargava2003,Rutstein2005,Bhalotra2008,Maitra2008,Makepeace2008,
-Jayachandran2011,Kumar2016,Jayachandran2017a,Ghosh2018}.
+\citep{Whitworth2002,Bhargava2003,Bhalotra2008,Maitra2008,
+Jayachandran2011,Jayachandran2017a}.
 Longer spacing between births then potentially lowers mortality, although there may
-be a counteracting effect of multiple abortions.
+be counteracting effects if the longer spacing arises because of multiple abortions.
+There has so far been no attempt to examine which mechanism dominates.
 
@@
 \citep{ben-porath76b,Leung1988}.
-Now, longer birth intervals in the absence of sons, rather than an indicator of 
-lower son preference, may instead arise because couples with a strong preference 
-for sons use sex selection, possibly to the point where we observe a reversal of 
-the traditional spacing pattern.
+Now, longer birth intervals in the absence of sons may instead arise because couples 
+with a strong preference for sons use sex selection, possibly to the point where we 
+observe a reversal of the traditional spacing pattern.
 Despite a large literature on son preference and birth spacing, there is, however,
@@
 Second, how has the distribution of birth spacing changed?
-Although examiniong average birth intervals helps us understand the overall changes in 
-spacing behavior, it tells us little about how these changes came about.
-For example, the motivations that lead to an increase in average spacing are different if 
-the increase comes mainly from parents trying to avoid very short birth intervals or from 
-continued use of sex selection to ensure a son.
-
-[TK this is unclear]
+Average birth intervals help us understand the overall changes in 
+spacing behavior, but tells us little about how these changes came about.
+Examining how the distribution has change allow us to separate out increases in birth
+spacing that come from women with strong son preference who still try to conceive early, 
+but are also the most likely to end up with very long spells because of multiple 
+abortions versus women who have longer average spacing because they try to avoid very
+short birth intervals.
+
+[TK this is unclear - complete rewrite]
 The traditional pattern of longer average spacing with sons appears to arise from 
@@
 
-\section{Birth Spacing: Mechanisms and Findings}
-
-This section provides a conceptual framework for understanding what determines  
-birth spacing.
-I first discuss the main determinants of spacing examined in the prior research, and 
-then how son preference and sex selection fits into the spacing decisions.
-Since sex selection and education are closely linked, I pay special attention to how 
-education affects spacing.
-
-In the simplest possible dynamic model of fertility, the spacing decision is trivial.
-Assume that parents derive benefits from the presence of children, not their births, 
-that spacing of children does impact parents' utility, 
-and that the parents fully control when to have children. 
-The optimal decision then is to have the children as early as possible 
-\citep{Newman1988}.
-The simplest model does not fit the observed spacing patterns, which suggests 
-that one or more of the assumptions are wrong.
-
-First, parents do not entirely control the timing of births, but rather decide on 
-the levels of sexual activity and contraceptive effort, which, in turn, affect the 
-likelihood of conceiving, while taking into account fecundity and their knowledge 
-of and access to contraceptive technology.
-
-Fecundity determinants, such as age and health of the mother, are, however, unlikely 
-to be significant factors in how spacing changed over time or across education levels 
-in India for the period covered.
-Outside of direct famine conditions, women's health and nutritional status do not 
-appear to affect spacing substantially \citep{Huffman1987,John1987,lindstrom99}.
-The Maharashtra drought occurred in 1970--1973 and would, therefore, only impact the first
-year or two of the data.
-Furthermore, I only examine spacing up to parity fourth, and the age of the mother is,
-therefore, unlikely to be a concern when it comes to fecundity, even though 
-better-educated women are, on average, older when they marry.
-
-Despite a general belief that better access to and knowledge of contraception 
-should lengthen average spacing, the empirical relationship between contraception 
-use and birth spacing is ambiguous 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
-This lack of evidence is consistent with the ambiguous theoretical effect of introducing 
-modern contraceptives on birth spacing.
-On the one hand, in the absence of high-efficacy contraceptive technologies, parents may 
-try to avoid overshooting their desired number of children by spacing their children 
-further apart than they would otherwise do.
-Increased reliability of the access to and effectiveness of contraceptives then lead to 
-shorter birth intervals because parents are more confident they can effectively
-stop childbearing when they want \citep{Keyfitz1971,Heckman1976}.
-On the other hand, through simple random variation, when contraceptives are ineffective, 
-some birth intervals will be shorter than ideal, in the way discussed below.
-With increased reliability of contraceptive efforts, parents can better avoid too short 
-birth spacing, and average spacing should go up.
-
-To further complicate the relationship between contraception and spacing, the ability 
-to successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, 
-is increasing in education, while there is no difference across education levels 
-when it comes to modern contraceptives such as pills or injectables \citep{Rosenzweig1989}.
-Additionally, even in the absence of modern contraceptives, families appear able to 
-time or at least postpone births when they have substantial enough incentive 
-\citep{Jayachandran2011,Alam2018}.
-
-Second, parents may care about the spacing between birth because of the 
-potential effects of spacing on the children.%
-\footnote{
-In principle, the mother could also be affected, but the estimated impact on 
-mothers' anthropometric status is mixed, and there appears to be no 
-effect on mortality 
-\citep{Ronsmans1998,Menken2003,Dewey2007,Conde-Agudelo2012}.
-}
-One theory is that child ``quality'' increases with spacing 
-since parental attention per child increases
+\section{Female Education and Labor Force Participation in India}
+
+To set the stage for the subsequent analyses, I first describe how female education
+and labor force participation has changed.
+Both are potentially important factors in the birth spacing decision, as I discuss
+in detail in the subsequent section.
+
+Female educational attainment has increased substantially over time.
+Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
+cohort for urban and rural women, 
+twenty years or older, whether married or not, based on the four rounds of the NFHS.
+The education groups are no education, one to seven years, and eight to eleven years,
+and twelve years and above.
+
+\begin{figure}[htpb]
+\centering
+\subfloat[Rural]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_rural}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_urban} 
+    \end{minipage}
+}
+\caption{Distribution of education by cohort for women twenty years or older at survey}
+\label{fig:education_over_time}
+\end{figure}
+
+For rural areas, the percentage of women with no education has gone from around 90 percent
+for the 1930s cohorts to less than 20 percent for the 1990s cohorts. 
+The proportion of women with one to seven years of education has remained remarkably
+constant at around ten percent.
+The difference is made up by the women with eight or more years of education, who have
+gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts,
+with about half in the eight to eleven years group and 
+the other half in the twelve years or more group.
+
+Female education is higher in urban areas than in rural areas.
+Around sixty percent of urban women born in the 1930s had no education, 25 percent had
+between one and seven years, about 10 had eight or more years of education, and only
+five percent has twelve years or more.
+The proportions with no education and one to seven years have both declined to just below 
+ten percent for the latest cohort.
+Although the proportion of women with eight to eleven years of education has increased
+to about twenty, most of the increase in urban female education has come from the 
+twelve plus group, which now account for more than half of all urban women.
+
+Even as the level of female education has increased, the female labor force participation 
+in both urban and rural areas has stagnated or decreased
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
+A decline in female labor force participation at the beginning of development is
+consistent with the hypothesis of a U-shaped labor force participation as a country
+develops \citep{Goldin1994}.
+India's female labor force participation is, however, lower than most other
+countries and more in line with countries in the Middle East and North Africa, and
+does not yet show any signs of increasing
+\citep{Klasen2015,Chatterjee2018}.
+
+Figure \ref{fig:work_by_survey} shows the percent of married women who are 
+currently working at the time of the survey by age group and education level.
+No other labor force participation question is consistently available across all 
+four surveys. 
+Because the question refers to currently working, the percentages are lower in previous
+studies.
+
+\begin{figure}[!htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{40 Years or Older}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_40}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_40} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_30}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_30} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_20}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_20} 
+    \end{minipage}
+}
+\caption{Percentage of married women who were working at the time of the 
+survey by age group and area of residence}
+\label{fig:work_by_survey}
+\end{figure}
+
+There is a U-shaped relationship between education and working in most cases with 
+the highest percent working for women with either no education or with twelve or 
+more years and the lowest for women with eight to eleven years of education.
+Women are more likely to report working if they live in rural than urban areas 
+and the older they are.
+Comparing 1992 and 2015, the percent of women who currently work has either 
+remained roughly the same or decreased.
+The cases were the numbers were higher in 1999 and 2006 than in 1992 or 2015 
+are mostly based on small samples, such as rural women with twelve or more 
+years of education in rural areas.
+
+\section{Birth Spacing: Mechanisms and Prior Findings}
+
+To understand the potential implications of the substantial changes in income, female 
+education, and female labor force participation that India has experience on birth
+spacing, this section discuss relevant theoretical frameworks and prior findings 
+on birth spacing.
+
+The standard economic argument for why increasing female education has predominantly
+been associated with shorter spacing is that parents incur time costs when they have 
+children \citep{Hotz1997,schultz97}.
+Specifically, if having children require the mother to reduce her market work, parents 
+can lower the cost of children by shorten birth spacing.
+With the shorter birth spacing, parents can take advantage of economies of scale in 
+childrearing, because taking care of two young children does not take twice as much 
+time as taking care of one child \citep{Vijverberg1982}.
+In this case, better-educated women will both have lower fertility and shorter
+spacing than less-educated women because of their higher opportunity cost of time 
+\citep{Ross1974,Newman1984}.
+
+If the mother is unlikely to work in market work, as has become more common over time in 
+India, there is little incentive to children more closely together for economic reasons.
+
+% [TK not clear that these two paragraphs add anything to this section]
+% The question is then why women appear to be leaving the labor force.
+% With the strong economic growth in India, real wages for both men and women have almost 
+% doubled between 1987 and 2011 \citep{Klasen2015}.
+% Despite the increases in wages and the higher female education, the mean male wage is
+% still close to 70 percent higher than the mean female wage and women’s labor supply 
+% appear to be more negatively elastic to their husbands' wages than it is positively 
+% elastic to own wages, suggesting that the reduction in female labor supply is driven by 
+% an income effect \citep{Bhargava2018}.%
+% \footnote{
+% Furthermore, the development in women's wages is not uniform across education 
+% levels \citep{Klasen2015,Bhargava2018}.
+% The real wages for women with middle school education or below have converged. 
+% For women with secondary education, the change over time depends on the sample used,
+% with some showing a substantial decline and others a modest increase.
+% Women with more than secondary education experienced an increased in their real 
+% wages, especially in cities.
+% }
+
+% However, even after controlling for household characteristics and husband income, there 
+% still is the U-shaped relationship between female education and labor supply shown
+% above with the lowest labor force participation for women with secondary 
+% education \citep{Chatterjee2018}.
+% There are two possible explanations for this effect, both directly related to the strong
+% pro-male bias in India.
+% First, it becomes less socially acceptable for women to work in manual labor as their
+% education increases, and women are still mostly excluded from white-collar
+% employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
+% Second, with increasing education, women's productivity at home also increases, 
+% especially in the production of offspring human capital.
+% With relatively more boys born because of increased access to sex-selective 
+% abortions and an increasing male income, demand for better-educated women can 
+% increase, even if they do not participate in the labor market \citep{Behrman1999}.
+
+With increasing income, parents may also prefer higher child ``quality'' and that would
+also predict longer birth intervals since parental attention per child increases
 \citep{Zajonc1975,Zajonc1976,Razin1980}.
-In this case, birth spacing should increase in family income, while the 
-effect of maternal education is ambiguous since higher education, on the 
-one hand, makes the mother's time spent out of the labor market more 
-costly and on the other hand increases how productive the mother is 
-in childrearing.
 The evidence on spacing's effect on child quality measures such as IQ 
@@
 \citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-
-For one crucial aspect of child quality---health and mortality---shorter spacing 
-does lead to worse outcomes, especially for very short intervals of 24 months 
-or less, although this effect decreases with maternal education
-\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.%
-\footnote{
-The underlying mortality risk could also affect birth spacing, but
-there is little empirical evidence for this 
-\citep{Newman1983,Newman1988,Bhalotra2008}.
-}
-If parents realize short birth spacing increases their children's mortality risk, 
-they likely prefer to space births further apart.
-However, this effect should diminish with education level since women with 
-secondary or tertiary education experience relatively low mortality risk for 
-their children, even with very short spacing is associated.
-
-Third, parents incur both direct and time costs when they have children, 
-and economic considerations can, therefore, affect birth spacing 
-\citep{Hotz1997,schultz97}.
-I divide the economic factors into the effects of economies of scale and
-the expected income trajectory of the husband and wife.
-
-The expected effect of economies of scale in childrearing, which, for example, 
-can arise because taking care of two young children does not take twice as much 
-time as taking care of one child, is to shorten intervals between births
-\citep{Vijverberg1982}.
-To the extent that children require the mother to do less market work, parents 
-can lower the cost of children by reducing birth spacing.
-In this case, better-educated women will both have lower fertility and shorter
-spacing than less-educated women because of their higher opportunity cost of time 
-\citep{Ross1974,Newman1984}.
-However, if the mother mainly works at home or as household income increases, there 
-is less incentive to space children for this reason.
-
-In the absence of perfect capital markets, theory predicts that the steeper 
-the parents' lifetime income profile, the longer the spacing between births, 
-which suggests that with economic development we should see a general increase 
-in spacing across education groups and that this increase in spacing should be 
-stronger with increasing education levels
-\citep{Heckman1976,wolpin84,Newman1988}.
-The idea is that although parents would prefer to have their children as early 
-as possible to enjoy them for longer, there is also a direct cost to children.
-Income is low early on, which means that the marginal utility of consumption is 
-higher, making parents less willing to give up consumption to have a child, 
-compare to later when they know that their income will be higher 
-\citep{Newman1984,Happel1984}.
-
-Finally, the discussion has so far assumed that children are identical---except 
+Nevertheless, for one crucial aspect of child quality---health and mortality---longer 
+spacing does lead to better outcomes, although this relationship weakens with maternal 
+education \citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
+
+While one might expect that increasing income and female education would also lengthen
+average birth spacing through access and knowledge of contraception, the empirical 
+relationship between contraception use and birth spacing is ambiguous 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+To further complicate the relationship between contraception and spacing, the ability 
+to successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, 
+is increasing in education, while there is no difference across education levels 
+when it comes to modern contraceptives such as pills or injectables 
+\citep{Rosenzweig1989}.
+Additionally, even in the absence of modern contraceptives, families appear able to 
+time or at least postpone births when they have substantial enough incentive 
+\citep{Jayachandran2011,Alam2018}.
+
+The discussion has so far assumed that children are identical---except 
 for any differences that arise from spacing---but there is substantial evidence 
@@
 \citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.
-There is also evidence of differential stopping behavior, with an additional child 
-more likely the fewer sons a family has 
-\citep{repetto72,Das1987,Arnold1997,arnold98,clark00,Basu2010,Barcellos2014}.
-
-If short spacing lowers the survival probability of the next child, as discussed above,
-it is not, however, apparent that we should expect shorter spacing in the absence of boys.
+
+If short spacing lowers the survival probability of the next child, it is not, however, 
+apparent that we should expect shorter spacing in the absence of boys.
 There are two potential reasons why parents might still try to conceive sooner 
-in the absence of boys.%
-\footnote{
-The significant differences in spacing by sex composition indicate that
-parents control the timing of birth, at least to some extent.
-In Matlab, the effect of son preference on birth spacing is stronger in 
-areas with better access to family planning \citep{Rahman1993}.
-}
+in the absence of boys.
 One possibility is that parents do not realize that short spacing is potentially
@@
 
-In summary, birth spacing is affected by female education through 
-multiple pathways, with the main one of interest here the use of 
-sex selection. 
-But, to fully understand how sex selection affects spacing, we also 
-need to understand the other changes that affect birth spacing over time.
-The most likely factors are the changes in household income and 
-wealth and the improvements in health as India has developed.
-I, therefore, examine how female education and labor force 
-participation has changed over time in India.
-
-%------------------------------------------------------------------------------------
-
-\section{Female Education and Labor Force Participation in India}
-
-Female educational attainment has increased substantially over time.
-Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
-cohort for urban and rural women, 
-twenty years or older, whether married or not, based on the four rounds of the NFHS.
-The education groups are no education, one to seven years, and eight to eleven years,
-and twelve years and above.
-
-\begin{figure}[htpb]
-\centering
-\subfloat[Rural]{
-    \begin{minipage}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{educ_over_time_rural}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{educ_over_time_urban} 
-    \end{minipage}
-}
-\caption{Distribution of education by cohort for women twenty years or older at survey}
-\label{fig:education_over_time}
-\end{figure}
-
-For rural areas, the percentage of women with no education has gone from around 90 percent
-for the 1930s cohorts to less than 20 percent for the 1990s cohorts. 
-The proportion of women with one to seven years of education has remained remarkably
-constant at around ten percent.
-The difference is made up by the women with eight or more years of education, who have
-gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts,
-with about half in the eight to eleven years group and 
-the other half in the twelve years or more group.
-
-Female education is higher in urban areas than in rural areas.
-Around sixty percent of urban women born in the 1930s had no education, 25 percent had
-between one and seven years, about 10 had eight or more years of education, and only
-five percent has twelve years or more.
-The proportions with no education and one to seven years have both declined to just below 
-ten percent for the latest cohort.
-Although the proportion of women with eight to eleven years of education has increased
-to about twenty, most of the increase in urban female education has come from the 
-twelve plus group, which now account for more than half of all urban women.
-
-Even as the level of female education has increased, the female labor force participation 
-in both urban and rural areas has stagnated or decreased
-\citep{Klasen2015,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-A decline in female labor force participation at the beginning of development is
-consistent with the hypothesis of a U-shaped labor force participation as a country
-develops \citep{Goldin1994}.
-India's female labor force participation is, however, lower than most other
-countries and more in line with countries in the Middle East and North Africa, and
-does not yet show any signs of increasing
-\citep{Klasen2015,Chatterjee2018}.
-
-Theory predicts that increasing women's wages leads to higher labor force participation, 
-while both a higher male income and stronger social restrictions on working, possibly in 
-specific industries or jobs, reduce female labor supply \citep{Goldin1994}.
-India's economy has grown substantially since the mid-seventies, with
-an average annual growth rate of about 5.5 percent from 1978 to 2004 \citet{Bosworth2008}.
-As a result, real wages for both men and women have almost doubled between 1987 and 2011 
-\citep{Klasen2015}.
-Despite the increases in wages and the higher female education, the mean male wage is
-still close to 70 percent higher than the mean female wage \citep{Bhargava2018}.
-Furthermore, the development in women's wages is not uniform across education 
-levels \citep{Klasen2015,Bhargava2018}.
-The real wages for women with middle school education or below have converged. 
-For women with secondary education, the change over time depends on the sample used,
-with some showing a substantial decline and others a modest increase.
-Women with more than secondary education experienced an increased in their real 
-wages, especially in cities.
-
-After controlling for household characteristics and husband income, there is
-still a U-shaped relationship between female education and labor supply with the
-lowest labor force participation for women with secondary education \citep{Chatterjee2018}.
-There are two possible explanations for this effect, both directly related to the strong
-pro-male bias in India.
-First, it becomes less socially acceptable for women to work in manual labor as their
-education increases, and women are still mostly excluded from white-collar
-employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
-Second, with increasing education, women's productivity at home also increases, especially
-in the production of offspring human capital.
-With relatively more boys born because of increased access to sex-selective 
-abortions and an increasing male income, demand for better-educated women can 
-increase, even if they do not participate in the labor market \citep{Behrman1999}.
-
-Figure \ref{fig:work_by_survey} shows the percent of married women who are 
-currently working at the time of the survey by age group and education level.
-No other labor force participation question is consistently available across all 
-four surveys. 
-Because the question refers to currently working, the percentages will be lower 
-than what other studies have found. 
-Furthermore, since the question is asked only of married women, the overall female labor 
-force participation might have developed differently, especially since many young, 
-unmarried women have begun working in, for example, the business process 
-outsourcing industry, which, in turn, has increased girls' schooling investments
-\citep{Jensen2012}.
-
-\begin{figure}[!htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{40 Years or Older}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_40}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_40} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_30}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_30} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_20}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_20} 
-    \end{minipage}
-}
-\caption{Percentage of married women who were working at the time of the 
-survey by age group and area of residence}
-\label{fig:work_by_survey}
-\end{figure}
-
-The U-shaped relationship between education and working holds in most cases with 
-the highest percent working for women with either no education or with twelve or 
-more years and the lowest for women with eight to eleven years of education.
-Women are more likely to report working if they live in rural than urban areas 
-and the older they are.
-Comparing 1992 and 2015, the percent of women who currently work has either 
-remained roughly the same or decreased.
-The cases were the numbers were higher in 1999 and 2006 than in 1992 or 2015 
-are mostly based on small samples, such as rural women with twelve or more 
-years of education in rural areas.
-
-Almost all of the urban women who work receive either cash or a combination of 
-cash and in-kind for their work (see Appendix Figure \ref{fig:work_cash_by_survey}). 
-Rural women have become more likely to receive cash for their labor over time, 
-and the better educated, the more likely they are to receive cash.
-
-Despite this, women across all groups have become substantially more likely to 
-work for a family member rather than for themselves or somebody else
-(see Appendix Figure \ref{fig:work_family_by_survey}).
-Hence, the lower likelihood of working stems mostly from women retracting from 
-the general labor market and self-employment.
-
 The increases in female educational attainment imply that access to education 
@@
 their children closer together without substantially increasing child mortality risk.
+
+%------------------------------------------------------------------------------------
 
@@
 afford prenatal sex determination
-\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.%
+\citep{das_gupta97,retherford03b,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.%
 \footnote{
@@
 sex-selective abortions 
-\citep{retherford03b,jha06,Bhalotra2008,abrevaya09,Portner2015b,Kumar2016,Soest2018}.
+\citep{retherford03b,Bhalotra2008,Portner2015b,Soest2018}.
 I capture sex composition with dummy variables for the
@@
 sex selection, both of which lead to higher use of sex-selective abortions than in 
-rural areas \citep{retherford03b,jha06,Portner2015b}.
+rural areas \citep{retherford03b,Portner2015b}.
 Area of residence is a dummy variable for the household living in an urban area.
@@
 
-Appendix Table \ref{tab:des_stat1} presents descriptive statistics for
+Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} presents descriptive statistics for
 the spells by education level and period.

### 2020-01-31 paper/sex_selection_spacing-ver3.tex
Wrong graph titles
Shorten conceptual framework section

@@
 
+A question is whether the rapid expansion in female educational attainment has led
+to significant changes in the composition of better-educate women and whether this will
+affect their son preference and desired fertility.
+It is clear that the increases in female educational attainment imply that access to 
+education has expanded beyond the higher castes. 
+However, ``Sanskritization'' implies that as lower castes females gain access to 
+education and their husbands' income increases, the women adopt higher caste 
+norms such as stronger son preference and a retraction from the formal labor 
+market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
+
 \section{Birth Spacing: Mechanisms and Prior Findings}
 
-To understand the potential implications of the substantial changes in income, female 
-education, and female labor force participation that India has experience on birth
-spacing, this section discuss relevant theoretical frameworks and prior findings 
-on birth spacing.
+To understand the potential implications for birth spacing of the substantial changes in 
+income, female education, and female labor force participation that India has experienced, 
+this section discuss relevant theories and prior findings on birth spacing.
 
@@
 
-If the mother is unlikely to work in market work, as has become more common over time in 
-India, there is little incentive to children more closely together for economic reasons.
-
-% [TK not clear that these two paragraphs add anything to this section]
-% The question is then why women appear to be leaving the labor force.
-% With the strong economic growth in India, real wages for both men and women have almost 
-% doubled between 1987 and 2011 \citep{Klasen2015}.
-% Despite the increases in wages and the higher female education, the mean male wage is
-% still close to 70 percent higher than the mean female wage and women’s labor supply 
-% appear to be more negatively elastic to their husbands' wages than it is positively 
-% elastic to own wages, suggesting that the reduction in female labor supply is driven by 
-% an income effect \citep{Bhargava2018}.%
-% \footnote{
-% Furthermore, the development in women's wages is not uniform across education 
-% levels \citep{Klasen2015,Bhargava2018}.
-% The real wages for women with middle school education or below have converged. 
-% For women with secondary education, the change over time depends on the sample used,
-% with some showing a substantial decline and others a modest increase.
-% Women with more than secondary education experienced an increased in their real 
-% wages, especially in cities.
-% }
-
-% However, even after controlling for household characteristics and husband income, there 
-% still is the U-shaped relationship between female education and labor supply shown
-% above with the lowest labor force participation for women with secondary 
-% education \citep{Chatterjee2018}.
-% There are two possible explanations for this effect, both directly related to the strong
-% pro-male bias in India.
-% First, it becomes less socially acceptable for women to work in manual labor as their
-% education increases, and women are still mostly excluded from white-collar
-% employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
-% Second, with increasing education, women's productivity at home also increases, 
-% especially in the production of offspring human capital.
-% With relatively more boys born because of increased access to sex-selective 
-% abortions and an increasing male income, demand for better-educated women can 
-% increase, even if they do not participate in the labor market \citep{Behrman1999}.
-
-With increasing income, parents may also prefer higher child ``quality'' and that would
-also predict longer birth intervals since parental attention per child increases
-\citep{Zajonc1975,Zajonc1976,Razin1980}.
+The low and declining female labor force participation, especially for younger women, 
+suggests, however, that families face little incentive to space children more closely 
+together for economic reasons.
+This may happen if household income has increased so substantially that the income effect 
+dominates any substitution effect.
+Two findings speak for this effect.
+First, although real wages for both men and women have almost doubled between 1987 and 
+2011, the mean male wage is still close to 70 higher than the female wage 
+\citep{Klasen2015,Bhargava2018}.
+Second, women’s labor supply appear to be more negatively elastic to their husbands' 
+wages than it is positively elastic to own wages \citep{Bhargava2018}.
+
+In fact, it may be that the combination of rising incomes and continued son preference 
+lead to even longer spacing than what we would expect from the standard income effect.
+As women's education increases, their productivity at home also increases, especially in 
+the production of offspring human capital.
+With relatively more boys born because of increased access to sex-selective 
+abortions and an increasing potential income for (male) offspring, demand for 
+better-educated women can increase, even if they do not participate in the labor market 
+\citep{Behrman1999}.
+The result would be longer birth intervals because that increases parental attention 
+per child resulting in higher child ``quality'' \citep{Zajonc1975,Zajonc1976,Razin1980}.
 The evidence on spacing's effect on child quality measures such as IQ 
@@
 While one might expect that increasing income and female education would also lengthen
-average birth spacing through access and knowledge of contraception, the empirical 
+average birth spacing through better access and knowledge of contraception, the empirical 
 relationship between contraception use and birth spacing is ambiguous 
 \citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
-To further complicate the relationship between contraception and spacing, the ability 
-to successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, 
-is increasing in education, while there is no difference across education levels 
-when it comes to modern contraceptives such as pills or injectables 
-\citep{Rosenzweig1989}.
-Additionally, even in the absence of modern contraceptives, families appear able to 
-time or at least postpone births when they have substantial enough incentive 
-\citep{Jayachandran2011,Alam2018}.
-
-The discussion has so far assumed that children are identical---except 
-for any differences that arise from spacing---but there is substantial evidence 
-that the sex composition of previous children affects birth spacing, with the
-absence of boys significantly decreasing the duration to next birth
-\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.
-
-If short spacing lowers the survival probability of the next child, it is not, however, 
-apparent that we should expect shorter spacing in the absence of boys.
-There are two potential reasons why parents might still try to conceive sooner 
-in the absence of boys.
-One possibility is that parents do not realize that short spacing is potentially
-detrimental to the next child's health, resulting in high mortality for both boys 
-and girls born after short spacing across all households.
-
-The other possibility is that parents realize that short spacing has adverse 
-health effects, but their preference for sons is so strong that they are willing to 
-divert substantial resources to the next child if it is a boy.
-Assuming that these investments can compensate for the adverse effects,
-we should see significant differences in mortality across sex for short-spacing 
-children in the absence of boys.
-If a son is born, his mortality risk should be substantially lower than expected 
-for the spacing duration, and we should expect worse outcomes for the other 
-children (all girls).
-If a girl is born, there are two possible outcomes.
-If parents treat all children/girls the same, we should see a slight worsening in 
-health outcomes because fewer resources are available per child; 
-if they do not, the last girl will have a much lower likelihood of surviving 
-because the parents' incentive is to invest in their prior children rather than 
-the new child.
-
-With the adverse effects of shorter spacing strongly mitigated by higher education,
-better-educated women can, in theory, have shorter spacing in the absence of a boy 
-without substantial increasing mortality risk.
-Differences in mortality outcomes across boys and girls are still possible,
-but should not be as large as for less-educated women.
+Furthermore, the ability to successfully use ``low efficacy'' contraceptive methods, 
+such as the rhythm method, is increasing in education, while there is no difference 
+across education levels when it comes to modern contraceptives such as pills or 
+injectables \citep{Rosenzweig1989}.
 
 With the introduction of sex selection, parents can avoid the birth of girls, 
-although at the cost of the procedure and having to wait longer until 
-the next child if they abort the fetus.
-
+although at the cost of the procedure and having to wait longer until the next child 
+if each aborted pregnancy.
 Theory suggests that sex selection increases with lower desired fertility, and, for a 
@@
 The increased use of sex selection in India with education and in urban
-areas is consistent with a lower desired fertility for both groups,
-either because of the higher cost of children or because of other
-changes in the preferred number of children
-\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
-Jayachandran2017}.%
-\footnote{
-Stronger son preference could also contribute, but better-educated women 
-have declining stated son preference over time \citep{bhat03,pande07}.
-}
-
-The higher the cost of prenatal sex determination and abortion, the less use we should 
-see.
-Similarly, any potential adverse effects on the mother and offspring 
-from repeated abortions should also reduce the use of sex selection---provided that 
-parents are aware of these costs.
-Furthermore, the more abortions between births, the less the parents can take advantage 
-of economies of scale.
-Better-educated women tend to live in households with higher income, which better enables 
-them to access prenatal sex determination and lowers the relative costs of using sex 
-selection.
-
-Given the increase in birth spacing with each abortion, parents may try to 
-conceive even sooner to compensate for the potentially longer spacing and, 
-thereby, still take advantage of economies of scale in childrearing.
-Furthermore, if health outcomes for short spacing births have improved over 
-time---as is likely---we should see an even stronger push toward shorter 
-spacing for women using sex selection.
-
-The increases in female educational attainment imply that access to education 
-has expanded beyond the higher castes. 
-However, ``Sanskritization'' implies that as lower castes females gain access to 
-education and their husbands' income increases, the women adopt higher caste 
-norms such as stronger son preference and a retraction from the formal labor 
-market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}. 
-``Sanskritization'' may also lead to an increased aversion to daughters, rather 
-than just an increased preference for sons, which, in turn, lowers desired 
-fertility \citep{Borooah2004}.
-
-Hence, with substantial increases in husband income and a declining female labor force 
-participation, I expect a push toward longer birth spacing over time, independent
+areas is consistent with a lower desired fertility for both groups
+\citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
+Better-educated women also tend to live in households with higher income, which better 
+enables them to access prenatal sex determination and lowers the relative costs of using 
+sex selection and have long birth intervals.
+
+In summary, with substantial increases in husband income and a declining female labor 
+force participation, I expect a push toward longer birth spacing over time, independent
 of education levels, based on the income effects and the effects of spacing
-on child outcomes in the theories above.
-The declining percentage of women working suggests that the opportunity cost
-effects with increasing education will not be strong enough to shorten the
-birth spacing.
-
+on child outcomes.
 As desired fertility decreases with increasing education, I, furthermore, expect 
 birth spacing to increase the most among the best-educated because of their 
-use of sex selection and because of "Sanskritization" the changing composition 
+use of sex selection and because of with "Sanskritization" the changing composition 
 of women in the better-educated group does not substantially change this 
-group's use of sex selection.
+group's use of sex selection.%
+\footnote{
 Working in the opposite direction is that women with more education can space
-their children closer together without substantially increasing child mortality risk.
+their children closer together without substantially increasing child mortality risk,
+although compared with those factors this effect is likely to be relatively small.
+}
 
@@
 
-\section{How Much has Fertility Really Fallen?\label{sec:fertility}}
+\section{What has Happened to Fertility?\label{sec:fertility}}
 
@@
 
+[From conceptual framework section]
+If short spacing lowers the survival probability of the next child, it is not, however, 
+apparent that we should expect shorter spacing in the absence of boys.
+There are two potential reasons why parents might still try to conceive sooner 
+in the absence of boys.
+One possibility is that parents do not realize that short spacing is potentially
+detrimental to the next child's health, resulting in high mortality for both boys 
+and girls born after short spacing across all households.
+
+The other possibility is that parents realize that short spacing has adverse 
+health effects, but their preference for sons is so strong that they are willing to 
+divert substantial resources to the next child if it is a boy.
+Assuming that these investments can compensate for the adverse effects,
+we should see significant differences in mortality across sex for short-spacing 
+children in the absence of boys.
+If a son is born, his mortality risk should be substantially lower than expected 
+for the spacing duration, and we should expect worse outcomes for the other 
+children (all girls).
+If a girl is born, there are two possible outcomes.
+If parents treat all children/girls the same, we should see a slight worsening in 
+health outcomes because fewer resources are available per child; 
+if they do not, the last girl will have a much lower likelihood of surviving 
+because the parents' incentive is to invest in their prior children rather than 
+the new child.
+
+With the adverse effects of shorter spacing strongly mitigated by higher education,
+better-educated women can, in theory, have shorter spacing in the absence of a boy 
+without substantial increasing mortality risk.
+Differences in mortality outcomes across boys and girls are still possible,
+but should not be as large as for less-educated women.
+[end fro conceptual framework section]
+
 The prior literature show that shorter birth spacing, especially very short spacing,
@@
 } 
-\caption{Predicted Probability of Infant Mortality for women with no education}
+\caption{Predicted Probability of Infant Mortality for women with one to
+seven years of education}
 \label{fig:mortality_med}
@@
 } 
-\caption{Predicted Probability of Infant Mortality for women with no education}
+\caption{Predicted Probability of Infant Mortality for women with eight
+to eleven years of education}
 \label{fig:mortality_high}
@@
 } 
-\caption{Predicted Probability of Infant Mortality for women with no education}
+\caption{Predicted Probability of Infant Mortality for women with twelve or
+more years of education}
 \label{fig:mortality_highest}

### 2020-01-31 paper/sex_selection_spacing-ver3.tex
No longer a need for a long descriptive stats description

@@
 I, therefore, use a competing risk set-up, which can capture both the non-randomness of
-the birth outcome and the differential spacing.
-To my knowledge, this is the first application of competing risk models to birth
-spacing.%
+the birth outcome and the differential spacing.%
 \footnote{
@@
 
-\subsection{Descriptive Statistics}
-
-Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} presents descriptive statistics for
-the spells by education level and period.
+Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} presents descriptive 
+statistics for the spells by education level and period.
 The level of censoring increases with parity and time, as we should expect with later 
@@
 sex-selective abortions.
-
-The share of urban women in the sample has fallen slightly over the
-periods, even though India's population has become more urbanized, presumably because the 
-age of marriage has increased faster in urban than in rural areas.
-Hence, there are relatively more urban women, but fewer show up in the
-sample because they are not yet married.
-
-Finally, the population has become substantially better educated over time.
-In the first period, almost 60\% of women had no education, and only twenty percent had
-eight or more years, while in the last period the reverse was the case.
-These changes underestimate the increase in education because many of the younger women 
-with more education are not yet married and therefore not in the sample.%
-\footnote{
-Women with eight or more years of education accounted for 65.9\% of
-unmarried women in NFHS-3 and 82.8\% of unmarried women in NFHS-4
-\citep{International-Institute-for-Population-Sciences-IIPS2007,International-Institute-for-Population-Sciences-IIPS2017}.
-}
-
-% \citep[p 56]{International-Institute-for-Population-Sciences-IIPS2007}
-% and \citet[p 61]{International-Institute-for-Population-Sciences-IIPS2017}
-% for more information.
-
-% Age at marriage increased over time across all three education groups.
-% The most substantial increase was for women without any education, where
-% the average went from below 16 years of age to 18.5.
-% The smallest change is for the most educated women where the average age
-% at marriage went up by less than a year---from 19.6 to 20.4---across the 
-% four periods.
 
@@
 In the interest of brevity, I discuss only two subsamples.
-Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex compositions for 
+Figures \ref{fig:pps_low} and \ref{fig:pps_highest} show spacing across sex compositions for 
 the second, third, and fourth spells for the first period, 1972--1984, and the last 
@@
 % } 
-% \caption{
-% Survival curves conditional on progression to next birth for urban women with eight or
-% more years of education; start point is nine months after prior birth
-% }
-\label{fig:pps_high}
+\caption{
+Survival curves conditional on progression to next birth for urban women with twelve or
+more years of education; start point is nine months after prior birth
+}
+\label{fig:pps_highest}
 \end{figure}

### 2020-02-01 paper/sex_selection_spacing-ver3.tex
Drop 4th spell for mortality because too few obs
Rewrite mortality section

@@
-% Revamped version for Demography focusing on method
-
 \documentclass[12pt,letterpaper]{article}
@@
 \usepackage{placeins}
+
+\usepackage{endfloat}`
 
@@
 
-[From conceptual framework section]
-If short spacing lowers the survival probability of the next child, it is not, however, 
-apparent that we should expect shorter spacing in the absence of boys.
-There are two potential reasons why parents might still try to conceive sooner 
-in the absence of boys.
-One possibility is that parents do not realize that short spacing is potentially
-detrimental to the next child's health, resulting in high mortality for both boys 
-and girls born after short spacing across all households.
-
-The other possibility is that parents realize that short spacing has adverse 
-health effects, but their preference for sons is so strong that they are willing to 
-divert substantial resources to the next child if it is a boy.
-Assuming that these investments can compensate for the adverse effects,
-we should see significant differences in mortality across sex for short-spacing 
-children in the absence of boys.
-If a son is born, his mortality risk should be substantially lower than expected 
-for the spacing duration, and we should expect worse outcomes for the other 
-children (all girls).
-If a girl is born, there are two possible outcomes.
-If parents treat all children/girls the same, we should see a slight worsening in 
-health outcomes because fewer resources are available per child; 
-if they do not, the last girl will have a much lower likelihood of surviving 
-because the parents' incentive is to invest in their prior children rather than 
-the new child.
-
-With the adverse effects of shorter spacing strongly mitigated by higher education,
-better-educated women can, in theory, have shorter spacing in the absence of a boy 
-without substantial increasing mortality risk.
-Differences in mortality outcomes across boys and girls are still possible,
-but should not be as large as for less-educated women.
-[end fro conceptual framework section]
-
 The prior literature show that shorter birth spacing, especially very short spacing,
 is associated with higher risk of infant mortality.
-Hence, it is possible that the increasing use of sex-selective abortions could
-directly reduce infant mortality by lengthening the duration from the prior birth.
-
-There are a number of potential issues with understanding to what extent this
-has happened.
-
-First, the sex of the next child is no longer random, and boys, in the absence of
-differential treatment, have higher infant mortality than girls.
-
-Second, it may be that what matters is not the time between births, but rather 
-between pregnancies, in which case multiple abortions followed quickly by new 
-pregnancies would lead to shorter real spells of recovery.
-The implication is that long spells might have a higher mortality risk since
-they are now more likely with multiple abortions.
-
-Third, as I show above the use of sex selection is more prevalent the higher the
-education level of the mother.
-Higher maternal education is, however, also associated with lower mortality risk
-to begin with.
-On top of this, with economic growth and better health care, infant mortality
-may have fallen across all education groups and areas in the period covered.
+Hence, the longer spacing, both from the increasing use of sex-selective abortions and
+from secular changes, may directly reduce infant mortality.
+To the extent that the longer birth intervals arise from multiple abortions
+the short duration between \emph{pregnancies} could, however, increase mortality risk.
 
 I address three questions.
-
-First, does the increased use of sex selection lead to higher mortality risk?
-
+First, how do the effects of short spacing vary by education level in India?
 Second, has the negative effects of short spacing changed over time?
-
-Third, how do the effects of short spacing vary by education level in India?
-
-There are a number of problems with estimating the relationship between 
-sex-selective abortions and infant mortality.
-
-First, there are potential selection problem.
-For example, women who face higher mortality risk of their children might forego 
-the use of sex selection to ensure that they reach their desired number of 
-children.
-If these women also know to avoid very short birth spacing, the precense of 
-these women in the sample would inflate the mortality of the "middle" birth
-spacing, relative to the very short or very long birth spacing.
-
-[our JDE paper]
-
-An additional selection with the opposite effect is that women who have
-difficulties conceiving or carrying a preganancy to term may also have higher 
-mortality risk for their offspring, leading to a supriuos correlation
-between very long birth spacing and mortality \citep{Kozuki2013}. 
-If better health care and higher income means that more of these women are
-now able to carry their pregnancy to term we can end up with more births
-after long spells that have higher mortality risk but not because of the
-increased use of sex selection.
-
-[Our Demography paper shows a different type of selection effect, where the
-use of sex selection biases the effect estimates of other variables that
-vary together with the use of sex selection.]
-
-Given the data and that the focus of this paper is mainly on the birth
-spacing, a more in-depth treatment of these issue is the topic of future work.
-Part of the problem here is also that the method used previously, such
-as family fixed effects does not work well when the number of births is
-very low as it is for higher education women who use sex 
-selection, especially since the spacing from marriage to first birth
-does not provide any information \citep{Kozuki2013,Molitoris2019}.
-However, the fixed effects results and linear probability do not deviate
-substantially.
-
-Second, the actual number of abortions are unobserved.
-The results above do show, however, how the use of sex selection vary
-by education and sex composition of prior children.
-I, therefore, estimate infant mortality risk taking into account the
-sex composition of the prior children, as well as the index child.
-
-Starting with the sample used for estimating birth spacing, I select, by
-parity, children born more than 12 months before the survey month.
+Finally, is the increased use of sex selection associated with higher mortality risk?
+
+Starting with the sample used for estimating birth spacing, I select children born 
+more than 12 months before the survey month.
+I restrict the analyses to parities two and three because of the small number
+of births and deaths for parity four.
+Furthermore, I do not show results for women with twelve or more years of
+education for the 1972--84 period because of the low number of women.
+
 The dependent variable is whether the child died within the first twelve
-months of life (infant mortality).
-As above, I restrict the analysis to parity two through four.
-
-The main set of explanatory variable consists of dummies for birth spacing,
-divided into less than 15 months from when conception could realistically
-could happen (same definition as above) and based on the finding that 
-spacing less than 24 months between birth is associated with higher
-infant mortality \citep{Molitoris2019}, and then in 12 months intervals
-until TK, where all births after and until 96 months are included.%
-\footnote{
-\citet{Molitoris2019} has used quartic functions, but the concern is
-that with the relatively small number sample here the shape
-of the function would be strongly influenced by a small number of
-observations.
-Using dummies provides a more flexible specification and the standard
-error will directly reflect the higher degree of noise for the
-spells periods with fewer observations.
-}
-In addition, I use dummies for sex of the index child (the child whose 
-mortality is estimated) and the sex composition of the prior children.
-Birth spacing dummies, sex of index child, and sex composition dummies
+months of life.
+The main set of explanatory variable consists of dummies for birth spacing
+covering 12 months intervals, starting from nine months after the prior birth 
+as above, until 48 months, which includes all births until 96 months.
+In addition, I use dummies for sex of the index child and the sex composition 
+of the prior children.
+The birth spacing dummies, the sex of index child, and the sex composition dummies
 are all interacted.
+Since the actual number of abortions are unobserved, the interactions between
+sex composition of prior children and the sex of the index child serve
+as proxies for the use of sex selection.
 The other explanatory variables are the same as above and estimations
-are done separately by education level.
-
-I estimate probability of infant mortality using a logit model.
-Results are presented as the predicted probability of dying within the
-first year at the possible combinations of index child sex, sex composition
-of prior children, and the birth spacing dummied.
+are done separately by education level and spell.
+
+I estimate the probability of infant mortality using a logit model.
+Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} present 
+the predicted probability of dying within the first year at the possible 
+combinations of index child sex, sex composition of prior children, and 
+the birth spacing dummied.
 All other variables are set to their average values.
-[TK ehh, did I also do urban/rural?]
-
-Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} show the 
-estimated probabilities.
 To ease legibility all confidence intervals are suppressed
 (graphs with confidence intervals are available on request).
+
+An important caveat is that the estimations do not 
+address potential selection problems.
+For example, if women who have difficulties conceiving or carrying a pregnancy 
+to term also have higher mortality risk for their offspring, the 
+result may be a supriuos correlation between long birth spacing and 
+mortality \citep{Kozuki2013}. 
+Unfortunately, methods used previously to address selection, such
+as family fixed effects do not work well when the number of births is
+low as it is for higher education women \citep{Kozuki2013,Molitoris2019}.
+On the positive side, the fixed effects results and linear probability in
+prior research do not deviate substantially.
 
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p1_low_dummies}
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p2_low_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p3_low_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p4_low_dummies} 
     \end{minipage}
@@
 \end{figure}
+
+Women with no education have experienced substantial
+improvements in infant mortality risk over time.
+The decrease is especially pronounced for shorter
+birth intervals.
+The mortality risk for children with the shortest 
+interval (the 0 to 11 months group, which is equivalent 
+to 9 to 20 months after the prior birth) is
+between 15 and 20 percent in the earlier periods, but
+fall to less than 10 percent in the last period.
+
+The mortality risk reductions for longer spells is
+less pronounced, but still there.
+For the latest period, the likelihood of dying within
+the first year is below five percent.
+
+Despite the prior findings of differential mortality
+by sex, there is little evidence that girls have
+substantially higher mortality risk, especially for
+second births.
+There is, however, some weak evidence that boys born
+after two girls have slightly lower mortality risk,
+although none of the differences are statistically
+significant.
 
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p1_med_dummies}
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p2_med_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p3_med_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p4_med_dummies} 
     \end{minipage}
@@
 
+Infant mortality risk for women with one to seven years 
+of education have also clearly decreased over time.
+This is also the first group that show increasing 
+mortality risk with longer spacing, although this effect 
+disappears for the later periods.
+In other words, it does not appear to be the result of 
+sex selection, but rather arise from the selection bias 
+discussed above.
+
 \begin{figure}[htpb]
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p1_high_dummies}
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p2_high_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p3_high_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p4_high_dummies} 
     \end{minipage}
@@
 
+For women with eight to eleven years of education, 
+mortality risk have decreased slightly between periods,
+although the changes are relatively minor.
+The elevated mortality risk with very short spacing
+is still evident, but the difference is much smaller 
+than for the lower education groups.
+
+If sex selective abortions lead to higher mortality
+risk we should see an increase for longer spacing
+when the child was a born and the prior children were
+all girls (the solid lines).
+There are no apparent differences between these groups
+and the other potential combinations.
+If anything, mortality risk for boys born after girls
+have slightly lower mortality.
+None of the differences are statistical signficant.
+
 \begin{figure}[htpb]
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p2_highest_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p3_highest_dummies} 
     \end{minipage}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s4_p4_highest_dummies} 
     \end{minipage}
@@
 
-For women with twelve or more years of education the results become very noisy
-because of the low number of births, especially for parity three and four, and
-the low mortality rate.
-As above, I do not show results for the 1972--84 period because there were too
-few women with this level of education for this period.
-
-Based on the second parity births, women with twelve or more years of education
-have the lowest infant mortality risk. 
-Even for very short birth intervals the mortality risk is less than five percent,
+Women with twelve or more years of education
+have the lowest infant mortality risk based on the
+second parity since the third parity results are very
+noisy. 
+Even for very short birth intervals the mortality risk is 
+less than five percent,
 and fall to less than half that for longer intervals.
-Given the low mortality there is, not surprisingly, much difference between
-the three periods covered.
-Furthermore, there is no evidence that longer intervals are associated with
-significantly higher mortality, especially for the groups most likely to have
-used sex selection (women with a girl as their first child and a boy as their
-second with a long interval).
-
-Women with eight to eleven years of education have marginally higher mortality
-risk than women with the most education, and also show slightly more evidence
-of increased mortality with very short spacing.
-Mortality risk have decreased slightly between periods, although the changes
-are relatively minor.
-As for women with the most education, there are not any statistically significant 
-differences or increases in mortality with longer spacing.
-Because of the low mortality risk and the relatively small number of births,
-the estimates for the third and fourth parity are noisy.
-
-Infant mortality risk for women with one to seven years of education have
-clearly decreased over time.
-This is also the first group that show increasing mortality risk with longer
-spacing, although this effect mostly disappears for the later periods.
-In other words, it does not appear to be the result of sex selection, but
-rather arise from the selection bias discussed above where women with long
-spells are those who find it difficult to either conceived and/or carry a 
-pregnancy to term and also have higher mortality risk for their offspring.
-
-Finally, women with no education have experienced substantial improvements
-in infant mortality risk over time.
-This decrease is especially pronounced for shorter intervals.
-For the longer intervals, there is surprisingly little difference across
-the education groups for the later periods.
+Given the low mortality there is, not surprisingly, much 
+difference between the three periods covered.
+Furthermore, there is still no evidence that longer 
+intervals are associated with significantly higher 
+mortality, especially for the groups most likely to have
+used sex selection (women with a girl as their first 
+child and a boy as their second with a long interval).
+
+Overall, the results show substantial convergence
+in mortality risk across groups over time.
+For the longer intervals, there is surprisingly little 
+difference across the education groups for the later 
+periods with even the no education group showing
+an infant mortality risk of less than five percent.
+Furthermore, with the adverse effects of shorter spacing 
+strongly mitigated by higher education and no apparent 
+increase in mortality risk from sex selection,
+better-educated women can both try to conceive early
+and and use multiple abortion in the absence of a boy
+without substantial increasing mortality risk.
 
@@
 - why has fertility fallen at all? Lower mortality, higher quality children?
+- lower mortality and a higher than previously anticipated fertility implies that 
+population growth in India is higher than expected.
 ]

### 2020-02-01 paper/sex_selection_spacing-ver3.tex
Typo in package name
Need complete new abstract and various edits

@@
 
-\usepackage{endfloat}`
+\usepackage{endfloat}
 
@@
 \noindent
-Strong son preference is typically associated with shorter birth spacing in the absence of 
-sons, but access to sex selection has the potential to reverse this pattern because each 
-abortion extends spacing by six to twelve months. 
-I apply an empirical method that simultaneously accounts for how sex selection 
-increases both birth spacing and the likelihood of a son. 
-Using the four rounds of India's National Family and Health Surveys, I show that birth 
-intervals increased substantially over the last four decades, with the most significant
-increases among women most likely to use sex selection.
-Specifically, well-educated women with no boys now have significantly longer birth
-intervals, and more male-biased sex ratios, than similar women with boys. 
-Women with no education still follow the standard pattern of short average spacing when 
-they have girls and little evidence of sex selection, with medium-educated women showing 
-mixed results.
-Furthermore, the traditional pattern of longer average spacing with sons appears to arise 
-not from fewer very short birth intervals, but rather from the upper end of the distribution.
 
@@
 Longer spacing between births then potentially lowers mortality, although there may
-be counteracting effects if the longer spacing arises because of multiple abortions.
-There has so far been no attempt to examine which mechanism dominates.
+be counteracting effects if the longer spacing arises because of multiple abortions, but
+there has so far been no attempt to examine which mechanism dominates.
 
@@
 Despite a large literature on son preference and birth spacing, there is, however,
-no prior research that has examined how sex selection affects spacing.
+no prior research has examined how sex selection affects spacing.
 
@@
 these changes relate to the use of sex selection?
-To show how sex selection has affected birth spacing, I focus on how birth intervals have
-changed for different education levels, urban or rural, and the sex composition of 
-prior children.
 
@@
 
+[Shorten/combine these two paragraphs]
 Second, how has the distribution of birth spacing changed?
@@
 
-Finally, has the relationship between birth spacing and mortality changed over time?
-[TK]
-
-[TK results]
+Finally, how has the relationship between birth spacing 
+and mortality changed over time?
+Mortality risk is inversely related to education level,
+especially for very short birth intervals.
+However, infant mortality risk has decline substantial 
+over time for the lower education groups and is now
+close to the level of women with the most education.
+There is no evidence that the increasing use of 
+sex selection is associated with higher mortality risk.
 
@@
 Both are potentially important factors in the birth spacing decision, as I discuss
-in detail in the subsequent section.
+in the subsequent section.
 
@@
 The elevated sex ratios strongly suggest that sex selection, possibly precipitated by
-declining fertility, drove the increases in birth intervals for women with only girls and 
+declining desired fertility, drove the increases in birth intervals for women with only girls and 
 that without sex selection we would instead have observed a diverging pattern in birth 
@@
 
-Women with eight or more years of education are expected to have the lowest fertility and 
-the highest use of sex selection, and we should, therefore, see the most substantial 
-effects on spacing.
+Women with eight to eleven years of education are 
+expected to have lower fertility and 
+higher use of sex selection, and we should, therefore, 
+see substantial effects on spacing.
 At first blush, it appears from Figure \ref{fig:bootstrap_high} that the second spell 

### 2020-02-07 paper/sex_selection_spacing-ver3.tex
Make paper more concise
- Rearrange sections
- Rewrite fertility section
- Rewrite mortality section
- Move/combine graphs

@@
 
-\usepackage{endfloat}
+% \usepackage{endfloat}
 
@@
 education levels have increased for both males and females,
-and the total fertility rate has fallen to 2.2, or just above replacement 
+and the total fertility rate has fallen to 2.2 
 \citep{Bosworth2008,Dharmalingam2014,
@@
 increase in the males-to-females ratio at birth
-\citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,Guilmoto2012,
-Bongaarts2013,Portner2015b,Jayachandran2017}.
+\citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,
+Portner2015b,Jayachandran2017}.
 
@@
 increases the interval between births by six to twelve months, the growing use of 
-sex-selective abortions has the potential to substantially increase birth spacing.%
+sex-selective abortions may substantially increase birth spacing.%
 \footnote{
@@
 Hence, the changes in birth spacing may be much more substantial in India 
-than what we have observed in other countries as they developed.
-
-Understanding how birth spacing changes is essential for three reasons.
-
-First, tempo effects, such as those arising from changes in birth spacing, bias 
-the total fertility rate (TFR), in the sense that the TFR becomes a more biased measure 
-of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
-If birth spacing increased substantially over time, India's fertility may, in 
-fact, be higher than generally accepted based on the TFR.
+than what we have observed in other countries.
+
+Understanding how birth spacing changes is essential for two main reasons.
+
+First, if birth intervals increase substantially over time, India's fertility may 
+be higher than generally accepted based on the total fertility rate (TFR).
+Increasing birth spacing is a tempo effect, which, by postponing births, makes the TFR a 
+downward biased estimate of cohort fertility 
+\citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
 
@@
 which likely contributed to the higher mortality and morbidity risk for girls
-\citep{Whitworth2002,Bhargava2003,Bhalotra2008,Maitra2008,
-Jayachandran2011,Jayachandran2017a}.
+\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
 Longer spacing between births then potentially lowers mortality, although there may
-be counteracting effects if the longer spacing arises because of multiple abortions, but
-there has so far been no attempt to examine which mechanism dominates.
-
-Finally, birth spacing has long served as a measure of son preference, with strong
-son preference associated with shorter birth intervals, the fewer sons a family has 
-\citep{ben-porath76b,Leung1988}.
-Now, longer birth intervals in the absence of sons may instead arise because couples 
-with a strong preference for sons use sex selection, possibly to the point where we 
-observe a reversal of the traditional spacing pattern.
-Despite a large literature on son preference and birth spacing, there is, however,
-no prior research has examined how sex selection affects spacing.
-
-Here, I examine how birth spacing in India has changed over time and across 
+be counteracting effects if the longer spacing arises because of multiple abortions.
+There has, so far, been no attempt to examine which mechanism dominates.
+
+% Finally, birth spacing has long served as a measure of son preference, with strong
+% son preference associated with shorter birth intervals, the fewer sons a family has 
+% \citep{ben-porath76b,Leung1988}.
+% Now, longer birth intervals in the absence of sons may instead arise because couples 
+% with a strong preference for sons use sex selection, possibly to the point where we 
+% observe a reversal of the traditional spacing pattern.
+% Despite a large literature on son preference and birth spacing, no prior research has,
+% however, examined how sex selection affects spacing.
+
+I examine how birth spacing in India has changed over time and across 
 groups with the introduction of sex selection.
@@
 Third, to what extent does TFR reflect cohort fertility?
-An advantage of the empirical model is that I can predict fertility behavior taking into
+The empirical model allows me to predict fertility behavior taking into
 account both the likelihood of parity progression and having a child of a specific sex.
@@
 Both are potentially important factors in the birth spacing decision, as I discuss
-in the subsequent section.
+in the next section.
 
@@
 Around sixty percent of urban women born in the 1930s had no education, 25 percent had
-between one and seven years, about 10 had eight or more years of education, and only
-five percent has twelve years or more.
+between one and seven years, about ten percent had eight or more years of education, and 
+only five percent has twelve years or more.
 The proportions with no education and one to seven years have both declined to just below 
@@
 
-Figure \ref{fig:work_by_survey} shows the percent of married women who are 
-currently working at the time of the survey by age group and education level.
-No other labor force participation question is consistently available across all 
-four surveys. 
-Because the question refers to currently working, the percentages are lower in previous
-studies.
-
-\begin{figure}[!htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{40 Years or Older}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_40}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_40} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_30}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_30} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_20}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_20} 
-    \end{minipage}
-}
-\caption{Percentage of married women who were working at the time of the 
-survey by age group and area of residence}
-\label{fig:work_by_survey}
-\end{figure}
-
-There is a U-shaped relationship between education and working in most cases with 
-the highest percent working for women with either no education or with twelve or 
-more years and the lowest for women with eight to eleven years of education.
+The NFHS data show a U-shaped relationship between education and working for married
+women, with the highest percent working for women with either no education 
+or with twelve or more years and the lowest for women with eight to eleven years of 
+education.%
+\footnote{
+See Appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
+}
 Women are more likely to report working if they live in rural than urban areas 
 and the older they are.
-Comparing 1992 and 2015, the percent of women who currently work has either 
-remained roughly the same or decreased.
-The cases were the numbers were higher in 1999 and 2006 than in 1992 or 2015 
-are mostly based on small samples, such as rural women with twelve or more 
-years of education in rural areas.
-
-A question is whether the rapid expansion in female educational attainment has led
-to significant changes in the composition of better-educate women and whether this will
-affect their son preference and desired fertility.
-It is clear that the increases in female educational attainment imply that access to 
-education has expanded beyond the higher castes. 
+For married women there is relatively little change in the percentage currently working 
+over time,
+but all education and age groups have become substantially more likely to work for
+a family member.
+
+The increases in female educational attainment imply that access to education has 
+expanded beyond the higher castes. 
+One possible effect of the rapid expansion in female education, and the 
+associated change in the composition of better-educated women, is that the behavior
+of the better-educated would change. 
 However, ``Sanskritization'' implies that as lower castes females gain access to 
@@
 market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
+The low and declining female labor force participation is a first indication that this
+process still operates.
 
@@
 Specifically, if having children require the mother to reduce her market work, parents 
-can lower the cost of children by shorten birth spacing.
-With the shorter birth spacing, parents can take advantage of economies of scale in 
-childrearing, because taking care of two young children does not take twice as much 
-time as taking care of one child \citep{Vijverberg1982}.
-In this case, better-educated women will both have lower fertility and shorter
-spacing than less-educated women because of their higher opportunity cost of time 
-\citep{Ross1974,Newman1984}.
+can lower the cost of children by shortening birth spacing to 
+take advantage of economies of scale in childrearing \citep{Vijverberg1982}.
 
@@
 First, although real wages for both men and women have almost doubled between 1987 and 
-2011, the mean male wage is still close to 70 higher than the female wage 
+2011, the mean male wage is still close to 70 percent higher than the female wage 
 \citep{Klasen2015,Bhargava2018}.
@@
 
-In fact, it may be that the combination of rising incomes and continued son preference 
-lead to even longer spacing than what we would expect from the standard income effect.
+The combination of rising incomes and continued son preference may even lead to longer 
+spacing than what we would expect from the standard income effect alone.
 As women's education increases, their productivity at home also increases, especially in 
@@
 \citep{Behrman1999}.
-The result would be longer birth intervals because that increases parental attention 
-per child resulting in higher child ``quality'' \citep{Zajonc1975,Zajonc1976,Razin1980}.
+The result would be longer birth intervals if parental attention per child results in 
+higher child ``quality'' \citep{Zajonc1975,Zajonc1976,Razin1980}.
 The evidence on spacing's effect on child quality measures such as IQ 
@@
 
-While one might expect that increasing income and female education would also lengthen
-average birth spacing through better access and knowledge of contraception, the empirical 
-relationship between contraception use and birth spacing is ambiguous 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
-Furthermore, the ability to successfully use ``low efficacy'' contraceptive methods, 
-such as the rhythm method, is increasing in education, while there is no difference 
-across education levels when it comes to modern contraceptives such as pills or 
-injectables \citep{Rosenzweig1989}.
+% While one might expect that increasing income and female education would also lengthen
+% average birth spacing through better access and knowledge of contraception, the empirical 
+% relationship between contraception use and birth spacing is ambiguous 
+% \citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+% Furthermore, the ability to successfully use ``low efficacy'' contraceptive methods, 
+% such as the rhythm method, is increasing in education, while there is no difference 
+% across education levels when it comes to modern contraceptives such as pills or 
+% injectables \citep{Rosenzweig1989}.
 
@@
 although at the cost of the procedure and having to wait longer until the next child 
-if each aborted pregnancy.
+for each aborted pregnancy.
 Theory suggests that sex selection increases with lower desired fertility, and, for a 
@@
 sex selection and have long birth intervals.
-
-In summary, with substantial increases in husband income and a declining female labor 
+We may even observe a ``delay'' effect, where parents conceive later because they know 
+that short spacing is detrimental to the next child's health, and that the next child is 
+more likely to be a boy because of access to sex selection.
+
+In summary, with substantial increases in husbands' income and a declining female labor 
 force participation, I expect a push toward longer birth spacing over time, independent
@@
 As desired fertility decreases with increasing education, I, furthermore, expect 
-birth spacing to increase the most among the best-educated because of their 
-use of sex selection and because of with "Sanskritization" the changing composition 
-of women in the better-educated group does not substantially change this 
-group's use of sex selection.%
+birth spacing to increase the most among the better-educated because of their 
+use of sex selection.%
 \footnote{
@@
 }
+Even with the large increase in the number of better-educated women, "Sanskritization" 
+imply that the changing composition does not substantially change this group's use of 
+sex selection.
 
@@
 }
-There are, however, two problems with the standard approach in this setting.
+There are two problems with the standard approach in this setting.
 First, and most importantly, the introduction of sex selection means that the sex of the 
@@
 
-The distribution of spacing is captured by the survival curve, which shows the probability 
-of not having had a birth yet by spell duration, for a given set of explanatory variables.
-The survival curve at time $t$ is 
-\begin{equation}
-\label{eq:survival}
-S_{t} 
-= 
-\prod_{d=1}^t
-\left(
-\frac{ 1 }
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
-\right).
-\end{equation}
-
-Because the probability of ever having a next birth varies across groups, a direct 
-comparison of standard survival curves tells us little about how the spread of sex 
-selection affects birth spacing across groups.
-I, therefore, condition on the predicted likelihood of parity progression when examining 
-birth spacing measures, such as the average duration to a birth.
-The reliability of this approach depends on whether the spell length covered is 
-sufficiently long that few women are likely to give birth after the spell cut-off.
-I discuss the choice of spell length below.%
-\footnote{
-It is important to note that the approach is not the same as merely calculating 
-the birth spacing measures for women who already have a given 
-parity child in the survey because that number does not take into account
-the censoring of spells that will eventually lead to a birth.
-}
-In addition, I present graphs of survival curves conditional on parity progression,
-which therefore begin at 100\% and end at 0\%.
+% The distribution of spacing is captured by the survival curve, which shows the probability 
+% of not having had a birth yet by spell duration, for a given set of explanatory variables.
+% The survival curve at time $t$ is 
+% \begin{equation}
+% \label{eq:survival}
+% S_{t} 
+% = 
+% \prod_{d=1}^t
+% \left(
+% \frac{ 1 }
+% {1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
+% \right).
+% \end{equation}
+% 
+% Because the probability of ever having a next birth varies across groups, a direct 
+% comparison of standard survival curves tells us little about how the spread of sex 
+% selection affects birth spacing across groups.
+% I, therefore, condition on the predicted likelihood of parity progression when examining 
+% birth spacing measures, such as the average duration to a birth.
+% The reliability of this approach depends on whether the spell length covered is 
+% sufficiently long that few women are likely to give birth after the spell cut-off.
+% I discuss the choice of spell length below.%
+% \footnote{
+% It is important to note that the approach is not the same as merely calculating 
+% the birth spacing measures for women who already have a given 
+% parity child in the survey because that number does not take into account
+% the censoring of spells that will eventually lead to a birth.
+% }
+% In addition, I present graphs of survival curves conditional on parity progression,
+% which therefore begin at 100\% and end at 0\%.
 
@@
 having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
-a set of explanatory variables and not having had a child before that period, as
-\begin{align}
-P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
-& =  
-\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
-{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
-\label{eq:probability_boy} \\
-P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
-& =  
-\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
-\label{eq:probability_girl}
-\end{align}
+a set of explanatory variables and not having had a child before that period.
+% , as
+% \begin{align}
+% P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
+% & =  
+% \frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
+% {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
+% \label{eq:probability_boy} \\
+% P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
+% & =  
+% \frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
+% {1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
+% \label{eq:probability_girl}
+% \end{align}
 It is then straightforward to calculate the estimated percentage of children born that 
@@
 
-In addition to the large number of women surveyed and the long period covered, one of the
-benefits of the NFHS is that surveys enumerators pay careful attention to spacing between 
+In addition to the large number of women surveyed and the long period covered, a
+benefit of the NFHS is that surveys enumerators pay careful attention to spacing between 
 births and probe for ``missed'' births.
@@
 The allocation of spells into periods is determined by when conception, and therefore 
-decisions on sex selection, can begin, even if we do not observe any births until nine 
-months later. 
+decisions on sex selection, can begin. 
 This allocation mechanism means that some spells cover two periods, which may bias 
@@
 marriage.
-The imputation results in large numbers of women with spells that are either negative or 
-less than nine months and makes a comparison of spell duration over time subject to an 
+The imputation results in large numbers of women with spells that are less than nine 
+months and makes a comparison of spell duration over time subject to an 
 excessive amount of noise.
@@
 With these cut-offs, less than one percent of observed births occur after
-the spell cut-off.%
-\footnote{
-\input{../tables/num_missed.tex}
-}
+the spell cut-off.
+
+% %
+% \footnote{
+% \input{../tables/num_missed.tex}
+% }
 
@@
 
-Women with different education levels have different hazard profiles, although the size 
-and direction of the effect vary across areas and time 
-\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Kim2010,Soest2018}.
-Furthermore, the use of sex selection increases with education, either because of the 
-associated lower fertility or because higher income enables them to access and
-afford prenatal sex determination
-\citep{das_gupta97,retherford03b,Guilmoto2009a,Bongaarts2013,Portner2015b,Jayachandran2017}.%
-\footnote{
-It is also possible that the effect is driven by a stronger son preference, although 
-higher education women have shown declining son preference \citep{bhat03,pande07}.
-}
-I divide women into three groups based on education attainment: no
-education, one to seven years of education, and eight and more years of education.
+Women with different education levels have different hazard profiles
+\citep{Whitworth2002,Bhalotra2008,Kim2010}.
+Furthermore, as discussed above, the use of sex selection increases with education, 
+either because of the associated lower fertility or because higher income enables them 
+to access and afford prenatal sex determination
+I divide women into four groups based on education attainment: no
+education, one to seven years of education, eight to eleven years of education,
+and twelve and more years of education.
 The models are estimated separately for each education level to reduce the potential 
@@
 
-\section{Results\label{sec:results}}
+\section{How Birth Spacing has Changed\label{sec:results}}
 
@@
 spell.
-Figures \ref{fig:bootstrap_low}, \ref{fig:bootstrap_med}, and  \ref{fig:bootstrap_high} 
-show these predicted outcomes for the three education levels separated by the area of 
+Figures \ref{fig:bootstrap_low} through \ref{fig:bootstrap_highest}
+show these predicted outcomes for the four education levels separated by the area of 
 residence.%
 \footnote{
-For legibility, none of the graphs show standard errors, which, together with the graphed 
-values, are shown in Appendix Tables 
-\ref{tab:avg_sex_ratio_low}, 
-\ref{tab:avg_sex_ratio_med}, and 
-\ref{tab:avg_sex_ratio_high}.
-}
-The predicted probability of having a birth by the end of the spell (parity progression
-probability) is $1-S_{T}$, that is the likelihood of having had a birth by 96 months after 
-the beginning of the spell.
-To find the expected average duration I first calculate for each woman the probability 
-of giving birth in each time $t$, which I use as weights to calculated her expected duration. 
+For legibility, the graphs do not show standard errors.
+The graphed values, with standard errors, are shown in Appendix Tables 
+\ref{tab:avg_sex_ratio_low} through \ref{tab:avg_sex_ratio_highest}.
+}
+
+The predicted parity progression probability is the likelihood of a birth by 96 months 
+after the beginning of the spell.
+To find the expected average duration I first calculate, for each woman, the probability 
+of giving birth in each period $t$, which I use as weights to calculated her expected 
+duration. 
 I then average the individual expected durations across women using the parity progression
@@
 
-The predicted sex ratio captures the percent boys that will have been born to women 
-in the sample when childbearing for that spell is over.
+The predicted sex ratio captures the percent boys to women in the sample when 
+childbearing for that spell is over.
 A woman's predicted sex ratio is the weighted average of the predicted percentage boys 
@@
 % \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
+
 \captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
@@
 
-Based on the literature, I expect women with no education to follow a traditional approach
-to son preference with high fertility, shorter birth intervals with fewer son, and  
-minimal use of sex selection.
-This pattern is supported by Figure \ref{fig:bootstrap_low}, but with crucial differences 
-across spells.
-Since only between ten and twenty percent of women without education live in urban areas, 
-I focus on rural women.
-
-Birth intervals have increased in length over time and are longer the higher the spell.
-The smallest increases in birth intervals have been for the second spell, with most 
-increases only between one and two months.
-Interestingly, son preference has little effect on spacing for the second spell, with 
-very small, albeit statistically significant, differences in birth intervals depending on 
-the sex of the first child and virtually all women still have a second birth.
-
+Figure \ref{fig:bootstrap_low} shows that women with no education follow a traditional 
+approach to son preference with high fertility, shorter birth intervals with fewer sons, 
+and minimal use of sex selection, but with crucial differences across spells.
+I focus on rural women since most women without education in the sample live in urban 
+areas.
+
+Birth intervals have all increased over time, with the increases larger the higher the 
+spell.
+The increase for the second spell was only between one and two months, while the 
+increases for the fourth spell were between five and nine months, depending on the
+sex composition, with larger increases the more boys.
+
+Consistent with a high desired fertility, son preference has little effect on spacing for 
+the second spell and virtually all women have a second birth independent of the sex of 
+the first child.
 Son preference in birth intervals shows up more clearly for the third, and, particularly, 
 the fourth spell.
-For the fourth spell, the difference across sex compositions are more pronounced over time, 
-and the likelihood of having a child has decreased for women with at least one son.
+Furthermore, for the fourth spell, the difference across sex compositions are more 
+pronounced over time, and the likelihood of having a fourth child has decreased for women 
+with at least one son.
 Women with only girls, show almost no reduction in the probability of having a birth 
 across time and spells.
-Despite the expectation that this group of women does not use sex selection, the predicted 
-sex ratios for those with only girls are statistically significantly higher than the 
-natural ratio for the third and fourth spell.
-Hence, it is possible that at least part of the increased  birth intervals for those
-with only girls comes from the use of sex selection and that the differences in birth 
-spacing across sex compositions would be even more substantial in the absence of sex 
-selection.
 
@@
 Figure \ref{fig:bootstrap_med} shows that for women with one to seven years of education
-birth intervals have increased over the four decades, and the increases are larger than 
-for women without any education.
+birth intervals have increased slightly more than for women with no education, especially 
+for the second spell where the increases are between three and six months.
+
 Contrary to women without education, however, there has not been an increased divergence 
@@
 Instead, for the third spell, the most substantial increases in birth intervals 
-are for women with two daughters and no sons, with an increase of about seven months.
+are for women with two daughters and no sons, with an increase of about eight months.
 The result is that the standard spacing pattern reversed for urban women, so the longest 
@@
 birth intervals are now almost identical across sex compositions of prior children.
-For the fourth spell, the increases in spacing for women with only girls have kept pace
-with the other sex compositions in rural areas.%
-\footnote{
-The pattern for the urban fourth spell is noisier because a low number of observations.
-}
-
-The substantial increases in spacing for women with only girls is not evidence of lower
-son preference as shown by the changes in the predicted sex ratios and the parity 
+
+That the substantial increases in spacing for women with only girls is not evidence of 
+lower son preference is shown by the changes in the predicted sex ratios and the parity 
 progression behavior.
-For both the third and fourth spell the predicted sex ratios in urban and rural areas are
-statistically significantly above the natural sex ratio at between 55.5\% and 57.7\% boys.
-The elevated sex ratios strongly suggest that sex selection, possibly precipitated by
-declining desired fertility, drove the increases in birth intervals for women with only girls and 
-that without sex selection we would instead have observed a diverging pattern in birth 
+For both the third and fourth spell, the predicted sex ratios in urban and rural areas are
+statistically significantly above the natural sex ratio at between 55.4 and 57.7
+percent boys.
+
+The elevated sex ratios strongly suggest that sex selection drove the increases in birth 
+intervals for women with only girls.
+Without sex selection we would likely instead have observed a diverging pattern in birth 
 intervals across sex composition similar to what we saw for women without education.
@@
 
-Women with eight to eleven years of education are 
-expected to have lower fertility and 
-higher use of sex selection, and we should, therefore, 
-see substantial effects on spacing.
-At first blush, it appears from Figure \ref{fig:bootstrap_high} that the second spell 
-spacing pattern looks remarkably similar to the two other education groups with little 
-difference in average birth spacing across sex composition.
-This similarity hides, however, a much faster decline in the likelihood of having a second 
-birth, substantial increases in spacing, and predicted sex ratios for women with a 
-first-born daughter above 55 percent for both urban and rural areas for the last two 
-periods.
-Hence, where it not for a substantial amount of sex selection brought on by falling
-fertility we would now have seen a standard son preference spacing pattern with 
-significantly shorter spacing after a first-born girl than after a first-born boy.
-
-The tremendous impact that sex selection can have on birth spacing is illustrated 
-particularly vividly by the changes for the third spell, where we see a complete reversal 
-of the standard spacing pattern.
-In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
-compositions were less than two months apart.
-For the later periods, however, the highest predicted average spacing was for women
-\emph{with only daughters}, with most of the differences to the other sex compositions 
-statistically significant.
-In urban areas, the predicted average birth interval for a woman with only daughters 
-increased by almost a full year from 26.8 to 38.3 months, while it ``only'' increased
-by around six months with only sons.
-Consistent with the rapidly falling fertility leading to increased use of sex selection, 
-women with no sons have around 65\% and 60\% boys in urban and rural areas, respectively.
-
-The reversal pattern also shows up for the fourth spell for urban women, but not for rural 
-women.
-An important caveat is that the falling fertility means that few women make it to the 
-fourth spell, and even if they do, we are unlikely to observe a birth by the survey making 
-the estimates noisy.
-Son preference, however, still shows clearly in the parity progression probabilities for 
+As Figure \ref{fig:bootstrap_high} shows, there is little difference for the second spell 
+between women with one to seven years of education and those with eight to eleven years, 
+except that the birth intervals have increased by about two months more for the 
+better-educated women.
+
+For the third spell, however, the better-educated women have substantial larger increases
+in birth intervals, with the largest increases when the first two children are girls,
+where the increases are more than ten months for urban women and more than six for rural.
+The result is that the longest average spells are for those without boys.
+That this reversal is due to sex selection is clear from the predicted sex ratios,
+which are around 60 percent.
+A similar reversal pattern also shows up for the fourth spell for urban women, although
+the estimates are noisier.
+
+Son preference still shows clearly in the parity progression probabilities for 
 women without a son, with the declines for the third and fourth spells substantially
 slower for both urban and rural women without a son than for those with at least one son.
-
-% When trying to understand the strength of son preference, it is interesting that the sex 
-% ratio is also statistically significantly different from the natural rate in the case 
-% where women already have one son for the third and fourth spells.
-% Again, the sex ratio in the presence of one son for the third and fourth spells are higher 
-% in urban areas than rural areas, although the difference is less than for women with only 
-% girls.
-% Hence, it is possible that women are still willing to use sex selection even after giving 
-% birth to one, although this behavior may also be in response to either experienced
-% or expected mortality of the first son born.
-% This result is different from prior studies using NFHS data.
-% The NFHS-4 sample is substantially larger than the three prior surveys.
-% Hence, it is possible that the effect has been there all along, but we did not have the 
-% power to detect it.
+This points to even well-educated women might still have relatively high fertility if
+they do not use sex selection, and that the majority will end up with at least two
+children.
 
@@
 
-\subsection{Distribution of Birth Spacing Within Spells}
+The impact that sex selection can have on birth spacing is illustrated particularly 
+vividly by the reversal of the standard spacing pattern for the third spell for urban 
+women with twelve or more years of education as shown in 
+Figure \ref{fig:bootstrap_highest}.%
+\footnote{
+I do not show the results for the fourth spell since the low number of births,
+especially for women with one or more boys make the spacing and sex ratio results
+very noisy.
+Results are available upon request.
+}
+In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
+compositions were only a couple of months apart, with the shortest spacing for women who 
+had two girls.
+Women with two girls had, however, the highest predicted average spacing in the later
+periods, with about seven months longer birth intervals than women with one or two boys.
+
+The increase in average birth intervals for urban women with two girls from 30.5 to 42.3 
+months corresponds directly to the sex ratio going from 60 to 77 percent. 
+The sex ratio of 60 percent for urban women with two girls in the first 
+period indicates that this group of women were early users of sex selection, and that
+in the absence of sex selection we would have observed an even larger difference in
+birth intervals for the first period.
+
+The seven months increases in spacing for the second spell are in line with the results 
+above, although with an average spacing of 29 months in the 1972--84 period, the birth
+intervals for this group begin where the women with eight to eleven years of education
+ended.
+Furthermore, the predicted sex ratio is significantly above the natural ratio for the 
+three later periods, and around 60 percent for the two last periods.
+
+Finally, despite decreases in the parity progression probability, women without sons 
+are still likely to have an additional child.
+Close to 80 percent of urban women with a girl as their first child are predicted to
+have a second child and more than half with two girls will have a third child.
+For women with sons the decline has been faster, but mainly for the third spell; with a
+boy as their first child, close to 70 percent will have a second child.
+
+\subsection{Distribution of Birth Spacing}
 
@@
 hide crucial differences in the distribution of spacing.
-Specifically, whether increases in average spacing come from fewer births after very short 
-intervals, from an even longer spacing of births with already long spacing, or from a 
-general increase in spacing have important implications for what effects the increases in 
-average spacing are likely to have and how to interpret the motivation for the changes.
-This section, therefore, examines the distribution of spacing within spells.
-I show survival curves conditional on predicted parity progression, which allows direct 
-comparisons of the distribution of spacing across groups independent of differences in 
-parity progression probabilities, rather than standard survival curves.
-
-% Because the conditional survival curves are independent of the likelihood of parity 
-% progression, they all begin at 100\% and end at 0\%.
-
-% On one hand, if there still are many births that occur after very short intervals, the 
-% increase in average spacing is unlikely to have a substantial impact on health outcomes
-% since the literature on birth spacing and child health suggests that an interpregnancy 
-% interval of fewer than 18 months is associated with a higher risk of adverse health 
-% outcomes and mortality \citep{Conde-Agudelo2012}.
-% On the other hand, we may see a reduction in early observed births and more long spells if 
-% families with fewer sons are both more likely to have a very early pregnancy and to 
-% continue through pregnancies and sex-selective abortions until they conceive a son.%
-% \footnote{
-% It is unclear what the optimal response in the timing of pregnancies to the availability 
-% of sex selection should be.
-% The expected birth intervals become longer with the use of sex selection, which may be 
-% costly for parents leading them to try to conceive even earlier than previously.
-% Conversely, if parents know that short birth intervals are detrimental to the next child's
-% health, and that, with sex selection, the next child is likely a boy, it might make sense to 
-% wait longer before conceiving.
-% }
-
-Instead of averaging across the entire sample, for each spell/education combination I 
-calculate the conditional survival curves using average values and the majority of
-categories, which means no ownership of land and not in a scheduled caste or tribe.
-The characteristics used do not change across the four decades to ensure that composition 
-effects do not drive the changes.
-In the interest of brevity, I discuss only two subsamples.
-Figures \ref{fig:pps_low} and \ref{fig:pps_highest} show spacing across sex compositions for 
-the second, third, and fourth spells for the first period, 1972--1984, and the last 
-period, 2005--2016, for rural women with no education and urban women with eight or 
-more years of education.
-The Appendix shows conditional survival curves for all groups and decades and to 
-complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
-\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
-percentiles durations with bootstrapped standard errors based on averages across all women.
-
-% First spell for low and high education women
-
-% \begin{figure}[htpb]
-% \centering
-% \setcounter{subfigure}{-1}
-% \subfloat[Rural Women with No Education]{
-%     \begin{minipage}{0.48\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_low_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{0}
-% \subfloat[Urban Women with 8 or More Years of Education]{
-%     \begin{minipage}{0.48\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell1_highest_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \caption{
-% Survival curves conditional on progression to first birth; start point is month of marriage
-% }
-% \label{fig:pps_spell1}
-% \end{figure}
-
-% The biased sex ratio for the first spell for the most educated 
-% women suggests that there might be sex selection on the first birth.
-% I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
-% of spacing has changed over time for rural women with no education and urban women 
-% with eight or more years of education.
-% What is most striking is how similar the distribution of spacing is across the
-% two groups.
-% 
-% Both groups show little change in median spacing, but that masks a substantial
-% compression of when most of the births occur.
-% In the 1972--1984 period, the middle 80\% of births for women with no education 
-% are predicted to occur between approximately 6 and 64 months, whereas in the 
-% 2005--2016 period it is between 12 and 54 months.
-% Hence, the compression is equivalent to more than a full year.
-% Women with eight or more years of education show a slightly smaller compression:
-% in the 1972--1984 period, the middle 80\% of births are predicted to occur between
-% approximately 6 and 48 months, whereas in the 2005--2016 period it is between
-% 12 and 46 months.
-% Hence, the compression is eight months.
-% 
-% Women became less likely to conceive before marriage over time.
-% In the first two periods there was a relatively smooth decline in the number of
-% women without a birth starting at the time of marriage, but in the last two
-% periods, there are few women who exit early after marriage and
-% instead there is a substantial dip between 9 and 12 months after
-% marriage.
-% 
-% It is likely that the compressed spacing, beginning at nine months
-% after marriage in the later periods, is associated with better health
-% and higher age at marriage.
-% For example, women without education have seen an increase in the average 
-% age at marriage from below 16 to 18.5 from the first period to the last 
-% while women with the most education increased from 19.5 to 20.4.
+For example, if sex selection drives the changes in birth spacing, most of the increase in 
+spacing will come from people who have two or more pregnancies rather than one and,
+therefore, from changes in the longer intervals,
+while a general increase in spacing would show up as an increase in spacing across the 
+board.
+
+Figures \ref{fig:combined_p25_p75_urban} and \ref{fig:combined_p25_p75_rural} 
+show how the predicted 25th and 75th percentile birth intervals has changed over time 
+by spell and education.
+For each woman in a given spell/period combination, I calculate the time point at 
+which there is a given percent chance that she will have given birth, relative to the
+probability that she will eventually give birth in that spell.
+The reported statistics is the average of the percentile duration
+across all women in a given sample using the individual predicted
+probabilities of having had a birth by the end of the spell as weights.%
+\footnote{
+The Appendix shows conditional survival curves for all groups and 
+Appendix Tables \ref{tab:p25_p50_p75_low} through \ref{tab:p25_p50_p75_highest} 
+show 25th, 50th, and 75th percentiles durations with bootstrapped standard errors.
+}
 
 \begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_low_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_low_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_low_urban}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_med_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_med_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_med_urban}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_high_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_high_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_high_urban}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_highest_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_highest_urban}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
 \caption{
-Survival curves conditional on progression to next birth for rural women without
-education; start point for each spell is nine months after prior birth
-}
-\label{fig:pps_low}
-\end{figure}
-
-The most striking results for women with no education are that, in both periods, close to 
-50\% had their second child by 18 months and that there are minimal differences in the 
-probability of very short intervals whether the first-born was a boy or a girl.
-Hence, almost 50\% of second-borns are born within an interval associated with a higher 
-risk of adverse outcomes, and, surprisingly, there do not appear to be any particular 
-disadvantage for the child born after a girl than after a boy.
-There is more evidence of son-preference driven short spacing for the third and fourth
-spells, but a large number of women still have very short intervals whether they have boys 
-or girls already.
-For both spells, the difference in average spacing mainly come from the upper end of the
-distribution; for example, the 75th percentile show a twelve months difference between 
-families with three girls and families with two or more boys.
+25th and 75th Percentile Birth Intervals for Urban Women by Spell and Education
+}
+\label{fig:combined_p25_p75_urban}
+\end{figure}
 
 \begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\footnotesize{Second Spell}}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{0}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\footnotesize{Third Spell}}
-\setcounter{subfigure}{1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.46\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-% \\
-% \rotatebox[origin=c]{90}{\footnotesize{Fourth Spell}}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.46\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_highest_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.46\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Probability of no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_highest_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup[subfigure]{position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_low_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_low_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_low_rural}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_med_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_med_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_med_rural}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_high_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_high_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_high_rural}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_highest_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_highest_rural}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
 \caption{
-Survival curves conditional on progression to next birth for urban women with twelve or
-more years of education; start point is nine months after prior birth
-}
-\label{fig:pps_highest}
-\end{figure}
-
-Another remarkable result is the similarity in the lower end of the distribution of
-spacing for the second spell between urban women with eight or more years of education and 
-rural women with no education for the 1972--1984 period with little difference across
-sex composition and close to 50\% with very short birth intervals.
-However, the high education women show an upward shift over time and spacing patterns that
-are close to identical after first-born girls and after first-born boys until after 
-approximately 80 percent have had their second child, driven by the significant use of sex 
-selection among women with a first-born girl.
-
-The sex selection induced reversal of the standard spacing pattern shows up clearly in the 
-2005--2016 period for the third and fourth spells, with spacing to the next child 
-consistently longer with only girls than with the other sex compositions.
-This pattern is most consistent with early and continued use of sex selection, rather 
-than a general reduction in the likelihood of very short birth intervals.
-It also means that the previously born girls can expect more time without a younger 
-sibling, which may reduce the sibling competition for resources.
-
-% Furthermore, the differences are substantial across most of the distribution.
-% Twelve months after the beginning of the spell there is a more than ten 
-% percentage points difference in the conditional survival curves for only girls
-% and only boys.
-% Both of the spells, therefore, show changes in the distribution of births that is in line
-% with extensive use of sex selection among families with no or one son.
-
-% We should expect 51.2 percent of the women to conceive a boy when they have their first 
-% pregnancy in the spell, which means that they do not need to use sex selection to have
-% a son.
-% Hence, even with sex selection, we might expect to observe a very short interval for the 
-% initial births if families with strong son preference still try to conceive sooner than 
-% those with lower son preference.
-% If, however, parents know that children born after short interpregnancy periods suffer 
-% from worse health outcomes it makes sense to wait longer before conceiving again in
-% this situation, precisely because they know that with sex selection the next child they 
-% carry to term will be a boy.
-% 
-% Hence, there are two potential reasons why son preference combined with access to
-% sex selection can lead to longer birth intervals.
-% First, the ``abortion'' effect, where each abortion extend birth spacing by between six
-% and twelve months.
-% Second, a ``delay'' effect, where parents conceive later because they know that short
-% spacing is detrimental to the next child's health, and that the next child is more likely
-% to be a boy because of access to sex selection.
+25th and 75th Percentile Birth Intervals for Rural Women by Spell and Education
+}
+\label{fig:combined_p25_p75_rural}
+\end{figure}
+
+For both women with no education and those with one to seven years of education,
+almost all of the increases in the average spacing discussed above come from increases in 
+the long end of the spacing distribution rather than from a general increase.
+Hence, spacing is still very short for many women, with 25 percent or more having
+their next birth within two years of the prior birth, even in the last period.
+Furthermore, the increases in the 75th percentile birth intervals are relatively small
+for the second spell and slightly larger for the third spell at around five months.
+Most of the divergence across sex compositions happen for the fourth spell, where 
+the largest increases are for women with two or three sons.
+However, even for women with no or one son there has been increases in the birth intervals 
+of a half to a full year consistent with some use of sex selection for this group.
+
+The 25th percentile birth intervals for women with eight to eleven years of education also 
+changed relatively little over time and is, as for the less-educated women, close to
+around two years since the prior birth.
+The result is that most of the change in average spacing is driven by increases in the
+longer spacing end of the distribution.
+For example, the 75th percentile spacing length for women with two girls in the third 
+spell increased by more than 15 months, mainly as the result of more widespread use of sex 
+selection as the sex ratios above indicate.
+
+The most educated urban women show an interesting pattern for the third spell, where there 
+is essentially no change in either the 25th or 75th percentile birth intervals in the
+presence of at least one boy.
+The 75th percentile birth interval, however, increases by more than 20 months,
+corresponding to the massive increase in the sex ratio to almost 80 precent in the 
+latest period.
+Hence, the increases in birth spacing and the reversal in spacing pattern by sex
+composition over time is mainly driven by increases in the length of the longer intervals, 
+consistent with a substantial use of sex selection.
+
+Although most of the increases come from among the longer intervals, there is some 
+evidence for the ``delay'' effect discussed above, where parents conceive later
+exactly because they know that the next child is likely to be a boy since they plan
+to use sex selection.
+The best example is for the best-educated urban women in the third spell, where, in the 
+last two periods, the spacing to the third child is significant longer if the two prior 
+children were girls than if they already had one or two boys.
+These two periods are the periods where the predicted sex ratios are 70 and 80 percent,
+respectively.
+There is also a significantly longer spacing with only girls for women with eight to
+eleven years of education in the last period for the third and fourth spell, although
+the difference is substantially smaller.
 
@@
 
-Birth spacing has increased substantially over time across all education groups, but 
-especially among those women likely to use sex selection.
-One of the potential effects of the increased birth spacing is that the total fertility
-rate may underestimate cohort fertility, at least temporarily.
-Whether tempo effects ``biases'' fertility depends on what the outcome of interest is,
-but since my outcome of interest is cohort fertility I will use ``bias''
-\citep{Ni-Bhrolchain2011}.
-
-Some tempo effects, such as those that arise from postponement of childbearing, are 
-studied extensively in the literature \citep{Bongaarts1999}.
-There are, however, to the best of my knowledge, no other cases where there has been
-as substantial an increasing in spacing as for India.
-
-To understand how cohort fertility has changed over time and how strong the bias in
-TFR is, I compare predicted fertility using both a version of the total fertility
-rate and the hazard model results presented above as shown in Table \ref{tab:fertility}.
+A potential effect of the substantial increases in birth spacing is that TFR may 
+underestimate cohort fertility, at least temporarily.
+I, therefore, compare predicted fertility based on a variation of the TFR and the 
+hazard model by urban/rural and education group in Table \ref{tab:fertility}.
 
@@
 
-The TFR measure uses births up to parity four to make the measure comparable to what I 
-can calculate for the hazard model, and I calculate this four-parity TFR by urban/rural 
-and the education groups used above.
-Hence, the TFRs are not directly comparable to those in the NFHS reports, although the
-differences should be smaller the higher the education group and the most recent the 
-survey provided that cohort fertility has fallen over time.
+To make the fertility rate comparable to the hazard model, it uses only births up to 
+parity four, and is, therefore, not directly comparable to those in the NFHS reports.
 Otherwise, I follow the procedure used in the NFHS reports and calculate age specific 
@@
 See \citet{Croft2018} for more detail.
-Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
-is based on the household rosters, assuming that never-married women have had no children.
-Because of the low number of births to women aged 45 to 49 this age group was not
-used for the hazard model estimations and, therefore, is also excluded for the fertility
-rate.
-The marital total fertility rate lead to unrealistically high numbers and is, therefore,
-not presented \citep{Hoem2011,Laplante2015}.
-}
-
-NFHS-1 was collected after sex selection was introduced and it is, therefore, not 
-possible to calculate a fertility rate in exactly the same manner for a period before 
-sex selection was widely available.
+% Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
+% is based on the household rosters, assuming that never-married women have had no children.
+% Because of the low number of births to women aged 45 to 49 this age group was not
+% used for the hazard model estimations and, therefore, is also excluded for the fertility
+% rate.
+% The marital total fertility rate lead to unrealistically high numbers and is, therefore,
+% not presented \citep{Hoem2011,Laplante2015}.
+}
+
+Because NFHS-1 was collected after the introduction of sex selection it is not possible 
+to calculate a fertility rate in exactly the same manner for a period 
+before sex selection was widely available.
 Instead, I calculate the fertility rates for women who was between 15 and 39 years of
@@
 not widespread.
-This fertility rate is shown as ``1987--88'' in the table.
+This fertility rate is shown as ``1987--88''.
 
@@
 of progression to the next parity for each spell.
-I include the spell from marriage to first birth, even those results are not examined 
-above because of the problems with capturing the exact timing of marriages for the first 
-two rounds of the survey.
-The estimated progression probabilities should, however, be less affected by this
-problem.
-
+Since the parity progression depends on the sex composition for prior children for parity 
+two and above, I estimate the progression probability for each possible sex composition
+and weigh those probabilities with the likelihood that they will occur based on the
+prior spells.
+
+I include the spell from marriage to first birth, despite the problems capturing the 
+exact timing of marriages for the first two rounds of the survey, since
+the estimated progression probabilities should not be affected by this problem.
 To ensure that the predictions depend solely on sample composition and the estimate, I
@@
 each parity, assuming three years increases in age between each parity.
-Hence, for a woman married at age 20, I use age 23 for predicting progression 
-to the second birth, 26 for the third, and 29 for the fourth.
-Decreasing the increases in age between parities leads to slightly higher predicted 
+Shorter assumed duration between parities leads to slightly higher predicted 
 fertility.
 
-As shown above, the parity progression depends critically on the sex composition for prior 
-children for parity two and above.
-I, therefore, estimate the progression probability for each possible sex composition
-and weigh those probabilities with the likelihood that they will occur based on the
-prior spells.
-
-The predicted fertility using the hazard model assumes that women in the sample
-follows the parity progression probability in the period. 
-For example, for the NFHS-4 the predictions I assume that all women in the sample follow
-the estimated behavior for all four spells based on the 2005--2016 results.
-
-The survey rounds do not coincide entirely with the periods I use for the hazard model.
+The survey rounds do not coincide directly with the periods I use for the hazard model.
 For the NFHS-4, I use the model results for the 2005--2016 period, 
@@
 
-The main result is that the predicted cohort fertility based on the hazard model is 
-consistently higher and declines faster than the four-parity fertility rate.
-The faster decline in predicted fertility based on the hazard model is consistent with
-a large bias in the fertility rate measure arising from later marriage, increased use of 
-sex selection, and the general increase in birth spacing shown above.
-
-The potential bias in the fertility rate is also evident in the fact that the 
-fertility rate is increasing over time for some groups.
+In almost all cases the predicted cohort fertility based on the hazard model is higher 
+than the four-parity fertility rate.
+Only for women with no education in the first period are there almost no difference 
+between the two fertility measures; a situation where fertility is high and spacing
+very short and likely unchanged over a long period before.
+
+Consistent with a larger bias in the fertility rate when age of marriage and the length of 
+birth intervals are increasing, the absolute bias is least in the first and the last 
+period and highest in the middle two periods.
+Hence, the fertility rate declined too fast between the mid-1980s and the end of the 
+century, and only recently as the rate of increase for the birth intervals have slowed 
+are the predicted cohort fertility and the fertility beginning to converge again.
+Even with the convergence, the predicted cohort fertility for the last period is above 
+the 1992--93 fertility rate for every group except urban women with no education.
+Furthermore, for the last period, the predicted cohort fertility is stil between
+and 20 percent higher than the fertility rate.
+
+The bias in the fertility rate is also evident in the fact that the fertility rate is 
+increasing over time for some groups.
 For example, urban women with eight to eleven years of education showed 1.84, 1.81, and
-1.87 over the last three surveys and the increase from NFHS-3 to NFHS-4 is even larger
-for rural women with one to seven years of education.
+1.87 over the last three surveys, and for rural women with one to seven years of
+education fertility rate goes from 2.25 for NFHS-3 to 2.37 for NFHS-4.
 These increases are likely the result of a stabilization of the age of first birth and
@@
 \footnote{
-Increases in TFR over time, even in the face of declining fertility is not 
+Increases in TFR over time, even in the face of declining cohort fertility is not 
 unusual, as shown by Columbia in the early 1990s \citep{Bongaarts1999}.
@@
 
-Despite the decline in the predicted cohort fertility based on the hazard model, these 
-are still generally above the generally accepted replacement level of 2.1.
+Despite the declines in the predicted cohort fertility based on the hazard model, 
+predicted cohort fertility is still mostly above the generally accepted replacement 
+level of 2.1.
 Only for urban women with twelve or more years of education is the predicted cohort
@@
 the short duration between \emph{pregnancies} could, however, increase mortality risk.
-
-I address three questions.
-First, how do the effects of short spacing vary by education level in India?
-Second, has the negative effects of short spacing changed over time?
-Finally, is the increased use of sex selection associated with higher mortality risk?
+This section addresses how infant mortality has changed and whether there is evidence
+of a negative impact of sex selective abortions.
 
@@
 The other explanatory variables are the same as above and estimations
-are done separately by education level and spell.
+are done separately by education level and parity.
 
 I estimate the probability of infant mortality using a logit model.
-Figures \ref{fig:mortality_low} to \ref{fig:mortality_highest} present 
-the predicted probability of dying within the first year at the possible 
-combinations of index child sex, sex composition of prior children, and 
-the birth spacing dummied.
+Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} present 
+the predicted probability of the second child dying within the first year at the 
+possible combinations of index child sex, sex composition of prior children, and 
+the birth spacing dummied.%
+\footnote{
+The online Appendix show the corresponding graphs for the third child.
+}
 All other variables are set to their average values.
-To ease legibility all confidence intervals are suppressed
-(graphs with confidence intervals are available on request).
+To ease legibility all confidence intervals are suppressed.
 
@@
 For example, if women who have difficulties conceiving or carrying a pregnancy 
-to term also have higher mortality risk for their offspring, the 
-result may be a supriuos correlation between long birth spacing and 
-mortality \citep{Kozuki2013}. 
+to term also have higher mortality risk for their offspring, a spurious correlation 
+between long birth spacing and mortality may arise \citep{Kozuki2013}. 
 Unfortunately, methods used previously to address selection, such
-as family fixed effects do not work well when the number of births is
+as family fixed effects, do not work well when the number of births is
 low as it is for higher education women \citep{Kozuki2013,Molitoris2019}.
-On the positive side, the fixed effects results and linear probability in
-prior research do not deviate substantially.
+However, in prior research the fixed effects results and linear probability do not 
+deviate substantially.
 
@@
 \rotatebox[origin=c]{90}{\small{1972-1984}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
+\setcounter{subfigure}{-1}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[No Eduction]{\includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\setcounter{subfigure}{-0} 
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[One to Seven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}}
+        \captionsetup[subfigure]{labelformat=parens}
     \end{minipage}
@@
 } 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
     \end{minipage}
@@
 } 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
     \end{minipage}
@@
 } 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with no education}
-\label{fig:mortality_low}
-\end{figure}
-
-Women with no education have experienced substantial
-improvements in infant mortality risk over time.
-The decrease is especially pronounced for shorter
-birth intervals.
-The mortality risk for children with the shortest 
-interval (the 0 to 11 months group, which is equivalent 
-to 9 to 20 months after the prior birth) is
-between 15 and 20 percent in the earlier periods, but
-fall to less than 10 percent in the last period.
-
-The mortality risk reductions for longer spells is
-less pronounced, but still there.
-For the latest period, the likelihood of dying within
-the first year is below five percent.
-
-Despite the prior findings of differential mortality
-by sex, there is little evidence that girls have
-substantially higher mortality risk, especially for
-second births.
-There is, however, some weak evidence that boys born
-after two girls have slightly lower mortality risk,
-although none of the differences are statistically
-significant.
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Second Child's Infant Mortality 
+for Women with No Education
+and Women with One to Seven Years of Education}
+\label{fig:mortality_low_med}
+\end{figure}
 
@@
 \rotatebox[origin=c]{90}{\small{1972-1984}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
-    \end{minipage}
-}
+\setcounter{subfigure}{-1}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+        \subfloat[Eight to Eleven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}}
+        \captionsetup[subfigure]{labelformat=parens}
+    \end{minipage}
+}
+\begin{minipage}[t]{0.42\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
 \\
@@
     \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
+        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
     \end{minipage}
@@
     \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
+        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
     \end{minipage}
@@
     \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with one to
-seven years of education}
-\label{fig:mortality_med}
-\end{figure}
-
-Infant mortality risk for women with one to seven years 
-of education have also clearly decreased over time.
-This is also the first group that show increasing 
-mortality risk with longer spacing, although this effect 
-disappears for the later periods.
-In other words, it does not appear to be the result of 
-sex selection, but rather arise from the selection bias 
-discussed above.
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{1972-1984}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
@@
 } 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with eight
-to eleven years of education}
-\label{fig:mortality_high}
-\end{figure}
-
-For women with eight to eleven years of education, 
-mortality risk have decreased slightly between periods,
-although the changes are relatively minor.
-The elevated mortality risk with very short spacing
-is still evident, but the difference is much smaller 
-than for the lower education groups.
-
-If sex selective abortions lead to higher mortality
-risk we should see an increase for longer spacing
-when the child was a born and the prior children were
-all girls (the solid lines).
-There are no apparent differences between these groups
-and the other potential combinations.
-If anything, mortality risk for boys born after girls
-have slightly lower mortality.
-None of the differences are statistical signficant.
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
 \subfloat[Second Spell]{
@@
 } 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with twelve or
-more years of education}
-\label{fig:mortality_highest}
-\end{figure}
-
-Women with twelve or more years of education
-have the lowest infant mortality risk based on the
-second parity since the third parity results are very
-noisy. 
-Even for very short birth intervals the mortality risk is 
-less than five percent,
-and fall to less than half that for longer intervals.
-Given the low mortality there is, not surprisingly, much 
-difference between the three periods covered.
-Furthermore, there is still no evidence that longer 
-intervals are associated with significantly higher 
-mortality, especially for the groups most likely to have
-used sex selection (women with a girl as their first 
-child and a boy as their second with a long interval).
-
-Overall, the results show substantial convergence
-in mortality risk across groups over time.
-For the longer intervals, there is surprisingly little 
-difference across the education groups for the later 
-periods with even the no education group showing
-an infant mortality risk of less than five percent.
-Furthermore, with the adverse effects of shorter spacing 
-strongly mitigated by higher education and no apparent 
-increase in mortality risk from sex selection,
-better-educated women can both try to conceive early
-and and use multiple abortion in the absence of a boy
-without substantial increasing mortality risk.
+\caption{Predicted Probability of Second Child's Infant Mortality 
+for Women with Eight to Eleven of Education
+and Women with Twelve or More Years of Education}
+\label{fig:mortality_high_highest}
+\end{figure}
+
+There has been substantial convergence in mortality risk across groups over time.
+For the 12 months and above intervals, there is now little difference across 
+the education groups, with even the no education group showing an infant mortality risk 
+below five percent.
+
+Very short birth intervals still exhibit a higher mortality risk, although the 
+effect declines with education level.
+For the best-educated women the mortality risk is three to four percent,
+whereas women with no education still show a risk that is close to ten percent.
+
+Despite the prior findings of differential mortality by sex, there is little evidence 
+that girls have substantially higher mortality risk.
+There is some weak evidence that a boy born after a girl have lower mortality
+risks in the earliest periods.
+This difference disappears, however, with the general decline in mortality risk.
+
+If sex selective abortions lead to higher mortality risk, boys born after a girl 
+(the solid lines)
+should have an increased risk with longer spacing for the two highest education groups 
+in the last two periods.
+There are, however, no apparent consistent differences between these groups and the other 
+potential combinations.
+
+% line 3661 in an_infant_mortality.log
+The raw numbers for the group with the most uneven sex ratio---women with twelve or more
+years of education who have no boys in the third spell in the last period---indicates
+that even with high use of sex selection there is no impact on child mortality.
+A total of 1,004 women in this group had a third child, of which 685 are boys.
+Of these 685 boys, only 6 died within the first year of life and half of those
+were in born the 0--23 months interval, and none in 48 months or more interval.
 
@@
 - ]
+
+[from fertility section]
+Some tempo effects, such as those that arise from postponement of childbearing, are 
+studied extensively in the literature \citep{Bongaarts1999}.
+There are, however, to the best of my knowledge, no other cases where there has been
+as substantial an increasing in spacing as for India.
+
+[from mortality section]
+Furthermore, with the adverse effects of shorter spacing 
+strongly mitigated by higher education and no apparent 
+increase in mortality risk from sex selection,
+better-educated women can both try to conceive early
+and and use multiple abortion in the absence of a boy
+without substantial increasing mortality risk.
+
+% Finally, birth spacing has long served as a measure of son preference, with strong
+% son preference associated with shorter birth intervals, the fewer sons a family has 
+% \citep{ben-porath76b,Leung1988}.
+% Now, longer birth intervals in the absence of sons may instead arise because couples 
+% with a strong preference for sons use sex selection, possibly to the point where we 
+% observe a reversal of the traditional spacing pattern.
+% Despite a large literature on son preference and birth spacing, no prior research has,
+% however, examined how sex selection affects spacing.
 
@@
 
+Figure \ref{fig:work_by_survey} shows the percent of married women who are 
+currently working at the time of the survey by age group and education level.
+No other labor force participation question is consistently available across all 
+four surveys. 
+Because the question refers to currently working, the percentages are lower in previous
+studies.
+
+\begin{figure}[!htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{40 Years or Older}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_40}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_40} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_30}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_30} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\subfloat[Rural]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_rural_20}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{currently_working_urban_20} 
+    \end{minipage}
+}
+\caption{Percentage of married women who were working at the time of the 
+survey by age group and area of residence}
+\label{fig:work_by_survey}
+\end{figure}
+
 \begin{figure}[!htpb]
@@
 }
-\caption{Percentage of women who were working for a family of those women who were
-working at the time of the survey by age group and area of residence}
+\caption{Percentage women who worked for a family member of those 
+working at the time of the survey, by age group and area of residence}
 \label{fig:work_family_by_survey}
@@
 \clearpage
+
+\begin{figure}[htpb]
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_urban}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_urban}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_urban}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_urban}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
+\caption{
+Changes in 25th Percentile Birth Intervals for Urban Women by Spell and Education
+}
+\label{fig:p25_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_rural}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_rural}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_rural}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_rural}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
+\caption{
+Changes in 25th Percentile Birth Intervals for Rural Women by Spell and Education
+}
+\label{fig:p25_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_urban}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_urban}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_urban}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_urban}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
+\caption{
+Changes in 50th Percentile Birth Intervals for Urban Women by Spell and Education
+}
+\label{fig:p50_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_rural}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_rural}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_rural}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_rural}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
+\caption{
+Changes in 50th Percentile Birth Intervals for Rural Women by Spell and Education
+}
+\label{fig:p50_rural}
+\end{figure}
+
+\begin{figure}[htpb]
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_urban}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_urban}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_urban}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_urban}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_urban}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_urban}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
+\caption{
+Changes in Average Birth Intervals for Urban Women by Spell and Education
+}
+\label{fig:avg_urban}
+\end{figure}
+
+\begin{figure}[htpb]
+\captionsetup[subfigure]{labelformat=empty,position=top}
+\captionsetup{font=footnotesize,skip=2pt}
+\centering
+\caption*{No education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_rural}}
+\\
+\caption*{One to Seven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_rural}}
+\\
+\caption*{Eight to Eleven Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_rural}}
+\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_rural}}
+\\
+\caption*{Twelve or More Years of Education}
+\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_rural}}
+\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_rural}}
+\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+\captionsetup{font=normalsize}
+\caption{
+Changes in Average Birth Intervals for Rural Women by Spell and Education
+}
+\label{fig:avg_rural}
+\end{figure}
+
+\clearpage
 \newpage
 
-\section{Graphs for All Education and Spell Groups}
+\section{Survival Curves Conditional on Parity Progression for All Education and Spell Groups}
 
@@
 
+\clearpage
+\newpage
+
+\section{Infant Mortality Graphs}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with no education}
+\label{fig:mortality_low}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with one to
+seven years of education}
+\label{fig:mortality_med}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1972-1984}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
+    \end{minipage}
+}
+\\
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with eight
+to eleven years of education}
+\label{fig:mortality_high}
+\end{figure}
+
+\begin{figure}[htpb]
+\centering
+\rotatebox[origin=c]{90}{\small{1985-1994}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{1995-2004}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
+    \end{minipage}
+} 
+\\
+\rotatebox[origin=c]{90}{\small{2005-2016}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.40\textwidth}
+        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
+    \end{minipage}
+} 
+\caption{Predicted Probability of Infant Mortality for women with twelve or
+more years of education}
+\label{fig:mortality_highest}
+\end{figure}
+
 \end{document}

### 2020-02-07 paper/sex_selection_spacing-ver3.tex
Sideways figure for spacing results

@@
 
-% \usepackage{endfloat}
+\usepackage{endfloat}
 
@@
 
-\begin{figure}[htpb]
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{Urban}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
+%     \end{minipage}
+% }
+% \subfloat[Fourth Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{Rural}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
+%     \end{minipage}
+% } 
+% \subfloat[Fourth Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
+%     \end{minipage}
+% } 
+% \caption{Estimated average spell length, sex ratio, and probability of 
+% a next birth for women with no education}
+% \label{fig:bootstrap_low}
+% \end{figure}
+
+\begin{sidewaysfigure}
 \centering
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.31\textwidth}
         \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
@@
 \subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.31\textwidth}
         \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
@@
 \subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
+    \begin{minipage}{0.31\textwidth}
         \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
     \end{minipage}
@@
 \label{fig:bootstrap_low}
-\end{figure}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}
+\ContinuedFloat
+\rotatebox[origin=c]{90}{\small{Rural}}
+\subfloat[Second Spell]{
+    \begin{minipage}{0.31\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
+    \end{minipage}
+} 
+\subfloat[Third Spell]{
+    \begin{minipage}{0.31\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
+    \end{minipage}
+} 
+\subfloat[Fourth Spell]{
+    \begin{minipage}{0.31\textwidth}
+        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
+    \end{minipage}
+} 
+\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
+a next birth for women with no education}
+\label{fig:bootstrap_low}
+\end{sidewaysfigure}
 
@@
 
-\begin{figure}[htpb]
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{Urban}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
+%     \end{minipage}
+% }
+% \subfloat[Fourth Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{Rural}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
+%     \end{minipage}
+% } 
+% \subfloat[Fourth Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
+%     \end{minipage}
+% } 
+% \caption{Estimated average spell length, sex ratio, and probability of 
+% a next birth for women with one to seven years of education}
+% \label{fig:bootstrap_med}
+% \end{figure}
+
+\begin{sidewaysfigure}
 \centering
@@
 }
-\\
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with one to seven years of education}
+\label{fig:bootstrap_med}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}
+\ContinuedFloat
 \rotatebox[origin=c]{90}{\small{Rural}}
@@
 } 
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
 a next birth for women with one to seven years of education}
 \label{fig:bootstrap_med}
-\end{figure}
+\end{sidewaysfigure}
 
@@
 
-\begin{figure}[htpb]
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{Urban}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
+%     \end{minipage}
+% }
+% \subfloat[Fourth Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{Rural}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
+%     \end{minipage}
+% } 
+% \subfloat[Fourth Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
+%     \end{minipage}
+% } 
+% \caption{Estimated average spell length, sex ratio, and probability of 
+% a next birth for women with eight to eleven years of education}
+% \label{fig:bootstrap_high}
+% \end{figure}
+
+\begin{sidewaysfigure}
 \centering
@@
 }
-\\
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with eight to eleven years of education}
+\label{fig:bootstrap_high}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}
+\ContinuedFloat
 \rotatebox[origin=c]{90}{\small{Rural}}
@@
 } 
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
 a next birth for women with eight to eleven years of education}
 \label{fig:bootstrap_high}
-\end{figure}
+\end{sidewaysfigure}
 
@@
 
-\begin{figure}[htpb]
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{Urban}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{Rural}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.29\textwidth}
+%         \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
+%     \end{minipage}
+% } 
+% \caption{Estimated average spell length, sex ratio, and probability of 
+% a next birth for women with twelve or more years of education}
+% \label{fig:bootstrap_highest}
+% \end{figure}
+
+\begin{sidewaysfigure}
 \centering
@@
 }
-\\
+\caption{Estimated average spell length, sex ratio, and probability of 
+a next birth for women with twelve or more years of education}
+\label{fig:bootstrap_highest}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}
+\ContinuedFloat
 \rotatebox[origin=c]{90}{\small{Rural}}
@@
 } 
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
 a next birth for women with twelve or more years of education}
 \label{fig:bootstrap_highest}
-\end{figure}
+\end{sidewaysfigure}
 

### 2020-02-10 paper/sex_selection_spacing-ver3.tex
Spacing discussion too diffuse and focused on detail

@@
 
-Understanding how birth spacing changes is essential for two main reasons.
-
-First, if birth intervals increase substantially over time, India's fertility may 
+Understanding how birth spacing changes is of interest for two main reasons, in 
+addition to a better general understanding how fertility decisions are made.
+
+First, if birth intervals increased substantially over time, India's fertility may 
 be higher than generally accepted based on the total fertility rate (TFR).
@@
 be counteracting effects if the longer spacing arises because of multiple abortions.
-There has, so far, been no attempt to examine which mechanism dominates.
+There has, so far, been no attempt to examine how mortality has responded to the
+increase in sex selection.
 
@@
 but also works in cases without prenatal sex selection.
+The empirical model allows me to predict fertility behavior taking into
+account both the likelihood of parity progression and having a child of a specific sex.
 
 % [Hypotheses / questions]
-I address four main questions.
-
-First, how did average birth intervals change over time for different groups, and how do 
-these changes relate to the use of sex selection?
-
-Birth intervals have increased for all education groups over the four decades, 
+There are four main set of results.
+
+First, birth intervals have increased for all education groups over the four decades, 
 with larger increases, the higher the parity and the higher the education level.
@@
 sons---have seen the most substantial increases in birth intervals.
-[TK check this!] As a result, well-educated women now show a reversal of the traditional spacing 
+[TK check this] As a result, well-educated women now show a reversal of the traditional spacing 
 pattern, with the longest intervals for women with no sons.
-Those least likely to use sex selection, women with no education in rural areas, 
+Those least likely to use sex selection, women with less education in rural areas, 
 still follow the traditional pattern of short spacing when they have girls and 
 little evidence of the use of sex selection.
-
-[Shorten/combine these two paragraphs]
-Second, how has the distribution of birth spacing changed?
-Average birth intervals help us understand the overall changes in 
-spacing behavior, but tells us little about how these changes came about.
-Examining how the distribution has change allow us to separate out increases in birth
-spacing that come from women with strong son preference who still try to conceive early, 
-but are also the most likely to end up with very long spells because of multiple 
-abortions versus women who have longer average spacing because they try to avoid very
-short birth intervals.
-
-[TK this is unclear - complete rewrite]
-The traditional pattern of longer average spacing with sons appears to arise from 
-an increase in the number of very long intervals, rather than from fewer very short 
-birth intervals. 
-Across education groups, there appears to be little difference in the likelihood of 
-having a very short birth interval across sex compositions, especially for lower parities.
-
-Third, to what extent does TFR reflect cohort fertility?
-The empirical model allows me to predict fertility behavior taking into
-account both the likelihood of parity progression and having a child of a specific sex.
-I compare those predictions with fertility rate estimates based on the same data to
-show how the increases in birth spacing have led to a substantial overestimate of how 
-fast fertility has declined. [TK too imprecise? underestimate of the level, rather?]
-
-Finally, how has the relationship between birth spacing 
-and mortality changed over time?
-Mortality risk is inversely related to education level,
-especially for very short birth intervals.
-However, infant mortality risk has decline substantial 
-over time for the lower education groups and is now
-close to the level of women with the most education.
-There is no evidence that the increasing use of 
-sex selection is associated with higher mortality risk.
+[TK add sex ratios and parity progression discussions]
+
+Second, there is little difference over time and across groups in the likelihood of 
+having a very short birth interval given the sex composition of prior children, 
+especially for the lower parities.
+Hence, the increases in average spacing come predominantly from the longer birth intervals
+getting even longer over time, driven to a large degree by a substantial use of sex 
+selection.
+The exception to this result is that the better-educated women with \emph{very high} 
+predicted use of sex selection appear to conceive later exactly because the next child is 
+almost certainly a boy.
+
+Third, the fertility rate substantially overestimated how fast cohort fertility fell 
+in the 1990s and early 2000s, when spacing began to increase as the result of secular 
+changes and increasing use of sex selection.
+Although predicted cohort fertility and the fertility rate has lately begun to converge,
+the predicted cohort fertility is still ten to twenty percent higher than the
+fertility rate.
+Furthermore, even with the convergence, predicted cohort fertility is still at or above 
+replacement level, except for the best-educated urban women.
+
+Finally, infant mortality risk has decline substantially over time for all groups,
+but fastest for the lower education groups, who are now close to the level of women with 
+the most education.
+Mortality risk is, however, still inversely related to education level, especially for 
+very short birth intervals.
+There is no evidence that the increasing use of sex selection is associated with higher 
+mortality risk.
 
@@
 
-The combination of rising incomes and continued son preference may even lead to longer 
-spacing than what we would expect from the standard income effect alone.
-As women's education increases, their productivity at home also increases, especially in 
-the production of offspring human capital.
+The combination of rising incomes and continued son preference may lead to even longer 
+spacing than the standard income effect alone predicts.
+As women's education increases, their productivity in the production of offspring human 
+capital also increases.
 With relatively more boys born because of increased access to sex-selective 
@@
 \citep{Behrman1999}.
-The result would be longer birth intervals if parental attention per child results in 
-higher child ``quality'' \citep{Zajonc1975,Zajonc1976,Razin1980}.
+If more and ``better'' parental attention per child results in higher child ``quality'' 
+we should expect longer birth intervals 
+\citep{Zajonc1975,Zajonc1976,Razin1980}.
 The evidence on spacing's effect on child quality measures such as IQ 
@@
 \citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-Nevertheless, for one crucial aspect of child quality---health and mortality---longer 
-spacing does lead to better outcomes, although this relationship weakens with maternal 
-education \citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
+The exception is one crucial aspect of child quality---health and mortality---where
+longer spacing does lead to better outcomes, although this relationship weakens with 
+maternal education \citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
 
@@
 
-With the introduction of sex selection, parents can avoid the birth of girls, 
-although at the cost of the procedure and having to wait longer until the next child 
-for each aborted pregnancy.
+The introduction of sex selection allows parents to avoid the birth of girls,
+but increases the expected duration to the next birth.
 Theory suggests that sex selection increases with lower desired fertility, and, for a 
@@
 sex selection and have long birth intervals.
+
 We may even observe a ``delay'' effect, where parents conceive later because they know 
@@
 more likely to be a boy because of access to sex selection.
+Working in the opposite direction is that women with more education can, in principle, 
+space their children closer together without substantially increasing child mortality 
+risk.
+Given the apparent lack of pressure to return to the labor force,
+this effect is, however, likely to be small.
 
@@
 As desired fertility decreases with increasing education, I, furthermore, expect 
-birth spacing to increase the most among the better-educated because of their 
-use of sex selection.%
-\footnote{
-Working in the opposite direction is that women with more education can space
-their children closer together without substantially increasing child mortality risk,
-although compared with those factors this effect is likely to be relatively small.
-}
+birth spacing to increase the most among the better-educated because of the larger
+increase in household income income---even with declining female labor participation---and 
+their use of sex selection.
 Even with the large increase in the number of better-educated women, "Sanskritization" 
@@
 the next birth and how soon couples want their next child if they are going to have one.
+
 The introduction of prenatal sex determination exacerbates any bias from the 
@@
 within a spell, which means that the effects of covariates vary within the spell as well.
+
 I, therefore, use a non-proportional hazard specification, which allows the shape of the 
@@
 \ref{tab:avg_sex_ratio_low} through \ref{tab:avg_sex_ratio_highest}.
+Furthermore, I do not show the results for the fourth spell the best-educated women since 
+the low number of births, especially with one or more boys, make the spacing and sex ratio 
+results very noisy.
+Results are available upon request.
 }
@@
 \citep{ben-porath76b,jacobsen99,Portner2015b}.
-
-\subsection{No Education Women}
 
@@
 % \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
-
-\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
 
@@
 \begin{sidewaysfigure}
+\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
 \centering
@@
 \end{sidewaysfigure}
-
-Figure \ref{fig:bootstrap_low} shows that women with no education follow a traditional 
-approach to son preference with high fertility, shorter birth intervals with fewer sons, 
-and minimal use of sex selection, but with crucial differences across spells.
-I focus on rural women since most women without education in the sample live in urban 
-areas.
-
-Birth intervals have all increased over time, with the increases larger the higher the 
-spell.
-The increase for the second spell was only between one and two months, while the 
-increases for the fourth spell were between five and nine months, depending on the
-sex composition, with larger increases the more boys.
-
-Consistent with a high desired fertility, son preference has little effect on spacing for 
-the second spell and virtually all women have a second birth independent of the sex of 
-the first child.
-Son preference in birth intervals shows up more clearly for the third, and, particularly, 
-the fourth spell.
-Furthermore, for the fourth spell, the difference across sex compositions are more 
-pronounced over time, and the likelihood of having a fourth child has decreased for women 
-with at least one son.
-Women with only girls, show almost no reduction in the probability of having a birth 
-across time and spells.
-
-\subsection{Low to Medium Education Women}
 
@@
 
-Figure \ref{fig:bootstrap_med} shows that for women with one to seven years of education
-birth intervals have increased slightly more than for women with no education, especially 
-for the second spell where the increases are between three and six months.
-
-Contrary to women without education, however, there has not been an increased divergence 
-in birth intervals across sex compositions for the third and fourth spells.
-Instead, for the third spell, the most substantial increases in birth intervals 
-are for women with two daughters and no sons, with an increase of about eight months.
-The result is that the standard spacing pattern reversed for urban women, so the longest 
-predicted spacing is now for those with only girls, while rural women's predicted average 
-birth intervals are now almost identical across sex compositions of prior children.
-
-That the substantial increases in spacing for women with only girls is not evidence of 
-lower son preference is shown by the changes in the predicted sex ratios and the parity 
-progression behavior.
-For both the third and fourth spell, the predicted sex ratios in urban and rural areas are
-statistically significantly above the natural sex ratio at between 55.4 and 57.7
-percent boys.
-
-The elevated sex ratios strongly suggest that sex selection drove the increases in birth 
-intervals for women with only girls.
-Without sex selection we would likely instead have observed a diverging pattern in birth 
-intervals across sex composition similar to what we saw for women without education.
-
-\subsection{High Education Women}
-
 % \begin{figure}[htpb]
@@
 
-As Figure \ref{fig:bootstrap_high} shows, there is little difference for the second spell 
-between women with one to seven years of education and those with eight to eleven years, 
-except that the birth intervals have increased by about two months more for the 
-better-educated women.
-
-For the third spell, however, the better-educated women have substantial larger increases
-in birth intervals, with the largest increases when the first two children are girls,
-where the increases are more than ten months for urban women and more than six for rural.
-The result is that the longest average spells are for those without boys.
-That this reversal is due to sex selection is clear from the predicted sex ratios,
-which are around 60 percent.
-A similar reversal pattern also shows up for the fourth spell for urban women, although
-the estimates are noisier.
-
-Son preference still shows clearly in the parity progression probabilities for 
-women without a son, with the declines for the third and fourth spells substantially
-slower for both urban and rural women without a son than for those with at least one son.
-This points to even well-educated women might still have relatively high fertility if
-they do not use sex selection, and that the majority will end up with at least two
-children.
-
-\subsection{Highest Education Women}
-
 % \begin{figure}[htpb]
@@
 
+Average birth intervals have increased over time across all groups, and are, for a given 
+parity, longer the more education a woman.
+The increases in birth spacing are larger the higher the parity
+and, within parities, the higher the education.
+
+In the latest period, the lowest average birth interval is for women with no 
+education in the second spell at just shy of 25 months, which is an increase of a
+couple of months from the first period.
+The longest average interval was 42 months for the third spell for women with twelve or 
+more years of education who had no boys, which is an increase of approximately a year.
+For comparison, the median birth intervals reported for the NFHS have barely
+moved over time, staying at approximately 22 months calculated with the starting point 
+nine months after the prior birth used here.%
+\footnote{
+See
+\citet[][p.\ 110--112]{International-Institute-for-Population-Sciences-IIPS1995},
+\citet[][p.\ 98--103]{International-Institute-for-Population-Sciences-IIPS2000},
+\citet[][p.\ 88--91]{International-Institute-for-Population-Sciences-IIPS2007}, and
+\citet[][p.\ 81--82]{International-Institute-for-Population-Sciences-IIPS2017}.
+Median estimates are in
+Appendix Tables \ref{tab:p25_p50_p75_low} through \ref{tab:p25_p50_p75_highest}.
+}
+This lack of change underscores the importance of accounting for censoring of birth spells 
+when trying to understand how birth spacing is changing over time.
+
+Parity progression probabilities are lower the higher the education and are
+falling across all groups over time, but the extent of the decline depends crucially on 
+the sex composition of prior children and the parity.
+As expected with a strong son preference, women with no sons still are the most likely to 
+have a next birth, and this group has seen often substantially smaller declines in
+the likelihood of having another birth than women with one or more sons.%
+\footnote{
+There is, however, also some evidence that parents prefer a mixed sex composition: for 
+the fourth spell women with two boys \emph{and} a girl
+consistently have the lowest parity progression probability.
+}
+For urban women with eight to eleven years of education, for example, the second spell
+probability of a next child declined by eight percentage points if the first child was a 
+girl, but 15 percentage points if it was a boy.
+Even more extreme is the fourth spell where the likelihood of a birth declined by six 
+percentage points to 75 percent if the woman had three children, but by almost 40 
+percentage points to 25 percent if she had two boys and a girl.
+
+To what extent has the introduction of sex selection changed birth spacing across sex 
+compositions?
+There are three broad groups in the data.
+
+First, women who have only girls but do not use sex selection had, and continue to have,
+the shortest spacing, as shown, for example, by rural women with no education.
+For this group spacing is shortest with only girls across all spell, and the difference
+between sex compositions have even widen over time.
+
+Second, even with sex selection, and the associated increases in expected spacing, the
+intervals for the other sex compositions have increased even more and the relatively 
+pattern, therefore, remains more or less the same.
+This is the case, for example, for the second spell for women with eight to eleven
+and twelve or more years of education.
+
+Finally, women with the most unequal sex ratios show the longest spacing in the 
+absence of boys, and this spacing is longer than for the other possible sex 
+compositions.
+The most extreme example is that with a sex ratio for the best-educated urban women  
+approaching 80 percent, the 42 months birth intervals with two girls is seven months 
+longer than with at least one boy.
+Even urban women with eight to eleven years of education show the longest intervals with 
+only girls in the last period.
+
+Figure \ref{fig:bootstrap_low} shows that women with no education follow a traditional 
+approach to son preference with high fertility, shorter birth intervals with fewer sons, 
+and minimal use of sex selection, but with crucial differences across spells.
+I focus on rural women since most women without education in the sample live in urban 
+areas.
+
+Birth intervals have all increased over time, with the increases larger the higher the 
+spell.
+The increase for the second spell was only between one and two months, while the 
+increases for the fourth spell were between five and nine months, depending on the
+sex composition, with larger increases the more boys.
+
+Consistent with a high desired fertility, son preference has little effect on spacing for 
+the second spell and virtually all women have a second birth independent of the sex of 
+the first child.
+Son preference in birth intervals shows up more clearly for the third, and, particularly, 
+the fourth spell.
+Furthermore, for the fourth spell, the difference across sex compositions are more 
+pronounced over time, and the likelihood of having a fourth child has decreased for women 
+with at least one son.
+Women with only girls, show almost no reduction in the probability of having a birth 
+across time and spells.
+
+Figure \ref{fig:bootstrap_med} shows that for women with one to seven years of education
+birth intervals have increased slightly more than for women with no education, especially 
+for the second spell where the increases are between three and six months.
+
+Contrary to women without education, however, there has not been an increased divergence 
+in birth intervals across sex compositions for the third and fourth spells.
+Instead, for the third spell, the most substantial increases in birth intervals 
+are for women with two daughters and no sons, with an increase of about eight months.
+The result is that the standard spacing pattern reversed for urban women, so the longest 
+predicted spacing is now for those with only girls, while rural women's predicted average 
+birth intervals are now almost identical across sex compositions of prior children.
+
+That the substantial increases in spacing for women with only girls is not evidence of 
+lower son preference is shown by the changes in the predicted sex ratios and the parity 
+progression behavior.
+For both the third and fourth spell, the predicted sex ratios in urban and rural areas are
+statistically significantly above the natural sex ratio at between 55.4 and 57.7
+percent boys.
+
+The elevated sex ratios strongly suggest that sex selection drove the increases in birth 
+intervals for women with only girls.
+Without sex selection we would likely instead have observed a diverging pattern in birth 
+intervals across sex composition similar to what we saw for women without education.
+
+As Figure \ref{fig:bootstrap_high} shows, there is little difference for the second spell 
+between women with one to seven years of education and those with eight to eleven years, 
+except that the birth intervals have increased by about two months more for the 
+better-educated women.
+
+For the third spell, however, the better-educated women have substantial larger increases
+in birth intervals, with the largest increases when the first two children are girls,
+where the increases are more than ten months for urban women and more than six for rural.
+The result is that the longest average spells are for those without boys.
+That this reversal is due to sex selection is clear from the predicted sex ratios,
+which are around 60 percent.
+A similar reversal pattern also shows up for the fourth spell for urban women, although
+the estimates are noisier.
+
+Son preference still shows clearly in the parity progression probabilities for 
+women without a son, with the declines for the third and fourth spells substantially
+slower for both urban and rural women without a son than for those with at least one son.
+This points to even well-educated women might still have relatively high fertility if
+they do not use sex selection, and that the majority will end up with at least two
+children.
+
 The impact that sex selection can have on birth spacing is illustrated particularly 
@@
 women with twelve or more years of education as shown in 
-Figure \ref{fig:bootstrap_highest}.%
-\footnote{
-I do not show the results for the fourth spell since the low number of births,
-especially for women with one or more boys make the spacing and sex ratio results
-very noisy.
-Results are available upon request.
-}
+Figure \ref{fig:bootstrap_highest}.
 In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
@@
 the 1992--93 fertility rate for every group except urban women with no education.
-Furthermore, for the last period, the predicted cohort fertility is stil between
+Furthermore, for the last period, the predicted cohort fertility is stil between ten
 and 20 percent higher than the fertility rate.

### 2020-02-10 paper/sex_selection_spacing-ver3.tex
Remove wordy discussion of spacing changes

@@
 
-Figure \ref{fig:bootstrap_low} shows that women with no education follow a traditional 
-approach to son preference with high fertility, shorter birth intervals with fewer sons, 
-and minimal use of sex selection, but with crucial differences across spells.
-I focus on rural women since most women without education in the sample live in urban 
-areas.
-
-Birth intervals have all increased over time, with the increases larger the higher the 
-spell.
-The increase for the second spell was only between one and two months, while the 
-increases for the fourth spell were between five and nine months, depending on the
-sex composition, with larger increases the more boys.
-
-Consistent with a high desired fertility, son preference has little effect on spacing for 
-the second spell and virtually all women have a second birth independent of the sex of 
-the first child.
-Son preference in birth intervals shows up more clearly for the third, and, particularly, 
-the fourth spell.
-Furthermore, for the fourth spell, the difference across sex compositions are more 
-pronounced over time, and the likelihood of having a fourth child has decreased for women 
-with at least one son.
-Women with only girls, show almost no reduction in the probability of having a birth 
-across time and spells.
-
-Figure \ref{fig:bootstrap_med} shows that for women with one to seven years of education
-birth intervals have increased slightly more than for women with no education, especially 
-for the second spell where the increases are between three and six months.
-
-Contrary to women without education, however, there has not been an increased divergence 
-in birth intervals across sex compositions for the third and fourth spells.
-Instead, for the third spell, the most substantial increases in birth intervals 
-are for women with two daughters and no sons, with an increase of about eight months.
-The result is that the standard spacing pattern reversed for urban women, so the longest 
-predicted spacing is now for those with only girls, while rural women's predicted average 
-birth intervals are now almost identical across sex compositions of prior children.
-
-That the substantial increases in spacing for women with only girls is not evidence of 
-lower son preference is shown by the changes in the predicted sex ratios and the parity 
-progression behavior.
-For both the third and fourth spell, the predicted sex ratios in urban and rural areas are
-statistically significantly above the natural sex ratio at between 55.4 and 57.7
-percent boys.
-
-The elevated sex ratios strongly suggest that sex selection drove the increases in birth 
-intervals for women with only girls.
-Without sex selection we would likely instead have observed a diverging pattern in birth 
-intervals across sex composition similar to what we saw for women without education.
-
-As Figure \ref{fig:bootstrap_high} shows, there is little difference for the second spell 
-between women with one to seven years of education and those with eight to eleven years, 
-except that the birth intervals have increased by about two months more for the 
-better-educated women.
-
-For the third spell, however, the better-educated women have substantial larger increases
-in birth intervals, with the largest increases when the first two children are girls,
-where the increases are more than ten months for urban women and more than six for rural.
-The result is that the longest average spells are for those without boys.
-That this reversal is due to sex selection is clear from the predicted sex ratios,
-which are around 60 percent.
-A similar reversal pattern also shows up for the fourth spell for urban women, although
-the estimates are noisier.
-
-Son preference still shows clearly in the parity progression probabilities for 
-women without a son, with the declines for the third and fourth spells substantially
-slower for both urban and rural women without a son than for those with at least one son.
-This points to even well-educated women might still have relatively high fertility if
-they do not use sex selection, and that the majority will end up with at least two
-children.
-
-The impact that sex selection can have on birth spacing is illustrated particularly 
-vividly by the reversal of the standard spacing pattern for the third spell for urban 
-women with twelve or more years of education as shown in 
-Figure \ref{fig:bootstrap_highest}.
-In the 1972-1984 period, the predicted average birth intervals for the three possible sex 
-compositions were only a couple of months apart, with the shortest spacing for women who 
-had two girls.
-Women with two girls had, however, the highest predicted average spacing in the later
-periods, with about seven months longer birth intervals than women with one or two boys.
-
-The increase in average birth intervals for urban women with two girls from 30.5 to 42.3 
-months corresponds directly to the sex ratio going from 60 to 77 percent. 
-The sex ratio of 60 percent for urban women with two girls in the first 
-period indicates that this group of women were early users of sex selection, and that
-in the absence of sex selection we would have observed an even larger difference in
-birth intervals for the first period.
-
-The seven months increases in spacing for the second spell are in line with the results 
-above, although with an average spacing of 29 months in the 1972--84 period, the birth
-intervals for this group begin where the women with eight to eleven years of education
-ended.
-Furthermore, the predicted sex ratio is significantly above the natural ratio for the 
-three later periods, and around 60 percent for the two last periods.
-
-Finally, despite decreases in the parity progression probability, women without sons 
-are still likely to have an additional child.
-Close to 80 percent of urban women with a girl as their first child are predicted to
-have a second child and more than half with two girls will have a third child.
-For women with sons the decline has been faster, but mainly for the third spell; with a
-boy as their first child, close to 70 percent will have a second child.
-
 \subsection{Distribution of Birth Spacing}

### 2020-02-10 paper/sex_selection_spacing-ver3.tex
New Conclusion (too long)

@@
 Hence, the fertility rate declined too fast between the mid-1980s and the end of the 
-century, and only recently as the rate of increase for the birth intervals have slowed 
+century, and only recently, as the rate of increase for the birth intervals have slowed, 
 are the predicted cohort fertility and the fertility beginning to converge again.
-Even with the convergence, the predicted cohort fertility for the last period is above 
-the 1992--93 fertility rate for every group except urban women with no education.
+Even with the convergence, however, the predicted cohort fertility for 2005--16 is 
+above the 1992--93 fertility rate for every group except urban women with no education.
 Furthermore, for the last period, the predicted cohort fertility is stil between ten
@@
 
-Despite the declines in the predicted cohort fertility based on the hazard model, 
-predicted cohort fertility is still mostly above the generally accepted replacement 
-level of 2.1.
+Despite the declines in the predicted cohort fertility it is still mostly above the 
+generally accepted replacement level of 2.1.
 Only for urban women with twelve or more years of education is the predicted cohort
@@
 
-[TK things to cover:
-- almost everybody marry, so these numbers should reflect cohort fertility relatively well
-- what happens when women begin to join the labor force in larger numbers?
-- better job oppportunities may be a direct way to affect sex selection since it makes 
-it more expensive to have long spacing
-- Incorporate Newman 1984 discussion (p 947) on income vs substitution effect
-- why has fertility fallen at all? Lower mortality, higher quality children?
-- lower mortality and a higher than previously anticipated fertility implies that 
-population growth in India is higher than expected.
-]
-
-[TK future research:
-- health effects of multiple abortions on women and prior children
-- better address selection effects for mortality estimations
-- long-term outcomes for children
-- labor force participation
-- ]
-
-[from fertility section]
-Some tempo effects, such as those that arise from postponement of childbearing, are 
-studied extensively in the literature \citep{Bongaarts1999}.
-There are, however, to the best of my knowledge, no other cases where there has been
-as substantial an increasing in spacing as for India.
-
-[from mortality section]
-Furthermore, with the adverse effects of shorter spacing 
-strongly mitigated by higher education and no apparent 
-increase in mortality risk from sex selection,
-better-educated women can both try to conceive early
-and and use multiple abortion in the absence of a boy
-without substantial increasing mortality risk.
-
-% Finally, birth spacing has long served as a measure of son preference, with strong
-% son preference associated with shorter birth intervals, the fewer sons a family has 
-% \citep{ben-porath76b,Leung1988}.
-% Now, longer birth intervals in the absence of sons may instead arise because couples 
-% with a strong preference for sons use sex selection, possibly to the point where we 
-% observe a reversal of the traditional spacing pattern.
-% Despite a large literature on son preference and birth spacing, no prior research has,
-% however, examined how sex selection affects spacing.
+% What has happened to spacing and why
+
+One effect of the major changes that India has experienced over the last four decades is
+that spacing between births have increased for everybody.
+The increases in spacing are larger the higher the parity and the higher the mother's 
+education and are larger in urban than in rural areas.
+
+The most substantial increases in birth intervals arise, however, with heavy use of sex 
+selection, as, for example, urban women with twelve or more years of education and two 
+girls.
+We, therefore, now in some cases observe a reversal of the traditional spacing
+pattern where strong son preference was associated with shorter birth intervals the fewer 
+sons a family has \citep{ben-porath76b,Leung1988}.
+This reversal comes about because couples with a strong preference for sons now use sex 
+selection, not because son preference has changed over time.
+
+Despite the longer average birth intervals, a large number of women still have very
+short birth intervals.
+Hence, the changes in birth spacing is driven by the longer intervals becoming longer
+over time, both for women who do not use sex selection, but especially for those who
+do and end up with multiple abortions.
+The exception to the small change in short spacing is the delay in conception for
+women with very high sex selection use, presumably because this group knows that the
+next child will be a boy.
+
+% fertility
+Fertility has declined for all groups, but the likelihood of having an additional child
+still depends strongly on the number of sons, with women with no sons having the highest 
+probabilities.
+
+That those women most likely to use sex selection are also the most likely to have a
+next birth, combined with the secular increases in spacing, makes the total fertility 
+rate a more biased measure of cohort fertility.
+This bias was most prominent early in the spread of sex selection, where the fertility
+rate was up to one child lower than the predicted cohort fertility, but is still
+present with the predicted cohort fertility ten to twenty percent higher than 
+the fertility rate.
+
+Tempo effects are studied extensively in the literature,%
+\footnote{
+See, for example, \citet{Bongaarts1999}.
+}
+but there are, however, to my knowledge, no other cases where there has been as 
+substantial an increase in birth intervals and associated bias in fertility rates 
+as for India.
+It is, therefore, conceivable that we might see increases in TFR as birth spacing 
+stabilizes or even declines again if interventions against sex selection are successful.
+
+The only group who have a predicted cohort fertility below replacement are the 
+best-educated urban women, with a predicted fertility of 1.8. 
+Note that the predicted cohort fertility estimates come with the caveats that they are
+based on married Hindu women and the model only includes births up to parity four.
+However, almost everybody marry and Hindu constitute 80 percent of the population,
+and since only the first fourth parities are used, it is possible that these 
+estimates are lower-bound, especially for the less educated women.
+
+% Mortality
+There has been a substantial reduction in infant mortality over time with the size of
+the reductions larger the less educated the mother.
+This convergence means that there is now little difference in mortality risk across
+education groups if the birth took place more than 21 months from the prior birth.
+Short birth spacing is still more dangerous for the child, with the least increase for
+the best-educated women.
+Despite the potential that extensive use of sex selection might negatively affect the 
+next child's survival, there is no evidence that children born to women who are the most
+likely to use sex selection have worse outcomes. 
+The rapid reduction in infant mortality risk, combined with the longer spacing,
+which further reduces mortality, and higher than previously realized fertility, 
+implies that population growth in India is, and will be, higher than expected.
+
+% Future research and policy
+
+The results here lead to two important questions that future research should address.
+
+First, how does the changing birth spacing affect prior children?
+We know that girls' health outcomes improve in the presence of sex selection 
+\citep{Lin2014,Hu2015}.
+An extensive use of sex selection implies is that only-girls families are much less 
+likely to have a very short birth interval, which may reduce sibling competition for 
+resources.
+Hence, better health outcomes for girls could be an unintended side-effect 
+of the longer spacing that arises from sex-selective abortions, rather than because the 
+smaller number of girls makes them more valued as is often assumed.
+A more positive reading would be that parents are more likely to view prior girls as
+wanted since they know that they will eventually have a son.
+In either case, an effective ban on sex selection could, at least temporarily, worsen
+health outcomes for girls.
+
+Second, is there an interaction between female labor force participation and 
+sex selection?
+Women may be staying out of the labor market exactly because the easier access to sex 
+selection means that they are now more likely to have a boy and because the expected 
+spacing between births has increased.
+The higher return to male offspring's human capital combined with access to sex
+selection may also explain another puzzle, why is the labor force participation so
+low when fertility is low and education has increased.
+As shown here, part of the answer may be that the number of children is, in fact, not as 
+low as previously thought, both because of the increased spacing and that more 
+children survive.
+
+Better job opportunities for women may be a direct way to affect sex selection for two 
+reasons.
+First, it makes it more expensive to be out of the labor market for long periods.
+Second, it would moderate the differential in potential earnings between husband and
+wife and make it more attractive to invest in female compared to male offspring's human 
+capital.
+This approach may, however, be a double-edged sword.
+If better job opportunities further lower desired fertility the result may be even
+higher use of sex selection, everything else equal.
+Hence, understanding the trade-off between long-term benefits from improvements in 
+women's labor force participation and short-term costs from potential increases in sex 
+selection is of paramount importance.
 

### 2020-02-10 paper/sex_selection_spacing-ver3.tex
Delete old conclusion

@@
 
-The central question addressed here is the extent to which spacing patterns significantly 
-changed as prenatal sex determination became available.
-The underlying idea is that in the absence of sex selection son preference leads to shorter 
-spacing after the birth of a girl than after the birth of a boy, whereas when prenatal sex 
-selection is available son preference increases the spacing after the birth of a girl 
-relative to after the birth of a boy.
-I apply an empirical method that simultaneously accounts for spacing between births 
-and the potential use of sex selection to four decades of data from India's NFHS.
-
-Three major, interrelated trends emerge.
-First, 
-the length of average birth intervals have increased for all education groups, and
-the increases are larger the higher the spell and the higher the education group.
-Second, fertility has declined for all groups with larger declines the more educated the 
-woman.
-Across all groups, the likelihood of having an additional child depends strongly on the 
-number of sons, with women with none or only one son having the highest probabilities.
-Finally, as shown by the increasing sex ratios for women with no or only one son, there
-has been a substantial increase in the use of sex selection.
-As for fertility and birth intervals, the increases are larger the higher the spell and
-with higher education.
-
-The results show two very different spacing patterns in response to son preference.
-At one extreme, rural women without education mostly follow the standard pattern of 
-shorter spacing in the absence of sons.
-The strength of this pattern does, however, depend critically on spell number.
-For the second spell, although the average interval after a first-born girl is shorter
-than after a first-born boy, the difference is small.
-The differences in spacing are larger for the third spell and largest for the fourth.
-For the fourth spell, the divergence in intervals has increased over time; the largest 
-increases are for women with two or three boys, but there has also been an increase for 
-women with only girls, likely because of an emerging use of sex selection.
-
-At the other extreme, urban women with eight or more years of education have experienced 
-an almost complete reversal of the traditional spacing patterns as the result of falling
-fertility and the associated extensive use of sex selection.
-Women with either no or one son now have substantially longer spacing than if they have 
-two or more sons.
-As shown by the increasingly significant deviations in the sex ratio from the natural sex 
-ratio, these changes are due to increased use of sex selection rather than a sudden
-reversal in son preference.
-Only the second spell has not seen a reversal despite a substantially increased use of
-sex selection, mainly because the average spacing with a first-born boy has increased 
-independently by more than nine months.
-
-The picture of how son preference affects spacing is, however, more complicated than 
-excepted.
-First, the differences in birth intervals for the first 50 percent of second births are 
-negligible across sex compositions, despite these births clearly within the 
-durations most likely to generate adverse outcomes.
-Hence, most of the divergence in spacing patterns arise from longer spells.
-Second, a side-effect of the extensive use of sex selection for third and fourth 
-spells is that only-girls families are much less likely to have a very short birth 
-interval, which may reduce the sibling competition for resources.
-
-The results here lead to three questions that future research should address.
-First, what is behind the substantial increases in spacing even for women unlikely to use 
-sex selection, and, related, why does spacing appear to increase with declining 
-parity progression probabilities?
-The distributional results suggest that most of the increases in average birth intervals 
-come from the upper end rather than from a general increase across the distribution.
-The longer average spacing and the relatively higher number of very long birth intervals 
-seem to run counter to a general reduction in the length of women's reproductive spans 
-found in earlier research \citep{Padmadas2004}.
-Understanding whether the longer average spacing is by choice, because of unplanned 
-pregnancies, or because of changes in economic circumstances that allow families to have 
-an additional child later has important implications for both policy design and outcomes 
-for mother and children.
-
-Second, to what extent are the improvements in health for girls relative to boys the result 
-of selection, the longer spacing between births, or changing son preference?
-We know that health outcomes for girls appear to improve in the presence of sex selection 
-\citep{Lin2014,Hu2015}.
-Furthermore, sample selection can make it appear that girls are healthier, even though the 
-underlying cause is a combination of sex selection and higher mortality together with 
-recall error \citep{Portner2018a}. 
-Understanding what role these factors play in better health for girls is especially 
-important when evaluating policies that aim to directly limit the use of sex selection 
-rather than changing preferences or incentives.
-If the better health outcomes for girls are, for example, an unintended side-effect of the 
-longer spacing that arises from sex-selective abortions, rather than because the smaller 
-number of girls makes them more valued as is often assumed, then an effective ban on sex 
-selection may, at least temporarily, worsen health outcomes for girls.
-
-Finally, we need to understand how female labor force participation interacts with the use 
-of sex selection.
-Increased autonomy for women, arising, for example, from better opportunities for working 
-outside the home, has been suggested as a way to increase women's status and thereby lower 
-the use of sex selection \citep{Das-Gupta2016}.
-This approach may, however, be a double-edged sword.
-On the one hand, it is a clear benefit to the women who gain bargaining power, and it 
-increases the cost of repeated sex-selective abortions because the increased duration 
-between births would cause a stronger disruption in labor market participation.
-On the other hand, it may further lower desired fertility, which, everything else equal, 
-may lead to higher use of sex selection.
-Understanding the trade-off between long-term benefits from improvements in women's labor 
-force participation and short-term costs from potential increases in sex selection is of 
-paramount importance.
-
 \clearpage

### 2020-02-12 paper/sex_selection_spacing-ver3.tex
Version close to submit worthy
Just over 8,000 words.

@@
 
-\usepackage{endfloat}
+% For word counting uncomment line below and raggedright below
+\usepackage[nolists]{endfloat}
 
@@
 
-\date{January 2019}
+\date{February 2020}
 
@@
 \noindent 
+Using four rounds of India's National Family and Health Surveys and a
+competing-risk hazard model, I show that average birth intervals
+increased over the last four decades for all education groups. The most
+significant increases are among the women most likely to use sex
+selection. Despite the rise in average intervals, the likelihood of very
+short spacing did not change substantially. Hence, the increases come
+predominantly from the longer birth intervals getting even longer. As a
+result of the longer spacing, fertility rates significantly
+overestimated how fast cohort fertility fell. Although cohort fertility
+and the fertility rate have started to converge, the cohort fertility is
+still substantially higher than the fertility rate. Furthermore, cohort
+fertility is still at or above replacement level for all but the
+best-educated urban women. Finally, infant mortality risk has declined
+substantially over time for all groups, but fastest for the lower
+education groups, who are now close to the level of women with the most
+education. Short birth spacing is still associated with higher
+mortality, although the difference is small for the best-educated women.
+There is no evidence that the increasing use of sex selection is
+associated with higher infant mortality risk.
 
@@
 \section{Introduction\label{sec:intro}}
+
+% For word counting remove comment on the line below
+\raggedright
 
@@
 
-Understanding how birth spacing changes is of interest for two main reasons, in 
-addition to a better general understanding how fertility decisions are made.
+There are two primary motivations for examining birth spacing in this
+situation, besides gaining a better general understanding of how
+families make fertility decisions.
 
@@
 \emph{and} 
-the likelihood of a son, 
+the likelihood of a son 
 but also works in cases without prenatal sex selection.
 The empirical model allows me to predict fertility behavior taking into
-account both the likelihood of parity progression and having a child of a specific sex.
+account both the likelihood of parity progression and the likelihood of having a child of 
+a specific sex.
 
 % [Hypotheses / questions]
-There are four main set of results.
+There are four main sets of results.
 
 First, birth intervals have increased for all education groups over the four decades, 
-with larger increases, the higher the parity and the higher the education level.
+the more so, the higher the parity and the higher the education level.
 Women who are most likely to use sex selection---well-educated women with no
-sons---have seen the most substantial increases in birth intervals.
-[TK check this] As a result, well-educated women now show a reversal of the traditional spacing 
-pattern, with the longest intervals for women with no sons.
+sons---have seen the most substantial increases in birth intervals and the most 
+biased sex ratios.
+As a result, we now see cases that reverse the traditional spacing
+pattern, with women with no sons having longer birth intervals than
+women with sons.
 Those least likely to use sex selection, women with less education in rural areas, 
@@
 little evidence of the use of sex selection.
-[TK add sex ratios and parity progression discussions]
+Women with no sons still are the most likely to have an additional birth.
+Although the probability of having a next child has declined for this group over time, the 
+declines are often substantially smaller than if a boy is present.
 
@@
 Hence, the increases in average spacing come predominantly from the longer birth intervals
-getting even longer over time, driven to a large degree by a substantial use of sex 
+getting even longer over time, driven in no small degree by substantial use of sex 
 selection.
-The exception to this result is that the better-educated women with \emph{very high} 
-predicted use of sex selection appear to conceive later exactly because the next child is 
-almost certainly a boy.
+The exception to this result is that the better-educated women with a \emph{very high} 
+predicted use of sex selection appear to conceive later precisely because the next child 
+is almost certainly a boy.
 
 Third, the fertility rate substantially overestimated how fast cohort fertility fell 
-in the 1990s and early 2000s, when spacing began to increase as the result of secular 
-changes and increasing use of sex selection.
-Although predicted cohort fertility and the fertility rate has lately begun to converge,
+in the 1990s and early 2000s when spacing began to increase.
+Although predicted cohort fertility and the fertility rate have lately begun to converge,
 the predicted cohort fertility is still ten to twenty percent higher than the
@@
 
-Finally, infant mortality risk has decline substantially over time for all groups,
+Finally, infant mortality risk has declined substantially over time for all groups,
 but fastest for the lower education groups, who are now close to the level of women with 
 the most education.
-Mortality risk is, however, still inversely related to education level, especially for 
+The mortality risk is, however, still inversely related to education level, especially for 
 very short birth intervals.
@@
 and the older they are.
-For married women there is relatively little change in the percentage currently working 
-over time,
-but all education and age groups have become substantially more likely to work for
+For married women, the percentage currently working changes relatively little over time. 
+All education and age groups have, however, become substantially more likely to work for 
 a family member.
@@
 market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
-The low and declining female labor force participation is a first indication that this
+The low and declining female labor force participation is an indication that this
 process still operates.
@@
 
-To understand the potential implications for birth spacing of the substantial changes in 
-income, female education, and female labor force participation that India has experienced, 
-this section discuss relevant theories and prior findings on birth spacing.
-
-The standard economic argument for why increasing female education has predominantly
-been associated with shorter spacing is that parents incur time costs when they have 
-children \citep{Hotz1997,schultz97}.
+To provide a conceptual framework for understanding how birth spacing
+may respond to the substantial changes in income, female education, and
+female labor force participation that India has experienced, I discuss
+in this section relevant theories and prior findings on birth spacing.
+
+The standard economic argument for the predominant association between
+increasing female education and shorter spacing is that parents incur
+time costs when they have children \citep{Hotz1997,schultz97}.
 Specifically, if having children require the mother to reduce her market work, parents 
@@
 together for economic reasons.
-This may happen if household income has increased so substantially that the income effect 
-dominates any substitution effect.
+One explanation is that household income has increased so substantially that the income 
+effect dominates any substitution effect.
 Two findings speak for this effect.
@@
 \citep{Klasen2015,Bhargava2018}.
-Second, women’s labor supply appear to be more negatively elastic to their husbands' 
-wages than it is positively elastic to own wages \citep{Bhargava2018}.
+Second, women’s labor supply appears to be more negatively elastic to their husbands' 
+wages than it is positively elastic to their wages \citep{Bhargava2018}.
 
@@
 \citep{Behrman1999}.
-If more and ``better'' parental attention per child results in higher child ``quality'' 
+If more and ``better'' parental attention per child results in higher child ``quality,'' 
 we should expect longer birth intervals 
@@
 
-The introduction of sex selection allows parents to avoid the birth of girls,
+The introduction of sex selection allows parents to avoid the birth of girls
 but increases the expected duration to the next birth.
@@
 \citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Better-educated women also tend to live in households with higher income, which better 
-enables them to access prenatal sex determination and lowers the relative costs of using 
-sex selection and have long birth intervals.
+Better-educated and urban women also tend to live in households with higher income, which 
+better enables them to access prenatal sex determination and lowers the relative costs of 
+using sex selection and have long birth intervals.
 
 We may even observe a ``delay'' effect, where parents conceive later because they know 
-that short spacing is detrimental to the next child's health, and that the next child is 
+that short spacing is detrimental to the next child's health and that the next child is 
 more likely to be a boy because of access to sex selection.
@@
 As desired fertility decreases with increasing education, I, furthermore, expect 
-birth spacing to increase the most among the better-educated because of the larger
-increase in household income income---even with declining female labor participation---and 
+birth spacing to increase the most among the better-educated because their household
+income increases the most---even with declining female labor participation---and 
 their use of sex selection.
-Even with the large increase in the number of better-educated women, "Sanskritization" 
-imply that the changing composition does not substantially change this group's use of 
-sex selection.
+Even with the substantial increase in the number of better-educated women, 
+"Sanskritization" implies that the changing composition does not substantially change 
+this group's use of sex selection.
 
@@
 There are two problems with the standard approach in this setting.
+
 First, and most importantly, the introduction of sex selection means that the sex of the 
@@
 characteristics, such as the sex composition of previous births, have the same effects 
-throughout the entire spell as is assumed by the proportional hazard model.
+throughout the entire spell, as is assumed by the proportional hazard model.
 The proportionality assumption is especially problematic for higher-order spells where 
@@
 
-The introduction of prenatal sex determination exacerbates any bias from the 
-proportionality assumption since sex-selective abortion use varies across groups,
-which affects birth spacing, and because a household's use of sex selection may vary 
-within a spell, which means that the effects of covariates vary within the spell as well.
+The introduction of prenatal sex determination exacerbates any bias from
+the proportionality assumption for two reasons. 
+First, sex-selective abortion use varies across groups, which affects birth spacing. 
+Second,
+a household's use of sex selection may vary within a spell, which means
+that the effects of covariates vary within the spell as well.
 
@@
 
-The model is a discrete time, non-proportional, competing risk hazard model with two exit 
+The model is a discrete-time, non-proportional, competing risk hazard model with two exit 
 states: either a boy or a girl is born.
@@
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
-the spell continues until time $t_i$, when either a birth occurs or the spell 
-is censored.%
+the spell continues until time $t_i$ when either birth or censoring of the spell 
+occurs.%
 \footnote{
@@
 $J_i$ is a random variable indicating which event took place.
-The discrete time hazard rate $h_{ijt}$ is 
+The discrete-time hazard rate $h_{ijt}$ is 
 \begin{equation}
@@
 with $D_m = 1$ if $t=m$ and zero otherwise.
-This approach to modeling the baseline hazard is flexible and does not place 
-overly strong restrictions on the baseline hazard.
+This approach to modeling the baseline hazard is flexible and does not restrict the 
+baseline hazard unnecessarily.
 
 The explanatory variables in $\mathbf{Z}$, and the interactions between them, 
-constitute the non-proportional part of the model, which means that they are
-interacted with the baseline hazard:
+constitute the non-proportional part of the model:
 \begin{equation}
- \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
+ \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2).
 \end{equation}
-where $D_j(t)$ is the piece-wise linear baseline hazard, $\mathbf{Z}_1$ captures sex 
-composition of previous children, if any, and $Z_2$ captures area of residence.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
-but to further minimize any potential bias from assuming proportionality, estimations 
+$D_j(t)$ is the piece-wise linear baseline hazard, $\mathbf{Z}_1$ captures sex 
+composition of previous children, and $Z_2$ captures the area of residence.
+The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
+However, to further minimize any potential bias from assuming proportionality, estimations 
 are done separately for different levels of mothers' education and different 
@@
 Hence, transforming the data, so each observation is an interval---here equal
-to three months---the model can be estimated using a standard multinomial logit model.
+to three months---I can estimate the model using a standard multinomial logit model.
 %
@@
 
-Interpretation of the model coefficients is challenging \citep{thomas96}.
+The interpretation of the model coefficients is challenging \citep{thomas96}.
 It is, however, possible to calculate the predicted probabilities of 
@@
 \end{equation}
-Combining the percentage boys and the likelihood of exiting the spell 
-across all $t$ gives the predicted percent boys born over the entire spell.
+Combining the percentage of boys and the likelihood of exiting the spell 
+across all $t$ gives the predicted percent of births that are boys over the entire spell.
 
@@
 The data come from the four rounds of the National Family Health Survey
-collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.%
-\footnote{
-A delay in the survey for Tripura means that NFHS-2 has some observation 
-collected in 2000.
-}
-The surveys are large: NFHS-1 covered 89,777 ever-married women 
-aged 13--49 from 88,562 households;
-NFHS-2 covered 90,303 ever-married women aged 15--49 from 92,486 households;
-NFHS-3 covered 124,385 never-married and ever-married women aged 
-15--49 from 109,041 households;
-and 
-NFHS-4 covered 699,686 never-married and ever-married women aged
-15--49 from 601,509 households surveyed.
-
-I exclude visitors to the household, as well as women who fall into any of the following 
+collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.
+The surveys are large: 89,777, 90,303, 124,385, and 699,686 women,
+respectively. NFHS-1 and NFHS-2 surveyed only ever-married women, while
+the later surveys also included never-married.
+
+I exclude visitors, as well as women in any of the following 
 categories: never married; no gauna yet; married more than once; divorced; 
 not living with husband; inconsistent age at marriage; or education information missing.  
-The same goes for women who had at least one multiple births, reported having a birth 
+The same goes for women who had at least one multiple births, reported giving birth 
 before age 12, had a birth before marriage, or an interval between births of less than 
 nine months. 
-Finally, I restrict the sample to Hindus, who constitute about 80\% of India’s population.%
+Finally, I restrict the sample to Hindus, who constitute about 80 percent of India’s 
+population.%
 \footnote{
-If the use of sex selection differ between Hindu and other groups assuming
-that the baseline hazard is the same would lead to bias. The other
-groups are each so small that it is not possible to estimate different
-baseline hazards for each group, and are so different that combining
-them into one group would not make sense.
-}
-
-In addition to the large number of women surveyed and the long period covered, a
-benefit of the NFHS is that surveys enumerators pay careful attention to spacing between 
-births and probe for ``missed'' births.
+If the use of sex selection differs across groups, assuming that the
+baseline hazard is the same leads to bias. 
+Furthermore, the other groups are each too small to estimate different
+baseline hazards for each and so different that combining them into one
+group would not make sense.
+}
+
+In addition to a large number of women surveyed and the long period covered, a
+benefit of the NFHS is that enumerators pay careful attention to the spacing 
+between births and probe for ``missed'' births.
 Nevertheless, systematic recall error, where the likelihood of reporting a deceased 
-child depends on the sex of the child, is still a potentially substantial problem and
-will bias both spacing and sex ratios.
-As I show in the online Appendix, recall error is heavily dependent on how long ago a 
-woman was married, and I, therefore, drop women married 22 years or more.
+child depends on the sex of the child, remains a potential problem.
+Recall error is heavily dependent on how long ago a woman was married, and I, therefore, 
+drop women married 22 years or more.%
+\footnote{
+See the discussion in the Appendix.
+}
 The final sample consists of 
@@
 
+I focus on the second through fourth spells, that is, on the intervals from the first 
+birth until at most the fourth birth.
+I exclude the marriage to the first birth spell because many are imputed.
+
+The spells all begin nine months after the previous birth, which is the earliest we should 
+expect to observe a new birth.
+A spell continues until either a child is born or censoring occurs.
+Censoring can happen for three reasons:
+the survey takes place,
+sterilization of the woman or her husband,
+or too few births are observed for the method to work.
+For all spells, censoring is set at 96 months (eight years) after a woman can first
+give birth in the spell.
+With these cut-offs, less than one percent of observed births occur after
+the spell cut-off.
+
+% %
+% \footnote{
+% \input{../tables/num_missed.tex}
+% }
+
 Direct information on the use of sex selection is not available, so I compare different 
-periods as a proxy, based on the changes in access and legality of prenatal sex 
+periods, based on the changes in access and legality of prenatal sex 
 determination in India.
@@
 }
-Although the use of sex selection increased even after 1994, some researchers argue that 
-we have passed a turning point in its use \citep{Das_Gupta2009,Diamond-Smith2015}.
+Although the use of sex selection increased even after 1994, we may have passed a 
+turning point in its use \citep{Das_Gupta2009,Diamond-Smith2015}.
 I, therefore, use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The allocation of spells into periods is determined by when conception, and therefore 
+The allocation of spells into periods is determined by when conception, and, therefore, 
 decisions on sex selection, can begin. 
-This allocation mechanism means that some spells cover two periods, which may bias 
-downward the differences between the periods.
-
-I focus here on the second through fourth spells, that is, on the intervals from the first 
-birth until at most the fourth birth.
-I exclude the spell from marriage to the first birth because of data issues.
-In NFHS-1 and NFHS-2 the only information on marriage is the age at marriage, and 
-all first spell durations are therefore imputed.
-In NFHS-3 about a third of respondent did not provide complete information on the
-timing of marriage and had the length of their first spell imputed using the age at 
-marriage.
-The imputation results in large numbers of women with spells that are less than nine 
-months and makes a comparison of spell duration over time subject to an 
-excessive amount of noise.
-
-The spells all begin nine months after the previous birth, which is the earliest we should 
-expect to observe a new birth.
-A spell continues until either a child is born or censoring occurs.
-Censoring can happen for three reasons:
-the survey takes place;
-sterilization of the woman or her husband;
-or too few births are observed for the method to work.
-For all spells censoring is set at 96 months (eight years) after a birth can occur.
-With these cut-offs, less than one percent of observed births occur after
-the spell cut-off.
-
-% %
-% \footnote{
-% \input{../tables/num_missed.tex}
-% }
+Hence, some spells cover two periods, which may bias downward the differences between the 
+periods.
 
@@
 The first group consists of characteristics that the prior literature finds affect 
-spacing choice and the use of sex selection:
+the spacing choice and the use of sex selection:
 mother's education, sex composition of previous children, and area of residence.
@@
 proportional effect on the hazard.
-These include the age of the mother at the beginning of the spell, whether the household 
-owns any land, and whether the household belongs to a scheduled tribe or caste.
+These include the mother's age when the spell begins, the household's
+land ownership, and whether the household belongs to a scheduled tribe
+or caste.
 
@@
 \citep{Whitworth2002,Bhalotra2008,Kim2010}.
-Furthermore, as discussed above, the use of sex selection increases with education, 
-either because of the associated lower fertility or because higher income enables them 
-to access and afford prenatal sex determination
-I divide women into four groups based on education attainment: no
+Furthermore, as discussed above, the use of sex selection increases with education.
+I, therefore, divide women into four educationgroups: no
 education, one to seven years of education, eight to eleven years of education,
 and twelve and more years of education.
-The models are estimated separately for each education level to reduce the potential 
-problem of including other variables as proportional.
-
-The sex composition of previous children affects both the timing of births and the use of 
-sex-selective abortions 
-\citep{retherford03b,Bhalotra2008,Portner2015b,Soest2018}.
+The models are estimated separately for each group to reduce any
+potential problem from including other variables as proportional.
+
 I capture sex composition with dummy variables for the
-possible combinations for the specific spell, ignoring the ordering of births.
-Finally, urban women have both lower fertility and, presumably, better access to
-sex selection, both of which lead to higher use of sex-selective abortions than in 
-rural areas \citep{retherford03b,Portner2015b}.
-Area of residence is a dummy variable for the household living in an urban area.
+possible combinations, ignoring the ordering of births.
+Area of residence is a dummy variable for living in an urban area.
 
@@
 Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} presents descriptive 
-statistics for the spells by education level and period.
+statistics.
 The level of censoring increases with parity and time, as we should expect with later 
@@
 
-The predicted parity progression probability is the likelihood of a birth by 96 months 
-after the beginning of the spell.
-To find the expected average duration I first calculate, for each woman, the probability 
+The predicted parity progression probability is the likelihood of giving birth by 96 
+months after the beginning of the spell.
+To find the expected average duration, I first calculate, for each woman, the probability 
 of giving birth in each period $t$, which I use as weights to calculated her expected 
@@
 
-The predicted sex ratio captures the percent boys to women in the sample when 
-childbearing for that spell is over.
+The predicted sex ratio captures the percent of births that are boys for women in 
+the sample when childbearing for that spell is over.
 A woman's predicted sex ratio is the weighted average of the predicted percentage boys 
@@
 \footnote{
-If T=2 with the estimated percent boys 54\% and 66\% and the likelihoods of giving 
-birth 20\% and 40\%, the percent boys is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$.
+With T=2, if 54 and 66 percent of the births are boys and the likelihoods of 
+giving birth 20 and 40 percent, then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent of the
+births are boys.
 }
@@
 ratios, using the parity progression probabilities as weights.
-For comparison, the graphs also show the natural sex ratio, approximately 51.2\% 
+For comparison, the graphs also show the natural sex ratio, approximately 51.2 percent 
 \citep{ben-porath76b,jacobsen99,Portner2015b}.
@@
 
-Average birth intervals have increased over time across all groups, and are, for a given 
-parity, longer the more education a woman.
-The increases in birth spacing are larger the higher the parity
-and, within parities, the higher the education.
-
-In the latest period, the lowest average birth interval is for women with no 
-education in the second spell at just shy of 25 months, which is an increase of a
-couple of months from the first period.
+Average birth intervals have increased over time across all groups, but
+the higher the parity and the higher the schooling, the larger the
+increases.
+
+In the latest period, the shortest average birth interval is 25 months for
+women with no education in the second spell, an increase of a couple of
+months from the first period.
 The longest average interval was 42 months for the third spell for women with twelve or 
@@
 the sex composition of prior children and the parity.
-As expected with a strong son preference, women with no sons still are the most likely to 
-have a next birth, and this group has seen often substantially smaller declines in
+Women with no sons still are the most likely to 
+have the next birth, and this group has seen often substantially smaller declines in
 the likelihood of having another birth than women with one or more sons.%
 \footnote{
-There is, however, also some evidence that parents prefer a mixed sex composition: for 
+There is, however, also some evidence that parents prefer a mix of boys and girls: for 
 the fourth spell women with two boys \emph{and} a girl
@@
 girl, but 15 percentage points if it was a boy.
-Even more extreme is the fourth spell where the likelihood of a birth declined by six 
+Even more extreme is the fourth spell, where the likelihood of a birth declined by six 
 percentage points to 75 percent if the woman had three children, but by almost 40 
@@
 the shortest spacing, as shown, for example, by rural women with no education.
-For this group spacing is shortest with only girls across all spell, and the difference
-between sex compositions have even widen over time.
-
-Second, even with sex selection, and the associated increases in expected spacing, the
-intervals for the other sex compositions have increased even more and the relatively 
+For this group, spacing is shortest with only girls across all spell, and the difference
+between sex compositions have even grown over time.
+
+Second, even with sex selection and the associated increases in expected spacing, the
+intervals for the other sex compositions have increased even more, and the relative 
 pattern, therefore, remains more or less the same.
-This is the case, for example, for the second spell for women with eight to eleven
+An example is for the second spell for women with eight to eleven
 and twelve or more years of education.
 
-Finally, women with the most unequal sex ratios show the longest spacing in the 
+Finally, women with the most biased sex ratios have the longest spacing in the 
 absence of boys, and this spacing is longer than for the other possible sex 
@@
 longer than with at least one boy.
-Even urban women with eight to eleven years of education show the longest intervals with 
-only girls in the last period.
-
-\subsection{Distribution of Birth Spacing}
+However, even urban women with eight to eleven years of education show the longest 
+intervals with only girls in the last period.
+
+\section{Distribution of Birth Spacing}
 
@@
 spacing will come from people who have two or more pregnancies rather than one and,
-therefore, from changes in the longer intervals,
-while a general increase in spacing would show up as an increase in spacing across the 
-board.
+therefore, from changes in the longer intervals.
+In contrast, a general increase in spacing would show up as an increase in spacing across 
+the board.
 
 Figures \ref{fig:combined_p25_p75_urban} and \ref{fig:combined_p25_p75_rural} 
-show how the predicted 25th and 75th percentile birth intervals has changed over time 
+show how the predicted 25th and 75th percentile birth intervals have changed over time 
 by spell and education.
@@
 \footnote{
-The Appendix shows conditional survival curves for all groups and 
+The Appendix shows conditional survival curves for all groups, and 
 Appendix Tables \ref{tab:p25_p50_p75_low} through \ref{tab:p25_p50_p75_highest} 
@@
 
-For both women with no education and those with one to seven years of education,
-almost all of the increases in the average spacing discussed above come from increases in 
-the long end of the spacing distribution rather than from a general increase.
+For women with no or little education, the increases in average spacing
+come predominantly from increases in the long end of the spacing
+distribution rather than from a general increase.
 Hence, spacing is still very short for many women, with 25 percent or more having
@@
 Furthermore, the increases in the 75th percentile birth intervals are relatively small
-for the second spell and slightly larger for the third spell at around five months.
+for the second spell and slightly more substantial for the third spell at around five months.
 Most of the divergence across sex compositions happen for the fourth spell, where 
-the largest increases are for women with two or three sons.
-However, even for women with no or one son there has been increases in the birth intervals 
-of a half to a full year consistent with some use of sex selection for this group.
+the most significant increases are for women with two or three sons.
+However, even for women with no or one son, the birth intervals have
+increased by a half to a full year, consistent with some use of sex
+selection.
 
@@
 around two years since the prior birth.
-The result is that most of the change in average spacing is driven by increases in the
-longer spacing end of the distribution.
+Hence, the increases in the longer end of the distribution drive
+the change in average spacing.
 For example, the 75th percentile spacing length for women with two girls in the third 
@@
 
-The most educated urban women show an interesting pattern for the third spell, where there 
-is essentially no change in either the 25th or 75th percentile birth intervals in the
+The most educated urban women show an unusual pattern for the third spell, where there 
+is virtually no change in either the 25th or 75th percentile birth intervals in the
 presence of at least one boy.
 The 75th percentile birth interval, however, increases by more than 20 months,
-corresponding to the massive increase in the sex ratio to almost 80 precent in the 
+corresponding to the massive increase in the sex ratio to almost 80 percent in the 
 latest period.
-Hence, the increases in birth spacing and the reversal in spacing pattern by sex
-composition over time is mainly driven by increases in the length of the longer intervals, 
-consistent with a substantial use of sex selection.
+Hence, the increases in the length of the longer intervals over time are
+the main reason for the increases in average birth spacing and the
+reversal in the spacing pattern by sex composition, consistent with
+substantial use of sex selection.
 
@@
 evidence for the ``delay'' effect discussed above, where parents conceive later
-exactly because they know that the next child is likely to be a boy since they plan
+precisely because they know that the next child is likely to be a boy since they plan
 to use sex selection.
 The best example is for the best-educated urban women in the third spell, where, in the 
-last two periods, the spacing to the third child is significant longer if the two prior 
+last two periods, the spacing to the third child is significantly longer if the two prior 
 children were girls than if they already had one or two boys.
@@
 I, therefore, compare predicted fertility based on a variation of the TFR and the 
-hazard model by urban/rural and education group in Table \ref{tab:fertility}.
+hazard model by urban/rural and education groups in Table \ref{tab:fertility}.
 
@@
 parity four, and is, therefore, not directly comparable to those in the NFHS reports.
-Otherwise, I follow the procedure used in the NFHS reports and calculate age specific 
-fertility rates for five-year age groups using the number of births in months 1 to 36 
-before the survey month (births in the survey month are not included) and the number
-of women in each age group.%
-\footnote{
-See \citet{Croft2018} for more detail.
+Otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
+I calculate age-specific fertility rates for five-year age groups using the number of 
+births in months 1 to 36 before the survey month and the number of women in each age 
+group.
+
+%
+% \footnote{
+% See \citet{Croft2018} for more detail.
 % Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
@@
 % not presented \citep{Hoem2011,Laplante2015}.
-}
-
-Because NFHS-1 was collected after the introduction of sex selection it is not possible 
-to calculate a fertility rate in exactly the same manner for a period 
+% }
+
+Because NFHS-1 was after the introduction of sex selection, it is not possible 
+to calculate a fertility rate in precisely the same manner for a period 
 before sex selection was widely available.
-Instead, I calculate the fertility rates for women who was between 15 and 39 years of
-age five years prior to the survey month, again using the number of births three years 
-before that.
+Instead, I calculate the fertility rates for women who were between 15 and 39 years of
+age five years before the survey month, again using the number of births three years 
+before that, shown as ``1987--88''.
 Given the relatively low number of births to women 40 to 45 years of age, this approach 
@@
 not widespread.
-This fertility rate is shown as ``1987--88''.
 
@@
 
-I include the spell from marriage to first birth, despite the problems capturing the 
-exact timing of marriages for the first two rounds of the survey, since
-the estimated progression probabilities should not be affected by this problem.
+I include the spell from marriage to first birth, despite the problems
+capturing the exact timing of marriages since the estimated progression
+probabilities should not be affected by this problem.
 To ensure that the predictions depend solely on sample composition and the estimate, I
@@
 each parity, assuming three years increases in age between each parity.
-Shorter assumed duration between parities leads to slightly higher predicted 
+Shorter assumed duration between births leads to slightly higher predicted 
 fertility.
 
-The survey rounds do not coincide directly with the periods I use for the hazard model.
-For the NFHS-4, I use the model results for the 2005--2016 period, 
-for NFHS-3 the 1995--2004 period, 
-for NFHS-2 the 1985--1994 period, 
-and for NFHS-1 the 1972--1984 period.
+The survey rounds do not coincide directly with the periods used for the hazard model.
+I, therefore, use the model results for 1972--1984, 1985--1994, 1995--2004,
+and 2005--2016 for rounds 1 through 4 of the NFHS, respectively.
 Because of the small number of women who had the highest level of education in the
-1972--1984 period, I do not present a predicted fertility for this case.
-
-In almost all cases the predicted cohort fertility based on the hazard model is higher 
-than the four-parity fertility rate.
-Only for women with no education in the first period are there almost no difference 
-between the two fertility measures; a situation where fertility is high and spacing
-very short and likely unchanged over a long period before.
-
-Consistent with a larger bias in the fertility rate when age of marriage and the length of 
-birth intervals are increasing, the absolute bias is least in the first and the last 
+1972--1984 period, I do not predict fertility for this case.
+
+The predicted cohort fertility based on the hazard model is higher than the four-parity 
+fertility rate in almost all cases.
+Only for women with no education in the first period is there almost no difference 
+between the two fertility measures; a situation where fertility is high, spacing
+very short and likely unchanged for an extended period before.
+
+Consistent with a more substantial bias in the fertility rate when the age of marriage 
+and the length of birth intervals are increasing, the absolute bias is least in the first and the last 
 period and highest in the middle two periods.
-Hence, the fertility rate declined too fast between the mid-1980s and the end of the 
-century, and only recently, as the rate of increase for the birth intervals have slowed, 
-are the predicted cohort fertility and the fertility beginning to converge again.
+Hence, the fertility rate declined too fast from the mid-1980s to the century's end.
+Only recently, as the rate of increase for the birth intervals have
+slowed, are the predicted cohort fertility and the fertility beginning
+to converge again.
 Even with the convergence, however, the predicted cohort fertility for 2005--16 is 
 above the 1992--93 fertility rate for every group except urban women with no education.
-Furthermore, for the last period, the predicted cohort fertility is stil between ten
+Furthermore, for the last period, the predicted cohort fertility is still between ten
 and 20 percent higher than the fertility rate.
 
-The bias in the fertility rate is also evident in the fact that the fertility rate is 
-increasing over time for some groups.
+Another indication of the fertility rate bias is that it is increasing over time for some 
+groups.
 For example, urban women with eight to eleven years of education showed 1.84, 1.81, and
-1.87 over the last three surveys, and for rural women with one to seven years of
-education fertility rate goes from 2.25 for NFHS-3 to 2.37 for NFHS-4.
-These increases are likely the result of a stabilization of the age of first birth and
-the spacing between births.%
+1.87 over the last three surveys.
+These increases likely arise from the stabilization of the age of first birth and the 
+spacing between births.%
 \footnote{
-Increases in TFR over time, even in the face of declining cohort fertility is not 
+Increases in TFR over time, even in the face of declining cohort fertility, are not 
 unusual, as shown by Columbia in the early 1990s \citep{Bongaarts1999}.
@@
 
-Despite the declines in the predicted cohort fertility it is still mostly above the 
+Despite the declines in the predicted cohort fertility, it is still mostly above the 
 generally accepted replacement level of 2.1.
 Only for urban women with twelve or more years of education is the predicted cohort
-fertility below 2.1, and even then it is still more than 0.3 children higher than the 
+fertility below 2.1, and even then, it is still more than 0.3 children higher than the 
 fertility rate estimate of 1.5.
-Furthermore, because only the first four births are used, the predicted cohort fertility
-numbers are likely too low, especially for the lower education groups.
+Furthermore, the predicted cohort fertility numbers are likely too low,
+especially for the lower education groups, since it relies only on the
+first four births.
 
@@
 
-The prior literature show that shorter birth spacing, especially very short spacing,
-is associated with higher risk of infant mortality.
+The prior literature shows that shorter birth spacing, especially very short spacing,
+is associated with a higher risk of infant mortality.
 Hence, the longer spacing, both from the increasing use of sex-selective abortions and
 from secular changes, may directly reduce infant mortality.
-To the extent that the longer birth intervals arise from multiple abortions
+To the extent that the longer birth intervals arise from multiple abortions,
 the short duration between \emph{pregnancies} could, however, increase mortality risk.
 This section addresses how infant mortality has changed and whether there is evidence
-of a negative impact of sex selective abortions.
+of a negative impact of sex-selective abortions.
 
@@
 months of life.
-The main set of explanatory variable consists of dummies for birth spacing
+The main set of explanatory variables consists of dummies for birth spacing
 covering 12 months intervals, starting from nine months after the prior birth 
 as above, until 48 months, which includes all births until 96 months.
-In addition, I use dummies for sex of the index child and the sex composition 
+I use dummies for sex of the index child and the sex composition 
 of the prior children.
@@
 are all interacted.
-Since the actual number of abortions are unobserved, the interactions between
-sex composition of prior children and the sex of the index child serve
+Since the actual number of abortions is unobserved, the interactions between
+the sex composition of prior children and the sex of the index child serve
 as proxies for the use of sex selection.
-The other explanatory variables are the same as above and estimations
+The other explanatory variables are the same as above, and estimations
 are done separately by education level and parity.
@@
 \footnote{
-The online Appendix show the corresponding graphs for the third child.
-}
-All other variables are set to their average values.
-To ease legibility all confidence intervals are suppressed.
+The online Appendix shows the corresponding graphs for the third child.
+}
+All other variables take their average values.
+The graphs do not show confidence intervals to ease their legibility.
 
@@
 For example, if women who have difficulties conceiving or carrying a pregnancy 
-to term also have higher mortality risk for their offspring, a spurious correlation 
+to term also have a higher mortality risk for their offspring, a spurious correlation 
 between long birth spacing and mortality may arise \citep{Kozuki2013}. 
@@
 as family fixed effects, do not work well when the number of births is
-low as it is for higher education women \citep{Kozuki2013,Molitoris2019}.
-However, in prior research the fixed effects results and linear probability do not 
+low as it is for better-educated women \citep{Kozuki2013,Molitoris2019}.
+However, in prior research, the fixed effects results and linear probability do not 
 deviate substantially.
@@
 There has been substantial convergence in mortality risk across groups over time.
-For the 12 months and above intervals, there is now little difference across 
+For intervals 12 months or longer, there is now little difference across 
 the education groups, with even the no education group showing an infant mortality risk 
@@
 effect declines with education level.
-For the best-educated women the mortality risk is three to four percent,
+For the best-educated women, the mortality risk is three to four percent,
 whereas women with no education still show a risk that is close to ten percent.
@@
 that girls have substantially higher mortality risk.
-There is some weak evidence that a boy born after a girl have lower mortality
-risks in the earliest periods.
+There is some weak evidence that a boy born after a girl has a lower mortality
+risk in the earliest periods.
 This difference disappears, however, with the general decline in mortality risk.
@@
 % line 3661 in an_infant_mortality.log
-The raw numbers for the group with the most uneven sex ratio---women with twelve or more
-years of education who have no boys in the third spell in the last period---indicates
-that even with high use of sex selection there is no impact on child mortality.
-A total of 1,004 women in this group had a third child, of which 685 are boys.
-Of these 685 boys, only 6 died within the first year of life and half of those
-were in born the 0--23 months interval, and none in 48 months or more interval.
+The raw numbers for the group with the most uneven sex ratio indicates
+that there is no impact on child mortality, even with high use of sex selection. 
+A total of 1,004 women with twelve or more years of
+education, who have no boys at the start of the third spell in the last
+period, had a third child, of which 685 were boys. 
+Of these 685 boys, only six died within the first year of life, and half of those were 
+born in the 0-23 months interval, and none in 48 months or more interval.
 
@@
 
-One effect of the major changes that India has experienced over the last four decades is
-that spacing between births have increased for everybody.
-The increases in spacing are larger the higher the parity and the higher the mother's 
-education and are larger in urban than in rural areas.
-
-The most substantial increases in birth intervals arise, however, with heavy use of sex 
-selection, as, for example, urban women with twelve or more years of education and two 
-girls.
-We, therefore, now in some cases observe a reversal of the traditional spacing
-pattern where strong son preference was associated with shorter birth intervals the fewer 
+One effect of the significant changes that India has experienced over the last four 
+decades is that spacing between births has increased.
+The size of the increase is increasing in parity and the mother's
+education and is larger in urban than in rural areas.
+
+The most substantial increases in birth intervals arise, however, with
+heavy use of sex selection. Some of these increases are so large that we
+even observe a reversal of the traditional spacing pattern where strong
+son preference was associated with shorter birth intervals, the fewer
 sons a family has \citep{ben-porath76b,Leung1988}.
-This reversal comes about because couples with a strong preference for sons now use sex 
-selection, not because son preference has changed over time.
-
-Despite the longer average birth intervals, a large number of women still have very
-short birth intervals.
-Hence, the changes in birth spacing is driven by the longer intervals becoming longer
-over time, both for women who do not use sex selection, but especially for those who
-do and end up with multiple abortions.
-The exception to the small change in short spacing is the delay in conception for
-women with very high sex selection use, presumably because this group knows that the
-next child will be a boy.
+
+Despite the longer average birth intervals, a large number of women
+still have very short birth intervals. 
+Hence, the changes in birth
+spacing are driven by the longer intervals becoming even longer over
+time, both for women who do not use sex selection, but especially for
+those who do and end up with multiple abortions. 
+The exception to the
+small change in short spacing is the delay in conception for women with
+very high use of sex selection, presumably because this group knows that
+the next child will be a boy.
 
@@
 
-That those women most likely to use sex selection are also the most likely to have a
-next birth, combined with the secular increases in spacing, makes the total fertility 
-rate a more biased measure of cohort fertility.
-This bias was most prominent early in the spread of sex selection, where the fertility
-rate was up to one child lower than the predicted cohort fertility, but is still
-present with the predicted cohort fertility ten to twenty percent higher than 
-the fertility rate.
-
-Tempo effects are studied extensively in the literature,%
+That those women most likely to use sex selection are also the most
+likely to have a next birth, combined with the secular increases in
+spacing, makes the total fertility rate a more biased measure of cohort
+fertility. 
+This bias was most prominent early in the spread of sex
+selection when the fertility rate was up to one child lower than the
+predicted cohort fertility. 
+It is, however, still present with the
+predicted cohort fertility ten to twenty percent higher than the
+fertility rate.
+
+Tempo effects are studied extensively in the literature.%
 \footnote{
@@
 }
-but there are, however, to my knowledge, no other cases where there has been as 
+Still, there are, to my knowledge, no other cases where there has been as 
 substantial an increase in birth intervals and associated bias in fertility rates 
 as for India.
-It is, therefore, conceivable that we might see increases in TFR as birth spacing 
-stabilizes or even declines again if interventions against sex selection are successful.
-
-The only group who have a predicted cohort fertility below replacement are the 
-best-educated urban women, with a predicted fertility of 1.8. 
-Note that the predicted cohort fertility estimates come with the caveats that they are
-based on married Hindu women and the model only includes births up to parity four.
-However, almost everybody marry and Hindu constitute 80 percent of the population,
-and since only the first fourth parities are used, it is possible that these 
-estimates are lower-bound, especially for the less educated women.
+It is conceivable that we might see increases in TFR as birth spacing 
+stabilizes or even shortens again if interventions against sex selection are successful.
+
+The best-educated urban women are the only group for whom the predicted cohort fertility 
+is below replacement at 1.8. 
+A caveat to the predicted cohort fertility is that only Hindu women are
+in the sample and that the model only includes births up to parity four.
+However, almost everybody marries, and Hindu constitute 80 percent of the population.
+Furthermore, with only the first fourth births used, these estimates may
+be lower-bound, especially for the less educated women.
 
 % Mortality
-There has been a substantial reduction in infant mortality over time with the size of
-the reductions larger the less educated the mother.
-This convergence means that there is now little difference in mortality risk across
+There has been a substantial reduction in infant mortality over time, and 
+the size of the reductions is inversely related to the mother's education.
+Hence, there is now little difference in mortality risk across
 education groups if the birth took place more than 21 months from the prior birth.
-Short birth spacing is still more dangerous for the child, with the least increase for
-the best-educated women.
-Despite the potential that extensive use of sex selection might negatively affect the 
-next child's survival, there is no evidence that children born to women who are the most
-likely to use sex selection have worse outcomes. 
-The rapid reduction in infant mortality risk, combined with the longer spacing,
-which further reduces mortality, and higher than previously realized fertility, 
-implies that population growth in India is, and will be, higher than expected.
+Short birth spacing is still associated with higher mortality, although the difference is 
+small for the best-educated women.
+There is no evidence that children born to women who are the most likely to use sex 
+selection have higher mortality risk.
+
+An implication of the results here is that population growth in India
+will be higher than expected. There has been a rapid reduction in infant
+mortality risk, the longer spacing should further reduce mortality risk,
+and cohort fertility is higher than previously realized.
 
@@
 
-The results here lead to two important questions that future research should address.
-
-First, how does the changing birth spacing affect prior children?
-We know that girls' health outcomes improve in the presence of sex selection 
-\citep{Lin2014,Hu2015}.
-An extensive use of sex selection implies is that only-girls families are much less 
-likely to have a very short birth interval, which may reduce sibling competition for 
-resources.
-Hence, better health outcomes for girls could be an unintended side-effect 
-of the longer spacing that arises from sex-selective abortions, rather than because the 
-smaller number of girls makes them more valued as is often assumed.
-A more positive reading would be that parents are more likely to view prior girls as
-wanted since they know that they will eventually have a son.
-In either case, an effective ban on sex selection could, at least temporarily, worsen
-health outcomes for girls.
-
-Second, is there an interaction between female labor force participation and 
-sex selection?
-Women may be staying out of the labor market exactly because the easier access to sex 
-selection means that they are now more likely to have a boy and because the expected 
-spacing between births has increased.
-The higher return to male offspring's human capital combined with access to sex
-selection may also explain another puzzle, why is the labor force participation so
-low when fertility is low and education has increased.
-As shown here, part of the answer may be that the number of children is, in fact, not as 
-low as previously thought, both because of the increased spacing and that more 
-children survive.
-
-Better job opportunities for women may be a direct way to affect sex selection for two 
-reasons.
-First, it makes it more expensive to be out of the labor market for long periods.
-Second, it would moderate the differential in potential earnings between husband and
-wife and make it more attractive to invest in female compared to male offspring's human 
-capital.
-This approach may, however, be a double-edged sword.
-If better job opportunities further lower desired fertility the result may be even
-higher use of sex selection, everything else equal.
-Hence, understanding the trade-off between long-term benefits from improvements in 
-women's labor force participation and short-term costs from potential increases in sex 
-selection is of paramount importance.
+The results here lead to two critical questions that future research should address.
+Sex selection means that girls-only families are less likely to have
+very short birth intervals, which may reduce sibling competition. 
+Hence, better health outcomes for girls with sex selection could be an
+unintended side-effect, rather than a result of girls becoming more
+valued as is often assumed. 
+Comparing prior children's outcomes across
+sex composition and the sex of the next child could be a way to
+understand why girls' health outcomes improve in the presence of sex selection.
+
+Second, is there a relationship between female labor force participation
+and sex selection? Women may be staying out of the labor market
+precisely because sex selection makes them more likely to have a boy and
+increases the expected birth spacing. Better job opportunities for women
+would affect sex selection for two reasons. First, it makes it more
+expensive to be out of the labor market for long periods. Second, it
+would moderate the differential in potential earnings between husband
+and wife and make it more attractive to invest in female compared to
+male offspring's human capital. This approach could, however, be a
+double-edged sword. If better job opportunities further lower desired
+fertility, the use of sex selection may increase, everything else equal.
+Hence, understanding the trade-off between long-term benefits from
+improvements in women's labor force participation and short-term costs
+from potential increases in sex selection is of paramount importance.
+
+% The higher return to male offspring's human capital combined with access to sex
+% selection may also explain another puzzle, why is the labor force participation so
+% low when fertility is low and education has increased.
+% As shown here, part of the answer may be that the number of children is, in fact, not as 
+% low as previously thought, both because of the increased spacing and that more 
+% children survive.
 

### 2020-02-14 response/response-demography-2.tex
Final version of response to editor/referees

@@
 %\usepackage[pdftex]{graphicx}
-\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black]{
-hyperref} 
+\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black]{hyperref} 
 \usepackage[margin=1.0in]{geometry} 
@@
 India's Experience over Four Decades.''
-I want to thank the three reviewers and the editor for the very helpful comments and 
+I want to thank the three reviewers and the editor for the constructive comments and 
 suggestions, which I believe substantially improved the paper.
+
+I have substantially rewritten the paper, so before responding to the
+individual comments, I provide an overview of the revised paper and the
+most significant changes.
+
+To clarify the contribution of the paper, I now focus on three
+questions. First, how has birth spacing changed over time with the
+introduction of sex selection and the other significant changes in
+India? Second, with substantial increases in spacing, how biased is our
+standard fertility estimates? Finally, how has infant mortality changed,
+and is there an effect of sex selection on infant mortality risk?
+
+I have added four new sections: 
+two analytical sections, one on fertility and one on infant mortality, 
+and two background sections, one on female education and labor force 
+participation and one on the conceptual framework.
+I have removed the section on regional differences.
+
+Section-by-section overview of significant changes:
+\begin{enumerate}
+
+\item I have completely rewritten the ``Introduction'' section to provide background on 
+India, discuss why examining birth spacing is relevant, and highlight main results.
+
+\item The first new section covers how female education and labor force
+participation changed over time in India. Both female education and
+labor force participation are factors in spacing decisions. That labor
+force participation has declined even with new groups received more
+schooling helps address the question of whether the expanded access to
+education might change behavior.
+
+Because labor force participation differs by education level, I now divide the original 
+eight or more years of education group into two groups: eight to eleven and twelve or
+more years of education. The eight to eleven group has the lowest labor
+force participation of any group, and twelve or more has one of the
+highest.
+
+\item The second new section provides a conceptual framework.
+I first work through the likely general changes based on the increasing female education 
+and the declining labor force participation and second through the potential effects of 
+access to sex selection.
+I end with a summary of the predictions.
+
+\item I have further shortened the ``Estimation Strategy'' section and
+edited it to focus on the motivation for the choice of model.
+
+\item The Data section is also shorter, and the discussion of potential
+effects of variables is now in the conceptual framework section.
+
+\item With the new education grouping, I have completely rewritten the
+section on how birth spacing has changed (the original Results section).
+Instead of going through each education level in detail, I now focus
+more broadly on how average birth spacing and parity progression have
+changed over time and then on the effects of sex selection, drawing on
+examples to illustrate the changes. The graphs are now easier to read.
+
+\item The original subsection ``Distribution of Birth Spacing Within
+Spells'' is now a new separate section ``Distribution of Birth Spacing''
+and has been completely rewritten. Instead of showing the conditional
+survival graphs, the section now includes figures with the 25th and 75th
+percentiles for birth intervals. These figures allow me to focus on the
+changes in both short and long intervals. Both to tie in with the
+subsequent mortality discussion.
+
+\item The new section, ``What has Happened to Fertility?'' looks at the
+degree of tempo effect that arises from the longer spacing by comparing
+a TFR-like measure with the predicted cohort fertility based on the
+hazard model results.
+
+\item The new section ``Mortality and the Changing Birth Spacing''
+examines how the association between infant mortality and birth spacing
+has changed over time by the education group and whether the increased
+use of sex selection increases mortality risk.
+
+\item Finally, the conclusion has been completely rewritten.
+\end{enumerate}
+
+The revised paper is just over 8,000 words per the author guidelines.
 
@@
 
+To better address why and how the changes in birth spacing are relevant,
+I have added two new sections. One discusses the bias that arises in
+fertility estimates from the significant increases in birth spacing,
+both from sex selection and from secular changes, and show that we
+likely have substantially overestimated how early and fast fertility
+fell in India. The other shows that mortality has fallen for all groups
+no matter how long birth intervals are and that there is no apparent
+adverse effect of high use of sex selection on infant mortality.
+
 \item Second, the paper lacks a conceptual framework to organize (and
@@
 [Response:]
+
+I address this in two parts.
+
+First, I included a new descriptive section on how female education and
+labor force participation has changed over time in India. I include the
+discussion of labor force participation because theories and prior
+results reveal it to be a crucial component in the link between female
+education and birth spacing. I argue that ``Sanskritization'' is behind
+the continued low labor force participation despite the expanded
+schooling and the associated changes in the composition of the education
+groups.
+The implication is that ``Sanskritization'' likely carries over to other decisions, such 
+as sex selection use.
+
+Second, I added a conceptual framework that focuses on how birth spacing
+is likely to respond in a situation where labor force participation is
+low and declining, and son preference is strong. A more general theory
+overview would be interesting, but that is not feasible given the word
+constraint. The conceptual framework section also discusses predictions
+for how access to sex selection is likely to impact birth spacing and
+summarizes the expected effect of the changes in India on birth spacing.
+
+Writing these sections also showed that my original classification of
+education was too broad because labor force participation differs
+markedly within the original eight-plus education group. I have,
+therefore, redone all analyses in the paper with four education groups.
 
@@
 [Response:]
+
+I agree that the regional analysis added little to the paper, and 
+have deleted this section. What I consider the two most
+important issues related to birth spacing are fertility and mortality.
+I, therefore, now focus on how both relate to spacing, in addition to
+examining how birth spacing changed.
+
+There are other relevant questions, such as the effect on the mother
+that I have ignored because of space considerations.
+
+As part of the rewrite, I have removed any remaining discussion that
+might make the paper seem more like a methodological paper. For example,
+I have shortened the ``Data'' and ``Estimation Strategy'' sections and
+rewritten the description of the method in the ``Introduction'' section.
 
@@
 
+Space limitations mean that I cannot add a more detailed examination of
+the raw data to the data description. I have instead tried to address
+this in three ways. First, I have added a discussion in the ``Estimation
+Strategy'' section of why hazard models are the preferred way of dealing
+with censoring. Second, I highlight that censoring of birth spells
+increases with parity and time in the ``Data'' section. Third, I added a
+comparison to the birth spacing numbers from the NFHS reports, which do
+not attempt to deal with censoring and, therefore, have shown virtually
+no change over time.
+
 \item Details on the estimation results are not presented. I assume
@@
 
+I have tried to move away from pitching the paper as a methodological
+contribution. As part of this, I shortened the empirical model
+discussion and removed any mention in the ``Conclusion'' section. I
+agree that a more in-depth examination of how a proportional model stack
+up against the non-proportional model would be fascinating. However, I
+believe this is best done separately, given the already considerable
+length of the paper and the Appendix.
+
+Furthermore, the non-proportionality assumption makes the model more
+flexible than it would have been without, but cannot introduce any bias
+compared to the proportional model. If the non-proportionality
+assumption is not needed, the only thing affected is the efficiency of
+the estimates. However, the reverse is not the case, with bias possible
+if proportionality does not hold.
+
 \item I found the analysis of geographical differences not very
@@
 [Response:]
+
+I agree and have removed the section, as discussed above.
 
@@
 
-Specific comments:
+Unfortunately, the questions on labor force participation are not
+detailed enough to allow a direct analysis using this data. I have
+instead included a discussion of how female labor force participation
+has changed over time in the two new background/conceptual framework
+sections. Furthermore, I now directly discuss the prior literature and
+theory on labor force participation and birth spacing in the ``Birth
+Spacing: Mechanisms and Prior Findings'' section.
+
+While one might expect that increasing income and female education would
+also lengthen average birth spacing through better access and knowledge
+of contraception, the empirical relationship between contraception use
+and birth spacing is ambiguous 
+\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
+Furthermore, the ability to successfully use ``low efficacy''
+contraceptive methods is increasing in education, while there is no
+difference by schooling when it comes to modern contraceptives
+\citep{Rosenzweig1989}.
+Because there is not sufficient historical information on contraception
+use in the data and that the prior literature does not provide a clear
+relationship, I have not included this discussion in the paper.
+\end{enumerate}
+
+\noindent Specific comments:
+
+\begin{enumerate}
 
@@
 [Response:]
+
+I have changed this throughout the paper.
 
@@
 
+That is correct and something that would be interesting to address in a future paper.
+For now, I have included a comment on this in the Estimation Strategy.
+
 \item p.7: Why use intervals of three months? Did the author(s) perform
@@
 [Response:]
+
+I tried shorter than three months, but because the method requires
+events to happen in each period, the estimations would often fail to
+converge. For the same reason, I combine some three months intervals to
+ensure enough information, especially when intervals are long and the
+likelihood of a next birth low.
 
@@
 [Response:]
+
+I have included this in the rewritten ``Introduction'' section and the abstract.
 
@@
 
+Across the entire sample, 36 percent of women report sterilization for
+either themselves or their husbands. The decision does, however, not lend
+itself easily to incorporation into the model as an additional competing
+risk. First, almost nobody is sterilized after their first birth (only
+around 0.5 percent), although this goes up to 19 percent after the
+second birth, and 27 percent after the third. Second, a majority---often
+up to 75 percent---of sterilizations take place in the same month as the
+last birth or within eight months of it. Most of the sterilizations are,
+therefore, never included in the model samples because those begin at
+nine months after the prior birth. Hence, the absolute numbers are too
+small for the competing risk model to work correctly, primarily because
+the likelihood of sterilization depends strongly on the sex composition
+of prior children. For a given parity, the fewer boys, the lower the
+probability.
+
+The results presented here are conditional on a prior birth and no
+sterilization within the nine months after the preceding birth. The main
+concern is that the parity progression probabilities are too high
+because they do not account for sterilization. There are two impacts of
+this.
+
+First, it biases downward the differences in the parity progression
+probabilities across sex compositions. I discuss this in the
+``Data'' section.
+
+Second, the predicted cohort fertility would be too high. I, therefore,
+estimate the likelihood of sterilization within the first nine months
+using a Logit model (results not shown in the paper). I then predict the
+probability of not getting sterilized and use that to scale down the
+parity progression probability when predicting cohort fertility. In
+practice, the effect of the scaling is relatively small, 0.05 to 0.25,
+which is consistent with the lowest use among women who have the highest
+estimated parity progression probabilities based on the hazard model.
+
 \item p.9: why put the marriage duration threshold at 22 years?
@@
 [Response:]
+
+I discuss this in the Appendix section ``Recall Error and the Sex
+Ratio''. Since most of the surveys start showing significantly biased
+sex ratio from around 22 years of marriage on, I drop all observations
+where the wedding took place 22 years or more. Changes of a couple of
+years more or less do not substantially change the results. However, a
+cut significantly higher than 22 does eventually make the sex ratio very
+uneven in the first period, even for less-educated women. There are no
+effects on the more recent periods.
 
@@
 
+I have tried to address this by increasing the font size for the legends
+and turning the graphs sideways. Originally the results were presented
+in table format (now available in the Appendix). Prior referees found it
+hard to get an overview of the results that way, and, on balance, I
+agree with that. Hence, I have kept the graphs for the spacing
+discussions. For the fertility section, I present the results as a
+table.
+
 \end{enumerate}
@@
 
-\begin{enumerate}
-
 This study uses four waves of the National Family and Health Surveys to
@@
 household, by maternal educational level, and over time.
+
+\begin{enumerate}
 
@@
 
-[Response:]
-
-\item The authors attempt to address this point by offering four motivations
+The authors attempt to address this point by offering four motivations
 for why we should care about spacing as an additional dimension. First,
@@
 [Response:]
+
+I have reframed the paper to be about birth spacing more
+generically (see also my response below) and tied it to two issues where
+changes in spacing have direct relevance: fertility estimates and infant mortality.
+I have removed most of the discussion of spacing as a measure of son preference,
+except to note that we now have cases where son preference results in longer
+spacing without boys than with because of sex selection.
+
+% What also makes birth spacing in India interesting is that opposite of what we
+% have seen elsewhere, birth spacing has increased over time with development.
+% The increases is especially pronounced because of the use of sex selection.
 
@@
 
+Thank you for this fascinating point on the potential adverse effects of
+the increased use of abortions. I have included this as one of the two
+main reasons why the changes in spacing are worth examining and have
+introduced a new section on infant mortality and how it varies by
+spacing and sex composition over time. There is, however, no apparent
+adverse effect of being a son born after girls and with longer spacing
+in situations with high use of sex selection. Hence, if there is a
+negative effect of multiple abortions, it is more than countered by the
+protective effect of higher maternal education. It is still possible
+that we would see more of an impact among less-educated women, but this
+group is, currently, not heavy users of sex selection.
+
+To focus the paper, I no longer discuss the potential effects on
+mothers, although I still find that an exciting topic for future
+analysis. The same goes for the long-term development of children.
+
 \item The fourth and final motivation offered is that we don’t know what
@@
 [Response:]
+
+As mentioned above, I now include a discussion of the changing spacing's effect on
+fertility estimates.
+Similarly, although I cannot directly examine the relationship between labor force
+participation and spacing because of data limitations, I do discuss the low and 
+falling labor force participation in India and the effects this may have on spacing.
+I have removed the discussion on contraceptive use (see also my response above).
 
@@
 
+As described above, I have substantially rewritten the paper and
+introduced new analyses to illustrate better how and why examining birth
+spacing is necessary, including linking birth spacing and infant
+mortality directly. I am, however, open for suggestions for alternative
+ways to focus the paper and the motivations.
+
 \end{enumerate}
@@
 \section*{Reviewer 3}
-
-\begin{enumerate}
 
@@
 
+\begin{enumerate}
+
 \item The paper still lacks a stronger narrative on the motivation and
@@
 evidence for importance of spacing).
+
+[Response:]
+
+I have entirely rewritten the paper to focus on how and why examining
+birth spacing is relevant, as described above. As part of that rewrite,
+I now estimate the relationship between spacing and infant mortality,
+mainly to understand whether the increased use of sex selection may
+increase mortality risk. Although I still find the effects on the
+mothers' health a fascinating question, I have decided not to discuss
+this effect because of lack of space.
 
@@
 
-\item As an illustration, the paper looks at changes over time during which
+As an illustration, the paper looks at changes over time during which
 the access the sex selection has become increasing difficult AND also
@@
 under consideration.
+
+[Response:]
+
+The second of the two new background sections draw together the
+different theories on the relationship between maternal education, labor
+force participation, birth spacing, and use of sex selection, and use
+those to guide the hypothesized changes.
+
+To address the broader changes in India, the first of the two new
+background sections show how female education has increased, while
+female labor force participation has decreased. I argue that the low
+female labor force participation is an indication of
+``Sanskritization''. The pool of educated women has expanded, but the
+behavior of the group does not change much.
+
+I also show that although fertility fell, it is higher than generally
+acknowledged, precisely because longer birth intervals biases downward
+our standard fertility measures.
 
@@
 
+[Response:]
+
+That was, indeed, an overstatement of the results. I now discuss the
+three possible outcomes---no sex selection, sex selection with no change
+in relative order by sex composition, and sex selection with a change in
+the order---and provide examples of each.
+
 \item While I really liked the methodology and visual presentation of the
@@
 
+[Response:]
+
+I have tried to move away from pitching the paper as a methodological
+contribution. As part of this, I shortened the empirical model
+discussion and removed any mention in the ``Conclusion'' section.
+I hope that the two new analytical sections and the two background sections 
+make the paper more of a definite contribution to the literature.
+
 \item Minor: It might be a disciplinary style, I would recommend cutting down
-on the footnotes. I would also not go into the effect of child spacing
+on the footnotes.
+
+[Response:]
+
+I have removed or incorporated into the text a large number of footnotes.
+
+\item I would also not go into the effect of child spacing
 in countries that are very dissimilar to the context of India, unless
-there is a wider point being made. Some points are not clear: for
+there is a wider point being made.
+
+[Response:]
+
+I have removed this discussion.
+
+\item Some points are not clear: for
 instance, “On the other hand, increased reliability of access and
@@
 children by accident (Keyfitz, 1971; Heckman and Willis, 1976).”
+
+[Response:]
+
+This discussion is no longer in the paper because of the new conceptual
+framework. If other parts are unclear, please let me know.
 

### 2020-02-14 paper/sex_selection_spacing-ver3-demography.tex
Final version of revised paper for Demography

--- 2020-02-12 paper/sex_selection_spacing-ver3.tex
@@
 % For word counting uncomment line below and raggedright below
-\usepackage[nolists]{endfloat}
+% \usepackage[nolists]{endfloat}
 
@@
 India's Experience over Four Decades%
-\protect\thanks{%
-I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-University of Washington, University of Aarhus, the Fourth 
-Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful 
-suggestions and comments.
-I would also like to thank Nalina Varanasi for research assistance.
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
-The views and findings expressed here are those of the author and
-should not be attributed to the World Bank or any of its member countries.
-Partial support for this research came from a Eunice Kennedy Shriver National
-Institute of Child Health and Human Development research infrastructure grant,
-5R24HD042828, to the Center for Studies in Demography and Ecology at the
-University of Washington.
-}
-}
-
-\author{Claus C P\"ortner\\
-    Department of Economics\\
-    Albers School of Business and Economics\\
-    Seattle University, P.O. Box 222000\\
-    Seattle, WA 98122\\
-    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
-    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
-    \& \\
-    Center for Studies in Demography and Ecology \\
-    University of Washington\\ \vspace{2cm}
-    }
+% \protect\thanks{%
+% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
+% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
+% University of Washington, University of Aarhus, the Fourth 
+% Annual Conference on Population, Reproductive Health, 
+% and Economic Development, and the Economic Demography Workshop for helpful 
+% suggestions and comments.
+% I would also like to thank Nalina Varanasi for research assistance.
+% Support for development of the method from the University of Washington Royalty 
+% Research Fund and the Development Research Group of the World Bank is gratefully 
+% acknowledged.
+% The views and findings expressed here are those of the author and
+% should not be attributed to the World Bank or any of its member countries.
+% Partial support for this research came from a Eunice Kennedy Shriver National
+% Institute of Child Health and Human Development research infrastructure grant,
+% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
+% University of Washington.
+% }
+}
+
+\author{}
+
+% \author{Claus C P\"ortner\\
+%     Department of Economics\\
+%     Albers School of Business and Economics\\
+%     Seattle University, P.O. Box 222000\\
+%     Seattle, WA 98122\\
+%     \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
+%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
+%     \& \\
+%     Center for Studies in Demography and Ecology \\
+%     University of Washington\\ \vspace{2cm}
+%     }
 
@@
 Using four rounds of India's National Family and Health Surveys and a
-competing-risk hazard model, I show that average birth intervals
+competing-risk hazard model, I show that Hindu women's average birth intervals
 increased over the last four decades for all education groups. The most
@@
 % For word counting remove comment on the line below
-\raggedright
+% \raggedright
 
@@
 but also works in cases without prenatal sex selection.
-The empirical model allows me to predict fertility behavior taking into
+The empirical model allows me to predict fertility, taking into
 account both the likelihood of parity progression and the likelihood of having a child of 
 a specific sex.
+Finally, I examine how infant mortality risk has changed with the changing birth spacing 
+and whether sex selection affects infant mortality.
 
@@
 throughout the entire spell, as is assumed by the proportional hazard model.
+If proportionality does not hold, the results are biased.
 The proportionality assumption is especially problematic for higher-order spells where 
@@
 the spell continues until time $t_i$ when either birth or censoring of the spell 
-occurs.%
-\footnote{
+occurs.
 The time of censoring is assumed independent of the hazard rate,
 as is standard in the literature.
-}
 There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
@@
 individual, household, and community characteristics discussed below,
-and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
+and $D_{j}(t)$ is the piece-wise constant baseline hazard for outcome $j$, captured
 by dummies and the associated coefficients,
@@
 \end{equation}
-$D_j(t)$ is the piece-wise linear baseline hazard, $\mathbf{Z}_1$ captures sex 
+$D_j(t)$ is the piece-wise constant baseline hazard, $\mathbf{Z}_1$ captures sex 
 composition of previous children, and $Z_2$ captures the area of residence.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
+The remaining explanatory variables, $\mathbf{X}$, enter proportionally.%
+\footnote{
+With sex selection, the composition of prior children is, in principle, endogenous.
+It is beyond the scope of this paper to develop a method for dealing with this issue.
+}
 However, to further minimize any potential bias from assuming proportionality, estimations 
@@
 nine months.
+
 Finally, I restrict the sample to Hindus, who constitute about 80 percent of India’s 
-population.%
-\footnote{
+population.
 If the use of sex selection differs across groups, assuming that the
@@
 group would not make sense.
-}
 
@@
 Recall error is heavily dependent on how long ago a woman was married, and I, therefore, 
-drop women married 22 years or more.%
-\footnote{
-See the discussion in the Appendix.
-}
+drop women married 22 years or more based on the discussion in the Appendix.
 The final sample consists of 
@@
 sterilization of the woman or her husband,
-or too few births are observed for the method to work.
+or too few births are observed for the method to work.%
+\footnote{
+Most sterilizations take place right after a woman gives birth, and,
+therefore, do not show up in the samples used. 
+Furthermore, sterilization depends strongly on the sex composition of prior children
+with lower probabilities, the fewer boys. 
+The effect is that the differences in parity progression probabilities are biased 
+downwards.
+}
 For all spells, censoring is set at 96 months (eight years) after a woman can first
@@
 
-The predicted parity progression probability is the likelihood of giving birth by 96 
-months after the beginning of the spell.
 To find the expected average duration, I first calculate, for each woman, the probability 
@@
 probabilities as weights.
+
+The predicted parity progression probability is the likelihood of giving birth by 96 
+months after the beginning of the spell.
 
@@
 \begin{sidewaysfigure}
+\centering
 \ContinuedFloat
@@
 
+Sterilizations are not incorporated into the hazard model because most occur
+immediately after giving birth. 
+To compensate, I estimate the likelihood of sterilization using a Logit model, predict 
+the probability of not getting sterilized, and then use that to scale down the parity
+progression probability when predicting cohort fertility.
+
 I include the spell from marriage to first birth, despite the problems
@@
 and 2005--2016 for rounds 1 through 4 of the NFHS, respectively.
-Because of the small number of women who had the highest level of education in the
-1972--1984 period, I do not predict fertility for this case.
+
+% Because of the small number of women who had the highest level of education in the
+% 1972--1984 period, I do not predict fertility for this case.
 
@@
 These increases likely arise from the stabilization of the age of first birth and the 
-spacing between births.%
-\footnote{
-Increases in TFR over time, even in the face of declining cohort fertility, are not 
-unusual, as shown by Columbia in the early 1990s \citep{Bongaarts1999}.
-}
+spacing between births.
+
+%
+% \footnote{
+% Increases in TFR over time, even in the face of declining cohort fertility, are not 
+% unusual, as shown by Columbia in the early 1990s \citep{Bongaarts1999}.
+% }
 
@@
 Only for urban women with twelve or more years of education is the predicted cohort
-fertility below 2.1, and even then, it is still more than 0.3 children higher than the 
-fertility rate estimate of 1.5.
+fertility clearly below 2.1, and even then, it is still more than 0.3 children higher than 
+the fertility rate estimate of 1.5.
 Furthermore, the predicted cohort fertility numbers are likely too low,
 especially for the lower education groups, since it relies only on the
-first four births.
+first four births and because the model ignores births that took place past the end
+of the 96 months long spell.
 
@@
 from secular changes, may directly reduce infant mortality.
+
 To the extent that the longer birth intervals arise from multiple abortions,
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
@@
 \subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
+    \begin{minipage}{0.37\textwidth}
         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies} 
@@
 
-Tempo effects are studied extensively in the literature.%
-\footnote{
-See, for example, \citet{Bongaarts1999}.
-}
+Tempo effects are studied extensively in the literature \citep[See, for example, ][]{Bongaarts1999}.
 Still, there are, to my knowledge, no other cases where there has been as 
@@
 
-The results here lead to two critical questions that future research should address.
+There are two critical questions that future research should address.
 Sex selection means that girls-only families are less likely to have

### 2020-06-16 response/response-demography-3.tex
Initial commit of response letter

\documentclass[letterpaper,12pt]{article}

% Xetex preamble
\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}

\usepackage[longnamesfirst]{natbib}
%\usepackage[tabhead,nolists,tablesfirst]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{rotating}  
\usepackage{dcolumn} 
\usepackage{setspace}
%\usepackage{flafter} 
%\usepackage{longtable}
%\usepackage[pdftex]{graphicx}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black]{hyperref} 
\usepackage[margin=1.0in]{geometry} 
\usepackage{multirow}

%opening
\title{} \author{}

\doublespacing

\begin{document}

\begin{center} \textbf{\large Birth Spacing in the Presence of Son
Preference and 
Sex-Selective Abortions: India's Experience over Four Decades}
\end{center}

\begin{center} Response to Editor and Reviewer Comments \end{center}

\noindent Please find attached the revised version of my paper,
``Birth Spacing in the Presence of Son Preference and Sex-Selective
Abortions:
India's Experience over Four Decades.''

\section*{Editors}

\begin{enumerate}

\item We note that you kept to the table/figure limit; however, some of
the figures are several pages long and relatively small. These will have
to be evaluated at the copy edit stage as there is no obvious quick fix
- the figures reflect the analyses carried out (and some additional ones
are in an online appendix). Please make sure to submit as
high-resolution image as possible in the format required by the journal.
We are somewhat concerned about figure/table size within the print form
of the journal.

[Response:]

\end{enumerate}

\section*{Deputy Editor}

\begin{enumerate}

\item The overall topic and research question is not clear in the
introduction. The main topic relates to changes in birth spacing over
time, which are influenced by sex selection/sex composition and maternal
education, and how this affects fertility and infant mortality. This is
a long list of interesting questions and analyses but this is confusing
for the reader. It would be useful to have a succinct statement about
what the study is about (what are key independent variables/concepts and
key outcomes) and place that in the introduction and before the data and
analyses section. This way, the reader can understand why the analyses
will proceed in a particular order and what is being tested. In
addition, the titles of the figures and tables should be reviewed to see
if they could better reflect the analyses undertaken. Overall, the
reader needs to be reminded at the beginning and in each section what
you aim to do.

[Response:]

\item Please define sex selection early on.

[Response:]

\item Please provide a motivation for using maternal education as a key
stratification measure and justify education cutoffs (which have meaning
in India).

[Response:]

\item The word “spell” is introduced with no definition. Is spell the
same as birth interval? Is it measured in months? This information would
be useful for the reader.

[Response:]

\item Please include a brief discussion or footnote about the quality of
birth date data in the DHS/NSFH and how this could bias your results or
not.

[Response:]

\item Perhaps the conclusion could start with a brief overview of your
topic and research question again to remind the reader of the overall
motivation for the study.

[Response:]

\item I see the point to reviewer’s comment #4 about the discussion on
women’s labor supply. It’s a complex topic to introduce in a few brief
sentences. Similarly, referring to Goldin’s U-shaped theory without a
more detailed explanation could be confusing for those not well versed
in this topic. Perhaps you could also mention that decreasing FLFP is
unexpected for developing countries and some potential reasons for this
in India.

[Response:]

\item The Klasen and Pieters article is now published.

[Response:]

\item Please have the paper carefully reviewed/edited, as there are
numerous grammatical and syntax mistakes.

[Response:]

\end{enumerate}

\newpage

\section*{Reviewer 1}

I already liked the previous version of this paper. I think the author
has done a good job incorporating most of my comments and those of the
other reviewers. Even though I would sometimes have made different
choices (for example, including fewer figures), the choices the author
has made are well understandable and appropriately motivated. I think
the paper is a useful contribution to Demography and my advice is to
accept it.

[Response:]

\begin{enumerate}

\item

\end{enumerate}

\newpage

\section*{Reviewer 2}

I think that the author has done a good job in addressing the comments
made by the three reviewers. However, on reading the draft, I felt a few
things were not clear.

\begin{enumerate}

\item It is not clear why the author restricts the analysis to Hindu
women. Given that data across four rounds of the NFHS data is being
pooled, I think there is enough data to examine this question for the
non-Hindu (and in particular Muslim) women. Given that patterns of son
preference varies across religious groups, I think it is worth examining
the question for non-Hindus. At the very lease include a discussion of
why the nonHindus have not been included.

[Response:]

\item There is actually no data on sex selection and in a sense the data
is backed out using evidence on birth spacing, institutional information
on the availability of technology that enables sex selection (ultra
sound techniques) and government regulations. To do this the author
subdivides the time into four segments: 1972–1984, 1985–1994, 19952004
and 2005–2016. I understand the logic of the first two breaks 1984 and
1994, but what is the logic of the third break in 2004? This needs to be
made clearer.

[Response:]

\item While I like results being presented in figures, what I don’t like
is that no standard errors or confidence intervals are presented.
Therefore, it is difficult to figure out whether the differences between
categories (composition of existing children) are statistically
significant or not.

[Response:]

\item In the context of the paper, I don’t see the point of the
discussion relating to labour supply.

[Response:]

\item Overall, I felt that the paper is still quite densely written and
it is not easy to follow what is going on. Considerable time needs to be
spent re-writing the paper and making it easier to read.

[Response:]

\end{enumerate}

\newpage
\bibliographystyle{econometrica}
\bibliography{../paper/sex_selection_spacing.bib}
\addcontentsline{toc}{section}{References}

\end{document}

### 2020-06-16 response/response-demography-3.tex
Respond to Klasen and Pieters comment and minor edits

@@
 
-\item The word “spell” is introduced with no definition. Is spell the
+\item The word ``spell'' is introduced with no definition. Is spell the
 same as birth interval? Is it measured in months? This information would
@@
 [Response:]
+
+Yes, I already had it listed as World Bank Economic Review 2015.
+Was there maybe another paper that I should cite?
 
@@
 
+[With respect to the reviewer’s comments, please address comments #1, #2, and #4.]
+
 I think that the author has done a good job in addressing the comments
@@
 the question for non-Hindus. At the very lease include a discussion of
-why the nonHindus have not been included.
+why the non-Hindus have not been included.
 
@@
 sound techniques) and government regulations. To do this the author
-subdivides the time into four segments: 1972–1984, 1985–1994, 19952004
-and 2005–2016. I understand the logic of the first two breaks 1984 and
+subdivides the time into four segments: 1972--1984, 1985--1994, 1995--2004
+and 2005--2016. I understand the logic of the first two breaks 1984 and
 1994, but what is the logic of the third break in 2004? This needs to be

### 2020-06-16 paper/sex_selection_spacing-ver4.tex
Initial commit of version 4 of paper

--- 2020-02-14 paper/sex_selection_spacing-ver3-demography.tex
@@
 India's Experience over Four Decades%
-% \protect\thanks{%
-% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
-% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-% University of Washington, University of Aarhus, the Fourth 
-% Annual Conference on Population, Reproductive Health, 
-% and Economic Development, and the Economic Demography Workshop for helpful 
-% suggestions and comments.
-% I would also like to thank Nalina Varanasi for research assistance.
-% Support for development of the method from the University of Washington Royalty 
-% Research Fund and the Development Research Group of the World Bank is gratefully 
-% acknowledged.
-% The views and findings expressed here are those of the author and
-% should not be attributed to the World Bank or any of its member countries.
-% Partial support for this research came from a Eunice Kennedy Shriver National
-% Institute of Child Health and Human Development research infrastructure grant,
-% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
-% University of Washington.
-% }
-}
-
-\author{}
-
-% \author{Claus C P\"ortner\\
-%     Department of Economics\\
-%     Albers School of Business and Economics\\
-%     Seattle University, P.O. Box 222000\\
-%     Seattle, WA 98122\\
-%     \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
-%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
-%     \& \\
-%     Center for Studies in Demography and Ecology \\
-%     University of Washington\\ \vspace{2cm}
-%     }
+\protect\thanks{%
+I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
+Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
+University of Washington, University of Aarhus, the Fourth 
+Annual Conference on Population, Reproductive Health, 
+and Economic Development, and the Economic Demography Workshop for helpful 
+suggestions and comments.
+I would also like to thank Nalina Varanasi for research assistance.
+Support for development of the method from the University of Washington Royalty 
+Research Fund and the Development Research Group of the World Bank is gratefully 
+acknowledged.
+The views and findings expressed here are those of the author and
+should not be attributed to the World Bank or any of its member countries.
+Partial support for this research came from a Eunice Kennedy Shriver National
+Institute of Child Health and Human Development research infrastructure grant,
+5R24HD042828, to the Center for Studies in Demography and Ecology at the
+University of Washington.
+}
+}
+
+\author{Claus C P\"ortner\\
+    Department of Economics\\
+    Albers School of Business and Economics\\
+    Seattle University, P.O. Box 222000\\
+    Seattle, WA 98122\\
+    \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
+    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
+    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
+    \& \\
+    Center for Studies in Demography and Ecology \\
+    University of Washington\\ \vspace{2cm}
+    }
 
@@
 
-% \setcounter{page}{-1}
+\setcounter{page}{-1}
 \maketitle
@@
 
-\setcounter{page}{0}
-
-% \newpage
+% \setcounter{page}{0}
+
+\newpage
 \thispagestyle{empty}

### 2020-06-17 paper/sex_selection_spacing-ver4.tex
Add sex selection definition and focus on questions

@@
 
-India has changed significantly over the last four decades:
-the economy has grown substantially,
-education levels have increased for both males and females,
-and the total fertility rate has fallen to 2.2 
+India saw many positive changes over the last four decades:
+the economy grew substantially,
+schooling increased for both males and females,
+and the total fertility rate fell to 2.2 
 \citep{Bosworth2008,Dharmalingam2014,
@@
 
-India has, however, also experienced a rapidly expanding 
-access to prenatal sex determination.
-Combined with continued strong son preference, the result has been a dramatic 
-increase in the males-to-females ratio at birth
-\citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,
-Portner2015b,Jayachandran2017}.
-
-What the prior research on India has not appreciated is that since each abortion 
-increases the interval between births by six to twelve months, the growing use of 
-sex-selective abortions may substantially increase birth spacing.%
+However, the males-to-females ratio at birth also increased dramatically over this period
+\citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,Portner2015b,Jayachandran2017}.
+Chorionic villus sampling (CVS), amniocentesis, and ultrasound all allow parents to learn 
+a fetus' sex, and access to these technologies expanded rapidly.
+With a continued strong preference for sons, the result has been an increase in sex 
+selection, the selective abortion of female fetuses based on prenatal sex determination.%
+\footnote{
+CVS requires the shortest period of gestation---eight to twelve
+weeks---which means that abortions can occur in the first trimester.
+Amniocentesis can be performed after fourteen weeks but requires three
+to four weeks before the result is available.
+Hence, any abortion would not take place until more than halfway through the second 
+trimester.
+Ultrasound has the advantages of being non-invasive and relatively cheap.
+The sex of a fetus can be determined in the third month of gestation if
+it is a boy and the fourth month if it a girl.
+}
+
+The main question I examine is: how did birth spacing respond to these
+significant changes, especially the introduction and spread of sex selection? 
+This question is motivated by two factors. 
+First, prior research has failed to appreciate that each abortion increases the
+interval between births by six to twelve months.%
 \footnote{
 The increase consists of three parts. 
-First, starting from the abortion, the uterus needs at 
-least two menstrual cycles to recover;  otherwise, the likelihood 
-of spontaneous abortion increases substantially \citep{zhou00b}.
-The second part is the waiting time to conception, which is between 
-one and six months \citep{Wang2003}.
-Finally, sex determination tests are reliable only from three months 
-of gestation onwards.
-}
-Furthermore, the combination of increasing female education, 
-lower fertility, higher household income, and the low and declining female 
-labor force participation are also likely to impact birth spacing.
-Hence, the changes in birth spacing may be much more substantial in India 
-than what we have observed in other countries.
-
-There are two primary motivations for examining birth spacing in this
-situation, besides gaining a better general understanding of how
-families make fertility decisions.
-
-First, if birth intervals increased substantially over time, India's fertility may 
-be higher than generally accepted based on the total fertility rate (TFR).
-Increasing birth spacing is a tempo effect, which, by postponing births, makes the TFR a 
-downward biased estimate of cohort fertility 
+First, after an abortion, the uterus needs at least two menstrual cycles to recover; 
+otherwise, the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
+The second part is the waiting time to conception, which is between one and six months. 
+Finally, sex determination tests are reliable only from three months of gestation onwards.
+}
+Hence, the growing use of sex-selective abortions may substantially increase birth spacing, 
+but we know little about how much. 
+Second, more female education, higher household income, and low and declining female labor 
+force participation are all likely to impact birth spacing, and the combined changes in 
+birth spacing may, therefore, be much more substantial in India than what we have observed 
+in other countries.
+
+Understanding birth spacing is valuable not only because it contributes not only to our 
+knowledge about fertility decisions but also because of the potential effects of birth 
+spacing on outcomes such as fertility measures and mortality. 
+I focus on two questions.
+
+First, to what extent do changes in birth spacing bias our standard fertility estimates?
+The tempo effect that arises from longer birth intervals means that the total fertility 
+rate is a downward biased estimate of cohort fertility 
 \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
-
-Second, longer birth spacing is associated with lower mortality and 
-morbidity risk \citep{Conde-Agudelo2012,Molitoris2019}.
+Hence, if birth intervals increased substantially over time, India's fertility may 
+be higher and have declined slower than generally accepted.
+
+Second, how do the changes in birth spacing and the increased use of abortions impact 
+children's survival chances?
 In India, the duration to the next birth has traditionally been shorter with fewer sons, 
@@
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
-Longer spacing between births then potentially lowers mortality, although there may
-be counteracting effects if the longer spacing arises because of multiple abortions.
-There has, so far, been no attempt to examine how mortality has responded to the
-increase in sex selection.
-
-% Finally, birth spacing has long served as a measure of son preference, with strong
-% son preference associated with shorter birth intervals, the fewer sons a family has 
-% \citep{ben-porath76b,Leung1988}.
-% Now, longer birth intervals in the absence of sons may instead arise because couples 
-% with a strong preference for sons use sex selection, possibly to the point where we 
-% observe a reversal of the traditional spacing pattern.
-% Despite a large literature on son preference and birth spacing, no prior research has,
-% however, examined how sex selection affects spacing.
-
-I examine how birth spacing in India has changed over time and across 
-groups with the introduction of sex selection.
-Using data from the four National Family and Health Surveys (NFHS), I apply
-a competing risk hazard model to the birth histories of Hindu women, covering
-the period 1972 to 2016.
+Longer birth spacing then potentially lowers mortality and morbidity risk 
+\citep{Conde-Agudelo2012,Molitoris2019}.
+There may, however, be counteracting effects if the longer spacing arises because of 
+multiple abortions.
+There has, so far, been no attempt to examine how infant mortality has responded 
+to the increase in sex selection.
+
+To examine how birth spacing in India has changed over time and across groups with the 
+introduction of sex selection, I apply a competing risk hazard model to the birth 
+histories of Hindu women, covering the period 1972 to 2016, using data from the four 
+National Family and Health Surveys (NFHS).
 The competing risk hazard model directly incorporates the effects of 
@@
 a specific sex.
-Finally, I examine how infant mortality risk has changed with the changing birth spacing 
-and whether sex selection affects infant mortality.
+I use the same data to examine how infant mortality risk has changed with the changing 
+birth spacing and whether sex selection affects infant mortality.
 

### 2020-06-18 paper/sex_selection_spacing-ver4.tex
Add three main questions and define sex selection

@@
 
-\date{February 2020}
+\date{June 2020}
 
@@
 
-However, the males-to-females ratio at birth also increased dramatically over this period
+However, India also witnessed the appearance of sex selection---the selective 
+abortion of female fetuses based on prenatal sex determination. 
+Sex selection became available in the mid-eighties with the introduction of technologies 
+such as ultrasound and amniocentesis. 
+Combined with continued strong son preference, the result was a dramatic increase in the 
+male-to-female ratio at birth
 \citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,Portner2015b,Jayachandran2017}.
-Chorionic villus sampling (CVS), amniocentesis, and ultrasound all allow parents to learn 
-a fetus' sex, and access to these technologies expanded rapidly.
-With a continued strong preference for sons, the result has been an increase in sex 
-selection, the selective abortion of female fetuses based on prenatal sex determination.%
-\footnote{
-CVS requires the shortest period of gestation---eight to twelve
-weeks---which means that abortions can occur in the first trimester.
-Amniocentesis can be performed after fourteen weeks but requires three
-to four weeks before the result is available.
-Hence, any abortion would not take place until more than halfway through the second 
-trimester.
-Ultrasound has the advantages of being non-invasive and relatively cheap.
-The sex of a fetus can be determined in the third month of gestation if
-it is a boy and the fourth month if it a girl.
-}
 
 The main question I examine is: how did birth spacing respond to these
-significant changes, especially the introduction and spread of sex selection? 
-This question is motivated by two factors. 
+changes, especially the introduction and spread of sex selection? 
+The motivation is twofold.
 First, prior research has failed to appreciate that each abortion increases the
@@
 otherwise, the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
-The second part is the waiting time to conception, which is between one and six months. 
-Finally, sex determination tests are reliable only from three months of gestation onwards.
+Second, the waiting time to conception is between one and six months. 
+Finally, sex determination tests are reliable only from three months of gestation. 
 }
@@
 Second, more female education, higher household income, and low and declining female labor 
-force participation are all likely to impact birth spacing, and the combined changes in 
-birth spacing may, therefore, be much more substantial in India than what we have observed 
-in other countries.
-
-Understanding birth spacing is valuable not only because it contributes not only to our 
-knowledge about fertility decisions but also because of the potential effects of birth 
-spacing on outcomes such as fertility measures and mortality. 
+force participation are all also likely to impact birth spacing, and the combined changes 
+may be much more substantial in India than what we have observed in other countries.
+
+Understanding birth spacing is valuable because it contributes to our knowledge about 
+fertility decisions and because of birth spacing's potential effects on outcomes such as 
+fertility measures and mortality. 
 I focus on two questions.
@@
 Hence, if birth intervals increased substantially over time, India's fertility may 
-be higher and have declined slower than generally accepted.
+be higher than generally accepted.
 
 Second, how do the changes in birth spacing and the increased use of abortions impact 
-children's survival chances?
+children's chances of survival?
 In India, the duration to the next birth has traditionally been shorter with fewer sons, 
@@
 
-To examine how birth spacing in India has changed over time and across groups with the 
-introduction of sex selection, I apply a competing risk hazard model to the birth 
-histories of Hindu women, covering the period 1972 to 2016, using data from the four 
-National Family and Health Surveys (NFHS).
-The competing risk hazard model directly incorporates the effects of 
-sex-selective abortions on birth intervals
-\emph{and} 
-the likelihood of a son 
-but also works in cases without prenatal sex selection.
+To examine how birth spacing has changed over time and across groups with the introduction 
+of sex selection, I apply a competing risk hazard model to the birth histories of Hindu 
+women, covering the period 1972 to 2016, using data from the four National Family and 
+Health Surveys (NFHS).
+The model directly incorporates the effects of sex-selective abortions on birth intervals
+and the likelihood of a son, but it also works with no sex selection.
 The empirical model allows me to predict fertility, taking into
@@
 % [Hypotheses / questions]
-There are four main sets of results.
-
-First, birth intervals have increased for all education groups over the four decades, 
-the more so, the higher the parity and the higher the education level.
-Women who are most likely to use sex selection---well-educated women with no
-sons---have seen the most substantial increases in birth intervals and the most 
-biased sex ratios.
-As a result, we now see cases that reverse the traditional spacing
-pattern, with women with no sons having longer birth intervals than
-women with sons.
-Those least likely to use sex selection, women with less education in rural areas, 
-still follow the traditional pattern of short spacing when they have girls and 
-little evidence of the use of sex selection.
-Women with no sons still are the most likely to have an additional birth.
-Although the probability of having a next child has declined for this group over time, the 
-declines are often substantially smaller than if a boy is present.
-
-Second, there is little difference over time and across groups in the likelihood of 
-having a very short birth interval given the sex composition of prior children, 
-especially for the lower parities.
-Hence, the increases in average spacing come predominantly from the longer birth intervals
-getting even longer over time, driven in no small degree by substantial use of sex 
-selection.
-The exception to this result is that the better-educated women with a \emph{very high} 
-predicted use of sex selection appear to conceive later precisely because the next child 
-is almost certainly a boy.
+There are four main results.
+
+First, birth intervals have increased for all education groups over the four decades, but 
+more so, the higher the parity and the higher the education. 
+Women most likely to use sex selection---well-educated women with no sons---had the most 
+substantial lengthening of birth intervals and the most biased sex ratios. 
+As a result, we now see cases that reverse the traditional spacing pattern, with women 
+with no sons having \emph{longer} birth intervals than women with sons. 
+Those least likely to use sex selection---women with less education in rural areas---still 
+follow the traditional pattern of short spacing when they have girls and little evidence 
+of sex selection.
+
+Second, there is little change in the likelihood of having a very short birth interval. 
+Hence, the increased average spacing comes mainly from the longer birth intervals getting 
+even longer, primarily driven by substantial use of sex selection. 
+The exception to this result is that those better-educated women who have a very high 
+predicted use of sex selection conceive later precisely because the next child is almost 
+certainly a boy.
 
@@
 Furthermore, even with the convergence, predicted cohort fertility is still at or above 
-replacement level, except for the best-educated urban women.
+replacement level for all but the best-educated urban women.
 
@@
 the most education.
-The mortality risk is, however, still inversely related to education level, especially for 
+However, the mortality risk is still inversely related to education level, especially for 
 very short birth intervals.

### 2020-06-19 response/response-demography-3.tex
Response to sex selection definition and partly to research question comments

@@
 
-[Response:]
+[Response:] I have rewritten the Introduction to emphasize the main question I address
+(``how did birth spacing respond to these changes, especially the introduction and spread 
+of sex selection?'') and the two associated questions on the effects of the changes in 
+birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
+estimates?'' and `` how do the changes in birth spacing and the increased use of abortions 
+impact children's chances of survival?'').
 
@@
 
-[Response:]
+[Response:] I now define ``sex selection'' as ``the selective abortion of female fetuses 
+based on prenatal sex determination'' in the second paragraph of the paper.
 

### 2020-06-22 paper/sex_selection_spacing-ver4.tex
Minor edits of Introduction

@@
 
+% Background
 India saw many positive changes over the last four decades:
@@
 
+% Questions addressed and why valuable
 The main question I examine is: how did birth spacing respond to these
@@
 Second, more female education, higher household income, and low and declining female labor 
-force participation are all also likely to impact birth spacing, and the combined changes 
-may be much more substantial in India than what we have observed in other countries.
-
-Understanding birth spacing is valuable because it contributes to our knowledge about 
+force participation are all also likely to impact birth spacing. 
+Hence, the combined changes in birth spacing in India may be much more substantial than
+ what we have observed in other countries.
+
+Studying birth spacing is valuable because it contributes to our knowledge about 
 fertility decisions and because of birth spacing's potential effects on outcomes such as 
 fertility measures and mortality. 
-I focus on two questions.
+To understand the effects of changes in birth spacing, I focus on two questions.
 
 First, to what extent do changes in birth spacing bias our standard fertility estimates?
-The tempo effect that arises from longer birth intervals means that the total fertility 
-rate is a downward biased estimate of cohort fertility 
-\citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
+Tempo effects from longer birth intervals make the total fertility rate a downward biased 
+estimate of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
 Hence, if birth intervals increased substantially over time, India's fertility may 
@@
 
-To examine how birth spacing has changed over time and across groups with the introduction 
+% How the study progresses
+To investigate how birth spacing has changed over time and across groups with the introduction 
 of sex selection, I apply a competing risk hazard model to the birth histories of Hindu 
@@
 a specific sex.
+
 I use the same data to examine how infant mortality risk has changed with the changing 
@@
 
-% [Hypotheses / questions]
+% Main results
 There are four main results.

### 2020-06-22 response/response-demography-3.tex
Minor edits of response letter

--- 2020-06-16 response/response-demography-3.tex
@@
 
-[Response:]
+[Response:] I have rewritten the Introduction to emphasize the main question I address
+(``how did birth spacing respond to these changes, especially the introduction and spread 
+of sex selection?'') and the two associated questions addressing the effects of changes in 
+birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
+estimates?'' and `` how do the changes in birth spacing and the increased use of abortions 
+impact children's chances of survival?'').
 

### 2020-06-23 paper/sex_selection_spacing-ver4.tex
Add key independent variables/concepts and outcomes
- Clarify hazard model set-up
- Add main outcomes and "explanatory" variables
- Explain fertility comparison
- Discuss infant mortality model

@@
 % How the study progresses
-To investigate how birth spacing has changed over time and across groups with the introduction 
-of sex selection, I apply a competing risk hazard model to the birth histories of Hindu 
-women, covering the period 1972 to 2016, using data from the four National Family and 
-Health Surveys (NFHS).
-The model directly incorporates the effects of sex-selective abortions on birth intervals
-and the likelihood of a son, but it also works with no sex selection.
-The empirical model allows me to predict fertility, taking into
-account both the likelihood of parity progression and the likelihood of having a child of 
-a specific sex.
-
-I use the same data to examine how infant mortality risk has changed with the changing 
-birth spacing and whether sex selection affects infant mortality.
+To investigate how birth spacing has changed over time and across groups with the 
+introduction of sex selection, I use a competing risk hazard model with two exit 
+states: the birth of a girl or the birth of a boy. 
+I apply the model to the birth histories of Hindu women covering 1972 to 2016 using 
+data from the four National Family and Health Surveys (NFHS).
+
+The primary outcomes I examine are average birth intervals, the sex ratio of births, 
+and the likelihood of a next birth. 
+Because sex selection might affect the distribution of birth intervals, I also
+examine the 25th and 75th percentiles of birth intervals. 
+I estimate the model across four periods to capture the changing access and 
+legality of sex selection. 
+The key explanatory variables are maternal education, the sex composition of previous 
+children, and area of residence.
+
+The empirical model allows me to predict cohort fertility. 
+To examine to what extent tempo effects bias our standard fertility measures, I compare 
+this predicted cohort fertility with fertility calculated from age-specific fertility rates.
+
+I use the same data to study how infant mortality risk has changed with the changing 
+birth spacing and whether sex selection directly affects infant mortality. 
+The explanatory variables are the same as for the spacing analysis, except for the 
+addition of birth spacing and index child sex.
 

### 2020-06-26 paper/sex_selection_spacing-ver4.tex
Edit for clarity and conciseness
Down to 879 words, not including references

@@
 % Background
-India saw many positive changes over the last four decades:
+India experienced many positive changes over the last four decades:
 the economy grew substantially,
@@
 
-However, India also witnessed the appearance of sex selection---the selective 
-abortion of female fetuses based on prenatal sex determination. 
-Sex selection became available in the mid-eighties with the introduction of technologies 
-such as ultrasound and amniocentesis. 
+However, India also witnessed the advent of sex selection---the selective abortion of 
+female fetuses based on prenatal sex determination---with the introduction of ultrasound 
+in the mid-eighties.
 Combined with continued strong son preference, the result was a dramatic increase in the 
@@
 % Questions addressed and why valuable
-The main question I examine is: how did birth spacing respond to these
-changes, especially the introduction and spread of sex selection? 
+The main question here is: how did birth spacing respond to these changes, especially 
+the spread of sex selection? 
 The motivation is twofold.
@@
 The increase consists of three parts. 
-First, after an abortion, the uterus needs at least two menstrual cycles to recover; 
-otherwise, the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
-Second, the waiting time to conception is between one and six months. 
+First, after an abortion, the uterus needs at least two menstrual cycles to recover, 
+or the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
+Second, the waiting time to conception is one to six months. 
 Finally, sex determination tests are reliable only from three months of gestation. 
@@
 Second, more female education, higher household income, and low and declining female labor 
-force participation are all also likely to impact birth spacing. 
-Hence, the combined changes in birth spacing in India may be much more substantial than
- what we have observed in other countries.
-
-Studying birth spacing is valuable because it contributes to our knowledge about 
-fertility decisions and because of birth spacing's potential effects on outcomes such as 
-fertility measures and mortality. 
-To understand the effects of changes in birth spacing, I focus on two questions.
-
-First, to what extent do changes in birth spacing bias our standard fertility estimates?
-Tempo effects from longer birth intervals make the total fertility rate a downward biased 
-estimate of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
+force participation are all likely to impact birth spacing. 
+The combined changes in birth spacing may, therefore, outpace what we have observed in 
+other countries.
+
+Studying birth spacing contributes to our understanding of fertility decisions, but, equally 
+important, birth spacing affects the reliability of our fertility measures and may 
+impact mortality. 
+To understand these effects, I address two additional questions.
+
+First, did birth spacing changes bias the fertility estimates for India?
+The tempo effect from longer birth intervals makes the total fertility rate a downward 
+biased estimate of cohort fertility. \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
 Hence, if birth intervals increased substantially over time, India's fertility may 
@@
 children's chances of survival?
-In India, the duration to the next birth has traditionally been shorter with fewer sons, 
-which likely contributed to the higher mortality and morbidity risk for girls
+In India, birth intervals have traditionally been shorter with fewer sons, contributing 
+to the higher mortality risk for girls
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
-Longer birth spacing then potentially lowers mortality and morbidity risk 
+Longer birth spacing may, therefore, lower mortality 
 \citep{Conde-Agudelo2012,Molitoris2019}.
-There may, however, be counteracting effects if the longer spacing arises because of 
+A counteracting effect is, however, possible if the longer spacing arises because of 
 multiple abortions. 
-There has, so far, been no attempt to examine how infant mortality has responded 
-to the increase in sex selection.
+Nevertheless, there has been no attempt to examine how infant mortality changed with 
+the increase in sex selection.
 
 % How the study progresses
-To investigate how birth spacing has changed over time and across groups with the 
-introduction of sex selection, I use a competing risk hazard model with two exit 
-states: the birth of a girl or the birth of a boy. 
+To investigate how birth spacing has changed, I use a competing risk hazard model with 
+two exit states: the birth of a girl or the birth of a boy. 
 I apply the model to the birth histories of Hindu women covering 1972 to 2016 using 
@@
 and the likelihood of a next birth. 
-Because sex selection might affect the distribution of birth intervals, I also
+Because sex selection might also affect the distribution of birth intervals, I furthermore
 examine the 25th and 75th percentiles of birth intervals. 
@@
 legality of sex selection. 
-The key explanatory variables are maternal education, the sex composition of previous 
+The key variables are maternal education, the sex composition of previous 
 children, and area of residence.
@@
 The empirical model allows me to predict cohort fertility. 
-To examine to what extent tempo effects bias our standard fertility measures, I compare 
-this predicted cohort fertility with fertility calculated from age-specific fertility rates.
-
-I use the same data to study how infant mortality risk has changed with the changing 
-birth spacing and whether sex selection directly affects infant mortality. 
-The explanatory variables are the same as for the spacing analysis, except for the 
-addition of birth spacing and index child sex.
+To examine whether tempo effects bias our standard fertility measures, I compare 
+the predicted cohort fertility with fertility calculated from age-specific fertility 
+rates.
+
+I use the same data to study how infant mortality changed with birth spacing and 
+the increasing use of sex selection. 
+The key explanatory variables remain the same, except for the addition of birth spacing 
+and the sex of the index child.
 
@@
 
-First, birth intervals have increased for all education groups over the four decades, but 
-more so, the higher the parity and the higher the education. 
-Women most likely to use sex selection---well-educated women with no sons---had the most 
+First, over the four decades, average birth intervals lengthen for all, but most for higher 
+parities and more educated women. 
+Women most likely to use sex selection---well-educated with no sons---had the most 
 substantial lengthening of birth intervals and the most biased sex ratios. 
-As a result, we now see cases that reverse the traditional spacing pattern, with women 
-with no sons having \emph{longer} birth intervals than women with sons. 
-Those least likely to use sex selection---women with less education in rural areas---still 
-follow the traditional pattern of short spacing when they have girls and little evidence 
-of sex selection.
-
-Second, there is little change in the likelihood of having a very short birth interval. 
-Hence, the increased average spacing comes mainly from the longer birth intervals getting 
-even longer, primarily driven by substantial use of sex selection. 
-The exception to this result is that those better-educated women who have a very high 
-predicted use of sex selection conceive later precisely because the next child is almost 
-certainly a boy.
-
-Third, the fertility rate substantially overestimated how fast cohort fertility fell 
-in the 1990s and early 2000s when spacing began to increase.
-Although predicted cohort fertility and the fertility rate have lately begun to converge,
-the predicted cohort fertility is still ten to twenty percent higher than the
-fertility rate.
-Furthermore, even with the convergence, predicted cohort fertility is still at or above 
-replacement level for all but the best-educated urban women.
-
-Finally, infant mortality risk has declined substantially over time for all groups,
-but fastest for the lower education groups, who are now close to the level of women with 
-the most education.
-However, the mortality risk is still inversely related to education level, especially for 
-very short birth intervals.
-There is no evidence that the increasing use of sex selection is associated with higher 
-mortality risk.
+As a result, we now see cases that reverse the traditional spacing pattern, with some 
+women with no sons having \emph{longer} birth intervals than those with sons. 
+Those least likely to use sex selection---less-educated in rural areas---still follow 
+the traditional pattern of short spacing when they have girls and little evidence of sex 
+selection.
+
+Second, the likelihood of a very short birth interval changed little. 
+Hence, the increased average spacing comes mainly from longer birth intervals getting even 
+longer, primarily because of sex selection. 
+The exception is that those better-educated women with a very high predicted use of sex 
+selection conceive later and are less likely to have a very short birth interval, precisely 
+because their next child is almost certainly a boy.
+
+Third, the fertility rate substantially overestimated how fast cohort fertility fell in the 
+1990s and early 2000s as spacing began to increase. 
+Although the two have lately been converging, the predicted cohort fertility is still ten to 
+twenty percent higher than the fertility rate. 
+Furthermore, predicted cohort fertility is still at or above replacement level for all but 
+the best-educated urban women.
+
+Finally, infant mortality has declined substantially over time for all groups, but fastest 
+for the less educated, who are now close to the level of the best-educated women. 
+However, mortality is still inversely related to education level, especially for very short 
+birth intervals. 
+There is no evidence that the increasing use of sex selection is associated with higher mortality.
 

### 2020-06-28 paper/sex_selection_spacing-ver4.tex
Highlight what question is answered by section
Also edited Introduction to avoid duplication and to cut text from
other sections

@@
 
-First, did birth spacing changes bias the fertility estimates for India?
-The tempo effect from longer birth intervals makes the total fertility rate a downward 
-biased estimate of cohort fertility. \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
-Hence, if birth intervals increased substantially over time, India's fertility may 
-be higher than generally accepted.
-
-Second, how do the changes in birth spacing and the increased use of abortions impact 
-children's chances of survival?
+First, did changes in birth spacing bias the fertility estimates for India? 
+With longer spacing, mothers will be older at each parity, and this tempo effect makes the 
+total fertility rate a downward biased estimate of cohort fertility
+\citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}. 
+Hence, if birth intervals increased substantially, India's fertility may be higher 
+than generally accepted.
+
+Second, what is the relationship between infant mortality and the changes in birth spacing 
+and sex selection?
 In India, birth intervals have traditionally been shorter with fewer sons, contributing 
@@
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
-Longer birth spacing may, therefore, lower mortality 
-\citep{Conde-Agudelo2012,Molitoris2019}.
-A counteracting effect is, however, possible if the longer spacing arises because of 
-multiple abortions. 
+Hence, longer birth spacing, whether from sex selection or secular changes, may reduce 
+mortality \citep{Conde-Agudelo2012,Molitoris2019}.
+However, a counteracting effect is possible if longer birth intervals arise from multiple 
+abortions since the short duration between \emph{pregnancies} could increase mortality. 
 Nevertheless, there has been no attempt to examine how infant mortality changed with 
@@
 
-To provide a conceptual framework for understanding how birth spacing
-may respond to the substantial changes in income, female education, and
-female labor force participation that India has experienced, I discuss
-in this section relevant theories and prior findings on birth spacing.
+To provide a framework for understanding how birth spacing responded to the advent 
+of sex selection and the substantial changes in income, education, and labor force 
+participation, I next discuss relevant theories and prior findings on birth spacing.
 
@@
 
-\section{How Birth Spacing has Changed\label{sec:results}}
-
-% [How to read tables]
-I estimate the model for each spell/education/period subsample, the results of which I use 
-to predict average birth spacing, sex ratio, and the probability of having a birth in that 
-spell.
+\section{How Birth Spacing Changed\label{sec:results}}
+
+% Explain question and what I am doing
+The first question I address is how birth spacing responded to the significant changes, 
+especially the spread of sex selection, that India experienced. 
+I estimate the competing risk hazard model for each spell/education/period subsample and 
+then predict average birth spacing, sex ratio, and the probability of having a birth 
+in that spell.
+
 Figures \ref{fig:bootstrap_low} through \ref{fig:bootstrap_highest}
-show these predicted outcomes for the four education levels separated by the area of 
-residence.%
+show the predicted outcomes for the four education levels by area of residence.%
 \footnote{
@@
 
+[TK this is not clear]
 Second, even with sex selection and the associated increases in expected spacing, the
@@
 
-Average spacing is a convenient way to understand the overall changes in behavior but may 
-hide crucial differences in the distribution of spacing.
-For example, if sex selection drives the changes in birth spacing, most of the increase in 
-spacing will come from people who have two or more pregnancies rather than one and,
-therefore, from changes in the longer intervals.
-In contrast, a general increase in spacing would show up as an increase in spacing across 
-the board.
+To better understand what factors are behind the changes in average spacing, I next 
+examine the distribution of birth spacing---represented by the 25th and 75th percentiles 
+of predicted birth intervals. 
+This approach can capture differences across groups with similar changes in average spacing. 
+For example, imagine that sex selection is behind an increase in average birth spacing, 
+but that women still try to conceive early. 
+In that case, we should see little change in the 25th percentile, but the 75th percentile 
+spacing becomes much longer because those who use sex selection will have two or more 
+pregnancies rather than one. 
+In contrast, a general increase in spacing would show up as lengthening of both percentiles.
 
@@
 
-A potential effect of the substantial increases in birth spacing is that TFR may 
-underestimate cohort fertility, at least temporarily.
-I, therefore, compare predicted fertility based on a variation of the TFR and the 
-hazard model by urban/rural and education groups in Table \ref{tab:fertility}.
+The tempo effect from longer birth intervals means that the total fertility rate may 
+underestimate cohort fertility. 
+The next question I address is, therefore, to what extent did the changes bias the 
+fertility estimates for India? 
+To this end, I compare fertility based on a variation of the total fertility rate with 
+predicted cohort fertility from the hazard model results.
 
@@
 
-To make the fertility rate comparable to the hazard model, it uses only births up to 
-parity four, and is, therefore, not directly comparable to those in the NFHS reports.
+Table \ref{tab:fertility} shows the two fertility measures by urban/rural and education.
+Because the hazard model predictions only use births up to parity four, I calculate
+fertility rates using only the same births.
+Hence, my fertility rates are not directly comparable to those in the NFHS reports.
 Otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
@@
 
-The prior literature shows that shorter birth spacing, especially very short spacing,
-is associated with a higher risk of infant mortality.
-Hence, the longer spacing, both from the increasing use of sex-selective abortions and
-from secular changes, may directly reduce infant mortality.
-
-To the extent that the longer birth intervals arise from multiple abortions,
-the short duration between \emph{pregnancies} could, however, increase mortality risk.
-This section addresses how infant mortality has changed and whether there is evidence
-of a negative impact of sex-selective abortions.
-
-Starting with the sample used for estimating birth spacing, I select children born 
-more than 12 months before the survey month.
-I restrict the analyses to parities two and three because of the small number
-of births and deaths for parity four.
-Furthermore, I do not show results for women with twelve or more years of
-education for the 1972--84 period because of the low number of women.
+The final question I address is whether there is an association between infant mortality 
+and increases in birth spacing and sex selection. 
+Starting with the sample used for estimating birth spacing, I select children born more 
+than 12 months before the survey month. 
+I restrict the analyses to parities two and three because of the small number of births 
+and deaths for parity four. 
+Furthermore, I do not show the results for women with twelve or more years of education 
+for the 1972--84 period because of the small number of women.
 
@@
 low as it is for better-educated women \citep{Kozuki2013,Molitoris2019}.
-However, in prior research, the fixed effects results and linear probability do not 
+However, in prior research, the fixed effects and linear probability results do not 
 deviate substantially.

### 2020-06-28 response/response-demography-3.tex
Respond to outline and question-by-section comments

--- 2020-06-16 response/response-demography-3.tex
@@
 
+TK review titles of figures and table to be better reflect the
+analyses undertaken.
+
 \end{enumerate}
@@
 
-[Response:]
+[Response:] I have rewritten the Introduction to emphasize the main question I address
+(``how did birth spacing respond to these changes, especially the introduction and spread 
+of sex selection?'') and the two questions addressing the effects of changes in 
+birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
+estimates?'' and `` how do the changes in birth spacing and the increased use of abortions 
+impact children's chances of survival?'').
+
+Following the three questions, I now outline how the study progresses focusing on 
+how I examine each of the three questions, including the key outcomes and key explanatory 
+variables.
+To prevent exceeding the word count I have also edited the entire introduction.
+Although sligthly longer than original, it is still less than 900 words 
+(not counting references).
+
+I have edited the introduction of each section to highlight what I question
+I am addressing.
+Furthermore, I have removed some of the repetition in, for example, the
+discussion of tempo effects and mortality, so that the motivation is now only
+in the Introduction rather than being spread over the Introduction and the
+relevant sections.
+
+TK I address the issue of the figure and table title above.
 

### 2020-06-28 paper/sex_selection_spacing-ver4.tex
Initial combine of spacing sections w/o edits

@@
 
-To what extent has the introduction of sex selection changed birth spacing across sex 
-compositions?
-There are three broad groups in the data.
-
-First, women who have only girls but do not use sex selection had, and continue to have,
-the shortest spacing, as shown, for example, by rural women with no education.
-For this group, spacing is shortest with only girls across all spell, and the difference
-between sex compositions have even grown over time.
-
-[TK this is not clear]
-Second, even with sex selection and the associated increases in expected spacing, the
-intervals for the other sex compositions have increased even more, and the relative 
-pattern, therefore, remains more or less the same.
-An example is for the second spell for women with eight to eleven
-and twelve or more years of education.
-
-Finally, women with the most biased sex ratios have the longest spacing in the 
-absence of boys, and this spacing is longer than for the other possible sex 
-compositions.
-The most extreme example is that with a sex ratio for the best-educated urban women  
-approaching 80 percent, the 42 months birth intervals with two girls is seven months 
-longer than with at least one boy.
-However, even urban women with eight to eleven years of education show the longest 
-intervals with only girls in the last period.
-
-\section{Distribution of Birth Spacing}
+\subsection{Distribution of Birth Spacing}
 
@@
 
-\section{What has Happened to Fertility?\label{sec:fertility}}
+\subsection{Interpretation}
+
+To what extent has the introduction of sex selection changed birth spacing across sex 
+compositions?
+There are three broad groups in the data.
+
+First, women who have only girls but do not use sex selection had, and continue to have,
+the shortest spacing, as shown, for example, by rural women with no education.
+For this group, spacing is shortest with only girls across all spell, and the difference
+between sex compositions have even grown over time.
+
+[TK this is not clear]
+Second, even with sex selection and the associated increases in expected spacing, the
+intervals for the other sex compositions have increased even more, and the relative 
+pattern, therefore, remains more or less the same.
+An example is for the second spell for women with eight to eleven
+and twelve or more years of education.
+
+Finally, women with the most biased sex ratios have the longest spacing in the 
+absence of boys, and this spacing is longer than for the other possible sex 
+compositions.
+The most extreme example is that with a sex ratio for the best-educated urban women  
+approaching 80 percent, the 42 months birth intervals with two girls is seven months 
+longer than with at least one boy.
+However, even urban women with eight to eleven years of education show the longest 
+intervals with only girls in the last period.
+
+\section{What Happened to Fertility?\label{sec:fertility}}
 
@@
 fertility rates using only the same births.
-Hence, my fertility rates are not directly comparable to those in the NFHS reports.
-Otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
+Hence, my fertility rates are not directly comparable to those in the NFHS reports,
+but otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
 I calculate age-specific fertility rates for five-year age groups using the number of 

### 2020-06-30 paper/sex_selection_spacing-ver4.tex
Edit for clarity and include summary of results in spacing section

@@
 
-\subsection{Interpretation}
-
-To what extent has the introduction of sex selection changed birth spacing across sex 
-compositions?
+\subsection{Sex Selection and Birth Spacing}
+
+The results above show that average birth intervals increased over time across all groups 
+and that these increases are larger for higher parities and with more schooling. 
+Furthermore, the increases come predominately from the longer intervals getting even 
+longer while there is little change in the length of the shortest intervals.
+
+What do these results tell us about the extent to which the introduction of sex selection 
+changed birth spacing across sex compositions? 
 There are three broad groups in the data.
 
-First, women who have only girls but do not use sex selection had, and continue to have,
-the shortest spacing, as shown, for example, by rural women with no education.
-For this group, spacing is shortest with only girls across all spell, and the difference
-between sex compositions have even grown over time.
-
-[TK this is not clear]
-Second, even with sex selection and the associated increases in expected spacing, the
-intervals for the other sex compositions have increased even more, and the relative 
-pattern, therefore, remains more or less the same.
-An example is for the second spell for women with eight to eleven
-and twelve or more years of education.
-
-Finally, women with the most biased sex ratios have the longest spacing in the 
-absence of boys, and this spacing is longer than for the other possible sex 
-compositions.
-The most extreme example is that with a sex ratio for the best-educated urban women  
-approaching 80 percent, the 42 months birth intervals with two girls is seven months 
-longer than with at least one boy.
-However, even urban women with eight to eleven years of education show the longest 
-intervals with only girls in the last period.
+The first group consists of women who do not use sex selection even if they have only 
+girls, such as rural women with no education. 
+For this group, the shortest spacing---across all spells---is when they have only girls. 
+Notably, the difference in birth intervals across sex compositions has even grown over 
+time as spacing when sons are present increased.
+
+In the second group are women who use sex selection and who, therefore, show the expected 
+associated increase in birth intervals for those sex compositions. 
+However, the intervals for their other sex compositions have increased even more. 
+The result is that the relative pattern remains more or less the same. 
+An example of this group is women with eight more years of education in the second spell.
+
+The final group consists of those women, who, in the absence of a son, have the most 
+biased sex ratios and the longest birth intervals, and where this spacing is longer than 
+for the other possible sex compositions. 
+The most extreme example is best-educated urban women with two girls with a sex ratio 
+approaching 80 and an average birth interval of 42 months. 
+This birth interval is seven months longer than with at least one boy.
+
+In summary, although birth spacing has increased over time with improving economic 
+conditions and falling fertility, it is clear that most of the increases in birth spacing 
+come from the increased use of sex selection. 
+The most substantial increase over the four decades is a full year for the best-educated 
+women with two girls.
 

### 2020-06-30 paper/sex_selection_spacing-ver4.tex
Reorganize spacing sections (#12)
* Combine spacing sections and add a summary of answer to main question

* Explain reorganized spacing section in the response letter

@@
 The result is that the relative pattern remains more or less the same. 
-An example of this group is women with eight more years of education in the second spell.
+An example is women with eight more years of education in the second spell.
 
@@
 for the other possible sex compositions. 
-The most extreme example is best-educated urban women with two girls with a sex ratio 
+The most extreme example is best-educated urban women with two girls, who have a sex ratio 
 approaching 80 and an average birth interval of 42 months. 
@@
 In summary, although birth spacing has increased over time with improving economic 
-conditions and falling fertility, it is clear that most of the increases in birth spacing 
-come from the increased use of sex selection. 
+conditions and falling fertility, most of the increases in birth spacing come from the
+increased use of sex selection. 
 The most substantial increase over the four decades is a full year for the best-educated 
-women with two girls.
+women with two girls, which is the group with the most biased sex ratio.
 

### 2020-07-06 response/response-demography-3.tex
Reorganize spacing sections (#12)
* Combine spacing sections and add a summary of answer to main question

* Explain reorganized spacing section in the response letter

@@
 
-[Response:] I have rewritten the Introduction to emphasize the main question I address
+[Response:]
+
+I have rewritten the Introduction to emphasize the main question I address
 (``how did birth spacing respond to these changes, especially the introduction and spread 
@@
 
+Finally, I have made the discussion of the distribution of spacing a subsection
+of the spacing section and combined the discussion of the results to another new 
+subsection as well.
+I hope this will make it easier for the reader to see the answer to the main
+question of the paper.
+
 TK I address the issue of the figure and table title above.
@@
 [Response:]
+
+To address this, and the questions about theories of female labor supply below, I have
+combined and reorganized the background and conceptual framework sections.
+I begin this combined section with a discussion of the three main reasons for using 
+maternal education as a key stratification measure.
+First, higher female education is associated with lower fertility, and, thereby, with
+potential increased use of sex selection.
+Second, female labor force participation in India, as well as other developing countries, 
+tend to first decrease and then increase with education.
+Finally, child morbidity and mortality decreases the better educated the mother.
+
+After the discussion of why female education is a key variable, I explain the choice
+of cut-offs, which is based on the prior literature on fertility and son preference in 
+India and the NFHS reports.
+The exception to the the cut-offs in the NFHS reports is that I combine
+the <5 years and 5--7 years of schooling completed and 
+the 8--9 and 10--11 years of schooling completed to reach sufficient sample sizes.
+
+This grouping also allows me to capture the U-shape in female labor force participation.
+The upper level of education could be split into having graduated secondary and having 
+graduated with a university degree since women with a completed university degree have 
+a higher labor force participation, but the sample of university graduates is too small 
+to allow for estimations, especially for the first three rounds of the surveys.
+Furthermore, with four groups there is already a substantially number of results to 
+present.
 
@@
 [Response:]
+
+I agree, and to help address this, and the question about maternal education cut-offs
+above, I have combined and reorganized the conceptual framework and background sections.
+
+The main relevant theory on female labor force participation and education is the income 
+and substitution effects discussed in \citet{Hotz1997} and \citet{schultz97}.
+With the reorganization of the sections, the introduction of this theory now more naturally 
+follows the discussion of increasing education in India.
+I then discuss the declining female labor force participation and that it may come
+about because of the rapid income increases.
+
+Since the Goldin theory is not central to this argument, I have removed the sentence 
+on the theory.
+It is worth pointing out, however, that a decline in female labor force participation  
+is in line with the hypothesis of a U-shaped labor force participation as a country 
+develops \citep{Goldin1994}.
+What is ``surprising" for India is that we have not yet seen any evidence of the upward 
+sloping part.
+I do think that the combination of rapidly rising male income, son preference, and 
+relatively meager job opportunities for women with, say, high school education have a lot 
+to do with this.
 
@@
 
+The discussion of labor supply was disjointed and unclear because I had split the 
+background and conceptual framework sections, making it difficult to see the connection.
+As explained above, I have combined and reorganized those two sections into one and
+removed the Goldin theory discussion since it is not directly relevant to my main
+argument of why labor supply is relevant.
+
 \item Overall, I felt that the paper is still quite densely written and

### 2020-07-06 paper/sex_selection_spacing-ver4.tex

@@
 
-\section{Female Education and Labor Force Participation in India}
-
-To set the stage for the subsequent analyses, I first describe how female education
-and labor force participation has changed.
-Both are potentially important factors in the birth spacing decision, as I discuss
-in the next section.
-
-Female educational attainment has increased substantially over time.
+% Combine descriptive and theory sections into one
+
+\section{Background and Conceptual Framework}
+
+To set the stage for the subsequent analyses and provide a conceptual framework for 
+understanding birth spacing, I first discuss female education and labor force 
+participation in India and relevant theories on birth spacing.
+
+% [Female education]
+
+Female education is a crucial explanatory variable here for three reasons.
+First, higher female education is associated with lower fertility and increased use of 
+sex selection
+\citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
+Second, female labor force participation in India, as in other developing countries, 
+first decreases and then increases with education
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
+Finally, child mortality decreases with maternal education
+\citep{Rosenzweig1982a,Whitworth2002,Maitra2008}.
+
+[TK where to put son preference discussion?]
+
+I divide eduction into four groups: no education, one to seven years, eight to eleven 
+years, and twelve and more years.
+The latter two correspond to having completed primary and completed secondary school, 
+respectively.%
+\footnote{
+Although there are variations by state, elementary education in India consists of a 
+primary school covering grades one through five and an upper primary---or middle 
+school---covering grades six through eight. 
+Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
+and eleven and twelve for ``upper secondary.''
+}
+To ensure that the results are comparable with the prior literature on fertility
+and mortality in India, I follow the NFHS reports, except that I combine the 
+less than five years and five to sevens years of schooling completed and the eight to nine 
+and ten to eleven years of schooling completed.
+There is a trade-off between having groups large enough for the analyses below and having 
+groups detailed enough to capture differences in behavior across education levels, such as 
+the U-shaped relationship between education and labor force participation.
+
+% [what has happened to education]
+Female education has increased substantially over time in rural and urban areas but 
+is still substantially higher in urban than in rural areas.
 Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
@@
 twenty years or older, whether married or not, based on the four rounds of the NFHS.
-The education groups are no education, one to seven years, and eight to eleven years,
-and twelve years and above.
+In rural areas, women with no education have gone from 90 percent for the 1930s cohorts to 
+less than 20 percent for the 1990s cohorts.
+Women with eight or more years of education have gone from almost zero for the 1930 cohort 
+to more than sixty percent for the 1990s cohorts, with about half in the eight to eleven 
+group and the other half in the twelve plus group.
+In urban areas, the proportions with no education or one to seven years have declined 
+to just below ten percent each.
+Most of the increase in urban female education came from the twelve plus group, which 
+now account for more than half of all urban women for the lastest cohorts.
 
@@
 
-For rural areas, the percentage of women with no education has gone from around 90 percent
-for the 1930s cohorts to less than 20 percent for the 1990s cohorts. 
-The proportion of women with one to seven years of education has remained remarkably
-constant at around ten percent.
-The difference is made up by the women with eight or more years of education, who have
-gone from almost zero for the 1930 cohort to more than sixty percent for the 1990s cohorts,
-with about half in the eight to eleven years group and 
-the other half in the twelve years or more group.
-
-Female education is higher in urban areas than in rural areas.
-Around sixty percent of urban women born in the 1930s had no education, 25 percent had
-between one and seven years, about ten percent had eight or more years of education, and 
-only five percent has twelve years or more.
-The proportions with no education and one to seven years have both declined to just below 
-ten percent for the latest cohort.
-Although the proportion of women with eight to eleven years of education has increased
-to about twenty, most of the increase in urban female education has come from the 
-twelve plus group, which now account for more than half of all urban women.
-
-Even as the level of female education has increased, the female labor force participation 
-in both urban and rural areas has stagnated or decreased
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-A decline in female labor force participation at the beginning of development is
-consistent with the hypothesis of a U-shaped labor force participation as a country
-develops \citep{Goldin1994}.
-India's female labor force participation is, however, lower than most other
-countries and more in line with countries in the Middle East and North Africa, and
-does not yet show any signs of increasing
-\citep{Klasen2015,Chatterjee2018}.
-
-The NFHS data show a U-shaped relationship between education and working for married
-women, with the highest percent working for women with either no education 
-or with twelve or more years and the lowest for women with eight to eleven years of 
-education.%
-\footnote{
-See Appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
-}
-Women are more likely to report working if they live in rural than urban areas 
-and the older they are.
-For married women, the percentage currently working changes relatively little over time. 
-All education and age groups have, however, become substantially more likely to work for 
-a family member.
-
-The increases in female educational attainment imply that access to education has 
-expanded beyond the higher castes. 
-One possible effect of the rapid expansion in female education, and the 
-associated change in the composition of better-educated women, is that the behavior
-of the better-educated would change. 
-However, ``Sanskritization'' implies that as lower castes females gain access to 
-education and their husbands' income increases, the women adopt higher caste 
-norms such as stronger son preference and a retraction from the formal labor 
-market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
-The low and declining female labor force participation is an indication that this
-process still operates.
-
-\section{Birth Spacing: Mechanisms and Prior Findings}
-
-To provide a framework for understanding how birth spacing responded to the advent 
-of sex selection and the substantial changes in income, education, and labor force 
-participation, I next discuss relevant theories and prior findings on birth spacing.
-
-The standard economic argument for the predominant association between
-increasing female education and shorter spacing is that parents incur
-time costs when they have children \citep{Hotz1997,schultz97}.
+% [female labor force participation]
+
+The standard economic argument for spacing becoming shorter with increasing female education 
+is that parents incur time costs when they have children \citep{Hotz1997,schultz97}.
 Specifically, if having children require the mother to reduce her market work, parents 
@@
 
+However, even as the level of female education has increased, the female labor force 
+participation in both urban and rural areas has stagnated or decreased
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
+India's female labor force participation is now lower than most other countries and does 
+not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
+In line with previous research, the NFHS data show a U-shaped relationship between 
+education and working for married women, with the highest percent working for women with 
+either no education or twelve or more years and the lowest for women with eight to 
+eleven years of education.%
+\footnote{
+See Appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
+}
+
 The low and declining female labor force participation, especially for younger women, 
-suggests, however, that families face little incentive to space children more closely 
+suggests that families face little incentive to space children more closely 
 together for economic reasons.
@@
 \citep{Klasen2015,Bhargava2018}.
-Second, women’s labor supply appears to be more negatively elastic to their husbands' 
-wages than it is positively elastic to their wages \citep{Bhargava2018}.
+Second, women’s labor supply appears to be more negatively elastic to husbands' 
+wages than positively elastic to own wages \citep{Bhargava2018}.
+
+% [sex selection]
+
+The introduction of sex selection allows parents to avoid giving birth to girls but 
+increases the expected duration to the next birth.
+Theory suggests that sex selection increases with lower desired fertility and with
+higher parity for a given desired number of children \citep{Portner2015b}.
+Sex selection is more widespread among better-educated than less-educated and among urban 
+than rural women, which is consistent with lower desired fertility increasing the
+use of sex selection 
+\citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
+Better-educated and urban women also tend to live in households with higher income, which 
+better enables them to access prenatal sex determination and lowers the relative costs of 
+using sex selection and have long birth intervals.
 
 The combination of rising incomes and continued son preference may lead to even longer 
-spacing than the standard income effect alone predicts.
+spacing than expected from the income effect alone.
 As women's education increases, their productivity in the production of offspring human 
@@
 With relatively more boys born because of increased access to sex-selective 
-abortions and an increasing potential income for (male) offspring, demand for 
+abortions and the increasing income potential for (male) offspring, demand for 
 better-educated women can increase, even if they do not participate in the labor market 
 \citep{Behrman1999}.
+
 If more and ``better'' parental attention per child results in higher child ``quality,'' 
-we should expect longer birth intervals 
-\citep{Zajonc1975,Zajonc1976,Razin1980}.
-The evidence on spacing's effect on child quality measures such as IQ 
-and education is, however, mixed for developed countries and non-existing 
-for developing countries
+we should expect longer birth intervals \citep{Zajonc1975,Zajonc1976,Razin1980}.
+However, the evidence on spacing's effect on child quality measures such as IQ 
+and education is mixed for developed countries and non-existing for developing countries
 \citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
@@
 
-% While one might expect that increasing income and female education would also lengthen
-% average birth spacing through better access and knowledge of contraception, the empirical 
-% relationship between contraception use and birth spacing is ambiguous 
-% \citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
-% Furthermore, the ability to successfully use ``low efficacy'' contraceptive methods, 
-% such as the rhythm method, is increasing in education, while there is no difference 
-% across education levels when it comes to modern contraceptives such as pills or 
-% injectables \citep{Rosenzweig1989}.
-
-The introduction of sex selection allows parents to avoid the birth of girls
-but increases the expected duration to the next birth.
-Theory suggests that sex selection increases with lower desired fertility, and, for a 
-given desired number of children, the higher the parity \citep{Portner2015b}.
-The increased use of sex selection in India with education and in urban
-areas is consistent with a lower desired fertility for both groups
-\citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Better-educated and urban women also tend to live in households with higher income, which 
-better enables them to access prenatal sex determination and lowers the relative costs of 
-using sex selection and have long birth intervals.
-
-We may even observe a ``delay'' effect, where parents conceive later because they know 
-that short spacing is detrimental to the next child's health and that the next child is 
-more likely to be a boy because of access to sex selection.
-Working in the opposite direction is that women with more education can, in principle, 
-space their children closer together without substantially increasing child mortality 
-risk.
-Given the apparent lack of pressure to return to the labor force,
-this effect is, however, likely to be small.
+If parents realize that longer spacing leads to better child outcomes, we may even observe 
+later conception, especially when, with sex selection, the next child is likely to be a boy.
+Working in the opposite direction of this "delay" effect is that women with more education 
+can, in principle, space their children closer together without substantially increasing 
+child mortality risk. 
+However, given the apparent lack of pressure to return to the labor force, this effect is 
+likely small.
+
+% Sanskritization
+
+The increases in female educational attainment imply that access to education has 
+expanded beyond the higher castes. 
+One possible effect of the associated change in the composition of better-educated women 
+is that this group's behavior would change.
+However, ``Sanskritization'' implies that as lower castes females gain access to 
+education and their husbands' income increases, they adopt higher caste 
+norms such as stronger son preference and a retraction from the formal labor 
+market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
+The low and declining female labor force participation is an indication that this
+process still operates.
+
+% Summary / hypotheses
 
@@
 on child outcomes.
-As desired fertility decreases with increasing education, I, furthermore, expect 
-birth spacing to increase the most among the better-educated because their household
-income increases the most---even with declining female labor participation---and 
-their use of sex selection.
+Furthermore, I expect birth spacing to increase the most among the better-educated 
+because their household income increases the most---even with declining female labor 
+participation---and their use of sex selection.
 Even with the substantial increase in the number of better-educated women, 
@@
 quickly increased \citep{Sudha1999,bhat06,Grover2006}.
-In 1994, the Prenatal Diagnostic Techniques (PNDT) Act made determining and communicating 
+In 1994, the Prenatal Diagnostic Techniques Act made determining and communicating 
 the sex of a fetus illegal.%
@@
 
-Women with different education levels have different hazard profiles
+The models are estimated separately for each of the four education group to reduce any
+potential problem from including other variables as proportional since
+women with different education levels have different hazard profiles
 \citep{Whitworth2002,Bhalotra2008,Kim2010}.
-Furthermore, as discussed above, the use of sex selection increases with education.
-I, therefore, divide women into four educationgroups: no
-education, one to seven years of education, eight to eleven years of education,
-and twelve and more years of education.
-The models are estimated separately for each group to reduce any
-potential problem from including other variables as proportional.
-
 I capture sex composition with dummy variables for the

### 2020-07-10 paper/sex_selection_spacing-ver4.tex
Clarify spell definition; use birth interval rather than spell length

@@
 spacing to the birth of a girl or a boy differently.
-I, therefore, use a competing risk set-up, which can capture both the non-randomness of
+I, therefore, use a competing risk set-up that captures both the non-randomness of
 the birth outcome and the differential spacing.%
@@
 
-Second, it is unlikely---even in the absence of prenatal sex determination---that 
-characteristics, such as the sex composition of previous births, have the same effects 
-throughout the entire spell, as is assumed by the proportional hazard model.
-If proportionality does not hold, the results are biased.
-The proportionality assumption is especially problematic for higher-order spells where 
-there are substantial differences across groups both in the likelihood of progressing to 
-the next birth and how soon couples want their next child if they are going to have one.
+Second, even without sex selection it is unlikely that characteristics, such as the sex
+composition of previous births, have the same effects throughout the entire birth interval.
+That is, however, the assumption behind the proportional hazard model, and if 
+proportionality does not hold, the results are biased.
+The proportionality assumption is especially problematic for higher-order birth 
+intervals where there are substantial differences across groups both in the likelihood of 
+progressing to the next birth and how soon couples want their next child if they are going 
+to have one \citep{Whitworth2002,Bhalotra2008,Kim2010}.
 
@@
 the proportionality assumption for two reasons. 
-First, sex-selective abortion use varies across groups, which affects birth spacing. 
-Second,
-a household's use of sex selection may vary within a spell, which means
-that the effects of covariates vary within the spell as well.
-
-I, therefore, use a non-proportional hazard specification, which allows the shape of the 
+First, different groups have different levels of sex-selective abortion use and, thereby, 
+birth spacing. 
+Second, within a birth interval, a household's use of sex selection may vary and that
+means that the effects of covariates vary as well.
+
+I, therefore, use a non-proportional hazard specification that allows the shape of the 
 hazard functions to vary across groups.
@@
 states: either a boy or a girl is born.
-The unit of analysis is a spell, the period from nine months after one birth to the next.
+The unit of analysis is a spell---the period from nine months after one birth to the 
+following birth or censoring.
+The spells begin nine months after the previous birth since this is the earliest we should 
+expect to observe a new birth.
+Censoring can happen for three reasons:
+the survey takes place,
+sterilization of the woman or her husband,
+or there are too few births for the method to work.
+
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
@@
 There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
-$J_i$ is a random variable indicating which event took place.
+$J_i$ indicates which event took place.
 The discrete-time hazard rate $h_{ijt}$ is 
@@
 }
-However, to further minimize any potential bias from assuming proportionality, estimations 
-are done separately for different levels of mothers' education and different 
-periods.%
-\footnote{
-I discuss the choice of which variables to use for non-proportionality in more detail
-in the ``Explanatory Variables'' section.
-}
+
+% To further minimize any potential bias from assuming proportionality, estimations 
+% are done separately for different levels of mothers' education and different periods.
+% I discuss the choice of which variables to use for non-proportionality below.
 
@@
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, transforming the data, so each observation is an interval---here equal
+Hence, transforming the data, so each observation is a time period---here equal
 to three months---I can estimate the model using a standard multinomial logit model.
@@
 
-The interpretation of the model coefficients is challenging \citep{thomas96}.
-It is, however, possible to calculate the predicted probabilities of 
-having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
-a set of explanatory variables and not having had a child before that period.
-% , as
-% \begin{align}
-% P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
-% & =  
-% \frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
-% {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
-% \label{eq:probability_boy} \\
-% P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
-% & =  
-% \frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
-% {1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
-% \label{eq:probability_girl}
-% \end{align}
-It is then straightforward to calculate the estimated percentage of children born that 
-are boys, $\hat{Y}$, at each $t$:  
+I use the model to predict birth interval measures, the probability of having a birth, 
+and the sex ratio.%
+\footnote{
+The interpretation of competing risk model coefficients is challenging \citep{thomas96}.
+}
+The sex ratio is based on the estimated percentage of children born at each $t$ that are 
+boys, $\hat{Y}$:  
 \begin{equation}
@@
 { P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-\times 100.
+\times 100,
 \label{eq:probability_son}
 \end{equation}
-Combining the percentage of boys and the likelihood of exiting the spell 
-across all $t$ gives the predicted percent of births that are boys over the entire spell.
+where $b$ and $g$ are the predicted probabilities of having a boy and a girl, respectively,
+conditional on the explanatory variables and not having had a child before $t$.
+Combining the percentage of boys and the likelihood of exiting the spell with a birth
+across all $t$ gives the predicted percent of births that are boys over the entire spell.%
+\footnote{
+With T=2, if 54 and 66 percent of the births are boys and the likelihoods of 
+giving birth 20 and 40 percent, then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent of the
+births are boys.
+}
+The predicted sex ratio shown is the weighted average of the individual predicted sex 
+ratios, using the parity progression probabilities as weights.
 
@@
 
-The data come from the four rounds of the National Family Health Survey
+The data come from the four rounds of the NFHS
 collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.
-The surveys are large: 89,777, 90,303, 124,385, and 699,686 women,
-respectively. NFHS-1 and NFHS-2 surveyed only ever-married women, while
-the later surveys also included never-married.
-
-I exclude visitors, as well as women in any of the following 
+The surveys are large: 89,777, 90,303, 124,385, and 699,686 women, respectively. 
+NFHS-1 and NFHS-2 surveyed only ever-married women, while the two later surveys included 
+never-married.
+
+I focus on the three birth intervals starting from the first birth and ending with the 
+fourth birth.
+I exclude the interval from marriage to the first birth because many are imputed and,
+with falling fertility, few women had five or more births, especially among the 
+better-educated.
+
+I restrict the sample to Hindus, who constitute about 80 percent of India’s population.
+If the use of sex selection differs across groups, assuming that the
+baseline hazard is the same leads to bias. 
+Furthermore, the other groups are each too small to estimate different
+baseline hazards for each and so different that combining them into one
+group would not make sense.
+
+Finally, I exclude visitors, as well as women in any of the following 
 categories: never married; no gauna yet; married more than once; divorced; 
@@
 nine months.
-
-Finally, I restrict the sample to Hindus, who constitute about 80 percent of India’s 
-population.
-If the use of sex selection differs across groups, assuming that the
-baseline hazard is the same leads to bias. 
-Furthermore, the other groups are each too small to estimate different
-baseline hazards for each and so different that combining them into one
-group would not make sense.
 
@@
 drop women married 22 years or more based on the discussion in the Appendix.
+
+To ensure that there are enough births for the method to work, I censor each spell at 96 
+months (eight years) after a woman can first give birth in the spell, which is equivalent 
+to 105 months after the birth of the prior child.
+Less than one percent of observed births occur after the cut-off.
 The final sample consists of 
@@
 % [number] women, with [number] parity one through four births.
-
-I focus on the second through fourth spells, that is, on the intervals from the first 
-birth until at most the fourth birth.
-I exclude the marriage to the first birth spell because many are imputed.
-
-The spells all begin nine months after the previous birth, which is the earliest we should 
-expect to observe a new birth.
-A spell continues until either a child is born or censoring occurs.
-Censoring can happen for three reasons:
-the survey takes place,
-sterilization of the woman or her husband,
-or too few births are observed for the method to work.%
-\footnote{
-Most sterilizations take place right after a woman gives birth, and,
-therefore, do not show up in the samples used. 
-Furthermore, sterilization depends strongly on the sex composition of prior children
-with lower probabilities, the fewer boys. 
-The effect is that the differences in parity progression probabilities are biased 
-downwards.
-}
-For all spells, censoring is set at 96 months (eight years) after a woman can first
-give birth in the spell.
-With these cut-offs, less than one percent of observed births occur after
-the spell cut-off.
 
@@
 
-\subsection{Explanatory Variables}
-
 I divide the explanatory variables into two groups.
@@
 
-The models are estimated separately for each of the four education group to reduce any
-potential problem from including other variables as proportional since
-women with different education levels have different hazard profiles
-\citep{Whitworth2002,Bhalotra2008,Kim2010}.
+I estimate a separate model for each birth interval, education group, and period 
+combination to minimize any potential bias from including proportional variables.
 I capture sex composition with dummy variables for the
@@
 especially the spread of sex selection, that India experienced. 
-I estimate the competing risk hazard model for each spell/education/period subsample and 
-then predict average birth spacing, sex ratio, and the probability of having a birth 
-in that spell.
+I estimate the competing risk hazard model for each spell, education, and period 
+subsample and then predict average birth spacing, sex ratio, and the probability of having 
+a birth in that spell.
 
@@
 
-To find the expected average duration, I first calculate, for each woman, the probability 
-of giving birth in each period $t$, which I use as weights to calculated her expected 
-duration. 
-I then average the individual expected durations across women using the parity progression
-probabilities as weights.
-
-The predicted parity progression probability is the likelihood of giving birth by 96 
-months after the beginning of the spell.
-
+To find the expected average birth interval, I first calculate, for each woman, the 
+probability of giving birth in each period $t$, which I use as weights to calculated her 
+expected spell lengths. 
+I then average the individual expected spell lengths across women using the parity 
+progression probabilities as weights.
+Finally, I add nine months to account for spell start to arrive at birth interval.
+
+The predicted parity progression probability is the likelihood of giving birth by the
+end of the spell.%
+\footnote{
+Most sterilizations take place right after a woman gives birth, and,
+therefore, do not show up in the samples used. 
+Furthermore, sterilization depends strongly on the sex composition of prior children
+with lower probabilities, the fewer boys. 
+The effect is to bias downward the differences in parity progression probabilities.
+}
 The predicted sex ratio captures the percent of births that are boys for women in 
-the sample when childbearing for that spell is over.
-A woman's predicted sex ratio is the weighted average of the predicted percentage boys 
-over each $t$ in the spell, calculated using equation (\ref{eq:probability_son}), using
-the probability of giving birth at time $t$ as weights.%
-\footnote{
-With T=2, if 54 and 66 percent of the births are boys and the likelihoods of 
-giving birth 20 and 40 percent, then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent of the
-births are boys.
-}
-The predicted sex ratio shown is the weighted average of the individual predicted sex 
-ratios, using the parity progression probabilities as weights.
+the sample when childbearing for that spell is over, calculated as shown above.
 For comparison, the graphs also show the natural sex ratio, approximately 51.2 percent 
@@
 }
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with no education}
@@
 } 
-\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with no education}
@@
 % } 
-% \caption{Estimated average spell length, sex ratio, and probability of 
+% \caption{Estimated average birth interval, sex ratio, and probability of 
 % a next birth for women with one to seven years of education}
@@
 }
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with one to seven years of education}
@@
 } 
-\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with one to seven years of education}
@@
 % } 
-% \caption{Estimated average spell length, sex ratio, and probability of 
+% \caption{Estimated average birth interval, sex ratio, and probability of 
 % a next birth for women with eight to eleven years of education}
@@
 }
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with eight to eleven years of education}
@@
 } 
-\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with eight to eleven years of education}
@@
 % } 
-% \caption{Estimated average spell length, sex ratio, and probability of 
+% \caption{Estimated average birth interval, sex ratio, and probability of 
 % a next birth for women with twelve or more years of education}
@@
 }
-\caption{Estimated average spell length, sex ratio, and probability of 
+\caption{Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with twelve or more years of education}
@@
 } 
-\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
+\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
 a next birth for women with twelve or more years of education}
@@
 
-In the latest period, the shortest average birth interval is 25 months for
+In the latest period, the shortest average birth interval is 33 months for
 women with no education in the second spell, an increase of a couple of
 months from the first period.
-The longest average interval was 42 months for the third spell for women with twelve or 
+The longest average interval was 51 months for the third spell for urban women with twelve or 
 more years of education who had no boys, which is an increase of approximately a year.
 For comparison, the median birth intervals reported for the NFHS have barely
-moved over time, staying at approximately 22 months calculated with the starting point 
-nine months after the prior birth used here.%
+moved over time, staying at approximately 31 months.%
 \footnote{
@@
 }
-\begin{minipage}[t]{0.42\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
+\begin{minipage}[t]{0.39\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
 \\

### 2020-07-11 paper/sex_selection_spacing-ver4.tex
Clarify spell definition and model set-up
- Spell period from one parity to next birth or censoring
- Only have discussion of explanatory variables in one place
- Original proportionality discussion unclear
- Edit model set-up for clarity and introduce non-proportional part
more generically rather than with variables
- Footnote on endogenous sex composition should be when that variable
is introduced
- Specify that predicted birth intervals are in months

@@
 The standard approach in the birth spacing literature is to use proportional hazard
-models with a single exit, the birth of a child.%
+models with a single exit---the birth of a child.%
 \footnote{
@@
 
-First, and most importantly, the introduction of sex selection means that the sex of the 
-next child is no longer necessarily random and that parents' choices will impact the 
-spacing to the birth of a girl or a boy differently.
-I, therefore, use a competing risk set-up that captures both the non-randomness of
+First and foremost, the use of sex selection means that the sex of the next child is 
+no longer random and that the spacing to the birth of a boy will differ from the 
+spacing to a girl. 
+Therefore, I use a competing risk set-up that captures both the non-randomness of 
 the birth outcome and the differential spacing.%
@@
 
-Second, even without sex selection it is unlikely that characteristics, such as the sex
-composition of previous births, have the same effects throughout the entire birth interval.
-That is, however, the assumption behind the proportional hazard model, and if 
-proportionality does not hold, the results are biased.
+Second, even without sex selection, it is unlikely that characteristics, such as 
+the sex composition of previous births, have the same effects throughout the entire 
+birth interval. 
+The proportional hazard model requires that the hazard for any individual is a 
+fixed proportion of the hazard for any other individual. 
+That the effects are not constant violates that assumption, and the results from a 
+proportional hazard model would, therefore, be biased. 
 The proportionality assumption is especially problematic for higher-order birth 
-intervals where there are substantial differences across groups both in the likelihood of 
-progressing to the next birth and how soon couples want their next child if they are going 
-to have one \citep{Whitworth2002,Bhalotra2008,Kim2010}.
+intervals since there are substantial differences across groups in the likelihood 
+of progressing to the next birth and how soon couples want their next child if they 
+are going to have one \citep{Whitworth2002,Bhalotra2008,Kim2010}.
 
@@
 birth spacing. 
-Second, within a birth interval, a household's use of sex selection may vary and that
+Second, within a birth interval, a household's use of sex selection may vary, and that
 means that the effects of covariates vary as well.
 
-I, therefore, use a non-proportional hazard specification that allows the shape of the 
+Therefore, I use a non-proportional hazard specification that allows the shape of the 
 hazard functions to vary across groups.
@@
 
-The model is a discrete-time, non-proportional, competing risk hazard model with two exit 
-states: either a boy or a girl is born.
-The unit of analysis is a spell---the period from nine months after one birth to the 
-following birth or censoring.
-The spells begin nine months after the previous birth since this is the earliest we should 
-expect to observe a new birth.
-Censoring can happen for three reasons:
-the survey takes place,
-sterilization of the woman or her husband,
-or there are too few births for the method to work.
+The model is a discrete-time, non-proportional, competing risk hazard model with two 
+exit states: either a boy or a girl is born. 
+The unit of analysis is a spell---the period from one parity birth to the following 
+birth or censoring. 
+For estimation purposes, the spells begin nine months after the previous birth since 
+this is the earliest we should expect to observe a new birth. 
+Censoring can happen for three reasons: the survey takes place, sterilization of the 
+woman or her husband, or imposed because of too few births for the method to work.
 
@@
 $J_i$ indicates which event took place.
+
 The discrete-time hazard rate $h_{ijt}$ is 
@@
  h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
- {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
+ {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2.
  \label{eq:hazard}
 \end{equation}
-where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
-individual, household, and community characteristics discussed below,
-and $D_{j}(t)$ is the piece-wise constant baseline hazard for outcome $j$, captured
+$D_{j}(t)$ is the piece-wise constant baseline hazard for outcome $j$, captured
 by dummies and the associated coefficients,
@@
 baseline hazard unnecessarily.
-
-The explanatory variables in $\mathbf{Z}$, and the interactions between them, 
-constitute the non-proportional part of the model:
-\begin{equation}
- \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2).
-\end{equation}
-$D_j(t)$ is the piece-wise constant baseline hazard, $\mathbf{Z}_1$ captures sex 
-composition of previous children, and $Z_2$ captures the area of residence.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally.%
-\footnote{
-With sex selection, the composition of prior children is, in principle, endogenous.
-It is beyond the scope of this paper to develop a method for dealing with this issue.
-}
+$\mathbf{Z}$ is the non-proportional part, which includes the interactions between 
+$D_j(t)$ and a set of explanatory variables and the interactions of those.
+The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
 
@@
 the spacing choice and the use of sex selection:
-mother's education, sex composition of previous children, and area of residence.
+mother's education, sex composition of previous children, and area of residence.%
+\footnote{
+With sex selection, the composition of prior children is, in principle, endogenous.
+It is beyond the scope of this paper to develop a method for dealing with this issue.
+}
 The second group of variables consists of those expected to have an approximately 
@@
 I estimate the competing risk hazard model for each spell, education, and period 
-subsample and then predict average birth spacing, sex ratio, and the probability of having 
-a birth in that spell.
+subsample and then predict average birth interval in months, sex ratio, and the 
+probability of having a birth in that spell.
 
@@
 
-To find the expected average birth interval, I first calculate, for each woman, the 
-probability of giving birth in each period $t$, which I use as weights to calculated her 
-expected spell lengths. 
+To find the expected average birth interval, I first calculate, for each woman, 
+the probability of giving birth in each period $t$, which I use as weights to calculated 
+her expected spell lengths. 
 I then average the individual expected spell lengths across women using the parity 
@@
 the sample when childbearing for that spell is over, calculated as shown above.
-For comparison, the graphs also show the natural sex ratio, approximately 51.2 percent 
+For comparison, I also show the natural sex ratio, approximately 51.2 percent 
 \citep{ben-porath76b,jacobsen99,Portner2015b}.

### 2020-07-11 paper/sex_selection_spacing-ver4.tex
Clarify transformation of data and sex ratio calculation
- use "interval" rather than period
- better wording for transformation
- reorganize description of sex ratio calculation method

@@
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, transforming the data, so each observation is a time period---here equal
-to three months---I can estimate the model using a standard multinomial logit model.
-%
-% \footnote{
-% The multinomial model assumes that alternative exit states are stochastically independent
-% (Independence of Irrelevant Alternatives or IIA), which rules out any individual-specific 
-% unmeasured or unobservable factors that affect both the hazard of having a girl and the 
-% hazard of having a boy.
-% I, therefore, include a proxy for fecundity discussed in Section \ref{sec:data}.
-% Also, the multivariate probit model can be used as an alternative because the IIA is not 
-% imposed \citep{han90}.
-% The results are substantially identical between these two models and
-% available upon request.
-% }
-In the reorganized data the outcome variable is 0 if the woman does not have a child in a 
-given interval (the base outcome), 1 if she gives birth to a son in that interval, and 2 
-if she gives birth to a daughter in that interval.
-
-% The distribution of spacing is captured by the survival curve, which shows the probability 
-% of not having had a birth yet by spell duration, for a given set of explanatory variables.
-% The survival curve at time $t$ is 
-% \begin{equation}
-% \label{eq:survival}
-% S_{t} 
-% = 
-% \prod_{d=1}^t
-% \left(
-% \frac{ 1 }
-% {1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
-% \right).
-% \end{equation}
-% 
-% Because the probability of ever having a next birth varies across groups, a direct 
-% comparison of standard survival curves tells us little about how the spread of sex 
-% selection affects birth spacing across groups.
-% I, therefore, condition on the predicted likelihood of parity progression when examining 
-% birth spacing measures, such as the average duration to a birth.
-% The reliability of this approach depends on whether the spell length covered is 
-% sufficiently long that few women are likely to give birth after the spell cut-off.
-% I discuss the choice of spell length below.%
-% \footnote{
-% It is important to note that the approach is not the same as merely calculating 
-% the birth spacing measures for women who already have a given 
-% parity child in the survey because that number does not take into account
-% the censoring of spells that will eventually lead to a birth.
-% }
-% In addition, I present graphs of survival curves conditional on parity progression,
-% which therefore begin at 100\% and end at 0\%.
+Hence, splitting spells into smaller intervals---here equal to three months---and 
+treating them as observations, I can estimate the model using a standard multinomial 
+logit model. 
+In the reorganized data, the outcome variable is 0 if the woman does not have a child 
+in a given interval (the base outcome), 1 if she gives birth to a son in that interval, 
+and 2 if she gives birth to a daughter in that interval.
 
@@
 }
-The sex ratio is based on the estimated percentage of children born at each $t$ that are 
-boys, $\hat{Y}$:  
+The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
+parity progression probabilities as weights.
+For an individual woman, the estimated percent of births that are boys at $t$, $\hat{Y_t}$, is:  
 \begin{equation}
@@
 conditional on the explanatory variables and not having had a child before $t$.
-Combining the percentage of boys and the likelihood of exiting the spell with a birth
-across all $t$ gives the predicted percent of births that are boys over the entire spell.%
+Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
+$t$ gives the predicted percent of boys over the entire spell for an individual.%
 \footnote{
-With T=2, if 54 and 66 percent of the births are boys and the likelihoods of 
-giving birth 20 and 40 percent, then $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent of the
-births are boys.
-}
-The predicted sex ratio shown is the weighted average of the individual predicted sex 
-ratios, using the parity progression probabilities as weights.
+Imagine $T=2$. 
+If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
+then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
+}
 

### 2020-07-12 paper/sex_selection_spacing-ver4.tex
Clean up remaining spell discussions
- use "imposed censoring" rather than generic end of spell
- update interval dummy numbers to reflect birth interval rather than
pregnancy intervals/spell lengths.
- minor edits/clarifications

@@
 
-To find the expected average birth interval, I first calculate, for each woman, 
-the probability of giving birth in each period $t$, which I use as weights to calculated 
-her expected spell lengths. 
-I then average the individual expected spell lengths across women using the parity 
-progression probabilities as weights.
-Finally, I add nine months to account for spell start to arrive at birth interval.
-
 The predicted parity progression probability is the likelihood of giving birth by the
-end of the spell.%
+imposed censoring based on standard survival curve calculations.%
 \footnote{
@@
 \citep{ben-porath76b,jacobsen99,Portner2015b}.
+To find the expected average birth interval, I first calculate, for each woman, 
+the probability of giving birth in each period $t$, which I use as weights to calculated 
+her expected spell lengths. 
+I then average the individual expected spell lengths across women using their parity 
+progression probabilities as weights.
+Finally, I add nine months to account for spell start to arrive at birth interval.
 
@@
 The longest average interval was 51 months for the third spell for urban women with twelve or 
-more years of education who had no boys, which is an increase of approximately a year.
+more years of education who had no boys, an increase of approximately a year.
 For comparison, the median birth intervals reported for the NFHS have barely
@@
 }
-This lack of change underscores the importance of accounting for censoring of birth spells 
-when trying to understand how birth spacing is changing over time.
+This lack of change in the NFHS reported birth intervals underscores the importance of 
+accounting for censoring of birth spells when trying to understand how birth spacing 
+is changing over time.
 
@@
 the sex composition of prior children and the parity.
-Women with no sons still are the most likely to 
-have the next birth, and this group has seen often substantially smaller declines in
+Women with no sons are still the most likely to 
+have the next birth, and this group has seen substantially smaller declines in
 the likelihood of having another birth than women with one or more sons.%
 \footnote{
-There is, however, also some evidence that parents prefer a mix of boys and girls: for 
+However, there is also some evidence that parents prefer a mix of boys and girls: for 
 the fourth spell women with two boys \emph{and} a girl
@@
 To better understand what factors are behind the changes in average spacing, I next 
-examine the distribution of birth spacing---represented by the 25th and 75th percentiles 
+examine its distribution---represented by the 25th and 75th percentiles 
 of predicted birth intervals. 
@@
 each parity, assuming three years increases in age between each parity.
-Shorter assumed duration between births leads to slightly higher predicted 
+Shorter assumed increases in age between births leads to slightly higher predicted 
 fertility.
@@
 the fertility rate estimate of 1.5.
-Furthermore, the predicted cohort fertility numbers are likely too low,
+Finally, the predicted cohort fertility numbers are likely too low,
 especially for the lower education groups, since it relies only on the
 first four births and because the model ignores births that took place past the end
-of the 96 months long spell.
+of the imposed 105 month birth interval censoring.
 
@@
 months of life.
-The main set of explanatory variables consists of dummies for birth spacing
-covering 12 months intervals, starting from nine months after the prior birth 
-as above, until 48 months, which includes all births until 96 months.
+The main set of explanatory variables consists of dummies for the spacing from
+the prior birth.
+Starting nine months after the prior birth, the birth interval dummies cover 12 
+month periods until 57 months, which covers until 105 months after the prior birth.
 I use dummies for sex of the index child and the sex composition 
@@
 
-I estimate the probability of infant mortality using a logit model.
+I estimate the probability of infant mortality using a Logit model.
 Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} present 
@@
 low as it is for better-educated women \citep{Kozuki2013,Molitoris2019}.
-However, in prior research, the fixed effects and linear probability results do not 
-deviate substantially.
+However, the fixed effects and linear probability results did not 
+deviate substantially in prior research.
 
@@
 There has been substantial convergence in mortality risk across groups over time.
-For intervals 12 months or longer, there is now little difference across 
+For intervals 21 months or longer, there is now little difference across 
 the education groups, with even the no education group showing an infant mortality risk 
@@
 % line 3661 in an_infant_mortality.log
-The raw numbers for the group with the most uneven sex ratio indicates
-that there is no impact on child mortality, even with high use of sex selection. 
+The raw numbers for women with the most uneven sex ratio also suggests that even with 
+high use of sex selection there is no impact on child mortality. 
 A total of 1,004 women with twelve or more years of
-education, who have no boys at the start of the third spell in the last
+education and no boys at the start of the third spell in the last
 period, had a third child, of which 685 were boys. 
-Of these 685 boys, only six died within the first year of life, and half of those were 
-born in the 0-23 months interval, and none in 48 months or more interval.
+Of these 685 boys, only six died within the first year of life.
+Half of those who died were born in the 9-32 months interval, and none in 57 months 
+or longer interval.
 

### 2020-07-12 paper/sex_selection_spacing-ver4.tex
Minor edit

@@
 fourth birth.
-I exclude the interval from marriage to the first birth because many are imputed and,
-with falling fertility, few women had five or more births, especially among the 
-better-educated.
+I exclude the interval from marriage to the first birth because many are imputed and
+higher order intervals because, with falling fertility, few women had five or more 
+births, especially among the better-educated.
 

### 2020-07-12 response/response-demography-3.tex
Move from spell lengths to birth interval throughout (#19)
* Use birth intervals rather than spell lengths

* Clarify spell definition and model set-up

- Spell period from one parity to next birth or censoring
- Only have discussion of explanatory variables in one place
- Original proportionality discussion unclear
- Edit model set-up for clarity and introduce non-proportional part
more generically rather than with variables
- Footnote on endogenous sex composition should be when that variable
is introduced
- Specify that predicted birth intervals are in months

* Clarify transformation of da

@@
 India's Experience over Four Decades.''
+
+[Other changes]
+\begin{enumerate}
+	\item Rewritten Estimation Strategy section
+	\begin{enumerate}
+		\item Clarify proportionality assumption
+		\item Better explain set-up of model and transformation of data needed
+		\item Remove discussion of explanatory variables so they are
+		only covered once (in the ``Data'' section)
+		\item Better explanation of how I calculate measures used for the spacing
+		analysis
+	\end{enumerate}
+	\item Changes in Data section
+	\begin{enumerate}
+		\item Lead with what birth intervals I cover right after introducing
+		data
+		\item Move restriction to only Hindus to be the first restriction
+		I discuss since that is the most important
+	\end{enumerate}
+\end{enumerate}
 
@@
 [Response:]
+
+I now define spell as the unit of analysis---the period from one parity birth to 
+the following birth or censoring---when I first use the word in the ``Estimation 
+Strategy'' section.
+Furthermore, I clarify that for estimation purposes spells begin nine months 
+after the previous birth since this is the earliest we should expect to observe 
+a new birth.
+This duration is equivalent to the interpregnancy interval, which is often used in 
+the literature on spacing and child mortality.
+
+To make comparison with both the NFHS reports and the prior literature on
+birth spacing easier and avoid confusion, I have rewritten the discussions of 
+spacing and redone the graphs and table, so all results now reflect birth 
+intervals in months.
+I still retain the use of ``spell'' to indicate a generic period from one parity 
+birth to another, i.e. second spell is from first birth to the second birth or
+censoring, in the graphs/tables.
+
+In the Data section, I have also changed the discussion of the imposed censoring 
+clearer by specifying the cut-offs for both the spell duration and the birth interval.
+In the ``How Birth Spacing Changed'' section, I explain that I add nine month
+to the estimated spell length to get to birth intervals.
+In the ``Mortality and the Changing Birth Spacing'' section, I retained the
+definition of the periods but updated the numbers and the discussion of
+results so they reflect birth intervals rather than pregnancy intervals.
 

### 2020-07-13 paper/sex_selection_spacing-ver4.tex
Add background/questions to Conclusion; begin data quality discussion

@@
 
-In addition to a large number of women surveyed and the long period covered, a
-benefit of the NFHS is that enumerators pay careful attention to the spacing 
-between births and probe for ``missed'' births.
-Nevertheless, systematic recall error, where the likelihood of reporting a deceased 
-child depends on the sex of the child, remains a potential problem.
-Recall error is heavily dependent on how long ago a woman was married, and I, therefore, 
-drop women married 22 years or more based on the discussion in the Appendix.
+In addition to a large number of women surveyed and the long period covered, a significant 
+benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
+spacing between births and probe for ``missed'' births.%
+\footnote{
+The method used to probe for missing births depends on the survey.
+NFHS-1 probe for each calendar birth interval that is four or more years.
+NFHS-2 asked for stillbirths, spontaneous and induced abortions, and also probed 
+for each calendar birth interval four or more years.
+NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether there were any 
+other live births between (name of previous birth) and (name), including any children who 
+died after birth, and asked for births before the birth listed as first birth and
+after the last birth listed as the last birth.
+}
+The quality of the birth date data is especially important here since the reliability of the 
+results depends on the correctness of the birth histories provided by the respondents.
+The main concern is underreporting of deceased children, especially a systematic recall error 
+where respondents' likelihood of reporting the birth of a deceased child depends 
+on the sex of that child.
+To establish the quality of the birth interval data, I provide a detailed discussion of the 
+degree of systematic recall error in the Online Appendix.
+Recall error appear heavily dependent on how long ago a woman was married, 
+and I, consequently, drop women married 22 years or more.
 
@@
 
+% Background
+Over the last four decades India saw a dramatic increase in the male-to-female
+sex ratio at birth as access to sex selection spread and son preference remained. 
+At the same time, economic growth was strong, schooling increased, and the total
+fertility rate fell to close to replacement.
+
+% Questions
+The main question I address in this paper is how birth spacing responded to the major changes
+that occurred in India over the last four decade, in particular the spread of sex selection.
+In addition, I examine two related questions.
+First, did the changes in birth spacing bias the standard fertility estimates for India? 
+Second, what is the relationship between infant mortality and the changes in birth spacing 
+and sex selection?
+
 % What has happened to spacing and why
-
-One effect of the significant changes that India has experienced over the last four 
-decades is that spacing between births has increased.
-The size of the increase is increasing in parity and the mother's
-education and is larger in urban than in rural areas.
-
-The most substantial increases in birth intervals arise, however, with
-heavy use of sex selection. Some of these increases are so large that we
-even observe a reversal of the traditional spacing pattern where strong
-son preference was associated with shorter birth intervals, the fewer
-sons a family has \citep{ben-porath76b,Leung1988}.
-
-Despite the longer average birth intervals, a large number of women
-still have very short birth intervals. 
-Hence, the changes in birth
-spacing are driven by the longer intervals becoming even longer over
-time, both for women who do not use sex selection, but especially for
-those who do and end up with multiple abortions. 
-The exception to the
-small change in short spacing is the delay in conception for women with
-very high use of sex selection, presumably because this group knows that
+Birth intervals has lengthen, often substantially, over the last four decades.
+The increases in spacing are larger, the higher the parity and the higher the mother's
+education, and is larger in urban than in rural areas.
+
+Groups with the highest use of sex selection have the most substantial increases in 
+birth intervals, with increases in average birth intervals of up to 12 months. 
+Some of these increases are so large that we even observe a reversal of the traditional 
+spacing pattern: instead of the absence of sons leading to the shortest birth intervals, 
+son preference and sex selection lead some groups to have longest birth intervals when
+they have no sons.
+
+Despite the longer average birth intervals, a large number of women still have very 
+short birth intervals. 
+Hence, the changes in birth spacing are driven predominately by the longer intervals 
+becoming even longer over time.
+This pattern holds generally, but is especially prevalent for those who use sex selection 
+and, therefore, may end up with multiple abortions. 
+The exception to the small change in short spacing is the delay in conception for women 
+with very high use of sex selection, presumably because this group knows that
 the next child will be a boy.
@@
 still depends strongly on the number of sons, with women with no sons having the highest 
-probabilities.
-
-That those women most likely to use sex selection are also the most
-likely to have a next birth, combined with the secular increases in
-spacing, makes the total fertility rate a more biased measure of cohort
-fertility. 
-This bias was most prominent early in the spread of sex
-selection when the fertility rate was up to one child lower than the
-predicted cohort fertility. 
-It is, however, still present with the
-predicted cohort fertility ten to twenty percent higher than the
-fertility rate.
+parity progression probabilities.
+
+The combination of the secular increases in spacing and the fact those women most likely to use
+sex selection are also those most likely to have a next birth, makes the total fertility rate a 
+more biased measure of cohort fertility. 
+This bias was most prominent early in the spread of sex selection, when the fertility rate 
+was up to one child lower than the predicted cohort fertility. 
+It is, however, still present, with the predicted cohort fertility ten to twenty percent 
+higher than the fertility rate.
 
@@
 as for India.
-It is conceivable that we might see increases in TFR as birth spacing 
-stabilizes or even shortens again if interventions against sex selection are successful.
+It is conceivable that we might see increases in the total fertility rate as birth spacing 
+stabilizes or, if interventions against sex selection are successful, even shortens again.
 
@@
 is below replacement at 1.8. 
-A caveat to the predicted cohort fertility is that only Hindu women are
-in the sample and that the model only includes births up to parity four.
+A caveat to the predicted cohort fertility is that only Hindu women are in the sample and 
+that the model only includes births up to parity four.
 However, almost everybody marries, and Hindu constitute 80 percent of the population.
@@
 % Mortality
-There has been a substantial reduction in infant mortality over time, and 
-the size of the reductions is inversely related to the mother's education.
-Hence, there is now little difference in mortality risk across
-education groups if the birth took place more than 21 months from the prior birth.
+There has been a substantial reduction in infant mortality over time, and the size of the 
+reductions is inversely related to the mother's education.
+Hence, there is now little difference in mortality risk across education groups if the 
+birth took place more than 21 months from the prior birth.
 Short birth spacing is still associated with higher mortality, although the difference is 
@@
 
-An implication of the results here is that population growth in India
-will be higher than expected. There has been a rapid reduction in infant
-mortality risk, the longer spacing should further reduce mortality risk,
-and cohort fertility is higher than previously realized.
+An important implication of the results here is that population growth in India
+may be higher than expected. 
+There has been a rapid reduction in infant mortality risk, the longer spacing should 
+further reduce mortality risk, and cohort fertility is higher than previously realized.
 
@@
 There are two critical questions that future research should address.
-Sex selection means that girls-only families are less likely to have
+First, sex selection means that girls-only families are less likely to have
 very short birth intervals, which may reduce sibling competition. 
@@
 valued as is often assumed. 
-Comparing prior children's outcomes across
-sex composition and the sex of the next child could be a way to
-understand why girls' health outcomes improve in the presence of sex selection.
+Comparing prior children's outcomes across sex composition and the sex of the next child 
+could be a way to understand why girls' health outcomes improve in the presence of sex selection.
 
 Second, is there a relationship between female labor force participation
-and sex selection? Women may be staying out of the labor market
-precisely because sex selection makes them more likely to have a boy and
-increases the expected birth spacing. Better job opportunities for women
-would affect sex selection for two reasons. First, it makes it more
-expensive to be out of the labor market for long periods. Second, it
-would moderate the differential in potential earnings between husband
+and sex selection? 
+Women may be staying out of the labor market precisely because sex selection makes 
+them more likely to have a boy and increases the expected birth spacing. 
+Better job opportunities for women would affect sex selection for two reasons. 
+First, it makes it more expensive to be out of the labor market for long periods. 
+Second, it would moderate the differential in potential earnings between husband
 and wife and make it more attractive to invest in female compared to
-male offspring's human capital. This approach could, however, be a
-double-edged sword. If better job opportunities further lower desired
-fertility, the use of sex selection may increase, everything else equal.
+male offspring's human capital. 
+This approach could, however, be a double-edged sword. 
+If better job opportunities further lower desired fertility, the use of sex selection 
+may increase, everything else equal.
 Hence, understanding the trade-off between long-term benefits from

### 2020-07-13 response/response-demography-3.tex
Explain changes in Conclusion: background and questions
Respond to data quality question

@@
 
+I have expanded the discussion of the birth history data in the ``Data'' section and
+why it is important.
+As part of this expanded discussion, I included more information about systematic
+recall error, why it is likely the main concern here, what the effect is on the
+estimates, and how I address this problem.
+I have also included a reference to \citet{Schoumaker2014} that finds that the first
+rounds of the NFHS are of ``moderate quality,'' although that is without the correction
+for recall error that I use.
+
 \item Perhaps the conclusion could start with a brief overview of your
@@
 [Response:]
+
+I have added a brief synopsis of the changes in India in the beginning of
+the Conclusion and recap the three questions after that.
+I have also slightly edited the Conclusion to tie better with the 
+questions.
 

### 2020-07-13 paper/sex_selection_spacing-ver4.tex
Add Schoumaker 2014 footnote and remove footnote on probing procedure in NFHS

@@
 benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
-spacing between births and probe for ``missed'' births.%
+spacing between births and probe for ``missed'' births.
+The quality of the birth date data is crucial since the reliability of the results depends 
+on the correctness of the birth histories provided by the respondents.
+For India, the main concern is underreporting of deceased children, especially a systematic 
+recall error where respondents' likelihood of reporting the birth of a deceased child depends 
+on the sex of that child.
+If deceased children are not reported the birth intervals will be inflated and likely make 
+the changes over time appear smaller than they really are.
+I, therefore, provide a detailed analysis of systematic recall error in the Online Appendix.
+Recall error is heavily dependent on how long ago a woman was married, and I, consequently, 
+drop women married 22 years or more.%
 \footnote{
-The method used to probe for missing births depends on the survey.
-NFHS-1 probe for each calendar birth interval that is four or more years.
-NFHS-2 asked for stillbirths, spontaneous and induced abortions, and also probed 
-for each calendar birth interval four or more years.
-NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether there were any 
-other live births between (name of previous birth) and (name), including any children who 
-died after birth, and asked for births before the birth listed as first birth and
-after the last birth listed as the last birth.
-}
-The quality of the birth date data is especially important here since the reliability of the 
-results depends on the correctness of the birth histories provided by the respondents.
-The main concern is underreporting of deceased children, especially a systematic recall error 
-where respondents' likelihood of reporting the birth of a deceased child depends 
-on the sex of that child.
-To establish the quality of the birth interval data, I provide a detailed discussion of the 
-degree of systematic recall error in the Online Appendix.
-Recall error appear heavily dependent on how long ago a woman was married, 
-and I, consequently, drop women married 22 years or more.
+\citet{Schoumaker2014} discusses the quality of birth histories in DHS surveys and the 
+impact on fertility estimates.
+Although that analysis does not directly examine systematic recall error, it is likely that
+it explain why the first rounds of NFHS are listed as ``moderate quality.''
+}
 

### 2020-07-13 response/response-demography-3.tex
Explain why 2004/05 break in periods (#21)

@@
 
+The 2004 break is an attempt to understand whether we are observing the beginning of
+a reversal in son preference and the use of sex selection as hypothesized by part of
+the prior literature.
+In the ``Data'' section, I have split the paragraph on the periods into two and expanded 
+the discussion of the motivation for the breaks, including adding two additional
+references arguing that we might see the reversal.
+Clearly, the 2004/05 break is somewhat arbitrary, but does have the advantage of making 
+the periods close to the same length (there are relatively few birth intervals that begin 
+in 2015 and 2016).
+
 \item While I like results being presented in figures, what I don’t like

### 2020-07-13 paper/sex_selection_spacing-ver4.tex
Explain why 2004/05 break in periods (#21)

@@
 
-[TK where to put son preference discussion?]
+% [TK where to put son preference discussion?]
+% %
+% \footnote{
+% It is also possible that the effect is driven by a stronger son preference, although 
+% higher education women have shown declining son preference \citep{bhat03,pande07}.
+% }
 
@@
 Direct information on the use of sex selection is not available, so I compare different 
-periods, based on the changes in access and legality of prenatal sex 
-determination in India.
+periods, based on the changes in access and legality of prenatal sex determination in India.
 Abortion has been legal in India since 1971.
@@
 }
-Although the use of sex selection increased even after 1994, we may have passed a 
-turning point in its use \citep{Das_Gupta2009,Diamond-Smith2015}.
-I, therefore, use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
+Finally, although the use of sex selection increased even after 1994, we may have passed a 
+turning point in its use in the mid-2000s with son preference declining
+\citep{Das_Gupta2009,Kumar2012,Bongaarts2013,Diamond-Smith2015}.%
+\footnote{
+Although see also \citep{Navaneetham2011}.
+}
+
+I use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
+The first period covers before sex selection became available and the second the period 
+from when sex selection became available until the Prenatal Diagnostic Techniques Act.
+I have split the period from 1995 until 2016 into two to understand if there is any 
+support for the prior literature's hypothesized reversal in child sex ratios and son 
+preference in India.
 The allocation of spells into periods is determined by when conception, and, therefore, 
@@
 women with two girls, which is the group with the most biased sex ratio.
+There is no clear evidence for or against a reversal in the use of sex selection, with 
+some showing increases in sex ratios between the last two periods, others little change, 
+and some a decline.
 

### 2020-07-14 paper/sex_selection_spacing-ver4.tex
Why focus on Hindus
- Hindus and Muslims fundamentally different in use of sex selection
- Too little information on Muslims to provide changes over time
- Edits for conciseness in Data section

@@
 % For word counting uncomment line below and raggedright below
+% http://countwordsfree.com/#
 % \usepackage[nolists]{endfloat}
@@
 as is standard in the literature.
-There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
-$J_i$ indicates which event took place.
+There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$.
 
@@
 fourth birth.
-I exclude the interval from marriage to the first birth because many are imputed and
-higher order intervals because, with falling fertility, few women had five or more 
-births, especially among the better-educated.
-
-I restrict the sample to Hindus, who constitute about 80 percent of India’s population.
-If the use of sex selection differs across groups, assuming that the
-baseline hazard is the same leads to bias. 
-Furthermore, the other groups are each too small to estimate different
-baseline hazards for each and so different that combining them into one
-group would not make sense.
-
-Finally, I exclude visitors, as well as women in any of the following 
-categories: never married; no gauna yet; married more than once; divorced; 
-not living with husband; inconsistent age at marriage; or education information missing.  
+I exclude the interval from marriage to the first birth because many are imputed and the
+higher-order intervals because few women had five or more births, especially among the 
+better-educated.
+
+I restrict the sample to Hindus for two reasons.
+First, Hindus are the majority population group, about 80 percent of India’s population.
+Second, the prior literature shows that son preference and use of sex selection vary 
+substantially between Hindus and the second largest group, Muslims. 
+Combining them and assuming that the baseline hazard is the same would lead to biased 
+results.
+Because of space constraints and the relatively small number of observations once split 
+by education and periods, I do not provide separate results for Muslims or any of the 
+remaining groups, such as Sikhs, Jains, and Christians.
+
+Finally, I exclude visitors and women in any of the following categories: never married; 
+no gauna yet; married more than once; divorced; not living with husband; inconsistent age 
+at marriage; or education information missing.  
 The same goes for women who had at least one multiple births, reported giving birth 
@@
 spacing between births and probe for ``missed'' births.
-The quality of the birth date data is crucial since the reliability of the results depends 
-on the correctness of the birth histories provided by the respondents.
 For India, the main concern is underreporting of deceased children, especially a systematic 
@@
 on the sex of that child.
-If deceased children are not reported the birth intervals will be inflated and likely make 
-the changes over time appear smaller than they really are.
+Unreported deceased children inflate the birth intervals and, with declining mortality, 
+make changes over time appear too small.
 I, therefore, provide a detailed analysis of systematic recall error in the Online Appendix.
-Recall error is heavily dependent on how long ago a woman was married, and I, consequently, 
+Recall error depends heavily on how long ago a woman was married, and I, consequently, 
 drop women married 22 years or more.%
 \footnote{
-\citet{Schoumaker2014} discusses the quality of birth histories in DHS surveys and the 
-impact on fertility estimates.
-Although that analysis does not directly examine systematic recall error, it is likely that
-it explain why the first rounds of NFHS are listed as ``moderate quality.''
+Recall error is likely behind the designation of the first two rounds of NFHS as ``moderate 
+quality'' in an analysis of the quality of birth histories in DHS surveys and its impact 
+on fertility estimates \citep{Schoumaker2014}.
 }
@@
 To ensure that there are enough births for the method to work, I censor each spell at 96 
-months (eight years) after a woman can first give birth in the spell, which is equivalent 
-to 105 months after the birth of the prior child.
+months (eight years) after a woman can first give birth, which is equivalent to 105 months 
+after the birth of the prior child.
 Less than one percent of observed births occur after the cut-off.
@@
 
-Direct information on the use of sex selection is not available, so I compare different 
-periods, based on the changes in access and legality of prenatal sex determination in India.
+Direct information on the use of sex selection is not available, so I compare periods 
+based on the changes in access and legality of prenatal sex determination in India.
 Abortion has been legal in India since 1971.
@@
 \footnote{
-Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
+% Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
 There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2016}.
 }
-Finally, although the use of sex selection increased even after 1994, we may have passed a 
-turning point in its use in the mid-2000s with son preference declining
-\citep{Das_Gupta2009,Kumar2012,Bongaarts2013,Diamond-Smith2015}.%
-\footnote{
-Although see also \citep{Navaneetham2011}.
-}
+Finally, although sex selection increased even after 1994, we may have passed a 
+turning point in its use in the mid-2000s \citep{Das_Gupta2009,Kumar2012,Bongaarts2013,Diamond-Smith2015}.
 
 I use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The first period covers before sex selection became available and the second the period 
-from when sex selection became available until the Prenatal Diagnostic Techniques Act.
-I have split the period from 1995 until 2016 into two to understand if there is any 
-support for the prior literature's hypothesized reversal in child sex ratios and son 
+The first covers before sex selection became available and the second from when sex 
+selection became available until the Prenatal Diagnostic Techniques Act.
+I have split the period from 1995 until 2016 into two to examine if there is support for 
+the prior literature's hypothesized reversal in child sex ratios and son 
 preference in India.
@@
 These include the mother's age when the spell begins, the household's
-land ownership, and whether the household belongs to a scheduled tribe
-or caste.
+land ownership, and whether it belongs to a scheduled tribe or caste.
+Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present descriptive statistics.
 
@@
 Area of residence is a dummy variable for living in an urban area.
-
-% %
-% \footnote{
-% Fathers' education has two opposite predicted effects: the associated higher income
-% should increase fertility and therefore lower the pressure to use sex selection, but
-% the higher income also makes the use of sex selection cheaper.
-% In practice, fathers' education had little effect on the hazards and the use of 
-% sex-selective abortions, and I, therefore, do not include it.
-% }
-
-Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} presents descriptive 
-statistics.
-The level of censoring increases with parity and time, as we should expect with later 
-childbearing, falling fertility, and the hypothesized increases in birth intervals from 
-sex-selective abortions.
 

### 2020-07-14 response/response-demography-3.tex
Why focus on Hindus (#24)
- Hindus and Muslims fundamentally different in use of sex selection
- Too little information on Muslims to provide changes over time
- Edits for conciseness in Data section

@@
 
+I focus on the Hindu population because they are the majority population group 
+and because the prior literature argue that this group has a strong son preference and 
+consequently uses sex selection.%
+\footnote{
+Sikhs and Jains likely have even higher use of sex selection than Hindus but Sikhs 
+constitutes less than two percent of the population and Jains less than half a percent.
+}
+Since there is little evidence that Muslim use sex selection, combining Hindu and Muslim 
+would lead to biased results.
+
+How birth spacing of Muslim women changed is certainly of interest and is worthy
+of a separate analysis.
+However, there are two problems with expanding the analysis.
+First, although the lastest round of NFHS provides enough data for the analyses, 
+it would be hard to provide much in the way of comparison with earlier periods.
+This problem becomes especially acute once the Muslim population is split by education 
+levels to make the results comparable to the Hindu population.
+Second, the paper is already very long and adding even more tables/graphs and the
+necessary discussions of the results does not seem feasible.
+
+I have edited the discussion in the ``Data'' section to make the reason for focusing
+on Hindus clearer, and hope to write a separate paper/note looking at how spacing
+has changed for Muslims later.
+
 \item There is actually no data on sex selection and in a sense the data

### 2020-07-14 paper/sex_selection_spacing-ver4.tex
Combine prediction calculation in Estimation Strategy

@@
 treating them as observations, I can estimate the model using a standard multinomial 
-logit model. 
+Logit model. 
 In the reorganized data, the outcome variable is 0 if the woman does not have a child 
@@
 
-I use the model to predict birth interval measures, the probability of having a birth, 
-and the sex ratio.%
-\footnote{
-The interpretation of competing risk model coefficients is challenging \citep{thomas96}.
-}
+I use the model to predict birth interval measures, parity progression probabilities, 
+and the sex ratio rather than present coefficients since the interpretation 
+of competing risk model coefficients is challenging \citep{thomas96}.
+The predicted parity progression probability is the likelihood of giving birth by the
+imposed censoring based on standard survival curve calculations averaged across all
+women in a given sample.
+
+For birth intervals, I estimate the average birth interval and a set of percentile
+birth intervals.
+To find the average birth interval, I calculate, for each woman, the probability of 
+giving birth in each $t$, and her expected spell length from these probabilities.
+I then average the individual expected spell lengths across women using their parity 
+progression probabilities as weights.
+Finally, I add nine months because spells begin nine months after the previous birth.
+The process is similar for the percentile birth intervals, except that I use the time 
+point when there is a given percent probability that a woman will give birth, conditional 
+on her giving birth in the spell.
+
 The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
@@
 preference in India.
+
 The allocation of spells into periods is determined by when conception, and, therefore, 
@@
 periods.
+Most sterilizations take place right after a woman gives birth, and,
+therefore, do not show up in the samples used. 
+Furthermore, sterilization depends strongly on the sex composition of prior children
+with lower probabilities, the fewer boys. 
+The effect is to bias downward the differences in parity progression probabilities.
 
@@
 I estimate the competing risk hazard model for each spell, education, and period 
-subsample and then predict average birth interval in months, sex ratio, and the 
+combination and then predict average birth interval in months, sex ratio, and the 
 probability of having a birth in that spell.
@@
 }
-
-The predicted parity progression probability is the likelihood of giving birth by the
-imposed censoring based on standard survival curve calculations.%
-\footnote{
-Most sterilizations take place right after a woman gives birth, and,
-therefore, do not show up in the samples used. 
-Furthermore, sterilization depends strongly on the sex composition of prior children
-with lower probabilities, the fewer boys. 
-The effect is to bias downward the differences in parity progression probabilities.
-}
-The predicted sex ratio captures the percent of births that are boys for women in 
-the sample when childbearing for that spell is over, calculated as shown above.
-For comparison, I also show the natural sex ratio, approximately 51.2 percent 
-\citep{ben-porath76b,jacobsen99,Portner2015b}.
-To find the expected average birth interval, I first calculate, for each woman, 
-the probability of giving birth in each period $t$, which I use as weights to calculated 
-her expected spell lengths. 
-I then average the individual expected spell lengths across women using their parity 
-progression probabilities as weights.
-Finally, I add nine months to account for spell start to arrive at birth interval.
+For comparison, the graphs for the sex ratio also show the natural sex ratio, 
+approximately 51.2 percent \citep{ben-porath76b,jacobsen99,Portner2015b}.
 
@@
 show how the predicted 25th and 75th percentile birth intervals have changed over time 
-by spell and education.
-For each woman in a given spell/period combination, I calculate the time point at 
-which there is a given percent chance that she will have given birth, relative to the
-probability that she will eventually give birth in that spell.
-The reported statistics is the average of the percentile duration
-across all women in a given sample using the individual predicted
-probabilities of having had a birth by the end of the spell as weights.%
+by spell and education.%
 \footnote{

### 2020-07-14 response/response-demography-3.tex
Consistent tables, graphs, and text and combined prediction explanation (#25)
* Averager rather than expected birth interval

* Combine prediction calculation in Estimation Strategy

* Explain consistency changes to text

@@
 		\item Better explanation of how I calculate measures used for the spacing
-		analysis
+		analysis and all explanations gathered in this section
 	\end{enumerate}
@@
 		\item Move restriction to only Hindus to be the first restriction
-		I discuss since that is the most important
+		I discuss since that is the most important. 
+		See also response to Review 2 below.
+	\end{enumerate}
+	\item Ensure consistent presentation of results
+	\begin{enumerate}
+		\item Use average rather than expected throughout now
+		\item Update table notes to better describe calculation methods
 	\end{enumerate}
@@
 
-[Response:] I now define ``sex selection'' as ``the selective abortion of female fetuses 
+[Response:]
+
+I now define ``sex selection'' as ``the selective abortion of female fetuses 
 based on prenatal sex determination'' in the second paragraph of the paper.

### 2020-07-21 paper/sex_selection_spacing-ver4.tex
Move to new combined graphs for spacing and mortality

@@
 \usepackage{setspace}
-\usepackage[justification=centering]{caption}
+\usepackage[justification=centering,skip=2pt]{caption}
 \usepackage[font=scriptsize]{subfig}
@@
 
-\date{June 2020}
+\date{July 2020}
 
@@
 the economy grew substantially,
-schooling increased for both males and females,
+schooling increased for males and females,
 and the total fertility rate fell to 2.2 
@@
 Second, more female education, higher household income, and low and declining female labor 
-force participation are all likely to impact birth spacing. 
+force participation all likely impact birth spacing. 
 The combined changes in birth spacing may, therefore, outpace what we have observed in 
@@
 The primary outcomes I examine are average birth intervals, the sex ratio of births, 
-and the likelihood of a next birth. 
+and the likelihood of giving birth. 
 Because sex selection might also affect the distribution of birth intervals, I furthermore
@@
 
-First, over the four decades, average birth intervals lengthen for all, but most for higher 
-parities and more educated women. 
+First, average birth intervals lengthen over the four decades, more so the higher the 
+parity and the more educated the woman.
 Women most likely to use sex selection---well-educated with no sons---had the most 
@@
 
-Figures \ref{fig:bootstrap_low} through \ref{fig:bootstrap_highest}
+Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
 show the predicted outcomes for the four education levels by area of residence.%
@@
 Results are available upon request.
+
+[Urban low and rural highest in online Appendix]
+
 }
@@
 
-% \begin{figure}[htpb]
+% \begin{figure}
 % \centering
-% \caption*{Urban}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_urban_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_urban_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_urban_all}} 
-% \\
-% \caption*{Rural}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_low_rural_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_low_rural_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_low_rural_all}} 
-% \caption{low education}
-% \label{fig:bootstrap_low}
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
+% \caption{combined graphs - low urban}
+% \label{fig:spacing_low_urban}
 % \end{figure}
 
-% \captionsetup[subfigure]{position=top,captionskip=-1pt,farskip=-0.5pt}
-
-% \begin{figure}[htpb]
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_rural}
+\caption{combined graphs - low rural}
+\label{fig:spacing_low_rural}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
+\caption{combined graphs - med urban}
+\label{fig:spacing_med_urban}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_rural}
+\caption{combined graphs - med rural}
+\label{fig:spacing_med_rural}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
+\caption{combined graphs - high urban}
+\label{fig:spacing_high_urban}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_rural}
+\caption{combined graphs - high rural}
+\label{fig:spacing_high_rural}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_urban}
+\caption{combined graphs - highest urban}
+\label{fig:spacing_highest_urban}
+\end{figure}
+
+% \begin{figure}
 % \centering
-% \rotatebox[origin=c]{90}{\small{Urban}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
-%     \end{minipage}
-% }
-% \subfloat[Fourth Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{Rural}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
-%     \end{minipage}
-% } 
-% \subfloat[Fourth Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
-%     \end{minipage}
-% } 
-% \caption{Estimated average spell length, sex ratio, and probability of 
-% a next birth for women with no education}
-% \label{fig:bootstrap_low}
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
+% \caption{combined graphs - highest rural}
+% \label{fig:spacing_highest_rural}
 % \end{figure}
-
-\begin{sidewaysfigure}
-\captionsetup[subfigure]{captionskip=-1pt,farskip=-0.5pt}
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.31\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.31\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.31\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
-    \end{minipage}
-}
-\caption{Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with no education}
-\label{fig:bootstrap_low}
-\end{sidewaysfigure}
-
-\begin{sidewaysfigure}
-\centering
-\ContinuedFloat
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.31\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.31\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.31\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
-    \end{minipage}
-} 
-\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with no education}
-\label{fig:bootstrap_low}
-\end{sidewaysfigure}
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_urban_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_urban_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_urban_all}} 
-% \\
-% \caption*{Rural}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_med_rural_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_med_rural_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_med_rural_all}} 
-% \caption{med education}
-% \label{fig:bootstrap_med}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{Urban}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
-%     \end{minipage}
-% }
-% \subfloat[Fourth Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{Rural}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
-%     \end{minipage}
-% } 
-% \subfloat[Fourth Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
-%     \end{minipage}
-% } 
-% \caption{Estimated average birth interval, sex ratio, and probability of 
-% a next birth for women with one to seven years of education}
-% \label{fig:bootstrap_med}
-% \end{figure}
-
-\begin{sidewaysfigure}
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
-    \end{minipage}
-}
-\caption{Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with one to seven years of education}
-\label{fig:bootstrap_med}
-\end{sidewaysfigure}
-
-\begin{sidewaysfigure}
-\centering
-\ContinuedFloat
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
-    \end{minipage}
-} 
-\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with one to seven years of education}
-\label{fig:bootstrap_med}
-\end{sidewaysfigure}
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_highest_urban_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_highest_urban_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_highest_urban_all}} 
-% \\
-% \caption*{Rural}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_highest_rural_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_highest_rural_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_highest_rural_all}} 
-% \caption{high education}
-% \label{fig:bootstrap_high}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{Urban}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
-%     \end{minipage}
-% }
-% \subfloat[Fourth Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{Rural}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
-%     \end{minipage}
-% } 
-% \subfloat[Fourth Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
-%     \end{minipage}
-% } 
-% \caption{Estimated average birth interval, sex ratio, and probability of 
-% a next birth for women with eight to eleven years of education}
-% \label{fig:bootstrap_high}
-% \end{figure}
-
-\begin{sidewaysfigure}
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
-    \end{minipage}
-}
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
-    \end{minipage}
-}
-\caption{Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with eight to eleven years of education}
-\label{fig:bootstrap_high}
-\end{sidewaysfigure}
-
-\begin{sidewaysfigure}
-\centering
-\ContinuedFloat
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
-    \end{minipage}
-} 
-\subfloat[Fourth Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
-    \end{minipage}
-} 
-\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with eight to eleven years of education}
-\label{fig:bootstrap_high}
-\end{sidewaysfigure}
-
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_highest_urban_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_highest_urban_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_highest_urban_all}} 
-% \\
-% \caption*{Rural}
-% \subfloat[Second Spell]{\includegraphics[width=0.27\textwidth]{bs_spell2_highest_rural_all}} 
-% \subfloat[Third Spell]{\includegraphics[width=0.27\textwidth]{bs_spell3_highest_rural_all}} 
-% \subfloat[Fourth Spell]{\includegraphics[width=0.27\textwidth]{bs_spell4_highest_rural_all}} 
-% \caption{high education}
-% \label{fig:bootstrap_high}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{Urban}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{Rural}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.29\textwidth}
-%         \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
-%     \end{minipage}
-% } 
-% \caption{Estimated average birth interval, sex ratio, and probability of 
-% a next birth for women with twelve or more years of education}
-% \label{fig:bootstrap_highest}
-% \end{figure}
-
-\begin{sidewaysfigure}
-\centering
-\rotatebox[origin=c]{90}{\small{Urban}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
-    \end{minipage}
-}
-\caption{Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with twelve or more years of education}
-\label{fig:bootstrap_highest}
-\end{sidewaysfigure}
-
-\begin{sidewaysfigure}
-\centering
-\ContinuedFloat
-\rotatebox[origin=c]{90}{\small{Rural}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.29\textwidth}
-        \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
-    \end{minipage}
-} 
-\caption{(Continued) Estimated average birth interval, sex ratio, and probability of 
-a next birth for women with twelve or more years of education}
-\label{fig:bootstrap_highest}
-\end{sidewaysfigure}
 
@@
 months from the first period.
-The longest average interval was 51 months for the third spell for urban women with twelve or 
-more years of education who had no boys, an increase of approximately a year.
+The longest average interval was 51 months for the third spell for urban women with twelve 
+or more years of education who had no boys, an increase of approximately a year over
+4 decades.
 For comparison, the median birth intervals reported for the NFHS have barely
-moved over time, staying at approximately 31 months.%
+moved over time, staying at approximately 31 months, and fast changing countries have 
+median birth intervals that increase change around 3.5 months per decade 
+\citep{Rutstein2011,Casterline2016}.%
 \footnote{
-See
-\citet[][p.\ 110--112]{International-Institute-for-Population-Sciences-IIPS1995},
-\citet[][p.\ 98--103]{International-Institute-for-Population-Sciences-IIPS2000},
-\citet[][p.\ 88--91]{International-Institute-for-Population-Sciences-IIPS2007}, and
-\citet[][p.\ 81--82]{International-Institute-for-Population-Sciences-IIPS2017}.
-Median estimates are in
-Appendix Tables \ref{tab:p25_p50_p75_low} through \ref{tab:p25_p50_p75_highest}.
-}
-This lack of change in the NFHS reported birth intervals underscores the importance of 
-accounting for censoring of birth spells when trying to understand how birth spacing 
-is changing over time.
+Median estimates are in Appendix Tables \ref{tab:p25_p50_p75_low} through 
+\ref{tab:p25_p50_p75_highest}.
+}
+This lack of change in the NFHS reported birth intervals over round underscores the 
+importance of accounting for censoring of birth spells when trying to understand how birth 
+spacing is changing over time.
 
@@
 }
-
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_low_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_low_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_low_urban}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_med_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_med_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_med_urban}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_high_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_high_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_high_urban}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_highest_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_highest_urban}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-25th and 75th Percentile Birth Intervals for Urban Women by Spell and Education
-}
-\label{fig:combined_p25_p75_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup[subfigure]{position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_low_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_low_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_low_rural}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_med_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_med_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_med_rural}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_high_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_high_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell4_high_rural}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell2_highest_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{combined_p25_p75_spell3_highest_rural}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-25th and 75th Percentile Birth Intervals for Rural Women by Spell and Education
-}
-\label{fig:combined_p25_p75_rural}
-\end{figure}
 
@@
 The most extreme example is best-educated urban women with two girls, who have a sex ratio 
-approaching 80 and an average birth interval of 42 months. 
+approaching 80 and an average birth interval of 51 months. 
 This birth interval is seven months longer than with at least one boy.
+
+Even more striking is the change for this group when sex selection was first introduced.
+There was a six months jump, from 39.5 to 45.4, in average spacing between the first and 
+the second period for women with two girls, but only a month increase for the other sex 
+compositions.
+Furthermore, the 75th percentile birth interval with two girls increased from 48 months to 
+64 months with two girls over the period, while the other sex compositions showed a 
+slightly decrease from around 55 months to 54 months.
+
+Theses changes may even be an underestimate of the changes in birth spacing sine
+this particular group appear to have had access to sex selection even before it became
+widespread as shown by the unequal sex ratio for the 1972--1984 period for women with
+two girls.
 
@@
 
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{1972-1984}}
-\setcounter{subfigure}{-1}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[No Eduction]{\includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{-0} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[One to Seven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Second Child's Infant Mortality 
-for Women with No Education
-and Women with One to Seven Years of Education}
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{1972-1984}}
+% \setcounter{subfigure}{-1}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[No Eduction]{\includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{-0} 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[One to Seven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{1985-1994}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{1995-2004}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{2005-2016}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
+%     \end{minipage}
+% } 
+% \caption{Predicted Probability of Second Child's Infant Mortality 
+% for Women with No Education
+% and Women with One to Seven Years of Education}
+% \label{fig:mortality_low_med}
+% \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{1972-1984}}
+% \setcounter{subfigure}{-1}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Eight to Eleven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \begin{minipage}[t]{0.39\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
+% \\
+% \rotatebox[origin=c]{90}{\small{1985-1994}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{1995-2004}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{2005-2016}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.37\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies} 
+%     \end{minipage}
+% } 
+% \caption{Predicted Probability of Second Child's Infant Mortality 
+% for Women with Eight to Eleven of Education
+% and Women with Twelve or More Years of Education}
+% \label{fig:mortality_high_highest}
+% \end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_low_med}
+\caption{Mortality low medium}
 \label{fig:mortality_low_med}
@@
 
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{1972-1984}}
-\setcounter{subfigure}{-1}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Eight to Eleven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\begin{minipage}[t]{0.39\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
-\\
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Second Spell]{
-    \begin{minipage}{0.37\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Second Child's Infant Mortality 
-for Women with Eight to Eleven of Education
-and Women with Twelve or More Years of Education}
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_high_highest}
+\caption{Mortality high highest}
 \label{fig:mortality_high_highest}

### 2020-07-30 paper/sex_selection_spacing-ver4.tex
Major editing of birth interval section(s) plus other edits
- remove delay effect discussion
- comment out conditional survival curves
- Reorganize birth interval discussion
- Remove average discussion of Estimation Strategy section

@@
 
-If parents realize that longer spacing leads to better child outcomes, we may even observe 
-later conception, especially when, with sex selection, the next child is likely to be a boy.
-Working in the opposite direction of this "delay" effect is that women with more education 
-can, in principle, space their children closer together without substantially increasing 
-child mortality risk. 
-However, given the apparent lack of pressure to return to the labor force, this effect is 
-likely small.
+% If parents realize that longer spacing leads to better child outcomes, we may even observe 
+% later conception, especially when, with sex selection, the next child is likely to be a boy.
+% Working in the opposite direction of this "delay" effect is that women with more education 
+% can, in principle, space their children closer together without substantially increasing 
+% child mortality risk. 
+% However, given the apparent lack of pressure to return to the labor force, this effect is 
+% likely small.
 
@@
 
-For birth intervals, I estimate the average birth interval and a set of percentile
-birth intervals.
-To find the average birth interval, I calculate, for each woman, the probability of 
-giving birth in each $t$, and her expected spell length from these probabilities.
-I then average the individual expected spell lengths across women using their parity 
-progression probabilities as weights.
-Finally, I add nine months because spells begin nine months after the previous birth.
-The process is similar for the percentile birth intervals, except that I use the time 
-point when there is a given percent probability that a woman will give birth, conditional 
-on her giving birth in the spell.
+For birth intervals, I estimate a set of percentile birth intervals.
+To find a given percentile birth interval, I first calculate for each woman when there is 
+a given percent chance that she will have given birth, conditional on the probability of 
+giving birth in the spell.
+I then add nine months to account for the start of the spell. 
+For example, with an 80 percent chance of giving birth by the end of the spell, the median birth 
+interval is the predicted number of months before a woman passes the 40 percent mark on her 
+survival curve. 
+The reported statistic is the average of a given percentile interval across all women in 
+a given sample using the individual progression probabilities as weights.
 
@@
 I estimate the competing risk hazard model for each spell, education, and period 
-combination and then predict average birth interval in months, sex ratio, and the 
-probability of having a birth in that spell.
+combination and then predict 25th, 50th, and 75th percentiles birth intervals in 
+months, the sex ratio, and the probability of having a birth in that spell.
+Sex selection increases all three percentile birth intervals, but the effects of abortions 
+are easiest to observe in the 75th percentile birth interval, 
+and it is also the changes in the longest birth intervals that will likely the largest 
+impact on fertility measures.
+The 25th percentile captures changes in the short spacing, which is the most likely to 
+have an adverse impact on health.
 
 Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
-show the predicted outcomes for the four education levels by area of residence.%
-\footnote{
-For legibility, the graphs do not show standard errors.
-The graphed values, with standard errors, are shown in Appendix Tables 
-\ref{tab:avg_sex_ratio_low} through \ref{tab:avg_sex_ratio_highest}.
-Furthermore, I do not show the results for the fourth spell the best-educated women since 
-the low number of births, especially with one or more boys, make the spacing and sex ratio 
-results very noisy.
-Results are available upon request.
-
-[Urban low and rural highest in online Appendix]
-
-}
-For comparison, the graphs for the sex ratio also show the natural sex ratio, 
-approximately 51.2 percent \citep{ben-porath76b,jacobsen99,Portner2015b}.
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
-% \caption{combined graphs - low urban}
-% \label{fig:spacing_low_urban}
-% \end{figure}
+show the predicted outcomes for the four education levels by area of residence.
+The underlying values with bootstrapped standard errors are available in the online 
+appendix.
+The sex ratio graphs also show the natural sex ratio, approximately 51.2 percent 
+\citep{ben-porath76b,jacobsen99,Portner2015b}.
+Results for urban women without education, rural women with twelve or more years of 
+education, and the fourth spell for women with twelve or more years of education are
+presented in the online appendix because they are based on relatively few observations.
 
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
-\caption{combined graphs - med urban}
-\label{fig:spacing_med_urban}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
+\caption{combined graphs - low urban}
+\label{fig:spacing_low_urban}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
-\caption{combined graphs - high urban}
-\label{fig:spacing_high_urban}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
+\caption{combined graphs - med urban}
+\label{fig:spacing_med_urban}
 \end{figure}
@@
 \centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
+\caption{combined graphs - high urban}
+\label{fig:spacing_high_urban}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
+\caption{combined graphs - highest rural}
+\label{fig:spacing_highest_rural}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_urban}
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
-% \caption{combined graphs - highest rural}
-% \label{fig:spacing_highest_rural}
-% \end{figure}
-
-Average birth intervals have increased over time across all groups, but
-the higher the parity and the higher the schooling, the larger the
-increases.
-
-In the latest period, the shortest average birth interval is 33 months for
-women with no education in the second spell, an increase of a couple of
-months from the first period.
-The longest average interval was 51 months for the third spell for urban women with twelve 
-or more years of education who had no boys, an increase of approximately a year over
-4 decades.
-For comparison, the median birth intervals reported for the NFHS have barely
-moved over time, staying at approximately 31 months, and fast changing countries have 
-median birth intervals that increase change around 3.5 months per decade 
-\citep{Rutstein2011,Casterline2016}.%
-\footnote{
-Median estimates are in Appendix Tables \ref{tab:p25_p50_p75_low} through 
-\ref{tab:p25_p50_p75_highest}.
-}
-This lack of change in the NFHS reported birth intervals over round underscores the 
-importance of accounting for censoring of birth spells when trying to understand how birth 
-spacing is changing over time.
-
-Parity progression probabilities are lower the higher the education and are
-falling across all groups over time, but the extent of the decline depends crucially on 
-the sex composition of prior children and the parity.
-Women with no sons are still the most likely to 
-have the next birth, and this group has seen substantially smaller declines in
-the likelihood of having another birth than women with one or more sons.%
-\footnote{
-However, there is also some evidence that parents prefer a mix of boys and girls: for 
-the fourth spell women with two boys \emph{and} a girl
-consistently have the lowest parity progression probability.
-}
-For urban women with eight to eleven years of education, for example, the second spell
-probability of a next child declined by eight percentage points if the first child was a 
-girl, but 15 percentage points if it was a boy.
-Even more extreme is the fourth spell, where the likelihood of a birth declined by six 
-percentage points to 75 percent if the woman had three children, but by almost 40 
-percentage points to 25 percent if she had two boys and a girl.
-
-\subsection{Distribution of Birth Spacing}
-
-To better understand what factors are behind the changes in average spacing, I next 
-examine its distribution---represented by the 25th and 75th percentiles 
-of predicted birth intervals. 
-This approach can capture differences across groups with similar changes in average spacing. 
-For example, imagine that sex selection is behind an increase in average birth spacing, 
-but that women still try to conceive early. 
-In that case, we should see little change in the 25th percentile, but the 75th percentile 
-spacing becomes much longer because those who use sex selection will have two or more 
-pregnancies rather than one. 
-In contrast, a general increase in spacing would show up as lengthening of both percentiles.
-
-Figures \ref{fig:combined_p25_p75_urban} and \ref{fig:combined_p25_p75_rural} 
-show how the predicted 25th and 75th percentile birth intervals have changed over time 
-by spell and education.%
-\footnote{
-The Appendix shows conditional survival curves for all groups, and 
-Appendix Tables \ref{tab:p25_p50_p75_low} through \ref{tab:p25_p50_p75_highest} 
-show 25th, 50th, and 75th percentiles durations with bootstrapped standard errors.
-}
-
-For women with no or little education, the increases in average spacing
-come predominantly from increases in the long end of the spacing
-distribution rather than from a general increase.
-Hence, spacing is still very short for many women, with 25 percent or more having
-their next birth within two years of the prior birth, even in the last period.
-Furthermore, the increases in the 75th percentile birth intervals are relatively small
-for the second spell and slightly more substantial for the third spell at around five months.
-Most of the divergence across sex compositions happen for the fourth spell, where 
-the most significant increases are for women with two or three sons.
-However, even for women with no or one son, the birth intervals have
-increased by a half to a full year, consistent with some use of sex
-selection.
-
-The 25th percentile birth intervals for women with eight to eleven years of education also 
-changed relatively little over time and is, as for the less-educated women, close to
-around two years since the prior birth.
-Hence, the increases in the longer end of the distribution drive
-the change in average spacing.
-For example, the 75th percentile spacing length for women with two girls in the third 
-spell increased by more than 15 months, mainly as the result of more widespread use of sex 
-selection as the sex ratios above indicate.
-
-The most educated urban women show an unusual pattern for the third spell, where there 
-is virtually no change in either the 25th or 75th percentile birth intervals in the
-presence of at least one boy.
-The 75th percentile birth interval, however, increases by more than 20 months,
-corresponding to the massive increase in the sex ratio to almost 80 percent in the 
-latest period.
-Hence, the increases in the length of the longer intervals over time are
-the main reason for the increases in average birth spacing and the
-reversal in the spacing pattern by sex composition, consistent with
-substantial use of sex selection.
-
-Although most of the increases come from among the longer intervals, there is some 
-evidence for the ``delay'' effect discussed above, where parents conceive later
-precisely because they know that the next child is likely to be a boy since they plan
-to use sex selection.
-The best example is for the best-educated urban women in the third spell, where, in the 
-last two periods, the spacing to the third child is significantly longer if the two prior 
-children were girls than if they already had one or two boys.
-These two periods are the periods where the predicted sex ratios are 70 and 80 percent,
-respectively.
-There is also a significantly longer spacing with only girls for women with eight to
-eleven years of education in the last period for the third and fourth spell, although
-the difference is substantially smaller.
-
-\subsection{Sex Selection and Birth Spacing}
-
-The results above show that average birth intervals increased over time across all groups 
-and that these increases are larger for higher parities and with more schooling. 
-Furthermore, the increases come predominately from the longer intervals getting even 
-longer while there is little change in the length of the shortest intervals.
-
-What do these results tell us about the extent to which the introduction of sex selection 
-changed birth spacing across sex compositions? 
-There are three broad groups in the data.
-
-The first group consists of women who do not use sex selection even if they have only 
-girls, such as rural women with no education. 
-For this group, the shortest spacing---across all spells---is when they have only girls. 
-Notably, the difference in birth intervals across sex compositions has even grown over 
-time as spacing when sons are present increased.
-
-In the second group are women who use sex selection and who, therefore, show the expected 
-associated increase in birth intervals for those sex compositions. 
-However, the intervals for their other sex compositions have increased even more. 
-The result is that the relative pattern remains more or less the same. 
-An example is women with eight more years of education in the second spell.
-
-The final group consists of those women, who, in the absence of a son, have the most 
-biased sex ratios and the longest birth intervals, and where this spacing is longer than 
-for the other possible sex compositions. 
-The most extreme example is best-educated urban women with two girls, who have a sex ratio 
-approaching 80 and an average birth interval of 51 months. 
-This birth interval is seven months longer than with at least one boy.
-
+The results show three broad trends.
+% [Birth intervals]
+First, 
+over the four decades, birth intervals have lengthen, whether measured by the
+25th, 50th, or 75th percentile.
+These increases are larger the higher the education of the mother, the higher the parity, 
+and the higher the percentile measure.
+
+% [Parity progression probability]
+Second, 
+the likelihood of a next birth has fallen over time, and the declines are
+larger the higher the education, the higher the parity, and with the presence of at
+least one son. 
+Within a given spell and period, parity progressions are lower in urban than in rural areas, 
+if at least one son is present, and the more educated the mother.
+
+% [Sex ratios]
+Finally, 
+the sex ratios of next births has become more male dominated for women with no
+sons, while there are no clear trends for the other sex compositions.
+The increases in the predicted percent boys are larger the higher the education and the 
+higher the parity.
+Furthermore, for a given spell and period, sex ratios in the absence of a son are higher 
+in urban than in rural areas, the higher the education of the mother, and the higher
+the parity.
+There is some evidence of unnaturally high percentage boys born even when women have one 
+son, although most are clearly lower than in the absence of a son and the failing fertility
+make more of those estimate noisy.
+
+% [25th percentile birth intervals]
+Despite the increases in birth intervals and the decline in fertility, a remarkably high 
+proportion of birth intervals are still very short.
+For all but the most educated, more than 25 percent of women have their second and their
+third child within 24 months of their previous child.
+Furthermore, even with the larger increases in birth intervals with higher parity, the 
+25th percentile birth intervals for the fourth spell is around 24 months for women with 
+less than eight years of education.
+
+% [median birth intervals]
+The median birth intervals have increased more than the 25th percentile birth intervals
+but are still also relatively short.
+Although most median birth intervals have increased by three to six months over the four 
+decades, the majority of median birth intervals are still at 36 months or below, 
+with the shortest only 29 months.
+For comparison, fast changing countries have median birth intervals that increase around 
+3.5 months per decade with declining fertility \citep{Rutstein2011,Casterline2016}.
+Furthermore, the NFHS reports show median closed birth intervals that have barely
+moved over time, staying at approximately 31 months, underscoring the importance of 
+accounting for censoring of birth spells when trying to understand how birth spacing 
+changes over time.
+
+An important exception to the relatively short median intervals come from the better 
+educated women, especially in the absence of sons.
+The longest median interval was 48 months for the third spell for urban women with twelve 
+or more years of education who had no boys, an increase of almost 15 months over
+four decades.
+Similary, urban women with eight to eleven years of education and no sons had median
+birth intervals of around 40 months, an increase of about 10 months.
+Finally, the best educated women now have a median second birth interval of around 42
+months whether their first child was a boy or a girl.
+
+% [75th percentile birth intervals]
+The most substantial differences across women come from the longer birth intervals, 
+captured by the 75th percentile birth intervals.
+For the two lowest education groups the increases in the 75th percentile birth 
+intervals are relatively small for the second spell and slightly more substantial for the 
+third spell at around five months.
+However, the fourth spell show significant increases, especially for women with two
+or three sons, with increases of fifteen to twenty months.
+The fourth spell is also where most of the divergence across sex compositions happen,
+but even for women with no or one son, the 75th percentile birth intervals have
+increased by a half to a full year.
+For women with eight to eleven years of education, the 75th percentile spacing length for 
+women with two girls in the third spell increased by more than 15 months, mainly as the 
+result of more widespread use of sex selection as the sex ratios above indicate.
+
+% [Exceptions to the results]
+The best-educated women are an especially interesting case that run somewhat counter
+to the results above.
+First, despite a rapidly declining probability of having a third child when they already 
+have a son, there is little change in the associated birth intervals and all are lower for 
+the third spell than for the second.
+Second, the massive increase in the sex ratio to almost 80 percent boys for women with two 
+girls is associated with a more than 20 month increase in the 75th percentile birth 
+interval.
+The third spell is also the case with the clearest reversal in the spacing pattern by sex 
+composition; the birth intervals with two girls are consistently longer than with one
+or two sons no matter the percentile used.
+
+What do these results tell us about the role of son preference and the extent to which 
+the introduction of sex selection changed birth spacing across sex compositions?
+
+The clearest illustration of how the combination of son preference and the introduction of 
+sex selection impacted birth spacing comes from the third spell of the best-educated urban 
+women.
+Women with two girls have a predicted sex ratio for their third child approaching 80 
+percent boys and a 75th percentile birth interval of almost 70 months, about 13 months
+longer than if they had at least one son.
 Even more striking is the change for this group when sex selection was first introduced.
-There was a six months jump, from 39.5 to 45.4, in average spacing between the first and 
-the second period for women with two girls, but only a month increase for the other sex 
-compositions.
-Furthermore, the 75th percentile birth interval with two girls increased from 48 months to 
-64 months with two girls over the period, while the other sex compositions showed a 
+The 75th percentile birth interval with two girls increased from 48 months to 
+64 months with two girls, while the other sex compositions showed a 
 slightly decrease from around 55 months to 54 months.
-
 Theses changes may even be an underestimate of the changes in birth spacing sine
@@
 
-In summary, although birth spacing has increased over time with improving economic 
+Even for the women the least likely to use sex selection, such as rural women with no 
+education, son preference shows up clearly. 
+For this group, the shortest spacing---across all spells---is when they have only girls. 
+Notably, the difference in birth intervals across sex compositions has grown over 
+time as spacing when sons are present increased.
+Despite the strong son preference in spacing and sex ratios, there is also some indication 
+that parents prefer a mix of boys and girls;
+women with two boys \emph{and} a girl consistently have the lowest parity progression 
+probability in the fourth spell across education levels.
+
+Did the predictions of a turn-around in the use of sex selection come true?
+There is no clear evidence for or against a reversal in the use of sex selection, with 
+some showing increases in sex ratios between the last two periods, others little change, 
+and some a decline.
+The best-educated women is again a good illustration.
+The percent boys born to women with two girls continued to increase over the last two
+periods, but the likelihood of a third birth declined and when the first child was a girl, 
+the sex ratio for the second birth dropped slightly as did the probability of a second birth. 
+There is, however, also cases where there is clearly no abatement in the increasing use of 
+sex selection. 
+The sex ratios in the absence of girls continued to increase for rural women with
+one to seven years of education and the likelihood of an additional birth remained high.
+
+% [Interpretation]
+How do these changes in birth intervals tie in with the changes in India over the four
+decades?
+% [TK economic growth? -> higher return to education for males -> lower fertility and
+% higher investment in boys' education -- has anybody looked at this?]
+First, the parity progression probabilities have been falling over time across all 
+education levels, especially for women with at least one son.
+Falling fertility is associated with increases in longer spacing, although it is still an 
+unresolved question why \citep{Casterline2016}.
+What is especially interesting is that the results for the most educated women show that 
+the rapidly declining probability of a third birth for women with one or two sons did not 
+lengthen the birth intervals at any of the percentiles.
+One possibility is that the most educated women have both better access to modern
+contraceptive and are better at using traditional contraceptive methods 
+\citep{Rosenzweig1989}.
+
+Second, there is evidence that in situations where sex selection does not play a role 
+in birth intervals, women with the smallest change in birth intervals are also those most 
+likely to work.
+For example, the increases in average third spell birth intervals for urban women with
+one boy and one girl over the four decades were 2.7, 3.4, 5.8, and 1.8 months from lowest 
+to highest education groups.%
+\footnote{
+For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0, respectively.
+See the online appendix tables for the average birth intervals.
+}
+This means that the group with the lowest labor force participation, women with eight to 
+eleven years of education, was also the group with the largest increases in average 
+spacing, likely driven by the substantial improvement in household income that came
+from economic growth.
+
+Finally, although birth spacing has increased over time with improving economic 
 conditions and falling fertility, most of the increases in birth spacing come from the
@@
 women with two girls, which is the group with the most biased sex ratio.
-There is no clear evidence for or against a reversal in the use of sex selection, with 
-some showing increases in sex ratios between the last two periods, others little change, 
-and some a decline.
 
@@
 and, therefore, may end up with multiple abortions.
-The exception to the small change in short spacing is the delay in conception for women 
-with very high use of sex selection, presumably because this group knows that
-the next child will be a boy.
 
@@
 \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
+\subfloat[NFHS-4]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
 \caption{Ratio of Boys for ``First'' Births by Survey Round}
@@
 \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3_bo2}} 
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4_bo2}} 
+\subfloat[NFHS-4]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4_bo2}} 
 \caption{Ratio of Boys for ``Second'' Births by Survey Round}
@@
 
-\section{Duration Results Tables}
+\section{Additional Results Figures and  Tables}
 
@@
 
-The first set of tables, Tables \ref{tab:avg_sex_ratio_low}, \ref{tab:avg_sex_ratio_med}, 
+Figures \ref{fig:spacing_low_urban} and \ref{fig:spacing_highest_rural} show 25th, 50th,
+and 75th percentile birth intervals, the sex ratio, and the probability of parity
+progression by spell for urban women with no education and rural women with twelve or
+more years of education, respectively.
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
+\caption{combined graphs - low urban}
+\label{fig:spacing_low_urban}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
+\caption{combined graphs - highest rural}
+\label{fig:spacing_highest_rural}
+\end{figure}
+
+The first set of tables, Tables \ref{tab:p25_p50_p75_low}, \ref{tab:p25_p50_p75_med},
+\ref{tab:p25_p50_p75_high}, and \ref{tab:p25_p50_p75_highest} show 25th, 50th, and
+75th percentile birth intervals together with their standard errors.
+The standard errors for all measures are based on bootstrapping,
+where the model is repeatedly estimated using resampling with replacement.
+
+The second set of tables, 
+Tables \ref{tab:avg_sex_ratio_low}, \ref{tab:avg_sex_ratio_med}, 
 \ref{tab:avg_sex_ratio_high}, and \ref{tab:avg_sex_ratio_highest}, show predicted average 
-birth intervals, sex ratios, and 
-probabilities of having a birth by decade, spell, and sex composition for the three 
-education levels separated by the area of residence, together with standard errors for all 
-three outcomes.
-The standard errors are based on bootstrapping for all three measures,
-where the model is repeatedly estimated using resampling with replacement.
+birth intervals, sex ratios, and probabilities of having a birth by decade, spell, and sex 
+composition for the four education levels separated by the area of residence, together 
+with bootstrapped standard errors for all three outcomes.
+To find the average birth interval, I calculate, for each woman, the probability of 
+giving birth in each t, and her expected spell length from these probabilities. 
+I then average the individual expected spell lengths across women using their parity 
+progression probabilities as weights. Finally, I add nine months because spells begin 
+nine months after the previous birth.
 
@@
 
+\input{../tables/bootstrap_duration_p25_p75_low_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_med_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_high_all.tex}
+
+\input{../tables/bootstrap_duration_p25_p75_highest_all.tex}
+
 \input{../tables/bootstrap_duration_avg_sex_ratio_low_all.tex}
@@
 
-\input{../tables/bootstrap_duration_p25_p75_low_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_med_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_highest_all.tex}
-
 \clearpage
 
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_urban}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_urban}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_urban}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_urban}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-Changes in 25th Percentile Birth Intervals for Urban Women by Spell and Education
-}
-\label{fig:p25_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_rural}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_rural}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_rural}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_rural}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-Changes in 25th Percentile Birth Intervals for Rural Women by Spell and Education
-}
-\label{fig:p25_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_urban}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_urban}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_urban}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_urban}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-Changes in 50th Percentile Birth Intervals for Urban Women by Spell and Education
-}
-\label{fig:p50_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_rural}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_rural}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_rural}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_rural}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-Changes in 50th Percentile Birth Intervals for Rural Women by Spell and Education
-}
-\label{fig:p50_rural}
-\end{figure}
-
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_urban}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_urban}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_urban}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_urban}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_urban}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_urban}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-Changes in Average Birth Intervals for Urban Women by Spell and Education
-}
-\label{fig:avg_urban}
-\end{figure}
-
-\begin{figure}[htpb]
-\captionsetup[subfigure]{labelformat=empty,position=top}
-\captionsetup{font=footnotesize,skip=2pt}
-\centering
-\caption*{No education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_rural}}
-\\
-\caption*{One to Seven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_rural}}
-\\
-\caption*{Eight to Eleven Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_rural}}
-\subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_rural}}
-\\
-\caption*{Twelve or More Years of Education}
-\subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_rural}}
-\subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_rural}}
-\begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-\captionsetup{font=normalsize}
-\caption{
-Changes in Average Birth Intervals for Rural Women by Spell and Education
-}
-\label{fig:avg_rural}
-\end{figure}
+% \begin{figure}[htpb]
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+% \captionsetup{font=footnotesize,skip=2pt}
+% \centering
+% \caption*{No education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_urban}}
+% \\
+% \caption*{One to Seven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_urban}}
+% \\
+% \caption*{Eight to Eleven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_urban}}
+% \\
+% \caption*{Twelve or More Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_urban}}
+% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+% \captionsetup{font=normalsize}
+% \caption{
+% Changes in 25th Percentile Birth Intervals for Urban Women by Spell and Education
+% }
+% \label{fig:p25_urban}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+% \captionsetup{font=footnotesize,skip=2pt}
+% \centering
+% \caption*{No education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_rural}}
+% \\
+% \caption*{One to Seven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_rural}}
+% \\
+% \caption*{Eight to Eleven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_rural}}
+% \\
+% \caption*{Twelve or More Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_rural}}
+% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+% \captionsetup{font=normalsize}
+% \caption{
+% Changes in 25th Percentile Birth Intervals for Rural Women by Spell and Education
+% }
+% \label{fig:p25_rural}
+% \end{figure}
+% 
+% \begin{figure}[htpb]
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+% \captionsetup{font=footnotesize,skip=2pt}
+% \centering
+% \caption*{No education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_urban}}
+% \\
+% \caption*{One to Seven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_urban}}
+% \\
+% \caption*{Eight to Eleven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_urban}}
+% \\
+% \caption*{Twelve or More Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_urban}}
+% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+% \captionsetup{font=normalsize}
+% \caption{
+% Changes in 50th Percentile Birth Intervals for Urban Women by Spell and Education
+% }
+% \label{fig:p50_urban}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+% \captionsetup{font=footnotesize,skip=2pt}
+% \centering
+% \caption*{No education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_rural}}
+% \\
+% \caption*{One to Seven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_rural}}
+% \\
+% \caption*{Eight to Eleven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_rural}}
+% \\
+% \caption*{Twelve or More Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_rural}}
+% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+% \captionsetup{font=normalsize}
+% \caption{
+% Changes in 50th Percentile Birth Intervals for Rural Women by Spell and Education
+% }
+% \label{fig:p50_rural}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+% \captionsetup{font=footnotesize,skip=2pt}
+% \centering
+% \caption*{No education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_urban}}
+% \\
+% \caption*{One to Seven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_urban}}
+% \\
+% \caption*{Eight to Eleven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_urban}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_urban}}
+% \\
+% \caption*{Twelve or More Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_urban}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_urban}}
+% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+% \captionsetup{font=normalsize}
+% \caption{
+% Changes in Average Birth Intervals for Urban Women by Spell and Education
+% }
+% \label{fig:avg_urban}
+% \end{figure}
+% 
+% 
+% \begin{figure}[htpb]
+% \captionsetup[subfigure]{labelformat=empty,position=top}
+% \captionsetup{font=footnotesize,skip=2pt}
+% \centering
+% \caption*{No education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_rural}}
+% \\
+% \caption*{One to Seven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_rural}}
+% \\
+% \caption*{Eight to Eleven Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_rural}}
+% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_rural}}
+% \\
+% \caption*{Twelve or More Years of Education}
+% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_rural}}
+% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_rural}}
+% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
+% \captionsetup{font=normalsize}
+% \caption{
+% Changes in Average Birth Intervals for Rural Women by Spell and Education
+% }
+% \label{fig:avg_rural}
+% \end{figure}
 
@@
 
-\section{Survival Curves Conditional on Parity Progression for All Education and Spell Groups}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% [FIRST SPELL]
-
-% \subsection{First Spell}
-% 
-% \input{../figures/appendix_spell1_low.tex}
-% 
-% \input{../figures/appendix_spell1_med.tex}
-% 
-% \input{../figures/appendix_spell1_high.tex}
+% \section{Survival Curves Conditional on Parity Progression for All Education and Spell Groups}
+% 
+% \setcounter{figure}{0}
+% \setcounter{table}{0}
+% 
+% 
+% % [FIRST SPELL]
+% 
+% % \subsection{First Spell}
+% % 
+% % \input{../figures/appendix_spell1_low.tex}
+% % 
+% % \input{../figures/appendix_spell1_med.tex}
+% % 
+% % \input{../figures/appendix_spell1_high.tex}
+% % 
+% % \begin{figure}[htpb]
+% % \centering
+% % \caption*{No Education}
+% % \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
+% % \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
+% % \caption*{1-7 Years of Education}
+% % \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
+% % \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
+% % \caption*{8 or more Years of Education}
+% % \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_highest_urban_pps}} 
+% % \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_highest_rural_pps}} 
+% % \caption{Survival curves conditional on progression to first birth; start point is month of marriage}
+% % \label{fig:results_spell1_pps}
+% % \end{figure}
+% % 
+% % 
+% % \clearpage
+% % \newpage
+% % 
+% \subsection{Second Spell}
+% 
+% 
+% % \input{../figures/appendix_spell2_low.tex}
+% 
+% 
+% % PARITY PROGRESSION SURVIVAL CURVES - Low
+% 
+% % Low education
+% \vspace*{-0.75cm}
+% \begin{figure}[hp!]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2005]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with no education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell2_low_pps}
+% \end{figure}
+% 
+% 
+% 
+% 
+% % SPELL 2 - URBAN - MEDIUM
+% 
+% % \input{../figures/appendix_spell2_med.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - MEDIUM
+% 
+% 
+% % Low education
 % 
@@
 % \centering
-% \caption*{No Education}
-% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
-% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
-% \caption*{1-7 Years of Education}
-% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
-% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
-% \caption*{8 or more Years of Education}
-% \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_highest_urban_pps}} 
-% \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_highest_rural_pps}} 
-% \caption{Survival curves conditional on progression to first birth; start point is month of marriage}
-% \label{fig:results_spell1_pps}
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.32\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with 1-7 years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell2_med_pps}
+% \end{figure}
+% 
+% 
+% 
+% % High education
+% 
+% % \input{../figures/appendix_spell2_high.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - High education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with eight to eleven years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell2_high_pps}
+% \end{figure}
+% 
+% 
+% % Highest education
+% 
+% % PARITY PROGRESSION SURVIVAL - Highest education
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with twelve or more years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell2_highest_pps}
 % \end{figure}
@@
 % 
-\subsection{Second Spell}
-
-% \input{../figures/appendix_spell2_low.tex}
-
-% PARITY PROGRESSION SURVIVAL CURVES - Low
-
-% Low education
-\vspace*{-0.75cm}
-\begin{figure}[hp!]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2005]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_low_pps}
-\end{figure}
-
-% SPELL 2 - URBAN - MEDIUM
-
-% \input{../figures/appendix_spell2_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-% Low education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.32\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1-7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_med_pps}
-\end{figure}
-
-% High education
-
-% \input{../figures/appendix_spell2_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - High education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with eight to eleven years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_high_pps}
-\end{figure}
-
-% Highest education
-
-% PARITY PROGRESSION SURVIVAL - Highest education
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with twelve or more years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell2_highest_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Third Spell}
-
-% low education
-% \input{../figures/appendix_spell3_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
-\vspace*{-0.75cm}
-\begin{figure}[hp!]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_low_pps}
-\end{figure}
-
-% Medium education
-
-% \input{../figures/appendix_spell3_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_med_pps}
-\end{figure}
-
-% High education
-
-% \input{../figures/appendix_spell3_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - high
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with eight to eleven years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_high_pps}
-\end{figure}
-
-% Highest education
-
-% PARITY PROGRESSION SURVIVAL - highest
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with twelve or more years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell3_highest_pps}
-\end{figure}
-
-\clearpage
-\newpage
-
-\subsection{Fourth Spell}
-
-% low education
-
-% \input{../figures/appendix_spell4_low.tex}
-
-% PARITY PROGRESSION SURVIVAL - LOW
-\vspace*{-0.75cm}
-\begin{figure}[hp!]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with no education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_low_pps}
-\end{figure}
-
-% Medium education
-
-% \input{../figures/appendix_spell4_med.tex}
-
-% PARITY PROGRESSION SURVIVAL - MEDIUM
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_med_pps}
-\end{figure}
-
-% High education
-
-% \input{../figures/appendix_spell4_high.tex}
-
-% PARITY PROGRESSION SURVIVAL - high
-
-\begin{figure}[htpb]
-\centering
-\caption*{Urban}
-\setcounter{subfigure}{-1}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{-0}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{1}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{2}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption*{Rural}
-\setcounter{subfigure}{3}
-\subfloat[1972--1984]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} 
-\setcounter{subfigure}{4}
-\subfloat[1985--1994]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-} \\
-\setcounter{subfigure}{5}
-\subfloat[1995--2004]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\setcounter{subfigure}{6}
-\subfloat[2005--2016]{
-    \begin{minipage}{0.31\textwidth}
-        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
-        \captionsetup[subfigure]{labelformat=parens}
-    \end{minipage}
-}
-\caption{Survival curves conditional on parity progression
-for women with eight to eleven years of education by month beginning 9 months after prior birth.
-}
-\label{fig:results_spell4_high_pps}
-\end{figure}
-
-\clearpage
-\newpage
+% \subsection{Third Spell}
+% 
+% % low education
+% % \input{../figures/appendix_spell3_low.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - LOW
+% \vspace*{-0.75cm}
+% \begin{figure}[hp!]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with no education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell3_low_pps}
+% \end{figure}
+% 
+% 
+% 
+% 
+% % Medium education
+% 
+% % \input{../figures/appendix_spell3_med.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - MEDIUM
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with 1 to 7 years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell3_med_pps}
+% \end{figure}
+% 
+% 
+% 
+% 
+% % High education
+% 
+% % \input{../figures/appendix_spell3_high.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - high
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with eight to eleven years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell3_high_pps}
+% \end{figure}
+% 
+% 
+% % Highest education
+% 
+% % PARITY PROGRESSION SURVIVAL - highest
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with twelve or more years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell3_highest_pps}
+% \end{figure}
+% 
+% 
+% 
+% 
+% 
+% \clearpage
+% \newpage
+% 
+% \subsection{Fourth Spell}
+% 
+% % low education
+% 
+% % \input{../figures/appendix_spell4_low.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - LOW
+% \vspace*{-0.75cm}
+% \begin{figure}[hp!]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with no education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell4_low_pps}
+% \end{figure}
+% 
+% 
+% 
+% 
+% % Medium education
+% 
+% % \input{../figures/appendix_spell4_med.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - MEDIUM
+% 
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with 1 to 7 years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell4_med_pps}
+% \end{figure}
+% 
+% 
+% 
+% % High education
+% 
+% % \input{../figures/appendix_spell4_high.tex}
+% 
+% % PARITY PROGRESSION SURVIVAL - high
+% 
+% \begin{figure}[htpb]
+% \centering
+% \caption*{Urban}
+% \setcounter{subfigure}{-1}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{-0}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{1}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{2}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption*{Rural}
+% \setcounter{subfigure}{3}
+% \subfloat[1972--1984]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } 
+% \setcounter{subfigure}{4}
+% \subfloat[1985--1994]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% } \\
+% \setcounter{subfigure}{5}
+% \subfloat[1995--2004]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \setcounter{subfigure}{6}
+% \subfloat[2005--2016]{
+%     \begin{minipage}{0.31\textwidth}
+%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
+%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
+%         \captionsetup[subfigure]{labelformat=parens}
+%     \end{minipage}
+% }
+% \caption{Survival curves conditional on parity progression
+% for women with eight to eleven years of education by month beginning 9 months after prior birth.
+% }
+% \label{fig:results_spell4_high_pps}
+% \end{figure}
+% 
+% 
+% \clearpage
+% \newpage
+%
 

### 2020-08-03 paper/sex_selection_spacing-ver4.tex
Combine and reorganize birth interval sections
- Make one section
- Discuss results w/o sex selection
- Discuss results w sex selection

@@
 % Explain question and what I am doing
-The first question I address is how birth spacing responded to the significant changes, 
-especially the spread of sex selection, that India experienced. 
-I estimate the competing risk hazard model for each spell, education, and period 
-combination and then predict 25th, 50th, and 75th percentiles birth intervals in 
-months, the sex ratio, and the probability of having a birth in that spell.
-Sex selection increases all three percentile birth intervals, but the effects of abortions 
-are easiest to observe in the 75th percentile birth interval, 
-and it is also the changes in the longest birth intervals that will likely the largest 
-impact on fertility measures.
-The 25th percentile captures changes in the short spacing, which is the most likely to 
-have an adverse impact on health.
-
+The first question I address is how birth spacing responded to the significant 
+changes in India.
 Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
-show the predicted outcomes for the four education levels by area of residence.
+show the 25th, 50th, and 75th percentiles birth intervals in 
+months, the sex ratio, and the probability of having a birth for each spell
+for the four education levels by area of residence.%
+\footnote{
+Results for urban women without education, rural women with twelve or more years of 
+education, and the fourth spell for women with twelve or more years of education are
+presented in the online appendix because they are based on relatively few observations.
+}
 The underlying values with bootstrapped standard errors are available in the online 
@@
 \citep{ben-porath76b,jacobsen99,Portner2015b}.
-Results for urban women without education, rural women with twelve or more years of 
-education, and the fourth spell for women with twelve or more years of education are
-presented in the online appendix because they are based on relatively few observations.
+
+% [not sure where this goes or simply delete]
+%Sex selection increases all three percentile birth intervals, but the effects of abortions 
+%are easiest to observe in the 75th percentile birth interval, 
+%and it is also the changes in the longest birth intervals that will likely the largest 
+%impact on fertility measures.
+%The 25th percentile captures changes in the short spacing, which is the most likely to 
+%have an adverse impact on health.
 
@@
 
-The results show three broad trends.
-% [Birth intervals]
+%The results show three broad trends.
+%% [Birth intervals]
+%First, 
+%over the four decades, birth intervals have lengthen, whether measured by the
+%25th, 50th, or 75th percentile.
+%These increases are larger the higher the education of the mother, the higher the parity, 
+%and the higher the percentile measure.
+
+% [Parity progression probability]
+The parity progression and the sex ratio show two broad trends.
 First, 
-over the four decades, birth intervals have lengthen, whether measured by the
-25th, 50th, or 75th percentile.
-These increases are larger the higher the education of the mother, the higher the parity, 
-and the higher the percentile measure.
-
-% [Parity progression probability]
-Second, 
-the likelihood of a next birth has fallen over time, and the declines are
-larger the higher the education, the higher the parity, and with the presence of at
-least one son. 
+in line with the observed fall in the total fertility rate, the likelihood of a next birth 
+has fallen over time.
+The declines in the likelihood of a next birth are larger the higher the education, 
+the higher the parity, and with the presence of at least one son. 
 Within a given spell and period, parity progressions are lower in urban than in rural areas, 
@@
 % [Sex ratios]
-Finally, 
-the sex ratios of next births has become more male dominated for women with no
-sons, while there are no clear trends for the other sex compositions.
+Second, 
+the spread of sex selection shows clearly in the sex ratios of next births, which has 
+become more male dominated for women with no sons.
 The increases in the predicted percent boys are larger the higher the education and the 
 higher the parity.
+There are no clear trends for the other sex compositions.
 Furthermore, for a given spell and period, sex ratios in the absence of a son are higher 
@@
 the parity.
-There is some evidence of unnaturally high percentage boys born even when women have one 
+There is some evidence of unnaturally high percentage boys for some women with one 
 son, although most are clearly lower than in the absence of a son and the failing fertility
-make more of those estimate noisy.
+make these estimate noisy.
+
+% [Birth intervals w/o sex selecition]
+
+To separate out the effects of the introduction of sex selection and the other changes in
+India, I first discuss how birth intervals have changed in situations where sex selection are 
+less likely to be used.
+This groups covers women with no education, no matter the sex composition of their children, 
+and women with any education who has one or two sons already. 
+[This is not a hard and fast separation ]
+
+% [median birth intervals]
+Most median birth intervals have increased by three to six months over the four 
+decades, but the majority of median birth intervals are still at 36 months or below, 
+with the shortest only 29 months.%
+\footnote{
+The NFHS reports show median closed birth intervals of approximately 31 months, which have 
+barely moved over time, underscoring the importance of accounting for censoring when examining 
+birth spacing.
+}
+These changes are substantially smaller than the 3.5 months increase per decade found
+in other countries with declining fertility \citep{Rutstein2011,Casterline2016}.
 
 % [25th percentile birth intervals]
-Despite the increases in birth intervals and the decline in fertility, a remarkably high 
-proportion of birth intervals are still very short.
+Despite the increases in median birth intervals and the decline in fertility, a remarkably 
+high proportion of birth intervals are still very short.
 For all but the most educated, more than 25 percent of women have their second and their
-third child within 24 months of their previous child.
+third child within 24 months of their previous child, which is substantially below
+the 24 between \emph{pregnancies} recommended by the WHO.
 Furthermore, even with the larger increases in birth intervals with higher parity, the 
@@
 less than eight years of education.
-
-% [median birth intervals]
-The median birth intervals have increased more than the 25th percentile birth intervals
-but are still also relatively short.
-Although most median birth intervals have increased by three to six months over the four 
-decades, the majority of median birth intervals are still at 36 months or below, 
-with the shortest only 29 months.
-For comparison, fast changing countries have median birth intervals that increase around 
-3.5 months per decade with declining fertility \citep{Rutstein2011,Casterline2016}.
-Furthermore, the NFHS reports show median closed birth intervals that have barely
-moved over time, staying at approximately 31 months, underscoring the importance of 
-accounting for censoring of birth spells when trying to understand how birth spacing 
-changes over time.
-
-An important exception to the relatively short median intervals come from the better 
-educated women, especially in the absence of sons.
-The longest median interval was 48 months for the third spell for urban women with twelve 
-or more years of education who had no boys, an increase of almost 15 months over
-four decades.
-Similary, urban women with eight to eleven years of education and no sons had median
-birth intervals of around 40 months, an increase of about 10 months.
-Finally, the best educated women now have a median second birth interval of around 42
-months whether their first child was a boy or a girl.
 
@@
 or three sons, with increases of fifteen to twenty months.
-The fourth spell is also where most of the divergence across sex compositions happen,
-but even for women with no or one son, the 75th percentile birth intervals have
-increased by a half to a full year.
-For women with eight to eleven years of education, the 75th percentile spacing length for 
-women with two girls in the third spell increased by more than 15 months, mainly as the 
-result of more widespread use of sex selection as the sex ratios above indicate.
-
-% [Exceptions to the results]
-The best-educated women are an especially interesting case that run somewhat counter
-to the results above.
-First, despite a rapidly declining probability of having a third child when they already 
-have a son, there is little change in the associated birth intervals and all are lower for 
-the third spell than for the second.
-Second, the massive increase in the sex ratio to almost 80 percent boys for women with two 
-girls is associated with a more than 20 month increase in the 75th percentile birth 
-interval.
-The third spell is also the case with the clearest reversal in the spacing pattern by sex 
-composition; the birth intervals with two girls are consistently longer than with one
-or two sons no matter the percentile used.
-
-What do these results tell us about the role of son preference and the extent to which 
-the introduction of sex selection changed birth spacing across sex compositions?
+
+These results are in line with prior research showing that falling fertility is 
+associated with increases in longer spacing, although it is still an 
+unresolved question why \citep{Casterline2016}.
+The parity progression probabilities have been falling over time across all 
+education levels, especially for women with at least one son, and have been
+failing less for the less educated women.
+
+However, despite the rapidly declining probability of a third birth for the best-educated
+women when they already have a son, the birth intervals changed little for any of the percentiles,
+and all are lower for the third spell than for the second.
+One possibility is that the most educated women have both better access to modern
+contraceptive and are better at using traditional contraceptive methods 
+\citep{Rosenzweig1989}.
+
+% [Interpretation]
+% How do these changes in birth intervals tie in with the changes in India over the four
+% decades?
+% [TK economic growth? -> higher return to education for males -> lower fertility and
+% higher investment in boys' education -- has anybody looked at this?]
+% First, the parity progression probabilities have been falling over time across all 
+% education levels, especially for women with at least one son.
+
+Women with the largest increases in birth intervals are also those least likely to work.
+For example, the increases in average third spell birth intervals for urban women with
+one boy and one girl over the four decades were 2.7, 3.4, 5.8, and 1.8 months from lowest 
+to highest education groups.%
+\footnote{
+For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0, respectively.
+See the online appendix tables for the average birth intervals.
+}
+This means that the group with the lowest labor force participation, women with eight to 
+eleven years of education, was also the group with the largest increases in average 
+spacing, likely driven by the substantial improvement in household income that came
+from economic growth.
+
+Son preference still show up clearly, even for the women the least likely to use sex 
+selection, such as rural women with no education. 
+For this group, the shortest spacing---across all spells---is when they have only girls. 
+Notably, the difference in birth intervals across sex compositions has grown over 
+time as spacing when sons are present increased.
+
+% [Birth intervals with sex selection]
 
 The clearest illustration of how the combination of son preference and the introduction of 
-sex selection impacted birth spacing comes from the third spell of the best-educated urban 
+sex selection affected birth spacing comes from the third spell of the best-educated urban 
 women.
@@
 percent boys and a 75th percentile birth interval of almost 70 months, about 13 months
-longer than if they had at least one son.
+longer than if they had at least one son, and an increase of more than 20 months over
+the four decades.
+
 Even more striking is the change for this group when sex selection was first introduced.
 The 75th percentile birth interval with two girls increased from 48 months to 
-64 months with two girls, while the other sex compositions showed a 
+64 months with two girls in a decade, while the other sex compositions showed a 
 slightly decrease from around 55 months to 54 months.
-Theses changes may even be an underestimate of the changes in birth spacing sine
+Theses changes may even be an underestimate of the changes in birth spacing since
 this particular group appear to have had access to sex selection even before it became
@@
 
-Even for the women the least likely to use sex selection, such as rural women with no 
-education, son preference shows up clearly. 
-For this group, the shortest spacing---across all spells---is when they have only girls. 
-Notably, the difference in birth intervals across sex compositions has grown over 
-time as spacing when sons are present increased.
-Despite the strong son preference in spacing and sex ratios, there is also some indication 
-that parents prefer a mix of boys and girls;
-women with two boys \emph{and} a girl consistently have the lowest parity progression 
-probability in the fourth spell across education levels.
-
-Did the predictions of a turn-around in the use of sex selection come true?
+Not surprisingly given these effects of sex selection, the third spell for the 
+best-educated women is also the case with the clearest reversal in the spacing pattern by 
+sex composition; the birth intervals with two girls are consistently longer than with one
+or two sons no matter the percentile used.
+[highlight others]
+
+% An important exception to the relatively short median intervals come from the better 
+% educated women, especially in the absence of sons.
+% The longest median interval was 48 months for the third spell for urban women with twelve 
+% or more years of education who had no boys, an increase of almost 15 months over
+% four decades.
+% Similary, urban women with eight to eleven years of education and no sons had median
+% birth intervals of around 40 months, an increase of about 10 months.
+% Finally, the best educated women now have a median second birth interval of around 42
+% months whether their first child was a boy or a girl.
+
+% Despite the strong son preference in spacing and sex ratios, there is also some indication 
+% that parents prefer a mix of boys and girls;
+% women with two boys \emph{and} a girl consistently have the lowest parity progression 
+% probability in the fourth spell across education levels.
+
+Did the predictions of declining use of sex selection come true?
 There is no clear evidence for or against a reversal in the use of sex selection, with 
-some showing increases in sex ratios between the last two periods, others little change, 
+some cases showing increases in sex ratios between the last two periods, others little change, 
 and some a decline.
@@
 
-% [Interpretation]
-How do these changes in birth intervals tie in with the changes in India over the four
-decades?
-% [TK economic growth? -> higher return to education for males -> lower fertility and
-% higher investment in boys' education -- has anybody looked at this?]
-First, the parity progression probabilities have been falling over time across all 
-education levels, especially for women with at least one son.
-Falling fertility is associated with increases in longer spacing, although it is still an 
-unresolved question why \citep{Casterline2016}.
-What is especially interesting is that the results for the most educated women show that 
-the rapidly declining probability of a third birth for women with one or two sons did not 
-lengthen the birth intervals at any of the percentiles.
-One possibility is that the most educated women have both better access to modern
-contraceptive and are better at using traditional contraceptive methods 
-\citep{Rosenzweig1989}.
-
-Second, there is evidence that in situations where sex selection does not play a role 
-in birth intervals, women with the smallest change in birth intervals are also those most 
-likely to work.
-For example, the increases in average third spell birth intervals for urban women with
-one boy and one girl over the four decades were 2.7, 3.4, 5.8, and 1.8 months from lowest 
-to highest education groups.%
-\footnote{
-For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0, respectively.
-See the online appendix tables for the average birth intervals.
-}
-This means that the group with the lowest labor force participation, women with eight to 
-eleven years of education, was also the group with the largest increases in average 
-spacing, likely driven by the substantial improvement in household income that came
-from economic growth.
-
 Finally, although birth spacing has increased over time with improving economic 
@@
 women with two girls, which is the group with the most biased sex ratio.
+
+First, 
+over the four decades, birth intervals have lengthen, whether measured by the
+25th, 50th, or 75th percentile.
+These increases are larger the higher the education of the mother, the higher the parity, 
+and the higher the percentile measure.
 

### 2020-08-03 paper/sex_selection_spacing-ver4.tex
Edit Abstract and Introduction

@@
 
-\date{July 2020}
+\date{August 2020}
 
@@
 Using four rounds of India's National Family and Health Surveys and a
-competing-risk hazard model, I show that Hindu women's average birth intervals
-increased over the last four decades for all education groups. The most
-significant increases are among the women most likely to use sex
-selection. Despite the rise in average intervals, the likelihood of very
-short spacing did not change substantially. Hence, the increases come
-predominantly from the longer birth intervals getting even longer. As a
-result of the longer spacing, fertility rates significantly
-overestimated how fast cohort fertility fell. Although cohort fertility
+competing-risk hazard model, I show that Hindu women's birth intervals
+increased over the last four decades, more so the higher the parity and
+the more educated the woman. 
+Women most likely to use sex selection---well-educated with no sons---had the most 
+substantial lengthening of birth intervals and the most biased sex ratios. 
+However, the likelihood of very short spacing did not change substantially. 
+As a result of the longer spacing, fertility rates significantly
+overestimated how fast cohort fertility fell. 
+Although cohort fertility
 and the fertility rate have started to converge, the cohort fertility is
-still substantially higher than the fertility rate. Furthermore, cohort
-fertility is still at or above replacement level for all but the
-best-educated urban women. Finally, infant mortality risk has declined
-substantially over time for all groups, but fastest for the lower
-education groups, who are now close to the level of women with the most
-education. Short birth spacing is still associated with higher
-mortality, although the difference is small for the best-educated women.
-There is no evidence that the increasing use of sex selection is
-associated with higher infant mortality risk.
-
+still substantially higher than the fertility rate. 
+Furthermore, cohort fertility is still at or above replacement level for all but the
+best-educated urban women. 
+Finally, infant mortality risk has declined substantially over time for all groups, but 
+fastest for the lower education groups, who are now close to the level of women with the most
+education. 
+Short birth spacing is still associated with higher mortality, although substantially less 
+so for the best-educated women. 
+There is no evidence that the increasing use of sex selection is associated with
+higher infant mortality risk.
 \noindent JEL: J1, O12, I1
@@
 force participation all likely impact birth spacing. 
-The combined changes in birth spacing may, therefore, outpace what we have observed in 
+Hence, the combined changes in birth spacing may outpace what we have observed in 
 other countries.
@@
 impact mortality. 
-To understand these effects, I address two additional questions.
+I, therefore, address two additional questions.
 
@@
 
-The primary outcomes I examine are average birth intervals, the sex ratio of births, 
-and the likelihood of giving birth. 
-Because sex selection might also affect the distribution of birth intervals, I furthermore
-examine the 25th and 75th percentiles of birth intervals. 
+The primary outcomes I examine are 25th, 50th, and 75th percentile birth intervals, the 
+sex ratio at birth, and the likelihood of giving birth. 
 I estimate the model across four periods to capture the changing access and 
@@
 % Main results
-There are four main results.
-
-First, average birth intervals lengthen over the four decades, more so the higher the 
-parity and the more educated the woman.
+There are three main results.
+
+First, birth intervals lengthen over the four decades, more so the higher the parity, the 
+more educated the woman, and the higher the percentile. 
 Women most likely to use sex selection---well-educated with no sons---had the most 
@@
 women with no sons having \emph{longer} birth intervals than those with sons. 
-Those least likely to use sex selection---less-educated in rural areas---still follow 
-the traditional pattern of short spacing when they have girls and little evidence of sex 
+Those least likely to use sex selection---less-educated in rural areas---still follow the 
+traditional pattern of short spacing when they have girls and only some evidence of sex 
 selection. 
-
-Second, the likelihood of a very short birth interval changed little. 
-Hence, the increased average spacing comes mainly from longer birth intervals getting even 
-longer, primarily because of sex selection. 
-The exception is that those better-educated women with a very high predicted use of sex 
-selection conceive later and are less likely to have a very short birth interval, precisely 
-because their next child is almost certainly a boy.
-
-Third, the fertility rate substantially overestimated how fast cohort fertility fell in the 
+The likelihood of a very short birth interval changed little.
+
+Second, the fertility rate substantially overestimated how fast cohort fertility fell in the 
 1990s and early 2000s as spacing began to increase. 

### 2020-08-03 paper/sex_selection_spacing-ver4.tex
Edit Background and Conceptual Framework section

@@
 and ten to eleven years of schooling completed.
-There is a trade-off between having groups large enough for the analyses below and having 
-groups detailed enough to capture differences in behavior across education levels, such as 
-the U-shaped relationship between education and labor force participation.
+This grouping allows me to capture the differences across education levels discussed below, 
+while also having groups large enough for the empirical method.
 
@@
 group and the other half in the twelve plus group.
-In urban areas, the proportions with no education or one to seven years have declined 
-to just below ten percent each.
+In urban areas, the proportions with no education or one to seven years have each declined 
+to just below ten percent.
 Most of the increase in urban female education came from the twelve plus group, which 
@@
 
-The standard economic argument for spacing becoming shorter with increasing female education 
+The standard economic argument for shorter spacing with increasing female education 
 is that parents incur time costs when they have children \citep{Hotz1997,schultz97}.
@@
 Better-educated and urban women also tend to live in households with higher income, which 
-better enables them to access prenatal sex determination and lowers the relative costs of 
-using sex selection and have long birth intervals.
+lowers the relative costs of using sex selection and have long birth intervals.
 
@@
 \citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-The exception is one crucial aspect of child quality---health and mortality---where
-longer spacing does lead to better outcomes, although this relationship weakens with 
-maternal education \citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
+The exception is health and mortality, where longer spacing does lead to better outcomes, 
+although this relationship weakens with maternal education 
+\citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
 
@@
 market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
-The low and declining female labor force participation is an indication that this
-process still operates.
+The low and declining female labor force participation suggests that this process still operates.
 
@@
 Even with the substantial increase in the number of better-educated women, 
-"Sanskritization" implies that the changing composition does not substantially change 
-this group's use of sex selection.
+"Sanskritization" implies that the changing composition will not substantially change 
+the use of sex selection.
 

### 2020-08-03 paper/sex_selection_spacing-ver4.tex
Fix percentile examples and edit Empirical Strategy section

@@
 higher infant mortality risk.
+
 \noindent JEL: J1, O12, I1
-\noindent Keywords: India, prenatal sex determination, censoring, competing risk, non-proportional hazard
+
+\noindent Keywords: India, prenatal sex determination, censoring, competing risk, 
+non-proportional hazard
 \end{abstract}
@@
 fixed proportion of the hazard for any other individual. 
-That the effects are not constant violates that assumption, and the results from a 
-proportional hazard model would, therefore, be biased. 
+Non-constant effects violate that assumption, and the results from a proportional hazard 
+model would, therefore, be biased. 
 The proportionality assumption is especially problematic for higher-order birth 
@@
 as is standard in the literature.
-There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$.
+The two exit states are the birth of a boy, $j=1$, or a girl, $j=2$.
 
@@
 Logit model. 
-In the reorganized data, the outcome variable is 0 if the woman does not have a child 
-in a given interval (the base outcome), 1 if she gives birth to a son in that interval, 
-and 2 if she gives birth to a daughter in that interval.
+% In the reorganized data, the outcome variable is 0 if the woman does not have a child 
+% in a given interval (the base outcome), 1 if she gives birth to a son in that interval, 
+% and 2 if she gives birth to a daughter in that interval.
 
@@
 For birth intervals, I estimate a set of percentile birth intervals. 
-To find a given percentile birth interval, I first calculate for each woman when there is 
-a given percent chance that she will have given birth, conditional on the probability of 
-giving birth in the spell.
-I then add nine months to account for the start of the spell. 
-For example, with an 80 percent chance of giving birth by the end of the spell, the median birth 
-interval is the predicted number of months before a woman passes the 40 percent mark on her 
-survival curve. 
+I first calculate for each woman when there is a given percent chance that she will have 
+given birth, conditional on the probability of giving birth in the spell. 
+For example, with an 80 percent parity progression probability, the median birth interval 
+is the predicted number of months before a woman passes the 60 percent mark on her survival 
+curve. 
+I then and add nine months to account for the start of the spell. 
 The reported statistic is the average of a given percentile interval across all women in 
@@
 
+% The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
+% parity progression probabilities as weights.
+% For an individual woman, the estimated percent of births that are boys at $t$, $\hat{Y_t}$, is:  
+% \begin{equation}
+% \hat{Y}_t 
+% = 
+% \frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
+% { P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
+% \times 100,
+% \label{eq:probability_son}
+% \end{equation}
+% where $b$ and $g$ are the predicted probabilities of having a boy and a girl, respectively,
+% conditional on the explanatory variables and not having had a child before $t$.
+% Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
+% $t$ gives the predicted percent of boys over the entire spell for an individual.%
+% \footnote{
+% Imagine $T=2$. 
+% If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
+% then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
+% }
+
 The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
 parity progression probabilities as weights.
-For an individual woman, the estimated percent of births that are boys at $t$, $\hat{Y_t}$, is:  
-\begin{equation}
-\hat{Y}_t 
-= 
-\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-\times 100,
-\label{eq:probability_son}
-\end{equation}
-where $b$ and $g$ are the predicted probabilities of having a boy and a girl, respectively,
-conditional on the explanatory variables and not having had a child before $t$.
+To find the individual sex ratio, I estimate the percent of births that are boys at $t$, 
+conditional on not having had a child before $t$.
 Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
@@
 \end{figure}
+
+\clearpage
+\newpage
+
+\section{Empirical Model Details}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+[More formal version of empirical strategy section]
+
+The model is a discrete time, non-proportional, competing risk hazard model with two exit 
+states: either a boy or a girl is born.
+The unit of analysis is a spell, the period from nine months after one birth to the next.
+For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
+the spell continues until time $t_i$, when either a birth occurs or the spell 
+is censored.%
+\footnote{
+The time of censoring is assumed independent of the hazard rate,
+as is standard in the literature.
+}
+There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
+$J_i$ is a random variable indicating which event took place.
+The discrete time hazard rate $h_{ijt}$ is 
+\begin{equation}
+ h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
+ {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
+ \label{eq:hazard}
+\end{equation}
+where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
+individual, household, and community characteristics,
+and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
+by dummies and the associated coefficients,
+\begin{equation}
+D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
+\end{equation}
+with $D_m = 1$ if $t=m$ and zero otherwise.
+This approach to modeling the baseline hazard is flexible and does not place 
+overly strong restrictions on the baseline hazard.
+
+The explanatory variables in $\mathbf{Z}$, and the interactions between them, 
+constitute the non-proportional part of the model, which means that they are
+interacted with the baseline hazard:
+\begin{equation}
+ \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
+\end{equation}
+where $D_j(t)$ is the piece-wise linear baseline hazard, $\mathbf{Z}_1$ captures sex 
+composition of previous children, if any, and $Z_2$ captures area of residence.
+The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
+but to further minimize any potential bias from assuming proportionality, estimations 
+are done separately for different levels of mothers' education and different 
+periods.
+
+Equation (\ref{eq:hazard}) is equivalent to the logistic hazard model and has the same 
+likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
+Hence, transforming the data, so each observation is an interval---here equal
+to three months---the model can be estimated using a standard multinomial logit model.
+
+The distribution of spacing is captured by the survival curve, which shows the probability 
+of not having had a birth yet by spell duration, for a given set of explanatory variables.
+The survival curve at time $t$ is 
+\begin{equation}
+\label{eq:survival}
+S_{t} 
+= 
+\prod_{d=1}^t
+\left(
+\frac{ 1 }
+{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
+\right).
+\end{equation}
+
+% Because the probability of ever having a next birth varies across groups, a direct 
+% comparison of standard survival curves tells us little about how the spread of sex 
+% selection affects birth spacing across groups.
+% I, therefore, condition on the predicted likelihood of parity progression when examining 
+% birth spacing measures, such as the average duration to a birth.
+% The reliability of this approach depends on whether the spell length covered is 
+% sufficiently long that few women are likely to give birth after the spell cut-off.
+% I discuss the choice of spell length below.%
+% \footnote{
+% It is important to note that the approach is not the same as merely calculating 
+% the birth spacing measures for women who already have a given 
+% parity child in the survey because that number does not take into account
+% the censoring of spells that will eventually lead to a birth.
+% }
+% In addition, I present graphs of survival curves conditional on parity progression,
+% which therefore begin at 100\% and end at 0\%.
+
+Interpretation of the model coefficients is challenging \citep{thomas96}.
+It is, however, possible to calculate the predicted probabilities of 
+having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
+a set of explanatory variables and not having had a child before that period, as
+\begin{align}
+P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
+& =  
+\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
+{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
+\label{eq:probability_boy} \\
+P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
+& =  
+\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
+{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
+\label{eq:probability_girl}
+\end{align}
+It is then straightforward to calculate the estimated percentage of children born that 
+are boys, $\hat{Y}$, at each $t$:  
+\begin{equation}
+\hat{Y}_t 
+= 
+\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
+{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
+\times 100.
+\label{eq:probability_son}
+\end{equation}
+Combining the percentage boys and the likelihood of exiting the spell 
+across all $t$ gives the predicted percent boys born over the entire spell.%
+\footnote{
+Imagine $T=2$. 
+If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
+then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
+}
 

### 2020-08-03 paper/sex_selection_spacing-ver4.tex
Edit Data section

@@
 
-I focus on the three birth intervals starting from the first birth and ending with the 
+I focus on the three spells starting from the first birth and ending with the 
 fourth birth.
@@
 make changes over time appear too small.
-I, therefore, provide a detailed analysis of systematic recall error in the Online Appendix.
-Recall error depends heavily on how long ago a woman was married, and I, consequently, 
-drop women married 22 years or more.%
+In the Online Appendix, I provide a detailed analysis of systematic recall error, which 
+shows that recall error depends heavily on how long ago a woman was married. 
+I, consequently, drop women married 22 years or more.%
 \footnote{
@@
 
-To ensure that there are enough births for the method to work, I censor each spell at 96 
-months (eight years) after a woman can first give birth, which is equivalent to 105 months 
+To ensure that there are enough births for the method to work, I censor spells at 96 
+months (eight years) after a woman can first give birth, equivalent to 105 months 
 after the birth of the prior child.
@@
 
-I divide the explanatory variables into two groups.
-The first group consists of characteristics that the prior literature finds affect 
-the spacing choice and the use of sex selection:
-mother's education, sex composition of previous children, and area of residence.%
+I divide the explanatory variables into two groups, non-proportional and proportional. 
+The first group consists of characteristics that the prior literature finds affect the 
+spacing choice and the use of sex selection: mother’s education, sex composition of 
+previous children, and area of residence. 
+To minimize any potential bias from including proportional variables, I estimate a 
+separate model for each birth interval, education group, and period combination, rather 
+than including education as a variable. 
+I capture sex composition with dummy variables for the possible combinations, ignoring 
+the ordering of births.%
 \footnote{
@@
 }
+Area of residence is a dummy variable for living in an urban area.
+
 The second group of variables consists of those expected to have an approximately 
@@
 Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present descriptive statistics.
-
-I estimate a separate model for each birth interval, education group, and period 
-combination to minimize any potential bias from including proportional variables.
-I capture sex composition with dummy variables for the
-possible combinations, ignoring the ordering of births.
-Area of residence is a dummy variable for living in an urban area.
 

### 2020-08-05 paper/sex_selection_spacing-ver4.tex
Edit birth interval section

@@
 months, the sex ratio, and the probability of having a birth for each spell
-for the four education levels by area of residence.%
+by education levels and area of residence.%
 \footnote{
@@
 education, and the fourth spell for women with twelve or more years of education are
-presented in the online appendix because they are based on relatively few observations.
-}
+in the online appendix because of relatively small samples.
+}
+The sex ratio graphs also show the natural sex ratio, approximately 51.2 percent 
+\citep{ben-porath76b,jacobsen99,Portner2015b}.
 The underlying values with bootstrapped standard errors are available in the online 
 appendix.
-The sex ratio graphs also show the natural sex ratio, approximately 51.2 percent 
-\citep{ben-porath76b,jacobsen99,Portner2015b}.
-
-% [not sure where this goes or simply delete]
-%Sex selection increases all three percentile birth intervals, but the effects of abortions 
-%are easiest to observe in the 75th percentile birth interval, 
-%and it is also the changes in the longest birth intervals that will likely the largest 
-%impact on fertility measures.
-%The 25th percentile captures changes in the short spacing, which is the most likely to 
-%have an adverse impact on health.
 
@@
 First, 
-in line with the observed fall in the total fertility rate, the likelihood of a next birth 
-has fallen over time.
-The declines in the likelihood of a next birth are larger the higher the education, 
-the higher the parity, and with the presence of at least one son. 
+in line with the falling total fertility rate, the likelihood of a next birth 
+has decreased over time.
+The likelihood of a next birth fell faster, the higher the education, the higher the 
+parity, and with at least one son.
 Within a given spell and period, parity progressions are lower in urban than in rural areas, 
@@
 the spread of sex selection shows clearly in the sex ratios of next births, which has 
-become more male dominated for women with no sons.
-The increases in the predicted percent boys are larger the higher the education and the 
+become more male-dominated for women with no sons.
+The percent of births that were boys increased faster, the higher the education and the 
 higher the parity.
 There are no clear trends for the other sex compositions.
-Furthermore, for a given spell and period, sex ratios in the absence of a son are higher 
-in urban than in rural areas, the higher the education of the mother, and the higher
-the parity.
-There is some evidence of unnaturally high percentage boys for some women with one 
-son, although most are clearly lower than in the absence of a son and the failing fertility
-make these estimate noisy.
-
-% [Birth intervals w/o sex selecition]
-
-To separate out the effects of the introduction of sex selection and the other changes in
-India, I first discuss how birth intervals have changed in situations where sex selection are 
-less likely to be used.
-This groups covers women with no education, no matter the sex composition of their children, 
-and women with any education who has one or two sons already. 
-[This is not a hard and fast separation ]
+Within a given spell and period combination and in the absence of a son, sex ratios are 
+higher, the more educated the mother, and the higher the parity. 
+Sex ratios are also higher in urban than in rural areas.
+Some women with one son also show an unnaturally high percentage of boys, although the 
+failing fertility makes these estimates noisy.
+
+% [Birth intervals w/o sex selection]
+\subsection{When Sex Selection is Less Used}
+
+To separate the effects of the introduction of sex selection and the other changes in
+India, I first discuss how birth intervals have changed in situations where sex selection 
+is less used.
+The group broadly covers women with no education, no matter the sex composition of their 
+children, and women with any education who has one or two sons already. 
+Despite the lower level of sex selection, son preference is still evident with the 
+shortest spacing when they have only girls. 
+Notably, for those least likely to use sex selection, rural women with no education, the 
+difference in birth intervals across sex compositions has grown over time as spacing when 
+sons are present increased.
+
+% [25th percentile birth intervals]
+A remarkably high proportion of birth intervals are still very short.
+For all but the most educated, more than 25 percent have their second and third child 
+within 24 months of the previous birth, substantially below the 24 months between 
+\emph{pregnancies} the WHO recommends.
+Furthermore, despite higher parities' more substantial increases in birth intervals, even 
+the 25th percentile birth intervals for the fourth spell are around 24 months for women 
+with less than eight years of education.
 
 % [median birth intervals]
-Most median birth intervals have increased by three to six months over the four 
-decades, but the majority of median birth intervals are still at 36 months or below, 
-with the shortest only 29 months.%
+Median birth intervals have also increased relatively little---only three to six months 
+over the four decades---compared to around 3.5 months \emph{per decade} in other countries with 
+declining fertility \citep{Rutstein2011,Casterline2016}.%
 \footnote{
@@
 }
-These changes are substantially smaller than the 3.5 months increase per decade found
-in other countries with declining fertility \citep{Rutstein2011,Casterline2016}.
-
-% [25th percentile birth intervals]
-Despite the increases in median birth intervals and the decline in fertility, a remarkably 
-high proportion of birth intervals are still very short.
-For all but the most educated, more than 25 percent of women have their second and their
-third child within 24 months of their previous child, which is substantially below
-the 24 between \emph{pregnancies} recommended by the WHO.
-Furthermore, even with the larger increases in birth intervals with higher parity, the 
-25th percentile birth intervals for the fourth spell is around 24 months for women with 
-less than eight years of education.
+The result is that most of the median birth intervals are still at 36 months or below, 
+with the shortest only 29 months.
+
+Birth intervals appeared to lengthen the most for women the least likely to work.
+For example, from lowest to higher education, the average third spell birth intervals for 
+urban women with one boy and one girl increased by 2.7, 3.4, 5.8, and 1.8 months over the 
+four decades.%
+\footnote{
+For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0.
+See the online appendix tables for the average birth intervals.
+}
+Hence, women with the lowest labor force participation, those with eight to eleven years 
+of education, also saw the largest increases in average spacing, possibly driven by the 
+substantial improvement in household income for this group from economic growth.
 
 % [75th percentile birth intervals]
-The most substantial differences across women come from the longer birth intervals, 
-captured by the 75th percentile birth intervals.
-For the two lowest education groups the increases in the 75th percentile birth 
-intervals are relatively small for the second spell and slightly more substantial for the 
-third spell at around five months.
-However, the fourth spell show significant increases, especially for women with two
-or three sons, with increases of fifteen to twenty months.
-
-These results are in line with prior research showing that falling fertility is 
-associated with increases in longer spacing, although it is still an 
-unresolved question why \citep{Casterline2016}.
-The parity progression probabilities have been falling over time across all 
-education levels, especially for women with at least one son, and have been
-failing less for the less educated women.
-
-However, despite the rapidly declining probability of a third birth for the best-educated
-women when they already have a son, the birth intervals changed little for any of the percentiles,
-and all are lower for the third spell than for the second.
-One possibility is that the most educated women have both better access to modern
-contraceptive and are better at using traditional contraceptive methods 
-\citep{Rosenzweig1989}.
+The most substantial changes occurred in the 75th percentile birth intervals, where the 
+more the parity progression probabilities declined, the more the birth interval lengthen. 
+For example, the probability of a fourth birth for urban women with eight to eleven years 
+of education and two sons and a girl has declined by almost forty percentage points as the 
+75th percentile birth interval increased by 22 months.
+Compare this with no education, rural women with a boy as their first child, where the 
+probability of a third birth declined by less than six percentage points while the birth 
+interval increased by only slightly over two months.
+
+%0.637 0.241
+
+These results are in line with prior research showing that falling fertility is associated 
+with increases in longer spacing, although why is still an unresolved question 
+\citep{Casterline2016}.
+The exception to this trend suggests one possible answer.
+For the most educated women who already have a son, the probability of a third birth 
+declined rapidly, but the birth intervals changed little.
+These women have both better access to modern contraceptives and are better at using 
+traditional contraceptive methods \citep{Rosenzweig1989}.
 
@@
 
-Women with the largest increases in birth intervals are also those least likely to work.
-For example, the increases in average third spell birth intervals for urban women with
-one boy and one girl over the four decades were 2.7, 3.4, 5.8, and 1.8 months from lowest 
-to highest education groups.%
-\footnote{
-For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0, respectively.
-See the online appendix tables for the average birth intervals.
-}
-This means that the group with the lowest labor force participation, women with eight to 
-eleven years of education, was also the group with the largest increases in average 
-spacing, likely driven by the substantial improvement in household income that came
-from economic growth.
-
-Son preference still show up clearly, even for the women the least likely to use sex 
-selection, such as rural women with no education. 
-For this group, the shortest spacing---across all spells---is when they have only girls. 
-Notably, the difference in birth intervals across sex compositions has grown over 
-time as spacing when sons are present increased.
-
 % [Birth intervals with sex selection]
-
-The clearest illustration of how the combination of son preference and the introduction of 
+\subsection{Sex Selection and Birth Spacing}
+
+A clear illustration of how the combination of son preference and the introduction of 
 sex selection affected birth spacing comes from the third spell of the best-educated urban 
 women.
-Women with two girls have a predicted sex ratio for their third child approaching 80 
-percent boys and a 75th percentile birth interval of almost 70 months, about 13 months
-longer than if they had at least one son, and an increase of more than 20 months over
-the four decades.
-
-Even more striking is the change for this group when sex selection was first introduced.
+With two girls, almost 80 percent of the third births are boys, and the 75th percentile 
+birth interval is close to 70 months. 
+This interval is about 13 months longer than if they had at least one son and represents 
+an increase of almost 21 months over the four decades.
+
+Even more striking is that most of the change took place right at the introduction of sex 
+selection.
 The 75th percentile birth interval with two girls increased from 48 months to 
-64 months with two girls in a decade, while the other sex compositions showed a 
-slightly decrease from around 55 months to 54 months.
-Theses changes may even be an underestimate of the changes in birth spacing since
-this particular group appear to have had access to sex selection even before it became
-widespread as shown by the unequal sex ratio for the 1972--1984 period for women with
-two girls.
-
-Not surprisingly given these effects of sex selection, the third spell for the 
-best-educated women is also the case with the clearest reversal in the spacing pattern by 
-sex composition; the birth intervals with two girls are consistently longer than with one
-or two sons no matter the percentile used.
-[highlight others]
+64 months in a decade, while the other sex compositions showed a slight decrease from 
+around 55 months to 54 months.
+These changes in birth spacing may even be an underestimate since this particular group 
+appears to have had access to sex selection even before it became widespread, as shown by 
+the unequal sex ratio for the 1972--1984 period for women with two girls.
+
+The 75th percentile changes are the most dramatic, but sex selection also impacts the 
+25th and median birth intervals. 
+For the best-educated urban women with two girls, the 25th percentile birth interval 
+increased by six months, or 23 percent, while the median percentile birth interval 
+increased by 15 months (43 percent).
+
+Not surprisingly, given these effects of sex selection, the third spell for the 
+best-educated women shows the clearest reversal in the spacing pattern; 
+the birth intervals with two girls are consistently longer than the intervals with one or 
+two boys, no matter the percentile used.
+A similar reversal, although more muted, occurred for the third spell for urban women 
+with one to seven years of education and both urban and rural women with eight to
+eleven years of education.
 
@@
 There is no clear evidence for or against a reversal in the use of sex selection, with 
-some cases showing increases in sex ratios between the last two periods, others little change, 
-and some a decline.
-The best-educated women is again a good illustration.
-The percent boys born to women with two girls continued to increase over the last two
-periods, but the likelihood of a third birth declined and when the first child was a girl, 
-the sex ratio for the second birth dropped slightly as did the probability of a second birth. 
-There is, however, also cases where there is clearly no abatement in the increasing use of 
-sex selection. 
-The sex ratios in the absence of girls continued to increase for rural women with
-one to seven years of education and the likelihood of an additional birth remained high.
-
-Finally, although birth spacing has increased over time with improving economic 
-conditions and falling fertility, most of the increases in birth spacing come from the
-increased use of sex selection. 
-The most substantial increase over the four decades is a full year for the best-educated 
-women with two girls, which is the group with the most biased sex ratio.
-
-First, 
-over the four decades, birth intervals have lengthen, whether measured by the
-25th, 50th, or 75th percentile.
-These increases are larger the higher the education of the mother, the higher the parity, 
-and the higher the percentile measure.
+some cases showing increases in sex ratios between the last two periods, others little 
+change, and some a decline. 
+The best-educated women are again a good illustration. 
+The sex ratio for women with two girls continued to increase over the last two periods, 
+but the likelihood of a third birth declined. 
+Furthermore, if the first child was a girl, the sex ratio for the second birth dropped 
+slightly, as did the probability of having a second birth. 
+However, there are also cases where there is no abatement in the increasing use of sex 
+selection. 
+For example, for rural women with one to seven years of education, the sex ratios in the 
+absence of girls continued to increase while the likelihood of an additional birth remained 
+high.
+
+In summary, over the four decades, birth intervals have lengthened with improving economic 
+conditions and falling fertility. 
+These increases are larger with higher parity and higher percentile measure. 
+Furthermore, when sex selection is less used, it appears that the women least likely to 
+work are also those with the most substantial increases.
+
+Sex selection, however, is behind the most substantial increases in birth spacing. 
+The best-educated women with two girls had the most biased sex ratio and the most 
+significant increase in birth intervals. 
+Over the four decades, the median birth interval for this group increased by almost 15, 
+and the 75th percentile birth interval increased by a staggering 21 months, most of that 
+within a decade.
 

### 2020-08-06 paper/sex_selection_spacing-ver4.tex
Edited fertility section

@@
 % http://countwordsfree.com/#
-% \usepackage[nolists]{endfloat}
+\usepackage[nolists]{endfloat}
 
@@
 % For word counting remove comment on the line below
-% \raggedright
+\raggedright
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
-\caption{combined graphs - low urban}
-\label{fig:spacing_low_urban}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
+% \caption{combined graphs - low urban}
+% \label{fig:spacing_low_urban}
+% \end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
-\caption{combined graphs - highest rural}
-\label{fig:spacing_highest_rural}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
+% \caption{combined graphs - highest rural}
+% \label{fig:spacing_highest_rural}
+% \end{figure}
 
@@
 To this end, I compare fertility based on a variation of the total fertility rate with 
-predicted cohort fertility from the hazard model results.
+predicted cohort fertility from the hazard model.
+Table \ref{tab:fertility} shows the two fertility measures by urban/rural and education.
 
@@
 
-Table \ref{tab:fertility} shows the two fertility measures by urban/rural and education.
-Because the hazard model predictions only use births up to parity four, I calculate
-fertility rates using only the same births.
-Hence, my fertility rates are not directly comparable to those in the NFHS reports,
-but otherwise, I follow the procedure used in the NFHS reports \citep{Croft2018}.
-I calculate age-specific fertility rates for five-year age groups using the number of 
-births in months 1 to 36 before the survey month and the number of women in each age 
-group.
+The fertility rate follows the same procedure as in the Demographic and Health Survey 
+reports: I use the births from 36 to 1 month before the survey month to calculate 
+age-specific fertility rates for five-year age groups and then sum the age-specific 
+fertility rates multiplied by five  \citep{Croft2018}.
+However, because the hazard model predictions only use births up to parity four, I use the 
+same set of births for the fertility rate and label it the ``four-parity'' fertility rate. 
+Hence, the presented fertility rates are not directly comparable to those in the NFHS reports.
 
@@
 
-Because NFHS-1 was after the introduction of sex selection, it is not possible 
-to calculate a fertility rate in precisely the same manner for a period 
-before sex selection was widely available.
-Instead, I calculate the fertility rates for women who were between 15 and 39 years of
-age five years before the survey month, again using the number of births three years 
-before that, shown as ``1987--88''.
+Because NFHS-1 was after the introduction of sex selection, I cannot calculate a fertility 
+rate in precisely the same manner for a period before sex selection was widely available.
+Instead, I calculate the fertility rates for women between 15 and 39 years of age five years 
+before the survey month, again using the number of births three years before.
+This rate is shown as ``1987--88'' in the table.
 Given the relatively low number of births to women 40 to 45 years of age, this approach 
-provides the best estimate of the fertility rate at the time when sex selection still was 
-not widespread.
-
-To predict cohort fertility based on the hazard models above, I estimate the probability 
-of progression to the next parity for each spell.
-Since the parity progression depends on the sex composition for prior children for parity 
-two and above, I estimate the progression probability for each possible sex composition
-and weigh those probabilities with the likelihood that they will occur based on the
-prior spells.
+provides the best estimate of the fertility rate when sex selection still was not 
+widespread.
+
+To predict cohort fertility based on the hazard models, I estimate the parity progression 
+probability for each spell. 
+Since parity progression depends on the sex composition of prior children, I estimate the 
+probability for each sex composition and weigh the probabilities with the likelihood of 
+the sex compositions.
+The survey rounds do not coincide directly with the periods used for the hazard model.
+Therefore, I compare the model results for 1972--1984, 1985--1994, 1995--2004,
+and 2005--2016 with rounds 1 through 4 of the NFHS, respectively.
+
+I include the spell from marriage to first birth, despite the problems capturing the exact 
+timing of marriages since the estimated progression probabilities should not be affected 
+by this problem. 
+I begin with the age of marriage for each woman and predict the likelihood of progressing 
+to each parity, assuming three years increases in age between births. 
+Shorter assumed increases in age lead to slightly higher predicted fertility.
 
@@
 immediately after giving birth. 
-To compensate, I estimate the likelihood of sterilization using a Logit model, predict 
-the probability of not getting sterilized, and then use that to scale down the parity
-progression probability when predicting cohort fertility.
-
-I include the spell from marriage to first birth, despite the problems
-capturing the exact timing of marriages since the estimated progression
-probabilities should not be affected by this problem.
-To ensure that the predictions depend solely on sample composition and the estimate, I
-use the age at marriage for each woman and predict the likelihood of progressing to
-each parity, assuming three years increases in age between each parity.
-Shorter assumed increases in age between births leads to slightly higher predicted 
-fertility.
-
-The survey rounds do not coincide directly with the periods used for the hazard model.
-I, therefore, use the model results for 1972--1984, 1985--1994, 1995--2004,
-and 2005--2016 for rounds 1 through 4 of the NFHS, respectively.
-
-% Because of the small number of women who had the highest level of education in the
-% 1972--1984 period, I do not predict fertility for this case.
+To compensate, I estimate the probability of sterilization using a Logit model and use 
+that to scale down the parity progression probability when predicting cohort fertility.
 
@@
 fertility rate in almost all cases. 
-Only for women with no education in the first period is there almost no difference 
-between the two fertility measures; a situation where fertility is high, spacing
-very short and likely unchanged for an extended period before.
+Only women with no education in the first period show little difference between the two 
+fertility measures, a situation where fertility is high, spacing very short, and likely 
+unchanged for an extended period.
 
 Consistent with a more substantial bias in the fertility rate when the age of marriage 
-and the length of birth intervals are increasing, the absolute bias is least in the first and the last 
-period and highest in the middle two periods.
+and the length of birth intervals increase, the absolute bias is least in the first 
+and the last period and highest in the middle two periods.
 Hence, the fertility rate declined too fast from the mid-1980s to the century's end.
-Only recently, as the rate of increase for the birth intervals have
-slowed, are the predicted cohort fertility and the fertility beginning
-to converge again.
-Even with the convergence, however, the predicted cohort fertility for 2005--16 is 
-above the 1992--93 fertility rate for every group except urban women with no education.
-Furthermore, for the last period, the predicted cohort fertility is still between ten
-and 20 percent higher than the fertility rate.
-
-Another indication of the fertility rate bias is that it is increasing over time for some 
-groups.
-For example, urban women with eight to eleven years of education showed 1.84, 1.81, and
-1.87 over the last three surveys.
-These increases likely arise from the stabilization of the age of first birth and the 
+Only recently, as the rate of increase for the birth intervals has slowed, do the two 
+fertility measures begin to converge again.
+Even with the convergence, the predicted 2005--16 cohort fertility is still above the 
+1992--93 fertility rate for every group, except urban women with no education. 
+Furthermore, for the last period, the predicted cohort fertility remains at least ten to 
+twenty percent higher than the fertility rate.
+
+Another indication of how tempo effects bias the fertility rate bias is that the
+fertility rate \emph{increases} for some groups.
+For example, for urban women with eight to eleven years of education, the fertility
+rates were 1.84, 1.81, and 1.87 over the last three surveys.
+This pattern likely arises from the stabilization of the age of first birth and the 
 spacing between births.
 
-%
-% \footnote{
-% Increases in TFR over time, even in the face of declining cohort fertility, are not 
-% unusual, as shown by Columbia in the early 1990s \citep{Bongaarts1999}.
-% }
-
-Despite the declines in the predicted cohort fertility, it is still mostly above the 
-generally accepted replacement level of 2.1.
+Finally, even with the declines in the predicted cohort fertility, it is still mostly 
+above replacement.
 Only for urban women with twelve or more years of education is the predicted cohort
-fertility clearly below 2.1, and even then, it is still more than 0.3 children higher than 
+fertility clearly below 2.1.
+Even then, cohort fertility is still more than 0.3 children higher than 
 the fertility rate estimate of 1.5.
-Finally, the predicted cohort fertility numbers are likely too low,
-especially for the lower education groups, since it relies only on the
-first four births and because the model ignores births that took place past the end
-of the imposed 105 month birth interval censoring.
+Furthermore, the predicted cohort fertility numbers are likely too low since I use only 
+the first four births and births before the imposed 105-month birth interval censoring.
 

### 2020-08-06 paper/sex_selection_spacing-ver4.tex
Editing mortality section

@@
 
-The dependent variable is whether the child died within the first twelve
-months of life.
+The dependent variable is whether the child died within the first twelve months of life.
 The main set of explanatory variables consists of dummies for the spacing from
 the prior birth.
-Starting nine months after the prior birth, the birth interval dummies cover 12 
-month periods until 57 months, which covers until 105 months after the prior birth.
+The birth interval dummies cover 12 month periods, starting nine months after the prior 
+birth, until the 57 months dummy, which covers until 105 months after the prior birth.
 I use dummies for sex of the index child and the sex composition 
@@
 I estimate the probability of infant mortality using a Logit model.
-Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} present 
+Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} show 
 the predicted probability of the second child dying within the first year at the 
 possible combinations of index child sex, sex composition of prior children, and 
-the birth spacing dummied.%
+birth spacing, with all other variables at their average values.%
 \footnote{
@@
 }
-All other variables take their average values.
-The graphs do not show confidence intervals to ease their legibility.
+The graphs do not show confidence intervals to improve legibility.
 
@@
 address potential selection problems.
-For example, if women who have difficulties conceiving or carrying a pregnancy 
-to term also have a higher mortality risk for their offspring, a spurious correlation 
-between long birth spacing and mortality may arise \citep{Kozuki2013}. 
-Unfortunately, methods used previously to address selection, such
-as family fixed effects, do not work well when the number of births is
-low as it is for better-educated women \citep{Kozuki2013,Molitoris2019}.
+For example, suppose women who have diﬀiculties conceiving or carrying a pregnancy to 
+term also have a higher mortality risk for their offspring. 
+In that case, a spurious correlation between long birth spacing and mortality may arise 
+\citep{Kozuki2013}. 
+Unfortunately, methods to address selection, such as family fixed effects, do not work 
+well when the number of births is as low as for better-educated women 
+\citep{Kozuki2013,Molitoris2019}.
 However, the fixed effects and linear probability results did not 
@@
 risk in the earliest periods.
-This difference disappears, however, with the general decline in mortality risk.
-
-If sex selective abortions lead to higher mortality risk, boys born after a girl 
-(the solid lines)
-should have an increased risk with longer spacing for the two highest education groups 
-in the last two periods.
-There are, however, no apparent consistent differences between these groups and the other 
+However, this difference disappears with the general decline in mortality risk.
+
+Despite the concern that multiple abortions might increase mortality risk by shortening 
+the interval between pregnancies, there is no evidence for this effect. 
+Suppose sex-selective abortions lead to higher mortality risk. In that case, boys born 
+after a girl---the solid lines---should have an increased risk with longer spacing for 
+the two highest education groups in the last two periods.
+However, there are no apparent consistent differences between these groups and the other 
 potential combinations. 
+The same holds for the third spell.
 
 % line 3661 in an_infant_mortality.log
-The raw numbers for women with the most uneven sex ratio also suggests that even with 
-high use of sex selection there is no impact on child mortality. 
-A total of 1,004 women with twelve or more years of
-education and no boys at the start of the third spell in the last
-period, had a third child, of which 685 were boys. 
+The raw numbers for women with the most uneven sex ratio also suggest that even with 
+very high use of sex selection, there is no impact on child mortality. 
+A total of 1,004 women with twelve or more years of education and no boys at the start of 
+the third spell in the last period, had a third child, of which 685 were boys. 
 Of these 685 boys, only six died within the first year of life. 
-Half of those who died were born in the 9-32 months interval, and none in 57 months 
-or longer interval.
+Half of those who died were born in the 9-32 months interval, and none in the 57 months 
+and up interval.
 

### 2020-08-06 paper/sex_selection_spacing-ver4.tex
Editing conclusion

@@
 % http://countwordsfree.com/#
-\usepackage[nolists]{endfloat}
+% \usepackage[nolists]{endfloat}
 
@@
 significant increase in birth intervals. 
-Over the four decades, the median birth interval for this group increased by almost 15, 
+Over the four decades, the median birth interval for this group increased by almost 15 
+months, 
 and the 75th percentile birth interval increased by a staggering 21 months, most of that 
@@
 % Background
-Over the last four decades India saw a dramatic increase in the male-to-female
-sex ratio at birth as access to sex selection spread and son preference remained. 
-At the same time, economic growth was strong, schooling increased, and the total
+Over the last four decades, India saw a dramatic increase in the male-to-female
+sex ratio at birth as access to sex selection spread and son preference remained high. 
+Simultaneously, economic growth was strong, schooling increased, and the total
 fertility rate fell to close to replacement.
@@
 % Questions
-The main question I address in this paper is how birth spacing responded to the major changes
-that occurred in India over the last four decade, in particular the spread of sex selection.
-In addition, I examine two related questions.
+The main question I address in this paper is how birth spacing responded to the 
+significant changes in India over the last four decades, particularly the spread of sex 
+selection.
+I also examine two related questions.
 First, did the changes in birth spacing bias the standard fertility estimates for India? 
@@
 % What has happened to spacing and why
-Birth intervals has lengthen, often substantially, over the last four decades.
-The increases in spacing are larger, the higher the parity and the higher the mother's
-education, and is larger in urban than in rural areas.
-
-Groups with the highest use of sex selection have the most substantial increases in 
-birth intervals, with increases in average birth intervals of up to 12 months. 
-Some of these increases are so large that we even observe a reversal of the traditional 
-spacing pattern: instead of the absence of sons leading to the shortest birth intervals, 
-son preference and sex selection lead some groups to have longest birth intervals when
-they have no sons.
-
-Despite the longer average birth intervals, a large number of women still have very 
-short birth intervals. 
-Hence, the changes in birth spacing are driven predominately by the longer intervals 
-becoming even longer over time.
-This pattern holds generally, but is especially prevalent for those who use sex selection 
-and, therefore, may end up with multiple abortions.
-
-% fertility
+The most substantial lengthening of birth intervals came from the best-educated women
+because of their substantial use of sex selection combined with falling fertility.
+As the sex ratio increased to almost 80 percent boys, the expected median birth interval 
+for a woman with twelve or more years of education who has two girls increased by almost 
+15 months, and the 75th percentile interval by 21 months.
+Most of that increase came right after the introduction of sex selection in India.
+
+Some of these increases are so large that we even observed a reversal of the traditional 
+spacing pattern for some groups; when there are no sons, we now see the longest, rather 
+than the shortest, birth intervals because of sex selection.
+The women who are the least likely to use sex selection still show the traditional 
+spacing pattern with short spacing in the absence of sons.
+
+Son preference continues to show in fertility decisions. 
 Fertility has declined for all groups, but the likelihood of having an additional child
@@
 
-The combination of the secular increases in spacing and the fact those women most likely to use
-sex selection are also those most likely to have a next birth, makes the total fertility rate a 
-more biased measure of cohort fertility. 
-This bias was most prominent early in the spread of sex selection, when the fertility rate 
+Birth intervals also lengthened in cases when sex selection is less likely to be used. 
+However, compared to other countries with similar declines in fertility, the median 
+spacing increases were smaller at three to six months over the four decades. 
+Most of the median intervals when sex selection is less used are still short at 36 months 
+or below. 
+Furthermore, many women still have very short birth intervals. 
+In many cases, more than 25 percent have their next child within 24 months of the previous 
+birth.
+
+% [predictions of declining sex selection] 
+Despite predictions that the use of sex selection would decline, there is no clear 
+evidence of this. 
+The original users of sex selection continue to show substantial male-biased sex ratios, 
+although there may be some leveling off. 
+More concerning, sex selection appears to be spreading to less educated women as their 
+fertility is falling.
+
+% fertility bias
+
+The increases in spacing make the total fertility rate a more biased measure of cohort 
+fertility. 
+This bias was most prominent early in the spread of sex selection when the fertility rate 
 was up to one child lower than the predicted cohort fertility. 
-It is, however, still present, with the predicted cohort fertility ten to twenty percent 
+However, it is still present, with the predicted cohort fertility ten to twenty percent 
 higher than the fertility rate. 
+At 1.8 children, the best-educated urban women are the only group for whom the predicted 
+cohort fertility is below replacement.
 
@@
 It is conceivable that we might see increases in the total fertility rate as birth spacing 
-stabilizes or, if interventions against sex selection are successful, even shortens again.
-
-The best-educated urban women are the only group for whom the predicted cohort fertility 
-is below replacement at 1.8. 
-A caveat to the predicted cohort fertility is that only Hindu women are in the sample and 
-that the model only includes births up to parity four.
-However, almost everybody marries, and Hindu constitute 80 percent of the population.
-Furthermore, with only the first fourth births used, these estimates may
-be lower-bound, especially for the less educated women.
+stabilizes or even shortens again if interventions against sex selection are successful.
 
@@
 birth took place more than 21 months from the prior birth.
-Short birth spacing is still associated with higher mortality, although the difference is 
+Short birth spacing is still associated with higher mortality, although the effect is 
 small for the best-educated women.
-There is no evidence that children born to women who are the most likely to use sex 
-selection have higher mortality risk.
-
-An important implication of the results here is that population growth in India
-may be higher than expected. 
-There has been a rapid reduction in infant mortality risk, the longer spacing should 
+There is no evidence that substantial use of sex selection is associated with higher 
+infant mortality.
+
+% Implications 
+An important implication of the results here is that population growth in India may
+not have fallen as much as recently suggested.
+There has been a rapid reduction in infant mortality risk, the longer birth spacing should 
 further reduce mortality risk, and cohort fertility is higher than previously realized.
@@
 very short birth intervals, which may reduce sibling competition. 
-Hence, better health outcomes for girls with sex selection could be an
-unintended side-effect, rather than a result of girls becoming more
-valued as is often assumed. 
+Hence, better health outcomes for girls with sex selection could be an unintended 
+side-effect, rather than the result of girls becoming more valued as is often assumed. 
 Comparing prior children's outcomes across sex composition and the sex of the next child 
@@
 
-Second, is there a relationship between female labor force participation
-and sex selection? 
+Second, what is the relationship between female labor force participation and sex selection? 
 Women may be staying out of the labor market precisely because sex selection makes 
@@
 First, it makes it more expensive to be out of the labor market for long periods. 
-Second, it would moderate the differential in potential earnings between husband
-and wife and make it more attractive to invest in female compared to
-male offspring's human capital. 
+Second, it would moderate the differential in potential earnings between husband and wife 
+and make it more attractive to invest in daughters' human capital. 
 This approach could, however, be a double-edged sword. 
-If better job opportunities further lower desired fertility, the use of sex selection 
-may increase, everything else equal.
-Hence, understanding the trade-off between long-term benefits from
-improvements in women's labor force participation and short-term costs
-from potential increases in sex selection is of paramount importance.
+If better job opportunities further lower fertility, the use of sex selection may increase, 
+everything else equal.
+Understanding the trade-off between long-term benefits from improvements in women's labor 
+force participation and short-term costs from potential increases in sex selection is of 
+paramount importance.
 
@@
 
-[More formal version of empirical strategy section]
+% [More formal version of empirical strategy section]
 

### 2020-08-11 paper/sex_selection_spacing-ver4.tex
Rewrite Abstract to focus on main questions

@@
 \noindent 
-Using four rounds of India's National Family and Health Surveys and a
-competing-risk hazard model, I show that Hindu women's birth intervals
-increased over the last four decades, more so the higher the parity and
-the more educated the woman. 
-Women most likely to use sex selection---well-educated with no sons---had the most 
-substantial lengthening of birth intervals and the most biased sex ratios. 
-However, the likelihood of very short spacing did not change substantially. 
-As a result of the longer spacing, fertility rates significantly
+In India, the most substantial lengthening in Hindu women's birth intervals over the last 
+four decades occurred for the women most likely to use sex-selective abortions. 
+For well-educated women with two girls, the median birth interval to the third child 
+increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
+sex ratio approached 80 percent boys. 
+Because of the rapid lengthening in spacing, standard fertility rates significantly 
 overestimated how fast cohort fertility fell. 
-Although cohort fertility
-and the fertility rate have started to converge, the cohort fertility is
-still substantially higher than the fertility rate. 
-Furthermore, cohort fertility is still at or above replacement level for all but the
-best-educated urban women. 
-Finally, infant mortality risk has declined substantially over time for all groups, but 
-fastest for the lower education groups, who are now close to the level of women with the most
-education. 
-Short birth spacing is still associated with higher mortality, although substantially less 
+Despite convergence, cohort fertility is still ten to twenty percent higher than the 
+fertility rate, and above replacement level for all but the best-educated urban women. 
+With the lengthening from sex selection, some women show a reversal of the traditional 
+spacing pattern; instead of the shortest birth interval in the absence of sons, they now 
+have the longest. 
+Finally, infant mortality has declined over time for all groups, but the decline was the 
+fastest for the less educated. 
+Short birth spacing is still associated with higher mortality, although considerably less 
 so for the best-educated women. 
-There is no evidence that the increasing use of sex selection is associated with
-higher infant mortality risk.
+There is no evidence that the increasing use of sex selection is associated with higher 
+infant mortality. 
+Neither does it appear that the use of sex selection is declining.
+
+% I show that, in India, the most substantial increases in Hindu women's
+% birth interval over the last four decades came from the increasing use
+% of sex-selective abortions. The women most likely to use sex
+% selection---well-educated with no sons---had the most substantial
+% lengthening of birth intervals and the most biased sex ratios.
 
@@
 15 months, and the 75th percentile interval by 21 months.
-Most of that increase came right after the introduction of sex selection in India.
+Most of the increase in the long intervals came right after the introduction of sex 
+selection in India.
 

### 2020-08-11 response/response-demography-3.tex
Respond to Editor concern about figures

@@
 ``Birth Spacing in the Presence of Son Preference and Sex-Selective
-Abortions:
-India's Experience over Four Decades.''
+Abortions: India's Experience over Four Decades.''
+Thank you for the comments and suggestions. 
+Below I outline my response to each issue raised.
 
-[Other changes]
+As part of rewriting the paper in response to the comments, I have changed a number of 
+additional parts to ensure that the paper is easier to follow and understand.
+The following are some of the more substantial changes not covered below in my responses:
 \begin{enumerate}
-	\item Rewritten Estimation Strategy section
+    \item The Abstract has been substantially rewritten to directly address the three
+    main questions I address in the paper
+	\item Rewritten ``Estimation Strategy'' section:
 	\begin{enumerate}
@@
 		analysis and all explanations gathered in this section
+		\item Remove the formular for percent boys since it added little to the
+		explanation. 
+		I have added a more formal version of the model to the online Appendix in the
+		``Empirical Model Details'' section.
 	\end{enumerate}
-	\item Changes in Data section
+	\item Changes in ``Data'' section:
 	\begin{enumerate}
-		\item Lead with what birth intervals I cover right after introducing
+		\item Lead with what birth spells I analyze right after introducing
 		data
-		\item Move restriction to only Hindus to be the first restriction
-		I discuss since that is the most important. 
-		See also response to Review 2 below.
+		\item Move discussion of restriction to only Hindus to be the first since that is 
+		the most important. 
+		See also response to Reviewer 2 below.
 	\end{enumerate}
-	\item Ensure consistent presentation of results
+	\item Ensure consistent presentation of results:
 	\begin{enumerate}
-		\item Use average rather than expected throughout now
-		\item Update table notes to better describe calculation methods
+		\item Update table notes to more clearly describe calculation methods
 	\end{enumerate}
@@
 [Response:]
+
+After trying a substantial number of different approaches, I believe the best way to 
+solve this problem is to fundamentally change the set-up of the birth spacing analysis.
+First examining how average birth spacing changed and then have a separate subsection on 
+distribution resulted in many graphs that each would become very small and hard to read.
+Instead, I now present three percentile birth intervals---25th, median, and 75th---together
+with the sex ratio and the parity progression probability.
+Furthermore, to keep within the figure/table limit and not have multiple-page figures,
+I moved the results for urban women without education and rural women with twelve or more 
+years of education to the online Appendix.
+
+The main advantage of this new approach, beside making the figures less challenging to 
+read, is that it more clearly ties the section directly to the main question I am asking.
+Furthermore, the new set-up makes it easier to understand similarities and differences 
+across groups and compare the results to the prior literature, as well as ties the
+birth spacing discussion directly to the fertility section that follows.
+
+The rewritten section proceeds in three parts.
+I now first present the broad trends for parity progression and sex ratio to set the
+stage for the analysis.
+
+Next, I discuss how birth spacing has changed in situations where there is the least use
+of sex selection (less educated women and among better educated women with one or more
+sons).
+To this part, I have added a discussion of how these results compare with what the
+prior literature has found \citep{Rutstein2011,Casterline2016}.
+To tie the results to the labor force participation, I also show how average spacing
+have increased the most for the women least likely to work.
+Finally, I show how the longest spacing has changed with declining fertility, and suggest 
+reasons why the best-educated women appear to be different from what has been observed 
+among other groups in India and elsewhere.
+
+The last part examines how birth spacing changed with use of sex selection.
+I use the third spell for the best-educated women as an illustration, especially the
+very rapid increase right after the introduction of sex selection.
+I then show where the reversal of the traditional spacing pattern occurred.
+As part of my response to reviewer 2's question about the period grouping, I have 
+included a discussion of whether the predicted decline in the use of sex selection
+came about.
+I end with a summary of results to tie the section to the fertility section.
 
@@
 in the Introduction rather than being spread over the Introduction and the
-relevant sections.
+other sections.
 
-Finally, I have made the discussion of the distribution of spacing a subsection
-of the spacing section and combined the discussion of the results to another new 
-subsection as well.
+Finally, I have completely redone the discussion of how spacing changed as described
+above.
 I hope this will make it easier for the reader to see the answer to the main

### 2020-08-11 paper/sex_selection_spacing-ver4.tex
Add better figure captions

@@
 
+\captionsetup[figure]{skip = -16}
+
 \begin{figure}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_rural}
-\caption{combined graphs - low rural}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for rural women with no education by spell, sex composition, and period}
 \label{fig:spacing_low_rural}
@@
 % \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
-% \caption{combined graphs - low urban}
+% \caption{Percentile birth intervals, sex ratios, and parity progression  
+% for urban women with no education by spell, sex composition, and period}
 % \label{fig:spacing_low_urban}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_rural}
-\caption{combined graphs - med rural}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for rural women with one to seven years of education by spell, sex composition, and period}
 \label{fig:spacing_med_rural}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
-\caption{combined graphs - med urban}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for urban women with one to seven years of education by spell, sex composition, and period}
 \label{fig:spacing_med_urban}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_rural}
-\caption{combined graphs - high rural}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for rural women with eight to eleven years of education by spell, sex composition, and period}
 \label{fig:spacing_high_rural}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
-\caption{combined graphs - high urban}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for urban women with eight to eleven years of education by spell, sex composition, and period}
 \label{fig:spacing_high_urban}
@@
 % \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
-% \caption{combined graphs - highest rural}
+% \caption{Percentile birth intervals, sex ratios, and parity progression  
+% for rural women with twelve or more years of education by spell, sex composition, and period}
 % \label{fig:spacing_highest_rural}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_urban}
-\caption{combined graphs - highest urban}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for urban women with twelve or more years of education by spell, sex composition, and period}
 \label{fig:spacing_highest_urban}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_low_med}
-\caption{Mortality low medium}
+\caption{Infant mortality by preceding birth interval across periods for women with 
+no education and women with one to seven years of education}
 \label{fig:mortality_low_med}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_high_highest}
-\caption{Mortality high highest}
+\caption{Infant mortality by preceding birth interval across periods for women with 
+eight to eleven and twelve and above years of education}
 \label{fig:mortality_high_highest}
@@
 studies.
+
+\captionsetup[figure]{skip = 10}
 
@@
 
+\captionsetup[figure]{skip = -16}
+
 Figures \ref{fig:spacing_low_urban} and \ref{fig:spacing_highest_rural} show 25th, 50th,
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
-\caption{combined graphs - low urban}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for urban women with no education by spell, sex composition, and period}
 \label{fig:spacing_low_urban}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
-\caption{combined graphs - highest rural}
+\caption{Percentile birth intervals, sex ratios, and parity progression  
+for rural women with twelve or more years of education by spell, sex composition, and period}
 \label{fig:spacing_highest_rural}
@@
 
+\captionsetup[figure]{skip = 5}
+
 \begin{figure}[htpb]

### 2020-08-17 paper/sex_selection_spacing-ver4.tex
Editing and update with Demography style guide

@@
 
-\title{Birth Spacing in the Presence of Son Preference and Sex-Selective Abortions:
+\title{Birth Spacing and Fertility in the Presence of Son Preference and Sex-Selective Abortions:
 India's Experience over Four Decades%
@@
 increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
-sex ratio approached 80 percent boys. 
+sex ratio approached 80\% boys. 
 Because of the rapid lengthening in spacing, standard fertility rates significantly 
 overestimated how fast cohort fertility fell. 
-Despite convergence, cohort fertility is still ten to twenty percent higher than the 
+Despite convergence, cohort fertility is still 10 to 20\% higher than the 
 fertility rate, and above replacement level for all but the best-educated urban women. 
@@
 % Background
-India experienced many positive changes over the last four decades:
-the economy grew substantially,
-schooling increased for males and females,
-and the total fertility rate fell to 2.2 
+India has experienced many positive changes over the past four decades:
+the economy has grown substantially,
+educational attainment has increased for males and females,
+and the total fertility rate has fallen to 2.2 children
 \citep{Bosworth2008,Dharmalingam2014,
@@
 female fetuses based on prenatal sex determination---with the introduction of ultrasound 
-in the mid-eighties.
-Combined with continued strong son preference, the result was a dramatic increase in the 
-male-to-female ratio at birth
+in the mid-1980s.
+Combined with a strong continued preference for sons, the result was a dramatic increase 
+in the male--female ratio at birth
 \citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,Portner2015b,Jayachandran2017}.
@@
 % Questions addressed and why valuable
-The main question here is: how did birth spacing respond to these changes, especially 
-the spread of sex selection? 
+The main question I address here is how birth spacing responded to these changes, 
+especially the spread of sex selection. 
 The motivation is twofold.
 First, prior research has failed to appreciate that each abortion increases the
-interval between births by six to twelve months.%
+interval between births by 6 to 12 months.%
 \footnote{
@@
 Hence, the growing use of sex-selective abortions may substantially increase birth spacing, 
-but we know little about how much. 
-Second, more female education, higher household income, and low and declining female labor 
-force participation all likely impact birth spacing. 
-Hence, the combined changes in birth spacing may outpace what we have observed in 
+although we do not know by how much. 
+Second, greater educational attainment by women, higher household income, and the low and 
+declining female labor force participation all likely influence birth spacing. 
+Thus, the combined changes in birth spacing may outpace what we have observed in 
 other countries.
@@
 Studying birth spacing contributes to our understanding of fertility decisions, but, equally 
-important, birth spacing affects the reliability of our fertility measures and may 
-impact mortality. 
-I, therefore, address two additional questions.
+important, birth spacing also affects the reliability of our fertility measures and may 
+affect mortality. 
+Therefore, I address two additional questions.
 
@@
 \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}. 
-Hence, if birth intervals increased substantially, India's fertility may be higher 
+Hence, if birth intervals increased substantially, then India's fertility may be higher 
 than generally accepted.
@@
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
-Hence, longer birth spacing, whether from sex selection or secular changes, may reduce 
+Therefore, longer birth spacing, whether from sex selection or secular changes, may reduce 
 mortality \citep{Conde-Agudelo2012,Molitoris2019}.
 However, a counteracting effect is possible if longer birth intervals arise from multiple 
-abortions since the short duration between \emph{pregnancies} could increase mortality. 
-Nevertheless, there has been no attempt to examine how infant mortality changed with 
+abortions because the short duration between pregnancies could increase mortality. 
+Nevertheless, there has been no attempt to examine how infant mortality has changed with 
 the increase in sex selection.
@@
 
-The primary outcomes I examine are 25th, 50th, and 75th percentile birth intervals, the 
-sex ratio at birth, and the likelihood of giving birth. 
+The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals;
+the sex ratio at birth; and the likelihood of giving birth. 
 I estimate the model across four periods to capture the changing access and 
 legality of sex selection. 
-The key variables are maternal education, the sex composition of previous 
-children, and area of residence.
+The key variables are maternal education, the sex of previous children, and the area of 
+residence.
 
@@
 
-First, birth intervals lengthen over the four decades, more so the higher the parity, the 
+First, birth intervals lengthen over the four decades---more so the higher the parity, the 
 more educated the woman, and the higher the percentile. 
-Women most likely to use sex selection---well-educated with no sons---had the most 
+Women most likely to use sex selection---well-educated women with no sons---had the most 
 substantial lengthening of birth intervals and the most biased sex ratios. 
@@
 women with no sons having \emph{longer} birth intervals than those with sons. 
-Those least likely to use sex selection---less-educated in rural areas---still follow the 
-traditional pattern of short spacing when they have girls and only some evidence of sex 
+Those least likely to use sex selection---less-educated women in rural areas---still follow the 
+traditional pattern of short spacing when they have girls with only some evidence of sex 
 selection. 
@@
 1990s and early 2000s as spacing began to increase. 
-Although the two have lately been converging, the predicted cohort fertility is still ten to 
-twenty percent higher than the fertility rate. 
+Although the two have lately been converging, the predicted cohort fertility is still 10 to 
+20\% higher than the fertility rate. 
 Furthermore, predicted cohort fertility is still at or above replacement level for all but 
@@
 
-I divide eduction into four groups: no education, one to seven years, eight to eleven 
-years, and twelve and more years.
+I divide eduction into four groups: no education, one to seven years, 8 to 11 years, and 
+12 and more years.
 The latter two correspond to having completed primary and completed secondary school, 
@@
 Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
-and eleven and twelve for ``upper secondary.''
+and 11 and 12 for ``upper secondary.''
 }
@@
 and mortality in India, I follow the NFHS reports, except that I combine the 
-less than five years and five to sevens years of schooling completed and the eight to nine 
-and ten to eleven years of schooling completed.
+less than five years and five to seven years of schooling completed and the eight to nine 
+and 10 to 11 years of schooling completed.
 This grouping allows me to capture the differences across education levels discussed below, 
@@
 twenty years or older, whether married or not, based on the four rounds of the NFHS.
-In rural areas, women with no education have gone from 90 percent for the 1930s cohorts to 
-less than 20 percent for the 1990s cohorts.
+In rural areas, women with no education have gone from 90\% for the 1930s cohorts to 
+less than 20\% for the 1990s cohorts.
 Women with eight or more years of education have gone from almost zero for the 1930 cohort 
-to more than sixty percent for the 1990s cohorts, with about half in the eight to eleven 
-group and the other half in the twelve plus group.
+to more than 60\% for the 1990s cohorts, with about half in the 8 to 11 group and the 
+other half in the 12 plus group.
 In urban areas, the proportions with no education or one to seven years have each declined 
-to just below ten percent.
-Most of the increase in urban female education came from the twelve plus group, which 
+to just below 10\%.
+Most of the increase in urban female education came from the 12 plus group, which 
 now account for more than half of all urban women for the lastest cohorts.
@@
 is that parents incur time costs when they have children \citep{Hotz1997,schultz97}.
-Specifically, if having children require the mother to reduce her market work, parents 
-can lower the cost of children by shortening birth spacing to 
-take advantage of economies of scale in childrearing \citep{Vijverberg1982}.
+Suppose having children requires the mother to reduce her market work. 
+Parents can then lower this cost of children by shortening birth spacing to take advantage 
+of economies of scale in childrearing  \citep{Vijverberg1982}.
 
@@
 First, although real wages for both men and women have almost doubled between 1987 and 
-2011, the mean male wage is still close to 70 percent higher than the female wage 
+2011, the mean male wage is still close to 70\% higher than the female wage 
 \citep{Klasen2015,Bhargava2018}.
@@
 given birth, conditional on the probability of giving birth in the spell. 
-For example, with an 80 percent parity progression probability, the median birth interval 
-is the predicted number of months before a woman passes the 60 percent mark on her survival 
+For example, with an 80\% parity progression probability, the median birth interval 
+is the predicted number of months before a woman passes the 60\% mark on her survival 
 curve. 
-I then and add nine months to account for the start of the spell. 
+I then add nine months to account for the start of the spell. 
 The reported statistic is the average of a given percentile interval across all women in 
@@
 Imagine $T=2$. 
-If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
-then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
+If 54 and 66\% of births are boys and the likelihood of giving birth 20 and 40\%, 
+then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$\% boys. 
 }
@@
 I restrict the sample to Hindus for two reasons.
-First, Hindus are the majority population group, about 80 percent of India’s population.
+First, Hindus are the majority population group, about 80\% of India’s population.
 Second, the prior literature shows that son preference and use of sex selection vary 
@@
 after the birth of the prior child.
-Less than one percent of observed births occur after the cut-off.
+Less than 1\% of observed births occur after the cut-off.
 The final sample consists of 
@@
 Abortion has been legal in India since 1971.
-Reports of sex determination appeared around 1982--83, and the number of clinics 
+Reports of sex determination appeared around 1982--1983, and the number of clinics 
 quickly increased \citep{Sudha1999,bhat06,Grover2006}.
@@
 }
-The sex ratio graphs also show the natural sex ratio, approximately 51.2 percent 
+The sex ratio graphs also show the natural sex ratio, approximately 51.2\% boys
 \citep{ben-porath76b,jacobsen99,Portner2015b}.
@@
 
-\captionsetup[figure]{skip = -16}
+\captionsetup[figure]{skip = -16pt}
 
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_rural}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_rural}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 % \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
 % \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_rural}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_rural}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_med_urban}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_urban}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_rural}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_rural}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_high_urban}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_urban}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 % \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
 % \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_urban}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_urban}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 become more male-dominated for women with no sons.
-The percent of births that were boys increased faster, the higher the education and the 
+The percentage of births that were boys increased faster, the higher the education and the 
 higher the parity.
@@
 A remarkably high proportion of birth intervals are still very short.
-For all but the most educated, more than 25 percent have their second and third child 
-within 24 months of the previous birth, substantially below the 24 months between 
+For all but the most educated, 25\% or more have their second and third child 
+within 24 months of the previous birth.
+These intervals are substantially below the 24 months between 
 \emph{pregnancies} the WHO recommends.
@@
 }
-Hence, women with the lowest labor force participation, those with eight to eleven years 
+Hence, women with the lowest labor force participation, those with 8 to 11 years 
 of education, also saw the largest increases in average spacing, possibly driven by the 
@@
 For example, the probability of a fourth birth for urban women with eight to eleven years 
-of education and two sons and a girl has declined by almost forty percentage points as the 
+of education and two sons and a girl has declined by almost 40 percentage points as the 
 75th percentile birth interval increased by 22 months.
@@
 women.
-With two girls, almost 80 percent of the third births are boys, and the 75th percentile 
+With two girls, almost 80\% of the third births are boys, and the 75th percentile 
 birth interval is close to 70 months. 
@@
 For the best-educated urban women with two girls, the 25th percentile birth interval 
-increased by six months, or 23 percent, while the median percentile birth interval 
+increased by six months, or 23\%, while the median percentile birth interval 
 increased by 15 months (43 percent).
@@
 A similar reversal, although more muted, occurred for the third spell for urban women 
-with one to seven years of education and both urban and rural women with eight to
-eleven years of education.
+with one to seven years of education and both urban and rural women with 8 to 11 years of 
+education.
 
@@
 before the survey month, again using the number of births three years before.
-This rate is shown as ``1987--88'' in the table.
+This rate is shown as ``1987--1988'' in the table.
 Given the relatively low number of births to women 40 to 45 years of age, this approach 
@@
 fertility measures begin to converge again.
-Even with the convergence, the predicted 2005--16 cohort fertility is still above the 
-1992--93 fertility rate for every group, except urban women with no education. 
-Furthermore, for the last period, the predicted cohort fertility remains at least ten to 
-twenty percent higher than the fertility rate.
+Even with the convergence, the predicted 2005--2016 cohort fertility is still above the 
+1992--1993 fertility rate for every group, except urban women with no education. 
+Furthermore, for the last period, the predicted cohort fertility remains at least 10 to 
+20\% higher than the fertility rate.
 
@@
 above replacement.
-Only for urban women with twelve or more years of education is the predicted cohort
-fertility clearly below 2.1.
+Only for urban women with 12 or more years of education is the predicted cohort
+fertility clearly below 2.1 children.
 Even then, cohort fertility is still more than 0.3 children higher than 
@@
 Furthermore, I do not show the results for women with twelve or more years of education 
-for the 1972--84 period because of the small number of women.
+for the 1972--1984 period because of the small number of women.
 
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_low_med}
-\caption{Infant mortality by preceding birth interval across periods for women with 
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_low_med}
+\caption{Infant mortality by preceding birth interval across periods for second child of women with 
 no education and women with one to seven years of education}
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{mortality_high_highest}
-\caption{Infant mortality by preceding birth interval across periods for women with 
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_high_highest}
+\caption{Infant mortality by preceding birth interval across periods for second child of women with 
 eight to eleven and twelve and above years of education}
@@
 the education groups, with even the no education group showing an infant mortality risk 
-below five percent.
+below 5\%.
 
@@
 effect declines with education level.
-For the best-educated women, the mortality risk is three to four percent,
-whereas women with no education still show a risk that is close to ten percent.
+For the best-educated women, the mortality risk is 3 to 4\%,
+whereas women with no education still show a risk that is close to 10\%.
 
@@
 Of these 685 boys, only six died within the first year of life. 
-Half of those who died were born in the 9-32 months interval, and none in the 57 months 
+Half of those who died were born in the 9--32 months interval, and none in the 57 months 
 and up interval.
@@
 because of their substantial use of sex selection combined with falling fertility.
-As the sex ratio increased to almost 80 percent boys, the expected median birth interval 
-for a woman with twelve or more years of education who has two girls increased by almost 
-15 months, and the 75th percentile interval by 21 months.
+Take, for example, women with 12 or more years of education who has two girls. 
+As the sex ratio increased to close to 80\% boys, the expected median birth interval 
+increased by almost 15 months, and the 75th percentile interval increased by 21 months.
 Most of the increase in the long intervals came right after the introduction of sex 
@@
 Furthermore, many women still have very short birth intervals. 
-In many cases, more than 25 percent have their next child within 24 months of the previous 
+In many cases, more than 25\% have their next child within 24 months of the previous 
 birth.
@@
 was up to one child lower than the predicted cohort fertility. 
-However, it is still present, with the predicted cohort fertility ten to twenty percent 
+However, it is still present, with the predicted cohort fertility 10 to 20\% 
 higher than the fertility rate. 
@@
 
-\captionsetup[figure]{skip = 10}
+\captionsetup[figure]{skip = 10pt}
 
@@
  {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
- \label{eq:hazard}
+ \label{eq:hazard_appendix}
 \end{equation}
@@
 
-Equation (\ref{eq:hazard}) is equivalent to the logistic hazard model and has the same 
+Equation (\ref{eq:hazard_appendix}) is equivalent to the logistic hazard model and has the same 
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_low_urban}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectration=true]{bs_highest_rural}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
 \caption{Percentile birth intervals, sex ratios, and parity progression  
@@
 
-\captionsetup[figure]{skip = 5}
-
-\begin{figure}[htpb]
+% \captionsetup[figure]{skip = 5pt}
+
+\begin{figure}
 \centering
-\rotatebox[origin=c]{90}{\small{1972-1984}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with no education}
-\label{fig:mortality_low}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_low_med}
+\caption{Infant mortality by preceding birth interval across periods for third child of women with 
+no education and women with one to seven years of education}
+\label{fig:mortality_low_med_spell_3}
 \end{figure}
 
-\begin{figure}[htpb]
+\begin{figure}
 \centering
-\rotatebox[origin=c]{90}{\small{1972-1984}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with one to
-seven years of education}
-\label{fig:mortality_med}
+\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_high_highest}
+\caption{Infant mortality by preceding birth interval across periods for third child of women with 
+eight to eleven and twelve and above years of education}
+\label{fig:mortality_high_highest_spell_3}
 \end{figure}
 
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{1972-1984}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with eight
-to eleven years of education}
-\label{fig:mortality_high}
-\end{figure}
-
-\begin{figure}[htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{1985-1994}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{1995-2004}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
-    \end{minipage}
-} 
-\\
-\rotatebox[origin=c]{90}{\small{2005-2016}}
-\subfloat[Second Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
-    \end{minipage}
-} 
-\subfloat[Third Spell]{
-    \begin{minipage}{0.40\textwidth}
-        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
-    \end{minipage}
-} 
-\caption{Predicted Probability of Infant Mortality for women with twelve or
-more years of education}
-\label{fig:mortality_highest}
-\end{figure}
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{1972-1984}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{1985-1994}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{1995-2004}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{2005-2016}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
+%     \end{minipage}
+% } 
+% \caption{Predicted Probability of Infant Mortality for women with no education}
+% \label{fig:mortality_low}
+% \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{1972-1984}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{1985-1994}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{1995-2004}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{2005-2016}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
+%     \end{minipage}
+% } 
+% \caption{Predicted Probability of Infant Mortality for women with one to
+% seven years of education}
+% \label{fig:mortality_med}
+% \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{1972-1984}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
+%     \end{minipage}
+% }
+% \\
+% \rotatebox[origin=c]{90}{\small{1985-1994}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{1995-2004}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{2005-2016}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
+%     \end{minipage}
+% } 
+% \caption{Predicted Probability of Infant Mortality for women with eight
+% to eleven years of education}
+% \label{fig:mortality_high}
+% \end{figure}
+
+% \begin{figure}[htpb]
+% \centering
+% \rotatebox[origin=c]{90}{\small{1985-1994}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{1995-2004}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
+%     \end{minipage}
+% } 
+% \\
+% \rotatebox[origin=c]{90}{\small{2005-2016}}
+% \subfloat[Second Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
+%     \end{minipage}
+% } 
+% \subfloat[Third Spell]{
+%     \begin{minipage}{0.40\textwidth}
+%         \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
+%     \end{minipage}
+% } 
+% \caption{Predicted Probability of Infant Mortality for women with twelve or
+% more years of education}
+% \label{fig:mortality_highest}
+% \end{figure}
 

### 2020-08-17 response/response-demography-3.tex
Editing response to Editor and referee

--- 2020-07-14 response/response-demography-3.tex
@@
 
-\noindent Please find attached the revised version of my paper,
+\noindent I have attached the revised version of my paper,
 ``Birth Spacing in the Presence of Son Preference and Sex-Selective
-Abortions:
-India's Experience over Four Decades.''
+Abortions: India's Experience over Four Decades.''
+Thank you for the comments and suggestions. 
+Below I outline my response to each issue raised.
 
-[Other changes]
+As part of rewriting the paper in response to the comments, I have changed several 
+additional components to ensure that it is easier to follow and understand.
+The following are the more substantial changes not covered below in my responses:
 \begin{enumerate}
-	\item Rewritten Estimation Strategy section
+    \item I substantially rewrote the Abstract to directly discuss the three main 
+    questions I address in the paper
+	\item ``Estimation Strategy'' section changes:
 	\begin{enumerate}
 		\item Clarify proportionality assumption
-		\item Better explain set-up of model and transformation of data needed
-		\item Remove discussion of explanatory variables so they are
+		\item Better explain the set-up of the model and transformation of data needed
+		\item Remove discussion of explanatory variables, so they are
 		only covered once (in the ``Data'' section)
-		\item Better explanation of how I calculate measures used for the spacing
+		\item Better explain how I calculate measures used for the spacing
 		analysis and all explanations gathered in this section
+		\item Remove the formula for percent boys since it added little. 
+		I have added a more formal version of the model to the online Appendix in the
+		``Empirical Model Details'' section.
 	\end{enumerate}
-	\item Changes in Data section
+	\item ``Data'' section changes:
 	\begin{enumerate}
-		\item Lead with what birth intervals I cover right after introducing
-		data
-		\item Move restriction to only Hindus to be the first restriction
-		I discuss since that is the most important. 
-		See also response to Review 2 below.
+		\item I now lead with a discussion of which birth spells I analyze right after 
+		introducing data
+		\item Move discussion of restriction to only Hindus to be the first since that is 
+		the most important. 
+		See also my response to Reviewer 2 below.
 	\end{enumerate}
-	\item Ensure consistent presentation of results
+	\item Consistent presentation of results:
 	\begin{enumerate}
-		\item Use average rather than expected throughout now
-		\item Update table notes to better describe calculation methods
+		\item Update table notes to describe calculation methods more clearly
 	\end{enumerate}
 \end{enumerate}
+
+Finally, I have decided to amend the paper title slightly to convey the main questions 
+addressed.
+The new title is ``Birth Spacing and Fertility in the Presence of Son Preference and 
+Sex-Selective Abortions: India's Experience over Four Decades.'' 
+If this becomes too long, removing ``Son Preference'' would be a possibility.
+Please let me know if you have any strong opinions on this.
 
@@
 
-TK review titles of figures and table to be better reflect the
-analyses undertaken.
+After trying a substantial number of different approaches, I believe the best way to solve 
+this problem is a complete rewrite of the birth spacing analysis section.
+Therefore, I now present three percentile birth intervals---25th, median, and 75th---together
+with the sex ratio and the parity progression probability.
+Furthermore, to keep within the figure/table limit and not have multiple-page figures,
+I moved the results for urban women without education and rural women with twelve or more 
+years of education to the online Appendix.
+
+The main advantage of this new approach---besides making the figures less challenging to 
+read---is that it more clearly ties the section directly to the main question I am asking.
+Furthermore, the new set-up makes it easier to understand similarities and differences 
+across groups and compare the results to the prior literature.
+It also ties the birth spacing discussion directly to the fertility section that follows.
+
+The rewritten section has three parts.
+I now first present the broad trends for parity progression and sex ratio to set the
+stage for the analysis.
+
+Next, I discuss how birth spacing has changed in situations where there is the least use
+of sex selection (less educated women no matter the sex composition and among 
+better-educated women with one or more sons).
+To this part, I added a discussion of how my results compare with the prior literature 
+\citep{Rutstein2011,Casterline2016}.
+To tie the results to the labor force participation, I also show how average spacing
+has increased the most for the women least likely to work.
+Finally, I show how the longest spacing has changed with declining fertility, and discuss 
+why the behavior of the best-educated women appear to be different from other groups in 
+India and elsewhere.
+
+The last part examines how birth spacing changed with the use of sex selection.
+To illustrate, I use the third spell for the best-educated women, especially the very 
+rapid increase right after sex selection became available.
+I then show where the reversal of the traditional spacing pattern occurred.
+As part of my response to reviewer 2's question about the period grouping, I include a 
+discussion of whether the predicted decline in the use of sex selection came about.
+I end with a summary of results to tie the section to the fertility section.
+
+Finally, I can produce figures in whatever format is best for printing.
+I can also easily change things like line width and labeling if that helps with the
+printing process.
 
@@
 
-I have rewritten the Introduction to emphasize the main question I address
-(``how did birth spacing respond to these changes, especially the introduction and spread 
-of sex selection?'') and the two questions addressing the effects of changes in 
+I have rewritten the Introduction to emphasize the main question I address (``how birth 
+spacing responded to these changes, especially the spread of sex selection'').
+I follow this with the two questions addressing the effects of changes in 
 birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
@@
 
-Following the three questions, I now outline how the study progresses focusing on 
-how I examine each of the three questions, including the key outcomes and key explanatory 
-variables.
-To prevent exceeding the word count I have also edited the entire introduction.
-Although sligthly longer than original, it is still less than 900 words 
-(not counting references).
+I next outline how the study progresses, focusing on how I examine each of the three 
+questions, including the key outcomes and key explanatory variables. 
+To prevent exceeding the word count, I have edited the entire Introduction.
 
-I have edited the introduction of each section to highlight what I question
-I am addressing.
-Furthermore, I have removed some of the repetition in, for example, the
-discussion of tempo effects and mortality, so that the motivation is now only
-in the Introduction rather than being spread over the Introduction and the
-relevant sections.
+The beginning of each section now highlights what I question I am addressing.
 
-Finally, I have made the discussion of the distribution of spacing a subsection
-of the spacing section and combined the discussion of the results to another new 
-subsection as well.
-I hope this will make it easier for the reader to see the answer to the main
-question of the paper.
+Furthermore, I have tried to removed repetitions throughout the paper. 
+One example is the discussion of tempo effects and mortality, where the motivation is now 
+only in the Introduction rather than being spread over multiple sections.
 
-TK I address the issue of the figure and table title above.
+As described above, I have completely redone the discussion of how spacing changed.
+I hope this will make it easier for the reader to see the answers to the paper's central 
+question.
+
+Finally, I have edited the figure and table titles to reflect the analyses better.
 
@@
 maternal education as a key stratification measure.
-First, higher female education is associated with lower fertility, and, thereby, with
+First, higher female education is associated with lower fertility, and, thereby, the 
 potential increased use of sex selection. 
-Second, female labor force participation in India, as well as other developing countries, 
-tend to first decrease and then increase with education.
-Finally, child morbidity and mortality decreases the better educated the mother.
+Second, female labor force participation in India, and other developing countries, 
+tend first to decrease and then increase with education. 
+Finally, child morbidity and mortality decrease the better educated the mother.
 
-After the discussion of why female education is a key variable, I explain the choice
-of cut-offs, which is based on the prior literature on fertility and son preference in 
-India and the NFHS reports.
-The exception to the the cut-offs in the NFHS reports is that I combine
+After discussing why female education is a crucial variable, I explain the choice of 
+cut-offs, which I based on the prior literature on fertility and son preference in India 
+and the NFHS reports.
+The exception to the cut-offs in the NFHS reports is that I combine
 the <5 years and 5--7 years of schooling completed and 
-the 8--9 and 10--11 years of schooling completed to reach sufficient sample sizes.
+the 8--9 and 10--11 years to reach sufficient sample sizes.
 
-This grouping also allows me to capture the U-shape in female labor force participation.
-The upper level of education could be split into having graduated secondary and having 
-graduated with a university degree since women with a completed university degree have 
-a higher labor force participation, but the sample of university graduates is too small 
-to allow for estimations, especially for the first three rounds of the surveys.
-Furthermore, with four groups there is already a substantially number of results to 
-present.
+This grouping also allows me to capture the U-shape in female labor force participation,
+which I refer to in my discussion of the changes in birth spacing when sex selection
+is less used.
+In principle, I could split the upper level of education into having graduated secondary 
+and having graduated with a university degree since women with a completed university 
+degree have a higher labor force participation. 
+The issue is that the sample of university graduates is too small to allow for estimations 
+for the first three rounds of the surveys. 
+Furthermore, with four groups, there is already a substantial number of results to present.
 
@@
 Strategy'' section.
-Furthermore, I clarify that for estimation purposes spells begin nine months 
+Furthermore, I clarify that for estimation purposes, spells begin nine months 
 after the previous birth since this is the earliest we should expect to observe 
 a new birth.
-This duration is equivalent to the interpregnancy interval, which is often used in 
-the literature on spacing and child mortality.
+% This duration is equivalent to the interpregnancy interval, which is often used in 
+% the literature on spacing and child mortality.
 
-To make comparison with both the NFHS reports and the prior literature on
+To make comparisons with both the NFHS reports and the prior literature on
 birth spacing easier and avoid confusion, I have rewritten the discussions of 
@@
 I still retain the use of ``spell'' to indicate a generic period from one parity 
-birth to another, i.e. second spell is from first birth to the second birth or
-censoring, in the graphs/tables.
+birth to another---i.e.,the second spell is from first birth to the second birth or
+censoring---in the graphs/tables.
 
@@
 clearer by specifying the cut-offs for both the spell duration and the birth interval.
-In the ``How Birth Spacing Changed'' section, I explain that I add nine month
+In the ``Estimation Strategy'' section, I explain that I add nine months
 to the estimated spell length to get to birth intervals.
@@
 definition of the periods but updated the numbers and the discussion of
-results so they reflect birth intervals rather than pregnancy intervals.
+results. 
+Hence, they now reflect birth intervals rather than pregnancy intervals.
 
@@
 
-I have expanded the discussion of the birth history data in the ``Data'' section and
-why it is important.
-As part of this expanded discussion, I included more information about systematic
-recall error, why it is likely the main concern here, what the effect is on the
-estimates, and how I address this problem.
+I have expanded the discussion of the quality of the birth history data in the ``Data'' 
+section and its importance. 
+As part of this expanded discussion, I included more information about systematic recall error, why it is likely the main concern here, the effect on the estimates, and how I address this problem.
 I have also included a reference to \citet{Schoumaker2014} that finds that the first
@@
 the Conclusion and recap the three questions after that.
-I have also slightly edited the Conclusion to tie better with the 
-questions.
+I have also edited the Conclusion to tie better with the questions.
 
@@
 
+As part of the rewrite, I have gone through the paper multiple times to try to catch
+any remaining mistakes.
+I have also had an copy editor go through the paper.
+
 \end{enumerate}
@@
 
-\begin{enumerate}
-
-\item
-
-\end{enumerate}
+I have tried to limit the number of figures as detailed above in my response to
+the Editors.
 
@@
 
-[With respect to the reviewer’s comments, please address comments #1, #2, and #4.]
+% [With respect to the reviewer’s comments, please address comments #1, #2, and #4.]
 
@@
 
+I now also discuss the changes between the last two papers in more detail in the 
+subsection on birth spacing with sex selection and in the Conclusion.
+
 \item While I like results being presented in figures, what I don’t like
@@
 [Response:]
+
+The main reason for not showing confidence intervals is that the figures would become
+close to impossible to read and previous reviewers felt that the tables were too dense
+to understand easily, a point I agree with.
+The original tables do have standard errors and test of whether differences are 
+statistically significant and these are available in the online Appendix.
+I have made it clearer in the text that the underlying values for the graphs and the
+bootstrapped standard errors are available in the Appendix.
 
@@
 
+As I have outline above, I have reorganize large parts of the paper and significantly
+rewritten the whole paper to make it easier to follow.
+
 \end{enumerate}

### 2020-08-17 response/response-demography-3.tex
Edit response

@@
 
-I have expanded the discussion of the quality of the birth history data in the ``Data'' 
-section and its importance. 
-As part of this expanded discussion, I included more information about systematic recall error, why it is likely the main concern here, the effect on the estimates, and how I address this problem.
-I have also included a reference to \citet{Schoumaker2014} that finds that the first
+I have expanded the discussion of the quality of the birth history data and why it is
+important in the ``Data''. 
+As part of this expanded discussion, I included more information about systematic recall 
+error, why it is likely the main concern here, its effect on the estimates, and how I 
+address this problem.
+I have also included a reference to \citet{Schoumaker2014}, who finds that the first
 rounds of the NFHS are of ``moderate quality,'' although that is without the correction
@@
 
-I have added a brief synopsis of the changes in India in the beginning of
-the Conclusion and recap the three questions after that.
+I have added a brief synopsis of the changes in India at the beginning of the Conclusion. 
+I recap the three questions after that. 
 I have also edited the Conclusion to tie better with the questions.
@@
 
-The main relevant theory on female labor force participation and education is the income 
+The most relevant theory on female labor force participation and education is the income 
 and substitution effects discussed in \citet{Hotz1997} and \citet{schultz97}.
@@
 
-Since the Goldin theory is not central to this argument, I have removed the sentence 
-on the theory.
-It is worth pointing out, however, that a decline in female labor force participation  
+Since the Goldin theory is not central to this argument, I have removed it.
+However, it is worth pointing out that a decline in female labor force participation  
 is in line with the hypothesis of a U-shaped labor force participation as a country 
 develops \citep{Goldin1994}.
-What is ``surprising" for India is that we have not yet seen any evidence of the upward 
+What is ``surprising" for India is that we have not yet seen evidence of the upward 
 sloping part.
-I do think that the combination of rapidly rising male income, son preference, and 
-relatively meager job opportunities for women with, say, high school education have a lot 
-to do with this.
+I think that the combination of rapidly rising male income, son preference, and relatively 
+meager job opportunities for women with, say, high school education has a lot to do with this.
 
@@
 
-As part of the rewrite, I have gone through the paper multiple times to try to catch
-any remaining mistakes.
-I have also had an copy editor go through the paper.
+As part of the rewrite, I have gone through the paper multiple times to catch any 
+remaining mistakes.
+I have also had an editor go through the paper.
 
@@
 
-I focus on the Hindu population because they are the majority population group 
-and because the prior literature argue that this group has a strong son preference and 
-consequently uses sex selection.%
-\footnote{
-Sikhs and Jains likely have even higher use of sex selection than Hindus but Sikhs 
-constitutes less than two percent of the population and Jains less than half a percent.
-}
-Since there is little evidence that Muslim use sex selection, combining Hindu and Muslim 
+I focus on the Hindu population for two reasons. 
+First, they are the majority population group. 
+Second, the prior literature argues that this group has a strong son preference and 
+consequently uses sex selection. 
+With little evidence that Muslims use sex selection combining Hindu and Muslim 
 would lead to biased results.
+Sikhs and Jains likely have even higher use of sex selection than Hindus, but Sikhs 
+constitute less than two percent of the population and Jains less than half a percent.
 
-How birth spacing of Muslim women changed is certainly of interest and is worthy
-of a separate analysis.
+How the birth spacing of Muslim women changed is undoubtedly an interesting question and 
+worthy of a separate analysis. 
 However, there are two problems with expanding the analysis. 
-First, although the lastest round of NFHS provides enough data for the analyses, 
-it would be hard to provide much in the way of comparison with earlier periods.
+First, although the latest round of NFHS provides enough data for the analyses, it would 
+be hard to provide much in the way of comparison with earlier periods. 
 This problem becomes especially acute once the Muslim population is split by education 
 levels to make the results comparable to the Hindu population. 
-Second, the paper is already very long and adding even more tables/graphs and the
-necessary discussions of the results does not seem feasible.
+Second, the paper is already very long, and adding even more tables/graphs and the 
+necessary discussion of the results does not seem feasible.
 
@@
 
-The 2004 break is an attempt to understand whether we are observing the beginning of
+The 2004 break is an attempt to understand whether we observe the beginning of
 a reversal in son preference and the use of sex selection as hypothesized by part of
@@
 references arguing that we might see the reversal.
-Clearly, the 2004/05 break is somewhat arbitrary, but does have the advantage of making 
+The 2004/2005 break is somewhat arbitrary but does have the advantage of making 
 the periods close to the same length (there are relatively few birth intervals that begin 
@@
 
-I now also discuss the changes between the last two papers in more detail in the 
-subsection on birth spacing with sex selection and in the Conclusion.
+I now discuss the changes between the last two periods in more detail in the 
+subsection on birth spacing with sex selection and the Conclusion.
 
@@
 
-The main reason for not showing confidence intervals is that the figures would become
-close to impossible to read and previous reviewers felt that the tables were too dense
-to understand easily, a point I agree with.
-The original tables do have standard errors and test of whether differences are 
-statistically significant and these are available in the online Appendix.
-I have made it clearer in the text that the underlying values for the graphs and the
-bootstrapped standard errors are available in the Appendix.
+The main reason for not showing confidence intervals is that the figures would become close 
+to impossible to read. 
+The original tables have both standard errors and tests of whether differences are 
+statistically significant. 
+These are available in the online Appendix. 
+I have made it more explicit in the text that the graphs' underlying values and the 
+bootstrapped standard errors are in the Appendix.
 
@@
 
-The discussion of labor supply was disjointed and unclear because I had split the 
-background and conceptual framework sections, making it difficult to see the connection.
-As explained above, I have combined and reorganized those two sections into one and
-removed the Goldin theory discussion since it is not directly relevant to my main
-argument of why labor supply is relevant.
+The female labor supply discussion was disjointed and unclear because I had split the 
+background and conceptual framework sections, making it diﬀicult to see the connection. 
+As explained above, I have combined and reorganized those two sections into one and removed 
+the Goldin theory discussion since it is not directly relevant to my main argument.
 
@@
 
-As I have outline above, I have reorganize large parts of the paper and significantly
-rewritten the whole paper to make it easier to follow.
+As I have outlined above, I have reorganized and significantly rewritten large parts of 
+the paper to make it easier to follow. 
+I have also had an editor go through the paper for both grammar and clarity.
 

### 2020-08-18 response/response-demography-3.tex
Edit for clarity

@@
 ``Birth Spacing in the Presence of Son Preference and Sex-Selective
-Abortions: India's Experience over Four Decades.''
+Abortions: India's Experience Over Four Decades.''
 Thank you for the comments and suggestions. 
@@
 
-As part of rewriting the paper in response to the comments, I have changed several 
-additional components to ensure that it is easier to follow and understand.
-The following are the more substantial changes not covered below in my responses:
+In addition to responding to the comments, I have rewritten substantial parts of the paper to ensure 
+that it is easier to follow. 
+The following are the more significant changes not covered below in my responses:
 \begin{enumerate}
@@
 		only covered once (in the ``Data'' section)
-		\item Better explain how I calculate measures used for the spacing
-		analysis and all explanations gathered in this section
+		\item Better explain how I calculate the outcomes used for the spacing analysis. 
+		All explanations are now gathered in this section
 		\item Remove the formula for percent boys since it added little. 
-		I have added a more formal version of the model to the online Appendix in the
+		I have added a more formal version of the model to the online appendix in the
 		``Empirical Model Details'' section.
@@
 		\item I now lead with a discussion of which birth spells I analyze right after 
-		introducing data
-		\item Move discussion of restriction to only Hindus to be the first since that is 
-		the most important. 
+		introducing the data sets
+		\item Move discussion of restriction to only Hindus to be the first restriction I 
+		discuss because that is the most important one. 
 		See also my response to Reviewer 2 below.
@@
 
-Finally, I have decided to amend the paper title slightly to convey the main questions 
+Finally, I have amended the paper title slightly to convey more clearly the main questions 
 addressed.
 The new title is ``Birth Spacing and Fertility in the Presence of Son Preference and 
-Sex-Selective Abortions: India's Experience over Four Decades.'' 
-If this becomes too long, removing ``Son Preference'' would be a possibility.
-Please let me know if you have any strong opinions on this.
+Sex-Selective Abortions: India's Experience Over Four Decades.'' 
+If this becomes too long, removing ``Son Preference and'' would be a possibility.
+Please let me know if you have any strong opinions on this change.
 
@@
 Furthermore, to keep within the figure/table limit and not have multiple-page figures,
-I moved the results for urban women without education and rural women with twelve or more 
-years of education to the online Appendix.
+I moved the results for urban women without education and rural women with 12 or more 
+years of education to the online appendix.
 
 The main advantage of this new approach---besides making the figures less challenging to 
-read---is that it more clearly ties the section directly to the main question I am asking.
+read---is that it more clearly ties the section to the main question I am asking.
 Furthermore, the new set-up makes it easier to understand similarities and differences 
@@
 It also ties the birth spacing discussion directly to the fertility section that follows.
+The basic gist of the results, of course, remains unchanged.
 
 The rewritten section has three parts.
-I now first present the broad trends for parity progression and sex ratio to set the
-stage for the analysis.
+First, I present the broad trends for parity progression and sex ratio to set the
+stage for the analyses.
 
@@
 better-educated women with one or more sons).
-To this part, I added a discussion of how my results compare with the prior literature 
+To this part, I have added a discussion of how my results compare with the prior literature 
 \citep{Rutstein2011,Casterline2016}.
-To tie the results to the labor force participation, I also show how average spacing
+To tie the results to the female labor force participation, I also show how average spacing
 has increased the most for the women least likely to work.
@@
 
-The last part examines how birth spacing changed with the use of sex selection.
+The last part of the section examines how birth spacing changed with the use of sex selection.
 To illustrate, I use the third spell for the best-educated women, especially the very 
@@
 I then show where the reversal of the traditional spacing pattern occurred.
-As part of my response to reviewer 2's question about the period grouping, I include a 
+As part of my response to reviewer 2's question about the period grouping, I now include a 
 discussion of whether the predicted decline in the use of sex selection came about.
@@
 Furthermore, I have tried to removed repetitions throughout the paper. 
-One example is the discussion of tempo effects and mortality, where the motivation is now 
+One example is the discussion of tempo effects, where the motivation is now 
 only in the Introduction rather than being spread over multiple sections.
@@
 
-Finally, I have edited the figure and table titles to reflect the analyses better.
+Finally, I have edited the figure and table titles so that they better reflect the analyses.
 
@@
 potential increased use of sex selection. 
-Second, female labor force participation in India, and other developing countries, 
-tend first to decrease and then increase with education. 
+Second, female labor force participation in India---and other developing countries---tend 
+first to decrease and then increase with education. 
 Finally, child morbidity and mortality decrease the better educated the mother.
@@
 The exception to the cut-offs in the NFHS reports is that I combine
-the <5 years and 5--7 years of schooling completed and 
-the 8--9 and 10--11 years to reach sufficient sample sizes.
+the <5 years and 5--7 years groups and 
+the 8--9 and 10--11 years groups to reach sufficient sample sizes.
 
@@
 Strategy'' section.
-Furthermore, I clarify that for estimation purposes, spells begin nine months 
-after the previous birth since this is the earliest we should expect to observe 
-a new birth.
+Furthermore, I clarify that for estimation purposes, spells begin nine months after the 
+previous birth, which is the earliest we should expect to observe a new birth.
 % This duration is equivalent to the interpregnancy interval, which is often used in 
@@
 birth spacing easier and avoid confusion, I have rewritten the discussions of 
-spacing and redone the graphs and table, so all results now reflect birth 
+spacing and redone the graphs and tables, so all results now reflect birth 
 intervals in months.
 I still retain the use of ``spell'' to indicate a generic period from one parity 
-birth to another---i.e.,the second spell is from first birth to the second birth or
+birth to another---i.e., the second spell is from first birth to the second birth or
 censoring---in the graphs/tables.
 
-In the Data section, I have also changed the discussion of the imposed censoring 
-clearer by specifying the cut-offs for both the spell duration and the birth interval.
+In the Data section, I have also clarified the discussion of the imposed censoring by 
+specifying the cut-offs for the spell duration and the birth interval.
 In the ``Estimation Strategy'' section, I explain that I add nine months
 to the estimated spell length to get to birth intervals.
-In the ``Mortality and the Changing Birth Spacing'' section, I retained the
-definition of the periods but updated the numbers and the discussion of
-results. 
-Hence, they now reflect birth intervals rather than pregnancy intervals.
+In the "Mortality and the Changing Birth Spacing" section, I retained the periods but 
+updated the numbers to reflect birth intervals rather than pregnancy intervals.
 
@@
 I have expanded the discussion of the quality of the birth history data and why it is
-important in the ``Data''. 
+important in the ``Data'' section. 
 As part of this expanded discussion, I included more information about systematic recall 
@@
 
-The most relevant theory on female labor force participation and education is the income 
-and substitution effects discussed in \citet{Hotz1997} and \citet{schultz97}.
-With the reorganization of the sections, the introduction of this theory now more naturally 
-follows the discussion of increasing education in India.
-I then discuss the declining female labor force participation and that it may come
-about because of the rapid income increases.
+One framework for understanding the relationship between female education, labor force 
+participation, and birth spacing is the income and substitution effects, as  discussed 
+in \citet{Hotz1997} and \citet{schultz97}.
+With the reorganization, the introduction of this now more naturally follows the discussion 
+of increasing education in India. 
+I then discuss the declining female labor force participation and that it may be the 
+result of the rapid income increases.
 
@@
 develops \citep{Goldin1994}.
-What is ``surprising" for India is that we have not yet seen evidence of the upward 
+What is peculiar about India is that we have not yet seen evidence of the upward 
 sloping part.
-I think that the combination of rapidly rising male income, son preference, and relatively 
+My prior is that the combination of rapidly rising male income, son preference, and relatively 
 meager job opportunities for women with, say, high school education has a lot to do with this.
@@
 
-As part of the rewrite, I have gone through the paper multiple times to catch any 
-remaining mistakes.
-I have also had an editor go through the paper.
+As part of the rewrite, I have endeavored to weed any remaining mistakes. 
+I have also had an editor work through the paper.
+There are some format changes that I am unclear about. 
+One of those is the best way to refer to numbers for the education groups. 
+The style guide says to write out numbers ten or less, but this becomes 
+unwieldy for ranges of years of education.
 
@@
 worthy of a separate analysis. 
-However, there are two problems with expanding the analysis. 
+However, there are two problems with expanding the analysis here. 
 First, although the latest round of NFHS provides enough data for the analyses, it would 
@@
 
-I have edited the discussion in the ``Data'' section to make the reason for focusing
+I have edited the discussion in the ``Data'' section to make my reasons for focusing
 on Hindus clearer, and hope to write a separate paper/note looking at how spacing
@@
 the prior literature.
-In the ``Data'' section, I have split the paragraph on the periods into two and expanded 
+I have made two changes to make this clearer.
+
+First, in the ``Data'' section, I have split the paragraph on the periods into two and expanded 
 the discussion of the motivation for the breaks, including adding two additional
-references arguing that we might see the reversal.
+references arguing that we might see a decline in use.
 The 2004/2005 break is somewhat arbitrary but does have the advantage of making 
@@
 
-I now discuss the changes between the last two periods in more detail in the 
-subsection on birth spacing with sex selection and the Conclusion.
+Second, I now discuss the changes between the last two periods in more detail in the 
+subsection on birth spacing with sex selection and in the Conclusion.
 
@@
 to impossible to read. 
-The original tables have both standard errors and tests of whether differences are 
-statistically significant. 
-These are available in the online Appendix. 
-I have made it more explicit in the text that the graphs' underlying values and the 
-bootstrapped standard errors are in the Appendix.
+The original tables are available in the online appendix and have both standard 
+errors and tests of whether differences are statistically significant. 
+I have clarified this in the text.
 
@@
 
-The female labor supply discussion was disjointed and unclear because I had split the 
+I believe the female labor supply discussion was disjointed and unclear because I had split the 
 background and conceptual framework sections, making it diﬀicult to see the connection. 

### 2020-08-19 paper/sex_selection_spacing-ver4.tex
Edit based on proof reader comments

@@
 \title{Birth Spacing and Fertility in the Presence of Son Preference and Sex-Selective Abortions:
-India's Experience over Four Decades%
+India's Experience Over Four Decades%
 \protect\thanks{%
@@
 \noindent 
-In India, the most substantial lengthening in Hindu women's birth intervals over the last 
-four decades occurred for the women most likely to use sex-selective abortions. 
-For well-educated women with two girls, the median birth interval to the third child 
-increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
-sex ratio approached 80\% boys. 
-Because of the rapid lengthening in spacing, standard fertility rates significantly 
+In India, the most substantial lengthening in Hindu women's birth intervals over the past 
+four decades has occurred for the women most likely to use sex-selective abortions. 
+For well-educated women with two girls, the median birth interval before the third child 
+has increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
+sex ratio has approached 80\% boys. 
+Because of the rapid lengthening in spacing, standard fertility rates have significantly 
 overestimated how fast cohort fertility fell. 
-Despite convergence, cohort fertility is still 10 to 20\% higher than the 
-fertility rate, and above replacement level for all but the best-educated urban women. 
+Despite convergence, cohort fertility is still 10\%--20\% higher than the 
+fertility rate and above replacement level for all but the best-educated urban women. 
 With the lengthening from sex selection, some women show a reversal of the traditional 
@@
 have the longest. 
-Finally, infant mortality has declined over time for all groups, but the decline was the 
+Finally, infant mortality has declined over time for all groups, but the decline was 
 fastest for the less educated. 
@@
 \noindent Keywords: India, prenatal sex determination, censoring, competing risk, 
-non-proportional hazard
+nonproportional hazard
 \end{abstract}
@@
 India has experienced many positive changes over the past four decades:
-the economy has grown substantially,
+The economy has grown substantially,
 educational attainment has increased for males and females,
@@
 The motivation is twofold.
-First, prior research has failed to appreciate that each abortion increases the
-interval between births by 6 to 12 months.%
+First, researchers have failed to appreciate that each abortion increases the
+interval between births by 6--12 months.%
 \footnote{
@@
 Hence, the growing use of sex-selective abortions may substantially increase birth spacing, 
-although we do not know by how much. 
+although we do not know to what extent. 
 Second, greater educational attainment by women, higher household income, and the low and 
@@
 With longer spacing, mothers will be older at each parity, and this tempo effect makes the 
-total fertility rate a downward biased estimate of cohort fertility
+total fertility rate a downward-biased estimate of cohort fertility
 \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}. 
@@
 To investigate how birth spacing has changed, I use a competing risk hazard model with 
-two exit states: the birth of a girl or the birth of a boy. 
-I apply the model to the birth histories of Hindu women covering 1972 to 2016 using 
+two exit states: The birth of a girl or the birth of a boy. 
+I apply the model to the birth histories of Hindu women covering 1972--2016 using 
 data from the four National Family and Health Surveys (NFHS).
@@
 
-First, birth intervals lengthen over the four decades---more so the higher the parity, the 
-more educated the woman, and the higher the percentile. 
+First, birth intervals lengthened over the four decades, and the lengthening was longer, 
+the higher the parity, the more educated the woman, and the higher the percentile. 
 Women most likely to use sex selection---well-educated women with no sons---had the most 
@@
 Those least likely to use sex selection---less-educated women in rural areas---still follow the 
-traditional pattern of short spacing when they have girls with only some evidence of sex 
+traditional pattern of short spacing when they have girls, with only some evidence of sex 
 selection. 
@@
 1990s and early 2000s as spacing began to increase. 
-Although the two have lately been converging, the predicted cohort fertility is still 10 to 
-20\% higher than the fertility rate. 
+Although the two have lately been converging, the predicted cohort fertility is still 
+10\%--20\% higher than the fertility rate. 
 Furthermore, predicted cohort fertility is still at or above replacement level for all but 
@@
 
-I divide eduction into four groups: no education, one to seven years, 8 to 11 years, and 
+I divide education levels into four groups: No education, 1--7 years, 8--11 years, and 
 12 and more years.
-The latter two correspond to having completed primary and completed secondary school, 
+The latter two correspond to having completed primary and secondary school, 
 respectively.%
@@
 and mortality in India, I follow the NFHS reports, except that I combine the 
-less than five years and five to seven years of schooling completed and the eight to nine 
-and 10 to 11 years of schooling completed.
+less than five years and 5--7 years of schooling completed and the 8--9 
+and 10--11 years of schooling completed.
 This grouping allows me to capture the differences across education levels discussed below, 
@@
 cohort for urban and rural women, 
-twenty years or older, whether married or not, based on the four rounds of the NFHS.
+20 years or older, whether married or not, based on the four rounds of the NFHS.
 In rural areas, women with no education have gone from 90\% for the 1930s cohorts to 
@@
 Women with eight or more years of education have gone from almost zero for the 1930 cohort 
-to more than 60\% for the 1990s cohorts, with about half in the 8 to 11 group and the 
+to more than 60\% for the 1990s cohorts, with about half in the 8--11 group and the 
 other half in the 12 plus group.
-In urban areas, the proportions with no education or one to seven years have each declined 
+In urban areas, the proportions with no education or 1--7 years have each declined 
 to just below 10\%.
 Most of the increase in urban female education came from the 12 plus group, which 
-now account for more than half of all urban women for the lastest cohorts.
+now accounts for more than half of all urban women for the most recent cohorts.
 
@@
 }
-\caption{Distribution of education by cohort for women twenty years or older at survey}
+\caption{Distribution of education by cohort for women 20 years or older at survey}
 \label{fig:education_over_time}
@@
 \citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-India's female labor force participation is now lower than most other countries and does 
+India's female labor force participation is now lower than that of most other countries and does 
 not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
 In line with previous research, the NFHS data show a U-shaped relationship between 
-education and working for married women, with the highest percent working for women with 
-either no education or twelve or more years and the lowest for women with eight to 
-eleven years of education.%
+education and working for married women, with the highest percentage working being women with 
+either no education or 12 or more years and the lowest being women with 8--11 years of education.%
 \footnote{
-See Appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
+See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
 }
@@
 effect dominates any substitution effect.
-Two findings speak for this effect.
+Two findings speak to this effect.
 First, although real wages for both men and women have almost doubled between 1987 and 
@@
 Second, women’s labor supply appears to be more negatively elastic to husbands' 
-wages than positively elastic to own wages \citep{Bhargava2018}.
+wages than positively elastic to their own wages \citep{Bhargava2018}.
 
@@
 The introduction of sex selection allows parents to avoid giving birth to girls but 
-increases the expected duration to the next birth.
+increases the expected interval to the next birth.
 Theory suggests that sex selection increases with lower desired fertility and with
@@
 Better-educated and urban women also tend to live in households with higher income, which 
-lowers the relative costs of using sex selection and have long birth intervals.
+lowers the relative costs of using sex selection and having long birth intervals.
 
 The combination of rising incomes and continued son preference may lead to even longer 
-spacing than expected from the income effect alone.
+spacing than might be expected from the income effect alone.
 As women's education increases, their productivity in the production of offspring human 
@@
 However, the evidence on spacing's effect on child quality measures such as IQ 
-and education is mixed for developed countries and non-existing for developing countries
+and education is mixed for developed countries and nonexisting for developing countries
 \citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
@@
 is that this group's behavior would change.
-However, ``Sanskritization'' implies that as lower castes females gain access to 
-education and their husbands' income increases, they adopt higher caste 
+However, ``Sanskritization'' implies that as lower-castes females gain access to 
+education and their husbands' income increases, they adopt higher-caste 
 norms such as stronger son preference and a retraction from the formal labor 
@@
 on child outcomes.
-Furthermore, I expect birth spacing to increase the most among the better-educated 
+Furthermore, I expect birth spacing to increase the most among the better educated 
 because their household income increases the most---even with declining female labor 
-participation---and their use of sex selection.
+participation---and because of their use of sex selection.
 Even with the substantial increase in the number of better-educated women, 
@@
 %  - Capture that the shape of the hazard function differ across groups
-%    (non-proportionality); needs a better description, maybe using example
+%    (nonproportionality); needs a better description, maybe using example
 %    of shorter spacing and/or use of sex selection. Differences in parity
@@
 spacing to a girl. 
-Therefore, I use a competing risk set-up that captures both the non-randomness of 
+Therefore, I use a competing risk setup that captures both the non-randomness of 
 the birth outcome and the differential spacing.%
@@
 \cite{Merli2000} used a discrete hazard model to examine whether 
-there were under-reporting of births in rural China, although they 
+there was underreporting of births in rural China, although they 
 estimated separate waiting time regressions for boys and girls.
@@
 fixed proportion of the hazard for any other individual. 
-Non-constant effects violate that assumption, and the results from a proportional hazard 
+Nonconstant effects violate that assumption, and the results from a proportional hazard 
 model would, therefore, be biased. 
 The proportionality assumption is especially problematic for higher-order birth 
-intervals since there are substantial differences across groups in the likelihood 
+intervals because there are substantial differences across groups in the likelihood 
 of progressing to the next birth and how soon couples want their next child if they 
@@
 
-Therefore, I use a non-proportional hazard specification that allows the shape of the 
+Therefore, I use a nonproportional hazard specification that allows the shape of the 
 hazard functions to vary across groups.
-The use of a non-proportional specification also mitigates any potential effects 
+The use of a nonproportional specification also mitigates any potential effects 
 of unobserved heterogeneity when used in conjunction with a flexible baseline hazard 
@@
 
-The model is a discrete-time, non-proportional, competing risk hazard model with two 
-exit states: either a boy or a girl is born. 
+The model is a discrete-time, nonproportional, competing risk hazard model with two 
+exit states: Either a boy or a girl is born. 
 The unit of analysis is a spell---the period from one parity birth to the following 
 birth or censoring. 
-For estimation purposes, the spells begin nine months after the previous birth since 
+For estimation purposes, the spells begin nine months after the previous birth because 
 this is the earliest we should expect to observe a new birth. 
-Censoring can happen for three reasons: the survey takes place, sterilization of the 
+Censoring can happen for three reasons: The survey takes place, sterilization of the 
 woman or her husband, or imposed because of too few births for the method to work.
@@
 For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
-the spell continues until time $t_i$ when either birth or censoring of the spell 
+the spell continues until time $t_i$, when either birth or censoring of the spell 
 occurs.
-The time of censoring is assumed independent of the hazard rate,
+The time of censoring is assumed to be independent of the hazard rate,
 as is standard in the literature.
@@
 baseline hazard unnecessarily.
-$\mathbf{Z}$ is the non-proportional part, which includes the interactions between 
+$\mathbf{Z}$ is the nonproportional part, which includes the interactions between 
 $D_j(t)$ and a set of explanatory variables and the interactions of those.
@@
 % are done separately for different levels of mothers' education and different periods.
-% I discuss the choice of which variables to use for non-proportionality below.
-
-Equation (\ref{eq:hazard}) is equivalent to the logistic hazard model and has the same 
+% I discuss the choice of which variables to use for nonproportionality below.
+
+Equation \ref{eq:hazard} is equivalent to the logistic hazard model and has the same 
 likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
@@
 treating them as observations, I can estimate the model using a standard multinomial 
-Logit model. 
+logit model. 
 % In the reorganized data, the outcome variable is 0 if the woman does not have a child 
@@
 I use the model to predict birth interval measures, parity progression probabilities, 
-and the sex ratio rather than present coefficients since the interpretation 
+and the sex ratio rather than present coefficients because the interpretation 
 of competing risk model coefficients is challenging \citep{thomas96}.
@@
 For birth intervals, I estimate a set of percentile birth intervals. 
-I first calculate for each woman when there is a given percent chance that she will have 
+I first calculate for each woman when there is a given percentage chance that she will have 
 given birth, conditional on the probability of giving birth in the spell. 
@@
 parity progression probabilities as weights.
-To find the individual sex ratio, I estimate the percent of births that are boys at $t$, 
+To find the individual sex ratio, I estimate the percentage of births that are boys at $t$, 
 conditional on not having had a child before $t$.
-Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
-$t$ gives the predicted percent of boys over the entire spell for an individual.%
+Weighting the percent boys with the likelihood of exiting the spell with a birth across all 
+$t$ gives the predicted percentage of boys over the entire spell for an individual.%
 \footnote{
 Imagine $T=2$. 
-If 54 and 66\% of births are boys and the likelihood of giving birth 20 and 40\%, 
+If 54\% and 66\% of births are boys and the likelihood of giving birth 20\% and 40\%, 
 then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$\% boys. 
@@
 
-Finally, I exclude visitors and women in any of the following categories: never married; 
+Finally, I exclude visitors and women in any of the following categories: Never married; 
 no gauna yet; married more than once; divorced; not living with husband; inconsistent age 
@@
 The same goes for women who had at least one multiple births, reported giving birth 
-before age 12, had a birth before marriage, or an interval between births of less than 
+before age 12, had a birth before marriage, or had an interval between births of less than 
 nine months.
@@
 make changes over time appear too small.
-In the Online Appendix, I provide a detailed analysis of systematic recall error, which 
+In the online appendix, I provide a detailed analysis of systematic recall error, which 
 shows that recall error depends heavily on how long ago a woman was married. 
@@
 after the birth of the prior child.
-Less than 1\% of observed births occur after the cut-off.
+Less than 1\% of observed births occur after the cutoff.
 The final sample consists of 
@@
 I use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The first covers before sex selection became available and the second from when sex 
+The first covers the period before sex selection became available and the second from when sex 
 selection became available until the Prenatal Diagnostic Techniques Act.
-I have split the period from 1995 until 2016 into two to examine if there is support for 
+I have split the period from 1995 until 2016 into two to examine if there was support for 
 the prior literature's hypothesized reversal in child sex ratios and son 
@@
 The allocation of spells into periods is determined by when conception, and, therefore, 
-decisions on sex selection, can begin. 
+decisions on sex selection can begin. 
 Hence, some spells cover two periods, which may bias downward the differences between the 
 periods.
-Most sterilizations take place right after a woman gives birth, and,
-therefore, do not show up in the samples used. 
+Most sterilizations take place soon after giving birth. 
+These spells, therefore, do not show up in the samples used. 
 Furthermore, sterilization depends strongly on the sex composition of prior children
@@
 
-I divide the explanatory variables into two groups, non-proportional and proportional. 
-The first group consists of characteristics that the prior literature finds affect the 
-spacing choice and the use of sex selection: mother’s education, sex composition of 
+I divide the explanatory variables into two groups, nonproportional and proportional. 
+The first group consists of characteristics shown in the prior literature to affect the 
+spacing choice and the use of sex selection: Mother’s education, sex composition of 
 previous children, and area of residence. 
@@
 Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
-show the 25th, 50th, and 75th percentiles birth intervals in 
+show the 25th, 50th, and 75th percentile birth intervals in 
 months, the sex ratio, and the probability of having a birth for each spell
@@
 \footnote{
-Results for urban women without education, rural women with twelve or more years of 
-education, and the fourth spell for women with twelve or more years of education are
+Results for urban women without education, rural women with 12 or more years of 
+education, and the fourth spell for women with 12 or more years of education are
 in the online appendix because of relatively small samples.
@@
 \caption{Percentile birth intervals, sex ratios, and parity progression  
-for rural women with one to seven years of education by spell, sex composition, and period}
+for rural women with 1--7 years of education by spell, sex composition, and period}
 \label{fig:spacing_med_rural}
@@
 \caption{Percentile birth intervals, sex ratios, and parity progression  
-for urban women with one to seven years of education by spell, sex composition, and period}
+for urban women with 1--7 years of education by spell, sex composition, and period}
 \label{fig:spacing_med_urban}
@@
 \caption{Percentile birth intervals, sex ratios, and parity progression  
-for rural women with eight to eleven years of education by spell, sex composition, and period}
+for rural women with 8--11 years of education by spell, sex composition, and period}
 \label{fig:spacing_high_rural}
@@
 \caption{Percentile birth intervals, sex ratios, and parity progression  
-for urban women with eight to eleven years of education by spell, sex composition, and period}
+for urban women with 8--11 years of education by spell, sex composition, and period}
 \label{fig:spacing_high_urban}
@@
 % \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for rural women with twelve or more years of education by spell, sex composition, and period}
+% for rural women with 12 or more years of education by spell, sex composition, and period}
 % \label{fig:spacing_highest_rural}
@@
 \caption{Percentile birth intervals, sex ratios, and parity progression  
-for urban women with twelve or more years of education by spell, sex composition, and period}
+for urban women with 12 or more years of education by spell, sex composition, and period}
 \label{fig:spacing_highest_urban}
 \end{figure}
-
-%The results show three broad trends.
-%% [Birth intervals]
-%First, 
-%over the four decades, birth intervals have lengthen, whether measured by the
-%25th, 50th, or 75th percentile.
-%These increases are larger the higher the education of the mother, the higher the parity, 
-%and the higher the percentile measure.
 
@@
 has decreased over time.
-The likelihood of a next birth fell faster, the higher the education, the higher the 
+The likelihood of a next birth fell more rapidly, the higher the education, the higher the 
 parity, and with at least one son.
-Within a given spell and period, parity progressions are lower in urban than in rural areas, 
+Within a given spell and period, parity progressions are lower in urban than rural areas, 
 if at least one son is present, and the more educated the mother.
@@
 become more male-dominated for women with no sons.
-The percentage of births that were boys increased faster, the higher the education and the 
+The percentage of births that were boys increased more quickly, the higher the education and the 
 higher the parity.
 There are no clear trends for the other sex compositions.
-Within a given spell and period combination and in the absence of a son, sex ratios are 
-higher, the more educated the mother, and the higher the parity. 
+Within a given spell and period combination and in the absence of a son, sex ratios are higher 
+the more educated the mother is and with higher parity. 
 Sex ratios are also higher in urban than in rural areas.
@@
 % [Birth intervals w/o sex selection]
-\subsection{When Sex Selection is Less Used}
+\subsection{When Sex Selection Is Less Used}
 
@@
 is less used.
-The group broadly covers women with no education, no matter the sex composition of their 
-children, and women with any education who has one or two sons already. 
+The group broadly covers women with no education, regardless of the sex composition of their 
+children, and women with any education who have one or two sons already. 
 Despite the lower level of sex selection, son preference is still evident with the 
 shortest spacing when they have only girls. 
-Notably, for those least likely to use sex selection, rural women with no education, the 
+Notably, for those least likely to use sex selection---rural women with no education---the 
 difference in birth intervals across sex compositions has grown over time as spacing when 
-sons are present increased.
+sons are present has increased.
 
@@
 Birth intervals appeared to lengthen the most for women the least likely to work.
-For example, from lowest to higher education, the average third spell birth intervals for 
+For example, from lowest to highest education, the average third-spell birth intervals for 
 urban women with one boy and one girl increased by 2.7, 3.4, 5.8, and 1.8 months over the 
@@
 }
-Hence, women with the lowest labor force participation, those with 8 to 11 years 
-of education, also saw the largest increases in average spacing, possibly driven by the 
+Hence, women with the lowest labor force participation---those with 8--11 years 
+of education---also saw the largest increases in average spacing, possibly driven by the 
 substantial improvement in household income for this group from economic growth.
@@
 The most substantial changes occurred in the 75th percentile birth intervals, where the 
-more the parity progression probabilities declined, the more the birth interval lengthen. 
-For example, the probability of a fourth birth for urban women with eight to eleven years 
+more the parity progression probabilities declined, the more the birth interval lengthened. 
+For example, the probability of a fourth birth for urban women with 8--11 years 
 of education and two sons and a girl has declined by almost 40 percentage points as the 
 75th percentile birth interval increased by 22 months.
-Compare this with no education, rural women with a boy as their first child, where the 
-probability of a third birth declined by less than six percentage points while the birth 
-interval increased by only slightly over two months.
+Compare this with rural women of no education with a boy as their first child, for whom the 
+probability of a third birth declined by fewer than six percentage points while the birth 
+interval increased only slightly over two months.
 
@@
 declined rapidly, but the birth intervals changed little.
-These women have both better access to modern contraceptives and are better at using 
+These women both have better access to modern contraceptives and are better at using 
 traditional contraceptive methods \citep{Rosenzweig1989}.
@@
 around 55 months to 54 months.
-These changes in birth spacing may even be an underestimate since this particular group 
+These changes in birth spacing may even be an underestimate because this particular group 
 appears to have had access to sex selection even before it became widespread, as shown by 
@@
 
-The 75th percentile changes are the most dramatic, but sex selection also impacts the 
+The 75th percentile changes are the most dramatic, but sex selection also affects the 
 25th and median birth intervals. 
@@
 increased by six months, or 23\%, while the median percentile birth interval 
-increased by 15 months (43 percent).
+increased by 15 months (43\%).
 
@@
 A similar reversal, although more muted, occurred for the third spell for urban women 
-with one to seven years of education and both urban and rural women with 8 to 11 years of 
+with 1--7 years of education and both urban and rural women with 8--11 years of 
 education.
@@
 selection. 
-For example, for rural women with one to seven years of education, the sex ratios in the 
+For example, for rural women with 1--7 years of education, the sex ratios in the 
 absence of girls continued to increase while the likelihood of an additional birth remained 
@@
 
-In summary, over the four decades, birth intervals have lengthened with improving economic 
+In summary, over the four decades, birth intervals lengthened with improving economic 
 conditions and falling fertility. 
@@
 predicted cohort fertility from the hazard model.
-Table \ref{tab:fertility} shows the two fertility measures by urban/rural and education.
+Table \ref{tab:fertility} shows the two fertility measures by area of residence and education.
 
@@
 This rate is shown as ``1987--1988'' in the table.
-Given the relatively low number of births to women 40 to 45 years of age, this approach 
+Given the relatively low number of births to women 40--45 years of age, this approach 
 provides the best estimate of the fertility rate when sex selection still was not 
@@
 probability for each spell. 
-Since parity progression depends on the sex composition of prior children, I estimate the 
+Because parity progression depends on the sex composition of prior children, I estimate the 
 probability for each sex composition and weigh the probabilities with the likelihood of 
@@
 I include the spell from marriage to first birth, despite the problems capturing the exact 
-timing of marriages since the estimated progression probabilities should not be affected 
+timing of marriages because the estimated progression probabilities should not be affected 
 by this problem. 
 I begin with the age of marriage for each woman and predict the likelihood of progressing 
-to each parity, assuming three years increases in age between births. 
+to each parity, assuming three-years increases in age between births. 
 Shorter assumed increases in age lead to slightly higher predicted fertility.
@@
 Hence, the fertility rate declined too fast from the mid-1980s to the century's end.
-Only recently, as the rate of increase for the birth intervals has slowed, do the two 
-fertility measures begin to converge again.
+Only recently, as the rate of increase for the birth intervals has slowed, have the two 
+fertility measures begun to converge again.
 Even with the convergence, the predicted 2005--2016 cohort fertility is still above the 
 1992--1993 fertility rate for every group, except urban women with no education. 
-Furthermore, for the last period, the predicted cohort fertility remains at least 10 to 
-20\% higher than the fertility rate.
+Furthermore, for the last period, the predicted cohort fertility remains at least 
+10\%--20\% higher than the fertility rate.
 
@@
 fertility rate \emph{increases} for some groups.
-For example, for urban women with eight to eleven years of education, the fertility
+For example, for urban women with 8--11 years of education, the fertility
 rates were 1.84, 1.81, and 1.87 over the last three surveys.
@@
 the fertility rate estimate of 1.5.
-Furthermore, the predicted cohort fertility numbers are likely too low since I use only 
+Furthermore, the predicted cohort fertility numbers are likely too low because I use only 
 the first four births and births before the imposed 105-month birth interval censoring.
@@
 and deaths for parity four. 
-Furthermore, I do not show the results for women with twelve or more years of education 
+Furthermore, I do not show the results for women with 12 or more years of education 
 for the 1972--1984 period because of the small number of women.
 
-The dependent variable is whether the child died within the first twelve months of life.
+The dependent variable is whether the child died within the first 12 months of life.
 The main set of explanatory variables consists of dummies for the spacing from
 the prior birth.
-The birth interval dummies cover 12 month periods, starting nine months after the prior 
-birth, until the 57 months dummy, which covers until 105 months after the prior birth.
+The birth interval dummies cover 12-month periods, starting nine months after the prior 
+birth, until the 57-month dummy, which covers until 105 months after the prior birth.
 I use dummies for sex of the index child and the sex composition 
@@
 are all interacted.
-Since the actual number of abortions is unobserved, the interactions between
+Because the actual number of abortions is unobserved, the interactions between
 the sex composition of prior children and the sex of the index child serve
@@
 \footnote{
-The online Appendix shows the corresponding graphs for the third child.
+The online appendix shows the corresponding graphs for the third child.
 }
@@
 \caption{Infant mortality by preceding birth interval across periods for second child of women with 
-no education and women with one to seven years of education}
+no education and women with 1--7 years of education}
 \label{fig:mortality_low_med}
@@
 \caption{Infant mortality by preceding birth interval across periods for second child of women with 
-eight to eleven and twelve and above years of education}
+8--11 and 12 and above years of education}
 \label{fig:mortality_high_highest}
@@
 For intervals 21 months or longer, there is now little difference across 
-the education groups, with even the no education group showing an infant mortality risk 
+the education groups, with even the no-education group showing an infant mortality risk 
 below 5\%.
@@
 effect declines with education level.
-For the best-educated women, the mortality risk is 3 to 4\%,
+For the best-educated women, the mortality risk is 3\%--4\%,
 whereas women with no education still show a risk that is close to 10\%.
@@
 very high use of sex selection, there is no impact on child mortality. 
-A total of 1,004 women with twelve or more years of education and no boys at the start of 
-the third spell in the last period, had a third child, of which 685 were boys. 
+A total of 1,004 women with 12 or more years of education and no boys at the start of 
+the third spell in the last period had a third child, of which 685 were boys. 
 Of these 685 boys, only six died within the first year of life. 
-Half of those who died were born in the 9--32 months interval, and none in the 57 months 
-and up interval.
+Half of those who died were born in the 9--32-month interval, and none in the 57-month+ 
+interval.
 
@@
 % Background
-Over the last four decades, India saw a dramatic increase in the male-to-female
+Over the past four decades, India saw a dramatic increase in the male-to-female
 sex ratio at birth as access to sex selection spread and son preference remained high. 
 Simultaneously, economic growth was strong, schooling increased, and the total
-fertility rate fell to close to replacement.
+fertility rate fell to close to the replacement level.
 
@@
 The main question I address in this paper is how birth spacing responded to the 
-significant changes in India over the last four decades, particularly the spread of sex 
+significant changes in India between 1972 and 2016, particularly the spread of sex 
 selection.
@@
 because of their substantial use of sex selection combined with falling fertility.
-Take, for example, women with 12 or more years of education who has two girls. 
+Take, for example, women with 12 or more years of education who had two girls. 
 As the sex ratio increased to close to 80\% boys, the expected median birth interval 
 increased by almost 15 months, and the 75th percentile interval increased by 21 months.
-Most of the increase in the long intervals came right after the introduction of sex 
+Most of the increase in the long intervals came immediately after the introduction of sex 
 selection in India.
@@
 However, compared to other countries with similar declines in fertility, the median 
-spacing increases were smaller at three to six months over the four decades. 
+spacing increases were smaller at three to six months over the period. 
 Most of the median intervals when sex selection is less used are still short at 36 months 
@@
 was up to one child lower than the predicted cohort fertility. 
-However, it is still present, with the predicted cohort fertility 10 to 20\% 
+However, it is still present, with the predicted cohort fertility 10\%--20\% 
 higher than the fertility rate. 
@@
 
-Tempo effects are studied extensively in the literature \citep[See, for example, ][]{Bongaarts1999}.
+Tempo effects are studied extensively in the literature \citep[see, for example, ][]{Bongaarts1999}.
 Still, there are, to my knowledge, no other cases where there has been as 
@@
 If better job opportunities further lower fertility, the use of sex selection may increase, 
-everything else equal.
+everything else being equal.
 Understanding the trade-off between long-term benefits from improvements in women's labor 
@@
 
-The model is a discrete time, non-proportional, competing risk hazard model with two exit 
-states: either a boy or a girl is born.
+The model is a discrete time, nonproportional, competing risk hazard model with two exit 
+states: Either a boy or a girl is born.
 The unit of analysis is a spell, the period from nine months after one birth to the next.
@@
 }
-There are two exit states: the birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
+There are two exit states: The birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
 $J_i$ is a random variable indicating which event took place.
@@
 The explanatory variables in $\mathbf{Z}$, and the interactions between them, 
-constitute the non-proportional part of the model, which means that they are
+constitute the nonproportional part of the model, which means that they are
 interacted with the baseline hazard:
@@
 sex of that child. 
-This Appendix section assesses the degree of recall error across the surveys and discusses 
+This appendix section assesses the degree of recall error across the surveys and discusses 
 methods to address it.

### 2020-08-20 response/response-demography-3.tex
Minor edits
Editing (#26)
* Editing and update with Demography style guide

- Edit based on proofreader comments
- Consistent presentation across appendix and main paper

* Edit Abstract and Introduction

- Focus on main questions

* Edit Background and Conceptual Framework section

*  Edit Empirical Strategy section

- Remove average discussion of Estimation Strategy section
- Fix percentile examples
- Remove unneeded formula

* Edit Data section

* Major editing of birth interval section(s) 

- Combined percentile spacing, sex ratio, parity progression graphs
- Thinner lines for easier separ

@@
 
-\item I see the point to reviewer’s comment #4 about the discussion on
+\item I see the point to reviewer’s comment \#4 about the discussion on
 women’s labor supply. It’s a complex topic to introduce in a few brief
@@
 the paper to make it easier to follow. 
-I have also had an editor go through the paper for both grammar and clarity.
+I have also had an editor go through the paper to help with grammar and clarity.
 

### 2020-08-20 paper/sex_selection_spacing-ver4.tex
Editing (#26)
* Editing and update with Demography style guide

- Edit based on proofreader comments
- Consistent presentation across appendix and main paper

* Edit Abstract and Introduction

- Focus on main questions

* Edit Background and Conceptual Framework section

*  Edit Empirical Strategy section

- Remove average discussion of Estimation Strategy section
- Fix percentile examples
- Remove unneeded formula

* Edit Data section

* Major editing of birth interval section(s) 

- Combined percentile spacing, sex ratio, parity progression graphs
- Thinner lines for easier separating lines

@@
 \\
-\rotatebox[origin=c]{90}{\small{30 to 39 Years Old}}
+\rotatebox[origin=c]{90}{\small{30--39 Years Old}}
 \subfloat[Rural]{
@@
 \\
-\rotatebox[origin=c]{90}{\small{20 to 29 Years Old}}
+\rotatebox[origin=c]{90}{\small{20--29 Years Old}}
 \subfloat[Rural]{
@@
 Imagine $T=2$. 
-If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
-then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
+If 54\% and 66\% of births are boys and the likelihood of giving birth 20\% and 40\%, 
+then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$\% boys. 
 }
@@
 The ``first-born'' sex ratios illustrate the systematic recall error problem well.
-In all four surveys around 55 percent of children reported as first-born are boys
+In all four surveys around 55\% of children reported as first-born are boys
 for the first cohort of births observed.
@@
 The solid line is the sex ratio of children reported as first-born by the number of years 
-between the survey and marriage, while the dashed lines indicate the 95 percent confidence 
+between the survey and marriage, while the dashed lines indicate the 95\% confidence 
 interval and the horizontal line the natural sex ratio (approximately 0.512).
@@
 and 75th percentile birth intervals, the sex ratio, and the probability of parity
-progression by spell for urban women with no education and rural women with twelve or
+progression by spell for urban women with no education and rural women with 12 or
 more years of education, respectively.
@@
 \caption{Percentile birth intervals, sex ratios, and parity progression  
-for rural women with twelve or more years of education by spell, sex composition, and period}
+for rural women with 12 or more years of education by spell, sex composition, and period}
 \label{fig:spacing_highest_rural}
@@
 To find the average birth interval, I calculate, for each woman, the probability of 
-giving birth in each t, and her expected spell length from these probabilities. 
+giving birth in each $t$, and her expected spell length from these probabilities. 
 I then average the individual expected spell lengths across women using their parity 
@@
 \caption{Infant mortality by preceding birth interval across periods for third child of women with 
-no education and women with one to seven years of education}
+no education and women with 1--7 years of education}
 \label{fig:mortality_low_med_spell_3}
@@
 \caption{Infant mortality by preceding birth interval across periods for third child of women with 
-eight to eleven and twelve and above years of education}
+8--11 and 12 and above years of education}
 \label{fig:mortality_high_highest_spell_3}

### 2020-08-20 paper/sex_selection_spacing-ver4-demography.tex
Front-less version

--- 2020-08-20 paper/sex_selection_spacing-ver4.tex
@@
 India's Experience Over Four Decades%
-\protect\thanks{%
-I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-University of Washington, University of Aarhus, the Fourth 
-Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful 
-suggestions and comments.
-I would also like to thank Nalina Varanasi for research assistance.
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
-The views and findings expressed here are those of the author and
-should not be attributed to the World Bank or any of its member countries.
-Partial support for this research came from a Eunice Kennedy Shriver National
-Institute of Child Health and Human Development research infrastructure grant,
-5R24HD042828, to the Center for Studies in Demography and Ecology at the
-University of Washington.
-}
-}
-
-\author{Claus C P\"ortner\\
-    Department of Economics\\
-    Albers School of Business and Economics\\
-    Seattle University, P.O. Box 222000\\
-    Seattle, WA 98122\\
-    \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
-    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
-    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
-    \& \\
-    Center for Studies in Demography and Ecology \\
-    University of Washington\\ \vspace{2cm}
-    }
+% \protect\thanks{%
+% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+% I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
+% Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
+% University of Washington, University of Aarhus, the Fourth 
+% Annual Conference on Population, Reproductive Health, 
+% and Economic Development, and the Economic Demography Workshop for helpful 
+% suggestions and comments.
+% I would also like to thank Nalina Varanasi for research assistance.
+% Support for development of the method from the University of Washington Royalty 
+% Research Fund and the Development Research Group of the World Bank is gratefully 
+% acknowledged.
+% The views and findings expressed here are those of the author and
+% should not be attributed to the World Bank or any of its member countries.
+% Partial support for this research came from a Eunice Kennedy Shriver National
+% Institute of Child Health and Human Development research infrastructure grant,
+% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
+% University of Washington.
+% }
+}
+
+\author{}
+
+% \author{Claus C P\"ortner\\
+%     Department of Economics\\
+%     Albers School of Business and Economics\\
+%     Seattle University, P.O. Box 222000\\
+%     Seattle, WA 98122\\
+%     \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
+%     \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
+%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
+%     \& \\
+%     Center for Studies in Demography and Ecology \\
+%     University of Washington\\ \vspace{2cm}
+%     }
 

### 2020-09-01 paper/sex_selection_spacing-ver4.tex

@@
 I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, seminar participants at University of Copenhagen, University of Michigan, 
-University of Washington, University of Aarhus, the Fourth 
-Annual Conference on Population, Reproductive Health, 
+I owe thanks to Monica Das Gupta, Shelly Lundberg, Daniel Rees, David Ribar, 
+Hendrik Wolff, three anonymous reviewers, and seminar participants at University of 
+Copenhagen, University of Michigan, University of Washington, University of Aarhus, the 
+Fourth Annual Conference on Population, Reproductive Health, 
 and Economic Development, and the Economic Demography Workshop for helpful 
@@
 \noindent 
-In India, the most substantial lengthening in Hindu women's birth intervals over the past 
-four decades has occurred for the women most likely to use sex-selective abortions. 
-For well-educated women with two girls, the median birth interval before the third child 
-has increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
-sex ratio has approached 80\% boys. 
-Because of the rapid lengthening in spacing, standard fertility rates have significantly 
+% In India, the most substantial lengthening in Hindu women's birth intervals over the past 
+% four decades has occurred for the women most likely to use sex-selective abortions. 
+% For well-educated women with two girls, the median birth interval before the third child 
+% has increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
+% sex ratio has approached 80\% boys. 
+% Because of the rapid lengthening in spacing, standard fertility rates have significantly 
+% overestimated how fast cohort fertility fell. 
+% Despite convergence, cohort fertility is still 10\%--20\% higher than the 
+% fertility rate and above replacement level for all but the best-educated urban women. 
+% With the lengthening from sex selection, some women show a reversal of the traditional 
+% spacing pattern; instead of the shortest birth interval in the absence of sons, they now 
+% have the longest. 
+% Finally, infant mortality has declined over time for all groups, but the decline was 
+% fastest for the less educated. 
+% Short birth spacing is still associated with higher mortality, although considerably less 
+% so for the best-educated women. 
+% There is no evidence that the increasing use of sex selection is associated with higher 
+% infant mortality. 
+% Neither does it appear that the use of sex selection is declining.
+
+\noindent Over the past four decades, the Hindu women in India most likely to use 
+sex-selective abortions---well-educated women with no sons---had the most substantial 
+lengthening of birth intervals and the most biased sex ratios. 
+As a result, we now see cases that reverse the traditional spacing pattern, with some
+women with no sons having longer birth intervals than those with sons. 
+Those least likely to use sex-selective abortions---less-educated women in rural 
+areas---still follow the traditional pattern of short spacing when they have girls, with 
+only limited evidence of sex selection. 
+Because of the rapid lengthening in spacing, the standard fertility rates substantially 
 overestimated how fast cohort fertility fell. 
-Despite convergence, cohort fertility is still 10\%--20\% higher than the 
-fertility rate and above replacement level for all but the best-educated urban women. 
-With the lengthening from sex selection, some women show a reversal of the traditional 
-spacing pattern; instead of the shortest birth interval in the absence of sons, they now 
-have the longest. 
-Finally, infant mortality has declined over time for all groups, but the decline was 
-fastest for the less educated. 
+Despite a convergence, cohort fertility is still 10\%--20\% higher than the fertility rate 
+and above replacement level for all but the best-educated urban women. 
+Infant mortality has declined substantially over time for all groups, with the fastest 
+decline among the less educated. 
 Short birth spacing is still associated with higher mortality, although considerably less 
 so for the best-educated women. 
-There is no evidence that the increasing use of sex selection is associated with higher 
-infant mortality. 
-Neither does it appear that the use of sex selection is declining.
+There is no evidence that repeated sex-selective abortions are associated with higher 
+infant mortality for the child eventually born. 
+Finally, it does not appear that the use of sex selection is declining.
 
@@
 abortions because the short duration between pregnancies could increase mortality. 
-Nevertheless, there has been no attempt to examine how infant mortality has changed with 
-the increase in sex selection.
+% Nevertheless, there has been no attempt to examine how infant mortality has changed with 
+% the increase in sex selection.
 
@@
 birth intervals. 
-There is no evidence that the increasing use of sex selection is associated with higher mortality.
+There is no evidence that repeated sex-selective abortions are associated with higher 
+mortality for the child eventually born.
 
@@
 % Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
-There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2016}.
+There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2019}.
 }
@@
 The raw numbers for women with the most uneven sex ratio also suggest that even with 
-very high use of sex selection, there is no impact on child mortality. 
+very high use of sex selection, there is no impact on mortality. 
 A total of 1,004 women with 12 or more years of education and no boys at the start of 
@@
 small for the best-educated women.
-There is no evidence that substantial use of sex selection is associated with higher 
-infant mortality.
+There is no evidence that repeated abortions are associated with higher infant mortality 
+for the child eventually born.
 
 % Implications 
-An important implication of the results here is that population growth in India may
-not have fallen as much as recently suggested.
-There has been a rapid reduction in infant mortality risk, the longer birth spacing should 
-further reduce mortality risk, and cohort fertility is higher than previously realized.
+The results here paint a less rosy picture of India's prospects for a continued reduction 
+in population growth than generally accepted. 
+With predicted cohort fertility still substantially higher than the fertility rate, 
+India's total fertility rate will likely stabilize or even increase as birth intervals slow 
+their lengthening. 
+The more successful the attempts at combatting sex selection are, the more likely an 
+increase in the total fertility rate will be. 
+Furthermore, the rapid decline in infant mortality risk, combined with likely future 
+declines as the proportion of very short birth intervals falls, may also slow the 
+reduction in population growth.
 
@@
 Hence, better health outcomes for girls with sex selection could be an unintended 
-side-effect, rather than the result of girls becoming more valued as is often assumed. 
+side-effect, rather than the result of girls becoming more valued as is often 
+assumed \citep{Hu2015}. 
 Comparing prior children's outcomes across sex composition and the sex of the next child 

### 2020-11-18 paper/2020-10-revision-background.tex
Flesh out economic theory and child outcome sections
- Instead of fertility as separate influence use it to introduce the other three theories
- move to new extension

This section provides a conceptual framework for understanding how birth spacing changes
and guiding the subsequent analysis.
In non-Western countries, lower fertility is associated with longer birth spacing, but 
outside a ``natural fertility'' regime it is not clear that lower fertility necessarily 
leads to longer spacing \citet{Newman1988,Rutstein2011,Casterline2016}.
Thus, I first introduce three theories that link fertility and birth spacing decisions
through economic conditions, desired child outcomes, and son preference \citep{Casterline2016,Portner2018}.
Next, I argue that female education and area of residence are the most important factors 
to consider in the empirical analysis and discuss how they tie into the three theories.
Finally, I describe how female education, together with female labor force participation, 
have changed over time in India and how these changes affect the predictions for how birth 
spacing has changed.

The dramatic improvements in economic conditions in India is best illustrated by the 
doubling of real wages between 1987 and 2011 \citep{Klasen2015}.
Economic theory predicts that the effect of higher wages on fertility is determined by 
the relative strengths of the substitution and income effects.
The substitute effect captures that as a good becomes more expensive relative to other
goods, people substitute away from the now more expensive good and towards other goods.
With higher wages, the substitute effect predicts that people work more and spend less 
time on other time-intensive non-wage earning activities, such as children or leisure.
The income effect captures that even if we ignore the substitution effect and hold hours 
worked constant higher wages increase the available income. 
This positive income effect leads people to spend more time on time-intensive activities 
such as children and leisure and less time working.

Empirically, higher female wages generally lowers fertility, whereas higher male 
wages increases fertility \citet{Hotz1997,schultz97}.
This pattern is consistent with women spending substantially more time on child care 
than men, leading to the substitution effect dominating for women while the income
effect dominates for men.

In addition to lowering fertility, higher female wages will tend to shorten spacing between 
children if having children requires the mother to reduce her economic activities.
Specifically, shortening birth spacing allows parents to take advantage of economies of 
scale in childrearing---for example, looking after two children simultaneously requires 
less than double the time needed to look after one child \citep{Vijverberg1982,Hotz1997}.
The reduction in the length of birth intervals from higher female wages will be more 
pronounced the more women participate in the labor force rather than working at home as 
economic activities at home are more compatible with child rearing.

[bla, bla]
The effect of increasing male wages on birth spacing is ambiguous.
On one hand, if fertility increases one might expect spacing to become shorter, although 
unless the updated desired fertility is close to natural fertility the higher desired 
fertility could simply be accommodated by having the last child later in life.
On the other hand, higher income could ``purchase'' both higher fertility and 
better quality children.
If child quality is increasing in birth spacing we would then expect higher male wages
to lead to longer birth spacing.

Parents care not only about how many children they have but also about the outcomes
for the children, and, everything else equal, more children means less resources to invest 
per child.
Hence, with declining fertility we should see better child outcomes such as lower 
mortality and more schooling.
However, with increasing income, it is, in principle, possible to have both more
children and better outcomes for them.
Increasing returns to education might make the parents reduce fertility and invest 
more in each of the children's education \citep{Rosenzweig1982a}.

Longer spacing between births is generally expected to have positive effects on 
child outcomes.
The clearest example of birth spacing affecting child outcomes is for health,
where very short spacing---approximately 24 months or less---leads to worse health 
and mortality outcomes for children 
\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
More speculative is whether the increased individual parental attention per child that 
should arise from longer spacing results in better human capital outcome for children 
\citep{Zajonc1975,Zajonc1976,Razin1980}.
The evidence on spacing's effect on child quality measures such as IQ and education is 
mixed for developed countries and nonexisting for developing countries
\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.

Finally, as mentioned above, the stronger the son preference, the more likely we are to
see short spacing, and the associated worse health outcomes, when there are no sons 
in the household 
\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.

The introduction of sex selection allows parents to avoid giving birth to girls but 
increases the expected interval to the next birth by 6--12 months.
The increase consists of three parts. 
First, after an abortion, the uterus needs at least two menstrual cycles to recover, 
or the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
Second, the waiting time to conception is one to six months. 
Finally, sex determination tests are reliable only from three months of gestation. 
Theory suggests that sex selection increases with lower desired fertility and with
higher parity for a given desired number of children \citep{Portner2015b}.

[move to the prediction part?]
In India, real wages for both men and women have almost doubled between 1987 and 
2011, although the mean male wage is still close to 70\% higher than the female wage 
\citep{Klasen2015,Bhargava2018}.

### 2020-11-29 paper/2020-10-revision-background.tex
Theories section drafted

@@
 leads to longer spacing \citet{Newman1988,Rutstein2011,Casterline2016}.
-Thus, I first introduce three theories that link fertility and birth spacing decisions
-through economic conditions, desired child outcomes, and son preference \citep{Casterline2016,Portner2018}.
+Thus, I first introduce three potential explanations that link fertility and birth 
+spacing decisions: economic conditions, desired child outcomes, and son preference 
+\citep{Casterline2016,Portner2018}.
 Next, I argue that female education and area of residence are the most important factors 
@@
 Longer spacing between births is generally expected to have positive effects on 
-child outcomes.
+child outcomes and if fertility falls because of increased desired for better child
+outcomes we would, therefore, also expect spacing to increase.
 The clearest example of birth spacing affecting child outcomes is for health,
@@
 
-Finally, as mentioned above, the stronger the son preference, the more likely we are to
-see short spacing, and the associated worse health outcomes, when there are no sons 
-in the household 
+Empirically, son preference has only a minor effect on overall fertility, but does impact 
+the sex composition within families through differential stopping behavior 
+\citet{repetto72,leung94,clark00,Basu2010,Barcellos2014}. 
+Furthermore, as mentioned above, stronger son preference leads to shorter spacing and the 
+associated worse health outcomes for daughters when there are no sons in the household 
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
 
-The introduction of sex selection allows parents to avoid giving birth to girls but 
-increases the expected interval to the next birth by 6--12 months.
-The increase consists of three parts. 
+The use of sex selection allows parents to avoid giving birth to a girl but each
+abortion increases the expected interval to the next birth by 6--12 months.
+This increase consists of three parts. 
 First, after an abortion, the uterus needs at least two menstrual cycles to recover, 
@@
 Finally, sex determination tests are reliable only from three months of gestation.
-Theory suggests that sex selection increases with lower desired fertility and with
-higher parity for a given desired number of children \citep{Portner2015b}.
+
+Holding son preference constant, lower desired fertility increases the use of sex 
+selection, suggesting that the first order effect of higher female wages is to increase 
+sex selection because of the fertility effect discussed above \citep{Portner2015b,Jayachandran2017}.  
+Furthermore, for a given desired number of children, the higher the parity the more 
+likely the use of sex selection if the desired number of sons has not been reached.
+
+% Factors/predictions
+
+% Descriptive
 

### 2020-11-30 paper/2020-10-revision-background.tex
Introduce female education and associated effects

@@
 sex selection because of the fertility effect discussed above \citep{Portner2015b,Jayachandran2017}.  
-Furthermore, for a given desired number of children, the higher the parity the more 
-likely the use of sex selection if the desired number of sons has not been reached.
+Furthermore, the higher the parity the more likely the use of sex selection if the 
+desired number of sons has not been reached.
+[cost of sex selection?]
 
 % Factors/predictions
+An important issue is how to operationalize the potential explanations of how 
+birth spacing has changed over time.
+Although the explanations are based on changes in wages, mortality risk, degree of son 
+preference, and access to and cost of sex selection, none of these are available for the 
+period when the decisions of interest were made.
+
+Two characteristics that are available in data and that have been shown to be associated 
+with fertility, child outcomes, and the use of sex selection are female education and 
+area of residence.
+[citations?]
+The problem is that both have multiple pathways through which they can affect fertility,
+birth spacing, and sex selection and that these do not necessarily line up neatly with the
+theories above.
+
+Families in urban areas are likely to have fewer children and higher rates of sex 
+selection and, therefore, increasingly longer birth intervals over time compared to
+rural families.
+With the costs of children higher in urban than in rural areas both because of the
+lower opportunities for productive work of children and the higher cost of consumption
+related to children, fertility is expected to be lower in urban than in rural areas.
+Furthermore, access to health care and generally a healthier environment because of,
+for example, cleaner water means that urban parents can have fewer children and invest
+more in each than in rural areas.%
+\footnote{
+However, holding parental education constant, there is evidence that children in
+Indian slums do worse than they would have in rural areas \citep{Portner2018a}.
+}
+However, the better access to health care also means that there is easier access to
+sex selection and the generally higher income of urban households makes it more
+affordable.
+[differences in birth intervals without sex selection?]
+
+Wages are generally increasing in education suggesting that with higher female education
+we should see shorter birth spacing and lower fertility, but also higher use of sex 
+selection.
+However, female education undoubtedly represents more than the value of their time.
+Two examples are child health and the production of offspring human capital.
+
+First, children of more educated women tend to have better health outcomes and
+lower mortality than less educated women, which may come from higher income, but could
+also be a result of better health knowledge 
+\citep{Rosenzweig1982a,Kovsted2002,Whitworth2002,Maitra2008}.
+Lower expected mortality means that fewer births are required to reach the desired
+number of surviving children.
+Similarly, although short birth spacing generally leads to worse health outcomes, 
+the more educated the mother, the more muted this relationship is, which, at least partly,
+removes the health outcome incentive for longer birth spacing
+\citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
+
+Second, more educated women are more efficient at producing child human capital 
+\citep{Behrman1999}.
+Hence, families that value sons' education more will both tend to demand better-educated
+women as mothers and to have fewer children because both allow for higher quality boys.
+With the increasing return to male education that India has experienced, this imply
+that there will be an increased demand for better-educated women combined with lower 
+fertility, and an increased use of sex selection when available.
+In this case, the associations between higher female education, lower fertility, and more
+sex selection are not a causal effect driven by higher wages but instead the result of the 
+increased return to male education.
 

### 2020-12-01 paper/2020-10-revision-background.tex
First complete draft of conceptual framework

@@
 to consider in the empirical analysis and discuss how they tie into the three theories.
-Finally, I describe how female education, together with female labor force participation, 
-have changed over time in India and how these changes affect the predictions for how birth 
-spacing has changed.
 
@@
 selection, suggesting that the first order effect of higher female wages is to increase 
-sex selection because of the fertility effect discussed above \citep{Portner2015b,Jayachandran2017}.  
+sex selection because of the fertility effect discussed above 
+\citep{Portner2015b,Jayachandran2017}.  
 Furthermore, the higher the parity the more likely the use of sex selection if the 
@@
 % Factors/predictions
-An important issue is how to operationalize the potential explanations of how 
-birth spacing has changed over time.
-Although the explanations are based on changes in wages, mortality risk, degree of son 
-preference, and access to and cost of sex selection, none of these are available for the 
-period when the decisions of interest were made.
+Female education and area of residence are the two principal explanatory variables I use
+in the empirical analyses.
+The main reason is that female education and area of residence are the closest proxies in 
+the data for wages and access to and cost of sex selection, none of which are available.
+In addition, both higher female education and urbanization are associated with lower 
+fertility and increased use of sex selection in past research
+\citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
 
-Two characteristics that are available in data and that have been shown to be associated 
-with fertility, child outcomes, and the use of sex selection are female education and 
-area of residence.
-[citations?]
-The problem is that both have multiple pathways through which they can affect fertility,
-birth spacing, and sex selection and that these do not necessarily line up neatly with the
-theories above.
+Finally, India has seen tremendous increases in both education and urbanization.
+The proportion of the population living in urban areas almost doubled from 18\%
+in 1960 to 35\% in 2019 \citep{United-Nations2019}.
+Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
+cohort for urban and rural women, 20 years or older, whether married or not, in the 
+four rounds of the NFHS.
+Female education has increased substantially in both rural and urban areas,
+but is still considerably higher in urban than in rural areas.
+In rural areas, women with eight or more years of education have gone from almost zero for 
+the 1930 cohort to more than 60\% for the 1990s cohorts, with about half in the 8--11 
+group and the other half in the 12 plus group.
+In urban areas, most of the increase in urban female education came from the 12 plus 
+group, which now accounts for more than half of all urban women for the most recent cohorts.
+
+\begin{figure}[htpb]
+\centering
+\subfloat[Rural]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_rural}
+    \end{minipage}
+} 
+\subfloat[Urban]{
+    \begin{minipage}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{educ_over_time_urban} 
+    \end{minipage}
+}
+\caption{Distribution of education by cohort for women 20 years or older at survey}
+\label{fig:education_over_time}
+\end{figure}
 
@@
 
-Wages are generally increasing in education suggesting that with higher female education
-we should see shorter birth spacing and lower fertility, but also higher use of sex 
+Wages generally increase with education suggesting that higher female education
+should shorten birth spacing and lower fertility, but also increase the use of sex 
 selection.
-However, female education undoubtedly represents more than the value of their time.
-Two examples are child health and the production of offspring human capital.
+However, female education undoubtedly represents more than the value of women's time.
+Two examples are the productions of child health and offspring human capital.
+[something on norms?]
 
-First, children of more educated women tend to have better health outcomes and
-lower mortality than less educated women, which may come from higher income, but could
-also be a result of better health knowledge 
+First, children of more educated women tend to have better health outcomes and lower 
+mortality than less educated women, either from higher income or better health knowledge 
 \citep{Rosenzweig1982a,Kovsted2002,Whitworth2002,Maitra2008}.
-Lower expected mortality means that fewer births are required to reach the desired
+Lower expected mortality means that fewer births are required to reach a desired
 number of surviving children.
@@
 
-Second, more educated women are more efficient at producing child human capital 
+Second, better-educated women are more efficient at producing child human capital 
 \citep{Behrman1999}.
-Hence, families that value sons' education more will both tend to demand better-educated
-women as mothers and to have fewer children because both allow for higher quality boys.
+[need something on son preference? Maybe simply use increasing returns to male education]
+Hence, families that value sons' education more will tend to both demand better-educated
+women as mothers and have fewer children because both allow for higher quality boys.
 With the increasing return to male education that India has experienced, this imply
-that there will be an increased demand for better-educated women combined with lower 
-fertility, and an increased use of sex selection when available.
+an increased demand for better-educated women combined with lower fertility, and an 
+increased use of sex selection when available.
 In this case, the associations between higher female education, lower fertility, and more
@@
 
-% Descriptive
+Even as the level of female education has increased, the female labor force 
+participation in both urban and rural areas has stagnated or decreased
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
+India's female labor force participation is now one of the lowest in the world  
+and does not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
+In line with previous research, the NFHS data show a U-shaped relationship between 
+education and working for married women, with the highest percentage working being women 
+with either no education or 12 or more years and the lowest being women with 8--11 years 
+of education.%
+\footnote{
+See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
+}
 
-[move to the prediction part?]
-In India, real wages for both men and women have almost doubled between 1987 and 
-2011, although the mean male wage is still close to 70\% higher than the female wage 
+The low and declining female labor force participation, especially for younger women, 
+suggests that families face little incentive to space children more closely 
+together for economic reasons.
+One explanation is that household income has increased so substantially that the income 
+effect dominates any substitution effect.
+Two findings speak to this effect.
+First, although real wages for both men and women have almost doubled between 1987 and 
+2011, the mean male wage is still close to 70\% higher than the female wage 
 \citep{Klasen2015,Bhargava2018}.
+Second, women’s labor supply appears to be more negatively elastic to husbands' 
+wages than positively elastic to their own wages \citep{Bhargava2018}.
+
+% Sanskritization
+
+The increases in female educational attainment imply that access to education has 
+expanded beyond the higher castes. 
+One possible effect of the associated change in the composition of better-educated women 
+is that this group's behavior would change.
+However, ``Sanskritization'' implies that as lower-castes females gain access to 
+education and their husbands' income increases, they adopt higher-caste 
+norms such as stronger son preference and a retraction from the formal labor 
+market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
+The low and declining female labor force participation suggests that this process still operates.
+
+% Summary / hypotheses
+
+In summary, with substantial increases in husbands' income and a declining female labor 
+force participation, I expect a push toward longer birth spacing over time, independent
+of education levels, based on the income effects and the effects of spacing
+on child outcomes.
+Furthermore, I expect birth spacing to increase the most among the better educated 
+because their household income increases the most---even with declining female labor 
+participation---and because of their use of sex selection.
+Even with the substantial increase in the number of better-educated women, 
+"Sanskritization" implies that the changing composition will not substantially change 
+the use of sex selection.

### 2020-12-02 paper/2020-10-revision-background.tex
Draft version of conceptual framework

@@
 economic activities at home are more compatible with child rearing.
-
-[bla, bla]
-The effect of increasing male wages on birth spacing is ambiguous.
-On one hand, if fertility increases one might expect spacing to become shorter, although 
-unless the updated desired fertility is close to natural fertility the higher desired 
-fertility could simply be accommodated by having the last child later in life.
-On the other hand, higher income could ``purchase'' both higher fertility and 
-better quality children.
-If child quality is increasing in birth spacing we would then expect higher male wages
-to lead to longer birth spacing.
 

### 2020-12-02 paper/sex_selection_spacing-ver5.tex
Initial commit of version 5 of paper
Draft version of conceptual framework

--- 2020-09-01 paper/sex_selection_spacing-ver4.tex
@@
     \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
-    \href{mailto:claus@clausportner.com}{\texttt{claus@clausportner.com}}\\
     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
@@
 
-\date{August 2020}
+\date{December 2020}
 
@@
 
-\section{Background and Conceptual Framework}
-
-To set the stage for the subsequent analyses and provide a conceptual framework for 
-understanding birth spacing, I first discuss female education and labor force 
-participation in India and relevant theories on birth spacing.
-
-% [Female education]
-
-Female education is a crucial explanatory variable here for three reasons.
-First, higher female education is associated with lower fertility and increased use of 
-sex selection
+\section{Conceptual Framework}
+
+This section provides a conceptual framework for understanding how birth spacing changes
+and guiding the subsequent analysis.
+In non-Western countries, lower fertility is associated with longer birth spacing, but 
+outside a ``natural fertility'' regime it is not clear that lower fertility necessarily 
+leads to longer spacing \citep{Newman1988,Rutstein2011,Casterline2016}.
+Thus, I first introduce three potential explanations that link fertility and birth 
+spacing decisions: economic conditions, desired child outcomes, and son preference 
+\citep{Casterline2016,Portner2018}.
+Next, I argue that female education and area of residence are the most important factors 
+to consider in the empirical analysis and discuss how they tie into the three theories.
+
+The dramatic improvements in economic conditions in India is best illustrated by the 
+doubling of real wages between 1987 and 2011 \citep{Klasen2015}.
+Economic theory predicts that the effect of higher wages on fertility is determined by 
+the relative strengths of the substitution and income effects.
+The substitute effect captures that as a good becomes more expensive relative to other
+goods, people substitute away from the now more expensive good and towards other goods.
+With higher wages, the substitute effect predicts that people work more and spend less 
+time on other time-intensive non-wage earning activities, such as children or leisure.
+The income effect captures that even if we ignore the substitution effect and hold hours 
+worked constant higher wages increase the available income. 
+This positive income effect leads people to spend more time on time-intensive activities 
+such as children and leisure and less time working.
+
+Empirically, higher female wages generally lowers fertility, whereas higher male 
+wages increases fertility \citep{Hotz1997,schultz97}.
+This pattern is consistent with women spending substantially more time on child care 
+than men, leading to the substitution effect dominating for women while the income
+effect dominates for men.
+
+In addition to lowering fertility, higher female wages will tend to shorten spacing between 
+children if having children requires the mother to reduce her economic activities.
+Specifically, shortening birth spacing allows parents to take advantage of economies of 
+scale in childrearing---for example, looking after two children simultaneously requires 
+less than double the time needed to look after one child \citep{Vijverberg1982,Hotz1997}.
+The reduction in the length of birth intervals from higher female wages will be more 
+pronounced the more women participate in the labor force rather than working at home as 
+economic activities at home are more compatible with child rearing.
+
+Parents care not only about how many children they have but also about the outcomes
+for the children, and, everything else equal, more children means less resources to invest 
+per child.
+Hence, with declining fertility we should see better child outcomes such as lower 
+mortality and more schooling.
+However, with increasing income, it is, in principle, possible to have both more
+children and better outcomes for them.
+Increasing returns to education might make the parents reduce fertility and invest 
+more in each of the children's education \citep{Rosenzweig1982a}.
+
+Longer spacing between births is generally expected to have positive effects on 
+child outcomes and if fertility falls because of increased desired for better child
+outcomes we would, therefore, also expect spacing to increase.
+The clearest example of birth spacing affecting child outcomes is for health,
+where very short spacing---approximately 24 months or less---leads to worse health 
+and mortality outcomes for children 
+\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
+More speculative is whether the increased individual parental attention per child that 
+should arise from longer spacing results in better human capital outcome for children 
+\citep{Zajonc1975,Zajonc1976,Razin1980}.
+The evidence on spacing's effect on child quality measures such as IQ and education is 
+mixed for developed countries and nonexisting for developing countries
+\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
+
+Empirically, son preference has only a minor effect on overall fertility, but does impact 
+the sex composition within families through differential stopping behavior 
+\citep{repetto72,leung94,clark00,Basu2010,Barcellos2014}. 
+Furthermore, as mentioned above, stronger son preference leads to shorter spacing and the 
+associated worse health outcomes for daughters when there are no sons in the household 
+\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
+
+The use of sex selection allows parents to avoid giving birth to a girl but each
+abortion increases the expected interval to the next birth by 6--12 months.
+This increase consists of three parts. 
+First, after an abortion, the uterus needs at least two menstrual cycles to recover, 
+or the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
+Second, the waiting time to conception is one to six months. 
+Finally, sex determination tests are reliable only from three months of gestation.
+
+Holding son preference constant, lower desired fertility increases the use of sex 
+selection, suggesting that the first order effect of higher female wages is to increase 
+sex selection because of the fertility effect discussed above 
+\citep{Portner2015b,Jayachandran2017}.  
+Furthermore, the higher the parity the more likely the use of sex selection if the 
+desired number of sons has not been reached.
+[cost of sex selection?]
+
+% Factors/predictions
+Female education and area of residence are the two principal explanatory variables I use
+in the empirical analyses.
+The main reason is that female education and area of residence are the closest proxies in 
+the data for wages and access to and cost of sex selection, none of which are available.
+In addition, both higher female education and urbanization are associated with lower 
+fertility and increased use of sex selection in past research
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Second, female labor force participation in India, as in other developing countries, 
-first decreases and then increases with education
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-Finally, child mortality decreases with maternal education
-\citep{Rosenzweig1982a,Whitworth2002,Maitra2008}.
-
-% [TK where to put son preference discussion?]
-% %
-% \footnote{
-% It is also possible that the effect is driven by a stronger son preference, although 
-% higher education women have shown declining son preference \citep{bhat03,pande07}.
-% }
-
-I divide education levels into four groups: No education, 1--7 years, 8--11 years, and 
-12 and more years.
-The latter two correspond to having completed primary and secondary school, 
-respectively.%
-\footnote{
-Although there are variations by state, elementary education in India consists of a 
-primary school covering grades one through five and an upper primary---or middle 
-school---covering grades six through eight. 
-Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
-and 11 and 12 for ``upper secondary.''
-}
-To ensure that the results are comparable with the prior literature on fertility
-and mortality in India, I follow the NFHS reports, except that I combine the 
-less than five years and 5--7 years of schooling completed and the 8--9 
-and 10--11 years of schooling completed.
-This grouping allows me to capture the differences across education levels discussed below, 
-while also having groups large enough for the empirical method.
-
-% [what has happened to education]
-Female education has increased substantially over time in rural and urban areas but 
-is still substantially higher in urban than in rural areas.
+
+Finally, India has seen tremendous increases in both education and urbanization.
+The proportion of the population living in urban areas almost doubled from 18\%
+in 1960 to 35\% in 2019 \citep{United-Nations2019}.
 Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
-cohort for urban and rural women, 
-20 years or older, whether married or not, based on the four rounds of the NFHS.
-In rural areas, women with no education have gone from 90\% for the 1930s cohorts to 
-less than 20\% for the 1990s cohorts.
-Women with eight or more years of education have gone from almost zero for the 1930 cohort 
-to more than 60\% for the 1990s cohorts, with about half in the 8--11 group and the 
-other half in the 12 plus group.
-In urban areas, the proportions with no education or 1--7 years have each declined 
-to just below 10\%.
-Most of the increase in urban female education came from the 12 plus group, which 
-now accounts for more than half of all urban women for the most recent cohorts.
+cohort for urban and rural women, 20 years or older, whether married or not, in the 
+four rounds of the NFHS.
+Female education has increased substantially in both rural and urban areas,
+but is still considerably higher in urban than in rural areas.
+In rural areas, women with eight or more years of education have gone from almost zero for 
+the 1930 cohort to more than 60\% for the 1990s cohorts, with about half in the 8--11 
+group and the other half in the 12 plus group.
+In urban areas, most of the increase in urban female education came from the 12 plus 
+group, which now accounts for more than half of all urban women for the most recent cohorts.
 
@@
 
-% [female labor force participation]
-
-The standard economic argument for shorter spacing with increasing female education 
-is that parents incur time costs when they have children \citep{Hotz1997,schultz97}.
-Suppose having children requires the mother to reduce her market work. 
-Parents can then lower this cost of children by shortening birth spacing to take advantage 
-of economies of scale in childrearing  \citep{Vijverberg1982}.
-
-However, even as the level of female education has increased, the female labor force 
+Families in urban areas are likely to have fewer children and higher rates of sex 
+selection and, therefore, increasingly longer birth intervals over time compared to
+rural families.
+With the costs of children higher in urban than in rural areas both because of the
+lower opportunities for productive work of children and the higher cost of consumption
+related to children, fertility is expected to be lower in urban than in rural areas.
+Furthermore, access to health care and generally a healthier environment because of,
+for example, cleaner water means that urban parents can have fewer children and invest
+more in each than in rural areas.%
+\footnote{
+However, holding parental education constant, there is evidence that children in
+Indian slums do worse than they would have in rural areas \citep{Portner2018a}.
+}
+However, the better access to health care also means that there is easier access to
+sex selection and the generally higher income of urban households makes it more
+affordable.
+[differences in birth intervals without sex selection?]
+
+Wages generally increase with education suggesting that higher female education
+should shorten birth spacing and lower fertility, but also increase the use of sex 
+selection.
+However, female education undoubtedly represents more than the value of women's time.
+Two examples are the productions of child health and offspring human capital.
+[something on norms?]
+
+First, children of more educated women tend to have better health outcomes and lower 
+mortality than less educated women, either from higher income or better health knowledge 
+\citep{Rosenzweig1982a,Kovsted2002,Whitworth2002,Maitra2008}.
+Lower expected mortality means that fewer births are required to reach a desired
+number of surviving children.
+Similarly, although short birth spacing generally leads to worse health outcomes, 
+the more educated the mother, the more muted this relationship is, which, at least partly,
+removes the health outcome incentive for longer birth spacing
+\citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
+
+Second, better-educated women are more efficient at producing child human capital 
+\citep{Behrman1999}.
+[need something on son preference? Maybe simply use increasing returns to male education]
+Hence, families that value sons' education more will tend to both demand better-educated
+women as mothers and have fewer children because both allow for higher quality boys.
+With the increasing return to male education that India has experienced, this imply
+an increased demand for better-educated women combined with lower fertility, and an 
+increased use of sex selection when available.
+In this case, the associations between higher female education, lower fertility, and more
+sex selection are not a causal effect driven by higher wages but instead the result of the 
+increased return to male education.
+
+Even as the level of female education has increased, the female labor force 
 participation in both urban and rural areas has stagnated or decreased
 \citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-India's female labor force participation is now lower than that of most other countries and does 
-not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
+India's female labor force participation is now one of the lowest in the world  
+and does not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
 In line with previous research, the NFHS data show a U-shaped relationship between 
-education and working for married women, with the highest percentage working being women with 
-either no education or 12 or more years and the lowest being women with 8--11 years of education.%
+education and working for married women, with the highest percentage working being women 
+with either no education or 12 or more years and the lowest being women with 8--11 years 
+of education.%
 \footnote{
@@
 wages than positively elastic to their own wages \citep{Bhargava2018}.
-
-% [sex selection]
-
-The introduction of sex selection allows parents to avoid giving birth to girls but 
-increases the expected interval to the next birth.
-Theory suggests that sex selection increases with lower desired fertility and with
-higher parity for a given desired number of children \citep{Portner2015b}.
-Sex selection is more widespread among better-educated than less-educated and among urban 
-than rural women, which is consistent with lower desired fertility increasing the
-use of sex selection 
-\citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Better-educated and urban women also tend to live in households with higher income, which 
-lowers the relative costs of using sex selection and having long birth intervals.
-
-The combination of rising incomes and continued son preference may lead to even longer 
-spacing than might be expected from the income effect alone.
-As women's education increases, their productivity in the production of offspring human 
-capital also increases.
-With relatively more boys born because of increased access to sex-selective 
-abortions and the increasing income potential for (male) offspring, demand for 
-better-educated women can increase, even if they do not participate in the labor market 
-\citep{Behrman1999}.
-
-If more and ``better'' parental attention per child results in higher child ``quality,'' 
-we should expect longer birth intervals \citep{Zajonc1975,Zajonc1976,Razin1980}.
-However, the evidence on spacing's effect on child quality measures such as IQ 
-and education is mixed for developed countries and nonexisting for developing countries
-\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-The exception is health and mortality, where longer spacing does lead to better outcomes, 
-although this relationship weakens with maternal education 
-\citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
-
-% If parents realize that longer spacing leads to better child outcomes, we may even observe 
-% later conception, especially when, with sex selection, the next child is likely to be a boy.
-% Working in the opposite direction of this "delay" effect is that women with more education 
-% can, in principle, space their children closer together without substantially increasing 
-% child mortality risk. 
-% However, given the apparent lack of pressure to return to the labor force, this effect is 
-% likely small.
 

### 2020-12-02 paper/2020-10-revision-background.tex
First go at shorten

@@
 and guiding the subsequent analysis.
-In non-Western countries, lower fertility is associated with longer birth spacing, but 
-outside a ``natural fertility'' regime it is not clear that lower fertility necessarily 
-leads to longer spacing \citet{Newman1988,Rutstein2011,Casterline2016}.
-Thus, I first introduce three potential explanations that link fertility and birth 
+I first introduce three potential explanations that link fertility and birth 
 spacing decisions: economic conditions, desired child outcomes, and son preference 
@@
 
-The dramatic improvements in economic conditions in India is best illustrated by the 
+% Economic conditions
+The dramatic improvements in economic conditions in India are best illustrated by the 
 doubling of real wages between 1987 and 2011 \citep{Klasen2015}.
@@
 the relative strengths of the substitution and income effects.
-The substitute effect captures that as a good becomes more expensive relative to other
-goods, people substitute away from the now more expensive good and towards other goods.
-With higher wages, the substitute effect predicts that people work more and spend less 
-time on other time-intensive non-wage earning activities, such as children or leisure.
-The income effect captures that even if we ignore the substitution effect and hold hours 
-worked constant higher wages increase the available income. 
+The substitute effect captures that as a good becomes more expensive, people substitute 
+away from that good and towards other goods.
+With higher wages, this means that people work more and spend less time on non-wage 
+earning activities, such as children or leisure.
+The income effect captures that, holding hours worked constant, higher wages increase the 
+available income. 
 This positive income effect leads people to spend more time on time-intensive activities 
@@
 This pattern is consistent with women spending substantially more time on child care 
-than men, leading to the substitution effect dominating for women while the income
+than men, leading to the substitution effect dominating for women whereas the income
 effect dominates for men.
 
-In addition to lowering fertility, higher female wages will tend to shorten spacing between 
-children if having children requires the mother to reduce her economic activities.
+In addition to lowering fertility, higher female wages will tend to shorten birth spacing 
+if having children requires the mother to reduce her economic activities.
 Specifically, shortening birth spacing allows parents to take advantage of economies of 
@@
 
+% Child outcomes
 Parents care not only about how many children they have but also about the outcomes
-for the children, and, everything else equal, more children means less resources to invest 
-per child.
-Hence, with declining fertility we should see better child outcomes such as lower 
-mortality and more schooling.
-However, with increasing income, it is, in principle, possible to have both more
-children and better outcomes for them.
-Increasing returns to education might make the parents reduce fertility and invest 
-more in each of the children's education \citep{Rosenzweig1982a}.
+for the children, and, everything else equal, more children means fewer resources to 
+invest per child.
+Hence, increasing returns to education provides parents with an incentive to reduce 
+fertility and invest more in each of the children's education \citep{Rosenzweig1982a}.
+Furthermore, lower expected mortality means that fewer births are required to reach a 
+desired number of surviving children and allow parents to invest more in each child.
 
@@
 child outcomes and if fertility falls because of increased desired for better child
-outcomes we would, therefore, also expect spacing to increase.
+outcomes we would also expect spacing to increase.
 The clearest example of birth spacing affecting child outcomes is for health,
@@
 and mortality outcomes for children 
-\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012,Molitoris2019}.
-More speculative is whether the increased individual parental attention per child that 
-should arise from longer spacing results in better human capital outcome for children 
-\citep{Zajonc1975,Zajonc1976,Razin1980}.
-The evidence on spacing's effect on child quality measures such as IQ and education is 
-mixed for developed countries and nonexisting for developing countries
-\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
+\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012}.
+Whether longer spacing results in increased parental attention per child and better 
+human capital outcome is unclear as the evidence is mixed for developed countries and 
+nonexistent for developing countries
+\citep{Zajonc1975,Zajonc1976,Razin1980,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
 
-Empirically, son preference has only a minor effect on overall fertility, but does impact 
-the sex composition within families through differential stopping behavior 
+% Son preference 
+Empirically, son preference has only a minor effect on average fertility, but does impact 
+the sex composition and family size within families through differential stopping behavior 
 \citet{repetto72,leung94,clark00,Basu2010,Barcellos2014}. 
-Furthermore, as mentioned above, stronger son preference leads to shorter spacing and the 
-associated worse health outcomes for daughters when there are no sons in the household 
+Furthermore, as mentioned above, stronger son preference leads to shorter spacing and  
+worse health outcomes for daughters when there are no sons in the household 
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
@@
 Holding son preference constant, lower desired fertility increases the use of sex 
-selection, suggesting that the first order effect of higher female wages is to increase 
-sex selection because of the fertility effect discussed above 
-\citep{Portner2015b,Jayachandran2017}.  
+selection \citep{Portner2015b,Jayachandran2017}.  
 Furthermore, the higher the parity the more likely the use of sex selection if the 
 desired number of sons has not been reached.
-[cost of sex selection?]
 
@@
 the data for wages and access to and cost of sex selection, none of which are available.
-In addition, both higher female education and urbanization are associated with lower 
-fertility and increased use of sex selection in past research
+In addition, earlier research show that both higher female education and urbanization are 
+associated with lower fertility and increased use of sex selection 
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-
 Finally, India has seen tremendous increases in both education and urbanization.
@@
 but is still considerably higher in urban than in rural areas.
-In rural areas, women with eight or more years of education have gone from almost zero for 
-the 1930 cohort to more than 60\% for the 1990s cohorts, with about half in the 8--11 
-group and the other half in the 12 plus group.
-In urban areas, most of the increase in urban female education came from the 12 plus 
-group, which now accounts for more than half of all urban women for the most recent cohorts.
 
@@
 Families in urban areas are likely to have fewer children and higher rates of sex 
-selection and, therefore, increasingly longer birth intervals over time compared to
-rural families.
-With the costs of children higher in urban than in rural areas both because of the
-lower opportunities for productive work of children and the higher cost of consumption
-related to children, fertility is expected to be lower in urban than in rural areas.
-Furthermore, access to health care and generally a healthier environment because of,
-for example, cleaner water means that urban parents can have fewer children and invest
-more in each than in rural areas.%
+selection 
+Two reasons fertility is lower in urban than rural areas are the higher cost of 
+children and the lower mortality risk that comes from better access to health care.%
 \footnote{
@@
 However, the better access to health care also means that there is easier access to
-sex selection and the generally higher income of urban households makes it more
-affordable.
-[differences in birth intervals without sex selection?]
+sex selection and the higher income of urban households makes it more affordable.
 
@@
 selection.
+
 However, female education undoubtedly represents more than the value of women's time.
-Two examples are the productions of child health and offspring human capital.
-[something on norms?]
+Beside propagation of low fertility norms, two examples are the productions of child 
+health and offspring human capital.
 
@@
 \citep{Rosenzweig1982a,Kovsted2002,Whitworth2002,Maitra2008}.
-Lower expected mortality means that fewer births are required to reach a desired
-number of surviving children.
-Similarly, although short birth spacing generally leads to worse health outcomes, 
-the more educated the mother, the more muted this relationship is, which, at least partly,
-removes the health outcome incentive for longer birth spacing
-\citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
+Especially of interest here is that, although short birth spacing generally leads to worse 
+health outcomes, the more educated the mother, the more muted this relationship is, which, 
+at least partly, removes the health outcome incentive for longer birth spacing
+\citep{Molitoris2019}.
 
@@
 In this case, the associations between higher female education, lower fertility, and more
-sex selection are not a causal effect driven by higher wages but instead the result of the 
-increased return to male education.
+sex selection are not a causal effect driven by higher female wages but instead the result 
+of the increased return to male education.
 
-Even as the level of female education has increased, the female labor force 
-participation in both urban and rural areas has stagnated or decreased
+Even as the level of female education has increased, the female labor force participation 
+in both urban and rural areas has stagnated or decreased and is now one of 
+the lowest in the world
 \citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-India's female labor force participation is now one of the lowest in the world  
-and does not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
 In line with previous research, the NFHS data show a U-shaped relationship between 
-education and working for married women, with the highest percentage working being women 
-with either no education or 12 or more years and the lowest being women with 8--11 years 
-of education.%
+education and working for married women, with women with either no education or 12 or more 
+years the most likely to participate in the labor force and women with 8--11 years of 
+education the least.%
 \footnote{

### 2020-12-03 paper/2020-10-revision-background.tex
Point commit before major outline changes

@@
 % Economic conditions
+
 The dramatic improvements in economic conditions in India are best illustrated by the 
@@
 % Son preference 
-Empirically, son preference has only a minor effect on average fertility, but does impact 
-the sex composition and family size within families through differential stopping behavior 
-\citet{repetto72,leung94,clark00,Basu2010,Barcellos2014}. 
+Empirically, son preference has only a minor effect on average fertility, but
+differential stopping behavior does affect the sex composition and fertility of
+individual families \citet{repetto72,leung94,clark00,Basu2010,Barcellos2014}. 
 Furthermore, as mentioned above, stronger son preference leads to shorter spacing and  
@@
 in the empirical analyses.
-The main reason is that female education and area of residence are the closest proxies in 
-the data for wages and access to and cost of sex selection, none of which are available.
+The main reason is that female education and area of residence are the closest 
+available proxies wages and the access to and cost of sex selection, none of which are 
+available in the data.
 In addition, earlier research show that both higher female education and urbanization are 
-associated with lower fertility and increased use of sex selection 
+associated with lower fertility and increased use of sex selection, and, therefore,
+likely also changes in birth spacing
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
@@
 in 1960 to 35\% in 2019 \citep{United-Nations2019}.
-Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
-cohort for urban and rural women, 20 years or older, whether married or not, in the 
-four rounds of the NFHS.
 Female education has increased substantially in both rural and urban areas,
-but is still considerably higher in urban than in rural areas.
+but is still considerably higher in urban than in rural areas, as illustrated by Figure 
+\ref{fig:education_over_time}, which shows the distribution of schooling by birth 
+cohort for all urban and rural women, 20 years or older, using the four rounds of the NFHS.
 
@@
 
-Families in urban areas are likely to have fewer children and higher rates of sex 
-selection 
-Two reasons fertility is lower in urban than rural areas are the higher cost of 
-children and the lower mortality risk that comes from better access to health care.%
+There are three reasons that families in urban areas are likely to have fewer children and 
+higher rates of sex selection. 
+First, the higher cost of children in urban than rural areas lowers fertility and 
+increases the use of sex selection.
+Second, better access to health care in urban areas lowers the mortality risk, further 
+reducing fertility.%
 \footnote{
@@
 }
-However, the better access to health care also means that there is easier access to
-sex selection and the higher income of urban households makes it more affordable.
+Finally, the better access to health care also imply easier access to sex selection and 
+the higher income of urban households makes it more affordable.
 
 Wages generally increase with education suggesting that higher female education
-should shorten birth spacing and lower fertility, but also increase the use of sex 
-selection.
+should shorten birth spacing and lower fertility, but the low and declining female labor 
+force participation, especially for younger women, suggests that families face little 
+incentive to space children more closely together for economic reasons.
+Even as the level of female education increased, the female labor force participation 
+in both urban and rural areas stagnated or decreased 
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
 
-However, female education undoubtedly represents more than the value of women's time.
+Female labor force participation does, however, still depend on education.
+In line with other countries, the NFHS data show a U-shaped relationship between 
+education and working for married women, with women with either no education or 12 or more 
+years the most likely to participate in the labor force and women with 8--11 years of 
+education the least \citep{Goldin1994,Chatterjee2018}.%
+\footnote{
+See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
+}
+
+One explanation for the low female labor force participation, especially for women
+with 8--11 years of education, is that household income has increased so substantially 
+that the income effect dominates any substitution effect.
+Two findings support this interpretation.
+First, although real wages for both men and women have almost doubled between 1987 and 
+2011, the mean male wage is still close to 70\% higher than the female wage 
+\citep{Klasen2015,Bhargava2018}.
+Second, women’s labor supply appears to be more negatively elastic to husbands' 
+wages than positively elastic to their own wages \citep{Bhargava2018}.
+
+Furthermore, female education undoubtedly represents more than the value of women's time.
 Beside propagation of low fertility norms, two examples are the productions of child 
@@
 
-First, children of more educated women tend to have better health outcomes and lower 
-mortality than less educated women, either from higher income or better health knowledge 
+First, children of more educated women have better health outcomes and lower mortality 
+than less educated women, either from higher income or better health knowledge 
 \citep{Rosenzweig1982a,Kovsted2002,Whitworth2002,Maitra2008}.
@@
 \citep{Behrman1999}.
-[need something on son preference? Maybe simply use increasing returns to male education]
-Hence, families that value sons' education more will tend to both demand better-educated
-women as mothers and have fewer children because both allow for higher quality boys.
-With the increasing return to male education that India has experienced, this imply
-an increased demand for better-educated women combined with lower fertility, and an 
-increased use of sex selection when available.
-In this case, the associations between higher female education, lower fertility, and more
-sex selection are not a causal effect driven by higher female wages but instead the result 
-of the increased return to male education.
-
-Even as the level of female education has increased, the female labor force participation 
-in both urban and rural areas has stagnated or decreased and is now one of 
-the lowest in the world
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-In line with previous research, the NFHS data show a U-shaped relationship between 
-education and working for married women, with women with either no education or 12 or more 
-years the most likely to participate in the labor force and women with 8--11 years of 
-education the least.%
-\footnote{
-See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
-}
-
-The low and declining female labor force participation, especially for younger women, 
-suggests that families face little incentive to space children more closely 
-together for economic reasons.
-One explanation is that household income has increased so substantially that the income 
-effect dominates any substitution effect.
-Two findings speak to this effect.
-First, although real wages for both men and women have almost doubled between 1987 and 
-2011, the mean male wage is still close to 70\% higher than the female wage 
-\citep{Klasen2015,Bhargava2018}.
-Second, women’s labor supply appears to be more negatively elastic to husbands' 
-wages than positively elastic to their own wages \citep{Bhargava2018}.
+Hence, the increasing return to male education may lead to an increased demand for 
+better-educated mothers, which, combined with lower fertility and an increased use
+of sex selection when available, allow families to achieve higher quality sons.
+In this explanation, the associations between higher female education, lower fertility, 
+and more sex selection are not a causal effect driven by higher female wages but instead 
+the result of the increased return to male education.
 
 % Sanskritization
-
-The increases in female educational attainment imply that access to education has 
-expanded beyond the higher castes. 
-One possible effect of the associated change in the composition of better-educated women 
-is that this group's behavior would change.
-However, ``Sanskritization'' implies that as lower-castes females gain access to 
-education and their husbands' income increases, they adopt higher-caste 
-norms such as stronger son preference and a retraction from the formal labor 
-market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
-The low and declining female labor force participation suggests that this process still operates.
+Although the expansion in female education might bring in groups with initially different 
+norms, the process of ``Sanskritization'' implies that as lower-castes females gain access 
+to education, they adopt higher-caste norms such as stronger son preference and a retraction 
+from the formal labor market \citep{Srinivas1956}.
+The low and declining female labor force participation as husbands' wages increase 
+is one indication that this process still operates \citep{Abraham2013,Chatterjee2018}.
 
@@
 participation---and because of their use of sex selection.
-Even with the substantial increase in the number of better-educated women, 
+Finally, even with the substantial increase in the number of better-educated women, 
 "Sanskritization" implies that the changing composition will not substantially change 

### 2020-12-05 paper/2020-10-revision-background.tex
Shorten version of conceptual framework

@@
 \citep{Casterline2016,Portner2018}.
-Next, I argue that female education and area of residence are the most important factors 
-to consider in the empirical analysis and discuss how they tie into the three theories.
+Next, I discuss why female education and area of residence are the principle factors 
+in the empirical analyses and how they tie into the three explanations.
 
 % Economic conditions
-
-The dramatic improvements in economic conditions in India are best illustrated by the 
-doubling of real wages between 1987 and 2011 \citep{Klasen2015}.
+The improvements in economic condition, especially the doubling of real wages,
+are likely to affect fertility although the direction is ambiguous, as, empirically, 
+higher female wages lowers fertility, whereas higher male wages increases fertility 
+\citep{Hotz1997,schultz97}.
 Economic theory predicts that the effect of higher wages on fertility is determined by 
 the relative strengths of the substitution and income effects.
-The substitute effect captures that as a good becomes more expensive, people substitute 
-away from that good and towards other goods.
-With higher wages, this means that people work more and spend less time on non-wage 
-earning activities, such as children or leisure.
-The income effect captures that, holding hours worked constant, higher wages increase the 
-available income. 
-This positive income effect leads people to spend more time on time-intensive activities 
-such as children and leisure and less time working.
+The substitute effect captures that as wages increase time becomes more expensive, and
+people therefore work more and spend less time on non-wage earning activities, such as 
+children or leisure.
+The income effect captures that higher wages increase the available income, which
+leads people to spend more time on time-intensive activities and less time working.
+Since women spend substantially more time on childrearing than men, the substitution effect 
+dominates for women but the income effect for men.
 
-Empirically, higher female wages generally lowers fertility, whereas higher male 
-wages increases fertility \citet{Hotz1997,schultz97}.
-This pattern is consistent with women spending substantially more time on child care 
-than men, leading to the substitution effect dominating for women whereas the income
-effect dominates for men.
-
-In addition to lowering fertility, higher female wages will tend to shorten birth spacing 
-if having children requires the mother to reduce her economic activities.
-Specifically, shortening birth spacing allows parents to take advantage of economies of 
-scale in childrearing---for example, looking after two children simultaneously requires 
+If having children requires the mother to curtail her economic activities, higher
+female wages, in addition to lowering fertility, will tend to shorten birth spacing.
+Shortening birth spacing allows parents to take advantage of economies of scale in 
+childrearing---for example, looking after two children simultaneously requires 
 less than double the time needed to look after one child \citep{Vijverberg1982,Hotz1997}.
-The reduction in the length of birth intervals from higher female wages will be more 
-pronounced the more women participate in the labor force rather than working at home as 
-economic activities at home are more compatible with child rearing.
 
 % Child outcomes
-Parents care not only about how many children they have but also about the outcomes
-for the children, and, everything else equal, more children means fewer resources to 
-invest per child.
-Hence, increasing returns to education provides parents with an incentive to reduce 
-fertility and invest more in each of the children's education \citep{Rosenzweig1982a}.
-Furthermore, lower expected mortality means that fewer births are required to reach a 
+Parents care both about how many children they have and their outcomes, and with 
+increasing returns to education and lower offspring mortality, parents are likely to 
+reduce fertility and invest more in each child \citep{Rosenzweig1982a,Wolpin1997}.
+The higher return to education means that parents have more of an incentive to 
+invest in their children's education, which increases the cost of children and 
+lowers fertility. 
+Lower expected mortality means that fewer births are required to reach a 
 desired number of surviving children and allow parents to invest more in each child.
@@
 and mortality outcomes for children 
-\citep{Whitworth2002,Conde-Agudelo2006,Conde-Agudelo2012}.
-Whether longer spacing results in increased parental attention per child and better 
-human capital outcome is unclear as the evidence is mixed for developed countries and 
-nonexistent for developing countries
-\citep{Zajonc1975,Zajonc1976,Razin1980,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
+\citep{Whitworth2002,Conde-Agudelo2012}.
+Whether longer spacing also results in better human capital outcome is unclear as the 
+evidence is mixed for developed countries and nonexistent for developing countries
+\citep{Zajonc1976,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
 
 % Son preference 
-Empirically, son preference has only a minor effect on average fertility, but
-differential stopping behavior does affect the sex composition and fertility of
-individual families \citet{repetto72,leung94,clark00,Basu2010,Barcellos2014}. 
-Furthermore, as mentioned above, stronger son preference leads to shorter spacing and  
-worse health outcomes for daughters when there are no sons in the household 
-\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}.
+Empirically, a stronger son preference has only a minor effect on average fertility, but
+son preference still affects the sex composition and fertility across families through 
+differential stopping behavior and leads to shorter spacing and  worse health outcomes for 
+daughters when there are no sons in the household 
+\citep{repetto72,clark00,Whitworth2002,Basu2010,Jayachandran2011,Barcellos2014}.
 
-The use of sex selection allows parents to avoid giving birth to a girl but each
-abortion increases the expected interval to the next birth by 6--12 months.
+Another result of son preference is the use of sex selection, which enables parents to 
+avoid giving birth to a girl but increases the expected interval to the next birth
+by 6--12 months for each abortion.
 This increase consists of three parts. 
@@
 
-Holding son preference constant, lower desired fertility increases the use of sex 
-selection \citep{Portner2015b,Jayachandran2017}.  
-Furthermore, the higher the parity the more likely the use of sex selection if the 
-desired number of sons has not been reached.
+The use of sex selection, and therefore the length of birth intervals, increases with
+lower desired fertility and the higher the parity provided the desired number of sons has 
+not been reached \citep{Portner2015b,Jayachandran2017}.
 
 % Factors/predictions
-Female education and area of residence are the two principal explanatory variables I use
-in the empirical analyses.
-The main reason is that female education and area of residence are the closest 
-available proxies wages and the access to and cost of sex selection, none of which are 
-available in the data.
-In addition, earlier research show that both higher female education and urbanization are 
-associated with lower fertility and increased use of sex selection, and, therefore,
-likely also changes in birth spacing
+Although the explanations above are based on economic conditions, desired child outcome,
+son preference, and the access to sex selection, none of these are available in the
+data, so I instead use female education and area of residence as the two main explanatory 
+variables in the empirical analyses.
+Female education and area of residence are the closest available proxies and earlier 
+research show that both higher female education and urbanization are associated with 
+lower fertility and increased use of sex selection, and, therefore, likely also changes 
+in birth spacing
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Finally, India has seen tremendous increases in both education and urbanization.
-The proportion of the population living in urban areas almost doubled from 18\%
-in 1960 to 35\% in 2019 \citep{United-Nations2019}.
-Female education has increased substantially in both rural and urban areas,
-but is still considerably higher in urban than in rural areas, as illustrated by Figure 
-\ref{fig:education_over_time}, which shows the distribution of schooling by birth 
-cohort for all urban and rural women, 20 years or older, using the four rounds of the NFHS.
+Furthermore, both variables are interesting given the tremendous increases in 
+both education and urbanization in India; 
+Figure \ref{fig:education_over_time} show the substantial increase in female education
+in both rural and urban areas, although it is still considerably higher in urban than in 
+rural areas and the proportion of the population living in urban areas almost doubled from 
+18\% in 1960 to 35\% in 2019 \citep{United-Nations2019}.
 
@@
 }
-\caption{Distribution of education by cohort for women 20 years or older at survey}
+\caption{Distribution of education by cohort for women 20 years or older
+using the four rounds of the NFHS}
 \label{fig:education_over_time}
@@
 
-There are three reasons that families in urban areas are likely to have fewer children and 
-higher rates of sex selection. 
-First, the higher cost of children in urban than rural areas lowers fertility and 
-increases the use of sex selection.
-Second, better access to health care in urban areas lowers the mortality risk, further 
-reducing fertility.%
+Women living in urban areas are likely to have lower fertility and higher use
+of sex selection than women in rural areas.
+The lower fertility is the result of higher cost of children and lower child mortality 
+risk in urban compared to rural areas.%
 \footnote{
@@
 }
-Finally, the better access to health care also imply easier access to sex selection and 
-the higher income of urban households makes it more affordable.
+The higher use of sex selection comes partly from the lower fertility and partly from 
+women in urban areas having higher income and better access to health care facilities.
 
-Wages generally increase with education suggesting that higher female education
-should shorten birth spacing and lower fertility, but the low and declining female labor 
-force participation, especially for younger women, suggests that families face little 
+As women receive more education their potential wages increase, which should shorten 
+birth spacing and lower fertility, but the low and declining female labor force 
+participation in India, especially for younger women, suggests that families face little 
 incentive to space children more closely together for economic reasons.
-Even as the level of female education increased, the female labor force participation 
-in both urban and rural areas stagnated or decreased 
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-
-Female labor force participation does, however, still depend on education.
-In line with other countries, the NFHS data show a U-shaped relationship between 
-education and working for married women, with women with either no education or 12 or more 
-years the most likely to participate in the labor force and women with 8--11 years of 
-education the least \citep{Goldin1994,Chatterjee2018}.%
+Even as women's education increased, their labor force participation stagnated or 
+decreased and is now one of the lowest outside the Middle East 
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018}.%
 \footnote{
+In line with other countries, there is still a U-shaped relationship between education and 
+labor force participation for married women, with the lowest participation for 
+women with 8--11 years of education \citep{Goldin1994,Chatterjee2018}.
 See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
@@
 
-One explanation for the low female labor force participation, especially for women
-with 8--11 years of education, is that household income has increased so substantially 
-that the income effect dominates any substitution effect.
-Two findings support this interpretation.
-First, although real wages for both men and women have almost doubled between 1987 and 
-2011, the mean male wage is still close to 70\% higher than the female wage 
-\citep{Klasen2015,Bhargava2018}.
-Second, women’s labor supply appears to be more negatively elastic to husbands' 
-wages than positively elastic to their own wages \citep{Bhargava2018}.
+One explanation for the low female labor force participation is that male wages have 
+increased so substantially that the income effect dominates any substitution effect.
+The average male wage is almost 70\% higher than the female wage and women’s labor 
+supply appears to be more negatively elastic to husbands' wages than positively elastic 
+to their own wages \citep{Klasen2015,Bhargava2018}.
 
-Furthermore, female education undoubtedly represents more than the value of women's time.
-Beside propagation of low fertility norms, two examples are the productions of child 
-health and offspring human capital.
-
-First, children of more educated women have better health outcomes and lower mortality 
-than less educated women, either from higher income or better health knowledge 
-\citep{Rosenzweig1982a,Kovsted2002,Whitworth2002,Maitra2008}.
-Especially of interest here is that, although short birth spacing generally leads to worse 
-health outcomes, the more educated the mother, the more muted this relationship is, which, 
-at least partly, removes the health outcome incentive for longer birth spacing
-\citep{Molitoris2019}.
-
-Second, better-educated women are more efficient at producing child human capital 
-\citep{Behrman1999}.
-Hence, the increasing return to male education may lead to an increased demand for 
-better-educated mothers, which, combined with lower fertility and an increased use
-of sex selection when available, allow families to achieve higher quality sons.
-In this explanation, the associations between higher female education, lower fertility, 
-and more sex selection are not a causal effect driven by higher female wages but instead 
-the result of the increased return to male education.
+Furthermore, the increasing return to male education may make it appear as if higher 
+female education results in lower fertility and more sex selection, if women with more 
+education are better at producing child human capital as suggested by \citet{Behrman1999},.
+The higher return to male education provides an additional incentive to invest in sons'
+education, and one such investment is a better-educated mother.
+As discussed above, the higher returns should also lower desired fertility, making the use 
+of sex selection even more appealing, and possibly increases birth spacing.
 
@@
 The low and declining female labor force participation as husbands' wages increase 
-is one indication that this process still operates \citep{Abraham2013,Chatterjee2018}.
+indicates that this process still operates \citep{Abraham2013,Chatterjee2018}.
 
@@
 In summary, with substantial increases in husbands' income and a declining female labor 
-force participation, I expect a push toward longer birth spacing over time, independent
-of education levels, based on the income effects and the effects of spacing
-on child outcomes.
-Furthermore, I expect birth spacing to increase the most among the better educated 
+force participation, I expect longer birth spacing over time, independent of education 
+levels.
+Furthermore, birth spacing likely increases the most among the better educated 
 because their household income increases the most---even with declining female labor 
@@
 Finally, even with the substantial increase in the number of better-educated women, 
-"Sanskritization" implies that the changing composition will not substantially change 
-the use of sex selection.
+"Sanskritization" implies that the changing composition will not substantially change the 
+use of sex selection.

### 2020-12-11 paper/2020-10-revision-background.tex
Shorten version of Conceptual Framework and Introduction

@@
-This section provides a conceptual framework for understanding how birth spacing changes
-and guiding the subsequent analysis.
+This section provides a conceptual framework for understanding changes in birth spacing.
 I first introduce three potential explanations that link fertility and birth 
@@
 \citep{Casterline2016,Portner2018}.
-Next, I discuss why female education and area of residence are the principle factors 
+Next, I discuss why female education and area of residence are the principal factors 
 in the empirical analyses and how they tie into the three explanations.
@@
 The improvements in economic condition, especially the doubling of real wages,
-are likely to affect fertility although the direction is ambiguous, as, empirically, 
+are likely to affect fertility although the direction is ambiguous; empirically, 
 higher female wages lowers fertility, whereas higher male wages increases fertility 
@@
 
-If having children requires the mother to curtail her economic activities, higher
-female wages, in addition to lowering fertility, will tend to shorten birth spacing.
+Higher female wages will also tend to shorten birth spacing if having children requires 
+the mother to curtail her economic activities.
 Shortening birth spacing allows parents to take advantage of economies of scale in 
-childrearing---for example, looking after two children simultaneously requires 
-less than double the time needed to look after one child \citep{Vijverberg1982,Hotz1997}.
+childrearing---for example, looking after two children requires less than double the time 
+needed for one child \citep{Vijverberg1982,Hotz1997}.
 
@@
 reduce fertility and invest more in each child \citep{Rosenzweig1982a,Wolpin1997}.
-The higher return to education means that parents have more of an incentive to 
-invest in their children's education, which increases the cost of children and 
-lowers fertility. 
-Lower expected mortality means that fewer births are required to reach a 
-desired number of surviving children and allow parents to invest more in each child.
+The higher return to education means a stronger incentive to invest in their children's
+education, which increases the cost of children and lowers fertility. 
+With lower expected mortality fewer births are required to reach a desired number 
+of surviving children, which furthermore allows parents to invest more in each child.
 
-Longer spacing between births is generally expected to have positive effects on 
-child outcomes and if fertility falls because of increased desired for better child
-outcomes we would also expect spacing to increase.
-The clearest example of birth spacing affecting child outcomes is for health,
-where very short spacing---approximately 24 months or less---leads to worse health 
-and mortality outcomes for children 
-\citep{Whitworth2002,Conde-Agudelo2012}.
-Whether longer spacing also results in better human capital outcome is unclear as the 
-evidence is mixed for developed countries and nonexistent for developing countries
+An increased desired for better child outcomes will also tend to lengthen birth spacing,
+provided it has positive effects on child outcomes.
+The clearest example of a positive effect of longer spacing that very short 
+spacing---approximately 24 months or less---leads to worse child health and mortality 
+outcomes \citep{Whitworth2002,Conde-Agudelo2012}.
+Whether longer spacing also improves human capital outcomes is more speculative with
+mixed evidence for developed countries and no evidence for developing countries
 \citep{Zajonc1976,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
@@
 % Son preference 
-Empirically, a stronger son preference has only a minor effect on average fertility, but
-son preference still affects the sex composition and fertility across families through 
-differential stopping behavior and leads to shorter spacing and  worse health outcomes for 
-daughters when there are no sons in the household 
+Empirically, stronger son preference only marginally increases average fertility, but
+differential stopping behavior still affects the sex composition and fertility across 
+families and leads to shorter spacing and worse health outcomes for daughters  
+when there are no sons in the household
 \citep{repetto72,clark00,Whitworth2002,Basu2010,Jayachandran2011,Barcellos2014}.
 
-Another result of son preference is the use of sex selection, which enables parents to 
-avoid giving birth to a girl but increases the expected interval to the next birth
-by 6--12 months for each abortion.
-This increase consists of three parts. 
-First, after an abortion, the uterus needs at least two menstrual cycles to recover, 
-or the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
-Second, the waiting time to conception is one to six months. 
-Finally, sex determination tests are reliable only from three months of gestation.
+Stronger son preference increases the use of sex selection and each sex-selective
+abortion increases the expected birth spacing by 6--12 months.
+After an abortion the uterus needs at least two menstrual cycles---approximately 
+two months---to recover, or the subsequent risk of spontaneous abortion increases 
+substantially \citep{zhou00b}.
+Once conception can be attempted, the waiting time to conception is likely between
+one and six months. 
+Finally, sex-determination tests are reliable only from three months of gestation. 
+Hence, it takes at least six months before the couple is at the same point in the next 
+pregnancy as they were in the prior pregnancy when they decided to abort.
 
 The use of sex selection, and therefore the length of birth intervals, increases with
-lower desired fertility and the higher the parity provided the desired number of sons has 
+lower desired fertility and with parity, provided the desired number of sons has 
 not been reached \citep{Portner2015b,Jayachandran2017}.
@@
 % Factors/predictions
-Although the explanations above are based on economic conditions, desired child outcome,
-son preference, and the access to sex selection, none of these are available in the
-data, so I instead use female education and area of residence as the two main explanatory 
-variables in the empirical analyses.
-Female education and area of residence are the closest available proxies and earlier 
-research show that both higher female education and urbanization are associated with 
-lower fertility and increased use of sex selection, and, therefore, likely also changes 
-in birth spacing
+Although the explanations above are based on economic conditions, desired child outcomes,
+son preference, and sex selection, none of these are available in the data, so I instead 
+use female education and area of residence as the two principal explanatory variables in 
+the empirical analyses.
+Not only are these the closest available proxies, prior research shows that both higher 
+female education and urbanization are associated with lower fertility and increased 
+sex selection use, and, therefore, likely also changes birth spacing
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Furthermore, both variables are interesting given the tremendous increases in 
-both education and urbanization in India; 
-Figure \ref{fig:education_over_time} show the substantial increase in female education
-in both rural and urban areas, although it is still considerably higher in urban than in 
-rural areas and the proportion of the population living in urban areas almost doubled from 
-18\% in 1960 to 35\% in 2019 \citep{United-Nations2019}.
+Furthermore, both variables are of interest given the tremendous changes in India; 
+Figure \ref{fig:education_over_time} shows the substantial increase in female education
+and the urban proportion of the population almost doubled from 18\% in 1960 to 35\% in 
+2019 \citep{United-Nations2019}.
 
@@
 
-Women living in urban areas are likely to have lower fertility and higher use
-of sex selection than women in rural areas.
+Urban women are likely to have lower fertility and higher use of sex selection than women 
+in rural areas.
 The lower fertility is the result of higher cost of children and lower child mortality 
@@
 \footnote{
-However, holding parental education constant, there is evidence that children in
-Indian slums do worse than they would have in rural areas \citep{Portner2018a}.
+However, holding parental education constant, children in Indian slums have worse
+health outcomes than in rural areas \citep{Portner2018a}.
 }
 The higher use of sex selection comes partly from the lower fertility and partly from
-women in urban areas having higher income and better access to health care facilities.
+higher income and better access to health care facilities in urban areas.
 
@@
 birth spacing and lower fertility, but the low and declining female labor force 
-participation in India, especially for younger women, suggests that families face little 
-incentive to space children more closely together for economic reasons.
+participation in India suggests that families face little incentive to space children 
+more closely together for economic reasons.
 Even as women's education increased, their labor force participation stagnated or 
 decreased and is now one of the lowest outside the Middle East 
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018}.%
-\footnote{
-In line with other countries, there is still a U-shaped relationship between education and 
-labor force participation for married women, with the lowest participation for 
-women with 8--11 years of education \citep{Goldin1994,Chatterjee2018}.
-See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
-}
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018}.
 
-One explanation for the low female labor force participation is that male wages have 
-increased so substantially that the income effect dominates any substitution effect.
-The average male wage is almost 70\% higher than the female wage and women’s labor 
-supply appears to be more negatively elastic to husbands' wages than positively elastic 
-to their own wages \citep{Klasen2015,Bhargava2018}.
+The decline in female labor force participation appear to be driven by a combination
+of a relatively small expansion in the sectors where women work and the income effect 
+from rapidly increasing male wages and education dominating the substitution effect from 
+higher female wages \citep{Klasen2015,Bhargava2018}.
+The income effect can dominate because not only do men have a higher average level of 
+education than women, men are also paid more than women for a given level of education, 
+and the returns to education increases with education in India \citep{Agrawal2011}.
+Hence, increasing male education will result in an larger increase in income than a 
+similar increase in female education.
 
-Furthermore, the increasing return to male education may make it appear as if higher 
-female education results in lower fertility and more sex selection, if women with more 
-education are better at producing child human capital as suggested by \citet{Behrman1999},.
+However, in a situation with increasing returns to male education and declining female labor 
+force participation, we might still observe an association between higher female education 
+and both lower fertility and increased use of sex selection, provided better-educated women 
+are better at producing child human capital as suggested by \citet{Behrman1999}.
+In this scenario, better-educated women are desired not for their ability to generate
+income but for their ability to produce better-educated sons.
 The higher return to male education provides an additional incentive to invest in sons'
-education, and one such investment is a better-educated mother.
-As discussed above, the higher returns should also lower desired fertility, making the use 
-of sex selection even more appealing, and possibly increases birth spacing.
+education---with a better-educated mother one such investment---and also lowers desired 
+fertility, makes sex selection more likely, and possibly increases birth spacing.
 
 % Sanskritization
-Although the expansion in female education might bring in groups with initially different 
-norms, the process of ``Sanskritization'' implies that as lower-castes females gain access 
-to education, they adopt higher-caste norms such as stronger son preference and a retraction 
-from the formal labor market \citep{Srinivas1956}.
-The low and declining female labor force participation as husbands' wages increase 
-indicates that this process still operates \citep{Abraham2013,Chatterjee2018}.
+Finally, although the expansion in female education will likely bring in groups who 
+initially have different norms, the process of ``Sanskritization'' implies that as 
+lower-castes females gain access to education, they adopt higher-caste norms such as stronger son 
+preference and a retraction from the formal labor market \citep{Srinivas1956}.
+The declining female labor force participation suggests that this process still 
+operates \citep{Abraham2013,Chatterjee2018}.
 
 % Summary / hypotheses
-
 In summary, with substantial increases in husbands' income and a declining female labor 
@@
 participation---and because of their use of sex selection.
-Finally, even with the substantial increase in the number of better-educated women, 
-"Sanskritization" implies that the changing composition will not substantially change the 
-use of sex selection.
+Finally, "Sanskritization" implies that the changing composition of better-educated
+women will not substantially change the use of sex selection.

### 2020-12-11 paper/sex_selection_spacing-ver5.tex
Shorten version of Conceptual Framework and Introduction

--- 2020-09-01 paper/sex_selection_spacing-ver4.tex
@@
 The economy has grown substantially,
+real wages have more than doubled,
 educational attainment has increased for males and females,
 and the total fertility rate has fallen to 2.2 children
-\citep{Bosworth2008,Dharmalingam2014,
+\citep{Bosworth2008,Dharmalingam2014,Klasen2015,
 International-Institute-for-Population-Sciences-IIPS2017}.
@@
 The motivation is twofold.
-First, researchers have failed to appreciate that each abortion increases the
-interval between births by 6--12 months.%
-\footnote{
-The increase consists of three parts. 
-First, after an abortion, the uterus needs at least two menstrual cycles to recover, 
-or the likelihood of spontaneous abortion increases substantially \citep{zhou00b}. 
-Second, the waiting time to conception is one to six months. 
-Finally, sex determination tests are reliable only from three months of gestation. 
-}
-Hence, the growing use of sex-selective abortions may substantially increase birth spacing, 
-although we do not know to what extent. 
+First, the growing use of sex-selective abortions may substantially increase birth spacing
+because, as detailed below, it takes 6 months or more after an abortion to reach the same 
+point in the next pregnancy.
+However, researchers have failed to appreciate this effect, and we do not know the size of 
+the impact.
 Second, greater educational attainment by women, higher household income, and the low and 
@@
 
-% Combine descriptive and theory sections into one
-
-\section{Background and Conceptual Framework}
-
-To set the stage for the subsequent analyses and provide a conceptual framework for 
-understanding birth spacing, I first discuss female education and labor force 
-participation in India and relevant theories on birth spacing.
-
-% [Female education]
-
-Female education is a crucial explanatory variable here for three reasons.
-First, higher female education is associated with lower fertility and increased use of 
-sex selection
+\section{Conceptual Framework}
+
+This section provides a conceptual framework for understanding changes in birth spacing.
+I first introduce three potential explanations that link fertility and birth 
+spacing decisions: economic conditions, desired child outcomes, and son preference 
+\citep{Casterline2016,Portner2018}.
+Next, I discuss why female education and area of residence are the principal factors 
+in the empirical analyses and how they tie into the three explanations.
+
+% Economic conditions
+The improvements in economic condition, especially the doubling of real wages,
+are likely to affect fertility although the direction is ambiguous; empirically, 
+higher female wages lowers fertility, whereas higher male wages increases fertility 
+\citep{Hotz1997,schultz97}.
+Economic theory predicts that the effect of higher wages on fertility is determined by 
+the relative strengths of the substitution and income effects.
+The substitute effect captures that as wages increase time becomes more expensive, and
+people therefore work more and spend less time on non-wage earning activities, such as 
+children or leisure.
+The income effect captures that higher wages increase the available income, which
+leads people to spend more time on time-intensive activities and less time working.
+Since women spend substantially more time on childrearing than men, the substitution effect 
+dominates for women but the income effect for men.
+
+Higher female wages will also tend to shorten birth spacing if having children requires 
+the mother to curtail her economic activities.
+Shortening birth spacing allows parents to take advantage of economies of scale in 
+childrearing---for example, looking after two children requires less than double the time 
+needed for one child \citep{Vijverberg1982,Hotz1997}.
+
+% Child outcomes
+Parents care both about how many children they have and their outcomes, and with 
+increasing returns to education and lower offspring mortality, parents are likely to 
+reduce fertility and invest more in each child \citep{Rosenzweig1982a,Wolpin1997}.
+The higher return to education means a stronger incentive to invest in their children's
+education, which increases the cost of children and lowers fertility. 
+With lower expected mortality fewer births are required to reach a desired number 
+of surviving children, which furthermore allows parents to invest more in each child.
+
+An increased desired for better child outcomes will also tend to lengthen birth spacing,
+provided it has positive effects on child outcomes.
+The clearest example of a positive effect of longer spacing that very short 
+spacing---approximately 24 months or less---leads to worse child health and mortality 
+outcomes \citep{Whitworth2002,Conde-Agudelo2012}.
+Whether longer spacing also improves human capital outcomes is more speculative with
+mixed evidence for developed countries and no evidence for developing countries
+\citep{Zajonc1976,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
+
+% Son preference 
+Empirically, stronger son preference only marginally increases average fertility, but
+differential stopping behavior still affects the sex composition and fertility across 
+families and leads to shorter spacing and worse health outcomes for daughters  
+when there are no sons in the household
+\citep{repetto72,clark00,Whitworth2002,Basu2010,Jayachandran2011,Barcellos2014}.
+
+Stronger son preference increases the use of sex selection and each sex-selective
+abortion increases the expected birth spacing by 6--12 months.
+After an abortion the uterus needs at least two menstrual cycles---approximately 
+two months---to recover, or the subsequent risk of spontaneous abortion increases 
+substantially \citep{zhou00b}.
+Once conception can be attempted, the waiting time to conception is likely between
+one and six months. 
+Finally, sex-determination tests are reliable only from three months of gestation. 
+Hence, it takes at least six months before the couple is at the same point in the next 
+pregnancy as they were in the prior pregnancy when they decided to abort.
+
+The use of sex selection, and therefore the length of birth intervals, increases with
+lower desired fertility and with parity, provided the desired number of sons has 
+not been reached \citep{Portner2015b,Jayachandran2017}.
+
+% Factors/predictions
+Although the explanations above are based on economic conditions, desired child outcomes,
+son preference, and sex selection, none of these are available in the data, so I instead 
+use female education and area of residence as the two principal explanatory variables in 
+the empirical analyses.
+Not only are these the closest available proxies, prior research shows that both higher 
+female education and urbanization are associated with lower fertility and increased 
+sex selection use, and, therefore, likely also changes birth spacing
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Second, female labor force participation in India, as in other developing countries, 
-first decreases and then increases with education
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-Finally, child mortality decreases with maternal education
-\citep{Rosenzweig1982a,Whitworth2002,Maitra2008}.
-
-% [TK where to put son preference discussion?]
-% %
-% \footnote{
-% It is also possible that the effect is driven by a stronger son preference, although 
-% higher education women have shown declining son preference \citep{bhat03,pande07}.
-% }
-
-I divide education levels into four groups: No education, 1--7 years, 8--11 years, and 
-12 and more years.
-The latter two correspond to having completed primary and secondary school, 
-respectively.%
-\footnote{
-Although there are variations by state, elementary education in India consists of a 
-primary school covering grades one through five and an upper primary---or middle 
-school---covering grades six through eight. 
-Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
-and 11 and 12 for ``upper secondary.''
-}
-To ensure that the results are comparable with the prior literature on fertility
-and mortality in India, I follow the NFHS reports, except that I combine the 
-less than five years and 5--7 years of schooling completed and the 8--9 
-and 10--11 years of schooling completed.
-This grouping allows me to capture the differences across education levels discussed below, 
-while also having groups large enough for the empirical method.
-
-% [what has happened to education]
-Female education has increased substantially over time in rural and urban areas but 
-is still substantially higher in urban than in rural areas.
-Figure \ref{fig:education_over_time} shows the distribution of schooling by birth 
-cohort for urban and rural women, 
-20 years or older, whether married or not, based on the four rounds of the NFHS.
-In rural areas, women with no education have gone from 90\% for the 1930s cohorts to 
-less than 20\% for the 1990s cohorts.
-Women with eight or more years of education have gone from almost zero for the 1930 cohort 
-to more than 60\% for the 1990s cohorts, with about half in the 8--11 group and the 
-other half in the 12 plus group.
-In urban areas, the proportions with no education or 1--7 years have each declined 
-to just below 10\%.
-Most of the increase in urban female education came from the 12 plus group, which 
-now accounts for more than half of all urban women for the most recent cohorts.
+Furthermore, both variables are of interest given the tremendous changes in India; 
+Figure \ref{fig:education_over_time} shows the substantial increase in female education
+and the urban proportion of the population almost doubled from 18\% in 1960 to 35\% in 
+2019 \citep{United-Nations2019}.
 
@@
 
-% [female labor force participation]
-
-The standard economic argument for shorter spacing with increasing female education 
-is that parents incur time costs when they have children \citep{Hotz1997,schultz97}.
-Suppose having children requires the mother to reduce her market work. 
-Parents can then lower this cost of children by shortening birth spacing to take advantage 
-of economies of scale in childrearing  \citep{Vijverberg1982}.
-
-However, even as the level of female education has increased, the female labor force 
-participation in both urban and rural areas has stagnated or decreased
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018,Bhargava2019}.
-India's female labor force participation is now lower than that of most other countries and does 
-not yet show any signs of increasing \citep{Klasen2015,Chatterjee2018}.
-In line with previous research, the NFHS data show a U-shaped relationship between 
-education and working for married women, with the highest percentage working being women with 
-either no education or 12 or more years and the lowest being women with 8--11 years of education.%
+Urban women are likely to have lower fertility and higher use of sex selection than women 
+in rural areas.
+The lower fertility is the result of higher cost of children and lower child mortality 
+risk in urban compared to rural areas.%
 \footnote{
-See appendix Figures \ref{fig:work_by_survey} through \ref{fig:work_family_by_survey}. 
-}
-
-The low and declining female labor force participation, especially for younger women, 
-suggests that families face little incentive to space children more closely 
-together for economic reasons.
-One explanation is that household income has increased so substantially that the income 
-effect dominates any substitution effect.
-Two findings speak to this effect.
-First, although real wages for both men and women have almost doubled between 1987 and 
-2011, the mean male wage is still close to 70\% higher than the female wage 
-\citep{Klasen2015,Bhargava2018}.
-Second, women’s labor supply appears to be more negatively elastic to husbands' 
-wages than positively elastic to their own wages \citep{Bhargava2018}.
-
-% [sex selection]
-
-The introduction of sex selection allows parents to avoid giving birth to girls but 
-increases the expected interval to the next birth.
-Theory suggests that sex selection increases with lower desired fertility and with
-higher parity for a given desired number of children \citep{Portner2015b}.
-Sex selection is more widespread among better-educated than less-educated and among urban 
-than rural women, which is consistent with lower desired fertility increasing the
-use of sex selection 
-\citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Better-educated and urban women also tend to live in households with higher income, which 
-lowers the relative costs of using sex selection and having long birth intervals.
-
-The combination of rising incomes and continued son preference may lead to even longer 
-spacing than might be expected from the income effect alone.
-As women's education increases, their productivity in the production of offspring human 
-capital also increases.
-With relatively more boys born because of increased access to sex-selective 
-abortions and the increasing income potential for (male) offspring, demand for 
-better-educated women can increase, even if they do not participate in the labor market 
-\citep{Behrman1999}.
-
-If more and ``better'' parental attention per child results in higher child ``quality,'' 
-we should expect longer birth intervals \citep{Zajonc1975,Zajonc1976,Razin1980}.
-However, the evidence on spacing's effect on child quality measures such as IQ 
-and education is mixed for developed countries and nonexisting for developing countries
-\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-The exception is health and mortality, where longer spacing does lead to better outcomes, 
-although this relationship weakens with maternal education 
-\citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.
-
-% If parents realize that longer spacing leads to better child outcomes, we may even observe 
-% later conception, especially when, with sex selection, the next child is likely to be a boy.
-% Working in the opposite direction of this "delay" effect is that women with more education 
-% can, in principle, space their children closer together without substantially increasing 
-% child mortality risk. 
-% However, given the apparent lack of pressure to return to the labor force, this effect is 
-% likely small.
+However, holding parental education constant, children in Indian slums have worse
+health outcomes than in rural areas \citep{Portner2018a}.
+}
+The higher use of sex selection comes partly from the lower fertility and partly from
+higher income and better access to health care facilities in urban areas.
+
+As women receive more education their potential wages increase, which should shorten 
+birth spacing and lower fertility, but the low and declining female labor force 
+participation in India suggests that families face little incentive to space children 
+more closely together for economic reasons.
+Even as women's education increased, their labor force participation stagnated or 
+decreased and is now one of the lowest outside the Middle East 
+\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018}.
+
+The decline in female labor force participation appear to be driven by a combination
+of a relatively small expansion in the sectors where women work and the income effect 
+from rapidly increasing male wages and education dominating the substitution effect from 
+higher female wages \citep{Klasen2015,Bhargava2018}.
+The income effect can dominate because not only do men have a higher average level of 
+education than women, men are also paid more than women for a given level of education, 
+and the returns to education increases with education in India \citep{Agrawal2011}.
+Hence, increasing male education will result in an larger increase in income than a 
+similar increase in female education.
+
+However, in a situation with increasing returns to male education and declining female labor 
+force participation, we might still observe an association between higher female education 
+and both lower fertility and increased use of sex selection, provided better-educated women 
+are better at producing child human capital as suggested by \citet{Behrman1999}.
+In this scenario, better-educated women are desired not for their ability to generate
+income but for their ability to produce better-educated sons.
+The higher return to male education provides an additional incentive to invest in sons'
+education---with a better-educated mother one such investment---and also lowers desired 
+fertility, makes sex selection more likely, and possibly increases birth spacing.
 
 % Sanskritization
-
-The increases in female educational attainment imply that access to education has 
-expanded beyond the higher castes. 
-One possible effect of the associated change in the composition of better-educated women 
-is that this group's behavior would change.
-However, ``Sanskritization'' implies that as lower-castes females gain access to 
-education and their husbands' income increases, they adopt higher-caste 
-norms such as stronger son preference and a retraction from the formal labor 
-market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.
-The low and declining female labor force participation suggests that this process still operates.
+Finally, although the expansion in female education will likely bring in groups who 
+initially have different norms, the process of ``Sanskritization'' implies that as 
+lower-castes females gain access to education, they adopt higher-caste norms such as stronger son 
+preference and a retraction from the formal labor market \citep{Srinivas1956}.
+The declining female labor force participation suggests that this process still 
+operates \citep{Abraham2013,Chatterjee2018}.
 
 % Summary / hypotheses
-
 In summary, with substantial increases in husbands' income and a declining female labor 
-force participation, I expect a push toward longer birth spacing over time, independent
-of education levels, based on the income effects and the effects of spacing
-on child outcomes.
-Furthermore, I expect birth spacing to increase the most among the better educated 
+force participation, I expect longer birth spacing over time, independent of education 
+levels.
+Furthermore, birth spacing likely increases the most among the better educated 
 because their household income increases the most---even with declining female labor 
 participation---and because of their use of sex selection.
-Even with the substantial increase in the number of better-educated women, 
-"Sanskritization" implies that the changing composition will not substantially change 
-the use of sex selection.
-
-%------------------------------------------------------------------------------------
+Finally, "Sanskritization" implies that the changing composition of better-educated
+women will not substantially change the use of sex selection.
 

### 2020-12-14 paper/sex_selection_spacing-ver5.tex
Discuss period vs cohort fertility in more detail

@@
 The motivation is twofold.
-First, the growing use of sex-selective abortions may substantially increase birth spacing
-because, as detailed below, it takes 6 months or more after an abortion to reach the same 
-point in the next pregnancy.
-However, researchers have failed to appreciate this effect, and we do not know the size of 
-the impact.
-Second, greater educational attainment by women, higher household income, and the low and 
+First, past research has failed to appreciate that the growing use of sex-selective 
+abortions may substantially increase birth spacing; as detailed below, it takes 6 months 
+or more after an abortion to reach the same point in the next pregnancy.
+Second, women's greater educational attainment, higher household income, but low and 
 declining female labor force participation all likely influence birth spacing. 
-Thus, the combined changes in birth spacing may outpace what we have observed in 
-other countries.
+The combination of the increasing use of sex selection and the other societal changes 
+can significantly impact birth spacing, but we know little about how much.
 
@@
 
-First, did changes in birth spacing bias the fertility estimates for India? 
-With longer spacing, mothers will be older at each parity, and this tempo effect makes the 
-total fertility rate a downward-biased estimate of cohort fertility
-\citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}. 
-Hence, if birth intervals increased substantially, then India's fertility may be higher 
-than generally accepted.
+First, did changes in birth spacing make us overestimate the decline in cohort fertility?
+With longer spacing, mothers will be older at each parity, and this tempo effect 
+makes period fertility measures, such as the total fertility rate, downward-biased
+estimates of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
+Hence, a rapidly expanding use of sex selection could make the total fertility rate---our 
+most used fertility measure---fall substantially faster than cohort fertility.
+In this case, households' fertility goals may be higher than generally accepted.
 

### 2020-12-16 paper/sex_selection_spacing-ver5.tex
Add problem and questions to abstract

@@
 
-\noindent Over the past four decades, the Hindu women in India most likely to use 
-sex-selective abortions---well-educated women with no sons---had the most substantial 
-lengthening of birth intervals and the most biased sex ratios. 
-As a result, we now see cases that reverse the traditional spacing pattern, with some
-women with no sons having longer birth intervals than those with sons. 
-Those least likely to use sex-selective abortions---less-educated women in rural 
-areas---still follow the traditional pattern of short spacing when they have girls, with 
-only limited evidence of sex selection. 
-Because of the rapid lengthening in spacing, the standard fertility rates substantially 
+% \noindent Over the past four decades, the Hindu women in India most likely to use 
+% sex-selective abortions---well-educated women with no sons---had the most substantial 
+% lengthening of birth intervals and the most biased sex ratios. 
+% As a result, we now see cases that reverse the traditional spacing pattern, with some
+% women with no sons having longer birth intervals than those with sons. 
+% Those least likely to use sex-selective abortions---less-educated women in rural 
+% areas---still follow the traditional pattern of short spacing when they have girls, with 
+% only limited evidence of sex selection. 
+% Because of the rapid lengthening in spacing, the standard fertility rates substantially 
+% overestimated how fast cohort fertility fell. 
+% Despite a convergence, cohort fertility is still 10\%--20\% higher than the fertility rate 
+% and above replacement level for all but the best-educated urban women. 
+% Infant mortality has declined substantially over time for all groups, with the fastest 
+% decline among the less educated. 
+% Short birth spacing is still associated with higher mortality, although considerably less 
+% so for the best-educated women. 
+% There is no evidence that repeated sex-selective abortions are associated with higher 
+% infant mortality for the child eventually born. 
+% Finally, it does not appear that the use of sex selection is declining.
+
+\noindent India has experienced an increasingly male-biased sex ratio at birth following
+the introduction of prenatal sex determination techniques. 
+I examine three questions.
+First, how did birth spacing respond to this and other secular developments? 
+Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
+Finally, did the advent of sex-selective abortions change the relationship between infant mortality and
+birth spacing? 
+Well-educated Hindu women with no sons had the most substantial lengthening of birth 
+intervals and the most male-biased sex ratios, likely from sex-selective abortions. 
+Hence, some women with no sons now have longer birth intervals than those with
+sons, reversing the traditional spacing pattern. 
+Less-educated women continued short spacing when they have girls, with only limited 
+evidence of male-biased sex ratios. 
+Because of the rapid lengthening in spacing, period fertility rates substantially 
 overestimated how fast cohort fertility fell. 
-Despite a convergence, cohort fertility is still 10\%--20\% higher than the fertility rate 
-and above replacement level for all but the best-educated urban women. 
-Infant mortality has declined substantially over time for all groups, with the fastest 
-decline among the less educated. 
-Short birth spacing is still associated with higher mortality, although considerably less 
-so for the best-educated women. 
-There is no evidence that repeated sex-selective abortions are associated with higher 
-infant mortality for the child eventually born. 
-Finally, it does not appear that the use of sex selection is declining.
-
-% I show that, in India, the most substantial increases in Hindu women's
-% birth interval over the last four decades came from the increasing use
-% of sex-selective abortions. The women most likely to use sex
-% selection---well-educated with no sons---had the most substantial
-% lengthening of birth intervals and the most biased sex ratios.
+Furthermore, predicted cohort fertility remains above replacement for all but the 
+best-educated urban women. 
+If lengthening of birth intervals occurs from repeated abortions, the associated short 
+pregnancy spacing may counteract any positive effects of longer birth spacing. 
+There is no evidence of this effect on infant mortality. 
+Finally, judging from sex ratios, sex-selective abortion use is not declining.
 
@@
 and sex selection? 
-In India, birth intervals have traditionally been shorter with fewer sons, contributing 
-to the higher mortality risk for girls
+In India, birth intervals have traditionally been shorter with fewer sons, contributing to 
+girls' higher mortality risk
 \citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}. 
-Therefore, longer birth spacing, whether from sex selection or secular changes, may reduce 
-mortality \citep{Conde-Agudelo2012,Molitoris2019}.
-However, a counteracting effect is possible if longer birth intervals arise from multiple 
-abortions because the short duration between pregnancies could increase mortality. 
-% Nevertheless, there has been no attempt to examine how infant mortality has changed with 
-% the increase in sex selection.
+Therefore, longer birth spacing may reduce mortality through, for example, diminished 
+sibling competition \citep{Conde-Agudelo2012,Molitoris2019}. 
+However, if the spacing between births lengthens because of sex-selective abortions, the 
+spacing between pregnancies may still be very short. 
+Short pregnancy spacing may lead to worse child outcomes because of maternal nutritional 
+depletion and insufficient time to recover from the previous pregnancy. 
+Hence, children born after long birth intervals where multiple abortions have punctuated 
+those intervals may not see the same benefits as a child born after a long interval that 
+is not punctuated by abortions.
 

### 2020-12-17 paper/sex_selection_spacing-ver5.tex
Specify birth interval length when needed

@@
 
-I use the model to predict birth interval measures, parity progression probabilities, 
+I use the model to predict birth interval lengths, parity progression probabilities, 
 and the sex ratio rather than present coefficients because the interpretation 
@@
 
-For birth intervals, I estimate a set of percentile birth intervals. 
+For birth interval lengths, I estimate a set of percentile durations. 
 I first calculate for each woman when there is a given percentage chance that she will have 
@@
 spacing between births and probe for ``missed'' births.
-For India, the main concern is underreporting of deceased children, especially a systematic 
+For India, the main concern is the underreporting of deceased children, especially a systematic 
 recall error where respondents' likelihood of reporting the birth of a deceased child depends 
 on the sex of that child.
-Unreported deceased children inflate the birth intervals and, with declining mortality, 
+Unreported deceased children inflate the length of birth intervals and, with declining mortality, 
 make changes over time appear too small.
@@
 Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
-show the 25th, 50th, and 75th percentile birth intervals in 
+show the 25th, 50th, and 75th percentile birth interval durations in 
 months, the sex ratio, and the probability of having a birth for each spell
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_rural}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval durations, sex ratios, and parity progression  
 for rural women with no education by spell, sex composition, and period}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_rural}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval durations, sex ratios, and parity progression  
 for rural women with 1--7 years of education by spell, sex composition, and period}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_urban}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval durations, sex ratios, and parity progression  
 for urban women with 1--7 years of education by spell, sex composition, and period}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_rural}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval durations, sex ratios, and parity progression  
 for rural women with 8--11 years of education by spell, sex composition, and period}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_urban}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval durations, sex ratios, and parity progression  
 for urban women with 8--11 years of education by spell, sex composition, and period}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_urban}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval durations, sex ratios, and parity progression  
 for urban women with 12 or more years of education by spell, sex composition, and period}
@@
 
-% [Birth intervals w/o sex selection]
 \subsection{When Sex Selection Is Less Used}
@@
 To separate the effects of the introduction of sex selection and the other changes in
-India, I first discuss how birth intervals have changed in situations where sex selection 
-is less used.
+India, I first discuss how the lengths of birth intervals have changed in situations where 
+sex selection is less used.
 The group broadly covers women with no education, regardless of the sex composition of their 
@@
 Notably, for those least likely to use sex selection---rural women with no education---the 
-difference in birth intervals across sex compositions has grown over time as spacing when 
-sons are present has increased.
+difference in birth interval length across sex compositions has grown over time as spacing when 
+sons are present has become longer.
 
@@
 \emph{pregnancies} the WHO recommends.
-Furthermore, despite higher parities' more substantial increases in birth intervals, even 
-the 25th percentile birth intervals for the fourth spell are around 24 months for women 
-with less than eight years of education.
+Even with the more substantial lengthening of birth intervals for higher parities, the 25th
+percentile duration is still around 24 months for the fourth spell for women with less than
+eight years of education.
 
 % [median birth intervals]
-Median birth intervals have also increased relatively little---only three to six months 
+Median birth interval lengths have also increased relatively little---only three to six months 
 over the four decades---compared to around 3.5 months \emph{per decade} in other countries with 
@@
 \footnote{
-The NFHS reports show median closed birth intervals of approximately 31 months, which have 
-barely moved over time, underscoring the importance of accounting for censoring when examining 
-birth spacing.
-}
-The result is that most of the median birth intervals are still at 36 months or below, 
-with the shortest only 29 months.
-
-Birth intervals appeared to lengthen the most for women the least likely to work.
-For example, from lowest to highest education, the average third-spell birth intervals for 
-urban women with one boy and one girl increased by 2.7, 3.4, 5.8, and 1.8 months over the 
-four decades.%
+The NFHS reports show median durations of closed birth intervals of approximately 31 months, 
+which have barely moved over time, underscoring the importance of accounting for censoring 
+when examining birth spacing.
+}
+The result is that most of the median birth interval durations are still at 36 months or
+below, with the shortest only 29 months.
+
+Birth intervals appeared to lengthen the most for women who are the least likely to work.
+For example, from lowest to highest education, the average duration of third-spell birth 
+intervals for urban women with one boy and one girl increased by 2.7, 3.4, 5.8, and 1.8 
+months over the four decades.%
 \footnote{
 For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0.
-See the online appendix tables for the average birth intervals.
+See the online appendix tables for the average birth interval durations.
 }
@@
 % [75th percentile birth intervals]
-The most substantial changes occurred in the 75th percentile birth intervals, where the 
-more the parity progression probabilities declined, the more the birth interval lengthened. 
+The most substantial changes occurred in the 75th percentile birth interval durations, 
+where the more the parity progression probabilities declined, the more the birth interval 
+lengthened. 
 For example, the probability of a fourth birth for urban women with 8--11 years 
-of education and two sons and a girl has declined by almost 40 percentage points as the 
-75th percentile birth interval increased by 22 months.
+of education and two sons and one girl has declined by almost 40 percentage points as the 
+75th percentile birth interval length increased by 22 months.
 Compare this with rural women of no education with a boy as their first child, for whom the 
@@
 These results are in line with prior research showing that falling fertility is associated 
-with increases in longer spacing, although why is still an unresolved question 
-\citep{Casterline2016}.
-The exception to this trend suggests one possible answer.
-For the most educated women who already have a son, the probability of a third birth 
-declined rapidly, but the birth intervals changed little.
+with a lengthening of particularly the longer birth intervals, although why is still an 
+unresolved question \citep{Casterline2016}.
+The most educated women who already have a son is an exception to this trend; the 
+probability of a third birth declined rapidly, but the birth interval lengths changed little. 
 These women both have better access to modern contraceptives and are better at using 
 traditional contraceptive methods \citep{Rosenzweig1989}. 
-
-% [Interpretation]
-% How do these changes in birth intervals tie in with the changes in India over the four
-% decades?
-% [TK economic growth? -> higher return to education for males -> lower fertility and
-% higher investment in boys' education -- has anybody looked at this?]
-% First, the parity progression probabilities have been falling over time across all 
-% education levels, especially for women with at least one son.
+Hence, it is possible that the lengthening of birth intervals with falling fertility arises
+because unintended births become a relatively larger proportion of the total number of
+births for a given parity.
 
@@
 With two girls, almost 80\% of the third births are boys, and the 75th percentile 
-birth interval is close to 70 months. 
+birth interval length is close to 70 months. 
 This interval is about 13 months longer than if they had at least one son and represents 
@@
 around 55 months to 54 months.
-These changes in birth spacing may even be an underestimate because this particular group 
+These birth spacing changes may even be underestimated because this particular group
 appears to have had access to sex selection even before it became widespread, as shown by
@@
 The 75th percentile changes are the most dramatic, but sex selection also affects the 
-25th and median birth intervals. 
+25th and median birth interval lengths. 
 For the best-educated urban women with two girls, the 25th percentile birth interval
-increased by six months, or 23\%, while the median percentile birth interval 
+length increased by six months, or 23\%, while the median percentile birth interval length
 increased by 15 months (43\%).
@@
 education.
-
-% An important exception to the relatively short median intervals come from the better 
-% educated women, especially in the absence of sons.
-% The longest median interval was 48 months for the third spell for urban women with twelve 
-% or more years of education who had no boys, an increase of almost 15 months over
-% four decades.
-% Similary, urban women with eight to eleven years of education and no sons had median
-% birth intervals of around 40 months, an increase of about 10 months.
-% Finally, the best educated women now have a median second birth interval of around 42
-% months whether their first child was a boy or a girl.
-
-% Despite the strong son preference in spacing and sex ratios, there is also some indication 
-% that parents prefer a mix of boys and girls;
-% women with two boys \emph{and} a girl consistently have the lowest parity progression 
-% probability in the fourth spell across education levels.
 
@@
 The best-educated women with two girls had the most biased sex ratio and the most 
-significant increase in birth intervals. 
-Over the four decades, the median birth interval for this group increased by almost 15 
-months, 
-and the 75th percentile birth interval increased by a staggering 21 months, most of that 
-within a decade.
+significant increase in birth interval lengths. 
+Over the four decades, the median birth interval length for this group increased by almost 
+15 months, 
+and the 75th percentile birth interval length increased by a staggering 21 months, most of 
+that within a decade.
 
@@
 Hence, the fertility rate declined too fast from the mid-1980s to the century's end.
-Only recently, as the rate of increase for the birth intervals has slowed, have the two 
-fertility measures begun to converge again.
+Only recently, as the rate of increase for the birth interval lengths has slowed, have the 
+two fertility measures begun to converge again.
 Even with the convergence, the predicted 2005--2016 cohort fertility is still above the 
@@
 Furthermore, the predicted cohort fertility numbers are likely too low because I use only
-the first four births and births before the imposed 105-month birth interval censoring.
+the first four births and births before the imposed 105-month censoring of birth interval
+durations.
 
@@
 the prior birth.
-The birth interval dummies cover 12-month periods, starting nine months after the prior 
-birth, until the 57-month dummy, which covers until 105 months after the prior birth.
+The birth interval duration dummies cover 12-month periods, starting nine months after the 
+prior birth, until the 57-month dummy, which covers until 105 months after the prior birth.
 I use dummies for sex of the index child and the sex composition 
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_low_med}
-\caption{Infant mortality by preceding birth interval across periods for second child of women with 
+\caption{Infant mortality by preceding birth interval length across periods for second child of women with 
 no education and women with 1--7 years of education}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_high_highest}
-\caption{Infant mortality by preceding birth interval across periods for second child of women with 
+\caption{Infant mortality by preceding birth interval length across periods for second child of women with 
 8--11 and 12 and above years of education}
@@
 Take, for example, women with 12 or more years of education who had two girls. 
-As the sex ratio increased to close to 80\% boys, the expected median birth interval 
-increased by almost 15 months, and the 75th percentile interval increased by 21 months.
+As the sex ratio increased to close to 80\% boys, the expected median birth interval length
+increased by almost 15 months, and the 75th percentile interval length increased by 21 months.
 Most of the increase in the long intervals came immediately after the introduction of sex 
@@
 Still, there are, to my knowledge, no other cases where there has been as 
-substantial an increase in birth intervals and associated bias in fertility rates 
+substantial an increase in birth interval lengths and associated bias in fertility rates 
 as for India.
@@
 for each calendar birth interval four or more years.
-NFHS-3 and NFHS-4 did not directly use birth intervals, but asked whether there were any 
+NFHS-3 and NFHS-4 did not directly use birth interval lengths, but asked whether there were any 
 other live births between (name of previous birth) and (name), including any children who 
@@
 Figures \ref{fig:spacing_low_urban} and \ref{fig:spacing_highest_rural} show 25th, 50th,
-and 75th percentile birth intervals, the sex ratio, and the probability of parity
+and 75th percentile birth interval lengths, the sex ratio, and the probability of parity
 progression by spell for urban women with no education and rural women with 12 or
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval lengths, sex ratios, and parity progression  
 for urban women with no education by spell, sex composition, and period}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
-\caption{Percentile birth intervals, sex ratios, and parity progression  
+\caption{Percentile birth interval lengths, sex ratios, and parity progression  
 for rural women with 12 or more years of education by spell, sex composition, and period}
@@
 \ref{tab:p25_p50_p75_high}, and \ref{tab:p25_p50_p75_highest} show 25th, 50th, and
-75th percentile birth intervals together with their standard errors.
+75th percentile birth interval lengths together with their standard errors.
 The standard errors for all measures are based on bootstrapping,
@@
 \ref{tab:avg_sex_ratio_high}, and \ref{tab:avg_sex_ratio_highest}, show predicted average 
-birth intervals, sex ratios, and probabilities of having a birth by decade, spell, and sex 
+birth interval lengths, sex ratios, and probabilities of having a birth by decade, spell, and sex 
 composition for the four education levels separated by the area of residence, together 
 with bootstrapped standard errors for all three outcomes.
-To find the average birth interval, I calculate, for each woman, the probability of 
+To find the average birth interval length, I calculate, for each woman, the probability of 
 giving birth in each $t$, and her expected spell length from these probabilities. 
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_low_med}
-\caption{Infant mortality by preceding birth interval across periods for third child of women with 
+\caption{Infant mortality by preceding birth interval length across periods for third child of women with 
 no education and women with 1--7 years of education}
@@
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_high_highest}
-\caption{Infant mortality by preceding birth interval across periods for third child of women with 
+\caption{Infant mortality by preceding birth interval length across periods for third child of women with 
 8--11 and 12 and above years of education}

### 2020-12-17 paper/sex_selection_spacing-ver5.tex
Edit Conceptual Framework

@@
 The improvements in economic condition, especially the doubling of real wages,
-are likely to affect fertility although the direction is ambiguous; empirically, 
-higher female wages lowers fertility, whereas higher male wages increases fertility 
+are likely to affect fertility, although the direction is ambiguous; empirically, 
+higher female wages reduce fertility, whereas higher male wages increase fertility 
 \citep{Hotz1997,schultz97}.
-Economic theory predicts that the effect of higher wages on fertility is determined by 
-the relative strengths of the substitution and income effects.
-The substitute effect captures that as wages increase time becomes more expensive, and
-people therefore work more and spend less time on non-wage earning activities, such as 
+According to economic theory, the substitution and income effects' relative strengths 
+determine the effect of higher wages on fertility.
+The substitute effect captures that when wages increase, time becomes more expensive, and
+people, therefore, work more and spend less time on non-wage earning activities, such as
 children or leisure.
@@
 leads people to spend more time on time-intensive activities and less time working.
-Since women spend substantially more time on childrearing than men, the substitution effect 
-dominates for women but the income effect for men.
-
-Higher female wages will also tend to shorten birth spacing if having children requires 
-the mother to curtail her economic activities.
+Because women spend substantially more time on childrearing than men, the substitution
+effect dominates for women while the income effect dominates for men.
+
+Higher female wages may also shorten birth spacing if having children requires mothers to
+curtail their economic activities.
 Shortening birth spacing allows parents to take advantage of economies of scale in 
@@
 % Child outcomes
-Parents care both about how many children they have and their outcomes, and with 
-increasing returns to education and lower offspring mortality, parents are likely to 
+With increasing returns to education and lower offspring mortality, parents are likely to 
 reduce fertility and invest more in each child \citep{Rosenzweig1982a,Wolpin1997}.
 The higher return to education means a stronger incentive to invest in their children's
-education, which increases the cost of children and lowers fertility. 
-With lower expected mortality fewer births are required to reach a desired number 
-of surviving children, which furthermore allows parents to invest more in each child.
-
-An increased desired for better child outcomes will also tend to lengthen birth spacing,
+education, which increases the cost of having children, thereby lowering fertility. 
+With lower expected mortality, parents need fewer births to reach the desired number of
+surviving children, allowing parents to invest more in each child.
+
+An increased desire for better child outcomes will also tend to lengthen birth spacing,
 provided it has positive effects on child outcomes.
@@
 % Son preference 
-Empirically, stronger son preference only marginally increases average fertility, but
-differential stopping behavior still affects the sex composition and fertility across 
-families and leads to shorter spacing and worse health outcomes for daughters  
-when there are no sons in the household
-\citep{repetto72,clark00,Whitworth2002,Basu2010,Jayachandran2011,Barcellos2014}.
-
-Stronger son preference increases the use of sex selection and each sex-selective
-abortion increases the expected birth spacing by 6--12 months.
-After an abortion the uterus needs at least two menstrual cycles---approximately 
+Stronger son preference has traditionally been associated with shorter spacing and worse
+health outcomes for daughters when there no sons in the household
+\citep{Whitworth2002,Jayachandran2011}.
+Although son preference increases average fertility only marginally, differential stopping
+behavior means that girls tend to end up in larger families, resulting in fewer resources
+per child \citep{repetto72,clark00,Basu2010,Barcellos2014}.
+
+However, with the advent of sex selection, stronger son preference may lead to longer
+spacing because each sex-selective abortion adds 6–12 months to the length of the birth
+interval.
+After an abortion, the uterus needs at least two menstrual cycles---approximately 
 two months---to recover, or the subsequent risk of spontaneous abortion increases 
@@
 % Factors/predictions
-Although the explanations above are based on economic conditions, desired child outcomes,
-son preference, and sex selection, none of these are available in the data, so I instead 
-use female education and area of residence as the two principal explanatory variables in 
-the empirical analyses.
-Not only are these the closest available proxies, prior research shows that both higher 
-female education and urbanization are associated with lower fertility and increased 
-sex selection use, and, therefore, likely also changes birth spacing
+I use female education and area of residence as the two principal explanatory variables in
+the empirical analyses because those are the two closest proxies available in the data to
+cover the explanations above. 
+Prior research shows that both higher female education and urbanization are associated with 
+lower fertility and increased sex selection use, and, therefore, likely also changes birth spacing
 \citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Furthermore, both variables are of interest given the tremendous changes in India; 
-Figure \ref{fig:education_over_time} shows the substantial increase in female education
+Furthermore, both variables are of interest, given the tremendous changes in India. 
+Figure \ref{fig:education_over_time} shows the substantial increase in female education,
 and the urban proportion of the population almost doubled from 18\% in 1960 to 35\% in 
@@
 in rural areas.
-The lower fertility is the result of higher cost of children and lower child mortality 
+The lower fertility results from the higher cost of children and lower child mortality 
 risk in urban compared to rural areas.%
@@
 However, holding parental education constant, children in Indian slums have worse
-health outcomes than in rural areas \citep{Portner2018a}.
+health outcomes than children in rural areas \citep{Portner2018a}.
 }
@@
 
-As women receive more education their potential wages increase, which should shorten 
-birth spacing and lower fertility, but the low and declining female labor force 
-participation in India suggests that families face little incentive to space children 
-more closely together for economic reasons.
+Despite that higher potential wages from more education should shorten birth spacing and
+lower fertility, the low and declining female labor force participation suggests little
+economic incentive to space children closer together.
 Even as women's education increased, their labor force participation stagnated or 
@@
 
-The decline in female labor force participation appear to be driven by a combination
+The decline in female labor force participation appears to be driven by a combination
 of a relatively small expansion in the sectors where women work and the income effect 
@@
 and the returns to education increases with education in India \citep{Agrawal2011}.
-Hence, increasing male education will result in an larger increase in income than a 
+Hence, increasing male education will result in a larger increase in income than a 
 similar increase in female education.
 
-However, in a situation with increasing returns to male education and declining female labor 
-force participation, we might still observe an association between higher female education 
-and both lower fertility and increased use of sex selection, provided better-educated women 
-are better at producing child human capital as suggested by \citet{Behrman1999}.
-In this scenario, better-educated women are desired not for their ability to generate
-income but for their ability to produce better-educated sons.
+However, higher female education might still be associated with lower fertility and more 
+sex selection, provided better-educated women are better at producing child human capital, 
+as suggested by \citet{Behrman1999}. 
+In a situation with increasing returns to male education, households may desire 
+better-educated women because of their ability to produce better-educated sons, 
+rather than because of their higher potential income. 
 The higher return to male education provides an additional incentive to invest in sons' 
-education---with a better-educated mother one such investment---and also lowers desired 
+education---with a better-educated mother one such investment---and leads to lower desired 
 fertility, makes sex selection more likely, and possibly increases birth spacing.
@@
 % Sanskritization
-Finally, although the expansion in female education will likely bring in groups who 
-initially have different norms, the process of ``Sanskritization'' implies that as 
-lower-castes females gain access to education, they adopt higher-caste norms such as stronger son 
-preference and a retraction from the formal labor market \citep{Srinivas1956}.
+Finally, the process of "Sanskritization" implies that as lower-caste females gain access
+to education, they adopt higher-caste norms such as stronger son preference and a
+retraction from the formal labor market \citep{Srinivas1956}. 
 The declining female labor force participation suggests that this process still 
 operates \citep{Abraham2013,Chatterjee2018}.
+Thus, although the expansion in female education will likely bring in groups who initially 
+have different norms, we are unlikely to see substantial changes in how women with a given 
+education level behave.
 
@@
 levels.
-Furthermore, birth spacing likely increases the most among the better educated 
-because their household income increases the most---even with declining female labor 
-participation---and because of their use of sex selection.
+Furthermore, birth spacing likely increases the most among the better educated as their
+household income increase the most, and because of their use of sex selection. 
 Finally, "Sanskritization" implies that the changing composition of better-educated

### 2020-12-17 paper/sex_selection_spacing-ver5.tex
Edit Abstract

@@
 Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
-Finally, did the advent of sex-selective abortions change the relationship between infant mortality and
-birth spacing? 
+Finally, did the advent of sex-selective abortions change the relationship between birth 
+spacing and infant mortality? 
 Well-educated Hindu women with no sons had the most substantial lengthening of birth 
 intervals and the most male-biased sex ratios, likely from sex-selective abortions. 
-Hence, some women with no sons now have longer birth intervals than those with
-sons, reversing the traditional spacing pattern. 
+Consequently, some women with no sons now have longer birth intervals than those with sons, 
+reversing India's traditional spacing pattern.
 Less-educated women continued short spacing when they have girls, with only limited
 evidence of male-biased sex ratios. 
-Because of the rapid lengthening in spacing, period fertility rates substantially 
+Because of the overall lengthening in spacing, period fertility rates substantially 
 overestimated how fast cohort fertility fell. 
@@
 best-educated urban women. 
-If lengthening of birth intervals occurs from repeated abortions, the associated short 
-pregnancy spacing may counteract any positive effects of longer birth spacing. 
+If lengthening of birth intervals occurs from repeated abortions, the associated
+short pregnancy spacing may counteract any positive effects of longer birth spacing. 
 There is no evidence of this effect on infant mortality. 

### 2020-12-18 paper/sex_selection_spacing-ver5.tex
Add guidepost for empirical strategy

@@
 
+The empirical analysis has three parts. 
+First, I document the changes in birth spacing over time and how the introduction of sex 
+selection influenced birth spacing. 
+Second, I compare period fertility estimates with predicted cohort fertility based on the 
+model of birth spacing. 
+Finally, I examine how birth intervals affect infant mortality and whether the apparent 
+increase in sex selection influenced mortality.
+
+This section presents the empirical model for my analysis of birth spacing. 
 The standard approach in the birth spacing literature is to use proportional hazard

### 2020-12-18 paper/sex_selection_spacing-ver5.tex
Key independent variables in Introduction
- Also, one more birth interval length problem

@@
 
-The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals;
+The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals lengths;
 the sex ratio at birth; and the likelihood of giving birth. 
@@
 legality of sex selection. 
-The key variables are maternal education, the sex of previous children, and the area of 
-residence.
+The key independent variables are maternal education, the sex of previous children, and 
+the area of residence.
 

### 2020-12-18 paper/sex_selection_spacing-ver5.tex
Tone down sex selection claims

@@
 two exit states: The birth of a girl or the birth of a boy. 
-I apply the model to the birth histories of Hindu women covering 1972--2016 using 
-data from the four National Family and Health Surveys (NFHS).
+I apply the model to Hindu women's birth histories covering 1972--2016 using data from the 
+four National Family and Health Surveys (NFHS).
 
@@
 
-First, birth intervals lengthened over the four decades, and the lengthening was longer, 
-the higher the parity, the more educated the woman, and the higher the percentile. 
-Women most likely to use sex selection---well-educated women with no sons---had the most 
-substantial lengthening of birth intervals and the most biased sex ratios. 
-As a result, we now see cases that reverse the traditional spacing pattern, with some 
-women with no sons having \emph{longer} birth intervals than those with sons. 
-Those least likely to use sex selection---less-educated women in rural areas---still follow the 
-traditional pattern of short spacing when they have girls, with only some evidence of sex 
-selection. 
-The likelihood of a very short birth interval changed little.
-
-Second, the fertility rate substantially overestimated how fast cohort fertility fell in the 
-1990s and early 2000s as spacing began to increase. 
+First, birth intervals lengthened over the four decades, with the lengthening longer, the
+higher the parity, the more educated the woman, and the higher the percentile.
+
+First, birth intervals lengthened over the four decades, with the lengthening longer, the 
+higher the parity, the more educated the woman, and the higher the percentile. 
+Well-educated women with no sons had the most substantial lengthening of birth intervals 
+and the most male-biased sex ratios, both likely arising from sex-selective abortions. 
+Consequently, some women with no sons now have \emph{longer} birth intervals than those 
+with sons, reversing India's traditional spacing pattern. 
+Less-educated women continued with short spacing when they have girls, with only limited 
+evidence of male-biased sex ratios.
+The likelihood of a very short birth interval changed little across most groups.
+
+Second, the period fertility rate substantially overestimated how fast cohort fertility 
+fell in the 1990s and early 2000s as spacing began to increase. 
 Although the two have lately been converging, the predicted cohort fertility is still 
-10\%--20\% higher than the fertility rate. 
+10\%--20\% higher than the period fertility rate. 
 Furthermore, predicted cohort fertility is still at or above replacement level for all but 
@@
 To separate the effects of the introduction of sex selection and the other changes in
-India, I first discuss how the lengths of birth intervals have changed in situations where 
-sex selection is less used.
-The group broadly covers women with no education, regardless of the sex composition of their 
-children, and women with any education who have one or two sons already. 
-Despite the lower level of sex selection, son preference is still evident with the 
-shortest spacing when they have only girls. 
-Notably, for those least likely to use sex selection---rural women with no education---the 
-difference in birth interval length across sex compositions has grown over time as spacing when 
-sons are present has become longer.
+India, I first discuss how the lengths of birth intervals have changed in situations where, 
+based on sex ratios, there appears to be less sex selection.
+The group broadly covers women with no education, regardless of their children's sex 
+composition, and women with any education who have one or two sons already. 
+Despite the apparent lower level of sex selection, son preference is still evident with 
+the shortest spacing when they have only girls. 
+Notably, for those who appear the least likely to use sex selection---rural women with no 
+education---the difference in birth interval length across sex compositions has grown over 
+time as spacing when sons are present has become longer.
 
@@
 traditional contraceptive methods \citep{Rosenzweig1989}. 
-Hence, it is possible that the lengthening of birth intervals with falling fertility arises
-because unintended births become a relatively larger proportion of the total number of
-births for a given parity.
+Hence, it is possible that the lengthening of birth intervals with falling fertility in 
+the prior research arises because unintended births become a relatively larger proportion 
+of the total number of births for a given parity.
 
@@
 
-The 75th percentile changes are the most dramatic, but sex selection also affects the 
-25th and median birth interval lengths. 
+The 75th percentile changes are the most dramatic, but the apparent use of sex selection 
+also affects the 25th and median birth interval lengths. 
 For the best-educated urban women with two girls, the 25th percentile birth interval
@@
 
-Not surprisingly, given these effects of sex selection, the third spell for the 
-best-educated women shows the clearest reversal in the spacing pattern; 
-the birth intervals with two girls are consistently longer than the intervals with one or 
-two boys, no matter the percentile used.
+Not surprisingly, given these changes, the third spell for the best-educated women shows
+the clearest reversal in the spacing pattern; the birth intervals with two girls are
+consistently longer than the intervals with one or two boys, no matter the percentile used.
 A similar reversal, although more muted, occurred for the third spell for urban women 
@@
 selection. 
-For example, for rural women with 1--7 years of education, the sex ratios in the 
-absence of girls continued to increase while the likelihood of an additional birth remained 
+For example, for rural women with 1--7 years of education, the sex ratios in the absence 
+of daughters continued to increase while the likelihood of an additional birth remained 
 high.
@@
 These increases are larger with higher parity and higher percentile measure. 
-Furthermore, when sex selection is less used, it appears that the women least likely to 
-work are also those with the most substantial increases.
-
-Sex selection, however, is behind the most substantial increases in birth spacing. 
+Furthermore, when there is little evidence of sex selection use, it appears that the women 
+least likely to work are also those with the most substantial increases in birth interval 
+lengths.
+
+Sex selection, however, appears to be behind the most substantial increases in birth spacing. 
 The best-educated women with two girls had the most biased sex ratio and the most 
@@
 
-Consistent with a more substantial bias in the fertility rate when the age of marriage 
+Consistent with a more substantial bias in the period fertility rate when the age of marriage 
 and the length of birth intervals increase, the absolute bias is least in the first 
@@
 The final question I address is whether there is an association between infant mortality 
-and increases in birth spacing and sex selection. 
+and increases in birth spacing associated with the introduction of sex selection. 
 Starting with the sample used for estimating birth spacing, I select children born more 
@@
 I restrict the analyses to parities two and three because of the small number of births 
-and deaths for parity four. 
+and deaths at parity four. 
 Furthermore, I do not show the results for women with 12 or more years of education 
@@
 prior birth, until the 57-month dummy, which covers until 105 months after the prior birth.
-I use dummies for sex of the index child and the sex composition 
+I use dummies for the sex of the index child and the sex composition 
 of the prior children.
-The birth spacing dummies, the sex of index child, and the sex composition dummies
+The birth spacing dummies, the sex of the index child, and the sex composition dummies
 are all interacted.
@@
 
-An important caveat is that the estimations do not 
-address potential selection problems.
+An important caveat is that the estimations do not address potential selection problems.
 For example, suppose women who have diﬀiculties conceiving or carrying a pregnancy to 
@@
 Unfortunately, methods to address selection, such as family fixed effects, do not work 
-well when the number of births is as low as for better-educated women 
+well when the number of births is as low as it is here for better-educated women 
 \citep{Kozuki2013,Molitoris2019}.
@@
 effect declines with education level.
-For the best-educated women, the mortality risk is 3\%--4\%,
-whereas women with no education still show a risk that is close to 10\%.
+The mortality risk is 3\%--4\% for the best-educated women, whereas women with no 
+education still show a risk that is close to 10\%.
 
@@
 the interval between pregnancies, there is no evidence for this effect. 
-Suppose sex-selective abortions lead to higher mortality risk. In that case, boys born 
-after a girl---the solid lines---should have an increased risk with longer spacing for 
-the two highest education groups in the last two periods.
+Suppose repeated sex-selective abortions lead to a higher mortality risk for the child
+eventually born. 
+In that case, boys born after a girl---the solid lines---should have an increased risk 
+with longer spacing for the two highest education groups in the last two periods.
 However, there are no apparent consistent differences between these groups and the other 
@@
 % line 3661 in an_infant_mortality.log
-The raw numbers for women with the most uneven sex ratio also suggest that even with 
-very high use of sex selection, there is no impact on mortality. 
+The raw numbers for women with the most uneven sex ratio also suggest that even with a 
+very high apparent use of sex selection, there is no impact on mortality. 
 A total of 1,004 women with 12 or more years of education and no boys at the start of 
@@
 Of these 685 boys, only six died within the first year of life. 
-Half of those who died were born in the 9--32-month interval, and none in the 57-month+ 
-interval.
+Half of those who died were born in the 9--32-month interval, and none died in the 
+57-month+ interval.
 
@@
 sex ratio at birth as access to sex selection spread and son preference remained high. 
-Simultaneously, economic growth was strong, schooling increased, and the total
-fertility rate fell to close to the replacement level.
+Simultaneously, economic growth was strong, schooling increased, and the total fertility 
+rate declined to almost replacement level.
 
@@
 % What has happened to spacing and why
-The most substantial lengthening of birth intervals came from the best-educated women
-because of their substantial use of sex selection combined with falling fertility.
+The most substantial lengthening of birth intervals came from the best-educated women,
+likely because of substantial use of sex selection combined with falling fertility.
 Take, for example, women with 12 or more years of education who had two girls. 
-As the sex ratio increased to close to 80\% boys, the expected median birth interval length
+As the sex ratio reached almost 80\% boys, the expected median birth interval length
 increased by almost 15 months, and the 75th percentile interval length increased by 21 months.
@@
 
-Some of these increases are so large that we even observed a reversal of the traditional 
-spacing pattern for some groups; when there are no sons, we now see the longest, rather 
-than the shortest, birth intervals because of sex selection.
-The women who are the least likely to use sex selection still show the traditional 
-spacing pattern with short spacing in the absence of sons.
+Some of the lengthening in birth intervals are so large that we even observed a reversal of
+the traditional spacing pattern for some groups: 
+For these groups, when there are no sons, we now see the longest, rather than the shortest, 
+birth intervals, consistent with substantial use of sex selection.
+The women who are the least likely to use sex selection, as indicated by their sex ratios
+at birth, still show the traditional spacing pattern with short spacing in the absence of
+sons.
 
@@
 
-Birth intervals also lengthened in cases when sex selection is less likely to be used. 
+Birth intervals also lengthened in cases when sex selection appears to be less used.
 However, compared to other countries with similar declines in fertility, the median 
 spacing increases were smaller at three to six months over the period. 
-Most of the median intervals when sex selection is less used are still short at 36 months 
-or below. 
+Most of the median intervals when sex ratios are close to normal are still short at 36 
+months or below. 
 Furthermore, many women still have very short birth intervals.
-In many cases, more than 25\% have their next child within 24 months of the previous 
-birth.
+More than 25\% of women have their next child within 24 months of the previous birth in 
+many cases.
 
@@
 evidence of this. 
-The original users of sex selection continue to show substantial male-biased sex ratios, 
+The most likely users of sex selection continue to show substantial male-biased sex ratios, 
 although there may be some leveling off.
-More concerning, sex selection appears to be spreading to less educated women as their 
-fertility is falling.
+More concerning, the increasingly male-biased sex ratios among less-educated women suggest
+that sex selection use appears to be spreading as fertility falls.
 
@@
 fertility. 
-This bias was most prominent early in the spread of sex selection when the fertility rate 
-was up to one child lower than the predicted cohort fertility. 
+This bias was most prominent early in the spread of access to sex selection when the 
+fertility rate was up to one child lower than the predicted cohort fertility. 
 However, it is still present, with the predicted cohort fertility 10\%--20\% 
@@
 There is no evidence that repeated abortions are associated with higher infant mortality
-for the child eventually born.
+for the child eventually born; boys born after long birth intervals to families with
+well-educated mothers, only daughters, and high predicted sex ratios, the combination of
+which suggests repeated sex-selective abortions, have no higher infant mortality than other
+children.
 

### 2020-12-19 paper/sex_selection_spacing-ver5.tex
Specify that sex selection is inferred

@@
 for the child eventually born; boys born after long birth intervals to families with
-well-educated mothers, only daughters, and high predicted sex ratios, the combination of
-which suggests repeated sex-selective abortions, have no higher infant mortality than other
+well-educated mothers, only daughters, and high predicted sex ratios---the combination of
+which suggests repeated sex-selective abortions---have no higher infant mortality than other
 children.
@@
 in population growth than generally accepted. 
-With predicted cohort fertility still substantially higher than the fertility rate, 
+With predicted cohort fertility still substantially higher than the period fertility rate, 
 India's total fertility rate will likely stabilize or even increase as birth intervals slow 
@@
 There are two critical questions that future research should address.
-First, sex selection means that girls-only families are less likely to have
+First, access to sex selection means that girls-only families are less likely to have
 very short birth intervals, which may reduce sibling competition. 
-Hence, better health outcomes for girls with sex selection could be an unintended 
-side-effect, rather than the result of girls becoming more valued as is often 
+Hence, better health outcomes for girls with sex selection is available could be an 
+unintended side-effect, rather than the result of girls becoming more valued as is often 
 assumed \citep{Hu2015}. 
@@
 them more likely to have a boy and increases the expected birth spacing. 
-Better job opportunities for women would affect sex selection for two reasons. 
-First, it makes it more expensive to be out of the labor market for long periods. 
-Second, it would moderate the differential in potential earnings between husband and wife 
-and make it more attractive to invest in daughters' human capital. 
+Better job opportunities for women could reduce sex selection use for two reasons. 
+First, it becomes more expensive to be out of the labor market for long periods. 
+Second, the differential in potential earnings between husband and wife would decline, 
+making it more attractive to invest in daughters' human capital.  
 This approach could, however, be a double-edged sword. 

### 2020-12-19 paper/sex_selection_spacing-ver5.tex
Add measure of education paragraph to Data

@@
 First, Hindus are the majority population group, about 80\% of India’s population.
-Second, the prior literature shows that son preference and use of sex selection vary 
+Second, the prior literature shows that son preference and sex selection vary 
 substantially between Hindus and the second largest group, Muslims. 
@@
 Because of space constraints and the relatively small number of observations once split 
-by education and periods, I do not provide separate results for Muslims or any of the 
+by education and periods, I do not provide separate results for Muslims or any  
 remaining groups, such as Sikhs, Jains, and Christians.
@@
 
-In addition to a large number of women surveyed and the long period covered, a significant 
+In addition to the large number of women surveyed and the long period covered, a significant 
 benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
@@
 
-Direct information on the use of sex selection is not available, so I compare periods 
+Direct information on sex selection is not available, so I compare periods 
 based on the changes in access and legality of prenatal sex determination in India.
@@
 These spells, therefore, do not show up in the samples used. 
-Furthermore, sterilization depends strongly on the sex composition of prior children
-with lower probabilities, the fewer boys. 
+Furthermore, sterilization depends strongly on prior children's sex composition; the 
+fewer boys, the lower the probability of sterilization. 
 The effect is to bias downward the differences in parity progression probabilities.
@@
 than including education as a variable.
+
+I divide education levels into four groups: No education, 1--7 years, 8--11 years, and 
+12 and more years.
+The latter two correspond to having completed primary and secondary school, 
+respectively.%
+\footnote{
+Although there are variations by state, elementary education in India consists of a 
+primary school covering grades one through five and an upper primary---or middle 
+school---covering grades six through eight. 
+Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
+and 11 and 12 for ``upper secondary.''
+}
+To ensure that the results are comparable with the prior literature on fertility
+and mortality in India, I follow the NFHS reports, except that I combine the 
+less than five years and 5--7 years of schooling completed and the 8--9 
+and 10--11 years of schooling completed to ensure sufficient cell sizes.
+
 I capture sex composition with dummy variables for the possible combinations, ignoring 
@@
 land ownership, and whether it belongs to a scheduled tribe or caste.
-Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present descriptive statistics.
+Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present the descriptive 
+statistics.
 

### 2020-12-20 paper/sex_selection_spacing-ver5.tex
Update Table titles and footnotes and clean up comments
Discuss statistical significance in birth spacing differences

@@
 \citep{ben-porath76b,jacobsen99,Portner2015b}.
-The underlying values with bootstrapped standard errors are available in the online 
-appendix.
+The underlying values with bootstrapped standard errors and tests for statistically
+significant differences across sex compositions are available in the online appendix.
 
@@
 become more male-dominated for women with no sons.
-The percentage of births that were boys increased more quickly, the higher the education and the 
-higher the parity.
+The percentage of births that were boys increased more quickly, the higher the education 
+and the higher the parity.
 There are no clear trends for the other sex compositions.
@@
 composition, and women with any education who have one or two sons already.
+
 Despite the apparent lower level of sex selection, son preference is still evident with 
@@
 Notably, for those who appear the least likely to use sex selection---rural women with no
-education---the difference in birth interval length across sex compositions has grown over 
+education---birth spacing is almost uniformly statistically significantly longer when at
+least one son is present than if no son is present. 
+Furthermore, the difference in birth interval length across sex compositions has grown over
 time as spacing when sons are present has become longer.
@@
 With two girls, almost 80\% of the third births are boys, and the 75th percentile 
-birth interval length is close to 70 months. 
-This interval is about 13 months longer than if they had at least one son and represents 
-an increase of almost 21 months over the four decades.
+birth interval length is close to 70 months, an increase of almost 21 months over the four
+decades. 
+This interval has gone from being statistically significantly shorter than the intervals 
+with at least one son to now being a statistically significant 13 months longer.
 
@@
 the clearest reversal in the spacing pattern; the birth intervals with two girls are
-consistently longer than the intervals with one or two boys, no matter the percentile used.
+consistently statistically significantly longer than the intervals with one or two boys, 
+no matter the percentile used.
 A similar reversal, although more muted, occurred for the third spell for urban women 
@@
 
-Sex selection, however, appears to be behind the most substantial increases in birth spacing. 
+However, sex selection appears to be behind the most substantial increases in birth spacing. 
 The best-educated women with two girls had the most biased sex ratio and the most 
@@
 Over the four decades, the median birth interval length for this group increased by almost
-15 months, 
-and the 75th percentile birth interval length increased by a staggering 21 months, most of 
-that within a decade.
+15 months. 
+Even more striking, the 75th percentile birth interval length increased by a staggering 21
+months, most of that within a decade of the introduction of sex selection.
 
@@
 I also examine two related questions.
-First, did the changes in birth spacing bias the standard fertility estimates for India? 
+First, did changes in birth spacing make us overestimate the decline in cohort fertility?
 Second, what is the relationship between infant mortality and the changes in birth spacing 
@@
 increased by almost 15 months, and the 75th percentile interval length increased by 21 months.
-Most of the increase in the long intervals came immediately after the introduction of sex 
+Most of the lengthening in the long intervals came immediately after the introduction of sex 
 selection in India.
@@
 the traditional spacing pattern for some groups: 
-For these groups, when there are no sons, we now see the longest, rather than the shortest, 
-birth intervals, consistent with substantial use of sex selection.
+For these groups, when there are no sons, we now see statistically significant longer,
+rather than statistically significant shorter, birth intervals than if there is at least
+one son.
 The women who are the least likely to use sex selection, as indicated by their sex ratios
@@
 \clearpage
-
-% \begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-% \captionsetup{font=footnotesize,skip=2pt}
-% \centering
-% \caption*{No education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_urban}}
-% \\
-% \caption*{One to Seven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_urban}}
-% \\
-% \caption*{Eight to Eleven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_urban}}
-% \\
-% \caption*{Twelve or More Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_urban}}
-% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-% \captionsetup{font=normalsize}
-% \caption{
-% Changes in 25th Percentile Birth Intervals for Urban Women by Spell and Education
-% }
-% \label{fig:p25_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-% \captionsetup{font=footnotesize,skip=2pt}
-% \centering
-% \caption*{No education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_low_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_low_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_low_rural}}
-% \\
-% \caption*{One to Seven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_med_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_med_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_med_rural}}
-% \\
-% \caption*{Eight to Eleven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_high_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_high_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p25_spell4_high_rural}}
-% \\
-% \caption*{Twelve or More Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p25_spell2_highest_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p25_spell3_highest_rural}}
-% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-% \captionsetup{font=normalsize}
-% \caption{
-% Changes in 25th Percentile Birth Intervals for Rural Women by Spell and Education
-% }
-% \label{fig:p25_rural}
-% \end{figure}
-% 
-% \begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-% \captionsetup{font=footnotesize,skip=2pt}
-% \centering
-% \caption*{No education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_urban}}
-% \\
-% \caption*{One to Seven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_urban}}
-% \\
-% \caption*{Eight to Eleven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_urban}}
-% \\
-% \caption*{Twelve or More Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_urban}}
-% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-% \captionsetup{font=normalsize}
-% \caption{
-% Changes in 50th Percentile Birth Intervals for Urban Women by Spell and Education
-% }
-% \label{fig:p50_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-% \captionsetup{font=footnotesize,skip=2pt}
-% \centering
-% \caption*{No education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_low_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_low_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_low_rural}}
-% \\
-% \caption*{One to Seven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_med_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_med_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_med_rural}}
-% \\
-% \caption*{Eight to Eleven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_high_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_high_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{p50_spell4_high_rural}}
-% \\
-% \caption*{Twelve or More Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{p50_spell2_highest_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{p50_spell3_highest_rural}}
-% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-% \captionsetup{font=normalsize}
-% \caption{
-% Changes in 50th Percentile Birth Intervals for Rural Women by Spell and Education
-% }
-% \label{fig:p50_rural}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-% \captionsetup{font=footnotesize,skip=2pt}
-% \centering
-% \caption*{No education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_urban}}
-% \\
-% \caption*{One to Seven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_urban}}
-% \\
-% \caption*{Eight to Eleven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_urban}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_urban}}
-% \\
-% \caption*{Twelve or More Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_urban}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_urban}}
-% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-% \captionsetup{font=normalsize}
-% \caption{
-% Changes in Average Birth Intervals for Urban Women by Spell and Education
-% }
-% \label{fig:avg_urban}
-% \end{figure}
-% 
-% 
-% \begin{figure}[htpb]
-% \captionsetup[subfigure]{labelformat=empty,position=top}
-% \captionsetup{font=footnotesize,skip=2pt}
-% \centering
-% \caption*{No education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_low_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_low_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_low_rural}}
-% \\
-% \caption*{One to Seven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_med_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_med_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_med_rural}}
-% \\
-% \caption*{Eight to Eleven Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_high_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_high_rural}}
-% \subfloat[][Fourth Spell]{\includegraphics[width=0.32\textwidth]{avg_spell4_high_rural}}
-% \\
-% \caption*{Twelve or More Years of Education}
-% \subfloat[][Second Spell]{\includegraphics[width=0.32\textwidth]{avg_spell2_highest_rural}}
-% \subfloat[][Third Spell]{\includegraphics[width=0.32\textwidth]{avg_spell3_highest_rural}}
-% \begin{minipage}{0.32\textwidth}\hspace{1cm}\end{minipage}
-% \captionsetup{font=normalsize}
-% \caption{
-% Changes in Average Birth Intervals for Rural Women by Spell and Education
-% }
-% \label{fig:avg_rural}
-% \end{figure}
-
-\clearpage
 \newpage
-
-% \section{Survival Curves Conditional on Parity Progression for All Education and Spell Groups}
-% 
-% \setcounter{figure}{0}
-% \setcounter{table}{0}
-% 
-% 
-% % [FIRST SPELL]
-% 
-% % \subsection{First Spell}
-% % 
-% % \input{../figures/appendix_spell1_low.tex}
-% % 
-% % \input{../figures/appendix_spell1_med.tex}
-% % 
-% % \input{../figures/appendix_spell1_high.tex}
-% % 
-% % \begin{figure}[htpb]
-% % \centering
-% % \caption*{No Education}
-% % \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
-% % \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
-% % \caption*{1-7 Years of Education}
-% % \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
-% % \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
-% % \caption*{8 or more Years of Education}
-% % \subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_highest_urban_pps}} 
-% % \subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_highest_rural_pps}} 
-% % \caption{Survival curves conditional on progression to first birth; start point is month of marriage}
-% % \label{fig:results_spell1_pps}
-% % \end{figure}
-% % 
-% % 
-% % \clearpage
-% % \newpage
-% % 
-% \subsection{Second Spell}
-% 
-% 
-% % \input{../figures/appendix_spell2_low.tex}
-% 
-% 
-% % PARITY PROGRESSION SURVIVAL CURVES - Low
-% 
-% % Low education
-% \vspace*{-0.75cm}
-% \begin{figure}[hp!]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2005]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with no education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell2_low_pps}
-% \end{figure}
-% 
-% 
-% 
-% 
-% % SPELL 2 - URBAN - MEDIUM
-% 
-% % \input{../figures/appendix_spell2_med.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - MEDIUM
-% 
-% 
-% % Low education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.32\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with 1-7 years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell2_med_pps}
-% \end{figure}
-% 
-% 
-% 
-% % High education
-% 
-% % \input{../figures/appendix_spell2_high.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - High education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with eight to eleven years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell2_high_pps}
-% \end{figure}
-% 
-% 
-% % Highest education
-% 
-% % PARITY PROGRESSION SURVIVAL - Highest education
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_highest_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_highest_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_highest_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_highest_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with twelve or more years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell2_highest_pps}
-% \end{figure}
-% 
-% 
-% \clearpage
-% \newpage
-% 
-% \subsection{Third Spell}
-% 
-% % low education
-% % \input{../figures/appendix_spell3_low.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - LOW
-% \vspace*{-0.75cm}
-% \begin{figure}[hp!]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with no education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell3_low_pps}
-% \end{figure}
-% 
-% 
-% 
-% 
-% % Medium education
-% 
-% % \input{../figures/appendix_spell3_med.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - MEDIUM
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell3_med_pps}
-% \end{figure}
-% 
-% 
-% 
-% 
-% % High education
-% 
-% % \input{../figures/appendix_spell3_high.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - high
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with eight to eleven years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell3_high_pps}
-% \end{figure}
-% 
-% 
-% % Highest education
-% 
-% % PARITY PROGRESSION SURVIVAL - highest
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_highest_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_highest_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_highest_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_highest_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with twelve or more years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell3_highest_pps}
-% \end{figure}
-% 
-% 
-% 
-% 
-% 
-% \clearpage
-% \newpage
-% 
-% \subsection{Fourth Spell}
-% 
-% % low education
-% 
-% % \input{../figures/appendix_spell4_low.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - LOW
-% \vspace*{-0.75cm}
-% \begin{figure}[hp!]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with no education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell4_low_pps}
-% \end{figure}
-% 
-% 
-% 
-% 
-% % Medium education
-% 
-% % \input{../figures/appendix_spell4_med.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - MEDIUM
-% 
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_med_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with 1 to 7 years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell4_med_pps}
-% \end{figure}
-% 
-% 
-% 
-% % High education
-% 
-% % \input{../figures/appendix_spell4_high.tex}
-% 
-% % PARITY PROGRESSION SURVIVAL - high
-% 
-% \begin{figure}[htpb]
-% \centering
-% \caption*{Urban}
-% \setcounter{subfigure}{-1}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_urban_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{-0}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{1}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{2}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_urban_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption*{Rural}
-% \setcounter{subfigure}{3}
-% \subfloat[1972--1984]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_rural_pps}} 
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } 
-% \setcounter{subfigure}{4}
-% \subfloat[1985--1994]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% } \\
-% \setcounter{subfigure}{5}
-% \subfloat[1995--2004]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{6}
-% \subfloat[2005--2016]{
-%     \begin{minipage}{0.31\textwidth}
-%         \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_high_rural_pps}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \caption{Survival curves conditional on parity progression
-% for women with eight to eleven years of education by month beginning 9 months after prior birth.
-% }
-% \label{fig:results_spell4_high_pps}
-% \end{figure}
-% 
-% 
-% \clearpage
-% \newpage
-%
 
@@
 \setcounter{table}{0}
-
-% \captionsetup[figure]{skip = 5pt}
 
@@
 
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p1_low_dummies} 
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p2_low_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p3_low_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p4_low_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Infant Mortality for women with no education}
-% \label{fig:mortality_low}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Infant Mortality for women with one to
-% seven years of education}
-% \label{fig:mortality_med}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Infant Mortality for women with eight
-% to eleven years of education}
-% \label{fig:mortality_high}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Third Spell]{
-%     \begin{minipage}{0.40\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Infant Mortality for women with twelve or
-% more years of education}
-% \label{fig:mortality_highest}
-% \end{figure}
-
 \end{document}

### 2020-12-20 response/response-demography-4.tex
Initial commit of 4th response to Demography

\documentclass[letterpaper,12pt]{article}

% Xetex preamble
\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}

\usepackage[longnamesfirst]{natbib}
%\usepackage[tabhead,nolists,tablesfirst]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{rotating}  
\usepackage{dcolumn} 
\usepackage{setspace}
%\usepackage{flafter} 
%\usepackage{longtable}
%\usepackage[pdftex]{graphicx}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black]{hyperref} 
\usepackage[margin=1.0in]{geometry} 
\usepackage{multirow}

%opening
\title{} \author{}

\doublespacing

\begin{document}

\begin{center} \textbf{\large Birth Spacing in the Presence of Son
Preference and 
Sex-Selective Abortions: India's Experience over Four Decades}
\end{center}

\begin{center} Response to Editor Comments \end{center}

\noindent I have attached the revised version of my paper,
``Birth Spacing and Fertility in the Presence of Son Preference and Sex-Selective
Abortions: India's Experience Over Four Decades.''
Thank you for the comments and suggestions. 
Below I outline my response to each issue raised.

The author has undertaken much reorganization and has made very useful clarifications to
benefit the reader in the text and tables. Nevertheless, we still find three issues with
the writing style:

(1) Explanations of key concepts or theories need to be spelled out more clearly,
particularly for the non-economist. Much has been done in this regard, but further work is
still needed.

(2) The arguments do not flow from section to section and paragraph to paragraph. Each
section and argument need to be introduced so the reader understands why this information
is being presented in this place. Many times, the author jumps into new arguments without
an introduction or transition or explanation.

(3) There is no clear outline of the arguments presented in the Background section. Each
argument is presented separately rather than tying into the overall framework and
subsequent analyses.

The following are some examples of (1) and (2); however, the author should check the entire
paper for similar issues and address (3) as well.

1. In general, each argument in the background section is not clear and fully described for
the reader.

a. P. 4 first sentence: The author states that female education is a crucial explanatory
variable and it matters for fertility, sex ratios, mortality, etc. in a list. It would be
useful for the reader to briefly spell out how female education fits into the entire
framework looking across all these outcomes. In addition, the second paragraph on
measurement of education seems like it belongs in the data section, unless there is some
conceptual reason why this information is included here.

b. The 2 paragraphs on female labor force participation on pp. 5-6: The two findings that
support the argument that changes in birth spacing are not due to economic reasons are
merely listed, leaving the reader to make the connection as to why these facts support the
argument herself. The income effect dominating the substitution effect and greater negative
elasticity of women’s wages need to be explained to readers unfamiliar with these concepts
or how they fit together.

c. P. 6 regarding sex selection: “The introduction of sex selection allows parents to avoid
giving birth to girls but increases the expected interval to the next birth.” The reader
needs an explanation here of why sex selection increases birth interval length. The author
mentions waiting time to conception and other components in the introduction (and
footnote). A clear explanation of this argument needs to be reiterated (or moved) here.

d. P. 6: “As women’s education increases, their productivity in the production of offspring
human capital also increases. With relatively more boys born because of increased access to
sexselective abortions and the increasing income potential for (male) offspring, demand for
bettereducated women can increase, even if they do not participate in the labor market.” I
am unclear as to why this argument is included. It needs explanation. Is this related to
length of birth intervals here? Or is this mentioned because women’s education and
increasing demand for better-education women will actually lower the sex ratio?

e. Pp. 6-7: I do not understand the importance of this argument and how it fits into the
authors’ story: “If more and “better” parental attention per child results in higher child
“quality,” we should expect longer birth intervals. However, the evidence on spacing’s
effect on child quality measures such as IQ and education is mixed for developed countries
and nonexisting for developing countries. The exception is health and mortality, where
longer spacing does lead to better outcomes, although this relationship weakens with
maternal education.”

f. P. 7: The final summary paragraph lists predictions based on the earlier arguments. Yet
it is hard to connect these predictions to the paragraphs above. Perhaps predictions could
be noted with the earlier arguments.

2. Estimation strategy section.

In the first paragraph, it would be useful to clearly outline the analyses that will be
undertaken (such as first, I document changes in birth intervals over time and how
influenced by sex selection, second how birth intervals affected fertility, and third how
birth intervals affected mortality). As it stands, this section jumps into a discussion of
the hazard model and the reader does not know in which analyses it will be used.

Some additional issue as examples where more clarification is needed:

3. Abstract. Please reorganize to start with a statement of the problem and main aims of
the study. As it stands, the abstract is a list of findings, with no context as to the
issues/questions the author investigates. Please be cognizant of using terms such as “women
most likely to use sexselective abortion.” The reader does not understand how this is
measured yet, and may get the false impression that sex-selection abortion is measured
directly.

4. P. 1: The second motivation is unclear. “the combined changes in birth spacing may
outpace what we have observed in other countries.” Outpaced means what? decreasing faster,
or increasing faster, or sex selection plays more of a role?

5. Throughout the paper, the author compares the total fertility rate to cohort fertility
rate. For the former, is the period fertility rate a more accurate definition?

6. P. 2: the main point of this sentence is unclear: “Counteracting effect is possible if
longer birth intervals arise from multiple abortions because the short duration between
pregnancies could increase mortality.”

7. Sometimes the use of the term “birth interval” actually refers to “birth interval
length.” Please check the uses of these terms and correct accordingly.

8. P. 2: “The key variables are maternal education, the sex of previous children, and the
area of residence.” Does the author mean key independent or predictor variables?

9. The author should clearly note that sex selection is not observed and tone down some
conclusions, such as “Sex selection, however, is behind the most substantial increases in
birth spacing. The best-educated women with two girls had the most biased sex ratio and the
most significant increase in birth intervals.” The author could say that sex selection
appears to be behind these findings; or evidence suggests that sex selection is behind
these findings, etc. In addition, clarify that those most likely to practice sex selection
(women with highest education and two girls) is based on your analysis, not settled in the
literature.

10. While it might be messy to show the confidence intervals in all the figures, is it
possible to note some significant differences in the text?

\newpage
\bibliographystyle{econometrica}
\bibliography{../paper/sex_selection_spacing.bib}
\addcontentsline{toc}{section}{References}

\end{document}

### 2020-12-21 paper/sex_selection_spacing-ver5.tex
Begin final round of editing

@@
 I examine three questions.
-First, how did birth spacing respond to this and other secular developments? 
+First, how did birth spacing change with this and other secular developments? 
 Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
@@
 The motivation is twofold.
-First, past research has failed to appreciate that the growing use of sex-selective 
-abortions may substantially increase birth spacing; as detailed below, it takes 6 months 
-or more after an abortion to reach the same point in the next pregnancy.
-Second, women's greater educational attainment, higher household income, but low and 
-declining female labor force participation all likely influence birth spacing. 
-The combination of the increasing use of sex selection and the other societal changes 
-can significantly impact birth spacing, but we know little about how much.
+First, past research has failed to appreciate that the use of sex-selective abortions could 
+substantially increase birth spacing. 
+As detailed below, it takes 6 months or more after an abortion to reach the same point in 
+the next pregnancy. 
+Second, other societal changes, such as women's greater educational attainment, higher 
+household income, and a low and declining female labor force participation, all 
+likely influence birth spacing. 
+The combination of the apparent increasing use of sex selection and the other societal 
+changes can significantly impact birth spacing, but we know little about how much.
 
@@
 
-First, did changes in birth spacing make us overestimate the decline in cohort fertility?
+First, did changes in birth spacing lead us to overestimate the decline in cohort fertility?
 With longer spacing, mothers will be older at each parity, and this tempo effect 
@@
 most used fertility measure---fall substantially faster than cohort fertility.
-In this case, households' fertility goals may be higher than generally accepted.
+In this case, households' fertility may be higher than generally accepted.
 
@@
 Hence, children born after long birth intervals where multiple abortions have punctuated 
-those intervals may not see the same benefits as a child born after a long interval that 
+those intervals may not see the same benefits as children born after a long interval that 
 is not punctuated by abortions.
@@
 
-The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals lengths;
+The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals 
+durations;
 the sex ratio at birth; and the likelihood of giving birth. 
@@
 legality of sex selection. 
-The key independent variables are maternal education, the sex of previous children, and 
+The key explanatory variables are maternal education, the sex of previous children, and 
 the area of residence.
@@
 There are three main results.
-
-First, birth intervals lengthened over the four decades, with the lengthening longer, the
-higher the parity, the more educated the woman, and the higher the percentile.
 
@@
 with sons, reversing India's traditional spacing pattern. 
-Less-educated women continued with short spacing when they have girls, with only limited 
+Less-educated women continued to have short spacing when they have girls, with only limited 
 evidence of male-biased sex ratios.
@@
 Second, the period fertility rate substantially overestimated how fast cohort fertility 
-fell in the 1990s and early 2000s as spacing began to increase. 
+fell in the 1990s and early 2000s as spacing initially increased. 
 Although the two have lately been converging, the predicted cohort fertility is still 
@@
 I first introduce three potential explanations that link fertility and birth 
-spacing decisions: economic conditions, desired child outcomes, and son preference 
+spacing decisions: economic conditions, investment in children, and son preference 
 \citep{Casterline2016,Portner2018}.
-Next, I discuss why female education and area of residence are the principal factors 
-in the empirical analyses and how they tie into the three explanations.
+Next, I discuss why female education, area of residence, and sex composition are the
+principal factors in the empirical analyses and tie them into the three explanations.
 
@@
 
-% Child outcomes
+% Investment in children
 With increasing returns to education and lower offspring mortality, parents are likely to 
@@
 The higher return to education means a stronger incentive to invest in their children's
-education, which increases the cost of having children, thereby lowering fertility. 
+education, thereby increasing the cost of having children and lowering fertility. 
 With lower expected mortality, parents need fewer births to reach the desired number of
-surviving children, allowing parents to invest more in each child.
-
-An increased desire for better child outcomes will also tend to lengthen birth spacing,
-provided it has positive effects on child outcomes.
-The clearest example of a positive effect of longer spacing that very short 
+surviving children, which, in turn, allows parents to invest more in each child.
+
+An increased desire to invest in children may also lengthen birth spacing, provided it has 
+positive effects on child outcomes. 
+The clearest example of a positive effect of longer spacing is for health as very short 
 spacing---approximately 24 months or less---leads to worse child health and mortality 
@@
 pregnancy as they were in the prior pregnancy when they decided to abort.
+
+[HERE!]
 

### 2020-12-24 paper/sex_selection_spacing-ver5.tex
Additional edits

@@
 
-[HERE!]
-
-The use of sex selection, and therefore the length of birth intervals, increases with
-lower desired fertility and with parity, provided the desired number of sons has 
-not been reached \citep{Portner2015b,Jayachandran2017}.
-
 % Factors/predictions
-I use female education and area of residence as the two principal explanatory variables in
-the empirical analyses because those are the two closest proxies available in the data to
-cover the explanations above. 
-Prior research shows that both higher female education and urbanization are associated with 
-lower fertility and increased sex selection use, and, therefore, likely also changes birth spacing
-\citep{das_gupta97,dreze01,bhat03,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
-Furthermore, both variables are of interest, given the tremendous changes in India. 
+The closest available proxies in the data for capturing the explanations linking
+fertility and birth spacing are the sex composition of previous children, mothers'
+education, and area of residence. 
+The remainder of the section discusses how the three variables tie into the
+explanations and the predicted effects.
+
+Sex composition proxies for son preference and the use of
+sex selection, both unobserved.%
+\footnote{
+The surveys ask about the ideal number of sons and 
+daughters, but these appear to be unreliable son 
+preference indicators; better-educated women simultaneously show 
+declining son preference and increasing sex selection 
+\citep{bhat03,pande07}.
+} 
+In the absence of sons, sex selection appears to increase 
+with lower desired fertility and higher parity
+\citep{Portner2015b,Jayachandran2017}. 
+Thus, for a given parity, birth intervals should lengthen 
+substantially over time for women with no sons, lower 
+desired fertility, and better access to sex selection.
+
+Both higher female education and urbanization are associated with 
+lower fertility and increased sex selection use, and, therefore, likely also changes in birth spacing
+\citep{das_gupta97,retherford03b,Portner2015b}.
+Furthermore, both variables are representative of
+the tremendous changes in India. 
 Figure \ref{fig:education_over_time} shows the substantial increase in female education,
@@
 has decreased over time.
-The likelihood of a next birth fell more rapidly, the higher the education, the higher the 
-parity, and with at least one son.
+The likelihood of a next birth fell more rapidly, the higher the education and the 
+higher the parity.
 Within a given spell and period, parity progressions are lower in urban than rural areas, 
@@
 % [Sex ratios]
-Second, 
-the spread of sex selection shows clearly in the sex ratios of next births, which has 
-become more male-dominated for women with no sons.
-The percentage of births that were boys increased more quickly, the higher the education 
-and the higher the parity.
+Second, sex ratios have become more male-dominated for women with no sons, indicating the spread 
+of sex selection. 
+The percentage of boys increased more quickly, the higher the education and the higher the parity. 
 There are no clear trends for the other sex compositions. 
-Within a given spell and period combination and in the absence of a son, sex ratios are higher 
-the more educated the mother is and with higher parity. 
-Sex ratios are also higher in urban than in rural areas.
+Within a given spell and period combination and in the absence of a son, sex ratios are higher, 
+the more educated the mother, and the higher the parity. Sex ratios are also higher in urban than 
+in rural areas.
 Some women with one son also show an unnaturally high percentage of boys, although the 
@@
 Hence, there is now little difference in mortality risk across education groups if the 
-birth took place more than 21 months from the prior birth.
+birth took place more than 21 months after the previous birth.
 Short birth spacing is still associated with higher mortality, although the effect is 
@@
 Second, the differential in potential earnings between husband and wife would decline, 
-making it more attractive to invest in daughters' human capital.  
+making it relatively more attractive to invest in daughters' human capital.  
 This approach could, however, be a double-edged sword. 

### 2020-12-24 paper/sex_selection_spacing-ver5.tex
Yet another abstract

@@
 
-\noindent India has experienced an increasingly male-biased sex ratio at birth following
-the introduction of prenatal sex determination techniques. 
-I examine three questions.
-First, how did birth spacing change with this and other secular developments? 
-Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
-Finally, did the advent of sex-selective abortions change the relationship between birth 
-spacing and infant mortality? 
-Well-educated Hindu women with no sons had the most substantial lengthening of birth 
-intervals and the most male-biased sex ratios, likely from sex-selective abortions. 
-Consequently, some women with no sons now have longer birth intervals than those with sons, 
-reversing India's traditional spacing pattern.
-Less-educated women continued short spacing when they have girls, with only limited
-evidence of male-biased sex ratios. 
-Because of the overall lengthening in spacing, period fertility rates substantially 
-overestimated how fast cohort fertility fell. 
-Furthermore, predicted cohort fertility remains above replacement for all but the 
-best-educated urban women. 
-If lengthening of birth intervals occurs from repeated abortions, the associated
-short pregnancy spacing may counteract any positive effects of longer birth spacing. 
-There is no evidence of this effect on infant mortality. 
+% \noindent India has experienced an increasingly male-biased sex ratio at birth following
+% the introduction of prenatal sex determination techniques. 
+% I examine three questions.
+% First, how did birth spacing change with this and other secular developments? 
+% Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
+% Finally, did the advent of sex-selective abortions change the relationship between birth 
+% spacing and infant mortality? 
+% Well-educated Hindu women with no sons had the most substantial lengthening of birth 
+% intervals and the most male-biased sex ratios, likely from sex-selective abortions. 
+% Consequently, some women with no sons now have longer birth intervals than those with sons, 
+% reversing India's traditional spacing pattern.
+% Less-educated women continued short spacing when they have girls, with only limited
+% evidence of male-biased sex ratios. 
+% Because of the overall lengthening in spacing, period fertility rates substantially 
+% overestimated how fast cohort fertility fell. 
+% Furthermore, predicted cohort fertility remains above replacement for all but the 
+% best-educated urban women. 
+% If lengthening of birth intervals occurs from repeated abortions, the associated
+% short pregnancy spacing may counteract any positive effects of longer birth spacing. 
+% There is no evidence of this effect on infant mortality. 
+% Finally, judging from sex ratios, sex-selective abortion use is not declining.
+
+\noindent Following the arrival of prenatal sex-determination technologies in the mid-1980s, 
+India has experienced an increasingly male-biased sex ratio at birth, presumably from sex-selective 
+abortions. 
+Abortions lengthen birth intervals, but we know little about how birth spacing has changed or the 
+effects of these changes. 
+This paper shows that the length of birth intervals has increased overall, but well-educated women 
+with no sons had the most substantial lengthening---and the most male-biased sex ratios. 
+Furthermore, most of the changes took place immediately after the introduction of sex-selective abortions. 
+Consequently, some women without sons now have longer birth intervals than those with sons, reversing 
+India's traditional spacing pattern. 
+Less-educated women continue short birth spacing when they have no sons, with only limited evidence 
+of male-biased sex ratios. 
+Because of the rapid lengthening of birth intervals, period fertility rates substantially overestimated 
+how fast cohort fertility fell. 
+Moreover, predicted cohort fertility is still 10\%--20\% above the period fertility rate. 
+If lengthening of birth intervals occurs from repeated abortions, the associated short pregnancy spacing 
+may counteract any positive effects of longer birth spacing. 
+There is, however, no evidence of this effect on infant mortality. 
 Finally, judging from sex ratios, sex-selective abortion use is not declining.

### 2020-12-27 paper/sex_selection_spacing-ver5.tex
Edited abstract and added transition/introduction paragraphs

@@
 effects of these changes. 
-This paper shows that the length of birth intervals has increased overall, but well-educated women 
+This paper shows that, although the length of birth intervals increased overall, well-educated women 
 with no sons had the most substantial lengthening---and the most male-biased sex ratios. 
-Furthermore, most of the changes took place immediately after the introduction of sex-selective abortions. 
+Furthermore, most of these changes took place immediately after the introduction of prenatal 
+sex-determination technologies. 
 Consequently, some women without sons now have longer birth intervals than those with sons, reversing 
@@
 increase in sex selection influenced mortality. 
-
 This section presents the empirical model for my analysis of birth spacing.
+
 The standard approach in the birth spacing literature is to use proportional hazard
-models with a single exit---the birth of a child.%
+models with a single exit---the birth of a child---but there are two problems with the 
+standard approach in this setting.%
 \footnote{
@@
 }
-There are two problems with the standard approach in this setting.
 
@@
 
+I first discuss sample restrictions and their motivations, then introduce the potential 
+issue of underreporting of female births and the imposed censoring of birth intervals.
+Next, I discuss how the analyses are split by periods to capture the introduction
+and changing legality in prenatal sex determination.
+Finally, I introduce the explanatory variables, split by whether they enter as
+proportional or nonproportional variables.
+
 I focus on the three spells starting from the first birth and ending with the 
@@
 changes in India.
+I begin with a broad outline of how parity progression probabilities and
+sex ratios have changed over time and by groups.
+I then use these results to separately discuss the changes in birth spacing for 
+women who do not appear to use sex selection and for those who do.
+
 Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}

### 2020-12-27 response/response-demography-4.tex
Initial complete response

@@
 
+RESPONSE: With the reorganization of the Conceptual Framework section described below, I now 
+have an early paragraph that explains income and substitution effects in detail and how they 
+tie into fertility decisions with increasing wages for both males and females.
+I then rely on this detailed explanation for my later discussions of female education and
+labor force participation.
+Furthermore, I have provided additional explanations for decisions on investment in children 
+based on the expected return to investment in their education.
+Finally, I have reorganized my discussion of increased demand for mothers with more education
+even in the presence of declining female labor force participation to make it clearer for
+non-economists.
+
 (2) The arguments do not flow from section to section and paragraph to paragraph. Each
@@
 
+RESPONSE: As detailed below, I have completely reorganized the Conceptual Framework section
+to create a better flow and make it easier for the reader to follow.
+Furthermore, I have added introductory paragraphs to the sections that did not already 
+have these or an equivalent transition ("Conceptual Framework", "Estimation Strategy", "Data", 
+and "How Birth Spacing Changed").
+I have also rewritten paragraphs so they have the main argument first, followed by details
+on the argument, which should make it easier to follow the thread of the arguments.
+
 (3) There is no clear outline of the arguments presented in the Background section. Each
@@
 subsequent analyses.
+
+RESPONSE: I have completely reorganized the Conceptual Framework section to address this and
+and both Issues (1) and (2) and the examples below.
+It now begins with an overview of the section, followed by three potential explanations that
+link fertility and birth spacing decisions: economic conditions, investment in children, and 
+son preference.
+I then introduce sex composition of previous children, female education, and area of
+residence as the primary explanatory variables that can both proxy for the explanations and
+that are available in the data.
+Finally, I tie each of the three primary explanatory variables to the explanations and
+discuss their predicted effects based on the potential explanations.
 
@@
 
+RESPONSE: I now introduce female education as a primary explanatory variable after the 
+potential explanations linking fertility and birth spacing.
+This allows me to better show how female education fits into the explanations and the potential 
+effects of education on birth spacing.
+I have moved the definitions of education groups to the Data section.
+
 b. The 2 paragraphs on female labor force participation on pp. 5-6: The two findings that
@@
 
+RESPONSE: As detailed above, I have reorganized the whole section and now introduce income
+and substitution effects early and apply these to fertility decisions.
+This change should make it easier to understand the new explanation for why we are unlikely
+to see a shortening of birth intervals in India even with increasing female wage.
+I have removed the discussion of elasticity (but kept the reference) since this is simply
+another way of saying that the income effect dominates the substitution effect.
+
 c. P. 6 regarding sex selection: “The introduction of sex selection allows parents to avoid
@@
 footnote). A clear explanation of this argument needs to be reiterated (or moved) here.
+
+RESPONSE: I have moved the original footnote into the text in the Conceptual Framework and
+expanded the discussion to make it easier to understand.
+The Introduction now simply says that it takes 6 months or more after an abortion to reach 
+the same point in the next pregnancy and refers to the detailed discussion in the
+Conceptual Framework section.
 
@@
 
+RESPONSE: Yes, that was a terrible explanation.
+The argument is exactly the opposite: the increased demand for better-educated women
+is associated with a more male-biased sex ratio.
+With declining female labor force participation it is clear that educated women are not
+desired because they bring income to the household.
+However, if better-educated women produce better-educated sons this may increase the
+demand for better-educated women given the strong son preference and the rapid increasing 
+return to male education.
+The result is that higher female education may be associated with lower fertility, longer 
+spacing, and increased use of sex selection even if the standard economic explanation
+based on wages does not hold.
+This is important because the usual policy recommendation of increased education may
+not change the use of sex selection in the absence of changes in the relative return
+to male and female education in the labor market.
+I have completely rewritten the explanation and refer to it when discussing better
+job opportunities in the Conclusion.
+
 e. Pp. 6-7: I do not understand the importance of this argument and how it fits into the
@@
 
+RESPONSE: The idea was to show that longer spacing could be thought of as an investment
+in children that may occur at the same time as lower fertility.
+I have completely rewritten that section to make this clearer.
+
 f. P. 7: The final summary paragraph lists predictions based on the earlier arguments. Yet
@@
 be noted with the earlier arguments.
+
+RESPONSE: With the new structure of the Conceptual Framework section, the final paragraph
+with the summary of predictions now follows directly the predictions for the three primary
+explanatory variables.
+Hence, it should connect better to the individual predictions.
 
@@
 the hazard model and the reader does not know in which analyses it will be used.
+
+RESPONSE: I have added an outline of the three parts of the empirical analysis at the 
+beginning of the section and highlighted that the Estimation Strategy section focuses
+on the empirical model for birth spacing.
 
@@
 
+RESPONSE: I now begin the abstract with the changing sex ratio after the introduction 
+of prenatal sex-determination technologies.
+I then state when main issue, which is that abortions increase birth spacing but we
+know little about how birth spacing has changed or the effects of these changes.
+After this, I highlight the main birth spacing results.
+I next discuss how the rapid lengthening of birth spacing led the period
+fertility measure to substantially overestimate the decline in cohort fertility.
+Finally, I disucss the question of whether repeated abortions can counteract the
+other positive effects of longer birth spacing on infant mortality.
+
+Throughout the abstract I have avoided ascribing use of sex-selection, instead refering to
+the introduction of prenatal sex-determination technologies and the presumed use 
+of sex-selective abortions.
+
 4. P. 1: The second motivation is unclear. “the combined changes in birth spacing may
@@
 
+RESPONSE: That was meant to capture the combined effect from more sex selection and the other changes.
+I have rewritten the paragraph to emphasize that we do not know how much of an effect the 
+combined changes will have on birth spacing and to remove the imprecise "outpace".
+The new sentence is "The combination of the apparent increasing 
+use of sex selection and the other societal changes can significantly impact birth spacing, 
+but we know little about how much."
+
 5. Throughout the paper, the author compares the total fertility rate to cohort fertility
 rate. For the former, is the period fertility rate a more accurate definition?
+
+RESPONSE: I would argue that the total fertility rate is our most commonly used period
+fertility measures, especially in "public-facing" discussions of changes in fertility 
+behavior (see also the discussion in \citet{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}).
+However, the make this clearer I have clarified whether I am referring to period fertility
+or to cohort fertility throughout the paper.
 
@@
 
+The idea is that even though the spacing between births become longer with sex-selective 
+abortions, the spacing between \emph{pregnancies} may still be very short as suggested by a 
+prior reviewer. 
+If short pregnancy spacing has negative effects on child outcomes, the short pregnancy spacing 
+may dampen or completely eliminate any positive effects from longer spacing. 
+I have expanded the discussion of the possible counteracting effects in the Introduction.
+
+The new paragraph is:
+\begin{quote}
+Second, what is the relationship between infant mortality and the changes in birth spacing
+and sex selection? 
+In India, birth intervals have traditionally been shorter with fewer sons, contributing to 
+girls' higher mortality risk
+\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}. 
+Therefore, longer birth spacing may reduce mortality through, for example, diminished 
+sibling competition \citep{Conde-Agudelo2012,Molitoris2019}. 
+However, if the spacing between births lengthens because of sex-selective abortions, the 
+spacing between pregnancies may still be very short. 
+Short pregnancy spacing may lead to worse child outcomes because of maternal nutritional 
+depletion and insufficient time to recover from the previous pregnancy. 
+Hence, children born after long birth intervals where multiple abortions have punctuated 
+those intervals may not see the same benefits as children born after a long interval that 
+is not punctuated by abortions.
+\end{quote}
+
 7. Sometimes the use of the term “birth interval” actually refers to “birth interval
@@
 
+RESPONSE: Thank you for pointing this out, that was not caught by the copy editor
+or me.
+I have corrected this 28 diferent places in the paper.
+
 8. P. 2: “The key variables are maternal education, the sex of previous children, and the
 area of residence.” Does the author mean key independent or predictor variables?
+
+RESPONSE: Yes, those are the key explanatory variables. 
+I have added that to the Introduction.
+If you think that "independent" or "predictor" variables would be better, I would
+be happy to change that throughout.
 
@@
 
+RESPONSE:  To address this, I have made the following changes:
+\begin{itemize}
+\item Rewritten the Abstract as detailed above
+\item In the Introduction's summary of results I lead with the changes in birth spacing and 
+sex ratios and then say that these are likely arising from sex-selective abortions.
+\item Specify that the grouping into more and less sex selection when analyzing birth spacing 
+is based on sex ratios and clarify that the use of sex selection is inferred rather than 
+established when analyzing birth spacing.
+\item For the Conclusion, tone down the conclusions to focus on lengthening of birth intervals and 
+that these likely came from sex selection as indicated by the increasingly male-biased sex ratio.
+\end{itemize}
+
 10. While it might be messy to show the confidence intervals in all the figures, is it
 possible to note some significant differences in the text?
+
+RESPONSE: I did try again to come up with a way to incorporate confidence intervals in the figures,
+but the only way that would work would triple the number of figures.
+Instead, I have expanded the discussion of results to include where there are statistically
+significant differences:
+\begin{itemize}
+\item I now highlighted that tests for statistically significant differences across sex compositions 
+are available in the online appendix.
+\item In the section on how birth spacing changed, I have added discussions of statistical significance 
+when discussing comparisons across sex compositions.
+\item In the Conclusion, I have also added that when there are no sons, we now see statistically 
+significant longer, rather than statistically significant shorter, birth intervals than if there 
+is at least one son, rather than simply discussing the reversal.
+\end{itemize}
 

### 2021-01-08 paper/sex_selection_spacing-ver5.tex
Edits throughout the paper; mostly minor

@@
 Moreover, predicted cohort fertility is still 10\%--20\% above the period fertility rate. 
-If lengthening of birth intervals occurs from repeated abortions, the associated short pregnancy spacing 
+If lengthening of birth intervals arise from repeated abortions, the associated short pregnancy spacing 
 may counteract any positive effects of longer birth spacing. 
@@
 
-An increased desire to invest in children may also lengthen birth spacing, provided it has 
-positive effects on child outcomes. 
+An increased desire to invest in children may also lengthen birth spacing. 
 The clearest example of a positive effect of longer spacing is for health as very short 
@@
 
-Despite that higher potential wages from more education should shorten birth spacing and
+Even though higher potential wages from more education should shorten birth spacing and
 lower fertility, the low and declining female labor force participation suggests little
@@
 fertility, makes sex selection more likely, and possibly increases birth spacing.
+The implication is that the usual policy recommendation of increased female education may not
+change sex selection unless there is a concurrent increase in the relative return to female
+education in the labor market.
 
@@
 Furthermore, birth spacing likely increases the most among the better educated as their
-household income increase the most, and because of their use of sex selection. 
+household income increase the most, and because of their presumptive use of sex selection. 
 Finally, "Sanskritization" implies that the changing composition of better-educated
@@
 
-Second, even without sex selection, it is unlikely that characteristics, such as 
-the sex composition of previous births, have the same effects throughout the entire 
-birth interval. 
-The proportional hazard model requires that the hazard for any individual is a 
+Second, even without sex selection, it is unlikely that characteristics, such as previous
+births' sex composition, have the same effects throughout the entire birth interval.
+The proportional hazard model requires that an individual's hazard is a 
 fixed proportion of the hazard for any other individual. 
@@
 of progressing to the next birth and how soon couples want their next child if they 
-are going to have one \citep{Whitworth2002,Bhalotra2008,Kim2010}.
+are going to have one \citep{Whitworth2002,Bhalotra2008}.
 
@@
 hazard functions to vary across groups.
-The use of a nonproportional specification also mitigates any potential effects 
-of unobserved heterogeneity when used in conjunction with a flexible baseline hazard 
-\citep{Dolton1995}.
+Furthermore, the combination of a nonproportional specification and a flexible baseline
+hazard mitigates the potential effects of unobserved heterogeneity \citep{Dolton1995}.
 
@@
 previous children, and area of residence.
-To minimize any potential bias from including proportional variables, I estimate a 
-separate model for each birth interval, education group, and period combination, rather 
-than including education as a variable.
+To minimize any potential bias from including proportional variables, I estimate separate 
+models for each birth interval, education group, and period combination, rather than 
+including education as a variable.
 
@@
 The sex ratio graphs also show the natural sex ratio, approximately 51.2\% boys
-\citep{ben-porath76b,jacobsen99,Portner2015b}.
+\citep{jacobsen99,Portner2015b}.
 The underlying values with bootstrapped standard errors and tests for statistically
@@
 probability of a third birth declined by fewer than six percentage points while the birth 
-interval increased only slightly over two months.
+interval increased by only slightly more than two months.
 
@@
 around 55 months to 54 months.
-These birth spacing changes may even be underestimated because this particular group
+These birth spacing changes may even understate the impact because this particular group
 appears to have had access to sex selection even before it became widespread, as shown by
@@
 % What has happened to spacing and why
-The most substantial lengthening of birth intervals came from the best-educated women,
+The most substantial lengthening of birth intervals occurred among the best-educated women,
 likely because of substantial use of sex selection combined with falling fertility.
@@
 
-Some of the lengthening in birth intervals are so large that we even observed a reversal of
-the traditional spacing pattern for some groups: 
-For these groups, when there are no sons, we now see statistically significant longer,
-rather than statistically significant shorter, birth intervals than if there is at least
-one son.
+For some groups, the lengthening in birth intervals was so substantial that it led to a
+reversal of the traditional spacing pattern: In the absence of sons, these groups now show
+statistically significant longer, rather than statistically significant shorter, birth
+intervals than if there is at least one son.
+
 The women who are the least likely to use sex selection, as indicated by their sex ratios
@@
 
-There are two critical questions that future research should address.
-First, access to sex selection means that girls-only families are less likely to have
+There are two crucial questions that future research should address.
+
+First, what is behind the improvements in girls' health status?
+Access to sex selection means that girls-only families are less likely to have
 very short birth intervals, which may reduce sibling competition. 
@@
 Comparing prior children's outcomes across sex composition and the sex of the next child 
-could be a way to understand why girls' health outcomes improve in the presence of sex selection.
+could be a way to understand why girls' health outcomes improve in the presence of sex 
+selection.
 
@@
 The natural sex ratio is approximately 105 boys to 100 girls or
-51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
+51.2\% \citep{jacobsen99,Portner2015b}.
 Prenatal sex determination techniques did not become widely available until the mid-1980s, 
@@
 The natural sex ratio is approximately 105 boys to 100 girls or
-51.2\% \citep{ben-porath76b,jacobsen99,Portner2015b}.
+51.2\% \citep{jacobsen99,Portner2015b}.
 The predicted percentage boys may differ from the natural rate because of 

### 2021-01-08 paper/sex_selection_spacing-ver5-demography.tex
Version 5 submitted to Demography

--- 2021-01-08 paper/sex_selection_spacing-ver5.tex
@@
 India's Experience Over Four Decades%
-\protect\thanks{%
-I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Monica Das Gupta, Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, three anonymous reviewers, and seminar participants at University of 
-Copenhagen, University of Michigan, University of Washington, University of Aarhus, the 
-Fourth Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful 
-suggestions and comments.
-I would also like to thank Nalina Varanasi for research assistance.
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
-The views and findings expressed here are those of the author and
-should not be attributed to the World Bank or any of its member countries.
-Partial support for this research came from a Eunice Kennedy Shriver National
-Institute of Child Health and Human Development research infrastructure grant,
-5R24HD042828, to the Center for Studies in Demography and Ecology at the
-University of Washington.
-}
-}
-
-\author{Claus C P\"ortner\\
-    Department of Economics\\
-    Albers School of Business and Economics\\
-    Seattle University, P.O. Box 222000\\
-    Seattle, WA 98122\\
-    \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
-    \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
-    \& \\
-    Center for Studies in Demography and Ecology \\
-    University of Washington\\ \vspace{2cm}
-    }
+% \protect\thanks{%
+% I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
+% I owe thanks to Monica Das Gupta, Shelly Lundberg, Daniel Rees, David Ribar, 
+% Hendrik Wolff, three anonymous reviewers, and seminar participants at University of 
+% Copenhagen, University of Michigan, University of Washington, University of Aarhus, the 
+% Fourth Annual Conference on Population, Reproductive Health, 
+% and Economic Development, and the Economic Demography Workshop for helpful 
+% suggestions and comments.
+% I would also like to thank Nalina Varanasi for research assistance.
+% Support for development of the method from the University of Washington Royalty 
+% Research Fund and the Development Research Group of the World Bank is gratefully 
+% acknowledged.
+% The views and findings expressed here are those of the author and
+% should not be attributed to the World Bank or any of its member countries.
+% Partial support for this research came from a Eunice Kennedy Shriver National
+% Institute of Child Health and Human Development research infrastructure grant,
+% 5R24HD042828, to the Center for Studies in Demography and Ecology at the
+% University of Washington.
+% }
+}
+
+\author{}
+
+% \author{Claus C P\"ortner\\
+%     Department of Economics\\
+%     Albers School of Business and Economics\\
+%     Seattle University, P.O. Box 222000\\
+%     Seattle, WA 98122\\
+%     \href{mailto:cportner@seattleu.edu}{\texttt{cportner@seattleu.edu}}\\
+%     \href{http://www.clausportner.com}{\texttt{www.clausportner.com}}\\
+%     \& \\
+%     Center for Studies in Demography and Ecology \\
+%     University of Washington\\ \vspace{2cm}
+%     }
 
@@
 \begin{abstract}
-
-% Demography abstract
-\noindent 
-% In India, the most substantial lengthening in Hindu women's birth intervals over the past 
-% four decades has occurred for the women most likely to use sex-selective abortions. 
-% For well-educated women with two girls, the median birth interval before the third child 
-% has increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
-% sex ratio has approached 80\% boys. 
-% Because of the rapid lengthening in spacing, standard fertility rates have significantly 
-% overestimated how fast cohort fertility fell. 
-% Despite convergence, cohort fertility is still 10\%--20\% higher than the 
-% fertility rate and above replacement level for all but the best-educated urban women. 
-% With the lengthening from sex selection, some women show a reversal of the traditional 
-% spacing pattern; instead of the shortest birth interval in the absence of sons, they now 
-% have the longest. 
-% Finally, infant mortality has declined over time for all groups, but the decline was 
-% fastest for the less educated. 
-% Short birth spacing is still associated with higher mortality, although considerably less 
-% so for the best-educated women. 
-% There is no evidence that the increasing use of sex selection is associated with higher 
-% infant mortality. 
-% Neither does it appear that the use of sex selection is declining.
-
-% \noindent Over the past four decades, the Hindu women in India most likely to use 
-% sex-selective abortions---well-educated women with no sons---had the most substantial 
-% lengthening of birth intervals and the most biased sex ratios. 
-% As a result, we now see cases that reverse the traditional spacing pattern, with some
-% women with no sons having longer birth intervals than those with sons. 
-% Those least likely to use sex-selective abortions---less-educated women in rural 
-% areas---still follow the traditional pattern of short spacing when they have girls, with 
-% only limited evidence of sex selection. 
-% Because of the rapid lengthening in spacing, the standard fertility rates substantially 
-% overestimated how fast cohort fertility fell. 
-% Despite a convergence, cohort fertility is still 10\%--20\% higher than the fertility rate 
-% and above replacement level for all but the best-educated urban women. 
-% Infant mortality has declined substantially over time for all groups, with the fastest 
-% decline among the less educated. 
-% Short birth spacing is still associated with higher mortality, although considerably less 
-% so for the best-educated women. 
-% There is no evidence that repeated sex-selective abortions are associated with higher 
-% infant mortality for the child eventually born. 
-% Finally, it does not appear that the use of sex selection is declining.
-
-% \noindent India has experienced an increasingly male-biased sex ratio at birth following
-% the introduction of prenatal sex determination techniques. 
-% I examine three questions.
-% First, how did birth spacing change with this and other secular developments? 
-% Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
-% Finally, did the advent of sex-selective abortions change the relationship between birth 
-% spacing and infant mortality? 
-% Well-educated Hindu women with no sons had the most substantial lengthening of birth 
-% intervals and the most male-biased sex ratios, likely from sex-selective abortions. 
-% Consequently, some women with no sons now have longer birth intervals than those with sons, 
-% reversing India's traditional spacing pattern.
-% Less-educated women continued short spacing when they have girls, with only limited
-% evidence of male-biased sex ratios. 
-% Because of the overall lengthening in spacing, period fertility rates substantially 
-% overestimated how fast cohort fertility fell. 
-% Furthermore, predicted cohort fertility remains above replacement for all but the 
-% best-educated urban women. 
-% If lengthening of birth intervals occurs from repeated abortions, the associated
-% short pregnancy spacing may counteract any positive effects of longer birth spacing. 
-% There is no evidence of this effect on infant mortality. 
-% Finally, judging from sex ratios, sex-selective abortion use is not declining.
-
 \noindent Following the arrival of prenatal sex-determination technologies in the mid-1980s, 

### 2021-01-08 response/response-demography-4.tex
Revise paper and response to editors' comments (#45)
* Revise and resubmit letter from Demography (number 4)

* Update bibliography
- Add World Urbanization Prospects to bib file
- Add health knowledge paper to bib file

* Rewrite Abstract
- Add problem and questions to abstract

* Edit Introduction
- Key independent variables in Introduction

* Edit Conceptual Framework
-  Add income/substitute discussion
- Add husband income effect
- Add intro paragraph and text snippets for theories/determinants
- Flesh out the economic theory and child outcome sections
- Instead of fertility as a separate

--- 2020-12-20 response/response-demography-4.tex
@@
 \usepackage{multirow}
+\usepackage{enumitem}
 
@@
 
-\begin{center} Response to Editor Comments \end{center}
+\begin{center} Response to Editors' Comments \end{center}
 
@@
 
+\subsection*{Comments and My Responses}
+
 The author has undertaken much reorganization and has made very useful clarifications to
@@
 
-(1) Explanations of key concepts or theories need to be spelled out more clearly,
+\begin{itemize}
+\item[(1)] Explanations of key concepts or theories need to be spelled out more clearly,
 particularly for the non-economist. Much has been done in this regard, but further work is
@@
 
-(2) The arguments do not flow from section to section and paragraph to paragraph. Each
+RESPONSE: With the reorganization of the Conceptual Framework section described below, I now 
+have an early paragraph that explains income and substitution effects in detail and how they 
+tie into fertility decisions with increasing wages for both males and females.
+I then rely on this detailed explanation for my later discussions of female education and
+labor force participation.
+Furthermore, I provide a more in-depth explanation of fertility and investment decisions in
+children based on the expected return to investment in children's education.
+Finally, I have reorganized my discussion of how demand for better-educated mothers can
+increase even if female labor force participation is declining to make it easier to follow
+for non-economists.
+
+\item[(2)] The arguments do not flow from section to section and paragraph to paragraph. Each
 section and argument need to be introduced so the reader understands why this information
@@
 
-(3) There is no clear outline of the arguments presented in the Background section. Each
+RESPONSE: As detailed below, I have completely reorganized the Conceptual Framework section
+to create a better flow and make it easier for the reader to follow.
+Furthermore, I have added introductory paragraphs to the sections that did not already 
+have these or an equivalent transition ("Conceptual Framework," "Estimation Strategy," "Data," 
+and "How Birth Spacing Changed").
+Finally, I have rewritten paragraphs in multiple places in the paper to make it easier 
+to follow the thread of the arguments.
+
+\item[(3)] There is no clear outline of the arguments presented in the Background section. Each
 argument is presented separately rather than tying into the overall framework and
@@
 
-The following are some examples of (1) and (2); however, the author should check the entire
+RESPONSE: I have completely reorganized the Conceptual Framework section to address this
+and  Issues (1) and (2) and the examples below.
+The framework section now begins with an overview of the section, followed by three 
+potential explanations that link fertility and birth spacing decisions: economic conditions, 
+investment in children, and son preference.
+I then introduce the sex composition of previous children, female education, and area of
+residence as the primary explanatory variables, which proxy for the explanations and are
+available in the data.
+Finally, I tie each of the three primary explanatory variables to the explanations and
+discuss their predicted effects.
+
+\end{itemize}
+
+\noindent The following are some examples of (1) and (2); however, the author should check the entire
 paper for similar issues and address (3) as well.
 
-1. In general, each argument in the background section is not clear and fully described for
+\begin{enumerate}
+
+\item  In general, each argument in the background section is not clear and fully described for
 the reader.
 
-a. P. 4 first sentence: The author states that female education is a crucial explanatory
+\begin{enumerate}
+
+\item  P. 4 first sentence: The author states that female education is a crucial explanatory
 variable and it matters for fertility, sex ratios, mortality, etc. in a list. It would be
@@
 
-b. The 2 paragraphs on female labor force participation on pp. 5-6: The two findings that
+RESPONSE: I now introduce female education as a primary explanatory variable after the 
+potential explanations linking fertility and birth spacing.
+This change allows me to show how female education fits into the explanations and 
+the potential effects of education on birth spacing.
+I have moved the definitions of education groups to the Data section.
+
+\item  The 2 paragraphs on female labor force participation on pp. 5-6: The two findings that
 support the argument that changes in birth spacing are not due to economic reasons are
@@
 
-c. P. 6 regarding sex selection: “The introduction of sex selection allows parents to avoid
+RESPONSE: As detailed above, I have reorganized the whole section and now introduce income
+and substitution effects early and apply these to fertility decisions.
+This change should make it easier to understand the new explanation for why we are unlikely
+to see a shortening of birth intervals in India, even with increasing female wages.
+I have removed the discussion of elasticity (but kept the reference) since this is simply
+another way of saying that the income effect dominates the substitution effect.
+
+\item  P. 6 regarding sex selection: “The introduction of sex selection allows parents to avoid
 giving birth to girls but increases the expected interval to the next birth.” The reader
@@
 
-d. P. 6: “As women’s education increases, their productivity in the production of offspring
+RESPONSE: I have moved the original footnote into the text in the Conceptual Framework and
+expanded the discussion to make it easier to understand.
+The Introduction section now only says that it takes 6 months or more after an abortion to
+reach the same point in the next pregnancy and refers to the Conceptual Framework section's
+detailed discussion.
+
+\item  P. 6: “As women’s education increases, their productivity in the production of offspring
 human capital also increases. With relatively more boys born because of increased access to
@@
 
-e. Pp. 6-7: I do not understand the importance of this argument and how it fits into the
+RESPONSE: That was, indeed, a terrible explanation. The argument is precisely the opposite
+of lowering the sex ratio: the increased demand for better-educated women is associated 
+with a more male-biased sex ratio. 
+With declining female labor force participation, it is clear that educated women are
+not desired because they bring income to the household. 
+However, suppose better-educated women produce better-educated sons. 
+In that case, this may increase the demand for better-educated women given the strong son 
+preference and the rapidly rising return to male education. 
+The result is that higher female education may be associated with lower fertility, longer 
+spacing, and increased use of sex selection even if the standard economic explanation based 
+on wages does not hold. 
+The implication is that the usual policy recommendation of increased female education may not
+change sex selection unless there is a concurrent increase in the relative return to female
+education in the labor market. 
+I have entirely rewritten the explanation and refer to it when discussing better job 
+opportunities in the Conclusion.
+
+\item  Pp. 6-7: I do not understand the importance of this argument and how it fits into the
 authors’ story: “If more and “better” parental attention per child results in higher child
@@
 
-f. P. 7: The final summary paragraph lists predictions based on the earlier arguments. Yet
+RESPONSE:The idea was to show that longer spacing could be considered an investment in
+children that may coincide with lower fertility. 
+I have rewritten the paragraph to make this clearer.
+
+\item  P. 7: The final summary paragraph lists predictions based on the earlier arguments. Yet
 it is hard to connect these predictions to the paragraphs above. Perhaps predictions could
@@
 
-2. Estimation strategy section.
+RESPONSE: With the Conceptual Framework section's new structure, 
+the summary of predictions now directly follows the predictions for the three primary
+explanatory variables. Hence, it should connect better to the individual predictions.
+
+\end{enumerate}
+
+\item  Estimation strategy section.
 
@@
 
-Some additional issue as examples where more clarification is needed:
+RESPONSE: I have added an outline of the three parts of the empirical analysis at the 
+beginning of the section and highlighted that the Estimation Strategy section focuses
+on the empirical model for birth spacing.
 
-3. Abstract. Please reorganize to start with a statement of the problem and main aims of
+\end{enumerate}
+
+\noindent Some additional issue as examples where more clarification is needed:
+
+\begin{enumerate}[resume]
+
+\item  Abstract. Please reorganize to start with a statement of the problem and main aims of
 the study. As it stands, the abstract is a list of findings, with no context as to the
@@
 
-4. P. 1: The second motivation is unclear. “the combined changes in birth spacing may
-outpace what we have observed in other countries.” Outpaced means what? decreasing faster,
+RESPONSE: I now begin the abstract with the changing sex ratio after the introduction of
+prenatal sex-determination technologies. I then state the main issue: abortions increase
+birth spacing, but we know little about how birth spacing has changed or the effects of
+these changes. After this, I highlight the main birth spacing results. Next, I discuss how
+the rapid lengthening of birth spacing led the period fertility measure to overestimate the
+decline in cohort fertility substantially. Finally, I cover whether repeated abortions can
+counteract the other positive effects of longer birth spacing on infant mortality.
+
+Throughout the abstract, I avoid ascribing use of sex-selection to anybody.
+Instead, I refer to the introduction of prenatal sex-determination technologies and the 
+presumed use of sex-selective abortions.
+
+\item  P. 1: The second motivation is unclear. ``the combined changes in birth spacing may
+outpace what we have observed in other countries.'' Outpaced means what? decreasing faster,
 or increasing faster, or sex selection plays more of a role?
 
-5. Throughout the paper, the author compares the total fertility rate to cohort fertility
+RESPONSE: The goal of the sentence was to capture the combined effect from more sex
+selection and the other changes.
+I have rewritten the paragraph to emphasize that we do not know how much impact
+the combined changes will have on birth spacing and remove the imprecise" outpace." The new
+sentence is: "The combination of the apparent increasing use of sex selection and the other
+societal changes can significantly impact birth spacing, but we know little about how
+much."
+
+\item  Throughout the paper, the author compares the total fertility rate to cohort fertility
 rate. For the former, is the period fertility rate a more accurate definition?
 
-6. P. 2: the main point of this sentence is unclear: “Counteracting effect is possible if
+RESPONSE: I would argue that the total fertility rate is our most commonly used period 
+fertility measures, especially in ``public-facing'' discussions of fertility behavior 
+changes \citep[see the discussion in][]{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
+I have clarified whether I am referring to period fertility or cohort fertility 
+throughout the paper.
+
+\item  P. 2: the main point of this sentence is unclear: “Counteracting effect is possible if
 longer birth intervals arise from multiple abortions because the short duration between
@@
 
-7. Sometimes the use of the term “birth interval” actually refers to “birth interval
+RESPONSE: The idea is that even though the spacing between births becomes longer with
+sex-selective abortions, the spacing between \emph{pregnancies} may still be very short, as
+suggested by a prior reviewer. If short pregnancy spacing negatively affects child
+outcomes, the short pregnancy spacing may dampen or eliminate any positive effects from
+longer spacing. 
+I have expanded the discussion of this possible counteracting impact in the Introduction.
+
+The new paragraph is:
+\begin{quote}
+Second, what is the relationship between infant mortality and the changes in birth spacing
+and sex selection? 
+In India, birth intervals have traditionally been shorter with fewer sons, contributing to 
+girls' higher mortality risk
+\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}. 
+Therefore, longer birth spacing may reduce mortality through, for example, diminished 
+sibling competition \citep{Conde-Agudelo2012,Molitoris2019}. 
+However, if the spacing between births lengthens because of sex-selective abortions, the 
+spacing between pregnancies may still be very short. 
+Short pregnancy spacing may lead to worse child outcomes because of maternal nutritional 
+depletion and insufficient time to recover from the previous pregnancy. 
+Hence, children born after long birth intervals where multiple abortions have punctuated 
+those intervals may not see the same benefits as children born after a long interval that 
+is not punctuated by abortions.
+\end{quote}
+
+\item  Sometimes the use of the term “birth interval” actually refers to “birth interval
 length.” Please check the uses of these terms and correct accordingly.
 
-8. P. 2: “The key variables are maternal education, the sex of previous children, and the
+RESPONSE: Thank you for pointing this out. 
+I have corrected this issue in 28 different places in the paper.
+
+\item  P. 2: “The key variables are maternal education, the sex of previous children, and the
 area of residence.” Does the author mean key independent or predictor variables?
 
-9. The author should clearly note that sex selection is not observed and tone down some
+RESPONSE: Yes, those are the key explanatory variables. 
+I have added that to the Introduction.
+If you think that "independent" or "predictor" variables would be better, I would
+be happy to change that throughout.
+
+\item  The author should clearly note that sex selection is not observed and tone down some
 conclusions, such as “Sex selection, however, is behind the most substantial increases in
@@
 
+RESPONSE:  To address this, I have made the following changes:
+\begin{itemize}
+\item Rewritten the Abstract as detailed above
+\item In the Introduction's summary of results, I lead with the changes in birth spacing and 
+sex ratios and then say that these are likely arising from sex-selective abortions.
+\item Specify that the grouping into more and less sex selection when analyzing birth spacing 
+is based on sex ratios and clarify that the use of sex selection is inferred rather than 
+established when analyzing birth spacing.
+\item In the Conclusion section, I now focus on the lengthening of birth intervals and how
+these likely arose from sex selection as indicated by the increasingly male-biased sex
+ratio.
+\end{itemize}
+
 10. While it might be messy to show the confidence intervals in all the figures, is it
 possible to note some significant differences in the text?
+
+RESPONSE: I tried again to incorporate confidence intervals in the figures, but the only 
+way I could find tripled the number of figures.
+Instead, I have expanded the discussion of results to include where there are statistically
+significant differences:
+\begin{itemize}
+\item I now highlighted that tests for statistically significant differences across sex compositions 
+are available in the online appendix.
+\item In the section on how birth spacing changed, I have added discussions of statistical significance 
+when discussing comparisons across sex compositions.
+\item In the Conclusion, I have also added that when there are no sons, we now see statistically 
+significant longer---rather than statistically significant shorter---birth intervals than 
+if there is at least one son, rather than merely discussing the reversal.
+\end{itemize}
+
+\end{enumerate}
 

### 2021-01-08 paper/birth_spacing_lit.tex
Revise paper and response to editors' comments (#45)
* Revise and resubmit letter from Demography (number 4)

* Update bibliography
- Add World Urbanization Prospects to bib file
- Add health knowledge paper to bib file

* Rewrite Abstract
- Add problem and questions to abstract

* Edit Introduction
- Key independent variables in Introduction

* Edit Conceptual Framework
-  Add income/substitute discussion
- Add husband income effect
- Add intro paragraph and text snippets for theories/determinants
- Flesh out the economic theory and child outcome sections
- Instead of fertility as a separate

@@
 and Koblinsky 1984; Palloni and Millman 1986; Habicht, DaVanzo, and Butz
-1988), such behaviorcanleadtogenderdisparities inchildhealth. Incontrast
+1988), such behavior can lead to gender disparities in child health. In contrast
 to the standard explanation of gender health disparities—that parents
@@
 causing a gender gapin health even when parents
-equallyvaluethehealthofall theirchildren. Ourresults highlight how
+equally value the health of all their children. Our results highlight how
 health disparities can arise “passively” from fertility preferences, and
@@
 breastfeeding’s contraceptive properties should rise as couples approach
-or exceed their ideal family size, andin fact shouldincrease
+or exceed their ideal family size, and in fact should increase
 discontinuously once ideal family size is met.
@@
 1987) or wait longer to have the next child (Rindfuss et al. 1982;
-Trussell et al. 1985; Arnold, Choe, and Roy 1998; RetherfordandRoy
+Trussell et al. 1985; Arnold, Choe, and Roy 1998; Retherford and Roy
 2003). Hemochandra, Singh, and Singh (2010) show that birth intervals

### 2021-05-03 paper/sex_selection_spacing-final.tex
Edit for final submission

--- 2021-01-08 paper/sex_selection_spacing-ver5.tex
@@
 University of Washington.
+Text and code for this paper is available at 
+\href{https://github.com/cportner/sexSelectionSpacing}{https://github.com/cportner/sexSelectionSpacing}
 }
@@
 
-\date{December 2020}
+\date{May 2021}
 
@@
 \begin{abstract}
-
-% Demography abstract
-\noindent 
-% In India, the most substantial lengthening in Hindu women's birth intervals over the past 
-% four decades has occurred for the women most likely to use sex-selective abortions. 
-% For well-educated women with two girls, the median birth interval before the third child 
-% has increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
-% sex ratio has approached 80\% boys. 
-% Because of the rapid lengthening in spacing, standard fertility rates have significantly 
-% overestimated how fast cohort fertility fell. 
-% Despite convergence, cohort fertility is still 10\%--20\% higher than the 
-% fertility rate and above replacement level for all but the best-educated urban women. 
-% With the lengthening from sex selection, some women show a reversal of the traditional 
-% spacing pattern; instead of the shortest birth interval in the absence of sons, they now 
-% have the longest. 
-% Finally, infant mortality has declined over time for all groups, but the decline was 
-% fastest for the less educated. 
-% Short birth spacing is still associated with higher mortality, although considerably less 
-% so for the best-educated women. 
-% There is no evidence that the increasing use of sex selection is associated with higher 
-% infant mortality. 
-% Neither does it appear that the use of sex selection is declining.
-
-% \noindent Over the past four decades, the Hindu women in India most likely to use 
-% sex-selective abortions---well-educated women with no sons---had the most substantial 
-% lengthening of birth intervals and the most biased sex ratios. 
-% As a result, we now see cases that reverse the traditional spacing pattern, with some
-% women with no sons having longer birth intervals than those with sons. 
-% Those least likely to use sex-selective abortions---less-educated women in rural 
-% areas---still follow the traditional pattern of short spacing when they have girls, with 
-% only limited evidence of sex selection. 
-% Because of the rapid lengthening in spacing, the standard fertility rates substantially 
-% overestimated how fast cohort fertility fell. 
-% Despite a convergence, cohort fertility is still 10\%--20\% higher than the fertility rate 
-% and above replacement level for all but the best-educated urban women. 
-% Infant mortality has declined substantially over time for all groups, with the fastest 
-% decline among the less educated. 
-% Short birth spacing is still associated with higher mortality, although considerably less 
-% so for the best-educated women. 
-% There is no evidence that repeated sex-selective abortions are associated with higher 
-% infant mortality for the child eventually born. 
-% Finally, it does not appear that the use of sex selection is declining.
-
-% \noindent India has experienced an increasingly male-biased sex ratio at birth following
-% the introduction of prenatal sex determination techniques. 
-% I examine three questions.
-% First, how did birth spacing change with this and other secular developments? 
-% Second, did changes in birth spacing make us overestimate the decline in cohort fertility? 
-% Finally, did the advent of sex-selective abortions change the relationship between birth 
-% spacing and infant mortality? 
-% Well-educated Hindu women with no sons had the most substantial lengthening of birth 
-% intervals and the most male-biased sex ratios, likely from sex-selective abortions. 
-% Consequently, some women with no sons now have longer birth intervals than those with sons, 
-% reversing India's traditional spacing pattern.
-% Less-educated women continued short spacing when they have girls, with only limited
-% evidence of male-biased sex ratios. 
-% Because of the overall lengthening in spacing, period fertility rates substantially 
-% overestimated how fast cohort fertility fell. 
-% Furthermore, predicted cohort fertility remains above replacement for all but the 
-% best-educated urban women. 
-% If lengthening of birth intervals occurs from repeated abortions, the associated
-% short pregnancy spacing may counteract any positive effects of longer birth spacing. 
-% There is no evidence of this effect on infant mortality. 
-% Finally, judging from sex ratios, sex-selective abortion use is not declining.
 
@@
 in the mid-1980s.
-Combined with a strong continued preference for sons, the result was a dramatic increase 
+Combined with a strong, continued preference for sons, the result was a dramatic increase 
 in the male--female ratio at birth
@@
 substantially increase birth spacing. 
-As detailed below, it takes 6 months or more after an abortion to reach the same point in 
+As detailed below, after an abortion it takes 6 months or more to reach the same point in 
 the next pregnancy. 
-Second, other societal changes, such as women's greater educational attainment, higher 
+Second, other major societal changes, such as women's greater educational attainment, higher 
 household income, and a low and declining female labor force participation, all 
 likely influence birth spacing. 
-The combination of the apparent increasing use of sex selection and the other societal 
+The combination of the apparent increasing use of sex selection and societal 
 changes can significantly impact birth spacing, but we know little about how much.
@@
 First, birth intervals lengthened over the four decades, with the lengthening longer, the
-higher the parity, the more educated the woman, and the higher the percentile.
+higher the parity, the more educated the woman, and the higher the percentile of the
+birth interval duration.
 Well-educated women with no sons had the most substantial lengthening of birth intervals 
@@
 Next, I discuss why female education, area of residence, and sex composition are the
-principal factors in the empirical analyses and tie them into the three explanations.
+principal factors in the empirical analyses and tie them to the three explanations.
 
@@
 An increased desire to invest in children may also lengthen birth spacing. 
-The clearest example of a positive effect of longer spacing is for health as very short 
+The clearest example of a positive effect of longer spacing is for health, as very short 
 spacing---approximately 24 months or less---leads to worse child health and mortality 
@@
 education, and area of residence. 
-The remainder of the section discusses how the three variables tie into the
+The remainder of the section discusses how the three variables fit into the
 explanations and the predicted effects.
@@
 For example, with an 80\% parity progression probability, the median birth interval 
-is the predicted number of months before a woman passes the 60\% mark on her survival 
-curve. 
+is the predicted number of months before a woman passes the 60\% $(100-\frac{80}{2})$ 
+mark on her survival curve. 
 I then add nine months to account for the start of the spell. 
@@
 the prior research arises because unintended births become a relatively larger proportion 
-of the total number of births for a given parity.
+of the total number of births for a given parity and those can occur at any time.
 
@@
 
-Even more striking is that most of the change took place right at the introduction of sex 
+Even more striking, most of the change took place right at the introduction of sex 
 selection.

### 2021-05-04 final/tables/fertility.tex
Demography needs figures in PDF and separate paper and appendices

\begin{table}[hp!]
\begin{center}
\begin{footnotesize}
\begin{threeparttable}
\caption{Four-parity fertility rate versus predicted cohort fertility based on hazard model}
\label{tab:fertility}
\begin{tabular}{@{} l D{.}{.}{2.2} D{.}{.}{2.2} D{.}{.}{2.2} D{.}{.}{2.2} D{.}{.}{2.2}  @{}}
\toprule
                       &            \mct{NFHS--1}          & \mco{NFHS--2}   & \mco{NFHS--3}   & \mco{NFHS--4}   \\
Fertility Rate Period  & \mco{1987--1988}  & \mco{1992--1993}  & \mco{1998--1999}  & \mco{2005--2006}  & \mco{2015--2016}  \\
Hazard Model Period    & \mco{1972--1984}  &                 & \mco{1985--1994}  & \mco{1995--2004}  & \mco{2004--2016}  \\
\midrule
 & \multicolumn{5}{c}{Urban} \\ \cmidrule(lr){2-6}
 & \multicolumn{5}{c}{No Education} \\
Fertility Rate\tnote{a}   &      3.55       &      3.06       &      2.80       &      2.54       &      2.45       \\
Hazard Model\tnote{b}     &      3.44       &                 &      3.29       &      3.06       &      2.79       \\
\addlinespace 
 & \multicolumn{5}{c}{1--7 Years of Education} \\
Fertility Rate\tnote{a}   &      2.85       &      2.29       &      2.09       &      1.99       &      2.04       \\
Hazard Model\tnote{b}     &      3.18       &                 &      2.88       &      2.62       &      2.42       \\
\addlinespace 
 & \multicolumn{5}{c}{8--11 Years of Education} \\
Fertility Rate\tnote{a}   &      2.43       &      2.04       &      1.84       &      1.81       &      1.87       \\
Hazard Model\tnote{b}     &      2.72       &                 &      2.41       &      2.28       &      2.07       \\
\addlinespace 
 & \multicolumn{5}{c}{12 or More Years of Education} \\
Fertility Rate\tnote{a}   &      2.05       &      1.68       &      1.57       &      1.55       &      1.51       \\
Hazard Model\tnote{b}     &      2.29       &                 &      2.06       &      1.94       &      1.80       \\
\addlinespace 
 & \multicolumn{5}{c}{Rural} \\ \cmidrule(lr){2-6}
 & \multicolumn{5}{c}{No Education} \\
Fertility Rate\tnote{a}   &      3.57       &      2.93       &      2.63       &      2.74       &      2.81       \\
Hazard Model\tnote{b}     &      3.55       &                 &      3.38       &      3.26       &      3.09       \\
\addlinespace 
 & \multicolumn{5}{c}{1--7 Years of Education} \\
Fertility Rate\tnote{a}   &      3.01       &      2.52       &      2.39       &      2.25       &      2.37       \\
Hazard Model\tnote{b}     &      3.29       &                 &      3.08       &      2.83       &      2.70       \\
\addlinespace 
 & \multicolumn{5}{c}{8--11 Years of Education} \\
Fertility Rate\tnote{a}   &      2.56       &      2.21       &      2.22       &      2.16       &      2.19       \\
Hazard Model\tnote{b}     &      2.93       &                 &      2.68       &      2.49       &      2.31       \\
\addlinespace 
 & \multicolumn{5}{c}{12 or More Years of Education} \\
Fertility Rate\tnote{a}   &      1.95       &      1.68       &      2.13       &      2.08       &      1.96       \\
Hazard Model\tnote{b}     &      2.64       &                 &      2.39       &      2.25       &      2.11       \\
\addlinespace 
\bottomrule
\end{tabular}
\begin{tablenotes} \scriptsize
\item \hspace*{-0.5em} \textbf{Note.}
All predictions based on births up to and including parity four births
for both fertility rate and model predictions.
NFHS-1 was collected in 1992--1993, and model results for 1972--1984 were
applied for the predictions.
NFHS-2 was collected in 1998--1999, and model results for 1985--1994 were
applied for the predictions.
NFHS-3 was collected in 2005--2006, and model results for 1995--2004 were
applied for the predictions.
NFHS-4 was collected in 2015--2016, and model results for 2005--2016 were
applied for the predictions.
\item[a] 
The fertility rate is based on five-year age groups, counting births that 
occurred 1--36 months before the survey months.
For NFHS-1 and NFHS-2, the total number of women in the five-year age
groups is based on the household roster because only ever-married women
are in the individual recode sample.
For NFHS-3 and NFHS-4, the total number of women is based on the individual
recode sample because all women were interviewed.
\item[b] 
The model predictions for fertility are the average predicted fertility
across all women in a given sample, using their age of marriage as the
starting point and adding three years for each spell.
Observed births are not taken into account for the predictions.
For each spell, the predicted probability is the likelihood of having a
next birth given sex composition multiplied with the probability of that
sex composition and the likelihood of getting to the spell,
corrected for the probability of sterilization.
\end{tablenotes}
\end{threeparttable}
\end{footnotesize}
\end{center}
\end{table}

### 2021-05-04 paper/sex_selection_spacing-final-appendix.tex
Demography needs figures in PDF and separate paper and appendices

--- 2021-05-03 paper/sex_selection_spacing-final.tex
@@
 \title{Birth Spacing and Fertility in the Presence of Son Preference and Sex-Selective Abortions:
-India's Experience Over Four Decades%
-\protect\thanks{%
-I am grateful to Andrew Foster and Darryl Holman for discussions about the method.
-I owe thanks to Monica Das Gupta, Shelly Lundberg, Daniel Rees, David Ribar, 
-Hendrik Wolff, three anonymous reviewers, and seminar participants at University of 
-Copenhagen, University of Michigan, University of Washington, University of Aarhus, the 
-Fourth Annual Conference on Population, Reproductive Health, 
-and Economic Development, and the Economic Demography Workshop for helpful 
-suggestions and comments.
-I would also like to thank Nalina Varanasi for research assistance.
-Support for development of the method from the University of Washington Royalty 
-Research Fund and the Development Research Group of the World Bank is gratefully 
-acknowledged.
-The views and findings expressed here are those of the author and
-should not be attributed to the World Bank or any of its member countries.
-Partial support for this research came from a Eunice Kennedy Shriver National
-Institute of Child Health and Human Development research infrastructure grant,
-5R24HD042828, to the Center for Studies in Demography and Ecology at the
-University of Washington.
-Text and code for this paper is available at 
-\href{https://github.com/cportner/sexSelectionSpacing}{https://github.com/cportner/sexSelectionSpacing}
-}
+India's Experience Over Four Decades \bigskip
+
+Online Appendices 
 }
@@
 
-\date{May 2021}
+\date{Text and code for this paper are available at 
+\href{https://github.com/cportner/sexSelectionSpacing}{https://github.com/cportner/sexSelectionSpacing}
+}
 
@@
 
-\setcounter{page}{-1}
+\setcounter{page}{0}
 \maketitle
 \thispagestyle{empty}
-
-% \setcounter{page}{0}
-
-\newpage
-\thispagestyle{empty}
-\doublespacing
-
-\begin{abstract}
-
-\noindent Following the arrival of prenatal sex-determination technologies in the mid-1980s, 
-India has experienced an increasingly male-biased sex ratio at birth, presumably from sex-selective 
-abortions. 
-Abortions lengthen birth intervals, but we know little about how birth spacing has changed or the 
-effects of these changes. 
-This paper shows that, although the length of birth intervals increased overall, well-educated women 
-with no sons had the most substantial lengthening---and the most male-biased sex ratios. 
-Furthermore, most of these changes took place immediately after the introduction of prenatal 
-sex-determination technologies. 
-Consequently, some women without sons now have longer birth intervals than those with sons, reversing 
-India's traditional spacing pattern. 
-Less-educated women continue short birth spacing when they have no sons, with only limited evidence 
-of male-biased sex ratios. 
-Because of the rapid lengthening of birth intervals, period fertility rates substantially overestimated 
-how fast cohort fertility fell. 
-Moreover, predicted cohort fertility is still 10\%--20\% above the period fertility rate. 
-If lengthening of birth intervals arise from repeated abortions, the associated short pregnancy spacing 
-may counteract any positive effects of longer birth spacing. 
-There is, however, no evidence of this effect on infant mortality. 
-Finally, judging from sex ratios, sex-selective abortion use is not declining.
-
-\noindent JEL: J1, O12, I1
-
-\noindent Keywords: India, prenatal sex determination, censoring, competing risk, 
-nonproportional hazard
-\end{abstract}
-
-\newpage
-
-%------------------------------------------------------------------------
-
-\section{Introduction\label{sec:intro}}
-
-% For word counting remove comment on the line below
-% \raggedright
-
-% Background
-India has experienced many positive changes over the past four decades:
-The economy has grown substantially,
-real wages have more than doubled,
-educational attainment has increased for males and females,
-and the total fertility rate has fallen to 2.2 children
-\citep{Bosworth2008,Dharmalingam2014,Klasen2015,
-International-Institute-for-Population-Sciences-IIPS2017}.
-
-However, India also witnessed the advent of sex selection---the selective abortion of 
-female fetuses based on prenatal sex determination---with the introduction of ultrasound 
-in the mid-1980s.
-Combined with a strong, continued preference for sons, the result was a dramatic increase 
-in the male--female ratio at birth
-\citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,Portner2015b,Jayachandran2017}.
-
-% Questions addressed and why valuable
-The main question I address here is how birth spacing responded to these changes, 
-especially the spread of sex selection. 
-The motivation is twofold.
-First, past research has failed to appreciate that the use of sex-selective abortions could 
-substantially increase birth spacing. 
-As detailed below, after an abortion it takes 6 months or more to reach the same point in 
-the next pregnancy. 
-Second, other major societal changes, such as women's greater educational attainment, higher 
-household income, and a low and declining female labor force participation, all 
-likely influence birth spacing. 
-The combination of the apparent increasing use of sex selection and societal 
-changes can significantly impact birth spacing, but we know little about how much.
-
-Studying birth spacing contributes to our understanding of fertility decisions, but, equally 
-important, birth spacing also affects the reliability of our fertility measures and may 
-affect mortality. 
-Therefore, I address two additional questions.
-
-First, did changes in birth spacing lead us to overestimate the decline in cohort fertility?
-With longer spacing, mothers will be older at each parity, and this tempo effect 
-makes period fertility measures, such as the total fertility rate, downward-biased
-estimates of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
-Hence, a rapidly expanding use of sex selection could make the total fertility rate---our 
-most used fertility measure---fall substantially faster than cohort fertility.
-In this case, households' fertility may be higher than generally accepted.
-
-Second, what is the relationship between infant mortality and the changes in birth spacing
-and sex selection? 
-In India, birth intervals have traditionally been shorter with fewer sons, contributing to 
-girls' higher mortality risk
-\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}. 
-Therefore, longer birth spacing may reduce mortality through, for example, diminished 
-sibling competition \citep{Conde-Agudelo2012,Molitoris2019}. 
-However, if the spacing between births lengthens because of sex-selective abortions, the 
-spacing between pregnancies may still be very short. 
-Short pregnancy spacing may lead to worse child outcomes because of maternal nutritional 
-depletion and insufficient time to recover from the previous pregnancy. 
-Hence, children born after long birth intervals where multiple abortions have punctuated 
-those intervals may not see the same benefits as children born after a long interval that 
-is not punctuated by abortions.
-
-% How the study progresses
-To investigate how birth spacing has changed, I use a competing risk hazard model with 
-two exit states: The birth of a girl or the birth of a boy. 
-I apply the model to Hindu women's birth histories covering 1972--2016 using data from the 
-four National Family and Health Surveys (NFHS).
-
-The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals 
-durations;
-the sex ratio at birth; and the likelihood of giving birth. 
-I estimate the model across four periods to capture the changing access and 
-legality of sex selection. 
-The key explanatory variables are maternal education, the sex of previous children, and 
-the area of residence.
-
-The empirical model allows me to predict cohort fertility. 
-To examine whether tempo effects bias our standard fertility measures, I compare 
-the predicted cohort fertility with fertility calculated from age-specific fertility 
-rates.
-
-I use the same data to study how infant mortality changed with birth spacing and 
-the increasing use of sex selection. 
-The key explanatory variables remain the same, except for the addition of birth spacing 
-and the sex of the index child.
-
-% Main results
-There are three main results.
-
-First, birth intervals lengthened over the four decades, with the lengthening longer, the
-higher the parity, the more educated the woman, and the higher the percentile of the
-birth interval duration.
-Well-educated women with no sons had the most substantial lengthening of birth intervals 
-and the most male-biased sex ratios, both likely arising from sex-selective abortions. 
-Consequently, some women with no sons now have \emph{longer} birth intervals than those 
-with sons, reversing India's traditional spacing pattern. 
-Less-educated women continued to have short spacing when they have girls, with only limited 
-evidence of male-biased sex ratios.
-The likelihood of a very short birth interval changed little across most groups.
-
-Second, the period fertility rate substantially overestimated how fast cohort fertility 
-fell in the 1990s and early 2000s as spacing initially increased. 
-Although the two have lately been converging, the predicted cohort fertility is still 
-10\%--20\% higher than the period fertility rate. 
-Furthermore, predicted cohort fertility is still at or above replacement level for all but 
-the best-educated urban women.
-
-Finally, infant mortality has declined substantially over time for all groups, but fastest 
-for the less educated, who are now close to the level of the best-educated women. 
-However, mortality is still inversely related to education level, especially for very short 
-birth intervals. 
-There is no evidence that repeated sex-selective abortions are associated with higher 
-mortality for the child eventually born.
-
-%------------------------------------------------------------------------------------
-
-\section{Conceptual Framework}
-
-This section provides a conceptual framework for understanding changes in birth spacing.
-I first introduce three potential explanations that link fertility and birth 
-spacing decisions: economic conditions, investment in children, and son preference 
-\citep{Casterline2016,Portner2018}.
-Next, I discuss why female education, area of residence, and sex composition are the
-principal factors in the empirical analyses and tie them to the three explanations.
-
-% Economic conditions
-The improvements in economic condition, especially the doubling of real wages,
-are likely to affect fertility, although the direction is ambiguous; empirically, 
-higher female wages reduce fertility, whereas higher male wages increase fertility 
-\citep{Hotz1997,schultz97}.
-According to economic theory, the substitution and income effects' relative strengths 
-determine the effect of higher wages on fertility.
-The substitute effect captures that when wages increase, time becomes more expensive, and
-people, therefore, work more and spend less time on non-wage earning activities, such as
-children or leisure.
-The income effect captures that higher wages increase the available income, which
-leads people to spend more time on time-intensive activities and less time working.
-Because women spend substantially more time on childrearing than men, the substitution
-effect dominates for women while the income effect dominates for men.
-
-Higher female wages may also shorten birth spacing if having children requires mothers to
-curtail their economic activities.
-Shortening birth spacing allows parents to take advantage of economies of scale in 
-childrearing---for example, looking after two children requires less than double the time 
-needed for one child \citep{Vijverberg1982,Hotz1997}.
-
-% Investment in children
-With increasing returns to education and lower offspring mortality, parents are likely to 
-reduce fertility and invest more in each child \citep{Rosenzweig1982a,Wolpin1997}.
-The higher return to education means a stronger incentive to invest in their children's
-education, thereby increasing the cost of having children and lowering fertility. 
-With lower expected mortality, parents need fewer births to reach the desired number of
-surviving children, which, in turn, allows parents to invest more in each child.
-
-An increased desire to invest in children may also lengthen birth spacing. 
-The clearest example of a positive effect of longer spacing is for health, as very short 
-spacing---approximately 24 months or less---leads to worse child health and mortality 
-outcomes \citep{Whitworth2002,Conde-Agudelo2012}.
-Whether longer spacing also improves human capital outcomes is more speculative with
-mixed evidence for developed countries and no evidence for developing countries
-\citep{Zajonc1976,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-
-% Son preference 
-Stronger son preference has traditionally been associated with shorter spacing and worse
-health outcomes for daughters when there no sons in the household
-\citep{Whitworth2002,Jayachandran2011}.
-Although son preference increases average fertility only marginally, differential stopping
-behavior means that girls tend to end up in larger families, resulting in fewer resources
-per child \citep{repetto72,clark00,Basu2010,Barcellos2014}.
-
-However, with the advent of sex selection, stronger son preference may lead to longer
-spacing because each sex-selective abortion adds 6–12 months to the length of the birth
-interval.
-After an abortion, the uterus needs at least two menstrual cycles---approximately 
-two months---to recover, or the subsequent risk of spontaneous abortion increases 
-substantially \citep{zhou00b}.
-Once conception can be attempted, the waiting time to conception is likely between
-one and six months. 
-Finally, sex-determination tests are reliable only from three months of gestation. 
-Hence, it takes at least six months before the couple is at the same point in the next 
-pregnancy as they were in the prior pregnancy when they decided to abort.
-
-% Factors/predictions
-The closest available proxies in the data for capturing the explanations linking
-fertility and birth spacing are the sex composition of previous children, mothers'
-education, and area of residence. 
-The remainder of the section discusses how the three variables fit into the
-explanations and the predicted effects.
-
-Sex composition proxies for son preference and the use of
-sex selection, both unobserved.%
-\footnote{
-The surveys ask about the ideal number of sons and 
-daughters, but these appear to be unreliable son 
-preference indicators; better-educated women simultaneously show 
-declining son preference and increasing sex selection 
-\citep{bhat03,pande07}.
-} 
-In the absence of sons, sex selection appears to increase 
-with lower desired fertility and higher parity
-\citep{Portner2015b,Jayachandran2017}. 
-Thus, for a given parity, birth intervals should lengthen 
-substantially over time for women with no sons, lower 
-desired fertility, and better access to sex selection.
-
-Both higher female education and urbanization are associated with 
-lower fertility and increased sex selection use, and, therefore, likely also changes in birth spacing
-\citep{das_gupta97,retherford03b,Portner2015b}.
-Furthermore, both variables are representative of
-the tremendous changes in India. 
-Figure \ref{fig:education_over_time} shows the substantial increase in female education,
-and the urban proportion of the population almost doubled from 18\% in 1960 to 35\% in 
-2019 \citep{United-Nations2019}.
-
-\begin{figure}[htpb]
-\centering
-\subfloat[Rural]{
-    \begin{minipage}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{educ_over_time_rural}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{educ_over_time_urban} 
-    \end{minipage}
-}
-\caption{Distribution of education by cohort for women 20 years or older
-using the four rounds of the NFHS}
-\label{fig:education_over_time}
-\end{figure}
-
-Urban women are likely to have lower fertility and higher use of sex selection than women 
-in rural areas.
-The lower fertility results from the higher cost of children and lower child mortality 
-risk in urban compared to rural areas.%
-\footnote{
-However, holding parental education constant, children in Indian slums have worse
-health outcomes than children in rural areas \citep{Portner2018a}.
-}
-The higher use of sex selection comes partly from the lower fertility and partly from
-higher income and better access to health care facilities in urban areas.
-
-Even though higher potential wages from more education should shorten birth spacing and
-lower fertility, the low and declining female labor force participation suggests little
-economic incentive to space children closer together.
-Even as women's education increased, their labor force participation stagnated or 
-decreased and is now one of the lowest outside the Middle East 
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018}.
-
-The decline in female labor force participation appears to be driven by a combination
-of a relatively small expansion in the sectors where women work and the income effect 
-from rapidly increasing male wages and education dominating the substitution effect from 
-higher female wages \citep{Klasen2015,Bhargava2018}.
-The income effect can dominate because not only do men have a higher average level of 
-education than women, men are also paid more than women for a given level of education, 
-and the returns to education increases with education in India \citep{Agrawal2011}.
-Hence, increasing male education will result in a larger increase in income than a 
-similar increase in female education.
-
-However, higher female education might still be associated with lower fertility and more 
-sex selection, provided better-educated women are better at producing child human capital, 
-as suggested by \citet{Behrman1999}. 
-In a situation with increasing returns to male education, households may desire 
-better-educated women because of their ability to produce better-educated sons, 
-rather than because of their higher potential income. 
-The higher return to male education provides an additional incentive to invest in sons' 
-education---with a better-educated mother one such investment---and leads to lower desired 
-fertility, makes sex selection more likely, and possibly increases birth spacing.
-The implication is that the usual policy recommendation of increased female education may not
-change sex selection unless there is a concurrent increase in the relative return to female
-education in the labor market.
-
-% Sanskritization
-Finally, the process of "Sanskritization" implies that as lower-caste females gain access
-to education, they adopt higher-caste norms such as stronger son preference and a
-retraction from the formal labor market \citep{Srinivas1956}. 
-The declining female labor force participation suggests that this process still 
-operates \citep{Abraham2013,Chatterjee2018}.
-Thus, although the expansion in female education will likely bring in groups who initially 
-have different norms, we are unlikely to see substantial changes in how women with a given 
-education level behave.
-
-% Summary / hypotheses
-In summary, with substantial increases in husbands' income and a declining female labor 
-force participation, I expect longer birth spacing over time, independent of education 
-levels.
-Furthermore, birth spacing likely increases the most among the better educated as their
-household income increase the most, and because of their presumptive use of sex selection. 
-Finally, "Sanskritization" implies that the changing composition of better-educated
-women will not substantially change the use of sex selection.
-
-\section{Estimation Strategy\label{sec:strategy}}
-
-% Requirements for method and the intuition behind each:  
-%  - Account for censoring (hazard model)
-%  - Work both with and without sex selection (competing risk part)
-%  - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
-%  - Capture that the shape of the hazard function differ across groups
-%    (nonproportionality); needs a better description, maybe using example
-%    of shorter spacing and/or use of sex selection. Differences in parity
-%    progression likelihood.
-
-The empirical analysis has three parts. 
-First, I document the changes in birth spacing over time and how the introduction of sex 
-selection influenced birth spacing. 
-Second, I compare period fertility estimates with predicted cohort fertility based on the 
-model of birth spacing. 
-Finally, I examine how birth intervals affect infant mortality and whether the apparent 
-increase in sex selection influenced mortality. 
-This section presents the empirical model for my analysis of birth spacing.
-
-The standard approach in the birth spacing literature is to use proportional hazard
-models with a single exit---the birth of a child---but there are two problems with the 
-standard approach in this setting.%
-\footnote{
-See \citet{Sheps1970} and \citet{Newman1984} for early discussions of why 
-hazard models are the preferred way to deal with the censoring of birth
-intervals.
-}
-
-First and foremost, the use of sex selection means that the sex of the next child is 
-no longer random and that the spacing to the birth of a boy will differ from the 
-spacing to a girl. 
-Therefore, I use a competing risk setup that captures both the non-randomness of 
-the birth outcome and the differential spacing.%
-\footnote{
-\cite{Merli2000} used a discrete hazard model to examine whether 
-there was underreporting of births in rural China, although they 
-estimated separate waiting time regressions for boys and girls.
-}
-
-Second, even without sex selection, it is unlikely that characteristics, such as previous
-births' sex composition, have the same effects throughout the entire birth interval.
-The proportional hazard model requires that an individual's hazard is a 
-fixed proportion of the hazard for any other individual. 
-Nonconstant effects violate that assumption, and the results from a proportional hazard 
-model would, therefore, be biased. 
-The proportionality assumption is especially problematic for higher-order birth 
-intervals because there are substantial differences across groups in the likelihood 
-of progressing to the next birth and how soon couples want their next child if they 
-are going to have one \citep{Whitworth2002,Bhalotra2008}.
-
-The introduction of prenatal sex determination exacerbates any bias from
-the proportionality assumption for two reasons. 
-First, different groups have different levels of sex-selective abortion use and, thereby, 
-birth spacing. 
-Second, within a birth interval, a household's use of sex selection may vary, and that
-means that the effects of covariates vary as well.
-
-Therefore, I use a nonproportional hazard specification that allows the shape of the 
-hazard functions to vary across groups.
-Furthermore, the combination of a nonproportional specification and a flexible baseline
-hazard mitigates the potential effects of unobserved heterogeneity \citep{Dolton1995}.
-
-The model is a discrete-time, nonproportional, competing risk hazard model with two 
-exit states: Either a boy or a girl is born. 
-The unit of analysis is a spell---the period from one parity birth to the following 
-birth or censoring. 
-For estimation purposes, the spells begin nine months after the previous birth because 
-this is the earliest we should expect to observe a new birth. 
-Censoring can happen for three reasons: The survey takes place, sterilization of the 
-woman or her husband, or imposed because of too few births for the method to work.
-
-For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
-the spell continues until time $t_i$, when either birth or censoring of the spell 
-occurs.
-The time of censoring is assumed to be independent of the hazard rate,
-as is standard in the literature.
-The two exit states are the birth of a boy, $j=1$, or a girl, $j=2$.
-
-The discrete-time hazard rate $h_{ijt}$ is 
-\begin{equation}
- h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
- {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2.
- \label{eq:hazard}
-\end{equation}
-$D_{j}(t)$ is the piece-wise constant baseline hazard for outcome $j$, captured
-by dummies and the associated coefficients,
-\begin{equation}
-D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
-\end{equation}
-with $D_m = 1$ if $t=m$ and zero otherwise.
-This approach to modeling the baseline hazard is flexible and does not restrict the 
-baseline hazard unnecessarily.
-$\mathbf{Z}$ is the nonproportional part, which includes the interactions between 
-$D_j(t)$ and a set of explanatory variables and the interactions of those.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
-
-% To further minimize any potential bias from assuming proportionality, estimations 
-% are done separately for different levels of mothers' education and different periods.
-% I discuss the choice of which variables to use for nonproportionality below.
-
-Equation \ref{eq:hazard} is equivalent to the logistic hazard model and has the same 
-likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, splitting spells into smaller intervals---here equal to three months---and 
-treating them as observations, I can estimate the model using a standard multinomial 
-logit model. 
-% In the reorganized data, the outcome variable is 0 if the woman does not have a child 
-% in a given interval (the base outcome), 1 if she gives birth to a son in that interval, 
-% and 2 if she gives birth to a daughter in that interval.
-
-I use the model to predict birth interval lengths, parity progression probabilities, 
-and the sex ratio rather than present coefficients because the interpretation 
-of competing risk model coefficients is challenging \citep{thomas96}.
-The predicted parity progression probability is the likelihood of giving birth by the
-imposed censoring based on standard survival curve calculations averaged across all
-women in a given sample.
-
-For birth interval lengths, I estimate a set of percentile durations. 
-I first calculate for each woman when there is a given percentage chance that she will have 
-given birth, conditional on the probability of giving birth in the spell. 
-For example, with an 80\% parity progression probability, the median birth interval 
-is the predicted number of months before a woman passes the 60\% $(100-\frac{80}{2})$ 
-mark on her survival curve. 
-I then add nine months to account for the start of the spell. 
-The reported statistic is the average of a given percentile interval across all women in 
-a given sample using the individual progression probabilities as weights.
-
-% The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
-% parity progression probabilities as weights.
-% For an individual woman, the estimated percent of births that are boys at $t$, $\hat{Y_t}$, is:  
-% \begin{equation}
-% \hat{Y}_t 
-% = 
-% \frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-% { P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-% \times 100,
-% \label{eq:probability_son}
-% \end{equation}
-% where $b$ and $g$ are the predicted probabilities of having a boy and a girl, respectively,
-% conditional on the explanatory variables and not having had a child before $t$.
-% Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
-% $t$ gives the predicted percent of boys over the entire spell for an individual.%
-% \footnote{
-% Imagine $T=2$. 
-% If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
-% then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
-% }
-
-The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
-parity progression probabilities as weights.
-To find the individual sex ratio, I estimate the percentage of births that are boys at $t$, 
-conditional on not having had a child before $t$.
-Weighting the percent boys with the likelihood of exiting the spell with a birth across all 
-$t$ gives the predicted percentage of boys over the entire spell for an individual.%
-\footnote{
-Imagine $T=2$. 
-If 54\% and 66\% of births are boys and the likelihood of giving birth 20\% and 40\%, 
-then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$\% boys. 
-}
-
-\section{Data\label{sec:data}}
-
-The data come from the four rounds of the NFHS
-collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.
-The surveys are large: 89,777, 90,303, 124,385, and 699,686 women, respectively. 
-NFHS-1 and NFHS-2 surveyed only ever-married women, while the two later surveys included 
-never-married.
-
-I first discuss sample restrictions and their motivations, then introduce the potential 
-issue of underreporting of female births and the imposed censoring of birth intervals.
-Next, I discuss how the analyses are split by periods to capture the introduction
-and changing legality in prenatal sex determination.
-Finally, I introduce the explanatory variables, split by whether they enter as
-proportional or nonproportional variables.
-
-I focus on the three spells starting from the first birth and ending with the 
-fourth birth.
-I exclude the interval from marriage to the first birth because many are imputed and the
-higher-order intervals because few women had five or more births, especially among the 
-better-educated.
-
-I restrict the sample to Hindus for two reasons.
-First, Hindus are the majority population group, about 80\% of India’s population.
-Second, the prior literature shows that son preference and sex selection vary 
-substantially between Hindus and the second largest group, Muslims. 
-Combining them and assuming that the baseline hazard is the same would lead to biased 
-results.
-Because of space constraints and the relatively small number of observations once split 
-by education and periods, I do not provide separate results for Muslims or any  
-remaining groups, such as Sikhs, Jains, and Christians.
-
-Finally, I exclude visitors and women in any of the following categories: Never married; 
-no gauna yet; married more than once; divorced; not living with husband; inconsistent age 
-at marriage; or education information missing.  
-The same goes for women who had at least one multiple births, reported giving birth 
-before age 12, had a birth before marriage, or had an interval between births of less than 
-nine months.
-
-In addition to the large number of women surveyed and the long period covered, a significant 
-benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
-spacing between births and probe for ``missed'' births.
-For India, the main concern is the underreporting of deceased children, especially a systematic 
-recall error where respondents' likelihood of reporting the birth of a deceased child depends 
-on the sex of that child.
-Unreported deceased children inflate the length of birth intervals and, with declining mortality, 
-make changes over time appear too small.
-In the online appendix, I provide a detailed analysis of systematic recall error, which 
-shows that recall error depends heavily on how long ago a woman was married. 
-I, consequently, drop women married 22 years or more.%
-\footnote{
-Recall error is likely behind the designation of the first two rounds of NFHS as ``moderate 
-quality'' in an analysis of the quality of birth histories in DHS surveys and its impact 
-on fertility estimates \citep{Schoumaker2014}.
-}
-
-To ensure that there are enough births for the method to work, I censor spells at 96 
-months (eight years) after a woman can first give birth, equivalent to 105 months 
-after the birth of the prior child.
-Less than 1\% of observed births occur after the cutoff.
-The final sample consists of 
-\input{../tables/num_women.tex}
-% [number] women, with [number] parity one through four births.
-
-% %
-% \footnote{
-% \input{../tables/num_missed.tex}
-% }
-
-Direct information on sex selection is not available, so I compare periods 
-based on the changes in access and legality of prenatal sex determination in India.
-Abortion has been legal in India since 1971.
-Reports of sex determination appeared around 1982--1983, and the number of clinics 
-quickly increased \citep{Sudha1999,bhat06,Grover2006}.
-In 1994, the Prenatal Diagnostic Techniques Act made determining and communicating 
-the sex of a fetus illegal.%
-\footnote{
-% Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
-There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2019}.
-}
-Finally, although sex selection increased even after 1994, we may have passed a 
-turning point in its use in the mid-2000s \citep{Das_Gupta2009,Kumar2012,Bongaarts2013,Diamond-Smith2015}.
-
-I use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The first covers the period before sex selection became available and the second from when sex 
-selection became available until the Prenatal Diagnostic Techniques Act.
-I have split the period from 1995 until 2016 into two to examine if there was support for 
-the prior literature's hypothesized reversal in child sex ratios and son 
-preference in India.
-
-The allocation of spells into periods is determined by when conception, and, therefore, 
-decisions on sex selection can begin. 
-Hence, some spells cover two periods, which may bias downward the differences between the 
-periods.
-Most sterilizations take place soon after giving birth. 
-These spells, therefore, do not show up in the samples used. 
-Furthermore, sterilization depends strongly on prior children's sex composition; the 
-fewer boys, the lower the probability of sterilization. 
-The effect is to bias downward the differences in parity progression probabilities.
-
-I divide the explanatory variables into two groups, nonproportional and proportional. 
-The first group consists of characteristics shown in the prior literature to affect the 
-spacing choice and the use of sex selection: Mother’s education, sex composition of 
-previous children, and area of residence.
-To minimize any potential bias from including proportional variables, I estimate separate 
-models for each birth interval, education group, and period combination, rather than 
-including education as a variable.
-
-I divide education levels into four groups: No education, 1--7 years, 8--11 years, and 
-12 and more years.
-The latter two correspond to having completed primary and secondary school, 
-respectively.%
-\footnote{
-Although there are variations by state, elementary education in India consists of a 
-primary school covering grades one through five and an upper primary---or middle 
-school---covering grades six through eight. 
-Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
-and 11 and 12 for ``upper secondary.''
-}
-To ensure that the results are comparable with the prior literature on fertility
-and mortality in India, I follow the NFHS reports, except that I combine the 
-less than five years and 5--7 years of schooling completed and the 8--9 
-and 10--11 years of schooling completed to ensure sufficient cell sizes.
-
-I capture sex composition with dummy variables for the possible combinations, ignoring 
-the ordering of births.%
-\footnote{
-With sex selection, the composition of prior children is, in principle, endogenous. 
-It is beyond the scope of this paper to develop a method for dealing with this issue. 
-}
-Area of residence is a dummy variable for living in an urban area.
-
-The second group of variables consists of those expected to have an approximately 
-proportional effect on the hazard.
-These include the mother's age when the spell begins, the household's
-land ownership, and whether it belongs to a scheduled tribe or caste.
-Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present the descriptive 
-statistics.
-
-\section{How Birth Spacing Changed\label{sec:results}}
-
-% Explain question and what I am doing
-The first question I address is how birth spacing responded to the significant 
-changes in India.
-I begin with a broad outline of how parity progression probabilities and
-sex ratios have changed over time and by groups.
-I then use these results to separately discuss the changes in birth spacing for 
-women who do not appear to use sex selection and for those who do.
-
-Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
-show the 25th, 50th, and 75th percentile birth interval durations in 
-months, the sex ratio, and the probability of having a birth for each spell
-by education levels and area of residence.%
-\footnote{
-Results for urban women without education, rural women with 12 or more years of 
-education, and the fourth spell for women with 12 or more years of education are
-in the online appendix because of relatively small samples.
-}
-The sex ratio graphs also show the natural sex ratio, approximately 51.2\% boys
-\citep{jacobsen99,Portner2015b}.
-The underlying values with bootstrapped standard errors and tests for statistically
-significant differences across sex compositions are available in the online appendix.
-
-\captionsetup[figure]{skip = -16pt}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_rural}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for rural women with no education by spell, sex composition, and period}
-\label{fig:spacing_low_rural}
-\end{figure}
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
-% \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for urban women with no education by spell, sex composition, and period}
-% \label{fig:spacing_low_urban}
-% \end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_rural}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for rural women with 1--7 years of education by spell, sex composition, and period}
-\label{fig:spacing_med_rural}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_urban}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for urban women with 1--7 years of education by spell, sex composition, and period}
-\label{fig:spacing_med_urban}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_rural}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for rural women with 8--11 years of education by spell, sex composition, and period}
-\label{fig:spacing_high_rural}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_urban}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for urban women with 8--11 years of education by spell, sex composition, and period}
-\label{fig:spacing_high_urban}
-\end{figure}
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
-% \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for rural women with 12 or more years of education by spell, sex composition, and period}
-% \label{fig:spacing_highest_rural}
-% \end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_urban}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for urban women with 12 or more years of education by spell, sex composition, and period}
-\label{fig:spacing_highest_urban}
-\end{figure}
-
-% [Parity progression probability]
-The parity progression and the sex ratio show two broad trends.
-First, 
-in line with the falling total fertility rate, the likelihood of a next birth 
-has decreased over time.
-The likelihood of a next birth fell more rapidly, the higher the education and the 
-higher the parity.
-Within a given spell and period, parity progressions are lower in urban than rural areas, 
-if at least one son is present, and the more educated the mother.
-
-% [Sex ratios]
-Second, sex ratios have become more male-dominated for women with no sons, indicating the spread 
-of sex selection. 
-The percentage of boys increased more quickly, the higher the education and the higher the parity. 
-There are no clear trends for the other sex compositions. 
-Within a given spell and period combination and in the absence of a son, sex ratios are higher, 
-the more educated the mother, and the higher the parity. Sex ratios are also higher in urban than 
-in rural areas.
-Some women with one son also show an unnaturally high percentage of boys, although the 
-failing fertility makes these estimates noisy.
-
-\subsection{When Sex Selection Is Less Used}
-
-To separate the effects of the introduction of sex selection and the other changes in
-India, I first discuss how the lengths of birth intervals have changed in situations where, 
-based on sex ratios, there appears to be less sex selection.
-The group broadly covers women with no education, regardless of their children's sex 
-composition, and women with any education who have one or two sons already.
-
-Despite the apparent lower level of sex selection, son preference is still evident with 
-the shortest spacing when they have only girls. 
-Notably, for those who appear the least likely to use sex selection---rural women with no
-education---birth spacing is almost uniformly statistically significantly longer when at
-least one son is present than if no son is present. 
-Furthermore, the difference in birth interval length across sex compositions has grown over
-time as spacing when sons are present has become longer.
-
-% [25th percentile birth intervals]
-A remarkably high proportion of birth intervals are still very short.
-For all but the most educated, 25\% or more have their second and third child 
-within 24 months of the previous birth.
-These intervals are substantially below the 24 months between 
-\emph{pregnancies} the WHO recommends.
-Even with the more substantial lengthening of birth intervals for higher parities, the 25th
-percentile duration is still around 24 months for the fourth spell for women with less than
-eight years of education.
-
-% [median birth intervals]
-Median birth interval lengths have also increased relatively little---only three to six months 
-over the four decades---compared to around 3.5 months \emph{per decade} in other countries with 
-declining fertility \citep{Rutstein2011,Casterline2016}.%
-\footnote{
-The NFHS reports show median durations of closed birth intervals of approximately 31 months, 
-which have barely moved over time, underscoring the importance of accounting for censoring 
-when examining birth spacing.
-}
-The result is that most of the median birth interval durations are still at 36 months or
-below, with the shortest only 29 months.
-
-Birth intervals appeared to lengthen the most for women who are the least likely to work.
-For example, from lowest to highest education, the average duration of third-spell birth 
-intervals for urban women with one boy and one girl increased by 2.7, 3.4, 5.8, and 1.8 
-months over the four decades.%
-\footnote{
-For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0.
-See the online appendix tables for the average birth interval durations.
-}
-Hence, women with the lowest labor force participation---those with 8--11 years 
-of education---also saw the largest increases in average spacing, possibly driven by the 
-substantial improvement in household income for this group from economic growth.
-
-% [75th percentile birth intervals]
-The most substantial changes occurred in the 75th percentile birth interval durations, 
-where the more the parity progression probabilities declined, the more the birth interval 
-lengthened. 
-For example, the probability of a fourth birth for urban women with 8--11 years 
-of education and two sons and one girl has declined by almost 40 percentage points as the 
-75th percentile birth interval length increased by 22 months.
-Compare this with rural women of no education with a boy as their first child, for whom the 
-probability of a third birth declined by fewer than six percentage points while the birth 
-interval increased by only slightly more than two months.
-
-%0.637 0.241
-
-These results are in line with prior research showing that falling fertility is associated 
-with a lengthening of particularly the longer birth intervals, although why is still an 
-unresolved question \citep{Casterline2016}.
-The most educated women who already have a son is an exception to this trend; the 
-probability of a third birth declined rapidly, but the birth interval lengths changed little. 
-These women both have better access to modern contraceptives and are better at using 
-traditional contraceptive methods \citep{Rosenzweig1989}. 
-Hence, it is possible that the lengthening of birth intervals with falling fertility in 
-the prior research arises because unintended births become a relatively larger proportion 
-of the total number of births for a given parity and those can occur at any time.
-
-% [Birth intervals with sex selection]
-\subsection{Sex Selection and Birth Spacing}
-
-A clear illustration of how the combination of son preference and the introduction of 
-sex selection affected birth spacing comes from the third spell of the best-educated urban 
-women.
-With two girls, almost 80\% of the third births are boys, and the 75th percentile 
-birth interval length is close to 70 months, an increase of almost 21 months over the four
-decades. 
-This interval has gone from being statistically significantly shorter than the intervals 
-with at least one son to now being a statistically significant 13 months longer.
-
-Even more striking, most of the change took place right at the introduction of sex 
-selection.
-The 75th percentile birth interval with two girls increased from 48 months to 
-64 months in a decade, while the other sex compositions showed a slight decrease from 
-around 55 months to 54 months.
-These birth spacing changes may even understate the impact because this particular group
-appears to have had access to sex selection even before it became widespread, as shown by
-the unequal sex ratio for the 1972--1984 period for women with two girls.
-
-The 75th percentile changes are the most dramatic, but the apparent use of sex selection 
-also affects the 25th and median birth interval lengths. 
-For the best-educated urban women with two girls, the 25th percentile birth interval
-length increased by six months, or 23\%, while the median percentile birth interval length
-increased by 15 months (43\%).
-
-Not surprisingly, given these changes, the third spell for the best-educated women shows
-the clearest reversal in the spacing pattern; the birth intervals with two girls are
-consistently statistically significantly longer than the intervals with one or two boys, 
-no matter the percentile used.
-A similar reversal, although more muted, occurred for the third spell for urban women 
-with 1--7 years of education and both urban and rural women with 8--11 years of 
-education.
-
-Did the predictions of declining use of sex selection come true? 
-There is no clear evidence for or against a reversal in the use of sex selection, with 
-some cases showing increases in sex ratios between the last two periods, others little 
-change, and some a decline. 
-The best-educated women are again a good illustration. 
-The sex ratio for women with two girls continued to increase over the last two periods, 
-but the likelihood of a third birth declined. 
-Furthermore, if the first child was a girl, the sex ratio for the second birth dropped 
-slightly, as did the probability of having a second birth. 
-However, there are also cases where there is no abatement in the increasing use of sex 
-selection. 
-For example, for rural women with 1--7 years of education, the sex ratios in the absence 
-of daughters continued to increase while the likelihood of an additional birth remained 
-high.
-
-In summary, over the four decades, birth intervals lengthened with improving economic 
-conditions and falling fertility. 
-These increases are larger with higher parity and higher percentile measure. 
-Furthermore, when there is little evidence of sex selection use, it appears that the women 
-least likely to work are also those with the most substantial increases in birth interval 
-lengths.
-
-However, sex selection appears to be behind the most substantial increases in birth spacing. 
-The best-educated women with two girls had the most biased sex ratio and the most 
-significant increase in birth interval lengths. 
-Over the four decades, the median birth interval length for this group increased by almost
-15 months. 
-Even more striking, the 75th percentile birth interval length increased by a staggering 21
-months, most of that within a decade of the introduction of sex selection.
-
-\section{What Happened to Fertility?\label{sec:fertility}}
-
-The tempo effect from longer birth intervals means that the total fertility rate may 
-underestimate cohort fertility. 
-The next question I address is, therefore, to what extent did the changes bias the 
-fertility estimates for India? 
-To this end, I compare fertility based on a variation of the total fertility rate with 
-predicted cohort fertility from the hazard model.
-Table \ref{tab:fertility} shows the two fertility measures by area of residence and education.
-
-\input{../tables/fertility.tex}
-
-The fertility rate follows the same procedure as in the Demographic and Health Survey 
-reports: I use the births from 36 to 1 month before the survey month to calculate 
-age-specific fertility rates for five-year age groups and then sum the age-specific 
-fertility rates multiplied by five  \citep{Croft2018}.
-However, because the hazard model predictions only use births up to parity four, I use the 
-same set of births for the fertility rate and label it the ``four-parity'' fertility rate. 
-Hence, the presented fertility rates are not directly comparable to those in the NFHS reports.
-
-%
-% \footnote{
-% See \citet{Croft2018} for more detail.
-% Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
-% is based on the household rosters, assuming that never-married women have had no children.
-% Because of the low number of births to women aged 45 to 49 this age group was not
-% used for the hazard model estimations and, therefore, is also excluded for the fertility
-% rate.
-% The marital total fertility rate lead to unrealistically high numbers and is, therefore,
-% not presented \citep{Hoem2011,Laplante2015}.
-% }
-
-Because NFHS-1 was after the introduction of sex selection, I cannot calculate a fertility 
-rate in precisely the same manner for a period before sex selection was widely available.
-Instead, I calculate the fertility rates for women between 15 and 39 years of age five years 
-before the survey month, again using the number of births three years before.
-This rate is shown as ``1987--1988'' in the table.
-Given the relatively low number of births to women 40--45 years of age, this approach 
-provides the best estimate of the fertility rate when sex selection still was not 
-widespread.
-
-To predict cohort fertility based on the hazard models, I estimate the parity progression 
-probability for each spell. 
-Because parity progression depends on the sex composition of prior children, I estimate the 
-probability for each sex composition and weigh the probabilities with the likelihood of 
-the sex compositions.
-The survey rounds do not coincide directly with the periods used for the hazard model.
-Therefore, I compare the model results for 1972--1984, 1985--1994, 1995--2004,
-and 2005--2016 with rounds 1 through 4 of the NFHS, respectively.
-
-I include the spell from marriage to first birth, despite the problems capturing the exact 
-timing of marriages because the estimated progression probabilities should not be affected 
-by this problem. 
-I begin with the age of marriage for each woman and predict the likelihood of progressing 
-to each parity, assuming three-years increases in age between births. 
-Shorter assumed increases in age lead to slightly higher predicted fertility.
-
-Sterilizations are not incorporated into the hazard model because most occur
-immediately after giving birth. 
-To compensate, I estimate the probability of sterilization using a Logit model and use 
-that to scale down the parity progression probability when predicting cohort fertility.
-
-The predicted cohort fertility based on the hazard model is higher than the four-parity 
-fertility rate in almost all cases. 
-Only women with no education in the first period show little difference between the two 
-fertility measures, a situation where fertility is high, spacing very short, and likely 
-unchanged for an extended period.
-
-Consistent with a more substantial bias in the period fertility rate when the age of marriage 
-and the length of birth intervals increase, the absolute bias is least in the first 
-and the last period and highest in the middle two periods.
-Hence, the fertility rate declined too fast from the mid-1980s to the century's end.
-Only recently, as the rate of increase for the birth interval lengths has slowed, have the 
-two fertility measures begun to converge again.
-Even with the convergence, the predicted 2005--2016 cohort fertility is still above the 
-1992--1993 fertility rate for every group, except urban women with no education. 
-Furthermore, for the last period, the predicted cohort fertility remains at least 
-10\%--20\% higher than the fertility rate.
-
-Another indication of how tempo effects bias the fertility rate bias is that the
-fertility rate \emph{increases} for some groups.
-For example, for urban women with 8--11 years of education, the fertility
-rates were 1.84, 1.81, and 1.87 over the last three surveys.
-This pattern likely arises from the stabilization of the age of first birth and the 
-spacing between births.
-
-Finally, even with the declines in the predicted cohort fertility, it is still mostly 
-above replacement.
-Only for urban women with 12 or more years of education is the predicted cohort
-fertility clearly below 2.1 children.
-Even then, cohort fertility is still more than 0.3 children higher than 
-the fertility rate estimate of 1.5.
-Furthermore, the predicted cohort fertility numbers are likely too low because I use only
-the first four births and births before the imposed 105-month censoring of birth interval
-durations.
-
-\section{Mortality and the Changing Birth Spacing\label{sec:mortality}}
-
-The final question I address is whether there is an association between infant mortality 
-and increases in birth spacing associated with the introduction of sex selection. 
-Starting with the sample used for estimating birth spacing, I select children born more 
-than 12 months before the survey month. 
-I restrict the analyses to parities two and three because of the small number of births 
-and deaths at parity four. 
-Furthermore, I do not show the results for women with 12 or more years of education 
-for the 1972--1984 period because of the small number of women.
-
-The dependent variable is whether the child died within the first 12 months of life.
-The main set of explanatory variables consists of dummies for the spacing from
-the prior birth.
-The birth interval duration dummies cover 12-month periods, starting nine months after the 
-prior birth, until the 57-month dummy, which covers until 105 months after the prior birth.
-I use dummies for the sex of the index child and the sex composition 
-of the prior children.
-The birth spacing dummies, the sex of the index child, and the sex composition dummies
-are all interacted.
-Because the actual number of abortions is unobserved, the interactions between
-the sex composition of prior children and the sex of the index child serve
-as proxies for the use of sex selection.
-The other explanatory variables are the same as above, and estimations
-are done separately by education level and parity.
-
-I estimate the probability of infant mortality using a Logit model.
-Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} show 
-the predicted probability of the second child dying within the first year at the 
-possible combinations of index child sex, sex composition of prior children, and 
-birth spacing, with all other variables at their average values.%
-\footnote{
-The online appendix shows the corresponding graphs for the third child.
-}
-The graphs do not show confidence intervals to improve legibility.
-
-An important caveat is that the estimations do not address potential selection problems.
-For example, suppose women who have diﬀiculties conceiving or carrying a pregnancy to 
-term also have a higher mortality risk for their offspring. 
-In that case, a spurious correlation between long birth spacing and mortality may arise 
-\citep{Kozuki2013}. 
-Unfortunately, methods to address selection, such as family fixed effects, do not work 
-well when the number of births is as low as it is here for better-educated women 
-\citep{Kozuki2013,Molitoris2019}.
-However, the fixed effects and linear probability results did not 
-deviate substantially in prior research.
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \setcounter{subfigure}{-1}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[No Eduction]{\includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{-0} 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[One to Seven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Second Child's Infant Mortality 
-% for Women with No Education
-% and Women with One to Seven Years of Education}
-% \label{fig:mortality_low_med}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \setcounter{subfigure}{-1}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Eight to Eleven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \begin{minipage}[t]{0.39\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Second Child's Infant Mortality 
-% for Women with Eight to Eleven of Education
-% and Women with Twelve or More Years of Education}
-% \label{fig:mortality_high_highest}
-% \end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_low_med}
-\caption{Infant mortality by preceding birth interval length across periods for second child of women with 
-no education and women with 1--7 years of education}
-\label{fig:mortality_low_med}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_high_highest}
-\caption{Infant mortality by preceding birth interval length across periods for second child of women with 
-8--11 and 12 and above years of education}
-\label{fig:mortality_high_highest}
-\end{figure}
-
-There has been substantial convergence in mortality risk across groups over time.
-For intervals 21 months or longer, there is now little difference across 
-the education groups, with even the no-education group showing an infant mortality risk 
-below 5\%.
-
-Very short birth intervals still exhibit a higher mortality risk, although the 
-effect declines with education level.
-The mortality risk is 3\%--4\% for the best-educated women, whereas women with no 
-education still show a risk that is close to 10\%.
-
-Despite the prior findings of differential mortality by sex, there is little evidence 
-that girls have substantially higher mortality risk.
-There is some weak evidence that a boy born after a girl has a lower mortality
-risk in the earliest periods.
-However, this difference disappears with the general decline in mortality risk.
-
-Despite the concern that multiple abortions might increase mortality risk by shortening 
-the interval between pregnancies, there is no evidence for this effect. 
-Suppose repeated sex-selective abortions lead to a higher mortality risk for the child
-eventually born. 
-In that case, boys born after a girl---the solid lines---should have an increased risk 
-with longer spacing for the two highest education groups in the last two periods.
-However, there are no apparent consistent differences between these groups and the other 
-potential combinations. 
-The same holds for the third spell.
-
-% line 3661 in an_infant_mortality.log
-The raw numbers for women with the most uneven sex ratio also suggest that even with a 
-very high apparent use of sex selection, there is no impact on mortality. 
-A total of 1,004 women with 12 or more years of education and no boys at the start of 
-the third spell in the last period had a third child, of which 685 were boys. 
-Of these 685 boys, only six died within the first year of life. 
-Half of those who died were born in the 9--32-month interval, and none died in the 
-57-month+ interval.
-
-\section{Conclusion\label{sec:conclusion}}
-
-% Background
-Over the past four decades, India saw a dramatic increase in the male-to-female
-sex ratio at birth as access to sex selection spread and son preference remained high. 
-Simultaneously, economic growth was strong, schooling increased, and the total fertility 
-rate declined to almost replacement level.
-
-% Questions
-The main question I address in this paper is how birth spacing responded to the 
-significant changes in India between 1972 and 2016, particularly the spread of sex 
-selection.
-I also examine two related questions.
-First, did changes in birth spacing make us overestimate the decline in cohort fertility?
-Second, what is the relationship between infant mortality and the changes in birth spacing 
-and sex selection?
-
-% What has happened to spacing and why
-The most substantial lengthening of birth intervals occurred among the best-educated women,
-likely because of substantial use of sex selection combined with falling fertility.
-Take, for example, women with 12 or more years of education who had two girls. 
-As the sex ratio reached almost 80\% boys, the expected median birth interval length
-increased by almost 15 months, and the 75th percentile interval length increased by 21 months.
-Most of the lengthening in the long intervals came immediately after the introduction of sex 
-selection in India.
-
-For some groups, the lengthening in birth intervals was so substantial that it led to a
-reversal of the traditional spacing pattern: In the absence of sons, these groups now show
-statistically significant longer, rather than statistically significant shorter, birth
-intervals than if there is at least one son.
-
-The women who are the least likely to use sex selection, as indicated by their sex ratios
-at birth, still show the traditional spacing pattern with short spacing in the absence of
-sons.
-
-Son preference continues to show in fertility decisions. 
-Fertility has declined for all groups, but the likelihood of having an additional child
-still depends strongly on the number of sons, with women with no sons having the highest 
-parity progression probabilities.
-
-Birth intervals also lengthened in cases when sex selection appears to be less used.
-However, compared to other countries with similar declines in fertility, the median 
-spacing increases were smaller at three to six months over the period. 
-Most of the median intervals when sex ratios are close to normal are still short at 36 
-months or below. 
-Furthermore, many women still have very short birth intervals.
-More than 25\% of women have their next child within 24 months of the previous birth in 
-many cases.
-
-% [predictions of declining sex selection] 
-Despite predictions that the use of sex selection would decline, there is no clear 
-evidence of this. 
-The most likely users of sex selection continue to show substantial male-biased sex ratios, 
-although there may be some leveling off.
-More concerning, the increasingly male-biased sex ratios among less-educated women suggest
-that sex selection use appears to be spreading as fertility falls.
-
-% fertility bias
-
-The increases in spacing make the total fertility rate a more biased measure of cohort 
-fertility. 
-This bias was most prominent early in the spread of access to sex selection when the 
-fertility rate was up to one child lower than the predicted cohort fertility. 
-However, it is still present, with the predicted cohort fertility 10\%--20\% 
-higher than the fertility rate. 
-At 1.8 children, the best-educated urban women are the only group for whom the predicted 
-cohort fertility is below replacement.
-
-Tempo effects are studied extensively in the literature \citep[see, for example, ][]{Bongaarts1999}.
-Still, there are, to my knowledge, no other cases where there has been as 
-substantial an increase in birth interval lengths and associated bias in fertility rates 
-as for India.
-It is conceivable that we might see increases in the total fertility rate as birth spacing 
-stabilizes or even shortens again if interventions against sex selection are successful.
-
-% Mortality
-There has been a substantial reduction in infant mortality over time, and the size of the 
-reductions is inversely related to the mother's education.
-Hence, there is now little difference in mortality risk across education groups if the 
-birth took place more than 21 months after the previous birth.
-Short birth spacing is still associated with higher mortality, although the effect is 
-small for the best-educated women.
-There is no evidence that repeated abortions are associated with higher infant mortality
-for the child eventually born; boys born after long birth intervals to families with
-well-educated mothers, only daughters, and high predicted sex ratios---the combination of
-which suggests repeated sex-selective abortions---have no higher infant mortality than other
-children.
-
-% Implications 
-The results here paint a less rosy picture of India's prospects for a continued reduction 
-in population growth than generally accepted. 
-With predicted cohort fertility still substantially higher than the period fertility rate, 
-India's total fertility rate will likely stabilize or even increase as birth intervals slow 
-their lengthening. 
-The more successful the attempts at combatting sex selection are, the more likely an 
-increase in the total fertility rate will be. 
-Furthermore, the rapid decline in infant mortality risk, combined with likely future 
-declines as the proportion of very short birth intervals falls, may also slow the 
-reduction in population growth.
-
-% Future research and policy
-
-There are two crucial questions that future research should address.
-
-First, what is behind the improvements in girls' health status?
-Access to sex selection means that girls-only families are less likely to have
-very short birth intervals, which may reduce sibling competition. 
-Hence, better health outcomes for girls with sex selection is available could be an 
-unintended side-effect, rather than the result of girls becoming more valued as is often 
-assumed \citep{Hu2015}. 
-Comparing prior children's outcomes across sex composition and the sex of the next child 
-could be a way to understand why girls' health outcomes improve in the presence of sex 
-selection.
-
-Second, what is the relationship between female labor force participation and sex selection? 
-Women may be staying out of the labor market precisely because sex selection makes 
-them more likely to have a boy and increases the expected birth spacing. 
-Better job opportunities for women could reduce sex selection use for two reasons. 
-First, it becomes more expensive to be out of the labor market for long periods. 
-Second, the differential in potential earnings between husband and wife would decline, 
-making it relatively more attractive to invest in daughters' human capital.  
-This approach could, however, be a double-edged sword. 
-If better job opportunities further lower fertility, the use of sex selection may increase, 
-everything else being equal.
-Understanding the trade-off between long-term benefits from improvements in women's labor 
-force participation and short-term costs from potential increases in sex selection is of 
-paramount importance.
-
-% The higher return to male offspring's human capital combined with access to sex
-% selection may also explain another puzzle, why is the labor force participation so
-% low when fertility is low and education has increased.
-% As shown here, part of the answer may be that the number of children is, in fact, not as 
-% low as previously thought, both because of the increased spacing and that more 
-% children survive.
-
-\clearpage
-
-\onehalfspacing
-\bibliographystyle{aer}
-\bibliography{sex_selection_spacing}
-
-\addcontentsline{toc}{section}{References}
-
-\clearpage
-\newpage
-
-\appendix
-
-% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
-\renewcommand\thefigure{\thesection.\arabic{figure}}    
-\renewcommand\thetable{\thesection.\arabic{table}}
 
@@
 \newpage
+
+\appendix
+
+% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
+\renewcommand\thefigure{\thesection.\arabic{figure}}    
+\renewcommand\thetable{\thesection.\arabic{table}}
 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{currently_working_rural_40}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{currently_working_urban_40} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{currently_working_rural_30}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{currently_working_urban_30} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{currently_working_rural_20}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{currently_working_urban_20} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_cash_rural_40}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_cash_urban_40} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_cash_rural_30}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_cash_urban_30} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_cash_rural_20}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_cash_urban_20} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_family_rural_40}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_family_urban_40} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_family_rural_30}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_family_urban_30} 
@@
 \subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_family_rural_20}
@@
 \subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \includegraphics[width=\textwidth]{work_family_urban_20} 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_low_med}
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth,keepaspectratio=true]{mortality_spell_3_low_med}
 \caption{Infant mortality by preceding birth interval length across periods for third child of women with 
@@
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_high_highest}
+\includegraphics[width=0.8\textwidth,keepaspectratio=true]{mortality_spell_3_high_highest}
 \caption{Infant mortality by preceding birth interval length across periods for third child of women with 
@@
 
+\clearpage
+
+\onehalfspacing
+\bibliographystyle{aer}
+\bibliography{sex_selection_spacing}
+
 \end{document}

### 2021-10-06 typesetting/sex_selection_spacing-figure_typesetting.tex
Figures for typesetting at Demography

--- 2021-05-03 paper/sex_selection_spacing-final.tex
@@
 
-% For word counting uncomment line below and raggedright below
-% http://countwordsfree.com/#
-% \usepackage[nolists]{endfloat}
-
-% \bibpunct{(}{)}{;}{a}{}{,}
 \newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
@@
 
-% Attempt to squeeze more floats in
 \renewcommand\floatpagefraction{.9}
@@
 University of Washington.
-Text and code for this paper is available at 
-\href{https://github.com/cportner/sexSelectionSpacing}{https://github.com/cportner/sexSelectionSpacing}
+Text and code for this paper are available at 
+\href{https://github.com/cportner/sexSelectionSpacing}{\texttt{https://github.com/cportner/sexSelectionSpacing}}.
 }
@@
 \begin{document}
-\graphicspath{{../figures/}}
+\graphicspath{{./figures/}}
 \DeclareGraphicsExtensions{.eps,.jpg,.pdf,.mps,.png}
@@
 
-% \setcounter{page}{0}
-
 \newpage
@@
 \doublespacing
-
-\begin{abstract}
-
-\noindent Following the arrival of prenatal sex-determination technologies in the mid-1980s, 
-India has experienced an increasingly male-biased sex ratio at birth, presumably from sex-selective 
-abortions. 
-Abortions lengthen birth intervals, but we know little about how birth spacing has changed or the 
-effects of these changes. 
-This paper shows that, although the length of birth intervals increased overall, well-educated women 
-with no sons had the most substantial lengthening---and the most male-biased sex ratios. 
-Furthermore, most of these changes took place immediately after the introduction of prenatal 
-sex-determination technologies. 
-Consequently, some women without sons now have longer birth intervals than those with sons, reversing 
-India's traditional spacing pattern. 
-Less-educated women continue short birth spacing when they have no sons, with only limited evidence 
-of male-biased sex ratios. 
-Because of the rapid lengthening of birth intervals, period fertility rates substantially overestimated 
-how fast cohort fertility fell. 
-Moreover, predicted cohort fertility is still 10\%--20\% above the period fertility rate. 
-If lengthening of birth intervals arise from repeated abortions, the associated short pregnancy spacing 
-may counteract any positive effects of longer birth spacing. 
-There is, however, no evidence of this effect on infant mortality. 
-Finally, judging from sex ratios, sex-selective abortion use is not declining.
-
-\noindent JEL: J1, O12, I1
-
-\noindent Keywords: India, prenatal sex determination, censoring, competing risk, 
-nonproportional hazard
-\end{abstract}
 
@@
 
-\section{Introduction\label{sec:intro}}
-
-% For word counting remove comment on the line below
-% \raggedright
-
-% Background
-India has experienced many positive changes over the past four decades:
-The economy has grown substantially,
-real wages have more than doubled,
-educational attainment has increased for males and females,
-and the total fertility rate has fallen to 2.2 children
-\citep{Bosworth2008,Dharmalingam2014,Klasen2015,
-International-Institute-for-Population-Sciences-IIPS2017}.
-
-However, India also witnessed the advent of sex selection---the selective abortion of 
-female fetuses based on prenatal sex determination---with the introduction of ultrasound 
-in the mid-1980s.
-Combined with a strong, continued preference for sons, the result was a dramatic increase 
-in the male--female ratio at birth
-\citep{das_gupta97,Arnold2002,retherford03b,Guilmoto2012,Portner2015b,Jayachandran2017}.
-
-% Questions addressed and why valuable
-The main question I address here is how birth spacing responded to these changes, 
-especially the spread of sex selection. 
-The motivation is twofold.
-First, past research has failed to appreciate that the use of sex-selective abortions could 
-substantially increase birth spacing. 
-As detailed below, after an abortion it takes 6 months or more to reach the same point in 
-the next pregnancy. 
-Second, other major societal changes, such as women's greater educational attainment, higher 
-household income, and a low and declining female labor force participation, all 
-likely influence birth spacing. 
-The combination of the apparent increasing use of sex selection and societal 
-changes can significantly impact birth spacing, but we know little about how much.
-
-Studying birth spacing contributes to our understanding of fertility decisions, but, equally 
-important, birth spacing also affects the reliability of our fertility measures and may 
-affect mortality. 
-Therefore, I address two additional questions.
-
-First, did changes in birth spacing lead us to overestimate the decline in cohort fertility?
-With longer spacing, mothers will be older at each parity, and this tempo effect 
-makes period fertility measures, such as the total fertility rate, downward-biased
-estimates of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
-Hence, a rapidly expanding use of sex selection could make the total fertility rate---our 
-most used fertility measure---fall substantially faster than cohort fertility.
-In this case, households' fertility may be higher than generally accepted.
-
-Second, what is the relationship between infant mortality and the changes in birth spacing
-and sex selection? 
-In India, birth intervals have traditionally been shorter with fewer sons, contributing to 
-girls' higher mortality risk
-\citep{Whitworth2002,Bhalotra2008,Maitra2008,Jayachandran2011,Jayachandran2017a}. 
-Therefore, longer birth spacing may reduce mortality through, for example, diminished 
-sibling competition \citep{Conde-Agudelo2012,Molitoris2019}. 
-However, if the spacing between births lengthens because of sex-selective abortions, the 
-spacing between pregnancies may still be very short. 
-Short pregnancy spacing may lead to worse child outcomes because of maternal nutritional 
-depletion and insufficient time to recover from the previous pregnancy. 
-Hence, children born after long birth intervals where multiple abortions have punctuated 
-those intervals may not see the same benefits as children born after a long interval that 
-is not punctuated by abortions.
-
-% How the study progresses
-To investigate how birth spacing has changed, I use a competing risk hazard model with 
-two exit states: The birth of a girl or the birth of a boy. 
-I apply the model to Hindu women's birth histories covering 1972--2016 using data from the 
-four National Family and Health Surveys (NFHS).
-
-The primary outcomes I examine are the 25th, 50th, and 75th percentile birth intervals 
-durations;
-the sex ratio at birth; and the likelihood of giving birth. 
-I estimate the model across four periods to capture the changing access and 
-legality of sex selection. 
-The key explanatory variables are maternal education, the sex of previous children, and 
-the area of residence.
-
-The empirical model allows me to predict cohort fertility. 
-To examine whether tempo effects bias our standard fertility measures, I compare 
-the predicted cohort fertility with fertility calculated from age-specific fertility 
-rates.
-
-I use the same data to study how infant mortality changed with birth spacing and 
-the increasing use of sex selection. 
-The key explanatory variables remain the same, except for the addition of birth spacing 
-and the sex of the index child.
-
-% Main results
-There are three main results.
-
-First, birth intervals lengthened over the four decades, with the lengthening longer, the
-higher the parity, the more educated the woman, and the higher the percentile of the
-birth interval duration.
-Well-educated women with no sons had the most substantial lengthening of birth intervals 
-and the most male-biased sex ratios, both likely arising from sex-selective abortions. 
-Consequently, some women with no sons now have \emph{longer} birth intervals than those 
-with sons, reversing India's traditional spacing pattern. 
-Less-educated women continued to have short spacing when they have girls, with only limited 
-evidence of male-biased sex ratios.
-The likelihood of a very short birth interval changed little across most groups.
-
-Second, the period fertility rate substantially overestimated how fast cohort fertility 
-fell in the 1990s and early 2000s as spacing initially increased. 
-Although the two have lately been converging, the predicted cohort fertility is still 
-10\%--20\% higher than the period fertility rate. 
-Furthermore, predicted cohort fertility is still at or above replacement level for all but 
-the best-educated urban women.
-
-Finally, infant mortality has declined substantially over time for all groups, but fastest 
-for the less educated, who are now close to the level of the best-educated women. 
-However, mortality is still inversely related to education level, especially for very short 
-birth intervals. 
-There is no evidence that repeated sex-selective abortions are associated with higher 
-mortality for the child eventually born.
-
-%------------------------------------------------------------------------------------
-
-\section{Conceptual Framework}
-
-This section provides a conceptual framework for understanding changes in birth spacing.
-I first introduce three potential explanations that link fertility and birth 
-spacing decisions: economic conditions, investment in children, and son preference 
-\citep{Casterline2016,Portner2018}.
-Next, I discuss why female education, area of residence, and sex composition are the
-principal factors in the empirical analyses and tie them to the three explanations.
-
-% Economic conditions
-The improvements in economic condition, especially the doubling of real wages,
-are likely to affect fertility, although the direction is ambiguous; empirically, 
-higher female wages reduce fertility, whereas higher male wages increase fertility 
-\citep{Hotz1997,schultz97}.
-According to economic theory, the substitution and income effects' relative strengths 
-determine the effect of higher wages on fertility.
-The substitute effect captures that when wages increase, time becomes more expensive, and
-people, therefore, work more and spend less time on non-wage earning activities, such as
-children or leisure.
-The income effect captures that higher wages increase the available income, which
-leads people to spend more time on time-intensive activities and less time working.
-Because women spend substantially more time on childrearing than men, the substitution
-effect dominates for women while the income effect dominates for men.
-
-Higher female wages may also shorten birth spacing if having children requires mothers to
-curtail their economic activities.
-Shortening birth spacing allows parents to take advantage of economies of scale in 
-childrearing---for example, looking after two children requires less than double the time 
-needed for one child \citep{Vijverberg1982,Hotz1997}.
-
-% Investment in children
-With increasing returns to education and lower offspring mortality, parents are likely to 
-reduce fertility and invest more in each child \citep{Rosenzweig1982a,Wolpin1997}.
-The higher return to education means a stronger incentive to invest in their children's
-education, thereby increasing the cost of having children and lowering fertility. 
-With lower expected mortality, parents need fewer births to reach the desired number of
-surviving children, which, in turn, allows parents to invest more in each child.
-
-An increased desire to invest in children may also lengthen birth spacing. 
-The clearest example of a positive effect of longer spacing is for health, as very short 
-spacing---approximately 24 months or less---leads to worse child health and mortality 
-outcomes \citep{Whitworth2002,Conde-Agudelo2012}.
-Whether longer spacing also improves human capital outcomes is more speculative with
-mixed evidence for developed countries and no evidence for developing countries
-\citep{Zajonc1976,Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
-
-% Son preference 
-Stronger son preference has traditionally been associated with shorter spacing and worse
-health outcomes for daughters when there no sons in the household
-\citep{Whitworth2002,Jayachandran2011}.
-Although son preference increases average fertility only marginally, differential stopping
-behavior means that girls tend to end up in larger families, resulting in fewer resources
-per child \citep{repetto72,clark00,Basu2010,Barcellos2014}.
-
-However, with the advent of sex selection, stronger son preference may lead to longer
-spacing because each sex-selective abortion adds 6–12 months to the length of the birth
-interval.
-After an abortion, the uterus needs at least two menstrual cycles---approximately 
-two months---to recover, or the subsequent risk of spontaneous abortion increases 
-substantially \citep{zhou00b}.
-Once conception can be attempted, the waiting time to conception is likely between
-one and six months. 
-Finally, sex-determination tests are reliable only from three months of gestation. 
-Hence, it takes at least six months before the couple is at the same point in the next 
-pregnancy as they were in the prior pregnancy when they decided to abort.
-
-% Factors/predictions
-The closest available proxies in the data for capturing the explanations linking
-fertility and birth spacing are the sex composition of previous children, mothers'
-education, and area of residence. 
-The remainder of the section discusses how the three variables fit into the
-explanations and the predicted effects.
-
-Sex composition proxies for son preference and the use of
-sex selection, both unobserved.%
-\footnote{
-The surveys ask about the ideal number of sons and 
-daughters, but these appear to be unreliable son 
-preference indicators; better-educated women simultaneously show 
-declining son preference and increasing sex selection 
-\citep{bhat03,pande07}.
-} 
-In the absence of sons, sex selection appears to increase 
-with lower desired fertility and higher parity
-\citep{Portner2015b,Jayachandran2017}. 
-Thus, for a given parity, birth intervals should lengthen 
-substantially over time for women with no sons, lower 
-desired fertility, and better access to sex selection.
-
-Both higher female education and urbanization are associated with 
-lower fertility and increased sex selection use, and, therefore, likely also changes in birth spacing
-\citep{das_gupta97,retherford03b,Portner2015b}.
-Furthermore, both variables are representative of
-the tremendous changes in India. 
-Figure \ref{fig:education_over_time} shows the substantial increase in female education,
-and the urban proportion of the population almost doubled from 18\% in 1960 to 35\% in 
-2019 \citep{United-Nations2019}.
-
-\begin{figure}[htpb]
+\begin{figure*}[htpb]
 \centering
-\subfloat[Rural]{
     \begin{minipage}{0.49\textwidth}
@@
     \end{minipage}
-} 
-\subfloat[Urban]{
     \begin{minipage}{0.49\textwidth}
@@
     \end{minipage}
-}
-\caption{Distribution of education by cohort for women 20 years or older
-using the four rounds of the NFHS}
-\label{fig:education_over_time}
-\end{figure}
-
-Urban women are likely to have lower fertility and higher use of sex selection than women 
-in rural areas.
-The lower fertility results from the higher cost of children and lower child mortality 
-risk in urban compared to rural areas.%
-\footnote{
-However, holding parental education constant, children in Indian slums have worse
-health outcomes than children in rural areas \citep{Portner2018a}.
-}
-The higher use of sex selection comes partly from the lower fertility and partly from
-higher income and better access to health care facilities in urban areas.
-
-Even though higher potential wages from more education should shorten birth spacing and
-lower fertility, the low and declining female labor force participation suggests little
-economic incentive to space children closer together.
-Even as women's education increased, their labor force participation stagnated or 
-decreased and is now one of the lowest outside the Middle East 
-\citep{Klasen2015,Fletcher2017,Afridi2018,Bhargava2018,Chatterjee2018}.
-
-The decline in female labor force participation appears to be driven by a combination
-of a relatively small expansion in the sectors where women work and the income effect 
-from rapidly increasing male wages and education dominating the substitution effect from 
-higher female wages \citep{Klasen2015,Bhargava2018}.
-The income effect can dominate because not only do men have a higher average level of 
-education than women, men are also paid more than women for a given level of education, 
-and the returns to education increases with education in India \citep{Agrawal2011}.
-Hence, increasing male education will result in a larger increase in income than a 
-similar increase in female education.
-
-However, higher female education might still be associated with lower fertility and more 
-sex selection, provided better-educated women are better at producing child human capital, 
-as suggested by \citet{Behrman1999}. 
-In a situation with increasing returns to male education, households may desire 
-better-educated women because of their ability to produce better-educated sons, 
-rather than because of their higher potential income. 
-The higher return to male education provides an additional incentive to invest in sons' 
-education---with a better-educated mother one such investment---and leads to lower desired 
-fertility, makes sex selection more likely, and possibly increases birth spacing.
-The implication is that the usual policy recommendation of increased female education may not
-change sex selection unless there is a concurrent increase in the relative return to female
-education in the labor market.
-
-% Sanskritization
-Finally, the process of "Sanskritization" implies that as lower-caste females gain access
-to education, they adopt higher-caste norms such as stronger son preference and a
-retraction from the formal labor market \citep{Srinivas1956}. 
-The declining female labor force participation suggests that this process still 
-operates \citep{Abraham2013,Chatterjee2018}.
-Thus, although the expansion in female education will likely bring in groups who initially 
-have different norms, we are unlikely to see substantial changes in how women with a given 
-education level behave.
-
-% Summary / hypotheses
-In summary, with substantial increases in husbands' income and a declining female labor 
-force participation, I expect longer birth spacing over time, independent of education 
-levels.
-Furthermore, birth spacing likely increases the most among the better educated as their
-household income increase the most, and because of their presumptive use of sex selection. 
-Finally, "Sanskritization" implies that the changing composition of better-educated
-women will not substantially change the use of sex selection.
-
-\section{Estimation Strategy\label{sec:strategy}}
-
-% Requirements for method and the intuition behind each:  
-%  - Account for censoring (hazard model)
-%  - Work both with and without sex selection (competing risk part)
-%  - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
-%  - Capture that the shape of the hazard function differ across groups
-%    (nonproportionality); needs a better description, maybe using example
-%    of shorter spacing and/or use of sex selection. Differences in parity
-%    progression likelihood.
-
-The empirical analysis has three parts. 
-First, I document the changes in birth spacing over time and how the introduction of sex 
-selection influenced birth spacing. 
-Second, I compare period fertility estimates with predicted cohort fertility based on the 
-model of birth spacing. 
-Finally, I examine how birth intervals affect infant mortality and whether the apparent 
-increase in sex selection influenced mortality. 
-This section presents the empirical model for my analysis of birth spacing.
-
-The standard approach in the birth spacing literature is to use proportional hazard
-models with a single exit---the birth of a child---but there are two problems with the 
-standard approach in this setting.%
-\footnote{
-See \citet{Sheps1970} and \citet{Newman1984} for early discussions of why 
-hazard models are the preferred way to deal with the censoring of birth
-intervals.
-}
-
-First and foremost, the use of sex selection means that the sex of the next child is 
-no longer random and that the spacing to the birth of a boy will differ from the 
-spacing to a girl. 
-Therefore, I use a competing risk setup that captures both the non-randomness of 
-the birth outcome and the differential spacing.%
-\footnote{
-\cite{Merli2000} used a discrete hazard model to examine whether 
-there was underreporting of births in rural China, although they 
-estimated separate waiting time regressions for boys and girls.
-}
-
-Second, even without sex selection, it is unlikely that characteristics, such as previous
-births' sex composition, have the same effects throughout the entire birth interval.
-The proportional hazard model requires that an individual's hazard is a 
-fixed proportion of the hazard for any other individual. 
-Nonconstant effects violate that assumption, and the results from a proportional hazard 
-model would, therefore, be biased. 
-The proportionality assumption is especially problematic for higher-order birth 
-intervals because there are substantial differences across groups in the likelihood 
-of progressing to the next birth and how soon couples want their next child if they 
-are going to have one \citep{Whitworth2002,Bhalotra2008}.
-
-The introduction of prenatal sex determination exacerbates any bias from
-the proportionality assumption for two reasons. 
-First, different groups have different levels of sex-selective abortion use and, thereby, 
-birth spacing. 
-Second, within a birth interval, a household's use of sex selection may vary, and that
-means that the effects of covariates vary as well.
-
-Therefore, I use a nonproportional hazard specification that allows the shape of the 
-hazard functions to vary across groups.
-Furthermore, the combination of a nonproportional specification and a flexible baseline
-hazard mitigates the potential effects of unobserved heterogeneity \citep{Dolton1995}.
-
-The model is a discrete-time, nonproportional, competing risk hazard model with two 
-exit states: Either a boy or a girl is born. 
-The unit of analysis is a spell---the period from one parity birth to the following 
-birth or censoring. 
-For estimation purposes, the spells begin nine months after the previous birth because 
-this is the earliest we should expect to observe a new birth. 
-Censoring can happen for three reasons: The survey takes place, sterilization of the 
-woman or her husband, or imposed because of too few births for the method to work.
-
-For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
-the spell continues until time $t_i$, when either birth or censoring of the spell 
-occurs.
-The time of censoring is assumed to be independent of the hazard rate,
-as is standard in the literature.
-The two exit states are the birth of a boy, $j=1$, or a girl, $j=2$.
-
-The discrete-time hazard rate $h_{ijt}$ is 
-\begin{equation}
- h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
- {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2.
- \label{eq:hazard}
-\end{equation}
-$D_{j}(t)$ is the piece-wise constant baseline hazard for outcome $j$, captured
-by dummies and the associated coefficients,
-\begin{equation}
-D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
-\end{equation}
-with $D_m = 1$ if $t=m$ and zero otherwise.
-This approach to modeling the baseline hazard is flexible and does not restrict the 
-baseline hazard unnecessarily.
-$\mathbf{Z}$ is the nonproportional part, which includes the interactions between 
-$D_j(t)$ and a set of explanatory variables and the interactions of those.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally.
-
-% To further minimize any potential bias from assuming proportionality, estimations 
-% are done separately for different levels of mothers' education and different periods.
-% I discuss the choice of which variables to use for nonproportionality below.
-
-Equation \ref{eq:hazard} is equivalent to the logistic hazard model and has the same 
-likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, splitting spells into smaller intervals---here equal to three months---and 
-treating them as observations, I can estimate the model using a standard multinomial 
-logit model. 
-% In the reorganized data, the outcome variable is 0 if the woman does not have a child 
-% in a given interval (the base outcome), 1 if she gives birth to a son in that interval, 
-% and 2 if she gives birth to a daughter in that interval.
-
-I use the model to predict birth interval lengths, parity progression probabilities, 
-and the sex ratio rather than present coefficients because the interpretation 
-of competing risk model coefficients is challenging \citep{thomas96}.
-The predicted parity progression probability is the likelihood of giving birth by the
-imposed censoring based on standard survival curve calculations averaged across all
-women in a given sample.
-
-For birth interval lengths, I estimate a set of percentile durations. 
-I first calculate for each woman when there is a given percentage chance that she will have 
-given birth, conditional on the probability of giving birth in the spell. 
-For example, with an 80\% parity progression probability, the median birth interval 
-is the predicted number of months before a woman passes the 60\% $(100-\frac{80}{2})$ 
-mark on her survival curve. 
-I then add nine months to account for the start of the spell. 
-The reported statistic is the average of a given percentile interval across all women in 
-a given sample using the individual progression probabilities as weights.
-
-% The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
-% parity progression probabilities as weights.
-% For an individual woman, the estimated percent of births that are boys at $t$, $\hat{Y_t}$, is:  
-% \begin{equation}
-% \hat{Y}_t 
-% = 
-% \frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-% { P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-% \times 100,
-% \label{eq:probability_son}
-% \end{equation}
-% where $b$ and $g$ are the predicted probabilities of having a boy and a girl, respectively,
-% conditional on the explanatory variables and not having had a child before $t$.
-% Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
-% $t$ gives the predicted percent of boys over the entire spell for an individual.%
-% \footnote{
-% Imagine $T=2$. 
-% If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
-% then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
-% }
-
-The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
-parity progression probabilities as weights.
-To find the individual sex ratio, I estimate the percentage of births that are boys at $t$, 
-conditional on not having had a child before $t$.
-Weighting the percent boys with the likelihood of exiting the spell with a birth across all 
-$t$ gives the predicted percentage of boys over the entire spell for an individual.%
-\footnote{
-Imagine $T=2$. 
-If 54\% and 66\% of births are boys and the likelihood of giving birth 20\% and 40\%, 
-then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$\% boys. 
-}
-
-\section{Data\label{sec:data}}
-
-The data come from the four rounds of the NFHS
-collected in 1992--1993, 1998--1999, 2005--2006, and 2015--2016.
-The surveys are large: 89,777, 90,303, 124,385, and 699,686 women, respectively. 
-NFHS-1 and NFHS-2 surveyed only ever-married women, while the two later surveys included 
-never-married.
-
-I first discuss sample restrictions and their motivations, then introduce the potential 
-issue of underreporting of female births and the imposed censoring of birth intervals.
-Next, I discuss how the analyses are split by periods to capture the introduction
-and changing legality in prenatal sex determination.
-Finally, I introduce the explanatory variables, split by whether they enter as
-proportional or nonproportional variables.
-
-I focus on the three spells starting from the first birth and ending with the 
-fourth birth.
-I exclude the interval from marriage to the first birth because many are imputed and the
-higher-order intervals because few women had five or more births, especially among the 
-better-educated.
-
-I restrict the sample to Hindus for two reasons.
-First, Hindus are the majority population group, about 80\% of India’s population.
-Second, the prior literature shows that son preference and sex selection vary 
-substantially between Hindus and the second largest group, Muslims. 
-Combining them and assuming that the baseline hazard is the same would lead to biased 
-results.
-Because of space constraints and the relatively small number of observations once split 
-by education and periods, I do not provide separate results for Muslims or any  
-remaining groups, such as Sikhs, Jains, and Christians.
-
-Finally, I exclude visitors and women in any of the following categories: Never married; 
-no gauna yet; married more than once; divorced; not living with husband; inconsistent age 
-at marriage; or education information missing.  
-The same goes for women who had at least one multiple births, reported giving birth 
-before age 12, had a birth before marriage, or had an interval between births of less than 
-nine months.
-
-In addition to the large number of women surveyed and the long period covered, a significant 
-benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
-spacing between births and probe for ``missed'' births.
-For India, the main concern is the underreporting of deceased children, especially a systematic 
-recall error where respondents' likelihood of reporting the birth of a deceased child depends 
-on the sex of that child.
-Unreported deceased children inflate the length of birth intervals and, with declining mortality, 
-make changes over time appear too small.
-In the online appendix, I provide a detailed analysis of systematic recall error, which 
-shows that recall error depends heavily on how long ago a woman was married. 
-I, consequently, drop women married 22 years or more.%
-\footnote{
-Recall error is likely behind the designation of the first two rounds of NFHS as ``moderate 
-quality'' in an analysis of the quality of birth histories in DHS surveys and its impact 
-on fertility estimates \citep{Schoumaker2014}.
-}
-
-To ensure that there are enough births for the method to work, I censor spells at 96 
-months (eight years) after a woman can first give birth, equivalent to 105 months 
-after the birth of the prior child.
-Less than 1\% of observed births occur after the cutoff.
-The final sample consists of 
-\input{../tables/num_women.tex}
-% [number] women, with [number] parity one through four births.
-
-% %
-% \footnote{
-% \input{../tables/num_missed.tex}
-% }
-
-Direct information on sex selection is not available, so I compare periods 
-based on the changes in access and legality of prenatal sex determination in India.
-Abortion has been legal in India since 1971.
-Reports of sex determination appeared around 1982--1983, and the number of clinics 
-quickly increased \citep{Sudha1999,bhat06,Grover2006}.
-In 1994, the Prenatal Diagnostic Techniques Act made determining and communicating 
-the sex of a fetus illegal.%
-\footnote{
-% Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
-There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2019}.
-}
-Finally, although sex selection increased even after 1994, we may have passed a 
-turning point in its use in the mid-2000s \citep{Das_Gupta2009,Kumar2012,Bongaarts2013,Diamond-Smith2015}.
-
-I use four periods: 1972--1984, 1985--1994, 1995--2004, and 2005--2016.
-The first covers the period before sex selection became available and the second from when sex 
-selection became available until the Prenatal Diagnostic Techniques Act.
-I have split the period from 1995 until 2016 into two to examine if there was support for 
-the prior literature's hypothesized reversal in child sex ratios and son 
-preference in India.
-
-The allocation of spells into periods is determined by when conception, and, therefore, 
-decisions on sex selection can begin. 
-Hence, some spells cover two periods, which may bias downward the differences between the 
-periods.
-Most sterilizations take place soon after giving birth. 
-These spells, therefore, do not show up in the samples used. 
-Furthermore, sterilization depends strongly on prior children's sex composition; the 
-fewer boys, the lower the probability of sterilization. 
-The effect is to bias downward the differences in parity progression probabilities.
-
-I divide the explanatory variables into two groups, nonproportional and proportional. 
-The first group consists of characteristics shown in the prior literature to affect the 
-spacing choice and the use of sex selection: Mother’s education, sex composition of 
-previous children, and area of residence.
-To minimize any potential bias from including proportional variables, I estimate separate 
-models for each birth interval, education group, and period combination, rather than 
-including education as a variable.
-
-I divide education levels into four groups: No education, 1--7 years, 8--11 years, and 
-12 and more years.
-The latter two correspond to having completed primary and secondary school, 
-respectively.%
-\footnote{
-Although there are variations by state, elementary education in India consists of a 
-primary school covering grades one through five and an upper primary---or middle 
-school---covering grades six through eight. 
-Similarly, secondary education covers grades nine and tenth for ``secondary education'' 
-and 11 and 12 for ``upper secondary.''
-}
-To ensure that the results are comparable with the prior literature on fertility
-and mortality in India, I follow the NFHS reports, except that I combine the 
-less than five years and 5--7 years of schooling completed and the 8--9 
-and 10--11 years of schooling completed to ensure sufficient cell sizes.
-
-I capture sex composition with dummy variables for the possible combinations, ignoring 
-the ordering of births.%
-\footnote{
-With sex selection, the composition of prior children is, in principle, endogenous. 
-It is beyond the scope of this paper to develop a method for dealing with this issue. 
-}
-Area of residence is a dummy variable for living in an urban area.
-
-The second group of variables consists of those expected to have an approximately 
-proportional effect on the hazard.
-These include the mother's age when the spell begins, the household's
-land ownership, and whether it belongs to a scheduled tribe or caste.
-Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present the descriptive 
-statistics.
-
-\section{How Birth Spacing Changed\label{sec:results}}
-
-% Explain question and what I am doing
-The first question I address is how birth spacing responded to the significant 
-changes in India.
-I begin with a broad outline of how parity progression probabilities and
-sex ratios have changed over time and by groups.
-I then use these results to separately discuss the changes in birth spacing for 
-women who do not appear to use sex selection and for those who do.
-
-Figures \ref{fig:spacing_low_rural} through \ref{fig:spacing_highest_urban}
-show the 25th, 50th, and 75th percentile birth interval durations in 
-months, the sex ratio, and the probability of having a birth for each spell
-by education levels and area of residence.%
-\footnote{
-Results for urban women without education, rural women with 12 or more years of 
-education, and the fourth spell for women with 12 or more years of education are
-in the online appendix because of relatively small samples.
-}
-The sex ratio graphs also show the natural sex ratio, approximately 51.2\% boys
-\citep{jacobsen99,Portner2015b}.
-The underlying values with bootstrapped standard errors and tests for statistically
-significant differences across sex compositions are available in the online appendix.
+% \caption{Distribution of education by cohort for women 20 years or older
+% using the four rounds of the NFHS}
+% \label{fig:education_over_time}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_rural}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for rural women with no education by spell, sex composition, and period}
-\label{fig:spacing_low_rural}
-\end{figure}
+% \caption{Percentile birth interval durations, sex ratios, and parity progression  
+% for rural women with no education by spell, sex composition, and period}
+% \label{fig:spacing_low_rural}
+\end{figure*}
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
-% \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for urban women with no education by spell, sex composition, and period}
-% \label{fig:spacing_low_urban}
-% \end{figure}
-
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_rural}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for rural women with 1--7 years of education by spell, sex composition, and period}
-\label{fig:spacing_med_rural}
-\end{figure}
+% \caption{Percentile birth interval durations, sex ratios, and parity progression  
+% for rural women with 1--7 years of education by spell, sex composition, and period}
+% \label{fig:spacing_med_rural}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_med_urban}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for urban women with 1--7 years of education by spell, sex composition, and period}
-\label{fig:spacing_med_urban}
-\end{figure}
+% \caption{Percentile birth interval durations, sex ratios, and parity progression  
+% for urban women with 1--7 years of education by spell, sex composition, and period}
+% \label{fig:spacing_med_urban}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_rural}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for rural women with 8--11 years of education by spell, sex composition, and period}
-\label{fig:spacing_high_rural}
-\end{figure}
+% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_rural}
+% \caption{Percentile birth interval durations, sex ratios, and parity progression  
+% for rural women with 8--11 years of education by spell, sex composition, and period}
+% \label{fig:spacing_high_rural}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_high_urban}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for urban women with 8--11 years of education by spell, sex composition, and period}
-\label{fig:spacing_high_urban}
-\end{figure}
+% \caption{Percentile birth interval durations, sex ratios, and parity progression  
+% for urban women with 8--11 years of education by spell, sex composition, and period}
+% \label{fig:spacing_high_urban}
+\end{figure*}
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
-% \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for rural women with 12 or more years of education by spell, sex composition, and period}
-% \label{fig:spacing_highest_rural}
-% \end{figure}
-
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_urban}
-\caption{Percentile birth interval durations, sex ratios, and parity progression  
-for urban women with 12 or more years of education by spell, sex composition, and period}
-\label{fig:spacing_highest_urban}
-\end{figure}
+% \caption{Percentile birth interval durations, sex ratios, and parity progression  
+% for urban women with 12 or more years of education by spell, sex composition, and period}
+% \label{fig:spacing_highest_urban}
+\end{figure*}
 
-% [Parity progression probability]
-The parity progression and the sex ratio show two broad trends.
-First, 
-in line with the falling total fertility rate, the likelihood of a next birth 
-has decreased over time.
-The likelihood of a next birth fell more rapidly, the higher the education and the 
-higher the parity.
-Within a given spell and period, parity progressions are lower in urban than rural areas, 
-if at least one son is present, and the more educated the mother.
-
-% [Sex ratios]
-Second, sex ratios have become more male-dominated for women with no sons, indicating the spread 
-of sex selection. 
-The percentage of boys increased more quickly, the higher the education and the higher the parity. 
-There are no clear trends for the other sex compositions. 
-Within a given spell and period combination and in the absence of a son, sex ratios are higher, 
-the more educated the mother, and the higher the parity. Sex ratios are also higher in urban than 
-in rural areas.
-Some women with one son also show an unnaturally high percentage of boys, although the 
-failing fertility makes these estimates noisy.
-
-\subsection{When Sex Selection Is Less Used}
-
-To separate the effects of the introduction of sex selection and the other changes in
-India, I first discuss how the lengths of birth intervals have changed in situations where, 
-based on sex ratios, there appears to be less sex selection.
-The group broadly covers women with no education, regardless of their children's sex 
-composition, and women with any education who have one or two sons already.
-
-Despite the apparent lower level of sex selection, son preference is still evident with 
-the shortest spacing when they have only girls. 
-Notably, for those who appear the least likely to use sex selection---rural women with no
-education---birth spacing is almost uniformly statistically significantly longer when at
-least one son is present than if no son is present. 
-Furthermore, the difference in birth interval length across sex compositions has grown over
-time as spacing when sons are present has become longer.
-
-% [25th percentile birth intervals]
-A remarkably high proportion of birth intervals are still very short.
-For all but the most educated, 25\% or more have their second and third child 
-within 24 months of the previous birth.
-These intervals are substantially below the 24 months between 
-\emph{pregnancies} the WHO recommends.
-Even with the more substantial lengthening of birth intervals for higher parities, the 25th
-percentile duration is still around 24 months for the fourth spell for women with less than
-eight years of education.
-
-% [median birth intervals]
-Median birth interval lengths have also increased relatively little---only three to six months 
-over the four decades---compared to around 3.5 months \emph{per decade} in other countries with 
-declining fertility \citep{Rutstein2011,Casterline2016}.%
-\footnote{
-The NFHS reports show median durations of closed birth intervals of approximately 31 months, 
-which have barely moved over time, underscoring the importance of accounting for censoring 
-when examining birth spacing.
-}
-The result is that most of the median birth interval durations are still at 36 months or
-below, with the shortest only 29 months.
-
-Birth intervals appeared to lengthen the most for women who are the least likely to work.
-For example, from lowest to highest education, the average duration of third-spell birth 
-intervals for urban women with one boy and one girl increased by 2.7, 3.4, 5.8, and 1.8 
-months over the four decades.%
-\footnote{
-For women with two sons, the numbers were 4.3, 6.3, 7.0, and 3.0.
-See the online appendix tables for the average birth interval durations.
-}
-Hence, women with the lowest labor force participation---those with 8--11 years 
-of education---also saw the largest increases in average spacing, possibly driven by the 
-substantial improvement in household income for this group from economic growth.
-
-% [75th percentile birth intervals]
-The most substantial changes occurred in the 75th percentile birth interval durations, 
-where the more the parity progression probabilities declined, the more the birth interval 
-lengthened. 
-For example, the probability of a fourth birth for urban women with 8--11 years 
-of education and two sons and one girl has declined by almost 40 percentage points as the 
-75th percentile birth interval length increased by 22 months.
-Compare this with rural women of no education with a boy as their first child, for whom the 
-probability of a third birth declined by fewer than six percentage points while the birth 
-interval increased by only slightly more than two months.
-
-%0.637 0.241
-
-These results are in line with prior research showing that falling fertility is associated 
-with a lengthening of particularly the longer birth intervals, although why is still an 
-unresolved question \citep{Casterline2016}.
-The most educated women who already have a son is an exception to this trend; the 
-probability of a third birth declined rapidly, but the birth interval lengths changed little. 
-These women both have better access to modern contraceptives and are better at using 
-traditional contraceptive methods \citep{Rosenzweig1989}. 
-Hence, it is possible that the lengthening of birth intervals with falling fertility in 
-the prior research arises because unintended births become a relatively larger proportion 
-of the total number of births for a given parity and those can occur at any time.
-
-% [Birth intervals with sex selection]
-\subsection{Sex Selection and Birth Spacing}
-
-A clear illustration of how the combination of son preference and the introduction of 
-sex selection affected birth spacing comes from the third spell of the best-educated urban 
-women.
-With two girls, almost 80\% of the third births are boys, and the 75th percentile 
-birth interval length is close to 70 months, an increase of almost 21 months over the four
-decades. 
-This interval has gone from being statistically significantly shorter than the intervals 
-with at least one son to now being a statistically significant 13 months longer.
-
-Even more striking, most of the change took place right at the introduction of sex 
-selection.
-The 75th percentile birth interval with two girls increased from 48 months to 
-64 months in a decade, while the other sex compositions showed a slight decrease from 
-around 55 months to 54 months.
-These birth spacing changes may even understate the impact because this particular group
-appears to have had access to sex selection even before it became widespread, as shown by
-the unequal sex ratio for the 1972--1984 period for women with two girls.
-
-The 75th percentile changes are the most dramatic, but the apparent use of sex selection 
-also affects the 25th and median birth interval lengths. 
-For the best-educated urban women with two girls, the 25th percentile birth interval
-length increased by six months, or 23\%, while the median percentile birth interval length
-increased by 15 months (43\%).
-
-Not surprisingly, given these changes, the third spell for the best-educated women shows
-the clearest reversal in the spacing pattern; the birth intervals with two girls are
-consistently statistically significantly longer than the intervals with one or two boys, 
-no matter the percentile used.
-A similar reversal, although more muted, occurred for the third spell for urban women 
-with 1--7 years of education and both urban and rural women with 8--11 years of 
-education.
-
-Did the predictions of declining use of sex selection come true? 
-There is no clear evidence for or against a reversal in the use of sex selection, with 
-some cases showing increases in sex ratios between the last two periods, others little 
-change, and some a decline. 
-The best-educated women are again a good illustration. 
-The sex ratio for women with two girls continued to increase over the last two periods, 
-but the likelihood of a third birth declined. 
-Furthermore, if the first child was a girl, the sex ratio for the second birth dropped 
-slightly, as did the probability of having a second birth. 
-However, there are also cases where there is no abatement in the increasing use of sex 
-selection. 
-For example, for rural women with 1--7 years of education, the sex ratios in the absence 
-of daughters continued to increase while the likelihood of an additional birth remained 
-high.
-
-In summary, over the four decades, birth intervals lengthened with improving economic 
-conditions and falling fertility. 
-These increases are larger with higher parity and higher percentile measure. 
-Furthermore, when there is little evidence of sex selection use, it appears that the women 
-least likely to work are also those with the most substantial increases in birth interval 
-lengths.
-
-However, sex selection appears to be behind the most substantial increases in birth spacing. 
-The best-educated women with two girls had the most biased sex ratio and the most 
-significant increase in birth interval lengths. 
-Over the four decades, the median birth interval length for this group increased by almost
-15 months. 
-Even more striking, the 75th percentile birth interval length increased by a staggering 21
-months, most of that within a decade of the introduction of sex selection.
-
-\section{What Happened to Fertility?\label{sec:fertility}}
-
-The tempo effect from longer birth intervals means that the total fertility rate may 
-underestimate cohort fertility. 
-The next question I address is, therefore, to what extent did the changes bias the 
-fertility estimates for India? 
-To this end, I compare fertility based on a variation of the total fertility rate with 
-predicted cohort fertility from the hazard model.
-Table \ref{tab:fertility} shows the two fertility measures by area of residence and education.
-
-\input{../tables/fertility.tex}
-
-The fertility rate follows the same procedure as in the Demographic and Health Survey 
-reports: I use the births from 36 to 1 month before the survey month to calculate 
-age-specific fertility rates for five-year age groups and then sum the age-specific 
-fertility rates multiplied by five  \citep{Croft2018}.
-However, because the hazard model predictions only use births up to parity four, I use the 
-same set of births for the fertility rate and label it the ``four-parity'' fertility rate. 
-Hence, the presented fertility rates are not directly comparable to those in the NFHS reports.
-
-%
-% \footnote{
-% See \citet{Croft2018} for more detail.
-% Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
-% is based on the household rosters, assuming that never-married women have had no children.
-% Because of the low number of births to women aged 45 to 49 this age group was not
-% used for the hazard model estimations and, therefore, is also excluded for the fertility
-% rate.
-% The marital total fertility rate lead to unrealistically high numbers and is, therefore,
-% not presented \citep{Hoem2011,Laplante2015}.
-% }
-
-Because NFHS-1 was after the introduction of sex selection, I cannot calculate a fertility 
-rate in precisely the same manner for a period before sex selection was widely available.
-Instead, I calculate the fertility rates for women between 15 and 39 years of age five years 
-before the survey month, again using the number of births three years before.
-This rate is shown as ``1987--1988'' in the table.
-Given the relatively low number of births to women 40--45 years of age, this approach 
-provides the best estimate of the fertility rate when sex selection still was not 
-widespread.
-
-To predict cohort fertility based on the hazard models, I estimate the parity progression 
-probability for each spell. 
-Because parity progression depends on the sex composition of prior children, I estimate the 
-probability for each sex composition and weigh the probabilities with the likelihood of 
-the sex compositions.
-The survey rounds do not coincide directly with the periods used for the hazard model.
-Therefore, I compare the model results for 1972--1984, 1985--1994, 1995--2004,
-and 2005--2016 with rounds 1 through 4 of the NFHS, respectively.
-
-I include the spell from marriage to first birth, despite the problems capturing the exact 
-timing of marriages because the estimated progression probabilities should not be affected 
-by this problem. 
-I begin with the age of marriage for each woman and predict the likelihood of progressing 
-to each parity, assuming three-years increases in age between births. 
-Shorter assumed increases in age lead to slightly higher predicted fertility.
-
-Sterilizations are not incorporated into the hazard model because most occur
-immediately after giving birth. 
-To compensate, I estimate the probability of sterilization using a Logit model and use 
-that to scale down the parity progression probability when predicting cohort fertility.
-
-The predicted cohort fertility based on the hazard model is higher than the four-parity 
-fertility rate in almost all cases. 
-Only women with no education in the first period show little difference between the two 
-fertility measures, a situation where fertility is high, spacing very short, and likely 
-unchanged for an extended period.
-
-Consistent with a more substantial bias in the period fertility rate when the age of marriage 
-and the length of birth intervals increase, the absolute bias is least in the first 
-and the last period and highest in the middle two periods.
-Hence, the fertility rate declined too fast from the mid-1980s to the century's end.
-Only recently, as the rate of increase for the birth interval lengths has slowed, have the 
-two fertility measures begun to converge again.
-Even with the convergence, the predicted 2005--2016 cohort fertility is still above the 
-1992--1993 fertility rate for every group, except urban women with no education. 
-Furthermore, for the last period, the predicted cohort fertility remains at least 
-10\%--20\% higher than the fertility rate.
-
-Another indication of how tempo effects bias the fertility rate bias is that the
-fertility rate \emph{increases} for some groups.
-For example, for urban women with 8--11 years of education, the fertility
-rates were 1.84, 1.81, and 1.87 over the last three surveys.
-This pattern likely arises from the stabilization of the age of first birth and the 
-spacing between births.
-
-Finally, even with the declines in the predicted cohort fertility, it is still mostly 
-above replacement.
-Only for urban women with 12 or more years of education is the predicted cohort
-fertility clearly below 2.1 children.
-Even then, cohort fertility is still more than 0.3 children higher than 
-the fertility rate estimate of 1.5.
-Furthermore, the predicted cohort fertility numbers are likely too low because I use only
-the first four births and births before the imposed 105-month censoring of birth interval
-durations.
-
-\section{Mortality and the Changing Birth Spacing\label{sec:mortality}}
-
-The final question I address is whether there is an association between infant mortality 
-and increases in birth spacing associated with the introduction of sex selection. 
-Starting with the sample used for estimating birth spacing, I select children born more 
-than 12 months before the survey month. 
-I restrict the analyses to parities two and three because of the small number of births 
-and deaths at parity four. 
-Furthermore, I do not show the results for women with 12 or more years of education 
-for the 1972--1984 period because of the small number of women.
-
-The dependent variable is whether the child died within the first 12 months of life.
-The main set of explanatory variables consists of dummies for the spacing from
-the prior birth.
-The birth interval duration dummies cover 12-month periods, starting nine months after the 
-prior birth, until the 57-month dummy, which covers until 105 months after the prior birth.
-I use dummies for the sex of the index child and the sex composition 
-of the prior children.
-The birth spacing dummies, the sex of the index child, and the sex composition dummies
-are all interacted.
-Because the actual number of abortions is unobserved, the interactions between
-the sex composition of prior children and the sex of the index child serve
-as proxies for the use of sex selection.
-The other explanatory variables are the same as above, and estimations
-are done separately by education level and parity.
-
-I estimate the probability of infant mortality using a Logit model.
-Figures \ref{fig:mortality_low_med} and \ref{fig:mortality_high_highest} show 
-the predicted probability of the second child dying within the first year at the 
-possible combinations of index child sex, sex composition of prior children, and 
-birth spacing, with all other variables at their average values.%
-\footnote{
-The online appendix shows the corresponding graphs for the third child.
-}
-The graphs do not show confidence intervals to improve legibility.
-
-An important caveat is that the estimations do not address potential selection problems.
-For example, suppose women who have diﬀiculties conceiving or carrying a pregnancy to 
-term also have a higher mortality risk for their offspring. 
-In that case, a spurious correlation between long birth spacing and mortality may arise 
-\citep{Kozuki2013}. 
-Unfortunately, methods to address selection, such as family fixed effects, do not work 
-well when the number of births is as low as it is here for better-educated women 
-\citep{Kozuki2013,Molitoris2019}.
-However, the fixed effects and linear probability results did not 
-deviate substantially in prior research.
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \setcounter{subfigure}{-1}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[No Eduction]{\includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{-0} 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[One to Seven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Second Child's Infant Mortality 
-% for Women with No Education
-% and Women with One to Seven Years of Education}
-% \label{fig:mortality_low_med}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \setcounter{subfigure}{-1}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Eight to Eleven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \begin{minipage}[t]{0.39\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Second Child's Infant Mortality 
-% for Women with Eight to Eleven of Education
-% and Women with Twelve or More Years of Education}
-% \label{fig:mortality_high_highest}
-% \end{figure}
-
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_low_med}
-\caption{Infant mortality by preceding birth interval length across periods for second child of women with 
-no education and women with 1--7 years of education}
-\label{fig:mortality_low_med}
-\end{figure}
+% \caption{Infant mortality by preceding birth interval length across periods for second child of women with 
+% no education and women with 1--7 years of education}
+% \label{fig:mortality_low_med}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_2_high_highest}
-\caption{Infant mortality by preceding birth interval length across periods for second child of women with 
-8--11 and 12 and above years of education}
-\label{fig:mortality_high_highest}
-\end{figure}
-
-There has been substantial convergence in mortality risk across groups over time.
-For intervals 21 months or longer, there is now little difference across 
-the education groups, with even the no-education group showing an infant mortality risk 
-below 5\%.
-
-Very short birth intervals still exhibit a higher mortality risk, although the 
-effect declines with education level.
-The mortality risk is 3\%--4\% for the best-educated women, whereas women with no 
-education still show a risk that is close to 10\%.
-
-Despite the prior findings of differential mortality by sex, there is little evidence 
-that girls have substantially higher mortality risk.
-There is some weak evidence that a boy born after a girl has a lower mortality
-risk in the earliest periods.
-However, this difference disappears with the general decline in mortality risk.
-
-Despite the concern that multiple abortions might increase mortality risk by shortening 
-the interval between pregnancies, there is no evidence for this effect. 
-Suppose repeated sex-selective abortions lead to a higher mortality risk for the child
-eventually born. 
-In that case, boys born after a girl---the solid lines---should have an increased risk 
-with longer spacing for the two highest education groups in the last two periods.
-However, there are no apparent consistent differences between these groups and the other 
-potential combinations. 
-The same holds for the third spell.
-
-% line 3661 in an_infant_mortality.log
-The raw numbers for women with the most uneven sex ratio also suggest that even with a 
-very high apparent use of sex selection, there is no impact on mortality. 
-A total of 1,004 women with 12 or more years of education and no boys at the start of 
-the third spell in the last period had a third child, of which 685 were boys. 
-Of these 685 boys, only six died within the first year of life. 
-Half of those who died were born in the 9--32-month interval, and none died in the 
-57-month+ interval.
-
-\section{Conclusion\label{sec:conclusion}}
-
-% Background
-Over the past four decades, India saw a dramatic increase in the male-to-female
-sex ratio at birth as access to sex selection spread and son preference remained high. 
-Simultaneously, economic growth was strong, schooling increased, and the total fertility 
-rate declined to almost replacement level.
-
-% Questions
-The main question I address in this paper is how birth spacing responded to the 
-significant changes in India between 1972 and 2016, particularly the spread of sex 
-selection.
-I also examine two related questions.
-First, did changes in birth spacing make us overestimate the decline in cohort fertility?
-Second, what is the relationship between infant mortality and the changes in birth spacing 
-and sex selection?
-
-% What has happened to spacing and why
-The most substantial lengthening of birth intervals occurred among the best-educated women,
-likely because of substantial use of sex selection combined with falling fertility.
-Take, for example, women with 12 or more years of education who had two girls. 
-As the sex ratio reached almost 80\% boys, the expected median birth interval length
-increased by almost 15 months, and the 75th percentile interval length increased by 21 months.
-Most of the lengthening in the long intervals came immediately after the introduction of sex 
-selection in India.
-
-For some groups, the lengthening in birth intervals was so substantial that it led to a
-reversal of the traditional spacing pattern: In the absence of sons, these groups now show
-statistically significant longer, rather than statistically significant shorter, birth
-intervals than if there is at least one son.
-
-The women who are the least likely to use sex selection, as indicated by their sex ratios
-at birth, still show the traditional spacing pattern with short spacing in the absence of
-sons.
-
-Son preference continues to show in fertility decisions. 
-Fertility has declined for all groups, but the likelihood of having an additional child
-still depends strongly on the number of sons, with women with no sons having the highest 
-parity progression probabilities.
-
-Birth intervals also lengthened in cases when sex selection appears to be less used.
-However, compared to other countries with similar declines in fertility, the median 
-spacing increases were smaller at three to six months over the period. 
-Most of the median intervals when sex ratios are close to normal are still short at 36 
-months or below. 
-Furthermore, many women still have very short birth intervals.
-More than 25\% of women have their next child within 24 months of the previous birth in 
-many cases.
-
-% [predictions of declining sex selection] 
-Despite predictions that the use of sex selection would decline, there is no clear 
-evidence of this. 
-The most likely users of sex selection continue to show substantial male-biased sex ratios, 
-although there may be some leveling off.
-More concerning, the increasingly male-biased sex ratios among less-educated women suggest
-that sex selection use appears to be spreading as fertility falls.
-
-% fertility bias
-
-The increases in spacing make the total fertility rate a more biased measure of cohort 
-fertility. 
-This bias was most prominent early in the spread of access to sex selection when the 
-fertility rate was up to one child lower than the predicted cohort fertility. 
-However, it is still present, with the predicted cohort fertility 10\%--20\% 
-higher than the fertility rate. 
-At 1.8 children, the best-educated urban women are the only group for whom the predicted 
-cohort fertility is below replacement.
-
-Tempo effects are studied extensively in the literature \citep[see, for example, ][]{Bongaarts1999}.
-Still, there are, to my knowledge, no other cases where there has been as 
-substantial an increase in birth interval lengths and associated bias in fertility rates 
-as for India.
-It is conceivable that we might see increases in the total fertility rate as birth spacing 
-stabilizes or even shortens again if interventions against sex selection are successful.
-
-% Mortality
-There has been a substantial reduction in infant mortality over time, and the size of the 
-reductions is inversely related to the mother's education.
-Hence, there is now little difference in mortality risk across education groups if the 
-birth took place more than 21 months after the previous birth.
-Short birth spacing is still associated with higher mortality, although the effect is 
-small for the best-educated women.
-There is no evidence that repeated abortions are associated with higher infant mortality
-for the child eventually born; boys born after long birth intervals to families with
-well-educated mothers, only daughters, and high predicted sex ratios---the combination of
-which suggests repeated sex-selective abortions---have no higher infant mortality than other
-children.
-
-% Implications 
-The results here paint a less rosy picture of India's prospects for a continued reduction 
-in population growth than generally accepted. 
-With predicted cohort fertility still substantially higher than the period fertility rate, 
-India's total fertility rate will likely stabilize or even increase as birth intervals slow 
-their lengthening. 
-The more successful the attempts at combatting sex selection are, the more likely an 
-increase in the total fertility rate will be. 
-Furthermore, the rapid decline in infant mortality risk, combined with likely future 
-declines as the proportion of very short birth intervals falls, may also slow the 
-reduction in population growth.
-
-% Future research and policy
-
-There are two crucial questions that future research should address.
-
-First, what is behind the improvements in girls' health status?
-Access to sex selection means that girls-only families are less likely to have
-very short birth intervals, which may reduce sibling competition. 
-Hence, better health outcomes for girls with sex selection is available could be an 
-unintended side-effect, rather than the result of girls becoming more valued as is often 
-assumed \citep{Hu2015}. 
-Comparing prior children's outcomes across sex composition and the sex of the next child 
-could be a way to understand why girls' health outcomes improve in the presence of sex 
-selection.
-
-Second, what is the relationship between female labor force participation and sex selection? 
-Women may be staying out of the labor market precisely because sex selection makes 
-them more likely to have a boy and increases the expected birth spacing. 
-Better job opportunities for women could reduce sex selection use for two reasons. 
-First, it becomes more expensive to be out of the labor market for long periods. 
-Second, the differential in potential earnings between husband and wife would decline, 
-making it relatively more attractive to invest in daughters' human capital.  
-This approach could, however, be a double-edged sword. 
-If better job opportunities further lower fertility, the use of sex selection may increase, 
-everything else being equal.
-Understanding the trade-off between long-term benefits from improvements in women's labor 
-force participation and short-term costs from potential increases in sex selection is of 
-paramount importance.
-
-% The higher return to male offspring's human capital combined with access to sex
-% selection may also explain another puzzle, why is the labor force participation so
-% low when fertility is low and education has increased.
-% As shown here, part of the answer may be that the number of children is, in fact, not as 
-% low as previously thought, both because of the increased spacing and that more 
-% children survive.
+% \caption{Infant mortality by preceding birth interval length across periods for second child of women with 
+% 8--11 and 12 and above years of education}
+% \label{fig:mortality_high_highest}
+\end{figure*}
 
@@
 \bibliographystyle{aer}
-\bibliography{sex_selection_spacing}
+\bibliography{sex_selection_spacing-final}
 
@@
 
-\clearpage
-\newpage
-
-\appendix
-
-% CHANGING NUMBERING OF FIGURES AND TABLES FOR APPENDIX
-\renewcommand\thefigure{\thesection.\arabic{figure}}    
-\renewcommand\thetable{\thesection.\arabic{table}}
-
-\section*{Appendices for Online Publication}
-
-These appendices are intended for online publication.
-They provide the descriptive statistics, additional
-estimated duration tables, and graphs for all 
-education groups and spells.
-
-\clearpage
-\newpage
-
-\section{Characteristics of Women's Work Experiences}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-Figure \ref{fig:work_by_survey} shows the percent of married women who are 
-currently working at the time of the survey by age group and education level.
-No other labor force participation question is consistently available across all 
-four surveys. 
-Because the question refers to currently working, the percentages are lower in previous
-studies.
-
-\captionsetup[figure]{skip = 10pt}
-
-\begin{figure}[!htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{40 Years or Older}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_40}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_40} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{30--39 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_30}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_30} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{20--29 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_rural_20}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{currently_working_urban_20} 
-    \end{minipage}
-}
-\caption{Percentage of married women who were working at the time of the 
-survey by age group and area of residence}
-\label{fig:work_by_survey}
-\end{figure}
-
-\begin{figure}[!htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{40 Years or Older}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_cash_rural_40}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_cash_urban_40} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{30--39 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_cash_rural_30}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_cash_urban_30} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{20--29 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_cash_rural_20}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_cash_urban_20} 
-    \end{minipage}
-}
-\caption{Percentage of women paid cash or cash and in-kind of those women who were 
-working at the time of the survey by age group and area of residence}
-\label{fig:work_cash_by_survey}
-\end{figure}
-
-\begin{figure}[!htpb]
-\centering
-\rotatebox[origin=c]{90}{\small{40 Years or Older}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_family_rural_40}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_family_urban_40} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{30--39 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_family_rural_30}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_family_urban_30} 
-    \end{minipage}
-}
-\\
-\rotatebox[origin=c]{90}{\small{20--29 Years Old}}
-\subfloat[Rural]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_family_rural_20}
-    \end{minipage}
-} 
-\subfloat[Urban]{
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[width=\textwidth]{work_family_urban_20} 
-    \end{minipage}
-}
-\caption{Percentage women who worked for a family member of those 
-working at the time of the survey, by age group and area of residence}
-\label{fig:work_family_by_survey}
-\end{figure}
-
-\clearpage
-\newpage
-
-\section{Empirical Model Details}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% [More formal version of empirical strategy section]
-
-The model is a discrete time, nonproportional, competing risk hazard model with two exit 
-states: Either a boy or a girl is born.
-The unit of analysis is a spell, the period from nine months after one birth to the next.
-For each woman, $i=1,\ldots,n$, the starting point for a spell is time $t=1$, and 
-the spell continues until time $t_i$, when either a birth occurs or the spell 
-is censored.%
-\footnote{
-The time of censoring is assumed independent of the hazard rate,
-as is standard in the literature.
-}
-There are two exit states: The birth of a boy, $j=1$, or the birth of a girl, $j=2$, and 
-$J_i$ is a random variable indicating which event took place.
-The discrete time hazard rate $h_{ijt}$ is 
-\begin{equation}
- h_{ijt} = \frac{\exp(D_j(t) + \alpha_{jt}'\mathbf{Z}_{it} + \beta_j'\mathbf{X}_{i})} 
- {1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{it} + \beta_l'\mathbf{X}_{i})} \: \: \; \; \;  j = 1,2
- \label{eq:hazard_appendix}
-\end{equation}
-where the explanatory variable vectors, $\mathbf{Z}_{it}$ and $\mathbf{X}_{i}$, capture 
-individual, household, and community characteristics,
-and $D_{j}(t)$ is the piece-wise linear baseline hazard for outcome $j$, captured
-by dummies and the associated coefficients,
-\begin{equation}
-D_j(t) = \gamma_{j1} D_1 + \gamma_{j2} D_2 + \ldots + \gamma_{jT} D_T,
-\end{equation}
-with $D_m = 1$ if $t=m$ and zero otherwise.
-This approach to modeling the baseline hazard is flexible and does not place 
-overly strong restrictions on the baseline hazard.
-
-The explanatory variables in $\mathbf{Z}$, and the interactions between them, 
-constitute the nonproportional part of the model, which means that they are
-interacted with the baseline hazard:
-\begin{equation}
- \mathbf{Z}_{it} = D_j(t) \times (\mathbf{Z}_1 + Z_2 + \mathbf{Z}_1 \times Z_2),
-\end{equation}
-where $D_j(t)$ is the piece-wise linear baseline hazard, $\mathbf{Z}_1$ captures sex 
-composition of previous children, if any, and $Z_2$ captures area of residence.
-The remaining explanatory variables, $\mathbf{X}$, enter proportionally,
-but to further minimize any potential bias from assuming proportionality, estimations 
-are done separately for different levels of mothers' education and different 
-periods.
-
-Equation (\ref{eq:hazard_appendix}) is equivalent to the logistic hazard model and has the same 
-likelihood function as the multinomial logit model \citep{allison82,jenkins95}.
-Hence, transforming the data, so each observation is an interval---here equal
-to three months---the model can be estimated using a standard multinomial logit model.
-
-The distribution of spacing is captured by the survival curve, which shows the probability 
-of not having had a birth yet by spell duration, for a given set of explanatory variables.
-The survival curve at time $t$ is 
-\begin{equation}
-\label{eq:survival}
-S_{t} 
-= 
-\prod_{d=1}^t
-\left(
-\frac{ 1 }
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{ld}'\mathbf{Z}_{kd} + \beta_l'\mathbf{X}_{k})}
-\right).
-\end{equation}
-
-% Because the probability of ever having a next birth varies across groups, a direct 
-% comparison of standard survival curves tells us little about how the spread of sex 
-% selection affects birth spacing across groups.
-% I, therefore, condition on the predicted likelihood of parity progression when examining 
-% birth spacing measures, such as the average duration to a birth.
-% The reliability of this approach depends on whether the spell length covered is 
-% sufficiently long that few women are likely to give birth after the spell cut-off.
-% I discuss the choice of spell length below.%
-% \footnote{
-% It is important to note that the approach is not the same as merely calculating 
-% the birth spacing measures for women who already have a given 
-% parity child in the survey because that number does not take into account
-% the censoring of spells that will eventually lead to a birth.
-% }
-% In addition, I present graphs of survival curves conditional on parity progression,
-% which therefore begin at 100\% and end at 0\%.
-
-Interpretation of the model coefficients is challenging \citep{thomas96}.
-It is, however, possible to calculate the predicted probabilities of 
-having a boy, $b$, and of having a girl, $g$, in period $t$, conditional on 
-a set of explanatory variables and not having had a child before that period, as
-\begin{align}
-P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt}, t ) 
-& =  
-\frac{ \exp(D_j(t) + \alpha_{1t}' \mathbf{Z}_{kt} + \beta_1' \mathbf{X}_{k} )}
-{1 + \sum_{l=1}^2 \exp(D_j(t) + \alpha_{lt} ' \mathbf{Z}_{kt} + \beta_l ' \mathbf{X}_{k})}
-\label{eq:probability_boy} \\
-P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t ) 
-& =  
-\frac{ \exp(D_j(t) + \alpha_{2t}'\mathbf{Z}_{kt} + \beta_2'\mathbf{X}_{k} )}
-{1 + \sum_{l=2}^2 \exp(D_j(t) + \alpha_{lt}'\mathbf{Z}_{kt} + \beta_l'\mathbf{X}_{k})}
-\label{eq:probability_girl}
-\end{align}
-It is then straightforward to calculate the estimated percentage of children born that 
-are boys, $\hat{Y}$, at each $t$:  
-\begin{equation}
-\hat{Y}_t 
-= 
-\frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-\times 100.
-\label{eq:probability_son}
-\end{equation}
-Combining the percentage boys and the likelihood of exiting the spell 
-across all $t$ gives the predicted percent boys born over the entire spell.%
-\footnote{
-Imagine $T=2$. 
-If 54\% and 66\% of births are boys and the likelihood of giving birth 20\% and 40\%, 
-then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$\% boys. 
-}
-
-\clearpage
-\newpage
-
-\section{Recall Error and the Sex Ratio}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-The reliability of the results depends on the correctness of the birth histories
-provided by the respondents.
-A significant concern here is underreporting of child mortality, especially a systematic
-recall error where respondents' likelihood of reporting a deceased child depends on the 
-sex of that child. 
-This appendix section assesses the degree of recall error across the surveys and discusses 
-methods to address it.
-
-NFHS enumerators probe for any missed births, although the method depends on the survey.
-NFHS-1 probe for each calendar birth interval that is four or more years.
-NFHS-2 asked for stillbirths, spontaneous and induced abortions and also probed 
-for each calendar birth interval four or more years.
-NFHS-3 and NFHS-4 did not directly use birth interval lengths, but asked whether there were any 
-other live births between (name of previous birth) and (name), including any children who 
-died after birth, and asked for births before the birth listed as first birth and
-after the last birth listed as the last birth.
-
-Probing catches many initially missed births, but systematic recall error based on son
-preference may still be a problem.
-First, son preference leads to significantly higher mortality for girls than boys.
-Secondly, son preference makes it more likely that parents will remember deceased boys 
-than deceased girls.
-Finally, in the absence of sex-selective abortions, parents with a preference for sons may
-have the next birth sooner if the last child was a girl than if it was a boy.
-If this girl subsequently dies, she is more likely to be missed if probing for missed 
-births is only done for long intervals as in NFHS-1 and NFHS-2.
-
-I use two approaches to examine the degree of recall error.
-The first approach is to test whether the observed sex ratio is significantly different
-from the natural sex ratio.
-The natural sex ratio is approximately 105 boys to 100 girls or
-51.2\% \citep{jacobsen99,Portner2015b}.
-Prenatal sex determination techniques did not become widely available until the mid-1980s, 
-so any significant deviation from the natural sex ratio before that time is likely the 
-result of recall error.
-The second approach is to compare births that took place during the same period but
-where captured in different surveys.
-Recall error is likely to increase with time, so births and deaths that took place earlier 
-are more likely to be subject to recall error than more recent events.
-
-Table \ref{tab:recallBirthBO1} shows the sex ratios of children recorded as first-born by 
-year of birth, together with tests for whether the observed sex ratio is significantly 
-higher than the natural sex ratio and whether more recent surveys have a higher sex ratio 
-for the cohort than earlier surveys for the same period births.
-Births are combined into five-year cohorts to achieve sufficient power.
-
-\input{../tables/recallBirthBO1.tex}
-
-% \input{../tables/recallBirthBO2.tex}
-
-The ``first-born'' sex ratios illustrate the systematic recall error problem well.
-In all four surveys around 55\% of children reported as first-born are boys
-for the first cohort of births observed.
-Given that these cohorts cover from 1960-1964 to 1980-1984, which is before sex selection 
-techniques became available in India, the most likely explanation for the skewed sex ratio 
-is that some children listed as first-borns were not, in fact, the first children born in 
-their families.
-Instead, for a substantial proportion of families, their first-born was a girl who died 
-and went unreported when enumerators asked about birth history.
-
-As expected, the difference between the observed sex ratio and the natural sex ratio is 
-less pronounced the closer to the survey date the cohort is.
-The observed sex ratio for children born just before the NFHS-1 survey and listed as 
-first-born is 0.517, which is not statistically significantly different from the
-natural sex ratio.
-The same general pattern holds for the other three surveys, with cohorts further away
-from the survey date more likely to have a sex ratio skewed male.
-
-% Second births show a pattern very similar to that for first births.
-% An interesting difference is that there is evidence of a U-shaped relationship between
-% time and sex ratio for second births.
-% Cohorts furthest away from the survey year show the highest sex ratios, but declines to the
-% natural sex ratio in the mid-1980s, and the sex ratio is then significantly higher again 
-% for more recent births.
-% This is in line with the results in the main paper that show that sex selective abortions 
-% take place on lower parity births as desired fertility declined.
-
-Finally, across surveys, the same cohort tends to show a higher sex ratio the more recent 
-the survey (births in the cohort took place earlier relative to the survey date).
-Despite this, few cohorts show significantly different sex ratios across surveys, most 
-likely because of a lack of power.
-The exception is that comparisons involving NFHS-4 are mostly statistically significant
-since the number of surveyed households in NFHS-4 were much larger than in prior surveys.
-
-The problem with the above approach is that the year of birth is affected by recall error; 
-a second born child listed as first-born is born later than the real first born child.
-Year of marriage should, however, be affected neither by parental recall error 
-nor the use of sex-selective abortions.
-Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2}, therefore, shows sex 
-ratios of children recorded as first-born and second-born by year of parents' marriage, 
-together with tests for whether the observed sex ratio is significantly higher than the 
-natural sex ratio and whether more recent surveys show a higher sex ratio for the cohort 
-than earlier surveys.
-The basic recall error pattern remains, with women married longer ago more
-likely to report that their first-born is a boy.
-Similarly, comparing women married in the same five-year period across surveys shows
-that women married longer ago are more likely to report having a son.
-
-\input{../tables/recallMarriageBO1.tex}
-
-\input{../tables/recallMarriageBO2.tex}
-
-The relationship between the length of marriage and recall error can also be seen in 
-Figures \ref{fig:sex_ratio_recall_rounds_bo1} and \ref{fig:sex_ratio_recall_rounds_bo2}, 
-which show the observed sex ratio for children reported as first born as a function of 
-the duration of marriage at the time of the survey.
-The solid line is the sex ratio of children reported as first-born by the number of years 
-between the survey and marriage, while the dashed lines indicate the 95\% confidence 
-interval and the horizontal line the natural sex ratio (approximately 0.512).
-To ensure sufficient cell sizes I group years into twos.
-In line with the results from Tables \ref{tab:recallMarriageBO1} and 
-\ref{tab:recallMarriageBO2}, the observed ratio of boys is increasingly above the expected 
-value the longer ago the parents were married.
-
-\begin{figure}
-\centering
-\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1}}
-\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2}} \\
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
-\subfloat[NFHS-4]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
-\caption{Ratio of Boys for ``First'' Births by Survey Round}
-\label{fig:sex_ratio_recall_rounds_bo1}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1_bo2}}
-\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2_bo2}} \\
-\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3_bo2}} 
-\subfloat[NFHS-4]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4_bo2}} 
-\caption{Ratio of Boys for ``Second'' Births by Survey Round}
-\label{fig:sex_ratio_recall_rounds_bo2}
-\end{figure}
-
-The increasingly unequal sex ratio with increasing marriage duration suggests that
-a solution to the recall error problem is to drop observations for 
-women who were married ``too far'' from the survey year.
-The main problem is establishing what the best cut-off point should be, with the
-trade-off between retaining enough observations and the correctness of the information.
-As Tables \ref{tab:recallMarriageBO1} and \ref{tab:recallMarriageBO2} show, there are 
-differences in recall error across the three surveys and between the two birth
-orders, although this may be the result of differences in the number of observations 
-across surveys.
-Furthermore, the recall error pattern is not entirely consistent across observed birth 
-orders.
-Since most of the surveys start showing significantly biased sex ratio from around 22
-years of marriage on, I drop all observations where the marriage took place 22 years
-or more.
-
-\clearpage
-\newpage
-
-\section{Descriptive Statistics}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-% Descriptive statistics tables
-\input{../tables/des_stat.tex}
-
-\clearpage
-\newpage
-
-\section{Additional Results Figures and  Tables}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\captionsetup[figure]{skip = -16pt}
-
-Figures \ref{fig:spacing_low_urban} and \ref{fig:spacing_highest_rural} show 25th, 50th,
-and 75th percentile birth interval lengths, the sex ratio, and the probability of parity
-progression by spell for urban women with no education and rural women with 12 or
-more years of education, respectively.
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
-\caption{Percentile birth interval lengths, sex ratios, and parity progression  
-for urban women with no education by spell, sex composition, and period}
-\label{fig:spacing_low_urban}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
-\caption{Percentile birth interval lengths, sex ratios, and parity progression  
-for rural women with 12 or more years of education by spell, sex composition, and period}
-\label{fig:spacing_highest_rural}
-\end{figure}
-
-The first set of tables, Tables \ref{tab:p25_p50_p75_low}, \ref{tab:p25_p50_p75_med},
-\ref{tab:p25_p50_p75_high}, and \ref{tab:p25_p50_p75_highest} show 25th, 50th, and
-75th percentile birth interval lengths together with their standard errors.
-The standard errors for all measures are based on bootstrapping,
-where the model is repeatedly estimated using resampling with replacement.
-
-The second set of tables, 
-Tables \ref{tab:avg_sex_ratio_low}, \ref{tab:avg_sex_ratio_med}, 
-\ref{tab:avg_sex_ratio_high}, and \ref{tab:avg_sex_ratio_highest}, show predicted average 
-birth interval lengths, sex ratios, and probabilities of having a birth by decade, spell, and sex 
-composition for the four education levels separated by the area of residence, together 
-with bootstrapped standard errors for all three outcomes.
-To find the average birth interval length, I calculate, for each woman, the probability of 
-giving birth in each $t$, and her expected spell length from these probabilities. 
-I then average the individual expected spell lengths across women using their parity 
-progression probabilities as weights. Finally, I add nine months because spells begin 
-nine months after the previous birth.
-
-I also show whether durations for sex composition other than only girls are statistically 
-significantly different from the duration with only girls based on bootstrapped 
-differences. 
-The cleanest test is comparing durations after only boys with durations after
-only girls, but the number of births to women with only sons becomes small 
-in the later periods.
-Hence, it is possible to have substantial differences in spacing that are
-not statistically significant because of low power, especially for the third 
-and fourth spell.
-
-Each predicted percent of boys is tested against the natural percentage of
-boys using the bootstrapped standard errors.
-The natural sex ratio is approximately 105 boys to 100 girls or
-51.2\% \citep{jacobsen99,Portner2015b}.
-The predicted percentage boys may differ from the natural rate because of 
-natural variation, any remaining recall error not corrected for, or 
-sex selection.
-
-\input{../tables/bootstrap_duration_p25_p75_low_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_med_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_high_all.tex}
-
-\input{../tables/bootstrap_duration_p25_p75_highest_all.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_low_all.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_med_all.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_high_all.tex}
-
-\input{../tables/bootstrap_duration_avg_sex_ratio_highest_all.tex}
-
-\clearpage
-\newpage
-
-\section{Infant Mortality Graphs}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_low_med}
-\caption{Infant mortality by preceding birth interval length across periods for third child of women with 
-no education and women with 1--7 years of education}
-\label{fig:mortality_low_med_spell_3}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{mortality_spell_3_high_highest}
-\caption{Infant mortality by preceding birth interval length across periods for third child of women with 
-8--11 and 12 and above years of education}
-\label{fig:mortality_high_highest_spell_3}
-\end{figure}
-
 \end{document}

### 2022-03-13 paper/sex_selection_spacing-final.tex
Ensure final version can be found by Make

@@
 \thispagestyle{empty}
-
-% \setcounter{page}{0}
 
@@
 
-% For word counting remove comment on the line below
-% \raggedright
-
-% Background
 India has experienced many positive changes over the past four decades:
@@
 
-% Questions addressed and why valuable
 The main question I address here is how birth spacing responded to these changes, 
@@
 
-% How the study progresses
 To investigate how birth spacing has changed, I use a competing risk hazard model with 
@@
 
-% Main results
 There are three main results.
@@
 
-% Economic conditions
 The improvements in economic condition, especially the doubling of real wages,
@@
 
-% Investment in children
 With increasing returns to education and lower offspring mortality, parents are likely to 
@@
 
-% Son preference 
 Stronger son preference has traditionally been associated with shorter spacing and worse
@@
 
-% Factors/predictions
 The closest available proxies in the data for capturing the explanations linking
@@
 
-% Sanskritization
 Finally, the process of "Sanskritization" implies that as lower-caste females gain access
@@
 
-% Summary / hypotheses
 In summary, with substantial increases in husbands' income and a declining female labor 
@@
 \section{Estimation Strategy\label{sec:strategy}}
-
-% Requirements for method and the intuition behind each:  
-%  - Account for censoring (hazard model)
-%  - Work both with and without sex selection (competing risk part)
-%  - Allow for changes in use of sex selection within spell (flexible specification of baseline hazard ?)
-%  - Capture that the shape of the hazard function differ across groups
-%    (nonproportionality); needs a better description, maybe using example
-%    of shorter spacing and/or use of sex selection. Differences in parity
-%    progression likelihood.
 
@@
 
-% To further minimize any potential bias from assuming proportionality, estimations 
-% are done separately for different levels of mothers' education and different periods.
-% I discuss the choice of which variables to use for nonproportionality below.
-
 Equation \ref{eq:hazard} is equivalent to the logistic hazard model and has the same 
@@
 logit model.
-% In the reorganized data, the outcome variable is 0 if the woman does not have a child 
-% in a given interval (the base outcome), 1 if she gives birth to a son in that interval, 
-% and 2 if she gives birth to a daughter in that interval.
 
@@
 For example, with an 80\% parity progression probability, the median birth interval 
-is the predicted number of months before a woman passes the 60\% $(100-\frac{80}{2})$ 
+is the predicted number of months before a woman passes the 60\% $\left(100-\frac{80}{2}\right)$ 
 mark on her survival curve. 
@@
 a given sample using the individual progression probabilities as weights.
-
-% The predicted sex ratio is the weighted average of individual predicted sex ratios, using 
-% parity progression probabilities as weights.
-% For an individual woman, the estimated percent of births that are boys at $t$, $\hat{Y_t}$, is:  
-% \begin{equation}
-% \hat{Y}_t 
-% = 
-% \frac{ P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )}
-% { P(b_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t) + P(g_{t} | \mathbf{X}_{k}, \mathbf{Z}_{kt},t )} 
-% \times 100,
-% \label{eq:probability_son}
-% \end{equation}
-% where $b$ and $g$ are the predicted probabilities of having a boy and a girl, respectively,
-% conditional on the explanatory variables and not having had a child before $t$.
-% Weighting the percentages boys with the likelihood of exiting the spell with a birth across all 
-% $t$ gives the predicted percent of boys over the entire spell for an individual.%
-% \footnote{
-% Imagine $T=2$. 
-% If 54 and 66 percent of births are boys and the likelihood of giving birth 20 and 40 percent, 
-% then the predicted sex ratio is $\frac{54*0.2+66*0.4}{0.2+0.4} = 62$ percent boys. 
-% }
 
@@
 The final sample consists of 
-\input{../tables/num_women.tex}
-% [number] women, with [number] parity one through four births.
-
-% %
-% \footnote{
-% \input{../tables/num_missed.tex}
-% }
+\input{./tables/num_women.tex}
 
@@
 \footnote{
-% Details about the act are at \href{http://pndt.gov.in/}{http://pndt.gov.in/}.
 There is little evidence that the ban significantly affected sex ratios \citep{Das-Gupta2019}.
@@
 land ownership, and whether it belongs to a scheduled tribe or caste.
-Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present the descriptive 
-statistics.
+The online appendix present the descriptive statistics.
 
@@
 
-% Explain question and what I am doing
 The first question I address is how birth spacing responded to the significant 
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_low_urban}
-% \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for urban women with no education by spell, sex composition, and period}
-% \label{fig:spacing_low_urban}
-% \end{figure}
-
 \begin{figure}
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{bs_highest_rural}
-% \caption{Percentile birth intervals, sex ratios, and parity progression  
-% for rural women with 12 or more years of education by spell, sex composition, and period}
-% \label{fig:spacing_highest_rural}
-% \end{figure}
-
 \begin{figure}
@@
 
-% [Parity progression probability]
 The parity progression and the sex ratio show two broad trends.
@@
 
-% [Sex ratios]
 Second, sex ratios have become more male-dominated for women with no sons, indicating the spread 
@@
 
-% [25th percentile birth intervals]
 A remarkably high proportion of birth intervals are still very short.
@@
 
-% [median birth intervals]
 Median birth interval lengths have also increased relatively little---only three to six months 
@@
 
-% [75th percentile birth intervals]
 The most substantial changes occurred in the 75th percentile birth interval durations, 
@@
 interval increased by only slightly more than two months.
-
-%0.637 0.241
 
@@
 
-% [Birth intervals with sex selection]
 \subsection{Sex Selection and Birth Spacing}
@@
 
-\input{../tables/fertility.tex}
+\input{./tables/fertility.tex}
 
@@
 Hence, the presented fertility rates are not directly comparable to those in the NFHS reports.
-
-%
-% \footnote{
-% See \citet{Croft2018} for more detail.
-% Because NFHS-1 and NFHS-2 did not interview all women about fertility, the number of women 
-% is based on the household rosters, assuming that never-married women have had no children.
-% Because of the low number of births to women aged 45 to 49 this age group was not
-% used for the hazard model estimations and, therefore, is also excluded for the fertility
-% rate.
-% The marital total fertility rate lead to unrealistically high numbers and is, therefore,
-% not presented \citep{Hoem2011,Laplante2015}.
-% }
 
@@
 
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \setcounter{subfigure}{-1}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[No Eduction]{\includegraphics[width=\textwidth]{mortality_s2_p1_low_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \setcounter{subfigure}{-0} 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[One to Seven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_low_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Second Child's Infant Mortality 
-% for Women with No Education
-% and Women with One to Seven Years of Education}
-% \label{fig:mortality_low_med}
-% \end{figure}
-
-% \begin{figure}[htpb]
-% \centering
-% \rotatebox[origin=c]{90}{\small{1972-1984}}
-% \setcounter{subfigure}{-1}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \captionsetup[subfigure]{font=footnotesize,labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
-%         \subfloat[Eight to Eleven Years of Education]{\includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}}
-%         \captionsetup[subfigure]{labelformat=parens}
-%     \end{minipage}
-% }
-% \begin{minipage}[t]{0.39\textwidth}\vspace{-2.68cm}\centering\footnotesize{Twelve or More Years of Education}\end{minipage}
-% \\
-% \rotatebox[origin=c]{90}{\small{1985-1994}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{1995-2004}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies} 
-%     \end{minipage}
-% } 
-% \\
-% \rotatebox[origin=c]{90}{\small{2005-2016}}
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
-%     \end{minipage}
-% } 
-% \subfloat[Second Spell]{
-%     \begin{minipage}{0.37\textwidth}
-%         \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies} 
-%     \end{minipage}
-% } 
-% \caption{Predicted Probability of Second Child's Infant Mortality 
-% for Women with Eight to Eleven of Education
-% and Women with Twelve or More Years of Education}
-% \label{fig:mortality_high_highest}
-% \end{figure}
-
 \begin{figure}
@@
 
-% Background
 Over the past four decades, India saw a dramatic increase in the male-to-female
@@
 
-% Questions
 The main question I address in this paper is how birth spacing responded to the 
@@
 
-% What has happened to spacing and why
 The most substantial lengthening of birth intervals occurred among the best-educated women,
@@
 
-% [predictions of declining sex selection] 
 Despite predictions that the use of sex selection would decline, there is no clear 
@@
 that sex selection use appears to be spreading as fertility falls.
-
-% fertility bias
 
@@
 
-% Mortality
 There has been a substantial reduction in infant mortality over time, and the size of the 
@@
 
-% Implications 
 The results here paint a less rosy picture of India's prospects for a continued reduction 
@@
 reduction in population growth.
-
-% Future research and policy
 
@@
 
-% The higher return to male offspring's human capital combined with access to sex
-% selection may also explain another puzzle, why is the labor force participation so
-% low when fertility is low and education has increased.
-% As shown here, part of the answer may be that the number of children is, in fact, not as 
-% low as previously thought, both because of the increased spacing and that more 
-% children survive.
-
 \clearpage
